### 2022-05-30 transitions/housing_mice.Rmd
adding clm model for housing and a lot of minor tweaks. needs pushing.

---
title: "Housing mice Notebook"
output: html_notebook
---

This notebook demonstrates how multiple imputation is applied to the household variables for application in MINOS transition probability models. It goes into visualisation of missingness structure for the six household variables and what variables are influential in them being missing. A MICE pipeline is constructed demostrating any differences between complete case and imputed demographics. First load in US data and some packages..

```{r}
source("utils.R") # for data formatting functions and other useful globals. 
require(VIM) # for missingness visualisation.
require(mice) # for mice multiple imputation.
require(lattice) # for mice imputation functions.
require(ordinal) # for clm models.
require(tidyr) # for data frame formatting.
require(viridis) # for python's nice colour palettes

# load data from 2011 and format it via utils.R functions. 
data_source<- "data/corrected_US/"
years <- c("2011")
file_names <- get_US_file_names(data_source, years)
data <- get_US_data(file_names)
data <- format_US_housing_data(data)

n_heating_missing <- nrow(data) - sum(complete.cases(data[,c("heating")]))
n_five_missing <- nrow(data) - sum(complete.cases(data[,c("fridge_freezer", "washing_machine", "tumble_dryer", "dishwasher", "microwave")]))
n_six_missing <- nrow(data) - sum(complete.cases(data[,c("fridge_freezer", "washing_machine", "tumble_dryer", "dishwasher", "microwave", "heating")]))
household_vars = c("fridge_freezer",
                   "washing_machine",
                   "tumble_dryer",
                   "dishwasher",
                   "microwave",
                   "heating")
```

Data description demonstrates the six SIPHER7 household variables as well as other variables used in imputation that may indicate missingness. To more clearly demonstrate missingness structure first use aggr plots from VIM.

```{r}
a <- aggr(data, cex.axis=.5, oma=c(5,2,2,5),numbers=T, cex.numbers=0.5) # cex and oma adjustments so all labels show up.

b <- aggr(data[, household_vars], numbers=T, cex.axis=.5, oma=c(5,2,2,5))
```

There are 40197 out of 134598 (29.9%) rows missing at least one of the six household variables. The vast majority 38757 (28.8%) are missing solely heating values. 1440 (1.07%) are missing 5/6 composite variables simultaneously with 621 (0.46%) missing all 6.

Since 5 household variables are simultaneous missing it is worth compositing them together and imputing them as one variable https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3074241/pdf/MPR-20-40.pdf. Heating will be imputed separately and then the two variables will be merged into one final SIPHER7 value.

The next part of the imputation strategy is which variables to include in analysis. It is suggested to have an imputation dataset larger than any dataset used in transition probability calibration ensuring any variable that may be indicative of missingness. VIM and MICE packages have good visualisation tools to represent this. These tools quantify distributional differences of variables between those missing houshold values and those not.

```{r}
is_missing_heating <- is.na(data$heating)
is_missing_five <- is.na(data$fridge_freezer)
histogram(~age|is_missing_heating, data)
histogram(~age|is_missing_five, data)
histogram(~SF.12|is_missing_heating, data)
histogram(~SF.12|is_missing_five, data)
```

```{r}
# needs better scaling for low % missing data
# scaling works with ylim change but ticks needs relabelling. 
#spineMiss(data[, c("job_sec", "heating")], col = c(blue, orange), ylim=c(0, 0.2))
#spineMiss(data[, c("job_sec", "fridge_freezer")], col = c(blue, orange), )

missing_barchart <- function(data, v1, v2){
  print(v1)
  print(v2)
  missing_table <- table(data[,v1], is.na(data[,v2]))
  # not guaranteed to be on these rows. needs forcing to correct labels somehow. 
  missing_percent <- missing_table[,2]/(missing_table[,1]+missing_table[,2])
  barchart(missing_percent, ylab = v1)
}
missing_barchart(data, "ethnicity", "heating")
```

```{r}
missing_barchart(data, "ethnicity", "heating")
missing_barchart(data, "depression_change", "heating")
missing_barchart(data, "education_state", "heating")
missing_barchart(data, "labour_state", "heating")
missing_barchart(data, "sex", "heating")
missing_barchart(data, "job_sec", "heating")

```

Can apply these plots to all variables used in imputation of heating and five others respectively.

```{r}
imp_columns <- c("five_household", "heating", "labour_state", "education_state",
                 "sex", "job_sec", "ethnicity", "age", "SF.12")
house_mice <- mice(data = data[,imp_columns],
                 m = 20, maxit = 20, seed = 500,
                 remove.collinear=T)
```

```{r}
print(summary(complete(house_mice)[,c("five_household","heating")]))
plot(house_mice)
```

```{r}
data2<- complete(house_mice)
data2 <- tidyr::drop_na(data2)
# format final housing composite. If they have no appliances assign 0.
# any up to 5 assign 1.
# all assign 2.
data2$housing <- rowSums(data2[, c("five_household", "heating")])
data2[which(data2$housing <= 3), "housing"] <- 0
data2[which(data2$housing <= 4 & data2$housing > 3), "housing"] <- 1
data2[which(data2$housing >= 5), "housing"] <- 2

data2$housing <- factor(data2$housing, levels = c(0,1,2))
n <- nrow(data2)
set.seed(88)
Inx <- sample(n, 0.8*n)
train<-data2[Inx,]
test<-data2[-Inx,]
y <- test$housing
test <- subset(test, select= - housing)

formula <- "housing ~ factor(sex) + 
                      age + 
                      SF.12 + 
                      factor(labour_state) +
                      factor(job_sec)"
housing.clmm <- clm(housing ~ factor(sex) + 
                                age + 
                                SF.12 + 
                                factor(labour_state) +
                                factor(job_sec) +
                                factor(ethnicity), 
                                data= train[complete.cases(train),],
                                link = "logit",
                                threshold = "flexible",
                                Hess=T)

print(summary(housing.clmm))
prs<- 1 - logLik(housing.clmm)/logLik(clm2(housing ~ 1,data= train))
print(prs)
```

```{r}
# remove housing column or predict function doesnt give full multinom probabilities.

preds <- predict(housing.clmm, test)$fit
markers <-as.numeric(as.character(factor(y, labels = c(0, 10, 25))))
markers <- as.integer(markers)
colours <-cividis(3)
v_colours <- factor(y, labels = cividis(3))

table(y, predict(housing.clmm, test, type="class")$fit)

test2<-test
test2$housing <- y
#par(mfrow(c(2,1)))
plot(predict(housing.clmm, test2, type="linear.predictor")$eta2, ylim=c(-10, 10)
, col=v_colours, pch=markers)
plot(predict(housing.clmm, test2, type="linear.predictor")$eta2, ylim=c(-100005, -99995)
, col=v_colours, pch=markers)
legend("topright", legend=c("None", "Some", "All"), col = colours, pch =c(0, 10, 25))

w1 <- which(y == 0)
plot(preds[w1, 1], col =  colours[1], pch=0)#dev.off()

w2 <- which(y == 1)
plot(preds[w2, 2], col =  colours[2], pch=10)#dev.off()

w3 <- which(y == 2)
plot(preds[w3, 3], col =  colours[3], pch=25)#dev.off()

```

### 2022-05-30 minos/utils.py

@@ -8,6 +8,8 @@ import yaml
 import numpy as np
 import os
 import pandas as pd
+import datetime
+
 #import humanleague as hl
 from scipy.sparse import coo_matrix
 import scipy
@@ -230,3 +232,6 @@ def get_age_bucket(simulation_data):
 def to_years(time: pd.Timedelta) -> float:
     """Converts a time delta to a float for years."""
     return time / pd.Timedelta(days=DAYS_PER_YEAR)
+
+def get_time():
+    print(datetime.datetime.now().strftime("%Y-%m-%d %H:%M:%S"))

### 2022-06-29 minos/transitions/housing/housing_mice.Rmd
add mwb framework. need to get ols model working now.

--- 2022-05-30 transitions/housing_mice.Rmd
@@
 require(viridis) # for python's nice colour palettes
+require(ggplot2) # for confusion matrix plots
+#require(dplyr) # matrix manipulation
+require(stringr)# for fancy wrapped text in confusion matrix axis labels
+require(shadowtext) #^
 
@@
 imp_columns <- c("five_household", "heating", "labour_state", "education_state",
-                 "sex", "job_sec", "ethnicity", "age", "SF.12")
-house_mice <- mice(data = data[,imp_columns],
-                 m = 20, maxit = 20, seed = 500,
+                 "sex", "job_sec", "ethnicity", "age", "SF.12", "hh_netinc")
+house_mice <- mice(data = data[, imp_columns],
+                 m = 10, maxit = 10, seed = 500,
                  remove.collinear=T)
@@
 data2$housing <- rowSums(data2[, c("five_household", "heating")])
-data2[which(data2$housing <= 3), "housing"] <- 0
-data2[which(data2$housing <= 4 & data2$housing > 3), "housing"] <- 1
-data2[which(data2$housing >= 5), "housing"] <- 2
+data2[which(data2$housing <= 0), "housing"] <- 0
+data2[which(data2$housing <= 5 & data2$housing > 1), "housing"] <- 1
+data2[which(data2$housing >= 6), "housing"] <- 2
 
@@
                       factor(job_sec)"
-housing.clmm <- clm(housing ~ factor(sex) + 
+housing.clmm <- clm(housing ~ (factor(sex) + 
+                                factor(education_state) + 
                                 age + 
@@
                                 factor(job_sec) +
-                                factor(ethnicity), 
+                                factor(ethnicity) + hh_netinc)**2, 
                                 data= train[complete.cases(train),],
@@
 ```
+
+```{r}
+confusion.matrix<- table(y, predict(housing.clmm, test, type="class")$fit)
+group_pops<-rowSums(confusion.matrix)
+confusion.frame <- as.data.frame(confusion.matrix/group_pops) # convert to data frame
+confusion.frame$Freq <-round(confusion.frame$Freq, 3) # round to 2dp
+row_names <- paste0(rownames(confusion.matrix), " [")
+row_names <- paste0(row_names,  as.character(group_pops))
+row_names <- paste0(row_names, "]")
+row_names <- str_wrap(row_names, width = 12)
+col_names <- str_wrap(colnames(confusion.matrix), 10)
+
+confusion.plot<- ggplot(confusion.frame, aes(Var2, rev(y), fill= Freq)) +
+  scale_fill_viridis_c("% of state")+
+  geom_tile() + 
+  geom_shadowtext(aes(label=Freq)) +
+  #scale_fill_gradient(high="#87ceeb", low="#e34234") +
+  labs(y = "True State [population in state]",x = "Predicted State (no units)") + 
+  scale_y_discrete(labels=rev(row_names)) + # label axes
+  scale_x_discrete(labels=col_names)
+print(confusion.plot)
+```

### 2022-06-29 minos/modules/housing.py

@@ -151,7 +151,7 @@ class Housing:
         """
         # load transition model based on year.
         year = min(self.year, 2018)
-        transition_model = r_utils.load_transitions(f"transitions/housing/clm_output/{year}_{year+1}_housing_clm", "")
+        transition_model = r_utils.load_transitions(f"data/transitions/housing/clm/{year}_{year+1}_housing_clm", "")
         # returns probability matrix (3xn) of next ordinal state.
         prob_df = r_utils.predict_next_timestep_clm(transition_model, pop)
         return prob_df
@@ -160,7 +160,6 @@ class Housing:
     @property
     def name(self):
         return 'housing'
-
 
     def __repr__(self):
         return "Housing()"

### 2022-12-15 docsrc/Coefficients/summarise_transitions_2.Rmd
attempting a workaround for ugly notebooks using Rmd>tex>rst conversion

---
title: "MINOS Transition Models"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# Setup

## Tobacco

Tobacco consumption is measured in the usual number of cigarettes smoked per day, and is taken directly from a US variable ([ncigs](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/ncigs)).

We estimated a zero inflated poisson model, with the formula:

> ncigs \~ age + sex + SF_12 + labour_state + job_sec + ethnicity + hh_income \| ethnicity + labour_state + SF_12

```{r}
require(tidyverse)
require(pscl)

workingDir <- "../.." #TODO stored in docsrc/Coefficients for now. move to data/transitions and change rst filepaths accordingly.
knitr::opts_knit$set(root.dir = workingDir)
trans.path <- paste0(workingDir,'/data/transitions/test/')
tobacco <- readRDS(paste0(trans.path, 'tobacco_zip_2018_2019.rds'))
summary(tobacco)
```

### 2022-12-15 docsrc/Coefficients/summarise_transitions_2.tex
attempting a workaround for ugly notebooks using Rmd>tex>rst conversion

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={MINOS Transition Models},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{MINOS Transition Models}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\hypertarget{setup}{%
\section{Setup}\label{setup}}

\hypertarget{tobacco}{%
\subsection{Tobacco}\label{tobacco}}

Tobacco consumption is measured in the usual number of cigarettes smoked
per day, and is taken directly from a US variable
(\href{https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/ncigs}{ncigs}).

We estimated a zero inflated poisson model, with the formula:

\begin{quote}
ncigs \textasciitilde{} age + sex + SF\_12 + labour\_state + job\_sec +
ethnicity + hh\_income \textbar{} ethnicity + labour\_state + SF\_12
\end{quote}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{require}\NormalTok{(tidyverse)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Loading required package: tidyverse
\end{verbatim}

\begin{verbatim}
## -- Attaching packages --------------------------------------- tidyverse 1.3.2 --
## v ggplot2 3.3.6      v purrr   0.3.4 
## v tibble  3.1.8      v dplyr   1.0.10
## v tidyr   1.2.0      v stringr 1.4.0 
## v readr   2.1.2      v forcats 0.5.1 
## -- Conflicts ------------------------------------------ tidyverse_conflicts() --
## x dplyr::filter() masks stats::filter()
## x dplyr::lag()    masks stats::lag()
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{require}\NormalTok{(pscl)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Loading required package: pscl
## Classes and Methods for R developed in the
## Political Science Computational Laboratory
## Department of Political Science
## Stanford University
## Simon Jackman
## hurdle and zeroinfl functions by Achim Zeileis
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{workingDir }\OtherTok{\textless{}{-}} \StringTok{"../.."} \CommentTok{\#TODO stored in docsrc/Coefficients for now. move to data/transitions and change rst filepaths accordingly.}
\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_knit}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{root.dir =}\NormalTok{ workingDir)}
\NormalTok{trans.path }\OtherTok{\textless{}{-}} \FunctionTok{paste0}\NormalTok{(workingDir,}\StringTok{\textquotesingle{}/data/transitions/test/\textquotesingle{}}\NormalTok{)}
\NormalTok{tobacco }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(trans.path, }\StringTok{\textquotesingle{}tobacco\_zip\_2018\_2019.rds\textquotesingle{}}\NormalTok{))}
\FunctionTok{summary}\NormalTok{(tobacco)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## zeroinfl(formula = y ~ factor(sex) + scale(age) + scale(SF_12) + factor(labour_state) | 
##     relevel(factor(ethnicity), ref = "WBI") + scale(age), data = data, 
##     dist = "pois")
## 
## Pearson residuals:
##      Min       1Q   Median       3Q      Max 
## -1.75024 -0.76329 -0.05563  0.58683 17.88004 
## 
## Count model coefficients (poisson with log link):
##                                      Estimate Std. Error z value Pr(>|z|)    
## (Intercept)                          1.158187   0.024071  48.116  < 2e-16 ***
## factor(sex)Male                      0.106336   0.025077   4.240 2.23e-05 ***
## scale(age)                           0.107561   0.017073   6.300 2.97e-10 ***
## scale(SF_12)                        -0.029366   0.013324  -2.204 0.027518 *  
## factor(labour_state)Family Care      0.207191   0.057175   3.624 0.000290 ***
## factor(labour_state)Maternity Leave -0.302883   0.501065  -0.604 0.545525    
## factor(labour_state)PT Employed      0.039547   0.044232   0.894 0.371273    
## factor(labour_state)Retired         -0.028738   0.042805  -0.671 0.501989    
## factor(labour_state)Self-employed    0.006792   0.047900   0.142 0.887239    
## factor(labour_state)Sick/Disabled    0.107874   0.044940   2.400 0.016377 *  
## factor(labour_state)Student         -0.391335   0.101514  -3.855 0.000116 ***
## factor(labour_state)Unemployed       0.052690   0.047488   1.110 0.267196    
## 
## Zero-inflation model coefficients (binomial with logit link):
##                                             Estimate Std. Error z value
## (Intercept)                                 -1.74690    0.06856 -25.480
## relevel(factor(ethnicity), ref = "WBI")BAN  -0.14975    0.51269  -0.292
## relevel(factor(ethnicity), ref = "WBI")BLA  -0.65053    0.86881  -0.749
## relevel(factor(ethnicity), ref = "WBI")BLC   0.31791    0.40897   0.777
## relevel(factor(ethnicity), ref = "WBI")CHI   1.51817    0.70312   2.159
## relevel(factor(ethnicity), ref = "WBI")IND   0.52296    0.36411   1.436
## relevel(factor(ethnicity), ref = "WBI")MIX   0.20122    0.35581   0.566
## relevel(factor(ethnicity), ref = "WBI")OAS   0.93407    0.60401   1.546
## relevel(factor(ethnicity), ref = "WBI")OBL -13.01639  538.48954  -0.024
## relevel(factor(ethnicity), ref = "WBI")OTH  -0.19411    0.99293  -0.195
## relevel(factor(ethnicity), ref = "WBI")PAK   0.03483    0.37297   0.093
## relevel(factor(ethnicity), ref = "WBI")WHO  -0.17955    0.31947  -0.562
## scale(age)                                  -0.31921    0.06479  -4.927
##                                            Pr(>|z|)    
## (Intercept)                                 < 2e-16 ***
## relevel(factor(ethnicity), ref = "WBI")BAN   0.7702    
## relevel(factor(ethnicity), ref = "WBI")BLA   0.4540    
## relevel(factor(ethnicity), ref = "WBI")BLC   0.4370    
## relevel(factor(ethnicity), ref = "WBI")CHI   0.0308 *  
## relevel(factor(ethnicity), ref = "WBI")IND   0.1509    
## relevel(factor(ethnicity), ref = "WBI")MIX   0.5717    
## relevel(factor(ethnicity), ref = "WBI")OAS   0.1220    
## relevel(factor(ethnicity), ref = "WBI")OBL   0.9807    
## relevel(factor(ethnicity), ref = "WBI")OTH   0.8450    
## relevel(factor(ethnicity), ref = "WBI")PAK   0.9256    
## relevel(factor(ethnicity), ref = "WBI")WHO   0.5741    
## scale(age)                                 8.35e-07 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1 
## 
## Number of iterations in BFGS optimization: 30 
## Log-likelihood: -5657 on 25 Df
\end{verbatim}

\end{document}

### 2022-12-15 docsrc/conf.py

@@ -27,11 +27,13 @@ author = 'Robert Clay, Luke Archer, Hugh Rice, and Nik Lomax'
 # extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
 # ones.
 extensions = ['myst_parser',
-              'sphinx.ext.autodoc', # autodoc functionality for docs.
-              'sphinx.ext.napoleon', # convert numpy style docstrings to reST.
-              'sphinx.ext.githubpages', # Auto adds .nojekyll file to docs source. If using make clean its deleted so auto add it back on compile.
-              'sphinx.ext.viewcode', # should allow "view source" buttons in api to work.
-              'sphinxcontrib.bibtex' # allows for references from a .bib biblatex file.
+              'sphinx.ext.autodoc',  # autodoc functionality for docs.
+              'sphinx.ext.napoleon',  # convert numpy style docstrings to reST.
+              'sphinx.ext.githubpages',  # Auto adds .nojekyll file to docs source.
+              # If using make clean its deleted so auto add it back on compile.
+              'sphinx.ext.viewcode',  # should allow "view source" buttons in api to work.
+              'sphinxcontrib.bibtex',  # allows for references from a .bib biblatex file.
+              'nbsphinx',  # notebooks in sphinx.
 ]
 
 source_suffix = {
@@ -51,6 +53,12 @@ exclude_patterns = ['_build', 'Thumbs.db', '.DS_Store']
 # see for more bibtext details.
 # https://sphinxcontrib-bibtex.readthedocs.io/en/latest/usage.html
 bibtex_bibfiles = ['refs.bib']
+
+#
+#nbsphinx_custom_formats = {
+#    '.Rmd': ['jupytext.reads', {'fmt': 'Rmd'}],
+#}
+#nbsphinx_kernel_name = 'IRkernel'
 
 ##############################################################################
 # -- Options for HTML output -------------------------------------------------

### 2022-12-16 docsrc/Coefficients/summarise_transitions_2.tex
make html wider so it doesnt wrap
adjust Rmd width to prevent wrapping

@@
 
-\hypertarget{setup}{%
-\section{Setup}\label{setup}}
-
-\hypertarget{tobacco}{%
-\subsection{Tobacco}\label{tobacco}}
+\hypertarget{tobacco-coefficients}{%
+\section{Tobacco Coefficients}\label{tobacco-coefficients}}
 
@@
 \begin{Highlighting}[]
+\FunctionTok{options}\NormalTok{(}\AttributeTok{width=}\DecValTok{120}\NormalTok{)}
 \FunctionTok{require}\NormalTok{(tidyverse)}
@@
 \begin{verbatim}
-## -- Attaching packages --------------------------------------- tidyverse 1.3.2 --
+## -- Attaching packages ------------------------------------------------------------------------------- tidyverse 1.3.2 --
 ## v ggplot2 3.3.6      v purrr   0.3.4 
@@
 ## v readr   2.1.2      v forcats 0.5.1 
-## -- Conflicts ------------------------------------------ tidyverse_conflicts() --
+## -- Conflicts ---------------------------------------------------------------------------------- tidyverse_conflicts() --
 ## x dplyr::filter() masks stats::filter()
@@
 ## Call:
-## zeroinfl(formula = y ~ factor(sex) + scale(age) + scale(SF_12) + factor(labour_state) | 
-##     relevel(factor(ethnicity), ref = "WBI") + scale(age), data = data, 
-##     dist = "pois")
+## zeroinfl(formula = y ~ factor(sex) + scale(age) + scale(SF_12) + factor(labour_state) | relevel(factor(ethnicity), 
+##     ref = "WBI") + scale(age), data = data, dist = "pois")
 ## 
@@
 ## Zero-inflation model coefficients (binomial with logit link):
-##                                             Estimate Std. Error z value
-## (Intercept)                                 -1.74690    0.06856 -25.480
-## relevel(factor(ethnicity), ref = "WBI")BAN  -0.14975    0.51269  -0.292
-## relevel(factor(ethnicity), ref = "WBI")BLA  -0.65053    0.86881  -0.749
-## relevel(factor(ethnicity), ref = "WBI")BLC   0.31791    0.40897   0.777
-## relevel(factor(ethnicity), ref = "WBI")CHI   1.51817    0.70312   2.159
-## relevel(factor(ethnicity), ref = "WBI")IND   0.52296    0.36411   1.436
-## relevel(factor(ethnicity), ref = "WBI")MIX   0.20122    0.35581   0.566
-## relevel(factor(ethnicity), ref = "WBI")OAS   0.93407    0.60401   1.546
-## relevel(factor(ethnicity), ref = "WBI")OBL -13.01639  538.48954  -0.024
-## relevel(factor(ethnicity), ref = "WBI")OTH  -0.19411    0.99293  -0.195
-## relevel(factor(ethnicity), ref = "WBI")PAK   0.03483    0.37297   0.093
-## relevel(factor(ethnicity), ref = "WBI")WHO  -0.17955    0.31947  -0.562
-## scale(age)                                  -0.31921    0.06479  -4.927
-##                                            Pr(>|z|)    
-## (Intercept)                                 < 2e-16 ***
-## relevel(factor(ethnicity), ref = "WBI")BAN   0.7702    
-## relevel(factor(ethnicity), ref = "WBI")BLA   0.4540    
-## relevel(factor(ethnicity), ref = "WBI")BLC   0.4370    
-## relevel(factor(ethnicity), ref = "WBI")CHI   0.0308 *  
-## relevel(factor(ethnicity), ref = "WBI")IND   0.1509    
-## relevel(factor(ethnicity), ref = "WBI")MIX   0.5717    
-## relevel(factor(ethnicity), ref = "WBI")OAS   0.1220    
-## relevel(factor(ethnicity), ref = "WBI")OBL   0.9807    
-## relevel(factor(ethnicity), ref = "WBI")OTH   0.8450    
-## relevel(factor(ethnicity), ref = "WBI")PAK   0.9256    
-## relevel(factor(ethnicity), ref = "WBI")WHO   0.5741    
-## scale(age)                                 8.35e-07 ***
+##                                             Estimate Std. Error z value Pr(>|z|)    
+## (Intercept)                                 -1.74690    0.06856 -25.480  < 2e-16 ***
+## relevel(factor(ethnicity), ref = "WBI")BAN  -0.14975    0.51269  -0.292   0.7702    
+## relevel(factor(ethnicity), ref = "WBI")BLA  -0.65053    0.86881  -0.749   0.4540    
+## relevel(factor(ethnicity), ref = "WBI")BLC   0.31791    0.40897   0.777   0.4370    
+## relevel(factor(ethnicity), ref = "WBI")CHI   1.51817    0.70312   2.159   0.0308 *  
+## relevel(factor(ethnicity), ref = "WBI")IND   0.52296    0.36411   1.436   0.1509    
+## relevel(factor(ethnicity), ref = "WBI")MIX   0.20122    0.35581   0.566   0.5717    
+## relevel(factor(ethnicity), ref = "WBI")OAS   0.93407    0.60401   1.546   0.1220    
+## relevel(factor(ethnicity), ref = "WBI")OBL -13.01639  538.48954  -0.024   0.9807    
+## relevel(factor(ethnicity), ref = "WBI")OTH  -0.19411    0.99293  -0.195   0.8450    
+## relevel(factor(ethnicity), ref = "WBI")PAK   0.03483    0.37297   0.093   0.9256    
+## relevel(factor(ethnicity), ref = "WBI")WHO  -0.17955    0.31947  -0.562   0.5741    
+## scale(age)                                  -0.31921    0.06479  -4.927 8.35e-07 ***
 ## ---

### 2022-12-19 docsrc/Coefficients/summarise_transitions_2.tex
automate rendering of R notebooks into sphinx. Rmd references as well using pandoc.

@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={MINOS Transition Models},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={MINOS Transition Models},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
@@
 \begin{verbatim}
-## -- Attaching packages ------------------------------------------------------------------------------- tidyverse 1.3.2 --
+## -- Attaching packages ------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- tidyverse 1.3.2 --
 ## v ggplot2 3.3.6      v purrr   0.3.4 
@@
 ## v readr   2.1.2      v forcats 0.5.1 
-## -- Conflicts ---------------------------------------------------------------------------------- tidyverse_conflicts() --
+## -- Conflicts ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- tidyverse_conflicts() --
 ## x dplyr::filter() masks stats::filter()

### 2022-12-19 docsrc/documentation/notebooks/household_income.Rmd
automate rendering of R notebooks into sphinx. Rmd references as well using pandoc.

---
title: "Household_Income"
output: html_document
date: "2022-12-16"
bibliography: references.bib  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Household Income

## Data

## Methods

## Results

### 2022-12-19 docsrc/documentation/notebooks/summarise_transitions_2.Rmd
automate rendering of R notebooks into sphinx. Rmd references as well using pandoc.

--- 2022-12-15 docsrc/Coefficients/summarise_transitions_2.Rmd
@@
 title: "MINOS Transition Models"
-output:
-  pdf_document: default
-  html_document:
-    df_print: paged
+output: html_document
+bibliography: 
+  - "refs.bib"
 ---
 
-# Setup
-
-## Tobacco
+# Tobacco Coefficients
 
 Tobacco consumption is measured in the usual number of cigarettes smoked per day, and is taken directly from a US variable ([ncigs](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/ncigs)).
+
+Test references [@1987:nelson].
 
@@
 
-```{r}
+```{r tobacco_output}
+options(width=120)
 require(tidyverse)
@@
 
-workingDir <- "../.." #TODO stored in docsrc/Coefficients for now. move to data/transitions and change rst filepaths accordingly.
+workingDir <- "../../.." #TODO stored in docsrc/Coefficients for now. move to data/transitions and change rst filepaths accordingly.
 knitr::opts_knit$set(root.dir = workingDir)
@@
 ```
+
+References
+----------

### 2022-12-19 docsrc/documentation/notebooks/tobacco.Rmd
automate rendering of R notebooks into sphinx. Rmd references as well using pandoc.

---
title: "tobacco"
output: html_document
date: "2022-12-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2022-12-19 docsrc/documentation/notebooks/household_income.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

@@
 ---
-title: "Household_Income"
+title: "Household Income"
 output: html_document
-date: "2022-12-16"
-bibliography: references.bib  
+bibliography: 
+  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
+  #- "../../refs.bib"
 ---
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
 
@@
 
-## Data
+Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].
+
+```{r setup, include=FALSE}
+source('sphinx_notebook_utils.R')
+```
 
@@
 
+  What methods are used? Justification due to output data type. explanation of model output.
+
+## Data
+
+  What variables are included? Why is this output chosen. What explanatory variables are used and why are they chosen
+
 ## Results
+
+  What are the results. Coefficients tables. diagnostic plots. measures of goodness of fit.
+
+```{r income_output, echo=FALSE}
+options(width=120)
+zip_output("../../../data/transitions/test/hh_income_2018_2019.rds")
+```
+
+## References

### 2022-12-19 docsrc/documentation/notebooks/housing.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

--- 2022-12-19 docsrc/documentation/notebooks/household_income.Rmd
@@
 ---
-title: "Household Income"
+title: "Housing"
 output: html_document
@@
   - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
-  #- "../../refs.bib"
+  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
 ---
 
-# Household Income
+# Housing Quality
 
@@
 
-```{r income_output, echo=FALSE}
+```{r housing_output, echo=FALSE}
 options(width=120)
-zip_output("../../../data/transitions/test/hh_income_2018_2019.rds")
+clm_output("../../../data/transitions/test/housing_clm_2018_2019.rds")
 ```

### 2022-12-19 docsrc/documentation/notebooks/labour.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

--- 2022-12-19 docsrc/documentation/notebooks/household_income.Rmd
@@
 ---
-title: "Household Income"
+title: "Labour"
 output: html_document
 bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
-  #- "../../refs.bib"
+  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
+  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
 ---
 
-# Household Income
+# Labour
 
-Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].
+Introductory fluff. Why do we need this module? test reference [@1987:nelson].
 
@@
 
-```{r income_output, echo=FALSE}
+```{r housing_output, echo=FALSE}
 options(width=120)
-zip_output("../../../data/transitions/test/hh_income_2018_2019.rds")
+nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
 ```

### 2022-12-19 docsrc/documentation/notebooks/loneliness.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

--- 2022-12-19 docsrc/documentation/notebooks/labour.Rmd
@@
 ---
-title: "Labour"
+title: "Loneliness"
 output: html_document
 bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
-  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
+  - "refs.bib"  # bib reference depending on where the file is being run. Use this one when compiling the website using the makefile.
+  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging. Make sure to switch back when done..
 ---
 
-# Labour
+# Loneliness
 
@@
 options(width=120)
-nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
+clm_output("../../../data/transitions/test/loneliness_clm_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
 ```

### 2022-12-19 docsrc/documentation/notebooks/mental_well_being.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

--- 2022-12-19 docsrc/documentation/notebooks/housing.Rmd
@@
 ---
-title: "Housing"
+title: "Mental Well-Being"
 output: html_document
@@
 
-# Housing Quality
+# Mental Well-Being
 
-Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].
+Introductory fluff. Why do we need this module? test reference [@1987:nelson].
 
@@
 options(width=120)
-clm_output("../../../data/transitions/test/housing_clm_2018_2019.rds")
+ols_output("../../../data/transitions/test/sf12_ols_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
 ```

### 2022-12-19 docsrc/documentation/notebooks/module_notebook_template.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

--- 2022-12-19 docsrc/documentation/notebooks/labour.Rmd
@@
 ---
-title: "Labour"
+title: "XXXX"
 output: html_document
@@
 
-# Labour
+# XXXX
 
@@
 options(width=120)
-nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
+clm_output("PATH_TO_TEST_MODEL_DATA") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
 ```

### 2022-12-19 docsrc/documentation/notebooks/neighbourhood.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

--- 2022-12-19 docsrc/documentation/notebooks/module_notebook_template.Rmd
@@
 ---
-title: "XXXX"
+title: "Neighbourhood"
 output: html_document
@@
 
-# XXXX
+# Neighbourhood
 
@@
 options(width=120)
-clm_output("PATH_TO_TEST_MODEL_DATA") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
+clm_output("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
 ```

### 2022-12-19 docsrc/documentation/notebooks/tobacco.Rmd
templates for 7/11 notebooks. fully automated make command compiles them into website

@@
 ---
-title: "tobacco"
+title: "Tobacco Transition Module"
 output: html_document
-date: "2022-12-19"
+bibliography: 
+  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
+  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
 ---
 
+# Tobacco
+
+Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].
+
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+source('sphinx_notebook_utils.R')
 ```
 
-## R Markdown
+## Methods
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+  What methods are used? Justification due to output data type. explanation of model output.
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+## Data
 
-```{r cars}
-summary(cars)
+  What variables are included? Why is this output chosen. What explanatory variables are used and why are they chosen
+
+## Results
+
+  What are the results. Coefficients tables. diagnostic plots. measures of goodness of fit.
+
+```{r tobacco_output, echo=FALSE}
+options(width=120)
+zip_output("../../../data/transitions/test/tobacco_zip_2018_2019.rds")
 ```
 
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+## References

### 2022-12-21 docsrc/documentation/notebooks/household_income.Rmd
get all current module templates with better formatting in taskbar.
bug fixing income, labour models. adding visualisation plots to all models for notebooks

@@
 bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
-  #- "../../refs.bib"
+  #- "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
+  - "../../refs.bib" # useful for debugging.
 ---
 
-# Household Income
+## Household Income
 
-Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].
+Household disposable income is a well known indicator of mental well-being.
 
@@
 source('sphinx_notebook_utils.R')
+notebook_setwd()
 ```
 
-## Methods
+### Methods
 
@@
 
-## Data
+### Data
 
@@
 
-## Results
+```{r, hh_income_data}
+ols_histogram("data/transitions/test/hh_income_2018_2019.rds", "hh_income_next")  
+```
+
+### Results
 
@@
 options(width=120)
-zip_output("../../../data/transitions/test/hh_income_2018_2019.rds")
+ols_output(hh_income_data_path <- "data/transitions/test/hh_income_2018_2019.rds"
+)
 ```
 
-## References
+### References

### 2022-12-21 docsrc/documentation/notebooks/neighbourhood.Rmd
get all current module templates with better formatting in taskbar.
bug fixing income, labour models. adding visualisation plots to all models for notebooks

@@
 bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
-  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
+  #- "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
+  - "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
 ---
 
-# Neighbourhood
+## Neighbourhood
 
@@
 
-## Methods
+### Methods
 
@@
 
-## Results
+### Results
 
@@
 
-## References
+### References

### 2022-12-21 docsrc/documentation/notebooks/tobacco.Rmd
get all current module templates with better formatting in taskbar.
bug fixing income, labour models. adding visualisation plots to all models for notebooks

@@
 
-# Tobacco
+## Tobacco
 
@@
 source('sphinx_notebook_utils.R')
+notebook_setwd()
+
 ```
 
-## Methods
+### Methods
 
@@
 
-## Results
+```{r tobacco_data}
+zip_density("data/transitions/test/tobacco_zip_2018_2019.rds", 'y')
+```
+### Results
 
@@
 options(width=120)
-zip_output("../../../data/transitions/test/tobacco_zip_2018_2019.rds")
+zip_output("data/transitions/test/tobacco_zip_2018_2019.rds")
 ```
 
-## References
+### References

### 2023-01-05 docsrc/documentation/notebooks/household_income.Rmd
get plots for all modules (except loneliness aaaaaaa)

--- 2022-12-19 docsrc/documentation/notebooks/household_income.Rmd
@@
 ---
-title: "Household_Income"
+title: "Household Income"
 output: html_document
-date: "2022-12-16"
-bibliography: references.bib  
+bibliography: 
+  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
+  #- "../../refs.bib" # useful for debugging.
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+source('sphinx_notebook_utils.R')
 ```
 
-# Household Income
+## Household Income
 
-## Data
+Household disposable income is a well known indicator of mental well-being [@graham2009understanding]. Estimating this is a crucial instrument for the effects of many policy interventions
 
-## Methods
+The output variable is monthly household disposable income.
+This is calculated as a composite using several variables.
+Rent, mortgages, and council tax are subtracted from net household income and adjusted by household size.
+This value is then adjusted for yearly inflation estimates.
 
-## Results
+$$    hh\_income\_intermediate = ((net\_hh\_income) - (rent + mortgage + council\_tax)) / hh\_size$$
+$$    hh\_income = hh\_income\_ * inflation\_factor$$
+This produces a continuous distribution of pounds per month available for a household to spend as it likes. This is plotted below with a median income of $~£1250$.
+
+```{r, hh_income_data}
+continuous_density("hh_income")  
+```
+
+### Methods
+
+  To estimate this variable Ordinary Least Squares (OLS) linear regression is used. This is a common  technique for estimating Gaussian distributed variables that is easy to implement using base R.
+
+### Data
+
+  The formula for this linear regression is given as
+
+  $$hh\_income\_next ~ age + sex + factor(ethnicity) + factor(region) + scale(hh\_income) + factor(job\_sec) + factor(labour\_state) + factor(education\_state) + scale(SF\_12) + factor(housing\_quality)$$
+Each variable included is defined as follows.
+Each variable with discrete values is defined in the data tables section of this documentation [here](https://leeds-mrg.github.io/Minos/documentation/data_tables.html).
+
+- sex. Individual's biological sex. [@dilmaghani2018sexual]
+- ethnicity. Individual ethnicity. Discrete string values White British, Black African, etc. [@clemens2014method]
+- region. Administrative region of the UK. Discrete strings such as London, North-East. [@brewer2007poverty]
+- household income. Previous household income values are a strong indicator of current value. [@dilmaghani2018sexual]
+- job_sec. NSSEC code for individual's employment. Ordinal values describing job quality. [@clemens2014method]
+- labour state. Is a person employed, unemployed, student etc. Discrete states. [@dilmaghani2018sexual]
+- education state. Highest attain qualification. Ordinal values based on UK government education tiers [@eika2019educational]
+- SF_12. Mental well-being. Continuous score indicating overall mental-wellbeing. is this an indicator of hh_income? [@viswanathan2005nature]
+- housing quality. Ordinal values indicating number of appliances in household. [@brewer2007poverty]
+
+### Results
+
+Model coefficients and diagnostics are displayed below. To summarise
+- r squared of 0.21 indicates reasonable fit. 
+- Gender not significant.
+Some ethnicities see increases.
+Only London has higher income.
+High quality jobs eanr more.
+PT employed earn less students earn more.
+Housing quality strong indicator of higher income.
+- diagnostic plots show underdispersion. Some extreme outlier values need investigating. 
+- overall decent fit.
+
+```{r income_output, echo=FALSE}
+options(width=120)
+ols_output("../../../data/transitions/test/hh_income_2018_2019.rds")
+ols_histogram("../../../data/transitions/test/hh_income_2018_2019.rds", "hh_income_next")  
+```
+
+### References

### 2023-01-05 docsrc/documentation/notebooks/labour.Rmd
get all current module templates with better formatting in taskbar.
get plots for all modules (except loneliness aaaaaaa)

@@
 
-# Labour
-
-Introductory fluff. Why do we need this module? test reference [@1987:nelson].
-
 ```{r setup, include=FALSE}
@@
 
-## Methods
+## Labour
 
-  What methods are used? Justification due to output data type. explanation of model output.
+Labour state is a measure of what an individual does. There are 8 distinctive categories including employment, unemployment, and retired. 
+The encodings of these states can be found [here]](https://leeds-mrg.github.io/Minos/documentation/data_tables.html).
 
-## Data
+```{r labour_barchart, echo=FALSE}
+discrete_barplot("labour_state")
+```
 
-  What variables are included? Why is this output chosen. What explanatory variables are used and why are they chosen
+### Methods
 
-## Results
+Labour state is a complex categorical data type. Single layer neural network is a simple way to estimate this state. Use multinom function from R's nnet package. Formula for weights included given as.
 
-  What are the results. Coefficients tables. diagnostic plots. measures of goodness of fit.
+$$labour\_state\_next = sex + ethnicity + age + education\_state + SF\_12 + housing\_quality + labour\_state + job\_sec + hh\_income + alcohol\_spending$$
 
-```{r housing_output, echo=FALSE}
+### Data
+
+Variables used in this model. Encodings for discrete variables found in data tables.
+
+- sex. Biological sex male/female.
+- ethnicity. Ethnicity e.g. white british. XXXX cite.
+- age in years. XXXX cite.
+- education. Highest qualification attained. XXXX cite 
+- sf12. Mental well-being score. XXXX cite
+- housing quality. Number of household appliances. Ordinal 1-3. XXXX cite
+- labour_state. Previous labour state. XXXX cite. Probably remove this. dominates prediction..
+- nssec. Socioeconomic code of job. Indicates job quality with 1-9 ordinal variable. XXXX cite
+- household income. Monthly disposable income of individuals household. XXXX cite.
+- alcohol spending. How much is spent on alcohol. XXXX cite. remove.
+
+### Results
+
+  - hard to determine goodness of fit. 
+  - use confusion matrix to estimate quality of fit. 
+  - employed/retired well predicted. unemployed/student volatile socially and expectedly hard to predict. 
+  - some deterministic replacement needed for categories like student that have specific time frames. e.g. three years for a degree.
+
+```{r labour_output, echo=FALSE}
 options(width=120)
 nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
+nnet_confusion_matrix("../../../data/transitions/test/labour_nnet_2018_2019.rds", mode='multinom', 'factor(labour_state)')
 ```
 
-## References
+### References

### 2023-01-05 docsrc/documentation/notebooks/neighbourhood.Rmd
get plots for all modules (except loneliness aaaaaaa)

--- 2022-12-19 docsrc/documentation/notebooks/neighbourhood.Rmd
@@
 
-# Neighbourhood
+## Neighbourhood
 
-Introductory fluff. Why do we need this module? test reference [@1987:nelson].
+Neighbourhood quality is an indicator of well-being suggested by the SIPHER-7 XXXX ref and others?.
 
-```{r setup, include=FALSE}
+```{r neighbourhood_setup, include=FALSE}
 source('sphinx_notebook_utils.R')
@@
 
-## Methods
+### Methods
 
-  What methods are used? Justification due to output data type. explanation of model output.
+```{r neighbourhood_barchart, echo=FALSE}
+print(table(real_data$neighbourhood_safety))
+discrete_barplot("neighbourhood_safety")
+getwd()
+```
 
-## Data
+  Neighbourhood data are presented as a likert scale from 1-6 indicating the number of harmful activities that happen in a persons
+  neighbourhood for individual health. These include robberies and vandalism with the full encoding available in the data tables.
+
+### Data
 
@@
 options(width=120)
-clm_output("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
+clm_barplot("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds", "neighbourhood_safety_next")
+clm_output("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds")
 ```
 
-## References
+### References

### 2023-01-06 docsrc/documentation/notebooks/loneliness.Rmd
get all current module templates with better formatting in taskbar.
update naming in some transition modules. improve website some more

@@
 
-# Loneliness
+## Loneliness
 
@@
 
-## Data
+```{r loneliness_data}
+discrete_barplot("loneliness")
+```
+
+### Data
 
@@
 options(width=120)
+clm_barplot("../../../data/transitions/test/loneliness_clm_2018_2019.rds", "loneliness_next") 
 clm_output("../../../data/transitions/test/loneliness_clm_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds

### 2023-01-06 minos/transitions/housing/Housing_clm.R

@@ -72,11 +72,14 @@ clm.housing.main <- function(years){
     #data2 <- format.housing.composite(data2)
 
     data2 <- data2[, c("pidp", "housing_quality")]
-    colnames(data2) <- c("pidp", "y")
+    colnames(data2) <- c("pidp", "housing_quality_next")
     data <- merge(data, data2,"pidp")
     data <- data[complete.cases(data),]
 
-    data$y <- factor(data$y, levels=c(1, 2, 3))
+    data$housing_quality_next <- factor(data$housing_quality_next, levels=c(1, 2, 3))
+    data$sex <- factor(data$sex)
+    data$labour_state <- factor(data$labour_state)
+    data$ethnicity <- factor(data$ethnicity)
     #formula <- "y ~ factor(sex) +
     #                age +
     #                scale(SF_12) +
@@ -84,12 +87,13 @@ clm.housing.main <- function(years){
     #                factor(job_sec) +
     #                factor(ethnicity) +
     #                scale(hh_income)"
-    formula <- "y ~ factor(sex) +
+    formula <- "housing_quality_next ~
+                    sex +
                     age +
-                    scale(SF_12) +
-                    factor(labour_state) +
-                    factor(ethnicity) +
-                    scale(hh_income)"
+                    SF_12 +
+                    labour_state +
+                    ethnicity +
+                    hh_income"
 
     # Handle the fact that first wave (2009) has no weight data
     if (year == 2009) {
@@ -109,7 +113,7 @@ clm.housing.main <- function(years){
                    weights = weight)
     }
 
-    prs<- 1 - logLik(clm.housing)/logLik(clm(y ~ 1, data=data))
+    prs<- 1 - logLik(clm.housing)/logLik(clm(housing_quality_next ~ 1, data=data))
     print(prs)
 
     out.path <- "data/transitions/housing/clm/"

### 2023-01-17 docsrc/documentation/notebooks/mental_well_being.Rmd
get all current module templates with better formatting in taskbar.

@@
 
-# Mental Well-Being
+## Mental Well-Being
 
@@
 
-## Data
+```{r neighbourhood_barchart, echo=FALSE}
+continuous_density("SF_12")
+```
+### Data
 
@@
 options(width=120)
-ols_output("../../../data/transitions/test/sf12_ols_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
+ols_histogram("../../../data/transitions/test/sf12_ols_2018_2019.rds", "y")
+ols_output("../../../data/transitions/test/sf12_ols_2018_2019.rds")
 ```
 
-## References
+### References

### 2023-02-15 docsrc/documentation/notebooks/housing.Rmd
get all current module templates with better formatting in taskbar.

@@
 
-# Housing Quality
+## Housing Quality
 
@@
 
-```{r setup, include=FALSE}
+```{r housing_setup, include=FALSE}
 source('sphinx_notebook_utils.R')
@@
 
-## Data
+```{r housing_barchart, echo=FALSE}
+print(table(real_data$housing_quality))
+discrete_barplot("housing_quality")
+```
+
+### Data
 
@@
 options(width=120)
+clm_barplot("../../../data/transitions/test/housing_clm_2018_2019.rds", "housing_quality_next")
 clm_output("../../../data/transitions/test/housing_clm_2018_2019.rds")

### 2023-02-15 docsrc/documentation/notebooks/labour.Rmd

@@
 options(width=120)
-nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
-nnet_confusion_matrix("../../../data/transitions/test/labour_nnet_2018_2019.rds", mode='multinom', 'factor(labour_state)')
+nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds")
+nnet_confusion_matrix("../../../data/transitions/test/labour_nnet_2018_2019.rds", mode='multinom', 'factor(labour_state_next)')
 ```

### 2023-02-15 docsrc/documentation/notebooks/tobacco.Rmd

--- 2022-12-19 docsrc/documentation/notebooks/tobacco.Rmd
@@
 ---
-title: "Tobacco Transition Module"
+title: "Tobacco"
 output: html_document
@@
 
-# Tobacco
+## Tobacco
 
-Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].
+Number of cigarettes consumed is an indicator of several mental illnesses including anxiety [@lawrence2010anxiety].
 
@@
 
-## Methods
-
-  What methods are used? Justification due to output data type. explanation of model output.
-
-## Data
+### Data
 
@@
 
-## Results
+```{r tobacco_data}
+counts_density('ncigs')
+```
 
-  What are the results. Coefficients tables. diagnostic plots. measures of goodness of fit.
+### Methods
+
+The number of zero inflated values is higher than expected for a count distribution such as a poisson distribution.
+This inflation occurs naturally as a large proportion (over 50\%) of the population do not smoke.
+There are two sources of cigarette consumption that can be modelled using zero inflated models.
+In this case a zero-inflated poisson (ZIP) is used.
+Two models are fitted simulatenously.
+One is a logistic regression that estimates whether a person smokes cigarettes or not.
+This provides a simple probability of smoking or not.
+The second is a poisson counts model estimating the number of cigarettes consumed.
+
+### Data
+
+Two set of variables are needed for the logistic and poisson parts of the ZIP model respectively.
+
+Variables that predict how much a person smokes.
+
+age. persons age. generally older people and very young smoke. 
+SF_12. wellbeing estimates number of cigarettes smoked.
+labour_state. whether a person is employed or not.
+ethnicity. certain ethnicities more likely to smoke cigarettes. 
+education_state. highest qualification.
+job_sec job quality
+hh_income household income
+ncigs previous number consumed.
+
+Variables that predict whether a person smokes
+
+ethnicity. certain ethnicities more likely to smoke cigarettes. 
+labour_state. whether a person is employed or not.
+age
+SF_12. wellbeing estimates number of cigarettes smoked.
+ncigs previous number consumed.
+
+### Results
+
+Almost all coefficients significant.
+Particularly prevous consumption of cigarettes.
+Good estimation of the number of non-smokers in the population at around 55\%.
+Counts of smoking are underdispersed and fail to estimate consumption over 20 cigarettes.
 
@@
 zip_output("../../../data/transitions/test/tobacco_zip_2018_2019.rds")
+zip_density("../../../data/transitions/test/tobacco_zip_2018_2019.rds", 'ncigs_next')
 ```
 
-## References
+### References

### 2023-02-17 docsrc/documentation/notebooks/mental_well_being.Rmd
updating sphinx to have root level file paths. tidying. matching new development changes to transition models

@@
 bibliography: 
-  - "refs.bib" # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
-  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
+  - "docsrc/refs.bib"
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_knit$set(root.dir= "../minos")
+```
 
@@
 
-```{r setup, include=FALSE}
-source('sphinx_notebook_utils.R')
+```{r load_data, include=FALSE}
+source("docsrc/documentation/notebooks/sphinx_notebook_utils.R")
 ```
@@
 
-```{r neighbourhood_barchart, echo=FALSE}
-continuous_density("SF_12")
+```{r SF12_Density}
+continuous_density("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")  
 ```
+
 ### Data
@@
 
-```{r housing_output, echo=FALSE}
+```{r SF12_Output, echo=FALSE}
 options(width=120)
-ols_histogram("../../../data/transitions/test/sf12_ols_2018_2019.rds", "y")
-ols_output("../../../data/transitions/test/sf12_ols_2018_2019.rds")
+ols_output("data/transitions/SF_12/OLS/SF_12_2018_2019.rds")
+ols_histogram("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")
 ```

### 2023-02-20 docsrc/documentation/notebooks/loneliness.Rmd

--- 2022-12-19 docsrc/documentation/notebooks/loneliness.Rmd
@@
 bibliography: 
-  - "refs.bib"  # bib reference depending on where the file is being run. Use this one when compiling the website using the makefile.
+  - "docsrc/refs.bib"  # bib reference depending on where the file is being run. Use this one when compiling the website using the makefile.
   #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging. Make sure to switch back when done..
@@
 
-# Loneliness
+## Loneliness
+
+```{r setup, include=FALSE}
+knitr::opts_knit$set(root.dir= "../minos")
+```
 
@@
 
-```{r setup, include=FALSE}
-source('sphinx_notebook_utils.R')
+```{r load_data, include=FALSE}
+source('docsrc/documentation/notebooks/sphinx_notebook_utils.R')
 ```
 
-## Methods
+### Methods
 
@@
 
-## Data
+```{r loneliness_data}
+discrete_barplot("data/transitions/loneliness/clm/loneliness_2018_2019.rds", 'next_loneliness')
+```
+
+### Data
 
@@
 options(width=120)
-clm_output("../../../data/transitions/test/loneliness_clm_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
+clm_barplot("data/transitions/loneliness/clm/loneliness_2018_2019.rds", "next_loneliness") 
+clm_output("data/transitions/loneliness/clm/loneliness_2018_2019.rds")
 ```
 
-## References
+### References

### 2023-02-21 docsrc/documentation/notebooks/labour.Rmd

@@
 bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
-  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
+  #- "docsrc/refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
+  - "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
 ---
@@
 ```{r setup, include=FALSE}
-source('sphinx_notebook_utils.R')
+#knitr::opts_knit$set(root.dir= "../minos")
+```
+
+```{r load_data, include=FALSE}
+source('docsrc/documentation/notebooks/sphinx_notebook_utils.R')
 ```
@@
 options(width=120)
-nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds")
-nnet_confusion_matrix("../../../data/transitions/test/labour_nnet_2018_2019.rds", mode='multinom', 'factor(labour_state_next)')
+#nnet_output("data/transitions/labour/nnet/labour_nnet_2018_2019.rds")
+nnet_confusion_matrix("data/transitions/labour/nnet/labour_nnet_2018_2019.rds", mode='multinom', 'labour_state_next')
 ```

### 2023-02-27 docsrc/documentation/notebooks/household_income.Rmd

@@
 bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
+  - "docsrc/refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
   #- "../../refs.bib" # useful for debugging.
@@
 ```{r setup, include=FALSE}
-source('sphinx_notebook_utils.R')
+knitr::opts_knit$set(root.dir= "../minos")
+```
+
+```{r load_data, include=FALSE}
+source('docsrc/documentation/notebooks/sphinx_notebook_utils.R')
 ```
@@
 ```{r, hh_income_data}
-continuous_density("hh_income")  
+continuous_density("data/transitions/hh_income/ols/hh_income_2018_2019.rds", "next_hh_income")  
 ```
@@
 options(width=120)
-ols_output("../../../data/transitions/test/hh_income_2018_2019.rds")
-ols_histogram("../../../data/transitions/test/hh_income_2018_2019.rds", "hh_income_next")  
+ols_output("data/transitions/hh_income/ols/hh_income_2018_2019.rds")
+ols_histogram("data/transitions/hh_income/ols/hh_income_2018_2019.rds", "next_hh_income")
 ```

### 2023-02-27 docsrc/documentation/notebooks/neighbourhood.Rmd

@@
 bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
+  - "docsrc/refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
   #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
 ---
+
+```{r load_data, include=FALSE}
+knitr::opts_knit$set(root.dir= "../minos")
+```
 
@@
 ```{r neighbourhood_setup, include=FALSE}
-source('sphinx_notebook_utils.R')
+source('docsrc/documentation/notebooks/sphinx_notebook_utils.R')
 ```
@@
 ```{r neighbourhood_barchart, echo=FALSE}
-print(table(real_data$neighbourhood_safety))
-discrete_barplot("neighbourhood_safety")
-getwd()
+discrete_barplot("data/transitions/neighbourhood_safety/clm/neighbourhood_safety_2014_2017.rds", 'next_neighbourhood_safety')
 ```
@@
 options(width=120)
-clm_barplot("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds", "neighbourhood_safety_next")
-clm_output("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds")
+clm_barplot("data/transitions/neighbourhood_safety/clm/neighbourhood_safety_2014_2017.rds", "next_neighbourhood_safety") 
+clm_output("data/transitions/neighbourhood_safety/clm/neighbourhood_safety_2014_2017.rds")  
 ```

### 2023-02-28 minos/validation/handovers.Rmd
Moved outcome visualisation scripts to a new outcomes directory, and added an R notebook for handover plots. Also some utils functions for validation

---
title: "MINOS Handover Plots"
output: html_notebook
---

This notebook shows the handover plots for all pathways in the MINOS microsimulation model.

Handover plots are not strictly statistical validation, but more a type of 'sanity check' for transitioned variables. A handover plot shows the 'handover' from input data to predicted outcomes, and allows us to see at a glance if the predicted outputs are following the same trends seen in the input data.

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

Source utils for some functions.

```{r}
source('R_Scripts/utils.r')
```

## Data

```{r}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

# baseline path and output subdirectory
base.path <- 'Minos/output/default_config/baseline/'
base.path <- get_runtime_subdirectory(base.path)

base.files <- list.files(base.path, 
                         pattern = '[0-9]{4}.csv',
                         full.names = TRUE)
base.dat <- do.call(rbind, lapply(base.files, read.csv))
```

## Constants

```{r}
start.year <- 2020
```

# PATHWAYS

## Income

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.income <- raw.dat %>% 
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = weighted.mean(hh_income, weight)) %>%
  mutate(source = 'final_US')

base.income <- base.dat %>%
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = weighted.mean(hh_income, weight, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
income <- rbind(raw.income, base.income)

# Now plot
ggplot(data = income, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.income.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.income2 <- raw.dat %>% 
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.income2 <- base.dat %>%
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

income2 <- rbind(raw.income2, base.income2)

# Now plot
ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

raw.income.check <- raw.dat %>% 
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

base.income.check <- base.dat %>%
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

#rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
#   raw.income.check, base.income.check)
```

## SF12

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.sf12 <- raw.dat %>% 
  select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12 <- base.dat %>%
  select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
sf12 <- rbind(raw.sf12, base.sf12)

# Now plot
ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.sf12.2 <- raw.dat %>% 
  select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.2 <- base.dat %>%
  select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

sf12.2 <- rbind(raw.sf12.2, base.sf12.2)

# Now plot
ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')
```

## Housing Quality

```{r}
raw.housing <- raw.dat %>% 
  select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'final_US')

base.housing <- base.dat %>%
  select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
housing <- rbind(raw.housing, base.housing)
housing$housing_quality <- as.factor(housing$housing_quality)

# Now plot
ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

housing.norm <- housing %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted')

rm(raw.housing, base.housing, housing, housing.norm)
```

## Neighbourhood Safety

```{r}
raw.neighbour <- raw.dat %>% 
  select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'final_US')

base.neighbour <- base.dat %>%
  select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
neighbour <- rbind(raw.neighbour, base.neighbour)
neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety)

# Now plot
ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

neighbour.norm <- neighbour %>%
  group_by(time) %>%
  filter(neighbourhood_safety != -9) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted')

#rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm)
```

## Loneliness

```{r}
raw.loneliness <- raw.dat %>% 
  select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'final_US')

base.loneliness <- base.dat %>%
  select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
loneliness <- rbind(raw.loneliness, base.loneliness)
loneliness$loneliness <- as.factor(loneliness$loneliness)

# Now plot
ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

loneliness.norm <- loneliness %>%
  group_by(time) %>%
  filter(loneliness != -9) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted')

rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
```

## Nutrition Quality

TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.nut <- raw.dat %>% 
  select(pidp, time, nutrition_quality) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.nut <- base.dat %>%
  select(pidp, time, nutrition_quality) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
nutrition_quality <- rbind(raw.nut, base.nut)

# Now plot
ggplot(data = nutrition_quality, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.nut2 <- raw.dat %>% 
  select(pidp, time, nutrition_quality) %>%
  filter(pidp %in% raw.wave1) %>%
  filter(nutrition_quality >= 0) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.nut2 <- base.dat %>%
  select(pidp, time, nutrition_quality) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

nutrition_quality2 <- rbind(raw.nut2, base.nut2)

# Now plot
ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2, 
    nutrition_quality2)
```

## Physical Health

NOTE: At present, physical health is not predicted or transitioned.

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.phealth <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth <- base.dat %>%
  select(pidp, time, phealth) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
phealth <- rbind(raw.phealth, base.phealth)

# Now plot
ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.phealth2 <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth2 <- base.dat %>%
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

phealth2 <- rbind(raw.phealth2, base.phealth2)

# Now plot
ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

raw.phealth.check <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1)

base.phealth.check <- base.dat %>%
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1)

rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, 
   raw.phealth.check, base.phealth.check, phealth2)
```

```{r}

```

### 2023-03-01 minos/validation/replenishing.Rmd
Added work in progress script for analysing the replenishing population

---
title: "Assessing Replenishing Population"
output: html_notebook
---

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(purrr)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

Source utils for some functions.
```{r}
source('R_Scripts/utils.r')
```

```{r}
# Replenishing data
repl <- read.csv('/home/luke/Documents/WORK/MINOS/Minos/data/replenishing/replenishing_pop_2019-2070.csv')

# scotland replenishing
#scot.repl <- read.csv('/home/luke/Documents/WORK/MINOS/Minos/data/replenishing/scotland/replenishing_pop_2019-2070.csv')
```

## EDUCATION

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
educ.state <- repl %>% 
  group_by(time, education_state) %>%
  count()

# set column types
educ.state$education_state <- as.factor(educ.state$education_state)

ggplot(data = educ.state, mapping = aes(x = education_state, y = n, fill=education_state)) +
  geom_col(position='dodge')
```

## ETHNICITY

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
ethnic.state <- repl %>% 
  group_by(time, ethnicity) %>%
  count()

# set column types
ethnic.state$ethnicity <- as.factor(ethnic.state$ethnicity)

ggplot(data = ethnic.state, mapping = aes(x = ethnicity, y = n, fill=ethnicity)) +
  geom_col(position='dodge')

ggplot(data = filter(ethnic.state, ethnicity != 'WBI'), mapping = aes(x = ethnicity, y = n, fill=ethnicity)) +
  geom_col(position='dodge')
```

### 2023-03-01 minos/validation/mwb_pathways.Rmd
Added WIP notebook for looking at the mental wellbeing pathway variables in the outputs

---
title: "Mental Wellbeing Pathways"
output: html_notebook
---

# Setup

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(purrr)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

Source utils for some functions.
```{r}
source('R_Scripts/utils.r')
```

## Data

```{r}
output.path <- 'Minos/output/default_config/'
baseline.path <- paste0(output.path, 'baseline')
base.path <- get_runtime_subdirectory(baseline.path)

# read in all the output data files
base.files <- list.files(base.path,
                         pattern = '[0-9]{4}.csv',
                         full.names = TRUE)
data <- do.call(rbind, lapply(base.files, read.csv))
```

# Analysis

## ncigs

DONE: Fixed problem where the rescale factor was still being applied in prediction but not in the estimation of the model.
DONE: Fixed line in the r_utils prediction method where the non-smokers were being predicted as smokers.
TODO: Fix the input data issue where lots of these vars are being reported as missing still (negative numbers). This should be in the run script somewhere.

```{r}
ncigs <- data %>% 
  select(pidp, time, ncigs)

# calculate and plot mean over time
ncigs.byyr <- data %>% group_by(time) %>%
  summarise(ncigs = mean(ncigs))

ggplot(data = ncigs.byyr, mapping = aes(x = time, y = ncigs)) +
  geom_line()
```

```{r}
# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
ncigs.2018 <- ncigs %>% filter(time == 2018)
ncigs.2020 <- ncigs %>% filter(time == 2020)
ncigs.2030 <- ncigs %>% filter(time == 2030)

ncigs.joined <- rbind(ncigs.2018, ncigs.2020, ncigs.2030)
ncigs.joined$time <- as.factor(ncigs.joined$time)

ggplot(data = ncigs.joined, mapping = aes(x = ncigs, group = time, fill = time, color = time)) +
  geom_histogram(position='dodge')
```

```{r}
# Lets also look at the number of smokers vs non-smokers
smokers.count <- ncigs %>% 
  group_by(time) %>%
  summarise(non.smoker = sum(ncigs == 0),
            smoker = sum(ncigs > 0)) %>%
  pivot_longer(cols = non.smoker:smoker,
               names_to = 'smoking_status',
               values_to = 'count')

ggplot(data = smokers.count, mapping = aes(x = time, y = count, group = smoking_status, color = smoking_status)) +
  geom_line()
```

## Housing Quality

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
housing.state <- data %>% 
  group_by(time, housing_quality) %>%
  count()

# set column types
housing.state$housing_quality <- as.factor(housing.state$housing_quality)

ggplot(data = housing.state, mapping = aes(x = time, y = n, group = housing_quality, color = housing_quality)) +
  geom_line()
```

## Neighbourhood Safety

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
neighbour.state <- data %>% 
  group_by(time, neighbourhood_safety) %>%
  count()

# set column types
neighbour.state$neighbourhood_safety <- as.factor(neighbour.state$neighbourhood_safety)

ggplot(data = neighbour.state, mapping = aes(x = time, y = n, group = neighbourhood_safety, color = neighbourhood_safety)) +
  geom_line()
```

## Loneliness

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
loneliness.state <- data %>% 
  group_by(time, loneliness) %>%
  count()

# set column types
loneliness.state$loneliness <- as.factor(loneliness.state$loneliness)

ggplot(data = loneliness.state, mapping = aes(x = time, y = n, group = loneliness, color = loneliness)) +
  geom_line()
```

```{r}

```

### 2023-03-01 minos/validation/replenishing.Rmd
Added to validation Makefile and made some paths relative instead of absolute

@@
 # Replenishing data
-repl <- read.csv('/home/luke/Documents/WORK/MINOS/Minos/data/replenishing/replenishing_pop_2019-2070.csv')
+repl <- read.csv('Minos/data/replenishing/replenishing_pop_2019-2070.csv')
 
 # scotland replenishing
-#scot.repl <- read.csv('/home/luke/Documents/WORK/MINOS/Minos/data/replenishing/scotland/replenishing_pop_2019-2070.csv')
+#scot.repl <- read.csv('Minos/data/replenishing/scotland/replenishing_pop_2019-2070.csv')
 ```

### 2023-03-01 minos/validation/mwb_pathways.Rmd
Added hh_income and SF12 to mwb_pathways notebook

@@
 # Analysis
+
+## SF 12
+
+```{r}
+sf12 <- data %>% 
+  select(pidp, time, SF_12)
+
+# calculate and plot mean over time
+sf12.byyr <- data %>% group_by(time) %>%
+  summarise(SF_12 = mean(SF_12))
+
+ggplot(data = sf12.byyr, mapping = aes(x = time, y = SF_12)) +
+  geom_line()
+```
+
+```{r}
+# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
+sf12.2018 <- sf12 %>% filter(time == 2018)
+sf12.2020 <- sf12 %>% filter(time == 2020)
+sf12.2030 <- sf12 %>% filter(time == 2030)
+
+sf12.joined <- rbind(sf12.2018, sf12.2020, sf12.2030)
+sf12.joined$time <- as.factor(sf12.joined$time)
+
+ggplot(data = sf12.joined, mapping = aes(x = SF_12, group = time, fill = time, color = time)) +
+  geom_histogram(position='dodge')
+```
+
+TODO: Why are we getting the same exact values from 2020 - 2030?
+
+```{r}
+print("2018:")
+sprintf("Min: %f", min(sf12.2018$SF_12))
+sprintf("Max: %f", max(sf12.2018$SF_12))
+sprintf("Mean: %f", mean(sf12.2018$SF_12))
+print("2020:")
+sprintf("Min: %f", min(sf12.2020$SF_12))
+sprintf("Max: %f", max(sf12.2020$SF_12))
+sprintf("Mean: %f", mean(sf12.2020$SF_12))
+print("2030:")
+sprintf("Min: %f", min(sf12.2030$SF_12))
+sprintf("Max: %f", max(sf12.2030$SF_12))
+sprintf("Mean: %f", mean(sf12.2030$SF_12))
+```
+
+## hh_income
+
+TODO: PLOT THE RAW DATA!!!
+
+```{r}
+income <- data %>% 
+  select(pidp, time, hh_income)
+
+# calculate and plot mean over time
+income.byyr <- data %>% group_by(time) %>%
+  summarise(hh_income = mean(hh_income))
+
+ggplot(data = income.byyr, mapping = aes(x = time, y = hh_income)) +
+  geom_line()
+```
+
+Again lets try overlaid histograms to see distributions over time.
+
+```{r}
+# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
+income.2018 <- income %>% filter(time == 2018)
+income.2020 <- income %>% filter(time == 2020)
+income.2030 <- income %>% filter(time == 2030)
+
+income.joined <- rbind(income.2018, income.2020, income.2030)
+
+income.joined$time <- as.factor(income.joined$time)
+income.joined$hh_income <- as.numeric(income.joined$hh_income)
+
+ggplot(data = income.joined, mapping = aes(x = hh_income, group = time, fill = time, color = time)) +
+  geom_histogram(bins = 50, position='dodge')
+```
+
+Check out the min/max for each time point, looks like it spreads out massively.
+```{r}
+print("2018:")
+sprintf("Min: %f", min(income.2018$hh_income))
+sprintf("Max: %f", max(income.2018$hh_income))
+sprintf("Mean: %f", mean(income.2018$hh_income))
+print("2020:")
+sprintf("Min: %f", min(income.2020$hh_income))
+sprintf("Max: %f", max(income.2020$hh_income))
+sprintf("Mean: %f", mean(income.2020$hh_income))
+print("2030:")
+sprintf("Min: %f", min(income.2030$hh_income))
+sprintf("Max: %f", max(income.2030$hh_income))
+sprintf("Mean: %f", mean(income.2030$hh_income))
+```
 

### 2023-03-01 minos/validation/handovers.Rmd
Small path changes to existing scripts, and added a notebook for investigating interventions

@@
 ```{r}
-source('R_Scripts/utils.r')
+source('Minos/minos/validation/utils.r')
 ```
@@
 
-# baseline path and output subdirectory
-base.path <- 'Minos/output/default_config/baseline/'
-base.path <- get_runtime_subdirectory(base.path)
-
-base.files <- list.files(base.path, 
-                         pattern = '[0-9]{4}.csv',
-                         full.names = TRUE)
-base.dat <- do.call(rbind, lapply(base.files, read.csv))
+out.path <- 'Minos/output/default_config/'
+base.dat <- read_output(out.path, 'baseline')
 ```

### 2023-03-01 minos/validation/DEBUG.Rmd

---
title: "MINOS Debug"
output: html_notebook
---

# Setup

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(purrr)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

Source utils for some functions.
```{r}
source('R_Scripts/utils.r')
```

Set up all the paths for the output directories and load in all waves of a single year of data.

```{r}
output.path <- 'Minos/output/default_config/'

baseline.path <- paste0(output.path, 'baseline')
allchild.path <- paste0(output.path, 'hhIncomeChildUplift')
povertychild.path <- paste0(output.path, 'hhIncomePovertyLineChildUplift')

# Handle the runtime subdirectory by selecting the most recent (utils.R func) 
base.path <- get_runtime_subdirectory(baseline.path)
#base.path <- baseline.path
```

```{r}
# Read scot datafiles in
scot.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/scotland_US/', full.names = TRUE)
scot.dat <- do.call(rbind, lapply(scot.files, read.csv))

# Replenishing data
#repl <- read.csv('/home/luke/Documents/WORK/MINOS/Minos/data/replenishing/replenishing_pop_2019-2070.csv')
#repl <- read.csv('/home/luke/Documents/WORK/MINOS/Minos/data/replenishing/replenishing_pop_2019-2070.csv')

# read in all the output data files
base.files <- list.files(base.path,
                         pattern = '[0-9]{4}.csv',
                         full.names = TRUE)
data <- do.call(rbind, lapply(base.files, read.csv))
```

## Input data files
```{r}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/stock/', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

# Replenishing data
repl <- read.csv('/home/luke/Documents/WORK/MINOS/Minos/data/replenishing/replenishing_pop_2019-2070.csv')
```

# REPLENISHING

## EDUCATION
```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
educ.state <- repl %>% 
  group_by(time, education_state) %>%
  count()

# set column types
educ.state$education_state <- as.factor(educ.state$education_state)

ggplot(data = educ.state, mapping = aes(x = education_state, y = n, fill=education_state)) +
  geom_col(position='dodge')
```
## Ethnicity
```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
ethnic.state <- repl %>% 
  group_by(time, ethnicity) %>%
  count()

# set column types
ethnic.state$ethnicity <- as.factor(ethnic.state$ethnicity)

ggplot(data = ethnic.state, mapping = aes(x = ethnicity, y = n, fill=ethnicity)) +
  geom_col(position='dodge')

ggplot(data = filter(ethnic.state, ethnicity != 'WBI'), mapping = aes(x = ethnicity, y = n, fill=ethnicity)) +
  geom_col(position='dodge')
```

# MODEL OUTPUT

## Handovers

First get the final_US data, and baseline output.
```{r}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

base.path <- 'Minos/output/default_config/baseline/'
base.path <- get_runtime_subdirectory(base.path)
#base.testpath <- 'tmp/test_out/baseline/'
base.files <- list.files(base.path,
                         pattern = '[0-9]{4}.csv',
                         full.names = TRUE)
base.dat <- do.call(rbind, lapply(base.files, read.csv))
```

Now we want to plot these against the output data, so it would be useful to create a generic function that would do it for us. Something that accepts both final_US data and output as an argument, meaning we can do all the loading and processing of outputs before the function call. Saves repeated code and means we can stick it in the utils for later.

```{r}
raw.income <- raw.dat %>% 
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = weighted.mean(hh_income, weight)) %>%
  mutate(source = 'final_US')

raw.income

test <- raw.dat %>%
  select(pidp, time, hh_income, weight)

test

#base.income <- base.dat %>%
#  select(pidp, time, hh_income, weight) %>%
#  group_by(time) %>%
#  summarise(income = weighted.mean(hh_income, weight, na.rm = TRUE)) %>%
#  mutate(source = 'baseline_output')#

#base.income
```

### Income
```{r}
# first figure out how to plot final_US
# start with hh_income
raw.income <- raw.dat %>% 
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = weighted.mean(hh_income, weight)) %>%
  mutate(source = 'final_US')

base.income <- base.dat %>%
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = weighted.mean(hh_income, weight, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
income <- rbind(raw.income, base.income)

# Now plot
ggplot(data = income, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.income.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.income2 <- raw.dat %>% 
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.income2 <- base.dat %>%
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

income2 <- rbind(raw.income2, base.income2)

# Now plot
ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

raw.income.check <- raw.dat %>% 
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

base.income.check <- base.dat %>%
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

#rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
#   raw.income.check, base.income.check)
```

### SF12
```{r}
# first figure out how to plot final_US
# start with hh_income
raw.sf12 <- raw.dat %>% 
  select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12 <- base.dat %>%
  select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
sf12 <- rbind(raw.sf12, base.sf12)

# Now plot
ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.sf12.2 <- raw.dat %>% 
  select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.2 <- base.dat %>%
  select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

sf12.2 <- rbind(raw.sf12.2, base.sf12.2)

# Now plot
ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')
```

### Housing Quality
```{r}
raw.housing <- raw.dat %>% 
  select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'final_US')

base.housing <- base.dat %>%
  select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
housing <- rbind(raw.housing, base.housing)
housing$housing_quality <- as.factor(housing$housing_quality)

# Now plot
ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

housing.norm <- housing %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=2018, linetype='dotted')

rm(raw.housing, base.housing, housing, housing.norm)
```

### Neighbourhood Safety

```{r}
raw.neighbour <- raw.dat %>% 
  select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'final_US')

base.neighbour <- base.dat %>%
  select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
neighbour <- rbind(raw.neighbour, base.neighbour)
neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety)

# Now plot
ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

neighbour.norm <- neighbour %>%
  group_by(time) %>%
  filter(neighbourhood_safety != -9) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=2018, linetype='dotted')

#rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm)
```

### Loneliness

```{r}
raw.loneliness <- raw.dat %>% 
  select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'final_US')

base.loneliness <- base.dat %>%
  select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
loneliness <- rbind(raw.loneliness, base.loneliness)
loneliness$loneliness <- as.factor(loneliness$loneliness)

# Now plot
ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

loneliness.norm <- loneliness %>%
  group_by(time) %>%
  filter(loneliness != -9) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=2018, linetype='dotted')

rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
```

### Nutrition Quality

TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.nut <- raw.dat %>% 
  select(pidp, time, nutrition_quality) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.nut <- base.dat %>%
  select(pidp, time, nutrition_quality) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
nutrition_quality <- rbind(raw.nut, base.nut)

# Now plot
ggplot(data = nutrition_quality, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.nut2 <- raw.dat %>% 
  select(pidp, time, nutrition_quality) %>%
  filter(pidp %in% raw.wave1) %>%
  filter(nutrition_quality >= 0) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.nut2 <- base.dat %>%
  select(pidp, time, nutrition_quality) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

nutrition_quality2 <- rbind(raw.nut2, base.nut2)

# Now plot
ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2, 
    nutrition_quality2)
```

### Physical Health

NOTE: At present, physical health is not predicted or transitioned.

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.phealth <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth <- base.dat %>%
  select(pidp, time, phealth) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
phealth <- rbind(raw.phealth, base.phealth)

# Now plot
ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.phealth2 <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth2 <- base.dat %>%
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

phealth2 <- rbind(raw.phealth2, base.phealth2)

# Now plot
ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

raw.phealth.check <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1)

base.phealth.check <- base.dat %>%
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1)

rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, 
   raw.phealth.check, base.phealth.check, phealth2)
```

## Demographics

### Age

DONE: Triple the number of 16 year olds in each replenishing cohort and look at this again.

TODO: Look at the leading cause of attrition - disease? older ages more likely?
In the raw data.

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
age.state <- data %>% 
  group_by(time, age_bucket) %>%
  count()

# set column types
age.state$age_bucket <- as.factor(age.state$age_bucket)
age.state$time <- as.integer(age.state$time)

ggplot(data = age.state, mapping = aes(x = time, y = n, group = age_bucket, color = age_bucket)) +
  geom_line()
```

```{r}
age.state2 <- data %>% 
  group_by(time) %>%
  summarise(age = mean(age))

age.state2$time <- as.integer(age.state2$time)

ggplot(data = age.state2, mapping = aes(x = time, y = age)) +
  geom_line()

```

TODO: Look at average age at death

```{r}
died <- data %>% group_by(time, cause_of_death) %>%
  summarise(mean_age = mean(age))

ggplot(data = died, mapping = aes(x = time, y = mean_age, group = cause_of_death, color = cause_of_death)) +
  geom_line()
```

```{r, include=FALSE}
rm(age.state, age.state2, died)
```

### Sex

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
sex.state <- data %>% 
  group_by(time, sex) %>%
  count()

# set column types
sex.state$sex <- as.factor(sex.state$sex)

ggplot(data = sex.state, mapping = aes(x = time, y = n, group = sex, color = sex)) +
  geom_line()
```
Product of mortality and replenishment - older age groups increase in number and women live longer than men.

### Education

TODO: Make this same plot for just the replenishing population, and see if they are the sole cause of the large increase in level 2 education. It could just be them, or it could also be that more people from other groups are dying. Need to find out regardless.

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
educ.state <- data %>% 
  group_by(time, education_state) %>%
  count()

# set column types
educ.state$education_state <- as.factor(educ.state$education_state)

ggplot(data = educ.state, mapping = aes(x = time, y = n, group = education_state, color = education_state)) +
  geom_line()
```

See transition model summaries at the bottom for reference.

### Ethnicity

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
ethnic.state <- data %>% 
  group_by(time, ethnicity) %>%
  count()

# set column types
ethnic.state$ethnicity <- as.factor(ethnic.state$ethnicity)

ggplot(data = ethnic.state, mapping = aes(x = time, y = n, group = ethnicity, color = ethnicity)) +
  geom_line()

ggplot(data = filter(ethnic.state, ethnicity != 'WBI'), mapping = aes(x = time, y = n, group = ethnicity, color = ethnicity)) +
  geom_line()
```

```{r}
# CLEANUP
#rm(age.state, educ.state, ethnic.state, sex.state)
```

## SF 12

```{r}
sf12 <- data %>% 
  select(pidp, time, SF_12)

# calculate and plot mean over time
sf12.byyr <- data %>% group_by(time) %>%
  summarise(SF_12 = mean(SF_12))

ggplot(data = sf12.byyr, mapping = aes(x = time, y = SF_12)) +
  geom_line()
```

```{r}
# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
sf12.2018 <- sf12 %>% filter(time == 2018)
sf12.2020 <- sf12 %>% filter(time == 2020)
sf12.2030 <- sf12 %>% filter(time == 2030)

sf12.joined <- rbind(sf12.2018, sf12.2020, sf12.2030)
sf12.joined$time <- as.factor(sf12.joined$time)

ggplot(data = sf12.joined, mapping = aes(x = SF_12, group = time, fill = time, color = time)) +
  geom_histogram(position='dodge')
```

TODO: Why are we getting the same exact values from 2020 - 2030?

```{r}
print("2018:")
sprintf("Min: %f", min(sf12.2018$SF_12))
sprintf("Max: %f", max(sf12.2018$SF_12))
sprintf("Mean: %f", mean(sf12.2018$SF_12))
print("2020:")
sprintf("Min: %f", min(sf12.2020$SF_12))
sprintf("Max: %f", max(sf12.2020$SF_12))
sprintf("Mean: %f", mean(sf12.2020$SF_12))
print("2030:")
sprintf("Min: %f", min(sf12.2030$SF_12))
sprintf("Max: %f", max(sf12.2030$SF_12))
sprintf("Mean: %f", mean(sf12.2030$SF_12))
```

## hh_income

TODO: PLOT THE RAW DATA!!!

```{r}
income <- data %>% 
  select(pidp, time, hh_income)

# calculate and plot mean over time
income.byyr <- data %>% group_by(time) %>%
  summarise(hh_income = mean(hh_income))

ggplot(data = income.byyr, mapping = aes(x = time, y = hh_income)) +
  geom_line()
```

Again lets try overlaid histograms to see distributions over time.

```{r}
# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
income.2018 <- income %>% filter(time == 2018)
income.2020 <- income %>% filter(time == 2020)
income.2030 <- income %>% filter(time == 2030)

income.joined <- rbind(income.2018, income.2020, income.2030)

income.joined$time <- as.factor(income.joined$time)
income.joined$hh_income <- as.numeric(income.joined$hh_income)

ggplot(data = income.joined, mapping = aes(x = hh_income, group = time, fill = time, color = time)) +
  geom_histogram(bins = 50, position='dodge')
```

Check out the min/max for each time point, looks like it spreads out massively.
```{r}
print("2018:")
sprintf("Min: %f", min(income.2018$hh_income))
sprintf("Max: %f", max(income.2018$hh_income))
sprintf("Mean: %f", mean(income.2018$hh_income))
print("2020:")
sprintf("Min: %f", min(income.2020$hh_income))
sprintf("Max: %f", max(income.2020$hh_income))
sprintf("Mean: %f", mean(income.2020$hh_income))
print("2030:")
sprintf("Min: %f", min(income.2030$hh_income))
sprintf("Max: %f", max(income.2030$hh_income))
sprintf("Mean: %f", mean(income.2030$hh_income))
```

## Pathways

### ncigs

DONE: Fixed problem where the rescale factor was still being applied in prediction but not in the estimation of the model.
DONE: Fixed line in the r_utils prediction method where the non-smokers were being predicted as smokers.
TODO: Fix the input data issue where lots of these vars are being reported as missing still (negative numbers). This should be in the run script somewhere.

```{r}
ncigs <- data %>% 
  select(pidp, time, ncigs)

# calculate and plot mean over time
ncigs.byyr <- data %>% group_by(time) %>%
  summarise(ncigs = mean(ncigs))

ggplot(data = ncigs.byyr, mapping = aes(x = time, y = ncigs)) +
  geom_line()
```

```{r}
# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
ncigs.2018 <- ncigs %>% filter(time == 2018)
ncigs.2020 <- ncigs %>% filter(time == 2020)
ncigs.2030 <- ncigs %>% filter(time == 2030)

ncigs.joined <- rbind(ncigs.2018, ncigs.2020, ncigs.2030)
ncigs.joined$time <- as.factor(ncigs.joined$time)

ggplot(data = ncigs.joined, mapping = aes(x = ncigs, group = time, fill = time, color = time)) +
  geom_histogram(position='dodge')
```

```{r}
# Lets also look at the number of smokers vs non-smokers
smokers.count <- ncigs %>% 
  group_by(time) %>%
  summarise(non.smoker = sum(ncigs == 0),
            smoker = sum(ncigs > 0)) %>%
  pivot_longer(cols = non.smoker:smoker,
               names_to = 'smoking_status',
               values_to = 'count')

ggplot(data = smokers.count, mapping = aes(x = time, y = count, group = smoking_status, color = smoking_status)) +
  geom_line()
```

### Housing Quality

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
housing.state <- data %>% 
  group_by(time, housing_quality) %>%
  count()

# set column types
housing.state$housing_quality <- as.factor(housing.state$housing_quality)

ggplot(data = housing.state, mapping = aes(x = time, y = n, group = housing_quality, color = housing_quality)) +
  geom_line()
```

### Neighbourhood Safety

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
neighbour.state <- data %>% 
  group_by(time, neighbourhood_safety) %>%
  count()

# set column types
neighbour.state$neighbourhood_safety <- as.factor(neighbour.state$neighbourhood_safety)

ggplot(data = neighbour.state, mapping = aes(x = time, y = n, group = neighbourhood_safety, color = neighbourhood_safety)) +
  geom_line()
```

### Loneliness

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
loneliness.state <- data %>% 
  group_by(time, loneliness) %>%
  count()

# set column types
loneliness.state$loneliness <- as.factor(loneliness.state$loneliness)

ggplot(data = loneliness.state, mapping = aes(x = time, y = n, group = loneliness, color = loneliness)) +
  geom_line()
```

# TRANSITION MODEL SUMMARIES

```{r, include=FALSE}
trans.path <- 'Minos/data/transitions/'

educ.mod <- readRDS(paste0(trans.path, 'education_state/nnet/education_state_2018_2019.rds'))
sf_12.mod <- readRDS(paste0(trans.path, 'SF_12/ols/SF_12_2018_2019.rds'))
house.mod <- readRDS(paste0(trans.path, 'housing_quality/clm/housing_quality_2018_2019.rds'))
income.mod <- readRDS(paste0(trans.path, 'hh_income/ols/hh_income_2018_2019.rds'))
```

## Education

```{r}
summary(income.mod)
```

# WIP NONSENSE

```{r}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/MINOS/Minos/data/final_US/', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

correct.files <- list.files('/home/luke/Documents/MINOS/Minos/data/corrected_US/', full.names = TRUE)
correct <- do.call(rbind, lapply(correct.files, read.csv))

```

```{r}
f.sf12 <- raw.dat %>% select(pidp, time, SF_12)
c.sf12 <- correct %>% select(pidp, time, SF_12)

```

Now see if any SF_12 values are missing in either the final data or corrected.

```{r}
sum(is.na(f.sf12$SF_12))
sum(is.na(c.sf12$SF_12))

sum(f.sf12$SF_12 == -9)
sum(c.sf12$SF_12 == -9)

f.drop <- f.sf12 %>% select(-pidp)
c.drop <- c.sf12 %>% select(-pidp)

# missing by year
final.miss <- f.drop %>% 
  group_by(time) %>%
  summarise(final.missing = sum((SF_12 == -9)))

correct.miss <- c.drop %>% 
  group_by(time) %>%
  summarise(correct.missing = sum((SF_12 == -9)))

compare <- merge(final.miss, correct.miss, by='time')
```

### 2023-03-01 minos/validation/interventions.Rmd

---
title: "Investigating Interventions"
output: html_notebook
---

# Setup

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(purrr)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

Source utils for some functions.
```{r}
source('Minos/minos/validation/utils.r')
```

## Data

```{r}
out.path <- 'Minos/output/default_config/'
#out.path <- 'Minos/output/scotland_mode/'

base <- read_output(out.path, 'baseline')
allchild <- read_output(out.path, 'hhIncomeChildUplift')
poverty <- read_output(out.path, 'hhIncomePovertyLineChildUplift')
wage <- read_output(out.path, 'livingWageIntervention')
energy <- read_output(out.path, 'energyDownlift')

```

# Energy Downlift

```{r}
income.base <- base %>% 
  select(pidp, time, hh_income)

income.energy <- energy %>% 
  select(pidp, time, hh_income, income_boosted)

# first rename and cbind
income.b <- rename(income.base, base = hh_income)
income.e <- rename(income.energy, energy = hh_income)

income.merged <- merge(income.b, income.e, by=c('pidp', 'time'))

income.merged <- pivot_longer(data = income.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'hh_income')

income.merged.byyr <- income.merged %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))

ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
  geom_line()
```

## SF_12

```{r}
sf12.base <- base %>% 
  select(pidp, time, SF_12)

sf12.energy <- energy %>% 
  select(pidp, time, SF_12, income_boosted)

# first rename and cbind
sf12.b <- rename(sf12.base, base = SF_12)
sf12.e <- rename(sf12.energy, energy = SF_12)

sf12.merged <- merge(sf12.b, sf12.e, by=c('pidp', 'time'))

sf12.merged <- pivot_longer(data = sf12.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'SF_12')

sf12.merged.byyr <- sf12.merged %>%
  group_by(time, scenario) %>%
  summarise(SF_12 = mean(SF_12))

ggplot(data = sf12.merged.byyr, mapping = aes(x = time, y = SF_12, color=scenario)) +
  geom_line()
```

## Boost Amount

```{r}
income.energy <- energy %>% 
  select(pidp, time, hh_income, income_boosted, boost_amount)

income.energy.byyr <- income.energy %>%
  group_by(time) %>%
  summarise(boost_amount = mean(boost_amount))

ggplot(data = income.energy.byyr, mapping = aes(x = time, y = boost_amount)) +
  geom_line()
```

## Who Boosted?

```{r}
boosted.byyr <- income.energy %>% 
  group_by(time) %>%
  count(income_boosted)

ggplot(data = filter(boosted.byyr, income_boosted == 'True'), mapping = aes(x = time, y = n)) +
  geom_line()
```

# Living Wage

```{r}
income.base <- base %>% 
  select(pidp, time, hh_income)

income.wage <- wage %>% 
  select(pidp, time, hh_income, income_boosted)

# first rename and cbind
income.b <- rename(income.base, base = hh_income)
income.w <- rename(income.wage, wage = hh_income)

income.merged <- merge(income.b, income.w, by=c('pidp', 'time'))

income.merged <- pivot_longer(data = income.merged,
                              cols = base:wage,
                              names_to = 'scenario',
                              values_to = 'hh_income')

income.merged.byyr <- income.merged %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))

ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
  geom_line()
```

```{r}
income.wage <- wage %>% 
  select(pidp, time, hh_income, income_boosted, boost_amount)

income.wage.byyr <- income.wage %>%
  group_by(time) %>%
  summarise(boost_amount = mean(boost_amount))

ggplot(data = income.wage.byyr, mapping = aes(x = time, y = boost_amount)) +
  geom_line()
```

## Who Boosted?

```{r}
boosted.byyr <- income.wage %>% 
  group_by(time) %>%
  count(income_boosted)

ggplot(data = filter(boosted.byyr, income_boosted == 'True'), mapping = aes(x = time, y = n)) +
  geom_line()

ggplot(data = boosted.byyr, mapping = aes(x = time, y = n, color = income_boosted)) +
  geom_line()
```

# All Child Uplift

```{r}
income.base <- base %>% 
  select(pidp, time, hh_income)

income.child <- allchild %>% 
  select(pidp, time, hh_income, income_boosted)

# first rename and cbind
income.base <- rename(income.base, base = hh_income)
income.child <- rename(income.child, allchild = hh_income)

income.merged <- merge(income.base, income.child, by=c('pidp', 'time'))

income.merged <- pivot_longer(data = income.merged,
                              cols = base:allchild,
                              names_to = 'scenario',
                              values_to = 'hh_income')

income.merged.byyr <- income.merged %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))

ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
  geom_line()
```

```{r}
income.child <- allchild %>% 
  select(pidp, time, hh_income, income_boosted, boost_amount)

income.child.byyr <- income.child %>%
  group_by(time) %>%
  summarise(boost_amount = mean(boost_amount))

ggplot(data = income.child.byyr, mapping = aes(x = time, y = boost_amount)) +
  geom_line()
```

## Who Boosted?

```{r}
boosted.byyr <- income.child %>% 
  group_by(time) %>%
  count(income_boosted)

ggplot(data = filter(boosted.byyr, income_boosted == 'True'), mapping = aes(x = time, y = n)) +
  geom_line()

ggplot(data = boosted.byyr, mapping = aes(x = time, y = n, color = income_boosted)) +
  geom_line()
```

```{r}

```

### 2023-03-01 minos/validation/handovers.Rmd
Added some more variable definitions to some makefile targets. Also added titles and axis labels to the handover plots

@@
   group_by(time) %>%
-  summarise(income = weighted.mean(hh_income, weight)) %>%
+  summarise(income = mean(hh_income, na.rm=TRUE)) %>%
   mutate(source = 'final_US')
@@
   group_by(time) %>%
-  summarise(income = weighted.mean(hh_income, weight, na.rm = TRUE)) %>%
+  summarise(income = mean(hh_income)) %>%
   mutate(source = 'baseline_output')
@@
   geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted')
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Household Income', subtitle = 'Full Sample') +
+  xlab('Year') +
+  ylab('Income')
 
@@
   geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted')
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Household Income', subtitle = 'Wave 1 Sample') +
+  xlab('Year') +
+  ylab('Income')
 
@@
   geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted')
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
+  xlab('Year') +
+  ylab('SF12')
 
@@
   geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted')
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Wave 1 Sample') +
+  xlab('Year') +
+  ylab('SF12')
 ```
@@
   geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted')
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Housing Quality', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
 
@@
   geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted')
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Housing Quality', subtitle = 'Proportion') +
+  xlab('Year') +
+  ylab('Proportion')
 
@@
   geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted')
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') +
+  xlab('Year') +
+  ylab('Count')
 
@@
   geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted')
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Loneliness', subtitle = 'Counts by level') +
+  xlab('Year') +
+  ylab('Count')
 
@@
   geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted')
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Loneliness', subtitle = 'Proportion') +
+  xlab('Year') +
+  ylab('Proportion')
 
@@
   geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted')
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Nutrition Quality', subtitle = 'Full Sample') +
+  xlab('Year') +
+  ylab('Nutrition Quality')
 
@@
   geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted')
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Nutrition Quality', subtitle = 'Wave 1 Sample') +
+  xlab('Year') +
+  ylab('Nutrition Quality')
 
@@
   select(pidp, time, phealth) %>%
+  filter(time > 2009) %>%
   group_by(time) %>%
@@
   geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted')
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Physical Health', subtitle = 'Full Sample') +
+  xlab('Year') +
+  ylab('Average')
 
@@
   select(pidp, time, phealth) %>%
+  filter(time > 2009) %>%
   filter(pidp %in% raw.wave1) %>%
@@
   geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted')
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Physical Health', subtitle = 'Wave 1 Sample') +
+  xlab('Year') +
+  ylab('Average')
 
-raw.phealth.check <- raw.dat %>% 
-  select(pidp, time, phealth) %>%
-  filter(pidp %in% raw.wave1)
+#raw.phealth.check <- raw.dat %>% 
+#  select(pidp, time, phealth) %>%
+#  filter(time > 2009) %>%
+#  filter(pidp %in% raw.wave1)
 
-base.phealth.check <- base.dat %>%
-  select(pidp, time, phealth) %>%
-  filter(pidp %in% raw.wave1)
+#base.phealth.check <- base.dat %>%
+#  select(pidp, time, phealth) %>%
+#  filter(time > 2009) %>%
+#  filter(pidp %in% raw.wave1)
 
-rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, 
-   raw.phealth.check, base.phealth.check, phealth2)
+rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2)
+#rm(raw.phealth.check, base.phealth.check)
 ```

### 2023-03-01 minos/validation/interventions.Rmd
Added plots assessing the how the pathways react to the energy downlift intervention

@@
 require(purrr)
+require(ordinal)
+require(nnet)
+require(pscl)
 
@@
 
+## Transition Models
+
+```{r, include=FALSE}
+trans.path <- 'Minos/data/transitions/'
+
+educ.mod <- readRDS(paste0(trans.path, 'education_state/nnet/education_state_2018_2019.rds'))
+sf_12.mod <- readRDS(paste0(trans.path, 'SF_12/ols/SF_12_2018_2019.rds'))
+house.mod <- readRDS(paste0(trans.path, 'housing_quality/clm/housing_quality_2018_2019.rds'))
+income.mod <- readRDS(paste0(trans.path, 'hh_income/ols/hh_income_2018_2019.rds'))
+nut.mod <- readRDS(paste0(trans.path, 'nutrition_quality/ols/nutrition_quality_2018_2019.rds'))
+```
+
 # Energy Downlift
+
+## Household Income
 
@@
 
+## Pathways
+
+### Housing Quality
+
+```{r}
+housing.base <- base %>% 
+  select(pidp, time, housing_quality)
+
+housing.energy <- energy %>% 
+  select(pidp, time, housing_quality, income_boosted)
+
+# first rename and cbind
+housing.b <- rename(housing.base, base = housing_quality)
+housing.e <- rename(housing.energy, energy = housing_quality)
+
+housing.merged <- merge(housing.b, housing.e, by=c('pidp', 'time'))
+
+housing.merged <- pivot_longer(data = housing.merged,
+                              cols = base:energy,
+                              names_to = 'scenario',
+                              values_to = 'housing')
+
+housing.merged.byyr <- housing.merged %>%
+  group_by(time, scenario) %>%
+  summarise(housing = mean(housing))
+
+ggplot(data = housing.merged.byyr, mapping = aes(x = time, y = housing, color=scenario)) +
+  geom_line()
+```
+
+### Neighbourhood Safety
+
+```{r}
+neighbourhood.base <- base %>% 
+  select(pidp, time, neighbourhood_safety)
+
+neighbourhood.energy <- energy %>% 
+  select(pidp, time, neighbourhood_safety, income_boosted)
+
+# first rename and cbind
+neighbourhood.b <- rename(neighbourhood.base, base = neighbourhood_safety)
+neighbourhood.e <- rename(neighbourhood.energy, energy = neighbourhood_safety)
+
+neighbourhood.merged <- merge(neighbourhood.b, neighbourhood.e, by=c('pidp', 'time'))
+
+neighbourhood.merged <- pivot_longer(data = neighbourhood.merged,
+                              cols = base:energy,
+                              names_to = 'scenario',
+                              values_to = 'neighbourhood')
+
+neighbourhood.merged.byyr <- neighbourhood.merged %>%
+  group_by(time, scenario) %>%
+  summarise(neighbourhood = mean(neighbourhood))
+
+ggplot(data = neighbourhood.merged.byyr, mapping = aes(x = time, y = neighbourhood, color=scenario)) +
+  geom_line()
+```
+
+### Tobacco Use
+
+```{r}
+ncigs.base <- base %>% 
+  select(pidp, time, ncigs)
+
+ncigs.energy <- energy %>% 
+  select(pidp, time, ncigs, income_boosted)
+
+# first rename and cbind
+ncigs.b <- rename(ncigs.base, base = ncigs)
+ncigs.e <- rename(ncigs.energy, energy = ncigs)
+
+ncigs.merged <- merge(ncigs.b, ncigs.e, by=c('pidp', 'time'))
+
+ncigs.merged <- pivot_longer(data = ncigs.merged,
+                              cols = base:energy,
+                              names_to = 'scenario',
+                              values_to = 'ncigs')
+
+ncigs.merged.byyr <- ncigs.merged %>%
+  group_by(time, scenario) %>%
+  summarise(ncigs = mean(ncigs))
+
+ggplot(data = ncigs.merged.byyr, mapping = aes(x = time, y = ncigs, color=scenario)) +
+  geom_line()
+```
+
+### Nutrition Quality
+
+```{r}
+nut.base <- base %>% 
+  select(pidp, time, nutrition_quality)
+
+nut.energy <- energy %>% 
+  select(pidp, time, nutrition_quality, income_boosted)
+
+# first rename and cbind
+nut.b <- rename(nut.base, base = nutrition_quality)
+nut.e <- rename(nut.energy, energy = nutrition_quality)
+
+nut.merged <- merge(nut.b, nut.e, by=c('pidp', 'time'))
+
+nut.merged <- pivot_longer(data = nut.merged,
+                              cols = base:energy,
+                              names_to = 'scenario',
+                              values_to = 'nutrition')
+
+nut.merged.byyr <- nut.merged %>%
+  group_by(time, scenario) %>%
+  summarise(nutrition = mean(nutrition))
+
+ggplot(data = nut.merged.byyr, mapping = aes(x = time, y = nutrition, color=scenario)) +
+  geom_line()
+```
+
+### Loneliness (NOT CURRENTLY IN SF12 MODEL)
+
+```{r}
+lnly.base <- base %>% 
+  select(pidp, time, loneliness)
+
+lnly.energy <- energy %>% 
+  select(pidp, time, loneliness, income_boosted)
+
+# first rename and cbind
+lnly.b <- rename(lnly.base, base = loneliness)
+lnly.e <- rename(lnly.energy, energy = loneliness)
+
+lnly.merged <- merge(lnly.b, lnly.e, by=c('pidp', 'time'))
+
+lnly.merged <- pivot_longer(data = lnly.merged,
+                              cols = base:energy,
+                              names_to = 'scenario',
+                              values_to = 'loneliness')
+
+lnly.merged.byyr <- lnly.merged %>%
+  group_by(time, scenario) %>%
+  summarise(loneliness = mean(loneliness))
+
+ggplot(data = lnly.merged.byyr, mapping = aes(x = time, y = loneliness, color=scenario)) +
+  geom_line()
+```
+
 ## Boost Amount
@@
 
+## Household Income
+
 ```{r}
@@
 ```
+
+## Boost Amount
 
@@
 
+# END
+
 ```{r}

### 2023-03-01 minos/validation/interventions.Rmd
Moved the code for visualising pathway variable comparisons between baseline and intervention into functions, and moved these functions into validation/utils.r. Then added pathway plots to the other interventions in interventions.Rmd

--- 2023-03-01 minos/validation/interventions.Rmd
@@
 
+## Pathways
+
+### Housing Quality
+
+```{r}
+compare_housing_out(base, energy)
+```
+
+### Neighbourhood Safety
+
+```{r}
+compare_neighbourhood_out(base, energy)
+```
+
+### Tobacco Use
+
+```{r}
+compare_ncigs_out(base, energy)
+```
+
+### Nutrition Quality
+
+```{r}
+compare_nutrition_out(base, energy)
+```
+
+### Loneliness (NOT CURRENTLY IN SF12 MODEL)
+
+```{r}
+compare_loneliness_out(base, energy)
+```
+
 ## Boost Amount
@@
 ```
+
+## Pathways
+
+```{r}
+compare_housing_out(base, wage)
+compare_neighbourhood_out(base, wage)
+compare_ncigs_out(base, wage)
+compare_nutrition_out(base, wage)
+compare_loneliness_out(base, wage)
+```
+
+## Boost Amount
 
@@
 ```
+
+## Pathways
+
+```{r}
+compare_housing_out(base, allchild)
+compare_neighbourhood_out(base, allchild)
+compare_ncigs_out(base, allchild)
+compare_nutrition_out(base, allchild)
+compare_loneliness_out(base, allchild)
+```
+
+## Boost Amount
 

### 2023-03-01 minos/validation/interventions.Rmd
Added a subtitle to each pathway plot to show which intervention it is showing

@@
 ```{r}
-compare_housing_out(base, energy)
-```
-
-### Neighbourhood Safety
-
-```{r}
-compare_neighbourhood_out(base, energy)
-```
-
-### Tobacco Use
-
-```{r}
-compare_ncigs_out(base, energy)
-```
-
-### Nutrition Quality
-
-```{r}
-compare_nutrition_out(base, energy)
-```
-
-### Loneliness (NOT CURRENTLY IN SF12 MODEL)
-
-```{r}
-compare_loneliness_out(base, energy)
+int.name <- 'Energy'
+compare_housing_out(base, energy, int.name)
+compare_neighbourhood_out(base, energy, int.name)
+compare_ncigs_out(base, energy, int.name)
+compare_nutrition_out(base, energy, int.name)
+compare_loneliness_out(base, energy, int.name)
 ```
@@
 ```{r}
-compare_housing_out(base, wage)
-compare_neighbourhood_out(base, wage)
-compare_ncigs_out(base, wage)
-compare_nutrition_out(base, wage)
-compare_loneliness_out(base, wage)
+int.name <- 'Living Wage'
+compare_housing_out(base, wage, int.name)
+compare_neighbourhood_out(base, wage, int.name)
+compare_ncigs_out(base, wage, int.name)
+compare_nutrition_out(base, wage, int.name)
+compare_loneliness_out(base, wage, int.name)
 ```
@@
 ```{r}
-compare_housing_out(base, allchild)
-compare_neighbourhood_out(base, allchild)
-compare_ncigs_out(base, allchild)
-compare_nutrition_out(base, allchild)
-compare_loneliness_out(base, allchild)
+int.name <- 'All Child'
+compare_housing_out(base, allchild, int.name)
+compare_neighbourhood_out(base, allchild, int.name)
+compare_ncigs_out(base, allchild, int.name)
+compare_nutrition_out(base, allchild, int.name)
+compare_loneliness_out(base, allchild, int.name)
 ```

### 2023-03-01 minos/validation/utils.r

@@ -135,7 +135,9 @@ get_summary_out <- function(scenario_out_path, year, var.list) {
 
 ################# Plotting Pathway Comparisons #################
 
-compare_housing_out <- function(base, int) {
+#TODO: Print out what the values mean with each plot (i.e. housing quality 1,2,3 == ?)
+
+compare_housing_out <- function(base, int, int.name) {
   
   housing.base <- base %>% 
     select(pidp, time, housing_quality)
@@ -160,13 +162,13 @@ compare_housing_out <- function(base, int) {
   
   ggplot(data = housing.merged.byyr, mapping = aes(x = time, y = housing, color=scenario)) +
     geom_line() +
-    labs(title = 'Housing Quality') +
+    labs(title = 'Housing Quality', subtitle = int.name) +
     xlab('Year') +
     ylab('Average')
 }
 
 
-compare_neighbourhood_out <- function(base, int) {
+compare_neighbourhood_out <- function(base, int, int.name) {
   
   neighbourhood.base <- base %>% 
     select(pidp, time, neighbourhood_safety)
@@ -191,13 +193,13 @@ compare_neighbourhood_out <- function(base, int) {
   
   ggplot(data = neighbourhood.merged.byyr, mapping = aes(x = time, y = neighbourhood, color=scenario)) +
     geom_line() +
-    labs(title = 'Neighbourhood Safety') +
+    labs(title = 'Neighbourhood Safety', subtitle = int.name) +
     xlab('Year') +
     ylab('Average')
 }
 
 
-compare_ncigs_out <- function(base, int) {
+compare_ncigs_out <- function(base, int, int.name) {
   ncigs.base <- base %>% 
     select(pidp, time, ncigs)
   
@@ -221,13 +223,13 @@ compare_ncigs_out <- function(base, int) {
   
   ggplot(data = ncigs.merged.byyr, mapping = aes(x = time, y = ncigs, color=scenario)) +
     geom_line() +
-    labs(title = 'Tobacco Use', subtitle = 'Cigarettes per day') +
+    labs(title = 'Tobacco Use', subtitle = int.name) +
     xlab('Year') +
-    ylab('Average')
+    ylab('Average cigs/day')
 }
 
 
-compare_nutrition_out <- function(base, int) {
+compare_nutrition_out <- function(base, int, int.name) {
   nut.base <- base %>% 
     select(pidp, time, nutrition_quality)
   
[…]

### 2023-03-07 minos/validation/cross_validation.Rmd
Added an R notebook for cross validation plots. Currently only looking at the means of hh_income and SF12, before long well want some T-test box plots and pathways stuff

---
title: "Cross Validation Analysis"
output: html_notebook
---

This notebook will compare the results of the cross-validation simulation run with real data from Understanding Society, so that we can evaluate the transition models.

### Method

After generation of the final datasets (final_US), the respondents were separated into 2 roughly equal halves based on their pidp. One half was labelled as the transition dataset, and the other for simulation. Transition models were then fit using the transition dataset, with the other half then simulated with these models.

The results of the simulation will now be compared to the simulation dataset to see how closely our models mimick reality.

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

Source utils for some functions.

```{r}
source('Minos/minos/validation/utils.r')
```

## Data

```{r}
# cross validation simulation output
out.path <- 'Minos/output/cross_validation/'
cv <- read_output(out.path, 'baseline')

# cv simulation pop (not used for transitions)
cv.simul.files <- list.files('Minos/data/final_US/cross_validation/simulation/',
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw <- do.call(rbind, lapply(cv.simul.files, read.csv))
```

# Analysis

First things first, we need to make sure that we are comparing the exact same people from each dataset. Therefore, we need a step here to check the pidps from both, and remove anybody not in both datasets.

```{r}
cv.pidps <- cv %>% select(pidp) %>% unique()
raw.pidps <- raw %>% select(pidp) %>% unique()

both.pidps <- intersect(cv.pidps, raw.pidps)

cv <- cv %>% filter(pidp %in% both.pidps$pidp)
raw <- raw %>% filter(pidp %in% both.pidps$pidp)

#cv2 <- cv[cv$pidp %in% both.pidps]
```

## hh_income

### Mean

```{r}
income.cv <- cv %>% 
  select(pidp, time, hh_income)

income.raw <- raw %>%
  select(pidp, time, hh_income)

# first rename and cbind
income.cv <- rename(income.cv, simulation = hh_income)
income.raw <- rename(income.raw, raw = hh_income)

income.merged <- merge(income.cv, income.raw, by=c('pidp', 'time'))

income.merged <- pivot_longer(data = income.merged,
                              cols = simulation:raw,
                              names_to = 'scenario',
                              values_to = 'hh_income')

income.merged.byyr <- income.merged %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))

ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
  geom_line()
```

### T-test

```{r}

```

## SF12

```{r}
SF_12.cv <- cv %>% 
  select(pidp, time, SF_12)

SF_12.raw <- raw %>%
  select(pidp, time, SF_12)

# first rename and cbind
SF_12.cv <- rename(SF_12.cv, simulation = SF_12)
SF_12.raw <- rename(SF_12.raw, raw = SF_12)

SF_12.merged <- merge(SF_12.cv, SF_12.raw, by=c('pidp', 'time'))

SF_12.merged <- pivot_longer(data = SF_12.merged,
                              cols = simulation:raw,
                              names_to = 'scenario',
                              values_to = 'SF_12')

SF_12.merged.byyr <- SF_12.merged %>%
  group_by(time, scenario) %>%
  summarise(SF_12 = mean(SF_12))

ggplot(data = SF_12.merged.byyr, mapping = aes(x = time, y = SF_12, color=scenario)) +
  geom_line()
```

## Housing Quality

```{r}

```

### 2023-03-08 minos/validation/cross_validation.Rmd
Created functions for processing data (combining multiple sources, pivoting, and summarising), producing plots to compare means, and producing box plots. Also have some code for running t-tests

@@
 raw <- raw %>% filter(pidp %in% both.pidps$pidp)
-
-#cv2 <- cv[cv$pidp %in% both.pidps]
 ```
@@
 ```{r}
-income.cv <- cv %>% 
-  select(pidp, time, hh_income)
+income.pivoted <- combine_and_pivot_long(cv, 'simulated', raw, 'raw', 'hh_income')
 
-income.raw <- raw %>%
-  select(pidp, time, hh_income)
-
-# first rename and cbind
-income.cv <- rename(income.cv, simulation = hh_income)
-income.raw <- rename(income.raw, raw = hh_income)
-
-income.merged <- merge(income.cv, income.raw, by=c('pidp', 'time'))
-
-income.merged <- pivot_longer(data = income.merged,
-                              cols = simulation:raw,
-                              names_to = 'scenario',
-                              values_to = 'hh_income')
-
-income.merged.byyr <- income.merged %>%
+income.merged.byyr <- income.pivoted %>%
   group_by(time, scenario) %>%
@@
 ```{r}
+qqnorm(cv$hh_income)
+qqnorm(raw$hh_income)
 
+# Check variance of both
+cv.inc.var <- var(cv$hh_income)
+raw.inc.var <- var(raw$hh_income, na.rm = TRUE)
+
+# if ratio of largest variance to smallest is less than 4 then assume variance is equal for t.test
+(raw.inc.var / cv.inc.var) < 4
+
+test.t <- t.test(cv$hh_income, raw$hh_income, var.equal = TRUE)
+
+for(year in unique(cv$time)) {
+  print(paste('T tests for year', year))
+  # filter the year
+  tmp.cv <- cv %>% filter(time == year)
+  tmp.raw <- raw %>% filter(time == year)
+
+  # check variance and test for equal variance
+  var.tmp.cv <- var(tmp.cv$hh_income)
+  var.tmp.raw <- var(tmp.raw$hh_income, na.rm = TRUE)
+
+  if(var.tmp.raw > var.tmp.cv) {
+    equal.var <- (var.tmp.cv / var.tmp.raw) < 4
+  } else {
+    equal.var <- (var.tmp.raw / var.tmp.cv) < 4
+  }
+
+  print(t.test(tmp.cv$hh_income, tmp.raw$hh_income, var.equal = equal.var))
+}
+```
+
+```{r}
+compare_boxplot_long(income.pivoted,
+                    var = 'hh_income',
+                    scen1 = 'raw',
+                    scen2 = 'simulation',
+                    subset.max = 5000,
+                    subset.min = -5000)
 ```

### 2023-03-08 minos/validation/cross_validation.Rmd
Functionalised t-test code. Now prints out the summary by year, as well as collecting important information (means, p.value) into a dataframe for a quicker summary. Also added a function to generate boxplots for each year

--- 2023-03-07 minos/validation/cross_validation.Rmd
@@
 
-Source utils for some functions.
-
-```{r}
+```{r, include=FALSE}
 source('Minos/minos/validation/utils.r')
@@
 
-```{r}
+```{r, include=FALSE}
 # cross validation simulation output
@@
 
-### Mean
+```{r}
+income.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                         df1.name = 'simulated', 
+                                         df2 = raw, 
+                                         df2.name = 'raw', 
+                                         var = 'hh_income')
+
+plot_mean_comparison(pivoted.df = income.pivoted, 
+                     var = 'hh_income', 
+                     group.var = 'scenario')
+
+compare_boxplot_long(pivoted.df = income.pivoted,
+                     var = 'hh_income',
+                     scen1 = 'raw',
+                     scen2 = 'simulation',
+                     subset.max = 5000,
+                     subset.min = -5000)
+```
+
+### T-tests
 
 ```{r}
-income.cv <- cv %>% 
-  select(pidp, time, hh_income)
-
-income.raw <- raw %>%
-  select(pidp, time, hh_income)
-
-# first rename and cbind
-income.cv <- rename(income.cv, simulation = hh_income)
-income.raw <- rename(income.raw, raw = hh_income)
-
-income.merged <- merge(income.cv, income.raw, by=c('pidp', 'time'))
-
-income.merged <- pivot_longer(data = income.merged,
-                              cols = simulation:raw,
-                              names_to = 'scenario',
-                              values_to = 'hh_income')
-
-income.merged.byyr <- income.merged %>%
-  group_by(time, scenario) %>%
-  summarise(hh_income = mean(hh_income))
-
-ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
-  geom_line()
+income.t.tests <- two_sample_t_test(cv, 'cv', raw, 'raw', 'hh_income')
+income.t.tests
 ```
 
-### T-test
-
 ```{r}
-
+yearly_box_plots(pivoted.df = income.pivoted,
+                 var = 'hh_income',
+                 scen1 = 'raw',
+                 scen2 = 'simulation',
+                 subset.max = 5000,
+                 subset.min = -5000)
 ```
@@
 ```{r}
-SF_12.cv <- cv %>% 
-  select(pidp, time, SF_12)
+sf12.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw, 
+                                       df2.name = 'raw', 
+                                       var = 'SF_12')
 
-SF_12.raw <- raw %>%
-  select(pidp, time, SF_12)
+plot_mean_comparison(pivoted.df = sf12.pivoted, 
+                     var = 'SF_12', 
+                     group.var = 'scenario')
 
-# first rename and cbind
-SF_12.cv <- rename(SF_12.cv, simulation = SF_12)
-SF_12.raw <- rename(SF_12.raw, raw = SF_12)
+compare_boxplot_long(pivoted.df = sf12.pivoted,
+                     var = 'SF_12',
+                     scen1 = 'raw',
+                     scen2 = 'simulation')
+```
 
-SF_12.merged <- merge(SF_12.cv, SF_12.raw, by=c('pidp', 'time'))
+### T-Tests
 
-SF_12.merged <- pivot_longer(data = SF_12.merged,
-                              cols = simulation:raw,
-                              names_to = 'scenario',
-                              values_to = 'SF_12')
+```{r}
+sf12.t.tests <- two_sample_t_test(cv, 'cv', raw, 'raw', 'hh_income')
+sf12.t.tests
+```
 
-SF_12.merged.byyr <- SF_12.merged %>%
-  group_by(time, scenario) %>%
-  summarise(SF_12 = mean(SF_12))
-
-ggplot(data = SF_12.merged.byyr, mapping = aes(x = time, y = SF_12, color=scenario)) +
-  geom_line()
+```{r}
+yearly_box_plots(pivoted.df = sf12.pivoted,
+                 var = 'SF_12',
+                 scen1 = 'raw',
+                 scen2 = 'simulation')
 ```

### 2023-03-16 minos/validation/handovers.Rmd
Improve the logic for reading in final_US files, so that it ignores any directories in the folder (i.e. cross-validation dir)

@@
 # Read raw datafiles in
-raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', full.names = TRUE)
+raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

### 2023-04-20 minos/validation/equivalent_income_checks.Rmd
Started R script for testing equivalent income

---
title: "Equivalent Income"
output: html_notebook
---

This notebook will visualise the new equivalent income outcome, and do some comparisons to hh_income and potentially also some validation using values from the original spreadsheet created by Chris Wu (where it was first derived).

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

```{r, include=FALSE}
source('Minos/minos/validation/utils.r')
```

# Data

```{r}
# set output path to SIPHER 7 experiment out
out.path <- 'Minos/output/SIPHER7/'
# read all files into dataframe (util function handles runtime subdirectory etc.)
base.dat <- read_output(out.path, 'baseline')
```

# Visualise

## Simple Lineplot

Currently the calculation only happens at the end of a timestep, so the value is 0 in the first year.

```{r}
base.subset <- base.dat %>%
  select(pidp, hidp, time, age, weight, hh_income, equivalent_income, starts_with('S7_'), loneliness) %>%
  group_by(time) %>%
  summarise(mean_household_income = weighted.mean(hh_income, w = weight, na.rm=TRUE),
            mean_equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm=TRUE),
            sd_household_income = sd(hh_income, na.rm=TRUE),
            sd_equivalent_income = sd(equivalent_income, na.rm=TRUE)) %>%
  pivot_longer(cols = mean_household_income:sd_equivalent_income,
               names_sep = '_',
               names_to = c('stat', 'var'),
               values_to = 'value')

## Not ideal pivot_longer as it cuts off everything after the second underscore, however we can still work with it
```

```{r}
base.subset2 <- base.subset %>%
  pivot_wider(names_from = 'stat') %>%
  filter(time > 2020)
```

Now visualise.

```{r}
ggplot(data = base.subset2, aes(x = time, y = mean, group = var, color = var)) +
  geom_line() +
  xlab('Year') +
  ylab('Mean income (£s)') +
  ggtitle('Comparison of Household Income to Equivalent Income')
```

```{r}
ggplot(data = base.subset2, aes(x = time, y = mean, group = var, color = var)) +
  geom_line() +
  geom_ribbon(aes(y = mean, ymin = mean - sd, ymax = mean + sd, fill = var), alpha = .2) +
  xlab('Year') +
  ylab('Mean income (£s)') +
  ggtitle('Comparison of Household Income to Equivalent Income (with sd)')
```

##

### 2023-04-27 minos/outcomes/standard_deviation_change_SF12.Rmd
Changed the utils script to separate out the datain utilities (now in own script). Also changed some function names in the new utils_datain script to be more obvious as to their purpose (some docstring style stuff in there too). Added a new script for testing out some new outcomes visualisations, in standard_deviation_change_SF12.Rmd. More to come

---
title: "Standard Deviation Outcome Change - DEVELOPMENT"
output: html_notebook
---

In this notebook, we will attempt to create a new outcome metric to replace the current metric, which is mean change in SF12. The current metric is difficult to interpret, as we currently have no way to map SF12 to a tangible thing (eventually we should be able to map SF12 changes to QALE's, but this requires properly including SF12 PCS to the model which requires additional modules / pathway changes).

The idea behind this new metric is to count the number of respondents that have a change in SF12 greater than 1 standard deviation, in either direction. We should be able to justify that a change of more than 1 SD is a significant change, and therefore we will have the number of people who had a significant positive response, those who had a significant negative response, and those who had no significant response.

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(ggExtra)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

```{r, include=FALSE}
source('Minos/minos/utils_datain.R')
```

# DATA

For the prototyping phase, we can develop the outcome metric using non-batch runs. We only need 1 baseline run and 1 intervention run for now. To start with therefore, I will use baseline and living wage intervention.

```{r}
out.path <- 'Minos/output/default_config/'

base <- read_singular_local_out(out.path, 'baseline')
int <- read_singular_local_out(out.path, 'livingWageIntervention')
```

# BEGIN

Right, what we want to do is calculate the difference in SF12 between individuals in each scenario. This calculation will have to happen in each year, and then we can calculate the standard deviation of SF12 in the baseline case for each year. After that, we create a simple ordinal variable to determine whether someone has had a significant reduction, significant increase, or no significant change.

STEPS:
- [x] Calculate difference in SF12 between individuals in both scenarios for every year
- [x] Calculate standard deviation for SF12 in the baseline outputs for each year
- [ ] Calculate increase, decrease, or no change
- [ ] Plot

```{r}
# Calculate difference in SF12 between individuals in both scenarios for every year
base.subset <- base %>% 
  select(pidp, time, SF_12) %>%
  rename(SF12.base = SF_12)
int.subset <- int %>% 
  select(pidp, time, income_boosted, SF_12) %>%
  rename(SF12.int = SF_12,
         boosted = income_boosted)

combined <- merge(base.subset, int.subset, by = c('pidp', 'time'))

# IMPORTANT - Must remove the missing values (-8) in both original and intervention
combined <- combined %>% filter(SF12.base != -8.0,
                                SF12.int != -8.0)

# calculate the difference
combined$SF12.diff <- combined$SF12.int - combined$SF12.base

# Now some quick checks
checks <- combined %>%
  group_by(time) %>%
  summarise(n = n(),
            increase = sum(SF12.diff > 0),
            decrease = sum(SF12.diff < 0),
            nochange = sum(SF12.diff == 0))

print(checks)
```

Looks like we have a similar number of people seeing an increase or decrease in SF12. Maybe the numbers for an SD change will be more like what we would expect?

```{r}
# Calculate standard deviation for SF12 in the baseline outputs for each year
# should be easy

sd <- combined %>%
  group_by(time) %>%
  mutate(sd = sd(SF12.base))

#print(sd$sd)

sd <- sd(combined$SF12.base)

print(sd)
```

```{r}
c <- combined

# Calculate increase, decrease, or no change
combined$change[(abs(combined$SF12.diff) > sd) & (combined$SF12.diff > 0)] <- 'increase'
combined$change[(abs(combined$SF12.diff) > sd) & (combined$SF12.diff < 0)] <- 'decrease'
combined$change[combined$SF12.diff < sd] <- 'nochange'

# THINK THERE IS A PROBLEM WITH THE CHECKS2 STUFF BELOW.

# checks
# Now some quick checks
checks2 <- combined %>%
  group_by(time, boosted) %>%
  summarise(n = n(),
            increase = sum(combined$change == 'increase'),
            decrease = sum(combined$change == 'decrease'),
            nochange = sum(combined$change == 'nochange'))

#print(checks2)
```

```{r}
# Calculate increase, decrease, or no change
c$increase <- (abs(c$SF12.diff) > sd) & (c$SF12.diff > 0)
c$decrease <- (abs(c$SF12.diff) > sd) & (c$SF12.diff < 0)
c$nochange <- !(abs(c$SF12.diff) > sd)

c2 <- c %>%
  group_by(time) %>%
  summarise(increase = sum(increase),
            decrease = sum(decrease),
            nochange = sum(nochange))

print(c2)
write.csv(c2, file = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/std_dev_change_living_wage.csv')
```

This isn't a good outcome... We have absolutely tiny numbers of people in both the increase and decrease box, because 1 standard deviation is so large. It also looks as though we'll see roughly equal numbers of people moving up and down, but maybe the group that move up move slightly higher on average? And this causes the mean increase we see? Either way not so pretty.

# Scatterplot w/ Marginal Distributions

Going to go down a different route before I functionalise all the above code. I'm going to try to produce the plot that is associated with the Lord's paradox. I don't know the name of it so it might be quite difficult but we'll have a go with ggplot and ggextra.

```{r}
out.path <- 'Minos/output/default_config/'

base <- read_singular_local_out(out.path, 'baseline')
int <- read_singular_local_out(out.path, 'livingWageIntervention')
```

```{r}
# get just one year
b.2020 <- base %>% filter(time == 2020, SF_12 != -8.0)
b.2030 <- base %>% filter(time == 2030, SF_12 != -8.0)
i.2030 <- int %>% filter(time == 2030, SF_12 != -8.0)
```

```{r}
# get just the SF12 columns
#b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(baseline = SF_12)
#i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(intervention = SF_12)
b.2020 <- b.2020 %>% select(pidp, SF_12) %>% rename(initial = SF_12)
b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
```

```{r}
# combine before we plot
b.2030$scen <- 'baseline'
i.2030$scen <- 'living_wage'

#combined <- merge(b.2030, i.2030, by = 'pidp')
combined <- rbind(b.2030, i.2030)

# now merge with initial
merged <- merge(b.2020, combined, by = 'pidp')
```

```{r}
p <- ggplot(data = merged, aes(x = initial, y = end, group = scen, color = scen)) +
  geom_point() +
  theme(legend.position = c(0.15, 0.9))

p1 <- ggMarginal(p, type='density', groupColour = TRUE)
p1
```

```{r}
p2 <- ggMarginal(p, type='histogram', groupColour = TRUE, xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
p2
```

```{r}
p3 <- ggMarginal(p, type='densigram', groupColour = TRUE, xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
p3
```

### 2023-04-27 minos/validation/equivalent_income_checks.Rmd
Changed the utils script to separate out the datain utilities (now in own script). Also changed some function names in the new utils_datain script to be more obvious as to their purpose (some docstring style stuff in there too). Added a new script for testing out some new outcomes visualisations, in standard_deviation_change_SF12.Rmd. More to come

@@
 require(ggplot2)
+require(readxl)
+require(stringr)
 
@@
 
-##
+## Adapting Chris' Spreadsheet
+
+```{r}
+# Want to remove the one-hot encoding but finding it very difficult in Python
+
+df <- read_excel(path = 'EI_calculation.xlsx')
+```
+
+```{r}
+df2 <- df %>%
+  pivot_longer(cols = phy1:lone3,
+               names_to = 'variable',
+               values_to = 'level')
+```
+
+```{r}
+df3 <- df %>%
+  pivot_longer(cols = -c(pidp, i_hidp, dis_hcost, hh_size, Yc, EI)) %>%
+  filter(value > 0) %>%
+  mutate(level = readr::parse_number(as.character(name)))
+
+df3$name <- gsub("\\d+", "", df3$name)
+
+df3 <- df3 %>% 
+  select(-value) %>%
+  pivot_wider(names_from = 'name',
+              values_from = 'level') %>%
+  rename(S7_physical_health = phy,
+         S7_mental_health = men,
+         loneliness = lone,
+         S7_labour_state = em,
+         S7_housing_quality = hous,
+         S7_neighbourhood_safety = safe) %>%
+
+write.csv(df3, 
+          file = '/home/luke/Documents/WORK/MINOS/EI_calc_prepared.csv')
+
+```

### 2023-04-27 minos/utils_datain.R

@@ -1,0 +1,157 @@
+### This utilities file deals only with reading in and formatting input and output data files
+
+
+# Function to read all output files from a singular (non-batch) local simulation run
+# This will read output files for all years within the latest runtime subdirectory
+# (which is automatically determined)
+# Args: 
+#       out.path - path to top level output directory
+#       scenario - string scenario name of which output files to read
+read_singular_local_out <- function(out.path, scenario) {
+  ## Start with scenario name
+  # attach full output path
+  # get runtime directory
+  # list files
+  # return do.call(...)
+  
+  scen.path <- paste0(out.path, scenario)
+  scen.path <- get_latest_runtime_subdirectory(scen.path)
+  
+  files <- list.files(scen.path,
+                      pattern = '[0-9]{4}.csv',
+                      full.names = TRUE)
+  return(do.call(rbind, lapply(files, read.csv)))
+}
+
+
+# Function to find the latest runtime subdirectory (most recent)
+# Reads all directories in a given path and returns the most recent subdir
+# This requires all folders in the given path to be named with a specific 
+# format, which is a datetime from Year to Second. If any directories in the
+# path are not in this format, the function will fail somewhow.
+# Args: 
+#       path - path to a directory containing runtime subdirectories
+get_latest_runtime_subdirectory <- function(path) {
+  # first select only the path (not filenames)
+  out.folders <- list.files(path)
+  
+  # if more than 1, take the most recent
+  if(length(out.folders) == 1) {
+    path = paste0(path, '/', out.folders[1], '/')
+  }
+  else if(length(out.folders) > 1) {
+    out.folders.date <- as.POSIXlt(out.folders, format='%Y_%m_%d_%H_%M_%S')
+    
+    max.date <- max(out.folders.date)
+    
+    # Collecting these objects here as they have to be formatted
+    yr <- max.date$year + 1900 # year is years since 1900
+    month <- formatC(max.date$mon + 1, width=2, flag='0') # months are zero indexed (WHY??)
+    day <- formatC(max.date$mday, width=2, flag='0')
+    hour <- formatC(max.date$hour, width=2, flag='0')
+    min <- formatC(max.date$min, width=2, flag='0')
+    sec <- formatC(max.date$sec, width=2, flag='0')
+    
+    str.date <- paste0(yr, '_', 
+                       month, '_',  
+                       day, '_',
+                       hour, '_',
+                       min, '_',
+                       sec)
+    
[…]

### 2023-04-27 minos/outcomes/standard_deviation_change_SF12.Rmd
Added smoothed loess lines to the marginal distribution plots, and added knitted RMarkdown html files in outcomes to .gitignore

@@
 base <- read_singular_local_out(out.path, 'baseline')
-int <- read_singular_local_out(out.path, 'livingWageIntervention')
+#int <- read_singular_local_out(out.path, 'livingWageIntervention')
+int <- read_singular_local_out(out.path, 'energyDownlift')
 ```
@@
 b.2030$scen <- 'baseline'
-i.2030$scen <- 'living_wage'
+i.2030$scen <- 'energyDownlift'
 
@@
 p <- ggplot(data = merged, aes(x = initial, y = end, group = scen, color = scen)) +
-  geom_point() +
+  geom_point(alpha = 0.6, size=0.1) +
+  geom_smooth() +
   theme(legend.position = c(0.15, 0.9))
@@
 p1
+
+ggsave(filename = 'scatter_marg_dens_energy.png',
+       plot = p1,
+       path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/')
 ```
@@
 p2
+
+ggsave(filename = 'scatter_marg_hist_energy.png',
+       plot = p2,
+       path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/')
 ```
@@
 p3
+ggsave(filename = 'scatter_marg_densigram_energy.png',
+       plot = p3,
+       path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/')
 ```
+
+```{r}
+
+```

### 2023-04-27 minos/outcomes/standard_deviation_change_SF12.Rmd
Functionalised the marginal density densigram plots, and created a new utils script for outcome visualisation functions

@@
 ```{r}
+# FUNCTION
+SF12_marg_dist_denigram_plot <- function(base, 
+                                         int, 
+                                         int.name, 
+                                         target.year = 2035,
+                                         save = FALSE,
+                                         path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/') {
+  # get just one year
+  b.start <- base %>% filter(time == 2020, SF_12 != -8.0)
+  b.end <- base %>% filter(time == target.year, SF_12 != -8.0)
+  i.end <- int %>% filter(time == target.year, SF_12 != -8.0)
+  # get just the SF12 columns and rename for later
+  b.start <- b.start %>% select(pidp, SF_12) %>% rename(initial = SF_12)
+  b.end <- b.end %>% select(pidp, SF_12) %>% rename(end = SF_12)
+  i.end <- i.end %>% select(pidp, SF_12) %>% rename(end = SF_12)
+
+  # combine before we plot
+  b.end$scen <- 'baseline'
+  i.end$scen <- int.name
+  combined <- rbind(b.end, i.end)
+
+  # now merge with initial
+  merged <- merge(b.start, combined, by = 'pidp')
+
+  p <- ggplot(data = merged, aes(x = initial, y = end, group = scen, color = scen)) +
+    geom_point(alpha = 0.6, size=0.1) +
+    geom_smooth() +
+    theme(legend.position = c(0.15, 0.9))
+
+  p1 <- ggMarginal(p, type='densigram', groupColour = TRUE, xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
+  p1
+
+  plot.name <- paste0('scatter_marg_densigram_', int.name, '.png')
+
+  if(save) {
+    ggsave(filename = plot.name,
+           plot = p1,
+           path = path)
+  }
+
+  print(p1)
+
+  return(p1)
+}
+```
+
+```{r}
 out.path <- 'Minos/output/default_config/'
@@
 ```{r}
+# Test out the new function above
+base <- read_singular_local_out(out.path, 'baseline')
+livWage <- read_singular_local_out(out.path, 'livingWageIntervention')
+energy <- read_singular_local_out(out.path, 'energyDownlift')
+poverty <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift')
+allchild <- read_singular_local_out(out.path, 'hhIncomeChildUplift')
+```
 
+```{r}
+p.livWage <- SF12_marg_dist_denigram_plot(base, 
+                                        livWage, 
+                                        int.name = 'Living Wage',
+                                        target.year = 2030,
+                                        save=TRUE)
+p.energy <- SF12_marg_dist_denigram_plot(base, 
+                                        energy, 
+                                        int.name = 'Energy Downlift',
+                                        target.year = 2030,
+                                        save=TRUE)
+p.poverty <- SF12_marg_dist_denigram_plot(base, 
+                                        poverty, 
+                                        int.name = 'Poverty Child Uplift',
+                                        target.year = 2030,
+                                        save=TRUE)
+p.allchild <- SF12_marg_dist_denigram_plot(base, 
+                                        allchild, 
+                                        int.name = 'Child Uplift',
+                                        target.year = 2030,
+                                        save=TRUE)
 ```

### 2023-04-27 minos/outcomes/standard_deviation_change_SF12.Rmd
Added function for producing marginal distribution plots for a single year (baseline vs intervention). Cleaned up some of the standard_deviation_change_SF12.Rmd script also

--- 2023-04-27 minos/outcomes/standard_deviation_change_SF12.Rmd
@@
 source('Minos/minos/utils_datain.R')
+source('Minos/minos/utils_outcome_vis.R')
 ```
@@
 
+## Workings
+
 ```{r}
@@
 # get just one year
-b.2020 <- base %>% filter(time == 2020, SF_12 != -8.0)
+#b.2020 <- base %>% filter(time == 2020, SF_12 != -8.0)
 b.2030 <- base %>% filter(time == 2030, SF_12 != -8.0)
@@
 # get just the SF12 columns
-#b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(baseline = SF_12)
-#i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(intervention = SF_12)
-b.2020 <- b.2020 %>% select(pidp, SF_12) %>% rename(initial = SF_12)
-b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
-i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
+b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(baseline = SF_12)
+i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(intervention = SF_12)
+#b.2020 <- b.2020 %>% select(pidp, SF_12) %>% rename(initial = SF_12)
+#b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
+#i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
 ```
@@
 # combine before we plot
-b.2030$scen <- 'baseline'
-i.2030$scen <- 'energyDownlift'
+#b.2030$scen <- 'baseline'
+#i.2030$scen <- 'energyDownlift'
 
-#combined <- merge(b.2030, i.2030, by = 'pidp')
-combined <- rbind(b.2030, i.2030)
+combined <- merge(b.2030, i.2030, by = 'pidp')
+#combined <- rbind(b.2030, i.2030)
 
 # now merge with initial
-merged <- merge(b.2020, combined, by = 'pidp')
+#merged <- merge(b.2020, combined, by = 'pidp')
 ```
@@
 ```{r}
-p <- ggplot(data = merged, aes(x = initial, y = end, group = scen, color = scen)) +
+p <- ggplot(data = combined, aes(x = baseline, y = intervention)) +
   geom_point(alpha = 0.6, size=0.1) +
@@
 
-p1 <- ggMarginal(p, type='density', groupColour = TRUE)
+p1 <- ggMarginal(p, type='density')
 p1
 
-ggsave(filename = 'scatter_marg_dens_energy.png',
-       plot = p1,
-       path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/')
+#ggsave(filename = 'scatter_marg_dens_energy.png',
+#       plot = p1,
+#       path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/')
+
+#p5 <- SF12_marg_dist_densigram_plot_oneyear(base,
+#                                           int,
+#                                           int.name = 'Energy Downlift',
+#                                           target.year = 2030)
 ```
@@
 ```{r}
-p2 <- ggMarginal(p, type='histogram', groupColour = TRUE, xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
+p2 <- ggMarginal(p, type='histogram', xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
 p2
@@
 ```{r}
-p3 <- ggMarginal(p, type='densigram', groupColour = TRUE, xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
+p3 <- ggMarginal(p, type='densigram', xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
 p3
@@
 
+## Testing
+
+```{r}
+out.path <- 'Minos/output/default_config/'
+# Test out the new function above
+base <- read_singular_local_out(out.path, 'baseline')
+livWage <- read_singular_local_out(out.path, 'livingWageIntervention')
+energy <- read_singular_local_out(out.path, 'energyDownlift')
+poverty <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift')
+allchild <- read_singular_local_out(out.path, 'hhIncomeChildUplift')
+```
+
+### Initial -> 2030
+
+```{r}
+p.livWage <- SF12_marg_dist_densigram_plot(base, 
+                                        livWage, 
+                                        int.name = 'Living Wage',
+                                        target.year = 2030,
+                                        save=TRUE)
+p.energy <- SF12_marg_dist_densigram_plot(base, 
+                                        energy, 
+                                        int.name = 'Energy Downlift',
+                                        target.year = 2030,
+                                        save=TRUE)
+p.poverty <- SF12_marg_dist_densigram_plot(base, 
+                                        poverty, 
+                                        int.name = 'Poverty Child Uplift',
+                                        target.year = 2030,
+                                        save=TRUE)
+p.allchild <- SF12_marg_dist_densigram_plot(base, 
+                                        allchild, 
+                                        int.name = 'Child Uplift',
+                                        target.year = 2030,
+                                        save=TRUE)
+```
+
+### Single Year
+
+```{r}
+p2.livWage <- SF12_marg_dist_densigram_plot_oneyear(base, 
+                                        livWage,
+                                        int.name = 'Living Wage',
+                                        target.year = 2030,
+                                        save=TRUE)
+p2.energy <- SF12_marg_dist_densigram_plot_oneyear(base, 
+                                        energy, 
+                                        int.name = 'Energy Downlift',
+                                        target.year = 2030,
+                                        save=TRUE)
+p2.poverty <- SF12_marg_dist_densigram_plot_oneyear(base, 
+                                        poverty, 
+                                        int.name = 'Poverty Child Uplift',
+                                        target.year = 2030,
+                                        save=TRUE)
+p2.allchild <- SF12_marg_dist_densigram_plot_oneyear(base, 
+                                        allchild, 
+                                        int.name = 'Child Uplift',
+                                        target.year = 2030,
+                                        save=TRUE)
+```
+
 ```{r}

### 2023-04-27 minos/utils_outcome_vis.R

@@ -21,7 +21,7 @@
 #       target.year - 'end' year to plot
 #       save - Binary, save or not
 #       save.path - path to directory in which to save the plots
-SF12_marg_dist_denigram_plot <- function(base, 
+SF12_marg_dist_densigram_plot <- function(base, 
                                          int, 
                                          int.name, 
                                          target.year = 2035,
@@ -53,6 +53,46 @@ SF12_marg_dist_denigram_plot <- function(base,
   p1
   
   plot.name <- paste0('scatter_marg_densigram_', int.name, '.png')
+  
+  if(save) {
+    ggsave(filename = plot.name,
+           plot = p1,
+           path = save.path)
+  }
+  
+  print(p1)
+  
+  return(p1)
+}
+
+
+# DOCSTRING HERE
+SF12_marg_dist_densigram_plot_oneyear <- function(base, 
+                                                  int,
+                                                  int.name,
+                                                  target.year = 2035,
+                                                  save = FALSE,
+                                                  save.path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/') {
+  # get just one year
+  b.end <- base %>% filter(time == target.year, SF_12 != -8.0)
+  i.end <- int %>% filter(time == target.year, SF_12 != -8.0)
+  # get just the SF12 columns and rename for later
+  b.end <- b.end %>% select(pidp, SF_12) %>% rename(baseline = SF_12)
+  i.end <- i.end %>% select(pidp, SF_12) %>% rename(intervention = SF_12)
+  
+  # combine before we plot
+  combined <- merge(b.end, i.end, by = 'pidp')
+  
+  p <- ggplot(data = combined, aes(x = baseline, y = intervention)) +
+    geom_point(alpha = 0.6, size=0.1) +
+    geom_smooth() +
+    theme(legend.position = c(0.15, 0.9)) +
+    labs(title = paste0(int.name, ' - ', target.year))
+  
+  p1 <- ggMarginal(p, type='densigram', xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
+  p1
+  
+  plot.name <- paste0('scatter_marg_densigram_', int.name, '_ONEYEAR.png')
   
   if(save) {
     ggsave(filename = plot.name,

### 2023-04-28 minos/validation/cross_validation.Rmd
Started R script for testing equivalent income
Changed names of a few functions

@@
 ```{r, include=FALSE}
+source('Minos/minos/utils_datain.R')
 source('Minos/minos/validation/utils.r')
@@
 out.path <- 'Minos/output/cross_validation/'
-cv <- read_output(out.path, 'baseline')
+cv <- read_singular_local_out(out.path, 'baseline')
 

### 2023-05-02 minos/validation/handovers.Rmd
Changed the utils script to separate out the datain utilities (now in own script). Also changed some function names in the new utils_datain script to be more obvious as to their purpose (some docstring style stuff in there too). Added a new script for testing out some new outcomes visualisations, in standard_deviation_change_SF12.Rmd. More to come
Added a save.path variable to handovers.Rmd, and added some calls to ggsave to save figures for adding to the overleaf paper. Also specified dplyr::select for the select functions as a different package was masking the select function

@@
 start.year <- 2020
+
+save.path <- '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Handovers/'
 ```
@@
 raw.income <- raw.dat %>% 
-  select(pidp, time, hh_income, weight) %>%
+  dplyr::select(pidp, time, hh_income, weight) %>%
   group_by(time) %>%
@@
 base.income <- base.dat %>%
-  select(pidp, time, hh_income, weight) %>%
+  dplyr::select(pidp, time, hh_income, weight) %>%
   group_by(time) %>%
@@
 raw.income2 <- raw.dat %>% 
-  select(pidp, time, hh_income) %>%
+  dplyr::select(pidp, time, hh_income) %>%
   filter(pidp %in% raw.income.wave1) %>%
@@
 base.income2 <- base.dat %>%
-  select(pidp, time, hh_income) %>%
+  dplyr::select(pidp, time, hh_income) %>%
   filter(pidp %in% raw.income.wave1) %>%
@@
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Household Income', subtitle = 'Wave 1 Sample') +
+  labs(title = 'Household Income') +
   xlab('Year') +
@@
 
+ggsave(filename = 'hh_income_wav1.png',
+       plot = last_plot(),
+       path = save.path)
+
 raw.income.check <- raw.dat %>% 
-  select(pidp, time, hh_income) %>%
+  dplyr::select(pidp, time, hh_income) %>%
   filter(pidp %in% raw.income.wave1)
@@
 base.income.check <- base.dat %>%
-  select(pidp, time, hh_income) %>%
+  dplyr::select(pidp, time, hh_income) %>%
   filter(pidp %in% raw.income.wave1)
@@
 raw.sf12 <- raw.dat %>% 
-  select(pidp, time, SF_12) %>%
+  dplyr::select(pidp, time, SF_12) %>%
   group_by(time) %>%
@@
 base.sf12 <- base.dat %>%
-  select(pidp, time, SF_12) %>%
+  dplyr::select(pidp, time, SF_12) %>%
   group_by(time) %>%
@@
 raw.sf12.2 <- raw.dat %>% 
-  select(pidp, time, SF_12) %>%
+  dplyr::select(pidp, time, SF_12) %>%
   filter(pidp %in% raw.sf12.wave1) %>%
@@
 base.sf12.2 <- base.dat %>%
-  select(pidp, time, SF_12) %>%
+  dplyr::select(pidp, time, SF_12) %>%
   filter(pidp %in% raw.sf12.wave1) %>%
@@
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Wave 1 Sample') +
+  labs(title = 'Mental Wellbeing (SF12 MCS)') +
   xlab('Year') +
   ylab('SF12')
+
+ggsave(filename = 'SF12_wav1.png',
+       plot = last_plot(),
+       path = save.path)
 ```
@@
 raw.housing <- raw.dat %>% 
-  select(pidp, time, housing_quality) %>%
+  dplyr::select(pidp, time, housing_quality) %>%
   group_by(time, housing_quality) %>%
@@
 base.housing <- base.dat %>%
-  select(pidp, time, housing_quality) %>%
+  dplyr::select(pidp, time, housing_quality) %>%
   group_by(time, housing_quality) %>%
@@
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Quality', subtitle = 'Proportion') +
+  labs(title = 'Housing Quality') +
   xlab('Year') +
   ylab('Proportion')
+
+ggsave(filename = 'housing_quality.png',
+       plot = last_plot(),
+       path = save.path)
 
@@
 raw.neighbour <- raw.dat %>% 
-  select(pidp, time, neighbourhood_safety) %>%
+  dplyr::select(pidp, time, neighbourhood_safety) %>%
   group_by(time, neighbourhood_safety) %>%
@@
 base.neighbour <- base.dat %>%
-  select(pidp, time, neighbourhood_safety) %>%
+  dplyr::select(pidp, time, neighbourhood_safety) %>%
   group_by(time, neighbourhood_safety) %>%
@@
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Quality', subtitle = 'Proportion') +
+  labs(title = 'Neighbourhood Safety') +
   xlab('Year') +
   ylab('Proportion')
+
+ggsave(filename = 'neighbourhood_safety.png',
+       plot = last_plot(),
+       path = save.path)
 
@@
 raw.loneliness <- raw.dat %>% 
-  select(pidp, time, loneliness) %>%
+  dplyr::select(pidp, time, loneliness) %>%
   group_by(time, loneliness) %>%
@@
 base.loneliness <- base.dat %>%
-  select(pidp, time, loneliness) %>%
+  dplyr::select(pidp, time, loneliness) %>%
   group_by(time, loneliness) %>%
@@
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Loneliness', subtitle = 'Proportion') +
+  labs(title = 'Loneliness') +
   xlab('Year') +
   ylab('Proportion')
+
+ggsave(filename = 'loneliness.png',
+       plot = last_plot(),
+       path = save.path)
 
@@
 raw.nut <- raw.dat %>% 
-  select(pidp, time, nutrition_quality) %>%
+  dplyr::select(pidp, time, nutrition_quality) %>%
   group_by(time) %>%
@@
 base.nut <- base.dat %>%
-  select(pidp, time, nutrition_quality) %>%
+  dplyr::select(pidp, time, nutrition_quality) %>%
   group_by(time) %>%
@@
 raw.nut2 <- raw.dat %>% 
-  select(pidp, time, nutrition_quality) %>%
+  dplyr::select(pidp, time, nutrition_quality) %>%
   filter(pidp %in% raw.wave1) %>%
@@
 base.nut2 <- base.dat %>%
-  select(pidp, time, nutrition_quality) %>%
+  dplyr::select(pidp, time, nutrition_quality) %>%
   filter(pidp %in% raw.wave1) %>%
@@
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Nutrition Quality', subtitle = 'Wave 1 Sample') +
+  labs(title = 'Nutrition Quality') +
   xlab('Year') +
   ylab('Nutrition Quality')
+
+ggsave(filename = 'nutrition_quality_wav1.png',
+       plot = last_plot(),
+       path = save.path)
 
@@
 raw.phealth <- raw.dat %>% 
-  select(pidp, time, phealth) %>%
+  dplyr::select(pidp, time, phealth) %>%
   filter(time > 2009) %>%
@@
 base.phealth <- base.dat %>%
-  select(pidp, time, phealth) %>%
+  dplyr::select(pidp, time, phealth) %>%
   filter(time > 2009) %>%
@@
 raw.phealth2 <- raw.dat %>% 
-  select(pidp, time, phealth) %>%
+  dplyr::select(pidp, time, phealth) %>%
   filter(time > 2009) %>%
@@
 base.phealth2 <- base.dat %>%
-  select(pidp, time, phealth) %>%
+  dplyr::select(pidp, time, phealth) %>%
   filter(time > 2009) %>%
@@
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health', subtitle = 'Wave 1 Sample') +
+  labs(title = 'Physical Health') +
   xlab('Year') +
   ylab('Average')
+
+ggsave(filename = 'physical_health_wav1.png',
+       plot = last_plot(),
+       path = save.path)
 

### 2023-05-03 minos/validation/cross_validation.Rmd
Created functions for visualising cross-validation comparisons of ordinal outputs in utils.r, and wrote them into the RNotebook for all the ordinal vars

--- 2023-03-08 minos/validation/cross_validation.Rmd
@@
 
-### Method
+# Method
 
@@
                      var = 'hh_income', 
-                     group.var = 'scenario')
+                     group.var = 'scenario',
+                     save = TRUE,
+                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
 
@@
                      var = 'SF_12', 
-                     group.var = 'scenario')
+                     group.var = 'scenario',
+                     save = TRUE,
+                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
 
@@
 
+## Nutrition Quality
+
+```{r}
+nut.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw, 
+                                       df2.name = 'raw', 
+                                       var = 'nutrition_quality')
+
+plot_mean_comparison(pivoted.df = nut.pivoted, 
+                     var = 'nutrition_quality', 
+                     group.var = 'scenario',
+                     save = TRUE,
+                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
+
+compare_boxplot_long(pivoted.df = nut.pivoted,
+                     var = 'nutrition_quality',
+                     scen1 = 'raw',
+                     scen2 = 'simulation')
+```
+
+```{r}
+yearly_box_plots(pivoted.df = nut.pivoted,
+                 var = 'nutrition_quality',
+                 scen1 = 'raw',
+                 scen2 = 'simulation')
+```
+
+## Tobacco Use
+
+```{r}
+tobacco.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw, 
+                                       df2.name = 'raw', 
+                                       var = 'ncigs')
+
+plot_mean_comparison(pivoted.df = tobacco.pivoted, 
+                     var = 'ncigs', 
+                     group.var = 'scenario',
+                     save = TRUE,
+                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
+
+compare_boxplot_long(pivoted.df = tobacco.pivoted,
+                     var = 'ncigs',
+                     scen1 = 'raw',
+                     scen2 = 'simulation')
+
+compare_boxplot_long(pivoted.df = tobacco.pivoted,
+                     var = 'ncigs',
+                     scen1 = 'raw',
+                     scen2 = 'simulation',
+                     subset.max = 100,
+                     subset.min = 0)
+```
+
+```{r}
+yearly_box_plots(pivoted.df = tobacco.pivoted,
+                 var = 'ncigs',
+                 scen1 = 'raw',
+                 scen2 = 'simulation',
+                 subset.max = 100,
+                 subset.min = 0)
+```
+
 ## Housing Quality
+
+```{r}
+hous.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw, 
+                                       df2.name = 'raw', 
+                                       var = 'housing_quality')
+
+cv_ordinal_plots(pivoted.df = hous.pivoted, 
+                 var = 'housing_quality',
+                 save = TRUE,
+                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
+```
+
+## Neighbourhood Safety
+
+```{r}
+nhsafe.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'neighbourhood_safety')
+
+cv_ordinal_plots(pivoted.df = nhsafe.pivoted, 
+                 var = 'neighbourhood_safety',
+                 save = TRUE,
+                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
+```
+
+## Loneliness
+
+```{r}
+lnly.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'loneliness')
+
+cv_ordinal_plots(pivoted.df = lnly.pivoted, 
+                 var = 'loneliness',
+                 save = TRUE,
+                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
+```
 

### 2023-05-03 minos/validation/utils.r

@@ -75,14 +75,31 @@ combine_and_pivot_long <- function(df1, df1.name, df2, df2.name, var) {
 
 # Function to plot the means of a single variable from 2 different datasets
 # The 2 datasets must either be input data (i.e. final_US) or simulated output
-plot_mean_comparison <- function(pivoted.df, var, group.var) {
+plot_mean_comparison <- function(pivoted.df, var, group.var, save=FALSE, save.path=NULL) {
   merged.byyr <- pivoted.df %>%
+    filter(.data[[var]] != -9) %>%
     group_by(time, .data[[group.var]]) %>%
     summarise(var = mean(.data[[var]]))
   
-  ggplot(data = merged.byyr, mapping = aes(x = time, y = var, color=scenario)) +
+  p <- ggplot(data = merged.byyr, mapping = aes(x = time, y = var, color=scenario)) +
     geom_line() +
-    ylab(var)
+    labs(title = paste0('Cross-Validation: ', var)) +
+    ylab('Mean') +
+    xlab('Year')
+  
+  print(p)
+  
+  if(save) {
+    if(is.null(save.path)) {
+      stop('ERROR: save.path must be defined when saving the plot')
+    }
+    save.filename <- paste0('cv_', var, '_continuous.png')
+    ggsave(filename = save.filename,
+           plot = p,
+           path = save.path,
+           width = 9,
+           height = 5)
+  }
 }
 
 
@@ -170,6 +187,65 @@ two_sample_t_test <- function(df1, df1.name, df2, df2.name, var) {
     df <- rbind(df, new.df)
   }
   return(df)
+}
+
+# Function to plot both count and proportion comparisons between raw and 
+# simulated data using cross-validation outputs.
+cv_ordinal_plots <- function(pivoted.df, var, save=FALSE, save.path) {
+  df <- pivoted.df %>%
+    group_by(time, scenario, .data[[var]]) %>%
+    summarise(n = n())
+  
+  df$scenario <- factor(df$scenario)
+  df[[var]] <- factor(df[[var]])
+  
+  df <- df %>% filter(.data[[var]] != -9)
+  
+  p1 <- ggplot(data = df, aes(x = time, y = n, group = interaction(scenario, .data[[var]]), color = .data[[var]], linetype = scenario)) +
+    geom_line() + 
+    geom_point() +
+    labs(title = paste0('Cross-Validation: ', var), subtitle = 'Count') +
+    xlab('Year') +
+    ylab('Count')
+  
+  print(p1)
[…]

### 2023-05-04 minos/outcomes/equivalent_income_out.Rmd
Created an RNotebook for visualising outputs from equivalent income scenarios, including comparisons of equivalent income between interventions and baseline for both the full population and treated population

---
title: "Equivalent Income Outcome Visualisation"
output: html_notebook
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)

workingDir <- "/home/luke/Documents/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

```{r, include=FALSE}
source('Minos/minos/validation/utils.r')
```

# Data

```{r}
# set output path to SIPHER 7 experiment out
out.path <- 'Minos/output/SIPHER7/'
# read all files into dataframe (util function handles runtime subdirectory etc.)
base.dat <- read_output(out.path, 'baseline')
allchild.dat <- read_output(out.path, 'hhIncomeChildUplift')
pov.dat <- read_output(out.path, 'hhIncomePovertyLineChildUplift')
wage.dat <- read_output(out.path, 'livingWageIntervention')
energy.dat <- read_output(out.path, 'energyDownlift')
```

# Baseline

```{r}
base.subset <- base.dat %>%
  select(pidp, time, equivalent_income) %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income))

base.subset$scenario <- 'Baseline'

ggplot(data = base.subset, aes(x = time, y = equivalent_income)) +
  geom_line()
```

# Comparisons

## Function

```{r}
equivalent_income_comparison_fullpop <- function(base, int, int.name, save=FALSE, save.path=NULL) {
  base.subset <- base %>%
    select(pidp, time, equivalent_income, alive) %>%
    filter(alive != 'dead') %>%
    group_by(time) %>%
    summarise(equivalent_income = mean(equivalent_income))
  int.subset <- int %>%
    select(pidp, time, equivalent_income, alive) %>%
    filter(alive != 'dead') %>%
    group_by(time) %>%
    summarise(equivalent_income = mean(equivalent_income))

  base.subset$scenario <- 'Baseline'
  int.subset$scenario <- int.name

  combined <- rbind(base.subset, int.subset)

  p <- ggplot(combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
    geom_line() +
    labs(title = paste0('Equivalent Income: ', int.name), subtitle = 'Full Population') +
    xlab('Year') +
    ylab('Equivalent Income (£)')

  print(p)

  if(save) {
    if(is.null(save.path)) {
      stop('ERROR: save.path cannot be missing if save=TRUE')
    }
    file.name <- paste0('EI_comp_', int.name, '_full.png')
    ggsave(filename = file.name,
           plot = p,
           path = save.path)
  }
}
```

## Plots

```{r}
equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
```

## Combined

```{r}
base.subset <- base.dat %>%
  select(pidp, time, equivalent_income, alive) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income))
base.subset$scenario <- 'Baseline'

allchild.subset <- allchild.dat %>%
  select(pidp, time, equivalent_income, alive) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income))
allchild.subset$scenario <- 'AllChild'

pov.subset <- pov.dat %>%
  select(pidp, time, equivalent_income, alive) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income))
pov.subset$scenario <- 'PovertyChild'

wage.subset <- wage.dat %>%
  select(pidp, time, equivalent_income, alive) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income))
wage.subset$scenario <- 'LivingWage'

energy.subset <- energy.dat %>%
  select(pidp, time, equivalent_income, alive) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income))
energy.subset$scenario <- 'EnergyDownlift'

all.combined <- rbind(base.subset, allchild.subset, pov.subset, wage.subset, energy.subset)
all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'AllChild', 'PovertyChild', 'LivingWage', 'EnergyDownlift'))

ggplot(data = all.combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
  geom_line() +
  labs(title = 'Equivalent Income Comparison', subtitle = 'Whole Population') +
  xlab('Year') +
  ylab('Equivalent Income (£)')
```

# Treatment on the Treated

## Function

```{r}
equivalent_income_comparison_treated <- function(base, int, int.name, save=FALSE, save.path=NULL) {
  base.sub <- base.dat %>%
    select(pidp, time, equivalent_income, alive) %>%
    filter(alive != 'dead') %>%
    select(-alive) %>%
    rename(baseline = equivalent_income)
  int.sub <- int %>%
    select(pidp, time, equivalent_income, income_boosted, alive) %>%
    filter(alive != 'dead') %>%
    select(-alive) %>%
    set_names(c('pidp', 'time', int.name, 'income_boosted'))

  merged <- merge(base.sub, int.sub, by = c('pidp', 'time'))

  boosted.pidps <- int.sub %>%
    filter(income_boosted == 'True') %>%
    select(pidp)

  boosted <- merged %>%
    filter(pidp %in% boosted.pidps$pidp) %>%
    filter(income_boosted == 'True' | time == 2020) %>%
    select(-income_boosted) %>%
    pivot_longer(cols = baseline:.data[[int.name]],
                 names_to = 'scenario',
                 values_to = 'equivalent_income') %>%
    group_by(time, scenario) %>%
    summarise(equivalent_income = mean(equivalent_income))

  p <- ggplot(data = boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
    geom_line() +
    labs(title = paste0('Equivalent Income: ', int.name), subtitle = 'Treated Population') +
    xlab('Year') +
    ylab('Equivalent Income (£)')

  print(p)

  if(save) {
    if(is.null(save.path)) {
      stop('ERROR: save.path cannot be missing if save=TRUE')
    }
    file.name <- paste0('EI_comp_', int.name, '_treated.png')
    ggsave(filename = file.name,
           plot = p,
           path = save.path)
  }
}
```

## AllChild

```{r}
equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
```

# Remove Income Effect

```{r}
# THink about this...
# We can use the income_boosted and boost_amount variables to remove the income boost from people and visualise that

base.sub2 <- base.dat %>%
  select(pidp, time, equivalent_income, alive) %>%
  filter(alive != 'dead') %>%
  select(-alive) %>%
  rename(baseline = equivalent_income)

allchild.sub2 <- allchild.dat %>%
  select(pidp, time, equivalent_income, income_boosted, boost_amount, alive) %>%
  filter(alive != 'dead') %>%
  select(-alive) %>%
  rename(allchild = equivalent_income)

allchild.merged <- merge(base.sub2, allchild.sub2, by = c('pidp', 'time'))

boosted.pidps <- allchild.sub2 %>%
  filter(income_boosted == 'True') %>%
  select(pidp)

allchild.boosted <- allchild.merged %>%
  filter(pidp %in% boosted.pidps$pidp) %>%
  filter(income_boosted == 'True' | time == 2020) %>%
  mutate(adjusted_EI = allchild - boost_amount) %>%
  select(-allchild, -income_boosted, -boost_amount) %>%
  group_by(time) %>%
  summarise(baseline = mean(baseline),
            allchild_adj = mean(adjusted_EI)) %>%
  pivot_longer(cols = baseline:allchild_adj,
               names_to = 'scenario',
               values_to = 'equivalent_income')

ggplot(data = allchild.boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
  geom_line()

```

NOTE: Can we 'remove' the income effect?
Use the boost amount and income_boosted variables to sort of 'undo' the intervention effect and then we are only visualising the difference from pathway changes and not just the income effect.

ALSO: Difference plots.

### 2023-05-05 minos/validation/mwb_pathways.Rmd
Small path changes to existing scripts, and added a notebook for investigating interventions

@@
 ```{r}
-source('R_Scripts/utils.r')
+source('Minos/minos/utils_datain.R')
 ```
@@
 baseline.path <- paste0(output.path, 'baseline')
-base.path <- get_runtime_subdirectory(baseline.path)
+base.path <- get_latest_runtime_subdirectory(baseline.path)
 

### 2023-05-16 minos/validation/cross_validation.Rmd
Changed order of modules in the cross_validation.yaml file (probably doesnt matter but did it anyway). Added another plot to the cross_validation Rmd script just showing box plots of hh_income with no min max subsetting (did that in another plot as the outliers dominate the plot if not)
Renamed all instances of SF_12 to SF_12_MCS, and added the SF_12_PCS variable. Also created a PCS module, and tried to modify the outcome visualisation stuff but made some mistakes so still WIP. Handovers work, but cross-validation also still has some issues

@@
 
-## SF12
+## SF12_MCS
 
 ```{r}
-sf12.pivoted <- combine_and_pivot_long(df1 = cv, 
+sf12.m.pivoted <- combine_and_pivot_long(df1 = cv, 
                                        df1.name = 'simulated', 
@@
                                        df2.name = 'raw', 
-                                       var = 'SF_12')
+                                       var = 'SF_12_MCS')
 
-plot_mean_comparison(pivoted.df = sf12.pivoted, 
-                     var = 'SF_12', 
+plot_mean_comparison(pivoted.df = sf12.m.pivoted, 
+                     var = 'SF_12_MCS', 
                      group.var = 'scenario',
@@
 
-compare_boxplot_long(pivoted.df = sf12.pivoted,
-                     var = 'SF_12',
+compare_boxplot_long(pivoted.df = sf12.m.pivoted,
+                     var = 'SF_12_MCS',
                      scen1 = 'raw',
@@
 ```{r}
-sf12.t.tests <- two_sample_t_test(cv, 'cv', raw, 'raw', 'hh_income')
-sf12.t.tests
+sf12.m.t.tests <- two_sample_t_test(cv, 'cv', raw, 'raw', 'SF_12_MCS')
+sf12.m.t.tests
 ```
@@
 ```{r}
-yearly_box_plots(pivoted.df = sf12.pivoted,
-                 var = 'SF_12',
+yearly_box_plots(pivoted.df = sf12.m.pivoted,
+                 var = 'SF_12_MCS',
+                 scen1 = 'raw',
+                 scen2 = 'simulation')
+```
+
+## SF_12_PCS
+
+```{r}
+sf12.p.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw, 
+                                       df2.name = 'raw', 
+                                       var = 'SF_12_PCS')
+
+plot_mean_comparison(pivoted.df = sf12.p.pivoted, 
+                     var = 'SF_12_PCS', 
+                     group.var = 'scenario',
+                     save = TRUE,
+                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
+
+compare_boxplot_long(pivoted.df = sf12.p.pivoted,
+                     var = 'SF_12_PCS',
+                     scen1 = 'raw',
+                     scen2 = 'simulation')
+```
+
+### T-tests
+
+```{r}
+sf12.p.t.tests <- two_sample_t_test(cv, 'cv', raw, 'raw', 'SF_12_PCS')
+sf12.p.t.tests
+```
+
+```{r}
+yearly_box_plots(pivoted.df = sf12.p.pivoted,
+                 var = 'nutrition_quality',
                  scen1 = 'raw',

### 2023-05-16 minos/validation/handovers.Rmd
Renamed all instances of SF_12 to SF_12_MCS, and added the SF_12_PCS variable. Also created a PCS module, and tried to modify the outcome visualisation stuff but made some mistakes so still WIP. Handovers work, but cross-validation also still has some issues

@@
 ```{r}
-source('Minos/minos/validation/utils.r')
+source('Minos/minos/utils_datain.R')
+```
+
+```{r, include=FALSE}
+start.year <- 2020
+
+save.path <- '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Handovers/'
 ```
@@
 out.path <- 'Minos/output/default_config/'
-base.dat <- read_output(out.path, 'baseline')
-```
-
-## Constants
-
-```{r}
-start.year <- 2020
-
-save.path <- '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Handovers/'
+base.dat <- read_singular_local_out(out.path, 'baseline')
 ```
@@
 
-## SF12
+## SF_12_MCS
 
@@
 # start with hh_income
-raw.sf12 <- raw.dat %>% 
-  dplyr::select(pidp, time, SF_12) %>%
+raw.sf12.m <- raw.dat %>% 
+  dplyr::select(pidp, time, SF_12_MCS) %>%
+  filter(SF_12_MCS > 0) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'final_US')
 
-base.sf12 <- base.dat %>%
-  dplyr::select(pidp, time, SF_12) %>%
+base.sf12.m <- base.dat %>%
+  dplyr::select(pidp, time, SF_12_MCS) %>%
+  filter(SF_12_MCS > 0) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'baseline_output')
@@
 # merge before plot
-sf12 <- rbind(raw.sf12, base.sf12)
+sf12.m <- rbind(raw.sf12.m, base.sf12.m)
 
 # Now plot
-ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+ggplot(data = sf12.m, mapping = aes(x = time, y = sf12.m, group = source, colour = source)) +
   geom_line() +
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
+  labs(title = 'Mental Wellbeing (SF12_MCS)', subtitle = 'Full Sample') +
   xlab('Year') +
-  ylab('SF12')
+  ylab('SF12_MCS')
 
@@
 # onwards because the sample refreshments are messing with the plot
-raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+raw.sf12.m.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
 
-raw.sf12.2 <- raw.dat %>% 
-  dplyr::select(pidp, time, SF_12) %>%
-  filter(pidp %in% raw.sf12.wave1) %>%
+raw.sf12.m.2 <- raw.dat %>% 
+  dplyr::select(pidp, time, SF_12_MCS) %>%
+  filter(SF_12_MCS > 0) %>%
+  filter(pidp %in% raw.sf12.m.wave1) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'final_US')
 
-base.sf12.2 <- base.dat %>%
-  dplyr::select(pidp, time, SF_12) %>%
-  filter(pidp %in% raw.sf12.wave1) %>%
+base.sf12.m.2 <- base.dat %>%
+  dplyr::select(pidp, time, SF_12_MCS) %>%
+  filter(SF_12_MCS > 0) %>%
+  filter(pidp %in% raw.sf12.m.wave1) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'baseline_output')
 
-sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
+sf12.m.2 <- rbind(raw.sf12.m.2, base.sf12.m.2)
 
 # Now plot
-ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+ggplot(data = sf12.m.2, mapping = aes(x = time, y = sf12.m, group = source, colour = source)) +
   geom_line() +
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Mental Wellbeing (SF12 MCS)') +
+  labs(title = 'Mental Wellbeing (SF12_MCS)') +
   xlab('Year') +
-  ylab('SF12')
+  ylab('SF12_MCS')
 
-ggsave(filename = 'SF12_wav1.png',
+ggsave(filename = 'SF12_MCS_wav1.png',
+       plot = last_plot(),
+       path = save.path)
+```
+
+## SF_12_PCS
+
+```{r}
+# first figure out how to plot final_US
+# start with hh_income
+raw.sf12.p <- raw.dat %>% 
+  dplyr::select(pidp, time, SF_12_PCS) %>%
+  filter(SF_12_PCS > 0) %>%
+  group_by(time) %>%
+  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
+  mutate(source = 'final_US')
+
+base.sf12.p <- base.dat %>%
+  dplyr::select(pidp, time, SF_12_PCS) %>%
+  filter(SF_12_PCS > 0) %>%
+  group_by(time) %>%
+  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+sf12.p <- rbind(raw.sf12.p, base.sf12.p)
+
+# Now plot
+ggplot(data = sf12.p, mapping = aes(x = time, y = sf12.p, group = source, colour = source)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Physical Wellbeing (SF12_PCS)', subtitle = 'Full Sample') +
+  xlab('Year') +
+  ylab('SF12_PCS')
+
+## Try a version where final_US is limited to only those present from wave 1 
+# onwards because the sample refreshments are messing with the plot
+raw.sf12.p.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+
+raw.sf12.p.2 <- raw.dat %>% 
+  dplyr::select(pidp, time, SF_12_PCS) %>%
+  filter(SF_12_PCS > 0) %>%
+  filter(pidp %in% raw.sf12.p.wave1) %>%
+  group_by(time) %>%
+  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
+  mutate(source = 'final_US')
+
+base.sf12.p.2 <- base.dat %>%
+  dplyr::select(pidp, time, SF_12_PCS) %>%
+  filter(SF_12_PCS > 0) %>%
+  filter(pidp %in% raw.sf12.p.wave1) %>%
+  group_by(time) %>%
+  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
+  mutate(source = 'baseline_output')
+
+sf12.p.2 <- rbind(raw.sf12.p.2, base.sf12.p.2)
+
+# Now plot
+ggplot(data = sf12.p.2, mapping = aes(x = time, y = sf12.p, group = source, colour = source)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Physical Wellbeing (SF12_PCS)') +
+  xlab('Year') +
+  ylab('SF12_PCS')
+
+ggsave(filename = 'SF12_PCS_wav1.png',
        plot = last_plot(),

### 2023-05-16 minos/modules/replenishment.py

@@ -53,7 +53,7 @@ class Replenishment(Base):
                         'birth_year',
                         'nobs',
                         'region',
-                        'SF_12',
+                        'SF_12_MCS',
                         'hh_int_y',
                         'hh_int_m',
                         'Date',
@@ -70,7 +70,7 @@ class Replenishment(Base):
                         'max_educ',
                         'yearly_energy',
                         'job_sector',
-                        'SF_12p',
+                        'SF_12_PCS',
                         'gross_pay_se',
                         'nutrition_quality',
                         'job_hours_se',
@@ -265,7 +265,7 @@ class NoReplenishment(Base):
                         'birth_year',
                         'nobs',
                         'region',
-                        'SF_12',
+                        'SF_12_MCS',
                         'hh_int_y',
                         'hh_int_m',
                         'Date',
@@ -282,7 +282,7 @@ class NoReplenishment(Base):
                         'max_educ',
                         'yearly_energy',
                         'job_sector',
-                        'SF_12p',
+                        'SF_12_PCS',
                         'gross_pay_se',
                         'nutrition_quality',
                         'job_hours_se',

### 2023-05-16 minos/modules/replenishment_nowcast.py

@@ -44,7 +44,7 @@ class ReplenishmentNowcast(Base):
                         'birth_year',
                         'nobs',
                         'region',
-                        'SF_12',
+                        'SF_12_MCS',
                         'hh_int_y',
                         'hh_int_m',
                         'Date',
@@ -61,7 +61,7 @@ class ReplenishmentNowcast(Base):
                         'max_educ',
                         'yearly_energy',
                         'job_sector',
-                        'SF_12p',
+                        'SF_12_PCS',
                         'gross_pay_se',
                         'nutrition_quality',
                         'job_hours_se',

### 2023-05-16 minos/outcomes/aggregate_minos_output.py

@@ -87,7 +87,7 @@ def main(source, mode, years, tag, v, method, subset_function_string):
     tag: list
         Corresponding name of the MINOS batch source. Usually what intervention was used. Baseline Uplift, etc..
     v: str
-        What variable to aggregate on. Defaults to SF_12
+        What variable to aggregate on. Defaults to SF_12_MCS
     method: func
         What function to aggregate over. Default np.nanmean.
     destination: str
@@ -115,7 +115,7 @@ if __name__ == '__main__':
                         help="Subdirectories within source that are aggregated. Usually experiment names baseline childUplift etc.")
     parser.add_argument("-t", "--tags", required=True, type=str,
                         help="Corresponding name tags for which data is being processed. I.E which intervention Baseline/£20 Uplift etc. Used as label in later plots.")
-    parser.add_argument("-v", "--variable", required=False, type=str, default='SF_12',
+    parser.add_argument("-v", "--variable", required=False, type=str, default='SF_12_MCS',
                         help="What variable from Minos is being aggregated. Defaults to SF12.")
     parser.add_argument("-a", "--aggregate_method", required=False, type=str, default="nanmean",
                         help="What method is used to aggregate population. Defaults to np.nanmean.")

### 2023-05-16 minos/transitions/estimate_transitions.R

@@ -121,8 +121,8 @@ estimate_yearly_zip <- function(data, formula, include_weights = FALSE, depend) 
   
   if(depend == 'next_ncigs' | depend == 'ncigs') {
     # first subset just the columns we want
-    cols <- c('pidp', depend, 'age', 'sex', 'education_state', 'SF_12', 'job_sec', 
-              'hh_income', 'ethnicity', 'weight')
+    cols <- c('pidp', depend, 'age', 'sex', 'education_state', 'SF_12_MCS', 'job_sec', 
+              'hh_income', 'ethnicity', 'weight', 'SF_12_PCS')
     dat.subset <- data[, cols]
     
     # Replace missing values with NA (util func)
@@ -236,7 +236,7 @@ run_yearly_models <- function(transitionDir_path,
       if(dependent == 'ncigs' & year < 2013) { next }
       #TODO: Maybe copy values from wave 2 onto wave 1? Assuming physical health changes slowly?
       # SF_12 predictor (physical health score) not available in wave 1
-      if(dependent == 'SF_12' & year == 2009) { next }
+      if(dependent %in% c('SF_12_MCS', 'SF_12_PCS') & year == 2009) { next }
       
       print(paste0('Starting estimation for ', dependent, ' in ', year))
       
@@ -267,10 +267,10 @@ run_yearly_models <- function(transitionDir_path,
       }
       
       #print(formula.string)
-      ## For the SF_12 model alone, we need to modify the formula on the fly
+      ## For the SF_12 models (MCS & PCS), we need to modify the formula on the fly
       # as neighbourhood_safety, loneliness, nutrition_quality and ncigs are 
       # not present every year
-      if(dependent == 'SF_12') {
+      if(dependent %in% c('SF_12_MCS', 'SF_12_PCS')) {
         if(!year %in% c(2011, 2014, 2017, 2020)) {
           formula.string <- str_remove(formula.string, " \\+ factor\\(neighbourhood_safety\\)")
         }

### 2023-05-17 minos/validation/handovers.Rmd
Embarassing fix here. Forgot to remove missing values from the raw data in handover plots (assumed that this had been done during complete_case but that was only for some variables). This has changed the shape of the SF12 MCS and PCS plots, and shows some problematic behaviour that needs to be monitored. I believe these will be vastly improved with the rate of change model work that is ongoing, but remains to be seen

@@
 sf12.m <- rbind(raw.sf12.m, base.sf12.m)
+
+print(sum(sf12.m$SF_12_MCS < 0))
 
@@
   dplyr::select(pidp, time, neighbourhood_safety) %>%
+  filter(neighbourhood_safety > 0) %>%
   group_by(time, neighbourhood_safety) %>%
@@
   dplyr::select(pidp, time, loneliness) %>%
+  filter(loneliness > 0) %>%
   group_by(time, loneliness) %>%
@@
   dplyr::select(pidp, time, nutrition_quality) %>%
+  filter(nutrition_quality >= 0) %>%
   group_by(time) %>%
@@
   dplyr::select(pidp, time, phealth) %>%
+  filter(phealth >= 0) %>%
   filter(time > 2009) %>%

### 2023-05-17 minos/validation/cross_validation.Rmd
Fixed typo in the cross-validation notebook, and updated the util function combine_and_pivot() to remove all missing values (negative 1-3, 7-9). Also removed some .pngs that were tracked by accident
Added a variable for the save.path in cross_validation.Rmd so it only has to be changed in one place

@@
 raw <- do.call(rbind, lapply(cv.simul.files, read.csv))
+
+savepath <- '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/'
 ```
@@
                      save = TRUE,
-                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
+                     save.path = savepath)
 
@@
 yearly_box_plots(pivoted.df = sf12.p.pivoted,
-                 var = 'nutrition_quality',
+                 var = 'SF_12_PCS',
                  scen1 = 'raw',
@@
                  save = TRUE,
-                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
+                 save.path = savepath)
 ```

### 2023-05-17 minos/testing/rate_of_change_testing.Rmd
Stopped ignoring the minos/testing/ folder, and started tracking an R notebook for testing the rate of change model stuff

---
title: "Testing Rate of Change Transition models"
output: html_notebook
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

```{r, include=FALSE}
source('Minos/minos/utils_datain.R')
source('Minos/minos/validation/utils.r')
```

## Data

```{r, include=FALSE}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

out.path <- 'Minos/output/default_config/'
base.dat <- read_singular_local_out(out.path, 'baseline')
```

The purpose of this notebook will be to test rate of change models for use in Minos. Early attempts at the rate of change models have been relatively successful, seeing vast improvements in the regression to the mean issue that has been a problem for a while. However, even with the new rate of change models we are seeing some regression to the mean (or something that looks like it at least), with those earning the highest amounts seeing massive decreases and those earning very little or negative values seeing larger increases. What I think we need to do, is to investigate the actual rate of change across different income groups, as well as fitting these models here and seeing what a prediction looks like where we can actually investigate it. We can also plot some handovers of the rate of change from raw US to baseline outputs.

# Raw Data Analysis

## hh_income

First stop here will be to test the rate of change in raw understanding Society data across varying income levels.

```{r}
# difference between rows by group is more complicated than it sounds
# see https://stackoverflow.com/questions/14846547/calculate-difference-between-values-in-consecutive-rows-by-group for info
# appears dplyr::lag function could be the solution

# Can we just remove the first year? Nobody has a difference for first year obvs

raw <- raw.dat %>%
  group_by(pidp) %>%
  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time)) %>%
  filter(time != 2009)

print(mean(raw$diff.hh_income, na.rm=TRUE))
print(sd(raw$diff.hh_income, na.rm=TRUE))

raw.sum <- raw %>%
  group_by(time) %>%
  summarise(diff.mean = mean(diff.hh_income, na.rm=TRUE),
            diff.sd = sd(diff.hh_income, na.rm=TRUE))

#raw.sum$time <- as.factor(raw.sum$time)

ggplot(data = raw.sum, aes(x = time, y = diff.mean)) +
  geom_line()

ggplot(data = raw.sum, aes(x = time, y = diff.sd)) +
  geom_line()

# Why wont this work with time as a factor?! Annoying!
```

So that is the mean rate of change and sd for the whole population. Now to do the same by income quintile.

QUESTION: Should I separate people into quintiles based on their average hh_income over all years? Or is it ok to stick with quintiles based on each year?
We are fitting one yearly models still (which is what need to be investi), so the rate of change per quintile per year is still valid I think.

### Yearly Quintile Assignment

```{r}
#raw.quintile <- raw %>%
#  mutate(rank = rank(hh_income, ties.method = "first"),
#         income.quint = cut(hh_income, breaks=quantile(rank, prob=c(0:5)/5, na.rm=TRUE), labels = c(1, 2, 3, 4, 5), include_lowest = TRUE))

# This is a pain in the arse
raw.quintile <- raw
raw.quintile$quintile <- cut(raw.quintile$hh_income, breaks=quantile(raw.quintile$hh_income, prob=c(0:5)/5, na.rm=TRUE), labels = c(1, 2, 3, 4, 5), include_lowest = TRUE)
# FINALLY

raw.quintile.sum <- raw.quintile %>%
  group_by(quintile) %>%
  summarise(diff.mean = mean(diff.hh_income, na.rm=TRUE),
            diff.sd = sd(diff.hh_income, na.rm=TRUE)) %>%
  filter(!is.na(quintile))

ggplot(data = raw.quintile.sum, aes(x = quintile, y = diff.mean, group=quintile, fill = quintile)) +
  geom_col()

ggplot(data = raw.quintile.sum, aes(x = quintile, y = diff.sd, group=quintile, fill = quintile)) +
  geom_col()

```

```{r}
raw.quintile.sum.time <- raw.quintile %>%
  group_by(quintile, time) %>%
  summarise(diff.mean = mean(diff.hh_income, na.rm=TRUE),
            diff.sd = sd(diff.hh_income, na.rm=TRUE)) %>%
  filter(!is.na(quintile))

ggplot(data = raw.quintile.sum.time, aes(x = time, y = diff.mean, group=quintile, color = quintile)) +
  geom_line()

ggplot(data = raw.quintile.sum.time, aes(x = time, y = diff.sd, group=quintile, color = quintile)) +
  geom_line()
```

### Whole Period Quintile Assignment

NOW CATEGORISE BY HH_INCOME QUINTILE ACROSS THE WHOLE TIME PERIOD.

```{r}
# Group people into income quintiles based on their mean income across the whole period
raw.time.quint <- raw %>%
  group_by(pidp) %>%
  summarise(hh_income = mean(hh_income, na.rm=TRUE)) %>%
  mutate(income.quint = cut(hh_income, breaks = quantile(x = hh_income, prob = c(0:5)/5), labels = c(1:5), include.lowest = TRUE)) %>%
  select(-hh_income)

# Add the income quintiles to the original raw data
raw.quint2 <- merge(raw, raw.time.quint, by='pidp')

# Now sort the data by time 
raw.quint2 <- raw.quint2 %>%
  select(pidp, time, age, sex, education_state, hh_income, diff.hh_income, income.quint) %>%
  group_by(pidp) %>%
  arrange(time, .by_group = TRUE)

#raw.quint2[order(raw.quint2$pidp, -raw.quint2$time), ]

raw.quintile.sum2 <- raw.quint2 %>%
  group_by(income.quint) %>%
  summarise(diff.mean = mean(diff.hh_income, na.rm = TRUE),
            diff.sd = sd(diff.hh_income, na.rm=TRUE))

#raw.quintile.sum2 <- raw.quint2 %>%
#  group_by(pidp) %>%
#  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time)) %>%
#  group_by(income.quint) %>%
#  summarise(diff.mean = mean(diff.hh_income, na.rm=TRUE),
#            diff.sd = sd(diff.hh_income, na.rm=TRUE)) %>%
#  filter(!is.na(income.quint))

ggplot(data = raw.quintile.sum2, aes(x = income.quint, y = diff.mean, group=income.quint, fill = income.quint)) +
  geom_col()

ggplot(data = raw.quintile.sum2, aes(x = income.quint, y = diff.sd, group=income.quint, fill = income.quint)) +
  geom_col()
```

## SF12

```{r}

diff_by_whole_period_quintile <- function(raw, var) {
  # first calculate diffs 
  raw <- raw %>%
    filter(!is.na(.data[[var]])) %>%  # remove missing
    filter(.data[[var]] >= 0) %>%  # remove negative missing codes
    group_by(pidp) %>%
    mutate(diff.var = .data[[var]] - lag(.data[[var]], order_by = time)) %>%
    filter(time != 2009) # remove 2009 as we can't have a diff in the first year

  #return(raw)

  raw.time.quint <- raw %>%
    group_by(pidp) %>%
    summarise(var.mean = mean(.data[[var]], na.rm = TRUE)) %>%
    mutate(var.quint = cut(var.mean, breaks = quantile(x = var.mean, prob = c(0:5)/5), labels = c(1:5), include.lowest = TRUE)) %>%
    select(-var.mean)

  #return(raw.time.quint)

  raw.quint <- merge(raw, raw.time.quint, by = 'pidp')

  raw.quint <- raw.quint %>%
    select(pidp, time, age, sex, education_state, hh_income, diff.var, var.quint) %>%
    group_by(pidp) %>%
    arrange(time, .by_group = TRUE)

  raw.quint.sum <- raw.quint %>%
    group_by(var.quint) %>%
    summarise(diff.mean = mean(diff.var, na.rm = TRUE),
              diff.sd = sd(diff.var, na.rm = TRUE),
              min = min(diff.var, na.rm = TRUE),
              max = max(diff.var, na.rm = TRUE))

  p1 <-ggplot(data = raw.quint.sum, aes(x = var.quint, y = diff.mean, group=var.quint, fill = var.quint)) +
    geom_col()

  p2 <- ggplot(data = raw.quint.sum, aes(x = var.quint, y = diff.sd, group=var.quint, fill = var.quint)) +
    geom_col()

  print(p1)
  print(p2)

  return(raw.quint.sum)
}

SF_12.stats <- diff_by_whole_period_quintile(raw.dat, 'SF_12')
```

```{r}
hh_income.stats <- diff_by_whole_period_quintile(raw.dat, 'hh_income')
```

```{r}
diff_by_year1_quintile <- function(raw, var) {
  # first calculate diffs 
  raw <- raw %>%
    filter(!is.na(.data[[var]])) %>%  # remove missing
    filter(.data[[var]] >= 0) %>%  # remove negative missing codes
    group_by(pidp) %>%
    mutate(diff.var = .data[[var]] - lag(.data[[var]], order_by = time))

  return(raw)

  raw.time.quint <- raw %>%
    filter(time == 2009) %>%
    mutate(var.quint = cut(.data[[var]], breaks = unique(quantile(x = .data[[var]], prob = c(0:5)/5)), include.lowest = TRUE))# %>% , labels = c(1:5)
    #select(-var.mean)

  return(raw.time.quint)

  raw.quint <- merge(raw, raw.time.quint, by = 'pidp')

  raw.quint <- raw.quint %>%
    select(pidp, time, age, sex, education_state, hh_income, diff.var, var.quint) %>%
    group_by(pidp) %>%
    arrange(time, .by_group = TRUE)

  raw.quint.sum <- raw.quint %>%
    group_by(var.quint) %>%
    summarise(diff.mean = mean(diff.var, na.rm = TRUE),
              diff.sd = sd(diff.var, na.rm = TRUE),
              min = min(diff.var, na.rm = TRUE),
              max = max(diff.var, na.rm = TRUE))

  p1 <-ggplot(data = raw.quint.sum, aes(x = var.quint, y = diff.mean, group=var.quint, fill = var.quint)) +
    geom_col()

  p2 <- ggplot(data = raw.quint.sum, aes(x = var.quint, y = diff.sd, group=var.quint, fill = var.quint)) +
    geom_col()

  print(p1)
  print(p2)

  return(raw.quint.sum)
}

hh_income.stats.yr1 <- diff_by_year1_quintile(raw.dat, 'hh_income')
```

```{r}
test <- hh_income.stats.yr1

test2 <- test %>%
  filter(time == 2009)

print(sum(is.na(test2$hh_income)))
print(sum(test2$hh_income == -9))

print(min(test2$hh_income))
print(sum(test2$hh_income == 0))

ggplot(data = test2, aes(x = hh_income)) +
  geom_histogram()
```

### 2023-05-18 minos/testing/rate_of_change_testing.Rmd
Rate of change models in a good working state for both income and SF_12_MCS now, success! Also added some testing plots to testing/rate_of_change_testing.Rmd

@@
 # Why wont this work with time as a factor?! Annoying!
+
+rm(raw.sum)
 ```
@@
 
+rm(raw.quintile.sum)
 ```
@@
   geom_line()
+
+rm(raw.quintile.sum.time)
 ```
@@
   geom_col()
+
+rm(raw.time.quint, raw.quint2, raw.quintile.sum2)
 ```
@@
 
-  return(raw)
+  #return(raw)
 
@@
     filter(time == 2009) %>%
-    mutate(var.quint = cut(.data[[var]], breaks = unique(quantile(x = .data[[var]], prob = c(0:5)/5)), include.lowest = TRUE))# %>% , labels = c(1:5)
+    mutate(varx = .data[[var]],
+           var.quint = cut(varx, breaks = unique(quantile(x = varx, prob = c(0:5)/5)), include.lowest = TRUE))# %>% , labels = c(1:5)
     #select(-var.mean)
@@
 
-hh_income.stats.yr1 <- diff_by_year1_quintile(raw.dat, 'hh_income')
+#hh_income.stats.yr1 <- diff_by_year1_quintile(raw.dat, 'hh_income')
 ```
@@
 ```{r}
-test <- hh_income.stats.yr1
+#test <- hh_income.stats.yr1
 
-test2 <- test %>%
-  filter(time == 2009)
+#test2 <- test %>%
+#  filter(time == 2009)
 
-print(sum(is.na(test2$hh_income)))
-print(sum(test2$hh_income == -9))
+#print(sum(is.na(test2$hh_income)))
+#print(sum(test2$hh_income == -9))
 
-print(min(test2$hh_income))
-print(sum(test2$hh_income == 0))
+#print(min(test2$hh_income))
+#print(sum(test2$hh_income == 0))
 
-ggplot(data = test2, aes(x = hh_income)) +
-  geom_histogram()
+#ggplot(data = test2, aes(x = hh_income)) +
+#  geom_histogram()
 ```
+
+# Comparing SF12_MCS Diff
+
+```{r}
+cv.path <- 'Minos/data/final_US/cross_validation/simulation/'
+cv.outpath <- 'Minos/output/cross_validation/'
+
+raw.files <- list.files(cv.path, pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.cv <- do.call(rbind, lapply(raw.files, read.csv))
+
+base.cv <- read_singular_local_out(cv.outpath, 'baseline')
+
+## MODELS
+mod.path <- 'Minos/data/transitions/cross_validation/'
+sf12.mod <- readRDS(paste0(mod.path, 'SF_12/ols2/SF_12_2017_2018.rds'))
+income.mod <- readRDS(paste0(mod.path, 'hh_income/ols2/hh_income_2019_2020.rds'))
+
+```
+
+## Model Summaries
+
+```{r}
+summary(sf12.mod)
+```
+```{r}
+summary(income.mod)
+```
+
+```{r}
+miss.values <- c(-9, -8, -7, -3, -2, -1, -10)
+raw <- raw.cv %>%
+  filter(!hh_income %in% miss.values, !SF_12 %in% miss.values) %>%
+  group_by(pidp) %>%
+  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time),
+         diff.SF12_MCS = SF_12 - lag(SF_12, order_by = time)) %>%
+  filter(time != 2009)
+
+base <- base.cv %>%
+  filter(!hh_income %in% miss.values, !SF_12 %in% miss.values) %>%
+  group_by(pidp) %>%
+  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time),
+         diff.SF12_MCS = SF_12 - lag(SF_12, order_by = time)) %>%
+  filter(time != 2014)
+```
+
+```{r}
+raw.sub <- raw %>%
+  select(pidp, time, diff.hh_income, diff.SF12_MCS) %>%
+  mutate(source = 'raw')
+base.sub <- base %>%
+  select(pidp, time, diff.hh_income, diff.SF12_MCS) %>%
+  mutate(source = 'output')
+
+combined <- rbind(raw.sub, base.sub)
+
+combined.sum <- combined %>%
+  group_by(time, source) %>%
+  summarise(hh_income = mean(diff.hh_income, na.rm = TRUE),
+            SF12_MCS = mean(diff.SF12_MCS, na.rm = TRUE))
+
+ggplot(combined.sum, aes(x = time, y = hh_income, group = source, color = source)) +
+  geom_line()
+
+ggplot(combined.sum, aes(x = time, y = SF12_MCS, group = source, color = source)) +
+  geom_line()
+```
+
+```{r}
+test <- base.cv %>%
+  group_by(time) %>%
+  summarise(mean.income = mean(hh_income, na.rm = TRUE),
+            mean.SF12 = mean(SF_12, na.rm = TRUE))
+
+ggplot(test, aes(x = time, y = mean.income)) +
+  geom_line()
+
+ggplot(test, aes(x = time, y = mean.SF12)) +
+  geom_line()
+```
+
+```{r}
+
+```

### 2023-05-19 minos/testing/rate_of_change_testing.Rmd
Plotted some marginal distribution plots in rate_of_change_testing.Rmd to see if the regression to the mean is noticeably better in those plots (it is just about I think). Also added require() calls for some packages in the utils_outcome_vis.R file because thats the most sensible place to put them (should do this for all utils scripts)

@@
 source('Minos/minos/validation/utils.r')
+source('Minos/minos/utils_outcome_vis.R')
 ```
@@
 
+## Marginal Distribtion Plots
+
+These plots are quite good at showing regression to the mean (and also sometimes nicer than looking at the mean lineplots even though differences are harder to spot) so lets plot them too just for fun.
+
 ```{r}
+# need baseline and interventions to compare with
+out.path <- 'Minos/output/default_config/'
+baseline <- read_singular_local_out(out.path, 'baseline')
+allchild <- read_singular_local_out(out.path, 'hhIncomeChildUplift')
+poverty <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift')
+livwage <- read_singular_local_out(out.path, 'livingWageIntervention')
+energy <- read_singular_local_out(out.path, 'energyDownlift')
+```
 
+```{r}
+alchild.plot <- SF12_marg_dist_densigram_plot(baseline,
+                              allchild,
+                              'All Child Uplift',
+                              target.year = 2030)
+pov.plot <- SF12_marg_dist_densigram_plot(baseline,
+                              poverty,
+                              'Poverty Child Uplift',
+                              target.year = 2030)
+livwage.plot <- SF12_marg_dist_densigram_plot(baseline,
+                              livwage,
+                              'Living Wage Uplift',
+                              target.year = 2030)
+energy.p <- SF12_marg_dist_densigram_plot(baseline,
+                              energy,
+                              'Energy Downlift',
+                              target.year = 2030)
 ```
+
+```{r}
+alchild.plot2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
+                              allchild,
+                              'All Child Uplift',
+                              target.year = 2030)
+pov.plot2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
+                              poverty,
+                              'Poverty Child Uplift',
+                              target.year = 2030)
+livwage.plot2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
+                              livwage,
+                              'Living Wage Uplift',
+                              target.year = 2030)
+energy.p2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
+                              energy,
+                              'Energy Downlift',
+                              target.year = 2030)
+```

### 2023-05-19 minos/testing/model_of_models_work.Rmd
Started an RNotebook for plotting coefficients of models over time and starting the work towards the model of models work. Currently very WIP and only looking at hh_income for now

---
title: "'Model of Models' stuff"
output: html_notebook
---

This is an investigation recommended by Robin Pursehouse from a meeting on 5/5/23.

We want to investigate the coefficients of our models over time, and from this investigation we can do a couple of things. For example, there are 2 possible good outcomes from this work (and one very bad outcome):
1. If we identify that our model coefficients are fairly steady over time, then we can assume that our coefficients are time invariant. This would mean that the influence of the predictors on the outcome doesn't change over time, and that these models will be able to successfully predict the outcome into the future. We would also be able to use multiple years of data for a single model instead of the yearly models we generate now.
2. If model coefficients trend in a predictable way, we can fit another regression model to this longitudinal set of coefficients. We can then use this model to predict future states of the coefficients, and generate transition models for future years where data is not available.
3. This is a possible outcome that should be mentioned, but we hope to not see it. If the coefficient trends are arbitrary, we will not be able to predict the future of the models, and would have no confidence that this set of predictors can predict the response in any year. This is the worst outcome, as it essentially means that the task is not possible or just not worth trying.

Rob also found [this paper](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6599683/) on the multinomial fused lasso technique, which is a data driven method of picking the correct set of predictors for a regression model that either are time-invariant or trend in a predictable way over the length of a longitudinal dataset. This is what we want, so is probably a good place to start trying to do this.

To start with,  we'll look at the hh_income variable, which has good (relatively complete) data over the length of Understanding Society. When some prototype code has been developed, we'll look at automation and expanding to the rest of the key variables.

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(tibble)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

```{r, include=FALSE}
source('Minos/minos/utils_datain.R')
source('Minos/minos/validation/utils.r')
source('Minos/minos/utils_outcome_vis.R')
```

## Models

```{r}
# note this is the path to the rate of change models, NOT the regenerative mean effects
mod.path <- 'Minos/data/transitions/hh_income/ols2/'
m1 <- readRDS(paste0(mod.path, 'hh_income_2009_2010.rds'))
m2 <- readRDS(paste0(mod.path, 'hh_income_2010_2011.rds'))
m3 <- readRDS(paste0(mod.path, 'hh_income_2011_2012.rds'))
m4 <- readRDS(paste0(mod.path, 'hh_income_2012_2013.rds'))
m5 <- readRDS(paste0(mod.path, 'hh_income_2013_2014.rds'))
m6 <- readRDS(paste0(mod.path, 'hh_income_2014_2015.rds'))
m7 <- readRDS(paste0(mod.path, 'hh_income_2015_2016.rds'))
m8 <- readRDS(paste0(mod.path, 'hh_income_2016_2017.rds'))
m9 <- readRDS(paste0(mod.path, 'hh_income_2017_2018.rds'))
m10 <- readRDS(paste0(mod.path, 'hh_income_2018_2019.rds'))
m11 <- readRDS(paste0(mod.path, 'hh_income_2019_2020.rds'))
```

## Coefficients

```{r}
c1 <- data.frame(m1$coefficients)
c2 <- data.frame(m2$coefficients)
c3 <- data.frame(m3$coefficients)
c4 <- data.frame(m4$coefficients)
c5 <- data.frame(m5$coefficients)
c6 <- data.frame(m6$coefficients)
c7 <- data.frame(m7$coefficients)
c8 <- data.frame(m8$coefficients)
c9 <- data.frame(m9$coefficients)
c10 <- data.frame(m10$coefficients)
c11 <- data.frame(m11$coefficients)

names(c1) <- 'y1'
names(c2) <- 'y2'
names(c3) <- 'y3'
names(c4) <- 'y4'
names(c5) <- 'y5'
names(c6) <- 'y6'
names(c7) <- 'y7'
names(c8) <- 'y8'
names(c9) <- 'y9'
names(c10) <- 'y10'
names(c11) <- 'y11'

#c1$pred <- rownames(c1)
#c2$pred <- rownames(c2)
#c3$pred <- rownames(c3)
#c4$pred <- rownames(c4)
#c5$pred <- rownames(c5)
#c6$pred <- rownames(c6)
#c7$pred <- rownames(c7)
#c8$pred <- rownames(c8)
#c9$pred <- rownames(c9)
#c10$pred <- rownames(c10)
#c11$pred <- rownames(c11)

c1 <- tibble::rownames_to_column(c1, "Predictor")
c2 <- tibble::rownames_to_column(c2, "Predictor")
c3 <- tibble::rownames_to_column(c3, "Predictor")
c4 <- tibble::rownames_to_column(c4, "Predictor")
c5 <- tibble::rownames_to_column(c5, "Predictor")
c6 <- tibble::rownames_to_column(c6, "Predictor")
c7 <- tibble::rownames_to_column(c7, "Predictor")
c8 <- tibble::rownames_to_column(c8, "Predictor")
c9 <- tibble::rownames_to_column(c9, "Predictor")
c10 <- tibble::rownames_to_column(c10, "Predictor")
c11 <- tibble::rownames_to_column(c11, "Predictor")

rm(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11)
```

```{r}
# now merge them all together in a bit rbind
#all.years <- merge(c(c1, c2, c3, c4, c5, c6, c7, c8, c9, c10, c11), by='Predictor')

merge.list <- list(c1, c2, c3, c4, c5, c6, c7, c8, c9, c10, c11)

all.years <- merge.list %>% reduce(full_join, by='Predictor')
```

```{r}
# now pivot_longer before plotting with ggplot
all.years.long <- pivot_longer(data = all.years,
                               cols = y1:y11,
                               names_to = 'year',
                               values_to = 'coefficient')
all.years.long$year <- factor(all.years.long$year, levels = c('y1', 'y2', 'y3', 'y4', 'y5', 'y6', 'y7', 'y8', 'y9', 'y10', 'y11'))
```

```{r}
ggplot(data = all.years.long, aes(x = year, y = coefficient, group = Predictor, color = Predictor)) +
  geom_line()
```

Too many point to plot so we can't see a thing! Separate out into the individual variables, so for example all regions on one plot, all ethnicities on another etc.

Print predictors so I don't have to keep opening the df to see them.

```{r}
print(all.years$Predictor)
```

# Intercept

First lets look at the intercept.

```{r}
intercept <- all.years.long %>%
  filter(grepl("Intercept", Predictor))

ggplot(intercept, aes(x = year, y = coefficient, group=1)) +
  geom_line() +
  labs(title = 'Intercept')
```

# Gender

```{r}
gender <- all.years.long %>%
  filter(grepl("sex", Predictor))

ggplot(gender, aes(x = year, y = coefficient, group=1)) +
  geom_line() +
  labs(title = 'Gender - Male', subtitle = 'Ref: Female')
```

# Ethnicity

```{r}
ethnicity <- all.years.long %>%
  filter(grepl("ethnicity", Predictor)) %>%
  mutate(ethnicity = str_extract(Predictor, pattern = '[^)]+$'))

ggplot(ethnicity, aes(x = year, y = coefficient, group = ethnicity, color = ethnicity)) +
  geom_line() +
  labs(title = 'Ethnicity', subtitle = 'Ref: WBI')
```

# Region

```{r}
region <- all.years.long %>%
  filter(grepl("region", Predictor)) %>%
  mutate(region = str_extract(Predictor, pattern = '[^)]+$'))

ggplot(region, aes(x = year, y = coefficient, group = region, color = region)) +
  geom_line() +
  labs(title = 'Region', subtitle = 'Ref: South East')
```

# Education State

```{r}
educ <- all.years.long %>%
  filter(grepl("education", Predictor)) %>%
  mutate(education = str_extract(Predictor, pattern = '[^)]+$'))

ggplot(educ, aes(x = year, y = coefficient, group = education, color = education)) +
  geom_line() +
  labs(title = 'Education State', subtitle = 'Ref: 1 - ')
```

# Job Sec

```{r}
jobsec <- all.years.long %>%
  filter(grepl("job_sec", Predictor)) %>%
  filter(!grepl("job_sector", Predictor)) %>%
  mutate(job_sec = str_extract(Predictor, pattern = '[^)]+$'))

ggplot(jobsec, aes(x = year, y = coefficient, group = job_sec, color = job_sec)) +
  geom_line() +
  labs(title = 'Job NSSEC')
```

# Job Sector

```{r}
jobsector <- all.years.long %>%
  filter(grepl("job_sector", Predictor)) %>%
  mutate(job_sector = str_extract(Predictor, pattern = '[^)]+$'))

ggplot(jobsector, aes(x = year, y = coefficient, group = job_sector, color = job_sector)) +
  geom_line() +
  labs(title = 'Job Sector (Public/Private)')
```

### 2023-05-20 minos/outcomes/lineplot_notebook.Rmd
putting lineplots into one file and tidying a lot

---
title: "Untitled"
output: html_document
date: "2023-05-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
```

```{python}
# packages need installing in R using py_install("package"). honestly this seems not worth it..
from minos.outcomes.make_lineplots import main as lineplot_main
# define test parameters and run.
directories = "baseline,livingWageIntervention"
tags = "Baseline,Living Wage Intervention"
subset_function_strings = "who_below_living_wage,who_boosted"
prefix="baseline_living_wage_"
lineplot_main(directories, tags, subset_function_strings, prefix, mode='default_config', ref="Baseline", v="SF_12", method='nanmean')
```

### 2023-05-22 minos/testing/rate_of_change_testing.Rmd
Started a utils script for validation visualisation functions. Also added Spaghetti plots to the rate_of_change_testing notebook. VERY insightful, clearly need more work on rate of change stuff

@@
 source('Minos/minos/utils_outcome_vis.R')
+source('Minos/minos/utils_validation_vis.R')
 ```
@@
 ```
+
+## Spaghetti Plots
+
+Final plot type we can use to investigate the rate of change models (or just trajectories in general) are Spaghetti plots (lovingly created an titled by Rob - more evidence as to why he was banned from naming things).
+
+These plots show trajectories of single variable for individuals over the length of simulation, and are very useful for making sure people are not just bouncing around the mean which would be impossible to see from mean or otherwise aggregated plots.
+
+```{r}
+
+```

### 2023-05-22 minos/utils_validation_vis.R

@@ -1,0 +1,22 @@
+## Validation plotting functions for MINOS
+
+
+
+spaghetti_plot <- function(data, v)
+{
+  # spaghetti plot displaying trajectories over time for continuous variable v
+  # data: list Some dataset to plot. Needs v, time and pidp variables.
+  # v : some continuous variable to plot. 
+  #TODO convert this to pure ggplot2 as with joint spaghetti plot below. Far more flexible and doesnt need stupid wide format conversion. 
+  data_plot <- data[, c("time", "pidp", v)]
+  output_plot <- ggplot(data_plot, aes(x = time, y = !!sym(v), group = pidp)) + 
+    ggplot2::labs(x = "time", y = v) + 
+    ggplot2::theme_classic() + 
+    ggplot2::theme(text = ggplot2::element_text(size = 12)) + 
+    ggplot2::scale_colour_viridis_d()+ 
+    #ggplot2::geom_smooth(colour="blue") +
+    ggplot2::geom_line(colour="blue", alpha=0.2) +
+    ggplot2::geom_point()
+  
+  return (output_plot)
+}

### 2023-05-22 minos/testing/model_of_models_work.Rmd
Started to functionalise plotting coefficients. Have function for reading in models and extracting coefficients to a dataframe, now need function for visualising each predictor group separately (or altogether)

@@
 m11 <- readRDS(paste0(mod.path, 'hh_income_2019_2020.rds'))
+```
+
+```{r}
+mod.list <- list.files(mod.path, pattern = '.+.rds', full.names = TRUE)
+
+mod.models <- lapply(mod.list, FUN=readRDS)
+
+mod.coefs <- as.data.frame(sapply(mod.models, function(x) return(coefficients(x))))
+
+mod.coefs <- tibble::rownames_to_column(mod.coefs, 'predictor')
 ```
@@
 ```
+
+# Function
+
+```{r}
+
+## Function to collect coefficients from a set of models into a dataframe
+collect_coefficients_to_df <- function(trans.path, var, mod.type) {
+
+  #TODO: find a way to write these as os agnostic paths instead of just pasting
+  # https://stackoverflow.com/questions/8197027/raw-text-strings-for-file-paths-in-r
+  mod.path <- paste0(trans.path, '/', var, '/', mod.type, '/')
+  # list all rds files in dir
+  file.list <- list.files(mod.path, pattern = ".+.rds", full.names = TRUE)
+  # read all .rds models into a list
+  mod.list <- lapply(mod.list, FUN=readRDS)
+  # Now collect all coefficients into a dataframe, each column is 1 year
+  mod.coefs <- sapply(mod.list, function(x) return(coefficients(x)))
+
+  return(mod.coefs)
+}
+
+```

### 2023-05-23 minos/testing/rate_of_change_testing.Rmd
Added violin plots to the utils script (and removed na values in the quantile func so we can plot raw data also), and added them to the rate_of_change_testing notebook

@@
 
+### hh_income
+
 ```{r}
+income.spag.base <- spaghetti_plot(base.dat, 'hh_income')
+income.spag.base
+```
 
+This one actually looks worse I think... Might need to have a look at subsetting to see the tight band in the middle in more detail. Also worth using the same plot on raw data to see how that looks:
+
+```{r}
+income.spag.raw <- spaghetti_plot(raw.dat, 'hh_income')
+income.spag.raw
 ```
+
+Very useful plot!
+Much more variability in the raw data that we don't keep hold of in the simulation.
+Also shows that the spike in 2015 is mostly due to about 5-6 data points by the looks of things.
+Again worth a chat with the group to figure out where our acceptable thresholds are, as we are unlikely to be able to capture all of the heterogeneity in such a varied and skewed variable like hh_income.
+
+### SF_12_MCS
+
+Quick look at SF_12_MCS also.
+
+```{r}
+sf12.spag.base <- spaghetti_plot(base.dat, 'SF_12')
+sf12.spag.base
+
+sf12.spag.raw <- spaghetti_plot(raw.dat, 'SF_12')
+sf12.spag.raw
+```
+Need to remove missing values.
+
+## Violin Plots
+
+### hh_income
+
+```{r}
+income.violin.base <- violin_plot(base.dat, 'hh_income')
+income.violin.base
+
+income.violin.raw <- violin_plot(raw.dat, 'hh_income')
+income.violin.raw
+```
+
+### SF12
+
+```{r}
+sf12.violin.base <- violin_plot(base.dat, 'SF_12')
+sf12.violin.base
+
+sf12.violin.raw <- violin_plot(raw.dat, 'SF_12')
+sf12.violin.raw
+```

### 2023-05-23 minos/testing/rate_of_change_testing.Rmd
Lots of WIP stuff still on the rate of change testing front. Some sections comparing old (mean regenerative models) with new (rate of change)

@@
 
+# read output and remove dead people
 out.path <- 'Minos/output/default_config/'
-base.dat <- read_singular_local_out(out.path, 'baseline')
+base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
 ```
@@
 ```{r}
-miss.values <- c(-9, -8, -7, -3, -2, -1, -10)
-raw <- raw.cv %>%
-  filter(!hh_income %in% miss.values, !SF_12 %in% miss.values) %>%
-  group_by(pidp) %>%
-  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time),
-         diff.SF12_MCS = SF_12 - lag(SF_12, order_by = time)) %>%
-  filter(time != 2009)
+#miss.values <- c(-9, -8, -7, -3, -2, -1, -10)
+#raw <- raw.cv %>%
+#  filter(!hh_income %in% miss.values, !SF_12 %in% miss.values) %>%
+#  group_by(pidp) %>%
+#  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time),
+#         diff.SF12_MCS = SF_12 - lag(SF_12, order_by = time)) %>%
+#  filter(time != 2009)
 
-base <- base.cv %>%
-  filter(!hh_income %in% miss.values, !SF_12 %in% miss.values) %>%
-  group_by(pidp) %>%
-  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time),
-         diff.SF12_MCS = SF_12 - lag(SF_12, order_by = time)) %>%
-  filter(time != 2014)
+#base <- base.cv %>%
+#  filter(!hh_income %in% miss.values, !SF_12 %in% miss.values) %>%
+#  group_by(pidp) %>%
+#  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time),
+#         diff.SF12_MCS = SF_12 - lag(SF_12, order_by = time)) %>%
+#  filter(time != 2014)
 ```
@@
 ```{r}
-raw.sub <- raw %>%
-  select(pidp, time, diff.hh_income, diff.SF12_MCS) %>%
-  mutate(source = 'raw')
-base.sub <- base %>%
-  select(pidp, time, diff.hh_income, diff.SF12_MCS) %>%
-  mutate(source = 'output')
+#raw.sub <- raw %>%
+#  select(pidp, time, diff.hh_income, diff.SF12_MCS) %>%
+#  mutate(source = 'raw')
+#base.sub <- base %>%
+#  select(pidp, time, diff.hh_income, diff.SF12_MCS) %>%
+#  mutate(source = 'output')
 
-combined <- rbind(raw.sub, base.sub)
+#combined <- rbind(raw.sub, base.sub)
 
-combined.sum <- combined %>%
-  group_by(time, source) %>%
-  summarise(hh_income = mean(diff.hh_income, na.rm = TRUE),
-            SF12_MCS = mean(diff.SF12_MCS, na.rm = TRUE))
+#combined.sum <- combined %>%
+#  group_by(time, source) %>%
+#  summarise(hh_income = mean(diff.hh_income, na.rm = TRUE),
+#            SF12_MCS = mean(diff.SF12_MCS, na.rm = TRUE))
 
-ggplot(combined.sum, aes(x = time, y = hh_income, group = source, color = source)) +
-  geom_line()
+#ggplot(combined.sum, aes(x = time, y = hh_income, group = source, color = source)) +
+#  geom_line()
 
-ggplot(combined.sum, aes(x = time, y = SF12_MCS, group = source, color = source)) +
-  geom_line()
+#ggplot(combined.sum, aes(x = time, y = SF12_MCS, group = source, color = source)) +
+#  geom_line()
 ```
@@
 ```{r}
-test <- base.cv %>%
-  group_by(time) %>%
-  summarise(mean.income = mean(hh_income, na.rm = TRUE),
-            mean.SF12 = mean(SF_12, na.rm = TRUE))
+#test <- base.cv %>%
+#  group_by(time) %>%
+#  summarise(mean.income = mean(hh_income, na.rm = TRUE),
+#            mean.SF12 = mean(SF_12, na.rm = TRUE))
 
-ggplot(test, aes(x = time, y = mean.income)) +
-  geom_line()
+#ggplot(test, aes(x = time, y = mean.income)) +
+#  geom_line()
 
-ggplot(test, aes(x = time, y = mean.SF12)) +
-  geom_line()
+#ggplot(test, aes(x = time, y = mean.SF12)) +
+#  geom_line()
 ```
@@
 # need baseline and interventions to compare with
-out.path <- 'Minos/output/default_config/'
-baseline <- read_singular_local_out(out.path, 'baseline')
-allchild <- read_singular_local_out(out.path, 'hhIncomeChildUplift')
-poverty <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift')
-livwage <- read_singular_local_out(out.path, 'livingWageIntervention')
-energy <- read_singular_local_out(out.path, 'energyDownlift')
+#out.path <- 'Minos/output/default_config/'
+#baseline <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+#allchild <- read_singular_local_out(out.path, 'hhIncomeChildUplift', drop.dead = TRUE)
+#poverty <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift', drop.dead = TRUE)
+#livwage <- read_singular_local_out(out.path, 'livingWageIntervention', drop.dead = TRUE)
+#energy <- read_singular_local_out(out.path, 'energyDownlift', drop.dead = TRUE)
 ```
@@
 ```{r}
-alchild.plot <- SF12_marg_dist_densigram_plot(baseline,
-                              allchild,
-                              'All Child Uplift',
-                              target.year = 2030)
-pov.plot <- SF12_marg_dist_densigram_plot(baseline,
-                              poverty,
-                              'Poverty Child Uplift',
-                              target.year = 2030)
-livwage.plot <- SF12_marg_dist_densigram_plot(baseline,
-                              livwage,
-                              'Living Wage Uplift',
-                              target.year = 2030)
-energy.p <- SF12_marg_dist_densigram_plot(baseline,
-                              energy,
-                              'Energy Downlift',
-                              target.year = 2030)
+#allchild.plot <- SF12_marg_dist_densigram_plot(baseline,
+#                              allchild,
+#                              'All Child Uplift',
+#                              target.year = 2030)
+#pov.plot <- SF12_marg_dist_densigram_plot(baseline,
+#                              poverty,
+#                              'Poverty Child Uplift',
+#                              target.year = 2030)
+#livwage.plot <- SF12_marg_dist_densigram_plot(baseline,
+#                              livwage,
+#                              'Living Wage Uplift',
+#                              target.year = 2030)
+#energy.p <- SF12_marg_dist_densigram_plot(baseline,
+#                              energy,
+#                              'Energy Downlift',
+#                              target.year = 2030)
 ```
@@
 ```{r}
-alchild.plot2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
-                              allchild,
-                              'All Child Uplift',
-                              target.year = 2030)
-pov.plot2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
-                              poverty,
-                              'Poverty Child Uplift',
-                              target.year = 2030)
-livwage.plot2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
-                              livwage,
-                              'Living Wage Uplift',
-                              target.year = 2030)
-energy.p2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
-                              energy,
-                              'Energy Downlift',
-                              target.year = 2030)
+#alchild.plot2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
+#                              allchild,
+#                              'All Child Uplift',
+#                              target.year = 2030)
+#pov.plot2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
+#                              poverty,
+#                              'Poverty Child Uplift',
+#                              target.year = 2030)
+#livwage.plot2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
+#                              livwage,
+#                              'Living Wage Uplift',
+#                              target.year = 2030)
+#energy.p2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
+#                              energy,
+#                              'Energy Downlift',
+#                              target.year = 2030)
 ```
@@
 income.spag.base
-```
 
-This one actually looks worse I think... Might need to have a look at subsetting to see the tight band in the middle in more detail. Also worth using the same plot on raw data to see how that looks:
-
-```{r}
 income.spag.raw <- spaghetti_plot(raw.dat, 'hh_income')
@@
 
-Very useful plot!
 Much more variability in the raw data that we don't keep hold of in the simulation.
@@
 Again worth a chat with the group to figure out where our acceptable thresholds are, as we are unlikely to be able to capture all of the heterogeneity in such a varied and skewed variable like hh_income.
+
+#### Comparison
+
+The base spaghetti plot doesn't look very good actually... I think I need a version using the previous models so I'll do a baseline run and save the data somewhere for testing purposes.
+
+```{r}
+old.files <- list.files('/home/luke/Documents/WORK/MINOS/PREVIOUS_OUTPUTS/mean_regen_income_sf12/', pattern='[0-9]{4}.csv', full.names = TRUE)
+old.dat <- do.call(rbind, lapply(old.files, read.csv))
+# remove dead people
+old.dat <- old.dat %>%
+  filter(alive != 'dead')
+
+income.spag.base <- spaghetti_plot(base.dat, 'hh_income')
+income.spag.base
+
+income.spag.old <- spaghetti_plot(old.dat, 'hh_income')
+income.spag.old
+```
+
+Almost no change.
+The only noticeable change at this resolution is a small shift up?
+Where some people who were below the zero line previously seem to have shifted up, and there are some trajectories that have been seemingly raised out of the main group and lie slightly above the average spread.
+Need to figure out why this is still happening with a completely different set of models...
+
+Very useful plot!
 
@@
 Need to remove missing values.
+
+#### Comparison
+
+```{r}
+sf12.spag.base <- spaghetti_plot(base.dat, 'SF_12')
+sf12.spag.base
+
+sf12.spag.old <- spaghetti_plot(old.dat, 'SF_12')
+sf12.spag.old
+```
 
@@
 ```
+
+```{r}
+
+```

### 2023-05-24 minos/outcomes/lineplot_notebook.Rmd
getting notebook working for all interventions and replenishment columns for default and glasgow_scaled configs

@@
 ---
-title: "Untitled"
+title: "R MINOS Lineplot notebooks noice"
 output: html_document
@@
 
+# MINOS Lineplot Outputs
+
+IMPORTANT NOTE TO RUN PYTHON YOU NEED TO SET THE PYTHON INTERPRETER 
+IN TOOLS>GLOBAL_OPTIIONS>PYTHON>CONDA_INTERPRETERS.
+
+Can just use minos_conda or create a miniconda env using reticulate package.
+
 ```{r setup, include=FALSE}
+library(reticulate)
+library(knitr)
+
 knitr::opts_chunk$set(echo = TRUE)
-library(reticulate)
+knitr::opts_knit$set(root.dir = '../..')
+knitr::knit_engines$set(python = reticulate::eng_python)
 ```
 
-```{python}
+# Baseline vs All Child Uplift
+
+```{python all_child_uplift_SF_12, fig.path="plots/"}
+# packages need installing in R using py_install("package"). honestly this seems not worth it..
+from minos.outcomes.make_lineplots import main as lineplot_main
+# define test parameters and run.
+directories = "baseline,hhIncomeIntervention"
+tags = "Baseline,All Child Uplift"
+subset_function_strings = "who_kids,who_boosted"
+prefix="baseline_all_child_uplift"
+config_mode = "default_config"
+lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
+```
+
+```{r }
+knitr::include_graphics("../../plots/baseline_all_child_uplift_SF_12_aggs_by_year.png", error=FALSE)
+```
+
+# Baseline vs Poverty Child Uplift
+
+```{python poverty_line_child_uplift_SF_12, fig.path="plots/"}
+# packages need installing in R using py_install("package"). honestly this seems not worth it..
+from minos.outcomes.make_lineplots import main as lineplot_main
+# define test parameters and run.
+directories = "baseline,hhIncomePovertyLineChildUplift"
+tags = "Baseline,Poverty Line Child Uplift"
+subset_function_strings = "who_below_poverty_line_and_kids,who_boosted"
+prefix="baseline_poverty_child_uplift"
+config_mode = "default_config"
+lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
+```
+
+```{r }
+knitr::include_graphics("../../plots/baseline_poverty_child_uplift_SF_12_aggs_by_year.png", error=FALSE)
+```
+
+# Baseline vs Living Wage
+
+```{python living_wage_SF_12, fig.path="plots/"}
 # packages need installing in R using py_install("package"). honestly this seems not worth it..
@@
 subset_function_strings = "who_below_living_wage,who_boosted"
-prefix="baseline_living_wage_"
-lineplot_main(directories, tags, subset_function_strings, prefix, mode='default_config', ref="Baseline", v="SF_12", method='nanmean')
+prefix="baseline_living_wage"
+config_mode = "default_config"
+lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
 ```
+
+```{r }
+knitr::include_graphics("../../plots/baseline_living_wage_SF_12_aggs_by_year.png", error=FALSE)
+```
+
+# Baseline vs Energy Downlift
+
+```{python energy_downlift_SF_12, fig.path="plots/"}
+# packages need installing in R using py_install("package"). honestly this seems not worth it..
+from minos.outcomes.make_lineplots import main as lineplot_main
+# define test parameters and run.
+directories = "baseline,energyDownlift"
+tags = "Baseline,Energy Downlift"
+subset_function_strings = "who_uses_energy,who_boosted"
+prefix="baseline_energy_downlift"
+config_mode = "default_config"
+lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
+```
+
+```{r }
+knitr::include_graphics("../../plots/baseline_energy_downlift_SF_12_aggs_by_year.png", error=FALSE)
+```
+
+# All Five combined
+
+```{python all_five_SF_12, fig.path="plots/"}
+# packages need installing in R using py_install("package"). honestly this seems not worth it..
+from minos.outcomes.make_lineplots import main as lineplot_main
+# define test parameters and run.
+directories = "baseline,hhIncomeIntervention,hhIncomePovertyLineChildUplift,livingWageIntervention,energyDownlift"
+tags = "Baseline,All Child Uplift,Poverty Line Child Uplift,Living Wage Intervention,Energy Downlift"
+subset_function_strings = "who_alive,who_boosted,who_boosted,who_boosted,who_boosted"
+prefix="all_five_combined"
+config_mode = "default_config"
+lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
+```
+
+```{r }
+knitr::include_graphics("../../plots/all_five_combined_SF_12_aggs_by_year.png", error=FALSE)
+```

### 2023-05-25 minos/testing/rate_of_change_testing.Rmd
Cosmetic changes to the rate_of_change_testing.Rmd notebook, and modified the spaghetti_plot() function in utils_validation_vis.R to allow for saving and automatically name handover plots as such in filenames

@@
 
+# Spaghetti Plots
+
+## Data
+```{r}
+old.files <- list.files('/home/luke/Documents/WORK/MINOS/PREVIOUS_OUTPUTS/mean_regen_income_sf12/', pattern='[0-9]{4}.csv', full.names = TRUE)
+old.dat <- do.call(rbind, lapply(old.files, read.csv))
+# remove dead people
+old.dat <- old.dat %>%
+  filter(alive != 'dead')
+
+new.files <- list.files('/home/luke/Documents/WORK/MINOS/PREVIOUS_OUTPUTS/diff_income_sf12/', pattern='[0-9]{4}.csv', full.names = TRUE)
+new.dat <- do.call(rbind, lapply(new.files, read.csv))
+new.dat <- new.dat %>%
+  filter(alive != 'dead')
+```
+
+Final plot type we can use to investigate the rate of change models (or just trajectories in general) are Spaghetti plots (lovingly created an titled by Rob - more evidence as to why he was banned from naming things).
+
+These plots show trajectories of single variable for individuals over the length of simulation, and are very useful for making sure people are not just bouncing around the mean which would be impossible to see from mean or otherwise aggregated plots.
+
+## hh_income
+
+```{r}
+spaghetti_plot(old.dat, 'hh_income')
+spaghetti_plot(new.dat, 'hh_income')
+spaghetti_plot(raw.dat, 'hh_income')
+```
+
+Much more variability in the raw data that we don't keep hold of in the simulation.
+Also shows that the spike in 2015 is mostly due to about 5-6 data points by the looks of things.
+Again worth a chat with the group to figure out where our acceptable thresholds are, as we are unlikely to be able to capture all of the heterogeneity in such a varied and skewed variable like hh_income.
+
+Almost no change.
+The only noticeable change at this resolution is a small shift up?
+Where some people who were below the zero line previously seem to have shifted up, and there are some trajectories that have been seemingly raised out of the main group and lie slightly above the average spread.
+Need to figure out why this is still happening with a completely different set of models...
+
+Very useful plot!
+
+## SF_12_MCS
+
+Quick look at SF_12_MCS also.
+
+```{r}
+spaghetti_plot(old.dat, 'SF_12')
+spaghetti_plot(new.dat, 'SF_12')
+spaghetti_plot(raw.dat, 'SF_12')
+```
+
+# Violin Plots
+
+## hh_income
+
+```{r}
+violin_plot(old.dat, 'hh_income')
+violin_plot(new.dat, 'hh_income')
+violin_plot(raw.dat, 'hh_income')
+```
+
+## SF12
+
+```{r}
+violin_plot(old.dat, 'SF_12')
+violin_plot(new.dat, 'SF_12')
+violin_plot(raw.dat, 'SF_12')
+```
+
 # Comparing SF12_MCS Diff
@@
 
-## Spaghetti Plots
-
-Final plot type we can use to investigate the rate of change models (or just trajectories in general) are Spaghetti plots (lovingly created an titled by Rob - more evidence as to why he was banned from naming things).
-
-These plots show trajectories of single variable for individuals over the length of simulation, and are very useful for making sure people are not just bouncing around the mean which would be impossible to see from mean or otherwise aggregated plots.
-
-### hh_income
-
-```{r}
-income.spag.base <- spaghetti_plot(base.dat, 'hh_income')
-income.spag.base
-
-income.spag.raw <- spaghetti_plot(raw.dat, 'hh_income')
-income.spag.raw
-```
-
-Much more variability in the raw data that we don't keep hold of in the simulation.
-Also shows that the spike in 2015 is mostly due to about 5-6 data points by the looks of things.
-Again worth a chat with the group to figure out where our acceptable thresholds are, as we are unlikely to be able to capture all of the heterogeneity in such a varied and skewed variable like hh_income.
-
-#### Comparison
-
-The base spaghetti plot doesn't look very good actually... I think I need a version using the previous models so I'll do a baseline run and save the data somewhere for testing purposes.
-
-```{r}
-old.files <- list.files('/home/luke/Documents/WORK/MINOS/PREVIOUS_OUTPUTS/mean_regen_income_sf12/', pattern='[0-9]{4}.csv', full.names = TRUE)
-old.dat <- do.call(rbind, lapply(old.files, read.csv))
-# remove dead people
-old.dat <- old.dat %>%
-  filter(alive != 'dead')
-
-income.spag.base <- spaghetti_plot(base.dat, 'hh_income')
-income.spag.base
-
-income.spag.old <- spaghetti_plot(old.dat, 'hh_income')
-income.spag.old
-```
-
-Almost no change.
-The only noticeable change at this resolution is a small shift up?
-Where some people who were below the zero line previously seem to have shifted up, and there are some trajectories that have been seemingly raised out of the main group and lie slightly above the average spread.
-Need to figure out why this is still happening with a completely different set of models...
-
-Very useful plot!
-
-### SF_12_MCS
-
-Quick look at SF_12_MCS also.
-
-```{r}
-sf12.spag.base <- spaghetti_plot(base.dat, 'SF_12')
-sf12.spag.base
-
-sf12.spag.raw <- spaghetti_plot(raw.dat, 'SF_12')
-sf12.spag.raw
-```
-Need to remove missing values.
-
-#### Comparison
-
-```{r}
-sf12.spag.base <- spaghetti_plot(base.dat, 'SF_12')
-sf12.spag.base
-
-sf12.spag.old <- spaghetti_plot(old.dat, 'SF_12')
-sf12.spag.old
-```
-
-## Violin Plots
-
-### hh_income
-
-```{r}
-income.violin.base <- violin_plot(base.dat, 'hh_income')
-income.violin.base
-
-income.violin.raw <- violin_plot(raw.dat, 'hh_income')
-income.violin.raw
-```
-
-### SF12
-
-```{r}
-sf12.violin.base <- violin_plot(base.dat, 'SF_12')
-sf12.violin.base
-
-sf12.violin.raw <- violin_plot(raw.dat, 'SF_12')
-sf12.violin.raw
-```
-
 ```{r}

### 2023-05-25 minos/validation/handovers.Rmd
Added spaghetti handovers for hh_income and SF_12 to handovers.Rmd

--- 2023-05-02 minos/validation/handovers.Rmd
@@
 ```{r}
-source('Minos/minos/validation/utils.r')
+source('Minos/minos/utils_datain.R')
+source('Minos/minos/utils_validation_vis.R')
 ```
@@
 out.path <- 'Minos/output/default_config/'
-base.dat <- read_output(out.path, 'baseline')
+base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
 ```
@@
 
-#rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
-#   raw.income.check, base.income.check)
+rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
+   raw.income.check, base.income.check)
+```
+
+### Spaghetti
+
+```{r}
+raw.inc <- raw.dat %>%
+  select(pidp, age, time, hh_income)
+base.inc <- base.dat %>%
+  select(pidp, age, time, hh_income)
+
+income.spag <- rbind(raw.inc, base.inc)
+
+spaghetti_plot(income.spag, 'hh_income',
+               save = TRUE,
+               save.path = save.path)
+
+rm(raw.inc, base.inc, income.spag)
 ```
@@
        path = save.path)
+
+rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
+```
+
+### Spaghetti
+
+```{r}
+raw.sf12 <- raw.dat %>%
+  select(pidp, age, time, SF_12)
+base.sf12 <- base.dat %>%
+  select(pidp, age, time, SF_12)
+
+sf12.spag <- rbind(raw.sf12, base.sf12)
+
+spaghetti_plot(sf12.spag, 'SF_12',
+               save = TRUE,
+               save.path = save.path)
+
+rm(raw.sf12, base.sf12, sf12.spag)
 ```

### 2023-06-01 minos/validation/handovers.Rmd

@@
 
-workingDir <- "/home/luke/Documents/WORK/MINOS/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/"
+workingDir <- "/home/luke/Documents/MINOS/"
 knitr::opts_knit$set(root.dir = workingDir)
@@
 # Read raw datafiles in
-raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files('/home/luke/Documents/MINOS/Minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 
-save.path <- '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Handovers/'
+save.path <- '/home/luke/Documents/MINOS/VALIDATION_PLOTS/Handovers/'
 ```

### 2023-06-01 minos/validation/cross_validation.Rmd

--- 2023-05-05 minos/validation/cross_validation.Rmd
@@
 
-workingDir <- "/home/luke/Documents/WORK/MINOS/"
+workingDir <- "/home/luke/Documents/MINOS/"
 knitr::opts_knit$set(root.dir = workingDir)
@@
                      save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
+
+compare_boxplot_long(pivoted.df = income.pivoted,
+                     var = 'hh_income',
+                     scen1 = 'raw',
+                     scen2 = 'simulation')
 

### 2023-06-09 minos/validation/handovers.Rmd
Added spaghetti handover plots for all ordinal variables. Might seem a bit daft but they at least tell us that people are moving between the levels in each wave (and therefore can identify a major problem)

--- 2023-05-25 minos/validation/handovers.Rmd
@@
 
+#workingDir <- "/home/luke/Documents/WORK/MINOS/"
 workingDir <- "/home/luke/Documents/WORK/MINOS/"
@@
 
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, housing_quality)
+base.s <- base.dat %>%
+  select(pidp, age, time, housing_quality)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'housing_quality',
+               save = TRUE,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
 ## Neighbourhood Safety
@@
 
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, neighbourhood_safety)
+base.s <- base.dat %>%
+  select(pidp, age, time, neighbourhood_safety)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'neighbourhood_safety',
+               save = TRUE,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
 ## Loneliness
@@
 rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, loneliness)
+base.s <- base.dat %>%
+  select(pidp, age, time, loneliness)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'loneliness',
+               save = TRUE,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
     nutrition_quality2)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, nutrition_quality)
+base.s <- base.dat %>%
+  select(pidp, age, time, nutrition_quality)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nutrition_quality',
+               save = TRUE,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, phealth)
+base.s <- base.dat %>%
+  select(pidp, age, time, phealth)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'phealth',
+               save = TRUE,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
 ```{r}

### 2023-06-09 minos/validation/handovers.Rmd
making relative paths in handovers and adding finsit graph

--- 2023-05-25 minos/validation/handovers.Rmd
@@
 title: "MINOS Handover Plots"
-output: html_notebook
+output:
+  html_document:
+    df_print: paged
 ---
@@
 require(ggplot2)
+require(knitr)
+require(here)
 
-workingDir <- "/home/luke/Documents/WORK/MINOS/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/"
+workingDir <- normalizePath('../')
 knitr::opts_knit$set(root.dir = workingDir)
@@
 ```{r}
-source('Minos/minos/utils_datain.R')
-source('Minos/minos/utils_validation_vis.R')
+source(here::here('minos', 'utils_datain.R'))
+source(here::here('minos', 'utils_validation_vis.R'))
 ```
@@
 # Read raw datafiles in
-raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
 
-out.path <- 'Minos/output/default_config/'
+out.path <- here::here('output', 'default_config/')
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
@@
 start.year <- 2020
-
-save.path <- '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Handovers/'
+save.path <- here::here("plots", "handovers")
+#create.if.not.exists(save.path)
 ```
@@
 rm(raw.sf12, base.sf12, sf12.spag)
+```
+
+## Financial Situation
+
+## Housing Quality
+
+```{r}
+raw.financial_situation <- raw.dat %>% 
+  dplyr::select(pidp, time, financial_situation) %>%
+  group_by(time, financial_situation) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.financial_situation <- base.dat %>%
+  dplyr::select(pidp, time, financial_situation) %>%
+  group_by(time, financial_situation) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+financial_situation <- rbind(raw.financial_situation, base.financial_situation)
+financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
+
+# Now plot
+ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+financial_situation.norm <- financial_situation %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial situation') +
+  xlab('Year') +
+  ylab('Proportion')
+
+ggsave(filename = 'financial_situation.png',
+       plot = last_plot(),
+       path = save.path)
+
+rm(raw.housing, base.housing, housing, housing.norm)
 ```

### 2023-06-12 minos/validation/handovers_S7.Rmd
Added a separate handovers script for SIPHER 7 vars, and modified the cv ordinal plots function to allow for handovers as they are useful in combination with other handovers

---
title: "Handovers - SIPHER 7 Equivalent Income"
output: html_notebook
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

Source utils for some functions.

```{r}
source('Minos/minos/utils_datain.R')
source('Minos/minos/utils_validation_vis.R')
```

## Data

```{r}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

out.path <- 'Minos/output/SIPHER7/'
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

## Constants

```{r}
start.year <- 2020

save.path <- '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/SIPHER7/Handovers/'
```

# INPUTS

## Income

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.income <- raw.dat %>% 
  dplyr::select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm=TRUE)) %>%
  mutate(source = 'final_US')

base.income <- base.dat %>%
  dplyr::select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income)) %>%
  mutate(source = 'baseline_output')

# merge before plot
income <- rbind(raw.income, base.income)

# Now plot
ggplot(data = income, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Household Income', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Income')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.income.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.income2 <- raw.dat %>% 
  dplyr::select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.income2 <- base.dat %>%
  dplyr::select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

income2 <- rbind(raw.income2, base.income2)

# Now plot
ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Household Income') +
  xlab('Year') +
  ylab('Income')

ggsave(filename = 'hh_income_wav1.png',
       plot = last_plot(),
       path = save.path)

raw.income.check <- raw.dat %>% 
  dplyr::select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

base.income.check <- base.dat %>%
  dplyr::select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
   raw.income.check, base.income.check)
```

### Spaghetti

```{r}
raw.inc <- raw.dat %>%
  select(pidp, age, time, hh_income)
base.inc <- base.dat %>%
  select(pidp, age, time, hh_income)

income.spag <- rbind(raw.inc, base.inc)

spaghetti_plot(income.spag, 'hh_income',
               save = TRUE,
               save.path = save.path)

rm(raw.inc, base.inc, income.spag)
```

# OUTCOMES

## Equivalent Income

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.ei <- raw.dat %>% 
  dplyr::select(pidp, time, equivalent_income) %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.ei <- base.dat %>%
  dplyr::select(pidp, time, equivalent_income) %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
ei <- rbind(raw.ei, base.ei)
# drop -9 values (missing)
ei <- ei %>%
  filter(equivalent_income != -9)

# Now plot
ggplot(data = ei, mapping = aes(x = time, y = equivalent_income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Equivalent Income', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('EI')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.ei.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.ei.2 <- raw.dat %>% 
  dplyr::select(pidp, time, equivalent_income) %>%
  filter(pidp %in% raw.ei.wave1) %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.ei.2 <- base.dat %>%
  dplyr::select(pidp, time, equivalent_income) %>%
  filter(pidp %in% raw.ei.wave1) %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

ei.2 <- rbind(raw.ei.2, base.ei.2)
# drop -9 values (missing)
ei.2 <- ei.2 %>%
  filter(equivalent_income != -9)

# Now plot
ggplot(data = ei.2, mapping = aes(x = time, y = equivalent_income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Equivalent Income') +
  xlab('Year') +
  ylab('EI')

ggsave(filename = 'EI_wav1.png',
       plot = last_plot(),
       path = save.path)

rm(raw.ei, base.ei, ei, raw.ei.wave1, raw.ei.2, base.ei.2, ei.2)
```

### Spaghetti

```{r}
raw.ei <- raw.dat %>%
  select(pidp, age, time, equivalent_income)
base.ei <- base.dat %>%
  select(pidp, age, time, equivalent_income)

ei.spag <- rbind(raw.ei, base.ei)

spaghetti_plot(ei.spag, 'equivalent_income',
               save = TRUE,
               save.path = save.path)

rm(raw.ei, base.ei, ei.spag)
```

# PATHWAYS

## Housing Quality

```{r}
# first figure out how to plot final_US
# start with hh_income
raw <- raw.dat %>% 
  dplyr::select(pidp, time, S7_housing_quality, weight) %>%
  group_by(time) %>%
  summarise(housing_quality = mean(S7_housing_quality, na.rm=TRUE)) %>%
  mutate(source = 'final_US')

base <- base.dat %>%
  dplyr::select(pidp, time, S7_housing_quality, weight) %>%
  group_by(time) %>%
  summarise(housing_quality = mean(S7_housing_quality)) %>%
  mutate(source = 'baseline_output')

# merge before plot
housing_quality <- rbind(raw, base)

# Now plot
ggplot(data = housing_quality, mapping = aes(x = time, y = housing_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Quality', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Income')
```

TODO: Make these ordinal plots as handovers (might just need to change cv to baseline?)

```{r}
hous.pivoted <- combine_and_pivot_long(df1 = cv, 
                                       df1.name = 'simulated', 
                                       df2 = raw, 
                                       df2.name = 'raw', 
                                       var = 'S7_housing_quality')

cv_ordinal_plots(pivoted.df = hous.pivoted, 
                 var = 'housing_quality',
                 save = TRUE,
                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
```

### Spaghetti

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_housing_quality)
base.s <- base.dat %>%
  select(pidp, age, time, S7_housing_quality)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'S7_housing_quality',
               save = TRUE,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

```{r}

```

### 2023-06-12 minos/validation/handovers_S7.Rmd
Setting factor levels of S7_neighbourhood_safety to ensure predicted values match the correct levels. Also expanding the handovers_S7 notebook

@@
 require(ggplot2)
+require(here)
 
-workingDir <- "/home/luke/Documents/WORK/MINOS/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/"
+workingDir <- normalizePath('../')
 knitr::opts_knit$set(root.dir = workingDir)
@@
 ```{r}
-source('Minos/minos/utils_datain.R')
-source('Minos/minos/utils_validation_vis.R')
+source(here::here('minos', 'utils_datain.R'))
+source(here::here('minos', 'utils_validation_vis.R'))
+source(here::here('minos', 'validation', 'utils.r'))
 ```
@@
 
-out.path <- 'Minos/output/SIPHER7/'
+#out.path <- 'Minos/output/SIPHER7/'
+out.path <- here::here('output', 'SIPHER7/')
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
@@
 
+spaghetti_plot(base.ei, 'equivalent_income')
+
 spaghetti_plot(ei.spag, 'equivalent_income',
@@
 
-## Housing Quality
+## S7 Housing Quality
 
 ```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw <- raw.dat %>% 
-  dplyr::select(pidp, time, S7_housing_quality, weight) %>%
-  group_by(time) %>%
-  summarise(housing_quality = mean(S7_housing_quality, na.rm=TRUE)) %>%
-  mutate(source = 'final_US')
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_housing_quality')
 
-base <- base.dat %>%
-  dplyr::select(pidp, time, S7_housing_quality, weight) %>%
-  group_by(time) %>%
-  summarise(housing_quality = mean(S7_housing_quality)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-housing_quality <- rbind(raw, base)
+housing <- prepped.list$var
+housing.norm <- prepped.list$norm
 
 # Now plot
-ggplot(data = housing_quality, mapping = aes(x = time, y = housing_quality, group = source, colour = source)) +
+ggplot(data = housing, mapping = aes(x = time, y = n, group = S7_housing_quality, colour = S7_housing_quality)) +
   geom_line() +
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Quality', subtitle = 'Full Sample') +
+  labs(title = 'S7 Housing Quality', subtitle = 'Counts by Level') +
   xlab('Year') +
-  ylab('Income')
+  ylab('Count')
+
+ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=S7_housing_quality)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Housing Quality') +
+  xlab('Year') +
+  ylab('Proportion')
+
+ggsave(filename = 'S7_housing_quality.png',
+       plot = last_plot(),
+       path = save.path)
+
+rm(prepped.list, housing, housing.norm)
 ```
 
-TODO: Make these ordinal plots as handovers (might just need to change cv to baseline?)
-
 ```{r}
-hous.pivoted <- combine_and_pivot_long(df1 = cv, 
+hous.pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                        df1.name = 'simulated', 
-                                       df2 = raw, 
+                                       df2 = raw.dat, 
                                        df2.name = 'raw', 
@@
 cv_ordinal_plots(pivoted.df = hous.pivoted, 
-                 var = 'housing_quality',
+                 var = 'S7_housing_quality',
                  save = TRUE,
@@
 spaghetti_plot(spag, 'S7_housing_quality',
+               save = FALSE,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+## S7 Neighbourhood Safety
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_neighbourhood_safety')
+
+nh_safety <- prepped.list$var
+nh_safety.norm <- prepped.list$norm
+
+# Now plot
+ggplot(data = nh_safety, mapping = aes(x = time, y = n, group = S7_neighbourhood_safety, colour = S7_neighbourhood_safety)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Neighbourhood Safety', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = nh_safety.norm, mapping = aes(x = time, y = prct, fill=S7_neighbourhood_safety)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Neighbourhood Safety') +
+  xlab('Year') +
+  ylab('Proportion')
+
+ggsave(filename = 'S7_neighbourhood_safety.png',
+       plot = last_plot(),
+       path = save.path)
+
+rm(prepped.list, nh_safety, nh_safety.norm)
+```
+
+```{r}
+hous.pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'S7_neighbourhood_safety')
+
+cv_ordinal_plots(pivoted.df = hous.pivoted, 
+                 var = 'S7_neighbourhood_safety',
+                 save = FALSE,
+                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, S7_neighbourhood_safety)
+base.s <- base.dat %>%
+  select(pidp, age, time, S7_neighbourhood_safety)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'S7_neighbourhood_safety',
                save = TRUE,

### 2023-06-12 minos/validation/handovers_S7.Rmd
Expanded the handovers_S7 script with lots of additional validation plots

@@
 # Read raw datafiles in
-raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 start.year <- 2020
+save.path <- here::here("plots", "handovers", 'SIPHER7')
+create.if.not.exists(save.path)
 
-save.path <- '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/SIPHER7/Handovers/'
+shall.we.save <- TRUE
 ```
@@
                  save = TRUE,
-                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
+                 save.path = save.path)
 ```
@@
 ```{r}
-hous.pivoted <- combine_and_pivot_long(df1 = base.dat, 
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                        df1.name = 'simulated', 
@@
 
-cv_ordinal_plots(pivoted.df = hous.pivoted, 
+cv_ordinal_plots(pivoted.df = pivoted, 
                  var = 'S7_neighbourhood_safety',
                  save = FALSE,
-                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
+                 save.path = save.path)
 ```
@@
 
+## S7 Labour State
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
+
+lab.state <- prepped.list$var
+lab.state.norm <- prepped.list$norm
+
+# Now plot
+ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State') +
+  xlab('Year') +
+  ylab('Proportion')
+
+ggsave(filename = 'S7_labour_state.png',
+       plot = last_plot(),
+       path = save.path)
+
+rm(prepped.list, lab.state, lab.state.norm)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'S7_labour_state')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'S7_labour_state',
+                 save = FALSE,
+                 save.path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, S7_labour_state)
+base.s <- base.dat %>%
+  select(pidp, age, time, S7_labour_state)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'S7_labour_state',
+               save = TRUE,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+## S7 Physical Health
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_physical_health')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'S7 Physical Health'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = S7_physical_health, colour = S7_physical_health)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=S7_physical_health)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+ggsave(filename = 'S7_physical_health.png',
+       plot = last_plot(),
+       path = save.path)
+
+rm(prepped.list, var, norm, tit)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'S7_physical_health')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'S7_physical_health',
+                 save = FALSE,
+                 save.path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, S7_physical_health)
+base.s <- base.dat %>%
+  select(pidp, age, time, S7_physical_health)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'S7_physical_health',
+               save = TRUE,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+## S7 Mental Health
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_mental_health')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'S7 Mental Health'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = S7_mental_health, colour = S7_mental_health)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=S7_mental_health)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+ggsave(filename = 'S7_mental_health.png',
+       plot = last_plot(),
+       path = save.path)
+
+rm(prepped.list, var, norm, tit)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'S7_mental_health')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'S7_mental_health',
+                 save = FALSE,
+                 save.path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, S7_mental_health)
+base.s <- base.dat %>%
+  select(pidp, age, time, S7_mental_health)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'S7_mental_health',
+               save = TRUE,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
 ```{r}

### 2023-06-13 minos/validation/handovers_S7.Rmd
Added physical health, mental health, loneliness, and education level to the handovers_S7 script

@@
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Equivalent Income') +
+  labs(title = 'Equivalent Income', subtitle = 'Wave 1 sample') +
   xlab('Year') +
@@
 
+## Loneliness
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'loneliness')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Loneliness'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+ggsave(filename = 'loneliness.png',
+       plot = last_plot(),
+       path = save.path)
+
+rm(prepped.list, var, norm, tit)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'loneliness')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'loneliness',
+                 save = FALSE,
+                 save.path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, loneliness)
+base.s <- base.dat %>%
+  select(pidp, age, time, loneliness)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'loneliness',
+               save = TRUE,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+## Education
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Education State'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+ggsave(filename = 'education_state.png',
+       plot = last_plot(),
+       path = save.path)
+
+rm(prepped.list, var, norm, tit)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'education_state')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'education_state',
+                 save = FALSE,
+                 save.path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, education_state)
+base.s <- base.dat %>%
+  select(pidp, age, time, education_state)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'education_state',
+               save = TRUE,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
 ```{r}

### 2023-06-13 minos/validation/handovers_S7.Rmd
Properly using the "shall.we.save" boolean to decide whether to save the plots or not

@@
 
+if (shall.we.save) {
   ggsave(filename = 'hh_income_wav1.png',
@@
          path = save.path)
+}
 
@@
 spaghetti_plot(income.spag, 'hh_income',
-               save = TRUE,
+               save = shall.we.save,
                save.path = save.path)
@@
 
+if (shall.we.save) {
   ggsave(filename = 'EI_wav1.png',
@@
 spaghetti_plot(ei.spag, 'equivalent_income',
-               save = TRUE,
+               save = shall.we.save,
                save.path = save.path)
@@
 
+if (shall.we.save) {
   ggsave(filename = 'S7_housing_quality.png',
@@
                  var = 'S7_housing_quality',
-                 save = TRUE,
+                 save = shall.we.save,
                  save.path = save.path)
@@
 spaghetti_plot(spag, 'S7_housing_quality',
-               save = FALSE,
+               save = shall.we.save,
                save.path = save.path)
@@
 
+if (shall.we.save) {
   ggsave(filename = 'S7_neighbourhood_safety.png',
@@
                  var = 'S7_neighbourhood_safety',
-                 save = FALSE,
+                 save = shall.we.save,
                  save.path = save.path)
@@
 spaghetti_plot(spag, 'S7_neighbourhood_safety',
-               save = TRUE,
+               save = shall.we.save,
                save.path = save.path)
@@
 
+if (shall.we.save) {
   ggsave(filename = 'S7_labour_state.png',
@@
                  var = 'S7_labour_state',
-                 save = FALSE,
+                 save = shall.we.save,
                  save.path = save.path)
@@
 spaghetti_plot(spag, 'S7_labour_state',
-               save = TRUE,
+               save = shall.we.save,
                save.path = save.path)
@@
 
+if (shall.we.save) {
   ggsave(filename = 'S7_physical_health.png',
@@
                  var = 'S7_physical_health',
-                 save = FALSE,
+                 save = shall.we.save,
                  save.path = save.path)
@@
 spaghetti_plot(spag, 'S7_physical_health',
-               save = TRUE,
+               save = shall.we.save,
                save.path = save.path)
@@
 
+if (shall.we.save) {
   ggsave(filename = 'S7_mental_health.png',
@@
                  var = 'S7_mental_health',
-                 save = FALSE,
+                 save = shall.we.save,
                  save.path = save.path)
@@
 spaghetti_plot(spag, 'S7_mental_health',
-               save = TRUE,
+               save = shall.we.save,
                save.path = save.path)
@@
 
+if (shall.we.save) {
   ggsave(filename = 'loneliness.png',
@@
                  var = 'loneliness',
-                 save = FALSE,
+                 save = shall.we.save,
                  save.path = save.path)
@@
 spaghetti_plot(spag, 'loneliness',
-               save = TRUE,
+               save = shall.we.save,
                save.path = save.path)
@@
 
+if (shall.we.save) {
   ggsave(filename = 'education_state.png',
@@
                  var = 'education_state',
-                 save = FALSE,
+                 save = shall.we.save,
                  save.path = save.path)
@@
 spaghetti_plot(spag, 'education_state',
-               save = TRUE,
+               save = shall.we.save,
                save.path = save.path)

### 2023-06-13 minos/validation/handovers.Rmd
Now saving handover plots to a default folder when running default handovers

@@
 start.year <- 2020
-save.path <- here::here("plots", "handovers")
-#create.if.not.exists(save.path)
+save.path <- here::here("plots", "handovers", 'default')
+create.if.not.exists(save.path)
 ```
@@
 
+## Education
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Education State'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'education_state.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'education_state')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'education_state',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, education_state)
+base.s <- base.dat %>%
+  select(pidp, age, time, education_state)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'education_state',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
 ```{r}

### 2023-06-13 minos/testing/education_transitions.Rmd
Started script for testing education transitions

--- 2023-06-13 minos/validation/handovers_S7.Rmd
@@
 ---
-title: "Handovers - SIPHER 7 Equivalent Income"
+title: "Testing Education State Transitions"
 output: html_notebook
 ---
+
+Currently, a respondents max education state is predicted before the pipeline begins, during production of the stock and replenishing populations (after estimating the education state model).
+Individuals are then deterministically transitioned to higher education states at specific ages.
+This is a big assumption in and of itself, but more work to get this closer to reality would most likely have a negligible effect on our population and even smaller on the outcomes.
+
+The issue with this is to handle the move from deterministic transitions to the model based predictions in the S7_labour_state variable.
+The labour state variable has a factor level for full time education, which needs to work in partnership with the education_state variable and the education module.
+What we can do is force the labour state variable to FT education until a respondent reaches their max education level, and then move to transitioning their labour state based on the transition model.
+This will probably mean some people are transitioned back into FT education throughout the model, but hopefully this number will be small enough to be negligible (fewer numbers still in education as age increases in raw data).
+
+Tasks:
+
+- [ ] Check what age people achieve each level of education
+- [ ] Average age plot (see if change over time in raw)
+  - [ ] Histograms
+  - [ ] Animated histograms?
+- [ ] Force labour_state to FT education until max_educ has been reached (this might already have been done)
+- [ ] Change labour_state prediction to only run for those who have reached max_educ
+- [ ] Check how many people move into FT education after age of 30
+- [ ] Make sure stock population is doing max_educ prediction
+
+IF all the above goes well, add S7_labour_state variable into the default income -> SF12 experiment, so we can use the same education functionality in there also.
+Plus labour_state is an important variable there that is currently missing.
 
@@
 
-# INPUTS
+# Raw Testing
 
-## Income
+What age do people generally transition into each education level?
 
 ```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.income <- raw.dat %>% 
-  dplyr::select(pidp, time, hh_income, weight) %>%
-  group_by(time) %>%
-  summarise(income = mean(hh_income, na.rm=TRUE)) %>%
-  mutate(source = 'final_US')
 
-base.income <- base.dat %>%
-  dplyr::select(pidp, time, hh_income, weight) %>%
-  group_by(time) %>%
-  summarise(income = mean(hh_income)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-income <- rbind(raw.income, base.income)
-
-# Now plot
-ggplot(data = income, mapping = aes(x = time, y = income, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Household Income', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Income')
-
-## Try a version where final_US is limited to only those present from wave 1 
-# onwards because the sample refreshments are messing with the plot
-raw.income.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.income2 <- raw.dat %>% 
-  dplyr::select(pidp, time, hh_income) %>%
-  filter(pidp %in% raw.income.wave1) %>%
-  group_by(time) %>%
-  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.income2 <- base.dat %>%
-  dplyr::select(pidp, time, hh_income) %>%
-  filter(pidp %in% raw.income.wave1) %>%
-  group_by(time) %>%
-  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-income2 <- rbind(raw.income2, base.income2)
-
-# Now plot
-ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Household Income') +
-  xlab('Year') +
-  ylab('Income')
-
-if (shall.we.save) {
-  ggsave(filename = 'hh_income_wav1.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-raw.income.check <- raw.dat %>% 
-  dplyr::select(pidp, time, hh_income) %>%
-  filter(pidp %in% raw.income.wave1)
-
-base.income.check <- base.dat %>%
-  dplyr::select(pidp, time, hh_income) %>%
-  filter(pidp %in% raw.income.wave1)
-
-rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
-   raw.income.check, base.income.check)
 ```
 
-### Spaghetti
-
-```{r}
-raw.inc <- raw.dat %>%
-  select(pidp, age, time, hh_income)
-base.inc <- base.dat %>%
-  select(pidp, age, time, hh_income)
-
-income.spag <- rbind(raw.inc, base.inc)
-
-spaghetti_plot(income.spag, 'hh_income',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.inc, base.inc, income.spag)
-```
-
-# OUTCOMES
-
-## Equivalent Income
-
-```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.ei <- raw.dat %>% 
-  dplyr::select(pidp, time, equivalent_income) %>%
-  group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.ei <- base.dat %>%
-  dplyr::select(pidp, time, equivalent_income) %>%
-  group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-ei <- rbind(raw.ei, base.ei)
-# drop -9 values (missing)
-ei <- ei %>%
-  filter(equivalent_income != -9)
-
-# Now plot
-ggplot(data = ei, mapping = aes(x = time, y = equivalent_income, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Equivalent Income', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('EI')
-
-## Try a version where final_US is limited to only those present from wave 1 
-# onwards because the sample refreshments are messing with the plot
-raw.ei.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.ei.2 <- raw.dat %>% 
-  dplyr::select(pidp, time, equivalent_income) %>%
-  filter(pidp %in% raw.ei.wave1) %>%
-  group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.ei.2 <- base.dat %>%
-  dplyr::select(pidp, time, equivalent_income) %>%
-  filter(pidp %in% raw.ei.wave1) %>%
-  group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-ei.2 <- rbind(raw.ei.2, base.ei.2)
-# drop -9 values (missing)
-ei.2 <- ei.2 %>%
-  filter(equivalent_income != -9)
-
-# Now plot
-ggplot(data = ei.2, mapping = aes(x = time, y = equivalent_income, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Equivalent Income', subtitle = 'Wave 1 sample') +
-  xlab('Year') +
-  ylab('EI')
-
-if (shall.we.save) {
-  ggsave(filename = 'EI_wav1.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(raw.ei, base.ei, ei, raw.ei.wave1, raw.ei.2, base.ei.2, ei.2)
-```
-
-### Spaghetti
-
-```{r}
-raw.ei <- raw.dat %>%
-  select(pidp, age, time, equivalent_income)
-base.ei <- base.dat %>%
-  select(pidp, age, time, equivalent_income)
-
-ei.spag <- rbind(raw.ei, base.ei)
-
-spaghetti_plot(base.ei, 'equivalent_income')
-
-spaghetti_plot(ei.spag, 'equivalent_income',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.ei, base.ei, ei.spag)
-```
-
-# PATHWAYS
-
-## S7 Housing Quality
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_housing_quality')
-
-housing <- prepped.list$var
-housing.norm <- prepped.list$norm
-
-# Now plot
-ggplot(data = housing, mapping = aes(x = time, y = n, group = S7_housing_quality, colour = S7_housing_quality)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Housing Quality', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=S7_housing_quality)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Housing Quality') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'S7_housing_quality.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, housing, housing.norm)
-```
-
-```{r}
-hous.pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'S7_housing_quality')
-
-cv_ordinal_plots(pivoted.df = hous.pivoted, 
-                 var = 'S7_housing_quality',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, S7_housing_quality)
-base.s <- base.dat %>%
-  select(pidp, age, time, S7_housing_quality)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'S7_housing_quality',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## S7 Neighbourhood Safety
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_neighbourhood_safety')
-
-nh_safety <- prepped.list$var
-nh_safety.norm <- prepped.list$norm
-
-# Now plot
-ggplot(data = nh_safety, mapping = aes(x = time, y = n, group = S7_neighbourhood_safety, colour = S7_neighbourhood_safety)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Neighbourhood Safety', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = nh_safety.norm, mapping = aes(x = time, y = prct, fill=S7_neighbourhood_safety)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Neighbourhood Safety') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'S7_neighbourhood_safety.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, nh_safety, nh_safety.norm)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'S7_neighbourhood_safety')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'S7_neighbourhood_safety',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, S7_neighbourhood_safety)
-base.s <- base.dat %>%
-  select(pidp, age, time, S7_neighbourhood_safety)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'S7_neighbourhood_safety',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## S7 Labour State
+# S7 Labour State
 
@@
 
-### Spaghetti
+## Spaghetti
 
@@
 
-## S7 Physical Health
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_physical_health')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'S7 Physical Health'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = S7_physical_health, colour = S7_physical_health)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=S7_physical_health)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'S7_physical_health.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'S7_physical_health')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'S7_physical_health',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, S7_physical_health)
-base.s <- base.dat %>%
-  select(pidp, age, time, S7_physical_health)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'S7_physical_health',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## S7 Mental Health
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_mental_health')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'S7 Mental Health'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = S7_mental_health, colour = S7_mental_health)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=S7_mental_health)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'S7_mental_health.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'S7_mental_health')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'S7_mental_health',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, S7_mental_health)
-base.s <- base.dat %>%
-  select(pidp, age, time, S7_mental_health)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'S7_mental_health',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## Loneliness
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'loneliness')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Loneliness'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'loneliness.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'loneliness')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'loneliness',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, loneliness)
-base.s <- base.dat %>%
-  select(pidp, age, time, loneliness)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'loneliness',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## Education
+# Education
 

### 2023-06-14 minos/validation/interventions.Rmd
Updated interventions.Rmd with here package

--- 2023-03-01 minos/validation/interventions.Rmd
@@
 require(purrr)
-require(ordinal)
-require(nnet)
-require(pscl)
+require(here)
 
-workingDir <- "/home/luke/Documents/WORK/MINOS/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/"
+workingDir <- normalizePath('../')
 knitr::opts_knit$set(root.dir = workingDir)
@@
 ```{r}
-source('Minos/minos/validation/utils.r')
+#source('Minos/minos/validation/utils.r')
+source(here::here('minos', 'validation', 'utils.r'))
 ```
@@
 #out.path <- 'Minos/output/scotland_mode/'
+out.path <- here::here('minos', 'default_config/')
 
-base <- read_output(out.path, 'baseline')
-allchild <- read_output(out.path, 'hhIncomeChildUplift')
-poverty <- read_output(out.path, 'hhIncomePovertyLineChildUplift')
-wage <- read_output(out.path, 'livingWageIntervention')
-energy <- read_output(out.path, 'energyDownlift')
+base <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+allchild <- read_singular_local_out(out.path, 'hhIncomeChildUplift', drop.dead = TRUE)
+poverty <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift', drop.dead = TRUE)
+wage <- read_singular_local_out(out.path, 'livingWageIntervention', drop.dead = TRUE)
+energy <- read_singular_local_out(out.path, 'energyDownlift', drop.dead = TRUE)
 
@@
 
-## Transition Models
-
-```{r, include=FALSE}
-trans.path <- 'Minos/data/transitions/'
-
-educ.mod <- readRDS(paste0(trans.path, 'education_state/nnet/education_state_2018_2019.rds'))
-sf_12.mod <- readRDS(paste0(trans.path, 'SF_12/ols/SF_12_2018_2019.rds'))
-house.mod <- readRDS(paste0(trans.path, 'housing_quality/clm/housing_quality_2018_2019.rds'))
-income.mod <- readRDS(paste0(trans.path, 'hh_income/ols/hh_income_2018_2019.rds'))
-nut.mod <- readRDS(paste0(trans.path, 'nutrition_quality/ols/nutrition_quality_2018_2019.rds'))
-```
-
 # Energy Downlift
-
-## Household Income
 
@@
 
-## Pathways
-
-### Housing Quality
-
-```{r}
-compare_housing_out(base, energy)
-```
-
-### Neighbourhood Safety
-
-```{r}
-compare_neighbourhood_out(base, energy)
-```
-
-### Tobacco Use
-
-```{r}
-compare_ncigs_out(base, energy)
-```
-
-### Nutrition Quality
-
-```{r}
-compare_nutrition_out(base, energy)
-```
-
-### Loneliness (NOT CURRENTLY IN SF12 MODEL)
-
-```{r}
-compare_loneliness_out(base, energy)
-```
-
 ## Boost Amount
@@
 
-## Household Income
-
 ```{r}
@@
 ```
-
-## Pathways
-
-```{r}
-compare_housing_out(base, wage)
-compare_neighbourhood_out(base, wage)
-compare_ncigs_out(base, wage)
-compare_nutrition_out(base, wage)
-compare_loneliness_out(base, wage)
-```
-
-## Boost Amount
 
@@
 ```
-
-## Pathways
-
-```{r}
-compare_housing_out(base, allchild)
-compare_neighbourhood_out(base, allchild)
-compare_ncigs_out(base, allchild)
-compare_nutrition_out(base, allchild)
-compare_loneliness_out(base, allchild)
-```
-
-## Boost Amount
 
@@
 
-# END
-
 ```{r}

### 2023-06-15 minos/testing/education_transitions.Rmd
WIP trying to figure out how many people transition into different education levels and at what age
Added some chunks to investigate the ages at which people achieve certain education levels, and the mean age for each level

@@
 ```{r}
+raw <- raw.dat %>%
+  select(pidp, time, age, education_state) %>%
+  arrange(pidp, time) %>%
+  group_by(pidp) %>%
+  mutate(levelUp = ifelse(education_state != dplyr::lag(education_state, order_by=time), TRUE, FALSE)) %>%
+  filter(!is.na(levelUp)) %>%
+  filter(levelUp == TRUE)
+
+ggplot(data = filter(raw, education_state == 2), aes(x = age)) +
+  geom_histogram() +
+  labs(title = 'Education State == 2')
+
+ggplot(data = filter(raw, education_state == 3), aes(x = age)) +
+  geom_histogram() +
+  labs(title = 'Education State == 3')
+
+ggplot(data = filter(raw, education_state == 5), aes(x = age)) +
+  geom_histogram() +
+  labs(title = 'Education State == 5')
+
+ggplot(data = filter(raw, education_state == 6), aes(x = age)) +
+  geom_histogram() +
+  labs(title = 'Education State == 6')
+
+ggplot(data = filter(raw, education_state == 7), aes(x = age)) +
+  geom_histogram() +
+  labs(title = 'Education State == 7')
+
+raw$education_state <- factor(raw$education_state)
+
+ggplot(data = raw, aes(x = age, group = education_state, fill = education_state)) +
+  geom_histogram()
+  labs(title = 'Education state')
 

### 2023-06-15 minos/validation/interventions.Rmd
Copied Robs changes into interventions.Rmd, and added some whitespace to make the notebook render properly on browsers

@@
 title: "Investigating Interventions"
-output: html_notebook
+output:
+  html_document:
+    df_print: paged
 ---
-
 # Setup
-
 ```{r "setup", include=FALSE}
-
 require(tidyverse)
@@
 require(here)
-
 #workingDir <- "/home/luke/Documents/WORK/MINOS/"
@@
 ```
+Source utils for some functions.
 
-Source utils for some functions.
 ```{r}
@@
 source(here::here('minos', 'validation', 'utils.r'))
+#source('/Users/robertclay/minos/minos/utils_datain.R')
+source(here::here('minos', 'utils_datain.r'))
+
 ```
@@
 ```{r}
-out.path <- 'Minos/output/default_config/'
+#out.path <- 'Minos/output/default_config/'
 #out.path <- 'Minos/output/scotland_mode/'
-out.path <- here::here('minos', 'default_config/')
-
+out.path <- here::here('output', 'default_config/')
 base <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
@@
 energy <- read_singular_local_out(out.path, 'energyDownlift', drop.dead = TRUE)
-
 ```
@@
   select(pidp, time, hh_income)
-
 income.energy <- energy %>% 
   select(pidp, time, hh_income, income_boosted)
-
 # first rename and cbind
@@
 income.e <- rename(income.energy, energy = hh_income)
-
 income.merged <- merge(income.b, income.e, by=c('pidp', 'time'))
-
 income.merged <- pivot_longer(data = income.merged,
@@
                               values_to = 'hh_income')
-
 income.merged.byyr <- income.merged %>%
@@
   summarise(hh_income = mean(hh_income))
-
 ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
@@
   select(pidp, time, SF_12)
-
 sf12.energy <- energy %>% 
   select(pidp, time, SF_12, income_boosted)
-
 # first rename and cbind
@@
 sf12.e <- rename(sf12.energy, energy = SF_12)
-
 sf12.merged <- merge(sf12.b, sf12.e, by=c('pidp', 'time'))
-
 sf12.merged <- pivot_longer(data = sf12.merged,
@@
                               values_to = 'SF_12')
-
 sf12.merged.byyr <- sf12.merged %>%
@@
   summarise(SF_12 = mean(SF_12))
-
 ggplot(data = sf12.merged.byyr, mapping = aes(x = time, y = SF_12, color=scenario)) +
@@
 ## Boost Amount
-
 ```{r}
@@
   select(pidp, time, hh_income, income_boosted, boost_amount)
-
 income.energy.byyr <- income.energy %>%
@@
   summarise(boost_amount = mean(boost_amount))
-
 ggplot(data = income.energy.byyr, mapping = aes(x = time, y = boost_amount)) +
@@
   count(income_boosted)
-
 ggplot(data = filter(boosted.byyr, income_boosted == 'True'), mapping = aes(x = time, y = n)) +
@@
   select(pidp, time, hh_income)
-
 income.wage <- wage %>% 
   select(pidp, time, hh_income, income_boosted)
-
 # first rename and cbind
@@
 income.w <- rename(income.wage, wage = hh_income)
-
 income.merged <- merge(income.b, income.w, by=c('pidp', 'time'))
-
 income.merged <- pivot_longer(data = income.merged,
@@
 ```
-
 ```{r}
@@
   select(pidp, time, hh_income, income_boosted, boost_amount)
-
 income.wage.byyr <- income.wage %>%
@@
   summarise(boost_amount = mean(boost_amount))
-
 ggplot(data = income.wage.byyr, mapping = aes(x = time, y = boost_amount)) +
@@
   count(income_boosted)
-
 ggplot(data = filter(boosted.byyr, income_boosted == 'True'), mapping = aes(x = time, y = n)) +
   geom_line()
-
 ggplot(data = boosted.byyr, mapping = aes(x = time, y = n, color = income_boosted)) +
@@
   select(pidp, time, hh_income)
-
 income.child <- allchild %>% 
   select(pidp, time, hh_income, income_boosted)
-
 # first rename and cbind
@@
 income.child <- rename(income.child, allchild = hh_income)
-
 income.merged <- merge(income.base, income.child, by=c('pidp', 'time'))
-
 income.merged <- pivot_longer(data = income.merged,
@@
   select(pidp, time, hh_income, income_boosted, boost_amount)
-
 income.child.byyr <- income.child %>%
@@
   summarise(boost_amount = mean(boost_amount))
-
 ggplot(data = income.child.byyr, mapping = aes(x = time, y = boost_amount)) +
@@
 ```
-
-```{r}
-
-```

### 2023-06-15 minos/validation/handovers.Rmd
adding nth order data to gee yj modules. tweaks to makefiles and notebooks so they run off relative paths.

--- 2023-06-09 minos/validation/handovers.Rmd
@@
 title: "MINOS Handover Plots"
-output:
-  html_document:
-    df_print: paged
+output: html_notebook
 ---
@@
 require(ggplot2)
-require(knitr)
-require(here)
 
 #workingDir <- "/home/luke/Documents/WORK/MINOS/"
-workingDir <- normalizePath('../')
+workingDir <- "/Users/robertclay/"
 knitr::opts_knit$set(root.dir = workingDir)
@@
 ```{r}
-source(here::here('minos', 'utils_datain.R'))
-source(here::here('minos', 'utils_validation_vis.R'))
+source('/Users/robertclay/minos/minos/utils_datain.R')
+source('/Users/robertclay/minos/minos/utils_validation_vis.R')
 ```
@@
 # Read raw datafiles in
-raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files('/Users/robertclay/minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
 
-out.path <- here::here('output', 'default_config/')
+out.path <- '/Users/robertclay/minos/output/default_config/'
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
@@
 start.year <- 2020
-save.path <- here::here("plots", "handovers")
-#create.if.not.exists(save.path)
+
+save.path <- '/Users/robertclay/minos/plots/andovers/'
 ```
@@
 rm(raw.sf12, base.sf12, sf12.spag)
-```
-
-## Financial Situation
-
-## Housing Quality
-
-```{r}
-raw.financial_situation <- raw.dat %>% 
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.financial_situation <- base.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-financial_situation <- rbind(raw.financial_situation, base.financial_situation)
-financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
-
-# Now plot
-ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-financial_situation.norm <- financial_situation %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial situation') +
-  xlab('Year') +
-  ylab('Proportion')
-
-ggsave(filename = 'financial_situation.png',
-       plot = last_plot(),
-       path = save.path)
-
-rm(raw.housing, base.housing, housing, housing.norm)
 ```

### 2023-06-15 minos/validation/interventions.Rmd
adding nth order data to gee yj modules. tweaks to makefiles and notebooks so they run off relative paths.

@@
 ```
-
 ## SF_12
-
 ```{r}
@@
 ```
-
 ## Who Boosted?
@@
 ```
-
 ## Who Boosted?
-
 ```{r}

### 2023-06-15 minos/outcomes/make_lineplots_all.Rmd
fixing lineplots notebook with relative imports and removing scrap ideas.

--- 2023-05-24 minos/outcomes/lineplot_notebook.Rmd
@@
 ---
-title: "R MINOS Lineplot notebooks noice"
+title: "R MINOS Lineplot Notebooks"
 output: html_document
@@
 ```{r setup, include=FALSE}
-library(reticulate)
+library(reticulate) # for python in Rmd. 
 library(knitr)
+require(here)
 
 knitr::opts_chunk$set(echo = TRUE)
-knitr::opts_knit$set(root.dir = '../..')
+knitr::opts_knit$set(root.dir = here::here())
 knitr::knit_engines$set(python = reticulate::eng_python)
+reticulate::use_condaenv("minos_conda", required = TRUE)
 ```
@@
 ```{r }
-knitr::include_graphics("../../plots/baseline_all_child_uplift_SF_12_aggs_by_year.png", error=FALSE)
+knitr::include_graphics(here::here("plots", "baseline_all_child_uplift_SF_12_aggs_by_year.png"), error=FALSE)
 ```
@@
 ```{r }
-knitr::include_graphics("../../plots/baseline_poverty_child_uplift_SF_12_aggs_by_year.png", error=FALSE)
+knitr::include_graphics(here::here("plots", "baseline_poverty_child_uplift_SF_12_aggs_by_year.png"), error=FALSE)
 ```
@@
 ```{r }
-knitr::include_graphics("../../plots/baseline_living_wage_SF_12_aggs_by_year.png", error=FALSE)
+knitr::include_graphics(here::here("plots", "baseline_living_wage_SF_12_aggs_by_year.png"), error=FALSE)
 ```
@@
 ```{r }
-knitr::include_graphics("../../plots/baseline_energy_downlift_SF_12_aggs_by_year.png", error=FALSE)
+knitr::include_graphics(here::here("plots", "baseline_energy_downlift_SF_12_aggs_by_year.png"), error=FALSE)
 ```
@@
 ```{r }
-knitr::include_graphics("../../plots/all_five_combined_SF_12_aggs_by_year.png", error=FALSE)
+knitr::include_graphics(here::here("plots", "all_five_combined_SF_12_aggs_by_year.png"), error=FALSE)
 ```

### 2023-06-15 minos/outcomes/make_lineplots_all.Rmd
fix child uplift directories

@@
 IN TOOLS>GLOBAL_OPTIIONS>PYTHON>CONDA_INTERPRETERS. 
+NOT SURE THIS IS NEEDED ANYMORE GIVEN WE'RE SETTING THE CONDA ENV MANUALLY.
 
@@
 ```{r setup, include=FALSE}
-library(reticulate) # for python in Rmd. 
-library(knitr)
+require(reticulate) # for python in Rmd. 
+require(knitr)
 require(here)
@@
 knitr::knit_engines$set(python = reticulate::eng_python)
-reticulate::use_condaenv("minos_conda", required = TRUE)
+reticulate::use_condaenv("minos_conda", required = FALSE)
 ```
@@
 # define test parameters and run.
-directories = "baseline,hhIncomeIntervention"
+directories = "baseline,hhIncomeChildUplift"
 tags = "Baseline,All Child Uplift"
@@
 # define test parameters and run.
-directories = "baseline,hhIncomeIntervention,hhIncomePovertyLineChildUplift,livingWageIntervention,energyDownlift"
+directories = "baseline,hhIncomeChildUplift,hhIncomePovertyLineChildUplift,livingWageIntervention,energyDownlift"
 tags = "Baseline,All Child Uplift,Poverty Line Child Uplift,Living Wage Intervention,Energy Downlift"

### 2023-06-15 minos/testing/education_transitions.Rmd
Added some more plots for testing what age people achieve different education levels, as well as a plot showing mean age when level achieved

@@
 
+ggplot(data = filter(raw, education_state == 0), aes(x = age)) +
+  geom_histogram() +
+  labs(title = 'Education State == 0')
+
+ggplot(data = filter(raw, education_state == 1), aes(x = age)) +
+  geom_histogram() +
+  labs(title = 'Education State == 1')
+
 ggplot(data = filter(raw, education_state == 2), aes(x = age)) +
@@
   labs(title = 'Education state')
+
+```
+
+Mean ages.
+
+```{r}
+
+raw.meanAge <- raw %>%
+  group_by(education_state) %>%
+  summarise(age = mean(age))
+
+ggplot(data = raw.meanAge, aes(x = education_state, y = age)) +
+  geom_col()
 

### 2023-06-16 minos/validation/handovers.Rmd
adding ridge plots into handovers notebook and tweaking arc4 script for all interventions

@@
 require(ggplot2)
+require(ggridges)
 
@@
 
-save.path <- '/Users/robertclay/minos/plots/andovers/'
+save.path <- '/Users/robertclay/minos/plots/handovers/'
 ```
@@
                save.path = save.path)
+density_ridges(income.spag, 'hh_income',
+               save=TRUE, 
+               save.path=save.path)
 
@@
 
+density_ridges(sf12.spag, "SF_12", 
+               save = T, 
+               save.path = save.path)
+
 rm(raw.sf12, base.sf12, sf12.spag)
@@
 
-## Housing Quality
+<!-- ## Housing Quality -->
 
-```{r}
-raw.housing <- raw.dat %>% 
-  dplyr::select(pidp, time, housing_quality) %>%
-  group_by(time, housing_quality) %>%
-  count() %>%
-  mutate(source = 'final_US')
+<!-- ```{r} -->
+<!-- raw.housing <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, housing_quality) %>% -->
+<!--   group_by(time, housing_quality) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'final_US') -->
 
-base.housing <- base.dat %>%
-  dplyr::select(pidp, time, housing_quality) %>%
-  group_by(time, housing_quality) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
+<!-- base.housing <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, housing_quality) %>% -->
+<!--   group_by(time, housing_quality) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'baseline_output') -->
 
-# merge before plot
-housing <- rbind(raw.housing, base.housing)
-housing$housing_quality <- as.factor(housing$housing_quality)
+<!-- # merge before plot -->
+<!-- housing <- rbind(raw.housing, base.housing) -->
+<!-- housing$housing_quality <- as.factor(housing$housing_quality) -->
 
-# Now plot
-ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Quality', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
+<!-- # Now plot -->
+<!-- ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Housing Quality', subtitle = 'Counts by Level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
 
-housing.norm <- housing %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
+<!-- housing.norm <- housing %>% -->
+<!--   group_by(time) %>% -->
+<!--   mutate(total = sum(n)) %>% -->
+<!--   mutate(prct = (n / total)) -->
 
-ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Quality') +
-  xlab('Year') +
-  ylab('Proportion')
+<!-- ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Housing Quality') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
 
-ggsave(filename = 'housing_quality.png',
-       plot = last_plot(),
-       path = save.path)
+<!-- ggsave(filename = 'housing_quality.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
 
-rm(raw.housing, base.housing, housing, housing.norm)
-```
+<!-- rm(raw.housing, base.housing, housing, housing.norm) -->
+<!-- ``` -->
 
-## Neighbourhood Safety
+<!-- ## Neighbourhood Safety -->
 
-```{r}
-raw.neighbour <- raw.dat %>% 
-  dplyr::select(pidp, time, neighbourhood_safety) %>%
-  group_by(time, neighbourhood_safety) %>%
-  count() %>%
-  mutate(source = 'final_US')
+<!-- ```{r} -->
+<!-- raw.neighbour <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, neighbourhood_safety) %>% -->
+<!--   group_by(time, neighbourhood_safety) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'final_US') -->
 
-base.neighbour <- base.dat %>%
-  dplyr::select(pidp, time, neighbourhood_safety) %>%
-  group_by(time, neighbourhood_safety) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
+<!-- base.neighbour <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, neighbourhood_safety) %>% -->
+<!--   group_by(time, neighbourhood_safety) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'baseline_output') -->
 
-# merge before plot
-neighbour <- rbind(raw.neighbour, base.neighbour)
-neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety)
+<!-- # merge before plot -->
+<!-- neighbour <- rbind(raw.neighbour, base.neighbour) -->
+<!-- neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety) -->
 
-# Now plot
-ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') +
-  xlab('Year') +
-  ylab('Count')
+<!-- # Now plot -->
+<!-- ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
 
-neighbour.norm <- neighbour %>%
-  group_by(time) %>%
-  filter(neighbourhood_safety != -9) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
+<!-- neighbour.norm <- neighbour %>% -->
+<!--   group_by(time) %>% -->
+<!--   filter(neighbourhood_safety != -9) %>% -->
+<!--   mutate(total = sum(n)) %>% -->
+<!--   mutate(prct = (n / total)) -->
 
-ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Neighbourhood Safety') +
-  xlab('Year') +
-  ylab('Proportion')
+<!-- ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Neighbourhood Safety') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
 
-ggsave(filename = 'neighbourhood_safety.png',
-       plot = last_plot(),
-       path = save.path)
+<!-- ggsave(filename = 'neighbourhood_safety.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
 
-#rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm)
-```
+<!-- #rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm) -->
+<!-- ``` -->
 
-## Loneliness
+<!-- ## Loneliness -->
 
-```{r}
-raw.loneliness <- raw.dat %>% 
-  dplyr::select(pidp, time, loneliness) %>%
-  group_by(time, loneliness) %>%
-  count() %>%
-  mutate(source = 'final_US')
+<!-- ```{r} -->
+<!-- raw.loneliness <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, loneliness) %>% -->
+<!--   group_by(time, loneliness) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'final_US') -->
 
-base.loneliness <- base.dat %>%
-  dplyr::select(pidp, time, loneliness) %>%
-  group_by(time, loneliness) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
+<!-- base.loneliness <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, loneliness) %>% -->
+<!--   group_by(time, loneliness) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'baseline_output') -->
 
-# merge before plot
-loneliness <- rbind(raw.loneliness, base.loneliness)
-loneliness$loneliness <- as.factor(loneliness$loneliness)
+<!-- # merge before plot -->
+<!-- loneliness <- rbind(raw.loneliness, base.loneliness) -->
+<!-- loneliness$loneliness <- as.factor(loneliness$loneliness) -->
 
-# Now plot
-ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Loneliness', subtitle = 'Counts by level') +
-  xlab('Year') +
-  ylab('Count')
+<!-- # Now plot -->
+<!-- ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Loneliness', subtitle = 'Counts by level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
 
-loneliness.norm <- loneliness %>%
-  group_by(time) %>%
-  filter(loneliness != -9) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
+<!-- loneliness.norm <- loneliness %>% -->
+<!--   group_by(time) %>% -->
+<!--   filter(loneliness != -9) %>% -->
+<!--   mutate(total = sum(n)) %>% -->
+<!--   mutate(prct = (n / total)) -->
 
-ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Loneliness') +
-  xlab('Year') +
-  ylab('Proportion')
+<!-- ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Loneliness') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
 
-ggsave(filename = 'loneliness.png',
-       plot = last_plot(),
-       path = save.path)
+<!-- ggsave(filename = 'loneliness.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
 
-rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
-```
+<!-- rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm) -->
+<!-- ``` -->
 
-## Nutrition Quality
+<!-- ## Nutrition Quality -->
 
-TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11
+<!-- TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11 -->
 
-```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.nut <- raw.dat %>% 
-  dplyr::select(pidp, time, nutrition_quality) %>%
-  group_by(time) %>%
-  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
+<!-- ```{r} -->
+<!-- # first figure out how to plot final_US -->
+<!-- # start with hh_income -->
+<!-- raw.nut <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, nutrition_quality) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'final_US') -->
 
-base.nut <- base.dat %>%
-  dplyr::select(pidp, time, nutrition_quality) %>%
-  group_by(time) %>%
-  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
+<!-- base.nut <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, nutrition_quality) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'baseline_output') -->
 
-# merge before plot
-nutrition_quality <- rbind(raw.nut, base.nut)
+<!-- # merge before plot -->
+<!-- nutrition_quality <- rbind(raw.nut, base.nut) -->
 
-# Now plot
-ggplot(data = nutrition_quality, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Nutrition Quality', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Nutrition Quality')
+<!-- # Now plot -->
+<!-- ggplot(data = nutrition_quality, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Nutrition Quality', subtitle = 'Full Sample') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Nutrition Quality') -->
 
-## Try a version where final_US is limited to only those present from wave 1 
-# onwards because the sample refreshments are messing with the plot
-raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+<!-- ## Try a version where final_US is limited to only those present from wave 1 -->
+<!-- # onwards because the sample refreshments are messing with the plot -->
+<!-- raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009] -->
 
-raw.nut2 <- raw.dat %>% 
-  dplyr::select(pidp, time, nutrition_quality) %>%
-  filter(pidp %in% raw.wave1) %>%
-  filter(nutrition_quality >= 0) %>%
-  group_by(time) %>%
-  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
+<!-- raw.nut2 <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, nutrition_quality) %>% -->
+<!--   filter(pidp %in% raw.wave1) %>% -->
+<!--   filter(nutrition_quality >= 0) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'final_US') -->
 
-base.nut2 <- base.dat %>%
-  dplyr::select(pidp, time, nutrition_quality) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
+<!-- base.nut2 <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, nutrition_quality) %>% -->
+<!--   filter(pidp %in% raw.wave1) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'baseline_output') -->
 
-nutrition_quality2 <- rbind(raw.nut2, base.nut2)
+<!-- nutrition_quality2 <- rbind(raw.nut2, base.nut2) -->
 
-# Now plot
-ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Nutrition Quality') +
-  xlab('Year') +
-  ylab('Nutrition Quality')
+<!-- # Now plot -->
+<!-- ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Nutrition Quality') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Nutrition Quality') -->
 
-ggsave(filename = 'nutrition_quality_wav1.png',
-       plot = last_plot(),
-       path = save.path)
+<!-- ggsave(filename = 'nutrition_quality_wav1.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
 
-rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2, 
-    nutrition_quality2)
-```
+<!-- rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2, -->
+<!--     nutrition_quality2) -->
+<!-- ``` -->
 
-## Physical Health
+<!-- ## Physical Health -->
 
-NOTE: At present, physical health is not predicted or transitioned.
+<!-- NOTE: At present, physical health is not predicted or transitioned. -->
 
-```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.phealth <- raw.dat %>% 
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
+<!-- ```{r} -->
+<!-- # first figure out how to plot final_US -->
+<!-- # start with hh_income -->
+<!-- raw.phealth <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'final_US') -->
 
-base.phealth <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
+<!-- base.phealth <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'baseline_output') -->
 
-# merge before plot
-phealth <- rbind(raw.phealth, base.phealth)
+<!-- # merge before plot -->
+<!-- phealth <- rbind(raw.phealth, base.phealth) -->
 
-# Now plot
-ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Average')
+<!-- # Now plot -->
+<!-- ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Physical Health', subtitle = 'Full Sample') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Average') -->
 
-## Try a version where final_US is limited to only those present from wave 1 
-# onwards because the sample refreshments are messing with the plot
-raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+<!-- ## Try a version where final_US is limited to only those present from wave 1 -->
+<!-- # onwards because the sample refreshments are messing with the plot -->
+<!-- raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009] -->
 
-raw.phealth2 <- raw.dat %>% 
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
+<!-- raw.phealth2 <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   filter(pidp %in% raw.wave1) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'final_US') -->
 
-base.phealth2 <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
+<!-- base.phealth2 <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   filter(pidp %in% raw.wave1) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'baseline_output') -->
 
-phealth2 <- rbind(raw.phealth2, base.phealth2)
+<!-- phealth2 <- rbind(raw.phealth2, base.phealth2) -->
 
-# Now plot
-ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health') +
-  xlab('Year') +
-  ylab('Average')
+<!-- # Now plot -->
+<!-- ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Physical Health') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Average') -->
 
-ggsave(filename = 'physical_health_wav1.png',
-       plot = last_plot(),
-       path = save.path)
+<!-- ggsave(filename = 'physical_health_wav1.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
 
-#raw.phealth.check <- raw.dat %>% 
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
+<!-- #raw.phealth.check <- raw.dat %>% -->
+<!-- #  select(pidp, time, phealth) %>% -->
+<!-- #  filter(time > 2009) %>% -->
+<!-- #  filter(pidp %in% raw.wave1) -->
 
-#base.phealth.check <- base.dat %>%
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
+<!-- #base.phealth.check <- base.dat %>% -->
+<!-- #  select(pidp, time, phealth) %>% -->
+<!-- #  filter(time > 2009) %>% -->
+<!-- #  filter(pidp %in% raw.wave1) -->
 
-rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2)
-#rm(raw.phealth.check, base.phealth.check)
-```
+<!-- rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2) -->
+<!-- #rm(raw.phealth.check, base.phealth.check) -->
+<!-- ``` -->
 
-```{r}
+<!-- ```{r} -->
 
-```
+<!-- ``` -->

### 2023-06-16 minos/testing/education_transitions.Rmd
Added some code to save plots in the education_transitions.Rmd testing notebook

@@
 start.year <- 2020
-save.path <- here::here("plots", "handovers", 'SIPHER7')
+save.path <- here::here("plots", "education")
 create.if.not.exists(save.path)
-
-shall.we.save <- TRUE
 ```
@@
 
+ggsave(filename = 'education_state_0.png',
+       path = save.path)
+
 ggplot(data = filter(raw, education_state == 1), aes(x = age)) +
@@
   labs(title = 'Education State == 1')
+
+ggsave(filename = 'education_state_1.png',
+       path = save.path)
 
@@
 
+ggsave(filename = 'education_state_2.png',
+       path = save.path)
+
 ggplot(data = filter(raw, education_state == 3), aes(x = age)) +
@@
   labs(title = 'Education State == 3')
+
+ggsave(filename = 'education_state_3.png',
+       path = save.path)
 
@@
 
+ggsave(filename = 'education_state_5.png',
+       path = save.path)
+
 ggplot(data = filter(raw, education_state == 6), aes(x = age)) +
@@
 
+ggsave(filename = 'education_state_6.png',
+       path = save.path)
+
 ggplot(data = filter(raw, education_state == 7), aes(x = age)) +
@@
   labs(title = 'Education State == 7')
+
+ggsave(filename = 'education_state_7.png',
+       path = save.path)
 
@@
   labs(title = 'Education state')
+
+ggsave(filename = 'education_state_overlaid.png',
+       path = save.path)
 
@@
   geom_col()
+
+ggsave(filename = 'mean_age_achieved_educ.png',
+       path = save.path)
 

### 2023-06-19 minos/testing/education_transitions.Rmd
Changed ages that people achieve certain education levels, and allowed transition into education_state==1 for people who achieve lower grades in GCSEs (or equivalent quals)

@@
 
-if (shall.we.save) {
 ggsave(filename = 'S7_labour_state.png',
@@
        path = save.path)
-}
 
@@
                  var = 'S7_labour_state',
-                 save = shall.we.save,
+                 save = TRUE,
                  save.path = save.path)
@@
 spaghetti_plot(spag, 'S7_labour_state',
-               save = shall.we.save,
+               save = TRUE,
                save.path = save.path)
@@
 
-if (shall.we.save) {
 ggsave(filename = 'education_state.png',
@@
                  var = 'education_state',
-                 save = shall.we.save,
+                 save = TRUE,
                  save.path = save.path)
@@
 spaghetti_plot(spag, 'education_state',
-               save = shall.we.save,
+               save = TRUE,
                save.path = save.path)

### 2023-06-19 minos/validation/handovers.Rmd
bug fixining income and mwb modules. adding to debug notebooks

--- 2023-06-15 minos/validation/handovers.Rmd
@@
                save = TRUE,
+               save.path = save.path)
+
+density_ridges(sf12.spag, "SF_12", 
+               save = T, 
                save.path = save.path)

### 2023-06-19 minos/modules/income.py

@@ -459,6 +459,7 @@ class geeYJIncome(Base):
         """
         # Get living people to update their income
         pop = self.population_view.get(event.index, query="alive =='alive'")
+        pop = pop.sort_values('pidp')
         self.year = event.time.year
 
         ## Predict next income value
@@ -494,7 +495,7 @@ class geeYJIncome(Base):
                                                            self.rpy2Modules,
                                                            self.history_data,
                                                            dependent='hh_income',
-                                                           noise_std=0.4)#2
+                                                           noise_std=0.5)#2
 
         return nextWaveIncome.iloc[self.history_data.loc[self.history_data['time']==self.year].index]
 

### 2023-06-19 minos/modules/mental_wellbeing.py

@@ -375,11 +375,9 @@ class geeYJMWB(Base):
         # individual graduate in an education module.
         builder.event.register_listener("time_step", self.on_time_step, priority=9)
 
-        self.max_sf12 = None
         #only need to load this once for now.
         self.gee_transition_model = r_utils.load_transitions(f"SF_12/gee_yj/SF_12_GEE_YJ", self.rpy2_modules)
-
-        self.history_data = self.generate_history_dataframe("final_US", [2014, 2017, 2020], view_columns)
+        self.history_data = self.generate_history_dataframe("final_US", [2017, 2020], view_columns)
 
     def update_prediction_population(self, current_pop):
         """ Update longitudinal data frame of past observations with current information.
@@ -406,20 +404,17 @@ class geeYJMWB(Base):
 
         # Get living people to update their income
         pop = self.population_view.get(event.index, query="alive =='alive'")
-        if self.max_sf12 == None:
-            self.max_sf12 = np.max(pop["SF_12"])
+        pop = pop.sort_values('pidp') #sorting aligns index to make sure individual gets their correct prediction.
 
         ## Predict next income value
-        # reflect SF_12 so right skewed and yj transform works.
         newWaveMWB = self.calculate_mwb(pop)
         newWaveMWB = pd.DataFrame(newWaveMWB, columns=["SF_12"])
+        newWaveMWB.index = pop.index # aligning index to vivarium builder dataframe. ensures assignment of new values to correct individuals.
+        newWaveMWB["SF_12"] = -newWaveMWB["SF_12"] # make sure to reflect SF_12 back to being positive.
         newWaveMWB["SF_12"] = np.clip(newWaveMWB["SF_12"], 0, 100)
-        # Set index type to int (instead of object as previous)
-        newWaveMWB.index = pop.index
-
-
+        #newWaveMWB.sort_index(inplace=True)
         #print(np.mean(newWaveMWB["SF_12"]))
-        # Draw individuals next states randomly from this distribution.
+
         # Update population with new income
         self.population_view.update(newWaveMWB['SF_12'])
 
@@ -433,9 +428,8 @@ class geeYJMWB(Base):
         Returns
         -------
         """
-        if self.year != 2020:
-            self.update_history_dataframe(pop, self.year)
-        self.history_data["SF_12"] = self.max_sf12 - self.history_data["SF_12"]
[…]

### 2023-06-20 minos/testing/education_transitions.Rmd
Added plots for hh_income and SF12 by education level

@@
 # Read raw datafiles in
-raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'stock_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 ggplot(data = raw.meanAge, aes(x = education_state, y = age)) +
-  geom_col()
+  geom_col() +
+  geom_text(aes(label = format(round(age, 2), nsmall = 2)), vjust = -0.5)
 
@@
 
+```
+
+## Summary stats by educ_state
+
+```{r}
+raw.by.educ <- raw.dat %>%
+  group_by(education_state) %>%
+  summarise(hh_income = mean(hh_income, na.rm = TRUE),
+            SF12 = mean(SF_12, na.rm = TRUE))
+
+raw.by.educ$education_state <- as.factor(raw.by.educ$education_state)
+
+ggplot(raw.by.educ, aes(x = education_state, y = hh_income)) +
+  geom_col()
+
+ggplot(raw.by.educ, aes(x = education_state, y = SF12)) +
+  geom_col()
+```
+
+## Max Education Predictions
+
+```{r}
+raw.maxEduc <- raw.dat %>%
+  dplyr::filter(age < 31) %>%
+  dplyr::select(pidp, time, age, education_state, max_educ, S7_labour_state)
+
+raw.maxEducDiff <- raw.maxEduc %>%
+  dplyr::filter(max_educ != education_state)
 ```
@@
 
+spaghetti_plot(raw.s, 'education_state',
+               save = FALSE)
+
 spaghetti_plot(spag, 'education_state',

### 2023-06-21 minos/testing/education_transitions.Rmd
Various tweaks to the labour and education modules, and additional plots for education_transitions.Rmd and handovers_S7.Rmd

@@
 
-- [ ] Check what age people achieve each level of education
-- [ ] Average age plot (see if change over time in raw)
-  - [ ] Histograms
+- [x] Check what age people achieve each level of education
+  - [x] Average age plot (see if change over time in raw)
+  - [x] Histograms
   - [ ] Animated histograms?
@@
 - [ ] Check how many people move into FT education after age of 30
-- [ ] Make sure stock population is doing max_educ prediction
+- [x] Make sure stock population is doing max_educ prediction
 
@@
 
-Mean ages.
+## Mean ages
 
@@
   geom_col()
+```
+
+## Transition into FT Education
+
+How many people transition into full time education? How many do this after the age of 30?
+
+```{r}
+raw.eductrans <- raw.dat %>%
+  select(pidp, time, age, education_state, max_educ, S7_labour_state) %>%
+  mutate(backInEduc = (S7_labour_state == 'FT Education') & (lag(S7_labour_state, order_by = time) != 'FT Education')) %>%
+  filter(backInEduc == TRUE)
+
+ggplot(raw.eductrans, aes(x = age)) +
+  geom_histogram() +
+  labs(title = 'Age came back to FT Education')
 ```
@@
 
+## Retirement
+
+Test that retirement is working as planned. Make sure that all 65+ are in the not working category in outputs.
+
+```{r}
+retired <- base.dat %>%
+  select(pidp, time, age, S7_labour_state) %>%
+  filter(age >= 65) %>%
+  group_by(S7_labour_state) %>%
+  count()
+
+ggplot(retired, aes(x = S7_labour_state, y = n)) +
+  geom_col()
+
+retired.by.ageGroup <- base.dat %>%
+  select(pidp, time, age, S7_labour_state) %>%
+  filter(age >= 65) %>%
+  mutate(age.group = cut(age, breaks = 0,65,70,75,80,85,90,120)) %>%
+  group_by(age.group, S7_labour_state) %>%
+  count()
+
+#ggplot(retired, aes(x = S7_labour_state, y = n)) +
+#  geom_col()
+
+```
+
 # Education

### 2023-06-21 minos/validation/handovers_S7.Rmd
Various tweaks to the labour and education modules, and additional plots for education_transitions.Rmd and handovers_S7.Rmd

@@
 
-spaghetti_plot(income.spag, 'hh_income',
-               save = shall.we.save,
-               save.path = save.path)
+#spaghetti_plot(income.spag, 'hh_income',
+#               save = shall.we.save,
+#               save.path = save.path)
 
@@
 
-spaghetti_plot(base.ei, 'equivalent_income')
+#spaghetti_plot(base.ei, 'equivalent_income')
 
-spaghetti_plot(ei.spag, 'equivalent_income',
-               save = shall.we.save,
-               save.path = save.path)
+#spaghetti_plot(ei.spag, 'equivalent_income',
+#               save = shall.we.save,
+#               save.path = save.path)
 
@@
 
-spaghetti_plot(spag, 'S7_housing_quality',
-               save = shall.we.save,
-               save.path = save.path)
+#spaghetti_plot(spag, 'S7_housing_quality',
+#               save = shall.we.save,
+#               save.path = save.path)
 
@@
 
-spaghetti_plot(spag, 'S7_neighbourhood_safety',
-               save = shall.we.save,
-               save.path = save.path)
+#spaghetti_plot(spag, 'S7_neighbourhood_safety',
+#               save = shall.we.save,
+#               save.path = save.path)
 
@@
 
-spaghetti_plot(spag, 'S7_physical_health',
-               save = shall.we.save,
-               save.path = save.path)
+#spaghetti_plot(spag, 'S7_physical_health',
+#               save = shall.we.save,
+#               save.path = save.path)
 
@@
 
-spaghetti_plot(spag, 'S7_mental_health',
-               save = shall.we.save,
-               save.path = save.path)
+#spaghetti_plot(spag, 'S7_mental_health',
+#               save = shall.we.save,
+#               save.path = save.path)
 
@@
 
-spaghetti_plot(spag, 'loneliness',
-               save = shall.we.save,
-               save.path = save.path)
+#spaghetti_plot(spag, 'loneliness',
+#               save = shall.we.save,
+#               save.path = save.path)
 

### 2023-06-22 minos/validation/cross_validation.Rmd
Reset config for cv back to 2014-2020 (previously tried to do cross-validation and handovers on the same plots), and updated the cross_validation.Rmd script with the here() package paths

@@
 require(ggplot2)
+require(here)
 
-workingDir <- "/home/luke/Documents/MINOS/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/"
+workingDir <- normalizePath('../')
 knitr::opts_knit$set(root.dir = workingDir)
@@
 ```{r, include=FALSE}
-source('Minos/minos/utils_datain.R')
-source('Minos/minos/validation/utils.r')
+source(here::here('minos', 'utils_datain.R'))
+source(here::here('minos', 'utils_validation_vis.R'))
+source(here::here('minos', 'validation', 'utils.r'))
 ```
@@
 # cross validation simulation output
-out.path <- 'Minos/output/cross_validation/'
+#out.path <- 'Minos/output/cross_validation/'
+out.path <- here::here('output', 'cross_validation_default/')
 cv <- read_singular_local_out(out.path, 'baseline')
@@
 # cv simulation pop (not used for transitions)
-cv.simul.files <- list.files('Minos/data/final_US/cross_validation/simulation/',
+cv.simul.files <- list.files(here::here('data', 'final_US', 'cross_validation', 'simulation'),
                              pattern = '[0-9]{4}_US_cohort.csv',

### 2023-06-26 minos/validation/cross_validation.Rmd
Adapted and improved the densigram plots for cross-validation. Also added lots of observed vs predicted plots to the cross_validation notebook

@@
 source(here::here('minos', 'validation', 'utils.r'))
+#source(here::here('minos', 'utils_outcome_vis.R'))
 ```
@@
 out.path <- here::here('output', 'cross_validation_default/')
-cv <- read_singular_local_out(out.path, 'baseline')
+cv.dat <- read_singular_local_out(out.path, 'baseline')
 
@@
                              full.names = TRUE)
-raw <- do.call(rbind, lapply(cv.simul.files, read.csv))
+raw.dat <- do.call(rbind, lapply(cv.simul.files, read.csv))
 ```
@@
 Therefore, we need a step here to check the pidps from both, and remove anybody not in both datasets.
+We can also filter the years out of the raw data here, as we only care about years that have been simulated for comparison.
 
 ```{r}
-cv.pidps <- cv %>% select(pidp) %>% unique()
-raw.pidps <- raw %>% select(pidp) %>% unique()
-
+# pidp filter
+cv.pidps <- cv.dat %>% select(pidp) %>% unique()
+raw.pidps <- raw.dat %>% select(pidp) %>% unique()
 both.pidps <- intersect(cv.pidps, raw.pidps)
 
-cv <- cv %>% filter(pidp %in% both.pidps$pidp)
-raw <- raw %>% filter(pidp %in% both.pidps$pidp)
+# year filter
+cv.years <- cv.dat %>% select(time) %>% unique()
+cv.years <- cv.years[['time']]
+
+cv <- cv.dat %>% filter(pidp %in% both.pidps$pidp)
+raw <- raw.dat %>% filter(pidp %in% both.pidps$pidp, 
+                      time %in% cv.years)
+
+rm(cv.pidps, raw.pidps, both.pidps, cv.years)
 ```
@@
                      subset.min = -5000)
+```
+
+### Snapshots
+
+Going to produce some comparison plots for snapshots throughout the simulation.
+
+NOTE: LOG SCALE!
+
+```{r}
+snap.timelist <- c(2014, 2016, 2018, 2020)
+
+cv.snap <- cv %>%
+  select(pidp, time, hh_income) %>%
+  filter(time %in% snap.timelist) %>%
+  rename(predicted = hh_income)
+
+raw.snap <- raw %>%
+  select(pidp, time, hh_income) %>%
+  filter(time %in% snap.timelist) %>%
+  rename(observed = hh_income)
+
+snap <- merge(cv.snap, raw.snap,
+                   by = c('pidp', 'time'))
+
+ggplot(snap, aes(x = observed, y = predicted)) +
+  geom_point() +
+  geom_abline(slope=1, intercept=0) +
+  facet_wrap(~time) +
+  labs(title = 'hh_income observed vs predicted')
+
+rm(snap.timelist, cv.snap, raw.snap, snap)
+```
+
+```{r}
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'hh_income', 
+                                 target.year = 2014)
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'hh_income', 
+                                 target.year = 2016)
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'hh_income', 
+                                 target.year = 2018)
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'hh_income', 
+                                 target.year = 2020)
 ```
@@
                      scen2 = 'simulation')
+```
+
+### Snapshots
+
+```{r}
+observed <- raw
+predicted <- cv
+var <- 'SF_12'
+target.year <- 2020
+
+# get just one year
+o.end <- observed %>% filter(time == target.year, .data[[var]] != -8.0)
+p.end <- predicted %>% filter(time == target.year, .data[[var]] != -8.0)
+# get just the SF12 columns and rename for later
+o.end <- o.end %>% select(pidp, .data[[var]]) %>% rename(observed = var)
+p.end <- p.end %>% select(pidp, .data[[var]]) %>% rename(predicted = var)
+
+# combine before we plot
+combined <- merge(o.end, p.end, by = 'pidp')
+
+p <- ggplot(data = combined, aes(x = observed, y = predicted)) +
+  geom_point(alpha = 0.6, size=0.1) +
+  geom_smooth() +
+  geom_abline(intercept = 0, scale=1) +
+  theme(legend.position = c(0.15, 0.9)) +
+  labs(title = paste0(var, ' - ', target.year))
+p
+
+p1 <- ggMarginal(p, type='densigram', xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
+p1
+```
+
+```{r}
+snap.timelist <- c(2014, 2016, 2018, 2020)
+
+cv.snap <- cv %>%
+  select(pidp, time, SF_12) %>%
+  filter(time %in% snap.timelist) %>%
+  rename(predicted = SF_12)
+
+raw.snap <- raw %>%
+  select(pidp, time, SF_12) %>%
+  filter(time %in% snap.timelist) %>%
+  rename(observed = SF_12)
+
+snap <- merge(cv.snap, raw.snap,
+                   by = c('pidp', 'time'))
+snap$time <- as.factor(snap$time)
+
+ggplot(filter(snap, time == 2014), aes(x = observed, y = predicted)) +
+  geom_point() +
+  geom_abline(slope=1, intercept=0) +
+  stat_ellipse(color='green') +
+  labs(title = 'SF_12 : 2014')
+
+ggplot(filter(snap, time == 2016), aes(x = observed, y = predicted)) +
+  geom_point() +
+  geom_abline(slope=1, intercept=0) +
+  stat_ellipse(color='green') +
+  labs(title = 'SF_12 : 2016')
+
+ggplot(filter(snap, time == 2018), aes(x = observed, y = predicted)) +
+  geom_point() +
+  geom_abline(slope=1, intercept=0) +
+  labs(title = 'SF_12 : 2018')
+
+ggplot(filter(snap, time == 2020), aes(x = observed, y = predicted)) +
+  geom_point() +
+  geom_abline(slope=1, intercept=0) +
+  labs(title = 'SF_12 : 2020')
+
+ggplot(snap, aes(x = observed, y = predicted, group = time, color = time, shape = time)) +
+  geom_point(size = 1) +
+  geom_abline(slope=1, intercept=0) +
+  labs(title = 'SF_12')
+
+rm(snap.timelist, cv.snap, raw.snap, snap)
+```
+
+```{r}
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12', 
+                                 target.year = 2014)
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12', 
+                                 target.year = 2016)
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12', 
+                                 target.year = 2018)
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12', 
+                                 target.year = 2020)
 ```

### 2023-06-26 minos/testing/model_of_models_work.Rmd

@@
 # note this is the path to the rate of change models, NOT the regenerative mean effects
-mod.path <- 'Minos/data/transitions/hh_income/ols2/'
+mod.path <- 'Minos/data/transitions/hh_income/ols/'
 m1 <- readRDS(paste0(mod.path, 'hh_income_2009_2010.rds'))
@@
 
+# hh_income
+
+```{r}
+income <- all.years.long %>%
+  filter(grepl("hh_income", Predictor))
+
+ggplot(income, aes(x = year, y = coefficient, group=1)) +
+  geom_line() +
+  labs(title = 'Household Income')
+```
+
 # Gender

### 2023-06-26 minos/validation/cross_validation.Rmd
Transformed hh_income with inverse hyperbolic sine for plotting. Added a package to the environment as part of this

@@
 require(here)
+require(scales)
 
@@
 
-NOTE: LOG SCALE!
-
 ```{r}
@@
 
+asinh_trans <- scales::trans_new(
+  "inverse_hyperbolic_sine",
+  transform = function(x) {asinh(x)},
+  inverse = function(x) {sinh(x)}
+)
+
 ggplot(snap, aes(x = observed, y = predicted)) +
   geom_point() +
+  scale_y_continuous(trans=asinh_trans) +
+  scale_x_continuous(trans=asinh_trans) +
   geom_abline(slope=1, intercept=0) +
+  stat_ellipse(color='red') +
   facet_wrap(~time) +
-  labs(title = 'hh_income observed vs predicted')
+  labs(title = 'hh_income observed vs predicted',
+       subtitle = 'inverse hyperbolic sine transformation')
 
@@
 
-ggplot(filter(snap, time == 2014), aes(x = observed, y = predicted)) +
-  geom_point() +
-  geom_abline(slope=1, intercept=0) +
-  stat_ellipse(color='green') +
-  labs(title = 'SF_12 : 2014')
-
-ggplot(filter(snap, time == 2016), aes(x = observed, y = predicted)) +
-  geom_point() +
-  geom_abline(slope=1, intercept=0) +
-  stat_ellipse(color='green') +
-  labs(title = 'SF_12 : 2016')
-
-ggplot(filter(snap, time == 2018), aes(x = observed, y = predicted)) +
-  geom_point() +
-  geom_abline(slope=1, intercept=0) +
-  labs(title = 'SF_12 : 2018')
-
-ggplot(filter(snap, time == 2020), aes(x = observed, y = predicted)) +
-  geom_point() +
-  geom_abline(slope=1, intercept=0) +
-  labs(title = 'SF_12 : 2020')
-
-ggplot(snap, aes(x = observed, y = predicted, group = time, color = time, shape = time)) +
+ggplot(snap, aes(x = observed, y = predicted, group = time)) +
   geom_point(size = 1) +
   geom_abline(slope=1, intercept=0) +
+  stat_ellipse(color='red') +
+  facet_wrap(~time) +
   labs(title = 'SF_12')

### 2023-06-26 minos/utils_validation_vis.R

@@ -3,6 +3,7 @@
 require(ggplot2)
 require(ggExtra)
 require(here)
+require(scales)
 
 miss.values <- c(-10, -9, -8, -7, -3, -2, -1,
                  -10., -9., -8., -7., -3., -2., -1.)
@@ -127,13 +128,33 @@ marg_dist_densigram_plot_oneyear <- function(observed,
   # combine before we plot
   combined <- merge(o.end, p.end, by = 'pidp')
   
-  p <- ggplot(data = combined, aes(x = observed, y = predicted)) +
-    geom_point(alpha = 0.6, size=0.1) +
-    geom_smooth() +
-    geom_abline(intercept = 0, scale=1) +
-    stat_ellipse(color = 'red') +
-    theme(legend.position = c(0.15, 0.9)) +
-    labs(title = paste0(var, ' - ', target.year))
+  if (var == 'hh_income') {
+    # do inverse hyperbolic sine transformation for hh_income
+    asinh_trans <- scales::trans_new(
+      "inverse_hyperbolic_sine",
+      transform = function(x) {asinh(x)},
+      inverse = function(x) {sinh(x)}
+    )
+    
+    p <- ggplot(data = combined, aes(x = observed, y = predicted)) +
+      geom_point(alpha = 0.6, size=0.1) +
+      geom_smooth() +
+      scale_y_continuous(trans=asinh_trans) +
+      scale_x_continuous(trans=asinh_trans) +
+      geom_abline(intercept = 0, scale=1) +
+      stat_ellipse(color = 'red') +
+      theme(legend.position = c(0.15, 0.9)) +
+      labs(title = paste0(var, ' - ', target.year))
+  } else {
+    # no transformation for other vars
+    p <- ggplot(data = combined, aes(x = observed, y = predicted)) +
+      geom_point(alpha = 0.6, size=0.1) +
+      geom_smooth() +
+      geom_abline(intercept = 0, scale=1) +
+      stat_ellipse(color = 'red') +
+      theme(legend.position = c(0.15, 0.9)) +
+      labs(title = paste0(var, ' - ', target.year))
+  }
   
   p1 <- ggMarginal(p, type='densigram', xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
   

### 2023-06-28 minos/validation/cross_validation_default.Rmd
Added some new functions to the utils_validation_vis.R, and created a cross_validation_default.Rmd to plot results from 5-fold cross-validation

--- 2023-06-22 minos/validation/cross_validation.Rmd
@@
 ---
-title: "Cross Validation Analysis"
+title: "Cross-Validation Default"
 output: html_notebook
 ---
-
-This notebook will compare the results of the cross-validation simulation run with real data from Understanding Society, so that we can evaluate the transition models.
-
-# Method
-
-After generation of the final datasets (final_US), the respondents were separated into 2 roughly equal halves based on their pidp.
-One half was labelled as the transition dataset, and the other for simulation.
-Transition models were then fit using the transition dataset, with the other half then simulated with these models.
-
-The results of the simulation will now be compared to the simulation dataset to see how closely our models mimick reality.
 
@@
 #out.path <- 'Minos/output/cross_validation/'
-out.path <- here::here('output', 'cross_validation_default/')
-cv <- read_singular_local_out(out.path, 'baseline')
+out.path <- here::here('output', 'cv')
+cv1 <- read_singular_local_out(here::here(out.path, 'default1/'), 'baseline')
+cv2 <- read_singular_local_out(here::here(out.path, 'default2/'), 'baseline')
+cv3 <- read_singular_local_out(here::here(out.path, 'default3/'), 'baseline')
+cv4 <- read_singular_local_out(here::here(out.path, 'default4/'), 'baseline')
+cv5 <- read_singular_local_out(here::here(out.path, 'default5/'), 'baseline')
 
-# cv simulation pop (not used for transitions)
-cv.simul.files <- list.files(here::here('data', 'final_US', 'cross_validation', 'simulation'),
+cvlist <- list(cv1, cv2, cv3, cv4, cv5)
+cv <- do.call(rbind, cvlist)
+
+# cv simulation batches
+cv.simul.files1 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch1'),
                              pattern = '[0-9]{4}_US_cohort.csv',
                              full.names = TRUE)
-raw <- do.call(rbind, lapply(cv.simul.files, read.csv))
+raw1 <- do.call(rbind, lapply(cv.simul.files1, read.csv))
+cv.simul.files2 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch2'),
+                             pattern = '[0-9]{4}_US_cohort.csv',
+                             full.names = TRUE)
+raw2 <- do.call(rbind, lapply(cv.simul.files2, read.csv))
+cv.simul.files3 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch3'),
+                             pattern = '[0-9]{4}_US_cohort.csv',
+                             full.names = TRUE)
+raw3 <- do.call(rbind, lapply(cv.simul.files3, read.csv))
+cv.simul.files4 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch4'),
+                             pattern = '[0-9]{4}_US_cohort.csv',
+                             full.names = TRUE)
+raw4 <- do.call(rbind, lapply(cv.simul.files4, read.csv))
+cv.simul.files5 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch5'),
+                             pattern = '[0-9]{4}_US_cohort.csv',
+                             full.names = TRUE)
+raw5 <- do.call(rbind, lapply(cv.simul.files5, read.csv))
+
+rawlist <- list(raw1, raw2, raw3, raw4, raw5)
+raw.dat <- do.call(rbind, rawlist)
 ```
-
-# Analysis
 
@@
 Therefore, we need a step here to check the pidps from both, and remove anybody not in both datasets.
+We can also filter the years out of the raw data here, as we only care about years that have been simulated for comparison.
 
 ```{r}
-cv.pidps <- cv %>% select(pidp) %>% unique()
-raw.pidps <- raw %>% select(pidp) %>% unique()
+# pidp filter
+#cv.pidps <- cv %>% select(pidp) %>% unique()
+#raw.pidps <- raw %>% select(pidp) %>% unique()
+#both.pidps <- intersect(cv.pidps, raw.pidps)
 
-both.pidps <- intersect(cv.pidps, raw.pidps)
+# year filter
+cv.years <- cv %>% select(time) %>% unique()
+cv.years <- cv.years[['time']]
 
-cv <- cv %>% filter(pidp %in% both.pidps$pidp)
-raw <- raw %>% filter(pidp %in% both.pidps$pidp)
+#cv <- cv.dat %>% filter(pidp %in% both.pidps$pidp)
+raw <- raw.dat %>% filter(time %in% cv.years)
+
+#rm(cv.pidps, raw.pidps, both.pidps, cv.years)
+rm(cv.years)
 ```
 
-## hh_income
+For all analyses, results will be calculated on each output separately and pooled.
+For example, the mean hh_income over time will be calculated for each output run seperately, and the mean of these 5 means is what will be plotted.
+This will be plotted against the entire raw sample.
+
+# hh_income
+
+```{r}
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hh_income')
+```
 
@@
                                          var = 'hh_income')
-
-plot_mean_comparison(pivoted.df = income.pivoted, 
-                     var = 'hh_income', 
-                     group.var = 'scenario',
-                     save = TRUE,
-                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
 
@@
 
-### T-tests
-
 ```{r}
-income.t.tests <- two_sample_t_test(cv, 'cv', raw, 'raw', 'hh_income')
-income.t.tests
+snapshot_OP_plots(raw, cv, 'hh_income')
 ```
@@
 ```{r}
-yearly_box_plots(pivoted.df = income.pivoted,
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
                                  var = 'hh_income', 
+                                 target.year = 2014)
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'hh_income', 
+                                 target.year = 2016)
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'hh_income', 
+                                 target.year = 2018)
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'hh_income', 
+                                 target.year = 2020)
+```
+
+# SF_12
+
+```{r}
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12')
+```
+
+```{r}
+income.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                         df1.name = 'simulated', 
+                                         df2 = raw, 
+                                         df2.name = 'raw', 
+                                         var = 'SF_12')
+
+compare_boxplot_long(pivoted.df = income.pivoted,
+                     var = 'SF_12',
+                     scen1 = 'raw',
+                     scen2 = 'simulation')
+
+compare_boxplot_long(pivoted.df = income.pivoted,
+                     var = 'SF_12',
                      scen1 = 'raw',
@@
 
-## SF12
+```{r}
+snapshot_OP_plots(raw, cv, 'SF_12')
+```
 
 ```{r}
-sf12.pivoted <- combine_and_pivot_long(df1 = cv, 
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12', 
+                                 target.year = 2014)
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12', 
+                                 target.year = 2016)
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12', 
+                                 target.year = 2018)
+marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12', 
+                                 target.year = 2020)
+```
+
+## Housing Quality
+
+```{r}
+hous.pivoted <- combine_and_pivot_long(df1 = cv, 
                                        df1.name = 'simulated', 
@@
                                        df2.name = 'raw', 
-                                       var = 'SF_12')
+                                       var = 'housing_quality')
 
-plot_mean_comparison(pivoted.df = sf12.pivoted, 
-                     var = 'SF_12', 
-                     group.var = 'scenario',
-                     save = TRUE,
-                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
-
-compare_boxplot_long(pivoted.df = sf12.pivoted,
-                     var = 'SF_12',
-                     scen1 = 'raw',
-                     scen2 = 'simulation')
+cv_ordinal_plots(pivoted.df = hous.pivoted, 
+                 var = 'housing_quality',
+                 save = FALSE)
 ```
 
-### T-Tests
+## Neighbourhood Safety
 
 ```{r}
-sf12.t.tests <- two_sample_t_test(cv, 'cv', raw, 'raw', 'hh_income')
-sf12.t.tests
+nhsafe.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'neighbourhood_safety')
+
+cv_ordinal_plots(pivoted.df = nhsafe.pivoted, 
+                 var = 'neighbourhood_safety',
+                 save = FALSE)
 ```
 
+## Loneliness
+
 ```{r}
-yearly_box_plots(pivoted.df = sf12.pivoted,
-                 var = 'SF_12',
-                 scen1 = 'raw',
-                 scen2 = 'simulation')
+lnly.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'loneliness')
+
+cv_ordinal_plots(pivoted.df = lnly.pivoted, 
+                 var = 'loneliness',
+                 save = FALSE)
 ```
@@
 compare_boxplot_long(pivoted.df = nut.pivoted,
-                     var = 'nutrition_quality',
-                     scen1 = 'raw',
-                     scen2 = 'simulation')
-```
-
-```{r}
-yearly_box_plots(pivoted.df = nut.pivoted,
                      var = 'nutrition_quality',
@@
 ```{r}
-yearly_box_plots(pivoted.df = tobacco.pivoted,
-                 var = 'ncigs',
-                 scen1 = 'raw',
-                 scen2 = 'simulation',
-                 subset.max = 100,
-                 subset.min = 0)
-```
-
-## Housing Quality
-
-```{r}
-hous.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw, 
-                                       df2.name = 'raw', 
-                                       var = 'housing_quality')
-
-cv_ordinal_plots(pivoted.df = hous.pivoted, 
-                 var = 'housing_quality',
-                 save = TRUE,
-                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
-```
-
-## Neighbourhood Safety
-
-```{r}
-nhsafe.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                          df1.name = 'simulated', 
-                                          df2 = raw, 
-                                          df2.name = 'raw', 
-                                          var = 'neighbourhood_safety')
-
-cv_ordinal_plots(pivoted.df = nhsafe.pivoted, 
-                 var = 'neighbourhood_safety',
-                 save = TRUE,
-                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
-```
-
-## Loneliness
-
-```{r}
-lnly.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                          df1.name = 'simulated', 
-                                          df2 = raw, 
-                                          df2.name = 'raw', 
-                                          var = 'loneliness')
-
-cv_ordinal_plots(pivoted.df = lnly.pivoted, 
-                 var = 'loneliness',
-                 save = TRUE,
-                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
-```
-
-```{r}
 

### 2023-06-29 minos/validation/cross_validation_default.Rmd
Stopped saving some plots in the cross_validation_default.Rmd notebook

@@
 require(ggplot2)
+require(ggExtra)
 require(here)
@@
                      group.var = 'scenario',
-                     save = TRUE,
-                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
+                     save = FALSE)
 

### 2023-06-30 minos/validation/cross_validation_default.Rmd
Tweaks to the filtering to ncigs, and implementation of the boxplot function in cross_validation_default.Rmd

@@
 ```{r}
-income.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                         df1.name = 'simulated', 
-                                         df2 = raw, 
-                                         df2.name = 'raw', 
-                                         var = 'hh_income')
-
-compare_boxplot_long(pivoted.df = income.pivoted,
-                     var = 'hh_income',
-                     scen1 = 'raw',
-                     scen2 = 'simulation')
-
-compare_boxplot_long(pivoted.df = income.pivoted,
-                     var = 'hh_income',
-                     scen1 = 'raw',
-                     scen2 = 'simulation',
-                     subset.max = 5000,
-                     subset.min = -5000)
+multi_year_boxplots(raw, cv, 'hh_income')
 ```
@@
                                  target.year = 2014)
+
 marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2016)
+
 marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2018)
+
 marg_dist_densigram_plot_oneyear(observed = raw, 
@@
 ```{r}
-income.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                         df1.name = 'simulated', 
-                                         df2 = raw, 
-                                         df2.name = 'raw', 
-                                         var = 'SF_12')
-
-compare_boxplot_long(pivoted.df = income.pivoted,
-                     var = 'SF_12',
-                     scen1 = 'raw',
-                     scen2 = 'simulation')
-
-compare_boxplot_long(pivoted.df = income.pivoted,
-                     var = 'SF_12',
-                     scen1 = 'raw',
-                     scen2 = 'simulation',
-                     subset.max = 5000,
-                     subset.min = -5000)
+multi_year_boxplots(raw, cv, 'SF_12')
 ```
@@
 ```{r}
-nut.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw, 
-                                       df2.name = 'raw', 
-                                       var = 'nutrition_quality')
-
-plot_mean_comparison(pivoted.df = nut.pivoted, 
-                     var = 'nutrition_quality', 
-                     group.var = 'scenario',
-                     save = FALSE)
-
-compare_boxplot_long(pivoted.df = nut.pivoted,
-                     var = 'nutrition_quality',
-                     scen1 = 'raw',
-                     scen2 = 'simulation')
+multi_year_boxplots(raw, cv, 'nutrition_quality')
 ```
@@
 
-compare_boxplot_long(pivoted.df = tobacco.pivoted,
-                     var = 'ncigs',
-                     scen1 = 'raw',
-                     scen2 = 'simulation')
-
-compare_boxplot_long(pivoted.df = tobacco.pivoted,
-                     var = 'ncigs',
-                     scen1 = 'raw',
-                     scen2 = 'simulation',
-                     subset.max = 100,
-                     subset.min = 0)
+multi_year_boxplots(raw, cv, 'ncigs')
 ```

### 2023-07-03 minos/validation/cross_validation_default.Rmd
Dropped dead people from output dataframes and removed missing values from mean plots. Cleaned up some sections of the cross_validation_default script also

@@
 out.path <- here::here('output', 'cv')
-cv1 <- read_singular_local_out(here::here(out.path, 'default1/'), 'baseline')
-cv2 <- read_singular_local_out(here::here(out.path, 'default2/'), 'baseline')
-cv3 <- read_singular_local_out(here::here(out.path, 'default3/'), 'baseline')
-cv4 <- read_singular_local_out(here::here(out.path, 'default4/'), 'baseline')
-cv5 <- read_singular_local_out(here::here(out.path, 'default5/'), 'baseline')
+cv1 <- read_singular_local_out(here::here(out.path, 'default1/'), 'baseline', drop.dead = TRUE)
+cv2 <- read_singular_local_out(here::here(out.path, 'default2/'), 'baseline', drop.dead = TRUE)
+cv3 <- read_singular_local_out(here::here(out.path, 'default3/'), 'baseline', drop.dead = TRUE)
+cv4 <- read_singular_local_out(here::here(out.path, 'default4/'), 'baseline', drop.dead = TRUE)
+cv5 <- read_singular_local_out(here::here(out.path, 'default5/'), 'baseline', drop.dead = TRUE)
 
@@
 ```{r}
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'nutrition_quality')
 multi_year_boxplots(raw, cv, 'nutrition_quality')
@@
 ```{r}
-tobacco.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw, 
-                                       df2.name = 'raw', 
-                                       var = 'ncigs')
-
-plot_mean_comparison(pivoted.df = tobacco.pivoted, 
-                     var = 'ncigs', 
-                     group.var = 'scenario',
-                     save = FALSE)
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'ncigs')
 

### 2023-07-03 minos/validation/cross_validation_default.Rmd
Added lots of secondary variables to cross_validation_default.Rmd

@@
 
-## Housing Quality
+# Housing Quality
 
@@
 
-## Neighbourhood Safety
+# Neighbourhood Safety
 
@@
 
-## Loneliness
+# Loneliness
 
@@
 
-## Nutrition Quality
+# Nutrition Quality
 
@@
 
-## Tobacco Use
+# Tobacco Use
 
@@
 
+# Financial Situation
+
+```{r}
+fsit.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'financial_situation')
+
+cv_ordinal_plots(pivoted.df = fsit.pivoted, 
+                 var = 'financial_situation',
+                 save = FALSE)
+
+rm(fsit.pivoted)
+```
+
+# Heating
+
+```{r}
+heat.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'heating')
+
+cv_ordinal_plots(pivoted.df = heat.pivoted, 
+                 var = 'heating',
+                 save = FALSE)
+```
+
+# SECONDARY VARS
+
+## Marital Status
+
+```{r}
+mstat.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'marital_status')
+
+cv_ordinal_plots(pivoted.df = mstat.pivoted, 
+                 var = 'marital_status',
+                 save = FALSE)
+
+rm(mstat.pivoted)
+```
+
+## hhsize
+
+```{r}
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hhsize')
+
+multi_year_boxplots(raw, cv, 'hhsize')
+```
+
+## housing tenure
+
+```{r}
+tenure.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'housing_tenure')
+
+cv_ordinal_plots(pivoted.df = tenure.pivoted, 
+                 var = 'housing_tenure',
+                 save = FALSE)
+
+rm(tenure.pivoted)
+```
+
+## Ethnicity
+
+```{r}
+ethnic.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'ethnicity')
+
+cv_ordinal_plots(pivoted.df = ethnic.pivoted, 
+                 var = 'ethnicity',
+                 save = FALSE)
+
+ethnic.piv.nowhite <- filter(ethnic.pivoted, ethnicity != 'WBI')
+
+cv_ordinal_plots(pivoted.df = ethnic.piv.nowhite, 
+                 var = 'ethnicity',
+                 save = FALSE)
+
+rm(ethnic.pivoted, ethnic.piv.nowhite)
+```
+
 ```{r}

### 2023-07-03 minos/validation/cross_validation_default.Rmd
Minor changes to cross_validation_default.Rmd

@@
 cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hh_income')
-```
+multi_year_boxplots(raw, cv, 'hh_income')
+snapshot_OP_plots(raw, cv, 'hh_income')
 
-```{r}
-multi_year_boxplots(raw, cv, 'hh_income')
-```
-
-```{r}
-snapshot_OP_plots(raw, cv, 'hh_income')
-```
-
-```{r}
 marg_dist_densigram_plot_oneyear(observed = raw, 
@@
 cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12')
-```
+multi_year_boxplots(raw, cv, 'SF_12')
+snapshot_OP_plots(raw, cv, 'SF_12')
 
-```{r}
-multi_year_boxplots(raw, cv, 'SF_12')
-```
-
-```{r}
-snapshot_OP_plots(raw, cv, 'SF_12')
-```
-
-```{r}
 marg_dist_densigram_plot_oneyear(observed = raw, 
@@
 cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hhsize')
-
 multi_year_boxplots(raw, cv, 'hhsize')

### 2023-07-03 minos/validation/cross_validation_S7.Rmd
Fixed end time and duration of the S7 cross-validation config files, and created a cross_validation notebook for visualising outputs from the S7 cv runs

--- 2023-07-03 minos/validation/cross_validation_default.Rmd
@@
 out.path <- here::here('output', 'cv')
-cv1 <- read_singular_local_out(here::here(out.path, 'default1/'), 'baseline', drop.dead = TRUE)
-cv2 <- read_singular_local_out(here::here(out.path, 'default2/'), 'baseline', drop.dead = TRUE)
-cv3 <- read_singular_local_out(here::here(out.path, 'default3/'), 'baseline', drop.dead = TRUE)
-cv4 <- read_singular_local_out(here::here(out.path, 'default4/'), 'baseline', drop.dead = TRUE)
-cv5 <- read_singular_local_out(here::here(out.path, 'default5/'), 'baseline', drop.dead = TRUE)
+cv1 <- read_singular_local_out(here::here(out.path, 'S7_1/'), 'baseline', drop.dead = TRUE)
+cv2 <- read_singular_local_out(here::here(out.path, 'S7_2/'), 'baseline', drop.dead = TRUE)
+cv3 <- read_singular_local_out(here::here(out.path, 'S7_3/'), 'baseline', drop.dead = TRUE)
+cv4 <- read_singular_local_out(here::here(out.path, 'S7_4/'), 'baseline', drop.dead = TRUE)
+cv5 <- read_singular_local_out(here::here(out.path, 'S7_5/'), 'baseline', drop.dead = TRUE)
 
@@
 
-# SF_12
+# Equivalent Income
 
 ```{r}
-cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12')
-```
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'equivalent_income')
+multi_year_boxplots(raw, cv, 'equivalent_income')
+snapshot_OP_plots(raw, cv, 'equivalent_income')
 
-```{r}
-multi_year_boxplots(raw, cv, 'SF_12')
-```
-
-```{r}
-snapshot_OP_plots(raw, cv, 'SF_12')
-```
-
-```{r}
 marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
-                                 var = 'SF_12', 
+                                 var = 'equivalent_income', 
                                  target.year = 2014)
+
 marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
-                                 var = 'SF_12', 
+                                 var = 'equivalent_income', 
                                  target.year = 2016)
+
 marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
-                                 var = 'SF_12', 
+                                 var = 'equivalent_income', 
                                  target.year = 2018)
+
 marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
-                                 var = 'SF_12', 
+                                 var = 'equivalent_income', 
                                  target.year = 2020)
@@
 
-## Housing Quality
+# S7 Housing Quality
 
@@
                                        df2.name = 'raw', 
-                                       var = 'housing_quality')
+                                       var = 'S7_housing_quality')
 
 cv_ordinal_plots(pivoted.df = hous.pivoted, 
-                 var = 'housing_quality',
+                 var = 'S7_housing_quality',
                  save = FALSE)
@@
 
-## Neighbourhood Safety
+# S7 Neighbourhood Safety
 
@@
                                           df2.name = 'raw', 
-                                          var = 'neighbourhood_safety')
+                                          var = 'S7_neighbourhood_safety')
 
 cv_ordinal_plots(pivoted.df = nhsafe.pivoted, 
-                 var = 'neighbourhood_safety',
+                 var = 'S7_neighbourhood_safety',
                  save = FALSE)
@@
 
-## Loneliness
+# S7 Physical Health
 
 ```{r}
-lnly.pivoted <- combine_and_pivot_long(df1 = cv, 
+physhealth.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'S7_physical_health')
+
+cv_ordinal_plots(pivoted.df = physhealth.pivoted, 
+                 var = 'S7_physical_health',
+                 save = FALSE)
+```
+
+# S7 Mental Health
+
+```{r}
+menhealth.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'S7_mental_health')
+
+cv_ordinal_plots(pivoted.df = menhealth.pivoted, 
+                 var = 'S7_mental_health',
+                 save = FALSE)
+```
+
+# S7 Labour State
+
+```{r}
+labstate.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'S7_labour_state')
+
+cv_ordinal_plots(pivoted.df = labstate.pivoted, 
+                 var = 'S7_labour_state',
+                 save = FALSE)
+```
+
+# Loneliness
+
+```{r}
+lon.pivoted <- combine_and_pivot_long(df1 = cv, 
                                           df1.name = 'simulated', 
@@
 
-cv_ordinal_plots(pivoted.df = lnly.pivoted, 
+cv_ordinal_plots(pivoted.df = lon.pivoted, 
                  var = 'loneliness',
@@
 
-## Nutrition Quality
+# Education
 
 ```{r}
-cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'nutrition_quality')
-multi_year_boxplots(raw, cv, 'nutrition_quality')
-```
+educ.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'education_state')
 
-## Tobacco Use
-
-```{r}
-cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'ncigs')
-
-multi_year_boxplots(raw, cv, 'ncigs')
+cv_ordinal_plots(pivoted.df = educ.pivoted, 
+                 var = 'education_state',
+                 save = FALSE)
 ```

### 2023-07-03 minos/validation/cross_validation_S7.Rmd
Added equivalent_income to the list of vars that do inverse hyperbolic sine transformation when visualising with marginal plots

@@
                                  var = 'equivalent_income', 
-                                 target.year = 2016)
-
-marg_dist_densigram_plot_oneyear(observed = raw, 
-                                 predicted = cv, 
-                                 var = 'equivalent_income', 
-                                 target.year = 2018)
+                                 target.year = 2017)
 

### 2023-07-04 minos/validation/cross_validation_S7.Rmd
More improvements and tweaks to both cross-val scripts and the utils functions

@@
 
-marg_dist_densigram_plot_oneyear(observed = raw, 
+inc.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
@@
 
-marg_dist_densigram_plot_oneyear(observed = raw, 
+inc.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
@@
 
-marg_dist_densigram_plot_oneyear(observed = raw, 
+inc.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
@@
 
-marg_dist_densigram_plot_oneyear(observed = raw, 
+inc.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
@@
                                  target.year = 2020)
+rm(inc.14, inc.16, inc.18, inc.20)
 ```
@@
 
-marg_dist_densigram_plot_oneyear(observed = raw, 
+ei.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
@@
 
-marg_dist_densigram_plot_oneyear(observed = raw, 
+ei.17 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
@@
 
-marg_dist_densigram_plot_oneyear(observed = raw, 
+ei.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
@@
                                  target.year = 2020)
+rm(ei.14, ei.17, ei.20)
 ```
@@
                  save = FALSE)
+rm(hous.pivoted)
 ```
@@
                  save = FALSE)
+rm(nhsafe.pivoted)
 ```
@@
                  save = FALSE)
+rm(physhealth.pivoted)
 ```
@@
                  save = FALSE)
+rm(menhealth.pivoted)
 ```
@@
                  save = FALSE)
+rm(labstate.pivoted)
 ```
@@
                  save = FALSE)
+rm(lon.pivoted)
 ```
@@
                  save = FALSE)
+rm(educ.pivoted)
 ```

### 2023-07-04 minos/validation/cross_validation_default.Rmd
More improvements and tweaks to both cross-val scripts and the utils functions

@@
                                  target.year = 2020)
+
+rm(inc.14, inc.16, inc.18, inc.20)
 ```
@@
 
-marg_dist_densigram_plot_oneyear(observed = raw, 
+sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
@@
                                  target.year = 2014)
-marg_dist_densigram_plot_oneyear(observed = raw, 
+sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
@@
                                  target.year = 2016)
-marg_dist_densigram_plot_oneyear(observed = raw, 
+sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
@@
                                  target.year = 2018)
-marg_dist_densigram_plot_oneyear(observed = raw, 
+sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                  predicted = cv, 
@@
                                  target.year = 2020)
+
+rm(sf12.14, sf12.16, sf12.18, sf12.20)
 ```
@@
                  save = FALSE)
+rm(lnly.pivoted)
 ```
@@
                  save = FALSE)
-
 rm(fsit.pivoted)
@@
                  save = FALSE)
+rm(heat.pivoted)
 ```
@@
                  save = FALSE)
-
 rm(mstat.pivoted)
@@
                  save = FALSE)
-
 rm(tenure.pivoted)

### 2023-07-04 minos/validation/cross_validation_S7.Rmd
Added q-q plots to utils and both cross_validation notebooks

@@
 snapshot_OP_plots(raw, cv, 'hh_income')
+q_q_comparison(raw, cv, 'hh_income')
 
@@
 snapshot_OP_plots(raw, cv, 'equivalent_income')
+q_q_comparison(raw, cv, 'equivalent_income')
 

### 2023-07-04 minos/validation/cross_validation_default.Rmd
Added q-q plots to utils and both cross_validation notebooks

@@
 snapshot_OP_plots(raw, cv, 'SF_12')
+q_q_comparison(raw, cv, 'SF_12')
 
@@
 multi_year_boxplots(raw, cv, 'nutrition_quality')
+q_q_comparison(raw, cv, 'nutrition_quality')
 ```
@@
 cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'ncigs')
-
 multi_year_boxplots(raw, cv, 'ncigs')
+q_q_comparison(raw, cv, 'ncigs')
 ```
@@
 multi_year_boxplots(raw, cv, 'hhsize')
+q_q_comparison(raw, cv, 'hhsize')
 ```

### 2023-07-04 minos/validation/cross_validation_S7.Rmd
Tweaks to some functions to make them work better in rendered html

@@
                                  target.year = 2014)
-
+print(inc.14)
 inc.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2016)
-
+print(inc.16)
 inc.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2018)
-
+print(inc.18)
 inc.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2020)
+print(inc.20)
 rm(inc.14, inc.16, inc.18, inc.20)
@@
                                  target.year = 2014)
-
+print(ei.14)
 ei.17 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2017)
-
+print(ei.17)
 ei.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2020)
+print(ei.20)
 rm(ei.14, ei.17, ei.20)

### 2023-07-04 minos/validation/cross_validation_default.Rmd
Tweaks to some functions to make them work better in rendered html

@@
                                  target.year = 2020)
-
+print(inc.20)
 rm(inc.14, inc.16, inc.18, inc.20)
@@
                                  target.year = 2014)
+print(sf12.14)
 sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2016)
+print(sf12.16)
 sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2018)
+print(sf12.18)
 sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2020)
-
+print(sf12.20)
 rm(sf12.14, sf12.16, sf12.18, sf12.20)

### 2023-07-04 minos/validation/cross_validation_default.Rmd
Final tweaks to get everything rendering properly in the html outputs. Ready to PR

--- 2023-07-04 minos/validation/cross_validation_default.Rmd
@@
 multi_year_boxplots(raw, cv, 'hh_income')
-snapshot_OP_plots(raw, cv, 'hh_income')
+snapshot_OP_plots(raw, cv, 'hh_income', target.years = c(2014, 2016, 2018, 2020))
 q_q_comparison(raw, cv, 'hh_income')
-
+```
+```{r}
 inc.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2014)
-
+print(inc.14)
+```
+```{r}
 inc.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2016)
-
+print(inc.16)
+```
+```{r}
 inc.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2018)
-
+print(inc.18)
+```
+```{r}
 inc.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2020)
-
+print(inc.20)
+```
+```{r}
 rm(inc.14, inc.16, inc.18, inc.20)
@@
 multi_year_boxplots(raw, cv, 'SF_12')
-snapshot_OP_plots(raw, cv, 'SF_12')
+snapshot_OP_plots(raw, cv, 'SF_12', target.years = c(2014, 2016, 2018, 2020))
 q_q_comparison(raw, cv, 'SF_12')
-
+```
+```{r}
 sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2014)
+print(sf12.14)
+```
+```{r}
 sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2016)
+print(sf12.16)
+```
+```{r}
 sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2018)
+print(sf12.18)
+```
+```{r}
 sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 

### 2023-07-05 minos/validation/cross_validation_S7.Rmd

--- 2023-07-04 minos/validation/cross_validation_S7.Rmd
@@
 multi_year_boxplots(raw, cv, 'hh_income')
-snapshot_OP_plots(raw, cv, 'hh_income')
+snapshot_OP_plots(raw, cv, 'hh_income', target.years = c(2014, 2016, 2018, 2020))
+q_q_comparison(raw, cv, 'hh_income')
+```
 
+```{r}
 inc.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
 multi_year_boxplots(raw, cv, 'equivalent_income')
-snapshot_OP_plots(raw, cv, 'equivalent_income')
-
+snapshot_OP_plots(raw, cv, 'equivalent_income', target.years = c(2014, 2017, 2020))
+q_q_comparison(raw, cv, 'equivalent_income')
+```
+```{r}
 ei.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2014)
-
+print(ei.14)
+```
+```{r}
 ei.17 <- marg_dist_densigram_plot_oneyear(observed = raw, 
@@
                                  target.year = 2017)
-
+print(ei.17)
+```
+```{r}
 ei.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 

### 2023-07-05 minos/validation/handovers.Rmd
Fixed the shall.we.wave logic in handovers.Rmd. Oops again I introduced these errors with a half finished idea, finished it now

--- 2023-06-15 minos/validation/handovers.Rmd
@@
 require(ggplot2)
+require(knitr)
+require(here)
 
 #workingDir <- "/home/luke/Documents/WORK/MINOS/"
-workingDir <- "/Users/robertclay/"
+workingDir <- normalizePath('../')
 knitr::opts_knit$set(root.dir = workingDir)
@@
 ```{r}
-source('/Users/robertclay/minos/minos/utils_datain.R')
-source('/Users/robertclay/minos/minos/utils_validation_vis.R')
+source(here::here('minos', 'utils_datain.R'))
+source(here::here('minos', 'utils_validation_vis.R'))
 ```
@@
 # Read raw datafiles in
-raw.files <- list.files('/Users/robertclay/minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
 
-out.path <- '/Users/robertclay/minos/output/default_config/'
+out.path <- here::here('output', 'default_config/')
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
@@
 start.year <- 2020
+save.path <- here::here("plots", "handovers", 'default')
+create.if.not.exists(save.path)
 
-save.path <- '/Users/robertclay/minos/plots/andovers/'
+shall.we.save <- FALSE
 ```
@@
        path = save.path)
+}
 
@@
 
+if (shall.we.save) {
   ggsave(filename = 'SF12_wav1.png',
@@
 spaghetti_plot(sf12.spag, 'SF_12',
-               save = TRUE,
+               save = shall.we.save,
                save.path = save.path)
@@
 rm(raw.sf12, base.sf12, sf12.spag)
+```
+
+## Financial Situation
+
+```{r}
+raw.financial_situation <- raw.dat %>% 
+  dplyr::select(pidp, time, financial_situation) %>%
+  group_by(time, financial_situation) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.financial_situation <- base.dat %>%
+  dplyr::select(pidp, time, financial_situation) %>%
+  group_by(time, financial_situation) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+financial_situation <- rbind(raw.financial_situation, base.financial_situation)
+financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
+
+# Now plot
+ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+financial_situation.norm <- financial_situation %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial situation') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'financial_situation.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.housing, base.housing, housing, housing.norm)
 ```
@@
 
+if (shall.we.save) {
   ggsave(filename = 'housing_quality.png',
@@
        path = save.path)
+}
 
 rm(raw.housing, base.housing, housing, housing.norm)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, housing_quality)
+base.s <- base.dat %>%
+  select(pidp, age, time, housing_quality)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'housing_quality',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 
+if (shall.we.save) {
   ggsave(filename = 'neighbourhood_safety.png',
@@
        path = save.path)
+}
 
 #rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, neighbourhood_safety)
+base.s <- base.dat %>%
+  select(pidp, age, time, neighbourhood_safety)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'neighbourhood_safety',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
        path = save.path)
+}
 
 rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, loneliness)
+base.s <- base.dat %>%
+  select(pidp, age, time, loneliness)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'loneliness',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 
+if (shall.we.save) {
   ggsave(filename = 'nutrition_quality_wav1.png',
@@
     nutrition_quality2)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, nutrition_quality)
+base.s <- base.dat %>%
+  select(pidp, age, time, nutrition_quality)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nutrition_quality',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 
+if (shall.we.save) {
   ggsave(filename = 'physical_health_wav1.png',
@@
 
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, phealth)
+base.s <- base.dat %>%
+  select(pidp, age, time, phealth)
+
+spag <- rbind(raw.s, base.s)
+
+if (shall.we.save) {
+  spaghetti_plot(spag, 'phealth',
+               save = shall.we.save,
+               save.path = save.path)
+}
+
+rm(raw.s, base.s, spag)
+```
+
+## Education
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Education State'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'education_state.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'education_state')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'education_state',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, education_state)
+base.s <- base.dat %>%
+  select(pidp, age, time, education_state)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'education_state',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
 ```{r}

### 2023-07-05 minos/validation/handovers.Rmd
Sourced the validation/utils.r file in handovers.Rmd as should have already been done
Added some additional features to the html files that render from RNotebook scripts. Stuff like table of contents and some formatting

@@
   html_document:
+    toc: true
+    toc_float: true
+      collapsed: false
+    number_sections: true
     df_print: paged
+    code_folding: hide
 ---
@@
 source(here::here('minos', 'utils_validation_vis.R'))
+source(here::here('minos', 'validation', 'utils.r'))
 ```
@@
 
-```{r}
+```{r, warning=FALSE}
 raw.inc <- raw.dat %>%
@@
 
-rm(raw.housing, base.housing, housing, housing.norm)
+rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
 ```
@@
 
-if (shall.we.save) {
 spaghetti_plot(spag, 'phealth',
@@
              save.path = save.path)
-}
 
@@
 
-```{r}
+```{r, warning=FALSE}
 pivoted <- combine_and_pivot_long(df1 = base.dat, 

### 2023-07-05 minos/validation/cross_validation_S7.Rmd
Added some additional features to the html files that render from RNotebook scripts. Stuff like table of contents and some formatting
Tweaks to the html document settings, and suppressing warnings and messages from chunks

@@
 ---
-title: "Cross-Validation Default"
-output: html_notebook
+title: "Cross-Validation SIPHER7 Equivalent Income"
+output:
+  html_document:
+    toc: true
+    toc_float: true
+    collapsed: false
+    number_sections: true
+    df_print: paged
+    code_folding: hide
 ---
@@
 knitr::opts_knit$set(root.dir = workingDir)
+knitr::opts_chunk$set(
+  warning = FALSE,
+  message = FALSE
+)
 rm(workingDir)
@@
 
-```{r}
+```{r, include=FALSE}
 # pidp filter

### 2023-07-05 minos/validation/cross_validation_default.Rmd
Added some additional features to the html files that render from RNotebook scripts. Stuff like table of contents and some formatting
Tweaks to the html document settings, and suppressing warnings and messages from chunks

@@
 title: "Cross-Validation Default"
-output: html_notebook
+output:
+  html_document:
+    toc: true
+    toc_float: true
+    collapsed: false
+    number_sections: true
+    df_print: paged
+    code_folding: hide
 ---
@@
 print(inc.20)
-```
-```{r}
 rm(inc.14, inc.16, inc.18, inc.20)

### 2023-07-05 minos/validation/handovers_S7.Rmd
Added some additional features to the html files that render from RNotebook scripts. Stuff like table of contents and some formatting
Tweaks to the html document settings, and suppressing warnings and messages from chunks

--- 2023-06-13 minos/validation/handovers_S7.Rmd
@@
 title: "Handovers - SIPHER 7 Equivalent Income"
-output: html_notebook
+output:
+  html_document:
+    toc: true
+    toc_float: true
+    collapsed: false
+    number_sections: true
+    df_print: paged
+    code_folding: hide
 ---

### 2023-07-06 minos/validation/handovers.Rmd
Fixed some references to SF_12 -> SF_12_MCS, and fixed the PCS section also

@@
 
-```{r, warning=FALSE}
+```{r}
 raw.inc <- raw.dat %>%
@@
 # merge before plot
-sf12 <- rbind(raw.sf12, base.sf12)
+sf12.m <- rbind(raw.sf12.m, base.sf12.m)
+
+print(sum(sf12.m$SF_12_MCS < 0))
 
 # Now plot
-ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+ggplot(data = sf12.m, mapping = aes(x = time, y = sf12.m, group = source, colour = source)) +
   geom_line() +
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
+  labs(title = 'Mental Wellbeing (SF12_MCS)', subtitle = 'Full Sample') +
   xlab('Year') +
-  ylab('SF12')
+  ylab('SF12_MCS')
 
@@
 # onwards because the sample refreshments are messing with the plot
-raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+raw.sf12.m.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
 
-raw.sf12.2 <- raw.dat %>% 
-  dplyr::select(pidp, time, SF_12) %>%
-  filter(pidp %in% raw.sf12.wave1) %>%
+raw.sf12.m.2 <- raw.dat %>% 
+  dplyr::select(pidp, time, SF_12_MCS) %>%
+  filter(SF_12_MCS > 0) %>%
+  filter(pidp %in% raw.sf12.m.wave1) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'final_US')
 
-base.sf12.2 <- base.dat %>%
-  dplyr::select(pidp, time, SF_12) %>%
-  filter(pidp %in% raw.sf12.wave1) %>%
+base.sf12.m.2 <- base.dat %>%
+  dplyr::select(pidp, time, SF_12_MCS) %>%
+  filter(SF_12_MCS > 0) %>%
+  filter(pidp %in% raw.sf12.m.wave1) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'baseline_output')
 
-sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
+sf12.m.2 <- rbind(raw.sf12.m.2, base.sf12.m.2)
 
 # Now plot
-ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+ggplot(data = sf12.m.2, mapping = aes(x = time, y = sf12.m, group = source, colour = source)) +
   geom_line() +
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Mental Wellbeing (SF12 MCS)') +
+  labs(title = 'Mental Wellbeing (SF12_MCS)') +
   xlab('Year') +
-  ylab('SF12')
+  ylab('SF12_MCS')
 
 if (shall.we.save) {
-  ggsave(filename = 'SF12_wav1.png',
+  ggsave(filename = 'SF12_MCS_wav1.png',
        plot = last_plot(),
@@
 ```{r}
-raw.sf12 <- raw.dat %>%
-  select(pidp, age, time, SF_12)
-base.sf12 <- base.dat %>%
-  select(pidp, age, time, SF_12)
+raw.sf12.m <- raw.dat %>%
+  select(pidp, age, time, SF_12_MCS)
+base.sf12.m <- base.dat %>%
+  select(pidp, age, time, SF_12_MCS)
 
-sf12.spag <- rbind(raw.sf12, base.sf12)
+sf12.m.spag <- rbind(raw.sf12.m, base.sf12.m)
 
-spaghetti_plot(sf12.spag, 'SF_12',
+spaghetti_plot(sf12.m.spag, 'SF_12_MCS',
                save = shall.we.save,
@@
 
-rm(raw.sf12, base.sf12, sf12.spag)
+rm(raw.sf12.m, base.sf12.m, sf12.m.spag)
+```
+
+## SF_12_PCS
+
+```{r}
+# first figure out how to plot final_US
+# start with hh_income
+raw.sf12.p <- raw.dat %>% 
+  dplyr::select(pidp, time, SF_12_PCS) %>%
+  filter(SF_12_PCS > 0) %>%
+  group_by(time) %>%
+  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
+  mutate(source = 'final_US')
+
+base.sf12.p <- base.dat %>%
+  dplyr::select(pidp, time, SF_12_PCS) %>%
+  filter(SF_12_PCS > 0) %>%
+  group_by(time) %>%
+  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+sf12.p <- rbind(raw.sf12.p, base.sf12.p)
+
+# Now plot
+ggplot(data = sf12.p, mapping = aes(x = time, y = sf12.p, group = source, colour = source)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Physical Wellbeing (SF12_PCS)', subtitle = 'Full Sample') +
+  xlab('Year') +
+  ylab('SF12_PCS')
+
+## Try a version where final_US is limited to only those present from wave 1 
+# onwards because the sample refreshments are messing with the plot
+raw.sf12.p.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+
+raw.sf12.p.2 <- raw.dat %>% 
+  dplyr::select(pidp, time, SF_12_PCS) %>%
+  filter(SF_12_PCS > 0) %>%
+  filter(pidp %in% raw.sf12.p.wave1) %>%
+  group_by(time) %>%
+  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
+  mutate(source = 'final_US')
+
+base.sf12.p.2 <- base.dat %>%
+  dplyr::select(pidp, time, SF_12_PCS) %>%
+  filter(SF_12_PCS > 0) %>%
+  filter(pidp %in% raw.sf12.p.wave1) %>%
+  group_by(time) %>%
+  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
+  mutate(source = 'baseline_output')
+
+sf12.p.2 <- rbind(raw.sf12.p.2, base.sf12.p.2)
+
+# Now plot
+ggplot(data = sf12.p.2, mapping = aes(x = time, y = sf12.p, group = source, colour = source)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Physical Wellbeing (SF12_PCS)') +
+  xlab('Year') +
+  ylab('SF12_PCS')
+
+ggsave(filename = 'SF12_PCS_wav1.png',
+       plot = last_plot(),
+       path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+raw.sf12.p <- raw.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+base.sf12.p <- base.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+
+sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)
+
+spaghetti_plot(sf12.m.spag, 'SF_12_PCS',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
 ```
@@
 
-```{r, warning=FALSE}
+```{r}
 pivoted <- combine_and_pivot_long(df1 = base.dat, 

### 2023-07-07 minos/validation/handovers.Rmd
Fit model for urban and added it to US_complete_case. Fixed formatting of housing_tenure and fixed typo in handover.Rmd
Functionalised the handovers plots in utils_validation_vis.R and updated the handovers.Rmd script

--- 2023-07-05 minos/validation/handovers.Rmd
@@
 ```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.income <- raw.dat %>% 
-  dplyr::select(pidp, time, hh_income, weight) %>%
-  group_by(time) %>%
-  summarise(income = mean(hh_income, na.rm=TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.income <- base.dat %>%
-  dplyr::select(pidp, time, hh_income, weight) %>%
-  group_by(time) %>%
-  summarise(income = mean(hh_income)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-income <- rbind(raw.income, base.income)
-
-# Now plot
-ggplot(data = income, mapping = aes(x = time, y = income, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Household Income', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Income')
-
-## Try a version where final_US is limited to only those present from wave 1 
-# onwards because the sample refreshments are messing with the plot
-raw.income.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.income2 <- raw.dat %>% 
-  dplyr::select(pidp, time, hh_income) %>%
-  filter(pidp %in% raw.income.wave1) %>%
-  group_by(time) %>%
-  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.income2 <- base.dat %>%
-  dplyr::select(pidp, time, hh_income) %>%
-  filter(pidp %in% raw.income.wave1) %>%
-  group_by(time) %>%
-  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-income2 <- rbind(raw.income2, base.income2)
-
-# Now plot
-ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Household Income') +
-  xlab('Year') +
-  ylab('Income')
-
-if (shall.we.save) {
-  ggsave(filename = 'hh_income_wav1.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-raw.income.check <- raw.dat %>% 
-  dplyr::select(pidp, time, hh_income) %>%
-  filter(pidp %in% raw.income.wave1)
-
-base.income.check <- base.dat %>%
-  dplyr::select(pidp, time, hh_income) %>%
-  filter(pidp %in% raw.income.wave1)
-
-rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
-   raw.income.check, base.income.check)
+handover_continuous(raw.dat, base.dat, var = 'hh_income')
 ```
@@
 
-## SF12
+## SF_12_MCS
 
 ```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.sf12 <- raw.dat %>% 
-  dplyr::select(pidp, time, SF_12) %>%
-  group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.sf12 <- base.dat %>%
-  dplyr::select(pidp, time, SF_12) %>%
-  group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-sf12 <- rbind(raw.sf12, base.sf12)
-
-# Now plot
-ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('SF12')
-
-## Try a version where final_US is limited to only those present from wave 1 
-# onwards because the sample refreshments are messing with the plot
-raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.sf12.2 <- raw.dat %>% 
-  dplyr::select(pidp, time, SF_12) %>%
-  filter(pidp %in% raw.sf12.wave1) %>%
-  group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.sf12.2 <- base.dat %>%
-  dplyr::select(pidp, time, SF_12) %>%
-  filter(pidp %in% raw.sf12.wave1) %>%
-  group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
-
-# Now plot
-ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Mental Wellbeing (SF12 MCS)') +
-  xlab('Year') +
-  ylab('SF12')
-
-if (shall.we.save) {
-  ggsave(filename = 'SF12_wav1.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
+handover_continuous(raw.dat, base.dat, var = 'SF_12_MCS')
 ```
@@
 
-rm(raw.sf12, base.sf12, sf12.spag)
+rm(raw.sf12.m, base.sf12.m, sf12.m.spag)
+```
+
+## SF_12_PCS
+
+```{r}
+handover_continuous(raw.dat, base.dat, var = 'SF_12_PCS')
+```
+
+### Spaghetti
+
+```{r}
+raw.sf12.p <- raw.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+base.sf12.p <- base.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+
+sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)
+
+spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
 ```
@@
 ```{r}
-raw.financial_situation <- raw.dat %>% 
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.financial_situation <- base.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-financial_situation <- rbind(raw.financial_situation, base.financial_situation)
-financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
-
-# Now plot
-ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-financial_situation.norm <- financial_situation %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial situation') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'financial_situation.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
+handover_ordinal(raw.dat, base.dat, var = 'financial_situation', save = shall.we.save)
 ```
@@
 ```{r}
-raw.housing <- raw.dat %>% 
-  dplyr::select(pidp, time, housing_quality) %>%
-  group_by(time, housing_quality) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.housing <- base.dat %>%
-  dplyr::select(pidp, time, housing_quality) %>%
-  group_by(time, housing_quality) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-housing <- rbind(raw.housing, base.housing)
-housing$housing_quality <- as.factor(housing$housing_quality)
-
-# Now plot
-ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Quality', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-housing.norm <- housing %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Quality') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'housing_quality.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.housing, base.housing, housing, housing.norm)
+handover_ordinal(raw.dat, base.dat, var = 'housing_quality', save = shall.we.save)
 ```
@@
 ```{r}
-raw.neighbour <- raw.dat %>% 
-  dplyr::select(pidp, time, neighbourhood_safety) %>%
-  group_by(time, neighbourhood_safety) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.neighbour <- base.dat %>%
-  dplyr::select(pidp, time, neighbourhood_safety) %>%
-  group_by(time, neighbourhood_safety) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-neighbour <- rbind(raw.neighbour, base.neighbour)
-neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety)
-
-# Now plot
-ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') +
-  xlab('Year') +
-  ylab('Count')
-
-neighbour.norm <- neighbour %>%
-  group_by(time) %>%
-  filter(neighbourhood_safety != -9) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Neighbourhood Safety') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'neighbourhood_safety.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-#rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm)
+handover_ordinal(raw.dat, base.dat, var = 'neighbourhood_safety', save = shall.we.save)
 ```
@@
 ```{r}
-raw.loneliness <- raw.dat %>% 
-  dplyr::select(pidp, time, loneliness) %>%
-  group_by(time, loneliness) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.loneliness <- base.dat %>%
-  dplyr::select(pidp, time, loneliness) %>%
-  group_by(time, loneliness) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-loneliness <- rbind(raw.loneliness, base.loneliness)
-loneliness$loneliness <- as.factor(loneliness$loneliness)
-
-# Now plot
-ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Loneliness', subtitle = 'Counts by level') +
-  xlab('Year') +
-  ylab('Count')
-
-loneliness.norm <- loneliness %>%
-  group_by(time) %>%
-  filter(loneliness != -9) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Loneliness') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'loneliness.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
+handover_ordinal(raw.dat, base.dat, var = 'loneliness', save = shall.we.save)
 ```
@@
 ```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.nut <- raw.dat %>% 
-  dplyr::select(pidp, time, nutrition_quality) %>%
-  group_by(time) %>%
-  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.nut <- base.dat %>%
-  dplyr::select(pidp, time, nutrition_quality) %>%
-  group_by(time) %>%
-  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-nutrition_quality <- rbind(raw.nut, base.nut)
-
-# Now plot
-ggplot(data = nutrition_quality, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Nutrition Quality', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Nutrition Quality')
-
-## Try a version where final_US is limited to only those present from wave 1 
-# onwards because the sample refreshments are messing with the plot
-raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.nut2 <- raw.dat %>% 
-  dplyr::select(pidp, time, nutrition_quality) %>%
-  filter(pidp %in% raw.wave1) %>%
-  filter(nutrition_quality >= 0) %>%
-  group_by(time) %>%
-  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.nut2 <- base.dat %>%
-  dplyr::select(pidp, time, nutrition_quality) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-nutrition_quality2 <- rbind(raw.nut2, base.nut2)
-
-# Now plot
-ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Nutrition Quality') +
-  xlab('Year') +
-  ylab('Nutrition Quality')
-
-if (shall.we.save) {
-  ggsave(filename = 'nutrition_quality_wav1.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2, 
-    nutrition_quality2)
+handover_continuous(raw.dat, base.dat, var = 'nutrition_quality')
 ```
@@
 ```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.phealth <- raw.dat %>% 
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.phealth <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-phealth <- rbind(raw.phealth, base.phealth)
-
-# Now plot
-ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Average')
-
-## Try a version where final_US is limited to only those present from wave 1 
-# onwards because the sample refreshments are messing with the plot
-raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.phealth2 <- raw.dat %>% 
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.phealth2 <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-phealth2 <- rbind(raw.phealth2, base.phealth2)
-
-# Now plot
-ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health') +
-  xlab('Year') +
-  ylab('Average')
-
-if (shall.we.save) {
-  ggsave(filename = 'physical_health_wav1.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-#raw.phealth.check <- raw.dat %>% 
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
-
-#base.phealth.check <- base.dat %>%
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
-
-rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2)
-#rm(raw.phealth.check, base.phealth.check)
+handover_continuous(raw.dat, base.dat, var = 'phealth')
 ```
@@
 ```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Education State'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'education_state.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
+handover_ordinal(raw.dat, base.dat, var = 'education_state', save = shall.we.save)
 ```
 
-```{r, warning=FALSE}
+```{r}
 pivoted <- combine_and_pivot_long(df1 = base.dat, 

### 2023-07-07 minos/outcomes/make_lineplots_all.Rmd
updating lineplot notebook to run on bash and nice pdfs

@@
 
-IMPORTANT NOTE TO RUN PYTHON YOU NEED TO SET THE PYTHON INTERPRETER 
-IN TOOLS>GLOBAL_OPTIIONS>PYTHON>CONDA_INTERPRETERS. 
-NOT SURE THIS IS NEEDED ANYMORE GIVEN WE'RE SETTING THE CONDA ENV MANUALLY.
-
+IMPORTANT NOTE TO RUN THIS NOTEBOOK YOU NEED TO INSTALL THE MINOS_CONDA conda environment for MINOS. 
 Can just use minos_conda or create a miniconda env using reticulate package.
@@
 knitr::opts_knit$set(root.dir = here::here())
-knitr::knit_engines$set(python = reticulate::eng_python)
-reticulate::use_condaenv("minos_conda", required = FALSE)
+reticulate::use_condaenv("minos_conda", required = TRUE)
+#knitr::knit_engines$set(python = reticulate::eng_python)
+#reticulate::py_config()
+
 ```
@@
 
-```{r }
-knitr::include_graphics(here::here("plots", "baseline_all_child_uplift_SF_12_aggs_by_year.png"), error=FALSE)
+```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+knitr::include_graphics(here::here("plots", "baseline_all_child_uplift_SF_12_aggs_by_year.pdf"), error=FALSE)
 ```
@@
 
-```{r }
-knitr::include_graphics(here::here("plots", "baseline_poverty_child_uplift_SF_12_aggs_by_year.png"), error=FALSE)
+```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+knitr::include_graphics(here::here("plots", "baseline_poverty_child_uplift_SF_12_aggs_by_year.pdf"), error=FALSE)
 ```
@@
 
-```{r }
-knitr::include_graphics(here::here("plots", "baseline_living_wage_SF_12_aggs_by_year.png"), error=FALSE)
+```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+knitr::include_graphics(here::here("plots", "baseline_living_wage_SF_12_aggs_by_year.pdf"), error=FALSE)
 ```
@@
 
-```{r }
-knitr::include_graphics(here::here("plots", "baseline_energy_downlift_SF_12_aggs_by_year.png"), error=FALSE)
+```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+knitr::include_graphics(here::here("plots", "baseline_energy_downlift_SF_12_aggs_by_year.pdf"), error=FALSE)
 ```
@@
 
-```{r }
-knitr::include_graphics(here::here("plots", "all_five_combined_SF_12_aggs_by_year.png"), error=FALSE)
+```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+knitr::include_graphics(here::here("plots", "all_five_combined_SF_12_aggs_by_year.pdf"), error=FALSE)
 ```

### 2023-07-07 minos/data_generation/US_upscaling.py

@@ -71,7 +71,14 @@ def main():
     4.
     """
     #synthpop_file_name = "../HH2011PopEst2020S_population.csv"
-    synthpop_data = pd.read_csv("../data/Ind2011PopEst2020S_population.csv") # this is individual population weighted data.
+    synthpop_file_path = "persistent_data/Ind2011PopEst2020S_population.csv"
+    try:
+        synthpop_data = pd.read_csv(synthpop_file_path) # this is individual population weighted data.
+    except FileNotFoundError as e:
+        print(e)
+        print(f"Synthetic population file not found at {synthpop_file_path}. Please ask MINOS maintainers for access.")
+        raise
+
     #synthpop_data = pd.read_csv("../data/HH2011PopEst2020S_population.csv") # this is household weighted data. not working atm. need to investigate.
     glasgow_data_zones = pd.read_csv("persistent_data/spatial_data/glasgow_data_zones.csv")["lsoa11cd"] # glasgow data zone IDs.
     US_data = pd.read_csv("data/final_US/2020_US_cohort.csv") # only expanding on one year of US data for 2020.

### 2023-07-07 minos/validation/longitudinal_visualisation.R

@@ -1,230 +1,0 @@
-#file for initial ideas on longitudinal visualisation of single minos model runs
-library(ggplot2) # plots plots plots plots plots
-library(tidyr) #data manipulation
-library(dplyr) # data manipulation
-library(stringr) # for nice formatting of axes labels.
-library(viridis) # for nice colour palettes
-
-get_latest_file <-function(path){
-  # find last file lexicographically in a given path.
-  # This will find the latest chronologically MINOS run output in this path. 
-  files = Sys.glob(path)
-  files = sort(files)
-  file = tail(files,1)[1]
-  return(file)
-}
-
-get_geojson_file_name <- function(mode, intervention, region, year) {
-  geojson_file_source <- paste0("output", "/", mode, "/", intervention, "/")
-  geojson_file_extension <- paste0(region, "_", "nanmean", "_", "SF_12", "_", year, ".geojson")
-  out.files <- list.files(geojson_file_source)
-  
-  if(length(out.files) == 1) {
-    geojson_file_name <- paste0(dirname(geojson_file_source), out.files[1], '/', geojson_file_source)
-  }
-  else if(length(out.files) > 1) {
-    out.files.date <- as.POSIXlt(out.files, format='%Y_%m_%d_%H_%M_%S')
-    max.date <- max(out.files.date)
-    
-    # Collecting these objects here as they have to be formatted
-    yr <- max.date$year + 1900 # year is years since 1900
-    month <- formatC(max.date$mon + 1, width=2, flag='0') # months are zero indexed (WHY??)
-    day <- formatC(max.date$mday, width=2, flag='0')
-    hour <- formatC(max.date$hour, width=2, flag='0')
-    min <- formatC(max.date$min, width=2, flag='0')
-    sec <- formatC(max.date$sec, width=2, flag='0')
-    # generate the string runtime directory so we can add to the path
-    str.date <- paste0(yr, '_',
-                       month, '_',
-                       day, '_',
-                       hour, '_',
-                       min, '_',
-                       sec)
-    geojson_file_name <- paste0(geojson_file_source, str.date, '/', geojson_file_extension)
-  }
-  return (geojson_file_name)
-}
-
-
-violin_plot <- function(data, v)
-{
[…]

### 2023-07-10 minos/testing/auditc.Rmd
Added script for testing auditc variable

---
title: "AUDITC Testing"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

Source utils for some functions.

```{r}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

## Data

```{r}
# Read raw datafiles in
comp.files <- list.files(here::here('data', 'composite_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
comp.dat <- do.call(rbind, lapply(comp.files, read.csv))

final.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
final.dat <- do.call(rbind, lapply(final.files, read.csv)) 
```

# Analysis

```{r}
comp <- comp.dat %>%
  dplyr::select(pidp, time, auditc) %>%
  dplyr::filter(time >= 2015) %>%
  dplyr::filter(time != 2016, time != 2018) %>%
  group_by(time, auditc) %>%
  count()

comp$auditc <- as.factor(comp$auditc)

ggplot(comp, aes(x = time, y = n, group = auditc, color = auditc)) +
  geom_line() +
  labs(title = 'AUDITC - Corrected Data') +
  ylab('Counts')
```

```{r}
final <- final.dat %>%
  dplyr::select(pidp, time, auditc) %>%
  dplyr::filter(time >= 2015) %>%
  dplyr::filter(time != 2016, time != 2018) %>%
  group_by(time, auditc) %>%
  count()

final$auditc <- as.factor(final$auditc)

ggplot(final, aes(x = time, y = n, group = auditc, color = auditc)) +
  geom_line() +
  labs(title = 'AUDITC - Final Data') +
  ylab('Counts')
```

```{r}

```

### 2023-07-11 minos/testing/auditc.Rmd
Added alcohol to the physical wellbeing model and module, and updated handovers and cross_validation with more plots

@@
 final.dat <- do.call(rbind, lapply(final.files, read.csv))
+
+cv.files <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch1'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+cv.dat <- do.call(rbind, lapply(final.files, read.csv))
 ```
@@
 ```{r}
+cv <- cv.dat %>%
+  dplyr::select(pidp, time, auditc) %>%
+  dplyr::filter(time >= 2015) %>%
+  dplyr::filter(time != 2016, time != 2018) %>%
+  group_by(time, auditc) %>%
+  count()
+
+cv$auditc <- as.factor(cv$auditc)
+
+ggplot(cv, aes(x = time, y = n, group = auditc, color = auditc)) +
+  geom_line() +
+  labs(title = 'AUDITC - Cross-Validation Batch 1') +
+  ylab('Counts')
+```
+
+```{r}
 

### 2023-07-11 minos/validation/cross_validation_default.Rmd
Added a section for alcohol to both handovers and cross_validation_default notebooks
Added alcohol to the physical wellbeing model and module, and updated handovers and cross_validation with more plots

@@
 
-# SF_12
+# SF_12_MCS
 
 ```{r}
-cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12')
-multi_year_boxplots(raw, cv, 'SF_12')
-snapshot_OP_plots(raw, cv, 'SF_12', target.years = c(2014, 2016, 2018, 2020))
-q_q_comparison(raw, cv, 'SF_12')
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12_MCS')
+multi_year_boxplots(raw, cv, 'SF_12_MCS')
+snapshot_OP_plots(raw, cv, 'SF_12_MCS', target.years = c(2014, 2016, 2018, 2020))
+q_q_comparison(raw, cv, 'SF_12_MCS')
 ```
@@
                                  predicted = cv, 
-                                 var = 'SF_12', 
+                                 var = 'SF_12_MCS', 
                                  target.year = 2014)
@@
                                  predicted = cv, 
-                                 var = 'SF_12', 
+                                 var = 'SF_12_MCS', 
                                  target.year = 2016)
@@
                                  predicted = cv, 
-                                 var = 'SF_12', 
+                                 var = 'SF_12_MCS', 
                                  target.year = 2018)
@@
                                  predicted = cv, 
-                                 var = 'SF_12', 
+                                 var = 'SF_12_MCS', 
+                                 target.year = 2020)
+print(sf12.20)
+rm(sf12.14, sf12.16, sf12.18, sf12.20)
+```
+
+# SF_12_PCS
+
+```{r}
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12_PCS')
+multi_year_boxplots(raw, cv, 'SF_12_PCS')
+snapshot_OP_plots(raw, cv, 'SF_12_PCS', target.years = c(2014, 2016, 2018, 2020))
+q_q_comparison(raw, cv, 'SF_12_PCS')
+```
+```{r}
+sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12_PCS', 
+                                 target.year = 2014)
+print(sf12.14)
+```
+```{r}
+sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12_PCS', 
+                                 target.year = 2016)
+print(sf12.16)
+```
+```{r}
+sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12_PCS', 
+                                 target.year = 2018)
+print(sf12.18)
+```
+```{r}
+sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12_PCS', 
                                  target.year = 2020)
@@
 
+# Alcohol
+
+```{r}
+alc.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'auditc')
+
+cv_ordinal_plots(pivoted.df = alc.pivoted, 
+                 var = 'auditc',
+                 save = FALSE)
+rm(alc.pivoted)
+```
+
 # SECONDARY VARS

### 2023-07-12 minos/validation/cross_validation.Rmd

--- 2023-06-22 minos/validation/cross_validation.Rmd
@@
 title: "Cross Validation Analysis"
-output: html_notebook
+output:
+  html_document:
+    df_print: paged
 ---
@@
 
-#workingDir <- "/home/luke/Documents/WORK/MINOS/"
-workingDir <- normalizePath('../')
+workingDir <- here::here()
 knitr::opts_knit$set(root.dir = workingDir)
@@
 source(here::here('minos', 'utils_datain.R'))
-source(here::here('minos', 'utils_validation_vis.R'))
 source(here::here('minos', 'validation', 'utils.r'))
@@
 # cross validation simulation output
-#out.path <- 'Minos/output/cross_validation/'
-out.path <- here::here('output', 'cross_validation_default/')
-cv <- read_singular_local_out(out.path, 'baseline')
+out.path <- here::here("output", "cross_validation")
+cv <- read_singular_local_out(out.path, '/baseline')
 
 # cv simulation pop (not used for transitions)
-cv.simul.files <- list.files(here::here('data', 'final_US', 'cross_validation', 'simulation'),
+cv.simul.files <- list.files(here::here('data', 'final_US', 'cross_validation', 'simulation/'),
                              pattern = '[0-9]{4}_US_cohort.csv',

### 2023-07-12 minos/validation/handovers.Rmd

@@
 require(ggplot2)
+require(ggridges) # for densities over time plots. 
 require(knitr)
@@
 knitr::opts_knit$set(root.dir = workingDir)
-knitr::opts_chunk$set(
-  warning = FALSE,
-  message = FALSE
-)
 rm(workingDir)
@@
 start.year <- 2020
-save.path <- here::here("plots", "handovers", 'default')
-create.if.not.exists(save.path)
 
@@
 
-if (shall.we.save) {
 ggsave(filename = 'hh_income_wav1.png',
@@
 spaghetti_plot(income.spag, 'hh_income',
-               save = shall.we.save,
+               save = TRUE,
                save.path = save.path)
+density_ridges(income.spag, 'hh_income',
+               save=TRUE, 
+               save.path=save.path)
 
@@
 
-if (shall.we.save) {
 ggsave(filename = 'SF12_wav1.png',
@@
 spaghetti_plot(sf12.spag, 'SF_12',
-               save = shall.we.save,
+               save = TRUE,
+               save.path = save.path)
+
+density_ridges(sf12.spag, "SF_12", 
+               save = T, 
                save.path = save.path)
@@
 rm(raw.sf12, base.sf12, sf12.spag)
-```
-
-## Financial Situation
-
-```{r}
-raw.financial_situation <- raw.dat %>% 
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.financial_situation <- base.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-financial_situation <- rbind(raw.financial_situation, base.financial_situation)
-financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
-
-# Now plot
-ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-financial_situation.norm <- financial_situation %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial situation') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'financial_situation.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
 ```
@@
 
-if (shall.we.save) {
 ggsave(filename = 'housing_quality.png',
@@
        path = save.path)
-}
 
 rm(raw.housing, base.housing, housing, housing.norm)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, housing_quality)
-base.s <- base.dat %>%
-  select(pidp, age, time, housing_quality)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'housing_quality',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
 ```
@@
 
-if (shall.we.save) {
 ggsave(filename = 'neighbourhood_safety.png',
@@
        path = save.path)
-}
 
 #rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, neighbourhood_safety)
-base.s <- base.dat %>%
-  select(pidp, age, time, neighbourhood_safety)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'neighbourhood_safety',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
 ```
@@
 
-if (shall.we.save) {
 ggsave(filename = 'loneliness.png',
@@
        path = save.path)
-}
 
 rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, loneliness)
-base.s <- base.dat %>%
-  select(pidp, age, time, loneliness)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'loneliness',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
 ```
@@
 
-if (shall.we.save) {
 ggsave(filename = 'nutrition_quality_wav1.png',
@@
     nutrition_quality2)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, nutrition_quality)
-base.s <- base.dat %>%
-  select(pidp, age, time, nutrition_quality)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nutrition_quality',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
 ```
@@
 
-if (shall.we.save) {
 ggsave(filename = 'physical_health_wav1.png',
@@
 
-### Spaghetti
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, phealth)
-base.s <- base.dat %>%
-  select(pidp, age, time, phealth)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'phealth',
-             save = shall.we.save,
-             save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## Education
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Education State'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'education_state.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'education_state')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'education_state',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, education_state)
-base.s <- base.dat %>%
-  select(pidp, age, time, education_state)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'education_state',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
 ```{r}

### 2023-07-12 minos/outcomes/make_lineplots_simd_deciles.Rmd
adding SIMD deciles lineplot

--- 2023-07-07 minos/outcomes/make_lineplots_all.Rmd
@@
+---
+title: "make_lineplots_simd_deciles"
+author: "RC"
+date: "2023-07-12"
+output: html_document
+---
 ---
@@
 
-```{python all_child_uplift_SF_12, fig.path="plots/"}
+```{python simd deciles, fig.path="plots/"}
 # packages need installing in R using py_install("package"). honestly this seems not worth it..
@@
 # define test parameters and run.
-directories = "baseline,hhIncomeChildUplift"
-tags = "Baseline,All Child Uplift"
-subset_function_strings = "who_kids,who_boosted"
-prefix="baseline_all_child_uplift"
-config_mode = "default_config"
-lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
+directories = "baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline"
+tags = "National Average,First,Second,Third,Fourth,Fifth,Sixth,Seventh,Eighth,Ninth,Tenth"
+subset_function_strings = "who_alive,who_first_decile,who_second_decile,who_third_decile,who_fourth_decile,who_fifth_decile,who_sixth_decile,who_seventh_decile,who_eigth_decile,who_ninth_decile,who_tenth_decile"
+prefix="simd_deciles"
+config_mode = "glasgow_scaled"
+lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="National Average", v="SF_12", method='nanmean')
 ```
@@
 ```
-
-# Baseline vs Poverty Child Uplift
-
-```{python poverty_line_child_uplift_SF_12, fig.path="plots/"}
-# packages need installing in R using py_install("package"). honestly this seems not worth it..
-from minos.outcomes.make_lineplots import main as lineplot_main
-# define test parameters and run.
-directories = "baseline,hhIncomePovertyLineChildUplift"
-tags = "Baseline,Poverty Line Child Uplift"
-subset_function_strings = "who_below_poverty_line_and_kids,who_boosted"
-prefix="baseline_poverty_child_uplift"
-config_mode = "default_config"
-lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
-```
-
-```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-knitr::include_graphics(here::here("plots", "baseline_poverty_child_uplift_SF_12_aggs_by_year.pdf"), error=FALSE)
-```
-
-# Baseline vs Living Wage
-
-```{python living_wage_SF_12, fig.path="plots/"}
-# packages need installing in R using py_install("package"). honestly this seems not worth it..
-from minos.outcomes.make_lineplots import main as lineplot_main
-# define test parameters and run.
-directories = "baseline,livingWageIntervention"
-tags = "Baseline,Living Wage Intervention"
-subset_function_strings = "who_below_living_wage,who_boosted"
-prefix="baseline_living_wage"
-config_mode = "default_config"
-lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
-```
-
-```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-knitr::include_graphics(here::here("plots", "baseline_living_wage_SF_12_aggs_by_year.pdf"), error=FALSE)
-```
-
-# Baseline vs Energy Downlift
-
-```{python energy_downlift_SF_12, fig.path="plots/"}
-# packages need installing in R using py_install("package"). honestly this seems not worth it..
-from minos.outcomes.make_lineplots import main as lineplot_main
-# define test parameters and run.
-directories = "baseline,energyDownlift"
-tags = "Baseline,Energy Downlift"
-subset_function_strings = "who_uses_energy,who_boosted"
-prefix="baseline_energy_downlift"
-config_mode = "default_config"
-lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
-```
-
-```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-knitr::include_graphics(here::here("plots", "baseline_energy_downlift_SF_12_aggs_by_year.pdf"), error=FALSE)
-```
-
-# All Five combined
-
-```{python all_five_SF_12, fig.path="plots/"}
-# packages need installing in R using py_install("package"). honestly this seems not worth it..
-from minos.outcomes.make_lineplots import main as lineplot_main
-# define test parameters and run.
-directories = "baseline,hhIncomeChildUplift,hhIncomePovertyLineChildUplift,livingWageIntervention,energyDownlift"
-tags = "Baseline,All Child Uplift,Poverty Line Child Uplift,Living Wage Intervention,Energy Downlift"
-subset_function_strings = "who_alive,who_boosted,who_boosted,who_boosted,who_boosted"
-prefix="all_five_combined"
-config_mode = "default_config"
-lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
-```
-
-```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-knitr::include_graphics(here::here("plots", "all_five_combined_SF_12_aggs_by_year.pdf"), error=FALSE)
-```

### 2023-07-12 minos/outcomes/make_lineplots_simd_deciles.Rmd
trying much smaller number of files for sanity

@@
 # define test parameters and run.
-directories = "baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline"
-tags = "National Average,First,Second,Third,Fourth,Fifth,Sixth,Seventh,Eighth,Ninth,Tenth"
-subset_function_strings = "who_alive,who_first_decile,who_second_decile,who_third_decile,who_fourth_decile,who_fifth_decile,who_sixth_decile,who_seventh_decile,who_eigth_decile,who_ninth_decile,who_tenth_decile"
+directories = "baseline,baseline"#,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline"
+tags = "National Average,First"#,Second,Third,Fourth,Fifth,Sixth,Seventh,Eighth,Ninth,Tenth"
+subset_function_strings = "who_alive,who_first_decile"#,who_second_decile,who_third_decile,who_fourth_decile,who_fifth_decile,who_sixth_decile,who_seventh_decile,who_eigth_decile,who_ninth_decile,who_tenth_decile"
 prefix="simd_deciles"

### 2023-07-12 minos/outcomes/make_lineplots_simd_deciles.Rmd
stupid bugs again

--- 2023-07-12 minos/outcomes/make_lineplots_simd_deciles.Rmd
@@
 tags = "National Average,First,Second,Third,Fourth,Fifth,Sixth,Seventh,Eighth,Ninth,Tenth"
-subset_function_strings = "who_alive,who_first_decile,who_second_decile,who_third_decile,who_fourth_decile,who_fifth_decile,who_sixth_decile,who_seventh_decile,who_eigth_decile,who_ninth_decile,who_tenth_decile"
+subset_function_strings = "who_alive,who_first_simd_decile,who_second_simd_decile,who_third_simd_decile,who_fourth_simd_decile,who_fifth_simd_decile,who_sixth_simd_decile,who_seventh_simd_decile,who_eighth_simd_decile,who_ninth_simd_decile,who_tenth_simd_decile"
 prefix="simd_deciles"
@@
 ```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-knitr::include_graphics(here::here("plots", "baseline_all_child_uplift_SF_12_aggs_by_year.pdf"), error=FALSE)
+knitr::include_graphics(here::here("plots", "simd_deciles_SF_12_aggs_by_year.pdf"), error=FALSE)
 ```

### 2023-07-13 minos/validation/handovers.Rmd
Revert "Merge branch '249_gee' of https://github.com/Leeds-MRG/Minos into 249_gee"
This reverts commit 9b14862ee861227563f95cd9aa374a570765f848, reversing
changes made to 9b764bff3730cdcdaee92edd8f337762bb80f60b.

--- 2023-07-11 minos/validation/handovers.Rmd
@@
                save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(sf12.spag, "SF_12", 
+               save = T, 
                save.path = save.path)

### 2023-07-13 minos/data_generation/generate_repl_pop.py

@@ -173,9 +173,9 @@ def generate_replenishing(projections, scotland_mode, cross_validation):
         output_dir = 'data/replenishing/scotland'
         transition_dir = 'data/transitions/scotland'
     if cross_validation:
-        data_source = 'final_US/cross_validation/simulation'
+        data_source = 'final_US/cross_validation/batch1'
         output_dir = 'data/replenishing/cross_validation'
-        transition_dir = 'data/transitions/cross_validation'
+        transition_dir = 'data/transitions/cross_validation/version1'
 
     # first collect and load the datafile for 2018
     file_name = f"data/{data_source}/2020_US_cohort.csv"

### 2023-07-13 minos/modules/mental_wellbeing.py

@@ -59,7 +59,7 @@ class MWB(Base):
                         'ethnicity',
                         'age',
                         'education_state',
-                        'labour_state',
+                        'S7_labour_state',
                         'job_sec',
                         'hh_income',
                         'SF_12',
@@ -109,6 +109,8 @@ class MWB(Base):
         event : vivarium.population.PopulationEvent
             The event time_step that called this function.
         """
+
+        logging.info("MENTAL WELLBEING (SF12 MCS)")
 
         self.year = event.time.year
 

### 2023-07-13 minos/validation/handovers.Rmd
Added active var to handovers and cross-validation

--- 2023-07-11 minos/validation/handovers.Rmd
@@
 ```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Education State'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'education_state.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
+handover_ordinal(raw.dat, base.dat, var = 'education_state', save = shall.we.save)
 ```
@@
 
+## Alcohol (AUDITC)
+
 ```{r}
+handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
+```
 
+## Physical Activity
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
 ```

### 2023-07-13 docsrc/documentation/notebooks/tobacco.Rmd
Started a notebook for physical activity documentation

@@
 title: "Tobacco"
-output: html_document
-bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
-  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
+output:
+  pdf_document: default
+  html_document: default
+bibliography: docsrc/refs.bib
 ---
 
+```{r setup, include=FALSE}
+knitr::opts_knit$set(root.dir= "../minos")
+```
 ## Tobacco
@@
 
-```{r setup, include=FALSE}
-source('sphinx_notebook_utils.R')
+```{r load_data, include=FALSE}
+source('docsrc/documentation/notebooks/sphinx_notebook_utils.R')
 ```
@@
 ```{r tobacco_data}
-counts_density('ncigs')
+counts_density("data/transitions/ncigs/zip/ncigs_2018_2019.rds", "y")
 ```
@@
 
-age. persons age. generally older people and very young smoke. 
-SF_12. wellbeing estimates number of cigarettes smoked.
-labour_state. whether a person is employed or not.
-ethnicity. certain ethnicities more likely to smoke cigarettes. 
-education_state. highest qualification.
-job_sec job quality
-hh_income household income
-ncigs previous number consumed.
+- age. persons age. generally older people and very young smoke. 
+- SF_12. wellbeing estimates number of cigarettes smoked.
+- labour_state. whether a person is employed or not.
+- ethnicity. certain ethnicities more likely to smoke cigarettes. 
+- education_state. highest qualification.
+- job_sec job quality
+- hh_income household income
+- ncigs previous number consumed.
 
@@
 
-ethnicity. certain ethnicities more likely to smoke cigarettes. 
-labour_state. whether a person is employed or not.
-age
-SF_12. wellbeing estimates number of cigarettes smoked.
-ncigs previous number consumed.
+- ethnicity. certain ethnicities more likely to smoke cigarettes. 
+- labour_state. whether a person is employed or not.
+- age
+- SF_12. wellbeing estimates number of cigarettes smoked.
+- ncigs previous number consumed.
 
@@
 Almost all coefficients significant.
-Particularly prevous consumption of cigarettes.
+Particularly previous consumption of cigarettes.
 Good estimation of the number of non-smokers in the population at around 55\%.
@@
 options(width=120)
-zip_output("../../../data/transitions/test/tobacco_zip_2018_2019.rds")
-zip_density("../../../data/transitions/test/tobacco_zip_2018_2019.rds", 'ncigs_next')
+zip_output("data/transitions/ncigs/zip/ncigs_2018_2019.rds")
+zip_density("data/transitions/ncigs/zip/ncigs_2018_2019.rds", 'y')
 ```

### 2023-07-15 minos/validation/cross_validation_default.Rmd
Added active var to handovers and cross-validation
tuning for final paper2 handovers and crossval

--- 2023-07-05 minos/validation/cross_validation_default.Rmd
@@
 #cv <- cv.dat %>% filter(pidp %in% both.pidps$pidp)
+# getting only people who were in 2014 population. 
+who_2014_pidps <- raw.dat %>% filter(time %in% c(2014) & hh_income<10000) %>% select(pidp) %>% unique()
 raw <- raw.dat %>% filter(time %in% cv.years)
+raw <- raw %>% filter (pidp %in% who_2014_pidps$pidp)
 

### 2023-07-15 minos/validation/handovers.Rmd
tuning for final paper2 handovers and crossval

@@
 ```{r}
-handover_continuous(raw.dat, base.dat, var = 'hh_income')
+# first figure out how to plot final_US
+# start with hh_income
+
+handover_boxplots(raw.dat, base.dat, 'hh_income')
+handover_lineplots(raw.dat, base.dat, "hh_income")
+
+# raw.income2 <- raw.dat %>% 
+#               dplyr::select(pidp, time, hh_income) %>%
+#               filter(pidp %in% raw.income.wave1)
+# 
+# base.income <-  base.income2 <- base.dat %>%
+#                                 dplyr::select(pidp, time, hh_income) %>%
+#                                 filter(pidp %in% raw.income.wave1)
+# 
+# handover_lineplots(raw.d)
+# ## Try a version where final_US is limited to only those present from wave 1 
+# # onwards because the sample refreshments are messing with the plot
+# raw.income.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+# 
+# raw.income2 <- raw.dat %>% 
+#   dplyr::select(pidp, time, hh_income) %>%
+#   filter(pidp %in% raw.income.wave1) %>%
+#   group_by(time) %>%
+#   summarise(income = mean(hh_income, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.income2 <- base.dat %>%
+#   dplyr::select(pidp, time, hh_income) %>%
+#   filter(pidp %in% raw.income.wave1) %>%
+#   group_by(time) %>%
+#   summarise(income = mean(hh_income, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# income2 <- rbind(raw.income2, base.income2)
+# 
+# # Now plot
+# ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
+#   geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Household Income') +
+#   xlab('Year') +
+#   ylab('Income')
+# 
+# if (shall.we.save) {
+#   ggsave(filename = 'hh_income_wav1.png',
+#        plot = last_plot(),
+#        path = save.path)
+# }
+# 
+# raw.income.check <- raw.dat %>% 
+#   dplyr::select(pidp, time, hh_income) %>%
+#   filter(pidp %in% raw.income.wave1)
+# 
+# base.income.check <- base.dat %>%
+#   dplyr::select(pidp, time, hh_income) %>%
+#   filter(pidp %in% raw.income.wave1)
+# 
+# rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
+#    raw.income.check, base.income.check)
 ```
@@
 
-## SF_12_MCS
+## SF12
 
 ```{r}
-handover_continuous(raw.dat, base.dat, var = 'SF_12_MCS')
+# sf12 boxplot handovers
+handover_boxplots(raw.dat, base.dat, 'SF_12')
+handover_lineplots(raw.dat, base.dat, "SF_12")
+# 
+# raw.sf12 <- raw.dat %>% 
+#   dplyr::select(pidp, time, SF_12) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.sf12 <- base.dat %>%
+#   dplyr::select(pidp, time, SF_12) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# # merge before plot
+# sf12 <- rbind(raw.sf12, base.sf12)
+# 
+# # Now plot
+# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+#   geom_smooth() +
+#   #geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
+#   xlab('Year') +
+#   ylab('SF12')
+# 
+# ## Try a version where final_US is limited to only those present from wave 1 
+# # onwards because the sample refreshments are messing with the plot
+# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+# 
+# raw.sf12.2 <- raw.dat %>% 
+#   dplyr::select(pidp, time, SF_12) %>%
+#   filter(pidp %in% raw.sf12.wave1) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.sf12.2 <- base.dat %>%
+#   dplyr::select(pidp, time, SF_12) %>%
+#   filter(pidp %in% raw.sf12.wave1) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
+# 
+# # Now plot
+# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+#   geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
+#   xlab('Year') +
+#   ylab('SF12')
+# 
+# if (shall.we.save) {
+#   ggsave(filename = 'SF12_wav1.png',
+#        plot = last_plot(),
+#        path = save.path)
+# }
+# 
+# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
 ```
@@
 ```{r}
-raw.sf12.m <- raw.dat %>%
-  select(pidp, age, time, SF_12_MCS)
-base.sf12.m <- base.dat %>%
-  select(pidp, age, time, SF_12_MCS)
+raw.sf12 <- raw.dat %>%
+  select(pidp, age, time, SF_12)
+base.sf12 <- base.dat %>%
+  select(pidp, age, time, SF_12)
 
-sf12.m.spag <- rbind(raw.sf12.m, base.sf12.m)
+sf12.spag <- rbind(raw.sf12, base.sf12)
 
-spaghetti_plot(sf12.m.spag, 'SF_12_MCS',
+spaghetti_plot(sf12.spag, 'SF_12',
                save = shall.we.save,
@@
 
-rm(raw.sf12.m, base.sf12.m, sf12.m.spag)
+density_ridges(sf12.spag, "SF_12", 
+               save = T, 
+               save.path = save.path)
+
+rm(raw.sf12, base.sf12, sf12.spag)
 ```
 
-## SF_12_PCS
+<!-- ## Financial Situation -->
 
-```{r}
-handover_continuous(raw.dat, base.dat, var = 'SF_12_PCS')
-```
+<!-- ```{r} -->
+<!-- raw.financial_situation <- raw.dat %>%  -->
+<!--   dplyr::select(pidp, time, financial_situation) %>% -->
+<!--   group_by(time, financial_situation) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'final_US') -->
 
-### Spaghetti
+<!-- base.financial_situation <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, financial_situation) %>% -->
+<!--   group_by(time, financial_situation) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'baseline_output') -->
 
-```{r}
-raw.sf12.p <- raw.dat %>%
-  select(pidp, age, time, SF_12_PCS)
-base.sf12.p <- base.dat %>%
-  select(pidp, age, time, SF_12_PCS)
+<!-- # merge before plot -->
+<!-- financial_situation <- rbind(raw.financial_situation, base.financial_situation) -->
+<!-- financial_situation$financial_situation <- as.factor(financial_situation$financial_situation) -->
 
-sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)
+<!-- # Now plot -->
+<!-- ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Financial Situation', subtitle = 'Counts by Level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
 
-spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
-               save = shall.we.save,
-               save.path = save.path)
+<!-- financial_situation.norm <- financial_situation %>% -->
+<!--   group_by(time) %>% -->
+<!--   mutate(total = sum(n)) %>% -->
+<!--   mutate(prct = (n / total)) -->
 
-rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
-```
+<!-- ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Financial situation') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
 
-## Financial Situation
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'financial_situation.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
+<!-- } -->
 
-```{r}
-handover_ordinal(raw.dat, base.dat, var = 'financial_situation', save = shall.we.save)
-```
+<!-- rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm) -->
+<!-- ``` -->
 
-## Housing Quality
+<!-- ## Housing Quality -->
 
-```{r}
-handover_ordinal(raw.dat, base.dat, var = 'housing_quality', save = shall.we.save)
-```
+<!-- ```{r} -->
+<!-- raw.housing <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, housing_quality) %>% -->
+<!--   group_by(time, housing_quality) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'final_US') -->
 
-### Spaghetti
+<!-- base.housing <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, housing_quality) %>% -->
+<!--   group_by(time, housing_quality) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'baseline_output') -->
 
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, housing_quality)
-base.s <- base.dat %>%
-  select(pidp, age, time, housing_quality)
+<!-- # merge before plot -->
+<!-- housing <- rbind(raw.housing, base.housing) -->
+<!-- housing$housing_quality <- as.factor(housing$housing_quality) -->
 
-spag <- rbind(raw.s, base.s)
+<!-- # Now plot -->
+<!-- ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Housing Quality', subtitle = 'Counts by Level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
 
-spaghetti_plot(spag, 'housing_quality',
-               save = shall.we.save,
-               save.path = save.path)
+<!-- housing.norm <- housing %>% -->
+<!--   group_by(time) %>% -->
+<!--   mutate(total = sum(n)) %>% -->
+<!--   mutate(prct = (n / total)) -->
 
-rm(raw.s, base.s, spag)
-```
+<!-- ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Housing Quality') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
 
-## Neighbourhood Safety
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'housing_quality.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
+<!-- } -->
 
-```{r}
-handover_ordinal(raw.dat, base.dat, var = 'neighbourhood_safety', save = shall.we.save)
-```
+<!-- rm(raw.housing, base.housing, housing, housing.norm) -->
+<!-- ``` -->
 
-### Spaghetti
+<!-- ### Spaghetti -->
 
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, neighbourhood_safety)
-base.s <- base.dat %>%
-  select(pidp, age, time, neighbourhood_safety)
+<!-- ```{r} -->
+<!-- raw.s <- raw.dat %>% -->
+<!--   select(pidp, age, time, housing_quality) -->
+<!-- base.s <- base.dat %>% -->
+<!--   select(pidp, age, time, housing_quality) -->
 
-spag <- rbind(raw.s, base.s)
+<!-- spag <- rbind(raw.s, base.s) -->
 
-spaghetti_plot(spag, 'neighbourhood_safety',
-               save = shall.we.save,
-               save.path = save.path)
+<!-- spaghetti_plot(spag, 'housing_quality', -->
+<!--                save = shall.we.save, -->
+<!--                save.path = save.path) -->
 
-rm(raw.s, base.s, spag)
-```
+<!-- rm(raw.s, base.s, spag) -->
+<!-- ``` -->
 
-## Loneliness
+<!-- ## Neighbourhood Safety -->
 
-```{r}
-handover_ordinal(raw.dat, base.dat, var = 'loneliness', save = shall.we.save)
-```
+<!-- ```{r} -->
+<!-- raw.neighbour <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, neighbourhood_safety) %>% -->
+<!--   group_by(time, neighbourhood_safety) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'final_US') -->
 
-### Spaghetti
+<!-- base.neighbour <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, neighbourhood_safety) %>% -->
+<!--   group_by(time, neighbourhood_safety) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'baseline_output') -->
 
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, loneliness)
-base.s <- base.dat %>%
-  select(pidp, age, time, loneliness)
+<!-- # merge before plot -->
+<!-- neighbour <- rbind(raw.neighbour, base.neighbour) -->
+<!-- neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety) -->
 
-spag <- rbind(raw.s, base.s)
+<!-- # Now plot -->
+<!-- ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
 
-spaghetti_plot(spag, 'loneliness',
-               save = shall.we.save,
-               save.path = save.path)
+<!-- neighbour.norm <- neighbour %>% -->
+<!--   group_by(time) %>% -->
+<!--   filter(neighbourhood_safety != -9) %>% -->
+<!--   mutate(total = sum(n)) %>% -->
+<!--   mutate(prct = (n / total)) -->
 
-rm(raw.s, base.s, spag)
-```
+<!-- ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Neighbourhood Safety') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
+
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'neighbourhood_safety.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
+<!-- } -->
+
+<!-- #rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm) -->
+<!-- ``` -->
+
+<!-- ### Spaghetti -->
+
+<!-- ```{r} -->
+<!-- raw.s <- raw.dat %>% -->
+<!--   select(pidp, age, time, neighbourhood_safety) -->
+<!-- base.s <- base.dat %>% -->
+<!--   select(pidp, age, time, neighbourhood_safety) -->
+
+<!-- spag <- rbind(raw.s, base.s) -->
+
+<!-- spaghetti_plot(spag, 'neighbourhood_safety', -->
+<!--                save = shall.we.save, -->
+<!--                save.path = save.path) -->
+
+<!-- rm(raw.s, base.s, spag) -->
+<!-- ``` -->
+
+<!-- ## Loneliness -->
+
+<!-- ```{r} -->
+<!-- raw.loneliness <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, loneliness) %>% -->
+<!--   group_by(time, loneliness) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'final_US') -->
+
+<!-- base.loneliness <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, loneliness) %>% -->
+<!--   group_by(time, loneliness) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'baseline_output') -->
+
+<!-- # merge before plot -->
+<!-- loneliness <- rbind(raw.loneliness, base.loneliness) -->
+<!-- loneliness$loneliness <- as.factor(loneliness$loneliness) -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Loneliness', subtitle = 'Counts by level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
+
+<!-- loneliness.norm <- loneliness %>% -->
+<!--   group_by(time) %>% -->
+<!--   filter(loneliness != -9) %>% -->
+<!--   mutate(total = sum(n)) %>% -->
+<!--   mutate(prct = (n / total)) -->
+
+<!-- ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Loneliness') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
+
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'loneliness.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
+<!-- } -->
+
+<!-- rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm) -->
+<!-- ``` -->
+
+<!-- ### Spaghetti -->
+
+<!-- ```{r} -->
+<!-- raw.s <- raw.dat %>% -->
+<!--   select(pidp, age, time, loneliness) -->
+<!-- base.s <- base.dat %>% -->
+<!--   select(pidp, age, time, loneliness) -->
+
+<!-- spag <- rbind(raw.s, base.s) -->
+
+<!-- spaghetti_plot(spag, 'loneliness', -->
+<!--                save = shall.we.save, -->
+<!--                save.path = save.path) -->
+
+<!-- rm(raw.s, base.s, spag) -->
+<!-- ``` -->
 
@@
 ```{r}
-handover_continuous(raw.dat, base.dat, var = 'nutrition_quality')
+#  nutriton quality line/boxplots.
+handover_boxplots(raw.dat, base.dat, 'nutrition_quality')
+handover_lineplots(raw.dat, base.dat, 'nutrition_quality')
+
+# Try a version where final_US is limited to only those present from wave 1
+# onwards because the sample refreshments are messing with the plot
+# raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+# 
+# raw.nut2 <- raw.dat %>%
+#   dplyr::select(pidp, time, nutrition_quality) %>%
+#   filter(pidp %in% raw.wave1) %>%
+#   filter(nutrition_quality >= 0) %>%
+#   group_by(time) %>%
+#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.nut2 <- base.dat %>%
+#   dplyr::select(pidp, time, nutrition_quality) %>%
+#   filter(pidp %in% raw.wave1) %>%
+#   group_by(time) %>%
+#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# nutrition_quality2 <- rbind(raw.nut2, base.nut2)
+# 
+# # Now plot
+# ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
+#   geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Nutrition Quality') +
+#   xlab('Year') +
+#   ylab('Nutrition Quality')
+# 
+# if (shall.we.save) {
+#   ggsave(filename = 'nutrition_quality_wav1.png',
+#        plot = last_plot(),
+#        path = save.path)
+# }
+# 
+# rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2,
+#     nutrition_quality2)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
+raw.nut <- raw.dat %>%
   select(pidp, age, time, nutrition_quality)
-base.s <- base.dat %>%
+base.nut <- base.dat %>%
   select(pidp, age, time, nutrition_quality)
 
-spag <- rbind(raw.s, base.s)
+nut.spag <- rbind(raw.nut, base.nut)
 
-spaghetti_plot(spag, 'nutrition_quality',
+spaghetti_plot(nut.spag, 'nutrition_quality',
                save = shall.we.save,
@@
 
-rm(raw.s, base.s, spag)
+density_ridges(nut.spag, "nutrition_quality", 
+               save = T, 
+               save.path = save.path)
+
+rm(raw.nut, base.nut, nut.spag)
 ```
 
-## Physical Health
+<!-- ## Physical Health -->
 
-NOTE: At present, physical health is not predicted or transitioned.
+<!-- NOTE: At present, physical health is not predicted or transitioned. -->
 
-```{r}
-handover_continuous(raw.dat, base.dat, var = 'phealth')
-```
+<!-- ```{r} -->
+<!-- # first figure out how to plot final_US -->
+<!-- # start with hh_income -->
+<!-- raw.phealth <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'final_US') -->
 
-### Spaghetti
+<!-- base.phealth <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'baseline_output') -->
 
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, phealth)
-base.s <- base.dat %>%
-  select(pidp, age, time, phealth)
+<!-- # merge before plot -->
+<!-- phealth <- rbind(raw.phealth, base.phealth) -->
 
-spag <- rbind(raw.s, base.s)
+<!-- # Now plot -->
+<!-- ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Physical Health', subtitle = 'Full Sample') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Average') -->
 
-spaghetti_plot(spag, 'phealth',
-             save = shall.we.save,
-             save.path = save.path)
+<!-- ## Try a version where final_US is limited to only those present from wave 1 -->
+<!-- # onwards because the sample refreshments are messing with the plot -->
+<!-- raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009] -->
 
-rm(raw.s, base.s, spag)
-```
+<!-- raw.phealth2 <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   filter(pidp %in% raw.wave1) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'final_US') -->
 
-## Education
+<!-- base.phealth2 <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   filter(pidp %in% raw.wave1) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'baseline_output') -->
 
-```{r}
-handover_ordinal(raw.dat, base.dat, var = 'education_state', save = shall.we.save)
-```
+<!-- phealth2 <- rbind(raw.phealth2, base.phealth2) -->
 
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'education_state')
+<!-- # Now plot -->
+<!-- ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Physical Health') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Average') -->
 
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'education_state',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'physical_health_wav1.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
+<!-- } -->
 
-### Spaghetti
+<!-- #raw.phealth.check <- raw.dat %>% -->
+<!-- #  select(pidp, time, phealth) %>% -->
+<!-- #  filter(time > 2009) %>% -->
+<!-- #  filter(pidp %in% raw.wave1) -->
 
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, education_state)
-base.s <- base.dat %>%
-  select(pidp, age, time, education_state)
+<!-- #base.phealth.check <- base.dat %>% -->
+<!-- #  select(pidp, time, phealth) %>% -->
+<!-- #  filter(time > 2009) %>% -->
+<!-- #  filter(pidp %in% raw.wave1) -->
 
-spag <- rbind(raw.s, base.s)
+<!-- rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2) -->
+<!-- #rm(raw.phealth.check, base.phealth.check) -->
+<!-- ``` -->
 
-spaghetti_plot(spag, 'education_state',
-               save = shall.we.save,
-               save.path = save.path)
+<!-- ### Spaghetti -->
 
-rm(raw.s, base.s, spag)
-```
+<!-- ```{r} -->
+<!-- raw.s <- raw.dat %>% -->
+<!--   select(pidp, age, time, phealth) -->
+<!-- base.s <- base.dat %>% -->
+<!--   select(pidp, age, time, phealth) -->
 
-## Alcohol (AUDITC)
+<!-- spag <- rbind(raw.s, base.s) -->
 
-```{r}
-handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
-```
+<!-- spaghetti_plot(spag, 'phealth', -->
+<!--              save = shall.we.save, -->
+<!--              save.path = save.path) -->
 
-## Physical Activity
+<!-- rm(raw.s, base.s, spag) -->
+<!-- ``` -->
 
-```{r}
-handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
-```
+<!-- ## Education -->
+
+<!-- ```{r} -->
+<!-- prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state') -->
+
+<!-- var <- prepped.list$var -->
+<!-- norm <- prepped.list$norm -->
+
+<!-- tit <- 'Education State' -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = tit, subtitle = 'Counts by Level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
+
+<!-- ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = tit) + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
+
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'education_state.png', -->
+<!--          plot = last_plot(), -->
+<!--          path = save.path) -->
+<!-- } -->
+
+<!-- rm(prepped.list, var, norm, tit) -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- pivoted <- combine_and_pivot_long(df1 = base.dat,  -->
+<!--                                        df1.name = 'simulated',  -->
+<!--                                        df2 = raw.dat,  -->
+<!--                                        df2.name = 'raw',  -->
+<!--                                        var = 'education_state') -->
+
+<!-- cv_ordinal_plots(pivoted.df = pivoted,  -->
+<!--                  var = 'education_state', -->
+<!--                  save = shall.we.save, -->
+<!--                  save.path = save.path) -->
+<!-- ``` -->
+
+<!-- ### Spaghetti -->
+
+<!-- ```{r} -->
+<!-- raw.s <- raw.dat %>% -->
+<!--   select(pidp, age, time, education_state) -->
+<!-- base.s <- base.dat %>% -->
+<!--   select(pidp, age, time, education_state) -->
+
+<!-- spag <- rbind(raw.s, base.s) -->
+
+<!-- spaghetti_plot(spag, 'education_state', -->
+<!--                save = shall.we.save, -->
+<!--                save.path = save.path) -->
+
+<!-- rm(raw.s, base.s, spag) -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+
+<!-- ``` -->

### 2023-07-15 minos/modules/mental_wellbeing.py

@@ -401,7 +401,7 @@ class geeYJMWB(Base):
         newWaveMWB = self.calculate_mwb(pop)
         newWaveMWB = pd.DataFrame(newWaveMWB, columns=["SF_12"])
         newWaveMWB.index = pop.index # aligning index to vivarium builder dataframe. ensures assignment of new values to correct individuals.
-        newWaveMWB["SF_12"] -= 2
+        #newWaveMWB["SF_12"] -= 2
         newWaveMWB["SF_12"] = np.clip(newWaveMWB["SF_12"], 0, 100) # keep within [0, 100] bounds of SF12.
         #newWaveMWB.sort_index(inplace=True)
         print(np.mean(newWaveMWB["SF_12"]))
@@ -497,7 +497,6 @@ class lmmYJMWB(Base):
 
         #only need to load this once for now.
         #self.gee_transition_model = r_utils.load_transitions(f"SF_12/lmm/SF_12_LMM", self.rpy2_modules, path=self.transition_dir)
-        print(self.transition_dir)
         self.gee_transition_model = r_utils.load_transitions(f"SF_12/glmm/SF_12_GLMM", self.rpy2_modules, path=self.transition_dir)
 
     def on_initialize_simulants(self, pop_data):
@@ -536,10 +535,13 @@ class lmmYJMWB(Base):
         newWaveMWB = pd.DataFrame(columns=['SF_12'])
         newWaveMWB['SF_12'] = self.calculate_mwb(pop)
         newWaveMWB.index = pop.index
-        #newWaveMWB["SF_12"] -= 2
+        #newWaveMWB["SF_12"] += 2
+        #newWaveMWB["SF_12"] *= (10/np.std(newWaveMWB["SF_12"]))
+        #newWaveMWB["SF_12"] += (50 - np.mean(newWaveMWB["SF_12"]))
         newWaveMWB["SF_12"] = np.clip(newWaveMWB["SF_12"], 0, 100) # keep within [0, 100] bounds of SF12.
         # Update population with new SF12
         print(np.mean(newWaveMWB["SF_12"]))
+        print(np.std(newWaveMWB["SF_12"]))
         self.population_view.update(newWaveMWB[['SF_12']])
 
 
@@ -552,22 +554,13 @@ class lmmYJMWB(Base):
         Returns
         -------
         """
-        #self.update_history_dataframe(pop, self.year, lag=10)
-        # out_data = r_utils.predict_next_timestep_yj_gaussian_lmm(self.gee_transition_model,
[…]

### 2023-07-15 minos/transitions/estimate_transitions.R

@@ -106,7 +106,7 @@ run_yearly_models <- function(transitionDir_path,
     # crossval needs to start in 2010, whereas default model can have reduced timespan
     # avoid first year as data is weird and missing in a lot of cases
     if(mode == 'cross_validation') {
-      year.range <- seq(min(data$time) + 1, (max(data$time) - 1))
+      year.range <- seq(min(data$time) + 4, (min(data$time) + 6))
     } else {
       year.range <- seq(max(data$time) - 6, (max(data$time) - 1))
       #year.range <- seq(min(data$time), (max(data$time) - 1)) # fit full range for model of models testing purposes

### 2023-07-18 minos/validation/cross_validation_default.Rmd
Added some dependencies to Rmd files to make them work in console and Rstudio

--- 2023-07-05 minos/validation/cross_validation_default.Rmd
@@
 require(scales)
+require(dplyr)
+require(tidyr)
+require(purrr)
 
@@
 
+## Parity
+
 ```{r}
+cv.parity <- cv %>%
+  filter(sex == "Female")
 
+cv1.parity <- cv1 %>%
+  filter(sex == "Female")
+
+cv2.parity <- cv2 %>%
+  filter(sex == "Female")
+
+cv3.parity <- cv3 %>%
+  filter(sex == "Female")
+
+cv4.parity <- cv4 %>%
+  filter(sex == "Female")
+
+cv5.parity <- cv5 %>%
+  filter(sex == "Female")
+
+raw.parity <- raw %>%
+  filter(sex == "Female")
+
+cv.mean.plots(cv1.parity, cv2.parity, cv3.parity, cv4.parity, cv5.parity, raw.parity, 'nkids_ind')
+multi_year_boxplots(raw.parity, cv.parity, 'nkids_ind')
+q_q_comparison(raw.parity, cv.parity, 'nkids_ind')
 ```
+```{r}
+parity.pivoted <- combine_and_pivot_long(df1 = cv.parity,
+                                         df1.name = 'simulated',
+                                         df2 = raw.parity,
+                                         df2.name = 'raw',
+                                         var = 'nkids_ind')
+
+cv_ordinal_plots(pivoted.df = parity.pivoted, 
+                 var = 'nkids_ind',
+                 save = FALSE)
+
+rm(parity.pivoted)
+```

### 2023-07-18 minos/validation/handovers.Rmd
Added some dependencies to Rmd files to make them work in console and Rstudio

--- 2023-07-13 minos/validation/handovers.Rmd
@@
 require(ggplot2)
-require(ggridges) # for densities over time plots. 
 require(knitr)
 require(here)
+require(dplyr)
+require(tidyr)
+require(purrr)
 
@@
                save.path = save.path)
-density_ridges(income.spag, 'hh_income',
-               save=TRUE, 
-               save.path=save.path)
 
@@
                save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(sf12.spag, "SF_12", 
-               save = T, 
                save.path = save.path)
@@
 
+## Parity
+
 ```{r}
+base.parity <- base.dat %>%
+  filter(sex == "Female")
 
+raw.parity <- raw.dat %>%
+  filter(sex == "Female")
+
+prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Parity (total no. of children)'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'parity.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
 ```
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.parity,
+                                  df1.name = 'simulated', 
+                                  df2 = raw.parity, 
+                                  df2.name = 'raw', 
+                                  var = 'nkids_ind')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'nkids_ind',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.parity %>%
+  select(pidp, age, time, nkids_ind)
+base.s <- base.parity %>%
+  select(pidp, age, time, nkids_ind)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nkids_ind',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+```{r}
+raw.s <- raw.parity %>%
+  select(pidp, age, time, nkids_ind_raw)
+base.s <- base.parity %>%
+  select(pidp, age, time, nkids_ind_raw)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nkids_ind_raw',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```

### 2023-07-19 minos/validation/cross_validation_default.Rmd
fixing lineplot, suggested improvements to visualisation, tuning income and SF12 for paper

--- 2023-07-15 minos/validation/cross_validation_default.Rmd
@@
 # getting only people who were in 2014 population. 
-who_2014_pidps <- raw.dat %>% filter(time %in% c(2014) & hh_income<10000) %>% select(pidp) %>% unique()
+#who_2014_pidps <- raw.dat %>% filter(time %in% c(2014) & hh_income<10000) %>% select(pidp) %>% unique()
 raw <- raw.dat %>% filter(time %in% cv.years)
-raw <- raw %>% filter (pidp %in% who_2014_pidps$pidp)
+#raw <- raw %>% filter (pidp %in% who_2014_pidps$pidp)
 

### 2023-07-19 minos/validation/handovers.Rmd
fixing lineplot, suggested improvements to visualisation, tuning income and SF12 for paper

--- 2023-07-15 minos/validation/handovers.Rmd
@@
 require(here)
+require(gghighlight)
 
@@
 
-spaghetti_plot(income.spag, 'hh_income',
-               save = shall.we.save,
-               save.path = save.path)
 density_ridges(income.spag, 'hh_income',
@@
                save.path=save.path)
+
+pidp_sample <- sample(unique(income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
+income.spag.sample <- income.spag[which(income.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(income.spag.sample, 'hh_income',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(income.spag.sample, 'hh_income',
+               save = shall.we.save,
+               save.path = save.path)
 
@@
 
-spaghetti_plot(sf12.spag, 'SF_12',
+sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(sf12.spag.sample, 'SF_12',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
                save = shall.we.save,

### 2023-07-19 minos/modules/r_utils.py

@@ -8,6 +8,7 @@ import rpy2.robjects as ro
 from rpy2.robjects import pandas2ri, r
 from rpy2.robjects.conversion import localconverter
 from rpy2.robjects.vectors import FactorVector
+from rpy2.robjects import numpy2ri
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as pl
@@ -399,13 +400,9 @@ def predict_next_timestep_yj_gamma_glmm(model, rpy2_modules, current, dependent,
     bestNormalize = rpy2_modules['bestNormalize']
     lme4 = rpy2_modules["lme4"]
 
-    #current = current.drop([dependent, 'time'], axis=1)
-    #current["pidp"] = -current["pidp"]
-
     # Convert from pandas to R using package converter
     with localconverter(ro.default_converter + pandas2ri.converter):
         currentRDF = ro.conversion.py2rpy(current)
-
 
     # flip left skewed data to right skewed about its maximum.
     if reflect:
@@ -425,11 +422,20 @@ def predict_next_timestep_yj_gamma_glmm(model, rpy2_modules, current, dependent,
 
     prediction = prediction.ro + (min_value.ro - 0.001) # invert shift to strictly positive values.
 
-    if dependent == "SF_12" or dependent == 'nutrition_quality':
+    if dependent == 'nutrition_quality':
         prediction = prediction.ro + stats.rnorm(current.shape[0], 0, noise_std) # add gaussian noise.
-    elif dependent == "hh_income_new" and noise_std:
+    elif dependent == "SF_12" and noise_std:
         VGAM = rpy2_modules["VGAM"]
         prediction = prediction.ro + VGAM.rlaplace(current.shape[0], 0, noise_std) # add gaussian noise.
+        #prediction = prediction.ro + stats.rnorm(current.shape[0], 0, noise_std) # add gaussian noise.
+    elif (dependent == "hh_income_new") and noise_std:
+        #VGAM = rpy2_modules["VGAM"]
+        #prediction = prediction.ro + VGAM.rlaplace(current.shape[0], 0, noise_std) # add gaussian noise.
+        prediction = prediction.ro + stats.rnorm(current.shape[0], 0, noise_std) # add gaussian noise.
+        noise = np.clip(stats.rcauchy(current.shape[0], 0, 0.0015), -3, 4) #0.075
+        with localconverter(ro.default_converter + numpy2ri.converter):
+            Rnoise = ro.conversion.py2rpy(noise)
[…]

### 2023-07-19 minos/transitions/estimate_longitudinal_transitions.R

@@ -61,7 +61,7 @@ run_longitudinal_models <- function(transitionDir_path, transitionSourceDir_path
     if(mode == 'cross_validation') {
       year.range <- seq(min(data$time) , (max(data$time)))
     } else {
-      year.range <- seq(max(data$time) - 9, (max(data$time)))
+      year.range <- seq(max(data$time) - 5, (max(data$time)))
       #year.range <- seq(min(data$time), (max(data$time) - 1)) # fit full range for model of models testing purposes
     }
     
@@ -82,83 +82,90 @@ run_longitudinal_models <- function(transitionDir_path, transitionSourceDir_path
     #} else {
     #  use.weights <- TRUE
     #}
+    
     if (dependent == "SF_12") {
-      do.reflect = TRUE
+      do.reflect = TRUE # only SF12 continuous data is reflected to be left skewed. 
     }
     else {
       do.reflect=FALSE
     }
-    if (dependent == "nutrition_quality") {
-      do.yeo.johnson = F
+    
+    if (dependent == "SF_12" || dependent == "hh_income") {
+      do.yeo.johnson = T #
     }
     else {
-      do.yeo.johnson = T
+      do.yeo.johnson = F
     }
     
-    if (mod.type == "LMM_DIFF") {
-      temp.dependent <-  paste0(dependent, "_diff") # shift income to left to avoid negative values.
-      formula.string <- paste0(temp.dependent, " ~ ", independents)
-      form <- as.formula(formula.string)      
-    } else if (dependent == 'nutrition_quality' || (dependent == "hh_income" && mod.type=="GLMM")) {
-      temp.dependent <-  paste0(dependent, "_new") # shift income to left to avoid negative values.
-      formula.string <- paste0(temp.dependent, " ~ ", independents)
-      form <- as.formula(formula.string)      
-    } else if (mod.type == "ORDGEE") {
-      temp.dependent <- paste0("ordered(", dependent, ")") # make dependent variable into ordered factor.
-      formula.string <- paste0(temp.dependent, " ~ ", independents)
-      form <- as.formula(formula.string)      
-    } 
-    else if (mod.type == "CLMM") {
-      formula.string <- paste0(dependent, " ~ ", independents)
-      form <- as.formula(formula.string)      
-    } else {
-      formula.string <- paste0(dependent, " ~ ", independents)
-      form <- as.formula(formula.string)
-    }
+    # experimental ordinal long models. ignore. 
[…]

### 2023-07-20 minos/validation/cross_validation_S7.Rmd
Pointed handovers and cross-validation notebooks to the newly imputed data (going to revert this but just for testing)

@@
 # cv simulation batches
-cv.simul.files1 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch1'),
+cv.simul.files1 <- list.files(here::here('data', 'stock', 'cross_validation', 'batch1'),
                              pattern = '[0-9]{4}_US_cohort.csv',
@@
 raw1 <- do.call(rbind, lapply(cv.simul.files1, read.csv))
-cv.simul.files2 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch2'),
+cv.simul.files2 <- list.files(here::here('data', 'stock', 'cross_validation', 'batch2'),
                              pattern = '[0-9]{4}_US_cohort.csv',
@@
 raw2 <- do.call(rbind, lapply(cv.simul.files2, read.csv))
-cv.simul.files3 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch3'),
+cv.simul.files3 <- list.files(here::here('data', 'stock', 'cross_validation', 'batch3'),
                              pattern = '[0-9]{4}_US_cohort.csv',
@@
 raw3 <- do.call(rbind, lapply(cv.simul.files3, read.csv))
-cv.simul.files4 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch4'),
+cv.simul.files4 <- list.files(here::here('data', 'stock', 'cross_validation', 'batch4'),
                              pattern = '[0-9]{4}_US_cohort.csv',
@@
 raw4 <- do.call(rbind, lapply(cv.simul.files4, read.csv))
-cv.simul.files5 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch5'),
+cv.simul.files5 <- list.files(here::here('data', 'stock', 'cross_validation', 'batch5'),
                              pattern = '[0-9]{4}_US_cohort.csv',

### 2023-07-20 minos/validation/cross_validation_default.Rmd
Pointed handovers and cross-validation notebooks to the newly imputed data (going to revert this but just for testing)

--- 2023-07-15 minos/validation/cross_validation_default.Rmd
@@
 #cv <- cv.dat %>% filter(pidp %in% both.pidps$pidp)
-# getting only people who were in 2014 population. 
-who_2014_pidps <- raw.dat %>% filter(time %in% c(2014) & hh_income<10000) %>% select(pidp) %>% unique()
 raw <- raw.dat %>% filter(time %in% cv.years)
-raw <- raw %>% filter (pidp %in% who_2014_pidps$pidp)
 

### 2023-07-20 minos/validation/handovers.Rmd
Pointed handovers and cross-validation notebooks to the newly imputed data (going to revert this but just for testing)

--- 2023-07-18 minos/validation/handovers.Rmd
@@
 require(here)
-require(dplyr)
-require(tidyr)
-require(purrr)
 
@@
 # Read raw datafiles in
-raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'stock'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 
-## Parity
+```{r}
 
-```{r}
-base.parity <- base.dat %>%
-  filter(sex == "Female")
-
-raw.parity <- raw.dat %>%
-  filter(sex == "Female")
-
-prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Parity (total no. of children)'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'parity.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
 ```
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.parity,
-                                  df1.name = 'simulated', 
-                                  df2 = raw.parity, 
-                                  df2.name = 'raw', 
-                                  var = 'nkids_ind')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'nkids_ind',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.parity %>%
-  select(pidp, age, time, nkids_ind)
-base.s <- base.parity %>%
-  select(pidp, age, time, nkids_ind)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids_ind',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-```{r}
-raw.s <- raw.parity %>%
-  select(pidp, age, time, nkids_ind_raw)
-base.s <- base.parity %>%
-  select(pidp, age, time, nkids_ind_raw)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids_ind_raw',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```

### 2023-07-20 minos/validation/handovers.Rmd
final tunining (probably for now) for handovers and cross val. look good for paper.

@@
 require(ggplot2)
+require(ggridges) # for densities over time plots. 
 require(knitr)
 require(here)
+require(gghighlight)
 
@@
 # Read raw datafiles in
-raw.files <- list.files(here::here('data', 'stock'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 # start with hh_income
-raw.income <- raw.dat %>% 
-  dplyr::select(pidp, time, hh_income, weight) %>%
-  group_by(time) %>%
-  summarise(income = mean(hh_income, na.rm=TRUE)) %>%
-  mutate(source = 'final_US')
 
-base.income <- base.dat %>%
-  dplyr::select(pidp, time, hh_income, weight) %>%
-  group_by(time) %>%
-  summarise(income = mean(hh_income)) %>%
-  mutate(source = 'baseline_output')
+handover_boxplots(raw.dat, base.dat, 'hh_income')
+handover_lineplots(raw.dat, base.dat, "hh_income")
 
-# merge before plot
-income <- rbind(raw.income, base.income)
-
-# Now plot
-ggplot(data = income, mapping = aes(x = time, y = income, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Household Income', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Income')
-
-## Try a version where final_US is limited to only those present from wave 1 
-# onwards because the sample refreshments are messing with the plot
-raw.income.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.income2 <- raw.dat %>% 
-  dplyr::select(pidp, time, hh_income) %>%
-  filter(pidp %in% raw.income.wave1) %>%
-  group_by(time) %>%
-  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.income2 <- base.dat %>%
-  dplyr::select(pidp, time, hh_income) %>%
-  filter(pidp %in% raw.income.wave1) %>%
-  group_by(time) %>%
-  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-income2 <- rbind(raw.income2, base.income2)
-
-# Now plot
-ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Household Income') +
-  xlab('Year') +
-  ylab('Income')
-
-if (shall.we.save) {
-  ggsave(filename = 'hh_income_wav1.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-raw.income.check <- raw.dat %>% 
-  dplyr::select(pidp, time, hh_income) %>%
-  filter(pidp %in% raw.income.wave1)
-
-base.income.check <- base.dat %>%
-  dplyr::select(pidp, time, hh_income) %>%
-  filter(pidp %in% raw.income.wave1)
-
-rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
-   raw.income.check, base.income.check)
+# raw.income2 <- raw.dat %>% 
+#               dplyr::select(pidp, time, hh_income) %>%
+#               filter(pidp %in% raw.income.wave1)
+# 
+# base.income <-  base.income2 <- base.dat %>%
+#                                 dplyr::select(pidp, time, hh_income) %>%
+#                                 filter(pidp %in% raw.income.wave1)
+# 
+# handover_lineplots(raw.d)
+# ## Try a version where final_US is limited to only those present from wave 1 
+# # onwards because the sample refreshments are messing with the plot
+# raw.income.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+# 
+# raw.income2 <- raw.dat %>% 
+#   dplyr::select(pidp, time, hh_income) %>%
+#   filter(pidp %in% raw.income.wave1) %>%
+#   group_by(time) %>%
+#   summarise(income = mean(hh_income, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.income2 <- base.dat %>%
+#   dplyr::select(pidp, time, hh_income) %>%
+#   filter(pidp %in% raw.income.wave1) %>%
+#   group_by(time) %>%
+#   summarise(income = mean(hh_income, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# income2 <- rbind(raw.income2, base.income2)
+# 
+# # Now plot
+# ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
+#   geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Household Income') +
+#   xlab('Year') +
+#   ylab('Income')
+# 
+# if (shall.we.save) {
+#   ggsave(filename = 'hh_income_wav1.png',
+#        plot = last_plot(),
+#        path = save.path)
+# }
+# 
+# raw.income.check <- raw.dat %>% 
+#   dplyr::select(pidp, time, hh_income) %>%
+#   filter(pidp %in% raw.income.wave1)
+# 
+# base.income.check <- base.dat %>%
+#   dplyr::select(pidp, time, hh_income) %>%
+#   filter(pidp %in% raw.income.wave1)
+# 
+# rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
+#    raw.income.check, base.income.check)
 ```
@@
 
-spaghetti_plot(income.spag, 'hh_income',
+density_ridges(income.spag, 'hh_income',
+               save=TRUE, 
+               save.path=save.path)
+
+pidp_sample <- sample(unique(income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
+income.spag.sample <- income.spag[which(income.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(income.spag.sample, 'hh_income',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(income.spag.sample, 'hh_income',
                save = shall.we.save,
@@
 ```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.sf12 <- raw.dat %>% 
-  dplyr::select(pidp, time, SF_12) %>%
-  group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.sf12 <- base.dat %>%
-  dplyr::select(pidp, time, SF_12) %>%
-  group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-sf12 <- rbind(raw.sf12, base.sf12)
-
-# Now plot
-ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('SF12')
-
-## Try a version where final_US is limited to only those present from wave 1 
-# onwards because the sample refreshments are messing with the plot
-raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.sf12.2 <- raw.dat %>% 
-  dplyr::select(pidp, time, SF_12) %>%
-  filter(pidp %in% raw.sf12.wave1) %>%
-  group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.sf12.2 <- base.dat %>%
-  dplyr::select(pidp, time, SF_12) %>%
-  filter(pidp %in% raw.sf12.wave1) %>%
-  group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
-
-# Now plot
-ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Mental Wellbeing (SF12 MCS)') +
-  xlab('Year') +
-  ylab('SF12')
-
-if (shall.we.save) {
-  ggsave(filename = 'SF12_wav1.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
+# sf12 boxplot handovers
+handover_boxplots(raw.dat, base.dat, 'SF_12')
+handover_lineplots(raw.dat, base.dat, "SF_12")
+# 
+# raw.sf12 <- raw.dat %>% 
+#   dplyr::select(pidp, time, SF_12) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.sf12 <- base.dat %>%
+#   dplyr::select(pidp, time, SF_12) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# # merge before plot
+# sf12 <- rbind(raw.sf12, base.sf12)
+# 
+# # Now plot
+# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+#   geom_smooth() +
+#   #geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
+#   xlab('Year') +
+#   ylab('SF12')
+# 
+# ## Try a version where final_US is limited to only those present from wave 1 
+# # onwards because the sample refreshments are messing with the plot
+# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+# 
+# raw.sf12.2 <- raw.dat %>% 
+#   dplyr::select(pidp, time, SF_12) %>%
+#   filter(pidp %in% raw.sf12.wave1) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.sf12.2 <- base.dat %>%
+#   dplyr::select(pidp, time, SF_12) %>%
+#   filter(pidp %in% raw.sf12.wave1) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
+# 
+# # Now plot
+# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+#   geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
+#   xlab('Year') +
+#   ylab('SF12')
+# 
+# if (shall.we.save) {
+#   ggsave(filename = 'SF12_wav1.png',
+#        plot = last_plot(),
+#        path = save.path)
+# }
+# 
+# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
 ```
@@
 
-spaghetti_plot(sf12.spag, 'SF_12',
+sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(sf12.spag.sample, 'SF_12',
                save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(sf12.spag, "SF_12", 
+               save = T, 
                save.path = save.path)
@@
 ```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.nut <- raw.dat %>% 
-  dplyr::select(pidp, time, nutrition_quality) %>%
-  group_by(time) %>%
-  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
+#  nutriton quality line/boxplots.
+handover_boxplots(raw.dat, base.dat, 'nutrition_quality')
+handover_lineplots(raw.dat, base.dat, 'nutrition_quality')
 
-base.nut <- base.dat %>%
-  dplyr::select(pidp, time, nutrition_quality) %>%
-  group_by(time) %>%
-  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-nutrition_quality <- rbind(raw.nut, base.nut)
-
-# Now plot
-ggplot(data = nutrition_quality, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Nutrition Quality', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Nutrition Quality')
-
-## Try a version where final_US is limited to only those present from wave 1 
+# Try a version where final_US is limited to only those present from wave 1
 # onwards because the sample refreshments are messing with the plot
-raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.nut2 <- raw.dat %>% 
-  dplyr::select(pidp, time, nutrition_quality) %>%
-  filter(pidp %in% raw.wave1) %>%
-  filter(nutrition_quality >= 0) %>%
-  group_by(time) %>%
-  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.nut2 <- base.dat %>%
-  dplyr::select(pidp, time, nutrition_quality) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-nutrition_quality2 <- rbind(raw.nut2, base.nut2)
-
-# Now plot
-ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Nutrition Quality') +
-  xlab('Year') +
-  ylab('Nutrition Quality')
-
-if (shall.we.save) {
-  ggsave(filename = 'nutrition_quality_wav1.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2, 
-    nutrition_quality2)
+# raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+# 
+# raw.nut2 <- raw.dat %>%
+#   dplyr::select(pidp, time, nutrition_quality) %>%
+#   filter(pidp %in% raw.wave1) %>%
+#   filter(nutrition_quality >= 0) %>%
+#   group_by(time) %>%
+#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.nut2 <- base.dat %>%
+#   dplyr::select(pidp, time, nutrition_quality) %>%
+#   filter(pidp %in% raw.wave1) %>%
+#   group_by(time) %>%
+#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# nutrition_quality2 <- rbind(raw.nut2, base.nut2)
+# 
+# # Now plot
+# ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
+#   geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Nutrition Quality') +
+#   xlab('Year') +
+#   ylab('Nutrition Quality')
+# 
+# if (shall.we.save) {
+#   ggsave(filename = 'nutrition_quality_wav1.png',
+#        plot = last_plot(),
+#        path = save.path)
+# }
+# 
+# rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2,
+#     nutrition_quality2)
 ```
@@
 
-rm(raw.s, base.s, spag)
+density_ridges(nut.spag, "nutrition_quality", 
+               save = T, 
+               save.path = save.path)
+
+rm(raw.nut, base.nut, nut.spag)
 ```

### 2023-07-20 minos/transitions/estimate_transitions.R

@@ -106,7 +106,7 @@ run_yearly_models <- function(transitionDir_path,
     # crossval needs to start in 2010, whereas default model can have reduced timespan
     # avoid first year as data is weird and missing in a lot of cases
     if(mode == 'cross_validation') {
-      year.range <- seq(min(data$time) + 4, (min(data$time) + 6))
+      year.range <- seq(max(data$time) - 3, (max(data$time)-1))
     } else {
       year.range <- seq(max(data$time) - 6, (max(data$time) - 1))
       #year.range <- seq(min(data$time), (max(data$time) - 1)) # fit full range for model of models testing purposes

### 2023-07-22 minos/testing/imputation_testing.Rmd
Lots more WIP stuff on imputation and fixing var types in modules. Also added a testing notebook for comparing final_US, complete_US, and imputed stock data to influence decisions

---
title: "Imputation Assessment"
output: html_notebook
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

Source utils for some functions.

```{r}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

## Data

```{r}
# Read raw datafiles in
imp.files <- list.files(here::here('data', 'stock'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
imp.dat <- do.call(rbind, lapply(imp.files, read.csv))

final.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
final.dat <- do.call(rbind, lapply(final.files, read.csv))

complete.files <- list.files(here::here('data', 'complete_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
complete.dat <- do.call(rbind, lapply(complete.files, read.csv))
```

# Functions

```{r}
compare_continuous <- function(final, complete, imputed, var) {

  final.var <- final %>% 
    dplyr::select(pidp, time, all_of(var), weight) %>%
    filter(time != 2009) %>%
    filter(!.data[[var]] %in% miss.values) %>%
    drop_na() %>%
    group_by(time) %>%
    summarise(mean = weighted.mean(x = .data[[var]],
                                   w = weight,
                                   na.rm=TRUE)) %>%
    mutate(source = 'final')

  complete.var <- complete %>% 
    dplyr::select(pidp, time, all_of(var), weight) %>%
    filter(time != 2009) %>%
    filter(!.data[[var]] %in% miss.values) %>%
    drop_na() %>%
    group_by(time) %>%
    summarise(mean = weighted.mean(x = .data[[var]],
                                   w = weight,
                                   na.rm=TRUE)) %>%
    mutate(source = 'complete')

  imputed.var <- imputed %>% 
    dplyr::select(pidp, time, all_of(var), weight) %>%
    filter(time != 2009) %>%
    filter(!.data[[var]] %in% miss.values) %>%
    drop_na() %>%
    group_by(time) %>%
    summarise(mean = weighted.mean(x = .data[[var]],
                                   w = weight,
                                   na.rm=TRUE)) %>%
    mutate(source = 'imputed')

  merged <- rbind(final.var, complete.var)
  merged <- rbind(merged, imputed.var)

  # Now plot
  p1 <- ggplot(data = merged, mapping = aes(x = time, y = mean, group = source, colour = source)) +
    geom_line() +
    labs(title = var, subtitle = 'Full Sample') +
    xlab('Year') +
    ylab(var)

  print(p1)
}

compare_ordinal <- function(final, complete, imputed, var) {

  final.var <- final %>% 
    dplyr::select(pidp, time, all_of(var)) %>%
    filter(.data[[var]] > 0) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    mutate(source = 'final')

  complete.var <- complete %>% 
    dplyr::select(pidp, time, all_of(var)) %>%
    filter(.data[[var]] > 0) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    mutate(source = 'complete')

  imputed.var <- imputed %>% 
    dplyr::select(pidp, time, all_of(var)) %>%
    filter(.data[[var]] > 0) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    mutate(source = 'imputed')

  merged <- rbind(final.var, complete.var)
  merged <- rbind(merged, imputed.var)
  merged[[var]] <- as.factor(merged[[var]])

  # Now plot
  p1 <- ggplot(data = merged, mapping = aes(x = .data[[var]], y = n, group = source, fill = source)) +
    geom_col(position='dodge') +
    labs(title = var, subtitle = 'Counts by Level') +
    xlab('Year') +
    ylab('Count')

  print(p1)
}

multi_year_boxplots <- function(final, complete, imputed, var) {
  final.var <- final %>%
    dplyr::select(pidp, time, all_of(var)) %>%
    filter(!.data[[var]] %in% miss.values)
  final.var$source <- 'final'

  complete.var <- complete %>%
    dplyr::select(pidp, time, all_of(var)) %>%
    filter(!.data[[var]] %in% miss.values)
  complete.var$source <- 'complete'

  imputed.var <- imputed %>%
    dplyr::select(pidp, time, all_of(var)) %>%
    filter(!.data[[var]] %in% miss.values)
  imputed.var$source <- 'imputed'

  combined <- rbind(final.var, complete.var)
  combined <- rbind(combined, imputed.var)
  combined$time <- as.factor(combined$time)
  combined <- drop_na(combined)
  combined <- filter(combined, .data[[var]] != -9)

  if (var %in% c('hh_income', 'equivalent_income')) {
    combined <- filter(combined, .data[[var]] < quantile(.data[[var]], 0.99), .data[[var]] > quantile(.data[[var]], 0.01))
  } else if (var == 'ncigs') {
    #combined <- filter(combined, .data[[var]] < quantile(.data[[var]], 0.99))
    combined <- filter(combined, .data[[var]] < quantile(.data[[var]], 0.99), !.data[[var]] == 0)
  }

  ggplot(data = combined, aes(x = time, y = .data[[var]], group = interaction(time, source), color = source)) +
    geom_boxplot(notch=TRUE) +
    labs(title = paste0(var, ': Yearly box plots'))
}

```

# Float Variables

## hh_income

```{r}
compare_continuous(final.dat, complete.dat, imp.dat, 'hh_income')
multi_year_boxplots(final.dat, complete.dat, imp.dat, 'hh_income')
```

## SF_12

```{r}
compare_continuous(final.dat, complete.dat, imp.dat, 'SF_12')
multi_year_boxplots(final.dat, complete.dat, imp.dat, 'SF_12')
```

# Str Variables

## Region

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'region')
```

## Ethnicity

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'ethnicity')
```

## Loneliness

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'loneliness')
```

## Sex

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'sex')
```

## Housing Quality

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'housing_quality')
```

## S7 Housing Quality

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'S7_housing_quality')
```

## Neighbourhood Safety

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'neighbourhood_safety')
```

## S7 Neighbourhood Safety

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'S7_neighbourhood_safety')
```

## S7 Labour State

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'S7_labour_state')
```

## Marital Status

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'marital_status')
```

# Int Variables

## Heating

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'heating')
```

## Job Sec

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'job_sec')
```

## ncigs

```{r}
compare_continuous(final.dat, complete.dat, imp.dat, 'ncigs')
multi_year_boxplots(final.dat, complete.dat, imp.dat, 'ncigs')
```

## Financial Situation

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'financial_situation')
```

## Education State

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'education_state')
```

## S7 Physical Health

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'S7_physical_health')
```

## S7 Mental Health

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'S7_mental_health')
```

## Housing Tenure

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'housing_tenure')
```

## Nutrition Quality

```{r}
compare_continuous(final.dat, complete.dat, imp.dat, 'nutrition_quality')
multi_year_boxplots(final.dat, complete.dat, imp.dat, 'nutrition_quality')
```

## Smoker

```{r}
compare_ordinal(final.dat, complete.dat, imp.dat, 'smoker')
```

```{r}

```

### 2023-07-22 minos/validation/handovers.Rmd
Lots more WIP stuff on imputation and fixing var types in modules. Also added a testing notebook for comparing final_US, complete_US, and imputed stock data to influence decisions

--- 2023-07-20 minos/validation/handovers.Rmd
@@
 
+## Financial Situation
+
+```{r}
+# first figure out how to plot final_US
+# start with hh_income
+raw.fsit <- raw.dat %>% 
+  dplyr::select(pidp, time, financial_situation) %>%
+  filter(time > 2009) %>%
+  group_by(time) %>%
+  summarise(financial_situation = mean(financial_situation, na.rm = TRUE)) %>%
+  mutate(source = 'final_US')
+
+base.fsit <- base.dat %>%
+  dplyr::select(pidp, time, financial_situation) %>%
+  filter(time > 2009) %>%
+  group_by(time) %>%
+  summarise(financial_situation = mean(financial_situation, na.rm = TRUE)) %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+fsit <- rbind(raw.fsit, base.fsit)
+
+# Now plot
+ggplot(data = fsit, mapping = aes(x = time, y = financial_situation, group = source, colour = source)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial Situation', subtitle = 'Full Sample') +
+  xlab('Year') +
+  ylab('Average')
+
+## Try a version where final_US is limited to only those present from wave 1 
+# onwards because the sample refreshments are messing with the plot
+raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+
+raw.fsit2 <- raw.dat %>% 
+  dplyr::select(pidp, time, financial_situation) %>%
+  filter(time > 2009) %>%
+  filter(pidp %in% raw.wave1) %>%
+  group_by(time) %>%
+  summarise(financial_situation = mean(financial_situation, na.rm = TRUE)) %>%
+  mutate(source = 'final_US')
+
+base.fsit2 <- base.dat %>%
+  dplyr::select(pidp, time, financial_situation) %>%
+  filter(time > 2009) %>%
+  filter(pidp %in% raw.wave1) %>%
+  group_by(time) %>%
+  summarise(financial_situation = mean(financial_situation, na.rm = TRUE)) %>%
+  mutate(source = 'baseline_output')
+
+fsit2 <- rbind(raw.fsit2, base.fsit2)
+
+# Now plot
+ggplot(data = fsit2, mapping = aes(x = time, y = financial_situation, group = source, colour = source)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial Situation') +
+  xlab('Year') +
+  ylab('Average')
+
+if (shall.we.save) {
+  ggsave(filename = 'financial_situation_wav1.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+#raw.phealth.check <- raw.dat %>% 
+#  select(pidp, time, phealth) %>%
+#  filter(time > 2009) %>%
+#  filter(pidp %in% raw.wave1)
+
+#base.phealth.check <- base.dat %>%
+#  select(pidp, time, phealth) %>%
+#  filter(time > 2009) %>%
+#  filter(pidp %in% raw.wave1)
+
+rm(raw.fsit, base.fsit, fsit, raw.wave1, raw.fsit2, base.fsit2, fsit2)
+#rm(raw.phealth.check, base.phealth.check)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, financial_situation)
+base.s <- base.dat %>%
+  select(pidp, age, time, financial_situation)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'financial_situation',
+             save = shall.we.save,
+             save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
 ## Education

### 2023-07-22 minos/modules/financial_situation.py

@@ -96,8 +96,8 @@ class financialSituation(Base):
                                                              list(nextWaveFinancialPerception.columns+1),
                                                              nextWaveFinancialPerception).astype(float)
         nextWaveFinancialPerception.index = pop.index
-        #nextWaveFinancialPerception["financial_situation"] = \
-        #    nextWaveFinancialPerception["financial_situation"].astype(int)
+        nextWaveFinancialPerception["financial_situation"] = \
+            nextWaveFinancialPerception["financial_situation"].astype(int)
         # Draw individuals next states randomly from this distribution.
         # Update population with new income.
         self.population_view.update(nextWaveFinancialPerception['financial_situation'])

### 2023-07-24 minos/testing/imputation_testing.Rmd
Another version of the imputation step. This time, we "seed" variables where information is completely missing within a year (copy another wave onto and remove half of values). This is to give the imputater something to work with as complete missing within a year was causing big problems

@@
 title: "Imputation Assessment"
-output: html_notebook
+output:
+  html_document:
+    toc: true
+    toc_float: true
+    collapsed: false
+    number_sections: true
+    df_print: paged
+    code_folding: hide
 ---
@@
   warning = FALSE,
-  message = FALSE
+  message = FALSE,
+  out.width = 3500
 )
+# 3000
+# '100%'
 rm(workingDir)
@@
     dplyr::select(pidp, time, all_of(var)) %>%
-    filter(.data[[var]] > 0) %>%
+    filter(.data[[var]] >= 0) %>%
     group_by(time, .data[[var]]) %>%
@@
   merged[[var]] <- as.factor(merged[[var]])
+  merged$time = as.factor(merged$time)
 
@@
 
+  p2 <- ggplot(data = merged, mapping = aes(x = time, y = n, group = .data[[var]], colour = .data[[var]])) +
+    geom_line() +
+    geom_point() +
+    facet_grid(.~source) +
+    theme(legend.position="none") +
+    labs(title = var, subtitle = 'Counts by Level') +
+    xlab('Year') +
+    ylab('Count')
+
   print(p1)
+  print(p2)
+
+  var.norm <- merged %>%
+    group_by(time, source) %>%
+    mutate(total = sum(n)) %>%
+    mutate(prct = (n / total))
+
+  p3 <- ggplot(data = var.norm, mapping = aes(x = time, y = prct, fill=.data[[var]], position='dodge')) +
+    geom_bar(stat = 'identity') +
+    facet_grid(.~source) +
+    theme(legend.position="none") +
+    labs(title = var) +
+    xlab('Year') +
+    ylab('Proportion')
+  print(p3)
 }

### 2023-08-01 minos/validation/handovers.Rmd

--- 2023-07-20 minos/validation/handovers.Rmd
@@
 require(here)
+require(dplyr)
+require(tidyr)
+require(purrr)
 require(gghighlight)
@@
 ```
+
+## Parity
+
+```{r}
+base.parity <- base.dat %>%
+  filter(sex == "Female")
+
+raw.parity <- raw.dat %>%
+  filter(sex == "Female")
+
+prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Parity (total no. of children)'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'parity.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.parity,
+                                  df1.name = 'simulated', 
+                                  df2 = raw.parity, 
+                                  df2.name = 'raw', 
+                                  var = 'nkids_ind')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'nkids_ind',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.parity %>%
+  select(pidp, age, time, nkids_ind)
+base.s <- base.parity %>%
+  select(pidp, age, time, nkids_ind)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nkids_ind',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+```{r}
+raw.s <- raw.parity %>%
+  select(pidp, age, time, nkids_ind_raw)
+base.s <- base.parity %>%
+  select(pidp, age, time, nkids_ind_raw)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nkids_ind_raw',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```

### 2023-08-01 minos/validation/handovers.Rmd
Now generating an inflated population for every year in raw data, and updated handovers to use this inflated population for validation

--- 2023-07-20 minos/validation/handovers.Rmd
@@
 # Read raw datafiles in
-raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'inflated_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 
+# SAMPLE
+
+```{r}
+raw.n <- raw.dat %>%
+  group_by(time) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.n <- base.dat %>%
+  group_by(time) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+combined <- rbind(raw.n, base.n)
+#combined$time <- as.factor(combined$time)
+
+ggplot(data = combined, aes(x = time, y = n, group = source, color = source, fill = source)) +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  geom_col(position='dodge') +
+  labs(title = 'Sample size over time')
+```
+
+# Check Weights
+
+```{r}
+# raw.weight <- raw.dat %>%
+#   group_by(time) %>%
+#   summarise(sum.weight = sum(weight, na.rm = TRUE))
+# 
+# ggplot(data = raw.weight, aes(x = time, y = sum.weight)) +
+#   geom_line()
+```
+
 # PATHWAYS
@@
 handover_lineplots(raw.dat, base.dat, "hh_income")
-
-# raw.income2 <- raw.dat %>% 
-#               dplyr::select(pidp, time, hh_income) %>%
-#               filter(pidp %in% raw.income.wave1)
-# 
-# base.income <-  base.income2 <- base.dat %>%
-#                                 dplyr::select(pidp, time, hh_income) %>%
-#                                 filter(pidp %in% raw.income.wave1)
-# 
-# handover_lineplots(raw.d)
-# ## Try a version where final_US is limited to only those present from wave 1 
-# # onwards because the sample refreshments are messing with the plot
-# raw.income.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-# 
-# raw.income2 <- raw.dat %>% 
-#   dplyr::select(pidp, time, hh_income) %>%
-#   filter(pidp %in% raw.income.wave1) %>%
-#   group_by(time) %>%
-#   summarise(income = mean(hh_income, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.income2 <- base.dat %>%
-#   dplyr::select(pidp, time, hh_income) %>%
-#   filter(pidp %in% raw.income.wave1) %>%
-#   group_by(time) %>%
-#   summarise(income = mean(hh_income, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# income2 <- rbind(raw.income2, base.income2)
-# 
-# # Now plot
-# ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
-#   geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Household Income') +
-#   xlab('Year') +
-#   ylab('Income')
-# 
-# if (shall.we.save) {
-#   ggsave(filename = 'hh_income_wav1.png',
-#        plot = last_plot(),
-#        path = save.path)
-# }
-# 
-# raw.income.check <- raw.dat %>% 
-#   dplyr::select(pidp, time, hh_income) %>%
-#   filter(pidp %in% raw.income.wave1)
-# 
-# base.income.check <- base.dat %>%
-#   dplyr::select(pidp, time, hh_income) %>%
-#   filter(pidp %in% raw.income.wave1)
-# 
-# rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
-#    raw.income.check, base.income.check)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, housing_quality)
-base.s <- base.dat %>%
-  select(pidp, age, time, housing_quality)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'housing_quality',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, housing_quality)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, housing_quality)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'housing_quality',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, neighbourhood_safety)
-base.s <- base.dat %>%
-  select(pidp, age, time, neighbourhood_safety)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'neighbourhood_safety',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, neighbourhood_safety)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, neighbourhood_safety)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'neighbourhood_safety',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, loneliness)
-base.s <- base.dat %>%
-  select(pidp, age, time, loneliness)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'loneliness',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, loneliness)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, loneliness)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'loneliness',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-raw.nut <- raw.dat %>%
-  select(pidp, age, time, nutrition_quality)
-base.nut <- base.dat %>%
-  select(pidp, age, time, nutrition_quality)
-
-nut.spag <- rbind(raw.nut, base.nut)
-
-spaghetti_plot(nut.spag, 'nutrition_quality',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(nut.spag, "nutrition_quality", 
-               save = T, 
-               save.path = save.path)
-
-rm(raw.nut, base.nut, nut.spag)
+# raw.nut <- raw.dat %>%
+#   select(pidp, age, time, nutrition_quality)
+# base.nut <- base.dat %>%
+#   select(pidp, age, time, nutrition_quality)
+# 
+# nut.spag <- rbind(raw.nut, base.nut)
+# 
+# spaghetti_plot(nut.spag, 'nutrition_quality',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# 
+# density_ridges(nut.spag, "nutrition_quality", 
+#                save = T, 
+#                save.path = save.path)
+# 
+# rm(raw.nut, base.nut, nut.spag)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, phealth)
-base.s <- base.dat %>%
-  select(pidp, age, time, phealth)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'phealth',
-             save = shall.we.save,
-             save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, phealth)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, phealth)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'phealth',
+#              save = shall.we.save,
+#              save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, education_state)
-base.s <- base.dat %>%
-  select(pidp, age, time, education_state)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, education_state)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, education_state)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'education_state',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
+```
 
-spag <- rbind(raw.s, base.s)
+```{r}
 
-spaghetti_plot(spag, 'education_state',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
 ```

### 2023-08-01 minos/utils_validation_vis.R

@@ -460,13 +460,13 @@ handover_boxplots <- function(raw, baseline, var) {
     labs(title = paste0(var, ': Yearly box plots'))
 }
 
-
+# summarise(summary_var = weighted.mean(x = .data[[var]], w = weight)) %>%
 handover_lineplots <- function(raw, base, var) {
   # GENERALISE THIS AND DOCSTRING
   raw.means <- raw %>% 
-    dplyr::select(pidp, time, var, weight) %>%
+    dplyr::select(pidp, time, var) %>%
     group_by(time) %>%
-    summarise(summary_var = weighted.mean(x = .data[[var]], w = weight, na.rm=TRUE)) %>%
+    summarise(summary_var = mean(.data[[var]], na.rm = TRUE)) %>%
     mutate(source = 'final_US')
   
   base.means <- base %>%

### 2023-08-03 minos/outcomes/child_poverty_reduction_vis.Rmd
Working on the child poverty reduction intervention and the visualisation script alongside

---
title: "Child Poverty Interventions"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

This document presents results from a host of interventions on child poverty, including visualisations of the change in SF_12_MCS compared with baseline.

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(ggridges) # for densities over time plots. 
require(knitr)
require(here)
require(gghighlight)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

```{r "imports", include=FALSE}
source(here::here('minos', 'utils_datain.R'))
#source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
int.dat <- read_singular_local_out(out.path, 'ChildPovertyReduction', drop.dead = TRUE)
#base.dat <- read_agg_subset_batch_out(out.path, 'baseline', drop.dead = TRUE)
#int1.dat <- read_agg_subset_batch_out(out.path, 'ChildPovertyReduction', drop.dead = TRUE)
```

# Relative Poverty Reduction

The first intervention we will focus on is a reduction in the prevalence of children in relative poverty.

## Threshold

Relative poverty is defined as the proportion of children living in households with income below 60% of the population median *in a given year*.

We can calculate the relative poverty threshold for our starting year of 2020:

```{r}
base.2020 <- base.dat %>%
  filter(time == 2020)

mean.hh_income <- weighted.mean(base.2020$hh_income, w = base.2020$weight)
rel.pov.threshold <- mean.hh_income * 0.6

print(paste0("Relative poverty threshold in 2020: ", rel.pov.threshold))
rm(base.2020, mean.hh_income, rel.pov.threshold)
```

We can also look at how this evolves over time in the baseline simulation:

```{r}
threshold <- base.dat %>%
  select(time, weight, hh_income) %>%
  group_by(time) %>%
  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))

ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
  geom_col() +
  geom_hline(yintercept = threshold$poverty_threshold[threshold$time == 2020], linetype='dashed') +
  labs(title = 'Relative poverty threshold over time') +
  xlab('Year') +
  ylab('Threshold')
```

The threshold for relative poverty decreases over time in our simulation (it's worth noting that monetary values in our simulation have been adjusted for inflation to 2020 £s). This suggests that our population is getting slightly less wealthy over time on average.

## Boosted Sample

We can also look at how many people are receiving the intervention over time, and the total and mean amounts of money being added to the system. This should slowly increase to 2030 and then hold fairly steady.

```{r}
hh_boosted <- int.dat %>%
  select(hidp, time, income_boosted, boost_amount, nkids) %>%
  filter(income_boosted == 'True') %>%
  group_by(time) %>%
  summarise(n_boosted = length(unique(hidp)),
            total_boost = sum(boost_amount),
            kids_boosted = sum(nkids))

ggplot(hh_boosted, aes(x = time, y = n_boosted)) +
  geom_line() +
  geom_vline(xintercept = 2030, linetype = 'dashed') +
  labs(title = 'Number of households receiving intervention') +
  xlab('Year') +
  ylab('Number Boosted')

ggplot(hh_boosted, aes(x = time, y = kids_boosted)) +
  geom_line() +
  geom_vline(xintercept = 2030, linetype = 'dashed') +
  labs(title = 'Number of children in households receiving intervention') +
  xlab('Year') +
  ylab('Number Children')

ggplot(hh_boosted, aes(x = time, y = total_boost)) +
  geom_line() +
  geom_vline(xintercept = 2030, linetype = 'dashed') +
  labs(title = 'Total boost amount') +
  xlab('Year') +
  ylab('Boost Amount')

mean.boost <- int.dat %>%
  select(time, income_boosted, boost_amount) %>%
  group_by(time, income_boosted) %>%
  summarise(mean_boost = mean(boost_amount)) %>%
  filter(income_boosted == 'True')

ggplot(mean.boost, aes(x = time, y = mean_boost)) +
  geom_line() +
  geom_vline(xintercept = 2030, linetype = 'dashed') +
  labs(title = 'Mean boost amount') +
  xlab('Year') +
  ylab('Boost Amount')
```

Now lets look at SF_12_MCS comparisons.

## SF_12_MCS

SF_12_MCS stands for the Mental Component Score (MCS) from the 12-item Short Form (SF) Survey. See [this paper](https://link.springer.com/referenceworkentry/10.1007/978-94-007-0753-5_2698) for more information about SF_12.

### Full Sample

First lets look at the effect of the intervention on the entire sample.

```{r}
base.all.SF12 <- base.dat %>%
  select(time, weight, SF_12) %>%
  group_by(time) %>%
  summarise(base.SF12 = weighted.mean(SF_12, w = weight))

int.all.SF12 <- int.dat %>%
  select(time, weight, SF_12) %>%
  group_by(time) %>%
  summarise(int.SF12 = weighted.mean(SF_12, w = weight))

combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
combined$diff <- combined$int.SF12 - combined$base.SF12

ggplot(combined, aes(x = time, y = diff)) +
  geom_line() +
  geom_hline(yintercept = 0, linetype='dashed') +
  labs(title = 'Relative change in SF12') +
  xlab('Year') +
  ylab('Difference')
```

### Families with children

Now focused only on families with children.

```{r}
base.all.SF12 <- base.dat %>%
  select(time, weight, SF_12, nkids) %>%
  filter(nkids > 0) %>%
  group_by(time) %>%
  summarise(base.SF12 = weighted.mean(SF_12, w = weight))

int.all.SF12 <- int.dat %>%
  select(time, weight, SF_12, nkids) %>%
  filter(nkids > 0) %>%
  group_by(time) %>%
  summarise(int.SF12 = weighted.mean(SF_12, w = weight))

combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
combined$diff <- combined$int.SF12 - combined$base.SF12

ggplot(combined, aes(x = time, y = diff)) +
  geom_line() +
  geom_hline(yintercept = 0, linetype='dashed') +
  labs(title = 'Relative change in SF12') +
  xlab('Year') +
  ylab('Difference')
```

### Families w/ children under poverty line

Now only households with children under the poverty line.

```{r}
base.thresh <- merge(base.dat, threshold, by = 'time')
int.thresh <- merge(int.dat, threshold, by = 'time')

base.all.SF12 <- base.thresh %>%
  select(time, weight, SF_12, nkids, hh_income, poverty_threshold) %>%
  filter(nkids > 0) %>%
  filter(hh_income < poverty_threshold) %>%
  group_by(time) %>%
  summarise(base.SF12 = weighted.mean(SF_12, w = weight))

int.all.SF12 <- int.thresh %>%
  select(time, weight, SF_12, nkids, hh_income, poverty_threshold) %>%
  filter(nkids > 0) %>%
  filter(hh_income < poverty_threshold) %>%
  group_by(time) %>%
  summarise(int.SF12 = weighted.mean(SF_12, w = weight))

combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
combined$diff <- combined$int.SF12 - combined$base.SF12

ggplot(combined, aes(x = time, y = diff)) +
  geom_line() +
  geom_hline(yintercept = 0, linetype='dashed') +
  labs(title = 'Relative change in SF12') +
  xlab('Year') +
  ylab('Difference')
```

This plot is perhaps a bit disingenuous, as the closer we get to 2030 the fewer households are actually under the poverty line. We might achieve what we want better by looking only at the boosted population.

### Treatment on the Treated

```{r}
boosted.overtime <- int.dat %>%
  filter(income_boosted == 'True')

base.all.SF12 <- base.dat %>%
  select(time, weight, SF_12, nkids, pidp) %>%
  filter(pidp %in% boosted.overtime$pidp) %>%
  group_by(time) %>%
  summarise(base.SF12 = weighted.mean(SF_12, w = weight))

int.all.SF12 <- int.dat %>%
  select(time, weight, SF_12, nkids, pidp) %>%
  filter(pidp %in% boosted.overtime$pidp) %>%
  group_by(time) %>%
  summarise(int.SF12 = weighted.mean(SF_12, w = weight))

combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
combined$diff <- combined$int.SF12 - combined$base.SF12

ggplot(combined, aes(x = time, y = diff)) +
  geom_line() +
  geom_hline(yintercept = 0, linetype='dashed') +
  labs(title = 'Relative change in SF12') +
  xlab('Year') +
  ylab('Difference')
```

```{r}

```

### 2023-08-03 minos/validation/cross_validation_default.Rmd

--- 2023-07-18 minos/validation/cross_validation_default.Rmd
@@
 #cv <- cv.dat %>% filter(pidp %in% both.pidps$pidp)
+# getting only people who were in 2014 population. 
+#who_2014_pidps <- raw.dat %>% filter(time %in% c(2014) & hh_income<10000) %>% select(pidp) %>% unique()
 raw <- raw.dat %>% filter(time %in% cv.years)
+#raw <- raw %>% filter (pidp %in% who_2014_pidps$pidp)
 

### 2023-08-04 minos/validation/handovers_S7.Rmd

--- 2023-07-05 minos/validation/handovers_S7.Rmd
@@
 require(here)
+require(dplyr)
+require(tidyr)
+require(purrr)
 
@@
 
+## Parity
+
 ```{r}
+base.parity <- base.dat %>%
+  filter(sex == "Female")
 
+raw.parity <- raw.dat %>%
+  filter(sex == "Female")
+
+prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Parity (total no. of children)'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'parity.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
 ```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.parity,
+                                  df1.name = 'simulated', 
+                                  df2 = raw.parity, 
+                                  df2.name = 'raw', 
+                                  var = 'nkids_ind')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'nkids_ind',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.parity %>%
+  select(pidp, age, time, nkids_ind)
+base.s <- base.parity %>%
+  select(pidp, age, time, nkids_ind)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nkids_ind',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```

### 2023-08-10 minos/validation/handovers_S7.Rmd
Tweaks to validation scripts for S7

@@
 
+### Boxplots
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'hh_income')
+```
+
 ### Spaghetti
@@
 
+### Boxplots
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'equivalent_income')
+```
+
 ### Spaghetti
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, S7_housing_quality)
-base.s <- base.dat %>%
-  select(pidp, age, time, S7_housing_quality)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'S7_housing_quality',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, S7_housing_quality)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, S7_housing_quality)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'S7_housing_quality',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, S7_neighbourhood_safety)
-base.s <- base.dat %>%
-  select(pidp, age, time, S7_neighbourhood_safety)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'S7_neighbourhood_safety',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, S7_neighbourhood_safety)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, S7_neighbourhood_safety)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'S7_neighbourhood_safety',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, S7_physical_health)
-base.s <- base.dat %>%
-  select(pidp, age, time, S7_physical_health)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'S7_physical_health',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, S7_physical_health)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, S7_physical_health)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'S7_physical_health',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, S7_mental_health)
-base.s <- base.dat %>%
-  select(pidp, age, time, S7_mental_health)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'S7_mental_health',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, S7_mental_health)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, S7_mental_health)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'S7_mental_health',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-raw.s <- raw.parity %>%
-  select(pidp, age, time, nkids_ind)
-base.s <- base.parity %>%
-  select(pidp, age, time, nkids_ind)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids_ind',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.parity %>%
+#   select(pidp, age, time, nkids_ind)
+# base.s <- base.parity %>%
+#   select(pidp, age, time, nkids_ind)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'nkids_ind',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```

### 2023-08-13 minos/validation/handovers.Rmd
Removed chunk in handovers.Rmd checking the nkids_ind_raw as its now removed during data generation

@@
 # Read raw datafiles in
-raw.files <- list.files(here::here('data', 'inflated_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 shall.we.save <- FALSE
-```
-
-# SAMPLE
-
-```{r}
-raw.n <- raw.dat %>%
-  group_by(time) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.n <- base.dat %>%
-  group_by(time) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-combined <- rbind(raw.n, base.n)
-#combined$time <- as.factor(combined$time)
-
-ggplot(data = combined, aes(x = time, y = n, group = source, color = source, fill = source)) +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  geom_col(position='dodge') +
-  labs(title = 'Sample size over time')
-```
-
-# Check Weights
-
-```{r}
-# raw.weight <- raw.dat %>%
-#   group_by(time) %>%
-#   summarise(sum.weight = sum(weight, na.rm = TRUE))
-# 
-# ggplot(data = raw.weight, aes(x = time, y = sum.weight)) +
-#   geom_line()
 ```
@@
 
+## Parity
+
+```{r}
+base.parity <- base.dat %>%
+  filter(sex == "Female")
+
+raw.parity <- raw.dat %>%
+  filter(sex == "Female")
+
+prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Parity (total no. of children)'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'parity.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.parity,
+                                  df1.name = 'simulated', 
+                                  df2 = raw.parity, 
+                                  df2.name = 'raw', 
+                                  var = 'nkids_ind')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'nkids_ind',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.parity %>%
+  select(pidp, age, time, nkids_ind)
+base.s <- base.parity %>%
+  select(pidp, age, time, nkids_ind)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nkids_ind',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
 ```{r}

### 2023-08-13 minos/validation/handovers_inflated.Rmd

--- 2023-08-01 minos/validation/handovers.Rmd
@@
 ---
-title: "MINOS Handover Plots"
+title: "MINOS Handover Plots - Inflated"
 output:
@@
 
-out.path <- here::here('output', 'default_config/')
+out.path <- here::here('output', 'inflated_default/')
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)

### 2023-08-14 minos/outcomes/equivalent_income_out.Rmd
Lots of additions to equivalent income validation and outcomes scripts, and tweaks to the pipeline

@@
 title: "Equivalent Income Outcome Visualisation"
-output: html_notebook
+output:
+  html_document:
+    toc: true
+    toc_float: true
+    collapsed: false
+    number_sections: true
+    df_print: paged
+    code_folding: hide
 ---
@@
 require(ggplot2)
+require(here)
+require(dplyr)
+require(tidyr)
+require(purrr)
 
-workingDir <- "/home/luke/Documents/MINOS/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/"
+workingDir <- normalizePath('../')
 knitr::opts_knit$set(root.dir = workingDir)
+knitr::opts_chunk$set(
+  warning = FALSE,
+  message = FALSE
+)
 rm(workingDir)
@@
 ```{r, include=FALSE}
-source('Minos/minos/validation/utils.r')
+source(here::here('minos', 'utils_datain.R'))
+source(here::here('minos', 'utils_validation_vis.R'))
+source(here::here('minos', 'validation', 'utils.r'))
 ```
@@
 # set output path to SIPHER 7 experiment out
-out.path <- 'Minos/output/SIPHER7/'
+out.path <- here::here('output', 'SIPHER7/')
 # read all files into dataframe (util function handles runtime subdirectory etc.)
-base.dat <- read_output(out.path, 'baseline')
-allchild.dat <- read_output(out.path, 'hhIncomeChildUplift')
-pov.dat <- read_output(out.path, 'hhIncomePovertyLineChildUplift')
-wage.dat <- read_output(out.path, 'livingWageIntervention')
-energy.dat <- read_output(out.path, 'energyDownlift')
+base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+allchild.dat <- read_singular_local_out(out.path, 'hhIncomeChildUplift', drop.dead = TRUE)
+pov.dat <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift', drop.dead = TRUE)
+wage.dat <- read_singular_local_out(out.path, 'livingWageIntervention', drop.dead = TRUE)
+energy.dat <- read_singular_local_out(out.path, 'energyDownlift', drop.dead = TRUE)
+```
+
+## Remove 2020 Data Point
+
+```{r}
+base.dat <- filter(base.dat, time > 2020)
+allchild.dat <- filter(allchild.dat, time > 2020)
+pov.dat <- filter(pov.dat, time > 2020)
+wage.dat <- filter(wage.dat, time > 2020)
+energy.dat <- filter(energy.dat, time > 2020)
+```
+
+## BATCH DATA
+
+```{r}
+S7.var.list <- c('hh_income', 'equivalent_income', 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness')
+out.path.batch <- here::here('output', 'SIPHER7_batch/')
+
+base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=TRUE)
+wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
+energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
 ```
@@
 base.subset <- base.dat %>%
-  select(pidp, time, equivalent_income) %>%
+  select(pidp, time, equivalent_income, weight) %>%
   group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income))
+  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
 
@@
 
-ggplot(data = base.subset, aes(x = time, y = equivalent_income)) +
+ggplot(data = base.subset, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
   geom_line()
+```
+
+## Batch
+
+```{r}
+base.bat.sub <- base.batch %>%
+  select(pidp, time, run_id, equivalent_income, weight) %>%
+  group_by(run_id, time) %>%
+  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm=TRUE))
+
+ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
+  geom_line()
+
+ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income)) +
+  geom_smooth()
+
+base.bat.sub2 <- base.bat.sub %>%
+  group_by(time) %>%
+  summarise(var = mean(equivalent_income),
+         min = min(equivalent_income),
+         max = max(equivalent_income))
+
+ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
+  geom_line() +
+  geom_ribbon(aes(ymin = min, ymax = max), 
+                alpha = 0.1,
+                linetype = 'dashed')
 ```
@@
   base.subset <- base %>%
-    select(pidp, time, equivalent_income, alive) %>%
+    select(pidp, time, equivalent_income, alive, weight) %>%
     filter(alive != 'dead') %>%
     group_by(time) %>%
-    summarise(equivalent_income = mean(equivalent_income))
+    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
   int.subset <- int %>%
-    select(pidp, time, equivalent_income, alive) %>%
+    select(pidp, time, equivalent_income, alive, weight) %>%
     filter(alive != 'dead') %>%
     group_by(time) %>%
-    summarise(equivalent_income = mean(equivalent_income))
+    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
 
@@
 }
+
+equivalent_income_comparison_fullpop_batch <- function(base.bat, int.bat, int.name, save=FALSE, save.path=NULL) {
+  base.subset <- base.bat %>%
+    select(pidp, time, run_id, equivalent_income, weight) %>%
+    group_by(time, run_id) %>%
+    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+  int.subset <- int.bat %>%
+    select(pidp, time, run_id, equivalent_income, weight) %>%
+    group_by(time, run_id) %>%
+    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+
+  base.subset$scenario <- 'Baseline'
+  int.subset$scenario <- int.name
+
+  combined <- rbind(base.subset, int.subset)
+
+  p <- ggplot(combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
+    geom_smooth() +
+    labs(title = paste0('Equivalent Income: ', int.name), subtitle = '10 Runs') +
+    xlab('Year') +
+    ylab('Equivalent Income (£)')
+
+  print(p)
+}
 ```
@@
 ```{r}
-equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
+
+equivalent_income_comparison_fullpop_batch(base.batch, wage.batch, 'LivingWage')
+equivalent_income_comparison_fullpop_batch(base.batch, energy.batch, 'EnergyCrisis')
 ```
@@
 base.subset <- base.dat %>%
-  select(pidp, time, equivalent_income, alive) %>%
+  select(pidp, time, equivalent_income, alive, weight) %>%
   filter(alive != 'dead') %>%
   group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income))
+  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
 base.subset$scenario <- 'Baseline'
@@
 allchild.subset <- allchild.dat %>%
-  select(pidp, time, equivalent_income, alive) %>%
+  select(pidp, time, equivalent_income, alive, weight) %>%
   filter(alive != 'dead') %>%
   group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income))
+  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
 allchild.subset$scenario <- 'AllChild'
@@
 pov.subset <- pov.dat %>%
-  select(pidp, time, equivalent_income, alive) %>%
+  select(pidp, time, equivalent_income, alive, weight) %>%
   filter(alive != 'dead') %>%
   group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income))
+  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
 pov.subset$scenario <- 'PovertyChild'
@@
 wage.subset <- wage.dat %>%
-  select(pidp, time, equivalent_income, alive) %>%
+  select(pidp, time, equivalent_income, alive, weight) %>%
   filter(alive != 'dead') %>%
   group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income))
+  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
 wage.subset$scenario <- 'LivingWage'
@@
 energy.subset <- energy.dat %>%
-  select(pidp, time, equivalent_income, alive) %>%
+  select(pidp, time, equivalent_income, alive, weight) %>%
   filter(alive != 'dead') %>%
   group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income))
+  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
 energy.subset$scenario <- 'EnergyDownlift'
@@
 
-# Treatment on the Treated
+# Treated Population
 
@@
 equivalent_income_comparison_treated <- function(base, int, int.name, save=FALSE, save.path=NULL) {
-  base.sub <- base.dat %>%
+  base.sub <- base %>%
     select(pidp, time, equivalent_income, alive) %>%
@@
   int.sub <- int %>%
-    select(pidp, time, equivalent_income, income_boosted, alive) %>%
+    select(pidp, time, equivalent_income, income_boosted, alive, weight) %>%
     filter(alive != 'dead') %>%
     select(-alive) %>%
-    set_names(c('pidp', 'time', int.name, 'income_boosted'))
+    set_names(c('pidp', 'time', int.name, 'income_boosted', 'weight'))
 
@@
     group_by(time, scenario) %>%
-    summarise(equivalent_income = mean(equivalent_income))
+    summarise(equivalent_income = weighted.mean(equivalent_income, w=weight))
 
@@
 }
+
+equivalent_income_comparison_treated_batch <- function(base.bat, int.bat, int.name, save=FALSE, save.path=NULL) {
+  base.sub <- base.bat %>%
+    select(pidp, time, run_id, equivalent_income) %>%
+    rename(baseline = equivalent_income)
+  int.sub <- int.bat %>%
+    select(pidp, time, run_id, equivalent_income, income_boosted, weight) %>%
+    set_names(c('pidp', 'time', 'run_id', int.name, 'income_boosted', 'weight'))
+
+  merged <- merge(base.sub, int.sub, by = c('pidp', 'time', 'run_id'))
+
+  boosted.pidps <- int.sub %>%
+    filter(income_boosted == 'True') %>%
+    select(pidp)
+
+  boosted <- merged %>%
+    filter(pidp %in% boosted.pidps$pidp) %>%
+    filter(income_boosted == 'True' | time == 2020) %>%
+    select(-income_boosted) %>%
+    pivot_longer(cols = baseline:.data[[int.name]],
+                 names_to = 'scenario',
+                 values_to = 'equivalent_income') %>%
+    group_by(time, scenario, run_id) %>%
+    summarise(equivalent_income = weighted.mean(equivalent_income, w=weight))
+
+  p <- ggplot(data = boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
+    geom_smooth() +
+    labs(title = paste0('Equivalent Income: ', int.name), subtitle = 'Treated Population') +
+    xlab('Year') +
+    ylab('Equivalent Income (£)')
+
+  print(p)
+}
 ```
 
-## AllChild
+## Plots
 
 ```{r}
-equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
+
+equivalent_income_comparison_treated_batch(base.batch, wage.batch, 'LivingWage')
+equivalent_income_comparison_treated_batch(base.batch, energy.batch, 'EnergyDownlift')
 ```
@@
 
-```{r}
+```{r, include=FALSE}
 # THink about this...
@@
                values_to = 'equivalent_income')
+```
 
+```{r}
 ggplot(data = allchild.boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
   geom_line()
-
 ```
@@
 ALSO: Difference plots.
+
+# DETAILED ANALYSIS
+
+## Living Wage
+
+For this, we're going to look at the difference in equivalent income and try to explain it by looking at the pathway variables.
+What we want to see is that as income is uplifted, the various pathways show a positive shift and that in part explains the difference in equivalent income.
+
+First visualise both income and equivalent income on one graph.
+
+### Income and Equivalent Income
+
+```{r}
+base.inc <- base.dat %>%
+  select(pidp, time, hh_income, equivalent_income, weight) %>%
+  group_by(time) %>%
+  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
+  mutate(source = 'Baseline')
+
+int.inc <- wage.dat %>%
+  select(pidp, time, hh_income, equivalent_income, weight) %>%
+  group_by(time) %>%
+  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
+  mutate(source = 'Living_Wage')
+
+combined <- rbind(base.inc, int.inc)
+combined <- combined %>%
+  pivot_longer(cols=hh_income:equivalent_income,
+               names_to = 'income_type',
+               values_to = 'value')
+
+ggplot(combined, aes(x = time, y = value, group = source, color = source)) +
+  geom_line() +
+  facet_wrap( ~ income_type, nrow=2, scales='free')
+```
+
+## Energy Crisis
+
+### Housing Quality
+
+```{r}
+S7_ordinal_pathway_vis <- function(base.dat, int.dat, int.name, var) {
+  base.hous <- base.dat %>%
+    select(pidp, time, all_of(var)) %>%
+    group_by(time, .data[[var]]) %>%
+    count() %>%
+    group_by(time) %>%
+    mutate(total = sum(n)) %>%
+    mutate(prop = n / total) %>%
+    select(-n, -total) %>%
+    mutate(source = 'Baseline')
+
+  inc.hous <- int.dat %>%
+    select(pidp, time, all_of(var)) %>%
+    group_by(time, .data[[var]]) %>%
+    count() %>%
+    group_by(time) %>%
+    mutate(total = sum(n)) %>%
+    mutate(prop = n / total) %>%
+    select(-n, -total) %>%
+    mutate(source = int.name)
+
+  combined <- rbind(base.hous, inc.hous)
+  combined[[var]] <- as.factor(combined[[var]])
+
+  p1 <- ggplot(combined, aes(x = time, y = prop, group = interaction(.data[[var]], source), color = .data[[var]], linetype = source)) +
+    geom_line() +
+    geom_point()
+
+  print(p1)
+
+  base.hous2 <- base.dat %>%
+    select(pidp, time, all_of(var)) %>%
+    group_by(time, .data[[var]]) %>%
+    count() %>%
+    group_by(time) %>%
+    mutate(total = sum(n)) %>%
+    mutate(prop = (n / total) * 100) %>%
+    select(-n, -total) %>%
+    rename(Baseline = prop)
+
+  int.hous2 <- int.dat %>%
+    select(pidp, time, all_of(var)) %>%
+    group_by(time, .data[[var]]) %>%
+    count() %>%
+    group_by(time) %>%
+    mutate(total = sum(n)) %>%
+    mutate(prop = (n / total) * 100) %>%
+    select(-n, -total) %>%
+    rename(int = prop)
+
+  combined2 <- merge(base.hous2, int.hous2, by = c('time', var))
+
+  combined2[[var]] <- as.factor(combined2[[var]])
+
+  combined2$diff <- combined2$int - combined2$Baseline
+
+  p2 <- ggplot(combined2, aes(x = time, y = diff, group = .data[[var]], color = .data[[var]])) +
+    geom_line() +
+    geom_point()
+
+  print(p2)
+}
+
+S7_ordinal_pathway_vis_batch <- function(base.bat, int.bat, int.name, var) {
+  base.hous <- base.bat %>%
+    select(pidp, time, run_id, all_of(var)) %>%
+    group_by(time, run_id, .data[[var]]) %>%
+    count() %>%
+    group_by(time, run_id) %>%
+    mutate(total = sum(n)) %>%
+    mutate(prop = n / total) %>%
+    select(-n, -total) %>%
+    mutate(source = 'Baseline')
+
+  inc.hous <- int.bat %>%
+    select(pidp, time, run_id, all_of(var)) %>%
+    group_by(time, run_id, .data[[var]]) %>%
+    count() %>%
+    group_by(time, run_id) %>%
+    mutate(total = sum(n)) %>%
+    mutate(prop = n / total) %>%
+    select(-n, -total) %>%
+    mutate(source = int.name)
+
+  combined <- rbind(base.hous, inc.hous)
+  combined[[var]] <- as.factor(combined[[var]])
+
+  p1 <- ggplot(combined, aes(x = time, y = prop, group = interaction(.data[[var]], source), color = .data[[var]], linetype = source)) +
+    geom_smooth()
+
+  print(p1)
+
+  base.hous2 <- base.bat %>%
+    select(pidp, time, run_id, all_of(var)) %>%
+    group_by(time, run_id, .data[[var]]) %>%
+    count() %>%
+    group_by(time, run_id) %>%
+    mutate(total = sum(n)) %>%
+    mutate(prop = (n / total) * 100) %>%
+    select(-n, -total) %>%
+    rename(Baseline = prop)
+
+  int.hous2 <- int.bat %>%
+    select(pidp, time, run_id, all_of(var)) %>%
+    group_by(time, run_id, .data[[var]]) %>%
+    count() %>%
+    group_by(time, run_id) %>%
+    mutate(total = sum(n)) %>%
+    mutate(prop = (n / total) * 100) %>%
+    select(-n, -total) %>%
+    rename(int = prop)
+
+  combined2 <- merge(base.hous2, int.hous2, by = c('time', 'run_id', var))
+
+  combined2[[var]] <- as.factor(combined2[[var]])
+
+  combined2$diff <- combined2$int - combined2$Baseline
+
+  p2 <- ggplot(combined2, aes(x = time, y = diff, group = .data[[var]], color = .data[[var]]), fill = .data[[var]]) +
+    geom_smooth() +
+    labs(title = paste0(int.name, ': Change from Baseline')) +
+    xlab('Year') +
+    ylab('Change')
+
+  print(p2)
+}
+
+```
+
+### Housing Quality
+
+```{r}
+S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_housing_quality')
+S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_housing_quality')
+```
+
+### Neighbourhood Safety
+
+```{r}
+S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_neighbourhood_safety')
+S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_neighbourhood_safety')
+```
+
+### Mental Wellbeing
+
+```{r}
+S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_mental_health')
+S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_mental_health')
+```
+
+### Physical Health
+
+```{r}
+S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_physical_health')
+S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_physical_health')
+```
+
+### Loneliness
+
+```{r}
+S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'loneliness')
+S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'loneliness')
+```
+
+### Labour State
+
+```{r}
+S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_labour_state')
+S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_labour_state')
+```
+
+```{r}
+boosted.pidps <- energy.dat %>%
+  filter(income_boosted == 'True') %>%
+  select(pidp)
+
+base.hous <- base.dat %>%
+  select(pidp, time, S7_housing_quality) %>%
+  filter(pidp %in% boosted.pidps$pidp) %>%
+  group_by(time, S7_housing_quality) %>%
+  count() %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prop = (n / total) * 100) %>%
+  select(-n, -total) %>%
+  rename(Baseline = prop)
+
+int.hous <- energy.dat %>%
+  select(pidp, time, S7_housing_quality, income_boosted) %>%
+  filter(pidp %in% boosted.pidps$pidp) %>%
+  group_by(time, S7_housing_quality) %>%
+  count() %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prop = (n / total) * 100) %>%
+  select(-n, -total) %>%
+  rename(EnergyCrisis = prop)
+
+combined <- merge(base.hous, int.hous, by = c('time', 'S7_housing_quality'))
+
+combined$diff <- combined$EnergyCrisis - combined$Baseline
+
+ggplot(combined, aes(x = time, y = diff, group = S7_housing_quality, color = S7_housing_quality)) +
+  geom_line() +
+  geom_point()
+```
+
+```{r}
+## just look at means in case the means are causing some problems
+base.dat.2 <- base.dat
+base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'No to all'] <- 1
+base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to some'] <- 2
+base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to all'] <- 3
+wage.dat.2 <- energy.dat
+wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'No to all'] <- 1
+wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to some'] <- 2
+wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to all'] <- 3
+
+base.hous.mean <- base.dat.2 %>%
+  select(pidp, time, S7_housing_quality2, weight) %>%
+  group_by(time) %>%
+  summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
+  mutate(source = 'Baseline')
+wage.hous.mean <- wage.dat.2 %>%
+  select(pidp, time, S7_housing_quality2, weight) %>%
+  group_by(time) %>%
+  summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
+  mutate(source = 'EnergyCrisis')
+
+combined <- rbind(base.hous.mean, wage.hous.mean)
+
+ggplot(combined, aes(x = time, y = mean_housing, group = source, color = source)) +
+  geom_line() +
+  geom_point()
+```
+
+```{r}
+
+df <- combine_and_pivot_long(base.dat, 'Baseline', wage.dat, 'LivingWage', c('S7_housing_quality', 'income_boosted'))
+
+outcomes.prep <- function(base.dat, int.dat, int.name, var) {
+  boosted.pidps <- int.dat %>%
+    filter(income_boosted == 'True') %>%
+    select(pidp, time)
+
+  df1 <- base.dat %>%
+    select(pidp, time, all_of(var), weight) %>%
+
+}
+
+combine_and_pivot_long <- function(df1, df1.name, df2, df2.name, var) {
+  # get only the columns we want a rename
+  df1 <- df1 %>%
+    select('pidp', 'time', all_of(var)) %>%
+    set_names(c('pidp', 'time', df1.name))
+  df2 <- df2 %>%
+    select('pidp', 'time', all_of(var)) %>%
+    set_names(c('pidp', 'time', df2.name))
+  # merge on pidp and time
+  merged <- merge(df1, df2, by = c('pidp', 'time'), all=TRUE)
+  pivoted <- pivot_longer(data = merged,
+                          cols = df1.name:df2.name,
+                          names_to = 'scenario',
+                          values_to = var)
+  return(pivoted)
+}
+
+```

### 2023-08-14 minos/validation/handovers_S7.Rmd
Lots of additions to equivalent income validation and outcomes scripts, and tweaks to the pipeline

@@
 
-shall.we.save <- TRUE
+shall.we.save <- FALSE
+```
+
+# Weight Testing
+
+```{r}
+raw.weight <- raw.dat %>%
+  select(pidp, time, weight) %>%
+  group_by(time) %>%
+  summarise(mean.weight = mean(weight, na.rm = TRUE))
+
+ggplot(raw.weight, aes(x = time, y = mean.weight)) +
+  geom_line()
+
+raw.weight.WBI <- raw.dat %>%
+  select(pidp, time, weight, ethnicity) %>%
+  filter(ethnicity == 'WBI') %>%
+  group_by(time) %>%
+  summarise(mean.weight = mean(weight, na.rm=TRUE))
+
+ggplot(raw.weight.WBI, aes(x=time, y = mean.weight)) +
+  geom_line()
+
+raw.weight.eth <- raw.dat %>%
+  select(pidp, time, weight, ethnicity) %>%
+  group_by(time, ethnicity) %>%
+  summarise(mean.weight = mean(weight, na.rm = TRUE))
+
+ggplot(raw.weight.eth, aes(x = time, y = mean.weight, group = ethnicity, color = ethnicity)) +
+  geom_line()
 ```
@@
 
+### Modified Lineplots
+
+```{r}
+handover_lineplots(raw.dat, base.dat, 'hh_income')
+```
+
 ### Boxplots
@@
 ```{r}
-raw.inc <- raw.dat %>%
-  select(pidp, age, time, hh_income)
-base.inc <- base.dat %>%
-  select(pidp, age, time, hh_income)
-
-income.spag <- rbind(raw.inc, base.inc)
-
-spaghetti_plot(income.spag, 'hh_income',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.inc, base.inc, income.spag)
+# raw.inc <- raw.dat %>%
+#   select(pidp, age, time, hh_income)
+# base.inc <- base.dat %>%
+#   select(pidp, age, time, hh_income)
+# 
+# income.spag <- rbind(raw.inc, base.inc)
+# 
+# spaghetti_plot(income.spag, 'hh_income',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.inc, base.inc, income.spag)
 ```
@@
 raw.ei <- raw.dat %>% 
-  dplyr::select(pidp, time, equivalent_income) %>%
+  dplyr::select(pidp, time, equivalent_income, weight) %>%
+  filter(equivalent_income != -9) %>%
   group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
+  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
   mutate(source = 'final_US')
@@
 base.ei <- base.dat %>%
-  dplyr::select(pidp, time, equivalent_income) %>%
+  dplyr::select(pidp, time, equivalent_income, weight) %>%
   group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
+  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
   mutate(source = 'baseline_output')
@@
 # onwards because the sample refreshments are messing with the plot
-raw.ei.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+raw.ei.wave1 <- raw.dat$pidp[raw.dat$time == 2017]
 
 raw.ei.2 <- raw.dat %>% 
-  dplyr::select(pidp, time, equivalent_income) %>%
+  dplyr::select(pidp, time, equivalent_income, weight) %>%
   filter(pidp %in% raw.ei.wave1) %>%
+  filter(equivalent_income != -9) %>%
   group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
+  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
   mutate(source = 'final_US')
@@
 base.ei.2 <- base.dat %>%
-  dplyr::select(pidp, time, equivalent_income) %>%
+  dplyr::select(pidp, time, equivalent_income, weight) %>%
   filter(pidp %in% raw.ei.wave1) %>%
   group_by(time) %>%
-  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
+  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
   mutate(source = 'baseline_output')
@@
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Equivalent Income', subtitle = 'Wave 1 sample') +
+  labs(title = 'Equivalent Income', subtitle = 'Wave 9 sample') +
   xlab('Year') +
@@
 
+### Modified Lineplots
+
+```{r}
+handover_lineplots(raw.dat, base.dat, 'equivalent_income')
+```
+
+### Check Replenishing Population
+
+Might give us a clue about the big correction in first year of simulation?
+
+```{r}
+repl.file <- here::here('data', 'replenishing', 'replenishing_pop_2019-2070.csv')
+repl.dat <- read.csv(repl.file)
+
+repl.equiv <- repl.dat %>%
+  select(time, equivalent_income, weight) %>%
+  group_by(time) %>%
+  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+ggplot(repl.equiv, aes(x = time, y = equivalent_income)) +
+  geom_line()
+```
+
 ### Boxplots
@@
 ```{r}
-raw.ei <- raw.dat %>%
-  select(pidp, age, time, equivalent_income)
-base.ei <- base.dat %>%
-  select(pidp, age, time, equivalent_income)
-
-ei.spag <- rbind(raw.ei, base.ei)
-
-spaghetti_plot(base.ei, 'equivalent_income')
-
-spaghetti_plot(ei.spag, 'equivalent_income',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.ei, base.ei, ei.spag)
+# raw.ei <- raw.dat %>%
+#   select(pidp, age, time, equivalent_income)
+# base.ei <- base.dat %>%
+#   select(pidp, age, time, equivalent_income)
+# 
+# ei.spag <- rbind(raw.ei, base.ei)
+# 
+# spaghetti_plot(base.ei, 'equivalent_income')
+# 
+# spaghetti_plot(ei.spag, 'equivalent_income',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.ei, base.ei, ei.spag)
 ```
@@
 }
+
+## just look at means in case the means are causing some problems
+raw.dat.2 <- raw.dat
+raw.dat.2$S7_housing_quality2[raw.dat.2$S7_housing_quality == 'No to all'] <- 1
+raw.dat.2$S7_housing_quality2[raw.dat.2$S7_housing_quality == 'Yes to some'] <- 2
+raw.dat.2$S7_housing_quality2[raw.dat.2$S7_housing_quality == 'Yes to all'] <- 3
+base.dat.2 <- base.dat
+base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'No to all'] <- 1
+base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to some'] <- 2
+base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to all'] <- 3
+
+handover_lineplots(raw.dat.2, base.dat.2, 'S7_housing_quality2')
 
@@
 
+## just look at means in case the means are causing some problems
+raw.dat.2 <- raw.dat
+raw.dat.2$S7_neighbourhood_safety2[raw.dat.2$S7_neighbourhood_safety == 'Often'] <- 1
+raw.dat.2$S7_neighbourhood_safety2[raw.dat.2$S7_neighbourhood_safety == 'Some of the time'] <- 2
+raw.dat.2$S7_neighbourhood_safety2[raw.dat.2$S7_neighbourhood_safety == 'Hardly ever'] <- 3
+base.dat.2 <- base.dat
+base.dat.2$S7_neighbourhood_safety2[base.dat.2$S7_neighbourhood_safety == 'Often'] <- 1
+base.dat.2$S7_neighbourhood_safety2[base.dat.2$S7_neighbourhood_safety == 'Some of the time'] <- 2
+base.dat.2$S7_neighbourhood_safety2[base.dat.2$S7_neighbourhood_safety == 'Hardly ever'] <- 3
+
+handover_lineplots(raw.dat.2, base.dat.2, 'S7_neighbourhood_safety2')
+
 rm(prepped.list, nh_safety, nh_safety.norm)
@@
 
+raw.dat.2 <- raw.dat
+raw.dat.2$S7_labour_state2[raw.dat.2$S7_labour_state == 'PT Employed'] <- 6
+raw.dat.2$S7_labour_state2[raw.dat.2$S7_labour_state == 'FT Employed'] <- 5
+raw.dat.2$S7_labour_state2[raw.dat.2$S7_labour_state == 'FT Education'] <- 4
+raw.dat.2$S7_labour_state2[raw.dat.2$S7_labour_state == 'Not Working'] <- 3
+raw.dat.2$S7_labour_state2[raw.dat.2$S7_labour_state == 'Job Seeking'] <- 2
+raw.dat.2$S7_labour_state2[raw.dat.2$S7_labour_state == 'Family Care'] <- 1
+base.dat.2 <- base.dat
+base.dat.2$S7_labour_state2[base.dat.2$S7_labour_state == 'PT Employed'] <- 6
+base.dat.2$S7_labour_state2[base.dat.2$S7_labour_state == 'FT Employed'] <- 5
+base.dat.2$S7_labour_state2[base.dat.2$S7_labour_state == 'FT Education'] <- 4
+base.dat.2$S7_labour_state2[base.dat.2$S7_labour_state == 'Not Working'] <- 3
+base.dat.2$S7_labour_state2[base.dat.2$S7_labour_state == 'Job Seeking'] <- 2
+base.dat.2$S7_labour_state2[base.dat.2$S7_labour_state == 'Family Care'] <- 1
+
+handover_lineplots(raw.dat.2, base.dat.2, 'S7_labour_state2')
+
 rm(prepped.list, lab.state, lab.state.norm)
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, S7_labour_state)
-base.s <- base.dat %>%
-  select(pidp, age, time, S7_labour_state)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'S7_labour_state',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, S7_labour_state)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, S7_labour_state)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'S7_labour_state',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 }
+
+handover_lineplots(raw.dat, base.dat, 'S7_physical_health')
 
@@
 
+handover_lineplots(raw.dat, base.dat, 'S7_mental_health')
+
 rm(prepped.list, var, norm, tit)
@@
 
+## loneliness only available from 2017 onwards
+var <- filter(var, time >= 2017)
+
 # Now plot
@@
 
+handover_lineplots(raw.dat, base.dat, 'loneliness')
+
 rm(prepped.list, var, norm, tit)
@@
                                        var = 'loneliness')
+
+pivoted <- filter(pivoted, time >= 2017)
 
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, education_state)
-base.s <- base.dat %>%
-  select(pidp, age, time, education_state)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'education_state',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, education_state)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, education_state)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'education_state',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```

### 2023-08-15 minos/outcomes/equivalent_income_out.Rmd
Additions to equivalent income visualisation script

@@
 ```{r}
-equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild')
+equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild')
+equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage')
+equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift')
 
@@
 ```{r}
-base.subset <- base.dat %>%
+base.subset <- base.batch %>%
   select(pidp, time, equivalent_income, alive, weight) %>%
@@
   geom_line() +
+  labs(title = 'Equivalent Income Comparison', subtitle = 'Whole Population') +
+  xlab('Year') +
+  ylab('Equivalent Income (£)')
+```
+
+```{r}
+base.subset <- base.batch %>%
+  select(pidp, time, run_id, equivalent_income, weight) %>%
+  group_by(time, run_id) %>%
+  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
+  mutate(scenario = 'Baseline')
+
+wage.subset <- wage.batch %>%
+  select(pidp, time, run_id, equivalent_income, weight) %>%
+  group_by(time, run_id) %>%
+  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
+  mutate(scenario = 'LivingWage')
+
+energy.subset <- energy.batch %>%
+  select(pidp, time, run_id, equivalent_income, weight) %>%
+  group_by(time, run_id) %>%
+  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
+  mutate(scenario = 'EnergyCrisis')
+
+all.combined <- rbind(base.subset, wage.subset, energy.subset)
+all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'LivingWage', 'EnergyCrisis'))
+
+ggplot(data = all.combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
+  geom_smooth() +
   labs(title = 'Equivalent Income Comparison', subtitle = 'Whole Population') +
@@
 ```{r}
-equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild')
+equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild')
+equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage')
+equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift')
 
@@
 ## Energy Crisis
+
+### CHANGE IN INCOME / EQUIVALENT INCOME
+
+```{r}
+base.inc <- base.dat %>%
+  select(pidp, time, hh_income, equivalent_income, weight) %>%
+  group_by(time) %>%
+  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
+  mutate(source = 'Baseline')
+
+int.inc <- wage.dat %>%
+  select(pidp, time, hh_income, equivalent_income, weight) %>%
+  group_by(time) %>%
+  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
+  mutate(source = 'Living_Wage')
+
+combined <- rbind(base.inc, int.inc)
+combined <- combined %>%
+  pivot_longer(cols=hh_income:equivalent_income,
+               names_to = 'income_type',
+               values_to = 'value')
+
+ggplot(combined, aes(x = time, y = value, group = source, color = source)) +
+  geom_line() +
+  facet_wrap( ~ income_type, nrow=2, scales='free')
+```
 

### 2023-08-17 minos/outcomes/equivalent_income_out.Rmd
Add lots of plots to equivalent_income_out.Rmd investigating change in income and equivalent income (and pathways) through interventions

@@
 ```{r}
-base.subset <- base.batch %>%
+base.subset <- base.dat %>%
   select(pidp, time, equivalent_income, alive, weight) %>%
@@
 
-## Energy Crisis
-
 ### CHANGE IN INCOME / EQUIVALENT INCOME
@@
 
-int.inc <- wage.dat %>%
+int.inc <- energy.dat %>%
   select(pidp, time, hh_income, equivalent_income, weight) %>%
@@
             equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
-  mutate(source = 'Living_Wage')
+  mutate(source = 'EnergyCrisis')
 
@@
 ```
+
+How about on the same plot to make it more clear?
+
+```{r}
+income_equivinc_change <- function(base.dat, int.dat) {
+  base.inc <- base.dat %>%
+    select(pidp, time, hh_income, equivalent_income, weight) %>%
+    group_by(time) %>%
+    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  int.inc <- int.dat %>%
+    select(pidp, time, hh_income, equivalent_income, weight) %>%
+    group_by(time) %>%
+    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  combined <- merge(base.inc, int.inc, by = c('time'))
+
+  combined$diff_income <- combined$energy_income - combined$base_income
+  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income
+
+  combined <- combined %>%
+    pivot_longer(cols = diff_income:diff_equiv_income,
+                 names_prefix = 'diff_',
+                 names_to = 'variable',
+                 values_to = 'diff')
+
+  ggplot(combined, aes(x = time, y = diff, group = variable, color = variable)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype = 'dashed')
+}
+
+income_equivinc_change_batch <- function(base.batch, int.batch) {
+  base.inc <- base.batch %>%
+    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
+    group_by(time, run_id) %>%
+    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  int.inc <- int.batch %>%
+    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
+    group_by(time, run_id) %>%
+    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  combined <- merge(base.inc, int.inc, by = c('time', 'run_id'))
+
+  combined$diff_income <- combined$energy_income - combined$base_income
+  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income
+
+  combined <- combined %>%
+    pivot_longer(cols = diff_income:diff_equiv_income,
+                 names_prefix = 'diff_',
+                 names_to = 'variable',
+                 values_to = 'diff')
+
+  ggplot(combined, aes(x = time, y = diff, group = variable, color = variable)) +
+    geom_smooth() +
+    geom_hline(yintercept = 0, linetype = 'dashed')
+}
+
+income_equivinc_change(base.dat, energy.dat)
+income_equivinc_change_batch(base.batch, energy.batch)
+
+income_equivinc_change(base.dat, wage.dat)
+income_equivinc_change_batch(base.batch, wage.batch)
+```
+
+### Percent Change
+
+Proportional difference? Percentage difference in income and equivalent income over time?
+
+```{r}
+income_equivinc_percent_change_batch <- function(base.batch, int.batch) {
+  base.inc <- base.batch %>%
+    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
+    group_by(time, run_id) %>%
+    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  int.inc <- int.batch %>%
+    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
+    group_by(time, run_id) %>%
+    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  combined <- merge(base.inc, int.inc, by = c('time', 'run_id'))
+
+  combined$diff_income <- combined$energy_income - combined$base_income
+  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income
+
+  combined <- combined %>%
+    group_by(time) %>%
+    summarise(mean_income = mean(base_income),
+              mean_equiv_income = mean(base_equiv_income),
+              mean_diff_income = mean(diff_income),
+              mean_diff_equiv_income = mean(diff_equiv_income)) %>%
+    mutate(percent_change_income = (mean_diff_income / mean_income) * 100,
+           percent_change_equiv_income = (mean_diff_equiv_income / mean_equiv_income) * 100) %>%
+    select(-mean_income, -mean_equiv_income, -mean_diff_income, -mean_diff_equiv_income) %>%
+    pivot_longer(cols = percent_change_income:percent_change_equiv_income,
+                 names_prefix = 'percent_change_',
+                 names_to = 'variable',
+                 values_to = 'change')
+
+  ggplot(combined, aes(x = time, y = change, group = variable, color = variable)) +
+    geom_smooth() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    labs(title = 'Percent change: Income vs Equivalent Income') +
+    xlab('Year') +
+    ylab('Percent Change')
+}
+
+income_equivinc_percent_change_batch(base.batch, energy.batch)
+income_equivinc_percent_change_batch(base.batch, wage.batch)
+
+```
+
+## Energy Crisis
 

### 2023-08-17 minos/validation/handovers.Rmd
Tried a marital status module and tried using longitudinal data for nnet models (and used this for education model and predicting max_educ for repl pops

@@
 ```{r}
-raw.s <- raw.parity %>%
-  select(pidp, age, time, nkids_ind)
-base.s <- base.parity %>%
-  select(pidp, age, time, nkids_ind)
+# raw.s <- raw.parity %>%
+#   select(pidp, age, time, nkids_ind)
+# base.s <- base.parity %>%
+#   select(pidp, age, time, nkids_ind)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'nkids_ind',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
+```
+
+## Total nkids
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')
+
+```
+
+## Marital Status
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'marital_status')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Marital Status'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = marital_status, colour = marital_status)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=marital_status)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'marital_status.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, marital_status)
+base.s <- base.dat %>%
+  select(pidp, age, time, marital_status)
 
@@
 
-spaghetti_plot(spag, 'nkids_ind',
+spaghetti_plot(spag, 'marital_status',
                save = shall.we.save,
@@
 
+## Education State
+
 ```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')
 
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Education State'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'education_state.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
 ```

### 2023-08-17 minos/data_generation/generate_repl_pop.py

@@ -65,7 +65,7 @@ def expand_repl(US_2018):
         # now update Date variable (just use US_utils function
         new_repl = US_utils.generate_interview_date_var(new_repl)
         # adjust pidp to ensure unique values (have checked this and made sure this will never give us a duplicate)
-        new_repl['pidp'] = new_repl['pidp'] + year + 1000000 + new_repl.index
+        new_repl['pidp'] = new_repl['pidp'] + year + 1000000 + (5 * new_repl.index)
 
         #print(f"There are {len(new_repl)} people in the replenishing population in year {year}.")
 
@@ -156,7 +156,7 @@ def predict_education(repl, transition_dir):
                     "ordinal": importr('ordinal'),
                     "zeroinfl": importr("pscl"),
                     }
-    transition_model = r_utils.load_transitions("education_state/nnet/education_state_2018_2019", rpy2_modules, path=transition_dir)
+    transition_model = r_utils.load_transitions("education_state/nnet2/education_state_NNET2", rpy2_modules, path=transition_dir)
     prob_df = r_utils.predict_nnet(transition_model, rpy2_modules, repl, cols)
 
     repl['max_educ'] = np.nan

### 2023-08-24 minos/outcomes/paper_1_notebook.Rmd
getting R plots from paper working on new branch

---
title: "Paper 1 Notebook"
output: html_notebook
---

```{r "preamble"}
source("minos/transitions/utils.R")
source("minos/transitions/transition_model_functions.R")
source("minos/transitions/paper_1_plots.R")
library(dplyr)
library(texreg)
library(lme4)
library(glmnet)
library(mice)
library(sjPlot)
library(visreg)
library(ggplot2)
library(ggpattern)
library(VIM)
```

```{r "raw_data_processing"}

dataDir <- "data/raw_US/"
filelist <- list.files(dataDir,
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = '[0-9]{4}_US_cohort.csv')[21:23] # get files for 2011-2013.
raw.data <- do.call(rbind, lapply(filelist, read.csv))

model_formula_string <- "SF_12 ~ factor(sex) + 
                  relevel(factor(ethnicity), ref='WBI') + 
                  scale(age) + 
                  factor(education_state) + 
                  factor(labour_state_raw) + 
                  relevel(factor(job_sec), ref=1) +
                  relevel(factor(region), ref='London') +
                  scale(hh_netinc)"
model_formula <- as.formula(model_formula_string)
variables <- all.vars(model_formula)
variables[1] <- "SF_12"

raw.data <- raw.data[, append(variables, c("time", 'pidp', 'weight'))]

raw.data <- raw.data %>%
        group_by(pidp) %>%
        #mutate(diff = .data[[dependent]] - lag(.data[[dependent]], order_by = time)) %>%
        mutate(last = lag(.data[["SF_12"]], order_by = time)) %>%
        rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff

raw.data <- replace.missing(raw.data)
raw.data <- drop_na(raw.data)
```

```{r "OLS"}

sf12.lm <- lm(model_formula_string,
              data= raw.data)
a<- summary(sf12.lm)
print(a)
print(a$adj.r.squared)

save.path <- "minos/outcomes/paper1_plots/"
create.if.not.exists(save.path)
texreg(sf12.lm, dcolumn=T, booktabs=T, file=paste0(save.path,'ols_coefficients.txt'), custom.model.names=c("OLS"), single.row=T)
save(sf12.lm, file = paste0(save.path,"baseline_OLS.RData"))

write_coefs <- T
if (write_coefs)
{
  texreg_file <- paste0(save.path, 'SF12_OLS_coefficients.txt')
  tex_label <- paste0("table: baseline_OLS_coefficients") 
  tex_headers <- c(texreg::names2latex("Baseline SF_12 OLS"))
  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "ols"))    
  texreg(sf12.lm, # what model to save coefs for. 
         file=texreg_file,  # where to save.
         custom.model.names = tex_headers, # title of table.
         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
         digits=4, # p values significant figures.
         caption=tex_caption, # \caption command option. 
         label = tex_label, # \label command option. 
         dcolumn=T,# nice column alignment. 
         booktabs=T, # nice hlines. (recommended)
         tabular=T,# tabular env.
         single.row = T, # nicer one row formatting.
         longtable=T, # allows tables to wrap over pages
         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
         fontsize='small') # small font
}

forest_plot_lm(sf12.lm, paste0(save.path, "presentation_forest.pdf"))
qq_plot(resid(sf12.lm), paste0(save.path, "presentation_qq.pdf"))
residual_density_plot(res=resid(sf12.lm), file_name=paste0(save.path, "presentation_residual_density.pdf"), guide="normal")

squareRootRes <- sqrt(abs(scale(resid(sf12.lm))))
fitted_residuals <- as.data.frame(cbind(fitted(sf12.lm), squareRootRes))
colnames(fitted_residuals) <- c("fitted", "sqrt_residuals")
fitted_residual_plot(fitted_residuals, paste0(save.path, "presentation_fitted_residual_plot.pdf"))

#visreg(sf12.lm, "age", by="sex", overlay=T)

pdf(paste0(save.path, "total_missingness_structure1.pdf"))
aggr(subset(raw.data[,reg_columns], select=-c(y)), sortVars=T,  oma=c(8,4,4,4), numbers=T, cex.axis=1.0, col = c(blue, orange), prop=F, combined=T, cex.numbers=0.5)
dev.off()

```

```{r final_data_processing}
# new formula and get data from final

dataDir <- "data/composite_US/"
filelist <- list.files(dataDir,
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = '[0-9]{4}_US_cohort.csv')[3:5] # get files for 2011-2013.
final.data <- do.call(rbind, lapply(filelist, read.csv))

# scale(SF_12_last) +
model_formula_string <- "SF_12 ~
                  factor(sex) + 
                  relevel(factor(ethnicity), ref='WBI') + 
                  scale(age) + 
                  scale(I(age**2)) +
                  factor(education_state) + 
                  factor(S7_labour_state) + 
                  relevel(factor(job_sec), ref=1) +
                  relevel(factor(region), ref='London') +
                  scale(hh_income) + 
                  scale(I(hh_income**2)) +
                  (1+time|pidp)"

final.data <- final.data %>%
        group_by(pidp) %>%
        #mutate(diff = .data[[dependent]] - lag(.data[[dependent]], order_by = time)) %>%
        mutate(last = lag(.data[["SF_12"]], order_by = time)) %>%
        rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff

glmm_model_formula <- as.formula(model_formula_string)
variables <- all.vars(glmm_model_formula)
#variables[2] <- "SF_12"

final.data <- final.data[, append(variables, c("time", 'pidp', 'weight'))]

final.data <- replace.missing(final.data)
final.data <- drop_na(final.data)

```

```{r MICE}

dataDir <- "data/composite_US/"
filelist <- list.files(dataDir,
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = '[0-9]{4}_US_cohort.csv')[3:5] # get files for 2011-2013.
mice.data <- do.call(rbind, lapply(filelist, read.csv))
mice.data <-replace.missing(mice.data)

model_formula_string <- "SF_12 ~ factor(sex) + 
                  relevel(factor(ethnicity), ref='WBI') + 
                  scale(age) + 
                  factor(education_state) + 
                  factor(S7_labour_state) + 
                  relevel(factor(job_sec), ref=1) +
                  relevel(factor(region), ref='London') +
                  scale(hh_income)"

# set up MICE and cache data
# plots of missingness pre and post raw US
# figures of convergence and difference in distribution.
cached <- F # if you just want the plots used cached data. MICE can take forever..
imp_columns <- c("SF_12",
                 'sex',
                 "job_sec",
                 "education_state",
                 "S7_labour_state", 
                 "region", 
                 "ethnicity", 
                 "age", 
                 "hh_income")

method <-   c('pmm',
            'pmm',#'polr',
            'pmm',
            'pmm', #'polr',
            'pmm',
            'pmm',
            'pmm',
            'pmm',
            'pmm' )

# structure plots for adding in auxliary variables

pdf(paste0(save.path, "total_missingness_structure2.pdf"))
aggr(subset(mice.data, select=-c(y)), sortVars=T,  oma=c(8,4,4,4), numbers=T, cex.axis=1.0, col = c(blue, orange), prop=F, combined=T, cex.numbers=0.5)
dev.off()

cached<-T
if (cached){
  load('papers/phd1/data/mice_set.RData')
  load('papers/phd1/data/mice_data.RData')
} else{
  pidps <- mice.data$pidp
  save(pidps, file = paste0(save.path, 'mice_pidps.RData'))
  mice.weights <- mice.data$weight
  save(mice.weights, file = paste0(save.path, 'mice_weights.RData'))

  mice_set <- mice(data = mice.data[,imp_columns], method=method,
                   m = 20, maxit = 10,
                   #m = 2, maxit = 2,
                   remove.collinear=T)
  mice.data <- complete(mice_set)

  save(mice_set, file = paste0(save.path,'mice_set.RData'))
  save(mice.data, file = paste0(save.path,'mice_data.RData'))
}

#pdf("papers/phd1/plots/ols_mice_convergence.pdf")
#print(plot(mice_set, y = SF_12 + y ~ .it | .ms))
#dev.off()
pdf(paste0(paste0(save.path,"ols_mice_convergence.pdf")))
print(plot(mice_set, SF_12 = SF_12 ~ .it | .ms))
dev.off()

mice.sf12.lm <- with(mice_set, lm(as.formula(model_formula_string)))
final.pool<- pool(mice.sf12.lm)

pooled_lm <- mice.sf12.lm$analyses[[1]]
pool.sum <- summary(final.pool)
pooled_lm$coefficients = pool.sum$estimate
mice.preds<- predict(pooled_lm)

pool.r.squared(final.pool)

# mice objects dont go in forest plot annoyingly. move coefficients over to a
# dummy lm that plot_models can read.
mice.lm.object <- summary(lm(model_formula_string, data = complete(mice_set)))
mice.lm.object$coefficients[,1] <- pool.sum$estimate
mice.lm.object$coefficients[,2] <- pool.sum$std.error
mice.lm.object$coefficients[,3] <- pool.sum$statistic
mice.lm.object$coefficients[,4] <- pool.sum$p.value
save(mice.lm.object, file = paste0(paste0(save.path,'mice_lm_object.RData')))

#texreg(mice.lm.object, dcolumn=T, booktabs=T, file='../plots/mice_ols_coefficients.txt', title="SF12 MICE OLS Coefficients", custom.model.names=c("SF12 OLS"), single.row=T, include.aic=T)

res <- as.data.frame(predict(pooled_lm))
real <- as.data.frame(data$SF_12)
res$type <- c("Predicted")
real$type <- c("Real")
colnames(res) <- c("SF12", 'type')
colnames(real) <- c("SF12", 'type')
hist.data <- rbind(res,real)
hist.data <- tidyr::drop_na(hist.data)

res <- as.data.frame(resid(pooled_lm))
residual_density_plot(res, paste0(save.path,'mice_ols_densities.pdf'), guide='normal')

forest_plot(mice.lm.object, paste0(save.path,'mice_SF12_forest.pdf'))

write_coefs <- T
if (write_coefs)
{
  texreg_file <- paste0(save.path, 'SF12_MICE_OLS_coefficients.txt')
  tex_label <- paste0("table: MICE_OLS_coefficients") 
  tex_headers <- c(texreg::names2latex("MICE SF_12 OLS"))
  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "ols"))    
  texreg(pooled_lm, # what model to save coefs for. 
         file=texreg_file,  # where to save.
         custom.model.names = tex_headers, # title of table.
         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
         digits=4, # p values significant figures.
         caption=tex_caption, # \caption command option. 
         label = tex_label, # \label command option. 
         dcolumn=T,# nice column alignment. 
         booktabs=T, # nice hlines. (recommended)
         tabular=T,# tabular env.
         single.row = T, # nicer one row formatting.
         longtable=T, # allows tables to wrap over pages
         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
         fontsize='small') # small font
}
```

```{r cross validated nowcasting}
# split data into five
# transition models
# compare coefficients in plots.

```

```{r lasso}
# just import from old paper
lasso.data <- tidyr::drop_na(final.data)
X <- model.matrix(as.formula(model_formula_string), data=lasso.data)
y <- lasso.data$SF_12
weight <- lasso.data$weight
cv.lasso <- cv.glmnet(X, y, family = "gaussian", weights = weight)
lasso <- glmnet(X, y, alpha = 1,  family = "gaussian", weights = weight)

# plots for this.

  pdf(paste0(save.path, 'ols_lasso_2013.pdf'))
  plot(lasso, xvar = "lambda", label = T) 
  abline(v = log(cv.lasso$lambda.min), col = "blue",lty=2)
  abline(v = log(cv.lasso$lambda.1se), col = "red", lty=3)
  legend('bottomright', legend=c("Minimum Standard Error", "First Standard Error"), col=c('blue', 'red'), lty=c(2, 3))
  dev.off()

  pdf(paste0(save.path, 'ols_cv_lasso_2013.pdf'))
  plot(cv.lasso)
  dev.off()

  print(coef(cv.lasso, s = "lambda.min"))
  print(coef(cv.lasso, s = "lambda.1se"))
```

```{r projection of weights}
# get from old paper as well? interesting idea on macro micro
sf12.lm.weighted <- lm(formula, weights = weights, data = final.data)

# plots as with SF12

```

```{r handovers}
# boxplots for handovers
#.estimating from 2014-2020.
# get data for 2013- 2020
# run 2013 pop through transition probability model a few times. 
# profit. 
# run it through model a few times
# compare with real data in boxplots and ridgelines.

dataDir <- "data/raw_US/"
filelist <- list.files(dataDir,
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = '[0-9]{4}_US_cohort.csv')[23:30] # get files for 2011-2013.
raw.data <- do.call(rbind, lapply(filelist, read.csv))
raw.data <- replace.missing(raw.data)
raw.data <- raw.data[, c('pidp', 'time', variables)]
raw.data <- drop_na(raw.data)
```

```{r handovers}
start.data <- raw.data[which(raw.data$time==2013),]
rolling.data <- start.data[, c("pidp", "SF_12", "time")]
handover.data <- rolling.data
for (i in 1:7){
  rolling.data$SF_12 <- predict(sf12.lm, start.data)
  start.data$SF_12 <- rolling.data$SF_12
  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
  handover.data <- rbind(handover.data, rolling.data)
}

handover_boxplots(raw.data, handover.data, "SF_12")
density_ridges(raw.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "raw_ridges")
density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "handover_ridges")

```

## HETEROGENEITY ###############################################################

```{r "glmm"}
glmm.data <- final.data
# yoink transition model function pre processing
reflect <- T
yeo_johnson <- T
include_weights <- T
depend <- "SF_12"
dependent_data <- glmm.data$SF_12

if (reflect) {
    max_value <- nanmax(glmm.data[[depend]])
    glmm.data[, c(depend)] <- max_value - glmm.data[, c(depend)] 
  }
if (yeo_johnson)
{
  yj <- yeojohnson(glmm.data[,c(depend)])
  glmm.data[, c(depend)] <- predict(yj)
}

min_value <- nanmin(glmm.data[[depend]])
glmm.data[[depend]] <- glmm.data[[depend]] - min_value + 0.001

if(include_weights) {
  sf12.glmm.model <- glmer(glmm_model_formula,  
                 nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes forever..
                 family=Gamma(link='log'), # gamma family with log link.
                 weights=weight, 
                 data = glmm.data)
} else {
  sf12.glmm.model <- glmer(model_formula, 
                 nAGQ=0, 
                 family=Gamma(link='log'),
                 data = glmm.data)
}

save(sf12.glmm.model, file = paste0(save.path,"sf12_glmm.RData"))

write_coefs <- T
if (write_coefs)
{
  texreg_file <- paste0(save.path, 'SF_12_GLMM_coefficients.txt')
  tex_label <- paste0("table: GLMM_SF_12_coefficients") 
  tex_headers <- c(texreg::names2latex("SF_12 GLMM"))
  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "glmm"))    
  texreg(glmm.sf12.lm, # what model to save coefs for. 
         file=texreg_file,  # where to save.
         custom.model.names = tex_headers, # title of table.
         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
         digits=4, # p values significant figures.
         caption=tex_caption, # \caption command option. 
         label = tex_label, # \label command option. 
         dcolumn=T,# nice column alignment. 
         booktabs=T, # nice hlines. (recommended)
         tabular=T,# tabular env.
         single.row = T, # nicer one row formatting.
         longtable=T, # allows tables to wrap over pages
         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
         fontsize='small') # small font
}

glmm.fitted <- (max_value - predict(yj, predict(sf12.glmm.model, type='response') + min_value, inverse=T))
glmm.resid <- scale(dependent_data - glmm.fitted)
forest_plot_glmm(sf12.glmm.model, paste0(save.path, "glmm_forest.pdf"))
qq_plot(glmm.resid, paste0(save.path, "glmm_qq.pdf"))
residual_density_plot(res=glmm.resid , file_name=paste0(save.path, "glmm_residual_density.pdf"), guide="normal")

squareRootRes <- sqrt(abs(scale(glmm.resid)))
fitted_residuals <- as.data.frame(cbind(glmm.fitted, squareRootRes))
colnames(fitted_residuals) <- c("fitted", "sqrt_residuals")
fitted_residual_plot(fitted_residuals, paste0(save.path, "glmm_fitted_residual_plot.pdf"))

```

### 2023-08-24 minos/transitions/paper_1_plots.R

@@ -1,0 +1,214 @@
+library(ggplot2)
+library(sjPlot)
+library(ggplot2)
+library(ggpattern)
+#source("papers/phd1/paper_plots.R")
+library(visreg)
+
+# forest plot for lm models. 
+forest_plot_lm <- function(model, file_name){
+  
+  sf12_coefs <- summary(model)$coefficients
+  sf12_coefs <- cbind(sf12_coefs, sf12_coefs[, 4])
+  colnames(sf12_coefs)[5] <- "p.stars"
+  what_ns <- which(sf12_coefs[, "Pr(>|t|)"] > 0.05)
+  what_one_star <- which(sf12_coefs[, "Pr(>|t|)"] <= 0.05)
+  what_two_star <- which(sf12_coefs[, "Pr(>|t|)"] <= 0.01)
+  what_three_star <- which(sf12_coefs[, "Pr(>|t|)"] <= 0.001)
+  
+  sf12_coefs[what_ns, 'p.stars'] <- ""
+  sf12_coefs[what_one_star, 'p.stars'] <- "*"
+  sf12_coefs[what_two_star, 'p.stars'] <- "**"
+  sf12_coefs[what_three_star, 'p.stars'] <- "***"
+  p.stars<- sf12_coefs[, 5]
+  browser()
+  pdf(file_name)
+  p <- plot_model(model, transform=NULL,
+                  title = "") + aes(shape=p.stars)
+  p$data$p.stars[which(p$data$p.stars == "")] <- 'n.s.'
+  p <- p +  scale_shape_manual(name='Significance Level',
+                               limits=c("n.s.", "*", "**", "***"),
+                               breaks=c("n.s.", "*", "**", "***"),
+                               values=c(1, 16, 17, 15)) # cast legend to certain title, variable names and shapes.
+  plot(p)
+  dev.off()
+}
+
+
+forest_plot_glmm <- function(model, file_name){
+  
+  sf12_coefs <- summary(model)$coefficients
+  sf12_coefs <- cbind(sf12_coefs, sf12_coefs[, 4])
+  colnames(sf12_coefs)[5] <- "p.stars"
+  what_ns <- which(sf12_coefs[, "Pr(>|z|)"] > 0.05)
+  what_one_star <- which(sf12_coefs[, "Pr(>|z|)"] <= 0.05)
[…]

### 2023-08-30 minos/outcomes/equivalent_income_out.Rmd
Additions to the equivalent_income_out.Rmd

--- 2023-08-14 minos/outcomes/equivalent_income_out.Rmd
@@
 
-df <- combine_and_pivot_long(base.dat, 'Baseline', wage.dat, 'LivingWage', c('S7_housing_quality', 'income_boosted'))
-
-outcomes.prep <- function(base.dat, int.dat, int.name, var) {
-  boosted.pidps <- int.dat %>%
-    filter(income_boosted == 'True') %>%
-    select(pidp, time)
-
-  df1 <- base.dat %>%
-    select(pidp, time, all_of(var), weight) %>%
-
-}
-
-combine_and_pivot_long <- function(df1, df1.name, df2, df2.name, var) {
-  # get only the columns we want a rename
-  df1 <- df1 %>%
-    select('pidp', 'time', all_of(var)) %>%
-    set_names(c('pidp', 'time', df1.name))
-  df2 <- df2 %>%
-    select('pidp', 'time', all_of(var)) %>%
-    set_names(c('pidp', 'time', df2.name))
-  # merge on pidp and time
-  merged <- merge(df1, df2, by = c('pidp', 'time'), all=TRUE)
-  pivoted <- pivot_longer(data = merged,
-                          cols = df1.name:df2.name,
-                          names_to = 'scenario',
-                          values_to = var)
-  return(pivoted)
-}
+# df <- combine_and_pivot_long(base.dat, 'Baseline', wage.dat, 'LivingWage', c('S7_housing_quality', 'income_boosted'))
+# 
+# outcomes.prep <- function(base.dat, int.dat, int.name, var) {
+#   boosted.pidps <- int.dat %>%
+#     filter(income_boosted == 'True') %>%
+#     select(pidp, time)
+#   
+#   df1 <- base.dat %>%
+#     select(pidp, time, all_of(var), weight) %>%
+#     
+# }
+# 
+# 
+# 
+# 
+# combine_and_pivot_long <- function(df1, df1.name, df2, df2.name, var) {
+#   # get only the columns we want a rename
+#   df1 <- df1 %>%
+#     select('pidp', 'time', all_of(var)) %>%
+#     set_names(c('pidp', 'time', df1.name))
+#   df2 <- df2 %>%
+#     select('pidp', 'time', all_of(var)) %>%
+#     set_names(c('pidp', 'time', df2.name))
+#   # merge on pidp and time
+#   merged <- merge(df1, df2, by = c('pidp', 'time'), all=TRUE)
+#   pivoted <- pivot_longer(data = merged,
+#                           cols = df1.name:df2.name,
+#                           names_to = 'scenario',
+#                           values_to = var)
+#   return(pivoted)
+# }
 

### 2023-08-31 minos/outcomes/equivalent_income_out.Rmd
Additions to testing scripts for equivalent income interventions, and expansion of the local batch logic

--- 2023-08-30 minos/outcomes/equivalent_income_out.Rmd
@@
 
-## BATCH DATA
-
-```{r}
-S7.var.list <- c('hh_income', 'equivalent_income', 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness')
-out.path.batch <- here::here('output', 'SIPHER7_batch/')
-
-base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=TRUE)
-wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
-energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
-```
-
 # Baseline
@@
   geom_line()
-```
-
-## Batch
-
-```{r}
-base.bat.sub <- base.batch %>%
-  select(pidp, time, run_id, equivalent_income, weight) %>%
-  group_by(run_id, time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm=TRUE))
-
-ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
-  geom_line()
-
-ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income)) +
-  geom_smooth()
-
-base.bat.sub2 <- base.bat.sub %>%
-  group_by(time) %>%
-  summarise(var = mean(equivalent_income),
-         min = min(equivalent_income),
-         max = max(equivalent_income))
-
-ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
-  geom_line() +
-  geom_ribbon(aes(ymin = min, ymax = max), 
-                alpha = 0.1,
-                linetype = 'dashed')
 ```
@@
 }
-
-equivalent_income_comparison_fullpop_batch <- function(base.bat, int.bat, int.name, save=FALSE, save.path=NULL) {
-  base.subset <- base.bat %>%
-    select(pidp, time, run_id, equivalent_income, weight) %>%
-    group_by(time, run_id) %>%
-    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
-  int.subset <- int.bat %>%
-    select(pidp, time, run_id, equivalent_income, weight) %>%
-    group_by(time, run_id) %>%
-    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
-
-  base.subset$scenario <- 'Baseline'
-  int.subset$scenario <- int.name
-
-  combined <- rbind(base.subset, int.subset)
-
-  p <- ggplot(combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
-    geom_smooth() +
-    labs(title = paste0('Equivalent Income: ', int.name), subtitle = '10 Runs') +
-    xlab('Year') +
-    ylab('Equivalent Income (£)')
-
-  print(p)
-}
 ```
@@
 ```{r}
-equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-
-equivalent_income_comparison_fullpop_batch(base.batch, wage.batch, 'LivingWage')
-equivalent_income_comparison_fullpop_batch(base.batch, energy.batch, 'EnergyCrisis')
+equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild')
+equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild')
+equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage')
+equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift')
 ```
@@
 }
-
-equivalent_income_comparison_treated_batch <- function(base.bat, int.bat, int.name, save=FALSE, save.path=NULL) {
-  base.sub <- base.bat %>%
-    select(pidp, time, run_id, equivalent_income) %>%
-    rename(baseline = equivalent_income)
-  int.sub <- int.bat %>%
-    select(pidp, time, run_id, equivalent_income, income_boosted, weight) %>%
-    set_names(c('pidp', 'time', 'run_id', int.name, 'income_boosted', 'weight'))
-
-  merged <- merge(base.sub, int.sub, by = c('pidp', 'time', 'run_id'))
-
-  boosted.pidps <- int.sub %>%
-    filter(income_boosted == 'True') %>%
-    select(pidp)
-
-  boosted <- merged %>%
-    filter(pidp %in% boosted.pidps$pidp) %>%
-    filter(income_boosted == 'True' | time == 2020) %>%
-    select(-income_boosted) %>%
-    pivot_longer(cols = baseline:.data[[int.name]],
-                 names_to = 'scenario',
-                 values_to = 'equivalent_income') %>%
-    group_by(time, scenario, run_id) %>%
-    summarise(equivalent_income = weighted.mean(equivalent_income, w=weight))
-
-  p <- ggplot(data = boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
-    geom_smooth() +
-    labs(title = paste0('Equivalent Income: ', int.name), subtitle = 'Treated Population') +
-    xlab('Year') +
-    ylab('Equivalent Income (£)')
-
-  print(p)
-}
 ```
@@
 ```{r}
-equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
-
-equivalent_income_comparison_treated_batch(base.batch, wage.batch, 'LivingWage')
-equivalent_income_comparison_treated_batch(base.batch, energy.batch, 'EnergyDownlift')
+equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild')
+equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild')
+equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage')
+equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift')
 ```
@@
 
+### CHANGE IN INCOME / EQUIVALENT INCOME
+
+```{r}
+base.inc <- base.dat %>%
+  select(pidp, time, hh_income, equivalent_income, weight) %>%
+  group_by(time) %>%
+  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
+  mutate(source = 'Baseline')
+
+int.inc <- energy.dat %>%
+  select(pidp, time, hh_income, equivalent_income, weight) %>%
+  group_by(time) %>%
+  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
+  mutate(source = 'EnergyCrisis')
+
+combined <- rbind(base.inc, int.inc)
+combined <- combined %>%
+  pivot_longer(cols=hh_income:equivalent_income,
+               names_to = 'income_type',
+               values_to = 'value')
+
+ggplot(combined, aes(x = time, y = value, group = source, color = source)) +
+  geom_line() +
+  facet_wrap( ~ income_type, nrow=2, scales='free')
+```
+
+How about on the same plot to make it more clear?
+
+```{r}
+income_equivinc_change <- function(base.dat, int.dat) {
+  base.inc <- base.dat %>%
+    select(pidp, time, hh_income, equivalent_income, weight) %>%
+    group_by(time) %>%
+    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  int.inc <- int.dat %>%
+    select(pidp, time, hh_income, equivalent_income, weight) %>%
+    group_by(time) %>%
+    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  combined <- merge(base.inc, int.inc, by = c('time'))
+
+  combined$diff_income <- combined$energy_income - combined$base_income
+  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income
+
+  combined <- combined %>%
+    pivot_longer(cols = diff_income:diff_equiv_income,
+                 names_prefix = 'diff_',
+                 names_to = 'variable',
+                 values_to = 'diff')
+
+  ggplot(combined, aes(x = time, y = diff, group = variable, color = variable)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype = 'dashed')
+}
+
+income_equivinc_change(base.dat, energy.dat)
+income_equivinc_change(base.dat, wage.dat)
+```
+
 ## Energy Crisis
-
-### Housing Quality
 
@@
 }
-
-S7_ordinal_pathway_vis_batch <- function(base.bat, int.bat, int.name, var) {
-  base.hous <- base.bat %>%
-    select(pidp, time, run_id, all_of(var)) %>%
-    group_by(time, run_id, .data[[var]]) %>%
-    count() %>%
-    group_by(time, run_id) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prop = n / total) %>%
-    select(-n, -total) %>%
-    mutate(source = 'Baseline')
-
-  inc.hous <- int.bat %>%
-    select(pidp, time, run_id, all_of(var)) %>%
-    group_by(time, run_id, .data[[var]]) %>%
-    count() %>%
-    group_by(time, run_id) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prop = n / total) %>%
-    select(-n, -total) %>%
-    mutate(source = int.name)
-
-  combined <- rbind(base.hous, inc.hous)
-  combined[[var]] <- as.factor(combined[[var]])
-
-  p1 <- ggplot(combined, aes(x = time, y = prop, group = interaction(.data[[var]], source), color = .data[[var]], linetype = source)) +
-    geom_smooth()
-
-  print(p1)
-
-  base.hous2 <- base.bat %>%
-    select(pidp, time, run_id, all_of(var)) %>%
-    group_by(time, run_id, .data[[var]]) %>%
-    count() %>%
-    group_by(time, run_id) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prop = (n / total) * 100) %>%
-    select(-n, -total) %>%
-    rename(Baseline = prop)
-
-  int.hous2 <- int.bat %>%
-    select(pidp, time, run_id, all_of(var)) %>%
-    group_by(time, run_id, .data[[var]]) %>%
-    count() %>%
-    group_by(time, run_id) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prop = (n / total) * 100) %>%
-    select(-n, -total) %>%
-    rename(int = prop)
-
-  combined2 <- merge(base.hous2, int.hous2, by = c('time', 'run_id', var))
-
-  combined2[[var]] <- as.factor(combined2[[var]])
-
-  combined2$diff <- combined2$int - combined2$Baseline
-
-  p2 <- ggplot(combined2, aes(x = time, y = diff, group = .data[[var]], color = .data[[var]]), fill = .data[[var]]) +
-    geom_smooth() +
-    labs(title = paste0(int.name, ': Change from Baseline')) +
-    xlab('Year') +
-    ylab('Change')
-
-  print(p2)
-}
-
 ```
@@
 S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_housing_quality')
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_housing_quality')
 ```
@@
 S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_neighbourhood_safety')
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_neighbourhood_safety')
 ```
@@
 S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_mental_health')
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_mental_health')
 ```
@@
 S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_physical_health')
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_physical_health')
 ```
@@
 S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'loneliness')
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'loneliness')
 ```
@@
 S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_labour_state')
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_labour_state')
 ```

### 2023-08-31 minos/outcomes/equivalent_income_out_batch.Rmd
Additions to testing scripts for equivalent income interventions, and expansion of the local batch logic

---
title: "Equivalent Income Outcome Visualisation - Batch out"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(here)
require(dplyr)
require(tidyr)
require(purrr)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

```{r, include=FALSE}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

# Data

## BATCH DATA

```{r}
S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
                 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
                 'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
out.path.batch <- here::here('output', 'SIPHER7_batch/')

base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=TRUE)
wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
```

## Calculate Age Group

```{r}
calc_age_group <- function(batch.dat) {
  batch.dat <- batch.dat %>%
    mutate(age.group = cut(age, 
                            breaks = c(15, 30, 45, 60, 75, 120),
                            labels = c('16-30', '30-45', '45-60', '60-75', '75+')))
  return(batch.dat)
}

base.batch <- calc_age_group(base.batch)
wage.batch <- calc_age_group(wage.batch)
energy.batch <- calc_age_group(energy.batch)
```

# Batch Baseline

```{r}
base.bat.sub <- base.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(run_id, time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm=TRUE))

base.bat.sub$run_id <- as.factor(base.bat.sub$run_id)

ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
  geom_line() +
  labs(title = 'Equivalent Income: Individual Runs')

ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income)) +
  geom_smooth() +
  labs(title = 'Equivalent Income: Smoothed mean')

base.bat.sub2 <- base.bat.sub %>%
  group_by(time) %>%
  summarise(var = mean(equivalent_income),
         min = min(equivalent_income),
         max = max(equivalent_income))

ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
  geom_line() +
  geom_ribbon(aes(ymin = min, ymax = max), 
                alpha = 0.1,
                linetype = 'dashed') +
  labs(title = 'Equivalent Income: Min - Max')
```

# Comparisons

## Function

```{r}
equivalent_income_comparison_fullpop_batch <- function(base.bat, int.bat, int.name, save=FALSE, save.path=NULL) {
  base.subset <- base.bat %>%
    select(pidp, time, run_id, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
  int.subset <- int.bat %>%
    select(pidp, time, run_id, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))

  base.subset$scenario <- 'Baseline'
  int.subset$scenario <- int.name

  combined <- rbind(base.subset, int.subset)

  p <- ggplot(combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
    geom_smooth() +
    labs(title = paste0('Equivalent Income: ', int.name), subtitle = '10 Runs') +
    xlab('Year') +
    ylab('Equivalent Income (£)')

  print(p)
}
```

```{r}
equivalent_income_comparison_fullpop_batch(base.batch, wage.batch, 'LivingWage')
equivalent_income_comparison_fullpop_batch(base.batch, energy.batch, 'EnergyCrisis')
```

```{r}
base.subset <- base.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'Baseline')

wage.subset <- wage.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'LivingWage')

energy.subset <- energy.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'EnergyCrisis')

all.combined <- rbind(base.subset, wage.subset, energy.subset)
all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'LivingWage', 'EnergyCrisis'))

ggplot(data = all.combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
  geom_smooth() +
  labs(title = 'Equivalent Income Comparison', subtitle = 'Whole Population') +
  xlab('Year') +
  ylab('Equivalent Income (£)')
```

# Treated Population

## Function

```{r}
equivalent_income_comparison_treated_batch <- function(base.bat, int.bat, int.name, save=FALSE, save.path=NULL) {
  base.sub <- base.bat %>%
    select(pidp, time, run_id, equivalent_income) %>%
    rename(baseline = equivalent_income)
  int.sub <- int.bat %>%
    select(pidp, time, run_id, equivalent_income, income_boosted, weight) %>%
    set_names(c('pidp', 'time', 'run_id', int.name, 'income_boosted', 'weight'))

  merged <- merge(base.sub, int.sub, by = c('pidp', 'time', 'run_id'))

  boosted.pidps <- int.sub %>%
    filter(income_boosted == 'True') %>%
    select(pidp)

  boosted <- merged %>%
    filter(pidp %in% boosted.pidps$pidp) %>%
    filter(income_boosted == 'True' | time == 2020) %>%
    select(-income_boosted) %>%
    pivot_longer(cols = baseline:.data[[int.name]],
                 names_to = 'scenario',
                 values_to = 'equivalent_income') %>%
    group_by(time, scenario, run_id) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w=weight))

  p <- ggplot(data = boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
    geom_smooth() +
    labs(title = paste0('Equivalent Income: ', int.name), subtitle = 'Treated Population') +
    xlab('Year') +
    ylab('Equivalent Income (£)')

  print(p)
}
```

```{r}
equivalent_income_comparison_treated_batch(base.batch, wage.batch, 'LivingWage')
equivalent_income_comparison_treated_batch(base.batch, energy.batch, 'EnergyDownlift')
```

# DETAILED ANALYSIS

## Living Wage

For this, we're going to look at the difference in equivalent income and try to explain it by looking at the pathway variables. What we want to see is that as income is uplifted, the various pathways show a positive shift and that in part explains the difference in equivalent income.

First visualise both income and equivalent income on one graph.

### Income and Equivalent Income

```{r}
income_equivinc_change_batch <- function(base.batch, int.batch) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  int.inc <- int.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  combined <- merge(base.inc, int.inc, by = c('time', 'run_id'))

  combined$diff_income <- combined$energy_income - combined$base_income
  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income

  combined <- combined %>%
    pivot_longer(cols = diff_income:diff_equiv_income,
                 names_prefix = 'diff_',
                 names_to = 'variable',
                 values_to = 'diff')

  ggplot(combined, aes(x = time, y = diff, group = variable, color = variable)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed')
}

income_equivinc_change_batch(base.batch, energy.batch)
income_equivinc_change_batch(base.batch, wage.batch)
```

### Percent Change

Proportional difference? Percentage difference in income and equivalent income over time?

```{r}
income_equivinc_percent_change_batch <- function(base.batch, int.batch) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  int.inc <- int.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  combined <- merge(base.inc, int.inc, by = c('time', 'run_id'))

  combined$diff_income <- combined$energy_income - combined$base_income
  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income

  combined <- combined %>%
    group_by(time) %>%
    summarise(mean_income = mean(base_income),
              mean_equiv_income = mean(base_equiv_income),
              mean_diff_income = mean(diff_income),
              mean_diff_equiv_income = mean(diff_equiv_income)) %>%
    mutate(percent_change_income = (mean_diff_income / mean_income) * 100,
           percent_change_equiv_income = (mean_diff_equiv_income / mean_equiv_income) * 100) %>%
    select(-mean_income, -mean_equiv_income, -mean_diff_income, -mean_diff_equiv_income) %>%
    pivot_longer(cols = percent_change_income:percent_change_equiv_income,
                 names_prefix = 'percent_change_',
                 names_to = 'variable',
                 values_to = 'change')

  ggplot(combined, aes(x = time, y = change, group = variable, color = variable)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = 'Percent change: Income vs Equivalent Income') +
    xlab('Year') +
    ylab('Percent Change')
}

income_equivinc_percent_change_batch(base.batch, energy.batch)
income_equivinc_percent_change_batch(base.batch, wage.batch)

```

#### By Subpopulation

```{r}
income_equivinc_percent_change_batch_subpop <- function(base.batch, int.batch, filter.var, subpop) {
  print(paste0('Calculating income and equivalent income for ', filter.var, ' == ', subpop))

  base.inc <- base.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight, all_of(filter.var)) %>%
    filter(.data[[filter.var]] == subpop) %>%
    group_by(time, run_id) %>%
    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  int.inc <- int.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight, all_of(filter.var)) %>%
    filter(.data[[filter.var]] == subpop) %>%
    group_by(time, run_id) %>%
    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  combined <- merge(base.inc, int.inc, by = c('time', 'run_id'))

  combined$diff_income <- combined$energy_income - combined$base_income
  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income

  combined <- combined %>%
    group_by(time) %>%
    summarise(mean_income = mean(base_income),
              mean_equiv_income = mean(base_equiv_income),
              mean_diff_income = mean(diff_income),
              mean_diff_equiv_income = mean(diff_equiv_income)) %>%
    mutate(percent_change_income = (mean_diff_income / mean_income) * 100,
           percent_change_equiv_income = (mean_diff_equiv_income / mean_equiv_income) * 100) %>%
    select(-mean_income, -mean_equiv_income, -mean_diff_income, -mean_diff_equiv_income) %>%
    pivot_longer(cols = percent_change_income:percent_change_equiv_income,
                 names_prefix = 'percent_change_',
                 names_to = 'variable',
                 values_to = 'change')

  ggplot(combined, aes(x = time, y = change, group = variable, color = variable)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = paste0('Percent change: ', filter.var, ' == ', subpop)) +
    xlab('Year') +
    ylab('Percent Change')
}

income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, filter.var = 'ethnicity', subpop = 'PAK')
income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, filter.var = 'urban', subpop = '1')
income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, filter.var = 'urban', subpop = '2')
```

#### On the Same Plot

```{r}
equivinc_percent_change_batch_subpop <- function(base.batch, int.batch, int.name, group.var) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, equivalent_income, weight, all_of(group.var)) %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    summarise(base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  int.inc <- int.batch %>%
    select(pidp, time, run_id, equivalent_income, weight, all_of(group.var)) %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    summarise(int_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  combined <- merge(base.inc, int.inc, by = c('time', 'run_id', group.var))
  combined[[group.var]] <- as.factor(combined[[group.var]])

  combined$diff_equiv_income <- combined$int_equiv_income - combined$base_equiv_income

  combined <- combined %>%
    group_by(time, .data[[group.var]]) %>%
    summarise(mean_equiv_income = mean(base_equiv_income),
              mean_diff_equiv_income = mean(diff_equiv_income)) %>%
    mutate(percent_change_equiv_income = (mean_diff_equiv_income / mean_equiv_income) * 100) %>%
    select(-mean_equiv_income, -mean_diff_equiv_income)# %>%
    #pivot_longer(cols = percent_change_income:percent_change_equiv_income,
    #             names_prefix = 'percent_change_',
    #             names_to = 'variable',
    #             values_to = 'change')

  ggplot(combined, aes(x = time, y = percent_change_equiv_income, group = .data[[group.var]], color = .data[[group.var]])) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = paste0('Percent change by ', group.var), subtitle = int.name) +
    xlab('Year') +
    ylab('Percent Change')
}

# 'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')

equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'housing_tenure')

equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'age.group')
```

```{r}
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'housing_tenure')
```

## Energy Crisis

```{r}
S7_ordinal_pathway_vis_batch <- function(base.bat, int.bat, int.name, var) {
  base.hous <- base.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = 'Baseline')

  inc.hous <- int.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = int.name)

  combined <- rbind(base.hous, inc.hous)
  combined[[var]] <- as.factor(combined[[var]])

  p1 <- ggplot(combined, aes(x = time, y = prop, group = interaction(.data[[var]], source), color = .data[[var]], linetype = source)) +
    geom_smooth()

  print(p1)

  base.hous2 <- base.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = (n / total) * 100) %>%
    select(-n, -total) %>%
    rename(Baseline = prop)

  int.hous2 <- int.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = (n / total) * 100) %>%
    select(-n, -total) %>%
    rename(int = prop)

  combined2 <- merge(base.hous2, int.hous2, by = c('time', 'run_id', var))

  combined2[[var]] <- as.factor(combined2[[var]])

  combined2$diff <- combined2$int - combined2$Baseline

  p2 <- ggplot(combined2, aes(x = time, y = diff, group = .data[[var]], color = .data[[var]]), fill = .data[[var]]) +
    geom_smooth() +
    labs(title = paste0(int.name, ': Change from Baseline')) +
    xlab('Year') +
    ylab('Change')

  print(p2)
}
```

### Housing Quality

```{r}
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_housing_quality')
```

### Neighbourhood Safety

```{r}
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_neighbourhood_safety')
```

### Mental Wellbeing

```{r}
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_mental_health')
```

### Physical Health

```{r}
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_physical_health')
```

### Loneliness

```{r}
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'loneliness')
```

### Labour State

```{r}
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_labour_state')
```

```{r}

```

### 2023-09-03 minos/outcomes/equivalent_income_out_batch.Rmd
Testing the addition of a job_sec module for transitioning to different job types. Could be quite important for equivalent income

@@
 
-base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=TRUE)
-wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
-energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
+base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
+wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
 ```
@@
 energy.batch <- calc_age_group(energy.batch)
+child.batch <- calc_age_group(child.batch)
+pov.batch <- calc_age_group(pov.batch)
 ```
@@
 equivalent_income_comparison_fullpop_batch(base.batch, energy.batch, 'EnergyCrisis')
+equivalent_income_comparison_fullpop_batch(base.batch, child.batch, 'AllChild')
+equivalent_income_comparison_fullpop_batch(base.batch, pov.batch, 'PovertyChild')
 ```
@@
 
-all.combined <- rbind(base.subset, wage.subset, energy.subset)
-all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'LivingWage', 'EnergyCrisis'))
+child.subset <- child.batch %>%
+  select(pidp, time, run_id, equivalent_income, weight) %>%
+  group_by(time, run_id) %>%
+  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
+  mutate(scenario = 'AllChild')
+
+pov.subset <- pov.batch %>%
+  select(pidp, time, run_id, equivalent_income, weight) %>%
+  group_by(time, run_id) %>%
+  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
+  mutate(scenario = 'PovertyChild')
+
+all.combined <- rbind(base.subset, wage.subset, energy.subset, child.subset, pov.subset)
+all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'LivingWage', 'EnergyCrisis', 'AllChild', 'PovertyChild'))
 
@@
 equivalent_income_comparison_treated_batch(base.batch, energy.batch, 'EnergyDownlift')
+equivalent_income_comparison_treated_batch(base.batch, child.batch, 'AllChild')
+equivalent_income_comparison_treated_batch(base.batch, pov.batch, 'PovertyChild')
 ```
@@
 # DETAILED ANALYSIS
-
-## Living Wage
 
@@
 
-### Income and Equivalent Income
+## Income and Equivalent Income
 
@@
 income_equivinc_change_batch(base.batch, wage.batch)
+income_equivinc_change_batch(base.batch, child.batch)
+income_equivinc_change_batch(base.batch, pov.batch)
 ```
 
-### Percent Change
+## Percent Change
 
@@
 income_equivinc_percent_change_batch(base.batch, wage.batch)
-
+income_equivinc_percent_change_batch(base.batch, child.batch)
+income_equivinc_percent_change_batch(base.batch, pov.batch)
 ```
 
-#### By Subpopulation
+### By Subpopulation
 
@@
 
-#### On the Same Plot
+### All Subgroups
 
@@
 
-# 'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
-
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'ethnicity')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'urban')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'age.group')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'region')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'job_sec')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'education_state')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'nkids_ind')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'housing_tenure')
-
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'age.group')
-```
-
-```{r}
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'ethnicity')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'urban')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'age.group')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'region')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'job_sec')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'education_state')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'nkids_ind')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'housing_tenure')
-```
-
-## Energy Crisis
-
-```{r}
 S7_ordinal_pathway_vis_batch <- function(base.bat, int.bat, int.name, var) {
@@
 
-### Housing Quality
+#### Energy Crisis
 
 ```{r}
+equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'ethnicity')
+equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'urban')
+equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'age.group')
+equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'region')
+equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'job_sec')
+equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'education_state')
+equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'nkids_ind')
+equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'housing_tenure')
+
 S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_housing_quality')
+S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_neighbourhood_safety')
+S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_mental_health')
+S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_physical_health')
+S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'loneliness')
+S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_labour_state')
 ```
 
-### Neighbourhood Safety
+#### Living Wage
 
 ```{r}
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_neighbourhood_safety')
+equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'ethnicity')
+equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'urban')
+equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'age.group')
+equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'region')
+equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'job_sec')
+equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'education_state')
+equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'nkids_ind')
+equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'housing_tenure')
+
+S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_housing_quality')
+S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_neighbourhood_safety')
+S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_mental_health')
+S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_physical_health')
+S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'loneliness')
+S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_labour_state')
 ```
 
-### Mental Wellbeing
+#### All Child
 
 ```{r}
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_mental_health')
+equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'ethnicity')
+equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'urban')
+equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'age.group')
+equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'region')
+equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'job_sec')
+equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'education_state')
+equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'nkids_ind')
+equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'housing_tenure')
+
+S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_housing_quality')
+S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_neighbourhood_safety')
+S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_mental_health')
+S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_physical_health')
+S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'loneliness')
+S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_labour_state')
 ```
 
-### Physical Health
+#### Poverty Child
 
 ```{r}
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_physical_health')
-```
+equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'ethnicity')
+equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'urban')
+equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'age.group')
+equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'region')
+equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'job_sec')
+equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'education_state')
+equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'nkids_ind')
+equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'housing_tenure')
 
-### Loneliness
-
-```{r}
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'loneliness')
-```
-
-### Labour State
-
-```{r}
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_labour_state')
+S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_housing_quality')
+S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_neighbourhood_safety')
+S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_mental_health')
+S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_physical_health')
+S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'loneliness')
+S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_labour_state')
 ```

### 2023-09-03 minos/validation/cross_validation_S7.Rmd
Testing the addition of a job_sec module for transitioning to different job types. Could be quite important for equivalent income

--- 2023-07-05 minos/validation/cross_validation_S7.Rmd
@@
 
+# Parity
+
 ```{r}
+cv.parity <- cv %>%
+  filter(sex == "Female")
 
+raw.parity <- raw %>%
+  filter(sex == "Female")
+
+parity.pivoted <- combine_and_pivot_long(df1 = cv.parity, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw.parity, 
+                                          df2.name = 'raw', 
+                                          var = 'nkids_ind')
+
+cv_ordinal_plots(pivoted.df = parity.pivoted, 
+                 var = 'nkids_ind',
+                 save = FALSE)
+rm(educ.pivoted)
 ```
+
+# Job NSSEC
+
+```{r}
+job_sec.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'job_sec')
+
+cv_ordinal_plots(pivoted.df = job_sec.pivoted, 
+                 var = 'job_sec',
+                 save = FALSE)
+rm(mstat.pivoted)
+```

### 2023-09-03 minos/validation/handovers.Rmd
Testing the addition of a job_sec module for transitioning to different job types. Could be quite important for equivalent income

@@
 ```
+
+## Job Sec
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'job_sec')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Job NSSEC'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = job_sec, colour = job_sec)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=job_sec)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'job_sec.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```

### 2023-09-03 minos/validation/handovers_S7.Rmd
Testing the addition of a job_sec module for transitioning to different job types. Could be quite important for equivalent income

@@
 
+## Job Sec
+
 ```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'job_sec')
 
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Job NSSEC'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = job_sec, colour = job_sec)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=job_sec)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'job_sec.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
 ```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat,
+                                  df1.name = 'simulated', 
+                                  df2 = raw.dat, 
+                                  df2.name = 'raw', 
+                                  var = 'job_sec')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'job_sec',
+                 save = shall.we.save,
+                 save.path = save.path)
+```

### 2023-09-04 minos/outcomes/equivalent_income_out_batch.Rmd
Additions to equivalent income batch test script

@@
 ```{r}
-S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
-                 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
-                 'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
-out.path.batch <- here::here('output', 'SIPHER7_batch/')
+# S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
+#                  'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
+#                  'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
+# out.path.batch <- here::here('output', 'SIPHER7_batch/')
+# 
+# base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
+# wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+# energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+# child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+# pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
 
-base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
-wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+out.path.arc <- here::here('output', 'SIPHER7_batch_ARC/')
+
+base.batch <- read.csv(paste0(out.path.arc, 'baseline_batch_aggregated.csv'))
+wage.batch <- read.csv(paste0(out.path.arc, 'wage_batch_aggregated.csv'))
+energy.batch <- read.csv(paste0(out.path.arc, 'energy_batch_aggregated.csv'))
+child.batch <- read.csv(paste0(out.path.arc, 'child_batch_aggregated.csv'))
+pov.batch <- read.csv(paste0(out.path.arc, 'pov_batch_aggregated.csv'))
 ```
@@
 
+## Calculate Income Quintile
+
+```{r}
+calc_income_quintile <- function(batch.dat) {
+  batch.dat <- batch.dat %>%
+    mutate(income.quint = cut(batch.dat$hh_income, breaks=c(quantile(batch.dat$hh_income, probs = seq(0, 1, by = 0.20))), 
+                          labels=c(1,2,3,4,5), include.lowest=TRUE))
+}
+
+base.batch <- calc_income_quintile(base.batch)
+wage.batch <- calc_income_quintile(wage.batch)
+energy.batch <- calc_income_quintile(energy.batch)
+child.batch <- calc_income_quintile(child.batch)
+pov.batch <- calc_income_quintile(pov.batch)
+```
+
 # Batch Baseline
+
+## Household Income
+
+```{r}
+base.bat.sub <- base.batch %>%
+  select(pidp, time, run_id, hh_income, weight) %>%
+  group_by(run_id, time) %>%
+  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm=TRUE))
+
+base.bat.sub$run_id <- as.factor(base.bat.sub$run_id)
+
+big.run.id <- base.bat.sub$run_id[which.max(base.bat.sub$hh_income)]
+
+base.bat.sub12 <- base.bat.sub %>%
+  filter(run_id != big.run.id)
+
+ggplot(data = base.bat.sub, aes(x = time, y = hh_income, group=run_id, color = run_id)) +
+  geom_line() +
+  labs(title = 'Household Income: Individual Runs')
+
+ggplot(data = base.bat.sub12, aes(x = time, y = hh_income, group=run_id, color = run_id)) +
+  geom_line() +
+  labs(title = 'Household Income: Individual Runs')
+
+ggplot(data = base.bat.sub, aes(x = time, y = hh_income)) +
+  geom_smooth() +
+  labs(title = 'Household Income: Smoothed mean')
+
+ggplot(data = base.bat.sub12, aes(x = time, y = hh_income)) +
+  geom_smooth() +
+  labs(title = 'Household Income: Smoothed mean')
+
+base.bat.sub2 <- base.bat.sub %>%
+  group_by(time) %>%
+  summarise(var = mean(hh_income),
+         min = min(hh_income),
+         max = max(hh_income))
+
+base.bat.sub22 <- base.bat.sub12 %>%
+  group_by(time) %>%
+  summarise(var = mean(hh_income),
+         min = min(hh_income),
+         max = max(hh_income))
+
+ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
+  geom_line() +
+  geom_ribbon(aes(ymin = min, ymax = max), 
+                alpha = 0.1,
+                linetype = 'dashed') +
+  labs(title = 'Household Income: Min - Max')
+
+ggplot(data = base.bat.sub22, aes(x = time, y = var)) +
+  geom_line() +
+  geom_ribbon(aes(ymin = min, ymax = max), 
+                alpha = 0.1,
+                linetype = 'dashed') +
+  labs(title = 'Household Income: Min - Max')
+```
+
+## Equivalent Income
 
@@
 
+big.run.id <- base.bat.sub$run_id[which.max(base.bat.sub$equivalent_income)]
+
+base.bat.sub12 <- base.bat.sub %>%
+  filter(run_id != big.run.id)
+
 ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
@@
 
+ggplot(data = base.bat.sub12, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
+  geom_line() +
+  labs(title = 'Equivalent Income: Individual Runs')
+
 ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income)) +
+  geom_smooth() +
+  labs(title = 'Equivalent Income: Smoothed mean')
+
+ggplot(data = base.bat.sub12, aes(x = time, y = equivalent_income)) +
   geom_smooth() +
@@
 
+base.bat.sub22 <- base.bat.sub12 %>%
+  group_by(time) %>%
+  summarise(var = mean(equivalent_income),
+         min = min(equivalent_income),
+         max = max(equivalent_income))
+
 ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
+  geom_line() +
+  geom_ribbon(aes(ymin = min, ymax = max), 
+                alpha = 0.1,
+                linetype = 'dashed') +
+  labs(title = 'Equivalent Income: Min - Max')
+
+ggplot(data = base.bat.sub22, aes(x = time, y = var)) +
   geom_line() +
@@
 ```{r}
+equivalent_income_comparison_fullpop_batch(base.batch, energy.batch, 'EnergyCrisis')
 equivalent_income_comparison_fullpop_batch(base.batch, wage.batch, 'LivingWage')
-equivalent_income_comparison_fullpop_batch(base.batch, energy.batch, 'EnergyCrisis')
 equivalent_income_comparison_fullpop_batch(base.batch, child.batch, 'AllChild')
@@
 
-First visualise both income and equivalent income on one graph.
-
 ## Income and Equivalent Income
@@
 ```{r}
-income_equivinc_change_batch <- function(base.batch, int.batch) {
+income_equivinc_change_batch <- function(base.batch, int.batch, int.name) {
   base.inc <- base.batch %>%
@@
 
+  combined2 <- combined %>%
+    group_by(time, variable) %>%
+    summarise(mean.diff = mean(diff))
+
+  print(combined2)
+
   ggplot(combined, aes(x = time, y = diff, group = variable, color = variable)) +
     geom_smooth() +
-    geom_hline(yintercept = 0, linetype = 'dashed')
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    labs(title = 'Change in Income and Equivalent Income', 
+         subtitle = int.name)
 }
 
-income_equivinc_change_batch(base.batch, energy.batch)
-income_equivinc_change_batch(base.batch, wage.batch)
-income_equivinc_change_batch(base.batch, child.batch)
-income_equivinc_change_batch(base.batch, pov.batch)
+income_equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
+income_equivinc_change_batch(base.batch, wage.batch, 'Living Wage')
+income_equivinc_change_batch(base.batch, child.batch, 'All Child')
+income_equivinc_change_batch(base.batch, pov.batch, 'Poverty Child')
+```
+
+## Equivalent Income Change
+
+```{r}
+equivinc_change_batch <- function(base.batch, int.batch, int.name) {
+  base.inc <- base.batch %>%
+    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
+    group_by(time, run_id) %>%
+    summarise(base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  int.inc <- int.batch %>%
+    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
+    group_by(time, run_id) %>%
+    summarise(energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  combined <- merge(base.inc, int.inc, by = c('time', 'run_id'))
+
+  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income
+
+  #print(combined)
+
+  ggplot(combined, aes(x = time, y = diff_equiv_income)) +
+    geom_smooth() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    labs(title = 'Percent change: Income vs Equivalent Income',
+         subtitle = int.name) +
+    xlab('Year') +
+    ylab('Percent Change')
+}
+
+equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
+equivinc_change_batch(base.batch, wage.batch, 'Living Wage')
+equivinc_change_batch(base.batch, child.batch, 'All Child')
+equivinc_change_batch(base.batch, pov.batch, 'Poverty Child')
+```
+
+### By Subpopulation
+
+```{r}
+equivinc_change_batch_subpop <- function(base.batch, int.batch, int.name, group.var) {
+  base.inc <- base.batch %>%
+    select(pidp, time, run_id, equivalent_income, weight, all_of(group.var)) %>%
+    group_by(time, run_id, .data[[group.var]]) %>%
+    summarise(base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  int.inc <- int.batch %>%
+    select(pidp, time, run_id, equivalent_income, weight, all_of(group.var)) %>%
+    group_by(time, run_id, .data[[group.var]]) %>%
+    summarise(int_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  combined <- merge(base.inc, int.inc, by = c('time', 'run_id', group.var))
+  combined[[group.var]] <- as.factor(combined[[group.var]])
+
+  combined$diff_equiv_income <- combined$int_equiv_income - combined$base_equiv_income
+
+  combined <- combined %>%
+    group_by(time, .data[[group.var]]) %>%
+    summarise(mean_diff_equiv_income = mean(diff_equiv_income))
+
+  ggplot(combined, aes(x = time, y = mean_diff_equiv_income, group = .data[[group.var]], color = .data[[group.var]])) +
+    geom_smooth() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    labs(title = paste0('Equivalent Income change by ', group.var), subtitle = int.name) +
+    xlab('Year') +
+    ylab('Equivalent Income (£s)')
+}
+
+equivinc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
+equivinc_change_batch_subpop(base.batch, wage.batch, 'Living Wage', group.var = 'income.quint')
+equivinc_change_batch_subpop(base.batch, child.batch, 'All Child', group.var = 'income.quint')
+equivinc_change_batch_subpop(base.batch, pov.batch, 'Poverty Child', group.var = 'income.quint')
 ```
@@
 ```{r}
-income_equivinc_percent_change_batch <- function(base.batch, int.batch) {
+income_equivinc_percent_change_batch <- function(base.batch, int.batch, int.name) {
   base.inc <- base.batch %>%
@@
     geom_hline(yintercept = 0, linetype = 'dashed') +
-    labs(title = 'Percent change: Income vs Equivalent Income') +
+    labs(title = 'Percent change: Income vs Equivalent Income',
+         subtitle = int.name) +
     xlab('Year') +
@@
 
-income_equivinc_percent_change_batch(base.batch, energy.batch)
-income_equivinc_percent_change_batch(base.batch, wage.batch)
-income_equivinc_percent_change_batch(base.batch, child.batch)
-income_equivinc_percent_change_batch(base.batch, pov.batch)
+income_equivinc_percent_change_batch(base.batch, energy.batch, 'Energy Crisis')
+income_equivinc_percent_change_batch(base.batch, wage.batch, 'Living Wage')
+income_equivinc_percent_change_batch(base.batch, child.batch, 'All Child')
+income_equivinc_percent_change_batch(base.batch, pov.batch, 'Poverty Child')
 ```
@@
 ```{r}
-income_equivinc_percent_change_batch_subpop <- function(base.batch, int.batch, filter.var, subpop) {
+income_equivinc_percent_change_batch_subpop <- function(base.batch, int.batch, int.name, filter.var, subpop) {
   print(paste0('Calculating income and equivalent income for ', filter.var, ' == ', subpop))
@@
     geom_hline(yintercept = 0, linetype = 'dashed') +
-    labs(title = paste0('Percent change: ', filter.var, ' == ', subpop)) +
+    labs(title = paste0('Percent change: ', filter.var, ' == ', subpop),
+         subtitle = int.name) +
     xlab('Year') +
@@
 
-income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, filter.var = 'ethnicity', subpop = 'PAK')
-income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, filter.var = 'urban', subpop = '1')
-income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, filter.var = 'urban', subpop = '2')
+income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'ethnicity', subpop = 'PAK')
+income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'urban', subpop = '1')
+income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'urban', subpop = '2')
+income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'income.quint', subpop = '1')
+income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'income.quint', subpop = '5')
 ```
@@
 ```{r}
+equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'income.quint')
 equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'ethnicity')
@@
 ```{r}
+equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'income.quint')
 equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'ethnicity')
@@
 ```{r}
+equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'income.quint')
 equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'ethnicity')
@@
 ```{r}
+equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'income.quint')
 equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'ethnicity')

### 2023-09-07 minos/outcomes/paper_1_notebook.Rmd
big beefing up of validation section for paper notebook

@@
 library(VIM)
+library(caret)
+library(tidyverse)
+
 ```
+
+##############################
+# baseline and presentation ##
+##############################
 
@@
 
-model_formula_string <- "SF_12 ~ factor(sex) + 
+raw_model_formula_string <- "SF_12 ~ factor(sex) + 
                   relevel(factor(ethnicity), ref='WBI') + 
@@
                   scale(hh_netinc)"
-model_formula <- as.formula(model_formula_string)
-variables <- all.vars(model_formula)
+raw_model_formula <- as.formula(raw_model_formula_string)
+variables <- all.vars(raw_model_formula)
 variables[1] <- "SF_12"
@@
 raw.data <- replace.missing(raw.data)
+
+#visreg(sf12.lm, "age", by="sex", overlay=T)
+
+pdf(paste0(save.path, "total_missingness_structure1.pdf"))
+aggr(raw.data[,variables], sortVars=T,  oma=c(8,4,4,4), numbers=T, cex.axis=1.0, col = c(blue, orange), prop=F, combined=T, cex.numbers=0.5)
+dev.off()
+
 raw.data <- drop_na(raw.data)
@@
 
-sf12.lm <- lm(model_formula_string,
+sf12.lm <- lm(raw_model_formula_string,
               data= raw.data)
@@
 
-#visreg(sf12.lm, "age", by="sex", overlay=T)
-
-pdf(paste0(save.path, "total_missingness_structure1.pdf"))
-aggr(subset(raw.data[,reg_columns], select=-c(y)), sortVars=T,  oma=c(8,4,4,4), numbers=T, cex.axis=1.0, col = c(blue, orange), prop=F, combined=T, cex.numbers=0.5)
-dev.off()
-
 ```
 
-```{r final_data_processing}
+```{r composite_data_processing}
 # new formula and get data from final
@@
                   scale(hh_income) + 
-                  scale(I(hh_income**2)) +
-                  (1+time|pidp)"
+                  scale(I(hh_income**2))"
 
@@
 
+##################################
+# missingness ####################
+##################################
+
 ```{r MICE}
@@
                        pattern = '[0-9]{4}_US_cohort.csv')[3:5] # get files for 2011-2013.
-mice.data <- do.call(rbind, lapply(filelist, read.csv))
-mice.data <-replace.missing(mice.data)
+composite.data <- do.call(rbind, lapply(filelist, read.csv))
+composite.data <- replace.missing(composite.data)
 
-model_formula_string <- "SF_12 ~ factor(sex) + 
-                  relevel(factor(ethnicity), ref='WBI') + 
-                  scale(age) + 
-                  factor(education_state) + 
-                  factor(S7_labour_state) + 
-                  relevel(factor(job_sec), ref=1) +
-                  relevel(factor(region), ref='London') +
-                  scale(hh_income)"
+pdf(paste0(save.path, "total_missingness_structure2.pdf"))
+aggr(composite.data[, all.vars(as.formula(model_formula_string))], sortVars=T,  oma=c(8,4,4,4), numbers=T, cex.axis=1.0, col = c(blue, orange), prop=F, combined=T, cex.numbers=0.5)
+dev.off()
+
+mice_pidps <- composite.data$pidp
+mice_weights <- composite.data$weight
+mice_time <- composite.data$time
+
+model_formula_string <- "SF_12 ~ factor(sex) +  relevel(factor(ethnicity), ref='WBI') + scale(age) + factor(education_state) + factor(S7_labour_state) + relevel(factor(job_sec), ref=1) + relevel(factor(region), ref='London') + scale(hh_income)"
 
@@
 # figures of convergence and difference in distribution.
-cached <- F # if you just want the plots used cached data. MICE can take forever..
 imp_columns <- c("SF_12",
@@
             'pmm',
-            'pmm' )
+            'pmm')
 
@@
 
-pdf(paste0(save.path, "total_missingness_structure2.pdf"))
-aggr(subset(mice.data, select=-c(y)), sortVars=T,  oma=c(8,4,4,4), numbers=T, cex.axis=1.0, col = c(blue, orange), prop=F, combined=T, cex.numbers=0.5)
-dev.off()
-
-cached<-T
+cached<-F
 if (cached){
@@
 } else{
-  pidps <- mice.data$pidp
+  pidps <- composite.data$pidp
   save(pidps, file = paste0(save.path, 'mice_pidps.RData'))
-  mice.weights <- mice.data$weight
+  mice.weights <- composite.data$weight
   save(mice.weights, file = paste0(save.path, 'mice_weights.RData'))
 
-  mice_set <- mice(data = mice.data[,imp_columns], method=method,
+  mice_set <- mice(data = composite.data[,imp_columns], method=method,
                    m = 20, maxit = 10,
@@
   mice.data <- complete(mice_set) 
+  mice.data$weight <- mice_weights
+  mice.data$pidp <- mice_pidps
+  mice.data$time <-mice_time
 
@@
   tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "ols"))    
-  texreg(pooled_lm, # what model to save coefs for. 
+  texreg(mice.lm.object, # what model to save coefs for. 
          file=texreg_file,  # where to save.
@@
 
+############################
+# validation ###############
+############################
+
 ```{r cross validated nowcasting}
@@
 
+# training the model by assigning sales column
+# as target variable and rest other column
+# as independent variable
+
+trControl <- trainControl(method = "cv", number=5, returnData=F, trim=T, verboseIter = TRUE)
+
+cross.val.sf12.model <- train(as.formula(raw_model_formula_string), data = raw.data,
+               method = "lm",
+               trControl = trControl)
+
+# printing model performance metrics
+# along with other details
+print(cross.val.sf12.model)
+
+write_coefs <- T
+if (write_coefs)
+{
+  texreg_file <- paste0(save.path, 'SF12_cross_val_OLS_coefficients.txt')
+  tex_label <- paste0("table: ols_cross_val_coefficients") 
+  tex_headers <- c(texreg::names2latex("5-Fold Cross Validated SF_12 OLS"))
+  tex_caption <- texreg::names2latex(get_tex_table_caption("cv_SF_12", "ols"))    
+  texreg(summary(cross.val.sf12.model), # what model to save coefs for. 
+         file=texreg_file,  # where to save.
+         custom.model.names = tex_headers, # title of table.
+         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
+         digits=4, # p values significant figures.
+         caption=tex_caption, # \caption command option. 
+         label = tex_label, # \label command option. 
+         dcolumn=T,# nice column alignment. 
+         booktabs=T, # nice hlines. (recommended)
+         tabular=T,# tabular env.
+         single.row = T, # nicer one row formatting.
+         longtable=T, # allows tables to wrap over pages
+         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
+         fontsize='small') # small font
+}
 ```
@@
 print(coef(cv.lasso, s = "lambda.1se"))
+
+# bind two sets of coefficients into a data frame
+# load them into a tex table using the latex package?
+lasso_coefs <- cbind(coef(cv.lasso, s = "lambda.min")[, 's1'], coef(cv.lasso, s = "lambda.1se")[, 's1'])
+colnames(lasso_coefs) <- c("Minimum Error", "First Standard Error")
+#lasso_coefs <- kable(as.data.frame(as.matrix(lasso_coefs)), "latex")
+
+texreg_file <- paste0(save.path, 'SF12_Lasso_coefficients.txt')
+tex_label <- paste0("table: sf12_lasso_coefficients") 
+tex_headers <- c(texreg::names2latex("SF_12 LASSO"))
+tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "lasso"))    
+lassoTexReg <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso_coefs[,1], se=lasso_coefs[,2])
+#lassoTexReg2 <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso_coefs[,2])#, lasso_coefs[, 2]))#, pvalues=lasso_coefs[,2])
+#matrixLassoTexReg <- matrixreg(list(lassoTexReg, lassoTexReg2))
+
+texreg(lassoTexReg, # what model to save coefs for. 
+       file=texreg_file,  # where to save.
+       custom.model.names = tex_headers, # title of table.
+       caption=tex_caption, # \caption command option. 
+       label = tex_label, # \label command option. 
+       dcolumn=T,# nice column alignment. 
+       booktabs=T, # nice hlines. (recommended)
+       tabular=T,# tabular env.
+       single.row = T, # nicer one row formatting.
+       longtable=T, # allows tables to wrap over pages
+       use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
+       fontsize='small') # small font
+
 ```
@@
 ```{r projection of weights}
-# get from old paper as well? interesting idea on macro micro
-sf12.lm.weighted <- lm(formula, weights = weights, data = final.data)
+# weighted ols
+model_formula_string <- "SF_12 ~ factor(sex) +  relevel(factor(ethnicity), ref='WBI') + scale(age) + factor(education_state) + factor(S7_labour_state) + relevel(factor(job_sec), ref=1) + relevel(factor(region), ref='London') + scale(hh_income)"
+sf12.lm.weighted <- lm(model_formula_string, weights = weight, data = mice.data)
 
 # plots as with SF12
-
+# get data with extrpolated weights for 2013-2018
+# data at data/extrapolated_weights...
 ```
 
-```{r handovers}
+```{r projected_data}
+
+dataDir <- "data/composite_US/"
+filelist <- list.files(dataDir,
+                       include.dirs = FALSE,
+                       full.names = TRUE,
+                       pattern = '[0-9]{4}_US_cohort.csv')[8:10] # get files for 2016-2018.
+new.raw.data <- do.call(rbind, lapply(filelist, read.csv))
+
+model_formula <- as.formula(model_formula_string)
+variables <- all.vars(model_formula)
+variables[1] <- "SF_12"
+
+new.raw.data <- new.raw.data[, append(variables, c("time", 'pidp', 'weight'))]
+
+new.raw.data <- new.raw.data %>%
+        group_by(pidp) %>%
+        #mutate(diff = .data[[dependent]] - lag(.data[[dependent]], order_by = time)) %>%
+        mutate(last = lag(.data[["SF_12"]], order_by = time)) %>%
+        rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff
+
+new.raw.data <- replace.missing(new.raw.data)
+new.raw.data <- drop_na(new.raw.data)
+
+dataDir <- "data"
+filelist <- list.files(dataDir,
+                       include.dirs = FALSE,
+                       full.names = TRUE,
+                       pattern = 'extrapolated_weights_data_[0-9]{4}.csv')[1:3]# get files for 2016-2018.
+
+extrapolated.raw.data <- do.call(rbind, lapply(filelist, read.csv))
+extrapolated.raw.data <- extrapolated.raw.data[, append(variables, c("time", 'pidp', 'weight', 'plus_5_weight'))]
+extrapolated.raw.data <- extrapolated.raw.data %>%
+        group_by(pidp) %>%
+        #mutate(diff = .data[[dependent]] - lag(.data[[dependent]], order_by = time)) %>%
+        mutate(last = lag(.data[["SF_12"]], order_by = time)) %>%
+        rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff
+extrapolated.raw.data <- replace.missing(extrapolated.raw.data)
+extrapolated.raw.data <- drop_na(extrapolated.raw.data)
+```
+
+```{r weighted_regressions}
+
+# weighted regression for 2016-2018 using 2011-2013 models and projected weights
+sf12.lm.weighted.2013 <- lm(model_formula_string, weights = plus_5_weight, data = extrapolated.raw.data)
+
+#  weighted regression for 2016-2018 using 2018 data.
+sf12.lm.weighted.2018 <- lm(model_formula_string, weights = weight, data = new.raw.data)
+
+# compare coefficients/diagnostics?
+
+#todo test.
+
+texreg_file <- paste0(save.path, 'projected_weights_coefficients.txt')
+tex_label <- paste0("table: sf12_projected_weights_coefficients") 
+tex_headers <- c(texreg::names2latex("SF_12 2018 With 2013 Extrapolated Weights"), texreg::names2latex("SF_12 2018 With Weights"))
+tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "ols"))    
+texreg(list(sf12.lm.weighted.2013,sf12.lm.weighted.2018), # what model to save coefs for. 
+       file=texreg_file,  # where to save.
+       custom.model.names = tex_headers, # title of table.
+       stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
+       digits=4, # p values significant figures.
+       caption=tex_caption, # \caption command option. 
+       label = tex_label, # \label command option. 
+       dcolumn=T,# nice column alignment. 
+       booktabs=T, # nice hlines. (recommended)
+       tabular=T,# tabular env.
+       single.row = T, # nicer one row formatting.
+       longtable=T, # allows tables to wrap over pages
+       use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
+       fontsize='small') # small font
+```
+
+```{r handover_data}
 # boxplots for handovers
@@
                        pattern = '[0-9]{4}_US_cohort.csv')[23:30] # get files for 2011-2013.
-raw.data <- do.call(rbind, lapply(filelist, read.csv))
-raw.data <- replace.missing(raw.data)
-raw.data <- raw.data[, c('pidp', 'time', variables)]
-raw.data <- drop_na(raw.data)
+crossval.raw.data <- do.call(rbind, lapply(filelist, read.csv))
+crossval.raw.data <- replace.missing(crossval.raw.data)
+crossval.raw.data <- crossval.raw.data[, c('pidp', 'time', all.vars(as.formula(raw_model_formula_string)))]
+crossval.raw.data <- drop_na(crossval.raw.data)
 ```
 
-```{r handovers}
-start.data <- raw.data[which(raw.data$time==2013),]
+```{r ols_handovers}
+start.data <- crossval.raw.data[which(raw.data$time==2013),]
 rolling.data <- start.data[, c("pidp", "SF_12", "time")]
@@
 
-handover_boxplots(raw.data, handover.data, "SF_12")
-density_ridges(raw.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "raw_ridges")
+handover_boxplots(crossval.raw.data, handover.data, "SF_12", paste0(save.path, "ols_SF12_boxplot"))
+density_ridges(crossval.raw.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "raw_ridges")
 density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "handover_ridges")
+
+```
+
+```{r mice_handovers}
+start.data <- mice.data[which(mice.data$time==2013),]
+rolling.data <- start.data[, c("pidp", "SF_12", "time")]
+handover.data <- rolling.data
+for (i in 1:7){
+  rolling.data$SF_12 <- predict(pooled_lm, start.data)
+  start.data$SF_12 <- rolling.data$SF_12
+  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
+  handover.data <- rbind(handover.data, rolling.data)
+}
+
+handover_boxplots(crossval.glmm.data, handover.data, "SF_12", paste0(save.path, "mice_SF12_boxplot"))
+density_ridges(crossval.glmm.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "mice_raw_ridges")
+density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "mice_handover_ridges")
+
+```
+
+```{r cross_val_handovers}
+start.data <- crossval.raw.data[which(raw.data$time==2013),]
+rolling.data <- start.data[, c("pidp", "SF_12", "time")]
+handover.data <- rolling.data
+for (i in 1:7){
+  rolling.data$SF_12 <- predict(cross.val.sf12.model, start.data)
+  start.data$SF_12 <- rolling.data$SF_12
+  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
+  handover.data <- rbind(handover.data, rolling.data)
+}
+
+handover_boxplots(crossval.raw.data, handover.data, "SF_12", paste0(save.path, "crossval_ols_SF12_boxplot"))
+density_ridges(crossval.raw.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossvalraw_ridges")
+density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_handover_ridges")
 
@@
 
+```{r prep}
+
+mice.data <- mice.data %>%
+            group_by(pidp) %>%
+            #mutate(diff = .data[[dependent]] - lag(.data[[dependent]], order_by = time)) %>%
+            mutate(last = lag(.data[["SF_12"]], order_by = time)) %>%
+            rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff
+
+```
+
 ```{r "glmm"}
-glmm.data <- final.data
+
+glmm.data <- mice.data
 # yoink transition model function pre processing
@@
 
+glmm_model_formula_string <- "SF_12 ~ I(scale(SF_12_last**2)) + scale(SF_12_last) + factor(sex) +factor(ethnicity) + scale(age) + I(scale(age)**2) + factor(education_state) + factor(S7_labour_state) + factor(job_sec) + factor(region) + scale(hh_income) + I(scale(hh_income)**2) + factor(time) + (1|pidp)"
+
 if (reflect) {
@@
 {
-  yj <- yeojohnson(glmm.data[,c(depend)])
-  glmm.data[, c(depend)] <- predict(yj)
+  yj <- yeojohnson(glmm.data[["SF_12"]])
+  glmm.data[["SF_12"]] <- predict(yj)
 }
@@
 
-if(include_weights) {
-  sf12.glmm.model <- glmer(glmm_model_formula,  
+sf12.glmm.model <- glmer(glmm_model_formula_string,  
                nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes forever..
@@
                data = glmm.data)
-} else {
-  sf12.glmm.model <- glmer(model_formula, 
-                 nAGQ=0, 
-                 family=Gamma(link='log'),
-                 data = glmm.data)
-}
 
@@
   tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "glmm"))    
-  texreg(glmm.sf12.lm, # what model to save coefs for. 
+  texreg(sf12.glmm.model, # what model to save coefs for. 
          file=texreg_file,  # where to save.
@@
 
-glmm.fitted <- (max_value - predict(yj, predict(sf12.glmm.model, type='response') + min_value, inverse=T))
-glmm.resid <- scale(dependent_data - glmm.fitted)
-forest_plot_glmm(sf12.glmm.model, paste0(save.path, "glmm_forest.pdf"))
+glmm.fitted <- (max_value - predict(yj, predict(sf12.glmm.model, type='response') + min_value + rnorm(nrow(glmm.data), 0,0.75), inverse=T))#
+glmm.resid <- (dependent_data - glmm.fitted)/sqrt(glmm.fitted)
 qq_plot(glmm.resid, paste0(save.path, "glmm_qq.pdf"))
@@
 
-squareRootRes <- sqrt(abs(scale(glmm.resid)))
+squareRootRes <- sqrt(residuals(sf12.glmm.model, type='pearson'))
 fitted_residuals <- as.data.frame(cbind(glmm.fitted, squareRootRes))
@@
 
+#TODO change cofficient and std scaling.
+# - (exp coefficients. - 1)??
+# start pm standard error and take above exponential formula?. 
+# test exp argument in plot_model
+
+forest_plot_glmm(sf12.glmm.model, paste0(save.path, "glmm_forest.pdf"))
 ```
+
+```{r glmm_handover_data}
+# boxplots for handovers
+#.estimating from 2014-2020.
+# get data for 2013- 2020
+# run 2013 pop through transition probability model a few times. 
+# profit. 
+# run it through model a few times
+# compare with real data in boxplots and ridgelines.
+
+dataDir <- "data/composite_US"
+filelist <- list.files(dataDir,
+                       include.dirs = FALSE,
+                       full.names = TRUE,
+                       pattern = '[0-9]{4}_US_cohort.csv')[5:12] # get files for 2011-2013.
+crossval.glmm.data <- do.call(rbind, lapply(filelist, read.csv))
+crossval.glmm.data <- replace.missing(crossval.glmm.data)
+crossval.glmm.data <- crossval.glmm.data[, c('pidp', 'time', "SF_12")]
+crossval.glmm.data <- drop_na(crossval.glmm.data)
+```
+
+```{r glmm_handovers}
+
+start.data <- mice.data[which(mice.data$time==2013),]
+start.data <- drop_na(start.data)
+
+rolling.data <- start.data[, c("pidp", "SF_12", "time")]
+handover.data <- rolling.data
+for (i in 1:7){
+  rolling.data$SF_12 <- predict(sf12.glmm.model, start.data, type='response')
+  rolling.data$SF_12 <- max_value - predict(yj, rolling.data$SF_12+min_value + rnorm(nrow(start.data),0,0.5), inverse=T)
+  start.data$SF_12 <- rolling.data$SF_12
+  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
+  handover.data <- rbind(handover.data, rolling.data)
+}
+
+handover_boxplots(crossval.glmm.data, handover.data, "SF_12", paste0(save.path, "glmm_SF12_boxplot"))
+density_ridges(crossval.glmm.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "glmm_raw_ridges")
+density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "glmm_handover_ridges")
+
+```

### 2023-09-07 minos/transitions/paper_1_plots.R

@@ -2,8 +2,11 @@ library(ggplot2)
 library(sjPlot)
 library(ggplot2)
 library(ggpattern)
-#source("papers/phd1/paper_plots.R")
 library(visreg)
+library(ggridges)
+
+source("minos/transitions/utils.R")
+source("minos/transitions/transition_model_functions.R")
 
 # forest plot for lm models. 
 forest_plot_lm <- function(model, file_name){
@@ -21,7 +24,7 @@ forest_plot_lm <- function(model, file_name){
   sf12_coefs[what_two_star, 'p.stars'] <- "**"
   sf12_coefs[what_three_star, 'p.stars'] <- "***"
   p.stars<- sf12_coefs[, 5]
-  browser()
+  #browser()
   pdf(file_name)
   p <- plot_model(model, transform=NULL,
                   title = "") + aes(shape=p.stars)
@@ -37,8 +40,16 @@ forest_plot_lm <- function(model, file_name){
 
 forest_plot_glmm <- function(model, file_name){
   
+  
+  
   sf12_coefs <- summary(model)$coefficients
   sf12_coefs <- cbind(sf12_coefs, sf12_coefs[, 4])
+  
+  # shift coefficients by exponential scale
+  
+  
+  # shift standard errors according to formula.
+  
   colnames(sf12_coefs)[5] <- "p.stars"
   what_ns <- which(sf12_coefs[, "Pr(>|z|)"] > 0.05)
   what_one_star <- which(sf12_coefs[, "Pr(>|z|)"] <= 0.05)
@@ -51,7 +62,7 @@ forest_plot_glmm <- function(model, file_name){
   sf12_coefs[what_three_star, 'p.stars'] <- "***"
   p.stars<- sf12_coefs[, 5]
   pdf(file_name)
-  p <- plot_model(model, transform=NULL,
+  p <- plot_model(model, transform="exp",
                   title = "") + aes(shape=p.stars)
   p$data$p.stars[which(p$data$p.stars == "")] <- 'n.s.'
   p <- p +  scale_shape_manual(name='Significance Level',
@@ -150,8 +161,8 @@ density_ridges <- function(data, v, save=FALSE, save.path=NULL, filename.tag=NUL
 {
   data_plot <- data[, c("time", v)]
   # Remove missing values
-  data_plot <- data_plot %>%
-    filter(!data_plot[[v]] %in% miss.values)
+  #data_plot <- data_plot %>%
+   # filter(!data_plot[[v]] %in% miss.values)
[…]

### 2023-09-12 minos/outcomes/paper_1_notebook.Rmd
tweaking paper plots

@@
 ```{r ols_handovers}
-start.data <- crossval.raw.data[which(raw.data$time==2013),]
-rolling.data <- start.data[, c("pidp", "SF_12", "time")]
-handover.data <- rolling.data
+start.data <- crossval.raw.data[which(crossval.raw.data$time==2013),]
+handover.data <- start.data
 for (i in 1:7){
-  rolling.data$SF_12 <- predict(sf12.lm, start.data)
-  start.data$SF_12 <- rolling.data$SF_12
-  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
-  handover.data <- rbind(handover.data, rolling.data)
+  start.data$SF_12 <- predict(sf12.lm, start.data)
+  start.data[, 'time'] <- start.data[, 'time'] +1
+  handover.data <- rbind(handover.data, start.data[, c("pidp", "SF_12", "time")])
 }
@@
 handover.data <- rolling.data
-for (i in 1:7){
+for (i in 1:6){
   rolling.data$SF_12 <- predict(pooled_lm, start.data)
@@
 ```{r cross_val_handovers}
-start.data <- crossval.raw.data[which(raw.data$time==2013),]
+start.data <- crossval.raw.data[which(crossval.raw.data$time==2013),]
 rolling.data <- start.data[, c("pidp", "SF_12", "time")]
@@
 handover_boxplots(crossval.raw.data, handover.data, "SF_12", paste0(save.path, "crossval_ols_SF12_boxplot"))
-density_ridges(crossval.raw.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossvalraw_ridges")
+density_ridges(crossval.raw.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_raw_ridges")
 density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_handover_ridges")

### 2023-09-12 minos/outcomes/EI_EnergyCrisis_PresPlots.Rmd
Changed loneliness to string var from numeric so its easier to understand. Also lots of changes to EI plots

---
title: "Equivalent Income Stuff - Energy Crisis Plots"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(here)
require(dplyr)
require(tidyr)
require(purrr)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

```{r, include=FALSE}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

# Data

## BATCH DATA

```{r}
# S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
#                  'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
#                  'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
# out.path.batch <- here::here('output', 'SIPHER7_batch/')
# 
# base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
# wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)

out.path.arc <- here::here('output', 'SIPHER7_batch_ARC/')

#base.batch <- read.csv(paste0(out.path.arc, 'baseline_batch_aggregated.csv'))
#energy.batch <- read.csv(paste0(out.path.arc, 'energy_batch_aggregated.csv'))
```

```{r}
## second batch dump
out.path.arc2 <- here::here('output', 'batch')

#target.pattern <- paste0('aggregated_run_id_', year, '.csv')
base.list <- list.files(path = paste0(out.path.arc2, '/baseline'),
                            full.names = TRUE)
base.batch <- do.call(rbind, lapply(base.list, read.csv))

energy.list <- list.files(path = paste0(out.path.arc2, '/energy'),
                            full.names = TRUE)
energy.batch <- do.call(rbind, lapply(energy.list, read.csv))

#base.batch <- 
```

## Calculate Age Group

```{r}
calc_age_group <- function(batch.dat) {
  batch.dat <- batch.dat %>%
    mutate(age.group = cut(age, 
                            breaks = c(15, 30, 45, 60, 75, 120),
                            labels = c('16-30', '30-45', '45-60', '60-75', '75+')))
  return(batch.dat)
}

base.batch <- calc_age_group(base.batch)
energy.batch <- calc_age_group(energy.batch)
```

## Calculate Income Quintile

```{r}
calc_income_quintile <- function(batch.dat) {
  batch.dat <- batch.dat %>%
    mutate(income.quint = cut(batch.dat$hh_income, breaks=c(quantile(batch.dat$hh_income, probs = seq(0, 1, by = 0.20))), 
                          labels=c(1,2,3,4,5), include.lowest=TRUE))
}

base.batch <- calc_income_quintile(base.batch)
energy.batch <- calc_income_quintile(energy.batch)
```

## FUNCTIONS

```{r}
income_equivinc_change_batch <- function(base.batch, int.batch, int.name) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  int.inc <- int.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  combined <- merge(base.inc, int.inc, by = c('time', 'run_id'))

  combined$diff_income <- combined$energy_income - combined$base_income
  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income

  combined <- combined %>%
    pivot_longer(cols = diff_income:diff_equiv_income,
                 names_prefix = 'diff_',
                 names_to = 'variable',
                 values_to = 'diff')

  combined2 <- combined %>%
    group_by(time, variable) %>%
    summarise(mean.diff = mean(diff))

  ggplot(combined, aes(x = time, y = diff, group = variable, color = variable)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = 'Change in Income and Equivalent Income', 
         subtitle = int.name)
}

equivinc_change_batch_subpop <- function(base.batch, int.batch, int.name, group.var) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, equivalent_income, weight, all_of(group.var)) %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    summarise(base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  int.inc <- int.batch %>%
    select(pidp, time, run_id, equivalent_income, weight, all_of(group.var)) %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    summarise(int_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  combined <- merge(base.inc, int.inc, by = c('time', 'run_id', group.var))
  combined[[group.var]] <- as.factor(combined[[group.var]])

  combined$diff_equiv_income <- combined$int_equiv_income - combined$base_equiv_income

  combined <- combined %>%
    group_by(time, .data[[group.var]]) %>%
    summarise(mean_diff_equiv_income = mean(diff_equiv_income))

  ggplot(combined, aes(x = time, y = mean_diff_equiv_income, group = .data[[group.var]], color = .data[[group.var]])) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = paste0('Equivalent Income change by ', group.var), subtitle = int.name) +
    xlab('Year') +
    ylab('Equivalent Income (£s)')
}

inc_change_batch_subpop <- function(base.batch, int.batch, int.name, group.var) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, hh_income, weight, all_of(group.var)) %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    summarise(base_hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE))

  int.inc <- int.batch %>%
    select(pidp, time, run_id, hh_income, weight, all_of(group.var)) %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    summarise(int_hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE))

  combined <- merge(base.inc, int.inc, by = c('time', 'run_id', group.var))
  combined[[group.var]] <- as.factor(combined[[group.var]])

  combined$diff_hh_income <- combined$int_hh_income - combined$base_hh_income

  combined <- combined %>%
    group_by(time, .data[[group.var]]) %>%
    summarise(mean_diff_hh_income = mean(diff_hh_income))

  ggplot(combined, aes(x = time, y = mean_diff_hh_income, group = .data[[group.var]], color = .data[[group.var]])) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = paste0('Household Income change by ', group.var), subtitle = int.name) +
    xlab('Year') +
    ylab('Household Income (£s)')
}
```

# Income and Equivalent Income

```{r}
income_equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
```

# EquivInc split by Income Quintile

```{r}
inc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
equivinc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
```

## Percent Change

```{r}
income_equivinc_percent_change_batch <- function(base.batch, int.batch, int.name, group.var) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, all_of(group.var), weight) %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  int.inc <- energy.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, all_of(group.var), weight) %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  combined <- merge(base.inc, int.inc, by = c('time', 'run_id', group.var))

  combined$diff_income <- combined$energy_income - combined$base_income
  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income

  combined <- combined %>%
    group_by(time, .data[[group.var]]) %>%
    summarise(mean_income = mean(base_income),
              mean_equiv_income = mean(base_equiv_income),
              mean_diff_income = mean(diff_income),
              mean_diff_equiv_income = mean(diff_equiv_income)) %>%
    mutate(percent_change_income = (mean_diff_income / mean_income) * 100,
           percent_change_equiv_income = (mean_diff_equiv_income / mean_equiv_income) * 100) %>%
    select(-mean_income, -mean_equiv_income, -mean_diff_income, -mean_diff_equiv_income) %>%
    pivot_longer(cols = percent_change_income:percent_change_equiv_income,
                 names_prefix = 'percent_change_',
                 names_to = 'variable',
                 values_to = 'change')

  ggplot(combined, aes(x = time, y = change, group = variable, color = variable)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    facet_wrap(~ income.quint, nrow = 1) +
    labs(title = 'Percent change: Income vs Equivalent Income',
         subtitle = int.name) +
    xlab('Year') +
    ylab('Percent Change')
}

income_equivinc_percent_change_batch(base.batch, int.batch, int.name, group.var = 'income.quint')
```

# Pathway Vars by Income Quintile

```{r}
S7_ordinal_pathway_batch <- function(base.bat, int.bat, int.name, var) {
  base.hous <- base.bat %>%
    select(pidp, time, run_id, all_of(var), weight) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = 'Baseline')

  inc.hous <- int.bat %>%
    select(pidp, time, run_id, all_of(var), weight) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = int.name)

  combined <- rbind(base.hous, inc.hous)
  combined[[var]] <- as.factor(combined[[var]])

  #print(combined)

  p1 <- ggplot(combined, aes(x = time, y = prop, group = interaction(.data[[var]], source), color = .data[[var]], linetype = source)) +
    geom_smooth() +
    geom_point()

  print(p1)

  base.hous2 <- base.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = (n / total) * 100) %>%
    select(-n, -total) %>%
    rename(Baseline = prop)

  int.hous2 <- int.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = (n / total) * 100) %>%
    select(-n, -total) %>%
    rename(int = prop)

  combined2 <- merge(base.hous2, int.hous2, by = c('time', 'run_id', var))

  print(combined2)

  combined2[[var]] <- as.factor(combined2[[var]])

  combined2$diff <- combined2$int - combined2$Baseline

  p2 <- ggplot(combined2, aes(x = time, y = diff, group = .data[[var]], color = .data[[var]])) +
    geom_smooth() +
    geom_point()

  print(p2)

}

S7_ordinal_pathway_batch(base.batch, energy.batch, 'Energy Crisis', 'S7_housing_quality')
```

```{r}
## ATTEMPT 2

group.var <- 'income.quint'
group.level <- 1
var <- 'S7_housing_quality'

base.sub <- base.batch %>%
  select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var), weight) %>%
  group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
  summarise(baseline_EI = weighted.mean(equivalent_income, w = weight))

int.sub <- energy.batch %>%
  select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var), weight) %>%
  group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
  summarise(int_EI = weighted.mean(equivalent_income, w = weight))

combined <- merge(base.sub, int.sub, by = c('time', 'run_id', group.var, var))
combined$diff <- combined$int_EI - combined$baseline_EI

ggplot(data = combined, aes(x = time, y = diff, group = .data[[var]], color = .data[[var]])) +
  geom_smooth() +
  facet_wrap(~ .data[[group.var]])

base.sub2 <- base.batch %>%
  select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var), weight) %>%
  filter(.data[[group.var]] == group.level) %>%
  group_by(time, run_id, .data[[var]]) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
```

```{r}
## ATTEMPT 3

S7_pathway_change_byGroup <- function(base.batch, int.batch, group.var, var) {
  base.sub <- base.batch %>%
    select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var)) %>%
    group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
    count() %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    mutate(total = sum(n),
           base_prop = n / total) %>%
    select(-n, -total)

  int.sub <- energy.batch %>%
    select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var)) %>%
    group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
    count() %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    mutate(total = sum(n),
           int_prop = n / total) %>%
    select(-n, -total)

  combined <- merge(base.sub, int.sub, by = c('time', 'run_id', group.var, var))
  combined$prop_diff <- combined$int_prop - combined$base_prop

  combined[[var]] <- as.factor(combined[[var]])

  ggplot(data = combined, aes(x = time, y = prop_diff, group = .data[[var]], color = .data[[var]])) +
    geom_smooth() +
    facet_wrap(~ .data[[group.var]], nrow=1) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
}
```

```{r}
S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health')
S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health')
S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness')
```

```{r}
S7_cumulative_pathwayChange_byGroup <- function(base.batch, int.batch, group.var, var) {
  base.sub <- base.batch %>%
    select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var)) %>%
    group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
    count() %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    mutate(total = sum(n),
           base_prop = n / total) %>%
    select(-n, -total)

  int.sub <- energy.batch %>%
    select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var)) %>%
    group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
    count() %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    mutate(total = sum(n),
           int_prop = n / total) %>%
    select(-n, -total)

  combined <- merge(base.sub, int.sub, by = c('time', 'run_id', group.var, var))
  combined$prop_diff <- combined$int_prop - combined$base_prop

  combined[[var]] <- as.factor(combined[[var]])

  combined <- combined %>%
    group_by(run_id, .data[[group.var]], .data[[var]]) %>%
    summarise(cumulative_diff = sum(prop_diff)) %>%
    group_by(.data[[group.var]], .data[[var]]) %>%
    summarise(cumulative_diff = mean(cumulative_diff))

  ggplot(data = combined, aes(x = .data[[var]], y = cumulative_diff, fill = .data[[var]])) +
    geom_col() +
    facet_wrap(~ .data[[group.var]], nrow=1) +
    labs(title = paste0('Cumulative Difference in ', var, ' by ', group.var)) +
    ylab('Cumulative Difference (%)') +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          legend.position = 'bottom')
}
```

## Income Quintile

```{r}
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness')
```

## Age Group

```{r}
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_housing_quality')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_neighbourhood_safety')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_physical_health')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_mental_health')
S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'loneliness')
```

# SIMPLIFIED Positive v Negative Change

```{r}
group.var <- 'income.quint'
var <- 'S7_mental_health'

base.sub <- base.batch %>%
  select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
  rename(Baseline_var = S7_mental_health,
         Baseline_income.quint = income.quint)

int.sub <- energy.batch %>%
  select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
  rename(Intervention_var = S7_mental_health,
         Intervention_income.quint = income.quint)

merged <- merge(base.sub, int.sub,
                by=c('pidp', 'time', 'run_id'),
                all = FALSE)

#combined <- rbind(base.sub, int.sub)

```

```{r}
# move further analysis here so we don't have to do that expensive merge every time
merged2 <- merged %>%
  mutate(varChange = Intervention_var - Baseline_var,
         effect = case_when(varChange > 0 ~ "Positive",
                            varChange < 0 ~ "Negative",
                            varChange == 0 ~ "No_Change")) %>%
  select(-Baseline_var, -Intervention_var, -Intervention_income.quint, -varChange) %>%
  rename(income.quint = Baseline_income.quint) %>%
  group_by(time, run_id, .data[[group.var]], effect) %>%
  count() %>%
  group_by(time, run_id, .data[[group.var]]) %>%
  mutate(total = sum(n),
         effect_prop = n / total) %>%
  select(-n, -total) %>%
  group_by(time, .data[[group.var]], effect) %>%
  summarise(effect_prop = mean(effect_prop)) %>%
  pivot_wider(names_from = 'effect',
              values_from = 'effect_prop') %>%
  mutate(change = Positive - Negative) %>%
  select(-Positive, -Negative, -No_Change, -time) %>%
  group_by(.data[[group.var]]) %>%
  summarise(change = sum(change))

ggplot(data = merged2, aes(x = income.quint, y = change)) +
  geom_col()
```

```{r}
simplified_component_change <- function(base.batch, int.batch, group.var, var, print = FALSE) {

  # it would be lovely if this was completely generic, but for some things that
  # is more hassle than its worth. Handling string vars here is one of these 
  # things

  if (var == 'S7_housing_quality') {
    base.batch$S7_housing_quality <- as.numeric(factor(base.batch$S7_housing_quality,
                                            levels = c('No to all',
                                                       'Yes to some',
                                                       'Yes to all'),
                                            labels = c(1, 2, 3)))
    int.batch$S7_housing_quality <- as.numeric(factor(int.batch$S7_housing_quality,
                                            levels = c('No to all',
                                                       'Yes to some',
                                                       'Yes to all'),
                                            labels = c(1, 2, 3)))
  } else if (var == 'S7_neighbourhood_safety') {
    base.batch$S7_neighbourhood_safety <- as.numeric(factor(base.batch$S7_neighbourhood_safety,
                                                 levels = c('Often',
                                                            'Some of the time',
                                                            'Hardly ever'),
                                                 labels = c(1, 2, 3)))
    int.batch$S7_neighbourhood_safety <- as.numeric(factor(int.batch$S7_neighbourhood_safety,
                                                 levels = c('Often',
                                                            'Some of the time',
                                                            'Hardly ever'),
                                                 labels = c(1, 2, 3)))
  } else if (var == 'loneliness') {
    base.batch$loneliness <- as.numeric(factor(base.batch$loneliness,
                                    levels = c(1, 2, 3),
                                    labels = c(3, 2, 1)))
    int.batch$loneliness <- as.numeric(factor(int.batch$loneliness,
                                    levels = c(1, 2, 3),
                                    labels = c(3, 2, 1)))
  }

  base.sub <- base.batch %>%
    select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
    rename(Baseline_var = .data[[var]],
           Baseline_group.var = .data[[group.var]])

  int.sub <- int.batch %>%
    select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
    rename(Intervention_var = .data[[var]],
           Intervention_group.var = .data[[group.var]])

  merged <- merge(base.sub, int.sub,
                  by=c('pidp', 'time', 'run_id'),
                  all = FALSE)

  merged2 <- merged %>%
    mutate(varChange = Intervention_var - Baseline_var,
           effect = case_when(varChange > 0 ~ "Positive",
                              varChange < 0 ~ "Negative",
                              varChange == 0 ~ "No_Change")) %>%
    select(-Baseline_var, -Intervention_var, -Intervention_group.var, -varChange) %>%
    rename(income.quint = Baseline_group.var) %>%
    group_by(time, run_id, .data[[group.var]], effect) %>%
    count() %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    mutate(total = sum(n),
           effect_prop = n / total) %>%
    select(-n, -total) %>%
    group_by(time, .data[[group.var]], effect) %>%
    summarise(effect_prop = mean(effect_prop)) %>%
    pivot_wider(names_from = 'effect',
                values_from = 'effect_prop') %>%
    mutate(change = Positive - Negative) %>%
    select(-Positive, -Negative, -No_Change, -time) %>%
    group_by(.data[[group.var]]) %>%
    summarise(change = sum(change))

  p1 <- ggplot(data = merged2, aes(x = .data[[group.var]], y = change)) +
    geom_col() +
    labs(title = paste0('Change in ', var, ' by ', group.var)) +
    ylab('% Change')

  if(print) {
    print(p1)
  }

  return(merged2)
}

```

```{r}

simplified_component_change_BOXPLOT <- function(base.batch, int.batch, group.var, var, print = FALSE) {

  # it would be lovely if this was completely generic, but for some things that
  # is more hassle than its worth. Handling string vars here is one of these 
  # things

  if (var == 'S7_housing_quality') {
    base.batch$S7_housing_quality <- as.numeric(factor(base.batch$S7_housing_quality,
                                            levels = c('No to all',
                                                       'Yes to some',
                                                       'Yes to all'),
                                            labels = c(1, 2, 3)))
    int.batch$S7_housing_quality <- as.numeric(factor(int.batch$S7_housing_quality,
                                            levels = c('No to all',
                                                       'Yes to some',
                                                       'Yes to all'),
                                            labels = c(1, 2, 3)))
  } else if (var == 'S7_neighbourhood_safety') {
    base.batch$S7_neighbourhood_safety <- as.numeric(factor(base.batch$S7_neighbourhood_safety,
                                                 levels = c('Often',
                                                            'Some of the time',
                                                            'Hardly ever'),
                                                 labels = c(1, 2, 3)))
    int.batch$S7_neighbourhood_safety <- as.numeric(factor(int.batch$S7_neighbourhood_safety,
                                                 levels = c('Often',
                                                            'Some of the time',
                                                            'Hardly ever'),
                                                 labels = c(1, 2, 3)))
  } else if (var == 'loneliness') {
    base.batch$loneliness <- as.numeric(factor(base.batch$loneliness,
                                    levels = c(1, 2, 3),
                                    labels = c(3, 2, 1)))
    int.batch$loneliness <- as.numeric(factor(int.batch$loneliness,
                                    levels = c(1, 2, 3),
                                    labels = c(3, 2, 1)))
  }

  base.sub <- base.batch %>%
    select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
    rename(Baseline_var = .data[[var]],
           Baseline_group.var = .data[[group.var]])

  int.sub <- int.batch %>%
    select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
    rename(Intervention_var = .data[[var]],
           Intervention_group.var = .data[[group.var]])

  merged <- merge(base.sub, int.sub,
                  by=c('pidp', 'time', 'run_id'),
                  all = FALSE)

  merged2 <- merged %>%
    mutate(varChange = Intervention_var - Baseline_var,
           effect = case_when(varChange > 0 ~ "Positive",
                              varChange < 0 ~ "Negative",
                              varChange == 0 ~ "No_Change")) %>%
    select(-Baseline_var, -Intervention_var, -Intervention_group.var, -varChange) %>%
    rename(!!group.var := Baseline_group.var) %>%
    group_by(time, run_id, .data[[group.var]], effect) %>%
    count() %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    mutate(total = sum(n),
           effect_prop = n / total) %>%
    select(-n, -total) %>%
    pivot_wider(names_from = 'effect',
                values_from = 'effect_prop') %>%
    mutate(change = Positive - Negative) %>%
    select(-Positive, -Negative, -No_Change) %>%
    group_by(run_id, .data[[group.var]]) %>%
    summarise(sum.change = sum(change))

  p1 <- ggplot(data = merged2, aes(x = .data[[group.var]], y = sum.change)) +
    geom_boxplot(notch = FALSE) +
    labs(title = paste0('Change in ', var, ' by ', group.var)) +
    ylab('% Change')

  if(print) {
    print(p1)
  }

  return(merged2)
}

```

```{r}
simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality', print = TRUE)
simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety', print = TRUE)
simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health', print = TRUE)
simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health', print = TRUE)
simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness', print = TRUE)
```

# Change in ALL vars

```{r}
varlist <- c('S7_neighbourhood_safety', 'loneliness',
             'S7_physical_health', 'S7_mental_health')

df <- simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
colnames(df) <- c('Income_Quintile', 'S7_housing_quality')
for (S7_var in varlist) {
  df2 <- simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = S7_var)
  colnames(df2) <- c('Income_Quintile', S7_var)
  df <- merge(df, df2, by = c('Income_Quintile'))
}
rm(df2)

# finally pivot_longer for ggplot and facet_wrap to take over
df2 <- df %>%
  pivot_longer(cols = S7_housing_quality:S7_mental_health,
               names_to = 'Variable',
               values_to = 'Change')

ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
  geom_col() +
  facet_wrap(~ Income_Quintile, nrow = 1) +
  theme(legend.position = 'bottom',
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
```

# BOXPLOT Change in ALL vars

```{r}
varlist <- c('S7_neighbourhood_safety', 'loneliness',
             'S7_physical_health', 'S7_mental_health')

df <- simplified_component_change_BOXPLOT(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
colnames(df) <- c('run_id', 'Income_Quintile', 'S7_housing_quality')
for (S7_var in varlist) {
  df2 <- simplified_component_change_BOXPLOT(base.batch, energy.batch, group.var = 'income.quint', var = S7_var)
  colnames(df2) <- c('run_id', 'Income_Quintile', S7_var)
  df <- merge(df, df2, by = c('run_id', 'Income_Quintile'))
}
rm(df2)

# finally pivot_longer for ggplot and facet_wrap to take over
df2 <- df %>%
  pivot_longer(cols = S7_housing_quality:S7_mental_health,
               names_to = 'Variable',
               values_to = 'Change')

ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
  geom_boxplot(notch = FALSE) +
  facet_wrap(~ Income_Quintile, nrow = 1) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  theme(legend.position = 'bottom',
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
```

```{r}

```

### 2023-09-12 minos/outcomes/EI_PresPlots_SimpleBatch.Rmd
Changed loneliness to string var from numeric so its easier to understand. Also lots of changes to EI plots

--- 2023-09-12 minos/outcomes/EI_EnergyCrisis_PresPlots.Rmd
@@
 ```{r}
-# S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
-#                  'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
-#                  'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
-# out.path.batch <- here::here('output', 'SIPHER7_batch/')
-# 
-# base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
-# wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-# energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-# child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-# pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
+                 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
+                 'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
+out.path.batch <- here::here('output', 'SIPHER7_batch/')
 
-out.path.arc <- here::here('output', 'SIPHER7_batch_ARC/')
+base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
+int.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
 
-#base.batch <- read.csv(paste0(out.path.arc, 'baseline_batch_aggregated.csv'))
-#energy.batch <- read.csv(paste0(out.path.arc, 'energy_batch_aggregated.csv'))
-```
-
-```{r}
-## second batch dump
-out.path.arc2 <- here::here('output', 'batch')
-
-#target.pattern <- paste0('aggregated_run_id_', year, '.csv')
-base.list <- list.files(path = paste0(out.path.arc2, '/baseline'),
-                            full.names = TRUE)
-base.batch <- do.call(rbind, lapply(base.list, read.csv))
-
-energy.list <- list.files(path = paste0(out.path.arc2, '/energy'),
-                            full.names = TRUE)
-energy.batch <- do.call(rbind, lapply(energy.list, read.csv))
-
-#base.batch <- 
+int.name <- 'Living Wage'
 ```
@@
 base.batch <- calc_age_group(base.batch)
-energy.batch <- calc_age_group(energy.batch)
+int.batch <- calc_age_group(int.batch)
 ```
@@
 base.batch <- calc_income_quintile(base.batch)
-energy.batch <- calc_income_quintile(energy.batch)
+int.batch <- calc_income_quintile(int.batch)
 ```
@@
 ```{r}
-income_equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
+income_equivinc_change_batch(base.batch, int.batch, int.name)
 ```
@@
 ```{r}
-inc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
-equivinc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
+inc_change_batch_subpop(base.batch, int.batch, int.name, group.var = 'income.quint')
+equivinc_change_batch_subpop(base.batch, int.batch, int.name, group.var = 'income.quint')
 ```
@@
 
-  int.inc <- energy.batch %>%
+  int.inc <- int.batch %>%
     select(pidp, time, run_id, hh_income, equivalent_income, all_of(group.var), weight) %>%
     group_by(time, run_id, .data[[group.var]]) %>%
-    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
-              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+    summarise(int_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+              int_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
 
@@
 
-  combined$diff_income <- combined$energy_income - combined$base_income
-  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income
+  combined$diff_income <- combined$int_income - combined$base_income
+  combined$diff_equiv_income <- combined$int_equiv_income - combined$base_equiv_income
 
@@
 income_equivinc_percent_change_batch(base.batch, int.batch, int.name, group.var = 'income.quint')
+
 ```
@@
 # Pathway Vars by Income Quintile
-
-```{r}
-S7_ordinal_pathway_batch <- function(base.bat, int.bat, int.name, var) {
-  base.hous <- base.bat %>%
-    select(pidp, time, run_id, all_of(var), weight) %>%
-    group_by(time, run_id, .data[[var]]) %>%
-    count() %>%
-    group_by(time, run_id) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prop = n / total) %>%
-    select(-n, -total) %>%
-    mutate(source = 'Baseline')
-
-  inc.hous <- int.bat %>%
-    select(pidp, time, run_id, all_of(var), weight) %>%
-    group_by(time, run_id, .data[[var]]) %>%
-    count() %>%
-    group_by(time, run_id) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prop = n / total) %>%
-    select(-n, -total) %>%
-    mutate(source = int.name)
-
-  combined <- rbind(base.hous, inc.hous)
-  combined[[var]] <- as.factor(combined[[var]])
-
-  #print(combined)
-
-  p1 <- ggplot(combined, aes(x = time, y = prop, group = interaction(.data[[var]], source), color = .data[[var]], linetype = source)) +
-    geom_smooth() +
-    geom_point()
-
-  print(p1)
-
-  base.hous2 <- base.bat %>%
-    select(pidp, time, run_id, all_of(var)) %>%
-    group_by(time, run_id, .data[[var]]) %>%
-    count() %>%
-    group_by(time, run_id) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prop = (n / total) * 100) %>%
-    select(-n, -total) %>%
-    rename(Baseline = prop)
-
-  int.hous2 <- int.bat %>%
-    select(pidp, time, run_id, all_of(var)) %>%
-    group_by(time, run_id, .data[[var]]) %>%
-    count() %>%
-    group_by(time, run_id) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prop = (n / total) * 100) %>%
-    select(-n, -total) %>%
-    rename(int = prop)
-
-  combined2 <- merge(base.hous2, int.hous2, by = c('time', 'run_id', var))
-
-  print(combined2)
-
-  combined2[[var]] <- as.factor(combined2[[var]])
-
-  combined2$diff <- combined2$int - combined2$Baseline
-
-  p2 <- ggplot(combined2, aes(x = time, y = diff, group = .data[[var]], color = .data[[var]])) +
-    geom_smooth() +
-    geom_point()
-
-  print(p2)
-
-}
-
-S7_ordinal_pathway_batch(base.batch, energy.batch, 'Energy Crisis', 'S7_housing_quality')
-```
-
-```{r}
-## ATTEMPT 2
-
-group.var <- 'income.quint'
-group.level <- 1
-var <- 'S7_housing_quality'
-
-base.sub <- base.batch %>%
-  select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var), weight) %>%
-  group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
-  summarise(baseline_EI = weighted.mean(equivalent_income, w = weight))
-
-int.sub <- energy.batch %>%
-  select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var), weight) %>%
-  group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
-  summarise(int_EI = weighted.mean(equivalent_income, w = weight))
-
-combined <- merge(base.sub, int.sub, by = c('time', 'run_id', group.var, var))
-combined$diff <- combined$int_EI - combined$baseline_EI
-
-ggplot(data = combined, aes(x = time, y = diff, group = .data[[var]], color = .data[[var]])) +
-  geom_smooth() +
-  facet_wrap(~ .data[[group.var]])
-
-base.sub2 <- base.batch %>%
-  select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var), weight) %>%
-  filter(.data[[group.var]] == group.level) %>%
-  group_by(time, run_id, .data[[var]]) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
-```
 
@@
 
-  int.sub <- energy.batch %>%
+  int.sub <- int.batch %>%
     select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var)) %>%
@@
 ```{r}
-S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
-S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
-S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health')
-S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health')
-S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness')
+S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality')
+S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
+S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_physical_health')
+S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_mental_health')
+S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'loneliness')
 ```
+
+## Cumulative Pathway Change
 
@@
 ```{r}
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_physical_health')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_mental_health')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'loneliness')
 ```
@@
 ```{r}
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_housing_quality')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_neighbourhood_safety')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_physical_health')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_mental_health')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'loneliness')
-```
-
-# SIMPLIFIED Positive v Negative Change
-
-```{r}
-group.var <- 'income.quint'
-var <- 'S7_mental_health'
-
-base.sub <- base.batch %>%
-  select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
-  rename(Baseline_var = S7_mental_health,
-         Baseline_income.quint = income.quint)
-
-int.sub <- energy.batch %>%
-  select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
-  rename(Intervention_var = S7_mental_health,
-         Intervention_income.quint = income.quint)
-
-merged <- merge(base.sub, int.sub,
-                by=c('pidp', 'time', 'run_id'),
-                all = FALSE)
-
-#combined <- rbind(base.sub, int.sub)
-
-```
-
-```{r}
-# move further analysis here so we don't have to do that expensive merge every time
-merged2 <- merged %>%
-  mutate(varChange = Intervention_var - Baseline_var,
-         effect = case_when(varChange > 0 ~ "Positive",
-                            varChange < 0 ~ "Negative",
-                            varChange == 0 ~ "No_Change")) %>%
-  select(-Baseline_var, -Intervention_var, -Intervention_income.quint, -varChange) %>%
-  rename(income.quint = Baseline_income.quint) %>%
-  group_by(time, run_id, .data[[group.var]], effect) %>%
-  count() %>%
-  group_by(time, run_id, .data[[group.var]]) %>%
-  mutate(total = sum(n),
-         effect_prop = n / total) %>%
-  select(-n, -total) %>%
-  group_by(time, .data[[group.var]], effect) %>%
-  summarise(effect_prop = mean(effect_prop)) %>%
-  pivot_wider(names_from = 'effect',
-              values_from = 'effect_prop') %>%
-  mutate(change = Positive - Negative) %>%
-  select(-Positive, -Negative, -No_Change, -time) %>%
-  group_by(.data[[group.var]]) %>%
-  summarise(change = sum(change))
-
-ggplot(data = merged2, aes(x = income.quint, y = change)) +
-  geom_col()
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'S7_housing_quality')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'S7_neighbourhood_safety')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'S7_physical_health')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'S7_mental_health')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'loneliness')
 ```
@@
     base.batch$loneliness <- as.numeric(factor(base.batch$loneliness,
-                                    levels = c(1, 2, 3),
-                                    labels = c(3, 2, 1)))
+                                    levels = c('Often', 'Sometimes', 'Never'),
+                                    labels = c(1, 2, 3)))
     int.batch$loneliness <- as.numeric(factor(int.batch$loneliness,
-                                    levels = c(1, 2, 3),
-                                    labels = c(3, 2, 1)))
+                                    levels = c('Often', 'Sometimes', 'Never'),
+                                    labels = c(1, 2, 3)))
   }
@@
 
-```
-
-```{r}
-
 simplified_component_change_BOXPLOT <- function(base.batch, int.batch, group.var, var, print = FALSE) {
@@
     base.batch$loneliness <- as.numeric(factor(base.batch$loneliness,
-                                    levels = c(1, 2, 3),
-                                    labels = c(3, 2, 1)))
+                                    levels = c('Often',
+                                               'Sometimes',
+                                               'Never'),
+                                    labels = c(1, 2, 3)))
     int.batch$loneliness <- as.numeric(factor(int.batch$loneliness,
-                                    levels = c(1, 2, 3),
-                                    labels = c(3, 2, 1)))
+                                    levels = c('Often',
+                                               'Sometimes',
+                                               'Never'),
+                                    labels = c(1, 2, 3)))
   }
@@
     geom_boxplot(notch = FALSE) +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
     labs(title = paste0('Change in ', var, ' by ', group.var)) +
@@
 ```{r}
-simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality', print = TRUE)
-simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety', print = TRUE)
-simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health', print = TRUE)
-simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health', print = TRUE)
-simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness', print = TRUE)
+# simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality', print = TRUE)
+# simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety', print = TRUE)
+# simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = 'S7_mental_health', print = TRUE)
+# simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = 'S7_physical_health', print = TRUE)
+simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = 'loneliness', print = TRUE)
+```
+
+```{r}
+# simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality', print = TRUE)
+# simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety', print = TRUE)
+# simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = 'S7_mental_health', print = TRUE)
+# simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = 'S7_physical_health', print = TRUE)
+simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = 'loneliness', print = TRUE)
 ```
@@
 
-df <- simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
+df <- simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality')
 colnames(df) <- c('Income_Quintile', 'S7_housing_quality')
+print("Completed for S7_housing_quality...")
 for (S7_var in varlist) {
-  df2 <- simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = S7_var)
+  df2 <- simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = S7_var)
   colnames(df2) <- c('Income_Quintile', S7_var)
   df <- merge(df, df2, by = c('Income_Quintile'))
+  print(paste0("Completed for ", S7_var, '...'))
 }
@@
 
-df <- simplified_component_change_BOXPLOT(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
+df <- simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality')
 colnames(df) <- c('run_id', 'Income_Quintile', 'S7_housing_quality')
+print("Completed for S7_housing_quality...")
 for (S7_var in varlist) {
-  df2 <- simplified_component_change_BOXPLOT(base.batch, energy.batch, group.var = 'income.quint', var = S7_var)
+  df2 <- simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = S7_var)
   colnames(df2) <- c('run_id', 'Income_Quintile', S7_var)
   df <- merge(df, df2, by = c('run_id', 'Income_Quintile'))
+  print(paste0("Completed for ", S7_var, '...'))
 }

### 2023-09-12 minos/outcomes/equivalent_income_out.Rmd
Changed loneliness to string var from numeric so its easier to understand. Also lots of changes to EI plots

@@
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-allchild.dat <- read_singular_local_out(out.path, 'hhIncomeChildUplift', drop.dead = TRUE)
-pov.dat <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift', drop.dead = TRUE)
-wage.dat <- read_singular_local_out(out.path, 'livingWageIntervention', drop.dead = TRUE)
+# allchild.dat <- read_singular_local_out(out.path, 'hhIncomeChildUplift', drop.dead = TRUE)
+# pov.dat <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift', drop.dead = TRUE)
+# wage.dat <- read_singular_local_out(out.path, 'livingWageIntervention', drop.dead = TRUE)
 energy.dat <- read_singular_local_out(out.path, 'energyDownlift', drop.dead = TRUE)
@@
 base.dat <- filter(base.dat, time > 2020)
-allchild.dat <- filter(allchild.dat, time > 2020)
-pov.dat <- filter(pov.dat, time > 2020)
-wage.dat <- filter(wage.dat, time > 2020)
+# allchild.dat <- filter(allchild.dat, time > 2020)
+# pov.dat <- filter(pov.dat, time > 2020)
+# wage.dat <- filter(wage.dat, time > 2020)
 energy.dat <- filter(energy.dat, time > 2020)
@@
 ```{r}
-equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild')
-equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild')
-equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage')
+# equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild')
+# equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild')
+# equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage')
 equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift')
@@
 
-allchild.subset <- allchild.dat %>%
-  select(pidp, time, equivalent_income, alive, weight) %>%
-  filter(alive != 'dead') %>%
-  group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
-allchild.subset$scenario <- 'AllChild'
-
-pov.subset <- pov.dat %>%
-  select(pidp, time, equivalent_income, alive, weight) %>%
-  filter(alive != 'dead') %>%
-  group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
-pov.subset$scenario <- 'PovertyChild'
-
-wage.subset <- wage.dat %>%
-  select(pidp, time, equivalent_income, alive, weight) %>%
-  filter(alive != 'dead') %>%
-  group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
-wage.subset$scenario <- 'LivingWage'
+# allchild.subset <- allchild.dat %>%
+#   select(pidp, time, equivalent_income, alive, weight) %>%
+#   filter(alive != 'dead') %>%
+#   group_by(time) %>%
+#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+# allchild.subset$scenario <- 'AllChild'
+# 
+# pov.subset <- pov.dat %>%
+#   select(pidp, time, equivalent_income, alive, weight) %>%
+#   filter(alive != 'dead') %>%
+#   group_by(time) %>%
+#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+# pov.subset$scenario <- 'PovertyChild'
+# 
+# wage.subset <- wage.dat %>%
+#   select(pidp, time, equivalent_income, alive, weight) %>%
+#   filter(alive != 'dead') %>%
+#   group_by(time) %>%
+#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+# wage.subset$scenario <- 'LivingWage'
 
@@
 
-all.combined <- rbind(base.subset, allchild.subset, pov.subset, wage.subset, energy.subset)
-all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'AllChild', 'PovertyChild', 'LivingWage', 'EnergyDownlift'))
+# all.combined <- rbind(base.subset, allchild.subset, pov.subset, wage.subset, energy.subset)
+# all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'AllChild', 'PovertyChild', 'LivingWage', 'EnergyDownlift'))
+
+all.combined <- rbind(base.subset, energy.subset)
+all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'EnergyDownlift'))
 
@@
 ```{r}
-equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild')
-equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild')
-equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage')
+# equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild')
+# equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild')
+# equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage')
 equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift')
@@
 ```{r, include=FALSE}
-# THink about this...
-# We can use the income_boosted and boost_amount variables to remove the income boost from people and visualise that
-
-base.sub2 <- base.dat %>%
-  select(pidp, time, equivalent_income, alive) %>%
-  filter(alive != 'dead') %>%
-  select(-alive) %>%
-  rename(baseline = equivalent_income)
-
-allchild.sub2 <- allchild.dat %>%
-  select(pidp, time, equivalent_income, income_boosted, boost_amount, alive) %>%
-  filter(alive != 'dead') %>%
-  select(-alive) %>%
-  rename(allchild = equivalent_income)
-
-allchild.merged <- merge(base.sub2, allchild.sub2, by = c('pidp', 'time'))
-
-boosted.pidps <- allchild.sub2 %>%
-  filter(income_boosted == 'True') %>%
-  select(pidp)
-
-allchild.boosted <- allchild.merged %>%
-  filter(pidp %in% boosted.pidps$pidp) %>%
-  filter(income_boosted == 'True' | time == 2020) %>%
-  mutate(adjusted_EI = allchild - boost_amount) %>%
-  select(-allchild, -income_boosted, -boost_amount) %>%
-  group_by(time) %>%
-  summarise(baseline = mean(baseline),
-            allchild_adj = mean(adjusted_EI)) %>%
-  pivot_longer(cols = baseline:allchild_adj,
-               names_to = 'scenario',
-               values_to = 'equivalent_income')
+# # THink about this...
+# # We can use the income_boosted and boost_amount variables to remove the income boost from people and visualise that
+# 
+# base.sub2 <- base.dat %>%
+#   select(pidp, time, equivalent_income, alive) %>%
+#   filter(alive != 'dead') %>%
+#   select(-alive) %>%
+#   rename(baseline = equivalent_income)
+# 
+# allchild.sub2 <- allchild.dat %>%
+#   select(pidp, time, equivalent_income, income_boosted, boost_amount, alive) %>%
+#   filter(alive != 'dead') %>%
+#   select(-alive) %>%
+#   rename(allchild = equivalent_income)
+# 
+# allchild.merged <- merge(base.sub2, allchild.sub2, by = c('pidp', 'time'))
+#   
+# boosted.pidps <- allchild.sub2 %>%
+#   filter(income_boosted == 'True') %>%
+#   select(pidp)
+# 
+# allchild.boosted <- allchild.merged %>%
+#   filter(pidp %in% boosted.pidps$pidp) %>%
+#   filter(income_boosted == 'True' | time == 2020) %>%
+#   mutate(adjusted_EI = allchild - boost_amount) %>%
+#   select(-allchild, -income_boosted, -boost_amount) %>%
+#   group_by(time) %>%
+#   summarise(baseline = mean(baseline),
+#             allchild_adj = mean(adjusted_EI)) %>%
+#   pivot_longer(cols = baseline:allchild_adj,
+#                names_to = 'scenario',
+#                values_to = 'equivalent_income')
 ```
@@
 ```{r}
-ggplot(data = allchild.boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
-  geom_line()
+# ggplot(data = allchild.boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
+#   geom_line()
 ```
@@
 ```{r}
-base.inc <- base.dat %>%
-  select(pidp, time, hh_income, equivalent_income, weight) %>%
-  group_by(time) %>%
-  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
-            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
-  mutate(source = 'Baseline')
-
-int.inc <- wage.dat %>%
-  select(pidp, time, hh_income, equivalent_income, weight) %>%
-  group_by(time) %>%
-  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
-            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
-  mutate(source = 'Living_Wage')
-
-combined <- rbind(base.inc, int.inc)
-combined <- combined %>%
-  pivot_longer(cols=hh_income:equivalent_income,
-               names_to = 'income_type',
-               values_to = 'value')
-
-ggplot(combined, aes(x = time, y = value, group = source, color = source)) +
-  geom_line() +
-  facet_wrap( ~ income_type, nrow=2, scales='free')
+# base.inc <- base.dat %>%
+#   select(pidp, time, hh_income, equivalent_income, weight) %>%
+#   group_by(time) %>%
+#   summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+#             equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
+#   mutate(source = 'Baseline')
+# 
+# int.inc <- wage.dat %>%
+#   select(pidp, time, hh_income, equivalent_income, weight) %>%
+#   group_by(time) %>%
+#   summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+#             equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
+#   mutate(source = 'Living_Wage')
+# 
+# combined <- rbind(base.inc, int.inc)
+# combined <- combined %>%
+#   pivot_longer(cols=hh_income:equivalent_income,
+#                names_to = 'income_type',
+#                values_to = 'value')
+# 
+# ggplot(combined, aes(x = time, y = value, group = source, color = source)) +
+#   geom_line() +
+#   facet_wrap( ~ income_type, nrow=2, scales='free')
 ```
@@
 
+income_equivinc_change_percent <- function(base.dat, int.dat) {
+  base.inc <- base.dat %>%
+    select(pidp, time, hh_income, equivalent_income, weight) %>%
+    group_by(time) %>%
+    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  int.inc <- int.dat %>%
+    select(pidp, time, hh_income, equivalent_income, weight) %>%
+    group_by(time) %>%
+    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
+              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
+
+  combined <- merge(base.inc, int.inc, by = c('time'))
+
+  combined$diff_income <- combined$energy_income - combined$base_income
+  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income
+
+  combined <- combined %>%
+    group_by(time) %>%
+    summarise(mean_income = mean(base_income),
+              mean_equiv_income = mean(base_equiv_income),
+              mean_diff_income = mean(diff_income),
+              mean_diff_equiv_income = mean(diff_equiv_income)) %>%
+    mutate(percent_change_income = (mean_diff_income / mean_income) * 100,
+           percent_change_equiv_income = (mean_diff_equiv_income / mean_equiv_income) * 100) %>%
+    select(-mean_income, -mean_equiv_income, -mean_diff_income, -mean_diff_equiv_income) %>%
+    pivot_longer(cols = percent_change_income:percent_change_equiv_income,
+                 names_prefix = 'percent_change_',
+                 names_to = 'variable',
+                 values_to = 'percent_change')
+
+  ggplot(combined, aes(x = time, y = percent_change, group = variable, color = variable)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype = 'dashed')
+}
+
 income_equivinc_change(base.dat, energy.dat)
-income_equivinc_change(base.dat, wage.dat)
+income_equivinc_change_percent(base.dat, energy.dat)
+#income_equivinc_change(base.dat, wage.dat)
 ```
@@
 ```{r}
-## just look at means in case the means are causing some problems
-base.dat.2 <- base.dat
-base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'No to all'] <- 1
-base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to some'] <- 2
-base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to all'] <- 3
-wage.dat.2 <- energy.dat
-wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'No to all'] <- 1
-wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to some'] <- 2
-wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to all'] <- 3
-
-base.hous.mean <- base.dat.2 %>%
-  select(pidp, time, S7_housing_quality2, weight) %>%
-  group_by(time) %>%
-  summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
-  mutate(source = 'Baseline')
-wage.hous.mean <- wage.dat.2 %>%
-  select(pidp, time, S7_housing_quality2, weight) %>%
-  group_by(time) %>%
-  summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
-  mutate(source = 'EnergyCrisis')
-
-combined <- rbind(base.hous.mean, wage.hous.mean)
-
-ggplot(combined, aes(x = time, y = mean_housing, group = source, color = source)) +
-  geom_line() +
-  geom_point()
+# ## just look at means in case the means are causing some problems
+# base.dat.2 <- base.dat
+# base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'No to all'] <- 1
+# base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to some'] <- 2
+# base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to all'] <- 3
+# wage.dat.2 <- energy.dat
+# wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'No to all'] <- 1
+# wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to some'] <- 2
+# wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to all'] <- 3
+# 
+# base.hous.mean <- base.dat.2 %>%
+#   select(pidp, time, S7_housing_quality2, weight) %>%
+#   group_by(time) %>%
+#   summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
+#   mutate(source = 'Baseline')
+# wage.hous.mean <- wage.dat.2 %>%
+#   select(pidp, time, S7_housing_quality2, weight) %>%
+#   group_by(time) %>%
+#   summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
+#   mutate(source = 'EnergyCrisis')
+# 
+# combined <- rbind(base.hous.mean, wage.hous.mean)
+# 
+# ggplot(combined, aes(x = time, y = mean_housing, group = source, color = source)) +
+#   geom_line() +
+#   geom_point()
 ```

### 2023-09-12 minos/outcomes/equivalent_income_out2.Rmd
Changed loneliness to string var from numeric so its easier to understand. Also lots of changes to EI plots

---
title: "Equivalent Income Outcome Visualisation - 2"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(here)
require(dplyr)
require(tidyr)
require(purrr)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

```{r, include=FALSE}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

# Data

```{r}
# set output path to SIPHER 7 experiment out
out.path <- here::here('output', 'SIPHER7/')
# read all files into dataframe (util function handles runtime subdirectory etc.)
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
allchild.dat <- read_singular_local_out(out.path, 'hhIncomeChildUplift', drop.dead = TRUE)
pov.dat <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift', drop.dead = TRUE)
wage.dat <- read_singular_local_out(out.path, 'livingWageIntervention', drop.dead = TRUE)
energy.dat <- read_singular_local_out(out.path, 'energyDownlift', drop.dead = TRUE)
```

## Remove 2020 Data Point

```{r}
base.dat <- filter(base.dat, time > 2020)
allchild.dat <- filter(allchild.dat, time > 2020)
pov.dat <- filter(pov.dat, time > 2020)
wage.dat <- filter(wage.dat, time > 2020)
energy.dat <- filter(energy.dat, time > 2020)
```

## BATCH DATA

```{r}
#S7.var.list <- c('hh_income', 'equivalent_income', 'housing_quality', 'neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness')
#out.path.batch <- here::here('output', 'SIPHER7_batch/')

#base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=TRUE)
#wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
#energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
```

# Baseline

```{r}
base.subset <- base.dat %>%
  select(pidp, time, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))

base.subset$scenario <- 'Baseline'

ggplot(data = base.subset, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
  geom_line()
```

## Batch

```{r}
# base.bat.sub <- base.batch %>%
#   select(pidp, time, run_id, equivalent_income, weight) %>%
#   group_by(run_id, time) %>%
#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm=TRUE))
# 
# ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
#   geom_line()
# 
# ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income)) +
#   geom_smooth()
# 
# base.bat.sub2 <- base.bat.sub %>%
#   group_by(time) %>%
#   summarise(var = mean(equivalent_income),
#          min = min(equivalent_income),
#          max = max(equivalent_income))
# 
# ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
#   geom_line() +
#   geom_ribbon(aes(ymin = min, ymax = max), 
#                 alpha = 0.1,
#                 linetype = 'dashed')
```

# Comparisons

## Function

```{r}
equivalent_income_comparison_fullpop <- function(base, int, int.name, save=FALSE, save.path=NULL) {
  base.subset <- base %>%
    select(pidp, time, equivalent_income, alive, weight) %>%
    filter(alive != 'dead') %>%
    group_by(time) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
  int.subset <- int %>%
    select(pidp, time, equivalent_income, alive, weight) %>%
    filter(alive != 'dead') %>%
    group_by(time) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))

  base.subset$scenario <- 'Baseline'
  int.subset$scenario <- int.name

  combined <- rbind(base.subset, int.subset)

  p <- ggplot(combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
    geom_line() +
    labs(title = paste0('Equivalent Income: ', int.name), subtitle = 'Full Population') +
    xlab('Year') +
    ylab('Equivalent Income (£)')

  print(p)

  if(save) {
    if(is.null(save.path)) {
      stop('ERROR: save.path cannot be missing if save=TRUE')
    }
    file.name <- paste0('EI_comp_', int.name, '_full.png')
    ggsave(filename = file.name,
           plot = p,
           path = save.path)
  }
}

equivalent_income_comparison_fullpop_batch <- function(base.bat, int.bat, int.name, save=FALSE, save.path=NULL) {
  base.subset <- base.bat %>%
    select(pidp, time, run_id, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
  int.subset <- int.bat %>%
    select(pidp, time, run_id, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))

  base.subset$scenario <- 'Baseline'
  int.subset$scenario <- int.name

  combined <- rbind(base.subset, int.subset)

  p <- ggplot(combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
    geom_smooth() +
    labs(title = paste0('Equivalent Income: ', int.name), subtitle = '10 Runs') +
    xlab('Year') +
    ylab('Equivalent Income (£)')

  print(p)
}
```

## Plots

```{r}
equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild')
equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild')
equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage')
equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift')

# equivalent_income_comparison_fullpop_batch(base.batch, wage.batch, 'LivingWage')
# equivalent_income_comparison_fullpop_batch(base.batch, energy.batch, 'EnergyCrisis')
```

## Combined

```{r}
base.subset <- base.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
base.subset$scenario <- 'Baseline'

allchild.subset <- allchild.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
allchild.subset$scenario <- 'AllChild'

pov.subset <- pov.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
pov.subset$scenario <- 'PovertyChild'

wage.subset <- wage.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
wage.subset$scenario <- 'LivingWage'

energy.subset <- energy.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
energy.subset$scenario <- 'EnergyDownlift'

all.combined <- rbind(base.subset, allchild.subset, pov.subset, wage.subset, energy.subset)
all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'AllChild', 'PovertyChild', 'LivingWage', 'EnergyDownlift'))

ggplot(data = all.combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
  geom_line() +
  labs(title = 'Equivalent Income Comparison', subtitle = 'Whole Population') +
  xlab('Year') +
  ylab('Equivalent Income (£)')
```

```{r}
# base.subset <- base.batch %>%
#   select(pidp, time, run_id, equivalent_income, weight) %>%
#   group_by(time, run_id) %>%
#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
#   mutate(scenario = 'Baseline')
# 
# wage.subset <- wage.batch %>%
#   select(pidp, time, run_id, equivalent_income, weight) %>%
#   group_by(time, run_id) %>%
#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
#   mutate(scenario = 'LivingWage')
# 
# energy.subset <- energy.batch %>%
#   select(pidp, time, run_id, equivalent_income, weight) %>%
#   group_by(time, run_id) %>%
#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
#   mutate(scenario = 'EnergyCrisis')
# 
# all.combined <- rbind(base.subset, wage.subset, energy.subset)
# all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'LivingWage', 'EnergyCrisis'))
# 
# ggplot(data = all.combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
#   geom_smooth() +
#   labs(title = 'Equivalent Income Comparison', subtitle = 'Whole Population') +
#   xlab('Year') +
#   ylab('Equivalent Income (£)')
```

# Treated Population

## Function

```{r}
equivalent_income_comparison_treated <- function(base, int, int.name, save=FALSE, save.path=NULL) {
  base.sub <- base %>%
    select(pidp, time, equivalent_income, alive) %>%
    filter(alive != 'dead') %>%
    select(-alive) %>%
    rename(baseline = equivalent_income)
  int.sub <- int %>%
    select(pidp, time, equivalent_income, income_boosted, alive, weight) %>%
    filter(alive != 'dead') %>%
    select(-alive) %>%
    set_names(c('pidp', 'time', int.name, 'income_boosted', 'weight'))

  merged <- merge(base.sub, int.sub, by = c('pidp', 'time'))

  boosted.pidps <- int.sub %>%
    filter(income_boosted == 'True') %>%
    select(pidp)

  boosted <- merged %>%
    filter(pidp %in% boosted.pidps$pidp) %>%
    filter(income_boosted == 'True' | time == 2020) %>%
    select(-income_boosted) %>%
    pivot_longer(cols = baseline:.data[[int.name]],
                 names_to = 'scenario',
                 values_to = 'equivalent_income') %>%
    group_by(time, scenario) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w=weight))

  p <- ggplot(data = boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
    geom_line() +
    labs(title = paste0('Equivalent Income: ', int.name), subtitle = 'Treated Population') +
    xlab('Year') +
    ylab('Equivalent Income (£)')

  print(p)

  if(save) {
    if(is.null(save.path)) {
      stop('ERROR: save.path cannot be missing if save=TRUE')
    }
    file.name <- paste0('EI_comp_', int.name, '_treated.png')
    ggsave(filename = file.name,
           plot = p,
           path = save.path)
  }
}

equivalent_income_comparison_treated_batch <- function(base.bat, int.bat, int.name, save=FALSE, save.path=NULL) {
  base.sub <- base.bat %>%
    select(pidp, time, run_id, equivalent_income) %>%
    rename(baseline = equivalent_income)
  int.sub <- int.bat %>%
    select(pidp, time, run_id, equivalent_income, income_boosted, weight) %>%
    set_names(c('pidp', 'time', 'run_id', int.name, 'income_boosted', 'weight'))

  merged <- merge(base.sub, int.sub, by = c('pidp', 'time', 'run_id'))

  boosted.pidps <- int.sub %>%
    filter(income_boosted == 'True') %>%
    select(pidp)

  boosted <- merged %>%
    filter(pidp %in% boosted.pidps$pidp) %>%
    filter(income_boosted == 'True' | time == 2020) %>%
    select(-income_boosted) %>%
    pivot_longer(cols = baseline:.data[[int.name]],
                 names_to = 'scenario',
                 values_to = 'equivalent_income') %>%
    group_by(time, scenario, run_id) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w=weight))

  p <- ggplot(data = boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
    geom_smooth() +
    labs(title = paste0('Equivalent Income: ', int.name), subtitle = 'Treated Population') +
    xlab('Year') +
    ylab('Equivalent Income (£)')

  print(p)
}
```

## Plots

```{r}
equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild')
equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild')
equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage')
equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift')

# equivalent_income_comparison_treated_batch(base.batch, wage.batch, 'LivingWage')
# equivalent_income_comparison_treated_batch(base.batch, energy.batch, 'EnergyDownlift')
```

# Remove Income Effect

```{r, include=FALSE}
# THink about this...
# We can use the income_boosted and boost_amount variables to remove the income boost from people and visualise that

base.sub2 <- base.dat %>%
  select(pidp, time, equivalent_income, alive) %>%
  filter(alive != 'dead') %>%
  select(-alive) %>%
  rename(baseline = equivalent_income)

allchild.sub2 <- allchild.dat %>%
  select(pidp, time, equivalent_income, income_boosted, boost_amount, alive) %>%
  filter(alive != 'dead') %>%
  select(-alive) %>%
  rename(allchild = equivalent_income)

allchild.merged <- merge(base.sub2, allchild.sub2, by = c('pidp', 'time'))

boosted.pidps <- allchild.sub2 %>%
  filter(income_boosted == 'True') %>%
  select(pidp)

allchild.boosted <- allchild.merged %>%
  filter(pidp %in% boosted.pidps$pidp) %>%
  filter(income_boosted == 'True' | time == 2020) %>%
  mutate(adjusted_EI = allchild - boost_amount) %>%
  select(-allchild, -income_boosted, -boost_amount) %>%
  group_by(time) %>%
  summarise(baseline = mean(baseline),
            allchild_adj = mean(adjusted_EI)) %>%
  pivot_longer(cols = baseline:allchild_adj,
               names_to = 'scenario',
               values_to = 'equivalent_income')
```

```{r}
ggplot(data = allchild.boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
  geom_line()
```

NOTE: Can we 'remove' the income effect?
Use the boost amount and income_boosted variables to sort of 'undo' the intervention effect and then we are only visualising the difference from pathway changes and not just the income effect.

ALSO: Difference plots.

# DETAILED ANALYSIS

## Living Wage

For this, we're going to look at the difference in equivalent income and try to explain it by looking at the pathway variables. What we want to see is that as income is uplifted, the various pathways show a positive shift and that in part explains the difference in equivalent income.

First visualise both income and equivalent income on one graph.

### Income and Equivalent Income

```{r}
base.inc <- base.dat %>%
  select(pidp, time, hh_income, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'Baseline')

int.inc <- wage.dat %>%
  select(pidp, time, hh_income, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'Living_Wage')

combined <- rbind(base.inc, int.inc)
combined <- combined %>%
  pivot_longer(cols=hh_income:equivalent_income,
               names_to = 'income_type',
               values_to = 'value')

ggplot(combined, aes(x = time, y = value, group = source, color = source)) +
  geom_line() +
  facet_wrap( ~ income_type, nrow=2, scales='free')
```

### CHANGE IN INCOME / EQUIVALENT INCOME

```{r}
base.inc <- base.dat %>%
  select(pidp, time, hh_income, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'Baseline')

int.inc <- energy.dat %>%
  select(pidp, time, hh_income, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'EnergyCrisis')

combined <- rbind(base.inc, int.inc)
combined <- combined %>%
  pivot_longer(cols=hh_income:equivalent_income,
               names_to = 'income_type',
               values_to = 'value')

ggplot(combined, aes(x = time, y = value, group = source, color = source)) +
  geom_line() +
  facet_wrap( ~ income_type, nrow=2, scales='free')
```

How about on the same plot to make it more clear?

```{r}
income_equivinc_change <- function(base.dat, int.dat) {
  base.inc <- base.dat %>%
    select(pidp, time, hh_income, equivalent_income, weight) %>%
    group_by(time) %>%
    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  int.inc <- int.dat %>%
    select(pidp, time, hh_income, equivalent_income, weight) %>%
    group_by(time) %>%
    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  combined <- merge(base.inc, int.inc, by = c('time'))

  combined$diff_income <- combined$energy_income - combined$base_income
  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income

  combined <- combined %>%
    pivot_longer(cols = diff_income:diff_equiv_income,
                 names_prefix = 'diff_',
                 names_to = 'variable',
                 values_to = 'diff')

  ggplot(combined, aes(x = time, y = diff, group = variable, color = variable)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype = 'dashed')
}

income_equivinc_change_batch <- function(base.batch, int.batch) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  int.inc <- int.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  combined <- merge(base.inc, int.inc, by = c('time', 'run_id'))

  combined$diff_income <- combined$energy_income - combined$base_income
  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income

  combined <- combined %>%
    pivot_longer(cols = diff_income:diff_equiv_income,
                 names_prefix = 'diff_',
                 names_to = 'variable',
                 values_to = 'diff')

  ggplot(combined, aes(x = time, y = diff, group = variable, color = variable)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed')
}

income_equivinc_change(base.dat, energy.dat)
# income_equivinc_change_batch(base.batch, energy.batch)

income_equivinc_change(base.dat, wage.dat)
# income_equivinc_change_batch(base.batch, wage.batch)
```

### Percent Change

Proportional difference? Percentage difference in income and equivalent income over time?

```{r}
income_equivinc_percent_change_batch <- function(base.batch, int.batch) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  int.inc <- int.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  combined <- merge(base.inc, int.inc, by = c('time', 'run_id'))

  combined$diff_income <- combined$energy_income - combined$base_income
  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income

  combined <- combined %>%
    group_by(time) %>%
    summarise(mean_income = mean(base_income),
              mean_equiv_income = mean(base_equiv_income),
              mean_diff_income = mean(diff_income),
              mean_diff_equiv_income = mean(diff_equiv_income)) %>%
    mutate(percent_change_income = (mean_diff_income / mean_income) * 100,
           percent_change_equiv_income = (mean_diff_equiv_income / mean_equiv_income) * 100) %>%
    select(-mean_income, -mean_equiv_income, -mean_diff_income, -mean_diff_equiv_income) %>%
    pivot_longer(cols = percent_change_income:percent_change_equiv_income,
                 names_prefix = 'percent_change_',
                 names_to = 'variable',
                 values_to = 'change')

  ggplot(combined, aes(x = time, y = change, group = variable, color = variable)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = 'Percent change: Income vs Equivalent Income') +
    xlab('Year') +
    ylab('Percent Change')
}

# income_equivinc_percent_change_batch(base.batch, energy.batch)
# income_equivinc_percent_change_batch(base.batch, wage.batch)

```

## Energy Crisis

### Housing Quality

```{r}
S7_ordinal_pathway_vis <- function(base.dat, int.dat, int.name, var) {
  base.hous <- base.dat %>%
    select(pidp, time, all_of(var)) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    group_by(time) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = 'Baseline')

  inc.hous <- int.dat %>%
    select(pidp, time, all_of(var)) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    group_by(time) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = int.name)

  combined <- rbind(base.hous, inc.hous)
  combined[[var]] <- as.factor(combined[[var]])

  p1 <- ggplot(combined, aes(x = time, y = prop, group = interaction(.data[[var]], source), color = .data[[var]], linetype = source)) +
    geom_line() +
    geom_point()

  print(p1)

  base.hous2 <- base.dat %>%
    select(pidp, time, all_of(var)) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    group_by(time) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = (n / total) * 100) %>%
    select(-n, -total) %>%
    rename(Baseline = prop)

  int.hous2 <- int.dat %>%
    select(pidp, time, all_of(var)) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    group_by(time) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = (n / total) * 100) %>%
    select(-n, -total) %>%
    rename(int = prop)

  combined2 <- merge(base.hous2, int.hous2, by = c('time', var))

  combined2[[var]] <- as.factor(combined2[[var]])

  combined2$diff <- combined2$int - combined2$Baseline

  p2 <- ggplot(combined2, aes(x = time, y = diff, group = .data[[var]], color = .data[[var]])) +
    geom_line() +
    geom_point()

  print(p2)
}

S7_ordinal_pathway_vis_batch <- function(base.bat, int.bat, int.name, var) {
  base.hous <- base.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = 'Baseline')

  inc.hous <- int.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = int.name)

  combined <- rbind(base.hous, inc.hous)
  combined[[var]] <- as.factor(combined[[var]])

  p1 <- ggplot(combined, aes(x = time, y = prop, group = interaction(.data[[var]], source), color = .data[[var]], linetype = source)) +
    geom_smooth()

  print(p1)

  base.hous2 <- base.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = (n / total) * 100) %>%
    select(-n, -total) %>%
    rename(Baseline = prop)

  int.hous2 <- int.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = (n / total) * 100) %>%
    select(-n, -total) %>%
    rename(int = prop)

  combined2 <- merge(base.hous2, int.hous2, by = c('time', 'run_id', var))

  combined2[[var]] <- as.factor(combined2[[var]])

  combined2$diff <- combined2$int - combined2$Baseline

  p2 <- ggplot(combined2, aes(x = time, y = diff, group = .data[[var]], color = .data[[var]]), fill = .data[[var]]) +
    geom_smooth() +
    labs(title = paste0(int.name, ': Change from Baseline')) +
    xlab('Year') +
    ylab('Change')

  print(p2)
}

```

### Housing Quality

```{r}
S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'housing_quality')
# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'housing_quality')
```

### Neighbourhood Safety

```{r}
S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'neighbourhood_safety')
# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'neighbourhood_safety')
```

### Mental Wellbeing

```{r}
S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_mental_health')
# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_mental_health')
```

### Physical Health

```{r}
S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_physical_health')
# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_physical_health')
```

### Loneliness

```{r}
S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'loneliness')
# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'loneliness')
```

### Labour State

```{r}
S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_labour_state')
# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_labour_state')
```

```{r}
boosted.pidps <- energy.dat %>%
  filter(income_boosted == 'True') %>%
  select(pidp)

base.hous <- base.dat %>%
  select(pidp, time, housing_quality) %>%
  filter(pidp %in% boosted.pidps$pidp) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prop = (n / total) * 100) %>%
  select(-n, -total) %>%
  rename(Baseline = prop)

int.hous <- energy.dat %>%
  select(pidp, time, housing_quality, income_boosted) %>%
  filter(pidp %in% boosted.pidps$pidp) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prop = (n / total) * 100) %>%
  select(-n, -total) %>%
  rename(EnergyCrisis = prop)

combined <- merge(base.hous, int.hous, by = c('time', 'housing_quality'))

combined$diff <- combined$EnergyCrisis - combined$Baseline

ggplot(combined, aes(x = time, y = diff, group = housing_quality, color = housing_quality)) +
  geom_line() +
  geom_point()
```

```{r}
## just look at means in case the means are causing some problems
base.dat.2 <- base.dat
base.dat.2$housing_quality2[base.dat.2$housing_quality == 'No to all'] <- 1
base.dat.2$housing_quality2[base.dat.2$housing_quality == 'Yes to some'] <- 2
base.dat.2$housing_quality2[base.dat.2$housing_quality == 'Yes to all'] <- 3
wage.dat.2 <- energy.dat
wage.dat.2$housing_quality2[wage.dat.2$housing_quality == 'No to all'] <- 1
wage.dat.2$housing_quality2[wage.dat.2$housing_quality == 'Yes to some'] <- 2
wage.dat.2$housing_quality2[wage.dat.2$housing_quality == 'Yes to all'] <- 3

base.hous.mean <- base.dat.2 %>%
  select(pidp, time, housing_quality2, weight) %>%
  group_by(time) %>%
  summarise(mean_housing = weighted.mean(housing_quality2, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'Baseline')
wage.hous.mean <- wage.dat.2 %>%
  select(pidp, time, housing_quality2, weight) %>%
  group_by(time) %>%
  summarise(mean_housing = weighted.mean(housing_quality2, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'EnergyCrisis')

combined <- rbind(base.hous.mean, wage.hous.mean)

ggplot(combined, aes(x = time, y = mean_housing, group = source, color = source)) +
  geom_line() +
  geom_point()
```

```{r}

# df <- combine_and_pivot_long(base.dat, 'Baseline', wage.dat, 'LivingWage', c('housing_quality', 'income_boosted'))
# 
# outcomes.prep <- function(base.dat, int.dat, int.name, var) {
#   boosted.pidps <- int.dat %>%
#     filter(income_boosted == 'True') %>%
#     select(pidp, time)
#   
#   df1 <- base.dat %>%
#     select(pidp, time, all_of(var), weight) %>%
#     
# }
# 
# 
# 
# 
# combine_and_pivot_long <- function(df1, df1.name, df2, df2.name, var) {
#   # get only the columns we want a rename
#   df1 <- df1 %>%
#     select('pidp', 'time', all_of(var)) %>%
#     set_names(c('pidp', 'time', df1.name))
#   df2 <- df2 %>%
#     select('pidp', 'time', all_of(var)) %>%
#     set_names(c('pidp', 'time', df2.name))
#   # merge on pidp and time
#   merged <- merge(df1, df2, by = c('pidp', 'time'), all=TRUE)
#   pivoted <- pivot_longer(data = merged,
#                           cols = df1.name:df2.name,
#                           names_to = 'scenario',
#                           values_to = var)
#   return(pivoted)
# }

```

### 2023-09-12 minos/outcomes/equivalent_income_out_batch.Rmd
Some tweaks to equivalent_income_out_batch and tweaked the aggregation to be more verbose
Lots of little things on equivalent income and job_sec module
Changed loneliness to string var from numeric so its easier to understand. Also lots of changes to EI plots

@@
 
-## Income and Equivalent Income
+# Income and Equivalent Income
 
@@
 
-  print(combined2)
-
   ggplot(combined, aes(x = time, y = diff, group = variable, color = variable)) +
@@
 
-## Equivalent Income Change
+# Equivalent Income Change
 
@@
 
-### By Subpopulation
+## By Subpopulation
 
@@
     geom_hline(yintercept = 0, linetype = 'dashed') +
-    labs(title = paste0('Equivalent Income change by ', group.var), subtitle = int.name) +
+    labs(title = paste0('Absolute change')) +
     xlab('Year') +
@@
 
-## Percent Change
+# Percent Change
 
@@
 
-### All Subgroups
+## All Subgroups
 
@@
     geom_hline(yintercept = 0, linetype = 'dashed') +
-    labs(title = paste0('Percent change by ', group.var), subtitle = int.name) +
+    labs(title = paste0('Percent change')) +
     xlab('Year') +
-    ylab('Percent Change')
+    ylab('Percent Change (%)') +
+    scale_fill_discrete(name = 'Income Quintile')
 }
@@
 
-#### Energy Crisis
+### Energy Crisis
 
@@
 
-#### Living Wage
+### Living Wage
 
@@
 
-#### All Child
+### All Child
 
@@
 
-#### Poverty Child
+### Poverty Child
 

### 2023-09-12 minos/validation/handovers_S7.Rmd
Changed loneliness to string var from numeric so its easier to understand. Also lots of changes to EI plots

@@
 
-## just look at means in case the means are causing some problems
-raw.dat.2 <- raw.dat
-raw.dat.2$S7_housing_quality2[raw.dat.2$S7_housing_quality == 'No to all'] <- 1
-raw.dat.2$S7_housing_quality2[raw.dat.2$S7_housing_quality == 'Yes to some'] <- 2
-raw.dat.2$S7_housing_quality2[raw.dat.2$S7_housing_quality == 'Yes to all'] <- 3
-base.dat.2 <- base.dat
-base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'No to all'] <- 1
-base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to some'] <- 2
-base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to all'] <- 3
-
-handover_lineplots(raw.dat.2, base.dat.2, 'S7_housing_quality2')
-
 rm(prepped.list, housing, housing.norm)
@@
 
-raw.dat.2 <- raw.dat
-raw.dat.2$S7_labour_state2[raw.dat.2$S7_labour_state == 'PT Employed'] <- 6
-raw.dat.2$S7_labour_state2[raw.dat.2$S7_labour_state == 'FT Employed'] <- 5
-raw.dat.2$S7_labour_state2[raw.dat.2$S7_labour_state == 'FT Education'] <- 4
-raw.dat.2$S7_labour_state2[raw.dat.2$S7_labour_state == 'Not Working'] <- 3
-raw.dat.2$S7_labour_state2[raw.dat.2$S7_labour_state == 'Job Seeking'] <- 2
-raw.dat.2$S7_labour_state2[raw.dat.2$S7_labour_state == 'Family Care'] <- 1
-base.dat.2 <- base.dat
-base.dat.2$S7_labour_state2[base.dat.2$S7_labour_state == 'PT Employed'] <- 6
-base.dat.2$S7_labour_state2[base.dat.2$S7_labour_state == 'FT Employed'] <- 5
-base.dat.2$S7_labour_state2[base.dat.2$S7_labour_state == 'FT Education'] <- 4
-base.dat.2$S7_labour_state2[base.dat.2$S7_labour_state == 'Not Working'] <- 3
-base.dat.2$S7_labour_state2[base.dat.2$S7_labour_state == 'Job Seeking'] <- 2
-base.dat.2$S7_labour_state2[base.dat.2$S7_labour_state == 'Family Care'] <- 1
-
-handover_lineplots(raw.dat.2, base.dat.2, 'S7_labour_state2')
-
 rm(prepped.list, lab.state, lab.state.norm)
@@
 
-handover_lineplots(raw.dat, base.dat, 'S7_mental_health')
-
 rm(prepped.list, var, norm, tit)
@@
 }
-
-handover_lineplots(raw.dat, base.dat, 'loneliness')
 

### 2023-09-12 minos/data_generation/US_format_raw.py

@@ -476,6 +476,22 @@ def format_analysis_weight(data, year):
     return data
 
 
+def format_loneliness(data):
+    data['new_loneliness'] = -9
+
+    data['new_loneliness'][data['loneliness'] == 1] = 'Never'
+    data['new_loneliness'][data['loneliness'] == 2] = 'Sometimes'
+    data['new_loneliness'][data['loneliness'] == 3] = 'Often'
+
+    data['loneliness'] = data['new_loneliness']
+
+    data.drop(labels=['new_loneliness'],
+              axis=1,
+              inplace=True)
+
+    return data
+
+
 def combine_indresp_hhresp(year, indresp_name, hhresp_name):
     """ Function to collect and merge the indresp and hhresp files for a specific year.
 
@@ -535,6 +551,7 @@ def format_data(year, data):
     #data = format_mental_state(data)
     data = format_time(data, year)
     data = format_location(data, year)
+    data = format_loneliness(data)
 
     data = format_ukhls_ethnicity(data)
     data = format_ukhls_employment(data)

### 2023-09-12 minos/modules/S7EquivalentIncome.py

@@ -140,9 +140,9 @@ class S7EquivalentIncome(Base):
             1: -0.877/1.282
         }
         loneliness_dict = {
-            1: 0,
-            2: -0.186/1.282,
-            3: -0.591/1.282
+            'Never': 0,
+            'Sometimes': -0.186/1.282,
+            'Often': -0.591/1.282
         }
         employment_dict = {
             'FT Employed': 0,

### 2023-09-13 minos/outcomes/EI_PresPlots_SimpleBatch.Rmd
Testing out nnet models and how that affects S7 and EI outcomes

@@
                  'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
-out.path.batch <- here::here('output', 'SIPHER7_batch/')
+out.path.batch <- here::here('output', 'SIPHER7_batch2/')
 
-base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
-int.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=TRUE)
+int.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
 
-int.name <- 'Living Wage'
+int.name <- 'Energy Crisis'
 ```

### 2023-09-13 minos/modules/S7Housing.py

@@ -91,18 +91,22 @@ class S7Housing(Base):
 
         housing_prob_df = self.calculate_housing(pop)
 
-        housing_prob_df["S7_housing_quality"] = self.random.choice(housing_prob_df.index,
-                                                                list(housing_prob_df.columns),
-                                                                housing_prob_df) + 1
+        # housing_prob_df["S7_housing_quality"] = self.random.choice(housing_prob_df.index,
+        #                                                         list(housing_prob_df.columns),
+        #                                                         housing_prob_df) + 1
+        #
+        # housing_prob_df.index = housing_prob_df.index.astype(int)
+        #
+        # # convert numeric prediction into string factors (low, medium, high)
+        # housing_factor_dict = {1: 'No to all',
+        #                        2: 'Yes to some',
+        #                        3: 'Yes to all'}
+        # housing_prob_df.replace({'S7_housing_quality': housing_factor_dict},
+        #                         inplace=True)
 
+        housing_prob_df["S7_housing_quality"] = self.random.choice(housing_prob_df.index, list(housing_prob_df.columns),
+                                                               housing_prob_df)
         housing_prob_df.index = housing_prob_df.index.astype(int)
-
-        # convert numeric prediction into string factors (low, medium, high)
-        housing_factor_dict = {1: 'No to all',
-                               2: 'Yes to some',
-                               3: 'Yes to all'}
-        housing_prob_df.replace({'S7_housing_quality': housing_factor_dict},
-                                inplace=True)
 
 
         self.population_view.update(housing_prob_df["S7_housing_quality"])
@@ -117,15 +121,18 @@ class S7Housing(Base):
         Returns
         -------
         """
+        cols = ['No to all', 'Yes to some', 'Yes to all']
+
         # load transition model based on year.
         if self.cross_validation:
             # if cross-val, fix year to final year model
             year = 2019
         else:
             year = min(self.year, 2019)
-        transition_model = r_utils.load_transitions(f"S7_housing_quality/clm/S7_housing_quality_{year}_{year+1}", self.rpy2Modules, path=self.transition_dir)
+        transition_model = r_utils.load_transitions(f"S7_housing_quality/nnet/S7_housing_quality_{year}_{year+1}", self.rpy2Modules, path=self.transition_dir)
         # returns probability matrix (3xn) of next ordinal state.
[…]

### 2023-09-17 minos/outcomes/EI_PresPlots_Refined.Rmd
Lots of testing on S7 component models. Also added a script to check the proportional odds assumption for deciding between clm and nnet. Still working on a function to add to the transition estimation scripts to produce a file with each model

--- 2023-09-12 minos/outcomes/EI_PresPlots_SimpleBatch.Rmd
@@
 ---
-title: "Equivalent Income Stuff - Energy Crisis Plots"
+title: "Equivalent Income Presentation Plots - FINAL"
 output:
@@
 
-base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
-int.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=TRUE)
+int.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
 
-int.name <- 'Living Wage'
+# out.path.arc2 <- here::here('output', 'batch')
+# 
+# #target.pattern <- paste0('aggregated_run_id_', year, '.csv')
+# base.list <- list.files(path = paste0(out.path.arc2, '/baseline'),
+#                             full.names = TRUE)
+# base.batch <- do.call(rbind, lapply(base.list, read.csv))
+# 
+# energy.list <- list.files(path = paste0(out.path.arc2, '/energy'),
+#                             full.names = TRUE)
+# int.batch <- do.call(rbind, lapply(energy.list, read.csv))
+
+int.name <- 'Energy Crisis'
 ```
@@
 }
-```
 
-# Income and Equivalent Income
-
-```{r}
-income_equivinc_change_batch(base.batch, int.batch, int.name)
-```
-
-# EquivInc split by Income Quintile
-
-```{r}
-inc_change_batch_subpop(base.batch, int.batch, int.name, group.var = 'income.quint')
-equivinc_change_batch_subpop(base.batch, int.batch, int.name, group.var = 'income.quint')
-```
-
-## Percent Change
-
-```{r}
 income_equivinc_percent_change_batch <- function(base.batch, int.batch, int.name, group.var) {
@@
 
-income_equivinc_percent_change_batch(base.batch, int.batch, int.name, group.var = 'income.quint')
-
-```
-
-# Pathway Vars by Income Quintile
-
-```{r}
-## ATTEMPT 3
-
 S7_pathway_change_byGroup <- function(base.batch, int.batch, group.var, var) {
@@
 }
-```
 
-```{r}
-S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality')
-S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
-S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_physical_health')
-S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_mental_health')
-S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'loneliness')
-```
-
-## Cumulative Pathway Change
-
-```{r}
 S7_cumulative_pathwayChange_byGroup <- function(base.batch, int.batch, group.var, var) {
@@
 }
-```
 
-## Income Quintile
-
-```{r}
-S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality')
-S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
-S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_physical_health')
-S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_mental_health')
-S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'loneliness')
-```
-
-## Age Group
-
-```{r}
-S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'S7_housing_quality')
-S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'S7_neighbourhood_safety')
-S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'S7_physical_health')
-S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'S7_mental_health')
-S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'loneliness')
-```
-
-```{r}
-simplified_component_change <- function(base.batch, int.batch, group.var, var, print = FALSE) {
+simplified_component_change_BOXPLOT <- function(base.batch, int.batch, group.var, var.list, print = FALSE) {
 
@@
 
-  if (var == 'S7_housing_quality') {
   base.batch$S7_housing_quality <- as.numeric(factor(base.batch$S7_housing_quality,
@@
                                           labels = c(1, 2, 3)))
-  } else if (var == 'S7_neighbourhood_safety') {
   base.batch$S7_neighbourhood_safety <- as.numeric(factor(base.batch$S7_neighbourhood_safety,
@@
                                                labels = c(1, 2, 3)))
-  } else if (var == 'loneliness') {
-    base.batch$loneliness <- as.numeric(factor(base.batch$loneliness,
-                                    levels = c('Often', 'Sometimes', 'Never'),
-                                    labels = c(1, 2, 3)))
-    int.batch$loneliness <- as.numeric(factor(int.batch$loneliness,
-                                    levels = c('Often', 'Sometimes', 'Never'),
-                                    labels = c(1, 2, 3)))
-  }
-
-  base.sub <- base.batch %>%
-    select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
-    rename(Baseline_var = .data[[var]],
-           Baseline_group.var = .data[[group.var]])
-
-  int.sub <- int.batch %>%
-    select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
-    rename(Intervention_var = .data[[var]],
-           Intervention_group.var = .data[[group.var]])
-
-  merged <- merge(base.sub, int.sub,
-                  by=c('pidp', 'time', 'run_id'),
-                  all = FALSE)
-
-  merged2 <- merged %>%
-    mutate(varChange = Intervention_var - Baseline_var,
-           effect = case_when(varChange > 0 ~ "Positive",
-                              varChange < 0 ~ "Negative",
-                              varChange == 0 ~ "No_Change")) %>%
-    select(-Baseline_var, -Intervention_var, -Intervention_group.var, -varChange) %>%
-    rename(income.quint = Baseline_group.var) %>%
-    group_by(time, run_id, .data[[group.var]], effect) %>%
-    count() %>%
-    group_by(time, run_id, .data[[group.var]]) %>%
-    mutate(total = sum(n),
-           effect_prop = n / total) %>%
-    select(-n, -total) %>%
-    group_by(time, .data[[group.var]], effect) %>%
-    summarise(effect_prop = mean(effect_prop)) %>%
-    pivot_wider(names_from = 'effect',
-                values_from = 'effect_prop') %>%
-    mutate(change = Positive - Negative) %>%
-    select(-Positive, -Negative, -No_Change, -time) %>%
-    group_by(.data[[group.var]]) %>%
-    summarise(change = sum(change))
-
-  p1 <- ggplot(data = merged2, aes(x = .data[[group.var]], y = change)) +
-    geom_col() +
-    labs(title = paste0('Change in ', var, ' by ', group.var)) +
-    ylab('% Change')
-
-  if(print) {
-    print(p1)
-  }
-
-  return(merged2)
-}
-
-simplified_component_change_BOXPLOT <- function(base.batch, int.batch, group.var, var, print = FALSE) {
-
-  # it would be lovely if this was completely generic, but for some things that
-  # is more hassle than its worth. Handling string vars here is one of these 
-  # things
-
-  if (var == 'S7_housing_quality') {
-    base.batch$S7_housing_quality <- as.numeric(factor(base.batch$S7_housing_quality,
-                                            levels = c('No to all',
-                                                       'Yes to some',
-                                                       'Yes to all'),
-                                            labels = c(1, 2, 3)))
-    int.batch$S7_housing_quality <- as.numeric(factor(int.batch$S7_housing_quality,
-                                            levels = c('No to all',
-                                                       'Yes to some',
-                                                       'Yes to all'),
-                                            labels = c(1, 2, 3)))
-  } else if (var == 'S7_neighbourhood_safety') {
-    base.batch$S7_neighbourhood_safety <- as.numeric(factor(base.batch$S7_neighbourhood_safety,
-                                                 levels = c('Often',
-                                                            'Some of the time',
-                                                            'Hardly ever'),
-                                                 labels = c(1, 2, 3)))
-    int.batch$S7_neighbourhood_safety <- as.numeric(factor(int.batch$S7_neighbourhood_safety,
-                                                 levels = c('Often',
-                                                            'Some of the time',
-                                                            'Hardly ever'),
-                                                 labels = c(1, 2, 3)))
-  } else if (var == 'loneliness') {
   base.batch$loneliness <- as.numeric(factor(base.batch$loneliness,
@@
                                   labels = c(1, 2, 3)))
-  }
 
   base.sub <- base.batch %>%
-    select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
-    rename(Baseline_var = .data[[var]],
-           Baseline_group.var = .data[[group.var]])
+    select(pidp, time, run_id, all_of(group.var), all_of(var.list)) %>%
+    rename_with(.fn = ~paste0('Baseline_', .), .cols = all_of(var.list))
 
   int.sub <- int.batch %>%
-    select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
-    rename(Intervention_var = .data[[var]],
-           Intervention_group.var = .data[[group.var]])
+    select(pidp, time, run_id, all_of(var.list)) %>%
+    rename_with(.fn = ~paste0('Intervention_', .), .cols = all_of(var.list))
 
@@
 
-  merged2 <- merged %>%
-    mutate(varChange = Intervention_var - Baseline_var,
-           effect = case_when(varChange > 0 ~ "Positive",
-                              varChange < 0 ~ "Negative",
-                              varChange == 0 ~ "No_Change")) %>%
-    select(-Baseline_var, -Intervention_var, -Intervention_group.var, -varChange) %>%
-    rename(!!group.var := Baseline_group.var) %>%
-    group_by(time, run_id, .data[[group.var]], effect) %>%
+  # https://stackoverflow.com/questions/49694353/dplyr-mutating-multiple-columns-by-prefix-and-suffix
+
+  merged2 <- map(var.list, ~ merged %>%
+                   mutate(!!paste0("Change_", .x) := !!as.name(paste0("Intervention_", .x)) - !!as.name(paste0("Baseline_", .x)))) %>%
+    reduce(left_join) %>%
+    select(-starts_with('Baseline_'), -starts_with('Intervention_')) %>%
+    pivot_longer(cols = paste0('Change_', first(var.list)):paste0('Change_', last(var.list)),
+                 names_to = 'Variable',
+                 names_prefix = 'Change_',
+                 values_to = 'Change') %>%
+    mutate(effect = case_when(Change > 0 ~ "Positive",
+                              Change < 0 ~ "Negative",
+                              Change == 0 ~ "No_Change")) %>%
+    select(-Change) %>%
+    group_by(time, run_id, .data[[group.var]], Variable, effect) %>%
     count() %>%
-    group_by(time, run_id, .data[[group.var]]) %>%
+    group_by(time, run_id, .data[[group.var]], Variable) %>%
     mutate(total = sum(n),
-           effect_prop = n / total) %>%
+           effect_prop = (n / total) * 100) %>%
     select(-n, -total) %>%
@@
     select(-Positive, -Negative, -No_Change) %>%
-    group_by(run_id, .data[[group.var]]) %>%
+    group_by(run_id, .data[[group.var]], Variable) %>%
     summarise(sum.change = sum(change))
 
-  p1 <- ggplot(data = merged2, aes(x = .data[[group.var]], y = sum.change)) +
+  ggplot(merged2, aes(x = Variable, y = sum.change, group = Variable, colour = Variable, fill = Variable)) +
     geom_boxplot(notch = FALSE) +
+    facet_wrap(~ .data[[group.var]], nrow = 1) +
     geom_hline(yintercept = 0, linetype = 'dashed') +
-    labs(title = paste0('Change in ', var, ' by ', group.var)) +
-    ylab('% Change')
-
-  if(print) {
-    print(p1)
-  }
-
-  return(merged2)
-}
-
-```
-
-```{r}
-# simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality', print = TRUE)
-# simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety', print = TRUE)
-# simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = 'S7_mental_health', print = TRUE)
-# simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = 'S7_physical_health', print = TRUE)
-simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = 'loneliness', print = TRUE)
-```
-
-```{r}
-# simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality', print = TRUE)
-# simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety', print = TRUE)
-# simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = 'S7_mental_health', print = TRUE)
-# simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = 'S7_physical_health', print = TRUE)
-simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = 'loneliness', print = TRUE)
-```
-
-# Change in ALL vars
-
-```{r}
-varlist <- c('S7_neighbourhood_safety', 'loneliness',
-             'S7_physical_health', 'S7_mental_health')
-
-df <- simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality')
-colnames(df) <- c('Income_Quintile', 'S7_housing_quality')
-print("Completed for S7_housing_quality...")
-for (S7_var in varlist) {
-  df2 <- simplified_component_change(base.batch, int.batch, group.var = 'income.quint', var = S7_var)
-  colnames(df2) <- c('Income_Quintile', S7_var)
-  df <- merge(df, df2, by = c('Income_Quintile'))
-  print(paste0("Completed for ", S7_var, '...'))
-}
-rm(df2)
-
-# finally pivot_longer for ggplot and facet_wrap to take over
-df2 <- df %>%
-  pivot_longer(cols = S7_housing_quality:S7_mental_health,
-               names_to = 'Variable',
-               values_to = 'Change')
-
-ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
-  geom_col() +
-  facet_wrap(~ Income_Quintile, nrow = 1) +
+    labs(title = paste0("Change in component variables by ", group.var)) +
+    ylab("Net Change (%)") +
     theme(legend.position = 'bottom',
@@
           axis.ticks.x = element_blank())
+
+}
 ```
 
-# BOXPLOT Change in ALL vars
+# Income and Equivalent Income
+
+## Absolute Change
 
 ```{r}
-varlist <- c('S7_neighbourhood_safety', 'loneliness',
+income_equivinc_change_batch(base.batch, int.batch, int.name)
+```
+
+## Percent Change
+
+```{r}
+
+```
+
+# EquivInc split by Income Quintile
+
+```{r}
+inc_change_batch_subpop(base.batch, int.batch, int.name, group.var = 'income.quint')
+equivinc_change_batch_subpop(base.batch, int.batch, int.name, group.var = 'income.quint')
+```
+
+## Percent Change
+
+```{r}
+income_equivinc_percent_change_batch(base.batch, int.batch, int.name, group.var = 'income.quint')
+```
+
+# Pathway Vars by Income Quintile
+
+```{r}
+S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality')
+S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
+S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_physical_health')
+S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_mental_health')
+S7_pathway_change_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'loneliness')
+```
+
+## Cumulative Pathway Change
+
+### Income Quintile
+
+```{r}
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_physical_health')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'S7_mental_health')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'income.quint', var = 'loneliness')
+```
+
+### Age Group
+
+```{r}
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'S7_housing_quality')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'S7_neighbourhood_safety')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'S7_physical_health')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'S7_mental_health')
+S7_cumulative_pathwayChange_byGroup(base.batch, int.batch, group.var = 'age.group', var = 'loneliness')
+```
+
+# Simplified Cumulative Change
+
+```{r}
+varlist <- c('S7_housing_quality', 'S7_neighbourhood_safety', 'loneliness',
              'S7_physical_health', 'S7_mental_health')
 
-df <- simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = 'S7_housing_quality')
-colnames(df) <- c('run_id', 'Income_Quintile', 'S7_housing_quality')
-print("Completed for S7_housing_quality...")
-for (S7_var in varlist) {
-  df2 <- simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var = S7_var)
-  colnames(df2) <- c('run_id', 'Income_Quintile', S7_var)
-  df <- merge(df, df2, by = c('run_id', 'Income_Quintile'))
-  print(paste0("Completed for ", S7_var, '...'))
-}
-rm(df2)
-
-# finally pivot_longer for ggplot and facet_wrap to take over
-df2 <- df %>%
-  pivot_longer(cols = S7_housing_quality:S7_mental_health,
-               names_to = 'Variable',
-               values_to = 'Change')
-
-ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
-  geom_boxplot(notch = FALSE) +
-  facet_wrap(~ Income_Quintile, nrow = 1) +
-  geom_hline(yintercept = 0, linetype = 'dashed') +
-  theme(legend.position = 'bottom',
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank())
+simplified_component_change_BOXPLOT(base.batch, int.batch, group.var = 'income.quint', var.list = varlist)
 ```

### 2023-09-17 minos/outcomes/equivalent_income_out.Rmd
Lots of testing on S7 component models. Also added a script to check the proportional odds assumption for deciding between clm and nnet. Still working on a function to add to the transition estimation scripts to produce a file with each model

@@
 # set output path to SIPHER 7 experiment out
-out.path <- here::here('output', 'SIPHER7/')
+out.path <- here::here('output', 'SIPHER7asd/')
 # read all files into dataframe (util function handles runtime subdirectory etc.)

### 2023-09-17 minos/testing/proportional_odds_assumption_test.Rmd
Lots of testing on S7 component models. Also added a script to check the proportional odds assumption for deciding between clm and nnet. Still working on a function to add to the transition estimation scripts to produce a file with each model

---
title: "R Notebook"
output: html_notebook
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(here)
require(dplyr)
require(tidyr)
require(purrr)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

Source utils for some functions.

```{r}
# source(here::here('minos', 'utils_datain.R'))
# source(here::here('minos', 'utils_validation_vis.R'))
# source(here::here('minos', 'validation', 'utils.r'))
```

## Data

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

#out.path <- 'Minos/output/SIPHER7/'
#out.path <- here::here('output', 'SIPHER7/')
#base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)

# raw.dat <- raw.dat %>%
#   #filter(loneliness != '-9')
#   #filter(S7_housing_quality != '-9')
#   filter(S7_labour_state != '-9')
```

# TEST

```{r}
require(car)
require(nnet)
#library(xlsx)
require(MASS)
#options(warn=1)
options(digits = 3)

var.name <- 'job_sec'

raw.dat <- raw.dat %>%
  filter(.data[[var.name]] != '-9')

file.name <- paste0('PROP_ODDS_TESTING/Prop_odds_', var.name, '.txt')

#
#Trial <- read.xlsx("Trial.xls", "Sheet 1")
# Set up an out file structure
sink(file.name)
# Trial$Outcome is assessed on a six point scale 0-5
# loneliness
#schtyp_M_M.f <- factor(raw.dat$loneliness, labels = c('Never', 'Sometimes', 'Often'))
#schtyp_M_M.f <- factor(raw.dat$S7_housing_quality, labels = c('No to all', 'Yes to some', 'Yes to all'))
#schtyp_M_M.f <- factor(raw.dat$S7_labour_state, labels = c('FT Employed', 'PT Employed', 'Job Seeking', 'Family Care', 'Not Working', 'FT Education'))
#schtyp_M_M.f <- factor(raw.dat$S7_labour_state)
schtyp_M_M.f <- factor(raw.dat[[var.name]])
#
cat("Multinomial logistic regression \n")
# Assign takes on a value of 1 (Treatment) or 0 (Control) 
mod.multinom <-multinom(schtyp_M_M.f~sex, data = raw.dat)
print(summary(mod.multinom, cor=F, Wald=T))
x1<-logLik(mod.multinom)
cat("Degrees of freedom Multinomial logistic regression \n")
print(df_of_multinom_model <- attributes(x1)$df)
cat("Proportional odds logistic regression\n")
mod.polr <- polr(schtyp_M_M.f ~ sex, data=raw.dat)
print(summary(mod.polr))
x2<-logLik(mod.polr)
cat("Degrees of freedom Proportional Odds Logistic Regression \n")
print(df_of_polr_model <- attributes(x2)$df)

cat("Answering the question: Is proportional odds model assumption violated\n")
cat("P value for difference in AIC between POLR and Multinomial Logit model\n")
# abs since the values could be negative. That is negative difference of degrees of freedom would produce p=NaN
print(1-pchisq(abs(mod.polr$deviance-mod.multinom$deviance),   abs(df_of_multinom_model-df_of_polr_model)))
sink()
```

```{r}

prop_odds_assumption_test <- function(test.dat, test.var, form.right) {
  # NOTE
  # The following code came from this stack overflow which itself came from a book:
  # https://stackoverflow.com/questions/37016215/testing-the-proportional-odds-assumption-in-r

  require(car)
  require(nnet)
  require(MASS)
  options(warn=1)
  options(digits = 3)

  # Set up an out file structure
  sink(paste0('Testing_adequacy_of_Prop_odds_', test.var, '.txt'))
  # set up response factor
  schtyp_M_M.f <- factor(test.dat[[test.var]])
  # set up formula object for multinom
  form <- as.formula(paste0("schtyp_M_M.f ~ ", form.right))
  print(form)
  #
  cat("Multinomial logistic regression \n")
  # Test against the formula from file
  mod.multinom <-multinom(formula = form, data = test.dat)
  print(summary(mod.multinom, cor=F, Wald=T))
  x1<-logLik(mod.multinom)
  cat("Degrees of freedom Multinomial logistic regression \n")
  print(df_of_multinom_model <- attributes(x1)$df)
  cat("Proportional odds logistic regression\n")
  mod.polr <- polr(formula = form, data = test.dat)
  print(summary(mod.polr))
  x2<-logLik(mod.polr)
  cat("Degrees of freedom Proportional Odds Logistic Regression \n")
  print(df_of_polr_model <- attributes(x2)$df)

  cat("Answering the question: Is proportional odds model assumption violated\n")
  cat("P value for difference in AIC between POLR and Multinomial Logit model\n")
  # abs since the values could be negative. That is negative difference of degrees of freedom would produce p=NaN
  print(1-pchisq(abs(mod.polr$deviance-mod.multinom$deviance),   abs(df_of_multinom_model-df_of_polr_model)))
  sink()
}
```

```{r}
raw.dat <- raw.dat %>%
  filter(loneliness != '-9')

form.rightside <- "factor(loneliness) + scale(age) + factor(sex) + relevel(factor(education_state), ref = '3') + relevel(factor(job_sec), ref = '3') + scale(hh_income) + relevel(factor(hh_comp), ref = '3') + relevel(factor(marital_status), ref = 'Partnered') + relevel(factor(ethnicity), ref = 'WBI')"

form.rightside <- 'sex'

#prop_odds_assumption_test(test.dat = raw.dat, test.var = 'loneliness', form.right = form.rightside)

test.dat <- raw.dat
test.var <- 'loneliness'
form.right <- form.rightside

require(car)
require(nnet)
require(MASS)
options(warn=1)
options(digits = 3)

# Set up an out file structure
sink(paste0('Testing_adequacy_of_Prop_odds_', test.var, '.txt'))
# set up response factor
schtyp_M_M.f <- factor(test.dat[[test.var]])
# set up formula object for multinom
form <- as.formula(paste0("schtyp_M_M.f ~ ", form.right))
print(form)
#
cat("Multinomial logistic regression \n")
# Test against the formula from file
mod.multinom <-multinom(formula = form, data = test.dat)
print(summary(mod.multinom, cor=F, Wald=T))
x1<-logLik(mod.multinom)
cat("Degrees of freedom Multinomial logistic regression \n")
print(df_of_multinom_model <- attributes(x1)$df)
cat("Proportional odds logistic regression\n")
mod.polr <- polr(formula = form, data = test.dat)
print(summary(mod.polr))
x2<-logLik(mod.polr)
cat("Degrees of freedom Proportional Odds Logistic Regression \n")
print(df_of_polr_model <- attributes(x2)$df)

cat("Answering the question: Is proportional odds model assumption violated\n")
cat("P value for difference in AIC between POLR and Multinomial Logit model\n")
# abs since the values could be negative. That is negative difference of degrees of freedom would produce p=NaN
print(1-pchisq(abs(mod.polr$deviance-mod.multinom$deviance),   abs(df_of_multinom_model-df_of_polr_model)))
sink()
```

```{r}

```

### 2023-10-02 minos/validation/cross_validation_default.Rmd
Testing the addition of a job_sec module for transitioning to different job types. Could be quite important for equivalent income

@@
 rm(heat.pivoted)
+```
+
+# Alcohol
+
+```{r}
+alc.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'auditc')
+
+cv_ordinal_plots(pivoted.df = alc.pivoted, 
+                 var = 'auditc',
+                 save = FALSE)
+rm(alc.pivoted)
+```
+
+# Physical Activity
+
+```{r}
+active.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'active')
+
+cv_ordinal_plots(pivoted.df = active.pivoted, 
+                 var = 'active',
+                 save = FALSE)
+rm(active.pivoted)
 ```

### 2023-10-02 minos/validation/handovers.Rmd

--- 2023-08-13 minos/validation/handovers.Rmd
@@
 # sf12 boxplot handovers
-handover_boxplots(raw.dat, base.dat, 'SF_12')
-handover_lineplots(raw.dat, base.dat, "SF_12")
-# 
-# raw.sf12 <- raw.dat %>% 
-#   dplyr::select(pidp, time, SF_12) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.sf12 <- base.dat %>%
-#   dplyr::select(pidp, time, SF_12) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# # merge before plot
-# sf12 <- rbind(raw.sf12, base.sf12)
-# 
-# # Now plot
-# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-#   geom_smooth() +
-#   #geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
-#   xlab('Year') +
-#   ylab('SF12')
-# 
-# ## Try a version where final_US is limited to only those present from wave 1 
-# # onwards because the sample refreshments are messing with the plot
-# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-# 
-# raw.sf12.2 <- raw.dat %>% 
-#   dplyr::select(pidp, time, SF_12) %>%
-#   filter(pidp %in% raw.sf12.wave1) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.sf12.2 <- base.dat %>%
-#   dplyr::select(pidp, time, SF_12) %>%
-#   filter(pidp %in% raw.sf12.wave1) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
-# 
-# # Now plot
-# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-#   geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
-#   xlab('Year') +
-#   ylab('SF12')
-# 
-# if (shall.we.save) {
-#   ggsave(filename = 'SF12_wav1.png',
-#        plot = last_plot(),
-#        path = save.path)
-# }
-# 
-# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
+handover_boxplots(raw.dat, base.dat, 'SF_12_MCS')
+handover_lineplots(raw.dat, base.dat, "SF_12_MCS")
 ```
@@
 ```{r}
-raw.sf12 <- raw.dat %>%
-  select(pidp, age, time, SF_12)
-base.sf12 <- base.dat %>%
-  select(pidp, age, time, SF_12)
+raw.sf12.m <- raw.dat %>%
+  select(pidp, age, time, SF_12_MCS)
+base.sf12.m <- base.dat %>%
+  select(pidp, age, time, SF_12_MCS)
 
-sf12.spag <- rbind(raw.sf12, base.sf12)
+sf12.m.spag <- rbind(raw.sf12.m, base.sf12.m)
 
-sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(sf12.spag.sample, 'SF_12',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
+# sf12.m.spag.sample <- sf12.m.spag[which(sf12.m.spag$pidp %in% pidp_sample), ]
+# spaghetti_plot(sf12.m.spag.sample, 'SF_12_MCS',
+#                save = shall.we.save,
+#                save.path = save.path)
+# spaghetti_highlight_max_plot(sf12.m.spag.sample, 'SF_12_MCS',
+#                save = shall.we.save,
+#                save.path = save.path)
+
+density_ridges(sf12.m.spag, "SF_12_MCS", 
                save = shall.we.save, 
@@
 
-density_ridges(sf12.spag, "SF_12", 
-               save = T, 
+rm(raw.sf12.m, base.sf12.m, sf12.m.spag, sf12.m.spag.sample)
+```
+
+## SF_12_PCS
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'SF_12_PCS')
+handover_lineplots(raw.dat, base.dat, "SF_12_PCS")
+```
+
+### Spaghetti
+
+```{r}
+raw.sf12.p <- raw.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+base.sf12.p <- base.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+
+sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)
+# 
+# spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
+#                save = shall.we.save,
+#                save.path = save.path)
+
+density_ridges(sf12.p.spag, "SF_12_PCS", 
+               save = shall.we.save, 
                save.path = save.path)
 
-rm(raw.sf12, base.sf12, sf12.spag)
+rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
 ```
@@
 ```{r}
-raw.financial_situation <- raw.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.financial_situation <- base.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-financial_situation <- rbind(raw.financial_situation, base.financial_situation)
-financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
-
-# Now plot
-ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-financial_situation.norm <- financial_situation %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial situation') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'financial_situation.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
+handover_ordinal(raw.dat, base.dat, var = 'financial_situation', save = shall.we.save)
 ```
@@
 ```{r}
-raw.housing <- raw.dat %>%
-  dplyr::select(pidp, time, housing_quality) %>%
-  group_by(time, housing_quality) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.housing <- base.dat %>%
-  dplyr::select(pidp, time, housing_quality) %>%
-  group_by(time, housing_quality) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-housing <- rbind(raw.housing, base.housing)
-housing$housing_quality <- as.factor(housing$housing_quality)
-
-# Now plot
-ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Quality', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-housing.norm <- housing %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Quality') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'housing_quality.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.housing, base.housing, housing, housing.norm)
+handover_ordinal(raw.dat, base.dat, var = 'housing_quality', save = shall.we.save)
 ```
@@
 ```{r}
-raw.neighbour <- raw.dat %>%
-  dplyr::select(pidp, time, neighbourhood_safety) %>%
-  group_by(time, neighbourhood_safety) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.neighbour <- base.dat %>%
-  dplyr::select(pidp, time, neighbourhood_safety) %>%
-  group_by(time, neighbourhood_safety) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-neighbour <- rbind(raw.neighbour, base.neighbour)
-neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety)
-
-# Now plot
-ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') +
-  xlab('Year') +
-  ylab('Count')
-
-neighbour.norm <- neighbour %>%
-  group_by(time) %>%
-  filter(neighbourhood_safety != -9) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Neighbourhood Safety') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'neighbourhood_safety.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-#rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm)
+handover_ordinal(raw.dat, base.dat, var = 'neighbourhood_safety', save = shall.we.save)
 ```
@@
 ```{r}
-raw.loneliness <- raw.dat %>%
-  dplyr::select(pidp, time, loneliness) %>%
-  group_by(time, loneliness) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.loneliness <- base.dat %>%
-  dplyr::select(pidp, time, loneliness) %>%
-  group_by(time, loneliness) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-loneliness <- rbind(raw.loneliness, base.loneliness)
-loneliness$loneliness <- as.factor(loneliness$loneliness)
-
-# Now plot
-ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Loneliness', subtitle = 'Counts by level') +
-  xlab('Year') +
-  ylab('Count')
-
-loneliness.norm <- loneliness %>%
-  group_by(time) %>%
-  filter(loneliness != -9) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Loneliness') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'loneliness.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
+handover_ordinal(raw.dat, base.dat, var = 'loneliness', save = shall.we.save)
 ```
@@
 handover_lineplots(raw.dat, base.dat, 'nutrition_quality')
-
-# Try a version where final_US is limited to only those present from wave 1
-# onwards because the sample refreshments are messing with the plot
-# raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-# 
-# raw.nut2 <- raw.dat %>%
-#   dplyr::select(pidp, time, nutrition_quality) %>%
-#   filter(pidp %in% raw.wave1) %>%
-#   filter(nutrition_quality >= 0) %>%
-#   group_by(time) %>%
-#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.nut2 <- base.dat %>%
-#   dplyr::select(pidp, time, nutrition_quality) %>%
-#   filter(pidp %in% raw.wave1) %>%
-#   group_by(time) %>%
-#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# nutrition_quality2 <- rbind(raw.nut2, base.nut2)
-# 
-# # Now plot
-# ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
-#   geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Nutrition Quality') +
-#   xlab('Year') +
-#   ylab('Nutrition Quality')
-# 
-# if (shall.we.save) {
-#   ggsave(filename = 'nutrition_quality_wav1.png',
-#        plot = last_plot(),
-#        path = save.path)
-# }
-# 
-# rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2,
-#     nutrition_quality2)
 ```
@@
 ```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.phealth <- raw.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.phealth <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-phealth <- rbind(raw.phealth, base.phealth)
-
-# Now plot
-ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Average')
-
-## Try a version where final_US is limited to only those present from wave 1
-# onwards because the sample refreshments are messing with the plot
-raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.phealth2 <- raw.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.phealth2 <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-phealth2 <- rbind(raw.phealth2, base.phealth2)
-
-# Now plot
-ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health') +
-  xlab('Year') +
-  ylab('Average')
-
-if (shall.we.save) {
-  ggsave(filename = 'physical_health_wav1.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-#raw.phealth.check <- raw.dat %>%
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
-
-#base.phealth.check <- base.dat %>%
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
-
-rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2)
-#rm(raw.phealth.check, base.phealth.check)
+handover_continuous(raw.dat, base.dat, var = 'phealth')
+handover_boxplots(raw.dat, base.dat, 'phealth')
+handover_lineplots(raw.dat, base.dat, 'phealth')
 ```
@@
 ```
+
 ```{r}
@@
 ```{r}
-raw.s <- raw.parity %>%
-  select(pidp, age, time, nkids_ind)
-base.s <- base.parity %>%
-  select(pidp, age, time, nkids_ind)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids_ind',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.parity %>%
+#   select(pidp, age, time, nkids_ind)
+# base.s <- base.parity %>%
+#   select(pidp, age, time, nkids_ind)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'nkids_ind',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
 
+## Alcohol (AUDITC)
+
 ```{r}
+handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
+```
 
+## Physical Activity
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
 ```
+
+## Material Deprivation
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'matdep')
+handover_lineplots(raw.dat, base.dat, 'matdep')
+```

### 2023-10-05 minos/outcomes/child_poverty_reduction_vis.Rmd

@@
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-int.dat <- read_singular_local_out(out.path, 'ChildPovertyReduction', drop.dead = TRUE)
+int.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionRANDOM', drop.dead = TRUE)
+int2.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionSUSTAIN', drop.dead = TRUE)
 #base.dat <- read_agg_subset_batch_out(out.path, 'baseline', drop.dead = TRUE)
@@
 The first intervention we will focus on is a reduction in the prevalence of children in relative poverty.
+In these interventions, we have a target level of child poverty to attain (10% of children in a household in poverty) by a specified target year, which is 2030 unless stated otherwise.
+To achieve this, we find households with a hh_income under the poverty line, and uplift a number of households each year to linearly achieve the target proportion by the target year.
 
@@
 
-## Boosted Sample
+## Random Uplift
+
+In this intervention, we will randomly select households to uplift in each year until we uplift the number of children required for that year.
+
+### Boosted Sample
 
@@
 ```{r}
+
+sample_information <- function(int.dat, target.year) {
   hh_boosted <- int.dat %>%
@@
 
-ggplot(hh_boosted, aes(x = time, y = n_boosted)) +
+  p1 <- ggplot(hh_boosted, aes(x = time, y = n_boosted)) +
     geom_line() +
-  geom_vline(xintercept = 2030, linetype = 'dashed') +
+    geom_vline(xintercept = target.year, linetype = 'dashed') +
     labs(title = 'Number of households receiving intervention') +
@@
 
-ggplot(hh_boosted, aes(x = time, y = kids_boosted)) +
+  p2 <- ggplot(hh_boosted, aes(x = time, y = kids_boosted)) +
     geom_line() +
-  geom_vline(xintercept = 2030, linetype = 'dashed') +
+    geom_vline(xintercept = target.year, linetype = 'dashed') +
     labs(title = 'Number of children in households receiving intervention') +
@@
 
-ggplot(hh_boosted, aes(x = time, y = total_boost)) +
+  p3 <- ggplot(hh_boosted, aes(x = time, y = total_boost)) +
     geom_line() +
-  geom_vline(xintercept = 2030, linetype = 'dashed') +
+    geom_vline(xintercept = target.year, linetype = 'dashed') +
     labs(title = 'Total boost amount') +
@@
 
-ggplot(mean.boost, aes(x = time, y = mean_boost)) +
+  p4 <- ggplot(mean.boost, aes(x = time, y = mean_boost)) +
     geom_line() +
-  geom_vline(xintercept = 2030, linetype = 'dashed') +
+    geom_vline(xintercept = target.year, linetype = 'dashed') +
     labs(title = 'Mean boost amount') +
@@
     ylab('Boost Amount')
+
+  print(p1)
+  print(p2)
+  print(p3)
+  print(p4)
+}
+
+sample_information(int.dat, target.year = 2030)
 ```
@@
 
-## SF_12_MCS
+### SF_12_MCS
 
@@
 
-### Full Sample
+#### Full Sample
 
@@
 ```{r}
+full.sample.change.SF12 <- function(base.dat, int.dat) {
   base.all.SF12 <- base.dat %>%
@@
     ylab('Difference')
+}
+
+full.sample.change.SF12(base.dat, int.dat)
 ```
 
-### Families with children
+#### Families with children
 
@@
 ```{r}
+all.families.change.SF12 <- function(base.dat, int.dat) {
   base.all.SF12 <- base.dat %>%
@@
     ylab('Difference')
+}
+all.families.change.SF12(base.dat, int.dat)
 ```
 
-### Families w/ children under poverty line
+#### Families w/ children under poverty line
 
@@
 ```{r}
+poverty.families.change.SF12 <- function(base.dat, int.dat, threshold) {
   base.thresh <- merge(base.dat, threshold, by = 'time')
@@
     ylab('Difference')
+}
+
+poverty.families.change.SF12(base.dat, int.dat, threshold)
 ```
@@
 
-### Treatment on the Treated
+#### Treatment on the Treated
 
 ```{r}
-boosted.overtime <- int.dat %>%
+treatment.on.treated.change.SF12 <- function(base.dat, int.dat) {
+  boosted.byyear <- int.dat %>%
     filter(income_boosted == 'True')
@@
     select(time, weight, SF_12, nkids, pidp) %>%
-  filter(pidp %in% boosted.overtime$pidp) %>%
+    filter(pidp %in% boosted.byyear$pidp) %>%
     group_by(time) %>%
@@
     ylab('Difference')
+}
+
+treatment.on.treated.change.SF12(base.dat, int.dat)
+```
+
+### True Treatment on Treated
+
+Instead of looking at the difference in means
+
+## Sustained Uplift
+
+This intervention is similar to the random uplift intervention with one difference.
+In the first year that the intervention is applied, households are randomly chosen for uplift until the correct number of children for that year are uplifted.
+The difference comes in subsequent years.
+From year 2 onwards, households that have been previously intervened on will once again be uplifted to above the poverty line (if they are once again below).
+This is the meaning of the sustained intervention, where families are chosen at random and then maintained above the poverty line, instead of picking a random subset of households under the poverty line as in the random intervention.
+
+### Boosted Sample
+
+```{r}
+sample_information(int2.dat, target.year = 2030)
+```
+
+### SF_12_MCS
+
+#### Full Sample
+
+```{r}
+full.sample.change.SF12(base.dat, int2.dat)
+```
+
+#### Families with children
+
+```{r}
+all.families.change.SF12(base.dat, int.dat)
+```
+
+#### Families w/ children under poverty line
+
+```{r}
+poverty.families.change.SF12(base.dat, int.dat, threshold)
+```
+
+#### Treatment on the Treated
+
+```{r}
+treatment.on.treated.change.SF12(base.dat, int.dat)
 ```

### 2023-10-05 minos/validation/handovers.Rmd
Changed matdep proxy to a 3 level ordinal and fit a CLM model to it. Handovers look good

@@
 handover_lineplots(raw.dat, base.dat, 'nutrition_quality')
+
+test.pidps <- raw.dat %>%
+  select(pidp)
+
+test.base <- base.dat %>%
+  filter(pidp %in% test.pidps$pidp)
+
+handover_boxplots(raw.dat, test.base, 'nutrition_quality')
+handover_lineplots(raw.dat, test.base, 'nutrition_quality')
 ```
@@
 ```{r}
-# raw.nut <- raw.dat %>%
-#   select(pidp, age, time, nutrition_quality)
-# base.nut <- base.dat %>%
-#   select(pidp, age, time, nutrition_quality)
-# 
-# nut.spag <- rbind(raw.nut, base.nut)
-# 
-# spaghetti_plot(nut.spag, 'nutrition_quality',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# 
-# density_ridges(nut.spag, "nutrition_quality", 
-#                save = T, 
-#                save.path = save.path)
-# 
-# rm(raw.nut, base.nut, nut.spag)
+raw.nut <- raw.dat %>%
+  select(pidp, age, time, nutrition_quality)
+base.nut <- base.dat %>%
+  select(pidp, age, time, nutrition_quality)
+
+nut.spag <- rbind(raw.nut, base.nut)
+
+spaghetti_plot(nut.spag, 'nutrition_quality',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(nut.spag, "nutrition_quality",
+               save = T,
+               save.path = save.path)
+
+rm(raw.nut, base.nut, nut.spag)
+```
+
+## Tobacco
+
+TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11
+
+```{r}
+#  nutriton quality line/boxplots.
+handover_boxplots(raw.dat, base.dat, 'ncigs')
+handover_lineplots(raw.dat, base.dat, 'ncigs')
+
+test.pidps <- raw.dat %>%
+  select(pidp)
+
+test.base <- base.dat %>%
+  filter(pidp %in% test.pidps$pidp)
+
+handover_boxplots(raw.dat, test.base, 'ncigs')
+handover_lineplots(raw.dat, test.base, 'ncigs')
+```
+
+### Spaghetti
+
+```{r}
+raw.nut <- raw.dat %>%
+  select(pidp, age, time, ncigs)
+base.nut <- base.dat %>%
+  select(pidp, age, time, ncigs)
+
+nut.spag <- rbind(raw.nut, base.nut)
+
+spaghetti_plot(nut.spag, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(nut.spag, "ncigs",
+               save = FALSE,
+               save.path = save.path)
+
+rm(raw.nut, base.nut, nut.spag)
 ```
@@
 ```{r}
-handover_boxplots(raw.dat, base.dat, 'matdep')
-handover_lineplots(raw.dat, base.dat, 'matdep')
+#handover_boxplots(raw.dat, base.dat, 'matdep')
+#handover_lineplots(raw.dat, base.dat, 'matdep')
+handover_ordinal(raw.dat, base.dat, var = 'matdep', save = shall.we.save)
 ```
+
+```{r}
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, matdep) %>%
+#   filter(!matdep %in% miss.values)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, matdep) %>%
+#   filter(!matdep %in% miss.values)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'matdep',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
+```

### 2023-10-05 minos/modules/material_deprivation.py

@@ -67,7 +67,6 @@ class MaterialDeprivation(Base):
                         'urban',
                         'financial_situation',
                         'matdep',
-                        'matdep_diff',
                         'weight']
 
         self.population_view = builder.population.get_view(columns=view_columns)
@@ -81,9 +80,13 @@ class MaterialDeprivation(Base):
         # individual graduate in an education module.
         builder.event.register_listener("time_step", self.on_time_step, priority=5)
 
+
+
         #only need to load this once for now.
         #self.gee_transition_model = r_utils.load_transitions(f"SF_12/lmm/SF_12_LMM", self.rpy2_modules, path=self.transition_dir)
-        self.gee_transition_model = r_utils.load_transitions(f"matdep/glmmb/matdep_GLMMB", self.rpy2_modules, path=self.transition_dir)
+        #self.gee_transition_model = r_utils.load_transitions(f"matdep/glmmb/matdep_GLMMB", self.rpy2_modules, path=self.transition_dir)
+        # self.gee_transition_model = r_utils.load_transitions(f"matdep/clm/matdep_2018-2019", self.rpy2_modules,
+        #                                                      path=self.transition_dir)
 
     def on_time_step(self, event):
         """Produces new children and updates parent status on time steps.
@@ -93,33 +96,53 @@ class MaterialDeprivation(Base):
             The event time_step that called this function.
         """
 
+        # self.year = event.time.year
+        # # Get living people to update their income
+        # pop = self.population_view.get(event.index, query="alive =='alive'")
+        # pop = pop.sort_values('pidp') #sorting aligns index to make sure individual gets their correct prediction.
+        # pop["matdep_last"] = pop["matdep"]
+        #
+        # # Predict next mwb value
+        # newWaveMatdep = pd.DataFrame(columns=['matdep'])
+        # newWaveMatdep['matdep'] = self.calculate_matdep(pop)
+        # newWaveMatdep.index = pop.index
+        # #newWaveMatdep["matdep"] -= 1
+        #
+        # sf12_mean = np.mean(newWaveMatdep["matdep"])
+        # std_ratio = (11/np.std(newWaveMatdep["matdep"]))
+        # newWaveMatdep["matdep"] *= (11/np.std(newWaveMatdep["matdep"]))
+        # newWaveMatdep["matdep"] -= ((std_ratio-1)*sf12_mean)
+        # newWaveMatdep["matdep"] -= 1.5
[…]

### 2023-10-05 minos/transitions/estimate_transitions.R

@@ -174,6 +174,7 @@ run_yearly_models <- function(transitionDir_path,
       if(dependent %in% c('SF_12_MCS', 'SF_12_PCS') & year == 2009) { next }
       # OLS_DIFF models can only start from wave 2 (no diff in first wave)
       if(tolower(mod.type) == 'ols_diff' & year == 2009) { next }
+      if(dependent %in% c('matdep') & year %in% c(2009, 2010, 2012, 2014, 2016, 2018)) { next }
 
       print(paste0('Starting estimation for ', dependent, ' in ', year))
 
@@ -224,6 +225,9 @@ run_yearly_models <- function(transitionDir_path,
         }
         if(!year %in% c(2015, 2017, 2019, 2020)) {
           formula.string <- str_remove(formula.string, " \\+ factor\\(active\\)")
+        }
+        if(!year %in% c(2009, 2010, 2012, 2014, 2016, 2018, 2020)) {
+          formula.string <- str_remove(formula.string, " \\+ factor\\(matdep\\)")
         }
       }
       #print(formula.string)

### 2023-10-09 minos/validation/handovers.Rmd
First stab at chronic disease module

@@
 density_ridges(income.spag, 'hh_income',
-               save=TRUE, 
+               save=shall.we.save, 
                save.path=save.path)
@@
 ```
+
+## Chronic Disease
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'chron_disease', save = shall.we.save)
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, chron_disease) %>%
+  filter(!chron_disease %in% miss.values)
+base.s <- base.dat %>%
+  select(pidp, age, time, chron_disease) %>%
+  filter(!chron_disease %in% miss.values)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'chron_disease',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(spag, 'chron_disease',
+               save=shall.we.save, 
+               save.path=save.path)
+
+pidp_sample <- sample(unique(spag$pidp), size=nrow(raw.s)/10, replace=FALSE)
+spag.sample <- spag[which(spag$pidp %in% pidp_sample), ]
+spaghetti_plot(spag.sample, 'chron_disease',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(spag.sample, 'chron_disease',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```

### 2023-10-09 minos/data_generation/generate_repl_pop.py

@@ -65,7 +65,7 @@ def expand_repl(US_2018):
         # now update Date variable (just use US_utils function
         new_repl = US_utils.generate_interview_date_var(new_repl)
         # adjust pidp to ensure unique values (have checked this and made sure this will never give us a duplicate)
-        new_repl['pidp'] = new_repl['pidp'] + year + 1000000 + (3 * new_repl.index)
+        new_repl['pidp'] = new_repl['pidp'] + year + 1000000 + (5 * new_repl.index)
 
         #print(f"There are {len(new_repl)} people in the replenishing population in year {year}.")
 

### 2023-10-09 minos/minosPipeline/RunPipeline.py

@@ -30,7 +30,13 @@ from minos.modules.tobacco import Tobacco
 from minos.modules.loneliness import Loneliness
 from minos.modules.education import Education
 from minos.modules.nutrition import Nutrition, lmmYJNutrition, lmmDiffNutrition
+from minos.modules.heating import Heating
+from minos.modules.financial_situation import financialSituation
+from minos.modules.housing_tenure import HousingTenure
+from minos.modules.physical_activity import PhysicalActivity
 from minos.modules.material_deprivation import MaterialDeprivation
+from minos.modules.chron_disease import ChronicDisease
+
 
 from minos.modules.S7Labour import S7Labour
 from minos.modules.S7Housing import S7Housing
@@ -38,10 +44,6 @@ from minos.modules.S7Neighbourhood import S7Neighbourhood
 from minos.modules.S7MentalHealth import S7MentalHealth
 from minos.modules.S7PhysicalHealth import S7PhysicalHealth
 from minos.modules.S7EquivalentIncome import S7EquivalentIncome
-from minos.modules.heating import Heating
-from minos.modules.financial_situation import financialSituation
-from minos.modules.housing_tenure import HousingTenure
-from minos.modules.physical_activity import PhysicalActivity
 
 from minos.modules.intervention import hhIncomeIntervention
 from minos.modules.intervention import hhIncomeChildUplift
@@ -89,6 +91,7 @@ components_map = {
     "MaterialDeprivation()": MaterialDeprivation(),
     "PhysicalActivity()": PhysicalActivity(),
     "HousingTenure()": HousingTenure(),
+    "ChronicDisease()": ChronicDisease(),
 }
 
 SIPHER7_components_map = {  # SIPHER7 stuff

### 2023-10-19 minos/validation/cross_validation_default.Rmd
Fixed dependency for CV runs and updated CV vis script with material deprivation composite visualisations
Addition of chron_disease to cross validation scripts, and small tweaks to both validation scripts

@@
 
+# Material Deprivation
+
+```{r}
+matdep.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'matdep')
+
+cv_ordinal_plots(pivoted.df = matdep.pivoted, 
+                 var = 'matdep',
+                 save = FALSE)
+rm(matdep.pivoted)
+```
+
+# Chronic Disease
+
+```{r}
+chron_disease.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'chron_disease')
+
+cv_ordinal_plots(pivoted.df = chron_disease.pivoted, 
+                 var = 'chron_disease',
+                 save = FALSE)
+rm(chron_disease.pivoted)
+```
+
 # SECONDARY VARS

### 2023-10-19 minos/validation/handovers.Rmd
Addition of chron_disease to cross validation scripts, and small tweaks to both validation scripts

@@
 sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)
-# 
-# spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
-#                save = shall.we.save,
-#                save.path = save.path)
+
+spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
+               save = shall.we.save,
+               save.path = save.path)
 
@@
 ```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, matdep) %>%
-#   filter(!matdep %in% miss.values)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, matdep) %>%
-#   filter(!matdep %in% miss.values)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'matdep',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+raw.s <- raw.dat %>%
+  select(pidp, age, time, matdep) %>%
+  filter(!matdep %in% miss.values)
+base.s <- base.dat %>%
+  select(pidp, age, time, matdep) %>%
+  filter(!matdep %in% miss.values)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'matdep',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```

### 2023-10-30 minos/testing/QALY_comparison_energyCrises.Rmd
Implemented utility score and QALY calculations, using the Energy Crises interventions as a test comparison

---
title: "QALY Comparisons - Energy Crisis Interventions"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)
require(MESS)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
)
rm(workingDir)
```

```{r}
source(here::here('minos', 'utils_datain.R'))
```

## Data

```{r}
# read in QALY files for baseline and interventions
out.path <- here::here('output', 'default_config')

base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
support.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownlift'))
noSupport.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownliftNoSupport'))

base <- read.csv(paste0(base.path, 'qalys.csv'))
support <- read.csv(paste0(support.path, 'qalys.csv'))
noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))
```

# QALY comparison

```{r}
# combine the dataframes
combined <- rbind(base, support, noSupport)

ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
  geom_line()
```

## Area Under the Curve Comparison

```{r}
#base.auc <- sum(diff(base$time)*rollmean(base$QALYs, 2))
base.auc <- data.frame(intervention = 'baseline', AUC = auc(x=base$year, y=base$QALYs, type = 'spline'))
support.auc <- data.frame(intervention = 'Support', AUC = auc(x=support$year, y=support$QALYs, type = 'spline'))
noSupport.auc <- data.frame(intervention = 'NoSupport', AUC = auc(x=noSupport$year, y=noSupport$QALYs, type = 'spline'))

combined.auc <- rbind(base.auc, support.auc, noSupport.auc)
```

```{r}
print(combined.auc)

ggplot(data = combined.auc, aes(x = intervention, y = AUC, group = intervention, fill = intervention)) +
  geom_col()
```

```{r}
# Another version showing difference from baseline for better comparison
combined.auc2 <- combined.auc %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'AUC') %>%
  mutate(change_baseline = baseline - baseline,
         change_Support = Support - baseline,
         change_noSupport = NoSupport - baseline) %>%
  pivot_longer(cols = change_baseline:change_noSupport,
               names_to = 'intervention',
               names_prefix = 'change_',
               values_to = 'AUC_difference')

print(combined.auc2)

ggplot(combined.auc2, aes(x = intervention, y = AUC_difference, group = intervention, fill = intervention)) +
  geom_col()
```

### 2023-10-31 minos/testing/QALY_comparison_energyCrises.Rmd
Added cost effectiveness calculations to QALY comparison energyCrises testing script. Added Make target to run QALY calculation for living wage intervention. Added MESS package to environment.yml

@@
 ```{r}
-# read in QALY files for baseline and interventions
+# # read in QALY files for baseline and interventions
 out.path <- here::here('output', 'default_config')
@@
 ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
-  geom_line()
+  geom_smooth()
+```
+
+## Groupby and Mean
+
+```{r}
+base <- base %>%
+  group_by(year) %>%
+  summarise(QALYs = mean(QALYs),
+            boost_amount = mean(total_boost))
+support <- support %>%
+  group_by(year) %>%
+  summarise(QALYs = mean(QALYs),
+            boost_amount = mean(total_boost))
+noSupport <- noSupport %>%
+  group_by(year) %>%
+  summarise(QALYs = mean(QALYs),
+            boost_amount = mean(total_boost))
 ```
@@
   pivot_wider(names_from = 'intervention',
-              values_from = 'AUC') %>%
+              values_from = c('AUC')) %>%
   mutate(change_baseline = baseline - baseline,
@@
 ```
+
+# Cost per QALY
+
+The [UK Government](https://www.gov.uk/government/publications/valuation-of-risks-to-life-and-health-monetary-value-of-a-life-year-voly/a-scoping-study-on-the-valuation-of-risks-to-life-and-health-the-monetary-value-of-a-life-year-voly) has set the value of 1 QALY to be equal to $60,000.
+This is the number we will use for our calculations.
+
+```{r}
+
+combined.cost <- combined %>%
+  select(-X, -pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
+  mutate(QALY_value = QALYs * 60000)
+
+ggplot(combined.cost, aes(x = year, y = QALY_value, group = intervention, colour = intervention)) +
+  geom_line()
+
+combined.cost.change <- combined.cost %>%
+  select(-total_boost, -QALYs) %>%
+  pivot_wider(names_from = 'intervention',
+              values_from = 'QALY_value') %>%
+  mutate(change_Support = energyDownlift - baseline,
+         change_NoSupport = energyDownliftNoSupport - baseline) %>%
+  select(-baseline, -energyDownlift, -energyDownliftNoSupport) %>%
+  pivot_longer(cols = -year,
+               names_prefix = 'change_',
+               names_to = 'intervention',
+               values_to = 'value_change')
+
+ggplot(combined.cost.change, aes(x = year, y = value_change, group = intervention, colour = intervention)) +
+  geom_line()
+
+  # select(-QALYs) %>%
+  # pivot_wider(names_from = 'intervention',
+  #             values_from = c('total_boost', 'QALY_value'),
+  #             names_sep = '000') %>%
+  # mutate(QALY_value_change000energyDownlift = QALY_value000energyDownlift - QALY_value000baseline,
+  #        QALY_value_change000energyDownliftNoSupport = QALY_value000energyDownliftNoSupport - QALY_value000baseline) %>%
+  # select(-QALY_value000baseline, -QALY_value000energyDownlift, -QALY_value000energyDownliftNoSupport, -total_boost000baseline) %>%
+  # pivot_longer(cols = total_boost000energyDownlift:QALY_value_change000energyDownliftNoSupport,
+  #              names_sep = '000',
+  #              names_to = c('.value', 'intervention'),
+  #              names_repair = 'unique') #%>%
+  # pivot_longer(cols = QALY_value_change_Support:QALY_value_change_NoSupport,
+  #              names_prefix = 'QALY_value_change_',
+  #              names_to = 'intervention2',
+  #              values_to = 'QALY_value_change')
+
+# combined.cost <- combined %>%
+#   select(-X, -pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
+#   pivot_wider(names_from = 'intervention',
+#               values_from = c('mean_boost', 'QALYs')) %>%
+#   mutate(change_energyDownlift = QALYs_energyDownlift - QALYs_baseline,
+#          change_energyDownliftNoSupport = QALYs_energyDownliftNoSupport - QALYs_baseline) %>%
+#   mutate(costPerQALY_energyDownlift = change_energyDownlift / mean_boost_energyDownlift,
+#          costPerQALY_energyDownliftNoSupport = change_energyDownliftNoSupport / mean_boost_energyDownliftNoSupport) %>%
+#   pivot_longer(cols = costPerQALY_energyDownlift:costPerQALY_energyDownliftNoSupport,
+#                names_prefix = 'costPerQALY_',
+#                names_to = 'intervention',
+#                values_to = 'costPerQALY') %>%
+#   select(year, intervention, costPerQALY)
+
+# options(scipen=999)
+# 
+# ggplot(data = combined.cost, aes(x = year, y = costPerQALY, group = intervention, colour = intervention)) +
+#   geom_line()
+```
+
+```{r}
+total.combined.cost <- combined.cost %>%
+  group_by(intervention) %>%
+  summarise(total_value_change = sum(value_change))
+
+ggplot(data = total.combined.cost, aes(x = intervention, y = total_value_change, group = intervention, fill = intervention)) +
+  geom_col()
+```
+
+# Incremental Cost-Effectiveness Ratio
+
+From [NICE guidelines](https://www.nice.org.uk/process/pmg6/chapter/assessing-cost-effectiveness) about the cost-effectiveness of health interventions (7.3), and works with a statistic called the Incremental Cost-Effectiveness Ratio (ICER).
+The formula for calculating the ICER can be found [here](https://en.wikipedia.org/wiki/Incremental_cost-effectiveness_ratio), but in short, it represents the average incremental cost associated with 1 additional unit of the measurement of effect.
+In our case, the unit of measurement of effect is a QALY.
+
+From the NICE guidelines, there is a general consensus that anything below £20,000 is cost effective, and anything above £30,000 is not.
+Between £20,000 and £30,000 is a grey area, and depends on the field and other factors to decide (i.e.
+if a rare or important condition is tackled by an intervention then the cost-effective threshold is higher).
+
+```{r}
+# ICER = (C1 - C0) / (E1 - E0)
+# where
+# C1 = cost of intervention
+# E1 = effect of intervention
+# C0 = cost of control group
+# E0 = effect of control group
+
+ICER <- combined.cost %>%
+  pivot_wider(names_from = 'intervention',
+              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
+  mutate(ICER_Support = (total_boost_energyDownlift - total_boost_baseline) / (QALYs_energyDownlift - QALYs_baseline),
+         ICER_NoSupport = (total_boost_energyDownliftNoSupport - total_boost_baseline) / (QALYs_energyDownliftNoSupport - QALYs_baseline)) %>%
+  select(year, ICER_Support, ICER_NoSupport) %>%
+  pivot_longer(cols = -year,
+               names_prefix = 'ICER_',
+               names_to = 'intervention',
+               values_to = 'ICER')
+
+ggplot(ICER, aes(x = year, y = ICER, group = intervention, colour = intervention)) +
+  geom_line()
+
+ICER.final <- ICER %>%
+  group_by(intervention) %>%
+  summarise(ICER = mean(ICER))
+
+ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention, colour = intervention)) +
+  geom_col()
+```

### 2023-11-01 minos/testing/QALY_comparison_energyCrises.Rmd
Added run_id to QALY_calculation outputs for plotting confidence. Improved script for comparing energy crises interventions, and added new script for QALY calculations on living wage intervention. Also fixed function to get runtime subdirectory path in utils

@@
 noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))
+
+# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
+# 
+# base <- read.csv(paste0(out.path, 'qaly_baseline.csv'))
+# support <- read.csv(paste0(out.path, 'qalys_support.csv'))
+# noSupport <- read.csv(paste0(out.path, 'qalys_noSupport.csv'))
 ```
@@
 ggplot(combined.cost, aes(x = year, y = QALY_value, group = intervention, colour = intervention)) +
-  geom_line()
+  geom_smooth()
 
@@
   pivot_wider(names_from = 'intervention',
-              values_from = 'QALY_value') %>%
-  mutate(change_Support = energyDownlift - baseline,
-         change_NoSupport = energyDownliftNoSupport - baseline) %>%
-  select(-baseline, -energyDownlift, -energyDownliftNoSupport) %>%
-  pivot_longer(cols = -year,
-               names_prefix = 'change_',
-               names_to = 'intervention',
-               values_to = 'value_change')
+              values_from = 'QALY_value') #%>%
+  # mutate(change_Support = energyDownlift - baseline,
+  #        change_NoSupport = energyDownliftNoSupport - baseline) %>%
+  # select(-baseline, -energyDownlift, -energyDownliftNoSupport) %>%
+  # pivot_longer(cols = -year,
+  #              names_prefix = 'change_',
+  #              names_to = 'intervention',
+  #              values_to = 'value_change')
 
 ggplot(combined.cost.change, aes(x = year, y = value_change, group = intervention, colour = intervention)) +
-  geom_line()
+  geom_smooth()
 
@@
 ```{r}
-total.combined.cost <- combined.cost %>%
+combined.cost.mean <- combined.cost %>%
+  group_by(year, intervention) %>%
+  summarise(across(everything(), mean))
+
+total.combined.cost <- combined.cost.change %>%
   group_by(intervention) %>%
@@
 
-ICER <- combined.cost %>%
+ICER_test2 <- combined.cost.mean %>%
   pivot_wider(names_from = 'intervention',
@@
   geom_col()
+
+ICER_test3 <- combined.cost.mean %>%
+  pivot_wider(names_from = 'intervention',
+              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
+  mutate(C_Support = total_boost_energyDownlift - total_boost_baseline,
+         E_Support = QALYs_energyDownlift - QALYs_baseline,
+         C_NoSupport = total_boost_energyDownliftNoSupport - total_boost_baseline,
+         E_NoSupport = QALYs_energyDownliftNoSupport - QALYs_baseline) %>%
+  select(year, C_Support, E_Support, C_NoSupport, E_NoSupport) %>%
+  mutate(ICER_Support = C_Support / E_Support,
+         ICER_NoSupport = C_NoSupport / E_NoSupport)# %>%
+  #select(year, ICER_Support, ICER_NoSupport)# %>%
+#   pivot_longer(cols = -year,
+#                names_prefix = 'ICER_',
+#                names_to = 'intervention',
+#                values_to = 'ICER')
+
 ```
+
+```{r}
+
+```

### 2023-11-01 minos/testing/QALY_comparison_livingWage.Rmd
Added run_id to QALY_calculation outputs for plotting confidence. Improved script for comparing energy crises interventions, and added new script for QALY calculations on living wage intervention. Also fixed function to get runtime subdirectory path in utils

---
title: "QALY Comparison - Living Wage Intervention"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)
require(MESS)
require(scales)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  options(scipen=999)
)
rm(workingDir)
```

```{r}
source(here::here('minos', 'utils_datain.R'))
```

## Data

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'default_config')

base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
wage.path <- get_latest_runtime_subdirectory(here::here(out.path, 'livingWageIntervention'))

base <- read.csv(paste0(base.path, 'qalys.csv'))
wage <- read.csv(paste0(wage.path, 'qalys.csv'))

# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
# 
# base <- read.csv(paste0(out.path, 'qaly_baseline.csv'))
# support <- read.csv(paste0(out.path, 'qalys_support.csv'))
# noSupport <- read.csv(paste0(out.path, 'qalys_noSupport.csv'))
```

# QALY comparison

```{r}
# combine the dataframes
combined <- rbind(base, wage)

ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
  geom_smooth()
```

...and SF_12 MCS and PCS for good measure.

```{r}
ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention)) +
  geom_smooth()

ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention)) +
  geom_smooth()
```

## Area Under the Curve Comparison

```{r}
base.auc <- base %>%
  group_by(run_id) %>%
  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
  mutate(intervention = 'baseline')

wage.auc <- wage %>%
  group_by(run_id) %>%
  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
  mutate(intervention = 'LivingWage')

combined.auc <- rbind(base.auc, wage.auc)

# #base.auc <- sum(diff(base$time)*rollmean(base$QALYs, 2))
# base.auc <- data.frame(intervention = 'baseline', AUC = auc(x=base$year, y=base$QALYs, type = 'spline'))
# support.auc <- data.frame(intervention = 'Support', AUC = auc(x=support$year, y=support$QALYs, type = 'spline'))
# noSupport.auc <- data.frame(intervention = 'NoSupport', AUC = auc(x=noSupport$year, y=noSupport$QALYs, type = 'spline'))
# 
# combined.auc <- rbind(base.auc, support.auc, noSupport.auc)
```

```{r}
print(combined.auc)

ggplot(data = combined.auc, aes(x = intervention, y = AUC, group = intervention, fill = intervention)) +
  stat_summary(fun = 'mean', geom = 'bar') +
  geom_errorbar(aes(ymin = min(AUC), ymax = max(AUC), width = 0.4)) +
  labs(title = 'Total AUC comparison', subtitle = 'Baseline vs Living Wage Intervention') +
  xlab('Intervention')
```

```{r}
# Another version showing difference from baseline for better comparison
combined.auc2 <- combined.auc %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('AUC')) %>%
  mutate(change_baseline = baseline - baseline,
         change_LivingWage = LivingWage - baseline) %>%
  pivot_longer(cols = change_baseline:change_LivingWage,
               names_to = 'intervention',
               names_prefix = 'change_',
               values_to = 'AUC_difference') %>%
  filter(intervention != 'baseline')

print(combined.auc2)

ggplot(combined.auc2, aes(x = intervention, y = AUC_difference, group = intervention, fill = intervention)) +
  stat_summary(fun = 'mean', geom = 'bar') +
  geom_errorbar(aes(ymin = min(AUC_difference), ymax = max(AUC_difference), width = 0.4)) +
  labs(title = 'Change in AUC', subtitle = 'Baseline vs Living Wage Intervention') +
  xlab('Intervention')
```

# Cost per QALY

The [UK Government](https://www.gov.uk/government/publications/valuation-of-risks-to-life-and-health-monetary-value-of-a-life-year-voly/a-scoping-study-on-the-valuation-of-risks-to-life-and-health-the-monetary-value-of-a-life-year-voly) has set the value of 1 QALY to be equal to $60,000. This is the number we will use for our calculations.

```{r}

# pivot_longer(cols = change_baseline:change_LivingWage,
#                names_to = 'intervention',
#                names_prefix = 'change_',
#                values_to = 'AUC_difference') %>%
#   filter(intervention != 'baseline')

combined.cost <- combined %>%
  select(-pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
  mutate(QALY_value = QALYs * 60000)

ggplot(combined.cost, aes(x = year, y = QALY_value, group = intervention, colour = intervention)) +
  geom_smooth() +
  scale_y_continuous(label = comma)

combined.cost.change <- combined.cost %>%
  select(-total_boost, -QALYs) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'QALY_value') %>%
  mutate(change_baseline = baseline - baseline,
         change_LivingWage = livingWageIntervention - baseline) %>%
  select(-baseline, -livingWageIntervention) %>%
  pivot_longer(cols = change_baseline:change_LivingWage,
               names_to = 'intervention',
               names_prefix = 'change_',
               values_to = 'QALY_value_change') %>%
  filter(intervention != 'baseline')

ggplot(combined.cost.change, aes(x = year, y = QALY_value_change, group = intervention, fill = intervention)) +
  geom_smooth() +
  scale_y_continuous(label = comma)
```

```{r}
total.combined.cost <- combined.cost.change %>%
  group_by(run_id, intervention) %>%
  summarise(TotalChange = sum(QALY_value_change))

#print(paste0('Total combined cost == ', format(round(as.numeric(total.combined.cost), 1), nsmall=1, big.mark=",")))

ggplot(total.combined.cost, aes(x = intervention, y = TotalChange, group = intervention, fill = intervention)) +
  stat_summary(fun = 'mean', geom = 'bar') +
  geom_errorbar(aes(ymin = min(TotalChange), ymax = max(TotalChange), width = 0.4)) +
  labs(title = 'Total Change in QALY Value', subtitle = 'Baseline vs Living Wage Intervention') +
  xlab('Intervention')
```

# Incremental Cost-Effectiveness Ratio

From [NICE guidelines](https://www.nice.org.uk/process/pmg6/chapter/assessing-cost-effectiveness) about the cost-effectiveness of health interventions (7.3), and works with a statistic called the Incremental Cost-Effectiveness Ratio (ICER). The formula for calculating the ICER can be found [here](https://en.wikipedia.org/wiki/Incremental_cost-effectiveness_ratio), but in short, it represents the average incremental cost associated with 1 additional unit of the measurement of effect. In our case, the unit of measurement of effect is a QALY.

From the NICE guidelines, there is a general consensus that anything below £20,000 is cost effective, and anything above £30,000 is not. Between £20,000 and £30,000 is a grey area, and depends on the field and other factors to decide (i.e. if a rare or important condition is tackled by an intervention then the cost-effective threshold is higher).There is also a hard limit of £100,000, where any intervention with an ICER above this value is never acceptable.

```{r}
combined.cost.mean <- combined.cost %>%
  group_by(run_id, year, intervention) %>%
  summarise(across(everything(), mean))

# ICER = (C1 - C0) / (E1 - E0)
# where
# C1 = cost of intervention
# E1 = effect of intervention
# C0 = cost of control group
# E0 = effect of control group

ICER <- combined.cost.mean %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
  mutate(ICER = (total_boost_livingWageIntervention - total_boost_baseline) / (QALYs_livingWageIntervention - QALYs_baseline)) %>%
  select(run_id, year, ICER) %>%
  mutate(intervention = 'LivingWage')

ggplot(ICER, aes(x = year, y = ICER)) +
  geom_smooth()

ICER.final <- ICER %>%
  group_by(run_id, intervention) %>%
  summarise(ICER = mean(ICER))

ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention)) +
  stat_summary(fun = 'mean', geom = 'bar') +
  geom_errorbar(aes(ymin = min(ICER), ymax = max(ICER), width = 0.4)) +
  labs(title = 'ICER', subtitle = 'Living Wage Intervention') +
  xlab('Intervention')
```

### 2023-11-01 minos/testing/QALY_comparison_energyCrises.Rmd
Updated the scripts for QALY comparison of living wage and energy crisis interventions

--- 2023-10-30 minos/testing/QALY_comparison_energyCrises.Rmd
@@
 require(MESS)
+require(scales)
 
@@
 knitr::opts_chunk$set(
+  options(scipen = 999)
 )
@@
 ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
-  geom_line()
+  geom_smooth()
 ```
@@
 ```{r}
-#base.auc <- sum(diff(base$time)*rollmean(base$QALYs, 2))
-base.auc <- data.frame(intervention = 'baseline', AUC = auc(x=base$year, y=base$QALYs, type = 'spline'))
-support.auc <- data.frame(intervention = 'Support', AUC = auc(x=support$year, y=support$QALYs, type = 'spline'))
-noSupport.auc <- data.frame(intervention = 'NoSupport', AUC = auc(x=noSupport$year, y=noSupport$QALYs, type = 'spline'))
+base.auc <- base %>%
+  group_by(run_id) %>%
+  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
+  mutate(intervention = 'baseline')
+
+support.auc <- support %>%
+  group_by(run_id) %>%
+  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
+  mutate(intervention = 'Support')
+
+noSupport.auc <- noSupport %>%
+  group_by(run_id) %>%
+  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
+  mutate(intervention = 'NoSupport')
 
@@
 ggplot(data = combined.auc, aes(x = intervention, y = AUC, group = intervention, fill = intervention)) +
-  geom_col()
+  stat_summary(fun = 'mean', geom = 'bar') +
+  geom_errorbar(aes(ymin = min(AUC), ymax = max(AUC), width = 0.4)) +
+  labs(title = 'Total AUC comparison', subtitle = 'Baseline vs Energy Crisis Interventions') +
+  xlab('Intervention')
 ```
@@
                names_prefix = 'change_',
-               values_to = 'AUC_difference')
+               values_to = 'AUC_difference') %>%
+  filter(intervention != 'baseline')
 
@@
 ggplot(combined.auc2, aes(x = intervention, y = AUC_difference, group = intervention, fill = intervention)) +
-  geom_col()
+  stat_summary(fun = 'mean', geom = 'bar') +
+  geom_errorbar(aes(ymin = min(AUC_difference), ymax = max(AUC_difference), width = 0.4)) +
+  labs(title = 'Change in AUC', subtitle = 'Baseline vs Energy Crisis Interventions') +
+  xlab('Intervention')
 ```
+
+# Cost per QALY
+
+The [UK Government](https://www.gov.uk/government/publications/valuation-of-risks-to-life-and-health-monetary-value-of-a-life-year-voly/a-scoping-study-on-the-valuation-of-risks-to-life-and-health-the-monetary-value-of-a-life-year-voly) has set the value of 1 QALY to be equal to $60,000.
+This is the number we will use for our calculations.
+
+```{r}
+combined.cost <- combined %>%
+  select(-pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
+  mutate(QALY_value = QALYs * 60000)
+
+ggplot(combined.cost, aes(x = year, y = QALY_value, group = intervention, colour = intervention)) +
+  geom_smooth() +
+  scale_y_continuous(label = comma)
+
+combined.cost.change <- combined.cost %>%
+  select(-total_boost, -QALYs) %>%
+  pivot_wider(names_from = 'intervention',
+              values_from = 'QALY_value') %>%
+  mutate(change_baseline = baseline - baseline,
+         change_Support = energyDownlift - baseline,
+         change_NoSupport = energyDownliftNoSupport - baseline) %>%
+  select(-baseline, -energyDownlift, -energyDownliftNoSupport) %>%
+  pivot_longer(cols = change_baseline:change_NoSupport,
+               names_to = 'intervention',
+               names_prefix = 'change_',
+               values_to = 'QALY_value_change') %>%
+  filter(intervention != 'baseline')
+
+ggplot(combined.cost.change, aes(x = year, y = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
+  geom_smooth() +
+  scale_y_continuous(label = comma)
+```
+
+```{r}
+total.combined.cost <- combined.cost.change %>%
+  group_by(run_id, intervention) %>%
+  summarise(TotalChange = sum(QALY_value_change))
+
+ggplot(total.combined.cost, aes(x = intervention, y = TotalChange, group = intervention, fill = intervention)) +
+  stat_summary(fun = 'mean', geom = 'bar') +
+  geom_errorbar(aes(ymin = min(TotalChange), ymax = max(TotalChange), width = 0.4)) +
+  labs(title = 'Total Change in QALY Value', subtitle = 'Baseline vs Energy Crisis Interventions') +
+  xlab('Intervention')
+```
+
+# Incremental Cost-Effectiveness Ratio
+
+From [NICE guidelines](https://www.nice.org.uk/process/pmg6/chapter/assessing-cost-effectiveness) about the cost-effectiveness of health interventions (7.3), and works with a statistic called the Incremental Cost-Effectiveness Ratio (ICER).
+The formula for calculating the ICER can be found [here](https://en.wikipedia.org/wiki/Incremental_cost-effectiveness_ratio), but in short, it represents the average incremental cost associated with 1 additional unit of the measurement of effect.
+In our case, the unit of measurement of effect is a QALY.
+
+From the NICE guidelines, there is a general consensus that anything below £20,000 is cost effective, and anything above £30,000 is not.
+Between £20,000 and £30,000 is a grey area, and depends on the field and other factors to decide (i.e.
+if a rare or important condition is tackled by an intervention then the cost-effective threshold is higher).
+
+```{r}
+combined.cost.mean <- combined.cost %>%
+  group_by(run_id, year, intervention) %>%
+  summarise(across(everything(), mean))
+
+# ICER = (C1 - C0) / (E1 - E0)
+# where
+# C1 = cost of intervention
+# E1 = effect of intervention
+# C0 = cost of control group
+# E0 = effect of control group
+
+ICER <- combined.cost.mean %>%
+  pivot_wider(names_from = 'intervention',
+              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
+  mutate(ICER_Support = (total_boost_energyDownlift - total_boost_baseline) / (QALYs_energyDownlift - QALYs_baseline),
+         ICER_NoSupport = (total_boost_energyDownliftNoSupport - total_boost_baseline) / (QALYs_energyDownliftNoSupport - QALYs_baseline)) %>%
+  select(run_id, year, ICER_Support, ICER_NoSupport) %>%
+  pivot_longer(cols = -c(run_id, year),
+               names_prefix = 'ICER_',
+               names_to = 'intervention',
+               values_to = 'ICER')
+
+ggplot(ICER, aes(x = year, y = ICER, group = intervention, fill = intervention, colour = intervention)) +
+  geom_smooth()
+
+ICER.final <- ICER %>%
+  group_by(run_id, intervention) %>%
+  summarise(ICER = mean(ICER))
+
+ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention)) +
+  stat_summary(fun = 'mean', geom = 'bar') +
+  geom_errorbar(aes(ymin = min(ICER), ymax = max(ICER), width = 0.4)) +
+  labs(title = 'ICER', subtitle = 'Living Wage Intervention') +
+  xlab('Intervention')
+```
+
+```{r}
+
+```

### 2023-11-01 minos/testing/QALY_comparison_livingWage.Rmd
Updated the scripts for QALY comparison of living wage and energy crisis interventions

@@
 combined.auc <- rbind(base.auc, wage.auc)
-
-# #base.auc <- sum(diff(base$time)*rollmean(base$QALYs, 2))
-# base.auc <- data.frame(intervention = 'baseline', AUC = auc(x=base$year, y=base$QALYs, type = 'spline'))
-# support.auc <- data.frame(intervention = 'Support', AUC = auc(x=support$year, y=support$QALYs, type = 'spline'))
-# noSupport.auc <- data.frame(intervention = 'NoSupport', AUC = auc(x=noSupport$year, y=noSupport$QALYs, type = 'spline'))
-# 
-# combined.auc <- rbind(base.auc, support.auc, noSupport.auc)
 ```
@@
 ```{r}
-
-# pivot_longer(cols = change_baseline:change_LivingWage,
-#                names_to = 'intervention',
-#                names_prefix = 'change_',
-#                values_to = 'AUC_difference') %>%
-#   filter(intervention != 'baseline')
-
 combined.cost <- combined %>%
@@
 
-ggplot(combined.cost.change, aes(x = year, y = QALY_value_change, group = intervention, fill = intervention)) +
+ggplot(combined.cost.change, aes(x = year, y = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
   geom_smooth() +

### 2023-11-01 minos/testing/QALY_comparison_energyCrises.Rmd
Added standard error bars, see how this works before moving to 95% confidence intervals

@@
 
-ggplot(data = combined.auc, aes(x = intervention, y = AUC, group = intervention, fill = intervention)) +
-  stat_summary(fun = 'mean', geom = 'bar') +
-  geom_errorbar(aes(ymin = min(AUC), ymax = max(AUC), width = 0.4)) +
+combined.auc.plot <- combined.auc %>%
+  group_by(intervention) %>%
+  summarise(sd = sd(AUC),
+            se = sd / sqrt(n()),
+            AUC = mean(AUC))
+
+ggplot(data = combined.auc.plot, aes(x = intervention, y = AUC, group = intervention, fill = intervention)) +
+  geom_col() +
+  geom_errorbar(aes(ymin = AUC - se, ymax = AUC + se, width = 0.4, group = intervention)) +
   labs(title = 'Total AUC comparison', subtitle = 'Baseline vs Energy Crisis Interventions') +
@@
 
-ggplot(combined.auc2, aes(x = intervention, y = AUC_difference, group = intervention, fill = intervention)) +
-  stat_summary(fun = 'mean', geom = 'bar') +
-  geom_errorbar(aes(ymin = min(AUC_difference), ymax = max(AUC_difference), width = 0.4)) +
+combined.auc2.plot <- combined.auc2 %>%
+  group_by(intervention) %>%
+  summarise(se = sd(AUC_difference) / sqrt(n()),
+            AUC_difference = mean(AUC_difference))
+
+ggplot(combined.auc2.plot, aes(x = intervention, y = AUC_difference, group = intervention, fill = intervention)) +
+  geom_col() +
+  geom_errorbar(aes(ymin = AUC_difference - se, ymax = AUC_difference + se, width = 0.4, group = intervention)) +
   labs(title = 'Change in AUC', subtitle = 'Baseline vs Energy Crisis Interventions') +
@@
   group_by(run_id, intervention) %>%
-  summarise(TotalChange = sum(QALY_value_change))
+  summarise(TotalChange = sum(QALY_value_change)) %>%
+  group_by(intervention) %>%
+  summarise(se = sd(TotalChange) / sqrt(n()),
+            TotalChange = mean(TotalChange))
 
 ggplot(total.combined.cost, aes(x = intervention, y = TotalChange, group = intervention, fill = intervention)) +
-  stat_summary(fun = 'mean', geom = 'bar') +
-  geom_errorbar(aes(ymin = min(TotalChange), ymax = max(TotalChange), width = 0.4)) +
+  geom_col() +
+  geom_errorbar(aes(ymin = TotalChange - se, ymax = TotalChange + se, width = 0.4, group = intervention)) +
+  scale_y_continuous(label = comma) +
   labs(title = 'Total Change in QALY Value', subtitle = 'Baseline vs Energy Crisis Interventions') +
@@
   group_by(run_id, intervention) %>%
-  summarise(ICER = mean(ICER))
+  summarise(ICER = mean(ICER)) %>%
+  group_by(intervention) %>%
+  summarise(se = sd(ICER) / sqrt(n()),
+            ICER = mean(ICER))
 
 ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention)) +
-  stat_summary(fun = 'mean', geom = 'bar') +
-  geom_errorbar(aes(ymin = min(ICER), ymax = max(ICER), width = 0.4)) +
+  geom_col() +
+  geom_errorbar(aes(ymin = ICER - se, ymax = ICER + se, width = 0.4, group = intervention)) +
+  scale_y_continuous(label = comma) +
   labs(title = 'ICER', subtitle = 'Living Wage Intervention') +

### 2023-11-01 minos/testing/QALY_comparison_livingWage.Rmd
Added standard error bars, see how this works before moving to 95% confidence intervals

@@
 
-ggplot(data = combined.auc, aes(x = intervention, y = AUC, group = intervention, fill = intervention)) +
-  stat_summary(fun = 'mean', geom = 'bar') +
-  geom_errorbar(aes(ymin = min(AUC), ymax = max(AUC), width = 0.4)) +
+combined.auc.plot <- combined.auc %>%
+  group_by(intervention) %>%
+  summarise(sd = sd(AUC),
+            se = sd / sqrt(n()),
+            AUC = mean(AUC))
+
+ggplot(data = combined.auc.plot, aes(x = intervention, y = AUC, group = intervention, fill = intervention)) +
+  geom_col() +
+  geom_errorbar(aes(ymin = AUC - se, ymax = AUC + se, width = 0.4, group = intervention)) +
   labs(title = 'Total AUC comparison', subtitle = 'Baseline vs Living Wage Intervention') +
@@
 
-ggplot(combined.auc2, aes(x = intervention, y = AUC_difference, group = intervention, fill = intervention)) +
-  stat_summary(fun = 'mean', geom = 'bar') +
-  geom_errorbar(aes(ymin = min(AUC_difference), ymax = max(AUC_difference), width = 0.4)) +
+combined.auc2.plot <- combined.auc2 %>%
+  group_by(intervention) %>%
+  summarise(se = sd(AUC_difference) / sqrt(n()),
+            AUC_difference = mean(AUC_difference))
+
+ggplot(combined.auc2.plot, aes(x = intervention, y = AUC_difference, group = intervention, fill = intervention)) +
+  geom_col() +
+  geom_errorbar(aes(ymin = AUC_difference - se, ymax = AUC_difference + se, width = 0.4, group = intervention)) +
   labs(title = 'Change in AUC', subtitle = 'Baseline vs Living Wage Intervention') +
@@
   group_by(run_id, intervention) %>%
-  summarise(TotalChange = sum(QALY_value_change))
+  summarise(TotalChange = sum(QALY_value_change)) %>%
+  group_by(intervention) %>%
+  summarise(se = sd(TotalChange) / sqrt(n()),
+            TotalChange = mean(TotalChange))
 
@@
 ggplot(total.combined.cost, aes(x = intervention, y = TotalChange, group = intervention, fill = intervention)) +
-  stat_summary(fun = 'mean', geom = 'bar') +
-  geom_errorbar(aes(ymin = min(TotalChange), ymax = max(TotalChange), width = 0.4)) +
+  geom_col() +
+  geom_errorbar(aes(ymin = TotalChange - se, ymax = TotalChange + se, width = 0.4, group = intervention)) +
+  scale_y_continuous(label = comma) +
   labs(title = 'Total Change in QALY Value', subtitle = 'Baseline vs Living Wage Intervention') +
@@
 ggplot(ICER, aes(x = year, y = ICER)) +
-  geom_smooth()
+  geom_smooth() +
+  scale_y_continuous(label=comma)
 

### 2023-11-02 minos/testing/QALY_comparison_livingWage.Rmd
Updates to QALY comparison script for living wage

@@
 # noSupport <- read.csv(paste0(out.path, 'qalys_noSupport.csv'))
+# combine the dataframes
+combined <- rbind(base, wage)
+```
+
+# Intervention Information
+
+Just going to plot some things here like how many people affected by an intervention and what the mean / total boost amounts look like.
+
+```{r}
+ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
+  geom_smooth()
+
+ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = total_boost, group = intervention, colour = intervention)) +
+  geom_smooth()
 ```
@@
 ```{r}
-# combine the dataframes
-combined <- rbind(base, wage)
-
 ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
   geom_smooth()
+
+# Now change from baseline
+combined.QALY.change <- combined %>%
+  select(run_id, year, intervention, QALYs) %>%
+  pivot_wider(names_from = 'intervention',
+              values_from = 'QALYs') %>%
+  mutate(QALYs = livingWageIntervention - baseline) %>%
+  select(run_id, year, QALYs) %>%
+  mutate(intervention = 'LivingWage')
+
+ggplot(data = combined.QALY.change, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
+  geom_hline(yintercept = 0, linetype = 'dashed') +
+  geom_smooth() +
+  labs(title = 'QALY change from Baseline')
 ```

### 2023-11-02 minos/testing/QALY_comparison_livingWage.Rmd
Seeded mortality to negate the potential effect in QALY calculations

@@
 ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = total_boost, group = intervention, colour = intervention)) +
+  geom_smooth()
+
+ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
   geom_smooth()
@@
 combined.cost <- combined %>%
-  select(-pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
+  select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
   mutate(QALY_value = QALYs * 60000)
@@
 combined.cost.change <- combined.cost %>%
-  select(-total_boost, -QALYs) %>%
+  select(run_id, year, intervention, QALY_value) %>%
   pivot_wider(names_from = 'intervention',
@@
 ICER <- combined.cost.mean %>%
+  select(run_id, year, intervention, total_boost, QALYs, QALY_value) %>%
   pivot_wider(names_from = 'intervention',

### 2023-11-02 minos/modules/mortality.py

@@ -84,7 +84,9 @@ class Mortality(Base):
         # Assign mortality a common random number stream (seeded).
         #self.random = builder.randomness.get_stream(f'mortality_handler')
         # Assign a random mortality CRN stream (unseeded).
-        self.random = builder.randomness.get_stream(self.generate_random_crn_key())
+        #self.random = builder.randomness.get_stream(self.generate_random_crn_key())
+        # generate fixed CRN stream (seeded)
+        self.random = builder.randomness.get_stream(self.generate_fixed_crn_key())
 
         # Which columns are created by this module in on_initialize_simulants.
         columns_created = ['cause_of_death', 'years_of_life_lost']

### 2023-11-02 minos/testing/QALY_comparison_livingWage.Rmd
More updates to QALY comparisons script, and additions to Makefile for no replenishment runs

@@
 # # read in QALY files for baseline and interventions
-out.path <- here::here('output', 'default_config')
+#out.path <- here::here('output', 'default_config')
+out.path <- here::here('output', 'default_no_replenishment')
 
@@
 ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
-  geom_smooth()
+  geom_smooth() +
+  labs(title = 'Number Individuals Receiving Intervention')
 
 ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = total_boost, group = intervention, colour = intervention)) +
-  geom_smooth()
+  geom_smooth() +
+  labs(title = 'Total Boost amount by year')
 
 ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
-  geom_smooth()
+  geom_smooth() +
+  labs(title = 'Ratio of living to dead in output dataframe')
+
+## incidence of mortality
+deaths <- combined %>%
+  select(run_id, intervention, year, alive_pop, dead_pop) %>%
+  group_by(run_id, intervention) %>%
+  mutate(total_pop = alive_pop + dead_pop,
+         deaths_this_year = dead_pop - lag(dead_pop)) %>%
+  group_by(run_id, year, intervention) %>%
+  summarise(death_incidence = deaths_this_year / total_pop)
+
+ggplot(deaths, aes(x = year, y = death_incidence, group = intervention, colour = intervention)) +
+  geom_smooth() +
+  labs(title = 'Incidence of Mortality Comparison')
+
+# pivot_wider(names_from = 'year',
+#               values_from = 'dead_pop')
 ```
@@
 ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
-  geom_smooth()
+  geom_smooth() +
+  labs(title = 'QALYs per year')
 

### 2023-11-02 minos/modules/replenishment.py

@@ -290,7 +290,6 @@ class NoReplenishment(Base):
                         'birth_year',
                         'nobs',
                         'region',
-                        'SF_12_MCS',
                         'hh_int_y',
                         'hh_int_m',
                         'Date',
@@ -302,12 +301,12 @@ class NoReplenishment(Base):
                         'smoker',
                         'loneliness',
                         'weight',
-                        'ndrinks',
                         'nkids',
+                        'nkids_ind',
+                        'ndrinks',
                         'max_educ',
                         'yearly_energy',
                         'job_sector',
-                        'SF_12_PCS',
                         'gross_pay_se',
                         'nutrition_quality',
                         'job_hours_se',
@@ -317,14 +316,33 @@ class NoReplenishment(Base):
                         'jb_inc_per',
                         'hourly_wage',
                         'gross_paypm',
-                        'marital_status',
                         'phealth',
+                        'marital_status',
                         'hh_comp',
+                        #'labour_state',
                         'S7_labour_state',
                         'S7_housing_quality',
                         'S7_neighbourhood_safety',
                         'S7_physical_health',
-                        'S7_mental_health',]
+                        'S7_mental_health',
+                        'equivalent_income',
+                        'heating',
+                        'hhsize',
+                        'financial_situation',
+                        'housing_tenure',
+                        'urban',
+                        'auditc',
+                        'active',
+                        'SF_12_MCS',
+                        'SF_12_MCS_diff',
+                        'hh_income_diff',
+                        'nutrition_quality_diff',
+                        'SF_12_PCS',
+                        'SF_12_PCS_diff',
+                        'matdep',
+                        'matdep_diff',
+                        'chron_disease',
+                        ]
 
         # Shorthand methods for readability.
         self.population_view = builder.population.get_view(view_columns)  # view simulants

### 2023-11-02 minos/outcomes/QALY_calculation.py

@@ -56,7 +56,7 @@ def aggregate_csv(filename, intervention):
     # from both of these pieces of information we can calculate incidence of mortality
     total_pop_size = len(df)
     alive_pop = df['alive'].value_counts()['alive']
-    dead = df['alive'].value_counts()['dead']
+    dead_pop = df['alive'].value_counts()['dead']
 
     # to investigate the mortality rate we can look at the ratio of dead to alive and compare across years
     alive_ratio = (alive_pop / total_pop_size) * 100
@@ -69,7 +69,7 @@ def aggregate_csv(filename, intervention):
         pop_boosted = df['income_boosted'].sum()
         total_boost = df['boost_amount'].sum()
 
-    return [run_id, alive_pop, pop_boosted, total_boost, alive_ratio, np.nanmean(df['SF_12_MCS']), np.nanmean(df['SF_12_PCS'])]
+    return [run_id, alive_pop, dead_pop, total_pop_size, pop_boosted, total_boost, alive_ratio, np.nanmean(df['SF_12_MCS']), np.nanmean(df['SF_12_PCS'])]
 
 
 def calculate_qaly(df):
@@ -133,7 +133,7 @@ def main(mode, intervention):
             aggregated_means = pool.starmap(aggregate_csv, zip(files, repeat(intervention)))
 
         new_df = pd.DataFrame(aggregated_means)
-        new_df.columns = ['run_id', 'alive_pop', 'pop_boosted', 'total_boost', 'alive_ratio', 'SF_12_MCS', 'SF_12_PCS']
+        new_df.columns = ['run_id', 'alive_pop', 'dead_pop', 'total_pop_size', 'pop_boosted', 'total_boost', 'alive_ratio', 'SF_12_MCS', 'SF_12_PCS']
         new_df['year'] = year
         new_df['intervention'] = intervention
         combined_output = pd.concat([combined_output, new_df])

### 2023-11-06 minos/testing/QALY_comparison_energyCrises.Rmd
Included some diagnostic histograms in QALY comparison scripts

@@
 # noSupport <- read.csv(paste0(out.path, 'qalys_noSupport.csv'))
+
+# combine the dataframes
+combined <- rbind(base, support, noSupport)
+```
+
+# Intervention Information
+
+Just going to plot some things here like how many people affected by an intervention and what the mean / total boost amounts look like.
+
+```{r}
+ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
+  geom_smooth() +
+  labs(title = 'Number Individuals Receiving Intervention')
+
+ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = total_boost, group = intervention, colour = intervention)) +
+  geom_smooth() +
+  labs(title = 'Total Boost amount by year')
+
+ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
+  geom_smooth() +
+  labs(title = 'Ratio of living to dead in output dataframe')
+
+## incidence of mortality
+deaths <- combined %>%
+  select(run_id, intervention, year, alive_pop, dead_pop) %>%
+  group_by(run_id, intervention) %>%
+  mutate(total_pop = alive_pop + dead_pop,
+         deaths_this_year = dead_pop - lag(dead_pop)) %>%
+  group_by(run_id, year, intervention) %>%
+  summarise(death_incidence = deaths_this_year / total_pop)
+
+ggplot(deaths, aes(x = year, y = death_incidence, group = intervention, colour = intervention)) +
+  geom_smooth() +
+  labs(title = 'Incidence of Mortality Comparison')
+
+pivot_wider(names_from = 'year',
+              values_from = 'dead_pop')
 ```
@@
 ```{r}
-# combine the dataframes
-combined <- rbind(base, support, noSupport)
+ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
+  geom_smooth() +
+  labs(title = 'QALYs per year')
 
-ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
-  geom_smooth()
+# Now change from baseline
+combined.QALY.change <- combined %>%
+  select(run_id, year, intervention, QALYs) %>%
+  pivot_wider(names_from = 'intervention',
+              values_from = 'QALYs') %>%
+  mutate(QALYs_Support = energyDownlift - baseline,
+         QALYs_NoSupport = energyDownliftNoSupport - baseline) %>%
+  select(run_id, year, QALYs_Support, QALYs_NoSupport) %>%
+  pivot_longer(cols = QALYs_Support:QALYs_NoSupport,
+               names_prefix = 'QALYs_',
+               names_to = 'intervention',
+               values_to = 'QALYs')
+
+ggplot(data = combined.QALY.change, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
+  geom_hline(yintercept = 0, linetype = 'dashed') +
+  geom_smooth() +
+  labs(title = 'QALY change from Baseline')
+```
+
+Can check histogram over each run to see the range of QALYs.
+
+```{r}
+# histogram of qalys
+ggplot(combined, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  facet_wrap(~year)
+
+ggplot(filter(combined, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'QALYs by run', subtitle = '2022')
+
+ggplot(filter(combined, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'QALYs by run', subtitle = '2028')
+
+ggplot(filter(combined, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'QALYs by run', subtitle = '2034')
+```
+
+and histograms of change...
+
+```{r}
+# histogram of qalys
+ggplot(combined.QALY.change, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  facet_wrap(~year) +
+  labs(title = 'QALY change by run', subtitle = 'All Years') +
+  xlab('QALY Change')
+
+ggplot(filter(combined.QALY.change, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'QALY change by run', subtitle = '2022') +
+  xlab('QALY Change')
+
+ggplot(filter(combined.QALY.change, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'QALY change by run', subtitle = '2028') +
+  xlab('QALY Change')
+
+ggplot(filter(combined.QALY.change, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'QALY change by run', subtitle = '2034') +
+  xlab('QALY Change')
+```
+
+...and SF_12 MCS and PCS for good measure.
+
+```{r}
+ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention)) +
+  geom_smooth() +
+  labs(title = 'SF_12_MCS')
+
+ggplot(combined, aes(x = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  facet_wrap(~year) +
+  labs(title = 'SF_12_MCS')
+
+ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention)) +
+  geom_smooth() +
+  labs(title = 'SF_12_PCS')
+
+ggplot(combined, aes(x = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  facet_wrap(~year) +
+  labs(title = 'SF_12_PCS')
 ```
@@
   xlab('Intervention')
+
+ggplot(combined.auc2, aes(x = AUC_difference, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'Area Under Curve change by run')
 ```
@@
   scale_y_continuous(label = comma)
+
+ggplot(combined.cost.change, aes(x = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  facet_wrap(~year) +
+  labs(title = 'QALY value change')
 ```
@@
 ```{r}
+ggplot(ICER, aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  facet_wrap(~year) +
+  labs(title = 'ICER by run', subtitle = 'All Years')
+
+ggplot(filter(ICER, year == 2022), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'ICER by run', subtitle = '2022')
+
+ggplot(filter(ICER, year == 2028), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'ICER by run', subtitle = '2028')
+
+ggplot(filter(ICER, year == 2031), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'ICER by run', subtitle = '2031')
+
+ggplot(filter(ICER, year == 2034), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'ICER by run', subtitle = '2034')
+```
+
+```{r}
 

### 2023-11-06 minos/testing/QALY_comparison_livingWage.Rmd
Included some diagnostic histograms in QALY comparison scripts

@@
 #out.path <- here::here('output', 'default_config')
-out.path <- here::here('output', 'default_no_replenishment')
+out.path <- here::here('output', 'default_config')
 
@@
 
-# pivot_wider(names_from = 'year',
-#               values_from = 'dead_pop')
+pivot_wider(names_from = 'year',
+              values_from = 'dead_pop')
 ```
@@
 
+Can check histogram over each run to see the range of QALYs.
+
+```{r}
+# histogram of qalys
+ggplot(combined, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  facet_wrap(~year)
+
+ggplot(filter(combined, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'QALYs by run', subtitle = '2022')
+
+ggplot(filter(combined, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'QALYs by run', subtitle = '2028')
+
+ggplot(filter(combined, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'QALYs by run', subtitle = '2034')
+```
+
+and histograms of change...
+
+```{r}
+# histogram of qalys
+ggplot(combined.QALY.change, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  facet_wrap(~year)
+
+ggplot(filter(combined.QALY.change, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'QALY change by run', subtitle = '2022')
+
+ggplot(filter(combined.QALY.change, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'QALY change by run', subtitle = '2028')
+
+ggplot(filter(combined.QALY.change, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'QALY change by run', subtitle = '2034')
+```
+
 ...and SF_12 MCS and PCS for good measure.
@@
 
+ggplot(combined, aes(x = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  facet_wrap(~year)
+
 ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention)) +
   geom_smooth()
+
+ggplot(combined, aes(x = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  facet_wrap(~year)
 ```
@@
 combined.cost <- combined %>%
-  select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
+  #select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
+  select(run_id, year, pop_size, total_boost, intervention, QALYs) %>%
   mutate(QALY_value = QALYs * 60000)
@@
   xlab('Intervention')
+
+ggplot(combined.cost.change, aes(x = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  facet_wrap(~year) +
+  labs(title = 'QALY value change')
 ```
@@
   xlab('Intervention')
+
+```
+
+```{r}
+ggplot(ICER, aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  facet_wrap(~year) +
+  labs(title = 'ICER by run', subtitle = 'All Years')
+
+ggplot(filter(ICER, year == 2022), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'ICER by run', subtitle = '2022')
+
+ggplot(filter(ICER, year == 2028), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'ICER by run', subtitle = '2028')
+
+ggplot(filter(ICER, year == 2031), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'ICER by run', subtitle = '2031')
+
+ggplot(filter(ICER, year == 2034), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+  geom_histogram() +
+  labs(title = 'ICER by run', subtitle = '2034')
 ```

### 2023-11-06 minos/testing/QALY_comparison_energyCrises.Rmd
Remove a line that was left by accident

@@
   labs(title = 'Incidence of Mortality Comparison')
-
-pivot_wider(names_from = 'year',
-              values_from = 'dead_pop')
 ```

### 2023-11-06 minos/testing/QALY_comparison_energyCrises.Rmd
Fixed another typo

@@
 combined.cost <- combined %>%
-  select(-pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
+  #select(-pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
+  select(run_id, year, pop_size, total_boost, intervention, QALYs) %>%
   mutate(QALY_value = QALYs * 60000)

### 2023-11-06 minos/testing/QALY_comparison_energyCrises.Rmd
Another one...

--- 2023-11-06 minos/testing/QALY_comparison_energyCrises.Rmd
@@
 combined.cost <- combined %>%
-  select(-pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
+  #select(-pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
+  select(run_id, year, alive_pop, total_boost, intervention, QALYs) %>%
   mutate(QALY_value = QALYs * 60000)

### 2023-11-06 minos/testing/QALY_comparison_livingWage.Rmd
Another one...

@@
   #select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
-  select(run_id, year, pop_size, total_boost, intervention, QALYs) %>%
+  select(run_id, year, alive_pop, total_boost, intervention, QALYs) %>%
   mutate(QALY_value = QALYs * 60000)

### 2023-11-06 minos/testing/QALY_comparison_energyCrises_diff.Rmd
New visualisation script for comparing energyDownlift with energyDownliftNoSupport

--- 2023-11-06 minos/testing/QALY_comparison_energyCrises.Rmd
@@
 ---
-title: "QALY Comparisons - Energy Crisis Interventions"
+title: "QALY Comparisons - Energy Crisis Interventions - NoSupport Baseline"
 output:
@@
 source(here::here('minos', 'utils_datain.R'))
+source(here::here('minos', 'utils_qaly.R'))
 ```
@@
 # combine the dataframes
-combined <- rbind(base, support, noSupport)
+combined <- rbind(support, noSupport)
 ```
@@
 ```{r}
-ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
+ggplot(combined, aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
   geom_smooth() +
@@
 
-ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = total_boost, group = intervention, colour = intervention)) +
+combined.diff <- combined %>%
+  select(run_id, year, intervention, total_boost) %>%
+  pivot_wider(names_from = 'intervention',
+              values_from = 'total_boost') %>%
+  mutate(diff.boost = energyDownlift - energyDownliftNoSupport)
+
+ggplot(combined.diff, aes(x = year, y = diff.boost)) +
   geom_smooth() +
-  labs(title = 'Total Boost amount by year')
+  labs(title = 'Total Boost amount by year') +
+  scale_y_continuous(label = comma)
 
@@
               values_from = 'QALYs') %>%
-  mutate(QALYs_Support = energyDownlift - baseline,
-         QALYs_NoSupport = energyDownliftNoSupport - baseline) %>%
-  select(run_id, year, QALYs_Support, QALYs_NoSupport) %>%
-  pivot_longer(cols = QALYs_Support:QALYs_NoSupport,
-               names_prefix = 'QALYs_',
-               names_to = 'intervention',
-               values_to = 'QALYs')
+  mutate(QALYs = energyDownlift - energyDownliftNoSupport) %>%
+  select(run_id, year, QALYs)
 
-ggplot(data = combined.QALY.change, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
+ggplot(data = combined.QALY.change, aes(x = year, y = QALYs)) +
   geom_hline(yintercept = 0, linetype = 'dashed') +
   geom_smooth() +
-  labs(title = 'QALY change from Baseline')
-```
-
-Can check histogram over each run to see the range of QALYs.
-
-```{r}
-# histogram of qalys
-ggplot(combined, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  facet_wrap(~year)
-
-ggplot(filter(combined, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'QALYs by run', subtitle = '2022')
-
-ggplot(filter(combined, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'QALYs by run', subtitle = '2028')
-
-ggplot(filter(combined, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'QALYs by run', subtitle = '2034')
-```
-
-and histograms of change...
-
-```{r}
-# histogram of qalys
-ggplot(combined.QALY.change, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  facet_wrap(~year) +
-  labs(title = 'QALY change by run', subtitle = 'All Years') +
-  xlab('QALY Change')
-
-ggplot(filter(combined.QALY.change, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'QALY change by run', subtitle = '2022') +
-  xlab('QALY Change')
-
-ggplot(filter(combined.QALY.change, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'QALY change by run', subtitle = '2028') +
-  xlab('QALY Change')
-
-ggplot(filter(combined.QALY.change, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'QALY change by run', subtitle = '2034') +
-  xlab('QALY Change')
-```
-
-...and SF_12 MCS and PCS for good measure.
-
-```{r}
-ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention)) +
-  geom_smooth() +
-  labs(title = 'SF_12_MCS')
-
-ggplot(combined, aes(x = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  facet_wrap(~year) +
-  labs(title = 'SF_12_MCS')
-
-ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention)) +
-  geom_smooth() +
-  labs(title = 'SF_12_PCS')
-
-ggplot(combined, aes(x = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  facet_wrap(~year) +
-  labs(title = 'SF_12_PCS')
+  labs(title = 'QALY change', subtitle = 'Support vs No Support')
 ```
@@
 ```{r}
-base.auc <- base %>%
-  group_by(run_id) %>%
-  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
-  mutate(intervention = 'baseline')
-
-support.auc <- support %>%
-  group_by(run_id) %>%
-  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
-  mutate(intervention = 'Support')
-
-noSupport.auc <- noSupport %>%
-  group_by(run_id) %>%
-  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
-  mutate(intervention = 'NoSupport')
-
-combined.auc <- rbind(base.auc, support.auc, noSupport.auc)
-```
-
-```{r}
-print(combined.auc)
-
-combined.auc.plot <- combined.auc %>%
-  group_by(intervention) %>%
-  summarise(sd = sd(AUC),
-            se = sd / sqrt(n()),
-            AUC = mean(AUC))
-
-ggplot(data = combined.auc.plot, aes(x = intervention, y = AUC, group = intervention, fill = intervention)) +
-  geom_col() +
-  geom_errorbar(aes(ymin = AUC - se, ymax = AUC + se, width = 0.4, group = intervention)) +
-  labs(title = 'Total AUC comparison', subtitle = 'Baseline vs Energy Crisis Interventions') +
-  xlab('Intervention')
-```
-
-```{r}
-# Another version showing difference from baseline for better comparison
-combined.auc2 <- combined.auc %>%
-  pivot_wider(names_from = 'intervention',
-              values_from = c('AUC')) %>%
-  mutate(change_baseline = baseline - baseline,
-         change_Support = Support - baseline,
-         change_noSupport = NoSupport - baseline) %>%
-  pivot_longer(cols = change_baseline:change_noSupport,
-               names_to = 'intervention',
-               names_prefix = 'change_',
-               values_to = 'AUC_difference') %>%
-  filter(intervention != 'baseline')
-
-print(combined.auc2)
-
-combined.auc2.plot <- combined.auc2 %>%
-  group_by(intervention) %>%
-  summarise(se = sd(AUC_difference) / sqrt(n()),
-            AUC_difference = mean(AUC_difference))
-
-ggplot(combined.auc2.plot, aes(x = intervention, y = AUC_difference, group = intervention, fill = intervention)) +
-  geom_col() +
-  geom_errorbar(aes(ymin = AUC_difference - se, ymax = AUC_difference + se, width = 0.4, group = intervention)) +
-  labs(title = 'Change in AUC', subtitle = 'Baseline vs Energy Crisis Interventions') +
-  xlab('Intervention')
-
-ggplot(combined.auc2, aes(x = AUC_difference, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'Area Under Curve change by run')
+auc.plots(base = noSupport, 
+          base.name = 'NoSupport',
+          intervention = support,
+          int.name = 'Support')
 ```
@@
 ```{r}
-combined.cost <- combined %>%
-  select(-pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
-  mutate(QALY_value = QALYs * 60000)
-
-ggplot(combined.cost, aes(x = year, y = QALY_value, group = intervention, colour = intervention)) +
-  geom_smooth() +
-  scale_y_continuous(label = comma)
-
-combined.cost.change <- combined.cost %>%
-  select(-total_boost, -QALYs) %>%
-  pivot_wider(names_from = 'intervention',
-              values_from = 'QALY_value') %>%
-  mutate(change_baseline = baseline - baseline,
-         change_Support = energyDownlift - baseline,
-         change_NoSupport = energyDownliftNoSupport - baseline) %>%
-  select(-baseline, -energyDownlift, -energyDownliftNoSupport) %>%
-  pivot_longer(cols = change_baseline:change_NoSupport,
-               names_to = 'intervention',
-               names_prefix = 'change_',
-               values_to = 'QALY_value_change') %>%
-  filter(intervention != 'baseline')
-
-ggplot(combined.cost.change, aes(x = year, y = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
-  geom_smooth() +
-  scale_y_continuous(label = comma)
-
-ggplot(combined.cost.change, aes(x = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  facet_wrap(~year) +
-  labs(title = 'QALY value change')
-```
-
-```{r}
-total.combined.cost <- combined.cost.change %>%
-  group_by(run_id, intervention) %>%
-  summarise(TotalChange = sum(QALY_value_change)) %>%
-  group_by(intervention) %>%
-  summarise(se = sd(TotalChange) / sqrt(n()),
-            TotalChange = mean(TotalChange))
-
-ggplot(total.combined.cost, aes(x = intervention, y = TotalChange, group = intervention, fill = intervention)) +
-  geom_col() +
-  geom_errorbar(aes(ymin = TotalChange - se, ymax = TotalChange + se, width = 0.4, group = intervention)) +
-  scale_y_continuous(label = comma) +
-  labs(title = 'Total Change in QALY Value', subtitle = 'Baseline vs Energy Crisis Interventions') +
-  xlab('Intervention')
+cost.per.qaly(base = noSupport,
+              base.name = 'energyDownliftNoSupport',
+              int = support,
+              int.name = 'energyDownlift',
+              QALY_value = 60000)  # QALY value == £60,000
 ```
@@
 ```{r}
-combined.cost.mean <- combined.cost %>%
-  group_by(run_id, year, intervention) %>%
-  summarise(across(everything(), mean))
-
-# ICER = (C1 - C0) / (E1 - E0)
-# where
-# C1 = cost of intervention
-# E1 = effect of intervention
-# C0 = cost of control group
-# E0 = effect of control group
-
-ICER <- combined.cost.mean %>%
-  pivot_wider(names_from = 'intervention',
-              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
-  mutate(ICER_Support = (total_boost_energyDownlift - total_boost_baseline) / (QALYs_energyDownlift - QALYs_baseline),
-         ICER_NoSupport = (total_boost_energyDownliftNoSupport - total_boost_baseline) / (QALYs_energyDownliftNoSupport - QALYs_baseline)) %>%
-  select(run_id, year, ICER_Support, ICER_NoSupport) %>%
-  pivot_longer(cols = -c(run_id, year),
-               names_prefix = 'ICER_',
-               names_to = 'intervention',
-               values_to = 'ICER')
-
-ggplot(ICER, aes(x = year, y = ICER, group = intervention, fill = intervention, colour = intervention)) +
-  geom_smooth()
-
-ICER.final <- ICER %>%
-  group_by(run_id, intervention) %>%
-  summarise(ICER = mean(ICER)) %>%
-  group_by(intervention) %>%
-  summarise(se = sd(ICER) / sqrt(n()),
-            ICER = mean(ICER))
-
-ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention)) +
-  geom_col() +
-  geom_errorbar(aes(ymin = ICER - se, ymax = ICER + se, width = 0.4, group = intervention)) +
-  scale_y_continuous(label = comma) +
-  labs(title = 'ICER', subtitle = 'Living Wage Intervention') +
-  xlab('Intervention')
-```
-
-```{r}
-ggplot(ICER, aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  facet_wrap(~year) +
-  labs(title = 'ICER by run', subtitle = 'All Years')
-
-ggplot(filter(ICER, year == 2022), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'ICER by run', subtitle = '2022')
-
-ggplot(filter(ICER, year == 2028), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'ICER by run', subtitle = '2028')
-
-ggplot(filter(ICER, year == 2031), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'ICER by run', subtitle = '2031')
-
-ggplot(filter(ICER, year == 2034), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'ICER by run', subtitle = '2034')
+ICER(base = noSupport,
+     base.name = 'energyDownliftNoSupport',
+     int = support,
+     int.name = 'energyDownlift',
+     QALY_value = 60000)
 ```

### 2023-11-06 minos/testing/QALY_comparison_livingWage.Rmd
New visualisation script for comparing energyDownlift with energyDownliftNoSupport

@@
 ```{r}
-# Another version showing difference from baseline for better comparison
-combined.auc2 <- combined.auc %>%
-  pivot_wider(names_from = 'intervention',
-              values_from = c('AUC')) %>%
-  mutate(change_baseline = baseline - baseline,
-         change_LivingWage = LivingWage - baseline) %>%
-  pivot_longer(cols = change_baseline:change_LivingWage,
-               names_to = 'intervention',
-               names_prefix = 'change_',
-               values_to = 'AUC_difference') %>%
-  filter(intervention != 'baseline')
-
-print(combined.auc2)
-
-combined.auc2.plot <- combined.auc2 %>%
-  group_by(intervention) %>%
-  summarise(se = sd(AUC_difference) / sqrt(n()),
-            AUC_difference = mean(AUC_difference))
-
-ggplot(combined.auc2.plot, aes(x = intervention, y = AUC_difference, group = intervention, fill = intervention)) +
-  geom_col() +
-  geom_errorbar(aes(ymin = AUC_difference - se, ymax = AUC_difference + se, width = 0.4, group = intervention)) +
-  labs(title = 'Change in AUC', subtitle = 'Baseline vs Living Wage Intervention') +
-  xlab('Intervention')
-
-ggplot(combined.auc2, aes(x = AUC_difference, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'Area Under Curve change by run')
+auc.plots(base = base, 
+          base.name = 'baseline',
+          intervention = wage,
+          int.name = 'LivingWage')
 ```

### 2023-11-07 minos/testing/QALY_comparison_livingWage.Rmd
Removed the 1st and 100th percentiles from some outputs

@@
 combined <- rbind(base, wage)
+```
+
+```{r}
+diff <- combined %>%
+  pivot_longer(cols = -c(run_id, year, intervention, total_pop_size, alive_pop, dead_pop),
+               names_to = 'measure') %>%
+  group_by(run_id, year, measure) %>%
+  summarise(diff = value[intervention == 'livingWageIntervention'] - value[intervention == 'baseline']) %>%
+  pivot_wider(names_from = 'measure',
+              values_from = 'diff')
+
+wage.short <- wage %>%
+  select(run_id, year, total_pop_size, alive_pop, dead_pop)
+
+combined.diff <- merge(wage.short, diff, by=c('run_id', 'year'))
+
+qalys_3sd <- 3 * sd(combined.diff$QALYs)
+combined.culled <- filter(combined.diff, 
+                          QALYs < QALYs + qalys_3sd,
+                          QALYs > QALYs - qalys_3sd)
+
+  # pivot_wider(id_cols = c(run_id, year),
+  #             names_from = 'intervention',
+  #             values_from = -c(run_id, year)) %>%
+  # mutate(across(ends_with('_livingWageIntervention'), .names = "{.col}_diff") - across(ends_with('_baseline')))
 ```
@@
 ```{r}
-base.auc <- base %>%
-  group_by(run_id) %>%
-  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
-  mutate(intervention = 'baseline')
-
-wage.auc <- wage %>%
-  group_by(run_id) %>%
-  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
-  mutate(intervention = 'LivingWage')
-
-combined.auc <- rbind(base.auc, wage.auc)
-```
-
-```{r}
-print(combined.auc)
-
-combined.auc.plot <- combined.auc %>%
-  group_by(intervention) %>%
-  summarise(sd = sd(AUC),
-            se = sd / sqrt(n()),
-            AUC = mean(AUC))
-
-ggplot(data = combined.auc.plot, aes(x = intervention, y = AUC, group = intervention, fill = intervention)) +
-  geom_col() +
-  geom_errorbar(aes(ymin = AUC - se, ymax = AUC + se, width = 0.4, group = intervention)) +
-  labs(title = 'Total AUC comparison', subtitle = 'Baseline vs Living Wage Intervention') +
-  xlab('Intervention')
-```
-
-```{r}
 auc.plots(base = base, 
@@
 ```{r}
-combined.cost <- combined %>%
-  #select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
-  select(run_id, year, alive_pop, total_boost, intervention, QALYs) %>%
-  mutate(QALY_value = QALYs * 60000)
-
-ggplot(combined.cost, aes(x = year, y = QALY_value, group = intervention, colour = intervention)) +
-  geom_smooth() +
-  scale_y_continuous(label = comma)
-
-combined.cost.change <- combined.cost %>%
-  select(run_id, year, intervention, QALY_value) %>%
-  pivot_wider(names_from = 'intervention',
-              values_from = 'QALY_value') %>%
-  mutate(change_baseline = baseline - baseline,
-         change_LivingWage = livingWageIntervention - baseline) %>%
-  select(-baseline, -livingWageIntervention) %>%
-  pivot_longer(cols = change_baseline:change_LivingWage,
-               names_to = 'intervention',
-               names_prefix = 'change_',
-               values_to = 'QALY_value_change') %>%
-  filter(intervention != 'baseline')
-
-ggplot(combined.cost.change, aes(x = year, y = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
-  geom_smooth() +
-  scale_y_continuous(label = comma)
+cost.per.qaly(base = base,
+              base.name = 'baseline',
+              int = wage,
+              int.name = 'livingWageIntervention',
+              QALY_value = 60000)  # QALY value == £60,000
 ```
@@
 ```{r}
-total.combined.cost <- combined.cost.change %>%
-  group_by(run_id, intervention) %>%
-  summarise(TotalChange = sum(QALY_value_change)) %>%
-  group_by(intervention) %>%
-  summarise(se = sd(TotalChange) / sqrt(n()),
-            TotalChange = mean(TotalChange))
-
-#print(paste0('Total combined cost == ', format(round(as.numeric(total.combined.cost), 1), nsmall=1, big.mark=",")))
-
-ggplot(total.combined.cost, aes(x = intervention, y = TotalChange, group = intervention, fill = intervention)) +
-  geom_col() +
-  geom_errorbar(aes(ymin = TotalChange - se, ymax = TotalChange + se, width = 0.4, group = intervention)) +
-  scale_y_continuous(label = comma) +
-  labs(title = 'Total Change in QALY Value', subtitle = 'Baseline vs Living Wage Intervention') +
-  xlab('Intervention')
-
-ggplot(combined.cost.change, aes(x = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  facet_wrap(~year) +
-  labs(title = 'QALY value change')
+# total.combined.cost <- combined.cost.change %>%
+#   group_by(run_id, intervention) %>%
+#   summarise(TotalChange = sum(QALY_value_change)) %>%
+#   group_by(intervention) %>%
+#   summarise(se = sd(TotalChange) / sqrt(n()),
+#             TotalChange = mean(TotalChange))
+# 
+# #print(paste0('Total combined cost == ', format(round(as.numeric(total.combined.cost), 1), nsmall=1, big.mark=",")))
+# 
+# ggplot(total.combined.cost, aes(x = intervention, y = TotalChange, group = intervention, fill = intervention)) +
+#   geom_col() +
+#   geom_errorbar(aes(ymin = TotalChange - se, ymax = TotalChange + se, width = 0.4, group = intervention)) +
+#   scale_y_continuous(label = comma) +
+#   labs(title = 'Total Change in QALY Value', subtitle = 'Baseline vs Living Wage Intervention') +
+#   xlab('Intervention')
+# 
+# ggplot(combined.cost.change, aes(x = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   facet_wrap(~year) +
+#   labs(title = 'QALY value change')
 ```
@@
 ```{r}
-combined.cost.mean <- combined.cost %>%
-  group_by(run_id, year, intervention) %>%
-  summarise(across(everything(), mean))
-
-# ICER = (C1 - C0) / (E1 - E0)
-# where
-# C1 = cost of intervention
-# E1 = effect of intervention
-# C0 = cost of control group
-# E0 = effect of control group
-
-ICER <- combined.cost.mean %>%
-  select(run_id, year, intervention, total_boost, QALYs, QALY_value) %>%
-  pivot_wider(names_from = 'intervention',
-              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
-  mutate(ICER = (total_boost_livingWageIntervention - total_boost_baseline) / (QALYs_livingWageIntervention - QALYs_baseline)) %>%
-  select(run_id, year, ICER) %>%
-  mutate(intervention = 'LivingWage')
-
-ggplot(ICER, aes(x = year, y = ICER)) +
-  geom_smooth() +
-  scale_y_continuous(label=comma)
-
-ICER.final <- ICER %>%
-  group_by(run_id, intervention) %>%
-  summarise(ICER = mean(ICER)) %>%
-  group_by(intervention) %>%
-  summarise(se = sd(ICER) / sqrt(n()),
-            ICER = mean(ICER))
-
-ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention)) +
-  geom_col() +
-  geom_errorbar(aes(ymin = ICER - se, ymax = ICER + se, width = 0.4, group = intervention)) +
-  scale_y_continuous(label = comma) +
-  labs(title = 'ICER', subtitle = 'Living Wage Intervention') +
-  xlab('Intervention')
-
+ICER(base = base,
+     base.name = 'baseline',
+     int = wage,
+     int.name = 'livingWageIntervention',
+     QALY_value = 60000)
 ```
@@
 ```{r}
-ggplot(ICER, aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  facet_wrap(~year) +
-  labs(title = 'ICER by run', subtitle = 'All Years')
-
-ggplot(filter(ICER, year == 2022), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'ICER by run', subtitle = '2022')
-
-ggplot(filter(ICER, year == 2028), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'ICER by run', subtitle = '2028')
-
-ggplot(filter(ICER, year == 2031), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'ICER by run', subtitle = '2031')
-
-ggplot(filter(ICER, year == 2034), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'ICER by run', subtitle = '2034')
+# ggplot(ICER, aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   facet_wrap(~year) +
+#   labs(title = 'ICER by run', subtitle = 'All Years')
+# 
+# ggplot(filter(ICER, year == 2022), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   labs(title = 'ICER by run', subtitle = '2022')
+# 
+# ggplot(filter(ICER, year == 2028), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   labs(title = 'ICER by run', subtitle = '2028')
+# 
+# ggplot(filter(ICER, year == 2031), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   labs(title = 'ICER by run', subtitle = '2031')
+# 
+# ggplot(filter(ICER, year == 2034), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   labs(title = 'ICER by run', subtitle = '2034')
 ```

### 2023-11-07 minos/validation/cross_validation_default.Rmd
Updating the job_hours and job_sec model (and switching them on) for the updated living wage intervention

--- 2023-08-03 minos/validation/cross_validation_default.Rmd
@@
 ```
+
+## Job Sec
+
+```{r}
+jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'job_sec')
+
+cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
+                 var = 'job_sec',
+                 save = FALSE)
+rm(jobsec.pivoted)
+```
+
+## Job Hours
+
+```{r}
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'job_hours')
+multi_year_boxplots(raw, cv, 'job_hours')
+q_q_comparison(raw, cv, 'job_hours')
+```

### 2023-11-07 minos/validation/handovers.Rmd
Updating the job_hours and job_sec model (and switching them on) for the updated living wage intervention

--- 2023-10-05 minos/validation/handovers.Rmd
@@
 
-## SF_12_MCS
+## SF12
 
@@
 # sf12 boxplot handovers
-handover_boxplots(raw.dat, base.dat, 'SF_12_MCS')
-handover_lineplots(raw.dat, base.dat, "SF_12_MCS")
+handover_boxplots(raw.dat, base.dat, 'SF_12')
+handover_lineplots(raw.dat, base.dat, "SF_12")
+# 
+# raw.sf12 <- raw.dat %>% 
+#   dplyr::select(pidp, time, SF_12) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.sf12 <- base.dat %>%
+#   dplyr::select(pidp, time, SF_12) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# # merge before plot
+# sf12 <- rbind(raw.sf12, base.sf12)
+# 
+# # Now plot
+# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+#   geom_smooth() +
+#   #geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
+#   xlab('Year') +
+#   ylab('SF12')
+# 
+# ## Try a version where final_US is limited to only those present from wave 1 
+# # onwards because the sample refreshments are messing with the plot
+# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+# 
+# raw.sf12.2 <- raw.dat %>% 
+#   dplyr::select(pidp, time, SF_12) %>%
+#   filter(pidp %in% raw.sf12.wave1) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.sf12.2 <- base.dat %>%
+#   dplyr::select(pidp, time, SF_12) %>%
+#   filter(pidp %in% raw.sf12.wave1) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
+# 
+# # Now plot
+# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+#   geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
+#   xlab('Year') +
+#   ylab('SF12')
+# 
+# if (shall.we.save) {
+#   ggsave(filename = 'SF12_wav1.png',
+#        plot = last_plot(),
+#        path = save.path)
+# }
+# 
+# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
 ```
@@
 ```{r}
-raw.sf12.m <- raw.dat %>%
-  select(pidp, age, time, SF_12_MCS)
-base.sf12.m <- base.dat %>%
-  select(pidp, age, time, SF_12_MCS)
+raw.sf12 <- raw.dat %>%
+  select(pidp, age, time, SF_12)
+base.sf12 <- base.dat %>%
+  select(pidp, age, time, SF_12)
 
-sf12.m.spag <- rbind(raw.sf12.m, base.sf12.m)
+sf12.spag <- rbind(raw.sf12, base.sf12)
 
-# sf12.m.spag.sample <- sf12.m.spag[which(sf12.m.spag$pidp %in% pidp_sample), ]
-# spaghetti_plot(sf12.m.spag.sample, 'SF_12_MCS',
-#                save = shall.we.save,
-#                save.path = save.path)
-# spaghetti_highlight_max_plot(sf12.m.spag.sample, 'SF_12_MCS',
-#                save = shall.we.save,
-#                save.path = save.path)
-
-density_ridges(sf12.m.spag, "SF_12_MCS", 
+sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(sf12.spag.sample, 'SF_12',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
                save = shall.we.save,
@@
 
-rm(raw.sf12.m, base.sf12.m, sf12.m.spag, sf12.m.spag.sample)
-```
-
-## SF_12_PCS
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'SF_12_PCS')
-handover_lineplots(raw.dat, base.dat, "SF_12_PCS")
-```
-
-### Spaghetti
-
-```{r}
-raw.sf12.p <- raw.dat %>%
-  select(pidp, age, time, SF_12_PCS)
-base.sf12.p <- base.dat %>%
-  select(pidp, age, time, SF_12_PCS)
-
-sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)
-# 
-# spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
-#                save = shall.we.save,
-#                save.path = save.path)
-
-density_ridges(sf12.p.spag, "SF_12_PCS", 
-               save = shall.we.save, 
+density_ridges(sf12.spag, "SF_12", 
+               save = T, 
                save.path = save.path)
 
-rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
+rm(raw.sf12, base.sf12, sf12.spag)
 ```
@@
 ```{r}
-handover_ordinal(raw.dat, base.dat, var = 'financial_situation', save = shall.we.save)
+raw.financial_situation <- raw.dat %>%
+  dplyr::select(pidp, time, financial_situation) %>%
+  group_by(time, financial_situation) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.financial_situation <- base.dat %>%
+  dplyr::select(pidp, time, financial_situation) %>%
+  group_by(time, financial_situation) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+financial_situation <- rbind(raw.financial_situation, base.financial_situation)
+financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
+
+# Now plot
+ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+financial_situation.norm <- financial_situation %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial situation') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'financial_situation.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
 ```
@@
 ```{r}
-handover_ordinal(raw.dat, base.dat, var = 'housing_quality', save = shall.we.save)
+raw.housing <- raw.dat %>%
+  dplyr::select(pidp, time, housing_quality) %>%
+  group_by(time, housing_quality) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.housing <- base.dat %>%
+  dplyr::select(pidp, time, housing_quality) %>%
+  group_by(time, housing_quality) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+housing <- rbind(raw.housing, base.housing)
+housing$housing_quality <- as.factor(housing$housing_quality)
+
+# Now plot
+ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Housing Quality', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+housing.norm <- housing %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Housing Quality') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'housing_quality.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.housing, base.housing, housing, housing.norm)
 ```
@@
 ```{r}
-handover_ordinal(raw.dat, base.dat, var = 'neighbourhood_safety', save = shall.we.save)
+raw.neighbour <- raw.dat %>%
+  dplyr::select(pidp, time, neighbourhood_safety) %>%
+  group_by(time, neighbourhood_safety) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.neighbour <- base.dat %>%
+  dplyr::select(pidp, time, neighbourhood_safety) %>%
+  group_by(time, neighbourhood_safety) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+neighbour <- rbind(raw.neighbour, base.neighbour)
+neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety)
+
+# Now plot
+ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') +
+  xlab('Year') +
+  ylab('Count')
+
+neighbour.norm <- neighbour %>%
+  group_by(time) %>%
+  filter(neighbourhood_safety != -9) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Neighbourhood Safety') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'neighbourhood_safety.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+#rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm)
 ```
@@
 ```{r}
-handover_ordinal(raw.dat, base.dat, var = 'loneliness', save = shall.we.save)
+raw.loneliness <- raw.dat %>%
+  dplyr::select(pidp, time, loneliness) %>%
+  group_by(time, loneliness) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.loneliness <- base.dat %>%
+  dplyr::select(pidp, time, loneliness) %>%
+  group_by(time, loneliness) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+loneliness <- rbind(raw.loneliness, base.loneliness)
+loneliness$loneliness <- as.factor(loneliness$loneliness)
+
+# Now plot
+ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Loneliness', subtitle = 'Counts by level') +
+  xlab('Year') +
+  ylab('Count')
+
+loneliness.norm <- loneliness %>%
+  group_by(time) %>%
+  filter(loneliness != -9) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Loneliness') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'loneliness.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
 ```
@@
 
-test.pidps <- raw.dat %>%
-  select(pidp)
-
-test.base <- base.dat %>%
-  filter(pidp %in% test.pidps$pidp)
-
-handover_boxplots(raw.dat, test.base, 'nutrition_quality')
-handover_lineplots(raw.dat, test.base, 'nutrition_quality')
+# Try a version where final_US is limited to only those present from wave 1
+# onwards because the sample refreshments are messing with the plot
+# raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+# 
+# raw.nut2 <- raw.dat %>%
+#   dplyr::select(pidp, time, nutrition_quality) %>%
+#   filter(pidp %in% raw.wave1) %>%
+#   filter(nutrition_quality >= 0) %>%
+#   group_by(time) %>%
+#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.nut2 <- base.dat %>%
+#   dplyr::select(pidp, time, nutrition_quality) %>%
+#   filter(pidp %in% raw.wave1) %>%
+#   group_by(time) %>%
+#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# nutrition_quality2 <- rbind(raw.nut2, base.nut2)
+# 
+# # Now plot
+# ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
+#   geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Nutrition Quality') +
+#   xlab('Year') +
+#   ylab('Nutrition Quality')
+# 
+# if (shall.we.save) {
+#   ggsave(filename = 'nutrition_quality_wav1.png',
+#        plot = last_plot(),
+#        path = save.path)
+# }
+# 
+# rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2,
+#     nutrition_quality2)
 ```
@@
 ```{r}
-raw.nut <- raw.dat %>%
-  select(pidp, age, time, nutrition_quality)
-base.nut <- base.dat %>%
-  select(pidp, age, time, nutrition_quality)
-
-nut.spag <- rbind(raw.nut, base.nut)
-
-spaghetti_plot(nut.spag, 'nutrition_quality',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(nut.spag, "nutrition_quality",
-               save = T,
-               save.path = save.path)
-
-rm(raw.nut, base.nut, nut.spag)
-```
-
-## Tobacco
-
-TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11
-
-```{r}
-#  nutriton quality line/boxplots.
-handover_boxplots(raw.dat, base.dat, 'ncigs')
-handover_lineplots(raw.dat, base.dat, 'ncigs')
-
-test.pidps <- raw.dat %>%
-  select(pidp)
-
-test.base <- base.dat %>%
-  filter(pidp %in% test.pidps$pidp)
-
-handover_boxplots(raw.dat, test.base, 'ncigs')
-handover_lineplots(raw.dat, test.base, 'ncigs')
-```
-
-### Spaghetti
-
-```{r}
-raw.nut <- raw.dat %>%
-  select(pidp, age, time, ncigs)
-base.nut <- base.dat %>%
-  select(pidp, age, time, ncigs)
-
-nut.spag <- rbind(raw.nut, base.nut)
-
-spaghetti_plot(nut.spag, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(nut.spag, "ncigs",
-               save = FALSE,
-               save.path = save.path)
-
-rm(raw.nut, base.nut, nut.spag)
+# raw.nut <- raw.dat %>%
+#   select(pidp, age, time, nutrition_quality)
+# base.nut <- base.dat %>%
+#   select(pidp, age, time, nutrition_quality)
+# 
+# nut.spag <- rbind(raw.nut, base.nut)
+# 
+# spaghetti_plot(nut.spag, 'nutrition_quality',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# 
+# density_ridges(nut.spag, "nutrition_quality", 
+#                save = T, 
+#                save.path = save.path)
+# 
+# rm(raw.nut, base.nut, nut.spag)
 ```
@@
 ```{r}
-handover_continuous(raw.dat, base.dat, var = 'phealth')
-handover_boxplots(raw.dat, base.dat, 'phealth')
-handover_lineplots(raw.dat, base.dat, 'phealth')
+# first figure out how to plot final_US
+# start with hh_income
+raw.phealth <- raw.dat %>%
+  dplyr::select(pidp, time, phealth) %>%
+  filter(time > 2009) %>%
+  group_by(time) %>%
+  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
+  mutate(source = 'final_US')
+
+base.phealth <- base.dat %>%
+  dplyr::select(pidp, time, phealth) %>%
+  filter(time > 2009) %>%
+  group_by(time) %>%
+  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+phealth <- rbind(raw.phealth, base.phealth)
+
+# Now plot
+ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Physical Health', subtitle = 'Full Sample') +
+  xlab('Year') +
+  ylab('Average')
+
+## Try a version where final_US is limited to only those present from wave 1
+# onwards because the sample refreshments are messing with the plot
+raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+
+raw.phealth2 <- raw.dat %>%
+  dplyr::select(pidp, time, phealth) %>%
+  filter(time > 2009) %>%
+  filter(pidp %in% raw.wave1) %>%
+  group_by(time) %>%
+  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
+  mutate(source = 'final_US')
+
+base.phealth2 <- base.dat %>%
+  dplyr::select(pidp, time, phealth) %>%
+  filter(time > 2009) %>%
+  filter(pidp %in% raw.wave1) %>%
+  group_by(time) %>%
+  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
+  mutate(source = 'baseline_output')
+
+phealth2 <- rbind(raw.phealth2, base.phealth2)
+
+# Now plot
+ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Physical Health') +
+  xlab('Year') +
+  ylab('Average')
+
+if (shall.we.save) {
+  ggsave(filename = 'physical_health_wav1.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+#raw.phealth.check <- raw.dat %>%
+#  select(pidp, time, phealth) %>%
+#  filter(time > 2009) %>%
+#  filter(pidp %in% raw.wave1)
+
+#base.phealth.check <- base.dat %>%
+#  select(pidp, time, phealth) %>%
+#  filter(time > 2009) %>%
+#  filter(pidp %in% raw.wave1)
+
+rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2)
+#rm(raw.phealth.check, base.phealth.check)
 ```
@@
 ```{r}
-handover_ordinal(raw.dat, base.dat, var = 'education_state', save = shall.we.save)
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Education State'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'education_state.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
 ```
@@
 ```{r}
-# raw.s <- raw.parity %>%
-#   select(pidp, age, time, nkids_ind)
-# base.s <- base.parity %>%
-#   select(pidp, age, time, nkids_ind)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'nkids_ind',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+raw.s <- raw.parity %>%
+  select(pidp, age, time, nkids_ind)
+base.s <- base.parity %>%
+  select(pidp, age, time, nkids_ind)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nkids_ind',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
 
-## Alcohol (AUDITC)
+## Job Hours
 
 ```{r}
-handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
-```
-
-## Physical Activity
-
-```{r}
-handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
-```
-
-## Material Deprivation
-
-```{r}
-#handover_boxplots(raw.dat, base.dat, 'matdep')
-#handover_lineplots(raw.dat, base.dat, 'matdep')
-handover_ordinal(raw.dat, base.dat, var = 'matdep', save = shall.we.save)
+handover_boxplots(raw.dat, base.dat, 'job_hours')
+handover_lineplots(raw.dat, base.dat, 'job_hours')
 ```
@@
 ```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, matdep) %>%
-#   filter(!matdep %in% miss.values)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, matdep) %>%
-#   filter(!matdep %in% miss.values)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'matdep',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+raw.s <- raw.dat %>%
+  select(pidp, age, time, job_hours)
+base.s <- base.dat %>%
+  select(pidp, age, time, job_hours)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'job_hours',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
+
+```{r}
+
+```

### 2023-11-08 minos/outcomes/paper_1_notebook.Rmd
part one of updating paper plots]

@@
                   relevel(factor(region), ref='London') +
-                  scale(hh_netinc)"
+                  scale(hh_netinc) + factor(loneliness)"
 raw_model_formula <- as.formula(raw_model_formula_string)
@@
 
-model_formula_string <- "SF_12 ~ factor(sex) +  relevel(factor(ethnicity), ref='WBI') + scale(age) + factor(education_state) + factor(S7_labour_state) + relevel(factor(job_sec), ref=1) + relevel(factor(region), ref='London') + scale(hh_income)"
+model_formula_string <- "SF_12 ~ factor(sex) +  relevel(factor(ethnicity), ref='WBI') + scale(age) + factor(education_state) + factor(S7_labour_state) + relevel(factor(job_sec), ref=1) + relevel(factor(region), ref='London') + scale(hh_income) + factor(housing_quality) + factor(loneliness) + factor(neighbourhood_safety)"
 
@@
 start.data <- crossval.raw.data[which(crossval.raw.data$time==2013),]
-handover.data <- start.data
+handover.data <- start.data[, c("pidp", "SF_12", "time")]
 for (i in 1:7){

### 2023-11-08 minos/testing/QALY_comparison_energyCrises.Rmd
New visualisation script for comparing energyDownlift with energyDownliftNoSupport
Added targets for calculating qalys on glasgow synthetic simulation runs

@@
 # # read in QALY files for baseline and interventions
-out.path <- here::here('output', 'default_config')
+#out.path <- here::here('output', 'default_config')
+out.path <- here::here('output', 'glasgow_scaled')
 

### 2023-11-08 minos/testing/QALY_comparison_livingWage.Rmd
Added targets for calculating qalys on glasgow synthetic simulation runs

@@
 #out.path <- here::here('output', 'default_config')
-out.path <- here::here('output', 'default_config')
+out.path <- here::here('output', 'glasgow_scaled')
 

### 2023-11-09 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Added targets for calculating qalys on glasgow synthetic simulation runs
Added diagnostic SF12 plots to QALY comparison scripts, and changed pointer to glasgow_scaled for visualising synthetic population runs

@@
 # # read in QALY files for baseline and interventions
-out.path <- here::here('output', 'default_config')
+out.path <- here::here('output', 'glasgow_scaled')
 
@@
 ```{r}
-ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
-  geom_smooth() +
-  labs(title = 'QALYs per year')
-
-# Now change from baseline
-combined.QALY.change <- combined %>%
-  select(run_id, year, intervention, QALYs) %>%
-  pivot_wider(names_from = 'intervention',
-              values_from = 'QALYs') %>%
-  mutate(QALYs = energyDownlift - energyDownliftNoSupport) %>%
-  select(run_id, year, QALYs)
-
-ggplot(data = combined.QALY.change, aes(x = year, y = QALYs)) +
-  geom_hline(yintercept = 0, linetype = 'dashed') +
-  geom_smooth() +
-  labs(title = 'QALY change', subtitle = 'Support vs No Support')
+QALY_comparison(base = noSupport,
+                base.name = 'energyDownliftNoSupport',
+                int = support,
+                int.name = 'energyDownlift')
 ```
 
-## Area Under the Curve Comparison
+## SF12 Change
+
+```{r}
+sf12.plots(base = noSupport,
+           base.name = 'energyDownliftNoSupport',
+           int = support,
+           int.name = 'energyDownlift')
+```
+
+## Area Under the Curve
 

### 2023-11-09 minos/testing/QALY_comparison_livingWage.Rmd
Added diagnostic SF12 plots to QALY comparison scripts, and changed pointer to glasgow_scaled for visualising synthetic population runs

@@
 ```{r}
-ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
-  geom_smooth() +
-  labs(title = 'QALYs per year')
-
-# Now change from baseline
-combined.QALY.change <- combined %>%
-  select(run_id, year, intervention, QALYs) %>%
-  pivot_wider(names_from = 'intervention',
-              values_from = 'QALYs') %>%
-  mutate(QALYs = livingWageIntervention - baseline) %>%
-  select(run_id, year, QALYs) %>%
-  mutate(intervention = 'LivingWage')
-
-ggplot(data = combined.QALY.change, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
-  geom_hline(yintercept = 0, linetype = 'dashed') +
-  geom_smooth() +
-  labs(title = 'QALY change from Baseline')
+QALY_comparison(base = base,
+                base.name = 'baseline',
+                int = wage,
+                int.name = 'livingWageIntervention')
 ```
@@
 ```{r}
-# histogram of qalys
-ggplot(combined, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  facet_wrap(~year)
-
-ggplot(filter(combined, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'QALYs by run', subtitle = '2022')
-
-ggplot(filter(combined, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'QALYs by run', subtitle = '2028')
-
-ggplot(filter(combined, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'QALYs by run', subtitle = '2034')
+# # histogram of qalys
+# ggplot(combined, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   facet_wrap(~year)
+# 
+# ggplot(filter(combined, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   labs(title = 'QALYs by run', subtitle = '2022')
+# 
+# ggplot(filter(combined, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   labs(title = 'QALYs by run', subtitle = '2028')
+# 
+# ggplot(filter(combined, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   labs(title = 'QALYs by run', subtitle = '2034')
 ```
@@
 ```{r}
-# histogram of qalys
-ggplot(combined.QALY.change, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  facet_wrap(~year)
-
-ggplot(filter(combined.QALY.change, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'QALY change by run', subtitle = '2022')
-
-ggplot(filter(combined.QALY.change, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'QALY change by run', subtitle = '2028')
-
-ggplot(filter(combined.QALY.change, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  labs(title = 'QALY change by run', subtitle = '2034')
+# # histogram of qalys
+# ggplot(combined.QALY.change, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   facet_wrap(~year)
+# 
+# ggplot(filter(combined.QALY.change, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   labs(title = 'QALY change by run', subtitle = '2022')
+# 
+# ggplot(filter(combined.QALY.change, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   labs(title = 'QALY change by run', subtitle = '2028')
+# 
+# ggplot(filter(combined.QALY.change, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   labs(title = 'QALY change by run', subtitle = '2034')
 ```
@@
 ```{r}
-ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention)) +
-  geom_smooth()
+# ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention)) +
+#   geom_smooth()
+# 
+# ggplot(combined, aes(x = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   facet_wrap(~year)
+# 
+# ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention)) +
+#   geom_smooth()
+# 
+# ggplot(combined, aes(x = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_histogram() +
+#   facet_wrap(~year)
+```
 
-ggplot(combined, aes(x = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  facet_wrap(~year)
+## SF12 Change
 
-ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention)) +
-  geom_smooth()
-
-ggplot(combined, aes(x = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
-  geom_histogram() +
-  facet_wrap(~year)
+```{r}
+sf12.plots(base = noSupport,
+           base.name = 'energyDownliftNoSupport',
+           int = support,
+           int.name = 'energyDownlift')
 ```

### 2023-11-09 minos/testing/QALY_comparison_energyCrises.Rmd
Updated the configs with some new packages

@@
 # # read in QALY files for baseline and interventions
-#out.path <- here::here('output', 'default_config')
-out.path <- here::here('output', 'glasgow_scaled')
+# out.path <- here::here('output', 'default_config')
+# #out.path <- here::here('output', 'glasgow_scaled')
+# 
+# base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
+# support.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownlift'))
+# noSupport.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownliftNoSupport'))
+# 
+# base <- read.csv(paste0(base.path, 'qalys.csv'))
+# support <- read.csv(paste0(support.path, 'qalys.csv'))
+# noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))
 
-base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
-support.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownlift'))
-noSupport.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownliftNoSupport'))
+out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
 
-base <- read.csv(paste0(base.path, 'qalys.csv'))
-support <- read.csv(paste0(support.path, 'qalys.csv'))
-noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))
-
-# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
-# 
-# base <- read.csv(paste0(out.path, 'qaly_baseline.csv'))
-# support <- read.csv(paste0(out.path, 'qalys_support.csv'))
-# noSupport <- read.csv(paste0(out.path, 'qalys_noSupport.csv'))
+base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
+support <- read.csv(paste0(out.path, 'qalys_support.csv'))
+noSupport <- read.csv(paste0(out.path, 'qalys_nosupport.csv'))
 

### 2023-11-09 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Updated the configs with some new packages

@@
 # # read in QALY files for baseline and interventions
-out.path <- here::here('output', 'glasgow_scaled')
+# #out.path <- here::here('output', 'glasgow_scaled')
+# out.path <- here::here('output', 'default_config')
+# 
+# base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
+# support.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownlift'))
+# noSupport.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownliftNoSupport'))
+# 
+# base <- read.csv(paste0(base.path, 'qalys.csv'))
+# support <- read.csv(paste0(support.path, 'qalys.csv'))
+# noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))
 
-base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
-support.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownlift'))
-noSupport.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownliftNoSupport'))
+out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
 
-base <- read.csv(paste0(base.path, 'qalys.csv'))
-support <- read.csv(paste0(support.path, 'qalys.csv'))
-noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))
-
-# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
-# 
-# base <- read.csv(paste0(out.path, 'qaly_baseline.csv'))
-# support <- read.csv(paste0(out.path, 'qalys_support.csv'))
-# noSupport <- read.csv(paste0(out.path, 'qalys_noSupport.csv'))
+base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
+support <- read.csv(paste0(out.path, 'qalys_support.csv'))
+noSupport <- read.csv(paste0(out.path, 'qalys_nosupport.csv'))
 

### 2023-11-09 minos/testing/QALY_comparison_livingWage.Rmd
Fixed mistake in one of the qaly scripts
Updated the configs with some new packages

@@
 # # read in QALY files for baseline and interventions
-#out.path <- here::here('output', 'default_config')
-out.path <- here::here('output', 'glasgow_scaled')
+# out.path <- here::here('output', 'default_config')
+# #out.path <- here::here('output', 'glasgow_scaled')
+# 
+# base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
+# wage.path <- get_latest_runtime_subdirectory(here::here(out.path, 'livingWageIntervention'))
+# 
+# base <- read.csv(paste0(base.path, 'qalys.csv'))
+# wage <- read.csv(paste0(wage.path, 'qalys.csv'))
 
-base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
-wage.path <- get_latest_runtime_subdirectory(here::here(out.path, 'livingWageIntervention'))
+out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
 
-base <- read.csv(paste0(base.path, 'qalys.csv'))
-wage <- read.csv(paste0(wage.path, 'qalys.csv'))
+base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
+wage <- read.csv(paste0(out.path, 'qalys_livwage.csv'))
 
-# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
-# 
-# base <- read.csv(paste0(out.path, 'qaly_baseline.csv'))
-# support <- read.csv(paste0(out.path, 'qalys_support.csv'))
-# noSupport <- read.csv(paste0(out.path, 'qalys_noSupport.csv'))
 # combine the dataframes
@@
 ```{r}
-ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
+
+test <- combined %>%
+  filter(intervention != 'baseline')
+
+ggplot(test, aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
   geom_smooth() +
@@
 
-ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
-  geom_smooth() +
-  labs(title = 'Ratio of living to dead in output dataframe')
+# ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
+#   geom_smooth() +
+#   labs(title = 'Ratio of living to dead in output dataframe')
 
@@
 ```{r}
-sf12.plots(base = noSupport,
-           base.name = 'energyDownliftNoSupport',
-           int = support,
-           int.name = 'energyDownlift')
+sf12.plots(base = base,
+           base.name = 'baseline',
+           int = wage,
+           int.name = 'livingWageIntervention')
 ```

### 2023-11-09 minos/utils_qaly.R

@@ -39,8 +39,8 @@ sf12.plots <- function(base, base.name, int, int.name) {
   p2 <- ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
     geom_smooth()
   
-  # print(p1)
-  # print(p2)
+  print(p1)
+  print(p2)
   
   combined.SF12 <- combined %>%
     select(run_id, year, intervention, SF_12_MCS, SF_12_PCS) %>%

### 2023-11-10 minos/testing/QALY_comparison_energyCrises.Rmd
Point to the right location for qaly outputs, remove some debugging stuff from earlier

--- 2023-11-08 minos/testing/QALY_comparison_energyCrises.Rmd
@@
 # # read in QALY files for baseline and interventions
-#out.path <- here::here('output', 'default_config')
-out.path <- here::here('output', 'glasgow_scaled')
+out.path <- here::here('output', 'default_config')
+#out.path <- here::here('output', 'glasgow_scaled')
 
@@
 # 
-# base <- read.csv(paste0(out.path, 'qaly_baseline.csv'))
+# base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
 # support <- read.csv(paste0(out.path, 'qalys_support.csv'))
-# noSupport <- read.csv(paste0(out.path, 'qalys_noSupport.csv'))
+# noSupport <- read.csv(paste0(out.path, 'qalys_nosupport.csv'))
 

### 2023-11-10 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Point to the right location for qaly outputs, remove some debugging stuff from earlier

--- 2023-11-09 minos/testing/QALY_comparison_energyCrises_diff.Rmd
@@
 # # read in QALY files for baseline and interventions
-out.path <- here::here('output', 'glasgow_scaled')
+#out.path <- here::here('output', 'glasgow_scaled')
+out.path <- here::here('output', 'default_config')
 

### 2023-11-10 minos/testing/QALY_comparison_livingWage.Rmd
Point to the right location for qaly outputs, remove some debugging stuff from earlier

@@
 # # read in QALY files for baseline and interventions
-# out.path <- here::here('output', 'default_config')
-# #out.path <- here::here('output', 'glasgow_scaled')
+out.path <- here::here('output', 'default_config')
+#out.path <- here::here('output', 'glasgow_scaled')
+
+base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
+wage.path <- get_latest_runtime_subdirectory(here::here(out.path, 'livingWageIntervention'))
+
+base <- read.csv(paste0(base.path, 'qalys.csv'))
+wage <- read.csv(paste0(wage.path, 'qalys.csv'))
+
+# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
 # 
-# base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
-# wage.path <- get_latest_runtime_subdirectory(here::here(out.path, 'livingWageIntervention'))
-# 
-# base <- read.csv(paste0(base.path, 'qalys.csv'))
-# wage <- read.csv(paste0(wage.path, 'qalys.csv'))
-
-out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
-
-base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
-wage <- read.csv(paste0(out.path, 'qalys_livwage.csv'))
+# base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
+# wage <- read.csv(paste0(out.path, 'qalys_livwage.csv'))
 

### 2023-11-10 minos/testing/QALY_comparison_energyCrises.Rmd
Switch to visualise glasgow synthetic runs

@@
 # # read in QALY files for baseline and interventions
-out.path <- here::here('output', 'default_config')
-#out.path <- here::here('output', 'glasgow_scaled')
+#out.path <- here::here('output', 'default_config')
+out.path <- here::here('output', 'glasgow_scaled')
 

### 2023-11-10 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Switch to visualise glasgow synthetic runs

@@
 # # read in QALY files for baseline and interventions
-#out.path <- here::here('output', 'glasgow_scaled')
-out.path <- here::here('output', 'default_config')
+out.path <- here::here('output', 'glasgow_scaled')
+#out.path <- here::here('output', 'default_config')
 

### 2023-11-13 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Added new make targets for the uk synthetic QALY calculations, and pointed the notebooks to the SF12_uk_scaled directory (on arc)

@@
 # # read in QALY files for baseline and interventions
-out.path <- here::here('output', 'glasgow_scaled')
 #out.path <- here::here('output', 'default_config')
+#out.path <- here::here('output', 'glasgow_scaled')
+out.path <- here::here('output', 'SF12_uk_scaled')
 

### 2023-11-13 minos/testing/QALY_comparison_livingWage.Rmd
Added new make targets for the uk synthetic QALY calculations, and pointed the notebooks to the SF12_uk_scaled directory (on arc)

@@
 #out.path <- here::here('output', 'default_config')
-out.path <- here::here('output', 'glasgow_scaled')
+#out.path <- here::here('output', 'glasgow_scaled')
+out.path <- here::here('output', 'SF12_uk_scaled')
 

### 2023-11-14 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Updated the way configs get the components for a current run. Now the components are read from a text file, so we only have to modify 1 file instead of several. Also updated some transition models to point to the correct MCS or PCS, and cleaned up some things in modules

@@
 
+```{r}
+base <- noSupport
+base.name <- 'energyDownliftNoSupport'
+int <- support
+int.name <- 'energyDownlift'
+
+combined <- rbind(base, int)
+
+## now SF12 plots for comparison
+p1 <- ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
+  geom_smooth()
+p2 <- ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
+  geom_smooth()
+
+print(p1)
+print(p2)
+
+combined.SF12 <- combined %>%
+  select(run_id, year, intervention, SF_12_MCS, SF_12_PCS) %>%
+  pivot_wider(names_from = 'intervention',
+              values_from = c('SF_12_MCS', 'SF_12_PCS')) %>%
+  mutate(MCS_diff = .data[[paste0('SF_12_MCS_', int.name)]] - .data[[paste0('SF_12_MCS_', base.name)]],
+         PCS_diff = .data[[paste0('SF_12_PCS_', int.name)]] - .data[[paste0('SF_12_PCS_', base.name)]]) %>%
+  select(run_id, year, MCS_diff, PCS_diff)
+
+p3 <- ggplot(combined.SF12, aes(x = year, y = MCS_diff)) +
+  geom_smooth() +
+  geom_hline(yintercept = 0, linetype = 'dashed') +
+  labs(title = 'Change in SF_12_MCS', subtitle = paste0(int.name, ' vs ', base.name)) +
+  xlab('Year') +
+  ylab('Change in MCS')
+
+p4 <- ggplot(combined.SF12, aes(x = year, y = PCS_diff)) +
+  geom_smooth() +
+  geom_hline(yintercept = 0, linetype = 'dashed') +
+  labs(title = 'Change in SF_12_PCS', subtitle = paste0(int.name, ' vs ', base.name)) +
+  xlab('Year') +
+  ylab('Change in MCS')
+
+print(p3)
+print(p4)
+
+```
+
 ## Area Under the Curve

### 2023-11-14 minos/minosPipeline/RunPipeline.py

@@ -234,8 +234,8 @@ def type_check(data):
     data['S7_physical_health'] = data['S7_physical_health'].astype(int)
     data['nutrition_quality_diff'] = data['nutrition_quality_diff'].astype(int)
     data['neighbourhood_safety'] = data['neighbourhood_safety'].astype(int)
-    data['chron_disease'] = data['chron_disease'].astype(float)
-    data['matdep'] = data['matdep'].astype(float)
+    data['chron_disease'] = data['chron_disease'].astype(int)
+    data['matdep'] = data['matdep'].astype(int)
 
     return data
 

### 2023-11-14 minos/modules/S7Housing.py

@@ -57,7 +57,6 @@ class S7Housing(Base):
         # transition models and any outputs.
         view_columns = ["sex",
                         "S7_labour_state",
-                        "SF_12",
                         "job_sec",
                         "ethnicity",
                         "age",

### 2023-11-14 minos/modules/chron_disease.py

@@ -102,7 +102,7 @@ class ChronicDisease(Base):
         # cd_prob_df['chron_disease'][cd_prob_df['previous_chron_disease'] > cd_prob_df['chron_disease']] = \
         #     cd_prob_df['previous_chron_disease']
 
-        self.population_view.update(cd_prob_df["chron_disease"].astype(float))
+        self.population_view.update(cd_prob_df["chron_disease"].astype(int))
 
     def calculate_chron_disease(self, pop):
         """Calculate chron_disease transition distribution based on provided people/indices

### 2023-11-14 minos/testing/QALY_comparison_energyCrises.Rmd
Attempting to fix weird bug where PCS doesnt transition. Think this will fix it. Updated some paths in config/uk_scaled.yaml, updated some functions in minos/utils_qaly.R and some tweaks to the QALY comparison scripts

@@
 # # read in QALY files for baseline and interventions
-#out.path <- here::here('output', 'default_config')
-out.path <- here::here('output', 'glasgow_scaled')
+out.path <- here::here('output', 'default_config')
+#out.path <- here::here('output', 'glasgow_scaled')
+#out.path <- here::here('output', 'SF12_uk_scaled')
 

### 2023-11-14 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Attempting to fix weird bug where PCS doesnt transition. Think this will fix it. Updated some paths in config/uk_scaled.yaml, updated some functions in minos/utils_qaly.R and some tweaks to the QALY comparison scripts

--- 2023-11-10 minos/testing/QALY_comparison_energyCrises_diff.Rmd
@@
 # # read in QALY files for baseline and interventions
-out.path <- here::here('output', 'glasgow_scaled')
-#out.path <- here::here('output', 'default_config')
+out.path <- here::here('output', 'default_config')
+#out.path <- here::here('output', 'glasgow_scaled')
+#out.path <- here::here('output', 'SF12_uk_scaled')
 
@@
 
+```{r}
+# base <- noSupport
+# base.name <- 'energyDownliftNoSupport'
+# int <- support
+# int.name <- 'energyDownlift'
+# 
+# combined <- rbind(base, int)
+# 
+# ## now SF12 plots for comparison
+# p1 <- ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_smooth()
+# p2 <- ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
+#   geom_smooth()
+# 
+# print(p1)
+# print(p2)
+# 
+# combined.SF12 <- combined %>%
+#   select(run_id, year, intervention, SF_12_MCS, SF_12_PCS) %>%
+#   pivot_wider(names_from = 'intervention',
+#               values_from = c('SF_12_MCS', 'SF_12_PCS')) %>%
+#   mutate(MCS_diff = .data[[paste0('SF_12_MCS_', int.name)]] - .data[[paste0('SF_12_MCS_', base.name)]],
+#          PCS_diff = .data[[paste0('SF_12_PCS_', int.name)]] - .data[[paste0('SF_12_PCS_', base.name)]]) %>%
+#   select(run_id, year, MCS_diff, PCS_diff)
+# 
+# p3 <- ggplot(combined.SF12, aes(x = year, y = MCS_diff)) +
+#   geom_smooth() +
+#   geom_hline(yintercept = 0, linetype = 'dashed') +
+#   labs(title = 'Change in SF_12_MCS', subtitle = paste0(int.name, ' vs ', base.name)) +
+#   xlab('Year') +
+#   ylab('Change in MCS')
+# 
+# p4 <- ggplot(combined.SF12, aes(x = year, y = PCS_diff)) +
+#   geom_smooth() +
+#   geom_hline(yintercept = 0, linetype = 'dashed') +
+#   labs(title = 'Change in SF_12_PCS', subtitle = paste0(int.name, ' vs ', base.name)) +
+#   xlab('Year') +
+#   ylab('Change in MCS')
+# 
+# print(p3)
+# print(p4)
+
+```
+
 ## Area Under the Curve
@@
               int.name = 'energyDownlift',
-              QALY_value = 60000)  # QALY value == £60,000
+              QALY_value = 60000,  # QALY value == £60,000
+              int.label <- 'EPCG')
 ```
@@
      int.name = 'energyDownlift',
-     QALY_value = 60000)
+     QALY_value = 60000,
+     int.label = 'EPCG')
+```
+
+```{r}
+#ICER <- function(base, base.name, int, int.name, QALY_value) {
+
+base <- noSupport
+base.name <- 'energyDownliftNoSupport'
+int <- support
+int.name <- 'energyDownlift'
+QALY_value <- 60000
+
+combined <- rbind(base, int)
+
+combined.cost.mean <- combined %>%
+  #select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
+  select(run_id, year, total_boost, intervention, QALYs) %>%
+  mutate(QALY_value = QALYs * QALY_value) %>%
+  group_by(run_id, year, intervention) %>%
+  summarise(across(everything(), mean))
+
+# ICER = (C1 - C0) / (E1 - E0)
+# where
+# C1 = cost of intervention
+# E1 = effect of intervention
+# C0 = cost of control group
+# E0 = effect of control group
+
+# prepare var names
+c1 <- paste('total_boost', int.name, sep='_')
+c0 <- paste('total_boost', base.name, sep='_')
+e1 <- paste('QALYs', int.name, sep='_')
+e0 <- paste('QALYs', base.name, sep='_')
+
+ICER <- combined.cost.mean %>%
+  pivot_wider(names_from = 'intervention',
+              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
+  mutate(ICER = (.data[[c1]] - .data[[c0]]) / (.data[[e1]] - .data[[e0]])) %>%
+  select(run_id, year, ICER) %>%
+  mutate(intervention = int.name)
+
+pc1 <- quantile(ICER$ICER, .01)
+print(pc1)
+print(min(ICER$ICER))
+pc99 <- quantile(ICER$ICER, .99)
+print(pc99)
+print(max(ICER$ICER))
+
+ICER <- filter(ICER, ICER < pc99, ICER > pc1)
+print(min(ICER$ICER))
+print(max(ICER$ICER))
+
+p1 <- ggplot(ICER, aes(x = year, y = ICER, group = intervention, fill = intervention, colour = intervention)) +
+  geom_smooth() +
+  scale_y_continuous(label = comma) +
+  labs(title = 'ICER', subtitle = paste0(int.name, ' vs ', base.name))
+print(p1)
+
+ICER.final <- ICER %>%
+  group_by(run_id, intervention) %>%
+  summarise(ICER = mean(ICER)) %>%
+  group_by(intervention) %>%
+  summarise(margin = (qt(0.975, df=n() - 1) * sd(ICER)) / sqrt(n()),
+            ICER = mean(ICER))
+
+p2 <- ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention)) +
+  geom_col() +
+  geom_errorbar(aes(ymin = ICER - margin, ymax = ICER + margin, width = 0.4, group = intervention)) +
+  scale_y_continuous(label = comma) +
+  labs(title = 'ICER', subtitle = paste0(int.name, ' vs ', base.name)) +
+  xlab('Intervention')
+print(p2)
+
+print(paste0('ICER == ', ICER.final$ICER, ' +- ', ICER.final$margin))
 ```

### 2023-11-14 minos/testing/QALY_comparison_livingWage.Rmd
Attempting to fix weird bug where PCS doesnt transition. Think this will fix it. Updated some paths in config/uk_scaled.yaml, updated some functions in minos/utils_qaly.R and some tweaks to the QALY comparison scripts

@@
               int.name = 'livingWageIntervention',
-              QALY_value = 60000)  # QALY value == £60,000
+              QALY_value = 60000,
+              int.label <- 'LivingWage')  # QALY value == £60,000
 ```
@@
      int.name = 'livingWageIntervention',
-     QALY_value = 60000)
+     QALY_value = 60000,
+     int.label = 'LivingWage')
+```
+
+```{r}
+#ICER <- function(base, base.name, int, int.name, QALY_value) {
+
+base <- base
+base.name <- 'baseline'
+int <- wage
+int.name <- 'livingWageIntervention'
+QALY_value <- 60000
+int.label <- 'LivingWage'
+
+combined <- rbind(base, int)
+
+combined.cost.mean <- combined %>%
+  #select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
+  select(run_id, year, total_boost, intervention, QALYs) %>%
+  mutate(QALY_value = QALYs * QALY_value) %>%
+  group_by(run_id, year, intervention) %>%
+  summarise(across(everything(), mean))
+
+# ICER = (C1 - C0) / (E1 - E0)
+# where
+# C1 = cost of intervention
+# E1 = effect of intervention
+# C0 = cost of control group
+# E0 = effect of control group
+
+# prepare var names
+c1 <- paste('total_boost', int.name, sep='_')
+c0 <- paste('total_boost', base.name, sep='_')
+e1 <- paste('QALYs', int.name, sep='_')
+e0 <- paste('QALYs', base.name, sep='_')
+
+ICER <- combined.cost.mean %>%
+  pivot_wider(names_from = 'intervention',
+              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
+  mutate(ICER = (.data[[c1]] - .data[[c0]]) / (.data[[e1]] - .data[[e0]])) %>%
+  select(run_id, year, ICER) %>%
+  mutate(intervention = int.label)
+
+pc1 <- quantile(ICER$ICER, .01)
+print(pc1)
+print(min(ICER$ICER))
+pc99 <- quantile(ICER$ICER, .99)
+print(pc99)
+print(max(ICER$ICER))
+
+ICER <- filter(ICER, ICER < pc99, ICER > pc1)
+print(min(ICER$ICER))
+print(max(ICER$ICER))
+
+p1 <- ggplot(ICER, aes(x = year, y = ICER, group = intervention, fill = intervention, colour = intervention)) +
+  geom_smooth() +
+  scale_y_continuous(label = comma) +
+  labs(title = 'ICER', subtitle = paste0(int.name, ' vs ', base.name))
+print(p1)
+
+ICER.final <- ICER %>%
+  group_by(run_id, intervention) %>%
+  summarise(ICER = mean(ICER)) %>%
+  group_by(intervention) %>%
+  summarise(margin = (qt(0.975, df=n() - 1) * sd(ICER)) / sqrt(n()),
+            ICER = mean(ICER))
+
+p2 <- ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention)) +
+  geom_col() +
+  geom_errorbar(aes(ymin = ICER - margin, ymax = ICER + margin, width = 0.4, group = intervention)) +
+  scale_y_continuous(label = comma) +
+  labs(title = 'ICER', subtitle = paste0(int.name, ' vs ', base.name)) +
+  xlab('Intervention')
+print(p2)
+
+print(paste0('ICER == ', ICER.final$ICER, ' +- ', ICER.final$margin))
 ```

### 2023-11-14 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Added make target for running uk qaly scenarios on arc, and updated path in comparison scripts to uk scaled output directory

@@
 # # read in QALY files for baseline and interventions
-out.path <- here::here('output', 'default_config')
+#out.path <- here::here('output', 'default_config')
 #out.path <- here::here('output', 'glasgow_scaled')
-#out.path <- here::here('output', 'SF12_uk_scaled')
+out.path <- here::here('output', 'SF12_uk_scaled')
 

### 2023-11-14 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Added a function to calculate the total cost of the intervention (int - baseline). Also fixed the QALY calculation as there was a small mistake (pointed to MCS instead of PCS in one leg of the calculation)

@@
 
+# Total Cost of Intervention
+
 ```{r}
-#ICER <- function(base, base.name, int, int.name, QALY_value) {
-
-base <- noSupport
-base.name <- 'energyDownliftNoSupport'
-int <- support
-int.name <- 'energyDownlift'
-QALY_value <- 60000
-
-combined <- rbind(base, int)
-
-combined.cost.mean <- combined %>%
-  #select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
-  select(run_id, year, total_boost, intervention, QALYs) %>%
-  mutate(QALY_value = QALYs * QALY_value) %>%
-  group_by(run_id, year, intervention) %>%
-  summarise(across(everything(), mean))
-
-# ICER = (C1 - C0) / (E1 - E0)
-# where
-# C1 = cost of intervention
-# E1 = effect of intervention
-# C0 = cost of control group
-# E0 = effect of control group
-
-# prepare var names
-c1 <- paste('total_boost', int.name, sep='_')
-c0 <- paste('total_boost', base.name, sep='_')
-e1 <- paste('QALYs', int.name, sep='_')
-e0 <- paste('QALYs', base.name, sep='_')
-
-ICER <- combined.cost.mean %>%
-  pivot_wider(names_from = 'intervention',
-              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
-  mutate(ICER = (.data[[c1]] - .data[[c0]]) / (.data[[e1]] - .data[[e0]])) %>%
-  select(run_id, year, ICER) %>%
-  mutate(intervention = int.name)
-
-pc1 <- quantile(ICER$ICER, .01)
-print(pc1)
-print(min(ICER$ICER))
-pc99 <- quantile(ICER$ICER, .99)
-print(pc99)
-print(max(ICER$ICER))
-
-ICER <- filter(ICER, ICER < pc99, ICER > pc1)
-print(min(ICER$ICER))
-print(max(ICER$ICER))
-
-p1 <- ggplot(ICER, aes(x = year, y = ICER, group = intervention, fill = intervention, colour = intervention)) +
-  geom_smooth() +
-  scale_y_continuous(label = comma) +
-  labs(title = 'ICER', subtitle = paste0(int.name, ' vs ', base.name))
-print(p1)
-
-ICER.final <- ICER %>%
-  group_by(run_id, intervention) %>%
-  summarise(ICER = mean(ICER)) %>%
-  group_by(intervention) %>%
-  summarise(margin = (qt(0.975, df=n() - 1) * sd(ICER)) / sqrt(n()),
-            ICER = mean(ICER))
-
-p2 <- ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention)) +
-  geom_col() +
-  geom_errorbar(aes(ymin = ICER - margin, ymax = ICER + margin, width = 0.4, group = intervention)) +
-  scale_y_continuous(label = comma) +
-  labs(title = 'ICER', subtitle = paste0(int.name, ' vs ', base.name)) +
-  xlab('Intervention')
-print(p2)
-
-print(paste0('ICER == ', ICER.final$ICER, ' +- ', ICER.final$margin))
+intervention.cost(base = noSupport,
+                  base.name = 'energyDownliftNoSupport',
+                  int = support,
+                  int.name = 'energyDownlift',
+                  int.label = 'EPCG')
 ```

### 2023-11-14 minos/testing/QALY_comparison_livingWage.Rmd
Added a function to calculate the total cost of the intervention (int - baseline). Also fixed the QALY calculation as there was a small mistake (pointed to MCS instead of PCS in one leg of the calculation)

--- 2023-11-13 minos/testing/QALY_comparison_livingWage.Rmd
@@
 
-Can check histogram over each run to see the range of QALYs.
-
-```{r}
-# # histogram of qalys
-# ggplot(combined, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   facet_wrap(~year)
-# 
-# ggplot(filter(combined, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   labs(title = 'QALYs by run', subtitle = '2022')
-# 
-# ggplot(filter(combined, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   labs(title = 'QALYs by run', subtitle = '2028')
-# 
-# ggplot(filter(combined, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   labs(title = 'QALYs by run', subtitle = '2034')
-```
-
-and histograms of change...
-
-```{r}
-# # histogram of qalys
-# ggplot(combined.QALY.change, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   facet_wrap(~year)
-# 
-# ggplot(filter(combined.QALY.change, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   labs(title = 'QALY change by run', subtitle = '2022')
-# 
-# ggplot(filter(combined.QALY.change, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   labs(title = 'QALY change by run', subtitle = '2028')
-# 
-# ggplot(filter(combined.QALY.change, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   labs(title = 'QALY change by run', subtitle = '2034')
-```
-
-...and SF_12 MCS and PCS for good measure.
-
-```{r}
-# ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention)) +
-#   geom_smooth()
-# 
-# ggplot(combined, aes(x = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   facet_wrap(~year)
-# 
-# ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention)) +
-#   geom_smooth()
-# 
-# ggplot(combined, aes(x = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   facet_wrap(~year)
-```
-
 ## SF12 Change
@@
               int.name = 'livingWageIntervention',
-              QALY_value = 60000)  # QALY value == £60,000
-```
-
-```{r}
-# total.combined.cost <- combined.cost.change %>%
-#   group_by(run_id, intervention) %>%
-#   summarise(TotalChange = sum(QALY_value_change)) %>%
-#   group_by(intervention) %>%
-#   summarise(se = sd(TotalChange) / sqrt(n()),
-#             TotalChange = mean(TotalChange))
-# 
-# #print(paste0('Total combined cost == ', format(round(as.numeric(total.combined.cost), 1), nsmall=1, big.mark=",")))
-# 
-# ggplot(total.combined.cost, aes(x = intervention, y = TotalChange, group = intervention, fill = intervention)) +
-#   geom_col() +
-#   geom_errorbar(aes(ymin = TotalChange - se, ymax = TotalChange + se, width = 0.4, group = intervention)) +
-#   scale_y_continuous(label = comma) +
-#   labs(title = 'Total Change in QALY Value', subtitle = 'Baseline vs Living Wage Intervention') +
-#   xlab('Intervention')
-# 
-# ggplot(combined.cost.change, aes(x = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   facet_wrap(~year) +
-#   labs(title = 'QALY value change')
+              QALY_value = 60000,
+              int.label <- 'LivingWage')  # QALY value == £60,000
 ```
@@
      int.name = 'livingWageIntervention',
-     QALY_value = 60000)
+     QALY_value = 60000,
+     int.label = 'LivingWage')
 ```
 
+# Total Cost of Intervention
+
 ```{r}
-# ggplot(ICER, aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   facet_wrap(~year) +
-#   labs(title = 'ICER by run', subtitle = 'All Years')
-# 
-# ggplot(filter(ICER, year == 2022), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   labs(title = 'ICER by run', subtitle = '2022')
-# 
-# ggplot(filter(ICER, year == 2028), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   labs(title = 'ICER by run', subtitle = '2028')
-# 
-# ggplot(filter(ICER, year == 2031), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   labs(title = 'ICER by run', subtitle = '2031')
-# 
-# ggplot(filter(ICER, year == 2034), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_histogram() +
-#   labs(title = 'ICER by run', subtitle = '2034')
+intervention.cost(base = baseline,
+                  base.name = 'baseline',
+                  int = livWage,
+                  int.name = 'livingWageIntervention',
+                  int.label = 'Living Wage')
 ```

### 2023-11-17 minos/validation/cross_validation_default.Rmd
a lot of bug fixing and inclusion in (cross validated) handovers

@@
 
-## Job Sec
+## Children Ageing
+
+Children ageing is now calculated in MINOS.
 
 ```{r}
-jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                          df1.name = 'simulated', 
-                                          df2 = raw, 
-                                          df2.name = 'raw', 
-                                          var = 'job_sec')
 
-cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
-                 var = 'job_sec',
-                 save = FALSE)
-rm(jobsec.pivoted)
+format_child_age_data <- function(dataset) {
+  formatted.age.data <- dataset %>%
+                        dplyr::select(hidp, time, child_ages, pidp) %>%
+                        filter(time >= 2014) %>%
+                        group_by(pidp, time) %>%
+                        summarise(child_ages = max(child_ages))
+
+  split.ages <- strsplit(formatted.age.data$child_ages, "_")
+
+  child.ages.expanded <- data.frame(time = rep(formatted.age.data$time, sapply(split.ages, length)), 
+                                    #hidp= rep(formatted.age.data$hidp, sapply(split.ages, length)), 
+                                    pidp= rep(formatted.age.data$pidp, sapply(split.ages, length)), 
+                                    expanded_child_ages = as.numeric(unlist(split.ages)))
+
+  #child.ages.expanded <- child.ages.expanded %>%
+  #  group_by(pidp, time) %>%
+  #  summarise(expanded_child_ages = median(expanded_child_ages))
+
+  return (child.ages.expanded)
+}
+
+find_mode <- function(x) {
+  u <- unique(x)
+  tab <- tabulate(match(x, u))
+  u[tab == max(tab)]
+}
+
+cv.child.ages <- format_child_age_data(cv)
+cv1.child.ages <- format_child_age_data(cv1)
+cv2.child.ages <- format_child_age_data(cv2)
+cv3.child.ages <- format_child_age_data(cv3)
+cv4.child.ages <- format_child_age_data(cv4)
+cv5.child.ages <- format_child_age_data(cv5)
+raw.child.ages <- format_child_age_data(raw.dat)
+
+cv.mean.plots(cv1.child.ages, cv2.child.ages, cv3.child.ages, cv4.child.ages, cv5.child.ages, raw.child.ages, 'expanded_child_ages')
+multi_year_boxplots(raw.child.ages, cv.child.ages, 'expanded_child_ages')
+q_q_comparison(raw.child.ages, cv.child.ages, 'expanded_child_ages')
+
 ```
 
-## Job Hours
+```{r} 
+#nkids
 
-```{r}
-cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'job_hours')
-multi_year_boxplots(raw, cv, 'job_hours')
-q_q_comparison(raw, cv, 'job_hours')
+format_nkids_data <- function(dataset) {
+  dataset %>%
+  group_by(time, hidp) %>%
+  summarise(nkids = max(nkids)) %>%
+  #group_by(time) %>%
+  #summarise(nkids_by_year = sum(nkids_counts))
+  return (dataset)
+}
+
+cv.nkids <- format_nkids_data(cv)
+cv1.nkids <- format_nkids_data(cv1)
+cv2.nkids <- format_nkids_data(cv2)
+cv3.nkids <- format_nkids_data(cv3)
+cv4.nkids <- format_nkids_data(cv4)
+cv5.nkids <- format_nkids_data(cv5)
+raw.nkids <- format_nkids_data(raw.dat)
+
+cv.mean.plots(cv1.nkids, cv2.nkids, cv3.nkids, cv4.nkids, cv5.nkids, raw.nkids, 'nkids')
+multi_year_boxplots(raw.nkids, cv.nkids, 'nkids')
+q_q_comparison(raw.nkids, cv.nkids, 'nkids')
 ```

### 2023-11-17 minos/utils_datain.R

@@ -169,3 +169,8 @@ get_summary_out <- function(scenario_out_path, year, var.list) {
   
   return(grouped)
 }
+
+
+extract_child_ages <- function(child_ages_string){
+  return (as.numeric(unlist(strsplit(child_ages_string, "_"))))
+}

### 2023-11-17 minos/validation/cross_validation_default.Rmd
slight bug fix

@@
                         filter(time >= 2014) %>%
-                        group_by(pidp, time) %>%
+                        group_by(time, pidp) %>%
                         summarise(child_ages = max(child_ages))
@@
   dataset %>%
-  group_by(time, hidp) %>%
+  group_by(hidp, time, pidp) %>%
   summarise(nkids = max(nkids)) %>%

### 2023-11-20 minos/validation/handovers.Rmd
Lots of small changes working on the job_hours and hourly_wage transitions and modules

@@
 
+## Hourly Wage
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'hourly_wage')
+handover_lineplots(raw.dat, base.dat, 'hourly_wage')
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, hourly_wage)
+base.s <- base.dat %>%
+  select(pidp, age, time, hourly_wage)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+# now a version limited to 0-100
+spag <- spag %>%
+  filter(hourly_wage <= 100)
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+```{r}
+# some basic statistics about hourly_wage variable
+print("Some basic statistics on hourly_wage. These are all for 2020.")
+raw.2020 <- raw.dat %>% filter(time == 2020)
+print('All living people in 2020')
+print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
+# number individuals with an hourly_wage > 0
+print('People not in work')
+print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
+
+# Number in work
+print('People in work')
+print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
+
+# Extreme hourly_wage values
+print('Extreme hourly wage values: HIGH')
+print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
+print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
+print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
+print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
+print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
+print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
+
+raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
+print('Extreme hourly wage values: LOW (non-zero)')
+print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
+print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
+print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
+print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
+
+```
+
 ## Job Hours

### 2023-11-20 minos/minosPipeline/RunPipeline.py

@@ -31,6 +31,7 @@ from minos.modules.education import Education
 from minos.modules.nutrition import Nutrition, lmmYJNutrition, lmmDiffNutrition
 from minos.modules.job_hours import JobHours
 from minos.modules.job_sec import JobSec
+from minos.modules.hourly_wage import HourlyWage
 
 from minos.modules.S7Labour import S7Labour
 from minos.modules.S7Housing import S7Housing
@@ -85,6 +86,7 @@ components_map = {
     "Education()": Education(),
     "JobHours()": JobHours(),
     "JobSec()": JobSec(),
+    "HourlyWage()": HourlyWage(),
 }
 
 SIPHER7_components_map = {  # SIPHER7 stuff

### 2023-11-20 minos/modules/hourly_wage.py

@@ -10,15 +10,15 @@ from seaborn import histplot
 import numpy as np
 import logging
 
-class JobHours(Base):
+class HourlyWage(Base):
 
     # Special methods used by vivarium.
     @property
     def name(self):
-        return 'job_hours'
+        return 'hourly_wage'
 
     def __repr__(self):
-        return "JobHours()"
+        return "HourlyWage()"
 
     def setup(self, builder):
         """ Initialise the module during simulation.setup().
@@ -63,9 +63,9 @@ class JobHours(Base):
                         'pidp',
                         'nkids',
                         'S7_labour_state',
-                        'job_hours',
-                        'job_hours_diff',
-                        'hh_income'
+                        'hh_income',
+                        'hourly_wage',
+                        'hourly_wage_diff',
                         ]
 
 
@@ -87,7 +87,7 @@ class JobHours(Base):
         #                                             path=self.transition_dir)
         #self.gee_transition_model = r_utils.load_transitions(f"hh_income/gee_diff/hh_income_GEE_DIFF", self.rpy2Modules,
         #                                                     path=self.transition_dir)
-        self.gee_transition_model = r_utils.load_transitions(f"job_hours/glmm/job_hours_GLMM", self.rpy2Modules,
+        self.gee_transition_model = r_utils.load_transitions(f"hourly_wage/glmm/hourly_wage_GLMM", self.rpy2Modules,
                                                              path=self.transition_dir)
         #self.history_data = self.generate_history_dataframe("final_US", [2018, 2019], view_columns)
         #self.history_data["hh_income_diff"] = self.history_data['hh_income'] - self.history_data.groupby(['pidp'])['hh_income'].shift(1)
@@ -106,11 +106,14 @@ class JobHours(Base):
         # Create frame with new 3 columns and add it to the main population frame.
         # This is the same for both new cohorts and newborn babies.
         # Neither should be dead yet.
-        pop_update = pd.DataFrame({'job_hours_diff': 0.,
-                                   'hourly_wage_calc': 0.},
+        pop_update = pd.DataFrame({'hourly_wage_diff': 0.},
                                   index=pop_data.index)
         self.population_view.update(pop_update)
 
+
+    ## NOTE::
[…]

### 2023-11-20 minos/outcomes/QALY_comparison.Rmd
Wrote a generic version of the QALY_comparison.Rmd notebook, where key parameters such as baseline and intervention data are set by arguments to the render call in outcomes/Makefile

--- 2023-11-14 minos/testing/QALY_comparison_energyCrises_diff.Rmd
@@
     code_folding: hide
+params: 
+  experiment: experiment 
+  baseline: baseline 
+  intervention: intervention
+  intervention_label: intervention_label
 ---
@@
 ## Data
+
+```{r read_data, include=False}
+experiment <- params$experiment
+baseline <- params$baseline
+intervention <- params$intervention
+intervention_label <- params$intervention_label
+
+out.path <- here::here('output', args$experiment)
+
+base.path <- get_latest_runtime_subdirectory(here::here(out.path, baseline))
+int.path <- get_latest_runtime_subdirectory(here::here(out.path, intervention))
+
+base <- read.csv(paste0(base.path, 'qalys.csv'))
+int <- read.csv(paste0(int.path, 'qalys.csv'))
+
+combined <- rbind(base, int)
+```
 
@@
 ```{r}
-QALY_comparison(base = noSupport,
-                base.name = 'energyDownliftNoSupport',
-                int = support,
-                int.name = 'energyDownlift')
+QALY_comparison(base = base,
+                base.name = baseline,
+                int = int,
+                int.name = intervention)
 ```
@@
 ```{r}
-sf12.plots(base = noSupport,
-           base.name = 'energyDownliftNoSupport',
-           int = support,
-           int.name = 'energyDownlift')
-```
-
-```{r}
-# base <- noSupport
-# base.name <- 'energyDownliftNoSupport'
-# int <- support
-# int.name <- 'energyDownlift'
-# 
-# combined <- rbind(base, int)
-# 
-# ## now SF12 plots for comparison
-# p1 <- ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_smooth()
-# p2 <- ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_smooth()
-# 
-# print(p1)
-# print(p2)
-# 
-# combined.SF12 <- combined %>%
-#   select(run_id, year, intervention, SF_12_MCS, SF_12_PCS) %>%
-#   pivot_wider(names_from = 'intervention',
-#               values_from = c('SF_12_MCS', 'SF_12_PCS')) %>%
-#   mutate(MCS_diff = .data[[paste0('SF_12_MCS_', int.name)]] - .data[[paste0('SF_12_MCS_', base.name)]],
-#          PCS_diff = .data[[paste0('SF_12_PCS_', int.name)]] - .data[[paste0('SF_12_PCS_', base.name)]]) %>%
-#   select(run_id, year, MCS_diff, PCS_diff)
-# 
-# p3 <- ggplot(combined.SF12, aes(x = year, y = MCS_diff)) +
-#   geom_smooth() +
-#   geom_hline(yintercept = 0, linetype = 'dashed') +
-#   labs(title = 'Change in SF_12_MCS', subtitle = paste0(int.name, ' vs ', base.name)) +
-#   xlab('Year') +
-#   ylab('Change in MCS')
-# 
-# p4 <- ggplot(combined.SF12, aes(x = year, y = PCS_diff)) +
-#   geom_smooth() +
-#   geom_hline(yintercept = 0, linetype = 'dashed') +
-#   labs(title = 'Change in SF_12_PCS', subtitle = paste0(int.name, ' vs ', base.name)) +
-#   xlab('Year') +
-#   ylab('Change in MCS')
-# 
-# print(p3)
-# print(p4)
-
+sf12.plots(base = base,
+           base.name = baseline,
+           int = int,
+           int.name = intervention)
 ```
@@
 ```{r}
-auc.plots(base = noSupport, 
-          base.name = 'NoSupport',
-          intervention = support,
-          int.name = 'Support')
+auc.plots(base = base,
+          base.name = baseline,
+          int = int,
+          int.name = intervention)
 ```
@@
 ```{r}
-cost.per.qaly(base = noSupport,
-              base.name = 'energyDownliftNoSupport',
-              int = support,
-              int.name = 'energyDownlift',
+cost.per.qaly(base = base,
+              base.name = baseline,
+              int = int,
+              int.name = intervention,
               QALY_value = 60000,  # QALY value == £60,000
-              int.label <- 'EPCG')
+              int.label <- intervention_label)
 ```
@@
 ```{r}
-ICER(base = noSupport,
-     base.name = 'energyDownliftNoSupport',
-     int = support,
-     int.name = 'energyDownlift',
+ICER(base = base,
+     base.name = baseline,
+     int = int,
+     int.name = intervention,
      QALY_value = 60000,
-     int.label = 'EPCG')
+     int.label = intervention_label)
 ```
@@
 ```{r}
-intervention.cost(base = noSupport,
-                  base.name = 'energyDownliftNoSupport',
-                  int = support,
-                  int.name = 'energyDownlift',
-                  int.label = 'EPCG')
+intervention.cost(base = base,
+                  base.name = baseline,
+                  int = int,
+                  int.name = intervention,
+                  int.label = intervention_label)
 ```

### 2023-11-20 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Fix issue in QALY_comparison script where something was left in that caused a problem

@@
 
-```{r}
-# base <- noSupport
-# base.name <- 'energyDownliftNoSupport'
-# int <- support
-# int.name <- 'energyDownlift'
-# 
-# combined <- rbind(base, int)
-# 
-# ## now SF12 plots for comparison
-# p1 <- ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_smooth()
-# p2 <- ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
-#   geom_smooth()
-# 
-# print(p1)
-# print(p2)
-# 
-# combined.SF12 <- combined %>%
-#   select(run_id, year, intervention, SF_12_MCS, SF_12_PCS) %>%
-#   pivot_wider(names_from = 'intervention',
-#               values_from = c('SF_12_MCS', 'SF_12_PCS')) %>%
-#   mutate(MCS_diff = .data[[paste0('SF_12_MCS_', int.name)]] - .data[[paste0('SF_12_MCS_', base.name)]],
-#          PCS_diff = .data[[paste0('SF_12_PCS_', int.name)]] - .data[[paste0('SF_12_PCS_', base.name)]]) %>%
-#   select(run_id, year, MCS_diff, PCS_diff)
-# 
-# p3 <- ggplot(combined.SF12, aes(x = year, y = MCS_diff)) +
-#   geom_smooth() +
-#   geom_hline(yintercept = 0, linetype = 'dashed') +
-#   labs(title = 'Change in SF_12_MCS', subtitle = paste0(int.name, ' vs ', base.name)) +
-#   xlab('Year') +
-#   ylab('Change in MCS')
-# 
-# p4 <- ggplot(combined.SF12, aes(x = year, y = PCS_diff)) +
-#   geom_smooth() +
-#   geom_hline(yintercept = 0, linetype = 'dashed') +
-#   labs(title = 'Change in SF_12_PCS', subtitle = paste0(int.name, ' vs ', base.name)) +
-#   xlab('Year') +
-#   ylab('Change in MCS')
-# 
-# print(p3)
-# print(p4)
-
-```
-
 ## Area Under the Curve

### 2023-11-23 minos/validation/handovers.Rmd
Added dependency to household upscaling, and some WIP stuff on the msm model for chron_disease

--- 2023-10-19 minos/validation/handovers.Rmd
@@
 ```{r}
-raw.nut <- raw.dat %>%
-  select(pidp, age, time, nutrition_quality)
-base.nut <- base.dat %>%
-  select(pidp, age, time, nutrition_quality)
-
-nut.spag <- rbind(raw.nut, base.nut)
-
-spaghetti_plot(nut.spag, 'nutrition_quality',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(nut.spag, "nutrition_quality",
-               save = T,
-               save.path = save.path)
-
-rm(raw.nut, base.nut, nut.spag)
+# raw.nut <- raw.dat %>%
+#   select(pidp, age, time, nutrition_quality)
+# base.nut <- base.dat %>%
+#   select(pidp, age, time, nutrition_quality)
+# 
+# nut.spag <- rbind(raw.nut, base.nut)
+# 
+# spaghetti_plot(nut.spag, 'nutrition_quality',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# 
+# density_ridges(nut.spag, "nutrition_quality",
+#                save = T,
+#                save.path = save.path)
+# 
+# rm(raw.nut, base.nut, nut.spag)
 ```
@@
 handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
+
+raw.2020.alc <- raw.dat %>% 
+  filter(time == 2020) %>%
+  group_by(auditc) %>%
+  summarise(n = n()) %>%
+  mutate(prop = n / sum(n))
+
 ```
@@
 handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
+
+raw.2020.phys <- raw.dat %>% 
+  filter(time == 2020) %>%
+  group_by(active) %>%
+  summarise(n = n()) %>%
+  mutate(prop = n / sum(n))
 ```
@@
 handover_ordinal(raw.dat, base.dat, var = 'matdep', save = shall.we.save)
+
+raw.dat$chron_disease <- as.factor(raw.dat$chron_disease)
+raw.2020.cd <- raw.dat %>%
+  select(time, chron_disease, age) %>%
+  filter(time == 2020) %>%
+  mutate(age_group = cut(age, 
+                         breaks = c(0,20,30,40,50,60,70,80,90,100,120),
+                         labels = c('16-19', '20-30', '30-40', '40-50', '50-60', '60-70', '70-80', '80-90', '90-100', '100+'))) %>%
+  group_by(age_group, chron_disease) %>%
+  summarise(n = n()) %>%
+  group_by(age_group) %>%
+  mutate(prop = n / sum(n),
+         perc = prop * 100)
+  # mutate(prop = n() / sum(n),
+  #        perc = prop * 100)
+
+raw.2020.cd
+
+ggplot(raw.2020.cd, aes(x = age_group, y = perc, group = chron_disease, colour = chron_disease, fill = chron_disease)) +
+  geom_col(position = 'dodge') +
+  xlab('Age Group') +
+  ylab('Proportion')
 ```

### 2023-11-23 minos/utils_qaly.R

@@ -62,7 +62,7 @@ sf12.plots <- function(base, base.name, int, int.name) {
     geom_hline(yintercept = 0, linetype = 'dashed') +
     labs(title = 'Change in SF_12_PCS', subtitle = paste0(int.name, ' vs ', base.name)) +
     xlab('Year') +
-    ylab('Change in MCS')
+    ylab('Change in PCS')
   
   print(p3)
   print(p4)

### 2023-11-24 minos/testing/QALY_comparison_livingWage.Rmd
Fixed some typos in living wage QALY comparison script
Created a new script to handle upscaling to uk individual population size, however this crashes my PC so Im going to have to test it on arc. Forgive me John Hodrien...

@@
 
+# Number people Below Living Wage
+
+```{r}
+# Only need this for the baseline 2020 input data
+base.num <- base %>%
+  filter()
+```
+
 # QALY comparison
@@
 ```{r}
-intervention.cost(base = baseline,
+intervention.cost(base = base,
                   base.name = 'baseline',
-                  int = livWage,
+                  int = wage,
                   int.name = 'livingWageIntervention',
-                  int.label = 'Living Wage')
+                  int.label = 'LivingWage')
 ```

### 2023-11-24 minos/data_generation/US_upscaling_test.py

@@ -22,7 +22,7 @@ import US_utils
 import argparse
 
 
-def merge_with_synthpop_households(synthpop, msim_data, merge_column="hidp"):
+def merge_with_synthpop_households(synthpop, msim_data, merge_column="pidp"):
     """ Merge US data on synthetic pop individual data.
 
     Parameters
@@ -117,16 +117,16 @@ def main(region, percentage=100, bootstrapping=False, n=100_000):
         subsetted_synthpop_data = subsetted_synthpop_data.sample(n, replace=True)
 
     # merge synthetic and US data together.
-    subsetted_synthpop_data['hidp'] = subsetted_synthpop_data['hhid']
+    subsetted_synthpop_data['pidp'] = subsetted_synthpop_data['pidp']
     merged_data = merge_with_synthpop_households(subsetted_synthpop_data, US_data)
     merged_data = merged_data.dropna(axis=0, subset=[
         "time"])  # remove rows that are missing in spatial data and aren't merged properly.
     print(f"{sum(merged_data['time'].value_counts())} rows out of {merged_data.shape[0]} successfully merged.")
 
     # scramble new hidp and pidp.
-    merged_data['hidp'] = merged_data['new_hidp']  # replace old pidp.
-    merged_data.drop(['new_hidp', 'hhid'], axis=1, inplace=True)  # removing old hidp columns
-    merged_data['pidp'] = merged_data.index  # creating new pidps.
+    merged_data['pidp'] = merged_data['new_pidp']  # replace old pidp.
+    merged_data.drop(['new_pidp', 'pidp'], axis=1, inplace=True)  # removing old hidp columns
+    #merged_data['pidp'] = merged_data.index  # creating new pidps.
 
     # take subset of sample if desired. defaults to 100% for now.
     sampled_data = take_synthpop_sample(merged_data, percentage / 100)
@@ -140,8 +140,8 @@ def main(region, percentage=100, bootstrapping=False, n=100_000):
     sampled_data['weight'] = 1  # force sample weights to 1. as this data is expanded weights no longer representative
     # but still updating weights helps with weighted aggregates later.
 
-    US_utils.check_output_dir(f"data/scaled_{region}_US/")  # check save directory exists or create it.
-    US_utils.save_file(sampled_data, f"data/scaled_{region}_US/", '', 2020)
+    US_utils.check_output_dir(f"data/scaled_{region}_US/ind/")  # check save directory exists or create it.
[…]

### 2023-11-27 minos/validation/handovers.Rmd
Cast vars to factor in the handovers_ordinal() function in validation
Lots of WIP tweaks to the hourly_wage model. Seems to be in a reasonable state, but could do with a bit of work

--- 2023-11-20 minos/validation/handovers.Rmd
@@
 ```
-
-## Job Hours
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'job_hours')
-handover_lineplots(raw.dat, base.dat, 'job_hours')
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, job_hours)
-base.s <- base.dat %>%
-  select(pidp, age, time, job_hours)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'job_hours',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-```{r}
-
-```

### 2023-11-27 minos/validation/handovers.Rmd
adding alternate file source to handovers for teswting

@@
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+#out.path <- here::here('output', 'scotland_scaled/')
+#base.dat <- read_first_singular_local_out(out.path, '25UniversalCredit', drop.dead = TRUE)
 ```
@@
 
-## Hourly Wage
-
 ```{r}
-handover_boxplots(raw.dat, base.dat, 'hourly_wage')
-handover_lineplots(raw.dat, base.dat, 'hourly_wage')
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, hourly_wage)
-base.s <- base.dat %>%
-  select(pidp, age, time, hourly_wage)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-# now a version limited to 0-100
-spag <- spag %>%
-  filter(hourly_wage <= 100)
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-```{r}
-# some basic statistics about hourly_wage variable
-print("Some basic statistics on hourly_wage. These are all for 2020.")
-raw.2020 <- raw.dat %>% filter(time == 2020)
-print('All living people in 2020')
-print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
-# number individuals with an hourly_wage > 0
-print('People not in work')
-print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
-
-# Number in work
-print('People in work')
-print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
-
-# Extreme hourly_wage values
-print('Extreme hourly wage values: HIGH')
-print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
-print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
-print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
-print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
-print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
-print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
-
-raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
-print('Extreme hourly wage values: LOW (non-zero)')
-print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
-print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
-print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
-print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
 

### 2023-11-29 minos/outcomes/paper_1_notebook.Rmd
making sure reuslts in notebook look good

--- 2023-09-12 minos/outcomes/paper_1_notebook.Rmd
@@
 title: "Paper 1 Notebook"
-output: html_notebook
+output:
+  pdf_document: default
+  html_document:
+    df_print: paged
 ---
@@
 library(tidyverse)
-
+library(performance)
+library(broom.mixed)
+library(ggridges)
+save.path <- "minos/outcomes/paper1_plots/"
+raw.data.dir <- "data/raw_US/"
+mice.data.dir <- "data/composite_US/"
+final.data.dir <- mice.data.dir
 ```
@@
 
-dataDir <- "data/raw_US/"
-filelist <- list.files(dataDir,
+# get raw data file names from 2011-2013.
+filelist <- list.files(raw.data.dir,
                        include.dirs = FALSE,
@@
                        pattern = '[0-9]{4}_US_cohort.csv')[21:23] # get files for 2011-2013.
+# load raw data.
 raw.data <- do.call(rbind, lapply(filelist, read.csv))
 
+# baseline OLS model formula. 
 raw_model_formula_string <- "SF_12 ~ factor(sex) + 
@@
                   scale(hh_netinc)"
+
+# Calculate required variables for regression to run. 
 raw_model_formula <- as.formula(raw_model_formula_string)
 variables <- all.vars(raw_model_formula)
-variables[1] <- "SF_12"
 
+# get only needed variables and replace missing codes with NA.
 raw.data <- raw.data[, append(variables, c("time", 'pidp', 'weight'))]
-
-raw.data <- raw.data %>%
-        group_by(pidp) %>%
-        #mutate(diff = .data[[dependent]] - lag(.data[[dependent]], order_by = time)) %>%
-        mutate(last = lag(.data[["SF_12"]], order_by = time)) %>%
-        rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff
-
 raw.data <- replace.missing(raw.data)
 
-#visreg(sf12.lm, "age", by="sex", overlay=T)
+raw.data <- drop_na(raw.data)
 
-pdf(paste0(save.path, "total_missingness_structure1.pdf"))
-aggr(raw.data[,variables], sortVars=T,  oma=c(8,4,4,4), numbers=T, cex.axis=1.0, col = c(blue, orange), prop=F, combined=T, cex.numbers=0.5)
-dev.off()
+# get raw data file names.
+full.raw.filelist <- list.files(raw.data.dir,
+                       include.dirs = FALSE,
+                       full.names = TRUE,
+                       pattern = '[0-9]{4}_US_cohort.csv')[21:30] # get files for 2011-2013.
+# load raw data.
+full.raw.data <- do.call(rbind, lapply(full.raw.filelist, read.csv))
 
-raw.data <- drop_na(raw.data)
+# get only needed variables and replace missing codes with NA.
+full.raw.data <- full.raw.data[, append(variables, c("time", 'pidp', 'weight'))]
+full.raw.data <- replace.missing(full.raw.data)
 ```
@@
 
+# calculate baseline OLS model.
 sf12.lm <- lm(raw_model_formula_string,
               data= raw.data)
-a<- summary(sf12.lm)
-print(a)
-print(a$adj.r.squared)
+# print summary statistics
+print(summary(sf12.lm))
 
-save.path <- "minos/outcomes/paper1_plots/"
+# create save.path if it doesn't exist and save OLS coefficients as a latex table there. 
 create.if.not.exists(save.path)
-texreg(sf12.lm, dcolumn=T, booktabs=T, file=paste0(save.path,'ols_coefficients.txt'), custom.model.names=c("OLS"), single.row=T)
-save(sf12.lm, file = paste0(save.path,"baseline_OLS.RData"))
-
 write_coefs <- T
@@
 
+# diagnostic plots for OLS presentation. 
 forest_plot_lm(sf12.lm, paste0(save.path, "presentation_forest.pdf"))
@@
 
-```
+# raw data handovers from 2011-2020.
 
-```{r composite_data_processing}
-# new formula and get data from final
+start.data <- raw.data[which(raw.data$time==2013),]
+handover.data <- start.data[, c("pidp", "SF_12", "time")]
+for (i in 1:7){
+  start.data$SF_12 <- predict(sf12.lm, start.data)
+  start.data[, 'time'] <- start.data[, 'time'] +1
+  handover.data <- rbind(handover.data, start.data[, c("pidp", "SF_12", "time")])
+}
 
-dataDir <- "data/composite_US/"
-filelist <- list.files(dataDir,
-                       include.dirs = FALSE,
-                       full.names = TRUE,
-                       pattern = '[0-9]{4}_US_cohort.csv')[3:5] # get files for 2011-2013.
-final.data <- do.call(rbind, lapply(filelist, read.csv))
+handover_boxplots(full.raw.data, handover.data, "SF_12", save.path, "ols_SF12_boxplot")
+density_ridges(full.raw.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "ols_raw_ridges")
+density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "ols_handover_ridges")
 
-# scale(SF_12_last) +
-model_formula_string <- "SF_12 ~
-                  factor(sex) + 
-                  relevel(factor(ethnicity), ref='WBI') + 
-                  scale(age) + 
-                  scale(I(age**2)) +
-                  factor(education_state) + 
-                  factor(S7_labour_state) + 
-                  relevel(factor(job_sec), ref=1) +
-                  relevel(factor(region), ref='London') +
-                  scale(hh_income) + 
-                  scale(I(hh_income**2))"
-
-final.data <- final.data %>%
-        group_by(pidp) %>%
-        #mutate(diff = .data[[dependent]] - lag(.data[[dependent]], order_by = time)) %>%
-        mutate(last = lag(.data[["SF_12"]], order_by = time)) %>%
-        rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff
-
-glmm_model_formula <- as.formula(model_formula_string)
-variables <- all.vars(glmm_model_formula)
-#variables[2] <- "SF_12"
-
-final.data <- final.data[, append(variables, c("time", 'pidp', 'weight'))]
-
-final.data <- replace.missing(final.data)
-final.data <- drop_na(final.data)
-
+# remove raw data to prevent lag. 
+#rm(raw.data)
+#rm(full.raw.data)
 ```
@@
 
+```{r}
+# load in all 2009-2020 datasets
+mice.filelist <- list.files(mice.data.dir,
+                       include.dirs = FALSE,
+                       full.names = TRUE,
+                       pattern = '[0-9]{4}_US_cohort.csv')
+mice.data <- do.call(rbind, lapply(mice.filelist, read.csv))
+
+# missingness MICE model formula
+mice_formula_string <- "SF_12 ~ 
+                        factor(sex) + 
+                        relevel(factor(ethnicity), ref='WBI') + 
+                        scale(age) + 
+                        factor(education_state) + 
+                        factor(S7_labour_state) + 
+                        relevel(factor(job_sec), ref=1) +
+                        relevel(factor(region), ref='London') +
+                        scale(hh_income) + 
+                        scale(I(hh_income**2)) +
+                        factor(housing_quality) +
+                        factor(neighbourhood_safety) + 
+                        factor(loneliness) +
+                        ncigs +
+                        nutrition_quality"
+
+mice_model_formula <- as.formula(mice_formula_string)
+variables <- all.vars(mice_model_formula)
+
+# get required variables and replace missing value codes.
+mice.data <- replace.missing(mice.data)
+
+# preserving key columns that aren't imputed for later. cant be included. in imputation set due to perfect seperation. 
+mice.pidp <- mice.data[which(mice.data$time %in% c(2011, 2012, 2013)), "pidp"]
+mice.time <- mice.data[which(mice.data$time %in% c(2011, 2012, 2013)), "time"]
+mice.weights <- mice.data[which(mice.data$time %in% c(2011, 2012, 2013)), "weight"]
+
+mice.2018.pidp <- mice.data[which(mice.data$time %in% c(2016, 2017, 2018)), "pidp"]
+mice.2018.time <- mice.data[which(mice.data$time %in% c(2016, 2017, 2018)), "time"]
+mice.2018.weights <- mice.data[which(mice.data$time %in% c(2016, 2017, 2018)), "weight"]
+```
+
 ```{r MICE}
 
-dataDir <- "data/composite_US/"
-filelist <- list.files(dataDir,
-                       include.dirs = FALSE,
-                       full.names = TRUE,
-                       pattern = '[0-9]{4}_US_cohort.csv')[3:5] # get files for 2011-2013.
-composite.data <- do.call(rbind, lapply(filelist, read.csv))
-composite.data <- replace.missing(composite.data)
-
-pdf(paste0(save.path, "total_missingness_structure2.pdf"))
-aggr(composite.data[, all.vars(as.formula(model_formula_string))], sortVars=T,  oma=c(8,4,4,4), numbers=T, cex.axis=1.0, col = c(blue, orange), prop=F, combined=T, cex.numbers=0.5)
-dev.off()
-
-mice_pidps <- composite.data$pidp
-mice_weights <- composite.data$weight
-mice_time <- composite.data$time
-
-model_formula_string <- "SF_12 ~ factor(sex) +  relevel(factor(ethnicity), ref='WBI') + scale(age) + factor(education_state) + factor(S7_labour_state) + relevel(factor(job_sec), ref=1) + relevel(factor(region), ref='London') + scale(hh_income)"
-
+#getting MICE data for 2011-2020. imputing loneliness, housing, neighbourhood. 
 # set up MICE and cache data
@@
 # figures of convergence and difference in distribution.
+
 imp_columns <- c("SF_12",
@@
                  "age", 
-                 "hh_income")
+                 "time", 
+                 "hh_income",
+                 "housing_quality",
+                 "neighbourhood_safety",
+                 "loneliness",
+                 "ncigs",
+                 'nutrition_quality'
+)
 
-method <-   c('pmm',
+method <- c("pmm",
+            'pmm',
+            'pmm',
             'pmm',#'polr',
@@
             'pmm',
+            'pmm', #'polr', #'pmm',
             'pmm',
@@
             'pmm',
-            'pmm')
+            'pmm',
+            'pmm',
+            'pmm',
+            "pmm",
+            "pmm")
 
@@
 
-cached<-F
-if (cached){
-  load('papers/phd1/data/mice_set.RData')
-  load('papers/phd1/data/mice_data.RData')
-} else{
-  pidps <- composite.data$pidp
-  save(pidps, file = paste0(save.path, 'mice_pidps.RData'))
-  mice.weights <- composite.data$weight
-  save(mice.weights, file = paste0(save.path, 'mice_weights.RData'))
+#pdf("papers/phd1/plots/total_missingness_structure2.pdf")
+#aggr(subset(final.data[,reg_columns], select=-c(y)), sortVars=T,  oma=c(8,4,4,4), numbers=T, cex.axis=1.0, col = c(blue, orange), prop=F, combined=T, cex.numbers=0.5)
+#dev.off()
 
-  mice_set <- mice(data = composite.data[,imp_columns], method=method,
-                   m = 20, maxit = 10,
-                   #m = 2, maxit = 2,
-                   remove.collinear=T)
-  mice.data <- complete(mice_set) 
-  mice.data$weight <- mice_weights
-  mice.data$pidp <- mice_pidps
-  mice.data$time <-mice_time
+mice.data$ethnicity <- factor(mice.data$ethnicity)
+mice.data$S7_labour_state <- factor(mice.data$S7_labour_state)
+mice.data$region <- factor(mice.data$region)
 
-  save(mice_set, file = paste0(save.path,'mice_set.RData'))
-  save(mice.data, file = paste0(save.path,'mice_data.RData'))
+aggr_columns <- c("SF_12",
+                 "job_sec",
+                 "education_state",
+                 "S7_labour_state", 
+                 "ethnicity", 
+                 "hh_income",
+                 "neighbourhood_safety",
+                 "loneliness",
+                 "ncigs",
+                 'nutrition_quality'
+)
+# initial missingness structure for 2011-2013 US data.
+pdf(paste0(save.path, "total_missingness_structure1.pdf"))
+aggr(mice.data[,aggr_columns], sortVars=T, prop=T, combined=F,varheight=T, oma=c(10,5,0,2), gap=0)
+dev.off()
+
+load_cache <- F
+if (load_cache) {
+  mice_set <- readRDS("data/transitions/MICE_set.rds")
+} else {
+  n_iter <- 30
+  max_iter <- 10
+  # future mice is parallelised version of MICE.
+  mice_set <- futuremice(data = mice.data, #method=method,
+                   #m = 10, maxit = 30,
+                   m = n_iter, maxit = max_iter,
+                   remove.collinear=F)
+  saveRDS(mice_set, "data/transitions/MICE_set.rds")
 }
 
-#pdf("papers/phd1/plots/ols_mice_convergence.pdf")
-#print(plot(mice_set, y = SF_12 + y ~ .it | .ms))
-#dev.off()
+```
+
+```{r mice_output}
+
+# only looking at 2011-2013 subset of data. convert to data frame, subset, and back to MICE mids. 
+# also adding variables that can't be imputed back in. pidp time weight.
+mice.long <- complete(mice_set, action = "long", include=T)
+#mice.long.subset <- mice.long[which(mice.long$time %in% c(2011, 2012, 2013)), ]
+
+mice.long$pidp <- mice.data$pidp
+mice.long$weight <- mice.data$weight
+mice.long$time <- mice.data$time
+mice_set.full <- as.mids(mice.long)
+
+mice.long.subset <- mice.long[which(mice.long$time %in% c(2011, 2012, 2013)), ]
+mice_set.subset <- as.mids(mice.long.subset)
+
+# convergence plots needs to be done on full mice subset. 
 pdf(paste0(paste0(save.path,"ols_mice_convergence.pdf")))
@@
 
-mice.sf12.lm <- with(mice_set, lm(as.formula(model_formula_string)))
+# pooling OLS estimate together. 
+mice.sf12.lm <- with(mice_set.subset, lm(as.formula(mice_formula_string)))
 final.pool<- pool(mice.sf12.lm)
 
+# summary stats for final pool. 
 pooled_lm <- mice.sf12.lm$analyses[[1]]
@@
 mice.preds<- predict(pooled_lm)
-
 pool.r.squared(final.pool)
@@
 # mice objects dont go in forest plot annoyingly. move coefficients over to a
-# dummy lm that plot_models can read.
-mice.lm.object <- summary(lm(model_formula_string, data = complete(mice_set)))
+# dummy lm that sjPlot::plot_models can read.
+mice.lm.object <- summary(lm(mice_formula_string, data = complete(mice_set.subset)))
 mice.lm.object$coefficients[,1] <- pool.sum$estimate
@@
 mice.lm.object$coefficients[,4] <- pool.sum$p.value
-save(mice.lm.object, file = paste0(paste0(save.path,'mice_lm_object.RData')))
 
-#texreg(mice.lm.object, dcolumn=T, booktabs=T, file='../plots/mice_ols_coefficients.txt', title="SF12 MICE OLS Coefficients", custom.model.names=c("SF12 OLS"), single.row=T, include.aic=T)
-
+# making density plot. 
 res <- as.data.frame(predict(pooled_lm))
-real <- as.data.frame(data$SF_12)
+real <- as.data.frame(mice.data$SF_12)
 res$type <- c("Predicted")
@@
 
+# coefficient forest plot. 
 forest_plot(mice.lm.object, paste0(save.path,'mice_SF12_forest.pdf'))
 
+# writing coefficients table for MICE. 
+# is there a version for pool table?
 write_coefs <- T
@@
          fontsize='small') # small font
+
+  # same again for MICE pool. 
+  texreg_file <- paste0(save.path, 'SF12_MICE_pool_OLS_coefficients.txt')
+  tex_label <- paste0("table: MICE_pool_OLS_coefficients") 
+  tex_headers <- c(texreg::names2latex("MICE SF_12 OLS Pool"))
+  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "ols"))    
+  texreg(final.pool, # what model to save coefs for. 
+         file=texreg_file,  # where to save.
+         custom.model.names = tex_headers, # title of table.
+         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
+         digits=4, # p values significant figures.
+         caption=tex_caption, # \caption command option. 
+         label = tex_label, # \label command option. 
+         dcolumn=T,# nice column alignment. 
+         booktabs=T, # nice hlines. (recommended)
+         tabular=T,# tabular env.
+         single.row = T, # nicer one row formatting.
+         longtable=T, # allows tables to wrap over pages
+         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
+         fontsize='small') # small font
 }
+
+#screenreg final.pool
 ```
@@
 
-cross.val.sf12.model <- train(as.formula(raw_model_formula_string), data = raw.data,
+cross.val.sf12.model <- train(as.formula(mice_formula_string), data = complete(mice_set.subset, 1, include=F),
                method = "lm",
@@
 
+# come back to this. 
+#with(mice_set.subset,  train(as.formula(mice_formula_string),
+#               method = "lm",
+#               trControl = trControl))
+
 # printing model performance metrics
 # along with other details
-print(cross.val.sf12.model)
+#print(summary(cross.val.sf12.model))
 
@@
 
+```{r cross_val_handovers}
+# boxplots for handovers
+#.estimating from 2014-2020.
+# get data for 2013- 2020
+# run 2013 pop through transition probability model a few times. 
+# profit. 
+# run it through model a few times
+# compare with real data in boxplots and ridgelines.
+
+crossval.mice.data <- complete(mice_set.full, 1, include = F)
+crossval.mice.data <- replace.missing(crossval.mice.data)
+crossval.mice.data <- drop_na(crossval.mice.data)
+```
+
+```{r mice_handovers}
+start.data <- crossval.mice.data[which(crossval.mice.data$time==2013),]
+rolling.data <- start.data[, c("pidp", "SF_12", "time")]
+handover.data <- rolling.data
+for (i in 1:7){
+  rolling.data$SF_12 <- predict(pooled_lm, start.data)
+  start.data$SF_12 <- rolling.data$SF_12
+  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
+  handover.data <- rbind(handover.data, rolling.data)
+}
+
+handover_boxplots(crossval.mice.data, handover.data, "SF_12", save.path, "mice_SF12_boxplots")
+density_ridges(crossval.mice.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "mice_raw_ridges")
+density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "mice_handover_ridges")
+
+```
+
+```{r cross_val_handovers}
+start.data <- crossval.mice.data[which(crossval.mice.data$time==2013),]
+rolling.data <- start.data[, c("pidp", "SF_12", "time")]
+handover.data <- rolling.data
+
+for (i in 1:7){
+  rolling.data$SF_12 <- predict(cross.val.sf12.model, start.data)
+  start.data$SF_12 <- rolling.data$SF_12
+  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
+  handover.data <- rbind(handover.data, rolling.data)
+}
+
+handover_boxplots(crossval.mice.data, handover.data, "SF_12", save.path, "crossval_SF12_boxplot")
+density_ridges(crossval.mice.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_raw_ridges")
+density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_handover_ridges")
+
+```
+
+### LASSO and variable selection.
+
 ```{r lasso}
 # just import from old paper
-lasso.data <- tidyr::drop_na(final.data)
-X <- model.matrix(as.formula(model_formula_string), data=lasso.data)
+lasso.data <- tidyr::drop_na(complete(mice_set.subset))
+X <- model.matrix(as.formula(mice_formula_string), data=lasso.data)
 y <- lasso.data$SF_12
@@
        booktabs=T, # nice hlines. (recommended)
-       tabular=T,# tabular env.
+       tabular=T,# tabulr env.
        single.row = T, # nicer one row formatting.
@@
 
-```{r projection of weights}
-# weighted ols
-model_formula_string <- "SF_12 ~ factor(sex) +  relevel(factor(ethnicity), ref='WBI') + scale(age) + factor(education_state) + factor(S7_labour_state) + relevel(factor(job_sec), ref=1) + relevel(factor(region), ref='London') + scale(hh_income)"
-sf12.lm.weighted <- lm(model_formula_string, weights = weight, data = mice.data)
+```{r weighted_ols}
+# weighted ols using mice data.
+sf12.lm.weighted <- with(mice_set.subset, lm(as.formula(mice_formula_string), weights = weight))
+summary(sf12.lm.weighted)
+
+#coefficients go here.
+texreg_file <- paste0(save.path, 'SF12_Lasso_coefficients.txt')
+tex_label <- paste0("table: sf12_lasso_coefficients") 
+tex_headers <- c(texreg::names2latex("SF_12 LASSO"))
+tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "lasso"))    
+lassoTexReg <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso_coefs[,1], se=lasso_coefs[,2])
+#lassoTexReg2 <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso_coefs[,2])#, lasso_coefs[, 2]))#, pvalues=lasso_coefs[,2])
+#matrixLassoTexReg <- matrixreg(list(lassoTexReg, lassoTexReg2))
+
+texreg(lassoTexReg, # what model to save coefs for. 
+       file=texreg_file,  # where to save.
+       custom.model.names = tex_headers, # title of table.
+       caption=tex_caption, # \caption command option. 
+       label = tex_label, # \label command option. 
+       dcolumn=T,# nice column alignment. 
+       booktabs=T, # nice hlines. (recommended)
+       tabular=T,# tabulr env.
+       single.row = T, # nicer one row formatting.
+       longtable=T, # allows tables to wrap over pages
+       use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
+       fontsize='small') # small font
+
+```
+
+```{r projected_data}
+
+##REDO THIS
+## GET MICE DATA 2011-2013. UPDATE WEIGHTS
+
+# GET MICE DAT 2016-2018
+
+# FIT TWO REGRESSIONS AND COMPARE. PARTICULARLY ASE DIFFERENCES.
 
@@
 # data at data/extrapolated_weights...
-```
 
-```{r projected_data}
+# creating 2016_data
+mice_set.subset.2016_2018 <- mice.long[which(mice.long$time %in% c(2016, 2017, 2018)), ]
+mice_set.subset.2016_2018$pidp <- mice.2018.pidp
+mice_set.subset.2016_2018$weight <- mice.2018.weights
+mice_set.subset.2016_2018$time <- mice.2018.time
+mice_set.subset.2016_2018 <- as.mids(mice_set.subset.2016_2018)
 
-dataDir <- "data/composite_US/"
-filelist <- list.files(dataDir,
-                       include.dirs = FALSE,
-                       full.names = TRUE,
-                       pattern = '[0-9]{4}_US_cohort.csv')[8:10] # get files for 2016-2018.
-new.raw.data <- do.call(rbind, lapply(filelist, read.csv))
-
-model_formula <- as.formula(model_formula_string)
-variables <- all.vars(model_formula)
-variables[1] <- "SF_12"
-
-new.raw.data <- new.raw.data[, append(variables, c("time", 'pidp', 'weight'))]
-
-new.raw.data <- new.raw.data %>%
-        group_by(pidp) %>%
-        #mutate(diff = .data[[dependent]] - lag(.data[[dependent]], order_by = time)) %>%
-        mutate(last = lag(.data[["SF_12"]], order_by = time)) %>%
-        rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff
-
-new.raw.data <- replace.missing(new.raw.data)
-new.raw.data <- drop_na(new.raw.data)
-
-dataDir <- "data"
-filelist <- list.files(dataDir,
+# getting updated weights for 2011-2013 data in 2018.
+extrapolated_weights.filelist <- list.files("data/",
                        include.dirs = FALSE,
@@
 
-extrapolated.raw.data <- do.call(rbind, lapply(filelist, read.csv))
-extrapolated.raw.data <- extrapolated.raw.data[, append(variables, c("time", 'pidp', 'weight', 'plus_5_weight'))]
-extrapolated.raw.data <- extrapolated.raw.data %>%
-        group_by(pidp) %>%
-        #mutate(diff = .data[[dependent]] - lag(.data[[dependent]], order_by = time)) %>%
-        mutate(last = lag(.data[["SF_12"]], order_by = time)) %>%
-        rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff
-extrapolated.raw.data <- replace.missing(extrapolated.raw.data)
-extrapolated.raw.data <- drop_na(extrapolated.raw.data)
+iextrapolated.weights.data <- do.call(rbind, lapply(extrapolated_weights.filelist, read.csv))
+extrapolated.weights.data <- replace.missing(extrapolated.weights.data)
+extrapolated.weights <- extrapolated.weights.data[, c("plus_5_weight")]
+
+# adding updated weights to MICE set. 
+mice_set.subset.2011_2013.updated_weights <- mice.long[which(mice.long$time %in% c(2011, 2012, 2013)), ]
+mice_set.subset.2011_2013.updated_weights$pidp <- mice.pidp
+mice_set.subset.2011_2013.updated_weights$weight <- extrapolated.weights
+mice_set.subset.2011_2013.updated_weights$time <- mice.time
+mice_set.subset.2011_2013.updated_weights <- as.mids(mice_set.subset.2011_2013.updated_weights)
+
 ```
@@
 # weighted regression for 2016-2018 using 2011-2013 models and projected weights
-sf12.lm.weighted.2013 <- lm(model_formula_string, weights = plus_5_weight, data = extrapolated.raw.data)
+sf12.lm.weighted.2013 <- pool(with(mice_set.subset.2011_2013.updated_weights, lm(as.formula(mice_formula_string), weights = weight)))
 
 #  weighted regression for 2016-2018 using 2018 data.
-sf12.lm.weighted.2018 <- lm(model_formula_string, weights = weight, data = new.raw.data)
+sf12.lm.weighted.2018 <- pool(with(mice_set.subset.2016_2018, lm(as.formula(mice_formula_string), weights = weight)))
 
@@
 tex_headers <- c(texreg::names2latex("SF_12 2018 With 2013 Extrapolated Weights"), texreg::names2latex("SF_12 2018 With Weights"))
-tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "ols"))    
+tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "projectied_ols"))    
 texreg(list(sf12.lm.weighted.2013,sf12.lm.weighted.2018), # what model to save coefs for. 
@@
        use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
-       fontsize='small') # small font
-```
-
-```{r handover_data}
-# boxplots for handovers
-#.estimating from 2014-2020.
-# get data for 2013- 2020
-# run 2013 pop through transition probability model a few times. 
-# profit. 
-# run it through model a few times
-# compare with real data in boxplots and ridgelines.
-
-dataDir <- "data/raw_US/"
-filelist <- list.files(dataDir,
-                       include.dirs = FALSE,
-                       full.names = TRUE,
-                       pattern = '[0-9]{4}_US_cohort.csv')[23:30] # get files for 2011-2013.
-crossval.raw.data <- do.call(rbind, lapply(filelist, read.csv))
-crossval.raw.data <- replace.missing(crossval.raw.data)
-crossval.raw.data <- crossval.raw.data[, c('pidp', 'time', all.vars(as.formula(raw_model_formula_string)))]
-crossval.raw.data <- drop_na(crossval.raw.data)
-```
-
-```{r ols_handovers}
-start.data <- crossval.raw.data[which(crossval.raw.data$time==2013),]
-handover.data <- start.data
-for (i in 1:7){
-  start.data$SF_12 <- predict(sf12.lm, start.data)
-  start.data[, 'time'] <- start.data[, 'time'] +1
-  handover.data <- rbind(handover.data, start.data[, c("pidp", "SF_12", "time")])
-}
-
-handover_boxplots(crossval.raw.data, handover.data, "SF_12", paste0(save.path, "ols_SF12_boxplot"))
-density_ridges(crossval.raw.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "raw_ridges")
-density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "handover_ridges")
-
-```
-
-```{r mice_handovers}
-start.data <- mice.data[which(mice.data$time==2013),]
-rolling.data <- start.data[, c("pidp", "SF_12", "time")]
-handover.data <- rolling.data
-for (i in 1:6){
-  rolling.data$SF_12 <- predict(pooled_lm, start.data)
-  start.data$SF_12 <- rolling.data$SF_12
-  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
-  handover.data <- rbind(handover.data, rolling.data)
-}
-
-handover_boxplots(crossval.glmm.data, handover.data, "SF_12", paste0(save.path, "mice_SF12_boxplot"))
-density_ridges(crossval.glmm.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "mice_raw_ridges")
-density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "mice_handover_ridges")
-
-```
-
-```{r cross_val_handovers}
-start.data <- crossval.raw.data[which(crossval.raw.data$time==2013),]
-rolling.data <- start.data[, c("pidp", "SF_12", "time")]
-handover.data <- rolling.data
-for (i in 1:7){
-  rolling.data$SF_12 <- predict(cross.val.sf12.model, start.data)
-  start.data$SF_12 <- rolling.data$SF_12
-  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
-  handover.data <- rbind(handover.data, rolling.data)
-}
-
-handover_boxplots(crossval.raw.data, handover.data, "SF_12", paste0(save.path, "crossval_ols_SF12_boxplot"))
-density_ridges(crossval.raw.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_raw_ridges")
-density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_handover_ridges")
-
+       fontsize='tiny') # small font
 ```
@@
 
-```{r prep}
-
-mice.data <- mice.data %>%
-            group_by(pidp) %>%
-            #mutate(diff = .data[[dependent]] - lag(.data[[dependent]], order_by = time)) %>%
-            mutate(last = lag(.data[["SF_12"]], order_by = time)) %>%
-            rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff
-
-```
-
 ```{r "glmm"}
 
-glmm.data <- mice.data
 # yoink transition model function pre processing
@@
 depend <- "SF_12"
-dependent_data <- glmm.data$SF_12
+dependent_data <- complete(mice_set.subset)$SF_12
 
-glmm_model_formula_string <- "SF_12 ~ I(scale(SF_12_last**2)) + scale(SF_12_last) + factor(sex) +factor(ethnicity) + scale(age) + I(scale(age)**2) + factor(education_state) + factor(S7_labour_state) + factor(job_sec) + factor(region) + scale(hh_income) + I(scale(hh_income)**2) + factor(time) + (1|pidp)"
+glmm.mice.long.subset <- complete(mice_set.subset, "long", include=T)
 
 if (reflect) {
-    max_value <- nanmax(glmm.data[[depend]])
-    glmm.data[, c(depend)] <- max_value - glmm.data[, c(depend)] 
+    max_value <- nanmax(mice.data[[depend]])
+    glmm.mice.long.subset[, c(depend)] <- max_value - glmm.mice.long.subset[, c(depend)] 
   }
@@
 {
-  yj <- yeojohnson(glmm.data[["SF_12"]])
-  glmm.data[["SF_12"]] <- predict(yj)
+  yj <- yeojohnson(glmm.mice.long.subset[["SF_12"]])
+  glmm.mice.long.subset[["SF_12"]] <- predict(yj)
 }
 
-min_value <- nanmin(glmm.data[[depend]])
-glmm.data[[depend]] <- glmm.data[[depend]] - min_value + 0.001
+min_value <- nanmin(glmm.mice.long.subset [[depend]])
+glmm.mice.long.subset[[depend]] <- glmm.mice.long.subset[[depend]] - min_value + 0.001
 
-sf12.glmm.model <- glmer(glmm_model_formula_string,  
+glmm.mice.long.subset <- glmm.mice.long.subset %>%
+            group_by(pidp) %>%
+            #mutate(diff = .data[[dependent]] - lag(.data[[dependent]], order_by = time)) %>%
+            mutate(last = lag(.data[["SF_12"]], order_by = time)) %>%
+            rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff
+glmm.mice.set <- as.mids(glmm.mice.long.subset)
+
+glmm_model_formula_string <- "SF_12 ~ SF_12_last +
+                  factor(sex) + 
+                  relevel(factor(ethnicity), ref='WBI') + 
+                  scale(age) + 
+                  factor(education_state) + 
+                  factor(S7_labour_state) + 
+                  relevel(factor(job_sec), ref=1) +
+                  relevel(factor(region), ref='London') +
+                  scale(hh_income) + 
+                  scale(I(hh_income**2)) +
+                  factor(housing_quality) +
+                  factor(neighbourhood_safety) +
+                  factor(loneliness) + 
+                  nutrition_quality + 
+                  ncigs + 
+                  (1|pidp)"
+
+sf12.glmm.model <- with(glmm.mice.set, glmer(glmm_model_formula_string,  
                nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes forever..
                family=Gamma(link='log'), # gamma family with log link.
-               weights=weight, 
-               data = glmm.data)
+               weights=weight))
 
-save(sf12.glmm.model, file = paste0(save.path,"sf12_glmm.RData"))
+sf12.glmm.pool <- pool(sf12.glmm.model)
+
+# mice objects dont go in forest plot annoyingly. move coefficients over to a
+# dummy lm that sjPlot::plot_models can read.
+mice.glmm.object <- sf12.glmm.model$analyses[[1]]
+mice.glmm.object@beta <- sf12.glmm.pool$pooled$estimate
+#attr(mice.glmm.object, "beta") <- sf12.glmm.pool$estimate
+#mice.glmm.object@ <- sf12.glmm.pool$std.error
+#mice.glmm.object$coefficients[,3] <- sf12.glmm.pool$statistic
+#mice.glmm.object$coefficients[,4] <- sf12.glmm.pool$p.value
+
+print(r2_nakagawa(sf12.glmm.model$analyses[[1]]))
+
+#save(sf12.glmm.model, file = paste0(save.path,"sf12_glmm.RData"))
 
@@
   tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "glmm"))    
-  texreg(sf12.glmm.model, # what model to save coefs for. 
+  texreg(sf12.glmm.pool, # what model to save coefs for. 
          file=texreg_file,  # where to save.
@@
 
-glmm.fitted <- (max_value - predict(yj, predict(sf12.glmm.model, type='response') + min_value + rnorm(nrow(glmm.data), 0,0.75), inverse=T))#
-glmm.resid <- (dependent_data - glmm.fitted)/sqrt(glmm.fitted)
-qq_plot(glmm.resid, paste0(save.path, "glmm_qq.pdf"))
-residual_density_plot(res=glmm.resid , file_name=paste0(save.path, "glmm_residual_density.pdf"), guide="normal")
+# + rnorm(nrow(complete(glmm.mice.set ,1)), 0,0.75)
+glmm.fitted <- (max_value - predict(yj, predict(mice.glmm.object, type='response') + min_value +rnorm(predict(mice.glmm.object, type='response'),0,0.2), inverse=T))#
+#glmm.fitted <- (max_value - predict(mice.glmm.object, type='response') + min_value + rnorm(nrow(glmm.mice.long.subset), 0, 1))
+glmm.fitted <- trunc(glmm.fitted, 0 , 100)
+qq_plot(residuals(mice.glmm.object, type='pearson'), paste0(save.path, "glmm_qq.pdf"))
+residual_density_plot(res=residuals(mice.glmm.object) , file_name=paste0(save.path, "glmm_residual_density.pdf"), guide="normal")
 
-squareRootRes <- sqrt(residuals(sf12.glmm.model, type='pearson'))
+squareRootRes <- sqrt(residuals(mice.glmm.object, type='pearson'))
 fitted_residuals <- as.data.frame(cbind(glmm.fitted, squareRootRes))
@@
 
-forest_plot_glmm(sf12.glmm.model, paste0(save.path, "glmm_forest.pdf"))
+#mice.glmm.object@beta <- mice.glmm.object@beta
+
+mice.glmm.object@beta <- -mice.glmm.object@beta 
+gamma_forest_plot(mice.glmm.object, paste0(save.path, "glmm_forest.pdf"))
+mice.glmm.object@beta <- -mice.glmm.object@beta
+
 ```
@@
 ```{r glmm_handover_data}
-# boxplots for handovers
-#.estimating from 2014-2020.
-# get data for 2013- 2020
-# run 2013 pop through transition probability model a few times. 
-# profit. 
-# run it through model a few times
-# compare with real data in boxplots and ridgelines.
-
-dataDir <- "data/composite_US"
-filelist <- list.files(dataDir,
-                       include.dirs = FALSE,
-                       full.names = TRUE,
-                       pattern = '[0-9]{4}_US_cohort.csv')[5:12] # get files for 2011-2013.
-crossval.glmm.data <- do.call(rbind, lapply(filelist, read.csv))
-crossval.glmm.data <- replace.missing(crossval.glmm.data)
-crossval.glmm.data <- crossval.glmm.data[, c('pidp', 'time', "SF_12")]
+# load raw composite data for glmm handovers.
+crossval.glmm.data <- replace.missing(complete(mice_set.full, 1)[, append(variables, c("time", 'pidp', 'weight'))])
+crossval.glmm.data <- crossval.glmm.data[which(crossval.glmm.data$time>=2013),]
 crossval.glmm.data <- drop_na(crossval.glmm.data)
@@
 
-start.data <- mice.data[which(mice.data$time==2013),]
+start.data <- complete(glmm.mice.set, 1)
+start.data <- start.data[which(start.data$time==2013),]
+start.data$SF_12 <- crossval.glmm.data[which(crossval.glmm.data$time==2013),]$SF_12
 start.data <- drop_na(start.data)
 
-rolling.data <- start.data[, c("pidp", "SF_12", "time")]
-handover.data <- rolling.data
+handover.data <- start.data
+
+rolling.data <- start.data
 for (i in 1:7){
-  rolling.data$SF_12 <- predict(sf12.glmm.model, start.data, type='response')
-  rolling.data$SF_12 <- max_value - predict(yj, rolling.data$SF_12+min_value + rnorm(nrow(start.data),0,0.5), inverse=T)
-  start.data$SF_12 <- rolling.data$SF_12
+  rolling.data$SF_12 <- max_value - predict(yj,  predict(mice.glmm.object, start.data, type='response',allow.new.levels=T) + rnorm(nrow(rolling.data),0,0.25)+min_value, inverse=T)
+  #rolling.data$SF_12 <- max_value - rolling.data$SF_12
+  rolling.data$SF_12 <- trunc(rolling.data$SF_12, 0 , 100)
+  rolling.data$SF_12_last <- rolling.data$SF_12
   rolling.data[, 'time'] <- rolling.data[, 'time'] +1
@@
 
-handover_boxplots(crossval.glmm.data, handover.data, "SF_12", paste0(save.path, "glmm_SF12_boxplot"))
+handover_boxplots(crossval.glmm.data, handover.data, "SF_12", save.path, "glmm_SF12_boxplot")
 density_ridges(crossval.glmm.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "glmm_raw_ridges")

### 2023-11-29 minos/transitions/paper_1_notebook.Rmd
making sure reuslts in notebook look good

---
title: "Paper 1 Notebook"
output: html_notebook
---

```{r "preamble"}
source("minos/transitions/utils.R")
source("minos/transitions/transition_model_functions.R")
library(dplyr)
```

```{r "OLS"}

model_formula_string <- "SF_12 ~ factor(sex) + 
                  relevel(factor(data$ethnicity), ref='WBI') + 
                  scale(age) + 
                  factor(education_state) + 
                  factor(labour_state_raw) + 
                  relevel(factor(data$job_sec), ref=1) +
                  relevel(factor(data$region), ref='London') +
                  scale(hh_netinc)"
model_formula <- as.formula(model_formula_string)

dataDir <- "data/raw_US/"
filelist <- list.files(dataDir,
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = '[0-9]{4}_US_cohort.csv')[21:23] # get files for 2011-2013.
raw.data <- do.call(rbind, lapply(filelist, read.csv))

raw.data <- raw.data[, append(all.vars(model_formula), c("time", 'pidp', 'weight'))]

raw.data <- raw.data %>%
        group_by(pidp) %>%
        #mutate(diff = .data[[dependent]] - lag(.data[[dependent]], order_by = time)) %>%
        mutate(last = lag(.data[["SF_12"]], order_by = time)) %>%
        rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff

```

### 2023-11-29 minos/transitions/paper1_utils.R

@@ -1,0 +1,11 @@
+
+format_SF12_data <- function(file_path, years) {
+  
+  # load files in for years and take required subset from formula string.
+  
+  # calculate sf12 lag using dplyr
+  
+  # return data
+  
+}
+  

### 2023-11-29 minos/transitions/paper_1_plots.R

@@ -1,0 +1,254 @@
+library(ggplot2)
+
+
+# forest plot for lm models. 
+forest_plot_lm <- function(model, file_name){
+  
+  sf12_coefs <- summary(model)$coefficients
+  sf12_coefs <- cbind(sf12_coefs, sf12_coefs[, 4])
+  colnames(sf12_coefs)[5] <- "p.stars"
+  what_ns <- which(sf12_coefs[, "Pr(>|t|)"] > 0.05)
+  what_one_star <- which(sf12_coefs[, "Pr(>|t|)"] <= 0.05)
+  what_two_star <- which(sf12_coefs[, "Pr(>|t|)"] <= 0.01)
+  what_three_star <- which(sf12_coefs[, "Pr(>|t|)"] <= 0.001)
+  
+  sf12_coefs[what_ns, 'p.stars'] <- ""
+  sf12_coefs[what_one_star, 'p.stars'] <- "*"
+  sf12_coefs[what_two_star, 'p.stars'] <- "**"
+  sf12_coefs[what_three_star, 'p.stars'] <- "***"
+  p.stars<- sf12_coefs[, 5]
+  
+  pdf(file_name)
+  p <- plot_model(model, transform=NULL,
+                  title = "") + aes(shape=p.stars)
+  p$data$p.stars[which(p$data$p.stars == "")] <- 'n.s.'
+  p <- p +  scale_shape_manual(name='Significance Level',
+                               limits=c("n.s.", "*", "**", "***"),
+                               breaks=c("n.s.", "*", "**", "***"),
+                               values=c(1, 16, 17, 15)) # cast legend to certain title, variable names and shapes.
+  plot(p)
+  dev.off()
+}
+
+
+
+# for glmm gamma
+forest_plot <- function(model, file_name){
+  pdf(file_name)
+  p <- plot_model(model,
+                  title = "") + aes(shape=p.stars)
+  p$data$p.stars[p$data$p.stars == ""] <- "n.s." # force empty shape strings to n.s. so they show up in legend.
+  p <- p +  scale_shape_manual(name='Significance Level',
+                               breaks=c('n.s.', "*", "**", "***"),
+                               values=c(1, 16, 17, 15)) # cast legend to certain title, variable names and shapes.
+  plot(p)
+  dev.off()
+}
+
+# for glmm gamma
+gamma_forest_plot <- function(model, file_name){
+  pdf(file_name)
+  p <- plot_model(model, transform=NULL, 
+                  title = "") + aes(shape=p.stars)
[…]

### 2023-11-29 minos/transitions/energy_price_forecasting.Rmd
adding energy forecasting notebook

---
title: "Energy Price Forecasting."
output: 'html_document'
---

This is an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*.

```{r}
# package preamble.
library(forecast)
library(ggfortify)
library(readxl)
library(tidyr)
source("minos/transitions/utils.R")
```

```{r}

process_input_data <- function(dataset, data.column, new.name){

  subvector <- dataset[, c(data.column)]
  subvector <- drop_na(subvector)
  colnames(subvector) <- c(new.name)
  return(subvector)
}

#energy_data <- readxl::read_xlsx("../data/energy_prices_simpler.xlsx")
## primary energy material sources. fuel and motor oil omitted due to no UKHLS data. 
#electricity_vector <- process_input_data(energy_data, "Real terms price indices: Electricity [Note 3]", 'electricity')
#gas_vector <- process_input_data(energy_data, "Real terms price indices: Gas [Note 3]", "gas")
#solid_fuel_vector <- process_input_data(energy_data, "Real terms price indices: Solid fuels [Note 3]", "solid_fuel")
#liquid_fuel_vector <- process_input_data(energy_data, "Real terms price indices: Liquid fuels [Note 3]", "liquid_fuel")

energy_data <- readxl::read_xlsx("../data/energy_prices_simpler_yearly.xlsx")
# primary energy material sources. fuel and motor oil omitted due to no UKHLS data. 
electricity_vector <- process_input_data(energy_data, "Real price indices: Electricity [Note 3]", 'electricity')
gas_vector <- process_input_data(energy_data, "Real price indices: Gas [Note 3]", "gas")
solid_fuel_vector <- process_input_data(energy_data, "Real price indices: Solid fuels [Note 3]", "solid_fuel")
liquid_fuel_vector <- process_input_data(energy_data, "Real price indices: Liquid fuels [Note 3]", "liquid_fuel")
# aggregate of the above 4. 
#domestic_fuel_vector <- process_input_data(energy_data, "Real terms price indices: Domestic fuels\r\n[Note 1, 3]", "domestic_fuel")

plot(electricity_vector$electricity, type='l', xlab="Quarter (0 = Q1 1990", ylab=c("Real Electricity Price indices"), main="Electricity")
plot(gas_vector$gas, type='l', xlab="Quarter (0 = Q1 1990", ylab=c("Real Gas Price indices"), main="Gas")
plot(solid_fuel_vector$solid_fuel, type='l', xlab="Quarter (0 = Q1 1990", ylab=c("Real Solid Fuel Price indices"), main="Solid Fuel (Coal)")
plot(liquid_fuel_vector$liquid_fuel, type='l', xlab="Quarter (0 = Q1 1990", ylab=c("Real Liquid Fuel Price indices"), main="Liquid Fuel (Petroleum, Diesel, LPG, Heating Oil)")
#plot(domestic_fuel_vector$domestic_fuel, type='l', xlab="Quarter (0 = Q1 1990", ylab=c("Real Demostrict Fuel Price indices"), main="Domestic Fuel #(Heating Oil)")
```

```{r}
electric.series <- electricity_vector$electricity #+ rnorm(length(electric.series))

# ACF, difference 1 ACF and PACF suggests AR(2)  difference 1 and MA(4) structure (2, 1, 4) in ARIMA.
acf(electric.series)
acf(diff(electric.series))
pacf(electric.series)

#arima.electric 
#m1 <- auto.arima(electric.series)
m1 <- arima(electric.series, order=c(5, 0, 1))
print(m1)
#Box.test(residuals(m1), type="Ljung-Box")
plot(residuals(m1))

autoplot(forecast(m1, 40))
checkresiduals(m1)
print(m1$aic)
# residuals appear to be in nominal range. large LB p-value also support no autocorrelation between residuals. 
```

```{r}
gas.series <- gas_vector$gas

# ACF, difference 1 ACF and PACF suggests AR(2)  difference 1 and MA(4) structure (2, 1, 4) in ARIMA.
acf(gas.series)
acf(diff(gas.series))
pacf(gas.series)

#arima.electric 
m2 <- arima(gas.series, order=c(4, 0 ,1))

#Box.test(residuals(m1), type="Ljung-Box")
plot(residuals(m2))

autoplot(forecast(m2, 15))
checkresiduals(m2)
print(m2$aic)
# residuals appear to be in nominal range. large LB p-value also support no autocorrelation between residuals. 
```

```{r}
solid.series <- solid_fuel_vector$solid_fuel

# ACF, difference 1 ACF and PACF suggests AR(2)  difference 1 and MA(4) structure (2, 1, 4) in ARIMA.
acf(solid.series)
acf(diff(solid.series))
pacf(solid.series)

#arima.electric 
m3 <- arima(solid.series, order=c(5, 0 ,1))

#Box.test(residuals(m1), type="Ljung-Box")
plot(residuals(m3))

autoplot(forecast(m3, 15))
checkresiduals(m3)
print(m3$aic)
# residuals appear to be in nominal range. large LB p-value also support no autocorrelation between residuals. 
```

```{r}
liquid.series <- liquid_fuel_vector$liquid_fuel

# ACF, difference 1 ACF and PACF suggests AR(2)  difference 1 and MA(4) structure (2, 1, 4) in ARIMA.
acf(liquid.series)
acf(diff(liquid.series))
pacf(liquid.series)

#arima.electric 
m4 <- arima(gas.series, order=c(5, 0 ,1))

#Box.test(residuals(m1), type="Ljung-Box")
plot(residuals(m4))

autoplot(forecast(m4,15))
checkresiduals(m4)
print(m4$aic)
# residuals appear to be in nominal range. large LB p-value also support no autocorrelation between residuals. 
```

```{r}
# saving data to R objects for use in MINOS
create.if.not.exists("data/transitions/energy_prices/")
write.csv(electric.series, "data/transitions/energy_prices/solid_historic.csv")
write.csv(gas.series, "data/transitions/energy_prices/gas_historic.csv")
write.csv(solid.series, "data/transitions/energy_prices/solid_historic.csv")
write.csv(liquid.series, "data/transitions/energy_prices/liquid_historic.csv")

write.csv(forecast(m1, 15), "data/transitions/energy_prices/electric_arima.csv")
write.csv(forecast(m2, 15), "data/transitions/energy_prices/gas_arima.csv")
write.csv(forecast(m3, 15), "data/transitions/energy_prices/solid_arima.csv")
write.csv(forecast(m4, 15), "data/transitions/energy_prices/liquid_arima.csv")
```

### 2023-11-30 minos/outcomes/paper_1_notebook.Rmd
slight adjustments to mice in plots

@@
 } else {
-  n_iter <- 30
-  max_iter <- 10
+  n_iter <- 20
+  max_iter <- 5
   # future mice is parallelised version of MICE.
@@
                    m = n_iter, maxit = max_iter,
-                   remove.collinear=F)
+                   remove.collinear=T)
   saveRDS(mice_set, "data/transitions/MICE_set.rds")
@@
 forest_plot(mice.lm.object, paste0(save.path,'mice_SF12_forest.pdf'))
+qq_plot(resid(mice.lm.object), paste0(save.path, "mice_qq.pdf"))
 

### 2023-11-30 minos/transitions/paper_1_plots.R

@@ -1,6 +1,9 @@
 library(ggplot2)
 
 
+miss.values <- c(-10, -9, -8, -7, -3, -2, -1,
+                 -10., -9., -8., -7., -3., -2., -1.)
+
 # forest plot for lm models. 
 forest_plot_lm <- function(model, file_name){
   

### 2023-11-30 minos/validation/handovers.Rmd

@@
 
+## Child Ages
+
 ```{r}
+base.child.ages <- base.dat %>%
+  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
+  filter(time > 2009) %>%
+  group_by(time, hidp) %>%
+  summarise(child_ages = find_mode(child_ages))
+
+s<- strsplit(base.child.ages$child_ages, "_")
+
+base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(s, length)), expanded_child_ages = unlist(s))
+base.child.ages.expanded <- base.child.ages.expanded %>%
+  group_by(time, expanded_child_ages) %>%
+  summarise(age_counts = n())
+
+ggplot(data = base.child.ages.expanded, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
+  geom_line() +
+  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
+  scale_colour_viridis_d() +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = base.child.ages.expanded, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
+  geom_line() +
+  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
+  scale_colour_viridis_d() +
+  xlab('Year') +
+  ylab('Count')
+
+base.child.ages.nkids <- base.dat %>%
+  group_by(time, hidp) %>%
+  summarise(nkids_counts = mean(nkids)) %>%
+  group_by(time) %>%
+  summarise(nkids_by_year = sum(nkids_counts))
+
+ggplot(data = base.child.ages.nkids, mapping = aes(x = time, y = nkids_by_year)) +
+  geom_line() +
+  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
 

### 2023-11-30 minos/outcomes/paper_1_notebook.Rmd
updating future mice to full params

@@
 
-mice.data$ethnicity <- factor(mice.data$ethnicity)
-mice.data$S7_labour_state <- factor(mice.data$S7_labour_state)
-mice.data$region <- factor(mice.data$region)
-
 aggr_columns <- c("SF_12",
@@
 
+mice_columns <- c("age", 
+                  "region", 
+                  #"heating", 
+                  "job_sec", 
+                  "ncigs",
+                  "education_state",            
+                  "ethnicity",
+                  "loneliness",
+                  "sex", 
+                  "SF_12",
+                  #"SF_12p",
+                  "smoker",
+                  "nkids",       
+                  "behind_on_bills",
+                  "financial_situation",
+                  "future_financial_situation",
+                  "likely_move",
+                  "ghq_depression",
+                  "ghq_happiness",
+                  "clinical_depression", 
+                  "scsf1",
+                  "health_limits_social",
+                  #"hhsize",
+                  #"housing_tenure",
+                  #"urban", 
+                  "housing_quality",
+                  "hh_income",
+                  "neighbourhood_safety",
+                  "S7_labour_state",
+                  #"yearly_energy",
+                  "nutrition_quality"
+                  #"hh_comp", 
+                  #"marital_status"
+)
+
+mice.data$ethnicity <- factor(mice.data$ethnicity)
+mice.data$S7_labour_state <- factor(mice.data$S7_labour_state)
+mice.data$region <- factor(mice.data$region)
+mice.data$heating <- factor(mice.data$heating)
+mice.data$job_sec <- factor(mice.data$job_sec)
+mice.data$education_state <- factor(mice.data$education_state)
+mice.data$sex <- factor(mice.data$sex)
+mice.data$smoker <- factor(mice.data$smoker)
+mice.data$behind_on_bills <- factor(mice.data$behind_on_bills)
+mice.data$ghq_depression <- factor(mice.data$ghq_depression)
+mice.data$ghq_happiness <- factor(mice.data$ghq_happiness)
+mice.data$clinical_depression <- factor(mice.data$clinical_depression)
+mice.data$scsf1 <- factor(mice.data$scsf1)
+mice.data$health_limits_social <- factor(mice.data$ghq_depression)
+mice.data$housing_tenure <- factor(mice.data$housing_tenure)
+mice.data$urban <- factor(mice.data$urban)
+mice.data$marital_status <- factor(mice.data$marital_status)
+
 load_cache <- F
@@
 } else {
-  n_iter <- 20
-  max_iter <- 5
+  n_iter <- 30
+  max_iter <- 10
+  ignore_cols = c("birth_year")
   # future mice is parallelised version of MICE.
-  mice_set <- futuremice(data = mice.data, #method=method,
-                   #m = 10, maxit = 30,
-                   m = n_iter, maxit = max_iter,
-                   remove.collinear=T)
+  #mice_set <- mice(data = mice.data[, mice_columns], #method=method,
+  #                 m = n_iter, maxit = max_iter,
+  #                 remove.collinear=T)
+
+  mice_set <- futuremice(data = mice.data[, imp_columns], #method=method,
+                   m = n_iter, minit = max_iter,
+                   remove.collinear=T, progressor = progressor)
   saveRDS(mice_set, "data/transitions/MICE_set.rds")

### 2023-12-01 minos/outcomes/paper_1_notebook.Rmd
adding progress bar to MICE

@@
 
-  mice_set <- futuremice(data = mice.data[, imp_columns], #method=method,
-                   m = n_iter, minit = max_iter,
-                   remove.collinear=T, progressor = progressor)
+  mice_set <- with_progress(futuremice(data = mice.data[, mice_columns], #method=method,
+                   m = n_iter, maxit = max_iter,
+                   remove.collinear=T, 
+                   progressor = progressr::handlers("progress")))
   saveRDS(mice_set, "data/transitions/MICE_set.rds")

### 2023-12-01 minos/outcomes/paper_1_notebook.Rmd
trying to run big MICE script on arc4 as its crashing my PC

--- 2023-11-30 minos/outcomes/paper_1_notebook.Rmd
@@
 
+mice_columns <- c("age", 
+                  "region", 
+                  #"heating", 
+                  "job_sec", 
+                  "ncigs",
+                  "education_state",            
+                  "ethnicity",
+                  "loneliness",
+                  "sex", 
+                  "SF_12",
+                  #"SF_12p",
+                  #"smoker",
+                  "nkids",       
+                  "behind_on_bills",
+                  "financial_situation",
+                  "future_financial_situation",
+                  "likely_move",
+                  "ghq_depression",
+                  "ghq_happiness",
+                  "clinical_depression", 
+                  "scsf1",
+                  "health_limits_social",
+                  #"hhsize",
+                  #"housing_tenure",
+                  #"urban", 
+                  "housing_quality",
+                  "hh_income",
+                  "neighbourhood_safety",
+                  "S7_labour_state",
+                  #"yearly_energy",
+                  "nutrition_quality"
+                  #"hh_comp", 
+                  #"marital_status"
+)
+
+mice.data$ethnicity <- factor(mice.data$ethnicity)
+mice.data$S7_labour_state <- factor(mice.data$S7_labour_state)
+mice.data$region <- factor(mice.data$region)
+mice.data$heating <- factor(mice.data$heating)
+mice.data$job_sec <- factor(mice.data$job_sec)
+mice.data$education_state <- factor(mice.data$education_state)
+mice.data$sex <- factor(mice.data$sex)
+#mice.data$smoker <- factor(mice.data$smoker)
+mice.data$behind_on_bills <- factor(mice.data$behind_on_bills)
+mice.data$ghq_depression <- factor(mice.data$ghq_depression)
+mice.data$ghq_happiness <- factor(mice.data$ghq_happiness)
+mice.data$clinical_depression <- factor(mice.data$clinical_depression)
+mice.data$scsf1 <- factor(mice.data$scsf1)
+mice.data$health_limits_social <- factor(mice.data$ghq_depression)
+mice.data$housing_tenure <- factor(mice.data$housing_tenure)
+mice.data$urban <- factor(mice.data$urban)
+mice.data$marital_status <- factor(mice.data$marital_status)
+
 load_cache <- F
@@
 } else {
-  n_iter <- 20
-  max_iter <- 5
+  n_iter <- 30
+  max_iter <- 10
+  ignore_cols = c("birth_year")
   # future mice is parallelised version of MICE.
-  mice_set <- futuremice(data = mice.data, #method=method,
-                   #m = 10, maxit = 30,
+  mice_set <- mice(data = mice.data[, imp_columns], #method=method,
                    m = n_iter, maxit = max_iter,
                    remove.collinear=T)
+
+  #mice_set <- with_progress(futuremice(data = mice.data[, mice_columns], #method=method,
+  #                m = n_iter, maxit = max_iter,
+  #                 remove.collinear=T, quiet=F,
+  #                 progressor = progressr::handlers("progress")))
   saveRDS(mice_set, "data/transitions/MICE_set.rds")

### 2023-12-01 scripts/mice_bash_script_paper1.R

@@ -1,0 +1,184 @@
+source("minos/transitions/utils.R")
+source("minos/transitions/transition_model_functions.R")
+source("minos/transitions/paper_1_plots.R")
+library(dplyr)
+library(texreg)
+library(lme4)
+library(glmnet)
+library(mice)
+library(sjPlot)
+library(visreg)
+library(ggplot2)
+library(ggpattern)
+library(VIM)
+library(caret)
+library(tidyverse)
+library(performance)
+library(broom.mixed)
+library(ggridges)
+save.path <- "minos/outcomes/paper1_plots/"
+raw.data.dir <- "data/raw_US/"
+mice.data.dir <- "data/composite_US/"
+final.data.dir <- mice.data.dir
+
+
+
+# load in all 2009-2020 datasets
+mice.filelist <- list.files(mice.data.dir,
+                            include.dirs = FALSE,
+                            full.names = TRUE,
+                            pattern = '[0-9]{4}_US_cohort.csv')
+mice.data <- do.call(rbind, lapply(mice.filelist, read.csv))
+
+# missingness MICE model formula
+mice_formula_string <- "SF_12 ~ 
+                        factor(sex) + 
+                        relevel(factor(ethnicity), ref='WBI') + 
+                        scale(age) + 
+                        factor(education_state) + 
+                        factor(S7_labour_state) + 
+                        relevel(factor(job_sec), ref=1) +
+                        relevel(factor(region), ref='London') +
+                        scale(hh_income) + 
+                        scale(I(hh_income**2)) +
+                        factor(housing_quality) +
+                        factor(neighbourhood_safety) + 
+                        factor(loneliness) +
+                        ncigs +
+                        nutrition_quality"
+
+mice_model_formula <- as.formula(mice_formula_string)
+variables <- all.vars(mice_model_formula)
+
+# get required variables and replace missing value codes.
+mice.data <- replace.missing(mice.data)
+
+
+
+imp_columns <- c("SF_12",
+                 'sex',
+                 "job_sec",
+                 "education_state",
+                 "S7_labour_state", 
+                 "region", 
+                 "ethnicity", 
+                 "age", 
+                 "time", 
+                 "hh_income",
+                 "housing_quality",
+                 "neighbourhood_safety",
+                 "loneliness",
+                 "ncigs",
+                 'nutrition_quality'
+)
+
[…]

### 2023-12-01 minos/outcomes/paper_1_notebook.Rmd
finish mice script

@@
 mice.data$region <- factor(mice.data$region)
-mice.data$heating <- factor(mice.data$heating)
-mice.data$job_sec <- factor(mice.data$job_sec)
-mice.data$education_state <- factor(mice.data$education_state)
-mice.data$sex <- factor(mice.data$sex)
+mice.data$loneliness <- factor(mice.data$loneliness)
+#mice.data$heating <- factor(mice.data$heating)
+#mice.data$job_sec <- factor(mice.data$job_sec)
+#mice.data$education_state <- factor(mice.data$education_state)
+#mice.data$sex <- factor(mice.data$sex)
 #mice.data$smoker <- factor(mice.data$smoker)
-mice.data$behind_on_bills <- factor(mice.data$behind_on_bills)
-mice.data$ghq_depression <- factor(mice.data$ghq_depression)
-mice.data$ghq_happiness <- factor(mice.data$ghq_happiness)
-mice.data$clinical_depression <- factor(mice.data$clinical_depression)
-mice.data$scsf1 <- factor(mice.data$scsf1)
-mice.data$health_limits_social <- factor(mice.data$ghq_depression)
-mice.data$housing_tenure <- factor(mice.data$housing_tenure)
-mice.data$urban <- factor(mice.data$urban)
-mice.data$marital_status <- factor(mice.data$marital_status)
+#mice.data$behind_on_bills <- factor(mice.data$behind_on_bills)
+#mice.data$ghq_depression <- factor(mice.data$ghq_depression)
+#mice.data$ghq_happiness <- factor(mice.data$ghq_happiness)
+#mice.data$clinical_depression <- factor(mice.data$clinical_depression)
+#mice.data$scsf1 <- factor(mice.data$scsf1)
+#mice.data$health_limits_social <- factor(mice.data$ghq_depression)
+#mice.data$housing_tenure <- factor(mice.data$housing_tenure)
+#mice.data$urban <- factor(mice.data$urban)
+#mice.data$marital_status <- factor(mice.data$marital_status)
 

### 2023-12-05 minos/validation/handovers.Rmd
LOTS of work on hourly_wage module to ensure living wage intervention is fully dynamic. Needs more work but its at a reasonable point. Some changes include: updated environment file to add missing R packages; small changes to transition estimation scripts to fix small issues; updated the hourly_wage module; improved the transitions Makefile to make it more clear which targets are for which runs; more I cant remember right now

--- 2023-11-27 minos/validation/handovers.Rmd
@@
 spag <- spag %>%
-  filter(hourly_wage <= 100)
+  filter(hourly_wage <= 300)
 spaghetti_plot(spag, 'hourly_wage',

### 2023-12-05 minos/modules/r_utils.py

@@ -341,6 +341,9 @@ def predict_next_timestep_yj_gaussian_lmm(model, rpy2_modules, current, dependen
         #yj = model.rx2('transform') # use yj from fitted model for latest year.
         currentRDF[currentRDF.names.index(dependent)] = stats.predict(yj, newdata=currentRDF.rx2(dependent))  # apply yj transform
 
+    # explicitly convert to matrix to overcome error in predict_merMod below
+    #currentRDF_matrix = matrix.as_matrix(currentRDF)
+
     ols_data = lme4.predict_merMod(model, currentRDF, type='response', allow_new_levels=True)  # estimate next income using OLS.
 
     # if dependent == "SF_12":

### 2023-12-05 minos/outcomes/paper_1_notebook.Rmd
final push with nice mice object

@@
 library(ggridges)
+library(ggmice)
+library(MASS)
 save.path <- "minos/outcomes/paper1_plots/"
@@
                   factor(labour_state_raw) + 
-                  relevel(factor(job_sec), ref=1) +
+                  relevel(factor(NSSEC), ref=1) +
                   relevel(factor(region), ref='London') +
@@
 # get only needed variables and replace missing codes with NA.
+raw.data.colnames <- colnames(raw.data)
+raw.data.colnames[which( colnames(raw.data)=="job_sec" )] <- "NSSEC"
+colnames(raw.data) <- raw.data.colnames
 raw.data <- raw.data[, append(variables, c("time", 'pidp', 'weight'))]
@@
 full.raw.data <- do.call(rbind, lapply(full.raw.filelist, read.csv))
-
+full.raw.data.colnames <- colnames(full.raw.data)
+full.raw.data.colnames[which( colnames(full.raw.data)=="job_sec" )] <- "NSSEC"
+colnames(full.raw.data) <- full.raw.data.colnames
 # get only needed variables and replace missing codes with NA.
@@
 colnames(fitted_residuals) <- c("fitted", "sqrt_residuals")
-fitted_residual_plot(fitted_residuals, paste0(save.path, "presentation_fitted_residual_plot.pdf"))
+fitted_residual_plot(fitted_residuals, paste0(save.path, "presentation_scale_location_plot.pdf"))
 
@@
 
+mice.data.colnames <- colnames(mice.data)
+mice.data.colnames[which(colnames(mice.data)=="job_sec" )] <- "NSSEC"
+colnames(mice.data) <- mice.data.colnames
+
 # missingness MICE model formula
@@
                         factor(S7_labour_state) + 
-                        relevel(factor(job_sec), ref=1) +
+                        relevel(factor(NSSEC), ref=1) +
                         relevel(factor(region), ref='London') +
@@
                  'sex',
-                 "job_sec",
+                 "NSSEC",
                  "education_state",
@@
 aggr_columns <- c("SF_12",
-                 "job_sec",
+                 "NSSEC",
                  "education_state",
@@
 pdf(paste0(save.path, "total_missingness_structure1.pdf"))
-aggr(mice.data[,aggr_columns], sortVars=T, prop=T, combined=F,varheight=T, oma=c(10,5,0,2), gap=0)
+aggr(mice.data[,aggr_columns], sortVars=T, prop=T, combined=F,varheight=T, oma=c(10,5,1,2), gap=0)
 dev.off()
@@
                   #"heating", 
-                  "job_sec", 
+                  "NSSEC", 
                   "ncigs",
@@
 
-load_cache <- F
+load_cache <- T
 if (load_cache) {
@@
   # future mice is parallelised version of MICE.
-  mice_set <- mice(data = mice.data[, imp_columns], #method=method,
+  mice_set <- mice(data = mice.data[, imp_columns],
                    m = n_iter, maxit = max_iter,
@@
 mice.long$time <- mice.data$time
+mice.long.colnames <- colnames(mice.long)
+mice.long.colnames[which( colnames(mice.long)=="job_sec" )] <- "NSSEC"
+colnames(mice.long) <- mice.long.colnames
+
 mice_set.full <- as.mids(mice.long)
@@
 pdf(paste0(paste0(save.path,"ols_mice_convergence.pdf")))
-print(plot(mice_set, SF_12 = SF_12 ~ .it | .ms))
+#print(plot(mice_set, SF_12 = SF_12 ~ .it | .ms))
+plot_trace(mice_set, "SF_12") + theme(legend.position="none")
 dev.off()
@@
 density_ridges(crossval.mice.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "mice_raw_ridges")
-density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "mice_handover_ridges")
+density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "mice_validation_ridges")
 
@@
 density_ridges(crossval.mice.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_raw_ridges")
-density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_handover_ridges")
+density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_validation_ridges")
+
+```
+
+###
+
+```{r random_coefficients}
+
+# for 100 iterations
+randomised.mice.model.data <- data.frame()
+random.mice.lm.object <- lm(mice_formula_string, data = complete(mice_set.subset, 1))
+
+for (i in 1:100) {
+  # choose a random OLS model
+  # randomise its coefficients from MVN dist from MASS.
+  #model.choice.ix <- ceiling(runif(1)*30)
+  #model.choice <- mice.sf12.lm$analyses[model.choice.ix]
+  model.choice <- random.mice.lm.object
+  model.choice$coefficients <- MASS::mvrnorm(n=1, mu=mice.lm.object$coefficients[, 1], Sigma=vcov(mice.lm.object))
+  # add to pool
+  # commentary
+  random.start.data <- crossval.mice.data[which(crossval.mice.data$time==2013),]
+  #random.start.data[, c("run_id")] <- i
+  #random.rolling.data <- random.start.data[, c("SF_12", "time", "run_id")]
+  #random.handover.data <- rolling.data
+  for (j in 1:7){
+    random.start.data$SF_12 <- predict(model.choice, random.start.data)
+    #random.start.data$SF_12 <- random.rolling.data$SF_12
+    #random.rolling.data[, 'time'] <- random.rolling.data[, 'time'] +1
+    #random.handover.data <- rbind(random.handover.data, random.rolling.data)
+  }
+  individual.density <- density(random.start.data$SF_12)
+  new.data.frame <- cbind(individual.density$x, individual.density$y, i)
+  colnames(new.data.frame) <- c("SF_12", "Density", "run_id")
+  randomised.mice.model.data <- rbind(randomised.mice.model.data, new.data.frame)
+
+}
+
+p <- ggplot(randomised.mice.model.data, aes(x=SF_12, y=Density, group=factor(run_id))) +
+     geom_line(alpha=0.1) + ylim(0, 0.15) + xlim(15,60)
+ggsave(paste0(save.path, "/", "randomised_coefficients_2020_density.pdf"))
+#ggplot(randomised.mice.model.data, aes(x=SF_12, y=Density)) +
+#    geom_line(alpha=0.2) + geom_ribbon()
 
@@
 
-print(coef(cv.lasso, s = "lambda.min"))
-print(coef(cv.lasso, s = "lambda.1se"))
-
 # bind two sets of coefficients into a data frame
 # load them into a tex table using the latex package?
-lasso_coefs <- cbind(coef(cv.lasso, s = "lambda.min")[, 's1'], coef(cv.lasso, s = "lambda.1se")[, 's1'])
-colnames(lasso_coefs) <- c("Minimum Error", "First Standard Error")
-#lasso_coefs <- kable(as.data.frame(as.matrix(lasso_coefs)), "latex")
+lasso.min.coefs <- coef(cv.lasso, s=cv.lasso$lambda.min)
+lasso.1se.coefs <- coef(cv.lasso, s=cv.lasso$lambda.1se)
+lasso_model_names <- c("Minimum Error", "First Standard Error")
 
@@
 tex_label <- paste0("table: sf12_lasso_coefficients") 
-tex_headers <- c(texreg::names2latex("SF_12 LASSO"))
+tex_headers <- c(texreg::names2latex("Minimum Error"), texreg::names2latex("First Standard Error"))
 tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "lasso"))    
-lassoTexReg <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso_coefs[,1], se=lasso_coefs[,2])
+#lassoTexReg <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso_coefs[,1], se=lasso_coefs[,2], model.names=c("Minimum Error", "First Standard Error"))
+
+lasso.min <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso.min.coefs[, "s1"])
+lasso.1se <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso.1se.coefs[, "s1"])
+
 #lassoTexReg2 <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso_coefs[,2])#, lasso_coefs[, 2]))#, pvalues=lasso_coefs[,2])
@@
 
-texreg(lassoTexReg, # what model to save coefs for. 
+texreg(c(lasso.min, lasso.1se), # what model to save coefs for. 
        file=texreg_file,  # where to save.
@@
 
-iextrapolated.weights.data <- do.call(rbind, lapply(extrapolated_weights.filelist, read.csv))
+extrapolated.weights.data <- do.call(rbind, lapply(extrapolated_weights.filelist, read.csv))
 extrapolated.weights.data <- replace.missing(extrapolated.weights.data)
@@
 reflect <- T
-yeo_johnson <- T
+yeo_johnson <- F
 include_weights <- T
@@
     max_value <- nanmax(mice.data[[depend]])
-    glmm.mice.long.subset[, c(depend)] <- max_value - glmm.mice.long.subset[, c(depend)] 
+    glmm.mice.long.subset[, c(depend)] <- max_value - glmm.mice.long.subset[, c(depend)] + 0.001
   }
@@
   glmm.mice.long.subset[["SF_12"]] <- predict(yj)
-}
 
@@
   glmm.mice.long.subset[[depend]] <- glmm.mice.long.subset[[depend]] - min_value + 0.001
+}
 
@@
 
+asd <- "SF_12_last +"
 glmm_model_formula_string <- "SF_12 ~ SF_12_last +
@@
                   factor(S7_labour_state) + 
-                  relevel(factor(job_sec), ref=1) +
+                  relevel(factor(NSSEC), ref=1) +
                   relevel(factor(region), ref='London') +
@@
                   nutrition_quality + 
-                  ncigs + 
+                  ncigs + time +
                   (1|pidp)"
@@
                nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes forever..
-               family=Gamma(link='log'), # gamma family with log link.
-               weights=weight))
+               family=Gamma(link='log')#, weights=weight# gamma family with log link.
+               ))
 
@@
 # + rnorm(nrow(complete(glmm.mice.set ,1)), 0,0.75)
-glmm.fitted <- (max_value - predict(yj, predict(mice.glmm.object, type='response') + min_value +rnorm(predict(mice.glmm.object, type='response'),0,0.2), inverse=T))#
+if (yeo_johnson == T) {
+  glmm.fitted <- (max_value - predict(yj, predict(mice.glmm.object, type='response') + min_value #+rnorm(predict(mice.glmm.object, type='response'),0,0.2)
+                                    , inverse=T))#
+} else {
+  glmm.fitted <-  max_value - predict(mice.glmm.object, type='response')
+}
+
 #glmm.fitted <- (max_value - predict(mice.glmm.object, type='response') + min_value + rnorm(nrow(glmm.mice.long.subset), 0, 1))
-glmm.fitted <- trunc(glmm.fitted, 0 , 100)
-qq_plot(residuals(mice.glmm.object, type='pearson'), paste0(save.path, "glmm_qq.pdf"))
+#glmm.mean <- mean(glmm.fitted)
+#glmm.sd <- sd(glmm.fitted)
+#glmm.fitted <- glmm.fitted * (glmm.sd/sd(raw.data$SF_12))
+#glmm.fitted <- glmm.fitted - (glmm.mean*(glmm.sd/sd(raw.data$SF_12)-1))
+#glmm.fitted <- trunc(glmm.fitted, 0 , 100) #+ rnorm(length(glmm.fitted),0,2)
+
+qq_plot(scale(residuals(mice.glmm.object, type='pearson')), paste0(save.path, "glmm_qq.pdf"))
+qq_plot(scale(residuals(mice.glmm.object, type='deviance')), paste0(save.path, "glmm_qq.pdf"))
+
 residual_density_plot(res=residuals(mice.glmm.object) , file_name=paste0(save.path, "glmm_residual_density.pdf"), guide="normal")
 
-squareRootRes <- sqrt(residuals(mice.glmm.object, type='pearson'))
+squareRootRes <- sqrt(residuals(mice.glmm.object, type='pearson')**2)
+#squareRootRes <- residuals(mice.glmm.object, type='pearson')
+
 fitted_residuals <- as.data.frame(cbind(glmm.fitted, squareRootRes))
 colnames(fitted_residuals) <- c("fitted", "sqrt_residuals")
-fitted_residual_plot(fitted_residuals, paste0(save.path, "glmm_fitted_residual_plot.pdf"))
+fitted_residual_plot(fitted_residuals, paste0(save.path, "glmm_scale_location_plot.pdf"))
 
@@
 for (i in 1:7){
-  rolling.data$SF_12 <- max_value - predict(yj,  predict(mice.glmm.object, start.data, type='response',allow.new.levels=T) + rnorm(nrow(rolling.data),0,0.25)+min_value, inverse=T)
+  if (yeo_johnson) {
+      rolling.data$SF_12 <- max_value - predict(yj,  predict(mice.glmm.object, start.data, type='response',allow.new.levels=T) +min_value, inverse=T)
+  }
+  else {
+    rolling.data$SF_12 <- max_value - predict(mice.glmm.object, start.data,type='response',allow.new.levels=T) + rnorm(nrow(rolling.data), 0, 1)
+  }
   #rolling.data$SF_12 <- max_value - rolling.data$SF_12

### 2023-12-05 minos/transitions/paper_1_plots.R

@@ -57,7 +57,7 @@ gamma_forest_plot <- function(model, file_name){
   p <- p +  scale_shape_manual(name='Significance Level',
                                breaks=c('n.s.', "*", "**", "***"),
                                values=c(1, 16, 17, 15)) # cast legend to certain title, variable names and shapes.
-  #p <- p + ylim(0.1, 1.9)
+  p <- p + ylim(c(-0.1, 0.1))
   plot(p)
   dev.off()
 }
@@ -79,8 +79,8 @@ residual_density_plot <- function(res, file_name, guide=NULL){
 
 qq_plot <- function(res, file_name){
   pdf(file_name)
-  print(qqnorm(scale(res)))
-  print(qqline(scale(res)))
+  qqnorm(scale(res))
+  qqline(scale(res))
   dev.off()
   print("saved qq plot to")
   print(file_name)
@@ -124,7 +124,10 @@ handover_boxplots <- function(raw, baseline, var, save.path, filename.prefix) {
   ggplot(data = combined, aes(x = time, y = .data[[var]],  group = interaction(time, source), fill= source)) +
     geom_boxplot(notch=TRUE) +
     labs(title = paste0(var, ': Yearly box plots'))
+  ggsave(paste0(save.path, '/', filename.prefix, ".pdf"))
 }
+
+
 
 # summarise(summary_var = weighted.mean(x = .data[[var]], w = weight)) %>%
 handover_lineplots <- function(raw, base, var) {
@@ -232,7 +235,8 @@ density_ridges <- function(data, v, save=FALSE, save.path=NULL, filename.tag=NUL
     geom_density_ridges(aes(y=time, color=time, linetype=time), alpha=0.6) +
     #scale_color_viridis_d() +
     scale_color_cyclical(values=c("#F8766D", "#00BA38","#619CFF")) +
-    scale_linetype_cyclical(values=c(1, 2, 3))
+    scale_linetype_cyclical(values=c(1, 2, 3)) +
+    xlim(c(0, 70))
   
   if(save) {
     if(is.null(save.path)) {
@@ -240,9 +244,9 @@ density_ridges <- function(data, v, save=FALSE, save.path=NULL, filename.tag=NUL
     }
     # add handover to filename if handover
     if (handover) {
-      save.filename <- paste0('density_ridges_handover_', v, '.png')
+      save.filename <- paste0('density_ridges_', v, '.pdf')
     } else {
[…]

### 2023-12-05 minos/validation/handovers.Rmd
Updated handover year in handovers to fit new 2021 start point

--- 2023-11-27 minos/validation/handovers.Rmd
@@
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-#out.path <- here::here('output', 'scotland_scaled/')
-#base.dat <- read_first_singular_local_out(out.path, '25UniversalCredit', drop.dead = TRUE)
 ```
@@
 ```{r}
-start.year <- 2020
+start.year <- 2021
 save.path <- here::here("plots", "handovers", 'default')

### 2023-12-06 minos/validation/cross_validation_S7.Rmd
Updated some R notebooks to point to 2021 instead of 2020 where necessary

@@
 multi_year_boxplots(raw, cv, 'hh_income')
-snapshot_OP_plots(raw, cv, 'hh_income', target.years = c(2014, 2016, 2018, 2020))
+snapshot_OP_plots(raw, cv, 'hh_income', target.years = c(2015, 2017, 2019, 2021))
 q_q_comparison(raw, cv, 'hh_income')
@@
                                  var = 'hh_income', 
-                                 target.year = 2020)
+                                 target.year = 2021)
 print(inc.20)
@@
 ```
-
-# Job NSSEC
-
-```{r}
-job_sec.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                          df1.name = 'simulated', 
-                                          df2 = raw, 
-                                          df2.name = 'raw', 
-                                          var = 'job_sec')
-
-cv_ordinal_plots(pivoted.df = job_sec.pivoted, 
-                 var = 'job_sec',
-                 save = FALSE)
-rm(mstat.pivoted)
-```

### 2023-12-06 minos/validation/cross_validation_default.Rmd
Lots of small changes working on the job_hours and hourly_wage transitions and modules
LOTS of work on hourly_wage module to ensure living wage intervention is fully dynamic. Needs more work but its at a reasonable point. Some changes include: updated environment file to add missing R packages; small changes to transition estimation scripts to fix small issues; updated the hourly_wage module; improved the transitions Makefile to make it more clear which targets are for which runs; more I cant remember right now
Updated some R notebooks to point to 2021 instead of 2020 where necessary

--- 2023-11-07 minos/validation/cross_validation_default.Rmd
@@
 multi_year_boxplots(raw, cv, 'SF_12')
-snapshot_OP_plots(raw, cv, 'SF_12', target.years = c(2014, 2016, 2018, 2020))
+snapshot_OP_plots(raw, cv, 'SF_12', target.years = c(2015, 2017, 2019, 2021))
 q_q_comparison(raw, cv, 'SF_12')
@@
                                  var = 'SF_12', 
-                                 target.year = 2020)
+                                 target.year = 2021)
 print(sf12.20)
@@
 ```
-
-## Job Sec
-
-```{r}
-jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                          df1.name = 'simulated', 
-                                          df2 = raw, 
-                                          df2.name = 'raw', 
-                                          var = 'job_sec')
-
-cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
-                 var = 'job_sec',
-                 save = FALSE)
-rm(jobsec.pivoted)
-```
-
-## Job Hours
-
-```{r}
-cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'job_hours')
-multi_year_boxplots(raw, cv, 'job_hours')
-q_q_comparison(raw, cv, 'job_hours')
-```

### 2023-12-07 minos/validation/cross_validation_default.Rmd
Fixed year range of cross-validation transition estimation to ensure neighbourhood_safety model is still estimated. Also added the synthetic tag to config files that were missing it. Finally added the wave data copy for neighbourhood safety onto 2015 for cross-validation

@@
                                  var = 'hh_income', 
-                                 target.year = 2014)
+                                 target.year = 2015)
 print(inc.14)
@@
                                  var = 'hh_income', 
-                                 target.year = 2016)
+                                 target.year = 2017)
 print(inc.16)
@@
                                  var = 'hh_income', 
-                                 target.year = 2018)
+                                 target.year = 2019)
 print(inc.18)
@@
                                  var = 'SF_12', 
-                                 target.year = 2014)
+                                 target.year = 2015)
 print(sf12.14)
@@
                                  var = 'SF_12', 
-                                 target.year = 2016)
+                                 target.year = 2017)
 print(sf12.16)
@@
                                  var = 'SF_12', 
-                                 target.year = 2018)
+                                 target.year = 2019)
 print(sf12.18)

### 2023-12-07 minos/validation/scot_input_pop_validation.Rmd
forgot a couple of things

---
title: "Scotpop validation notebook"
output:
  html_document:
    df_print: paged
---

This notebook is for validation of the scottish population for child poverty interventions. It contains descriptive statistics for the population and validated against provided child poverty data spatially and nationally.

```{r}
library(tidyr)
library(dplyr)
library(sf)
library(sp)
library(tibble) # converting spatial objects to data frames.
library(broom)
library(here)
library(ggplot2)

source( here::here("minos", "outcomes", "minos_SF12_maps.R"))
```

```{r}
scotland.data <- read.csv("data/scaled_scotland_US/2020_US_cohort.csv")
#scotland.data <- drop_na(scotland.data)
uk.geojson <- st_read("persistent_data/spatial_data/UK_super_outputs.geojson")
uk.geojson <- geojson_to_tibble(uk.geojson)

scotland.data.zones <- read.csv("persistent_data/spatial_data/scotland_data_zones.csv")
glasgow.data.zones <- read.csv("persistent_data/spatial_data/glasgow_data_zones.csv")
edinburgh.data.zones <- read.csv("persistent_data/spatial_data/edinburgh_data_zones.csv")

scotland.geojson <- uk.geojson[which(uk.geojson$ZoneID %in% (scotland.data.zones$LSOA11CD)), ]
glasgow.geojson <- uk.geojson[which(uk.geojson$ZoneID %in% (glasgow.data.zones)$LSOA11CD), ]
edinburgh.geojson <- uk.geojson[which(uk.geojson$ZoneID %in% (edinburgh.data.zones)$LSOA11CD), ]

scotland.LADs.geojson <-  st_read("persistent_data/spatial_data/scotland_LADs.json")
scotland.LADs.geojson <- geojson_to_tibble(scotland.LADs.geojson)
scotland.LADs.geojson[6, "LAD13NM"] <- "Na h-Eileanan Siar" # conflicting name. Think this has been updated since 2013?

```

Description of SF12 MCS

```{r}
hist(scotland.data$SF_12, breaks=100)
print(summary(scotland.data$SF_12))
print(sd(scotland.data$SF_12))
```

```{r}
#https://www.gov.scot/publications/tackling-child-poverty-delivery-plan-forecasting-child-poverty-scotland/pages/4/
glasgow.poverty.stats <- read.csv("persistent_data/spatial_data/Child-Poverty-Glasgow-City-2021-22.csv")
#glasgow.poverty.stats$X..of.children.in.poverty <- glasgow.poverty.stats$X..of.children.in.poverty %% 100
# getting households in relative poverty
scotland.relative_poverty <- scotland.data %>%
                                filter(hh_income < 0.7*median(hh_income))

glasgow.relative_poverty.map <- scotland.relative_poverty %>%
                                  filter(ZoneID %in% (glasgow.data.zones)) %>%
                                  group_by(ZoneID) %>%
                                  summarize(sf12_mean = mean(SF_12, na.rm=T))

glasgow.relative_poverty.map.data <- merge(glasgow.geojson, glasgow.relative_poverty.map, by ='ZoneID')

glasgow.relative.poverty.map <- ggplot(data = glasgow.relative_poverty.map.data , aes(geometry = geometry, fill=.data[["sf12_mean"]])) +
  #geom_sf() + # black outlines on borders for clarity.
  geom_sf(color=NA) + # black outlines on borders for clarity.
  scale_fill_viridis_c(alpha = 1.0, direction=-1) + # use viridis colour scale and reverse it  so brighter is better.
  labs(fill="sf12_mean")  + # colour bar label.
  theme(aspect.ratio=9/16) + # change plot to widescreen dimensions.
  xlab("Longitude") + # axis labels
  ylab("Latitude")
plot(glasgow.relative.poverty.map)
```

```{r}

glasgow.percentage.relative.poverty.data <- scotland.data %>%
                                  filter(ZoneID %in% (glasgow.data.zones)) %>%
                                  mutate(in_relative_poverty = hh_income < 0.75*median(hh_income)) %>%
                                  group_by(hidp) %>%
                                  summarize(ZoneID= max(ZoneID), nkids = max(nkids), in_relative_poverty = max(in_relative_poverty)) %>%
                                  group_by(ZoneID) %>%
                                  summarize(relative.poverty.freq = 100 * sum(nkids*in_relative_poverty)/sum(nkids))

glasgow.percentage.relative.poverty.map.data <- merge(glasgow.geojson, glasgow.percentage.relative.poverty.data, by ='ZoneID')

glasgow.percentage.relative.poverty.map <- ggplot(data = glasgow.percentage.relative.poverty.map.data  , aes(geometry = geometry, fill=.data[["relative.poverty.freq"]])) +
  #geom_sf() + # black outlines on borders for clarity.
  geom_sf(color=NA) + # black outlines on borders for clarity.
  scale_fill_viridis_c(alpha = 1.0, direction=-1) + # use viridis colour scale and reverse it  so brighter is better.
  labs(fill="Percentage Poverty")  + # colour bar label.
  theme(aspect.ratio=9/16) + # change plot to widescreen dimensions.
  xlab("Longitude") + # axis labels
  ylab("Latitude")
plot(glasgow.percentage.relative.poverty.map)

glasgow.percentage.relative.poverty.diff <- merge(glasgow.percentage.relative.poverty.map.data, glasgow.poverty.stats, by.x = "ZoneID", by.y="DataZone")
glasgow.percentage.relative.poverty.diff$diff <- glasgow.percentage.relative.poverty.diff$X..of.children.in.poverty - glasgow.percentage.relative.poverty.diff$relative.poverty.freq

# bluer indicates the synth pop underestimates percentage poverty. orange indicates overestimation. 
minos_diff_map(glasgow.percentage.relative.poverty.diff, "plots/poverty_diff_map.pdf", "PP", F)
print("MAE:")
print(mean(abs(glasgow.percentage.relative.poverty.diff$diff)))
hist(abs(glasgow.percentage.relative.poverty.diff$diff))
```

```{r}
#https://www.healthscotland.scot/media/2607/child-poverty-scales-and-trends.pdf
scotland.lad.poverty.data <- scotland.data[, c("hh_income", "nkids", "hidp", "ZoneID")]
scotland.lad.poverty.data <- merge(scotland.lad.poverty.data, scotland.geojson, by = "ZoneID")
scotland.lad.poverty.data <- scotland.lad.poverty.data[, c("hh_income", "nkids", "hidp", "LAName")]

scotland.lad.percentage.relative.poverty.data <- scotland.lad.poverty.data %>%
                                  mutate(in_relative_poverty = hh_income < 0.6*median(hh_income)) %>%
                                  group_by(hidp) %>%
                                  summarize(LAName= max(LAName), nkids = max(nkids), in_relative_poverty = max(in_relative_poverty)) %>%
                                  group_by(LAName) %>%
                                  summarize(relative.poverty.freq = 100 * sum(nkids*in_relative_poverty)/sum(nkids))

scotland.lad.percentage.relative.poverty.map.data  <- merge(scotland.lad.percentage.relative.poverty.data, scotland.LADs.geojson, by.x = "LAName", by.y="LAD13NM")

scotland.lad.percentage.relative.poverty.map <- ggplot(data = scotland.lad.percentage.relative.poverty.map.data  , aes(geometry = geometry, fill=.data[["relative.poverty.freq"]])) +
  #geom_sf() + # black outlines on borders for clarity.
  geom_sf(color=NA) + # black outlines on borders for clarity.
  scale_fill_viridis_c(alpha = 1.0, direction=-1) + # use viridis colour scale and reverse it  so brighter is better.
  labs(fill="Percentage Poverty")  + # colour bar label.
  xlab("Longitude") + # axis labels
  ylab("Latitude")
plot(scotland.lad.percentage.relative.poverty.map)
print(mean(scotland.lad.percentage.relative.poverty.map.data$relative.poverty.freq))

# download from here https://www.jrf.org.uk/data/uk-child-poverty-rates-local-authority.
rowntree.percentage.child.poverty <- readxl::read_xlsx("persistent_data/spatial_data/6_chld_pov_rate_by_la.xlsx")
rowntree.percentage.child.poverty <- rowntree.percentage.child.poverty[which(rowntree.percentage.child.poverty$`Title:` %in% scotland.LADs.geojson$LAD13NM), ]
rowntree.percentage.child.poverty$percentage_poverty <- as.numeric(rowntree.percentage.child.poverty$`Child poverty rate estimate by local authority`) * 100

scotland.lad.percentage.relative.poverty.diff <- merge(scotland.lad.percentage.relative.poverty.map.data, rowntree.percentage.child.poverty, by.x = "LAName", by.y="Title:")
scotland.lad.percentage.relative.poverty.diff $diff <- scotland.lad.percentage.relative.poverty.diff$percentage_poverty - scotland.lad.percentage.relative.poverty.diff$relative.poverty.freq

# bluer indicates the synth pop underestimates percentage poverty. orange indicates overestimation. 
minos_diff_map(scotland.lad.percentage.relative.poverty.diff, "plots/poverty_diff_map.pdf", "PP", F)
print("MAE:")
print(mean(abs(scotland.lad.percentage.relative.poverty.diff$diff)))
hist(abs(scotland.lad.percentage.relative.poverty.diff$diff), breaks=100)

```

Description of Household Income

```{r}

```

Description of Household (Absolute/Relative) Poverty.

```{r}

```

Description of Material Deprivation and Low Income

```{r}

```

Description of Persistent poverty? Not sure this is feasible with one year of synth data.

```{r}

```

### 2023-12-11 minos/validation/handovers.Rmd
Copied information from wave 12 to wave 13 about FT and PT employment (due to a missing var in wave 13, this will be replaced by imputed data soon!!!)

--- 2023-12-05 minos/validation/handovers.Rmd
@@
 
+## S7 Labour State
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
+
+lab.state <- prepped.list$var
+lab.state.norm <- prepped.list$norm
+
+# Now plot
+ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'S7_labour_state.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, lab.state, lab.state.norm)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'S7_labour_state')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'S7_labour_state',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
 ```{r}

### 2023-12-11 minos/validation/cross_validation_default.Rmd
Copied information from wave 12 to wave 13 about FT and PT employment (due to a missing var in wave 13, this will be replaced by imputed data soon!!!)

@@
 
+# S7 Labour State
+
+```{r}
+labstate.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'S7_labour_state')
+
+cv_ordinal_plots(pivoted.df = labstate.pivoted, 
+                 var = 'S7_labour_state',
+                 save = FALSE)
+rm(labstate.pivoted)
+```
+
 # SECONDARY VARS
@@
 ```
+
+## Children Ageing
+
+Children ageing is now calculated in MINOS.
+
+```{r}
+
+format_child_age_data <- function(dataset) {
+  formatted.age.data <- dataset %>%
+                        dplyr::select(hidp, time, child_ages, pidp) %>%
+                        filter(time >= 2014) %>%
+                        group_by(time, pidp) %>%
+                        summarise(child_ages = max(child_ages))
+
+  split.ages <- strsplit(formatted.age.data$child_ages, "_")
+
+  child.ages.expanded <- data.frame(time = rep(formatted.age.data$time, sapply(split.ages, length)), 
+                                    #hidp= rep(formatted.age.data$hidp, sapply(split.ages, length)), 
+                                    pidp= rep(formatted.age.data$pidp, sapply(split.ages, length)), 
+                                    expanded_child_ages = as.numeric(unlist(split.ages)))
+
+  #child.ages.expanded <- child.ages.expanded %>%
+  #  group_by(pidp, time) %>%
+  #  summarise(expanded_child_ages = median(expanded_child_ages))
+
+  return (child.ages.expanded)
+}
+
+find_mode <- function(x) {
+  u <- unique(x)
+  tab <- tabulate(match(x, u))
+  u[tab == max(tab)]
+}
+
+cv.child.ages <- format_child_age_data(cv)
+cv1.child.ages <- format_child_age_data(cv1)
+cv2.child.ages <- format_child_age_data(cv2)
+cv3.child.ages <- format_child_age_data(cv3)
+cv4.child.ages <- format_child_age_data(cv4)
+cv5.child.ages <- format_child_age_data(cv5)
+raw.child.ages <- format_child_age_data(raw.dat)
+
+cv.mean.plots(cv1.child.ages, cv2.child.ages, cv3.child.ages, cv4.child.ages, cv5.child.ages, raw.child.ages, 'expanded_child_ages')
+multi_year_boxplots(raw.child.ages, cv.child.ages, 'expanded_child_ages')
+q_q_comparison(raw.child.ages, cv.child.ages, 'expanded_child_ages')
+
+```
+
+```{r} 
+#nkids
+
+format_nkids_data <- function(dataset) {
+  dataset %>%
+  group_by(hidp, time, pidp) %>%
+  summarise(nkids = max(nkids)) %>%
+  #group_by(time) %>%
+  #summarise(nkids_by_year = sum(nkids_counts))
+  return (dataset)
+}
+
+cv.nkids <- format_nkids_data(cv)
+cv1.nkids <- format_nkids_data(cv1)
+cv2.nkids <- format_nkids_data(cv2)
+cv3.nkids <- format_nkids_data(cv3)
+cv4.nkids <- format_nkids_data(cv4)
+cv5.nkids <- format_nkids_data(cv5)
+raw.nkids <- format_nkids_data(raw.dat)
+
+cv.mean.plots(cv1.nkids, cv2.nkids, cv3.nkids, cv4.nkids, cv5.nkids, raw.nkids, 'nkids')
+multi_year_boxplots(raw.nkids, cv.nkids, 'nkids')
+q_q_comparison(raw.nkids, cv.nkids, 'nkids')
+```

### 2023-12-11 minos/validation/cross_validation_default.Rmd

@@
 multi_year_boxplots(raw, cv, 'hh_income')
-snapshot_OP_plots(raw, cv, 'hh_income', target.years = c(2015, 2017, 2019, 2021))
+snapshot_OP_plots(raw, cv, 'hh_income', target.years = c(2014, 2016, 2018, 2020))
 q_q_comparison(raw, cv, 'hh_income')
@@
                                  var = 'hh_income', 
-                                 target.year = 2015)
+                                 target.year = 2014)
 print(inc.14)
@@
                                  var = 'hh_income', 
-                                 target.year = 2017)
+                                 target.year = 2016)
 print(inc.16)
@@
                                  var = 'hh_income', 
-                                 target.year = 2019)
+                                 target.year = 2018)
 print(inc.18)
@@
                                  var = 'hh_income', 
-                                 target.year = 2021)
+                                 target.year = 2020)
 print(inc.20)
@@
 multi_year_boxplots(raw, cv, 'SF_12')
-snapshot_OP_plots(raw, cv, 'SF_12', target.years = c(2015, 2017, 2019, 2021))
+snapshot_OP_plots(raw, cv, 'SF_12', target.years = c(2014, 2016, 2018, 2020))
 q_q_comparison(raw, cv, 'SF_12')
@@
                                  var = 'SF_12', 
-                                 target.year = 2015)
+                                 target.year = 2014)
 print(sf12.14)
@@
                                  var = 'SF_12', 
-                                 target.year = 2017)
+                                 target.year = 2016)
 print(sf12.16)
@@
                                  var = 'SF_12', 
-                                 target.year = 2019)
+                                 target.year = 2018)
 print(sf12.18)
@@
                                  var = 'SF_12', 
-                                 target.year = 2021)
+                                 target.year = 2020)
 print(sf12.20)
@@
 rm(heat.pivoted)
-```
-
-# S7 Labour State
-
-```{r}
-labstate.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                          df1.name = 'simulated', 
-                                          df2 = raw, 
-                                          df2.name = 'raw', 
-                                          var = 'S7_labour_state')
-
-cv_ordinal_plots(pivoted.df = labstate.pivoted, 
-                 var = 'S7_labour_state',
-                 save = FALSE)
-rm(labstate.pivoted)
 ```
@@
 
+## Job Sec
+
+```{r}
+jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'job_sec')
+
+cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
+                 var = 'job_sec',
+                 save = FALSE)
+rm(jobsec.pivoted)
+```
+
+## Hourly Wage
+
+```{r}
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hourly_wage')
+multi_year_boxplots(raw, cv, 'hourly_wage')
+q_q_comparison(raw, cv, 'hourly_wage')
+```
+
 ## Children Ageing

### 2023-12-11 minos/validation/handovers.Rmd

--- 2023-12-08 minos/validation/handovers.Rmd
@@
 
+## Hourly Wage
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'hourly_wage')
+handover_lineplots(raw.dat, base.dat, 'hourly_wage')
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, hourly_wage)
+base.s <- base.dat %>%
+  select(pidp, age, time, hourly_wage)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+# now a version limited to 0-100
+spag <- spag %>%
+  filter(hourly_wage <= 300)
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+```{r}
+# some basic statistics about hourly_wage variable
+print("Some basic statistics on hourly_wage. These are all for 2020.")
+raw.2020 <- raw.dat %>% filter(time == 2020)
+print('All living people in 2020')
+print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
+# number individuals with an hourly_wage > 0
+print('People not in work')
+print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
+
+# Number in work
+print('People in work')
+print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
+
+# Extreme hourly_wage values
+print('Extreme hourly wage values: HIGH')
+print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
+print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
+print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
+print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
+print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
+print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
+
+raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
+print('Extreme hourly wage values: LOW (non-zero)')
+print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
+print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
+print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
+print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
+```
+
 ## Child Ages

### 2023-12-11 minos/validation/handovers.Rmd

--- 2023-12-08 minos/validation/handovers.Rmd
@@
 
+## S7 Labour State
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
+
+lab.state <- prepped.list$var
+lab.state.norm <- prepped.list$norm
+
+# Now plot
+ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'S7_labour_state.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, lab.state, lab.state.norm)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'S7_labour_state')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'S7_labour_state',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
 ## Child Ages

### 2023-12-11 minos/validation/replenishing.Rmd
Small path changes to existing scripts, and added a notebook for investigating interventions

@@
 # Replenishing data
-repl <- read.csv('Minos/data/replenishing/replenishing_pop_2019-2070.csv')
+repl <- read.csv('Minos/data/replenishing/replenishing_pop_2015-2070.csv')
 
 # scotland replenishing
-#scot.repl <- read.csv('Minos/data/replenishing/scotland/replenishing_pop_2019-2070.csv')
+#scot.repl <- read.csv('Minos/data/replenishing/scotland/replenishing_pop_2015-2070.csv')
 ```

### 2023-12-12 minos/outcomes/paper_1_notebook.Rmd
adding some mice analysis

@@
                   factor(education_state) + 
-                  factor(labour_state_raw) + 
+                  factor(labour_state) + 
                   relevel(factor(NSSEC), ref=1) +
                   relevel(factor(region), ref='London') +
-                  scale(hh_netinc)"
+                  scale(hh_income)"
 
@@
 # get only needed variables and replace missing codes with NA.
-raw.data.colnames <- colnames(raw.data)
-raw.data.colnames[which( colnames(raw.data)=="job_sec" )] <- "NSSEC"
-colnames(raw.data) <- raw.data.colnames
+raw.data <- update_column_names(raw.data)
 raw.data <- raw.data[, append(variables, c("time", 'pidp', 'weight'))]
@@
 full.raw.data <- do.call(rbind, lapply(full.raw.filelist, read.csv))
-full.raw.data.colnames <- colnames(full.raw.data)
-full.raw.data.colnames[which( colnames(full.raw.data)=="job_sec" )] <- "NSSEC"
-colnames(full.raw.data) <- full.raw.data.colnames
+full.raw.data <- update_column_names(full.raw.data)
+
 # get only needed variables and replace missing codes with NA.
@@
 # print summary statistics
-print(summary(sf12.lm))
+#print(summary(sf12.lm))
 
@@
 start.data <- raw.data[which(raw.data$time==2013),]
+start.data.colnames <- colnames(start.data)
+start.data.colnames[which( colnames(start.data)=="job_sec" )] <- "NSSEC"
+start.data.colnames[which( colnames(start.data)=="hh_netinc" )] <- "hh_income"
+start.data.colnames[which( colnames(start.data)=="labour_state_raw" )] <- "labour_state"
+colnames(start.data) <- start.data.colnames
 handover.data <- start.data[, c("pidp", "SF_12", "time")]
+rolling.data <- start.data
+
 for (i in 1:7){
-  start.data$SF_12 <- predict(sf12.lm, start.data)
+  start.data$SF_12 <- predict(sf12.lm, rolling.data)
   start.data[, 'time'] <- start.data[, 'time'] +1
@@
 
-mice.data.colnames <- colnames(mice.data)
-mice.data.colnames[which(colnames(mice.data)=="job_sec" )] <- "NSSEC"
-colnames(mice.data) <- mice.data.colnames
+mice.data <- update_column_names(mice.data)
 
@@
 mice.2018.weights <- mice.data[which(mice.data$time %in% c(2016, 2017, 2018)), "weight"]
+
+lm.no.mice <- lm(mice_formula_string, data=mice.data)
+forest_plot(lm.no.mice,  paste0(save.path, "no_mice_forest.pdf"))
 ```
@@
                  "education_state",
-                 "S7_labour_state", 
+                 "labour_state", 
                  "region", 
@@
                  "education_state",
-                 "S7_labour_state", 
+                 "labour_state", 
                  "ethnicity", 
@@
                   "neighbourhood_safety",
-                  "S7_labour_state",
+                  "labour_state",
                   #"yearly_energy",
@@
 mice.long$time <- mice.data$time
-mice.long.colnames <- colnames(mice.long)
-mice.long.colnames[which( colnames(mice.long)=="job_sec" )] <- "NSSEC"
-colnames(mice.long) <- mice.long.colnames
-
+mice.long <- update_column_names(mice.long)
 mice_set.full <- as.mids(mice.long)
@@
 
-```{r cross_val_handovers}
+```{r mice_cross_val_handovers_data}
 # boxplots for handovers
@@
 crossval.mice.data <- drop_na(crossval.mice.data)
+crossval.mice.data <- update_column_names(crossval.mice.data)
 ```
@@
 start.data <- crossval.mice.data[which(crossval.mice.data$time==2013),]
-rolling.data <- start.data[, c("pidp", "SF_12", "time")]
-handover.data <- rolling.data
+rolling.data <- start.data#[, c("pidp", "SF_12", "time")]
+handover.data <- rolling.data[, c("pidp", "SF_12", "time")]
 for (i in 1:7){
-  rolling.data$SF_12 <- predict(pooled_lm, start.data)
+  rolling.data$SF_12 <- predict(pooled_lm, newdata = rolling.data)
   start.data$SF_12 <- rolling.data$SF_12
   rolling.data[, 'time'] <- rolling.data[, 'time'] +1
-  handover.data <- rbind(handover.data, rolling.data)
+  handover.data <- rbind(handover.data, rolling.data[, c("pidp", "SF_12", "time")])
 }
@@
 
-```{r cross_val_handovers}
+```{r cross_val_mice_handovers}
 start.data <- crossval.mice.data[which(crossval.mice.data$time==2013),]
-rolling.data <- start.data[, c("pidp", "SF_12", "time")]
-handover.data <- rolling.data
+rolling.data <- start.data
+handover.data <- rolling.data[, c("pidp", "SF_12", "time")]
 
 for (i in 1:7){
-  rolling.data$SF_12 <- predict(cross.val.sf12.model, start.data)
+  rolling.data$SF_12 <- predict(cross.val.sf12.model, rolling.data)
   start.data$SF_12 <- rolling.data$SF_12
   rolling.data[, 'time'] <- rolling.data[, 'time'] +1
-  handover.data <- rbind(handover.data, rolling.data)
+  handover.data <- rbind(handover.data, rolling.data[, c("pidp", "SF_12", "time")])
 }
@@
 
-lasso.min <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso.min.coefs[, "s1"])
-lasso.1se <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso.1se.coefs[, "s1"])
+lasso.min <-createTexreg(coef.names=rownames(lasso.min.coefs), coef = lasso.min.coefs[, "s1"])
+lasso.1se <-createTexreg(coef.names=rownames(lasso.min.coefs), coef = lasso.1se.coefs[, "s1"])
 
@@
 #coefficients go here.
-texreg_file <- paste0(save.path, 'SF12_Lasso_coefficients.txt')
-tex_label <- paste0("table: sf12_lasso_coefficients") 
-tex_headers <- c(texreg::names2latex("SF_12 LASSO"))
-tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "lasso"))    
-lassoTexReg <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso_coefs[,1], se=lasso_coefs[,2])
-#lassoTexReg2 <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso_coefs[,2])#, lasso_coefs[, 2]))#, pvalues=lasso_coefs[,2])
-#matrixLassoTexReg <- matrixreg(list(lassoTexReg, lassoTexReg2))
+texreg_file <- paste0(save.path, 'SF12_weighted_OLS_coefficients.txt')
+tex_label <- paste0("table: sf12_weighted_coefficients") 
+tex_headers <- c(texreg::names2latex("SF_12 Weighted OLS"))
+tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "weighted_OLS"))
 
-texreg(lassoTexReg, # what model to save coefs for. 
+texreg(pool(sf12.lm.weighted), # what model to save coefs for. 
        file=texreg_file,  # where to save.
@@
 reflect <- T
-yeo_johnson <- F
+yeo_johnson <- T
 include_weights <- T
@@
                   factor(education_state) + 
-                  factor(S7_labour_state) + 
+                  factor(labour_state) + 
                   relevel(factor(NSSEC), ref=1) +
@@
 
-mice.glmm.object@beta <- -mice.glmm.object@beta 
+#mice.glmm.object@beta <- -mice.glmm.object@beta 
 gamma_forest_plot(mice.glmm.object, paste0(save.path, "glmm_forest.pdf"))
-mice.glmm.object@beta <- -mice.glmm.object@beta
+#mice.glmm.object@beta <- -mice.glmm.object@beta
 
@@
 start.data <- start.data[which(start.data$time==2013),]
-start.data$SF_12 <- crossval.glmm.data[which(crossval.glmm.data$time==2013),]$SF_12
+#start.data$SF_12 <- crossval.glmm.data[which(crossval.glmm.data$time==2013),]$SF_12
+if (yeo_johnson == T) {
+start.data$SF_12 <- max_value - predict(yj, start.data$SF_12 +min_value, inverse=T)
 start.data <- drop_na(start.data)
-
+} else {
+  start.data$SF_12 <- max_value - start.data$SF_12
+}
+#start.data$SF_12_last <- max_value - start.data$SF_12_last
 handover.data <- start.data
@@
 for (i in 1:7){
-  if (yeo_johnson) {
-      rolling.data$SF_12 <- max_value - predict(yj,  predict(mice.glmm.object, start.data, type='response',allow.new.levels=T) +min_value, inverse=T)
+  if (yeo_johnson == T) {
+      rolling.data$SF_12 <- predict(mice.glmm.object, rolling.data, type='response',allow.new.levels=T)
+      rolling.data$SF_12_last <- rolling.data$SF_12                           
+      rolling.data$SF_12 <- max_value - predict(yj,  rolling.data$SF_12 +min_value+ rnorm(nrow(rolling.data), 0, 0.3), inverse=T)
   }
   else {
-    rolling.data$SF_12 <- max_value - predict(mice.glmm.object, start.data,type='response',allow.new.levels=T) + rnorm(nrow(rolling.data), 0, 1)
+    rolling.data$SF_12 <- max_value - predict(mice.glmm.object, rolling.data, type='response',allow.new.levels=T) + rnorm(nrow(rolling.data), 0, 1)
+    rolling.data$SF_12_last <- rolling.data$SF_12
   }
@@
   rolling.data$SF_12 <- trunc(rolling.data$SF_12, 0 , 100)
-  rolling.data$SF_12_last <- rolling.data$SF_12
   rolling.data[, 'time'] <- rolling.data[, 'time'] +1

### 2023-12-14 minos/validation/handovers.Rmd
Adding poverty metrics to handovers

--- 2023-12-11 minos/validation/handovers.Rmd
@@
 ```{r}
-start.year <- 2021
+start.year <- 2020
 save.path <- here::here("plots", "handovers", 'default')
@@
 
-## S7 Labour State
+## Poverty
+
+### Absolute poverty
 
 ```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')
 
-lab.state <- prepped.list$var
-lab.state.norm <- prepped.list$norm
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Absolute Poverty'
 
 # Now plot
-ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
+ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
   geom_line() +
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
+  labs(title = tit, subtitle = 'Counts by Level') +
   xlab('Year') +
@@
 
-ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
   geom_bar(stat = 'identity') +
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State') +
+  labs(title = tit) +
   xlab('Year') +
@@
 if (shall.we.save) {
-  ggsave(filename = 'S7_labour_state.png',
+  ggsave(filename = 'absolute_poverty.png',
          plot = last_plot(),
@@
 
-rm(prepped.list, lab.state, lab.state.norm)
+rm(prepped.list, var, norm, tit)
+```
+
+### Relative poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Relative Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'relative_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+### Persistent poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Persistent Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'persistent_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+
+```
+
+### Material Deprivation
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'matdep_child')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Material Deprivation Child'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = matdep_child, colour = matdep_child)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=matdep_child)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'matdep_child.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+
 ```
@@
 ```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'S7_labour_state')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'S7_labour_state',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-## Child Ages
-
-```{r}
-base.child.ages <- base.dat %>%
-  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
-  filter(time > 2009) %>%
-  group_by(time, hidp) %>%
-  summarise(child_ages = find_mode(child_ages))
-
-s<- strsplit(base.child.ages$child_ages, "_")
-
-base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(s, length)), expanded_child_ages = unlist(s))
-base.child.ages.expanded <- base.child.ages.expanded %>%
-  group_by(time, expanded_child_ages) %>%
-  summarise(age_counts = n())
-
-ggplot(data = base.child.ages.expanded, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
-  geom_line() +
-  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
-  scale_colour_viridis_d() +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = base.child.ages.expanded, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
-  geom_line() +
-  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
-  scale_colour_viridis_d() +
-  xlab('Year') +
-  ylab('Count')
-
-base.child.ages.nkids <- base.dat %>%
-  group_by(time, hidp) %>%
-  summarise(nkids_counts = mean(nkids)) %>%
-  group_by(time) %>%
-  summarise(nkids_by_year = sum(nkids_counts))
-
-ggplot(data = base.child.ages.nkids, mapping = aes(x = time, y = nkids_by_year)) +
-  geom_line() +
-  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
 

### 2023-12-15 minos/validation/handovers_S7.Rmd

@@
 ```{r}
-start.year <- 2020
+start.year <- 2021
 save.path <- here::here("plots", "handovers", 'SIPHER7')
@@
 
-shall.we.save <- FALSE
-```
-
-# Weight Testing
-
-```{r}
-raw.weight <- raw.dat %>%
-  select(pidp, time, weight) %>%
-  group_by(time) %>%
-  summarise(mean.weight = mean(weight, na.rm = TRUE))
-
-ggplot(raw.weight, aes(x = time, y = mean.weight)) +
-  geom_line()
-
-raw.weight.WBI <- raw.dat %>%
-  select(pidp, time, weight, ethnicity) %>%
-  filter(ethnicity == 'WBI') %>%
-  group_by(time) %>%
-  summarise(mean.weight = mean(weight, na.rm=TRUE))
-
-ggplot(raw.weight.WBI, aes(x=time, y = mean.weight)) +
-  geom_line()
-
-raw.weight.eth <- raw.dat %>%
-  select(pidp, time, weight, ethnicity) %>%
-  group_by(time, ethnicity) %>%
-  summarise(mean.weight = mean(weight, na.rm = TRUE))
-
-ggplot(raw.weight.eth, aes(x = time, y = mean.weight, group = ethnicity, color = ethnicity)) +
-  geom_line()
+shall.we.save <- TRUE
 ```
@@
 
-### Modified Lineplots
-
-```{r}
-handover_lineplots(raw.dat, base.dat, 'hh_income')
-```
-
-### Boxplots
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'hh_income')
-```
-
 ### Spaghetti
@@
 ```{r}
-# raw.inc <- raw.dat %>%
-#   select(pidp, age, time, hh_income)
-# base.inc <- base.dat %>%
-#   select(pidp, age, time, hh_income)
-# 
-# income.spag <- rbind(raw.inc, base.inc)
-# 
-# spaghetti_plot(income.spag, 'hh_income',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.inc, base.inc, income.spag)
+raw.inc <- raw.dat %>%
+  select(pidp, age, time, hh_income)
+base.inc <- base.dat %>%
+  select(pidp, age, time, hh_income)
+
+income.spag <- rbind(raw.inc, base.inc)
+
+spaghetti_plot(income.spag, 'hh_income',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.inc, base.inc, income.spag)
 ```
@@
 raw.ei <- raw.dat %>% 
-  dplyr::select(pidp, time, equivalent_income, weight) %>%
-  filter(equivalent_income != -9) %>%
+  dplyr::select(pidp, time, equivalent_income) %>%
   group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
+  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
   mutate(source = 'final_US')
@@
 base.ei <- base.dat %>%
-  dplyr::select(pidp, time, equivalent_income, weight) %>%
+  dplyr::select(pidp, time, equivalent_income) %>%
   group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
+  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
   mutate(source = 'baseline_output')
@@
 # onwards because the sample refreshments are messing with the plot
-raw.ei.wave1 <- raw.dat$pidp[raw.dat$time == 2017]
+raw.ei.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
 
 raw.ei.2 <- raw.dat %>% 
-  dplyr::select(pidp, time, equivalent_income, weight) %>%
+  dplyr::select(pidp, time, equivalent_income) %>%
   filter(pidp %in% raw.ei.wave1) %>%
-  filter(equivalent_income != -9) %>%
   group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
+  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
   mutate(source = 'final_US')
@@
 base.ei.2 <- base.dat %>%
-  dplyr::select(pidp, time, equivalent_income, weight) %>%
+  dplyr::select(pidp, time, equivalent_income) %>%
   filter(pidp %in% raw.ei.wave1) %>%
   group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
+  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
   mutate(source = 'baseline_output')
@@
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Equivalent Income', subtitle = 'Wave 9 sample') +
+  labs(title = 'Equivalent Income', subtitle = 'Wave 1 sample') +
   xlab('Year') +
@@
 
-### Modified Lineplots
-
-```{r}
-handover_lineplots(raw.dat, base.dat, 'equivalent_income')
-```
-
-### Check Replenishing Population
-
-Might give us a clue about the big correction in first year of simulation?
-
-```{r}
-repl.file <- here::here('data', 'replenishing', 'replenishing_pop_2019-2070.csv')
-repl.dat <- read.csv(repl.file)
-
-repl.equiv <- repl.dat %>%
-  select(time, equivalent_income, weight) %>%
-  group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
-
-ggplot(repl.equiv, aes(x = time, y = equivalent_income)) +
-  geom_line()
-```
-
-### Boxplots
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'equivalent_income')
-```
-
 ### Spaghetti
@@
 ```{r}
-# raw.ei <- raw.dat %>%
-#   select(pidp, age, time, equivalent_income)
-# base.ei <- base.dat %>%
-#   select(pidp, age, time, equivalent_income)
-# 
-# ei.spag <- rbind(raw.ei, base.ei)
-# 
-# spaghetti_plot(base.ei, 'equivalent_income')
-# 
-# spaghetti_plot(ei.spag, 'equivalent_income',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.ei, base.ei, ei.spag)
+raw.ei <- raw.dat %>%
+  select(pidp, age, time, equivalent_income)
+base.ei <- base.dat %>%
+  select(pidp, age, time, equivalent_income)
+
+ei.spag <- rbind(raw.ei, base.ei)
+
+spaghetti_plot(base.ei, 'equivalent_income')
+
+spaghetti_plot(ei.spag, 'equivalent_income',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.ei, base.ei, ei.spag)
 ```
@@
 ```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, S7_housing_quality)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, S7_housing_quality)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'S7_housing_quality',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+raw.s <- raw.dat %>%
+  select(pidp, age, time, S7_housing_quality)
+base.s <- base.dat %>%
+  select(pidp, age, time, S7_housing_quality)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'S7_housing_quality',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 
-## just look at means in case the means are causing some problems
-raw.dat.2 <- raw.dat
-raw.dat.2$S7_neighbourhood_safety2[raw.dat.2$S7_neighbourhood_safety == 'Often'] <- 1
-raw.dat.2$S7_neighbourhood_safety2[raw.dat.2$S7_neighbourhood_safety == 'Some of the time'] <- 2
-raw.dat.2$S7_neighbourhood_safety2[raw.dat.2$S7_neighbourhood_safety == 'Hardly ever'] <- 3
-base.dat.2 <- base.dat
-base.dat.2$S7_neighbourhood_safety2[base.dat.2$S7_neighbourhood_safety == 'Often'] <- 1
-base.dat.2$S7_neighbourhood_safety2[base.dat.2$S7_neighbourhood_safety == 'Some of the time'] <- 2
-base.dat.2$S7_neighbourhood_safety2[base.dat.2$S7_neighbourhood_safety == 'Hardly ever'] <- 3
-
-handover_lineplots(raw.dat.2, base.dat.2, 'S7_neighbourhood_safety2')
-
 rm(prepped.list, nh_safety, nh_safety.norm)
@@
 ```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, S7_neighbourhood_safety)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, S7_neighbourhood_safety)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'S7_neighbourhood_safety',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+raw.s <- raw.dat %>%
+  select(pidp, age, time, S7_neighbourhood_safety)
+base.s <- base.dat %>%
+  select(pidp, age, time, S7_neighbourhood_safety)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'S7_neighbourhood_safety',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, S7_labour_state)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, S7_labour_state)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'S7_labour_state',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+raw.s <- raw.dat %>%
+  select(pidp, age, time, S7_labour_state)
+base.s <- base.dat %>%
+  select(pidp, age, time, S7_labour_state)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'S7_labour_state',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 
-handover_lineplots(raw.dat, base.dat, 'S7_physical_health')
-
 rm(prepped.list, var, norm, tit)
@@
 ```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, S7_physical_health)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, S7_physical_health)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'S7_physical_health',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+raw.s <- raw.dat %>%
+  select(pidp, age, time, S7_physical_health)
+base.s <- base.dat %>%
+  select(pidp, age, time, S7_physical_health)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'S7_physical_health',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, S7_mental_health)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, S7_mental_health)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'S7_mental_health',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+raw.s <- raw.dat %>%
+  select(pidp, age, time, S7_mental_health)
+base.s <- base.dat %>%
+  select(pidp, age, time, S7_mental_health)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'S7_mental_health',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 tit <- 'Loneliness'
-
-## loneliness only available from 2017 onwards
-var <- filter(var, time >= 2017)
 
@@
 
-pivoted <- filter(pivoted, time >= 2017)
-
 cv_ordinal_plots(pivoted.df = pivoted, 
@@
 ```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, loneliness)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, loneliness)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'loneliness',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+raw.s <- raw.dat %>%
+  select(pidp, age, time, loneliness)
+base.s <- base.dat %>%
+  select(pidp, age, time, loneliness)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'loneliness',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, education_state)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, education_state)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'education_state',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+raw.s <- raw.dat %>%
+  select(pidp, age, time, education_state)
+base.s <- base.dat %>%
+  select(pidp, age, time, education_state)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'education_state',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-# raw.s <- raw.parity %>%
-#   select(pidp, age, time, nkids_ind)
-# base.s <- base.parity %>%
-#   select(pidp, age, time, nkids_ind)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'nkids_ind',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
+raw.s <- raw.parity %>%
+  select(pidp, age, time, nkids_ind)
+base.s <- base.parity %>%
+  select(pidp, age, time, nkids_ind)
 
-## Job Sec
+spag <- rbind(raw.s, base.s)
 
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'job_sec')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Job NSSEC'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = job_sec, colour = job_sec)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=job_sec)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'job_sec.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat,
-                                  df1.name = 'simulated', 
-                                  df2 = raw.dat, 
-                                  df2.name = 'raw', 
-                                  var = 'job_sec')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'job_sec',
+spaghetti_plot(spag, 'nkids_ind',
                save = shall.we.save,
                save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```

### 2023-12-15 minos/validation/handovers.Rmd

--- 2023-12-11 minos/validation/handovers.Rmd
@@
 ---
-title: "MINOS Handover Plots"
+params:
+    file_path: '' # default arguments. specify others in command line.
+    intervention: ''
+title: "`r paste(params$file_path, ' ', params$intervention, ' Handover Plots')`"
 output:
+  #output_file: "`r paste('minos/validation/', params$file_path, '_', params$intervention, '_handovers.html') `"
   html_document:
@@
     code_folding: hide
+
 ---
@@
 ```{r}
+
+file_path <- params$file_path
+intervention <- params$intervention
+
 # Read raw datafiles in
@@
 
-out.path <- here::here('output', 'default_config/')
-base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+#out.path <- here::here('output', 'default_config/')
+#base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+
+out.path <- here::here('output', file_path)
+base.dat <- read_singular_local_out(out.path, intervention, drop.dead = TRUE)
 ```
@@
 ```{r}
+raw.child.ages <- raw.dat %>%
+  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
+  filter(time > 2013) %>%
+  group_by(time, hidp) %>%
+  summarise(child_ages = find_mode(child_ages))
+
+r.s<- strsplit(raw.child.ages$child_ages, "_")
+
+raw.child.ages.expanded <- data.frame(time = rep(raw.child.ages$time, sapply(r.s, length)), expanded_child_ages = unlist(r.s))
+raw.child.ages.expanded <- raw.child.ages.expanded %>%
+  group_by(time, expanded_child_ages) %>%
+  summarise(age_counts = n()) %>%
+  mutate(source = 'final_US') %>%
+  filter(expanded_child_ages <= 16)
+
 base.child.ages <- base.dat %>%
@@
 
-s<- strsplit(base.child.ages$child_ages, "_")
+b.s<- strsplit(base.child.ages$child_ages, "_")
 
-base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(s, length)), expanded_child_ages = unlist(s))
+base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(b.s, length)), expanded_child_ages = unlist(b.s))
 base.child.ages.expanded <- base.child.ages.expanded %>%
   group_by(time, expanded_child_ages) %>%
-  summarise(age_counts = n())
+  summarise(age_counts = n()) %>%
+  mutate(source = 'baseline')
 
-ggplot(data = base.child.ages.expanded, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
+combined <- rbind(raw.child.ages.expanded, base.child.ages.expanded)
+
+ggplot(data = combined, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
   geom_line() +
+  geom_vline(xintercept = start.year) +
   labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
@@
 
-ggplot(data = base.child.ages.expanded, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
+ggplot(data = combined, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
   geom_line() +
+  geom_vline(xintercept = start.year) +
   labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
@@
   group_by(time) %>%
-  summarise(nkids_by_year = sum(nkids_counts))
+  summarise(nkids_by_year = sum(nkids_counts)) %>%
+  mutate(source = 'baseline')
 
-ggplot(data = base.child.ages.nkids, mapping = aes(x = time, y = nkids_by_year)) +
+raw.child.ages.nkids <- raw.dat %>%
+  group_by(time, hidp) %>%
+  summarise(nkids_counts = mean(nkids)) %>%
+  group_by(time) %>%
+  summarise(nkids_by_year = sum(nkids_counts)) %>%
+  mutate(source = 'final_US')
+
+combined.nkids <- rbind(base.child.ages.nkids, raw.child.ages.nkids)
+
+ggplot(data = combined.nkids, mapping = aes(x = time, y = nkids_by_year, group = source, colour = source)) +
   geom_line() +

### 2023-12-15 minos/validation/handovers.Rmd
adding file path option to handovers.Rmd:

--- 2023-12-14 minos/validation/handovers.Rmd
@@
 
-## Poverty
-
-### Absolute poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Absolute Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'absolute_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-### Relative poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Relative Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'relative_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-### Persistent poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Persistent Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'persistent_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-
-```
-
-### Material Deprivation
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'matdep_child')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Material Deprivation Child'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = matdep_child, colour = matdep_child)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=matdep_child)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'matdep_child.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-
-```
-
 ```{r}

### 2023-12-19 minos/validation/cross_validation_default.Rmd
Adding poverty vars to handovers and cross-validation

--- 2023-12-11 minos/validation/cross_validation_default.Rmd
@@
 
-## hhsize
+## Household Size
 
@@
 
-## housing tenure
+## Housing Tenure
 
@@
 
-## Job Sec
+# CHILD POVERTY VARS
+
+## Relative Poverty
 
 ```{r}
-jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
+relative_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
                                                    df1.name = 'simulated', 
@@
                                                    df2.name = 'raw', 
-                                          var = 'job_sec')
+                                                   var = 'relative_poverty')
 
-cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
-                 var = 'job_sec',
+cv_ordinal_plots(pivoted.df = relative_poverty.pivoted, 
+                 var = 'relative_poverty',
                  save = FALSE)
-rm(jobsec.pivoted)
+rm(relative_poverty.pivoted)
 ```
 
-## Hourly Wage
+## Absolute Poverty
 
 ```{r}
-cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hourly_wage')
-multi_year_boxplots(raw, cv, 'hourly_wage')
-q_q_comparison(raw, cv, 'hourly_wage')
+absolute_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                                   df1.name = 'simulated', 
+                                                   df2 = raw, 
+                                                   df2.name = 'raw', 
+                                                   var = 'absolute_poverty')
+
+cv_ordinal_plots(pivoted.df = absolute_poverty.pivoted, 
+                 var = 'absolute_poverty',
+                 save = FALSE)
+rm(absolute_poverty.pivoted)
 ```
 
-## Children Ageing
-
-Children ageing is now calculated in MINOS.
+## Material Deprivation
 
 ```{r}
+matdep_child.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                               df1.name = 'simulated', 
+                                               df2 = raw, 
+                                               df2.name = 'raw', 
+                                               var = 'matdep_child')
 
-format_child_age_data <- function(dataset) {
-  formatted.age.data <- dataset %>%
-                        dplyr::select(hidp, time, child_ages, pidp) %>%
-                        filter(time >= 2014) %>%
-                        group_by(time, pidp) %>%
-                        summarise(child_ages = max(child_ages))
-
-  split.ages <- strsplit(formatted.age.data$child_ages, "_")
-
-  child.ages.expanded <- data.frame(time = rep(formatted.age.data$time, sapply(split.ages, length)), 
-                                    #hidp= rep(formatted.age.data$hidp, sapply(split.ages, length)), 
-                                    pidp= rep(formatted.age.data$pidp, sapply(split.ages, length)), 
-                                    expanded_child_ages = as.numeric(unlist(split.ages)))
-
-  #child.ages.expanded <- child.ages.expanded %>%
-  #  group_by(pidp, time) %>%
-  #  summarise(expanded_child_ages = median(expanded_child_ages))
-
-  return (child.ages.expanded)
-}
-
-find_mode <- function(x) {
-  u <- unique(x)
-  tab <- tabulate(match(x, u))
-  u[tab == max(tab)]
-}
-
-cv.child.ages <- format_child_age_data(cv)
-cv1.child.ages <- format_child_age_data(cv1)
-cv2.child.ages <- format_child_age_data(cv2)
-cv3.child.ages <- format_child_age_data(cv3)
-cv4.child.ages <- format_child_age_data(cv4)
-cv5.child.ages <- format_child_age_data(cv5)
-raw.child.ages <- format_child_age_data(raw.dat)
-
-cv.mean.plots(cv1.child.ages, cv2.child.ages, cv3.child.ages, cv4.child.ages, cv5.child.ages, raw.child.ages, 'expanded_child_ages')
-multi_year_boxplots(raw.child.ages, cv.child.ages, 'expanded_child_ages')
-q_q_comparison(raw.child.ages, cv.child.ages, 'expanded_child_ages')
-
+cv_ordinal_plots(pivoted.df = matdep_child.pivoted, 
+                 var = 'matdep_child',
+                 save = FALSE)
+rm(matdep_child.pivoted)
 ```
 
+## Low Income and Material Deprivation
+
 ```{r}
-#nkids
+low_income_matdep_child.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                                          df1.name = 'simulated', 
+                                                          df2 = raw, 
+                                                          df2.name = 'raw', 
+                                                          var = 'low_income_matdep_child')
 
-format_nkids_data <- function(dataset) {
-  dataset %>%
-  group_by(hidp, time, pidp) %>%
-  summarise(nkids = max(nkids)) %>%
-  #group_by(time) %>%
-  #summarise(nkids_by_year = sum(nkids_counts))
-  return (dataset)
-}
+cv_ordinal_plots(pivoted.df = low_income_matdep_child.pivoted, 
+                 var = 'low_income_matdep_child',
+                 save = FALSE)
+rm(low_income_matdep_child.pivoted)
+```
 
-cv.nkids <- format_nkids_data(cv)
-cv1.nkids <- format_nkids_data(cv1)
-cv2.nkids <- format_nkids_data(cv2)
-cv3.nkids <- format_nkids_data(cv3)
-cv4.nkids <- format_nkids_data(cv4)
-cv5.nkids <- format_nkids_data(cv5)
-raw.nkids <- format_nkids_data(raw.dat)
+## Persistent Poverty
 
-cv.mean.plots(cv1.nkids, cv2.nkids, cv3.nkids, cv4.nkids, cv5.nkids, raw.nkids, 'nkids')
-multi_year_boxplots(raw.nkids, cv.nkids, 'nkids')
-q_q_comparison(raw.nkids, cv.nkids, 'nkids')
+```{r}
+persistent_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                                     df1.name = 'simulated', 
+                                                     df2 = raw, 
+                                                     df2.name = 'raw', 
+                                                     var = 'persistent_poverty')
+
+cv_ordinal_plots(pivoted.df = persistent_poverty.pivoted, 
+                 var = 'persistent_poverty',
+                 save = FALSE)
+rm(persistent_poverty.pivoted)
 ```

### 2023-12-19 minos/validation/handovers.Rmd
Adding poverty vars to handovers and cross-validation

--- 2023-12-14 minos/validation/handovers.Rmd
@@
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+# out.path <- here::here('output', 'child_poverty_config/')
+# base.dat <- read_singular_local_out(out.path, 'ChildPovertyIntervention', drop.dead = TRUE)
 ```
@@
 
-## Poverty
-
-### Absolute poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Absolute Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'absolute_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
+## CHILD POVERTY VARS
 
@@
 
-### Persistent poverty
+### Absolute Poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Absolute Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'absolute_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+### Persistent Poverty
 
@@
 
-### Material Deprivation
+### Low Income and Material Deprivation
 
 ```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'matdep_child')
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')
 
@@
 # Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = matdep_child, colour = matdep_child)) +
+ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
   geom_line() +
@@
 
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=matdep_child)) +
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
   geom_bar(stat = 'identity') +
@@
 if (shall.we.save) {
-  ggsave(filename = 'matdep_child.png',
+  ggsave(filename = 'low_income_matdep_child.png',
          plot = last_plot(),

### 2024-01-03 minos/outcomes/paper_1_notebook.Rmd
adding more MICE plots

@@
   saveRDS(mice_set, "data/transitions/MICE_set.rds")
+}
+
+```
+
+```{r mar_analyses}
+
+aux_vars <- c("SF_12",
+              #"SF_12p",
+              #"smoker",
+              "nkids",       
+              "behind_on_bills",
+              "financial_situation",
+              "future_financial_situation",
+              "likely_move",
+              "ghq_depression",
+              "ghq_happiness",
+              "clinical_depression", 
+              "scsf1",
+              "health_limits_social")
+ggmice::plot_corr(mice.data[, aux_vars])
+
+pre.mice.lm <- lm(mice_formula_string, data=mice.data, weights = weight)
+forest_plot(pre.mice.lm , paste0(save.path,'mice_SF12_forest.pdf'))
+qq_plot(resid(pre.mice.lm ), paste0(save.path, "mice_qq.pdf"))
+
+# writing coefficients table for MICE. 
+# is there a version for pool table?
+write_coefs <- T
+if (write_coefs)
+{
+  texreg_file <- paste0(save.path, 'SF12_without_MICE_OLS_coefficients.txt')
+  tex_label <- paste0("table: without_MICE_OLS_coefficients") 
+  tex_headers <- c(texreg::names2latex("Without MICE SF_12 OLS"))
+  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "without_mice"))    
+  texreg(mice.lm.object, # what model to save coefs for. 
+         file=texreg_file,  # where to save.
+         custom.model.names = tex_headers, # title of table.
+         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
+         digits=4, # p values significant figures.
+         caption=tex_caption, # \caption command option. 
+         label = tex_label, # \label command option. 
+         dcolumn=T,# nice column alignment. 
+         booktabs=T, # nice hlines. (recommended)
+         tabular=T,# tabular env.
+         single.row = T, # nicer one row formatting.
+         longtable=T, # allows tables to wrap over pages
+         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
+         fontsize='small') # small font
+
+  # same again for MICE pool. 
+  texreg_file <- paste0(save.path, 'SF12_MICE_pool_OLS_coefficients.txt')
+  tex_label <- paste0("table: MICE_pool_OLS_coefficients") 
+  tex_headers <- c(texreg::names2latex("MICE SF_12 OLS Pool"))
+  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "ols"))    
+  texreg(final.pool, # what model to save coefs for. 
+         file=texreg_file,  # where to save.
+         custom.model.names = tex_headers, # title of table.
+         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
+         digits=4, # p values significant figures.
+         caption=tex_caption, # \caption command option. 
+         label = tex_label, # \label command option. 
+         dcolumn=T,# nice column alignment. 
+         booktabs=T, # nice hlines. (recommended)
+         tabular=T,# tabular env.
+         single.row = T, # nicer one row formatting.
+         longtable=T, # allows tables to wrap over pages
+         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
+         fontsize='small') # small font
 }

### 2024-01-05 minos/outcomes/EI_allScen_Plots.Rmd
Amelia still WIP. Added script for visualising various things from interventions in Equivalent Income terms

--- 2023-09-12 minos/outcomes/EI_EnergyCrisis_PresPlots.Rmd
@@
 ```{r}
-# S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
-#                  'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
-#                  'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
-# out.path.batch <- here::here('output', 'SIPHER7_batch/')
-# 
-# base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
-# wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-# energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-# child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-# pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
+                 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
+                 'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
+out.path.batch <- here::here('output', 'SIPHER7_batch/')
 
-out.path.arc <- here::here('output', 'SIPHER7_batch_ARC/')
+base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
+wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+
+#out.path.arc <- here::here('output', 'SIPHER7_batch_ARC/')
 
@@
 ## second batch dump
-out.path.arc2 <- here::here('output', 'batch')
-
-#target.pattern <- paste0('aggregated_run_id_', year, '.csv')
-base.list <- list.files(path = paste0(out.path.arc2, '/baseline'),
-                            full.names = TRUE)
-base.batch <- do.call(rbind, lapply(base.list, read.csv))
-
-energy.list <- list.files(path = paste0(out.path.arc2, '/energy'),
-                            full.names = TRUE)
-energy.batch <- do.call(rbind, lapply(energy.list, read.csv))
+# out.path.arc2 <- here::here('output', 'batch')
+# 
+# #target.pattern <- paste0('aggregated_run_id_', year, '.csv')
+# base.list <- list.files(path = paste0(out.path.arc2, '/baseline'),
+#                             full.names = TRUE)
+# base.batch <- do.call(rbind, lapply(base.list, read.csv))
+# 
+# energy.list <- list.files(path = paste0(out.path.arc2, '/energy'),
+#                             full.names = TRUE)
+# energy.batch <- do.call(rbind, lapply(energy.list, read.csv))
 
@@
 base.batch <- calc_age_group(base.batch)
+wage.batch <- calc_age_group(wage.batch)
 energy.batch <- calc_age_group(energy.batch)
+child.batch <- calc_age_group(child.batch)
+pov.batch <- calc_age_group(pov.batch)
 ```
@@
 base.batch <- calc_income_quintile(base.batch)
+wage.batch <- calc_income_quintile(wage.batch)
 energy.batch <- calc_income_quintile(energy.batch)
+child.batch <- calc_income_quintile(child.batch)
+pov.batch <- calc_income_quintile(pov.batch)
 ```
@@
 income_equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
+income_equivinc_change_batch(base.batch, wage.batch, 'Living Wage')
+income_equivinc_change_batch(base.batch, child.batch, 'All Child Uplift')
+income_equivinc_change_batch(base.batch, pov.batch, 'Poverty Child Uplift')
 ```
@@
 equivinc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
+
+inc_change_batch_subpop(base.batch, wage.batch, 'Living Wage', group.var = 'income.quint')
+equivinc_change_batch_subpop(base.batch, wage.batch, 'Living Wage', group.var = 'income.quint')
+
+inc_change_batch_subpop(base.batch, child.batch, 'All Child Uplift', group.var = 'income.quint')
+equivinc_change_batch_subpop(base.batch, child.batch, 'All Child Uplift', group.var = 'income.quint')
+
+inc_change_batch_subpop(base.batch, pov.batch, 'Poverty Child Uplift', group.var = 'income.quint')
+equivinc_change_batch_subpop(base.batch, pov.batch, 'Poverty Child Uplift', group.var = 'income.quint')
 ```

### 2024-01-05 minos/outcomes/EI_allScen_Plots.Rmd
Additions to the EI plotting script

@@
 
-income_equivinc_percent_change_batch(base.batch, int.batch, int.name, group.var = 'income.quint')
+income_equivinc_percent_change_batch(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
+income_equivinc_percent_change_batch(base.batch, wage.batch, 'Living Wage', group.var = 'income.quint')
+income_equivinc_percent_change_batch(base.batch, child.batch, 'All Child Uplift', group.var = 'income.quint')
+income_equivinc_percent_change_batch(base.batch, pov.batch, 'Povety Child Uplift', group.var = 'income.quint')
 ```
@@
 S7_ordinal_pathway_batch(base.batch, energy.batch, 'Energy Crisis', 'S7_housing_quality')
+S7_ordinal_pathway_batch(base.batch, wage.batch, 'Living Wage', 'S7_housing_quality')
+S7_ordinal_pathway_batch(base.batch, child.batch, 'All Child Uplift', 'S7_housing_quality')
+S7_ordinal_pathway_batch(base.batch, pov.batch, 'Poverty Child Uplift', 'S7_housing_quality')
 ```
@@
 ```{r}
-S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
-S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
-S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health')
-S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health')
-S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness')
+# S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
+# S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
+# S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health')
+# S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health')
+# S7_pathway_change_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness')
 ```
@@
 ```{r}
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness')
+# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
+# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety')
+# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health')
+# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health')
+# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness')
 ```
@@
 ```{r}
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_housing_quality')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_neighbourhood_safety')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_physical_health')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_mental_health')
-S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'loneliness')
+# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_housing_quality')
+# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_neighbourhood_safety')
+# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_physical_health')
+# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'S7_mental_health')
+# S7_cumulative_pathwayChange_byGroup(base.batch, energy.batch, group.var = 'age.group', var = 'loneliness')
 ```
@@
 ```{r}
-group.var <- 'income.quint'
-var <- 'S7_mental_health'
-
-base.sub <- base.batch %>%
-  select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
-  rename(Baseline_var = S7_mental_health,
-         Baseline_income.quint = income.quint)
-
-int.sub <- energy.batch %>%
-  select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
-  rename(Intervention_var = S7_mental_health,
-         Intervention_income.quint = income.quint)
-
-merged <- merge(base.sub, int.sub,
-                by=c('pidp', 'time', 'run_id'),
-                all = FALSE)
-
-#combined <- rbind(base.sub, int.sub)
+# group.var <- 'income.quint'
+# var <- 'S7_mental_health'
+# 
+# base.sub <- base.batch %>%
+#   select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
+#   rename(Baseline_var = S7_mental_health,
+#          Baseline_income.quint = income.quint)
+# 
+# int.sub <- energy.batch %>%
+#   select(pidp, time, run_id, all_of(group.var), all_of(var)) %>%
+#   rename(Intervention_var = S7_mental_health,
+#          Intervention_income.quint = income.quint)
+# 
+# merged <- merge(base.sub, int.sub,
+#                 by=c('pidp', 'time', 'run_id'),
+#                 all = FALSE)
+# 
+# #combined <- rbind(base.sub, int.sub)
 
@@
 # move further analysis here so we don't have to do that expensive merge every time
-merged2 <- merged %>%
-  mutate(varChange = Intervention_var - Baseline_var,
-         effect = case_when(varChange > 0 ~ "Positive",
-                            varChange < 0 ~ "Negative",
-                            varChange == 0 ~ "No_Change")) %>%
-  select(-Baseline_var, -Intervention_var, -Intervention_income.quint, -varChange) %>%
-  rename(income.quint = Baseline_income.quint) %>%
-  group_by(time, run_id, .data[[group.var]], effect) %>%
-  count() %>%
-  group_by(time, run_id, .data[[group.var]]) %>%
-  mutate(total = sum(n),
-         effect_prop = n / total) %>%
-  select(-n, -total) %>%
-  group_by(time, .data[[group.var]], effect) %>%
-  summarise(effect_prop = mean(effect_prop)) %>%
-  pivot_wider(names_from = 'effect',
-              values_from = 'effect_prop') %>%
-  mutate(change = Positive - Negative) %>%
-  select(-Positive, -Negative, -No_Change, -time) %>%
-  group_by(.data[[group.var]]) %>%
-  summarise(change = sum(change))
-
-ggplot(data = merged2, aes(x = income.quint, y = change)) +
-  geom_col()
+# merged2 <- merged %>%
+#   mutate(varChange = Intervention_var - Baseline_var,
+#          effect = case_when(varChange > 0 ~ "Positive",
+#                             varChange < 0 ~ "Negative",
+#                             varChange == 0 ~ "No_Change")) %>%
+#   select(-Baseline_var, -Intervention_var, -Intervention_income.quint, -varChange) %>%
+#   rename(income.quint = Baseline_income.quint) %>%
+#   group_by(time, run_id, .data[[group.var]], effect) %>%
+#   count() %>%
+#   group_by(time, run_id, .data[[group.var]]) %>%
+#   mutate(total = sum(n),
+#          effect_prop = n / total) %>%
+#   select(-n, -total) %>%
+#   group_by(time, .data[[group.var]], effect) %>%
+#   summarise(effect_prop = mean(effect_prop)) %>%
+#   pivot_wider(names_from = 'effect',
+#               values_from = 'effect_prop') %>%
+#   mutate(change = Positive - Negative) %>%
+#   select(-Positive, -Negative, -No_Change, -time) %>%
+#   group_by(.data[[group.var]]) %>%
+#   summarise(change = sum(change))
+# 
+# ggplot(data = merged2, aes(x = income.quint, y = change)) +
+#   geom_col()
 ```
@@
 ```{r}
-simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality', print = TRUE)
-simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety', print = TRUE)
-simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health', print = TRUE)
-simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health', print = TRUE)
-simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness', print = TRUE)
+# simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality', print = TRUE)
+# simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_neighbourhood_safety', print = TRUE)
+# simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_mental_health', print = TRUE)
+# simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_physical_health', print = TRUE)
+# simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'loneliness', print = TRUE)
 ```
@@
 
+sccb_all_vars <- function(base.batch, int.batch, group.var, varlist) {
   df <- simplified_component_change(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
@@
                  values_to = 'Change')
-
-ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
+  p1 <- ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
   geom_col() +
@@
         axis.ticks.x = element_blank())
+  print(p1)
+}
+
+sccb_all_vars(base.batch, energy.batch, group.var = 'income.quint', varlist = varlist)
+sccb_all_vars(base.batch, wage.batch, group.var = 'income.quint', varlist = varlist)
+sccb_all_vars(base.batch, child.batch, group.var = 'income.quint', varlist = varlist)
+sccb_all_vars(base.batch, pov.batch, group.var = 'income.quint', varlist = varlist)
+
 ```
@@
 
-df <- simplified_component_change_BOXPLOT(base.batch, energy.batch, group.var = 'income.quint', var = 'S7_housing_quality')
+sccb_all_vars_BOXPLOT <- function(base.batch, int.batch, group.var, varlist) {
+  df <- simplified_component_change_BOXPLOT(base.batch, energy.batch, group.var = group.var, var = 'S7_housing_quality')
   colnames(df) <- c('run_id', 'Income_Quintile', 'S7_housing_quality')
@@
 
-ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
+  p1 <- ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
     geom_boxplot(notch = FALSE) +
@@
           axis.ticks.x = element_blank())
+  print(p1)
+}
+
+sccb_all_vars_BOXPLOT(base.batch, energy.batch, group.var = 'income.quint', varlist = varlist)
+sccb_all_vars_BOXPLOT(base.batch, wage.batch, group.var = 'income.quint', varlist = varlist)
+sccb_all_vars_BOXPLOT(base.batch, child.batch, group.var = 'income.quint', varlist = varlist)
+sccb_all_vars_BOXPLOT(base.batch, pov.batch, group.var = 'income.quint', varlist = varlist)
 ```

### 2024-01-05 minos/outcomes/equivalent_income_out_batch.Rmd
Forgot to track the script...

@@
 ```{r}
-# S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
-#                  'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
-#                  'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
-# out.path.batch <- here::here('output', 'SIPHER7_batch/')
+S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
+                 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
+                 'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
+out.path.batch <- here::here('output', 'SIPHER7/')
+
+base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
+wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+
+# out.path.arc <- here::here('output', 'SIPHER7_batch_ARC/')
 # 
-# base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
-# wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-# energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-# child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-# pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-
-out.path.arc <- here::here('output', 'SIPHER7_batch_ARC/')
-
-base.batch <- read.csv(paste0(out.path.arc, 'baseline_batch_aggregated.csv'))
-wage.batch <- read.csv(paste0(out.path.arc, 'wage_batch_aggregated.csv'))
-energy.batch <- read.csv(paste0(out.path.arc, 'energy_batch_aggregated.csv'))
-child.batch <- read.csv(paste0(out.path.arc, 'child_batch_aggregated.csv'))
-pov.batch <- read.csv(paste0(out.path.arc, 'pov_batch_aggregated.csv'))
+# base.batch <- read.csv(paste0(out.path.arc, 'baseline_batch_aggregated.csv'))
+# wage.batch <- read.csv(paste0(out.path.arc, 'wage_batch_aggregated.csv'))
+# energy.batch <- read.csv(paste0(out.path.arc, 'energy_batch_aggregated.csv'))
+# child.batch <- read.csv(paste0(out.path.arc, 'child_batch_aggregated.csv'))
+# pov.batch <- read.csv(paste0(out.path.arc, 'pov_batch_aggregated.csv'))
 ```

### 2024-01-06 minos/testing/clustering_EI.Rmd
Clustering script and tweaks to some utils

---
params:
    out_path: 'SIPHER7_batch/' # default arguments. specify others in command line.
    intervention: 'livingWageIntervention'
    type: 'batch'
title: "`r paste(params$file_path, ' ', params$intervention, ' ', params$type, ' CLUSTER ANALYSIS')`"
output: 
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)
require(cluster)
require(foreach)
require(doParallel)
require(clustMixType)
require(ggplot2)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
)
rm(workingDir)
```

Source utils for some functions.

```{r}
source(here::here('minos', 'transitions', 'utils.R'))
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
source(here::here('minos', 'utils_S7.R'))
```

## Data

```{r}
## Parameters
out.path.batch <- here::here('output', params$out_path)
intervention <- params$intervention
out.type <- params$type

# base.dat <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
# wage.dat <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# energy.dat <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# child.dat <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# pov.dat <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)

if (out.type == 'batch') {
  S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
                 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
                 'ethnicity', 'age', 'sex', 'region', 'job_sec', 'education_state', 'nkids_ind', 'hourly_wage')

  base.dat <- read_batch_out_summarise(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
  int.dat <- read_batch_out_summarise(out.path.batch, paste0(intervention, '/'), start.year = 2021, var.list = c('income_boosted', 'boost_amount', S7.var.list))
} else if (out.type == 'single') {
  base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
  int.dat <- read_singular_local_out(out.path, intervention, drop.dead = TRUE)
} else {
  print('You have supplied an incorrect output type. The options are batch or
        single.')
}
```

```{r}

large_df <- base.dat

# Function to identify variable types
variable_type <- function(x) {
  if (is.numeric(x) && !is.integer(x)) {
    return("continuous")  # float values
  } else if (is.numeric(x) && is.integer(x) && length(unique(x)) > 15) {
    return("continuous")  # int but lots of unique values
  } else if (is.numeric(x) && is.integer(x) && length(unique(x)) < 15) {
    return("ordinal")
  } else if (is.character(x)) {
    return("nominal")
  } else {
    return("other")
  }
}

# Now identify columns and calculate summary values
# Define a list of columns to group by
group_cols <- c("pidp", "hidp", "time")

# Identify variable types
var_types <- sapply(large_df, variable_type)

# Separate variables by type
continuous_vars <- names(var_types[var_types == "continuous"])
ordinal_vars <- names(var_types[var_types == "ordinal"])
nominal_vars <- names(var_types[var_types == "nominal"])

# Calculate mean for continuous variables and mode for ordinal and nominal variables
result_df <- large_df %>%
  group_by(across(all_of(group_cols))) %>%
  summarize(
    across(all_of(setdiff(continuous_vars, group_cols)), mean, na.rm = TRUE),
    across(all_of(ordinal_vars), ~ mode(.x)),
    across(all_of(nominal_vars), ~ mode(.x))
  )
```

Some data preparation.

```{r}
calc_age_group <- function(batch.dat) {
  batch.dat <- batch.dat %>%
    mutate(age.group = cut(age, 
                            breaks = c(15, 30, 45, 60, 75, 120),
                            labels = c('16-30', '30-45', '45-60', '60-75', '75+')))
  return(batch.dat)
}

calc_income_quintile <- function(batch.dat) {
  batch.dat <- batch.dat %>%
    mutate(income.quint = cut(batch.dat$hh_income, breaks=c(quantile(batch.dat$hh_income, probs = seq(0, 1, by = 0.20))), 
                          labels=c(1,2,3,4,5), include.lowest=TRUE))
}

base.dat <- calc_age_group(base.dat)
int.dat <- calc_age_group(int.dat)

base.dat <- calc_income_quintile(base.dat)
int.dat <- calc_income_quintile(int.dat)
```

# CLUSTERING

Going to start with the k-prototypes algorithm as this is a clustering algorithm that can handle ordinal and continuous input variables.

Also need to be clear about the structure of this clustering. I am going to cluster individuals in a single year (start wit 2030) based on the change in each component variable (i.e. S7_mental_health) and the change in Equivalent Income. I can then investigate the clusters and look at things like:
- age range
- other demographics characteristics (sex, ethnicity, region, education_state)
- Change in components (is one group dominated by people who improved housing_quality for example?)
- Change in Equivalent Income

```{r}
# # first add scenario column to each
# base <- base.dat %>%
#   mutate(scenario = 'baseline',
#          boost_amount = 0,
#          income_boosted = 0)
# int <- int.dat %>%
#   mutate(scenario = 'LivingWage')
```

```{r}
# so need a function to generate a dataframe with all those additional metrics for the clustering

calculate_clustering_metrics <- function(base.dat, int.dat, int.name, target.year) {

  # first add scenario column to each
  base.dat <- base.dat %>%
    mutate(scenario = 'baseline',
           boost_amount = 0,
           income_boosted = 0)
  int.dat <- int.dat %>%
    mutate(scenario = int.name)

  miss.cols <- setdiff(names(int.dat), names(base.dat))
  print('Missing Columns!')
  print(miss.cols)

  # now bind together before subsetting
  combined <- rbind(base.dat, int.dat)

  # drop the original datafiles now for better memory handling with batch
  rm(base.dat, int.dat)

  combined <- combined %>%
    select(pidp, hidp, time, scenario, age, age.group, sex, ethnicity, region, education_state, hh_income, equivalent_income, S7_housing_quality, S7_neighbourhood_safety, S7_physical_health, S7_mental_health, S7_labour_state, loneliness, job_sec, hourly_wage)

  combined$S7_housing_quality <- as.numeric(factor(combined$S7_housing_quality,
                                          levels = c('No to all',
                                                     'Yes to some',
                                                     'Yes to all'),
                                          labels = c(1, 2, 3)))

  combined$S7_neighbourhood_safety <- as.numeric(factor(combined$S7_neighbourhood_safety,
                                               levels = c('Often',
                                                          'Some of the time',
                                                          'Hardly ever'),
                                               labels = c(1, 2, 3)))

  combined$loneliness <- as.numeric(factor(combined$loneliness,
                                  levels = c(1, 2, 3),
                                  labels = c(3, 2, 1)))

  # Now calculate metrics. We need:
  # - change in Equivalent Income
  # - change in components
  #
  # This is all change from start.year (usually 2021) to target.year (start with 2031)
  combined <- combined %>%
    filter(time %in% c(target.year)) %>%
    pivot_wider(
      names_from = 'scenario',
      values_from = c('age', 'age.group', 'sex', 'ethnicity', 'region', 'education_state', 'hh_income', 'equivalent_income', 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness', 'job_sec', 'hourly_wage')
    )

  return(combined)

  combined <- combined[complete.cases(combined), ]
  #return(combined)

  ############# Now calculate the difference between intervention and baseline in target.year ###########
  # List of variables to ignore (no difference calculation)
  ignore_vars <- c('pidp', 'hidp', 'time')
  rename_vars <- c("age", "sex", "ethnicity", "region", "age.group", "S7_labour_state", "education_state")

  for (var in rename_vars) {
    combined <- combined %>%
      select(-contains(paste0(var, '_LivingWage'))) %>%
      rename(!!var := .data[[paste0(var, '_baseline')]])
  }

  # Get the names of all variables in the 'combined' dataframe
  all_vars <- names(combined)

  # Find the variables that are in 'all_vars' but not in 'ignore_vars' or 'rename_vars'
  remaining_vars <- setdiff(all_vars, c(ignore_vars, rename_vars))
  # drop the scenarios suffixes
  remaining_vars <- lapply(remaining_vars, function(x) modified_string <- sub("_[^_]*$", "", x))
  remaining_vars <- unique(remaining_vars)

  for (var in remaining_vars) {
    base.var <- paste0(var, '_baseline')
    int.var <- paste0(var, '_', int.name)

    combined <- combined %>%
      mutate(!!var := !!sym(int.var) - !!sym(base.var)) %>%
      select(-base.var, -int.var)
  }

  # Final step is to pivot long to get the run_id column back
  combined <- combined %>%
    pivot_longer(age_baseline_1)

  return(combined)
}

# First calculate clustering metrics
combined <- calculate_clustering_metrics(base.dat, int.dat, int.name = intervention, target.year = 2031)
# Now remove original data for better memory handling
#rm(base.dat, int.dat)
```

```{r}
run_clustering <- function(combined) {

  # Identify categorical columns
  categorical_cols <- c('sex', 'ethnicity', 'region', 'education_state', 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness', 'job_sec')

  # Convert categorical variables to factors
  combined[, categorical_cols] <- lapply(combined[, categorical_cols], as.factor)

  cluster_model <- kproto(x = combined,
                    k = 4, 
                    num_rounds = 20, 
                    verbose = FALSE, 
                    cat.vars = which(names(combined) %in% categorical_cols))

  return(cluster_model)
}

clust <- run_clustering(combined)
```

## Plotting

```{r}
# Now analyze the clustering output
table(clust$cluster)

cluster_profiles <- aggregate(combined, by = list(clust$cluster), FUN = function(x) {
  if (is.numeric(x)) mean(x) else names(sort(table(x), decreasing = TRUE)[1])
})

plot.vars <- c('age', 'region', 'education_state', 'hh_income', 'equivalent_income', 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness', 'job_sec', 'hourly_wage')

for (var in plot.vars) {
  p1 <-ggplot(combined, aes(x = factor(clust$cluster), y = .data[[var]])) +
    geom_boxplot() +
    labs(x = "Cluster", y = var) +
    theme_minimal()
  print(p1)
}
```

# Plotting Change in Components

```{r}
varlist <- c('S7_neighbourhood_safety', 'loneliness',
             'S7_physical_health', 'S7_mental_health')

sccb_all_vars_BOXPLOT(base.dat, int.dat, group.var = 'income.quint', varlist = varlist)
```

# Testing Number of Clusters

```{r}
# # so need a function to generate a dataframe with all those additional metrics for the clustering
# base.data <- base.dat
# int.dat <- wage.dat
# int.name <- 'livingWage'
# 
# # first add scenario column to each
# base <- base.data %>%
#   mutate(scenarios = 'baseline',
#          boost_amount = 0,
#          income_boosted = 0)
# int <- int.dat %>%
#   mutate(scenarios = int.name)
# 
# # now bind together before subsetting
# combined <- rbind(base, int)
# combined <- combined %>%
#   select(pidp, hidp, time, age, sex, ethnicity, region, education_state, hh_income, equivalent_income, S7_housing_quality, S7_neighbourhood_safety, S7_physical_health, S7_mental_health, S7_labour_state, loneliness, job_sec, nkids_ind, hourly_wage)
# 
# # Identify categorical columns
# categorical_cols <- c('sex', 'ethnicity', 'region', 'education_state', 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness', 'job_sec')
# 
# # Convert categorical variables to factors
# combined[, categorical_cols] <- lapply(combined[, categorical_cols], as.factor)
# 
# # Choose a range of values for 'k' (number of clusters)
# k_values <- 2:8 # You can adjust the range
# 
# # Initialize vectors to store evaluation metrics
# wss <- vector('numeric', length(k_values))  # Within-cluster sum of squares
# silhouette_scores <- vector('numeric', length(k_values))
# 
# # # Register parallel cores (adjust the number as needed)
# # num_cores <- 8
# # cl <- makeCluster(num_cores)
# # registerDoParallel(cl)
# # 
# # # Create a function to compute wss and silhouette scores for a given k
# # compute_metrics <- function(k, data) {
# #   kp_model <- kproto(data, k = k, num_rounds = 20, verbose = FALSE, cat.vars = which(names(data) %in% categorical_cols))
# #   wss <- kp_model$tot.withinss
# #   silhouette_score <- silhouette(kp_model$cluster, dist(data))$avg.width
# #   return(c(k, wss, silhouette_score))
# # }
# 
# # Iterate through different values of 'k'
# for (i in 1:length(k_values)) {
#   # Fit the k-prototypes model
#   kp_model <- kproto(combined, k = k_values[i], num_rounds = 20, verbose = FALSE, cat.vars = which(names(combined) %in% categorical_columns))
#   # Compute within-cluster sum of squares
#   wss[i] <- kp_model$tot.withinss
#   # Compute silhouette score
#   # Silhouette score measures the quality of clustering (higher is better)
#   #silhouette_scores[i] <- silhouette(kp_model$cluster, dist(combined))$avg.width
# }
# 
# # Plot the elbow curve
# #par(mfrow = c(1, 2))
# plot(k_values, wss, type = "b", pch = 19, xlab = "Number of Clusters (k)", ylab = "Within-Cluster Sum of Squares (WSS)", main = "Elbow Method")
# #plot(k_values, silhouette_scores, type = "b", pch = 19, xlab = "Number of Clusters (k)", ylab = "Silhouette Score", main = "Silhouette Score Method")
# 
# # Use the elbow or silhouette method to select the optimal number of clusters
# # Elbow method: Look for an 'elbow point' where the WSS starts to level off
# # Silhouette method: Look for the highest silhouette score
```

### 2024-01-09 minos/testing/S7_comp_change_boxplot.Rmd
Boxplots of component change script

---
params:
    out_path: '' # default arguments. specify others in command line.
    intervention: ''
title: "`r paste(params$file_path, ' ', params$intervention, ' ANALYSIS')`"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(here)
require(dplyr)
require(tidyr)
require(purrr)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

```{r, include=FALSE}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

```{r}
out.path.batch <- here::here('output', params$out_path)
intervention <- params$intervention

S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
                 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
                 'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
out.path.batch <- here::here('output', 'SIPHER7/')

base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
int.batch <- read_batch_out_all_years(out.path.batch, intervention, start.year = 2021, var.list = c('income_boosted', 'boost_amount', S7.var.list), verbose=FALSE)

# add income_boosted and boost_amount to baseline
base.batch$income_boosted <- 0
base.batch$boost_amount <- 0
```

```{r}
# S7_pathway_change_byGroup <- function(base.batch, int.batch, group.var, var) {
#   base.sub <- base.batch %>%
#     select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var)) %>%
#     group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
#     count() %>%
#     group_by(time, run_id, .data[[group.var]]) %>%
#     mutate(total = sum(n),
#            base_prop = n / total) %>%
#     select(-n, -total)
#
#   int.sub <- energy.batch %>%
#     select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var)) %>%
#     group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
#     count() %>%
#     group_by(time, run_id, .data[[group.var]]) %>%
#     mutate(total = sum(n),
#            int_prop = n / total) %>%
#     select(-n, -total)
#
#   combined <- merge(base.sub, int.sub, by = c('time', 'run_id', group.var, var))
#   combined$prop_diff <- combined$int_prop - combined$base_prop
#
#   combined[[var]] <- as.factor(combined[[var]])
#
#   ggplot(data = combined, aes(x = time, y = prop_diff, group = .data[[var]], color = .data[[var]])) +
#     geom_smooth() +
#     facet_wrap(~ .data[[group.var]], nrow=1) +
#     theme(axis.title.x = element_blank(),
#           axis.text.x = element_blank(),
#           axis.ticks.x = element_blank())
# }
```

```{r}
simplified_component_change_BOXPLOT <- function(base.batch, int.batch, var, print = FALSE) {

  # it would be lovely if this was completely generic, but for some things that
  # is more hassle than its worth. Handling string vars here is one of these
  # things

  if (var == 'S7_housing_quality') {
    base.batch$S7_housing_quality <- as.numeric(factor(base.batch$S7_housing_quality,
                                            levels = c('No to all',
                                                       'Yes to some',
                                                       'Yes to all'),
                                            labels = c(1, 2, 3)))
    int.batch$S7_housing_quality <- as.numeric(factor(int.batch$S7_housing_quality,
                                            levels = c('No to all',
                                                       'Yes to some',
                                                       'Yes to all'),
                                            labels = c(1, 2, 3)))
  } else if (var == 'S7_neighbourhood_safety') {
    base.batch$S7_neighbourhood_safety <- as.numeric(factor(base.batch$S7_neighbourhood_safety,
                                                 levels = c('Often',
                                                            'Some of the time',
                                                            'Hardly ever'),
                                                 labels = c(1, 2, 3)))
    int.batch$S7_neighbourhood_safety <- as.numeric(factor(int.batch$S7_neighbourhood_safety,
                                                 levels = c('Often',
                                                            'Some of the time',
                                                            'Hardly ever'),
                                                 labels = c(1, 2, 3)))
  } else if (var == 'loneliness') {
    base.batch$loneliness <- as.numeric(factor(base.batch$loneliness,
                                    levels = c(1, 2, 3),
                                    labels = c(3, 2, 1)))
    int.batch$loneliness <- as.numeric(factor(int.batch$loneliness,
                                    levels = c(1, 2, 3),
                                    labels = c(3, 2, 1)))
  }

  base.sub <- base.batch %>%
    select(pidp, time, run_id, all_of(var)) %>%
    rename(Baseline_var = .data[[var]])

  int.sub <- int.batch %>%
    select(pidp, time, run_id, all_of(var)) %>%
    rename(Intervention_var = .data[[var]])

  merged <- merge(base.sub, int.sub,
                  by=c('pidp', 'time', 'run_id'),
                  all = FALSE)

  merged2 <- merged %>%
    mutate(varChange = Intervention_var - Baseline_var,
           effect = case_when(varChange > 0 ~ "Positive",
                              varChange < 0 ~ "Negative",
                              varChange == 0 ~ "No_Change")) %>%
    select(-Baseline_var, -Intervention_var, -varChange) %>%
    group_by(time, run_id, effect) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n),
           effect_prop = n / total) %>%
    select(-n, -total) %>%
    pivot_wider(names_from = 'effect',
                values_from = 'effect_prop') %>%
    mutate(change = Positive - Negative) %>%
    select(-Positive, -Negative, -No_Change) %>%
    group_by(run_id) %>%
    summarise(sum.change = sum(change))

  p1 <- ggplot(data = merged2, aes(y = sum.change)) +
    geom_boxplot(notch = FALSE) +
    labs(title = paste0('Change in ', var)) +
    ylab('% Change')

  if(print) {
    print(p1)
  }

  return(merged2)
}
```

```{r}
varlist <- c('S7_neighbourhood_safety', 'loneliness',
             'S7_physical_health', 'S7_mental_health')

sccb_all_vars_BOXPLOT <- function(base.batch, int.batch, varlist) {
  df <- simplified_component_change_BOXPLOT(base.batch, int.batch, var = 'S7_housing_quality')
  colnames(df) <- c('run_id', 'S7_housing_quality')
  for (S7_var in varlist) {
    df2 <- simplified_component_change_BOXPLOT(base.batch, int.batch, var = S7_var)
    colnames(df2) <- c('run_id', S7_var)
    df <- merge(df, df2, by = c('run_id'))
  }
  rm(df2)

  # finally pivot_longer for ggplot and facet_wrap to take over
  df2 <- df %>%
    pivot_longer(cols = S7_housing_quality:S7_mental_health,
                 names_to = 'Variable',
                 values_to = 'Change')

  p1 <- ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
    geom_boxplot(notch = FALSE) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    theme(legend.position = 'bottom',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
  print(p1)
}

sccb_all_vars_BOXPLOT(base.batch, int.batch, varlist = varlist)

```

### 2024-01-09 minos/testing/S7_comp_change_boxplot_child.Rmd
Created notebook for component boxplots of top 10 percent

--- 2024-01-09 minos/testing/S7_comp_change_boxplot.Rmd
@@
 ---
-params:
-    out_path: '' # default arguments. specify others in command line.
-    intervention: ''
-title: "`r paste(params$file_path, ' ', params$intervention, ' ANALYSIS')`"
+title: "TOP10 COMPONENT ANALYSIS - ChildUplift"
 output:
@@
 ```{r}
-out.path.batch <- here::here('output', params$out_path)
-intervention <- params$intervention
+# out.path.batch <- here::here('output', params$out_path)
+# intervention <- params$intervention
+
+out.path.batch <- here::here('output', 'SIPHER7')
+intervention <- 'hhIncomeChildUplift'
 
@@
 ```{r}
-# S7_pathway_change_byGroup <- function(base.batch, int.batch, group.var, var) {
-#   base.sub <- base.batch %>%
-#     select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var)) %>%
-#     group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
-#     count() %>%
-#     group_by(time, run_id, .data[[group.var]]) %>%
-#     mutate(total = sum(n),
-#            base_prop = n / total) %>%
-#     select(-n, -total)
-#
-#   int.sub <- energy.batch %>%
-#     select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var)) %>%
-#     group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
-#     count() %>%
-#     group_by(time, run_id, .data[[group.var]]) %>%
-#     mutate(total = sum(n),
-#            int_prop = n / total) %>%
-#     select(-n, -total)
-#
-#   combined <- merge(base.sub, int.sub, by = c('time', 'run_id', group.var, var))
-#   combined$prop_diff <- combined$int_prop - combined$base_prop
-#
-#   combined[[var]] <- as.factor(combined[[var]])
-#
-#   ggplot(data = combined, aes(x = time, y = prop_diff, group = .data[[var]], color = .data[[var]])) +
-#     geom_smooth() +
-#     facet_wrap(~ .data[[group.var]], nrow=1) +
-#     theme(axis.title.x = element_blank(),
-#           axis.text.x = element_blank(),
-#           axis.ticks.x = element_blank())
-# }
+# select only top 10% of equivalent income increases
+base.sub <- base.batch %>%
+  select(pidp, time, equivalent_income) %>%
+  rename(baseline = equivalent_income)
+
+int.sub <- int.batch %>%
+  select(pidp, time, equivalent_income) %>%
+  rename(intervention = equivalent_income)
+
+merged <- merge(x = base.sub,
+                y = int.sub,
+                by = c('pidp', 'time'))
+
+rm(base.sub, int.sub)
+
+top10p <- merged %>%
+  mutate(diff = intervention - baseline) %>%
+  group_by(pidp) %>%
+  summarise(sum_diff = sum(diff)) %>%
+  filter(sum_diff > quantile(sum_diff, .9))
+
+rm(merged)
+
+print(paste0('Top 10% of improvers: n = ', nrow(top10p)))
+
+base.batch <- base.batch %>%
+  filter(pidp %in% unique(top10p$pidp))
+int.batch <- int.batch %>%
+  filter(pidp %in% unique(top10p$pidp))
+
+rm(top10p)
 ```

### 2024-01-09 minos/testing/S7_comp_change_boxplot_livWage.Rmd
Created notebook for component boxplots of top 10 percent

--- 2024-01-09 minos/testing/S7_comp_change_boxplot_child.Rmd
@@
 ---
-title: "TOP10 COMPONENT ANALYSIS - ChildUplift"
+title: "TOP10 COMPONENT ANALYSIS - Living Wage"
 output:
@@
 out.path.batch <- here::here('output', 'SIPHER7')
-intervention <- 'hhIncomeChildUplift'
+intervention <- 'livingWageIntervention'
 

### 2024-01-09 minos/testing/S7_comp_change_boxplot_pov.Rmd
Created notebook for component boxplots of top 10 percent

--- 2024-01-09 minos/testing/S7_comp_change_boxplot_child.Rmd
@@
 ---
-title: "TOP10 COMPONENT ANALYSIS - ChildUplift"
+title: "TOP10 COMPONENT ANALYSIS - PovertyChild"
 output:
@@
 out.path.batch <- here::here('output', 'SIPHER7')
-intervention <- 'hhIncomeChildUplift'
+intervention <- 'hhIncomePovertyLineChildUplift'
 

### 2024-01-09 minos/testing/S7_comp_change_boxplot_child.Rmd
Didnt render properly on arc, moving to explicitly save the image we want

@@
   print(p1)
+
+  ggsave(filename = paste0('sccb_boxplot_', intervention, '_top10.png'),
+         plot = p1,
+         path = 'plots/')
 }

### 2024-01-09 minos/testing/S7_comp_change_boxplot_livWage.Rmd
Didnt render properly on arc, moving to explicitly save the image we want

@@
 ---
-title: "TOP10 COMPONENT ANALYSIS - Living Wage"
+title: "COMPONENT ANALYSIS - Living Wage"
 output:
@@
   print(p1)
+
+  ggsave(filename = paste0('sccb_boxplot_', intervention, '.png'),
+         plot = p1,
+         path = 'plots/')
 }

### 2024-01-09 minos/testing/S7_comp_change_child.Rmd
Didnt render properly on arc, moving to explicitly save the image we want

--- 2024-01-09 minos/testing/S7_comp_change_boxplot_pov.Rmd
@@
 ---
-title: "TOP10 COMPONENT ANALYSIS - PovertyChild"
+title: "COMPONENT ANALYSIS"
 output:
@@
 out.path.batch <- here::here('output', 'SIPHER7')
-intervention <- 'hhIncomePovertyLineChildUplift'
+intervention <- 'hhIncomeChildUplift'
 
@@
 ```{r}
-# select only top 10% of equivalent income increases
-base.sub <- base.batch %>%
-  select(pidp, time, equivalent_income) %>%
-  rename(baseline = equivalent_income)
-
-int.sub <- int.batch %>%
-  select(pidp, time, equivalent_income) %>%
-  rename(intervention = equivalent_income)
-
-merged <- merge(x = base.sub,
-                y = int.sub,
-                by = c('pidp', 'time'))
-
-rm(base.sub, int.sub)
-
-top10p <- merged %>%
-  mutate(diff = intervention - baseline) %>%
-  group_by(pidp) %>%
-  summarise(sum_diff = sum(diff)) %>%
-  filter(sum_diff > quantile(sum_diff, .9))
-
-rm(merged)
-
-print(paste0('Top 10% of improvers: n = ', nrow(top10p)))
-
-base.batch <- base.batch %>%
-  filter(pidp %in% unique(top10p$pidp))
-int.batch <- int.batch %>%
-  filter(pidp %in% unique(top10p$pidp))
-
-rm(top10p)
+# # select only top 10% of equivalent income increases
+# base.sub <- base.batch %>%
+#   select(pidp, time, equivalent_income) %>%
+#   rename(baseline = equivalent_income)
+# 
+# int.sub <- int.batch %>%
+#   select(pidp, time, equivalent_income) %>%
+#   rename(intervention = equivalent_income)
+# 
+# merged <- merge(x = base.sub,
+#                 y = int.sub,
+#                 by = c('pidp', 'time'))
+# 
+# rm(base.sub, int.sub)
+# 
+# top10p <- merged %>%
+#   mutate(diff = intervention - baseline) %>%
+#   group_by(pidp) %>%
+#   summarise(sum_diff = sum(diff)) %>%
+#   filter(sum_diff > quantile(sum_diff, .9))
+# 
+# rm(merged)
+# 
+# print(paste0('Top 10% of improvers: n = ', nrow(top10p)))
+# 
+# base.batch <- base.batch %>%
+#   filter(pidp %in% unique(top10p$pidp))
+# int.batch <- int.batch %>%
+#   filter(pidp %in% unique(top10p$pidp))
+# 
+# rm(top10p)
 ```

### 2024-01-10 minos/outcomes/equivalent_income_out_batch.Rmd
Last ditch scrawling effort to get some results for Vienna. Struggle

@@
                  'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
-out.path.batch <- here::here('output', 'SIPHER7/')
+out.path.batch <- here::here('output', 'TEST_BATCH/')
 
-base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
-wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
-pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2024, var.list = S7.var.list, verbose=TRUE)
+wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2024, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
+#energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
+child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2024, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
+#pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
 
@@
 wage.batch <- calc_age_group(wage.batch)
-energy.batch <- calc_age_group(energy.batch)
+#energy.batch <- calc_age_group(energy.batch)
 child.batch <- calc_age_group(child.batch)
-pov.batch <- calc_age_group(pov.batch)
+#pov.batch <- calc_age_group(pov.batch)
 ```
@@
 wage.batch <- calc_income_quintile(wage.batch)
-energy.batch <- calc_income_quintile(energy.batch)
+#energy.batch <- calc_income_quintile(energy.batch)
 child.batch <- calc_income_quintile(child.batch)
-pov.batch <- calc_income_quintile(pov.batch)
+#pov.batch <- calc_income_quintile(pov.batch)
 ```
@@
 ```{r}
-base.bat.sub <- base.batch %>%
-  select(pidp, time, run_id, hh_income, weight) %>%
-  group_by(run_id, time) %>%
-  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm=TRUE))
-
-base.bat.sub$run_id <- as.factor(base.bat.sub$run_id)
-
-big.run.id <- base.bat.sub$run_id[which.max(base.bat.sub$hh_income)]
-
-base.bat.sub12 <- base.bat.sub %>%
-  filter(run_id != big.run.id)
-
-ggplot(data = base.bat.sub, aes(x = time, y = hh_income, group=run_id, color = run_id)) +
-  geom_line() +
-  labs(title = 'Household Income: Individual Runs')
-
-ggplot(data = base.bat.sub12, aes(x = time, y = hh_income, group=run_id, color = run_id)) +
-  geom_line() +
-  labs(title = 'Household Income: Individual Runs')
-
-ggplot(data = base.bat.sub, aes(x = time, y = hh_income)) +
-  geom_smooth() +
-  labs(title = 'Household Income: Smoothed mean')
-
-ggplot(data = base.bat.sub12, aes(x = time, y = hh_income)) +
-  geom_smooth() +
-  labs(title = 'Household Income: Smoothed mean')
-
-base.bat.sub2 <- base.bat.sub %>%
-  group_by(time) %>%
-  summarise(var = mean(hh_income),
-         min = min(hh_income),
-         max = max(hh_income))
-
-base.bat.sub22 <- base.bat.sub12 %>%
-  group_by(time) %>%
-  summarise(var = mean(hh_income),
-         min = min(hh_income),
-         max = max(hh_income))
-
-ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
-  geom_line() +
-  geom_ribbon(aes(ymin = min, ymax = max), 
-                alpha = 0.1,
-                linetype = 'dashed') +
-  labs(title = 'Household Income: Min - Max')
-
-ggplot(data = base.bat.sub22, aes(x = time, y = var)) +
-  geom_line() +
-  geom_ribbon(aes(ymin = min, ymax = max), 
-                alpha = 0.1,
-                linetype = 'dashed') +
-  labs(title = 'Household Income: Min - Max')
+# base.bat.sub <- base.batch %>%
+#   select(pidp, time, run_id, hh_income, weight) %>%
+#   group_by(run_id, time) %>%
+#   summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm=TRUE))
+# 
+# base.bat.sub$run_id <- as.factor(base.bat.sub$run_id)
+# 
+# big.run.id <- base.bat.sub$run_id[which.max(base.bat.sub$hh_income)]
+# 
+# base.bat.sub12 <- base.bat.sub %>%
+#   filter(run_id != big.run.id)
+# 
+# ggplot(data = base.bat.sub, aes(x = time, y = hh_income, group=run_id, color = run_id)) +
+#   geom_line() +
+#   labs(title = 'Household Income: Individual Runs')
+# 
+# ggplot(data = base.bat.sub12, aes(x = time, y = hh_income, group=run_id, color = run_id)) +
+#   geom_line() +
+#   labs(title = 'Household Income: Individual Runs')
+# 
+# ggplot(data = base.bat.sub, aes(x = time, y = hh_income)) +
+#   geom_smooth() +
+#   labs(title = 'Household Income: Smoothed mean')
+# 
+# ggplot(data = base.bat.sub12, aes(x = time, y = hh_income)) +
+#   geom_smooth() +
+#   labs(title = 'Household Income: Smoothed mean')
+# 
+# base.bat.sub2 <- base.bat.sub %>%
+#   group_by(time) %>%
+#   summarise(var = mean(hh_income),
+#          min = min(hh_income),
+#          max = max(hh_income))
+# 
+# base.bat.sub22 <- base.bat.sub12 %>%
+#   group_by(time) %>%
+#   summarise(var = mean(hh_income),
+#          min = min(hh_income),
+#          max = max(hh_income))
+# 
+# ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
+#   geom_line() +
+#   geom_ribbon(aes(ymin = min, ymax = max), 
+#                 alpha = 0.1,
+#                 linetype = 'dashed') +
+#   labs(title = 'Household Income: Min - Max')
+# 
+# ggplot(data = base.bat.sub22, aes(x = time, y = var)) +
+#   geom_line() +
+#   geom_ribbon(aes(ymin = min, ymax = max), 
+#                 alpha = 0.1,
+#                 linetype = 'dashed') +
+#   labs(title = 'Household Income: Min - Max')
 ```
@@
 ```{r}
-base.bat.sub <- base.batch %>%
-  select(pidp, time, run_id, equivalent_income, weight) %>%
-  group_by(run_id, time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm=TRUE))
-
-base.bat.sub$run_id <- as.factor(base.bat.sub$run_id)
-
-big.run.id <- base.bat.sub$run_id[which.max(base.bat.sub$equivalent_income)]
-
-base.bat.sub12 <- base.bat.sub %>%
-  filter(run_id != big.run.id)
-
-ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
-  geom_line() +
-  labs(title = 'Equivalent Income: Individual Runs')
-
-ggplot(data = base.bat.sub12, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
-  geom_line() +
-  labs(title = 'Equivalent Income: Individual Runs')
-
-ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income)) +
-  geom_smooth() +
-  labs(title = 'Equivalent Income: Smoothed mean')
-
-ggplot(data = base.bat.sub12, aes(x = time, y = equivalent_income)) +
-  geom_smooth() +
-  labs(title = 'Equivalent Income: Smoothed mean')
-
-base.bat.sub2 <- base.bat.sub %>%
-  group_by(time) %>%
-  summarise(var = mean(equivalent_income),
-         min = min(equivalent_income),
-         max = max(equivalent_income))
-
-base.bat.sub22 <- base.bat.sub12 %>%
-  group_by(time) %>%
-  summarise(var = mean(equivalent_income),
-         min = min(equivalent_income),
-         max = max(equivalent_income))
-
-ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
-  geom_line() +
-  geom_ribbon(aes(ymin = min, ymax = max), 
-                alpha = 0.1,
-                linetype = 'dashed') +
-  labs(title = 'Equivalent Income: Min - Max')
-
-ggplot(data = base.bat.sub22, aes(x = time, y = var)) +
-  geom_line() +
-  geom_ribbon(aes(ymin = min, ymax = max), 
-                alpha = 0.1,
-                linetype = 'dashed') +
-  labs(title = 'Equivalent Income: Min - Max')
+# base.bat.sub <- base.batch %>%
+#   select(pidp, time, run_id, equivalent_income, weight) %>%
+#   group_by(run_id, time) %>%
+#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm=TRUE))
+# 
+# base.bat.sub$run_id <- as.factor(base.bat.sub$run_id)
+# 
+# big.run.id <- base.bat.sub$run_id[which.max(base.bat.sub$equivalent_income)]
+# 
+# base.bat.sub12 <- base.bat.sub %>%
+#   filter(run_id != big.run.id)
+# 
+# ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
+#   geom_line() +
+#   labs(title = 'Equivalent Income: Individual Runs')
+# 
+# ggplot(data = base.bat.sub12, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
+#   geom_line() +
+#   labs(title = 'Equivalent Income: Individual Runs')
+# 
+# ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income)) +
+#   geom_smooth() +
+#   labs(title = 'Equivalent Income: Smoothed mean')
+# 
+# ggplot(data = base.bat.sub12, aes(x = time, y = equivalent_income)) +
+#   geom_smooth() +
+#   labs(title = 'Equivalent Income: Smoothed mean')
+# 
+# base.bat.sub2 <- base.bat.sub %>%
+#   group_by(time) %>%
+#   summarise(var = mean(equivalent_income),
+#          min = min(equivalent_income),
+#          max = max(equivalent_income))
+# 
+# base.bat.sub22 <- base.bat.sub12 %>%
+#   group_by(time) %>%
+#   summarise(var = mean(equivalent_income),
+#          min = min(equivalent_income),
+#          max = max(equivalent_income))
+# 
+# ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
+#   geom_line() +
+#   geom_ribbon(aes(ymin = min, ymax = max), 
+#                 alpha = 0.1,
+#                 linetype = 'dashed') +
+#   labs(title = 'Equivalent Income: Min - Max')
+# 
+# ggplot(data = base.bat.sub22, aes(x = time, y = var)) +
+#   geom_line() +
+#   geom_ribbon(aes(ymin = min, ymax = max), 
+#                 alpha = 0.1,
+#                 linetype = 'dashed') +
+#   labs(title = 'Equivalent Income: Min - Max')
 ```
@@
     group_by(time, run_id) %>%
-    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+    summarise(equivalent_income = mean(equivalent_income))
   int.subset <- int.bat %>%
@@
     group_by(time, run_id) %>%
-    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+    summarise(equivalent_income =  mean(equivalent_income))
 
@@
     geom_smooth() +
-    labs(title = paste0('Equivalent Income: ', int.name), subtitle = '10 Runs') +
+    labs(title = paste0('Equivalent Income: ', int.name)) +
     xlab('Year') +
@@
 ```{r}
-equivalent_income_comparison_fullpop_batch(base.batch, energy.batch, 'EnergyCrisis')
 equivalent_income_comparison_fullpop_batch(base.batch, wage.batch, 'LivingWage')
-equivalent_income_comparison_fullpop_batch(base.batch, child.batch, 'AllChild')
-equivalent_income_comparison_fullpop_batch(base.batch, pov.batch, 'PovertyChild')
+equivalent_income_comparison_fullpop_batch(base.batch, child.batch, 'ChildBenefit')
 ```
@@
 ```{r}
-base.subset <- base.batch %>%
-  select(pidp, time, run_id, equivalent_income, weight) %>%
-  group_by(time, run_id) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
-  mutate(scenario = 'Baseline')
-
-wage.subset <- wage.batch %>%
-  select(pidp, time, run_id, equivalent_income, weight) %>%
-  group_by(time, run_id) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
-  mutate(scenario = 'LivingWage')
-
-energy.subset <- energy.batch %>%
-  select(pidp, time, run_id, equivalent_income, weight) %>%
-  group_by(time, run_id) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
-  mutate(scenario = 'EnergyCrisis')
-
-child.subset <- child.batch %>%
-  select(pidp, time, run_id, equivalent_income, weight) %>%
-  group_by(time, run_id) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
-  mutate(scenario = 'AllChild')
-
-pov.subset <- pov.batch %>%
-  select(pidp, time, run_id, equivalent_income, weight) %>%
-  group_by(time, run_id) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
-  mutate(scenario = 'PovertyChild')
-
-all.combined <- rbind(base.subset, wage.subset, energy.subset, child.subset, pov.subset)
-all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'LivingWage', 'EnergyCrisis', 'AllChild', 'PovertyChild'))
-
-ggplot(data = all.combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
-  geom_smooth() +
-  labs(title = 'Equivalent Income Comparison', subtitle = 'Whole Population') +
-  xlab('Year') +
-  ylab('Equivalent Income (£)')
+# base.subset <- base.batch %>%
+#   select(pidp, time, run_id, equivalent_income, weight) %>%
+#   group_by(time, run_id) %>%
+#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
+#   mutate(scenario = 'Baseline')
+# 
+# wage.subset <- wage.batch %>%
+#   select(pidp, time, run_id, equivalent_income, weight) %>%
+#   group_by(time, run_id) %>%
+#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
+#   mutate(scenario = 'LivingWage')
+# 
+# # energy.subset <- energy.batch %>%
+# #   select(pidp, time, run_id, equivalent_income, weight) %>%
+# #   group_by(time, run_id) %>%
+# #   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
+# #   mutate(scenario = 'EnergyCrisis')
+# 
+# child.subset <- child.batch %>%
+#   select(pidp, time, run_id, equivalent_income, weight) %>%
+#   group_by(time, run_id) %>%
+#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
+#   mutate(scenario = 'AllChild')
+# 
+# # pov.subset <- pov.batch %>%
+# #   select(pidp, time, run_id, equivalent_income, weight) %>%
+# #   group_by(time, run_id) %>%
+# #   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
+# #   mutate(scenario = 'PovertyChild')
+# 
+# all.combined <- rbind(base.subset, wage.subset, energy.subset, child.subset, pov.subset)
+# all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'LivingWage', 'EnergyCrisis', 'AllChild', 'PovertyChild'))
+# 
+# ggplot(data = all.combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
+#   geom_smooth() +
+#   labs(title = 'Equivalent Income Comparison', subtitle = 'Whole Population') +
+#   xlab('Year') +
+#   ylab('Equivalent Income (£)')
 ```
@@
     group_by(time, scenario, run_id) %>%
-    summarise(equivalent_income = weighted.mean(equivalent_income, w=weight))
+    summarise(equivalent_income =  mean(equivalent_income))
 
@@
 equivalent_income_comparison_treated_batch(base.batch, wage.batch, 'LivingWage')
-equivalent_income_comparison_treated_batch(base.batch, energy.batch, 'EnergyDownlift')
-equivalent_income_comparison_treated_batch(base.batch, child.batch, 'AllChild')
-equivalent_income_comparison_treated_batch(base.batch, pov.batch, 'PovertyChild')
+#equivalent_income_comparison_treated_batch(base.batch, energy.batch, 'EnergyDownlift')
+equivalent_income_comparison_treated_batch(base.batch, child.batch, 'ChildBenefit')
+#equivalent_income_comparison_treated_batch(base.batch, pov.batch, 'PovertyChild')
 ```
@@
 
-income_equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
+#income_equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
 income_equivinc_change_batch(base.batch, wage.batch, 'Living Wage')
 income_equivinc_change_batch(base.batch, child.batch, 'All Child')
-income_equivinc_change_batch(base.batch, pov.batch, 'Poverty Child')
+#income_equivinc_change_batch(base.batch, pov.batch, 'Poverty Child')
 ```
@@
 
-equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
+#equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
 equivinc_change_batch(base.batch, wage.batch, 'Living Wage')
 equivinc_change_batch(base.batch, child.batch, 'All Child')
-equivinc_change_batch(base.batch, pov.batch, 'Poverty Child')
+#equivinc_change_batch(base.batch, pov.batch, 'Poverty Child')
 ```
@@
 
-equivinc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
-equivinc_change_batch_subpop(base.batch, wage.batch, 'Living Wage', group.var = 'income.quint')
-equivinc_change_batch_subpop(base.batch, child.batch, 'All Child', group.var = 'income.quint')
-equivinc_change_batch_subpop(base.batch, pov.batch, 'Poverty Child', group.var = 'income.quint')
+# equivinc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
+# equivinc_change_batch_subpop(base.batch, wage.batch, 'Living Wage', group.var = 'income.quint')
+# equivinc_change_batch_subpop(base.batch, child.batch, 'All Child', group.var = 'income.quint')
+# equivinc_change_batch_subpop(base.batch, pov.batch, 'Poverty Child', group.var = 'income.quint')
 ```
@@
 
-income_equivinc_percent_change_batch(base.batch, energy.batch, 'Energy Crisis')
+#income_equivinc_percent_change_batch(base.batch, energy.batch, 'Energy Crisis')
 income_equivinc_percent_change_batch(base.batch, wage.batch, 'Living Wage')
 income_equivinc_percent_change_batch(base.batch, child.batch, 'All Child')
-income_equivinc_percent_change_batch(base.batch, pov.batch, 'Poverty Child')
+#income_equivinc_percent_change_batch(base.batch, pov.batch, 'Poverty Child')
 ```
@@
 
-income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'ethnicity', subpop = 'PAK')
-income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'urban', subpop = '1')
-income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'urban', subpop = '2')
-income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'income.quint', subpop = '1')
-income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'income.quint', subpop = '5')
+# income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'ethnicity', subpop = 'PAK')
+# income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'urban', subpop = '1')
+# income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'urban', subpop = '2')
+# income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'income.quint', subpop = '1')
+# income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'income.quint', subpop = '5')
 ```
@@
 ```{r}
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'income.quint')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'ethnicity')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'urban')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'age.group')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'region')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'job_sec')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'education_state')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'nkids_ind')
-equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'housing_tenure')
-
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_housing_quality')
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_neighbourhood_safety')
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_mental_health')
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_physical_health')
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'loneliness')
-S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_labour_state')
+# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'income.quint')
+# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'ethnicity')
+# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'urban')
+# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'age.group')
+# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'region')
+# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'job_sec')
+# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'education_state')
+# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'nkids_ind')
+# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'housing_tenure')
+# 
+# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_housing_quality')
+# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_neighbourhood_safety')
+# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_mental_health')
+# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_physical_health')
+# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'loneliness')
+# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_labour_state')
 ```
@@
 ```{r}
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'income.quint')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'ethnicity')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'urban')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'age.group')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'region')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'job_sec')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'education_state')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'nkids_ind')
-equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'housing_tenure')
-
-S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_housing_quality')
-S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_neighbourhood_safety')
-S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_mental_health')
-S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_physical_health')
-S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'loneliness')
-S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_labour_state')
+# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'income.quint')
+# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'ethnicity')
+# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'urban')
+# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'age.group')
+# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'region')
+# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'job_sec')
+# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'education_state')
+# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'nkids_ind')
+# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'housing_tenure')
+# 
+# S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_housing_quality')
+# S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_neighbourhood_safety')
+# S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_mental_health')
+# S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_physical_health')
+# S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'loneliness')
+# S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_labour_state')
 ```
@@
 ```{r}
-equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'income.quint')
-equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'ethnicity')
-equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'urban')
-equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'age.group')
-equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'region')
-equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'job_sec')
-equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'education_state')
-equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'nkids_ind')
-equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'housing_tenure')
-
-S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_housing_quality')
-S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_neighbourhood_safety')
-S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_mental_health')
-S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_physical_health')
-S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'loneliness')
-S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_labour_state')
+# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'income.quint')
+# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'ethnicity')
+# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'urban')
+# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'age.group')
+# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'region')
+# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'job_sec')
+# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'education_state')
+# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'nkids_ind')
+# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'housing_tenure')
+# 
+# S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_housing_quality')
+# S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_neighbourhood_safety')
+# S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_mental_health')
+# S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_physical_health')
+# S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'loneliness')
+# S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_labour_state')
 ```
@@
 ```{r}
-equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'income.quint')
-equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'ethnicity')
-equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'urban')
-equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'age.group')
-equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'region')
-equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'job_sec')
-equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'education_state')
-equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'nkids_ind')
-equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'housing_tenure')
-
-S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_housing_quality')
-S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_neighbourhood_safety')
-S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_mental_health')
-S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_physical_health')
-S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'loneliness')
-S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_labour_state')
+# equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'income.quint')
+# equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'ethnicity')
+# equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'urban')
+# equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'age.group')
+# equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'region')
+# equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'job_sec')
+# equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'education_state')
+# equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'nkids_ind')
+# equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'housing_tenure')
+# 
+# S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_housing_quality')
+# S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_neighbourhood_safety')
+# S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_mental_health')
+# S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_physical_health')
+# S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'loneliness')
+# S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_labour_state')
 ```

### 2024-01-10 minos/testing/S7_comp_change_boxplot_pov.Rmd
Distinct names for top 10% analysis plots
Last ditch scrawling effort to get some results for Vienna. Struggle

@@
   group_by(pidp) %>%
-  summarise(sum_diff = sum(diff)) %>%
-  filter(sum_diff > quantile(sum_diff, .9))
+  summarise(sum_diff = sum(diff))
+
+threshold <- quantile(top10p$sum_diff, 0.9)
+print(threshold)
+
+top10p <- top10p %>%
+  filter(sum_diff > threshold)
 
@@
 
-  ggsave(filename = paste0('sccb_boxplot_', intervention, '.png'),
+  ggsave(filename = paste0('sccb_boxplot_', intervention, '_top10.png'),
          plot = p1,

### 2024-01-10 minos/testing/num_clusters_test.Rmd
Last ditch scrawling effort to get some results for Vienna. Struggle

---
params:
    out_path: '' # default arguments. specify others in command line.
    intervention: ''
    baseline: ''
title: "`r paste(params$file_path, ' ', params$intervention, ' NUM CLUSTER CHECK')`"
output: 
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)
require(cluster)
require(clustMixType)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
)
rm(workingDir)
```

Source utils for some functions.

```{r}
source(here::here('minos', 'transitions', 'utils.R'))
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
source(here::here('minos', 'utils_S7.R'))
```

## Data

```{r}
out.path.batch <- here::here('output', params$out_path)
intervention <- params$intervention
baseline <- params$baseline
if (baseline == '') {
  baseline <- 'baseline'
}

base.dat <- read.csv(file = paste0(out.path.batch, baseline, '_summary.csv'))
int.dat <- read.csv(file = paste0(out.path.batch, intervention, '_summary.csv'))
```

```{r}
calc_age_group <- function(batch.dat) {
  batch.dat <- batch.dat %>%
    mutate(age.group = cut(age, 
                            breaks = c(15, 30, 45, 60, 75, 120),
                            labels = c('16-30', '30-45', '45-60', '60-75', '75+')))
  return(batch.dat)
}

calc_income_quintile <- function(batch.dat) {
  batch.dat <- batch.dat %>%
    mutate(income.quint = cut(batch.dat$hh_income, breaks=c(quantile(batch.dat$hh_income, probs = seq(0, 1, by = 0.20))), 
                          labels=c(1,2,3,4,5), include.lowest=TRUE))
}

base.dat <- calc_age_group(base.dat)
int.dat <- calc_age_group(int.dat)

base.dat <- calc_income_quintile(base.dat)
int.dat <- calc_income_quintile(int.dat)
```

```{r}
# Function to calculate equivalent income using SIPHER calculation
# For this I asked chatGPT to port the Python function into R, so it's maybe
# not the best way to do this in R (I needed speed...)
calculate_equivalent_income <- function(data) {
  message('Calculating equivalent income...')

  # Setting up dictionaries for each variable to hold its factor weights
  phys_health_dict <- c(`5` = 0, 
                        `4` = -0.116/1.282, 
                        `3` = -0.135/1.282, 
                        `2` = -0.479/1.282, 
                        `1` = -0.837/1.282)
  men_health_dict <- c(`5` = 0, 
                       `4` = -0.14/1.282, 
                       `3` = -0.215/1.282, 
                       `2` = -0.656/1.282, 
                       `1` = -0.877/1.282)
  loneliness_dict <- c(`1` = 0, 
                       `2` = -0.186/1.282, 
                       `3` = -0.591/1.282)
  employment_dict <- c('FT Employed' = 0, 
                       'PT Employed' = 0.033/1.282, 
                       'Job Seeking' = -0.283/1.282, 
                       'FT Education' = -0.184/1.282, 
                       'Family Care' = -0.755/1.282, 
                       'Not Working' = -0.221/1.282)
  housing_dict <- c(`3` = 0, 
                    `2` = -0.235/1.282, 
                    `1` = -0.696/1.282)
  nh_safety_dict <- c(`3` = 0, 
                      `2` = -0.291/1.282,
                      `1` = -0.599/1.282)

  # Function to safely get value from dictionary
  get_dict_value <- function(x, dict) {
    if(is.na(x) || !as.character(x) %in% names(dict)) {
      return(NA)
    }
    return(dict[as.character(x)])
  }

  # print(typeof(data$S7_physical_health))
  # print(typeof(data$S7_mental_health))
  # print(typeof(data$loneliness))
  # print(typeof(data$S7_labour_state))
  # print(typeof(data$S7_housing_quality))
  # print(typeof(data$S7_neighbourhood_safety))

  # Creating the exponent term for modifying income to equivalent income
  data$EI_exp_term <- as.numeric(0)
  data$EI_exp_term <- data$EI_exp_term + sapply(data$S7_physical_health, function(x) get_dict_value(x, phys_health_dict))
  data$EI_exp_term <- data$EI_exp_term + sapply(data$S7_mental_health, function(x) get_dict_value(x, men_health_dict))
  data$EI_exp_term <- data$EI_exp_term + sapply(data$loneliness, function(x) get_dict_value(x, loneliness_dict))
  data$EI_exp_term <- data$EI_exp_term + sapply(data$S7_labour_state, function(x) get_dict_value(x, employment_dict))
  data$EI_exp_term <- data$EI_exp_term + sapply(data$S7_housing_quality, function(x) get_dict_value(x, housing_dict))
  data$EI_exp_term <- data$EI_exp_term + sapply(data$S7_neighbourhood_safety, function(x) get_dict_value(x, nh_safety_dict))

  # Calculate equivalent income
  data$hh_income_abs <- abs(data$hh_income)
  data$equivalent_income <- data$hh_income_abs * exp(data$EI_exp_term)

  print('Remaining Null values for Equivalent Income:')
  print(sum(is.na(data$equivalent_income)))

  # Adjusting the sign of the equivalent income based on the original income sign
  data$equivalent_income[(data$hh_income < 0) & !is.na(data$hh_income)] <- data$equivalent_income[(data$hh_income < 0) & !is.na(data$hh_income)] * -1

  # Handling missing values
  var_list_num <- c('S7_physical_health', 'S7_mental_health', 'loneliness')
  var_list_str <- c('S7_labour_state', 'S7_housing_quality', 'S7_neighbourhood_safety')
  data$equivalent_income[rowSums(data[var_list_num] < 0, na.rm = TRUE) > 0] <- -9
  data$equivalent_income[apply(data[var_list_str], 1, function(x) any(x %in% c('-1', '-2', '-7', '-8', '-9', '-10')))] <- '-9'

  # Dropping the EI_exp_term column
  data$EI_exp_term <- NULL
  data$hh_income_abs <- NULL

  return(data)
}

base.dat <- calculate_equivalent_income(base.dat)
int.dat <- calculate_equivalent_income(int.dat)
```

```{r}
# so need a function to generate a dataframe with all those additional metrics for the clustering

calculate_clustering_metrics <- function(base.dat, base.name, int.dat, int.name, target.year) {

  # first add scenario column to each
  base.dat <- base.dat %>%
    mutate(scenario = base.name)#,
           #boost_amount = 0,
           #income_boosted = 0)
  int.dat <- int.dat %>%
    mutate(scenario = int.name)

  miss.cols <- setdiff(names(int.dat), names(base.dat))
  print('Missing Columns!')
  print(miss.cols)

  # now bind together before subsetting
  combined <- rbind(base.dat, int.dat)

  # drop the original datafiles now for better memory handling with batch
  rm(base.dat, int.dat)

  combined <- combined %>%
    select(pidp, time, scenario, age, age.group, sex, ethnicity, region, education_state, hh_income, equivalent_income, S7_housing_quality, S7_neighbourhood_safety, S7_physical_health, S7_mental_health, S7_labour_state, loneliness, job_sec, nkids_ind) #hidp hourly_wage

  # combined$S7_housing_quality <- as.numeric(factor(combined$S7_housing_quality,
  #                                         levels = c('No to all',
  #                                                    'Yes to some',
  #                                                    'Yes to all'),
  #                                         labels = c(1, 2, 3)))
  # 
  # combined$S7_neighbourhood_safety <- as.numeric(factor(combined$S7_neighbourhood_safety,
  #                                              levels = c('Often',
  #                                                         'Some of the time',
  #                                                         'Hardly ever'),
  #                                              labels = c(1, 2, 3)))
  # 
  # combined$loneliness <- as.numeric(factor(combined$loneliness,
  #                                 levels = c(1, 2, 3),
  #                                 labels = c(3, 2, 1)))

  # Now calculate metrics. We need:
  # - change in Equivalent Income
  # - change in components
  #
  # This is all change from start.year (usually 2021) to target.year (start with 2031)
  combined <- combined %>%
    filter(time %in% c(target.year)) %>%
    pivot_wider(
      names_from = 'scenario',
      values_from = c('age', 'age.group', 'sex', 'ethnicity', 'region', 'education_state', 'hh_income', 'equivalent_income', 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness', 'job_sec') # 'hourly_wage'
    )

  #return(combined)

  combined <- combined[complete.cases(combined), ]
  #return(combined)

  ############# Now calculate the difference between intervention and baseline in target.year ###########
  # List of variables to ignore (no difference calculation)
  ignore_vars <- c('pidp', 'time', 'nkids_ind') #'hidp'
  rename_vars <- c("age", "sex", "ethnicity", "region", "age.group", "S7_labour_state", "education_state")

  #return(combined)

  for (var in rename_vars) {
    combined <- combined %>%
      select(-contains(paste0(var, '_', intervention))) %>%
      rename(!!var := .data[[paste0(var, '_', base.name)]])
  }

  #return(combined)

  # Get the names of all variables in the 'combined' dataframe
  all_vars <- names(combined)

  # Find the variables that are in 'all_vars' but not in 'ignore_vars' or 'rename_vars'
  remaining_vars <- setdiff(all_vars, c(ignore_vars, rename_vars))
  # drop the scenarios suffixes
  remaining_vars <- lapply(remaining_vars, function(x) modified_string <- sub("_[^_]*$", "", x))
  remaining_vars <- unique(remaining_vars)

  # print('remaining_vars:')
  # print(remaining_vars)
  # 
  # print('colnames(combined)')
  # print(colnames(combined))
  # 
  # print('Set numeric types where necessary')

  # create EI var names with intervention suffix
  ei_base <- paste0('equivalent_income_', base.name)
  ei_var <- paste0('equivalent_income_', intervention)

  combined <- combined %>%
    mutate(!!ei_base := as.numeric(.data[[ei_base]]),
           !!ei_var := as.numeric(.data[[ei_var]]))

  print('Type of equivalent_income:')
  print(typeof(combined[[paste0('equivalent_income_', base.name)]]))
  print(typeof(combined[[paste0('equivalent_income_', intervention)]]))

  print('About to start final calculation')

  for (var in remaining_vars) {
    base.var <- paste0(var, '_', base.name)
    int.var <- paste0(var, '_', int.name)
    print(base.var)
    print(int.var)

    combined <- combined %>%
      mutate(!!var := !!sym(int.var) - !!sym(base.var)) %>%
      select(-base.var, -int.var)
  }

  # # Final step is to pivot long to get the run_id column back
  # combined <- combined %>%
  #   pivot_longer(age_baseline_1)

  return(combined)
}

# First calculate clustering metrics
combined <- calculate_clustering_metrics(base.dat, base.name = baseline, int.dat, int.name = intervention, target.year = 2031)
# Now remove original data for better memory handling
#rm(base.dat, int.dat)
```

# Testing Number of Clusters

```{r}
# so need a function to generate a dataframe with all those additional metrics for the clustering
#base.data <- base.dat
base.name <- baseline
int.name <- intervention

# # first add scenario column to each
# base <- base.dat %>%
#   mutate(scenarios = base.name)
# int <- int.dat %>%
#   mutate(scenarios = int.name)
# 
# # now bind together before subsetting
# combined2 <- rbind(base, int)
# combined2 <- combined2 %>%
#   select(pidp, time, age, sex, ethnicity, region, education_state, hh_income, equivalent_income, S7_housing_quality, S7_neighbourhood_safety, S7_physical_health, S7_mental_health, S7_labour_state, loneliness, job_sec, nkids_ind, hourly_wage)

# Identify categorical columns
categorical_cols <- c('sex', 'ethnicity', 'region', 'education_state', 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness', 'job_sec')

# Convert categorical variables to factors
combined[, categorical_cols] <- lapply(combined[, categorical_cols], as.factor)

# Choose a range of values for 'k' (number of clusters)
k_values <- 2:6 # You can adjust the range

# Initialize vectors to store evaluation metrics
wss <- vector('numeric', length(k_values))  # Within-cluster sum of squares
#silhouette_scores <- vector('numeric', length(k_values))

# Iterate through different values of 'k'
for (i in 1:length(k_values)) {
  # Fit the k-prototypes model
  kp_model <- kproto(combined, k = k_values[i], num_rounds = 20, verbose = FALSE, cat.vars = which(names(combined2) %in% categorical_columns))
  # Compute within-cluster sum of squares
  wss[i] <- kp_model$tot.withinss
  # Compute silhouette score
  # Silhouette score measures the quality of clustering (higher is better)
  #silhouette_scores[i] <- silhouette(kp_model$cluster, dist(combined))$avg.width
}

# Plot the elbow curve
#par(mfrow = c(1, 2))
plot(k_values, wss, type = "b", pch = 19, xlab = "Number of Clusters (k)", ylab = "Within-Cluster Sum of Squares (WSS)", main = "Elbow Method")
#plot(k_values, silhouette_scores, type = "b", pch = 19, xlab = "Number of Clusters (k)", ylab = "Silhouette Score", main = "Silhouette Score Method")

# Use the elbow or silhouette method to select the optimal number of clusters
# Elbow method: Look for an 'elbow point' where the WSS starts to level off
# Silhouette method: Look for the highest silhouette score
```

```{r}

```

### 2024-01-10 minos/testing/proportional_odds_assumption_test.Rmd
Last ditch scrawling effort to get some results for Vienna. Struggle

@@
 
-var.name <- 'job_sec'
+var.name <- 'loneliness'
 
-raw.dat <- raw.dat %>%
+raw.dat2 <- raw.dat %>%
   filter(.data[[var.name]] != '-9')
 
-file.name <- paste0('PROP_ODDS_TESTING/Prop_odds_', var.name, '.txt')
+file.path <- here::here('PROP_ODDS_TESTING')
+
+file.name <- paste0(file.path, '/Prop_odds_', var.name, '.txt')
 
@@
 #schtyp_M_M.f <- factor(raw.dat$S7_labour_state)
-schtyp_M_M.f <- factor(raw.dat[[var.name]])
+schtyp_M_M.f <- factor(raw.dat2[[var.name]])
 #
@@
 # Assign takes on a value of 1 (Treatment) or 0 (Control) 
-mod.multinom <-multinom(schtyp_M_M.f~sex, data = raw.dat)
+mod.multinom <-multinom(schtyp_M_M.f~sex, data = raw.dat2)
 print(summary(mod.multinom, cor=F, Wald=T))
@@
 cat("Proportional odds logistic regression\n")
-mod.polr <- polr(schtyp_M_M.f ~ sex, data=raw.dat)
+mod.polr <- polr(schtyp_M_M.f ~ sex, data=raw.dat2)
 print(summary(mod.polr))
@@
 ```{r}
-raw.dat <- raw.dat %>%
-  filter(loneliness != '-9')
+form.rightside <- "factor(loneliness) + scale(age) + factor(sex) + relevel(factor(education_state), ref = '3') + relevel(factor(job_sec), ref = '3') + scale(hh_income) + relevel(factor(hh_comp), ref = '3') + relevel(factor(marital_status), ref = 'Partnered') + relevel(factor(ethnicity), ref = 'WBI')"
+#form.rightside <- "factor(job_sec) + scale(age) + factor(sex) + relevel(factor(ethnicity), ref = 'WBI') + relevel(factor(region), ref = 'South East') + relevel(factor(education_state), ref = '3')"
 
-form.rightside <- "factor(loneliness) + scale(age) + factor(sex) + relevel(factor(education_state), ref = '3') + relevel(factor(job_sec), ref = '3') + scale(hh_income) + relevel(factor(hh_comp), ref = '3') + relevel(factor(marital_status), ref = 'Partnered') + relevel(factor(ethnicity), ref = 'WBI')"
-
-form.rightside <- 'sex'
+#form.rightside <- 'sex'
 
@@
 
+raw.dat2 <- raw.dat %>%
+  filter(.data[[var.name]] != '-9')
+
+file.path <- here::here('PROP_ODDS_TESTING')
+
+file.name <- paste0(file.path, '/Prop_odds_', var.name, '.txt')
+
 # Set up an out file structure
-sink(paste0('Testing_adequacy_of_Prop_odds_', test.var, '.txt'))
+sink(file.name)
 # set up response factor
-schtyp_M_M.f <- factor(test.dat[[test.var]])
+schtyp_M_M.f <- factor(raw.dat2[[test.var]])
 # set up formula object for multinom
@@
 # Test against the formula from file
-mod.multinom <-multinom(formula = form, data = test.dat)
+mod.multinom <-multinom(formula = form, data = raw.dat2)
 print(summary(mod.multinom, cor=F, Wald=T))
@@
 cat("Proportional odds logistic regression\n")
-mod.polr <- polr(formula = form, data = test.dat)
+mod.polr <- polr(formula = form, data = raw.dat2)
 print(summary(mod.polr))

### 2024-01-10 minos/testing/testing_matdep_transformations.Rmd
Last ditch scrawling effort to get some results for Vienna. Struggle

--- 2023-12-15 minos/validation/handovers.Rmd
@@
 ---
-params:
-    file_path: '' # default arguments. specify others in command line.
-    intervention: ''
-title: "`r paste(params$file_path, ' ', params$intervention, ' Handover Plots')`"
+title: "Testing Raw Data and Models"
 output:
-  #output_file: "`r paste('minos/validation/', params$file_path, '_', params$intervention, '_handovers.html') `"
   html_document:
@@
     code_folding: hide
-
 ---
@@
 require(gghighlight)
+require(describedata)
 
@@
 knitr::opts_chunk$set(
-  warning = FALSE,
-  message = FALSE
+  #warning = FALSE,
+  #message = FALSE
 )
@@
 ```{r}
-
-file_path <- params$file_path
-intervention <- params$intervention
-
 # Read raw datafiles in
@@
 
-#out.path <- here::here('output', 'default_config/')
-#base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-
-out.path <- here::here('output', file_path)
-base.dat <- read_singular_local_out(out.path, intervention, drop.dead = TRUE)
+# out.path <- here::here('output', 'default_config/')
+# base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
 ```
@@
 
-# PATHWAYS
-
-## Income
+## TESTING WITH LADDER
 
 ```{r}
-# first figure out how to plot final_US
-# start with hh_income
+var <- 'matdep'
+miss.values <- c(-10, -9, -8, -7, -3, -2, -1,
+                 -10., -9., -8., -7., -3., -2., -1.)
 
-handover_boxplots(raw.dat, base.dat, 'hh_income')
-handover_lineplots(raw.dat, base.dat, "hh_income")
-```
+test.dat <- raw.dat %>% filter(!.data[[var]] %in% miss.values)
+test.var <- sample(test.dat$matdep, size = 5000)
 
-### Spaghetti
-
-```{r}
-raw.inc <- raw.dat %>%
-  select(pidp, age, time, hh_income)
-base.inc <- base.dat %>%
-  select(pidp, age, time, hh_income)
-
-income.spag <- rbind(raw.inc, base.inc)
-
-density_ridges(income.spag, 'hh_income',
-               save=TRUE, 
-               save.path=save.path)
-
-pidp_sample <- sample(unique(income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
-income.spag.sample <- income.spag[which(income.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(income.spag.sample, 'hh_income',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(income.spag.sample, 'hh_income',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.inc, base.inc, income.spag)
-```
-
-## SF12
-
-```{r}
-# sf12 boxplot handovers
-handover_boxplots(raw.dat, base.dat, 'SF_12')
-handover_lineplots(raw.dat, base.dat, "SF_12")
-# 
-# raw.sf12 <- raw.dat %>% 
-#   dplyr::select(pidp, time, SF_12) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.sf12 <- base.dat %>%
-#   dplyr::select(pidp, time, SF_12) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# # merge before plot
-# sf12 <- rbind(raw.sf12, base.sf12)
-# 
-# # Now plot
-# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-#   geom_smooth() +
-#   #geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
-#   xlab('Year') +
-#   ylab('SF12')
-# 
-# ## Try a version where final_US is limited to only those present from wave 1 
-# # onwards because the sample refreshments are messing with the plot
-# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-# 
-# raw.sf12.2 <- raw.dat %>% 
-#   dplyr::select(pidp, time, SF_12) %>%
-#   filter(pidp %in% raw.sf12.wave1) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.sf12.2 <- base.dat %>%
-#   dplyr::select(pidp, time, SF_12) %>%
-#   filter(pidp %in% raw.sf12.wave1) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
-# 
-# # Now plot
-# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-#   geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
-#   xlab('Year') +
-#   ylab('SF12')
-# 
-# if (shall.we.save) {
-#   ggsave(filename = 'SF12_wav1.png',
-#        plot = last_plot(),
-#        path = save.path)
-# }
-# 
-# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
-```
-
-### Spaghetti
-
-```{r}
-raw.sf12 <- raw.dat %>%
-  select(pidp, age, time, SF_12)
-base.sf12 <- base.dat %>%
-  select(pidp, age, time, SF_12)
-
-sf12.spag <- rbind(raw.sf12, base.sf12)
-
-sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(sf12.spag.sample, 'SF_12',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(sf12.spag, "SF_12", 
-               save = T, 
-               save.path = save.path)
-
-rm(raw.sf12, base.sf12, sf12.spag)
-```
-
-## Financial Situation
-
-```{r}
-raw.financial_situation <- raw.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.financial_situation <- base.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-financial_situation <- rbind(raw.financial_situation, base.financial_situation)
-financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
-
-# Now plot
-ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-financial_situation.norm <- financial_situation %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial situation') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'financial_situation.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
-```
-
-## Housing Quality
-
-```{r}
-raw.housing <- raw.dat %>%
-  dplyr::select(pidp, time, housing_quality) %>%
-  group_by(time, housing_quality) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.housing <- base.dat %>%
-  dplyr::select(pidp, time, housing_quality) %>%
-  group_by(time, housing_quality) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-housing <- rbind(raw.housing, base.housing)
-housing$housing_quality <- as.factor(housing$housing_quality)
-
-# Now plot
-ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Quality', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-housing.norm <- housing %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Quality') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'housing_quality.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.housing, base.housing, housing, housing.norm)
-```
-
-### Spaghetti
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, housing_quality)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, housing_quality)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'housing_quality',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
-
-## Neighbourhood Safety
-
-```{r}
-raw.neighbour <- raw.dat %>%
-  dplyr::select(pidp, time, neighbourhood_safety) %>%
-  group_by(time, neighbourhood_safety) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.neighbour <- base.dat %>%
-  dplyr::select(pidp, time, neighbourhood_safety) %>%
-  group_by(time, neighbourhood_safety) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-neighbour <- rbind(raw.neighbour, base.neighbour)
-neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety)
-
-# Now plot
-ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') +
-  xlab('Year') +
-  ylab('Count')
-
-neighbour.norm <- neighbour %>%
-  group_by(time) %>%
-  filter(neighbourhood_safety != -9) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Neighbourhood Safety') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'neighbourhood_safety.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-#rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm)
-```
-
-### Spaghetti
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, neighbourhood_safety)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, neighbourhood_safety)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'neighbourhood_safety',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
-
-## Loneliness
-
-```{r}
-raw.loneliness <- raw.dat %>%
-  dplyr::select(pidp, time, loneliness) %>%
-  group_by(time, loneliness) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.loneliness <- base.dat %>%
-  dplyr::select(pidp, time, loneliness) %>%
-  group_by(time, loneliness) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-loneliness <- rbind(raw.loneliness, base.loneliness)
-loneliness$loneliness <- as.factor(loneliness$loneliness)
-
-# Now plot
-ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Loneliness', subtitle = 'Counts by level') +
-  xlab('Year') +
-  ylab('Count')
-
-loneliness.norm <- loneliness %>%
-  group_by(time) %>%
-  filter(loneliness != -9) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Loneliness') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'loneliness.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
-```
-
-### Spaghetti
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, loneliness)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, loneliness)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'loneliness',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
-
-## Nutrition Quality
-
-TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11
-
-```{r}
-#  nutriton quality line/boxplots.
-handover_boxplots(raw.dat, base.dat, 'nutrition_quality')
-handover_lineplots(raw.dat, base.dat, 'nutrition_quality')
-
-# Try a version where final_US is limited to only those present from wave 1
-# onwards because the sample refreshments are messing with the plot
-# raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-# 
-# raw.nut2 <- raw.dat %>%
-#   dplyr::select(pidp, time, nutrition_quality) %>%
-#   filter(pidp %in% raw.wave1) %>%
-#   filter(nutrition_quality >= 0) %>%
-#   group_by(time) %>%
-#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.nut2 <- base.dat %>%
-#   dplyr::select(pidp, time, nutrition_quality) %>%
-#   filter(pidp %in% raw.wave1) %>%
-#   group_by(time) %>%
-#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# nutrition_quality2 <- rbind(raw.nut2, base.nut2)
-# 
-# # Now plot
-# ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
-#   geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Nutrition Quality') +
-#   xlab('Year') +
-#   ylab('Nutrition Quality')
-# 
-# if (shall.we.save) {
-#   ggsave(filename = 'nutrition_quality_wav1.png',
-#        plot = last_plot(),
-#        path = save.path)
-# }
-# 
-# rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2,
-#     nutrition_quality2)
-```
-
-### Spaghetti
-
-```{r}
-# raw.nut <- raw.dat %>%
-#   select(pidp, age, time, nutrition_quality)
-# base.nut <- base.dat %>%
-#   select(pidp, age, time, nutrition_quality)
-# 
-# nut.spag <- rbind(raw.nut, base.nut)
-# 
-# spaghetti_plot(nut.spag, 'nutrition_quality',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# 
-# density_ridges(nut.spag, "nutrition_quality", 
-#                save = T, 
-#                save.path = save.path)
-# 
-# rm(raw.nut, base.nut, nut.spag)
-```
-
-## Physical Health
-
-NOTE: At present, physical health is not predicted or transitioned.
-
-```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.phealth <- raw.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.phealth <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-phealth <- rbind(raw.phealth, base.phealth)
-
-# Now plot
-ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Average')
-
-## Try a version where final_US is limited to only those present from wave 1
-# onwards because the sample refreshments are messing with the plot
-raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.phealth2 <- raw.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.phealth2 <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-phealth2 <- rbind(raw.phealth2, base.phealth2)
-
-# Now plot
-ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health') +
-  xlab('Year') +
-  ylab('Average')
-
-if (shall.we.save) {
-  ggsave(filename = 'physical_health_wav1.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-#raw.phealth.check <- raw.dat %>%
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
-
-#base.phealth.check <- base.dat %>%
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
-
-rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2)
-#rm(raw.phealth.check, base.phealth.check)
-```
-
-### Spaghetti
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, phealth)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, phealth)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'phealth',
-#              save = shall.we.save,
-#              save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
-
-## Education
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Education State'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'education_state.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
+ladder(test.var)
+norm_dist_plot(test.dat, 'matdep')
 ```
@@
 ```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat,
-                                       df1.name = 'simulated',
-                                       df2 = raw.dat,
-                                       df2.name = 'raw',
-                                       var = 'education_state')
+## Cubic transform
+new.test.dat <- raw.dat %>%
+  mutate(test.matdep = matdep^(1/3))
 
-cv_ordinal_plots(pivoted.df = pivoted,
-                 var = 'education_state',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
+ladder(sample(new.test.dat$test.matdep, size = 5000))
+norm_dist_plot(new.test.dat, 'test.matdep')
+qqnorm(new.test.dat$test.matdep)
 
-### Spaghetti
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, education_state)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, education_state)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'education_state',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
-
-## Parity
-
-```{r}
-base.parity <- base.dat %>%
-  filter(sex == "Female")
-
-raw.parity <- raw.dat %>%
-  filter(sex == "Female")
-
-prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Parity (total no. of children)'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'parity.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.parity,
-                                  df1.name = 'simulated', 
-                                  df2 = raw.parity, 
-                                  df2.name = 'raw', 
-                                  var = 'nkids_ind')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'nkids_ind',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.parity %>%
-  select(pidp, age, time, nkids_ind)
-base.s <- base.parity %>%
-  select(pidp, age, time, nkids_ind)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids_ind',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
+## Square Root transform
+new.test.dat <- raw.dat %>%
+  mutate(test.matdep = sqrt(matdep))
 
+ladder(sample(new.test.dat$test.matdep, size = 5000))
+norm_dist_plot(new.test.dat, 'test.matdep')
+qqnorm(new.test.dat$test.matdep)
 ```

### 2024-01-15 minos/validation/cross_validation_default.Rmd

--- 2023-12-11 minos/validation/cross_validation_default.Rmd
@@
 
-## Job Sec
-
-```{r}
-jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                          df1.name = 'simulated', 
-                                          df2 = raw, 
-                                          df2.name = 'raw', 
-                                          var = 'job_sec')
-
-cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
-                 var = 'job_sec',
-                 save = FALSE)
-rm(jobsec.pivoted)
-```
-
-## Hourly Wage
-
-```{r}
-cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hourly_wage')
-multi_year_boxplots(raw, cv, 'hourly_wage')
-q_q_comparison(raw, cv, 'hourly_wage')
-```
-
-## Children Ageing
+## CHILDREN AGEING
 
@@
 ```
+
+# CHILD POVERTY VARS
+
+## Relative Poverty
+
+```{r}
+relative_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                                   df1.name = 'simulated', 
+                                                   df2 = raw, 
+                                                   df2.name = 'raw', 
+                                                   var = 'relative_poverty')
+
+cv_ordinal_plots(pivoted.df = relative_poverty.pivoted, 
+                 var = 'relative_poverty',
+                 save = FALSE)
+rm(relative_poverty.pivoted)
+```
+
+## Absolute Poverty
+
+```{r}
+absolute_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                                   df1.name = 'simulated', 
+                                                   df2 = raw, 
+                                                   df2.name = 'raw', 
+                                                   var = 'absolute_poverty')
+
+cv_ordinal_plots(pivoted.df = absolute_poverty.pivoted, 
+                 var = 'absolute_poverty',
+                 save = FALSE)
+rm(absolute_poverty.pivoted)
+```
+
+## Material Deprivation
+
+```{r}
+matdep_child.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                               df1.name = 'simulated', 
+                                               df2 = raw, 
+                                               df2.name = 'raw', 
+                                               var = 'matdep_child')
+
+cv_ordinal_plots(pivoted.df = matdep_child.pivoted, 
+                 var = 'matdep_child',
+                 save = FALSE)
+rm(matdep_child.pivoted)
+```
+
+## Low Income and Material Deprivation
+
+```{r}
+low_income_matdep_child.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                                          df1.name = 'simulated', 
+                                                          df2 = raw, 
+                                                          df2.name = 'raw', 
+                                                          var = 'low_income_matdep_child')
+
+cv_ordinal_plots(pivoted.df = low_income_matdep_child.pivoted, 
+                 var = 'low_income_matdep_child',
+                 save = FALSE)
+rm(low_income_matdep_child.pivoted)
+```
+
+## Persistent Poverty
+
+```{r}
+persistent_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                                     df1.name = 'simulated', 
+                                                     df2 = raw, 
+                                                     df2.name = 'raw', 
+                                                     var = 'persistent_poverty')
+
+cv_ordinal_plots(pivoted.df = persistent_poverty.pivoted, 
+                 var = 'persistent_poverty',
+                 save = FALSE)
+rm(persistent_poverty.pivoted)
+```

### 2024-01-15 minos/validation/handovers.Rmd

@@
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+
+#out.path <- here::here('output', 'scotland_scaled/')
+#base.dat <- read_first_singular_local_out(out.path, '25UniversalCredit', drop.dead = TRUE)
+
+# HR 283-285 older version (285)
 # out.path <- here::here('output', 'child_poverty_config/')
@@
 
+## Child Ages
+
+```{r}
+base.child.ages <- base.dat %>%
+  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
+  filter(time > 2009) %>%
+  group_by(time, hidp) %>%
+  summarise(child_ages = find_mode(child_ages))
+
+s<- strsplit(base.child.ages$child_ages, "_")
+
+base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(s, length)), expanded_child_ages = unlist(s))
+base.child.ages.expanded <- base.child.ages.expanded %>%
+  group_by(time, expanded_child_ages) %>%
+  summarise(age_counts = n())
+
+ggplot(data = base.child.ages.expanded, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
+  geom_line() +
+  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
+  scale_colour_viridis_d() +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = base.child.ages.expanded, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
+  geom_line() +
+  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
+  scale_colour_viridis_d() +
+  xlab('Year') +
+  ylab('Count')
+
+base.child.ages.nkids <- base.dat %>%
+  group_by(time, hidp) %>%
+  summarise(nkids_counts = mean(nkids)) %>%
+  group_by(time) %>%
+  summarise(nkids_by_year = sum(nkids_counts))
+
+ggplot(data = base.child.ages.nkids, mapping = aes(x = time, y = nkids_by_year)) +
+  geom_line() +
+  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+```
+
 ## CHILD POVERTY VARS

### 2024-01-15 minos/outcomes/CPR_vis.Rmd
Additions to utils_datain for reading batch and single outputs in R, and a function to automatically pick between them

--- 2023-10-05 minos/outcomes/child_poverty_reduction_vis.Rmd
@@
 ---
-title: "Child Poverty Interventions"
+title: "Child Poverty Reduction Interventions"
 output:
@@
 
-This document presents results from a host of interventions on child poverty, including visualisations of the change in SF_12_MCS compared with baseline.
+# SETUP
 
@@
 require(ggplot2)
-require(ggridges) # for densities over time plots. 
 require(knitr)
 require(here)
-require(gghighlight)
+require(dplyr)
+require(tidyr)
+require(purrr)
 
@@
 
-```{r "imports", include=FALSE}
+Source utils for some functions.
+
+```{r}
 source(here::here('minos', 'utils_datain.R'))
 #source(here::here('minos', 'utils_validation_vis.R'))
-source(here::here('minos', 'validation', 'utils.r'))
+#source(here::here('minos', 'validation', 'utils.r'))
 ```
 
-```{r, include=FALSE}
-out.path <- here::here('output', 'default_config/')
-base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-int.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionRANDOM', drop.dead = TRUE)
-int2.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionSUSTAIN', drop.dead = TRUE)
-#base.dat <- read_agg_subset_batch_out(out.path, 'baseline', drop.dead = TRUE)
-#int1.dat <- read_agg_subset_batch_out(out.path, 'ChildPovertyReduction', drop.dead = TRUE)
+```{r}
+out.path <- here::here('output', 'default_config')
+
+# define subset of variables to reduce size of batch output
+var.list <- c('pidp', 'hidp', 'time', 'weight', 
+              'age', 'ethnicity', 'education_state', 'region', 
+              'hh_income',
+              'housing_quality', 'neighbourhood_safety', 'loneliness', 'ncigs', 'nutrition_quality', 'financial_situation', 'urban', 'housing_tenure',
+              'SF_12', 'matdep_child')
+
+base <- read_output(out.path, 
+                        scenario = 'baseline', 
+                        var.list = var.list,
+                        verbose = TRUE)
+int <- read_output(out.path, 
+                            scenario = 'ChildPovertyReductionSUSTAIN', 
+                            var.list = var.list,
+                            verbose = TRUE)
 ```
 
-# Relative Poverty Reduction
+# PLOTS
 
-The first intervention we will focus on is a reduction in the prevalence of children in relative poverty.
-In these interventions, we have a target level of child poverty to attain (10% of children in a household in poverty) by a specified target year, which is 2030 unless stated otherwise.
-To achieve this, we find households with a hh_income under the poverty line, and uplift a number of households each year to linearly achieve the target proportion by the target year.
+## Relative Poverty
 
-## Threshold
+### Threshold
 
@@
 
-We can calculate the relative poverty threshold for our starting year of 2020:
+For our starting year of 2020:
 
-```{r}
-base.2020 <- base.dat %>%
+```{r, echo=FALSE}
+base.2020 <- base %>%
   filter(time == 2020)
@@
 
-We can also look at how this evolves over time in the baseline simulation:
+Then looking at how this threshold changes over the length of our simulation:
 
-```{r}
-threshold <- base.dat %>%
+```{r, echo=FALSE}
+threshold <- base %>%
   select(time, weight, hh_income) %>%
@@
 
-The threshold for relative poverty decreases over time in our simulation (it's worth noting that monetary values in our simulation have been adjusted for inflation to 2020 £s).
-This suggests that our population is getting slightly less wealthy over time on average.
-
-## Random Uplift
-
-In this intervention, we will randomly select households to uplift in each year until we uplift the number of children required for that year.
-
-### Boosted Sample
-
-We can also look at how many people are receiving the intervention over time, and the total and mean amounts of money being added to the system.
-This should slowly increase to 2030 and then hold fairly steady.
+### MCS - Whole Pop
 
 ```{r}
+full.sample.change.SF12 <- function(base.dat, int.dat) {
+  base.all.SF12 <- base.dat %>%
+    select(time, weight, SF_12) %>%
+    group_by(time) %>%
+    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
 
+  int.all.SF12 <- int.dat %>%
+    select(time, weight, SF_12) %>%
+    group_by(time) %>%
+    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
+
+  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
+  combined$diff <- combined$int.SF12 - combined$base.SF12
+
+  ggplot(combined, aes(x = time, y = diff)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12') +
+    xlab('Year') +
+    ylab('Difference')
+}
+
+full.sample.change.SF12(base, int)
+```
+
+## DIAGNOSTICS
+
+```{r}
 sample_information <- function(int.dat, target.year) {
@@
 
-sample_information(int.dat, target.year = 2030)
+sample_information(int, target.year = 2030)
 ```
-
-Now lets look at SF_12_MCS comparisons.
-
-### SF_12_MCS
-
-SF_12_MCS stands for the Mental Component Score (MCS) from the 12-item Short Form (SF) Survey.
-See [this paper](https://link.springer.com/referenceworkentry/10.1007/978-94-007-0753-5_2698) for more information about SF_12.
-
-#### Full Sample
-
-First lets look at the effect of the intervention on the entire sample.
-
-```{r}
-full.sample.change.SF12 <- function(base.dat, int.dat) {
-  base.all.SF12 <- base.dat %>%
-    select(time, weight, SF_12) %>%
-    group_by(time) %>%
-    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
-
-  int.all.SF12 <- int.dat %>%
-    select(time, weight, SF_12) %>%
-    group_by(time) %>%
-    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
-
-  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
-  combined$diff <- combined$int.SF12 - combined$base.SF12
-
-  ggplot(combined, aes(x = time, y = diff)) +
-    geom_line() +
-    geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12') +
-    xlab('Year') +
-    ylab('Difference')
-}
-
-full.sample.change.SF12(base.dat, int.dat)
-```
-
-#### Families with children
-
-Now focused only on families with children.
-
-```{r}
-all.families.change.SF12 <- function(base.dat, int.dat) {
-  base.all.SF12 <- base.dat %>%
-    select(time, weight, SF_12, nkids) %>%
-    filter(nkids > 0) %>%
-    group_by(time) %>%
-    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
-
-  int.all.SF12 <- int.dat %>%
-    select(time, weight, SF_12, nkids) %>%
-    filter(nkids > 0) %>%
-    group_by(time) %>%
-    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
-
-  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
-  combined$diff <- combined$int.SF12 - combined$base.SF12
-
-  ggplot(combined, aes(x = time, y = diff)) +
-    geom_line() +
-    geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12') +
-    xlab('Year') +
-    ylab('Difference')
-}
-all.families.change.SF12(base.dat, int.dat)
-```
-
-#### Families w/ children under poverty line
-
-Now only households with children under the poverty line.
-
-```{r}
-poverty.families.change.SF12 <- function(base.dat, int.dat, threshold) {
-  base.thresh <- merge(base.dat, threshold, by = 'time')
-  int.thresh <- merge(int.dat, threshold, by = 'time')
-
-  base.all.SF12 <- base.thresh %>%
-    select(time, weight, SF_12, nkids, hh_income, poverty_threshold) %>%
-    filter(nkids > 0) %>%
-    filter(hh_income < poverty_threshold) %>%
-    group_by(time) %>%
-    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
-
-  int.all.SF12 <- int.thresh %>%
-    select(time, weight, SF_12, nkids, hh_income, poverty_threshold) %>%
-    filter(nkids > 0) %>%
-    filter(hh_income < poverty_threshold) %>%
-    group_by(time) %>%
-    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
-
-  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
-  combined$diff <- combined$int.SF12 - combined$base.SF12
-
-  ggplot(combined, aes(x = time, y = diff)) +
-    geom_line() +
-    geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12') +
-    xlab('Year') +
-    ylab('Difference')
-}
-
-poverty.families.change.SF12(base.dat, int.dat, threshold)
-```
-
-This plot is perhaps a bit disingenuous, as the closer we get to 2030 the fewer households are actually under the poverty line.
-We might achieve what we want better by looking only at the boosted population.
-
-#### Treatment on the Treated
-
-```{r}
-treatment.on.treated.change.SF12 <- function(base.dat, int.dat) {
-  boosted.byyear <- int.dat %>%
-    filter(income_boosted == 'True')
-
-  base.all.SF12 <- base.dat %>%
-    select(time, weight, SF_12, nkids, pidp) %>%
-    filter(pidp %in% boosted.byyear$pidp) %>%
-    group_by(time) %>%
-    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
-
-  int.all.SF12 <- int.dat %>%
-    select(time, weight, SF_12, nkids, pidp) %>%
-    filter(pidp %in% boosted.byyear$pidp) %>%
-    group_by(time) %>%
-    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
-
-  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
-  combined$diff <- combined$int.SF12 - combined$base.SF12
-
-  ggplot(combined, aes(x = time, y = diff)) +
-    geom_line() +
-    geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12') +
-    xlab('Year') +
-    ylab('Difference')
-}
-
-treatment.on.treated.change.SF12(base.dat, int.dat)
-```
-
-### True Treatment on Treated
-
-Instead of looking at the difference in means
-
-## Sustained Uplift
-
-This intervention is similar to the random uplift intervention with one difference.
-In the first year that the intervention is applied, households are randomly chosen for uplift until the correct number of children for that year are uplifted.
-The difference comes in subsequent years.
-From year 2 onwards, households that have been previously intervened on will once again be uplifted to above the poverty line (if they are once again below).
-This is the meaning of the sustained intervention, where families are chosen at random and then maintained above the poverty line, instead of picking a random subset of households under the poverty line as in the random intervention.
-
-### Boosted Sample
-
-```{r}
-sample_information(int2.dat, target.year = 2030)
-```
-
-### SF_12_MCS
-
-#### Full Sample
-
-```{r}
-full.sample.change.SF12(base.dat, int2.dat)
-```
-
-#### Families with children
-
-```{r}
-all.families.change.SF12(base.dat, int.dat)
-```
-
-#### Families w/ children under poverty line
-
-```{r}
-poverty.families.change.SF12(base.dat, int.dat, threshold)
-```
-
-#### Treatment on the Treated
-
-```{r}
-treatment.on.treated.change.SF12(base.dat, int.dat)
-```
-
-```{r}
-
-```

### 2024-01-15 minos/outcomes/CPR_vis.Rmd
Added some plots for assessing SF_12 change from Child Poverty Reduction (CPR) intervention

@@
     geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12') +
+    labs(title = 'Relative change in SF12', subtitle = 'Whole population') +
     xlab('Year') +
@@
 full.sample.change.SF12(base, int)
+```
+
+### MCS - Families with children
+
+Now focused only on families with children.
+
+```{r}
+all.families.change.SF12 <- function(base.dat, int.dat) {
+  base.all.SF12 <- base.dat %>%
+    select(time, weight, SF_12, nkids) %>%
+    filter(nkids > 0) %>%
+    group_by(time) %>%
+    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
+
+  int.all.SF12 <- int.dat %>%
+    select(time, weight, SF_12, nkids) %>%
+    filter(nkids > 0) %>%
+    group_by(time) %>%
+    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
+
+  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
+  combined$diff <- combined$int.SF12 - combined$base.SF12
+
+  ggplot(combined, aes(x = time, y = diff)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12', subtitle = 'Families with children') +
+    xlab('Year') +
+    ylab('Difference')
+}
+all.families.change.SF12(base, int)
+```
+
+### MCS - Treatment on the Treated
+
+```{r}
+treatment.on.treated.change.SF12 <- function(base.dat, int.dat) {
+  boosted.byyear <- int.dat %>%
+    filter(income_boosted == 'True')
+
+  base.all.SF12 <- base.dat %>%
+    select(time, weight, SF_12, nkids, pidp) %>%
+    filter(pidp %in% boosted.byyear$pidp) %>%
+    group_by(time) %>%
+    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
+
+  int.all.SF12 <- int.dat %>%
+    select(time, weight, SF_12, nkids, pidp) %>%
+    filter(pidp %in% boosted.byyear$pidp) %>%
+    group_by(time) %>%
+    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
+
+  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
+  combined$diff <- combined$int.SF12 - combined$base.SF12
+
+  ggplot(combined, aes(x = time, y = diff)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12', subtitle = 'Treatment on the treated') +
+    xlab('Year') +
+    ylab('Difference')
+}
+
+treatment.on.treated.change.SF12(base, int)
 ```
@@
 ```
+
+```{r, echo=FALSE}
+
+```

### 2024-01-15 minos/outcomes/SCP_vis.Rmd
Started on notebook for visualising Scottish Child Payment (SCP) interventions

--- 2024-01-15 minos/outcomes/CPR_vis.Rmd
@@
 ---
-title: "Child Poverty Reduction Interventions"
+title: "Scottish Child Payment Interventions"
 output:
@@
                     verbose = TRUE)
-int <- read_output(out.path, 
-                            scenario = 'ChildPovertyReductionSUSTAIN', 
+int25All <- read_output(out.path, 
+                        scenario = '25All', 
                         var.list = var.list,
                         verbose = TRUE)
+int50All <- read_output(out.path, 
+                        scenario = '50All', 
+                        var.list = var.list,
+                        verbose = TRUE)
+int75All <- read_output(out.path, 
+                        scenario = '75All', 
+                        var.list = var.list,
+                        verbose = TRUE)
+int100All <- read_output(out.path, 
+                        scenario = '100All', 
+                        var.list = var.list,
+                        verbose = TRUE)
+
+int.list <- c(int25All, int50All, int75All, int100All)
 ```
@@
 
-## Relative Poverty
-
-### Threshold
-
-Relative poverty is defined as the proportion of children living in households with income below 60% of the population median *in a given year*.
-
-For our starting year of 2020:
-
-```{r, echo=FALSE}
-base.2020 <- base %>%
-  filter(time == 2020)
-
-mean.hh_income <- weighted.mean(base.2020$hh_income, w = base.2020$weight)
-rel.pov.threshold <- mean.hh_income * 0.6
-
-print(paste0("Relative poverty threshold in 2020: ", rel.pov.threshold))
-rm(base.2020, mean.hh_income, rel.pov.threshold)
-```
-
-Then looking at how this threshold changes over the length of our simulation:
-
-```{r, echo=FALSE}
-threshold <- base %>%
-  select(time, weight, hh_income) %>%
-  group_by(time) %>%
-  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
-
-ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
-  geom_col() +
-  geom_hline(yintercept = threshold$poverty_threshold[threshold$time == 2020], linetype='dashed') +
-  labs(title = 'Relative poverty threshold over time') +
-  xlab('Year') +
-  ylab('Threshold')
-```
-
-### MCS - Whole Pop
+## MCS - Whole Population
 
@@
 ```
-
-## DIAGNOSTICS
-
-```{r}
-sample_information <- function(int.dat, target.year) {
-  hh_boosted <- int.dat %>%
-    select(hidp, time, income_boosted, boost_amount, nkids) %>%
-    filter(income_boosted == 'True') %>%
-    group_by(time) %>%
-    summarise(n_boosted = length(unique(hidp)),
-              total_boost = sum(boost_amount),
-              kids_boosted = sum(nkids))
-
-  p1 <- ggplot(hh_boosted, aes(x = time, y = n_boosted)) +
-    geom_line() +
-    geom_vline(xintercept = target.year, linetype = 'dashed') +
-    labs(title = 'Number of households receiving intervention') +
-    xlab('Year') +
-    ylab('Number Boosted')
-
-  p2 <- ggplot(hh_boosted, aes(x = time, y = kids_boosted)) +
-    geom_line() +
-    geom_vline(xintercept = target.year, linetype = 'dashed') +
-    labs(title = 'Number of children in households receiving intervention') +
-    xlab('Year') +
-    ylab('Number Children')
-
-  p3 <- ggplot(hh_boosted, aes(x = time, y = total_boost)) +
-    geom_line() +
-    geom_vline(xintercept = target.year, linetype = 'dashed') +
-    labs(title = 'Total boost amount') +
-    xlab('Year') +
-    ylab('Boost Amount')
-
-  mean.boost <- int.dat %>%
-    select(time, income_boosted, boost_amount) %>%
-    group_by(time, income_boosted) %>%
-    summarise(mean_boost = mean(boost_amount)) %>%
-    filter(income_boosted == 'True')
-
-  p4 <- ggplot(mean.boost, aes(x = time, y = mean_boost)) +
-    geom_line() +
-    geom_vline(xintercept = target.year, linetype = 'dashed') +
-    labs(title = 'Mean boost amount') +
-    xlab('Year') +
-    ylab('Boost Amount')
-
-  print(p1)
-  print(p2)
-  print(p3)
-  print(p4)
-}
-
-sample_information(int, target.year = 2030)
-```

### 2024-01-16 minos/outcomes/CPR_vis.Rmd
Additions to the CPR and SCP vis scripts, and modified some of the datain functions to better handle batch files

--- 2024-01-15 minos/outcomes/CPR_vis.Rmd
@@
 var.list <- c('pidp', 'hidp', 'time', 'weight', 
-              'age', 'ethnicity', 'education_state', 'region', 
+              'age', 'ethnicity', 'education_state', 'region', 'nkids',
               'hh_income',
@@
                             verbose = TRUE)
+
+# base$income_boosted <- FALSE
+# base$boost_amount <- 0
+
+# set up a boolean tag for batch or not
+# this is necessary because batch runs need slightly different processing before visualisation
+if ('run_id' %in% names(base)) {
+  batch <- TRUE
+} else {
+  batch <- FALSE
+}
+
+# Save path and save flag
+save.path <- here::here('plots', 'SCOTGOV', 'CPR')
+shall.we.save <- FALSE
+plot.width <- 10
+plot.height <- 5
+```
+
+# FUNCTIONS
+
+```{r SF12_full_sample, echo=FALSE}
+SF12.change.full.sample.single <- function(base.dat, int.dat) {
+  base.all.SF12 <- base.dat %>%
+    select(time, weight, SF_12) %>%
+    group_by(time) %>%
+    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
+
+  int.all.SF12 <- int.dat %>%
+    select(time, weight, SF_12) %>%
+    group_by(time) %>%
+    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
+
+  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
+  combined$diff <- combined$int.SF12 - combined$base.SF12
+
+  p1 <- ggplot(combined, aes(x = time, y = diff)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12', subtitle = 'Whole population') +
+    xlab('Year') +
+    ylab('Difference')
+
+  print(p1)
+
+  if (shall.we.save) {
+    filename <- paste0(save.path, 'SF12_whole_pop_single.png')
+
+    ggsave(filename = filename,
+           plot = p1,
+           width = plot.width,
+           height = plot.height)
+  }
+}
+
+SF12.change.full.sample.batch <- function(base.dat, int.dat, batch) {
+  base.all.SF12 <- base.dat %>%
+    select(time, weight, run_id, SF_12) %>%
+    group_by(time, run_id) %>%
+    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
+
+  int.all.SF12 <- int.dat %>%
+    select(time, weight, run_id, SF_12) %>%
+    group_by(time, run_id) %>%
+    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
+
+  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = c('time', 'run_id'))
+  combined$diff <- combined$int.SF12 - combined$base.SF12
+
+  p1 <- ggplot(combined, aes(x = time, y = diff)) +
+    geom_smooth() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12', subtitle = 'Whole population') +
+    xlab('Year') +
+    ylab('Difference')
+
+  print(p1)
+
+  if (shall.we.save) {
+    filename <- paste0(save.path, 'SF12_whole_pop_batch.png')
+    ggsave(filename = filename,
+           plot = p1,
+           width = plot.width,
+           height = plot.height)
+  }
+}
+```
+
+```{r SF12_subpop, echo=FALSE}
+SF12.change.families.single <- function(base.dat, int.dat) {
+  base.all.SF12 <- base.dat %>%
+    select(time, weight, SF_12, nkids) %>%
+    filter(nkids > 0) %>%
+    group_by(time) %>%
+    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
+
+  int.all.SF12 <- int.dat %>%
+    select(time, weight, SF_12, nkids) %>%
+    filter(nkids > 0) %>%
+    group_by(time) %>%
+    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
+
+  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
+  combined$diff <- combined$int.SF12 - combined$base.SF12
+
+  p1 <- ggplot(combined, aes(x = time, y = diff)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12', subtitle = 'Families with children') +
+    xlab('Year') +
+    ylab('Difference')
+
+  print(p1)
+
+  if (shall.we.save) {
+    filename <- paste0(save.path, 'SF12_families_single.png')
+
+    ggsave(filename = filename,
+           plot = p1,
+           width = plot.width,
+           height = plot.height)
+  }
+}
+
+SF12.change.families.batch <- function(base.dat, int.dat) {
+  base.all.SF12 <- base.dat %>%
+    select(time, weight, run_id, SF_12, nkids) %>%
+    filter(nkids > 0) %>%
+    group_by(time, run_id) %>%
+    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
+
+  int.all.SF12 <- int.dat %>%
+    select(time, weight, run_id, SF_12, nkids) %>%
+    filter(nkids > 0) %>%
+    group_by(time, run_id) %>%
+    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
+
+  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
+  combined$diff <- combined$int.SF12 - combined$base.SF12
+
+  p1 <- ggplot(combined, aes(x = time, y = diff)) +
+    geom_smooth() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12', subtitle = 'Families with children') +
+    xlab('Year') +
+    ylab('Difference')
+
+  print(p1)
+
+  if (shall.we.save) {
+    filename <- paste0(save.path, 'SF12_families_batch.png')
+    ggsave(filename = filename,
+           plot = p1,
+           width = plot.width,
+           height = plot.height)
+  }
+}
+```
+
+```{r SF12_treated, echo=FALSE}
+SF12.change.treated.single <- function(base.dat, int.dat) {
+  boosted.byyear <- int.dat %>%
+    filter(income_boosted == 'True')
+
+  base.all.SF12 <- base.dat %>%
+    select(time, weight, SF_12, nkids, pidp) %>%
+    filter(pidp %in% boosted.byyear$pidp) %>%
+    group_by(time) %>%
+    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
+
+  int.all.SF12 <- int.dat %>%
+    select(time, weight, SF_12, nkids, pidp) %>%
+    filter(pidp %in% boosted.byyear$pidp) %>%
+    group_by(time) %>%
+    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
+
+  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
+  combined$diff <- combined$int.SF12 - combined$base.SF12
+
+  p1 <- ggplot(combined, aes(x = time, y = diff)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12', subtitle = 'Treatment on the treated') +
+    xlab('Year') +
+    ylab('Difference')
+
+  print(p1)
+
+  if (shall.we.save) {
+    filename <- paste0(save.path, 'SF12_treated_single.png')
+    ggsave(filename = filename,
+           plot = p1,
+           width = plot.width,
+           height = plot.height)
+  }
+}
+
+SF12.change.treated.batch <- function(base.dat, int.dat) {
+
+  #TODO: Filter pidps by run_id by year instead of taking all pidps across runs
+  boosted.byyear <- int.dat %>%
+    filter(income_boosted == 'True')
+
+  base.all.SF12 <- base.dat %>%
+    select(time, weight, run_id, SF_12, nkids, pidp) %>%
+    filter(pidp %in% boosted.byyear$pidp) %>%
+    group_by(time, run_id) %>%
+    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
+
+  int.all.SF12 <- int.dat %>%
+    select(time, weight, run_id, SF_12, nkids, pidp) %>%
+    filter(pidp %in% boosted.byyear$pidp) %>%
+    group_by(time, run_id) %>%
+    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
+
+  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = c('time', 'run_id'))
+  combined$diff <- combined$int.SF12 - combined$base.SF12
+
+  p1 <- ggplot(combined, aes(x = time, y = diff)) +
+    geom_smooth() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12', subtitle = 'Treatment on the treated') +
+    xlab('Year') +
+    ylab('Difference')
+
+  print(p1)
+
+  if (shall.we.save) {
+    filename <- paste0(save.path, 'SF12_treated_single.png')
+    ggsave(filename = filename,
+           plot = p1,
+           width = plot.width,
+           height = plot.height)
+  }
+}
 ```
@@
 print(paste0("Relative poverty threshold in 2020: ", rel.pov.threshold))
-rm(base.2020, mean.hh_income, rel.pov.threshold)
+rm(base.2020, mean.hh_income)
 ```
@@
   geom_col() +
-  geom_hline(yintercept = threshold$poverty_threshold[threshold$time == 2020], linetype='dashed') +
+  geom_hline(yintercept = rel.pov.threshold, linetype='dashed') +
+  labs(title = 'Relative poverty threshold over time') +
+  xlab('Year') +
+  ylab('Threshold')
+
+threshold <- base %>%
+  select(time, weight, run_id, hh_income) %>%
+  group_by(time, run_id) %>%
+  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6)) %>%
+  group_by(time) %>%
+  summarise(poverty_threshold_mean = mean(poverty_threshold),
+            lower = min(poverty_threshold),
+            upper = max(poverty_threshold))
+
+ggplot(data = threshold, aes(x = time, y = poverty_threshold_mean)) +
+  geom_col() +
+  geom_errorbar(aes(ymin = lower, ymax = upper), position = 'dodge') +
+  geom_hline(yintercept = rel.pov.threshold, linetype='dashed') +
   labs(title = 'Relative poverty threshold over time') +
@@
 ```{r}
-full.sample.change.SF12 <- function(base.dat, int.dat) {
-  base.all.SF12 <- base.dat %>%
-    select(time, weight, SF_12) %>%
-    group_by(time) %>%
-    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
+if (batch) {
+  SF12.change.full.sample.batch(base, int)
+} else {
+  SF12.change.full.sample.single(base, int)
+}
+```
 
-  int.all.SF12 <- int.dat %>%
-    select(time, weight, SF_12) %>%
-    group_by(time) %>%
-    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
+### MCS - Families with children
 
-  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
-  combined$diff <- combined$int.SF12 - combined$base.SF12
+Now focused only on families with children.
 
-  ggplot(combined, aes(x = time, y = diff)) +
-    geom_line() +
-    geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12') +
-    xlab('Year') +
-    ylab('Difference')
+```{r}
+if (batch) {
+  SF12.change.families.batch(base, int)
+} else {
+  SF12.change.families.single(base, int)
 }
+```
 
-full.sample.change.SF12(base, int)
+### MCS - Treatment on the Treated
+
+```{r}
+if (batch) {
+  SF12.change.treated.batch(base, int)
+} else {
+  SF12.change.treated.single(base, int)
+}
 ```

### 2024-01-16 minos/outcomes/SCP_vis.Rmd
Additions to the CPR and SCP vis scripts, and modified some of the datain functions to better handle batch files

@@
 ```{r}
-out.path <- here::here('output', 'default_config')
+out.path <- here::here('output', 'default_config_batch')
 
@@
 int.list <- c(int25All, int50All, int75All, int100All)
+
+# set up a boolean tag for batch or not
+# this is necessary because batch runs need slightly different processing before visualisation
+if ('run_id' %in% names(base)) {
+  batch <- TRUE
+} else {
+  batch <- FALSE
+}
+
+# Save path and save flag
+save.path <- here::here('plots', 'SCOTGOV', 'CPR')
+shall.we.save <- FALSE
+plot.width <- 10
+plot.height <- 5
 ```
@@
 ```{r}
-full.sample.change.SF12 <- function(base.dat, int.dat) {
+SF12.change.full.sample.single <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
+  base <- base.dat %>%
+    select(time, weight, SF_12) %>%
+    group_by(time) %>%
+    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
+
+  int1 <- int.dat1 %>%
+    select(time, weight, SF_12) %>%
+    group_by(time) %>%
+    summarise(int1.SF12 = weighted.mean(SF_12, w = weight))
+  int2 <- int.dat2 %>%
+    select(time, weight, SF_12) %>%
+    group_by(time) %>%
+    summarise(int2.SF12 = weighted.mean(SF_12, w = weight))
+  int3 <- int.dat3 %>%
+    select(time, weight, SF_12) %>%
+    group_by(time) %>%
+    summarise(int3.SF12 = weighted.mean(SF_12, w = weight))
+  int4 <- int.dat4 %>%
+    select(time, weight, SF_12) %>%
+    group_by(time) %>%
+    summarise(int4.SF12 = weighted.mean(SF_12, w = weight))
+
+  # now combine all data together and calculate differences
+  combined <- merge(x = base, y = int1, by = 'time')
+  combined <- merge(x = merged, y = int2, by = 'time')
+  combined <- merge(x = merged, y = int3, by = 'time')
+  combined <- merge(x = merged, y = int4, by = 'time')
+
+  combined$diff <- combined$int.SF12 - combined$base.SF12
+
+  ggplot(combined, aes(x = time, y = diff)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12', subtitle = 'Whole population') +
+    xlab('Year') +
+    ylab('Difference')
+}
+
+full.sample.change.SF12(base, int)
+```
+
+```{r}
+SF12.change.full.sample.single <- function(base.dat, int.dat) {
   base.all.SF12 <- base.dat %>%
@@
 
-  ggplot(combined, aes(x = time, y = diff)) +
+  p1 <- ggplot(combined, aes(x = time, y = diff)) +
     geom_line() +
@@
     ylab('Difference')
+
+  print(p1)
+
+  if (shall.we.save) {
+    filename <- paste0(save.path, 'SF12_whole_pop_single.png')
+
+    ggsave(filename = filename,
+           plot = p1,
+           width = plot.width,
+           height = plot.height)
+  }
 }
 
-full.sample.change.SF12(base, int)
+SF12.change.full.sample.batch <- function(base.dat, int.dat, batch) {
+  base.all.SF12 <- base.dat %>%
+    select(time, weight, run_id, SF_12) %>%
+    group_by(time, run_id) %>%
+    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
+
+  int.all.SF12 <- int.dat %>%
+    select(time, weight, run_id, SF_12) %>%
+    group_by(time, run_id) %>%
+    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
+
+  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = c('time', 'run_id'))
+  combined$diff <- combined$int.SF12 - combined$base.SF12
+
+  p1 <- ggplot(combined, aes(x = time, y = diff)) +
+    geom_smooth() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12', subtitle = 'Whole population') +
+    xlab('Year') +
+    ylab('Difference')
+
+  print(p1)
+
+  if (shall.we.save) {
+    filename <- paste0(save.path, 'SF12_whole_pop_batch.png')
+    ggsave(filename = filename,
+           plot = p1,
+           width = plot.width,
+           height = plot.height)
+  }
+}
 ```

### 2024-01-16 minos/outcomes/CPR_vis.Rmd
More additions to visualisation scripts and small changes to datain functions

@@
                         verbose = TRUE)
+
+### NOTE: READING INTERVENTION OUTPUTS IS CURRENTLY BROKEN FOR BATCH RUNS
+#         THIS IS BECAUSE WE ARE NO LONGER USING BOOST_AMOUNT
+
 int <- read_output(out.path, 
@@
                             verbose = TRUE)
-
-# base$income_boosted <- FALSE
-# base$boost_amount <- 0
 
@@
     geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12', subtitle = 'Families with children') +
+    labs(title = 'Relative change in SF12', subtitle = 'Households with children') +
     xlab('Year') +

### 2024-01-16 minos/outcomes/SCP_vis.Rmd
More additions to visualisation scripts and small changes to datain functions

--- 2024-01-15 minos/outcomes/SCP_vis.Rmd
@@
 int.list <- c(int25All, int50All, int75All, int100All)
+
+# set up a boolean tag for batch or not
+# this is necessary because batch runs need slightly different processing before visualisation
+if ('run_id' %in% names(base)) {
+  batch <- TRUE
+} else {
+  batch <- FALSE
+}
+
+# Save path and save flag
+save.path <- here::here('plots', 'SCOTGOV', 'CPR')
+create.if.not.exists(save.path)
+shall.we.save <- FALSE
+plot.width <- 10
+plot.height <- 5
+```
+
+# FUNCTIONS
+
+```{r SF12_whole_pop, echo=FALSE}
+SF12.change.full.sample.single <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
+  single.mean <- function(data, scen) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, SF_12) %>%
+      group_by(time) %>%
+      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  base <- single.mean(base.dat, scen = 'base')
+  int1 <- single.mean(int.dat1, scen = 'int25')
+  int2 <- single.mean(int.dat2, scen = 'int50')
+  int3 <- single.mean(int.dat3, scen = 'int75')
+  int4 <- single.mean(int.dat4, scen = 'int100')
+
+  df.list <- list(base, int1, int2, int3, int4)
+  combined <- df.list %>%
+    reduce(full_join, by='time')
+
+  combined$diff25 <- combined$int25.SF12 - combined$base.SF12
+  combined$diff50 <- combined$int50.SF12 - combined$base.SF12
+  combined$diff75 <- combined$int75.SF12 - combined$base.SF12
+  combined$diff100 <- combined$int100.SF12 - combined$base.SF12
+
+  combined <- combined %>%
+    select(time, contains('diff')) %>%
+    pivot_longer(cols = diff25:diff100,
+                 names_to = 'scen',
+                 values_to = 'diff')
+
+  # TODO: Rename factor levels
+  # correct factor levels for plot
+  combined$scen <- factor(combined$scen,
+                          levels = c('diff100', 'diff75', 'diff50', 'diff25'))
+
+  p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
+    xlab('Year') +
+    ylab('Difference')
+
+  print(p1)
+}
+
+SF12.change.full.sample.batch <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
+  batch.mean <- function(data, scen) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, run_id, SF_12) %>%
+      group_by(time, run_id) %>%
+      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  base <- batch.mean(base.dat, scen = 'base')
+  int1 <- batch.mean(int.dat1, scen = 'int25')
+  int2 <- batch.mean(int.dat2, scen = 'int50')
+  int3 <- batch.mean(int.dat3, scen = 'int75')
+  int4 <- batch.mean(int.dat4, scen = 'int100')
+
+  df.list <- list(base, int1, int2, int3, int4)
+  combined <- df.list %>%
+    reduce(full_join, by=c('time', 'run_id'))
+
+  combined$diff25 <- combined$int25.SF12 - combined$base.SF12
+  combined$diff50 <- combined$int50.SF12 - combined$base.SF12
+  combined$diff75 <- combined$int75.SF12 - combined$base.SF12
+  combined$diff100 <- combined$int100.SF12 - combined$base.SF12
+
+  combined <- combined %>%
+    select(time, run_id, contains('diff')) %>%
+    pivot_longer(cols = diff25:diff100,
+                 names_to = 'scen',
+                 values_to = 'diff')
+
+  # TODO: Rename factor levels
+  # correct factor levels for plot
+  combined$scen <- factor(combined$scen,
+                          levels = c('diff100', 'diff75', 'diff50', 'diff25'))
+
+  p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
+    geom_smooth() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
+    xlab('Year') +
+    ylab('Difference')
+
+  print(p1)
+}
+```
+
+```{r SF12_families, echo=FALSE}
+SF12.change.families.single <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
+  single.mean <- function(data, scen) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, SF_12, nkids) %>%
+      filter(nkids > 0) %>%
+      group_by(time) %>%
+      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  base <- single.mean(base.dat, scen = 'base')
+  int1 <- single.mean(int.dat1, scen = 'int25')
+  int2 <- single.mean(int.dat2, scen = 'int50')
+  int3 <- single.mean(int.dat3, scen = 'int75')
+  int4 <- single.mean(int.dat4, scen = 'int100')
+
+  df.list <- list(base, int1, int2, int3, int4)
+  combined <- df.list %>%
+    reduce(full_join, by='time')
+
+  combined$diff25 <- combined$int25.SF12 - combined$base.SF12
+  combined$diff50 <- combined$int50.SF12 - combined$base.SF12
+  combined$diff75 <- combined$int75.SF12 - combined$base.SF12
+  combined$diff100 <- combined$int100.SF12 - combined$base.SF12
+
+  combined <- combined %>%
+    select(time, contains('diff')) %>%
+    pivot_longer(cols = diff25:diff100,
+                 names_to = 'scen',
+                 values_to = 'diff')
+
+  # TODO: Rename factor levels
+  # correct factor levels for plot
+  combined$scen <- factor(combined$scen,
+                          levels = c('diff100', 'diff75', 'diff50', 'diff25'))
+
+  p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12 MCS', subtitle = 'Households with Children') +
+    xlab('Year') +
+    ylab('Difference')
+
+  print(p1)
+}
+
+SF12.change.families.batch <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
+  batch.mean <- function(data, scen) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, run_id, SF_12, nkids) %>%
+      filter(nkids > 0) %>%
+      group_by(time, run_id) %>%
+      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  base <- batch.mean(base.dat, scen = 'base')
+  int1 <- batch.mean(int.dat1, scen = 'int25')
+  int2 <- batch.mean(int.dat2, scen = 'int50')
+  int3 <- batch.mean(int.dat3, scen = 'int75')
+  int4 <- batch.mean(int.dat4, scen = 'int100')
+
+  df.list <- list(base, int1, int2, int3, int4)
+  combined <- df.list %>%
+    reduce(full_join, by=c('time', 'run_id'))
+
+  combined$diff25 <- combined$int25.SF12 - combined$base.SF12
+  combined$diff50 <- combined$int50.SF12 - combined$base.SF12
+  combined$diff75 <- combined$int75.SF12 - combined$base.SF12
+  combined$diff100 <- combined$int100.SF12 - combined$base.SF12
+
+  combined <- combined %>%
+    select(time, run_id, contains('diff')) %>%
+    pivot_longer(cols = diff25:diff100,
+                 names_to = 'scen',
+                 values_to = 'diff')
+
+  # TODO: Rename factor levels
+  # correct factor levels for plot
+  combined$scen <- factor(combined$scen,
+                          levels = c('diff100', 'diff75', 'diff50', 'diff25'))
+
+  p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
+    geom_smooth() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12 MCS', subtitle = 'Households with Children') +
+    xlab('Year') +
+    ylab('Difference')
+
+  print(p1)
+}
+```
+
+```{r SF12_treated, echo=FALSE}
+SF12.change.treated.single <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
+  single.mean <- function(data, scen, boosted) {
+    # define varname
+    newvar.name <- paste0(scen, '.SF12')
+    # prepare data
+    data <- data %>%
+      select(pidp, time, weight, SF_12) %>%
+      filter(pidp %in% boosted) %>%
+      group_by(time) %>%
+      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  #TODO: FIX THIS! NEED DIFFERENT BASELINE FOR EACH INT?? THINK SO!
+  # NEED A FUNCTION TO DO THE DIFF CALCULATION AND ANOTHER TO RUN IT THROUGH
+  # EACH DF
+  # get boosted pidps
+  boosted <- int.dat1 %>%
+    select(pidp, income_boosted) %>%
+    filter(income_boosted == 'True')
+
+  base <- single.mean(base.dat, scen = 'base', boosted$pidp)
+  int1 <- single.mean(int.dat1, scen = 'int25', boosted$pidp)
+  int2 <- single.mean(int.dat2, scen = 'int50', boosted$pidp)
+  int3 <- single.mean(int.dat3, scen = 'int75', boosted$pidp)
+  int4 <- single.mean(int.dat4, scen = 'int100', boosted$pidp)
+
+  df.list <- list(base, int1, int2, int3, int4)
+  combined <- df.list %>%
+    reduce(full_join, by='time')
+
+  combined$diff25 <- combined$int25.SF12 - combined$base.SF12
+  combined$diff50 <- combined$int50.SF12 - combined$base.SF12
+  combined$diff75 <- combined$int75.SF12 - combined$base.SF12
+  combined$diff100 <- combined$int100.SF12 - combined$base.SF12
+
+  combined <- combined %>%
+    select(time, contains('diff')) %>%
+    pivot_longer(cols = diff25:diff100,
+                 names_to = 'scen',
+                 values_to = 'diff')
+
+  # TODO: Rename factor levels
+  # correct factor levels for plot
+  combined$scen <- factor(combined$scen,
+                          levels = c('diff100', 'diff75', 'diff50', 'diff25'))
+
+  p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12 MCS', subtitle = 'Treated Population') +
+    xlab('Year') +
+    ylab('Difference')
+
+  print(p1)
+}
+
+SF12.change.treated.batch <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
+  batch.mean <- function(data, scen, boosted) {
+    # define varname
+    newvar.name <- paste0(scen, '.SF12')
+    # prepare data
+    data <- data %>%
+      select(pidp, time, weight, run_id, SF_12) %>%
+      filter(pidp %in% boosted) %>%
+      group_by(time, run_id) %>%
+      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  #TODO: FIX THIS! NEED DIFFERENT BASELINE FOR EACH INT?? THINK SO!
+  # NEED A FUNCTION TO DO THE DIFF CALCULATION AND ANOTHER TO RUN IT THROUGH
+  # EACH DF
+  # get boosted pidps
+  boosted <- int.dat1 %>%
+    select(pidp, income_boosted) %>%
+    filter(income_boosted == 'True')
+
+  base <- batch.mean(base.dat, scen = 'base', boosted$pidp)
+  int1 <- batch.mean(int.dat1, scen = 'int25', boosted$pidp)
+  int2 <- batch.mean(int.dat2, scen = 'int50', boosted$pidp)
+  int3 <- batch.mean(int.dat3, scen = 'int75', boosted$pidp)
+  int4 <- batch.mean(int.dat4, scen = 'int100', boosted$pidp)
+
+  df.list <- list(base, int1, int2, int3, int4)
+  combined <- df.list %>%
+    reduce(full_join, by=c('time', 'run_id'))
+
+  combined$diff25 <- combined$int25.SF12 - combined$base.SF12
+  combined$diff50 <- combined$int50.SF12 - combined$base.SF12
+  combined$diff75 <- combined$int75.SF12 - combined$base.SF12
+  combined$diff100 <- combined$int100.SF12 - combined$base.SF12
+
+  combined <- combined %>%
+    select(time, run_id, contains('diff')) %>%
+    pivot_longer(cols = diff25:diff100,
+                 names_to = 'scen',
+                 values_to = 'diff')
+
+  # TODO: Rename factor levels
+  # correct factor levels for plot
+  combined$scen <- factor(combined$scen,
+                          levels = c('diff100', 'diff75', 'diff50', 'diff25'))
+
+  p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
+    geom_smooth() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12 MCS', subtitle = 'Treated Population') +
+    xlab('Year') +
+    ylab('Difference')
+
+  print(p1)
+}
 ```
@@
 ```{r}
-full.sample.change.SF12 <- function(base.dat, int.dat) {
-  base.all.SF12 <- base.dat %>%
-    select(time, weight, SF_12) %>%
-    group_by(time) %>%
-    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
+if (batch) {
+  SF12.change.full.sample.batch(base, int25All, int50All, int75All, int100All)
+} else {
+  SF12.change.full.sample.single(base, int25All, int50All, int75All, int100All)
+}
+```
 
-  int.all.SF12 <- int.dat %>%
-    select(time, weight, SF_12) %>%
-    group_by(time) %>%
-    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
+## MCS - Households with Children
 
-  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
-  combined$diff <- combined$int.SF12 - combined$base.SF12
+```{r}
+if (batch) {
+  SF12.change.families.batch(base, int25All, int50All, int75All, int100All)
+} else {
+  SF12.change.families.single(base, int25All, int50All, int75All, int100All)
+}
+```
 
-  ggplot(combined, aes(x = time, y = diff)) +
-    geom_line() +
-    geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12', subtitle = 'Whole population') +
-    xlab('Year') +
-    ylab('Difference')
+## MCS - Treatment on Treated
+
+```{r}
+if (batch) {
+  print('batch')
+  SF12.change.treated.batch(base, int25All, int50All, int75All, int100All)
+} else {
+  SF12.change.treated.single(base, int25All, int50All, int75All, int100All)
 }
-
-full.sample.change.SF12(base, int)
 ```

### 2024-01-17 minos/outcomes/SCP_vis.Rmd
More additions to SCP_vis.Rmd

@@
 if (batch) {
-  print('batch')
   SF12.change.treated.batch(base, int25All, int50All, int75All, int100All)

### 2024-01-18 minos/outcomes/SCP_vis.Rmd
Fix path to work with arc outputs
Modified SCP_vis to accept an arbitrary number of intervention scenarios. Next step is to fully automate scenario labels

@@
 ```{r}
-out.path <- here::here('output', 'default_config_batch')
+# out.path <- here::here('output', 'default_config')
+# 
+# # define subset of variables to reduce size of batch output
+# var.list <- c('pidp', 'hidp', 'time', 'weight', 
+#               'age', 'ethnicity', 'education_state', 'region', 'nkids',
+#               'hh_income',
+#               'housing_quality', 'neighbourhood_safety', 'loneliness', 'ncigs', 'nutrition_quality', 'financial_situation', 'urban', 'housing_tenure',
+#               'SF_12', 'matdep_child')
+# 
+# base <- read_output(out.path, 
+#                     scenario = 'baseline', 
+#                     var.list = var.list,
+#                     verbose = TRUE)
+# int25All <- read_output(out.path, 
+#                         scenario = '25All', 
+#                         var.list = var.list,
+#                         verbose = TRUE)
+# int50All <- read_output(out.path, 
+#                         scenario = '50All', 
+#                         var.list = var.list,
+#                         verbose = TRUE)
+# int75All <- read_output(out.path, 
+#                         scenario = '75All', 
+#                         var.list = var.list,
+#                         verbose = TRUE)
+# int100All <- read_output(out.path, 
+#                         scenario = '100All', 
+#                         var.list = var.list,
+#                         verbose = TRUE)
+# 
+# int.list <- c(int25All, int50All, int75All, int100All)
+# 
+# # set up a boolean tag for batch or not
+# # this is necessary because batch runs need slightly different processing before visualisation
+# if ('run_id' %in% names(base)) {
+#   batch <- TRUE
+# } else {
+#   batch <- FALSE
+# }
+# 
+# # Save path and save flag
+# save.path <- here::here('plots', 'SCOTGOV', 'CPR')
+# create.if.not.exists(save.path)
+# shall.we.save <- FALSE
+# plot.width <- 10
+# plot.height <- 5
+```
+
+```{r}
+#out.path <- here::here('output', 'default_config')
+out.path <- here::here('output', 'glasgow_scaled')
 
@@
                     verbose = TRUE)
-int25All <- read_output(out.path, 
-                        scenario = '25All', 
+int25 <- read_output(out.path, 
+                      scenario = '25UniversalCredit', 
                       var.list = var.list,
                       verbose = TRUE)
-int50All <- read_output(out.path, 
-                        scenario = '50All', 
+int30 <- read_output(out.path,
+                      scenario = '30UniversalCredit',
                       var.list = var.list,
                       verbose = TRUE)
-int75All <- read_output(out.path, 
-                        scenario = '75All', 
+int35 <- read_output(out.path,
+                      scenario = '35UniversalCredit',
                       var.list = var.list,
                       verbose = TRUE)
-int100All <- read_output(out.path, 
-                        scenario = '100All', 
+int40 <- read_output(out.path,
+                      scenario = '40UniversalCredit',
+                      var.list = var.list,
+                      verbose = TRUE)
+int45 <- read_output(out.path,
+                      scenario = '45UniversalCredit',
+                      var.list = var.list,
+                      verbose = TRUE)
+int50 <- read_output(out.path,
+                      scenario = '50UniversalCredit',
                       var.list = var.list,
@@
 
-int.list <- c(int25All, int50All, int75All, int100All)
+#int.list <- c(int25, int30, int35, int40, int45, int50)
+int.list <- list(base, int25, int30, int35, int40, int45, int50)
+# 
+scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')
 
@@
 
+```{r}
+# single.mean <- function(data, scen) {
+#   newvar.name <- paste0(scen, '.SF12')
+#   print(newvar.name)
+#   data <- data %>%
+#     select(time, weight, SF_12) %>%
+#     group_by(time) %>%
+#     summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+#   return(data)
+# }
+# 
+# int.list <- list(base, int25, int30)
+# 
+# scen.list <- c('base', 'int25', 'int30')
+# 
+# #mod.list <- lapply(int.list, single.mean, scen.list)
+# #mod.list <- mapply(single.mean, int.list, scen.list)
+# 
+# mod.list <- mapply(single.mean, int.list, scen.list, SIMPLIFY = FALSE)
+# 
+# combined <- mod.list %>%
+#   reduce(full_join, by='time')
+# 
+# # List of intervention columns
+# int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
+# 
+# # # Create the new dataframe with differences
+# # combined_diff <- combined %>%
+# #   mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}"))
+# 
+# # Create the new dataframe with differences
+# combined_diff <- combined %>%
+#   mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
+#   select(time, starts_with("diff")) %>%
+#   rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
+
+```
+
 ```{r SF12_whole_pop, echo=FALSE}
-SF12.change.full.sample.single <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
+SF12.change.full.sample.single <- function(df.list, scen.list) {
   single.mean <- function(data, scen) {
@@
 
-  base <- single.mean(base.dat, scen = 'base')
-  int1 <- single.mean(int.dat1, scen = 'int25')
-  int2 <- single.mean(int.dat2, scen = 'int50')
-  int3 <- single.mean(int.dat3, scen = 'int75')
-  int4 <- single.mean(int.dat4, scen = 'int100')
+  df.list <- mapply(single.mean, df.list, scen.list, SIMPLIFY = FALSE)
 
-  df.list <- list(base, int1, int2, int3, int4)
   combined <- df.list %>%
@@
 
-  combined$diff25 <- combined$int25.SF12 - combined$base.SF12
-  combined$diff50 <- combined$int50.SF12 - combined$base.SF12
-  combined$diff75 <- combined$int75.SF12 - combined$base.SF12
-  combined$diff100 <- combined$int100.SF12 - combined$base.SF12
+  # List of intervention columns
+  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
+
+  # Create the new dataframe with differences
+  combined <- combined %>%
+    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
+    select(time, starts_with("diff")) %>%
+    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
 
   combined <- combined %>%
-    select(time, contains('diff')) %>%
-    pivot_longer(cols = diff25:diff100,
+    pivot_longer(cols = starts_with('diff'),
                  names_to = 'scen',
@@
 
-  # TODO: Rename factor levels
-  # correct factor levels for plot
-  combined$scen <- factor(combined$scen,
-                          levels = c('diff100', 'diff75', 'diff50', 'diff25'))
+  #return(combined)
+
+  scen.list <- scen.list[-1]
+
+  #TODO: Rename factor levels
+  #correct factor levels for plot
+  # combined$scen <- factor(combined$scen,
+  #                         levels = scen.list)
+
+  #return(combined)
 
@@
 
-SF12.change.full.sample.batch <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
+SF12.change.full.sample.batch <- function(df.list, scen.list) {
   batch.mean <- function(data, scen) {
@@
       group_by(time, run_id) %>%
-      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
     return(data)
@@
 
-  base <- batch.mean(base.dat, scen = 'base')
-  int1 <- batch.mean(int.dat1, scen = 'int25')
-  int2 <- batch.mean(int.dat2, scen = 'int50')
-  int3 <- batch.mean(int.dat3, scen = 'int75')
-  int4 <- batch.mean(int.dat4, scen = 'int100')
+  # base <- batch.mean(base.dat, scen = 'base')
+  # int1 <- batch.mean(int.dat1, scen = 'int25')
+  # int2 <- batch.mean(int.dat2, scen = 'int50')
+  # int3 <- batch.mean(int.dat3, scen = 'int75')
+  # int4 <- batch.mean(int.dat4, scen = 'int100')
 
-  df.list <- list(base, int1, int2, int3, int4)
+  df.list <- mapply(single.mean, df.list, scen.list, SIMPLIFY = FALSE)
+
+  #df.list <- list(base, int1, int2, int3, int4)
   combined <- df.list %>%
@@
 
-  combined$diff25 <- combined$int25.SF12 - combined$base.SF12
-  combined$diff50 <- combined$int50.SF12 - combined$base.SF12
-  combined$diff75 <- combined$int75.SF12 - combined$base.SF12
-  combined$diff100 <- combined$int100.SF12 - combined$base.SF12
+  # combined$diff25 <- combined$int25.SF12 - combined$base.SF12
+  # combined$diff50 <- combined$int50.SF12 - combined$base.SF12
+  # combined$diff75 <- combined$int75.SF12 - combined$base.SF12
+  # combined$diff100 <- combined$int100.SF12 - combined$base.SF12
+
+  # List of intervention columns
+  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
+
+  # Create the new dataframe with differences
+  combined <- combined %>%
+    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
+    select(time, starts_with("diff")) %>%
+    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
 
   combined <- combined %>%
-    select(time, run_id, contains('diff')) %>%
-    pivot_longer(cols = diff25:diff100,
+    pivot_longer(cols = starts_with('diff'),
                  names_to = 'scen',
@@
 
+  # combined <- combined %>%
+  #   select(time, run_id, contains('diff')) %>%
+  #   pivot_longer(cols = diff25:diff100,
+  #                names_to = 'scen',
+  #                values_to = 'diff')
+
   # TODO: Rename factor levels
   # correct factor levels for plot
-  combined$scen <- factor(combined$scen,
-                          levels = c('diff100', 'diff75', 'diff50', 'diff25'))
+  # combined$scen <- factor(combined$scen,
+  #                         levels = c('diff100', 'diff75', 'diff50', 'diff25'))
 
@@
 ```{r SF12_families, echo=FALSE}
-SF12.change.families.single <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
+SF12.change.families.single <- function(df.list, scen.list) {
   single.mean <- function(data, scen) {
@@
 
-  combined$diff25 <- combined$int25.SF12 - combined$base.SF12
-  combined$diff50 <- combined$int50.SF12 - combined$base.SF12
-  combined$diff75 <- combined$int75.SF12 - combined$base.SF12
-  combined$diff100 <- combined$int100.SF12 - combined$base.SF12
+  # List of intervention columns
+  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
+
+  # Create the new dataframe with differences
+  combined <- combined %>%
+    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
+    select(time, starts_with("diff")) %>%
+    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
 
   combined <- combined %>%
-    select(time, contains('diff')) %>%
-    pivot_longer(cols = diff25:diff100,
+    pivot_longer(cols = starts_with('diff'),
                  names_to = 'scen',
                  values_to = 'diff')
-
-  # TODO: Rename factor levels
-  # correct factor levels for plot
-  combined$scen <- factor(combined$scen,
-                          levels = c('diff100', 'diff75', 'diff50', 'diff25'))
 
@@
 
-SF12.change.families.batch <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
+SF12.change.families.batch <- function(df.list, scen.list) {
   batch.mean <- function(data, scen) {
@@
 
-  base <- batch.mean(base.dat, scen = 'base')
-  int1 <- batch.mean(int.dat1, scen = 'int25')
-  int2 <- batch.mean(int.dat2, scen = 'int50')
-  int3 <- batch.mean(int.dat3, scen = 'int75')
-  int4 <- batch.mean(int.dat4, scen = 'int100')
+  df.list <- mapply(batch.mean, df.list, scen.list, SIMPLIFY = FALSE)
 
-  df.list <- list(base, int1, int2, int3, int4)
   combined <- df.list %>%
@@
 
-  combined$diff25 <- combined$int25.SF12 - combined$base.SF12
-  combined$diff50 <- combined$int50.SF12 - combined$base.SF12
-  combined$diff75 <- combined$int75.SF12 - combined$base.SF12
-  combined$diff100 <- combined$int100.SF12 - combined$base.SF12
+  # List of intervention columns
+  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
+
+  # Create the new dataframe with differences
+  combined <- combined %>%
+    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
+    select(time, starts_with("diff")) %>%
+    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
 
   combined <- combined %>%
-    select(time, run_id, contains('diff')) %>%
-    pivot_longer(cols = diff25:diff100,
+    pivot_longer(cols = starts_with('diff'),
                  names_to = 'scen',
                  values_to = 'diff')
-
-  # TODO: Rename factor levels
-  # correct factor levels for plot
-  combined$scen <- factor(combined$scen,
-                          levels = c('diff100', 'diff75', 'diff50', 'diff25'))
 
@@
 ```{r SF12_treated, echo=FALSE}
-SF12.change.treated.single <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
+SF12.change.treated.single <- function(df.list, scen.list) {
   single.mean <- function(data, scen, boosted) {
@@
   # get boosted pidps
-  boosted <- int.dat1 %>%
+  boosted <- df.list[[2]] %>%
     select(pidp, income_boosted) %>%
     filter(income_boosted == 'True')
+  rm(tmp)
 
-  base <- single.mean(base.dat, scen = 'base', boosted$pidp)
-  int1 <- single.mean(int.dat1, scen = 'int25', boosted$pidp)
-  int2 <- single.mean(int.dat2, scen = 'int50', boosted$pidp)
-  int3 <- single.mean(int.dat3, scen = 'int75', boosted$pidp)
-  int4 <- single.mean(int.dat4, scen = 'int100', boosted$pidp)
+  df.list <- mapply(single.mean, df.list, scen.list, boosted, SIMPLIFY = FALSE)
 
-  df.list <- list(base, int1, int2, int3, int4)
   combined <- df.list %>%
@@
 
-SF12.change.treated.batch <- function(base.dat, int.dat1, int.dat2, int.dat3, int.dat4) {
+SF12.change.treated.batch <- function(df.list, scen.list) {
   batch.mean <- function(data, scen, boosted) {
@@
   # get boosted pidps
-  boosted <- int.dat1 %>%
+  boosted <- df.list[[2]] %>%
     select(pidp, income_boosted) %>%
@@
 
-  base <- batch.mean(base.dat, scen = 'base', boosted$pidp)
-  int1 <- batch.mean(int.dat1, scen = 'int25', boosted$pidp)
-  int2 <- batch.mean(int.dat2, scen = 'int50', boosted$pidp)
-  int3 <- batch.mean(int.dat3, scen = 'int75', boosted$pidp)
-  int4 <- batch.mean(int.dat4, scen = 'int100', boosted$pidp)
+  df.list <- mapply(single.mean, df.list, scen.list, boosted, SIMPLIFY = FALSE)
 
-  df.list <- list(base, int1, int2, int3, int4)
   combined <- df.list %>%
@@
 if (batch) {
-  SF12.change.full.sample.batch(base, int25All, int50All, int75All, int100All)
+  SF12.change.full.sample.batch(int.list, scen.list)
 } else {
-  SF12.change.full.sample.single(base, int25All, int50All, int75All, int100All)
+  SF12.change.full.sample.single(int.list, scen.list)
 }
@@
 if (batch) {
-  SF12.change.families.batch(base, int25All, int50All, int75All, int100All)
+  SF12.change.families.batch(int.list, scen.list)
 } else {
-  SF12.change.families.single(base, int25All, int50All, int75All, int100All)
+  SF12.change.families.single(int.list, scen.list)
 }
@@
 if (batch) {
-  SF12.change.treated.batch(base, int25All, int50All, int75All, int100All)
+  SF12.change.treated.batch(int.list, scen.list)
 } else {
-  SF12.change.treated.single(base, int25All, int50All, int75All, int100All)
+  SF12.change.treated.single(int.list, scen.list)
 }
 ```
+
+```{r}
+
+```

### 2024-01-18 minos/outcomes/SCP_vis.Rmd
More additions to SCP plotting scripts, added some decile plots

@@
 int.list <- list(base, int25, int30, int35, int40, int45, int50)
-# 
 scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')
@@
 ```{r}
-# single.mean <- function(data, scen) {
-#   newvar.name <- paste0(scen, '.SF12')
-#   print(newvar.name)
-#   data <- data %>%
-#     select(time, weight, SF_12) %>%
-#     group_by(time) %>%
-#     summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-#   return(data)
-# }
-# 
-# int.list <- list(base, int25, int30)
-# 
-# scen.list <- c('base', 'int25', 'int30')
-# 
-# #mod.list <- lapply(int.list, single.mean, scen.list)
-# #mod.list <- mapply(single.mean, int.list, scen.list)
-# 
-# mod.list <- mapply(single.mean, int.list, scen.list, SIMPLIFY = FALSE)
-# 
-# combined <- mod.list %>%
-#   reduce(full_join, by='time')
-# 
-# # List of intervention columns
-# int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
-# 
-# # # Create the new dataframe with differences
-# # combined_diff <- combined %>%
-# #   mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}"))
-# 
-# # Create the new dataframe with differences
-# combined_diff <- combined %>%
-#   mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
-#   select(time, starts_with("diff")) %>%
-#   rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
 
@@
 
+```{r SF12_deciles, echo=FALSE}
+SF12.by.simd.deciles <- function(df.list, scen.list, start.year = 2020, batch=FALSE) {
+  single.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, simd_decile, SF_12) %>%
+      filter(time >= start.year) %>%
+      group_by(time, simd_decile) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+  batch.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, simd_decile, run_id, SF_12) %>%
+      filter(time >= start.year) %>%
+      group_by(time, run_id) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  if (batch) {
+    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time', 'simd_decile', 'run_id'))
+  } else {
+    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time', 'simd_decile'))
+  }
+
+  combined$simd_decile <- as.factor(combined$simd_decile)
+
+  int.labels <- scen.list[-1]
+
+  for (int in int.labels) {
+    int.name <- paste0(int, '.SF12')
+    if (batch) {
+      p1 <- ggplot(combined, aes(x = time, group = simd_decile, colour = simd_decile)) +
+        geom_smooth(aes(y = base.SF12)) +
+        geom_smooth(aes(y = .data[[int.name]]), linetype='dashed') +
+        labs(title = 'SF12 MCS Deciles', subtitle = paste0('Baseline vs ', int)) +
+        xlab('Year') +
+        ylab('Difference')
+    } else {
+      p1 <- ggplot(combined, aes(x = time, group = simd_decile, colour = simd_decile)) +
+        geom_line(aes(y = base.SF12)) +
+        geom_line(aes(y = .data[[int.name]]), linetype='dashed') +
+        labs(title = 'SF12 MCS Deciles', subtitle = int) +
+        xlab('Year') +
+        ylab('Difference')
+    }
+    print(p1)
+  }
+}
+```
+
+```{r SF_change_deciles, echo=FALSE}
+SF12.change.by.deciles <- function(df.list, scen.list, start.year = 2020, batch = FALSE) {
+  single.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, simd_decile, SF_12) %>%
+      filter(time >= start.year) %>%
+      group_by(time, simd_decile) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+  batch.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, simd_decile, run_id, SF_12) %>%
+      filter(time >= start.year) %>%
+      group_by(time, run_id) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  if (batch) {
+    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time', 'simd_decile', 'run_id'))
+  } else {
+    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time', 'simd_decile'))
+  }
+
+  combined$simd_decile <- as.factor(combined$simd_decile)
+
+  # List of intervention columns
+  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
+
+  # Create the new dataframe with differences
+  combined <- combined %>%
+    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
+    select(time, simd_decile, starts_with("diff")) %>%
+    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
+
+  combined <- combined %>%
+    pivot_longer(cols = starts_with('diff'),
+                 names_to = 'scen',
+                 values_to = 'diff')
+
+  options(repr.plot.width =9, repr.plot.height =20)
+
+  p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    facet_wrap(. ~ scen, ncol=1) +
+    labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
+    xlab('Year') +
+    ylab('Difference')
+
+  ggsave(filename = 'test_plot.png',
+         plot = p1,
+         path = here::here('plots', 'SCOTGOVWORK'),
+         width = 9,
+         height = 20)
+
+  print(p1)
+}
+```
+
 # PLOTS
@@
 
+## MCS - DECILES
+
 ```{r}
+SF12.by.simd.deciles(int.list, scen.list)
+```
 
+```{r}
+SF12.by.simd.deciles(int.list, scen.list, start.year = 2024, batch = FALSE)
 ```
+
+## MCS - CHANGE BY DECILES
+
+```{r}
+SF12.change.by.deciles(int.list, scen.list)
+```
+
+## TESTING
+
+```{r}
+```

### 2024-01-18 minos/outcomes/SCP_vis.Rmd
Added intervention diagnostics plots (cost etc.) to SCP_vis.Rmd

@@
 
+# DIAGNOSTICS
+
+```{r}
+sample_information_single <- function(int.dat, int.name, target.year) {
+  hh_boosted <- int.dat %>%
+    select(hidp, time, income_boosted, boost_amount, nkids) %>%
+    filter(income_boosted == 'True') %>%
+    group_by(time) %>%
+    summarise(n_boosted = length(unique(hidp)),
+              total_boost = sum(boost_amount),
+              kids_boosted = sum(nkids))
+
+  p1 <- ggplot(hh_boosted, aes(x = time, y = n_boosted)) +
+    geom_line() +
+    geom_vline(xintercept = target.year, linetype = 'dashed') +
+    labs(title = 'Number of households receiving intervention', subtitle = int.name) +
+    xlab('Year') +
+    ylab('Number Boosted')
+
+  p2 <- ggplot(hh_boosted, aes(x = time, y = kids_boosted)) +
+    geom_line() +
+    geom_vline(xintercept = target.year, linetype = 'dashed') +
+    labs(title = 'Number of children in households receiving intervention', subtitle = int.name) +
+    xlab('Year') +
+    ylab('Number Children')
+
+  p3 <- ggplot(hh_boosted, aes(x = time, y = total_boost)) +
+    geom_line() +
+    geom_vline(xintercept = target.year, linetype = 'dashed') +
+    labs(title = 'Total boost amount', subtitle = int.name) +
+    xlab('Year') +
+    ylab('Boost Amount')
+
+  mean.boost <- int.dat %>%
+    select(time, income_boosted, boost_amount) %>%
+    group_by(time, income_boosted) %>%
+    summarise(mean_boost = mean(boost_amount)) %>%
+    filter(income_boosted == 'True')
+
+  p4 <- ggplot(mean.boost, aes(x = time, y = mean_boost)) +
+    geom_line() +
+    geom_vline(xintercept = target.year, linetype = 'dashed') +
+    labs(title = 'Mean boost amount', subtitle = int.name) +
+    xlab('Year') +
+    ylab('Boost Amount')
+
+  print(p1)
+  print(p2)
+  print(p3)
+  print(p4)
+}
+
+sample_information_batch <- function(int.dat, int.name, target.year) {
+  hh_boosted <- int.dat %>%
+    select(hidp, time, run_id, income_boosted, boost_amount, nkids) %>%
+    filter(income_boosted == 'True') %>%
+    group_by(time, run_id) %>%
+    summarise(n_boosted = length(unique(hidp)),
+              total_boost = sum(boost_amount),
+              kids_boosted = sum(nkids))
+
+  p1 <- ggplot(hh_boosted, aes(x = time, y = n_boosted)) +
+    geom_smooth() +
+    geom_vline(xintercept = target.year, linetype = 'dashed') +
+    labs(title = 'Number of households receiving intervention', subtitle = int.name) +
+    xlab('Year') +
+    ylab('Number Boosted')
+
+  p2 <- ggplot(hh_boosted, aes(x = time, y = kids_boosted)) +
+    geom_smooth() +
+    geom_vline(xintercept = target.year, linetype = 'dashed') +
+    labs(title = 'Number of children in households receiving intervention', subtitle = int.name) +
+    xlab('Year') +
+    ylab('Number Children')
+
+  p3 <- ggplot(hh_boosted, aes(x = time, y = total_boost)) +
+    geom_smooth() +
+    geom_vline(xintercept = target.year, linetype = 'dashed') +
+    labs(title = 'Total boost amount', subtitle = int.name) +
+    xlab('Year') +
+    ylab('Boost Amount')
+
+  mean.boost <- int.dat %>%
+    select(time, income_boosted, boost_amount) %>%
+    group_by(time, run_id, income_boosted) %>%
+    summarise(mean_boost = mean(boost_amount)) %>%
+    filter(income_boosted == 'True')
+
+  p4 <- ggplot(mean.boost, aes(x = time, y = mean_boost)) +
+    geom_smooth() +
+    geom_vline(xintercept = target.year, linetype = 'dashed') +
+    labs(title = 'Mean boost amount', subtitle = int.name) +
+    xlab('Year') +
+    ylab('Boost Amount')
+
+  print(p1)
+  print(p2)
+  print(p3)
+  print(p4)
+}
+```
+
+## 25
+
+```{r}
+if (batch) {
+  sample_information_batch(int25, int.name = 'int25', target.year = 2030)
+} else {
+  sample_information_single(int25, int.name = 'int25', target.year = 2030)
+}
+```
+
+## 35
+
+```{r}
+if (batch) {
+  sample_information_batch(int35, int.name = 'int35', target.year = 2030)
+} else {
+  sample_information_single(int35, int.name = 'int35', target.year = 2030)
+}
+```
+
+## 45
+
+```{r}
+if (batch) {
+  sample_information_batch(int45, int.name = 'int45', target.year = 2030)
+} else {
+  sample_information_single(int45, int.name = 'int45', target.year = 2030)
+}
+```
+
 ## TESTING

### 2024-01-18 minos/outcomes/SCP_vis.Rmd
Adding some WIP plots for poverty statistics

@@
 source(here::here('minos', 'utils_datain.R'))
-#source(here::here('minos', 'utils_validation_vis.R'))
-#source(here::here('minos', 'validation', 'utils.r'))
-```
-
-```{r}
-# out.path <- here::here('output', 'default_config')
-# 
-# # define subset of variables to reduce size of batch output
-# var.list <- c('pidp', 'hidp', 'time', 'weight', 
-#               'age', 'ethnicity', 'education_state', 'region', 'nkids',
-#               'hh_income',
-#               'housing_quality', 'neighbourhood_safety', 'loneliness', 'ncigs', 'nutrition_quality', 'financial_situation', 'urban', 'housing_tenure',
-#               'SF_12', 'matdep_child')
-# 
-# base <- read_output(out.path, 
-#                     scenario = 'baseline', 
-#                     var.list = var.list,
-#                     verbose = TRUE)
-# int25All <- read_output(out.path, 
-#                         scenario = '25All', 
-#                         var.list = var.list,
-#                         verbose = TRUE)
-# int50All <- read_output(out.path, 
-#                         scenario = '50All', 
-#                         var.list = var.list,
-#                         verbose = TRUE)
-# int75All <- read_output(out.path, 
-#                         scenario = '75All', 
-#                         var.list = var.list,
-#                         verbose = TRUE)
-# int100All <- read_output(out.path, 
-#                         scenario = '100All', 
-#                         var.list = var.list,
-#                         verbose = TRUE)
-# 
-# int.list <- c(int25All, int50All, int75All, int100All)
-# 
-# # set up a boolean tag for batch or not
-# # this is necessary because batch runs need slightly different processing before visualisation
-# if ('run_id' %in% names(base)) {
-#   batch <- TRUE
-# } else {
-#   batch <- FALSE
-# }
-# 
-# # Save path and save flag
-# save.path <- here::here('plots', 'SCOTGOV', 'CPR')
-# create.if.not.exists(save.path)
-# shall.we.save <- FALSE
-# plot.width <- 10
-# plot.height <- 5
 ```
@@
 
+# Poverty Statistics
+
+See how interventions affect child poverty.
+
+## Relative Poverty
+
+```{r}
+# First need the relative poverty thresholds from baseline
+threshold <- base %>%
+  select(time, weight, hh_income) %>%
+  group_by(time) %>%
+  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
+
+ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
+  geom_col() +
+  labs(title = 'Relative poverty threshold over time') +
+  xlab('Year') +
+  ylab('Threshold')
+```
+
+```{r}
+int25.test <- merge(int25, threshold, by = 'time')
+# Now calculate number of households and number of children below threshold
+hh_boosted <- int25.test %>%
+  select(hidp, time, hh_income, income_boosted, boost_amount, nkids, poverty_threshold) %>%
+  filter(income_boosted == 'True') %>%
+  filter(hh_income < poverty_threshold) %>%
+  group_by(time) %>%
+  summarise(n = n(),
+            n_boosted = length(unique(hidp)),
+            total_boost = sum(boost_amount),
+            kids_boosted = sum(nkids)) %>%
+  mutate(prop_boosted = n_boosted / n,
+         prop_kids_boosted)
+
+p1 <- ggplot(hh_boosted, aes(x = time, y = n_boosted)) +
+  geom_line() +
+  labs(title = 'Number of households receiving intervention', subtitle = int.name) +
+  xlab('Year') +
+  ylab('Number Boosted')
+print(p1)
+
+p2 <- ggplot(hh_boosted, aes(x = time, y = kids_boosted)) +
+  geom_line() +
+  labs(title = 'Number of children in households receiving intervention', subtitle = int.name) +
+  xlab('Year') +
+  ylab('Number Children')
+print(p2)
+```
+
 # DIAGNOSTICS
@@
 ```{r}
-sample_information_single <- function(int.dat, int.name, target.year) {
+intervention_information_single <- function(int.dat, int.name, target.year) {
   hh_boosted <- int.dat %>%
@@
 
-sample_information_batch <- function(int.dat, int.name, target.year) {
+intervention_information_batch <- function(int.dat, int.name, target.year) {
   hh_boosted <- int.dat %>%
@@
 if (batch) {
-  sample_information_batch(int25, int.name = 'int25', target.year = 2030)
+  intervention_information_batch(int25, int.name = 'int25', target.year = 2030)
 } else {
-  sample_information_single(int25, int.name = 'int25', target.year = 2030)
+  intervention_information_single(int25, int.name = 'int25', target.year = 2030)
+}
+```
+
+## 30
+
+```{r}
+if (batch) {
+  intervention_information_batch(int30, int.name = 'int30', target.year = 2030)
+} else {
+  intervention_information_single(int30, int.name = 'int30', target.year = 2030)
 }
@@
 if (batch) {
-  sample_information_batch(int35, int.name = 'int35', target.year = 2030)
+  intervention_information_batch(int35, int.name = 'int35', target.year = 2030)
 } else {
-  sample_information_single(int35, int.name = 'int35', target.year = 2030)
+  intervention_information_single(int35, int.name = 'int35', target.year = 2030)
+}
+```
+
+## 40
+
+```{r}
+if (batch) {
+  intervention_information_batch(int40, int.name = 'int40', target.year = 2030)
+} else {
+  intervention_information_single(int40, int.name = 'int40', target.year = 2030)
 }
@@
 if (batch) {
-  sample_information_batch(int45, int.name = 'int45', target.year = 2030)
+  intervention_information_batch(int45, int.name = 'int45', target.year = 2030)
 } else {
-  sample_information_single(int45, int.name = 'int45', target.year = 2030)
+  intervention_information_single(int45, int.name = 'int45', target.year = 2030)
 }
@@
 
-## TESTING
+## 50
+
+```{r}
+if (batch) {
+  intervention_information_batch(int50, int.name = 'int50', target.year = 2030)
+} else {
+  intervention_information_single(int50, int.name = 'int50', target.year = 2030)
+}
+```
+
+# TESTING
 

### 2024-01-19 docsrc/documentation/notebooks/housing.Rmd

--- 2022-12-19 docsrc/documentation/notebooks/housing.Rmd
@@
 bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
+  - "docsrc/refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
   #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
@@
 
-# Housing Quality
+```{r setup, include=FALSE}
+knitr::opts_knit$set(root.dir= "../minos")
+```
+
+## Housing Quality
 
@@
 
-## Data
+```{r housing_barchart, echo=FALSE}
+discrete_barplot("data/transitions/housing_quality/clm/housing_quality_2018_2019.rds", 'next_housing_quality')
+```
+
+### Data
 
@@
 options(width=120)
-clm_output("../../../data/transitions/test/housing_clm_2018_2019.rds")
+clm_barplot("data/transitions/housing_quality/clm/housing_quality_2018_2019.rds", "next_housing_quality") 
+clm_output("data/transitions/housing_quality/clm/housing_quality_2018_2019.rds")
 ```
 
-## References
+### References

### 2024-01-19 minos/outcomes/equivalent_income_out.Rmd

--- 2023-08-31 minos/outcomes/equivalent_income_out.Rmd
@@
 title: "Equivalent Income Outcome Visualisation"
-output:
-  html_document:
-    toc: true
-    toc_float: true
-    collapsed: false
-    number_sections: true
-    df_print: paged
-    code_folding: hide
+output: html_notebook
 ---
@@
 require(ggplot2)
-require(here)
-require(dplyr)
-require(tidyr)
-require(purrr)
 
-#workingDir <- "/home/luke/Documents/WORK/MINOS/"
-workingDir <- normalizePath('../')
+workingDir <- "/home/luke/Documents/WORK/MINOS/"
 knitr::opts_knit$set(root.dir = workingDir)
-knitr::opts_chunk$set(
-  warning = FALSE,
-  message = FALSE
-)
 rm(workingDir)
@@
 ```{r, include=FALSE}
-source(here::here('minos', 'utils_datain.R'))
-source(here::here('minos', 'utils_validation_vis.R'))
-source(here::here('minos', 'validation', 'utils.r'))
+source('Minos/minos/validation/utils.r')
 ```
@@
 # set output path to SIPHER 7 experiment out
-out.path <- here::here('output', 'SIPHER7/')
+out.path <- 'Minos/output/SIPHER7/'
 # read all files into dataframe (util function handles runtime subdirectory etc.)
-base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-allchild.dat <- read_singular_local_out(out.path, 'hhIncomeChildUplift', drop.dead = TRUE)
-pov.dat <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift', drop.dead = TRUE)
-wage.dat <- read_singular_local_out(out.path, 'livingWageIntervention', drop.dead = TRUE)
-energy.dat <- read_singular_local_out(out.path, 'energyDownlift', drop.dead = TRUE)
-```
-
-## Remove 2020 Data Point
-
-```{r}
-base.dat <- filter(base.dat, time > 2020)
-allchild.dat <- filter(allchild.dat, time > 2020)
-pov.dat <- filter(pov.dat, time > 2020)
-wage.dat <- filter(wage.dat, time > 2020)
-energy.dat <- filter(energy.dat, time > 2020)
+base.dat <- read_output(out.path, 'baseline')
+allchild.dat <- read_output(out.path, 'hhIncomeChildUplift')
+pov.dat <- read_output(out.path, 'hhIncomePovertyLineChildUplift')
+wage.dat <- read_output(out.path, 'livingWageIntervention')
+energy.dat <- read_output(out.path, 'energyDownlift')
 ```
@@
 base.subset <- base.dat %>%
-  select(pidp, time, equivalent_income, weight) %>%
+  select(pidp, time, equivalent_income) %>%
   group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+  summarise(equivalent_income = mean(equivalent_income))
 
@@
 
-ggplot(data = base.subset, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
+ggplot(data = base.subset, aes(x = time, y = equivalent_income)) +
   geom_line()
@@
   base.subset <- base %>%
-    select(pidp, time, equivalent_income, alive, weight) %>%
+    select(pidp, time, equivalent_income, alive) %>%
     filter(alive != 'dead') %>%
     group_by(time) %>%
-    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+    summarise(equivalent_income = mean(equivalent_income))
   int.subset <- int %>%
-    select(pidp, time, equivalent_income, alive, weight) %>%
+    select(pidp, time, equivalent_income, alive) %>%
     filter(alive != 'dead') %>%
     group_by(time) %>%
-    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+    summarise(equivalent_income = mean(equivalent_income))
 
@@
 ```{r}
-equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild')
-equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild')
-equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage')
-equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift')
+equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
 ```
@@
 base.subset <- base.dat %>%
-  select(pidp, time, equivalent_income, alive, weight) %>%
+  select(pidp, time, equivalent_income, alive) %>%
   filter(alive != 'dead') %>%
   group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+  summarise(equivalent_income = mean(equivalent_income))
 base.subset$scenario <- 'Baseline'
@@
 allchild.subset <- allchild.dat %>%
-  select(pidp, time, equivalent_income, alive, weight) %>%
+  select(pidp, time, equivalent_income, alive) %>%
   filter(alive != 'dead') %>%
   group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+  summarise(equivalent_income = mean(equivalent_income))
 allchild.subset$scenario <- 'AllChild'
@@
 pov.subset <- pov.dat %>%
-  select(pidp, time, equivalent_income, alive, weight) %>%
+  select(pidp, time, equivalent_income, alive) %>%
   filter(alive != 'dead') %>%
   group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+  summarise(equivalent_income = mean(equivalent_income))
 pov.subset$scenario <- 'PovertyChild'
@@
 wage.subset <- wage.dat %>%
-  select(pidp, time, equivalent_income, alive, weight) %>%
+  select(pidp, time, equivalent_income, alive) %>%
   filter(alive != 'dead') %>%
   group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+  summarise(equivalent_income = mean(equivalent_income))
 wage.subset$scenario <- 'LivingWage'
@@
 energy.subset <- energy.dat %>%
-  select(pidp, time, equivalent_income, alive, weight) %>%
+  select(pidp, time, equivalent_income, alive) %>%
   filter(alive != 'dead') %>%
   group_by(time) %>%
-  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
+  summarise(equivalent_income = mean(equivalent_income))
 energy.subset$scenario <- 'EnergyDownlift'
@@
 equivalent_income_comparison_treated <- function(base, int, int.name, save=FALSE, save.path=NULL) {
-  base.sub <- base %>%
+  base.sub <- base.dat %>%
     select(pidp, time, equivalent_income, alive) %>%
@@
   int.sub <- int %>%
-    select(pidp, time, equivalent_income, income_boosted, alive, weight) %>%
+    select(pidp, time, equivalent_income, income_boosted, alive) %>%
     filter(alive != 'dead') %>%
     select(-alive) %>%
-    set_names(c('pidp', 'time', int.name, 'income_boosted', 'weight'))
+    set_names(c('pidp', 'time', int.name, 'income_boosted'))
 
@@
     filter(pidp %in% boosted.pidps$pidp) %>%
-    filter(income_boosted == 'True' | time == 2020) %>%
+    filter(income_boosted == 'True' | time == 2021) %>%
     select(-income_boosted) %>%
@@
     group_by(time, scenario) %>%
-    summarise(equivalent_income = weighted.mean(equivalent_income, w=weight))
+    summarise(equivalent_income = mean(equivalent_income))
 
@@
 ```{r}
-equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild')
-equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild')
-equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage')
-equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift')
+equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
+equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
 ```
@@
   filter(pidp %in% boosted.pidps$pidp) %>%
-  filter(income_boosted == 'True' | time == 2020) %>%
+  filter(income_boosted == 'True' | time == 2021) %>%
   mutate(adjusted_EI = allchild - boost_amount) %>%
@@
                values_to = 'equivalent_income')
-```
 
-```{r}
 ggplot(data = allchild.boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
   geom_line()
+
 ```
@@
 ALSO: Difference plots.
-
-# DETAILED ANALYSIS
-
-## Living Wage
-
-For this, we're going to look at the difference in equivalent income and try to explain it by looking at the pathway variables.
-What we want to see is that as income is uplifted, the various pathways show a positive shift and that in part explains the difference in equivalent income.
-
-First visualise both income and equivalent income on one graph.
-
-### Income and Equivalent Income
-
-```{r}
-base.inc <- base.dat %>%
-  select(pidp, time, hh_income, equivalent_income, weight) %>%
-  group_by(time) %>%
-  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
-            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
-  mutate(source = 'Baseline')
-
-int.inc <- wage.dat %>%
-  select(pidp, time, hh_income, equivalent_income, weight) %>%
-  group_by(time) %>%
-  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
-            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
-  mutate(source = 'Living_Wage')
-
-combined <- rbind(base.inc, int.inc)
-combined <- combined %>%
-  pivot_longer(cols=hh_income:equivalent_income,
-               names_to = 'income_type',
-               values_to = 'value')
-
-ggplot(combined, aes(x = time, y = value, group = source, color = source)) +
-  geom_line() +
-  facet_wrap( ~ income_type, nrow=2, scales='free')
-```
-
-### CHANGE IN INCOME / EQUIVALENT INCOME
-
-```{r}
-base.inc <- base.dat %>%
-  select(pidp, time, hh_income, equivalent_income, weight) %>%
-  group_by(time) %>%
-  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
-            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
-  mutate(source = 'Baseline')
-
-int.inc <- energy.dat %>%
-  select(pidp, time, hh_income, equivalent_income, weight) %>%
-  group_by(time) %>%
-  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
-            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
-  mutate(source = 'EnergyCrisis')
-
-combined <- rbind(base.inc, int.inc)
-combined <- combined %>%
-  pivot_longer(cols=hh_income:equivalent_income,
-               names_to = 'income_type',
-               values_to = 'value')
-
-ggplot(combined, aes(x = time, y = value, group = source, color = source)) +
-  geom_line() +
-  facet_wrap( ~ income_type, nrow=2, scales='free')
-```
-
-How about on the same plot to make it more clear?
-
-```{r}
-income_equivinc_change <- function(base.dat, int.dat) {
-  base.inc <- base.dat %>%
-    select(pidp, time, hh_income, equivalent_income, weight) %>%
-    group_by(time) %>%
-    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
-              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
-
-  int.inc <- int.dat %>%
-    select(pidp, time, hh_income, equivalent_income, weight) %>%
-    group_by(time) %>%
-    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
-              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
-
-  combined <- merge(base.inc, int.inc, by = c('time'))
-
-  combined$diff_income <- combined$energy_income - combined$base_income
-  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income
-
-  combined <- combined %>%
-    pivot_longer(cols = diff_income:diff_equiv_income,
-                 names_prefix = 'diff_',
-                 names_to = 'variable',
-                 values_to = 'diff')
-
-  ggplot(combined, aes(x = time, y = diff, group = variable, color = variable)) +
-    geom_line() +
-    geom_hline(yintercept = 0, linetype = 'dashed')
-}
-
-income_equivinc_change(base.dat, energy.dat)
-income_equivinc_change(base.dat, wage.dat)
-```
-
-## Energy Crisis
-
-```{r}
-S7_ordinal_pathway_vis <- function(base.dat, int.dat, int.name, var) {
-  base.hous <- base.dat %>%
-    select(pidp, time, all_of(var)) %>%
-    group_by(time, .data[[var]]) %>%
-    count() %>%
-    group_by(time) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prop = n / total) %>%
-    select(-n, -total) %>%
-    mutate(source = 'Baseline')
-
-  inc.hous <- int.dat %>%
-    select(pidp, time, all_of(var)) %>%
-    group_by(time, .data[[var]]) %>%
-    count() %>%
-    group_by(time) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prop = n / total) %>%
-    select(-n, -total) %>%
-    mutate(source = int.name)
-
-  combined <- rbind(base.hous, inc.hous)
-  combined[[var]] <- as.factor(combined[[var]])
-
-  p1 <- ggplot(combined, aes(x = time, y = prop, group = interaction(.data[[var]], source), color = .data[[var]], linetype = source)) +
-    geom_line() +
-    geom_point()
-
-  print(p1)
-
-  base.hous2 <- base.dat %>%
-    select(pidp, time, all_of(var)) %>%
-    group_by(time, .data[[var]]) %>%
-    count() %>%
-    group_by(time) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prop = (n / total) * 100) %>%
-    select(-n, -total) %>%
-    rename(Baseline = prop)
-
-  int.hous2 <- int.dat %>%
-    select(pidp, time, all_of(var)) %>%
-    group_by(time, .data[[var]]) %>%
-    count() %>%
-    group_by(time) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prop = (n / total) * 100) %>%
-    select(-n, -total) %>%
-    rename(int = prop)
-
-  combined2 <- merge(base.hous2, int.hous2, by = c('time', var))
-
-  combined2[[var]] <- as.factor(combined2[[var]])
-
-  combined2$diff <- combined2$int - combined2$Baseline
-
-  p2 <- ggplot(combined2, aes(x = time, y = diff, group = .data[[var]], color = .data[[var]])) +
-    geom_line() +
-    geom_point()
-
-  print(p2)
-}
-```
-
-### Housing Quality
-
-```{r}
-S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_housing_quality')
-```
-
-### Neighbourhood Safety
-
-```{r}
-S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_neighbourhood_safety')
-```
-
-### Mental Wellbeing
-
-```{r}
-S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_mental_health')
-```
-
-### Physical Health
-
-```{r}
-S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_physical_health')
-```
-
-### Loneliness
-
-```{r}
-S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'loneliness')
-```
-
-### Labour State
-
-```{r}
-S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_labour_state')
-```
-
-```{r}
-boosted.pidps <- energy.dat %>%
-  filter(income_boosted == 'True') %>%
-  select(pidp)
-
-base.hous <- base.dat %>%
-  select(pidp, time, S7_housing_quality) %>%
-  filter(pidp %in% boosted.pidps$pidp) %>%
-  group_by(time, S7_housing_quality) %>%
-  count() %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prop = (n / total) * 100) %>%
-  select(-n, -total) %>%
-  rename(Baseline = prop)
-
-int.hous <- energy.dat %>%
-  select(pidp, time, S7_housing_quality, income_boosted) %>%
-  filter(pidp %in% boosted.pidps$pidp) %>%
-  group_by(time, S7_housing_quality) %>%
-  count() %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prop = (n / total) * 100) %>%
-  select(-n, -total) %>%
-  rename(EnergyCrisis = prop)
-
-combined <- merge(base.hous, int.hous, by = c('time', 'S7_housing_quality'))
-
-combined$diff <- combined$EnergyCrisis - combined$Baseline
-
-ggplot(combined, aes(x = time, y = diff, group = S7_housing_quality, color = S7_housing_quality)) +
-  geom_line() +
-  geom_point()
-```
-
-```{r}
-## just look at means in case the means are causing some problems
-base.dat.2 <- base.dat
-base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'No to all'] <- 1
-base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to some'] <- 2
-base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to all'] <- 3
-wage.dat.2 <- energy.dat
-wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'No to all'] <- 1
-wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to some'] <- 2
-wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to all'] <- 3
-
-base.hous.mean <- base.dat.2 %>%
-  select(pidp, time, S7_housing_quality2, weight) %>%
-  group_by(time) %>%
-  summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
-  mutate(source = 'Baseline')
-wage.hous.mean <- wage.dat.2 %>%
-  select(pidp, time, S7_housing_quality2, weight) %>%
-  group_by(time) %>%
-  summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
-  mutate(source = 'EnergyCrisis')
-
-combined <- rbind(base.hous.mean, wage.hous.mean)
-
-ggplot(combined, aes(x = time, y = mean_housing, group = source, color = source)) +
-  geom_line() +
-  geom_point()
-```
-
-```{r}
-
-# df <- combine_and_pivot_long(base.dat, 'Baseline', wage.dat, 'LivingWage', c('S7_housing_quality', 'income_boosted'))
-# 
-# outcomes.prep <- function(base.dat, int.dat, int.name, var) {
-#   boosted.pidps <- int.dat %>%
-#     filter(income_boosted == 'True') %>%
-#     select(pidp, time)
-#   
-#   df1 <- base.dat %>%
-#     select(pidp, time, all_of(var), weight) %>%
-#     
-# }
-# 
-# 
-# 
-# 
-# combine_and_pivot_long <- function(df1, df1.name, df2, df2.name, var) {
-#   # get only the columns we want a rename
-#   df1 <- df1 %>%
-#     select('pidp', 'time', all_of(var)) %>%
-#     set_names(c('pidp', 'time', df1.name))
-#   df2 <- df2 %>%
-#     select('pidp', 'time', all_of(var)) %>%
-#     set_names(c('pidp', 'time', df2.name))
-#   # merge on pidp and time
-#   merged <- merge(df1, df2, by = c('pidp', 'time'), all=TRUE)
-#   pivoted <- pivot_longer(data = merged,
-#                           cols = df1.name:df2.name,
-#                           names_to = 'scenario',
-#                           values_to = var)
-#   return(pivoted)
-# }
-
-```

### 2024-01-19 minos/validation/cross_validation_S7.Rmd

@@
 multi_year_boxplots(raw, cv, 'equivalent_income')
-snapshot_OP_plots(raw, cv, 'equivalent_income', target.years = c(2014, 2017, 2020))
+snapshot_OP_plots(raw, cv, 'equivalent_income', target.years = c(2017, 2020))
 q_q_comparison(raw, cv, 'equivalent_income')
@@
 ```{r}
-ei.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
-                                 predicted = cv, 
-                                 var = 'equivalent_income', 
-                                 target.year = 2014)
-print(ei.14)
+# ei.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
+#                                  predicted = cv, 
+#                                  var = 'equivalent_income', 
+#                                  target.year = 2014)
+#print(ei.14)
 ```

### 2024-01-19 minos/validation/handovers.Rmd

--- 2023-12-15 minos/validation/handovers.Rmd
@@
 ---
-params:
-    file_path: '' # default arguments. specify others in command line.
-    intervention: ''
-title: "`r paste(params$file_path, ' ', params$intervention, ' Handover Plots')`"
+title: "MINOS Handover Plots"
 output:
-  #output_file: "`r paste('minos/validation/', params$file_path, '_', params$intervention, '_handovers.html') `"
   html_document:
@@
 
-#out.path <- here::here('output', 'default_config/')
-#base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-
-out.path <- here::here('output', file_path)
-base.dat <- read_singular_local_out(out.path, intervention, drop.dead = TRUE)
+out.path <- here::here('output', 'default_config/')
+base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
 ```
@@
 
+## Hourly Wage
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'hourly_wage')
+handover_lineplots(raw.dat, base.dat, 'hourly_wage')
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, hourly_wage)
+base.s <- base.dat %>%
+  select(pidp, age, time, hourly_wage)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+# now a version limited to 0-100
+spag <- spag %>%
+  filter(hourly_wage <= 300)
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+```{r}
+# some basic statistics about hourly_wage variable
+print("Some basic statistics on hourly_wage. These are all for 2020.")
+raw.2020 <- raw.dat %>% filter(time == 2020)
+print('All living people in 2020')
+print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
+# number individuals with an hourly_wage > 0
+print('People not in work')
+print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
+
+# Number in work
+print('People in work')
+print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
+
+# Extreme hourly_wage values
+print('Extreme hourly wage values: HIGH')
+print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
+print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
+print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
+print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
+print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
+print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
+
+raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
+print('Extreme hourly wage values: LOW (non-zero)')
+print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
+print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
+print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
+print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
+```
+
+## S7 Labour State
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
+
+lab.state <- prepped.list$var
+lab.state.norm <- prepped.list$norm
+
+# Now plot
+ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'S7_labour_state.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, lab.state, lab.state.norm)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'S7_labour_state')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'S7_labour_state',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
+## Child Ages
+
+```{r}
+raw.child.ages <- raw.dat %>%
+  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
+  filter(time > 2013) %>%
+  group_by(time, hidp) %>%
+  summarise(child_ages = find_mode(child_ages))
+
+r.s<- strsplit(raw.child.ages$child_ages, "_")
+
+raw.child.ages.expanded <- data.frame(time = rep(raw.child.ages$time, sapply(r.s, length)), expanded_child_ages = unlist(r.s))
+raw.child.ages.expanded <- raw.child.ages.expanded %>%
+  group_by(time, expanded_child_ages) %>%
+  summarise(age_counts = n()) %>%
+  mutate(source = 'final_US') %>%
+  filter(expanded_child_ages <= 16)
+
+base.child.ages <- base.dat %>%
+  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
+  filter(time > 2009) %>%
+  group_by(time, hidp) %>%
+  summarise(child_ages = find_mode(child_ages))
+
+b.s<- strsplit(base.child.ages$child_ages, "_")
+
+base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(b.s, length)), expanded_child_ages = unlist(b.s))
+base.child.ages.expanded <- base.child.ages.expanded %>%
+  group_by(time, expanded_child_ages) %>%
+  summarise(age_counts = n()) %>%
+  mutate(source = 'baseline')
+
+combined <- rbind(raw.child.ages.expanded, base.child.ages.expanded)
+
+ggplot(data = combined, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
+  geom_line() +
+  geom_vline(xintercept = start.year) +
+  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
+  scale_colour_viridis_d() +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = combined, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
+  geom_line() +
+  geom_vline(xintercept = start.year) +
+  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
+  scale_colour_viridis_d() +
+  xlab('Year') +
+  ylab('Count')
+
+base.child.ages.nkids <- base.dat %>%
+  group_by(time, hidp) %>%
+  summarise(nkids_counts = mean(nkids)) %>%
+  group_by(time) %>%
+  summarise(nkids_by_year = sum(nkids_counts)) %>%
+  mutate(source = 'baseline')
+
+raw.child.ages.nkids <- raw.dat %>%
+  group_by(time, hidp) %>%
+  summarise(nkids_counts = mean(nkids)) %>%
+  group_by(time) %>%
+  summarise(nkids_by_year = sum(nkids_counts)) %>%
+  mutate(source = 'final_US')
+
+combined.nkids <- rbind(base.child.ages.nkids, raw.child.ages.nkids)
+
+ggplot(data = combined.nkids, mapping = aes(x = time, y = nkids_by_year, group = source, colour = source)) +
+  geom_line() +
+  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+```
+
 ```{r}

### 2024-01-19 minos/validation/interventions.Rmd

@@
 ```
+
+## Poverty Line Child Uplift
+
+```{r}
+income.base <- base %>% 
+  select(pidp, time, hh_income)
+income.poverty <- poverty %>% 
+  select(pidp, time, hh_income, income_boosted)
+# first rename and cbind
+income.b <- rename(income.base, base = hh_income)
+income.e <- rename(income.poverty, poverty = hh_income)
+income.merged <- merge(income.b, income.e, by=c('pidp', 'time'))
+income.merged <- pivot_longer(data = income.merged,
+                              cols = base:poverty,
+                              names_to = 'scenario',
+                              values_to = 'hh_income')
+income.merged.byyr <- income.merged %>%
+  group_by(time, scenario) %>%
+  summarise(hh_income = mean(hh_income))
+ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
+  geom_line()
+```
+## SF_12
+```{r}
+sf12.base <- base %>% 
+  select(pidp, time, SF_12)
+sf12.poverty <- poverty %>% 
+  select(pidp, time, SF_12, income_boosted)
+# first rename and cbind
+sf12.b <- rename(sf12.base, base = SF_12)
+sf12.e <- rename(sf12.poverty, poverty = SF_12)
+sf12.merged <- merge(sf12.b, sf12.e, by=c('pidp', 'time'))
+sf12.merged <- pivot_longer(data = sf12.merged,
+                              cols = base:poverty,
+                              names_to = 'scenario',
+                              values_to = 'SF_12')
+sf12.merged.byyr <- sf12.merged %>%
+  group_by(time, scenario) %>%
+  summarise(SF_12 = mean(SF_12))
+ggplot(data = sf12.merged.byyr, mapping = aes(x = time, y = SF_12, color=scenario)) +
+  geom_line()
+```
+
+## Boost Amount
+```{r}
+income.poverty <- poverty %>% 
+  select(pidp, time, hh_income, income_boosted, boost_amount)
+income.poverty.byyr <- income.poverty %>%
+  group_by(time) %>%
+  summarise(boost_amount = mean(boost_amount))
+ggplot(data = income.poverty.byyr, mapping = aes(x = time, y = boost_amount)) +
+  geom_line()
+```
+## Who Boosted?
+
+```{r}
+boosted.byyr <- income.poverty %>% 
+  group_by(time) %>%
+  count(income_boosted)
+ggplot(data = filter(boosted.byyr, income_boosted == 'True'), mapping = aes(x = time, y = n)) +
+  geom_line()
+```

### 2024-01-19 minos/outcomes/SCP_vis.Rmd
Adding plots for priority groups, and changing to use scotland scaled data

@@
 #out.path <- here::here('output', 'default_config')
-out.path <- here::here('output', 'glasgow_scaled')
+#out.path <- here::here('output', 'glasgow_scaled')
+out.path <- here::here('output', 'scaled_scotland')
 
@@
       filter(time >= start.year) %>%
-      group_by(time, run_id) %>%
+      group_by(time, simd_decile, run_id) %>%
       summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
@@
 
-  options(repr.plot.width =9, repr.plot.height =20)
-
+  if (batch) {
+    p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
+      geom_smooth() +
+      geom_hline(yintercept = 0, linetype='dashed') +
+      facet_wrap(. ~ scen, ncol=1) +
+      labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
+      xlab('Year') +
+      ylab('Difference')
+  } else {
     p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
@@
       ylab('Difference')
+  }
 
@@
 SF12.change.by.deciles(int.list, scen.list)
+```
+
+## MCS - PRIORITY GROUPS
+
+### All Priority Subgroups
+
+```{r}
+
+```
+
+### Minority Ethnic Groups
+
+```{r}
+priority_filter_ethnicity <- function(df.list, scen.list, start.year) {
+  single.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, ethnicity, SF_12) %>%
+      filter(ethnicity != 'WBI') %>%
+      group_by(time) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+  batch.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, ethnicity, run_id, SF_12) %>%
+      filter(ethnicity != 'WBI') %>%
+      group_by(time, run_id) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  if (batch) {
+    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time', 'run_id'))
+  } else {
+    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time'))
+  }
+  return(combined)
+}
+
+priority_filter_child_under_one <- function(df.list, scen.list, start.year) {
+  single.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, child_ages, SF_12) %>%
+      filter(substr(child_ages, 1, 1) == 0) %>%
+      group_by(time) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+  batch.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, child_ages, run_id, SF_12) %>%
+      filter(substr(child_ages, 1, 1) == 0) %>%
+      group_by(time, run_id) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  if (batch) {
+    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time', 'run_id'))
+  } else {
+    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time'))
+  }
+  return(combined)
+}
+
+priority_filter_three_plus_children <- function(df.list, scen.list, start.year) {
+  single.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, nkids, SF_12) %>%
+      filter(nkids >= 3) %>%
+      group_by(time) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+  batch.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, nkids, run_id, SF_12) %>%
+      filter(nkids >= 3) %>%
+      group_by(time, run_id) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  if (batch) {
+    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time', 'run_id'))
+  } else {
+    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time'))
+  }
+  return(combined)
+}
+
+priority_filter_mother_under_25 <- function(df.list, scen.list, start.year) {
+  single.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, age, nkids_ind, SF_12) %>%
+      filter(nkids_ind > 0 & age < 25) %>%
+      group_by(time) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+  batch.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, age, nkids_ind, run_id, SF_12) %>%
+      filter((nkids_ind > 0) && (age < 25)) %>%
+      group_by(time, run_id) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  if (batch) {
+    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time', 'run_id'))
+  } else {
+    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time'))
+  }
+  return(combined)
+}
+
+priority_filter_disabled <- function(df.list, scen.list, start.year) {
+  single.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, hidp, weight, S7_labour_state, SF_12) %>%
+      group_by(hidp) %>%
+      mutate(disabled_flag = ifelse(any(S7_labour_state) == 'disabled')) %>%
+      filter(disabled_flag == TRUE) %>%
+      group_by(time) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+  batch.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, hidp, weight, S7_labour_state, run_id, SF_12) %>%
+      group_by(hidp) %>%
+      mutate(disabled_flag = ifelse(any(S7_labour_state) == 'disabled')) %>%
+      filter(disabled_flag == TRUE) %>%
+      group_by(time, run_id) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  if (batch) {
+    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time', 'run_id'))
+  } else {
+    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time'))
+  }
+  return(combined)
+}
+
+SF12.change.priority.group <- function(df.list, scen.list, priority.group, start.year = 2020, batch=FALSE) {
+
+  # Filter data for priority groups
+  if (priority.group == 'minority_ethnic') { combined <- priority_filter_ethnicity(df.list, scen.list, start.year) }
+  if (priority.group == 'child_under_one') { combined <- priority_filter_child_under_one(df.list, scen.list, start.year) }
+  if (priority.group == 'three_plus_children') { combined <- priority_filter_three_plus_children(df.list, scen.list, start.year) }
+  if (priority.group == 'mother_under_25') { combined <- priority_filter_mother_under_25(df.list, scen.list, start.year) }
+  if (priority.group == 'disabled') { combined <- priority_filter_disabled(df.list, scen.list, start.year) }
+
+  # List of intervention columns
+  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
+
+  # Create the new dataframe with differences
+  combined <- combined %>%
+    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
+    select(time, starts_with("diff")) %>%
+    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
+
+  combined <- combined %>%
+    pivot_longer(cols = starts_with('diff'),
+                 names_to = 'scen',
+                 values_to = 'diff')
+
+  if (batch) {
+    p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
+      geom_smooth() +
+      geom_hline(yintercept = 0, linetype='dashed') +
+      labs(title = paste0('SF12 MCS Change - ', priority.group)) +
+      xlab('Year') +
+      ylab('Difference')
+  } else {
+    p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
+      geom_line() +
+      geom_hline(yintercept = 0, linetype='dashed') +
+      labs(title = paste0('SF12 MCS Change - ', priority.group)) +
+      xlab('Year') +
+      ylab('Difference')
+  }
+
+  print(p1)
+}
+
+batch <- FALSE
+start.year <- 2020
+
+SF12.change.priority.group(int.list, scen.list, priority.group = 'minority_ethnic')
+SF12.change.priority.group(int.list, scen.list, priority.group = 'child_under_one')
+SF12.change.priority.group(int.list, scen.list, priority.group = 'three_plus_children')
+SF12.change.priority.group(int.list, scen.list, priority.group = 'mother_under_25')
+SF12.change.priority.group(int.list, scen.list, priority.group = 'disabled')
+
 ```

### 2024-01-19 minos/outcomes/SCP_vis.Rmd
Stopped producing plot for disabled priority subgroup as the filter is killing the script. Needs some work, just turning off for now as rest of script is good.

@@
 #out.path <- here::here('output', 'default_config')
-#out.path <- here::here('output', 'glasgow_scaled')
-out.path <- here::here('output', 'scaled_scotland')
+out.path <- here::here('output', 'glasgow_scaled')
+#out.path <- here::here('output', 'scaled_scotland')
 
@@
 SF12.change.priority.group(int.list, scen.list, priority.group = 'mother_under_25')
-SF12.change.priority.group(int.list, scen.list, priority.group = 'disabled')
+#SF12.change.priority.group(int.list, scen.list, priority.group = 'disabled')
 

### 2024-01-19 minos/outcomes/SCP_vis.Rmd
Changing CPR vis to run on scotland scaled data

@@
 
-```{r}
+```{r source_functions, include=FALSE}
 source(here::here('minos', 'utils_datain.R'))
@@
 
-```{r}
+```{r read_data}
 #out.path <- here::here('output', 'default_config')
-out.path <- here::here('output', 'glasgow_scaled')
-#out.path <- here::here('output', 'scaled_scotland')
+#out.path <- here::here('output', 'glasgow_scaled')
+out.path <- here::here('output', 'scaled_scotland')
 
@@
 
-```{r}
-
-```
-
 ```{r SF12_whole_pop, echo=FALSE}

### 2024-01-19 minos/outcomes/CPR_vis.Rmd
More additions to SCP plotting scripts, added some decile plots
Changing CPR vis to run on scotland scaled data
Added some variables that were missing from the batch run, and upped the vmem assigned to the full 192GB. Fingers crossed...

@@
 
-```{r}
+```{r source_functions}
 source(here::here('minos', 'utils_datain.R'))
@@
 
-```{r}
-out.path <- here::here('output', 'default_config')
+```{r read_data}
+#out.path <- here::here('output', 'default_config')
+#out.path <- here::here('output', 'glasgow_scaled')
+out.path <- here::here('output', 'scaled_scotland')
 
@@
 var.list <- c('pidp', 'hidp', 'time', 'weight', 
-              'age', 'ethnicity', 'education_state', 'region', 'nkids',
+              'age', 'ethnicity', 'education_state', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
               'hh_income',

### 2024-01-19 minos/outcomes/SCP_vis.Rmd
Added some variables that were missing from the batch run, and upped the vmem assigned to the full 192GB. Fingers crossed...

@@
 var.list <- c('pidp', 'hidp', 'time', 'weight', 
-              'age', 'ethnicity', 'education_state', 'region', 'nkids',
-              'hh_income',
+              'age', 'ethnicity', 'education_state', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
+              'hh_income', 'child_ages', 'simd_deciles',
               'housing_quality', 'neighbourhood_safety', 'loneliness', 'ncigs', 'nutrition_quality', 'financial_situation', 'urban', 'housing_tenure',

### 2024-01-19 scripts/arc_CPR_vis_run.sh

@@ -7,19 +7,23 @@
 ## Use current environment variables and modules
 #$ -V
 ## Request hours of runtime
-#$ -l h_rt=4:00:00
+#$ -l h_rt=12:00:00
 ## Email if a run aborts
 #$ -m a
 ## Select memory
-#$ -l h_vmem=50G # was 15 for big runs
+#$ -l h_vmem=192G # was 15 for big runs
 ## Choose cores. See arc website for more details. 5 high memory cores chosen here.
 #$ -pe smp 1
 ## Set logs directories
-#$ -o ./logs/log
-#$ -e ./logs/errors
+#$ -o ./logs/SCP/log
+#$ -e ./logs/SCP/errors
 
 ############## SET NUMBER OF RUNS HERE ##############
 ## Tell computer this is an array job with tasks from 1 to N
 #$ -t 1-1
+
+mkdir -p logs/SCP
+mkdir -p logs/SCP/log
+mkdir -p logs/SCP/errors
 
 Rscript -e "require(rmarkdown); render('minos/outcomes/CPR_vis.Rmd')"

### 2024-01-19 scripts/arc_SCP_vis_run.sh

@@ -7,19 +7,23 @@
 ## Use current environment variables and modules
 #$ -V
 ## Request hours of runtime
-#$ -l h_rt=4:00:00
+#$ -l h_rt=12:00:00
 ## Email if a run aborts
 #$ -m a
 ## Select memory
-#$ -l h_vmem=50G # was 15 for big runs
+#$ -l h_vmem=192G # was 15 for big runs
 ## Choose cores. See arc website for more details. 5 high memory cores chosen here.
 #$ -pe smp 1
 ## Set logs directories
-#$ -o ./logs/log
-#$ -e ./logs/errors
+#$ -o ./logs/SCP/log
+#$ -e ./logs/SCP/errors
 
 ############## SET NUMBER OF RUNS HERE ##############
 ## Tell computer this is an array job with tasks from 1 to N
 #$ -t 1-1
+
+mkdir -p logs/SCP
+mkdir -p logs/SCP/log
+mkdir -p logs/SCP/errors
 
 Rscript -e "require(rmarkdown); render('minos/outcomes/SCP_vis.Rmd')"

### 2024-01-20 minos/outcomes/CPR_vis.Rmd
Fix typo in one of the variables for vis scripts...

@@
 var.list <- c('pidp', 'hidp', 'time', 'weight', 
-              'age', 'ethnicity', 'education_state', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
-              'hh_income',
-              'housing_quality', 'neighbourhood_safety', 'loneliness', 'ncigs', 'nutrition_quality', 'financial_situation', 'urban', 'housing_tenure',
+              'age', 'ethnicity', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
+              'hh_income', 'child_ages', 'simd_decile',
               'SF_12', 'matdep_child')

### 2024-01-20 minos/outcomes/SCP_vis.Rmd
Fix typo in one of the variables for vis scripts...

--- 2024-01-19 minos/outcomes/SCP_vis.Rmd
@@
 var.list <- c('pidp', 'hidp', 'time', 'weight', 
-              'age', 'ethnicity', 'education_state', 'region', 'nkids',
-              'hh_income',
-              'housing_quality', 'neighbourhood_safety', 'loneliness', 'ncigs', 'nutrition_quality', 'financial_situation', 'urban', 'housing_tenure',
+              'age', 'ethnicity', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
+              'hh_income', 'child_ages', 'simd_decile',
               'SF_12', 'matdep_child')

### 2024-01-20 minos/outcomes/CPR_vis.Rmd
Added more to CPR vis script and added a missing argument to some function calls in SCP vis

@@
                             verbose = TRUE)
+
+int.list <- list(base, int)
+scen.list <- c('base', 'ChildPovReduction')
 
@@
 
+```{r SF12_deciles}
+SF12.by.simd.deciles <- function(df.list, scen.list, start.year = 2020, batch=FALSE) {
+  single.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, simd_decile, SF_12) %>%
+      filter(time >= start.year) %>%
+      group_by(time, simd_decile) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+  batch.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, simd_decile, run_id, SF_12) %>%
+      filter(time >= start.year) %>%
+      group_by(time, simd_decile, run_id) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  if (batch) {
+    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time', 'simd_decile', 'run_id'))
+  } else {
+    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time', 'simd_decile'))
+  }
+
+  combined$simd_decile <- as.factor(combined$simd_decile)
+
+  int.labels <- scen.list[-1]
+
+  for (int in int.labels) {
+    int.name <- paste0(int, '.SF12')
+    if (batch) {
+      p1 <- ggplot(combined, aes(x = time, group = simd_decile, colour = simd_decile)) +
+        geom_smooth(aes(y = base.SF12)) +
+        geom_smooth(aes(y = .data[[int.name]]), linetype='dashed') +
+        labs(title = 'SF12 MCS Deciles', subtitle = paste0('Baseline vs ', int)) +
+        xlab('Year') +
+        ylab('Difference')
+    } else {
+      p1 <- ggplot(combined, aes(x = time, group = simd_decile, colour = simd_decile)) +
+        geom_line(aes(y = base.SF12)) +
+        geom_line(aes(y = .data[[int.name]]), linetype='dashed') +
+        labs(title = 'SF12 MCS Deciles', subtitle = int) +
+        xlab('Year') +
+        ylab('Difference')
+    }
+    print(p1)
+  }
+}
+```
+
+```{r SF_change_deciles, echo=FALSE}
+SF12.change.by.deciles <- function(df.list, scen.list, start.year = 2020, batch = FALSE) {
+  single.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, simd_decile, SF_12) %>%
+      filter(time >= start.year) %>%
+      group_by(time, simd_decile) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+  batch.mean <- function(data, scen, start.year) {
+    newvar.name <- paste0(scen, '.SF12')
+    data <- data %>%
+      select(time, weight, simd_decile, run_id, SF_12) %>%
+      filter(time >= start.year) %>%
+      group_by(time, simd_decile, run_id) %>%
+      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+    return(data)
+  }
+
+  if (batch) {
+    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time', 'simd_decile', 'run_id'))
+  } else {
+    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
+    combined <- mod.list %>%
+      reduce(full_join, by=c('time', 'simd_decile'))
+  }
+
+  combined$simd_decile <- as.factor(combined$simd_decile)
+
+  # List of intervention columns
+  int_cols <- grep("ChildPovReduction.SF12", names(combined), value = TRUE)
+
+  # Create the new dataframe with differences
+  combined <- combined %>%
+    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
+    select(time, simd_decile, starts_with("diff")) %>%
+    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
+
+  combined <- combined %>%
+    pivot_longer(cols = starts_with('diff'),
+                 names_to = 'scen',
+                 values_to = 'diff')
+
+  if (batch) {
+    p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
+      geom_smooth() +
+      geom_hline(yintercept = 0, linetype='dashed') +
+      facet_wrap(. ~ scen, ncol=1) +
+      labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
+      xlab('Year') +
+      ylab('Difference')
+  } else {
+    p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
+      geom_line() +
+      geom_hline(yintercept = 0, linetype='dashed') +
+      facet_wrap(. ~ scen, ncol=1) +
+      labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
+      xlab('Year') +
+      ylab('Difference')
+  }
+
+  ggsave(filename = 'test_plot.png',
+         plot = p1,
+         path = here::here('plots', 'SCOTGOVWORK'),
+         width = 9,
+         height = 20)
+
+  print(p1)
+}
+```
+
 # PLOTS
@@
 ```{r, echo=FALSE}
-threshold <- base %>%
-  select(time, weight, hh_income) %>%
-  group_by(time) %>%
-  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
-
-ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
-  geom_col() +
-  geom_hline(yintercept = rel.pov.threshold, linetype='dashed') +
-  labs(title = 'Relative poverty threshold over time') +
-  xlab('Year') +
-  ylab('Threshold')
-
+if (batch) {
   threshold <- base %>%
@@
   ylab('Threshold')
+} else {
+  threshold <- base %>%
+  select(time, weight, hh_income) %>%
+  group_by(time) %>%
+  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
+
+ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
+  geom_col() +
+  geom_hline(yintercept = rel.pov.threshold, linetype='dashed') +
+  labs(title = 'Relative poverty threshold over time') +
+  xlab('Year') +
+  ylab('Threshold')
+}
 ```
@@
 }
+```
+
+## DECILES
+
+```{r}
+SF12.by.simd.deciles(int.list, scen.list, start.year = 2020, batch = batch)
+```
+
+```{r}
+SF12.by.simd.deciles(int.list, scen.list, start.year = 2024, batch = batch)
+```
+
+```{r}
+SF12.change.by.deciles(int.list, scen.list, start.year = 2020, batch = batch)
 ```

### 2024-01-20 minos/outcomes/SCP_vis.Rmd
Added more to CPR vis script and added a missing argument to some function calls in SCP vis

@@
 ```{r}
-SF12.by.simd.deciles(int.list, scen.list)
-```
-
-```{r}
-SF12.by.simd.deciles(int.list, scen.list, start.year = 2024, batch = FALSE)
+SF12.by.simd.deciles(int.list, scen.list, batch = batch)
+```
+
+```{r}
+SF12.by.simd.deciles(int.list, scen.list, start.year = 2024, batch = batch)
 ```
@@
 ```{r}
-SF12.change.by.deciles(int.list, scen.list)
+SF12.change.by.deciles(int.list, scen.list, batch = batch)
 ```
@@
 
-SF12.change.priority.group(int.list, scen.list, priority.group = 'minority_ethnic')
-SF12.change.priority.group(int.list, scen.list, priority.group = 'child_under_one')
-SF12.change.priority.group(int.list, scen.list, priority.group = 'three_plus_children')
-SF12.change.priority.group(int.list, scen.list, priority.group = 'mother_under_25')
-#SF12.change.priority.group(int.list, scen.list, priority.group = 'disabled')
+SF12.change.priority.group(int.list, scen.list, priority.group = 'minority_ethnic', batch = batch)
+SF12.change.priority.group(int.list, scen.list, priority.group = 'child_under_one', batch = batch)
+SF12.change.priority.group(int.list, scen.list, priority.group = 'three_plus_children', batch = batch)
+SF12.change.priority.group(int.list, scen.list, priority.group = 'mother_under_25', batch = batch)
+#SF12.change.priority.group(int.list, scen.list, priority.group = 'disabled', batch = batch)
 

### 2024-01-22 minos/validation/handovers.Rmd
adding council tax module in. trying to tweak mean value its still overestimating.

--- 2023-12-19 minos/validation/handovers.Rmd
@@
 ---
-title: "MINOS Handover Plots"
+params:
+    file_path: '' # default arguments. specify others in command line.
+    intervention: ''
+title: "Handovers"
 output:
+  #output_file: "`r paste('minos/validation/', params$file_path, '_', params$intervention, '_handovers.html') `"
   html_document:
@@
 ```{r}
+
 # Read raw datafiles in
@@
 
-out.path <- here::here('output', 'default_config/')
-base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-# out.path <- here::here('output', 'child_poverty_config/')
-# base.dat <- read_singular_local_out(out.path, 'ChildPovertyIntervention', drop.dead = TRUE)
+#out.path <- here::here('output', 'default_config/')
+#base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+
+out.path <- here::here("output", "default_config")
+base.dat <- read_singular_local_out(out.path, "/baseline", drop.dead = TRUE)
 ```
@@
 ```{r}
-start.year <- 2020
 save.path <- here::here("plots", "handovers", 'default')
 create.if.not.exists(save.path)
+start.year <- 2021
+# make sure we only overlap on one year for now or else tomfoolery happens. (the plots look bad).
+# we may want this overlap in the future? probably not.
+raw.dat <- raw.dat[which(raw.dat$time <= start.year), ]
+base.dat <- base.dat[which(base.dat$time>=start.year), ]
 
@@
 rm(raw.inc, base.inc, income.spag)
+```
+
+## Net Income & Rent & Mortgage
+
+```{r net_income}
+# get required variables. 
+raw.inc <- raw.dat %>%
+  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
+base.inc <- base.dat %>%
+  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
+
+# net household income. 
+handover_boxplots(raw.inc, base.inc, 'net_hh_income')
+handover_lineplots(raw.inc, base.inc, "net_hh_income")
+inc.spag<-rbind(raw.inc, base.inc)
+density_ridges(inc.spag, 'net_hh_income',
+               save=TRUE, 
+               save.path=save.path)
+
+# rent
+handover_boxplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], 'hh_rent')
+handover_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
+density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
+               save=TRUE, 
+               save.path=save.path)
+
+# mortgage
+handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], 'hh_mortgage')
+handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
+density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
+               save=TRUE, 
+               save.path=save.path)
+
+#council tax
+handover_boxplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], 'council_tax')
+handover_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
+density_ridges(inc.spag[which(inc.spag$council_tax>1), ], 'council_tax',
+               save=TRUE, 
+               save.path=save.path)
+
+# oecd equivalence scale. (NOT TRANSITIONED YET. REQUIRES LEAVING THE NEST MODULE.. )
+handover_boxplots(raw.inc, base.inc, 'oecd_equiv')
+handover_lineplots(raw.inc, base.inc, 'oecd_equiv')
+density_ridges(inc.spag, 'oecd_equiv',
+               save=TRUE, 
+               save.path=save.path)
+
+# tidy up.
+rm(raw.inc, base.inc, inc.spag)
 ```
@@
 # rm(raw.s, base.s, spag)
+```
+
+## Housing Tenure
+
+```{r}
+raw.tenure <- raw.dat %>%
+  dplyr::select(pidp, time, housing_tenure) %>%
+  group_by(time, housing_tenure) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.tenure <- base.dat %>%
+  dplyr::select(pidp, time, housing_tenure) %>%
+  group_by(time, housing_tenure) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+tenure <- rbind(raw.tenure, base.tenure)
+tenure$housing_tenure <- as.factor(tenure$housing_tenure)
+
+# Now plot
+ggplot(data = tenure, mapping = aes(x = time, y = n, group = housing_tenure, colour = housing_tenure)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Housing Tenure', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+tenure.norm <- tenure %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = tenure.norm, mapping = aes(x = time, y = prct, fill=housing_tenure)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Housing Tenure') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'housing_tenure.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.tenure, base.tenure, tenure, tenure.norm)
 ```
@@
 
-## CHILD POVERTY VARS
-
-### Relative poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Relative Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'relative_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-### Absolute Poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Absolute Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'absolute_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-### Persistent Poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Persistent Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'persistent_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-
-```
-
-### Low Income and Material Deprivation
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Material Deprivation Child'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'low_income_matdep_child.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-
-```
-
 ```{r}

### 2024-01-22 minos/outcomes/SCP_vis.Rmd
Additions to SCP_vis.Rmd script, handovers.Rmd (nkids plots), and changing some interventions to 1% scottish scaled pop

@@
 require(purrr)
+require(parallel)
 
@@
 #out.path <- here::here('output', 'glasgow_scaled')
-out.path <- here::here('output', 'scaled_scotland')
+#out.path <- here::here('output', 'scaled_scotland')
+#out.path <- here::here('output', 'default_config_batch')
+out.path <- here::here('output', 'scaled_scotland_batch')
+#out.path <- here::here('output', 'scaled_scotland_small')
 
@@
                       verbose = TRUE)
-int30 <- read_output(out.path,
-                      scenario = '30UniversalCredit',
-                      var.list = var.list,
-                      verbose = TRUE)
-int35 <- read_output(out.path,
-                      scenario = '35UniversalCredit',
-                      var.list = var.list,
-                      verbose = TRUE)
-int40 <- read_output(out.path,
-                      scenario = '40UniversalCredit',
-                      var.list = var.list,
-                      verbose = TRUE)
-int45 <- read_output(out.path,
-                      scenario = '45UniversalCredit',
-                      var.list = var.list,
-                      verbose = TRUE)
+# int30 <- read_output(out.path,
+#                       scenario = '30UniversalCredit',
+#                       var.list = var.list,
+#                       verbose = TRUE)
+# int35 <- read_output(out.path,
+#                       scenario = '35UniversalCredit',
+#                       var.list = var.list,
+#                       verbose = TRUE)
+# int40 <- read_output(out.path,
+#                       scenario = '40UniversalCredit',
+#                       var.list = var.list,
+#                       verbose = TRUE)
+# int45 <- read_output(out.path,
+#                       scenario = '45UniversalCredit',
+#                       var.list = var.list,
+#                       verbose = TRUE)
 int50 <- read_output(out.path,
@@
 
-  df.list <- mapply(single.mean, df.list, scen.list, SIMPLIFY = FALSE)
+  df.list <- mapply(batch.mean, df.list, scen.list, SIMPLIFY = FALSE)
 
@@
 
-  df.list <- mapply(single.mean, df.list, scen.list, boosted, SIMPLIFY = FALSE)
+  df.list <- mapply(batch.mean, df.list, scen.list, boosted, SIMPLIFY = FALSE)
 
@@
 
-  ggsave(filename = 'test_plot.png',
-         plot = p1,
-         path = here::here('plots', 'SCOTGOVWORK'),
-         width = 9,
-         height = 20)
+  #ggsave(filename = 'test_plot.png',
+  #       plot = p1,
+  #       path = here::here('plots', 'SCOTGOVWORK'),
+  #       width = 9,
+  #       height = 20)
 
@@
 }
-
-batch <- FALSE
-start.year <- 2020
 
@@
             kids_boosted = sum(nkids)) %>%
-  mutate(prop_boosted = n_boosted / n,
-         prop_kids_boosted)
+  mutate(prop_boosted = n_boosted / n)
+	#prop_kids_boosted = # MORE HERE
 
@@
   geom_line() +
-  labs(title = 'Number of households receiving intervention', subtitle = int.name) +
+  labs(title = 'Number of households receiving intervention', subtitle = 'int25') +
   xlab('Year') +
@@
   geom_line() +
-  labs(title = 'Number of children in households receiving intervention', subtitle = int.name) +
+  labs(title = 'Number of children in households receiving intervention', subtitle = 'int25') +
   xlab('Year') +

### 2024-01-22 minos/validation/handovers.Rmd
Additions to SCP_vis.Rmd script, handovers.Rmd (nkids plots), and changing some interventions to 1% scottish scaled pop

--- 2024-01-15 minos/validation/handovers.Rmd
@@
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+
+#
 
@@
 
+## nkids Household
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'nkids')
+handover_lineplots(raw.dat, base.dat, 'nkids')
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, nkids)
+base.s <- base.dat %>%
+  select(pidp, age, time, nkids)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nkids',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+## nkids Max
+
+```{r}
+# first figure out how to plot final_US
+# start with hh_income
+raw.nkids_max <- raw.dat %>%
+  dplyr::select(pidp, time, nkids) %>%
+  group_by(time) %>%
+  summarise(max_nkids = max(nkids)) %>%
+  mutate(source = 'final_US')
+
+base.nkids_max <- base.dat %>%
+  dplyr::select(pidp, time, nkids) %>%
+  group_by(time) %>%
+  summarise(max_nkids = max(nkids)) %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+max_nkids <- rbind(raw.nkids_max, base.nkids_max)
+
+# Now plot
+ggplot(data = max_nkids, mapping = aes(x = time, y = max_nkids, group = source, colour = source)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Max nkids', subtitle = 'Full Sample') +
+  xlab('Year') +
+  ylab('Average')
+```
+
 ## Parity

### 2024-01-22 minos/outcomes/SCP_vis_summary.Rmd
Reading batch output files now multiprocessed and chunked. Also added some functions for reading and summarising outputs when file sizes get too large, still WIP

--- 2024-01-20 minos/outcomes/SCP_vis.Rmd
@@
 #out.path <- here::here('output', 'glasgow_scaled')
-out.path <- here::here('output', 'scaled_scotland')
+#out.path <- here::here('output', 'scaled_scotland')
+#out.path <- here::here('output', 'default_config_batch')
+out.path <- here::here('output', 'scaled_scotland_batch')
 
@@
               'age', 'ethnicity', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
-              'hh_income', 'child_ages', 'simd_decile',
+              'hh_income', 'child_ages', #'simd_decile',
               'SF_12', 'matdep_child')
 
-base <- read_output(out.path, 
+# base <- read_output(out.path, 
+#                     scenario = 'baseline', 
+#                     var.list = var.list,
+#                     verbose = TRUE)
+# int25 <- read_output(out.path, 
+#                       scenario = '25UniversalCredit', 
+#                       var.list = var.list,
+#                       verbose = TRUE)
+# int30 <- read_output(out.path,
+#                       scenario = '30UniversalCredit',
+#                       var.list = var.list,
+#                       verbose = TRUE)
+# int35 <- read_output(out.path,
+#                       scenario = '35UniversalCredit',
+#                       var.list = var.list,
+#                       verbose = TRUE)
+# int40 <- read_output(out.path,
+#                       scenario = '40UniversalCredit',
+#                       var.list = var.list,
+#                       verbose = TRUE)
+# int45 <- read_output(out.path,
+#                       scenario = '45UniversalCredit',
+#                       var.list = var.list,
+#                       verbose = TRUE)
+# int50 <- read_output(out.path,
+#                       scenario = '50UniversalCredit',
+#                       var.list = var.list,
+#                       verbose = TRUE)
+
+base <- read_batch_out_all_years_summarise(out.path, 
                                             scenario = 'baseline',
-                    var.list = var.list,
                                             verbose = TRUE)
-int25 <- read_output(out.path, 
+int25 <- read_batch_out_all_years_summarise(out.path, 
                       scenario = '25UniversalCredit',
-                      var.list = var.list,
                       verbose = TRUE)
-int30 <- read_output(out.path,
-                      scenario = '30UniversalCredit',
-                      var.list = var.list,
+# int30 <- read_batch_out_all_years_summarise(out.path,
+#                       scenario = '30UniversalCredit',
+#                       verbose = TRUE)
+# int35 <- read_batch_out_all_years_summarise(out.path,
+#                       scenario = '35UniversalCredit',
+#                       verbose = TRUE)
+# int40 <- read_batch_out_all_years_summarise(out.path,
+#                       scenario = '40UniversalCredit',
+#                       verbose = TRUE)
+# int45 <- read_batch_out_all_years_summarise(out.path,
+#                       scenario = '45UniversalCredit',
+#                       verbose = TRUE)
+int50 <- read_batch_out_all_years_summarise(out.path,
+                      scenario = '50UniversalCredit',
                       verbose = TRUE)
-int35 <- read_output(out.path,
-                      scenario = '35UniversalCredit',
-                      var.list = var.list,
-                      verbose = TRUE)
-int40 <- read_output(out.path,
-                      scenario = '40UniversalCredit',
-                      var.list = var.list,
-                      verbose = TRUE)
-int45 <- read_output(out.path,
-                      scenario = '45UniversalCredit',
-                      var.list = var.list,
-                      verbose = TRUE)
-int50 <- read_output(out.path,
-                      scenario = '50UniversalCredit',
-                      var.list = var.list,
-                      verbose = TRUE)
 
 #int.list <- c(int25, int30, int35, int40, int45, int50)
-int.list <- list(base, int25, int30, int35, int40, int45, int50)
-scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')
+# int.list <- list(base, int25, int30, int35, int40, int45, int50)
+# scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')
+
+int.list <- list(base, int25, int50)
+scen.list <- c('base', 'int25', 'int50')
+
+# make sure all data are in dataframes
+int.list <- lapply(int.list, as.data.frame)
 
@@
 # Save path and save flag
-save.path <- here::here('plots', 'SCOTGOV', 'CPR')
+save.path <- here::here('plots', 'SCOTGOV', 'SPC')
 create.if.not.exists(save.path)
@@
     data <- data %>%
-      select(time, weight, SF_12) %>%
+      select(time, SF_12) %>%
+      filter(SF_12 != -8) %>%
       group_by(time) %>%
-      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm =TRUE))
     return(data)
@@
     data <- data %>%
-      select(time, weight, run_id, SF_12) %>%
+      select(time, run_id, SF_12) %>%
+      filter(SF_12 != -8) %>%
       group_by(time, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-
-  # base <- batch.mean(base.dat, scen = 'base')
-  # int1 <- batch.mean(int.dat1, scen = 'int25')
-  # int2 <- batch.mean(int.dat2, scen = 'int50')
-  # int3 <- batch.mean(int.dat3, scen = 'int75')
-  # int4 <- batch.mean(int.dat4, scen = 'int100')
-
-  df.list <- mapply(single.mean, df.list, scen.list, SIMPLIFY = FALSE)
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm =TRUE))
+    return(data)
+  }
+
+  df.list <- mapply(batch.mean, df.list, scen.list, SIMPLIFY = FALSE)
 
@@
     reduce(full_join, by=c('time', 'run_id'))
-
-  # combined$diff25 <- combined$int25.SF12 - combined$base.SF12
-  # combined$diff50 <- combined$int50.SF12 - combined$base.SF12
-  # combined$diff75 <- combined$int75.SF12 - combined$base.SF12
-  # combined$diff100 <- combined$int100.SF12 - combined$base.SF12
 
@@
     data <- data %>%
-      select(time, weight, SF_12, nkids) %>%
+      select(time, SF_12, nkids) %>%
       filter(nkids > 0) %>%
+      filter(SF_12 != -8) %>%
       group_by(time) %>%
-      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm =TRUE))
+    return(data)
+  }
+  ########################################### CHANGE EVERYTHING FROM WEIGHTED MEAN TO MEAN ###########################################
 
@@
     data <- data %>%
-      select(time, weight, run_id, SF_12, nkids) %>%
+      select(time, run_id, SF_12, nkids) %>%
       filter(nkids > 0) %>%
+      filter(SF_12 != -8) %>%
       group_by(time, run_id) %>%
-      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm =TRUE))
     return(data)
@@
 SF12.change.treated.single <- function(df.list, scen.list) {
-  single.mean <- function(data, scen, boosted) {
+  single.mean <- function(data, scen) {
     # define varname
@@
     data <- data %>%
-      select(pidp, time, weight, SF_12) %>%
-      filter(pidp %in% boosted) %>%
+      select(time, boosted, SF_12) %>%
+      filter(boosted == TRUE) %>%
       group_by(time) %>%
-      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm =TRUE))
     return(data)
@@
   # get boosted pidps
-  boosted <- df.list[[2]] %>%
-    select(pidp, income_boosted) %>%
-    filter(income_boosted == 'True')
-  rm(tmp)
-
-  df.list <- mapply(single.mean, df.list, scen.list, boosted, SIMPLIFY = FALSE)
+  # boosted <- df.list[[2]] %>%
+  #   select(pidp, income_boosted) %>%
+  #   filter(income_boosted == 'True')
+  # rm(tmp)
+
+  df.list <- mapply(single.mean, df.list, scen.list, SIMPLIFY = FALSE)
 
@@
 SF12.change.treated.batch <- function(df.list, scen.list) {
-  batch.mean <- function(data, scen, boosted) {
+  batch.mean <- function(data, scen) {
     # define varname
@@
     data <- data %>%
-      select(pidp, time, weight, run_id, SF_12) %>%
-      filter(pidp %in% boosted) %>%
+      select(time, boosted, run_id, SF_12) %>%
+      filter(boosted == TRUE) %>%
       group_by(time, run_id) %>%
-      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm =TRUE))
     return(data)
@@
   # get boosted pidps
-  boosted <- df.list[[2]] %>%
-    select(pidp, income_boosted) %>%
-    filter(income_boosted == 'True')
-
-  df.list <- mapply(single.mean, df.list, scen.list, boosted, SIMPLIFY = FALSE)
+  # boosted <- df.list[[2]] %>%
+  #   select(pidp, income_boosted) %>%
+  #   filter(income_boosted == 'True')
+
+  df.list <- mapply(batch.mean, df.list, scen.list, SIMPLIFY = FALSE)
 
@@
     reduce(full_join, by=c('time', 'run_id'))
+
+  return(combined)
 
@@
 }
+
+test <- SF12.change.treated.batch(int.list, scen.list)
 ```
@@
     data <- data %>%
-      select(time, weight, simd_decile, SF_12) %>%
+      select(time, simd_decile, SF_12) %>%
       filter(time >= start.year) %>%
       group_by(time, simd_decile) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm =TRUE))
     return(data)
@@
     data <- data %>%
-      select(time, weight, simd_decile, run_id, SF_12) %>%
+      select(time, simd_decile, run_id, SF_12) %>%
       filter(time >= start.year) %>%
       group_by(time, simd_decile, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12))
     return(data)
@@
 
+```{r}
+# SF12.change.full.sample.batch <- function(df.list, scen.list) {
+#   batch.mean <- function(data, scen) {
+#     newvar.name <- paste0(scen, '.SF12')
+#     data <- data %>%
+#       select(time, run_id, SF_12) %>%
+#       group_by(time, run_id) %>%
+#       summarise(!!sym(newvar.name) := mean(SF_12))
+#     return(data)
+#   }
+#   
+#   df.list <- mapply(batch.mean, df.list, scen.list, SIMPLIFY = FALSE)
+#   
+#   #df.list <- list(base, int1, int2, int3, int4)
+#   combined <- df.list %>%
+#     reduce(full_join, by=c('time', 'run_id'))
+#   
+#   return(combined)
+#   
+#   # List of intervention columns
+#   int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
+#   
+#   # Create the new dataframe with differences
+#   combined <- combined %>%
+#     mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
+#     select(time, starts_with("diff")) %>%
+#     rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
+# 
+#   combined <- combined %>%
+#     pivot_longer(cols = starts_with('diff'),
+#                  names_to = 'scen',
+#                  values_to = 'diff')
+#   
+#   return(combined)
+# 
+#   # combined <- combined %>%
+#   #   select(time, run_id, contains('diff')) %>%
+#   #   pivot_longer(cols = diff25:diff100,
+#   #                names_to = 'scen',
+#   #                values_to = 'diff')
+#   
+#   # TODO: Rename factor levels
+#   # correct factor levels for plot
+#   # combined$scen <- factor(combined$scen,
+#   #                         levels = c('diff100', 'diff75', 'diff50', 'diff25'))
+#   
+#   p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
+#     geom_smooth() +
+#     geom_hline(yintercept = 0, linetype='dashed') +
+#     labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
+#     xlab('Year') +
+#     ylab('Difference')
+#   
+#   print(p1)
+# }
+# 
+# batch.mean <- function(data, scen) {
+#   newvar.name <- paste0(scen, '.SF12')
+#   data <- data %>%
+#     select(time, run_id, SF_12) %>%
+#     group_by(time, run_id) %>%
+#     summarise(!!sym(newvar.name) := mean(SF_12))
+#   return(data)
+# }
+# 
+# # base <- as.data.frame(base)
+# # 
+# # test2 <- batch.mean(base, 'base')
+# 
+# 
+# test3 <- base %>%
+#   select(time, run_id, SF_12) %>%
+#   group_by(time, run_id) %>%
+#   summarise(base.SF12= mean(SF_12, na.rm =TRUE))
+```
+
+```{r}
+# test4 <- as.data.frame(int25) %>%
+#   dplyr::select(time, run_id, SF_12)
+```
+
 # PLOTS
@@
 ```{r}
+
 if (batch) {
@@
 }
+
 ```
@@
     data <- data %>%
-      select(time, weight, ethnicity, SF_12) %>%
+      select(time, ethnicity, SF_12) %>%
       filter(ethnicity != 'WBI') %>%
+      filter(SF_12 >= 0) %>%
       group_by(time) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE))
     return(data)
@@
     data <- data %>%
-      select(time, weight, ethnicity, run_id, SF_12) %>%
+      select(time, ethnicity, run_id, SF_12) %>%
       filter(ethnicity != 'WBI') %>%
+      filter(SF_12 >= 0) %>%
       group_by(time, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE))
     return(data)
@@
     data <- data %>%
-      select(time, weight, child_ages, SF_12) %>%
-      filter(substr(child_ages, 1, 1) == 0) %>%
+      select(time, child_under_one, SF_12) %>%
+      filter(child_under_one == TRUE) %>%
+      filter(SF_12 >= 0) %>%
       group_by(time) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE))
     return(data)
@@
     data <- data %>%
-      select(time, weight, child_ages, run_id, SF_12) %>%
-      filter(substr(child_ages, 1, 1) == 0) %>%
+      select(time, child_under_one, run_id, SF_12) %>%
+      filter(child_under_one == TRUE) %>%
+      filter(SF_12 >= 0) %>%
       group_by(time, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE))
     return(data)
@@
     data <- data %>%
-      select(time, weight, nkids, SF_12) %>%
-      filter(nkids >= 3) %>%
+      select(time, three_plus_child, SF_12) %>%
+      filter(three_plus_child == TRUE) %>%
+      filter(SF_12 >= 0) %>%
       group_by(time) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE))
     return(data)
@@
     data <- data %>%
-      select(time, weight, nkids, run_id, SF_12) %>%
-      filter(nkids >= 3) %>%
+      select(time, three_plus_child, run_id, SF_12) %>%
+      filter(three_plus_child) %>%
+      filter(SF_12 >= 0) %>%
       group_by(time, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE))
     return(data)
@@
     data <- data %>%
-      select(time, weight, age, nkids_ind, SF_12) %>%
-      filter(nkids_ind > 0 & age < 25) %>%
+      select(time, mother_under_25, SF_12) %>%
+      filter(mother_under_25 == TRUE) %>%
+      filter(SF_12 >= 0) %>%
       group_by(time) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE))
     return(data)
@@
     data <- data %>%
-      select(time, weight, age, nkids_ind, run_id, SF_12) %>%
-      filter((nkids_ind > 0) && (age < 25)) %>%
+      select(time, mother_under_25, run_id, SF_12) %>%
+      filter(mother_under_25 == TRUE) %>%
+      filter(SF_12 >= 0) %>%
       group_by(time, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE))
     return(data)
@@
     data <- data %>%
-      select(time, hidp, weight, S7_labour_state, SF_12) %>%
+      select(time, hidp, S7_labour_state, SF_12) %>%
       group_by(hidp) %>%
@@
       group_by(time) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE))
     return(data)
@@
     data <- data %>%
-      select(time, hidp, weight, S7_labour_state, run_id, SF_12) %>%
+      select(time, hidp, S7_labour_state, run_id, SF_12) %>%
       group_by(hidp) %>%
@@
       group_by(time, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
+      summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE))
     return(data)
@@
 threshold <- base %>%
-  select(time, weight, hh_income) %>%
+  select(time, hh_income) %>%
   group_by(time) %>%
-  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
+  summarise(poverty_threshold = (mean(hh_income, na.rm = TRUE) * 0.6))
 
@@
             kids_boosted = sum(nkids)) %>%
-  mutate(prop_boosted = n_boosted / n,
-         prop_kids_boosted)
+  mutate(prop_boosted = n_boosted / n)
 
@@
   geom_line() +
-  labs(title = 'Number of households receiving intervention', subtitle = int.name) +
+  labs(title = 'Number of households receiving intervention') +
   xlab('Year') +
@@
   geom_line() +
-  labs(title = 'Number of children in households receiving intervention', subtitle = int.name) +
+  labs(title = 'Number of children in households receiving intervention') +
   xlab('Year') +
@@
   hh_boosted <- int.dat %>%
-    select(hidp, time, run_id, income_boosted, boost_amount, nkids) %>%
+    select(time, run_id, boosted, boost_amount, nkids) %>%
     filter(income_boosted == 'True') %>%
@@
 ```{r}
-if (batch) {
-  intervention_information_batch(int25, int.name = 'int25', target.year = 2030)
-} else {
-  intervention_information_single(int25, int.name = 'int25', target.year = 2030)
-}
+# if (batch) {
+#   intervention_information_batch(int25, int.name = 'int25', target.year = 2030)
+# } else {
+#   intervention_information_single(int25, int.name = 'int25', target.year = 2030)
+# }
 ```
@@
 ```{r}
-if (batch) {
-  intervention_information_batch(int30, int.name = 'int30', target.year = 2030)
-} else {
-  intervention_information_single(int30, int.name = 'int30', target.year = 2030)
-}
+# if (batch) {
+#   intervention_information_batch(int30, int.name = 'int30', target.year = 2030)
+# } else {
+#   intervention_information_single(int30, int.name = 'int30', target.year = 2030)
+# }
 ```
@@
 ```{r}
-if (batch) {
-  intervention_information_batch(int35, int.name = 'int35', target.year = 2030)
-} else {
-  intervention_information_single(int35, int.name = 'int35', target.year = 2030)
-}
+# if (batch) {
+#   intervention_information_batch(int35, int.name = 'int35', target.year = 2030)
+# } else {
+#   intervention_information_single(int35, int.name = 'int35', target.year = 2030)
+# }
 ```
@@
 ```{r}
-if (batch) {
-  intervention_information_batch(int40, int.name = 'int40', target.year = 2030)
-} else {
-  intervention_information_single(int40, int.name = 'int40', target.year = 2030)
-}
+# if (batch) {
+#   intervention_information_batch(int40, int.name = 'int40', target.year = 2030)
+# } else {
+#   intervention_information_single(int40, int.name = 'int40', target.year = 2030)
+# }
 ```
@@
 ```{r}
-if (batch) {
-  intervention_information_batch(int45, int.name = 'int45', target.year = 2030)
-} else {
-  intervention_information_single(int45, int.name = 'int45', target.year = 2030)
-}
+# if (batch) {
+#   intervention_information_batch(int45, int.name = 'int45', target.year = 2030)
+# } else {
+#   intervention_information_single(int45, int.name = 'int45', target.year = 2030)
+# }
 ```
@@
 ```{r}
-if (batch) {
-  intervention_information_batch(int50, int.name = 'int50', target.year = 2030)
-} else {
-  intervention_information_single(int50, int.name = 'int50', target.year = 2030)
-}
+# if (batch) {
+#   intervention_information_batch(int50, int.name = 'int50', target.year = 2030)
+# } else {
+#   intervention_information_single(int50, int.name = 'int50', target.year = 2030)
+# }
 ```

### 2024-01-22 minos/outcomes/CPR_vis.Rmd

@@
 #out.path <- here::here('output', 'default_config')
-out.path <- here::here('output', 'glasgow_scaled')
+#out.path <- here::here('output', 'glasgow_scaled')
 #out.path <- here::here('output', 'scaled_scotland')
+out.path <- here::here('output', 'default_config_batch')
 
@@
 
-  if (shall.we.save) {
-    filename <- paste0(save.path, 'SF12_whole_pop_single.png')
-
-    ggsave(filename = filename,
-           plot = p1,
-           width = plot.width,
-           height = plot.height)
-  }
+  # if (shall.we.save) {
+  #   filename <- paste0(save.path, 'SF12_whole_pop_single.png')
+  # 
+  #   ggsave(filename = filename,
+  #          plot = p1,
+  #          width = plot.width,
+  #          height = plot.height)
+  # }
 }
@@
 
-  if (shall.we.save) {
-    filename <- paste0(save.path, 'SF12_whole_pop_batch.png')
-    ggsave(filename = filename,
-           plot = p1,
-           width = plot.width,
-           height = plot.height)
-  }
+  # if (shall.we.save) {
+  #   filename <- paste0(save.path, 'SF12_whole_pop_batch.png')
+  #   ggsave(filename = filename,
+  #          plot = p1,
+  #          width = plot.width,
+  #          height = plot.height)
+  # }
 }
@@
 
-  if (shall.we.save) {
-    filename <- paste0(save.path, 'SF12_families_single.png')
-
-    ggsave(filename = filename,
-           plot = p1,
-           width = plot.width,
-           height = plot.height)
-  }
+  # if (shall.we.save) {
+  #   filename <- paste0(save.path, 'SF12_families_single.png')
+  # 
+  #   ggsave(filename = filename,
+  #          plot = p1,
+  #          width = plot.width,
+  #          height = plot.height)
+  # }
 }
@@
 
-  if (shall.we.save) {
-    filename <- paste0(save.path, 'SF12_families_batch.png')
-    ggsave(filename = filename,
-           plot = p1,
-           width = plot.width,
-           height = plot.height)
-  }
+  # if (shall.we.save) {
+  #   filename <- paste0(save.path, 'SF12_families_batch.png')
+  #   ggsave(filename = filename,
+  #          plot = p1,
+  #          width = plot.width,
+  #          height = plot.height)
+  # }
 }
@@
 
-  if (shall.we.save) {
-    filename <- paste0(save.path, 'SF12_treated_single.png')
-    ggsave(filename = filename,
-           plot = p1,
-           width = plot.width,
-           height = plot.height)
-  }
+  # if (shall.we.save) {
+  #   filename <- paste0(save.path, 'SF12_treated_single.png')
+  #   ggsave(filename = filename,
+  #          plot = p1,
+  #          width = plot.width,
+  #          height = plot.height)
+  # }
 }
@@
       geom_hline(yintercept = 0, linetype='dashed') +
-      facet_wrap(. ~ scen, ncol=1) +
       labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
@@
 
-  ggsave(filename = 'test_plot.png',
-         plot = p1,
-         path = here::here('plots', 'SCOTGOVWORK'),
-         width = 9,
-         height = 20)
+  # ggsave(filename = 'test_plot.png',
+  #        plot = p1,
+  #        path = here::here('plots', 'SCOTGOVWORK'),
+  #        width = 9,
+  #        height = 20)
 

### 2024-01-22 minos/outcomes/SCP_vis.Rmd

@@
 # define subset of variables to reduce size of batch output
-var.list <- c('pidp', 'hidp', 'time', 'weight', 
-              'age', 'ethnicity', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
+var.list <- c('age', 'ethnicity', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
               'hh_income', 'child_ages', 'simd_decile',
@@
 #int.list <- c(int25, int30, int35, int40, int45, int50)
-int.list <- list(base, int25, int30, int35, int40, int45, int50)
-scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')
+# int.list <- list(base, int25, int30, int35, int40, int45, int50)
+# scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')
+
+int.list <- list(base, int25, int50)
+scen.list <- c('base', 'int25', 'int50')
 
@@
 # Save path and save flag
-save.path <- here::here('plots', 'SCOTGOV', 'CPR')
+save.path <- here::here('plots', 'SCOTGOVWORK', 'CPR')
 create.if.not.exists(save.path)

### 2024-01-22 minos/validation/cross_validation_default.Rmd

--- 2023-12-15 minos/validation/cross_validation_default.Rmd
@@
 
-## Job Sec
-
-```{r}
-jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                          df1.name = 'simulated', 
-                                          df2 = raw, 
-                                          df2.name = 'raw', 
-                                          var = 'job_sec')
-
-cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
-                 var = 'job_sec',
-                 save = FALSE)
-rm(jobsec.pivoted)
-```
-
-## Hourly Wage
-
-```{r}
-cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hourly_wage')
-multi_year_boxplots(raw, cv, 'hourly_wage')
-q_q_comparison(raw, cv, 'hourly_wage')
-```
+%## Job Sec
+%
+%```{r}
+%jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
+%                                          df1.name = 'simulated', 
+%                                          df2 = raw, 
+%                                          df2.name = 'raw', 
+%                                          var = 'job_sec')
+%
+%cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
+%                 var = 'job_sec',
+%                 save = FALSE)
+%rm(jobsec.pivoted)
+%```
+%
+%## Hourly Wage
+%
+%```{r}
+%cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hourly_wage')
+%multi_year_boxplots(raw, cv, 'hourly_wage')
+%q_q_comparison(raw, cv, 'hourly_wage')
+%```
 
 ## Children Ageing
+
+## CHILDREN AGEING
 

### 2024-01-22 minos/validation/handovers.Rmd

@@
 
-out.path <- here::here('output', 'default_config/')
-base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+#out.path <- here::here('output', 'default_config/')
+#base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
 
-#
-
-#out.path <- here::here('output', 'scotland_scaled/')
-#base.dat <- read_first_singular_local_out(out.path, '25UniversalCredit', drop.dead = TRUE)
-
-# HR 283-285 older version (285)
-# out.path <- here::here('output', 'child_poverty_config/')
-# base.dat <- read_singular_local_out(out.path, 'ChildPovertyIntervention', drop.dead = TRUE)
+out.path <- here::here('output', file_path)
+base.dat <- read_singular_local_out(out.path, intervention, drop.dead = TRUE)
 ```
@@
 
-## Child Ages
-
 ```{r}

### 2024-01-22 minos/outcomes/CPR_vis.Rmd
Further speed improvements to data reading functions using fread function from data.table. Also changed submission scripts to request a full node

@@
     code_folding: hide
+editor_options: 
+  chunk_output_type: console #inline
 ---
@@
 #out.path <- here::here('output', 'glasgow_scaled')
-#out.path <- here::here('output', 'scaled_scotland')
-out.path <- here::here('output', 'default_config_batch')
+out.path <- here::here('output', 'scaled_scotland')
+#out.path <- here::here('output', 'default_config_batch')
+out.path <- here::here('output', 'default_config_batch2')
 
@@
               'age', 'ethnicity', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
-              'hh_income', 'child_ages', 'simd_decile',
+              'hh_income', 'child_ages', #'simd_decile',
               'SF_12', 'matdep_child')
@@
                         verbose = TRUE)
-
-### NOTE: READING INTERVENTION OUTPUTS IS CURRENTLY BROKEN FOR BATCH RUNS
-#         THIS IS BECAUSE WE ARE NO LONGER USING BOOST_AMOUNT
 

### 2024-01-22 minos/outcomes/SCP_vis.Rmd
Further speed improvements to data reading functions using fread function from data.table. Also changed submission scripts to request a full node

@@
 require(parallel)
+require(data.table)
 
@@
 #out.path <- here::here('output', 'glasgow_scaled')
-#out.path <- here::here('output', 'scaled_scotland')
+out.path <- here::here('output', 'scaled_scotland')
 #out.path <- here::here('output', 'default_config_batch')
-out.path <- here::here('output', 'scaled_scotland_batch')
+#out.path <- here::here('output', 'scaled_scotland_batch')
 #out.path <- here::here('output', 'scaled_scotland_small')
+#out.path <- here::here('output', 'tmp_default_baseline')
 
@@
                       verbose = TRUE)
-# int30 <- read_output(out.path,
-#                       scenario = '30UniversalCredit',
-#                       var.list = var.list,
-#                       verbose = TRUE)
-# int35 <- read_output(out.path,
-#                       scenario = '35UniversalCredit',
-#                       var.list = var.list,
-#                       verbose = TRUE)
-# int40 <- read_output(out.path,
-#                       scenario = '40UniversalCredit',
-#                       var.list = var.list,
-#                       verbose = TRUE)
-# int45 <- read_output(out.path,
-#                       scenario = '45UniversalCredit',
-#                       var.list = var.list,
-#                       verbose = TRUE)
+int30 <- read_output(out.path,
+                      scenario = '30UniversalCredit',
+                      var.list = var.list,
+                      verbose = TRUE)
+int35 <- read_output(out.path,
+                      scenario = '35UniversalCredit',
+                      var.list = var.list,
+                      verbose = TRUE)
+int40 <- read_output(out.path,
+                      scenario = '40UniversalCredit',
+                      var.list = var.list,
+                      verbose = TRUE)
+int45 <- read_output(out.path,
+                      scenario = '45UniversalCredit',
+                      var.list = var.list,
+                      verbose = TRUE)
 int50 <- read_output(out.path,
@@
 #int.list <- c(int25, int30, int35, int40, int45, int50)
-# int.list <- list(base, int25, int30, int35, int40, int45, int50)
-# scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')
-
-int.list <- list(base, int25, int50)
-scen.list <- c('base', 'int25', 'int50')
+int.list <- list(base, int25, int30, int35, int40, int45, int50)
+scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')
+
+# int.list <- list(base, int25, int50)
+# scen.list <- c('base', 'int25', 'int50')
 

### 2024-01-22 scripts/arc_SCP_vis_run.sh

@@ -7,20 +7,15 @@
 ## Use current environment variables and modules
 #$ -V
 ## Request hours of runtime
-#$ -l h_rt=12:00:00
+#$ -l h_rt=6:00:00
 ## Email if a run aborts
 #$ -m a
 ## Select memory
-#$ -l h_vmem=192G # was 15 for big runs
-## Choose cores. See arc website for more details. 5 high memory cores chosen here.
-#$ -pe smp 1
+## Select a full node
+#$ -l nodes=1
 ## Set logs directories
 #$ -o ./logs/SCP/log
 #$ -e ./logs/SCP/errors
-
-############## SET NUMBER OF RUNS HERE ##############
-## Tell computer this is an array job with tasks from 1 to N
-#$ -t 1-1
 
 mkdir -p logs/SCP
 mkdir -p logs/SCP/log

### 2024-01-23 minos/outcomes/SCP_vis_summary.Rmd
Created a script to visualise summary outputs created by new read and summarise functions

--- 2024-01-20 minos/outcomes/SCP_vis.Rmd
@@
     code_folding: hide
+editor_options: 
+  chunk_output_type: inline
 ---
@@
 #out.path <- here::here('output', 'glasgow_scaled')
-out.path <- here::here('output', 'scaled_scotland')
+#out.path <- here::here('output', 'scaled_scotland')
+#out.path <- here::here('output', 'default_config_batch')
+out.path <- here::here('output', 'scaled_scotland_batch', 'summary_files')
 
-# define subset of variables to reduce size of batch output
-var.list <- c('pidp', 'hidp', 'time', 'weight', 
-              'age', 'ethnicity', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
-              'hh_income', 'child_ages', 'simd_decile',
-              'SF_12', 'matdep_child')
+# Whole population summaries
+allpop.files <- list.files(out.path,
+                           pattern = "*_whole_pop_summary.csv",
+                           full.names = TRUE)
+allpop <- do.call(rbind, lapply(allpop.files, read.csv))
+allpop <- allpop %>% select(-X)
+rm(allpop.files)
 
-base <- read_output(out.path, 
-                    scenario = 'baseline', 
-                    var.list = var.list,
-                    verbose = TRUE)
-int25 <- read_output(out.path, 
-                      scenario = '25UniversalCredit', 
-                      var.list = var.list,
-                      verbose = TRUE)
-int30 <- read_output(out.path,
-                      scenario = '30UniversalCredit',
-                      var.list = var.list,
-                      verbose = TRUE)
-int35 <- read_output(out.path,
-                      scenario = '35UniversalCredit',
-                      var.list = var.list,
-                      verbose = TRUE)
-int40 <- read_output(out.path,
-                      scenario = '40UniversalCredit',
-                      var.list = var.list,
-                      verbose = TRUE)
-int45 <- read_output(out.path,
-                      scenario = '45UniversalCredit',
-                      var.list = var.list,
-                      verbose = TRUE)
-int50 <- read_output(out.path,
-                      scenario = '50UniversalCredit',
-                      var.list = var.list,
-                      verbose = TRUE)
+# Families with children
+families.files <- list.files(out.path,
+                           pattern = "*_families_summary.csv",
+                           full.names = TRUE)
+families <- do.call(rbind, lapply(families.files, read.csv))
+families <- families %>% select(-X)
+rm(families.files)
 
-#int.list <- c(int25, int30, int35, int40, int45, int50)
-int.list <- list(base, int25, int30, int35, int40, int45, int50)
-scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')
+# Treatment on Treated
+treated.files <- list.files(out.path,
+                           pattern = "*_treated_summary.csv",
+                           full.names = TRUE)
+treated <- do.call(rbind, lapply(treated.files, read.csv))
+treated <- treated %>% select(-X)
+rm(treated.files)
 
-# set up a boolean tag for batch or not
-# this is necessary because batch runs need slightly different processing before visualisation
-if ('run_id' %in% names(base)) {
-  batch <- TRUE
-} else {
-  batch <- FALSE
-}
+# SIMD Deciles
+simd_decile.files <- list.files(out.path,
+                           pattern = "*_simd_decile_summary.csv",
+                           full.names = TRUE)
+simd_decile <- do.call(rbind, lapply(simd_decile.files, read.csv))
+simd_decile <- simd_decile %>% select(-X)
+rm(simd_decile.files)
 
 # Save path and save flag
-save.path <- here::here('plots', 'SCOTGOV', 'CPR')
+save.path <- here::here('plots', 'SCOTGOV', 'SPC')
 create.if.not.exists(save.path)
@@
 
-# FUNCTIONS
+# SF12 Change
 
-```{r SF12_whole_pop, echo=FALSE}
-SF12.change.full.sample.single <- function(df.list, scen.list) {
-  single.mean <- function(data, scen) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, SF_12) %>%
-      group_by(time) %>%
-      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-
-  df.list <- mapply(single.mean, df.list, scen.list, SIMPLIFY = FALSE)
-
-  combined <- df.list %>%
-    reduce(full_join, by='time')
-
-  # List of intervention columns
-  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
-
-  # Create the new dataframe with differences
-  combined <- combined %>%
-    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
-    select(time, starts_with("diff")) %>%
-    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
-
-  combined <- combined %>%
-    pivot_longer(cols = starts_with('diff'),
-                 names_to = 'scen',
-                 values_to = 'diff')
-
-  #return(combined)
-
-  scen.list <- scen.list[-1]
-
-  #TODO: Rename factor levels
-  #correct factor levels for plot
-  # combined$scen <- factor(combined$scen,
-  #                         levels = scen.list)
-
-  #return(combined)
-
-  p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
-    geom_line() +
-    geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
-    xlab('Year') +
-    ylab('Difference')
-
-  print(p1)
-}
-
-SF12.change.full.sample.batch <- function(df.list, scen.list) {
-  batch.mean <- function(data, scen) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, run_id, SF_12) %>%
-      group_by(time, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-
-  # base <- batch.mean(base.dat, scen = 'base')
-  # int1 <- batch.mean(int.dat1, scen = 'int25')
-  # int2 <- batch.mean(int.dat2, scen = 'int50')
-  # int3 <- batch.mean(int.dat3, scen = 'int75')
-  # int4 <- batch.mean(int.dat4, scen = 'int100')
-
-  df.list <- mapply(single.mean, df.list, scen.list, SIMPLIFY = FALSE)
-
-  #df.list <- list(base, int1, int2, int3, int4)
-  combined <- df.list %>%
-    reduce(full_join, by=c('time', 'run_id'))
-
-  # combined$diff25 <- combined$int25.SF12 - combined$base.SF12
-  # combined$diff50 <- combined$int50.SF12 - combined$base.SF12
-  # combined$diff75 <- combined$int75.SF12 - combined$base.SF12
-  # combined$diff100 <- combined$int100.SF12 - combined$base.SF12
-
-  # List of intervention columns
-  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
-
-  # Create the new dataframe with differences
-  combined <- combined %>%
-    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
-    select(time, starts_with("diff")) %>%
-    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
-
-  combined <- combined %>%
-    pivot_longer(cols = starts_with('diff'),
-                 names_to = 'scen',
-                 values_to = 'diff')
-
-  # combined <- combined %>%
-  #   select(time, run_id, contains('diff')) %>%
-  #   pivot_longer(cols = diff25:diff100,
-  #                names_to = 'scen',
-  #                values_to = 'diff')
-
-  # TODO: Rename factor levels
-  # correct factor levels for plot
-  # combined$scen <- factor(combined$scen,
-  #                         levels = c('diff100', 'diff75', 'diff50', 'diff25'))
-
-  p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
-    geom_smooth() +
-    geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
-    xlab('Year') +
-    ylab('Difference')
-
-  print(p1)
-}
-```
-
-```{r SF12_families, echo=FALSE}
-SF12.change.families.single <- function(df.list, scen.list) {
-  single.mean <- function(data, scen) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, SF_12, nkids) %>%
-      filter(nkids > 0) %>%
-      group_by(time) %>%
-      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-
-  df.list <- mapply(single.mean, df.list, scen.list, SIMPLIFY = FALSE)
-
-  combined <- df.list %>%
-    reduce(full_join, by='time')
-
-  # List of intervention columns
-  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
-
-  # Create the new dataframe with differences
-  combined <- combined %>%
-    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
-    select(time, starts_with("diff")) %>%
-    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
-
-  combined <- combined %>%
-    pivot_longer(cols = starts_with('diff'),
-                 names_to = 'scen',
-                 values_to = 'diff')
-
-  p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
-    geom_line() +
-    geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12 MCS', subtitle = 'Households with Children') +
-    xlab('Year') +
-    ylab('Difference')
-
-  print(p1)
-}
-
-SF12.change.families.batch <- function(df.list, scen.list) {
-  batch.mean <- function(data, scen) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, run_id, SF_12, nkids) %>%
-      filter(nkids > 0) %>%
-      group_by(time, run_id) %>%
-      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-
-  df.list <- mapply(batch.mean, df.list, scen.list, SIMPLIFY = FALSE)
-
-  combined <- df.list %>%
-    reduce(full_join, by=c('time', 'run_id'))
-
-  # List of intervention columns
-  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
-
-  # Create the new dataframe with differences
-  combined <- combined %>%
-    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
-    select(time, starts_with("diff")) %>%
-    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
-
-  combined <- combined %>%
-    pivot_longer(cols = starts_with('diff'),
-                 names_to = 'scen',
-                 values_to = 'diff')
-
-  p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
-    geom_smooth() +
-    geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12 MCS', subtitle = 'Households with Children') +
-    xlab('Year') +
-    ylab('Difference')
-
-  print(p1)
-}
-```
-
-```{r SF12_treated, echo=FALSE}
-SF12.change.treated.single <- function(df.list, scen.list) {
-  single.mean <- function(data, scen, boosted) {
-    # define varname
-    newvar.name <- paste0(scen, '.SF12')
-    # prepare data
-    data <- data %>%
-      select(pidp, time, weight, SF_12) %>%
-      filter(pidp %in% boosted) %>%
-      group_by(time) %>%
-      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-
-  #TODO: FIX THIS! NEED DIFFERENT BASELINE FOR EACH INT?? THINK SO!
-  # NEED A FUNCTION TO DO THE DIFF CALCULATION AND ANOTHER TO RUN IT THROUGH
-  # EACH DF
-  # get boosted pidps
-  boosted <- df.list[[2]] %>%
-    select(pidp, income_boosted) %>%
-    filter(income_boosted == 'True')
-  rm(tmp)
-
-  df.list <- mapply(single.mean, df.list, scen.list, boosted, SIMPLIFY = FALSE)
-
-  combined <- df.list %>%
-    reduce(full_join, by='time')
-
-  # List of intervention columns
-  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
-
-  # Create the new dataframe with differences
-  combined <- combined %>%
-    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
-    select(time, starts_with("diff")) %>%
-    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
-
-  combined <- combined %>%
-    pivot_longer(cols = starts_with('diff'),
-                 names_to = 'scen',
-                 values_to = 'diff')
-
-  p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
-    geom_line() +
-    geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12 MCS', subtitle = 'Treated Population') +
-    xlab('Year') +
-    ylab('Difference')
-
-  print(p1)
-}
-
-SF12.change.treated.batch <- function(df.list, scen.list) {
-  batch.mean <- function(data, scen, boosted) {
-    # define varname
-    newvar.name <- paste0(scen, '.SF12')
-    # prepare data
-    data <- data %>%
-      select(pidp, time, weight, run_id, SF_12) %>%
-      filter(pidp %in% boosted) %>%
-      group_by(time, run_id) %>%
-      summarise(!!newvar.name := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-
-  #TODO: FIX THIS! NEED DIFFERENT BASELINE FOR EACH INT?? THINK SO!
-  # NEED A FUNCTION TO DO THE DIFF CALCULATION AND ANOTHER TO RUN IT THROUGH
-  # EACH DF
-  # get boosted pidps
-  boosted <- df.list[[2]] %>%
-    select(pidp, income_boosted) %>%
-    filter(income_boosted == 'True')
-
-  df.list <- mapply(single.mean, df.list, scen.list, boosted, SIMPLIFY = FALSE)
-
-  combined <- df.list %>%
-    reduce(full_join, by=c('time', 'run_id'))
-
-  # List of intervention columns
-  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
-
-  # Create the new dataframe with differences
-  combined <- combined %>%
-    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
-    select(time, starts_with("diff")) %>%
-    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
-
-  combined <- combined %>%
-    pivot_longer(cols = starts_with('diff'),
-                 names_to = 'scen',
-                 values_to = 'diff')
-
-  p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
-    geom_smooth() +
-    geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12 MCS', subtitle = 'Treated Population') +
-    xlab('Year') +
-    ylab('Difference')
-
-  print(p1)
-}
-```
-
-```{r SF12_deciles, echo=FALSE}
-SF12.by.simd.deciles <- function(df.list, scen.list, start.year = 2020, batch=FALSE) {
-  single.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, simd_decile, SF_12) %>%
-      filter(time >= start.year) %>%
-      group_by(time, simd_decile) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-  batch.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, simd_decile, run_id, SF_12) %>%
-      filter(time >= start.year) %>%
-      group_by(time, simd_decile, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-
-  if (batch) {
-    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time', 'simd_decile', 'run_id'))
-  } else {
-    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time', 'simd_decile'))
-  }
-
-  combined$simd_decile <- as.factor(combined$simd_decile)
-
-  int.labels <- scen.list[-1]
-
-  for (int in int.labels) {
-    int.name <- paste0(int, '.SF12')
-    if (batch) {
-      p1 <- ggplot(combined, aes(x = time, group = simd_decile, colour = simd_decile)) +
-        geom_smooth(aes(y = base.SF12)) +
-        geom_smooth(aes(y = .data[[int.name]]), linetype='dashed') +
-        labs(title = 'SF12 MCS Deciles', subtitle = paste0('Baseline vs ', int)) +
-        xlab('Year') +
-        ylab('Difference')
-    } else {
-      p1 <- ggplot(combined, aes(x = time, group = simd_decile, colour = simd_decile)) +
-        geom_line(aes(y = base.SF12)) +
-        geom_line(aes(y = .data[[int.name]]), linetype='dashed') +
-        labs(title = 'SF12 MCS Deciles', subtitle = int) +
-        xlab('Year') +
-        ylab('Difference')
-    }
-    print(p1)
-  }
-}
-```
-
-```{r SF_change_deciles, echo=FALSE}
-SF12.change.by.deciles <- function(df.list, scen.list, start.year = 2020, batch = FALSE) {
-  single.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, simd_decile, SF_12) %>%
-      filter(time >= start.year) %>%
-      group_by(time, simd_decile) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-  batch.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, simd_decile, run_id, SF_12) %>%
-      filter(time >= start.year) %>%
-      group_by(time, simd_decile, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-
-  if (batch) {
-    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time', 'simd_decile', 'run_id'))
-  } else {
-    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time', 'simd_decile'))
-  }
-
-  combined$simd_decile <- as.factor(combined$simd_decile)
-
-  # List of intervention columns
-  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
-
-  # Create the new dataframe with differences
-  combined <- combined %>%
-    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
-    select(time, simd_decile, starts_with("diff")) %>%
-    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
-
-  combined <- combined %>%
-    pivot_longer(cols = starts_with('diff'),
-                 names_to = 'scen',
-                 values_to = 'diff')
-
-  if (batch) {
-    p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
-      geom_smooth() +
-      geom_hline(yintercept = 0, linetype='dashed') +
-      facet_wrap(. ~ scen, ncol=1) +
-      labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
-      xlab('Year') +
-      ylab('Difference')
-  } else {
-    p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
-      geom_line() +
-      geom_hline(yintercept = 0, linetype='dashed') +
-      facet_wrap(. ~ scen, ncol=1) +
-      labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
-      xlab('Year') +
-      ylab('Difference')
-  }
-
-  ggsave(filename = 'test_plot.png',
-         plot = p1,
-         path = here::here('plots', 'SCOTGOVWORK'),
-         width = 9,
-         height = 20)
-
-  print(p1)
-}
-```
-
-# PLOTS
-
-## MCS - Whole Population
+## Whole Pop
 
 ```{r}
-if (batch) {
-  SF12.change.full.sample.batch(int.list, scen.list)
-} else {
-  SF12.change.full.sample.single(int.list, scen.list)
-}
-```
+allpop.plot <- allpop %>%
+  select(run_id, time, scenario, SF_12) %>%
+  pivot_wider(names_from = scenario,
+              values_from = SF_12) %>%
+  mutate(across(ends_with("UniversalCredit"), ~ . - baseline, .names = "diff_{col}")) %>%
+  select(run_id, time, starts_with('diff_')) %>%
+  pivot_longer(cols = starts_with('diff_'),
+               names_to = 'Intervention',
+               names_prefix = 'diff_',
+               values_to = 'SF_12_change')
 
-## MCS - Households with Children
-
-```{r}
-if (batch) {
-  SF12.change.families.batch(int.list, scen.list)
-} else {
-  SF12.change.families.single(int.list, scen.list)
-}
-```
-
-## MCS - Treatment on Treated
-
-```{r}
-if (batch) {
-  SF12.change.treated.batch(int.list, scen.list)
-} else {
-  SF12.change.treated.single(int.list, scen.list)
-}
-```
-
-## MCS - DECILES
-
-```{r}
-SF12.by.simd.deciles(int.list, scen.list, batch = batch)
-```
-
-```{r}
-SF12.by.simd.deciles(int.list, scen.list, start.year = 2024, batch = batch)
-```
-
-## MCS - CHANGE BY DECILES
-
-```{r}
-SF12.change.by.deciles(int.list, scen.list, batch = batch)
-```
-
-## MCS - PRIORITY GROUPS
-
-### All Priority Subgroups
-
-```{r}
+ggplot(allpop.plot, aes(x = time, y = SF_12_change, group = Intervention, colour = Intervention)) +
+  geom_smooth() +
+  geom_hline(yintercept = 0, linetype = 'dashed')
 
@@
 
-### Minority Ethnic Groups
+## Families
 
 ```{r}
-priority_filter_ethnicity <- function(df.list, scen.list, start.year) {
-  single.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, ethnicity, SF_12) %>%
-      filter(ethnicity != 'WBI') %>%
-      group_by(time) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-  batch.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, ethnicity, run_id, SF_12) %>%
-      filter(ethnicity != 'WBI') %>%
-      group_by(time, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
+fam.plot <- families %>%
+  select(run_id, time, scenario, SF_12) %>%
+  pivot_wider(names_from = scenario,
+              values_from = SF_12) %>%
+  mutate(across(ends_with("UniversalCredit"), ~ . - baseline, .names = "diff_{col}")) %>%
+  select(run_id, time, starts_with('diff_')) %>%
+  pivot_longer(cols = starts_with('diff_'),
+               names_to = 'Intervention',
+               names_prefix = 'diff_',
+               values_to = 'SF_12_change')
 
-  if (batch) {
-    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time', 'run_id'))
-  } else {
-    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time'))
-  }
-  return(combined)
-}
-
-priority_filter_child_under_one <- function(df.list, scen.list, start.year) {
-  single.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, child_ages, SF_12) %>%
-      filter(substr(child_ages, 1, 1) == 0) %>%
-      group_by(time) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-  batch.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, child_ages, run_id, SF_12) %>%
-      filter(substr(child_ages, 1, 1) == 0) %>%
-      group_by(time, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-
-  if (batch) {
-    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time', 'run_id'))
-  } else {
-    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time'))
-  }
-  return(combined)
-}
-
-priority_filter_three_plus_children <- function(df.list, scen.list, start.year) {
-  single.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, nkids, SF_12) %>%
-      filter(nkids >= 3) %>%
-      group_by(time) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-  batch.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, nkids, run_id, SF_12) %>%
-      filter(nkids >= 3) %>%
-      group_by(time, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-
-  if (batch) {
-    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time', 'run_id'))
-  } else {
-    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time'))
-  }
-  return(combined)
-}
-
-priority_filter_mother_under_25 <- function(df.list, scen.list, start.year) {
-  single.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, age, nkids_ind, SF_12) %>%
-      filter(nkids_ind > 0 & age < 25) %>%
-      group_by(time) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-  batch.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, weight, age, nkids_ind, run_id, SF_12) %>%
-      filter((nkids_ind > 0) && (age < 25)) %>%
-      group_by(time, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-
-  if (batch) {
-    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time', 'run_id'))
-  } else {
-    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time'))
-  }
-  return(combined)
-}
-
-priority_filter_disabled <- function(df.list, scen.list, start.year) {
-  single.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, hidp, weight, S7_labour_state, SF_12) %>%
-      group_by(hidp) %>%
-      mutate(disabled_flag = ifelse(any(S7_labour_state) == 'disabled')) %>%
-      filter(disabled_flag == TRUE) %>%
-      group_by(time) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-  batch.mean <- function(data, scen, start.year) {
-    newvar.name <- paste0(scen, '.SF12')
-    data <- data %>%
-      select(time, hidp, weight, S7_labour_state, run_id, SF_12) %>%
-      group_by(hidp) %>%
-      mutate(disabled_flag = ifelse(any(S7_labour_state) == 'disabled')) %>%
-      filter(disabled_flag == TRUE) %>%
-      group_by(time, run_id) %>%
-      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
-    return(data)
-  }
-
-  if (batch) {
-    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time', 'run_id'))
-  } else {
-    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
-    combined <- mod.list %>%
-      reduce(full_join, by=c('time'))
-  }
-  return(combined)
-}
-
-SF12.change.priority.group <- function(df.list, scen.list, priority.group, start.year = 2020, batch=FALSE) {
-
-  # Filter data for priority groups
-  if (priority.group == 'minority_ethnic') { combined <- priority_filter_ethnicity(df.list, scen.list, start.year) }
-  if (priority.group == 'child_under_one') { combined <- priority_filter_child_under_one(df.list, scen.list, start.year) }
-  if (priority.group == 'three_plus_children') { combined <- priority_filter_three_plus_children(df.list, scen.list, start.year) }
-  if (priority.group == 'mother_under_25') { combined <- priority_filter_mother_under_25(df.list, scen.list, start.year) }
-  if (priority.group == 'disabled') { combined <- priority_filter_disabled(df.list, scen.list, start.year) }
-
-  # List of intervention columns
-  int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
-
-  # Create the new dataframe with differences
-  combined <- combined %>%
-    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
-    select(time, starts_with("diff")) %>%
-    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))
-
-  combined <- combined %>%
-    pivot_longer(cols = starts_with('diff'),
-                 names_to = 'scen',
-                 values_to = 'diff')
-
-  if (batch) {
-    p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
+ggplot(fam.plot, aes(x = time, y = SF_12_change, group = Intervention, colour = Intervention)) +
   geom_smooth() +
-      geom_hline(yintercept = 0, linetype='dashed') +
-      labs(title = paste0('SF12 MCS Change - ', priority.group)) +
-      xlab('Year') +
-      ylab('Difference')
-  } else {
-    p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) +
-      geom_line() +
-      geom_hline(yintercept = 0, linetype='dashed') +
-      labs(title = paste0('SF12 MCS Change - ', priority.group)) +
-      xlab('Year') +
-      ylab('Difference')
-  }
-
-  print(p1)
-}
-
-batch <- FALSE
-start.year <- 2020
-
-SF12.change.priority.group(int.list, scen.list, priority.group = 'minority_ethnic', batch = batch)
-SF12.change.priority.group(int.list, scen.list, priority.group = 'child_under_one', batch = batch)
-SF12.change.priority.group(int.list, scen.list, priority.group = 'three_plus_children', batch = batch)
-SF12.change.priority.group(int.list, scen.list, priority.group = 'mother_under_25', batch = batch)
-#SF12.change.priority.group(int.list, scen.list, priority.group = 'disabled', batch = batch)
+  geom_hline(yintercept = 0, linetype = 'dashed')
 
@@
 
-# Poverty Statistics
-
-See how interventions affect child poverty.
-
-## Relative Poverty
+## Treated
 
 ```{r}
-# First need the relative poverty thresholds from baseline
-threshold <- base %>%
-  select(time, weight, hh_income) %>%
-  group_by(time) %>%
-  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
+treated.plot <- treated %>%
+  select(run_id, time, scenario, SF_12) %>%
+  pivot_wider(names_from = scenario,
+              values_from = SF_12) %>%
+  mutate(across(ends_with("UniversalCredit"), ~ . - baseline, .names = "diff_{col}")) %>%
+  select(run_id, time, starts_with('diff_')) %>%
+  pivot_longer(cols = starts_with('diff_'),
+               names_to = 'Intervention',
+               names_prefix = 'diff_',
+               values_to = 'SF_12_change')
 
-ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
-  geom_col() +
-  labs(title = 'Relative poverty threshold over time') +
-  xlab('Year') +
-  ylab('Threshold')
+ggplot(treated.plot, aes(x = time, y = SF_12_change, group = Intervention, colour = Intervention)) +
+  geom_smooth() +
+  geom_hline(yintercept = 0, linetype = 'dashed')
+
 ```
 
+## SIMD Deciles
+
 ```{r}
-int25.test <- merge(int25, threshold, by = 'time')
-# Now calculate number of households and number of children below threshold
-hh_boosted <- int25.test %>%
-  select(hidp, time, hh_income, income_boosted, boost_amount, nkids, poverty_threshold) %>%
-  filter(income_boosted == 'True') %>%
-  filter(hh_income < poverty_threshold) %>%
-  group_by(time) %>%
-  summarise(n = n(),
-            n_boosted = length(unique(hidp)),
-            total_boost = sum(boost_amount),
-            kids_boosted = sum(nkids)) %>%
-  mutate(prop_boosted = n_boosted / n,
-         prop_kids_boosted)
+simd_decile.plot <- simd_decile %>%
+  select(run_id, time, scenario, simd_decile, SF_12) %>%
+  pivot_wider(names_from = scenario,
+              values_from = SF_12) %>%
+  mutate(across(ends_with("UniversalCredit"), ~ . - baseline, .names = "diff_{col}")) %>%
+  select(run_id, time, simd_decile, starts_with('diff_')) %>%
+  pivot_longer(cols = starts_with('diff_'),
+               names_to = 'Intervention',
+               names_prefix = 'diff_',
+               values_to = 'SF_12_change')
+simd_decile.plot$simd_decile <- as.factor(simd_decile.plot$simd_decile)
 
-p1 <- ggplot(hh_boosted, aes(x = time, y = n_boosted)) +
-  geom_line() +
-  labs(title = 'Number of households receiving intervention', subtitle = int.name) +
-  xlab('Year') +
-  ylab('Number Boosted')
-print(p1)
+# for (i in 1:10) {
+#   p1 <- ggplot(filter(simd_decile.plot, simd_decile == i), aes(x = time, y = SF_12_change, group = Intervention, colour = Intervention)) +
+#     geom_smooth() +
+#     geom_hline(yintercept = 0, linetype = 'dashed') +
+#     labs(title = 'SF_12 Change', subtitle = paste0('SIMD Decile ', i))
+#   print(p1)
+# }
 
-p2 <- ggplot(hh_boosted, aes(x = time, y = kids_boosted)) +
-  geom_line() +
-  labs(title = 'Number of children in households receiving intervention', subtitle = int.name) +
-  xlab('Year') +
-  ylab('Number Children')
+p2 <- ggplot(simd_decile.plot, aes(x = time, y = SF_12_change, group = Intervention, colour = Intervention)) +
+  geom_smooth() +
+  geom_hline(yintercept = 0, linetype = 'dashed') +
+  facet_wrap(. ~ simd_decile) +
+  labs(title = 'SF_12 Change', subtitle = 'By Decile')
 print(p2)
+
+p3 <- ggplot(simd_decile.plot, aes(x = time, y = SF_12_change, group = simd_decile, colour = simd_decile)) +
+  geom_smooth() +
+  geom_hline(yintercept = 0, linetype = 'dashed') +
+  facet_wrap(. ~ Intervention) +
+  labs(title = 'SF_12 Change All Deciles', subtitle = 'By Intervention')
+print(p3)
 ```
 
-# DIAGNOSTICS
+<!-- # MCS - PRIORITY GROUPS -->
 
-```{r}
-intervention_information_single <- function(int.dat, int.name, target.year) {
-  hh_boosted <- int.dat %>%
-    select(hidp, time, income_boosted, boost_amount, nkids) %>%
-    filter(income_boosted == 'True') %>%
-    group_by(time) %>%
-    summarise(n_boosted = length(unique(hidp)),
-              total_boost = sum(boost_amount),
-              kids_boosted = sum(nkids))
+<!-- ## All Priority Subgroups -->
 
-  p1 <- ggplot(hh_boosted, aes(x = time, y = n_boosted)) +
-    geom_line() +
-    geom_vline(xintercept = target.year, linetype = 'dashed') +
-    labs(title = 'Number of households receiving intervention', subtitle = int.name) +
-    xlab('Year') +
-    ylab('Number Boosted')
+<!-- ```{r} -->
 
-  p2 <- ggplot(hh_boosted, aes(x = time, y = kids_boosted)) +
-    geom_line() +
-    geom_vline(xintercept = target.year, linetype = 'dashed') +
-    labs(title = 'Number of children in households receiving intervention', subtitle = int.name) +
-    xlab('Year') +
-    ylab('Number Children')
+<!-- ``` -->
 
-  p3 <- ggplot(hh_boosted, aes(x = time, y = total_boost)) +
-    geom_line() +
-    geom_vline(xintercept = target.year, linetype = 'dashed') +
-    labs(title = 'Total boost amount', subtitle = int.name) +
-    xlab('Year') +
-    ylab('Boost Amount')
+<!-- ## Minority Ethnic Groups -->
 
-  mean.boost <- int.dat %>%
-    select(time, income_boosted, boost_amount) %>%
-    group_by(time, income_boosted) %>%
-    summarise(mean_boost = mean(boost_amount)) %>%
-    filter(income_boosted == 'True')
+<!-- ```{r} -->
+<!-- priority_filter_ethnicity <- function(df.list, scen.list, start.year) { -->
+<!--   single.mean <- function(data, scen, start.year) { -->
+<!--     newvar.name <- paste0(scen, '.SF12') -->
+<!--     data <- data %>% -->
+<!--       select(time, ethnicity, SF_12) %>% -->
+<!--       filter(ethnicity != 'WBI') %>% -->
+<!--       filter(SF_12 >= 0) %>% -->
+<!--       group_by(time) %>% -->
+<!--       summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE)) -->
+<!--     return(data) -->
+<!--   } -->
+<!--   batch.mean <- function(data, scen, start.year) { -->
+<!--     newvar.name <- paste0(scen, '.SF12') -->
+<!--     data <- data %>% -->
+<!--       select(time, ethnicity, run_id, SF_12) %>% -->
+<!--       filter(ethnicity != 'WBI') %>% -->
+<!--       filter(SF_12 >= 0) %>% -->
+<!--       group_by(time, run_id) %>% -->
+<!--       summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE)) -->
+<!--     return(data) -->
+<!--   } -->
 
-  p4 <- ggplot(mean.boost, aes(x = time, y = mean_boost)) +
-    geom_line() +
-    geom_vline(xintercept = target.year, linetype = 'dashed') +
-    labs(title = 'Mean boost amount', subtitle = int.name) +
-    xlab('Year') +
-    ylab('Boost Amount')
+<!--   if (batch) { -->
+<!--     mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE) -->
+<!--     combined <- mod.list %>% -->
+<!--       reduce(full_join, by=c('time', 'run_id')) -->
+<!--   } else { -->
+<!--     mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE) -->
+<!--     combined <- mod.list %>% -->
+<!--       reduce(full_join, by=c('time')) -->
+<!--   } -->
+<!--   return(combined) -->
+<!-- } -->
 
-  print(p1)
-  print(p2)
-  print(p3)
-  print(p4)
-}
+<!-- priority_filter_child_under_one <- function(df.list, scen.list, start.year) { -->
+<!--   single.mean <- function(data, scen, start.year) { -->
+<!--     newvar.name <- paste0(scen, '.SF12') -->
+<!--     data <- data %>% -->
+<!--       select(time, child_under_one, SF_12) %>% -->
+<!--       filter(child_under_one == TRUE) %>% -->
+<!--       filter(SF_12 >= 0) %>% -->
+<!--       group_by(time) %>% -->
+<!--       summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE)) -->
+<!--     return(data) -->
+<!--   } -->
+<!--   batch.mean <- function(data, scen, start.year) { -->
+<!--     newvar.name <- paste0(scen, '.SF12') -->
+<!--     data <- data %>% -->
+<!--       select(time, child_under_one, run_id, SF_12) %>% -->
+<!--       filter(child_under_one == TRUE) %>% -->
+<!--       filter(SF_12 >= 0) %>% -->
+<!--       group_by(time, run_id) %>% -->
+<!--       summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE)) -->
+<!--     return(data) -->
+<!--   } -->
 
-intervention_information_batch <- function(int.dat, int.name, target.year) {
-  hh_boosted <- int.dat %>%
-    select(hidp, time, run_id, income_boosted, boost_amount, nkids) %>%
-    filter(income_boosted == 'True') %>%
-    group_by(time, run_id) %>%
-    summarise(n_boosted = length(unique(hidp)),
-              total_boost = sum(boost_amount),
-              kids_boosted = sum(nkids))
+<!--   if (batch) { -->
+<!--     mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE) -->
+<!--     combined <- mod.list %>% -->
+<!--       reduce(full_join, by=c('time', 'run_id')) -->
+<!--   } else { -->
+<!--     mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE) -->
+<!--     combined <- mod.list %>% -->
+<!--       reduce(full_join, by=c('time')) -->
+<!--   } -->
+<!--   return(combined) -->
+<!-- } -->
 
-  p1 <- ggplot(hh_boosted, aes(x = time, y = n_boosted)) +
-    geom_smooth() +
-    geom_vline(xintercept = target.year, linetype = 'dashed') +
-    labs(title = 'Number of households receiving intervention', subtitle = int.name) +
-    xlab('Year') +
-    ylab('Number Boosted')
+<!-- priority_filter_three_plus_children <- function(df.list, scen.list, start.year) { -->
+<!--   single.mean <- function(data, scen, start.year) { -->
+<!--     newvar.name <- paste0(scen, '.SF12') -->
+<!--     data <- data %>% -->
+<!--       select(time, three_plus_child, SF_12) %>% -->
+<!--       filter(three_plus_child == TRUE) %>% -->
+<!--       filter(SF_12 >= 0) %>% -->
+<!--       group_by(time) %>% -->
+<!--       summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE)) -->
+<!--     return(data) -->
+<!--   } -->
+<!--   batch.mean <- function(data, scen, start.year) { -->
+<!--     newvar.name <- paste0(scen, '.SF12') -->
+<!--     data <- data %>% -->
+<!--       select(time, three_plus_child, run_id, SF_12) %>% -->
+<!--       filter(three_plus_child) %>% -->
+<!--       filter(SF_12 >= 0) %>% -->
+<!--       group_by(time, run_id) %>% -->
+<!--       summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE)) -->
+<!--     return(data) -->
+<!--   } -->
 
-  p2 <- ggplot(hh_boosted, aes(x = time, y = kids_boosted)) +
-    geom_smooth() +
-    geom_vline(xintercept = target.year, linetype = 'dashed') +
-    labs(title = 'Number of children in households receiving intervention', subtitle = int.name) +
-    xlab('Year') +
-    ylab('Number Children')
+<!--   if (batch) { -->
+<!--     mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE) -->
+<!--     combined <- mod.list %>% -->
+<!--       reduce(full_join, by=c('time', 'run_id')) -->
+<!--   } else { -->
+<!--     mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE) -->
+<!--     combined <- mod.list %>% -->
+<!--       reduce(full_join, by=c('time')) -->
+<!--   } -->
+<!--   return(combined) -->
+<!-- } -->
 
-  p3 <- ggplot(hh_boosted, aes(x = time, y = total_boost)) +
-    geom_smooth() +
-    geom_vline(xintercept = target.year, linetype = 'dashed') +
-    labs(title = 'Total boost amount', subtitle = int.name) +
-    xlab('Year') +
-    ylab('Boost Amount')
+<!-- priority_filter_mother_under_25 <- function(df.list, scen.list, start.year) { -->
+<!--   single.mean <- function(data, scen, start.year) { -->
+<!--     newvar.name <- paste0(scen, '.SF12') -->
+<!--     data <- data %>% -->
+<!--       select(time, mother_under_25, SF_12) %>% -->
+<!--       filter(mother_under_25 == TRUE) %>% -->
+<!--       filter(SF_12 >= 0) %>% -->
+<!--       group_by(time) %>% -->
+<!--       summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE)) -->
+<!--     return(data) -->
+<!--   } -->
+<!--   batch.mean <- function(data, scen, start.year) { -->
+<!--     newvar.name <- paste0(scen, '.SF12') -->
+<!--     data <- data %>% -->
+<!--       select(time, mother_under_25, run_id, SF_12) %>% -->
+<!--       filter(mother_under_25 == TRUE) %>% -->
+<!--       filter(SF_12 >= 0) %>% -->
+<!--       group_by(time, run_id) %>% -->
+<!--       summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE)) -->
+<!--     return(data) -->
+<!--   } -->
 
-  mean.boost <- int.dat %>%
-    select(time, income_boosted, boost_amount) %>%
-    group_by(time, run_id, income_boosted) %>%
-    summarise(mean_boost = mean(boost_amount)) %>%
-    filter(income_boosted == 'True')
+<!--   if (batch) { -->
+<!--     mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE) -->
+<!--     combined <- mod.list %>% -->
+<!--       reduce(full_join, by=c('time', 'run_id')) -->
+<!--   } else { -->
+<!--     mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE) -->
+<!--     combined <- mod.list %>% -->
+<!--       reduce(full_join, by=c('time')) -->
+<!--   } -->
+<!--   return(combined) -->
+<!-- } -->
 
-  p4 <- ggplot(mean.boost, aes(x = time, y = mean_boost)) +
-    geom_smooth() +
-    geom_vline(xintercept = target.year, linetype = 'dashed') +
-    labs(title = 'Mean boost amount', subtitle = int.name) +
-    xlab('Year') +
-    ylab('Boost Amount')
+<!-- priority_filter_disabled <- function(df.list, scen.list, start.year) { -->
+<!--   single.mean <- function(data, scen, start.year) { -->
+<!--     newvar.name <- paste0(scen, '.SF12') -->
+<!--     data <- data %>% -->
+<!--       select(time, hidp, S7_labour_state, SF_12) %>% -->
+<!--       group_by(hidp) %>% -->
+<!--       mutate(disabled_flag = ifelse(any(S7_labour_state) == 'disabled')) %>% -->
+<!--       filter(disabled_flag == TRUE) %>% -->
+<!--       group_by(time) %>% -->
+<!--       summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE)) -->
+<!--     return(data) -->
+<!--   } -->
+<!--   batch.mean <- function(data, scen, start.year) { -->
+<!--     newvar.name <- paste0(scen, '.SF12') -->
+<!--     data <- data %>% -->
+<!--       select(time, hidp, S7_labour_state, run_id, SF_12) %>% -->
+<!--       group_by(hidp) %>% -->
+<!--       mutate(disabled_flag = ifelse(any(S7_labour_state) == 'disabled')) %>% -->
+<!--       filter(disabled_flag == TRUE) %>% -->
+<!--       group_by(time, run_id) %>% -->
+<!--       summarise(!!sym(newvar.name) := mean(SF_12, na.rm = TRUE)) -->
+<!--     return(data) -->
+<!--   } -->
 
-  print(p1)
-  print(p2)
-  print(p3)
-  print(p4)
-}
-```
+<!--   if (batch) { -->
+<!--     mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE) -->
+<!--     combined <- mod.list %>% -->
+<!--       reduce(full_join, by=c('time', 'run_id')) -->
+<!--   } else { -->
+<!--     mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE) -->
+<!--     combined <- mod.list %>% -->
+<!--       reduce(full_join, by=c('time')) -->
+<!--   } -->
+<!--   return(combined) -->
+<!-- } -->
 
-## 25
+<!-- SF12.change.priority.group <- function(df.list, scen.list, priority.group, start.year = 2020, batch=FALSE) { -->
 
-```{r}
-if (batch) {
-  intervention_information_batch(int25, int.name = 'int25', target.year = 2030)
-} else {
-  intervention_information_single(int25, int.name = 'int25', target.year = 2030)
-}
-```
+<!--   # Filter data for priority groups -->
+<!--   if (priority.group == 'minority_ethnic') { combined <- priority_filter_ethnicity(df.list, scen.list, start.year) } -->
+<!--   if (priority.group == 'child_under_one') { combined <- priority_filter_child_under_one(df.list, scen.list, start.year) } -->
+<!--   if (priority.group == 'three_plus_children') { combined <- priority_filter_three_plus_children(df.list, scen.list, start.year) } -->
+<!--   if (priority.group == 'mother_under_25') { combined <- priority_filter_mother_under_25(df.list, scen.list, start.year) } -->
+<!--   if (priority.group == 'disabled') { combined <- priority_filter_disabled(df.list, scen.list, start.year) } -->
 
-## 30
+<!--   # List of intervention columns -->
+<!--   int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE) -->
 
-```{r}
-if (batch) {
-  intervention_information_batch(int30, int.name = 'int30', target.year = 2030)
-} else {
-  intervention_information_single(int30, int.name = 'int30', target.year = 2030)
-}
-```
+<!--   # Create the new dataframe with differences -->
+<!--   combined <- combined %>% -->
+<!--     mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>% -->
+<!--     select(time, starts_with("diff")) %>% -->
+<!--     rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1")) -->
 
-## 35
+<!--   combined <- combined %>% -->
+<!--     pivot_longer(cols = starts_with('diff'), -->
+<!--                  names_to = 'scen', -->
+<!--                  values_to = 'diff') -->
 
-```{r}
-if (batch) {
-  intervention_information_batch(int35, int.name = 'int35', target.year = 2030)
-} else {
-  intervention_information_single(int35, int.name = 'int35', target.year = 2030)
-}
-```
+<!--   if (batch) { -->
+<!--     p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) + -->
+<!--       geom_smooth() + -->
+<!--       geom_hline(yintercept = 0, linetype='dashed') + -->
+<!--       labs(title = paste0('SF12 MCS Change - ', priority.group)) + -->
+<!--       xlab('Year') + -->
+<!--       ylab('Difference') -->
+<!--   } else { -->
+<!--     p1 <- ggplot(combined, aes(x = time, y = diff, group = scen, colour = scen)) + -->
+<!--       geom_line() + -->
+<!--       geom_hline(yintercept = 0, linetype='dashed') + -->
+<!--       labs(title = paste0('SF12 MCS Change - ', priority.group)) + -->
+<!--       xlab('Year') + -->
+<!--       ylab('Difference') -->
+<!--   } -->
 
-## 40
+<!--   print(p1) -->
+<!-- } -->
 
-```{r}
-if (batch) {
-  intervention_information_batch(int40, int.name = 'int40', target.year = 2030)
-} else {
-  intervention_information_single(int40, int.name = 'int40', target.year = 2030)
-}
-```
+<!-- batch <- FALSE -->
+<!-- start.year <- 2020 -->
 
-## 45
+<!-- SF12.change.priority.group(int.list, scen.list, priority.group = 'minority_ethnic', batch = batch) -->
+<!-- SF12.change.priority.group(int.list, scen.list, priority.group = 'child_under_one', batch = batch) -->
+<!-- SF12.change.priority.group(int.list, scen.list, priority.group = 'three_plus_children', batch = batch) -->
+<!-- SF12.change.priority.group(int.list, scen.list, priority.group = 'mother_under_25', batch = batch) -->
+<!-- #SF12.change.priority.group(int.list, scen.list, priority.group = 'disabled', batch = batch) -->
 
-```{r}
-if (batch) {
-  intervention_information_batch(int45, int.name = 'int45', target.year = 2030)
-} else {
-  intervention_information_single(int45, int.name = 'int45', target.year = 2030)
-}
-```
+<!-- ``` -->
 
-## 50
+<!-- # Poverty Statistics -->
 
-```{r}
-if (batch) {
-  intervention_information_batch(int50, int.name = 'int50', target.year = 2030)
-} else {
-  intervention_information_single(int50, int.name = 'int50', target.year = 2030)
-}
-```
+<!-- See how interventions affect child poverty. -->
 
-# TESTING
+<!-- ## Relative Poverty -->
 
-```{r}
-```
+<!-- ```{r} -->
+<!-- # First need the relative poverty thresholds from baseline -->
+<!-- threshold <- base %>% -->
+<!--   select(time, hh_income) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(poverty_threshold = (mean(hh_income, na.rm = TRUE) * 0.6)) -->
+
+<!-- ggplot(data = threshold, aes(x = time, y = poverty_threshold)) + -->
+<!--   geom_col() + -->
+<!--   labs(title = 'Relative poverty threshold over time') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Threshold') -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- int25.test <- merge(int25, threshold, by = 'time') -->
+<!-- # Now calculate number of households and number of children below threshold -->
+<!-- hh_boosted <- int25.test %>% -->
+<!--   select(hidp, time, hh_income, income_boosted, boost_amount, nkids, poverty_threshold) %>% -->
+<!--   filter(income_boosted == 'True') %>% -->
+<!--   filter(hh_income < poverty_threshold) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(n = n(), -->
+<!--             n_boosted = length(unique(hidp)), -->
+<!--             total_boost = sum(boost_amount), -->
+<!--             kids_boosted = sum(nkids)) %>% -->
+<!--   mutate(prop_boosted = n_boosted / n) -->
+
+<!-- p1 <- ggplot(hh_boosted, aes(x = time, y = n_boosted)) + -->
+<!--   geom_line() + -->
+<!--   labs(title = 'Number of households receiving intervention') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Number Boosted') -->
+<!-- print(p1) -->
+
+<!-- p2 <- ggplot(hh_boosted, aes(x = time, y = kids_boosted)) + -->
+<!--   geom_line() + -->
+<!--   labs(title = 'Number of children in households receiving intervention') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Number Children') -->
+<!-- print(p2) -->
+<!-- ``` -->
+
+<!-- # DIAGNOSTICS -->
+
+<!-- ```{r} -->
+<!-- intervention_information_single <- function(int.dat, int.name, target.year) { -->
+<!--   hh_boosted <- int.dat %>% -->
+<!--     select(hidp, time, income_boosted, boost_amount, nkids) %>% -->
+<!--     filter(income_boosted == 'True') %>% -->
+<!--     group_by(time) %>% -->
+<!--     summarise(n_boosted = length(unique(hidp)), -->
+<!--               total_boost = sum(boost_amount), -->
+<!--               kids_boosted = sum(nkids)) -->
+
+<!--   p1 <- ggplot(hh_boosted, aes(x = time, y = n_boosted)) + -->
+<!--     geom_line() + -->
+<!--     geom_vline(xintercept = target.year, linetype = 'dashed') + -->
+<!--     labs(title = 'Number of households receiving intervention', subtitle = int.name) + -->
+<!--     xlab('Year') + -->
+<!--     ylab('Number Boosted') -->
+
+<!--   p2 <- ggplot(hh_boosted, aes(x = time, y = kids_boosted)) + -->
+<!--     geom_line() + -->
+<!--     geom_vline(xintercept = target.year, linetype = 'dashed') + -->
+<!--     labs(title = 'Number of children in households receiving intervention', subtitle = int.name) + -->
+<!--     xlab('Year') + -->
+<!--     ylab('Number Children') -->
+
+<!--   p3 <- ggplot(hh_boosted, aes(x = time, y = total_boost)) + -->
+<!--     geom_line() + -->
+<!--     geom_vline(xintercept = target.year, linetype = 'dashed') + -->
+<!--     labs(title = 'Total boost amount', subtitle = int.name) + -->
+<!--     xlab('Year') + -->
+<!--     ylab('Boost Amount') -->
+
+<!--   mean.boost <- int.dat %>% -->
+<!--     select(time, income_boosted, boost_amount) %>% -->
+<!--     group_by(time, income_boosted) %>% -->
+<!--     summarise(mean_boost = mean(boost_amount)) %>% -->
+<!--     filter(income_boosted == 'True') -->
+
+<!--   p4 <- ggplot(mean.boost, aes(x = time, y = mean_boost)) + -->
+<!--     geom_line() + -->
+<!--     geom_vline(xintercept = target.year, linetype = 'dashed') + -->
+<!--     labs(title = 'Mean boost amount', subtitle = int.name) + -->
+<!--     xlab('Year') + -->
+<!--     ylab('Boost Amount') -->
+
+<!--   print(p1) -->
+<!--   print(p2) -->
+<!--   print(p3) -->
+<!--   print(p4) -->
+<!-- } -->
+
+<!-- intervention_information_batch <- function(int.dat, int.name, target.year) { -->
+<!--   hh_boosted <- int.dat %>% -->
+<!--     select(time, run_id, boosted, boost_amount, nkids) %>% -->
+<!--     filter(income_boosted == 'True') %>% -->
+<!--     group_by(time, run_id) %>% -->
+<!--     summarise(n_boosted = length(unique(hidp)), -->
+<!--               total_boost = sum(boost_amount), -->
+<!--               kids_boosted = sum(nkids)) -->
+
+<!--   p1 <- ggplot(hh_boosted, aes(x = time, y = n_boosted)) + -->
+<!--     geom_smooth() + -->
+<!--     geom_vline(xintercept = target.year, linetype = 'dashed') + -->
+<!--     labs(title = 'Number of households receiving intervention', subtitle = int.name) + -->
+<!--     xlab('Year') + -->
+<!--     ylab('Number Boosted') -->
+
+<!--   p2 <- ggplot(hh_boosted, aes(x = time, y = kids_boosted)) + -->
+<!--     geom_smooth() + -->
+<!--     geom_vline(xintercept = target.year, linetype = 'dashed') + -->
+<!--     labs(title = 'Number of children in households receiving intervention', subtitle = int.name) + -->
+<!--     xlab('Year') + -->
+<!--     ylab('Number Children') -->
+
+<!--   p3 <- ggplot(hh_boosted, aes(x = time, y = total_boost)) + -->
+<!--     geom_smooth() + -->
+<!--     geom_vline(xintercept = target.year, linetype = 'dashed') + -->
+<!--     labs(title = 'Total boost amount', subtitle = int.name) + -->
+<!--     xlab('Year') + -->
+<!--     ylab('Boost Amount') -->
+
+<!--   mean.boost <- int.dat %>% -->
+<!--     select(time, income_boosted, boost_amount) %>% -->
+<!--     group_by(time, run_id, income_boosted) %>% -->
+<!--     summarise(mean_boost = mean(boost_amount)) %>% -->
+<!--     filter(income_boosted == 'True') -->
+
+<!--   p4 <- ggplot(mean.boost, aes(x = time, y = mean_boost)) + -->
+<!--     geom_smooth() + -->
+<!--     geom_vline(xintercept = target.year, linetype = 'dashed') + -->
+<!--     labs(title = 'Mean boost amount', subtitle = int.name) + -->
+<!--     xlab('Year') + -->
+<!--     ylab('Boost Amount') -->
+
+<!--   print(p1) -->
+<!--   print(p2) -->
+<!--   print(p3) -->
+<!--   print(p4) -->
+<!-- } -->
+<!-- ``` -->
+
+<!-- ## 25 -->
+
+<!-- ```{r} -->
+<!-- # if (batch) { -->
+<!-- #   intervention_information_batch(int25, int.name = 'int25', target.year = 2030) -->
+<!-- # } else { -->
+<!-- #   intervention_information_single(int25, int.name = 'int25', target.year = 2030) -->
+<!-- # } -->
+<!-- ``` -->
+
+<!-- ## 30 -->
+
+<!-- ```{r} -->
+<!-- # if (batch) { -->
+<!-- #   intervention_information_batch(int30, int.name = 'int30', target.year = 2030) -->
+<!-- # } else { -->
+<!-- #   intervention_information_single(int30, int.name = 'int30', target.year = 2030) -->
+<!-- # } -->
+<!-- ``` -->
+
+<!-- ## 35 -->
+
+<!-- ```{r} -->
+<!-- # if (batch) { -->
+<!-- #   intervention_information_batch(int35, int.name = 'int35', target.year = 2030) -->
+<!-- # } else { -->
+<!-- #   intervention_information_single(int35, int.name = 'int35', target.year = 2030) -->
+<!-- # } -->
+<!-- ``` -->
+
+<!-- ## 40 -->
+
+<!-- ```{r} -->
+<!-- # if (batch) { -->
+<!-- #   intervention_information_batch(int40, int.name = 'int40', target.year = 2030) -->
+<!-- # } else { -->
+<!-- #   intervention_information_single(int40, int.name = 'int40', target.year = 2030) -->
+<!-- # } -->
+<!-- ``` -->
+
+<!-- ## 45 -->
+
+<!-- ```{r} -->
+<!-- # if (batch) { -->
+<!-- #   intervention_information_batch(int45, int.name = 'int45', target.year = 2030) -->
+<!-- # } else { -->
+<!-- #   intervention_information_single(int45, int.name = 'int45', target.year = 2030) -->
+<!-- # } -->
+<!-- ``` -->
+
+<!-- ## 50 -->
+
+<!-- ```{r} -->
+<!-- # if (batch) { -->
+<!-- #   intervention_information_batch(int50, int.name = 'int50', target.year = 2030) -->
+<!-- # } else { -->
+<!-- #   intervention_information_single(int50, int.name = 'int50', target.year = 2030) -->
+<!-- # } -->
+<!-- ``` -->
+
+<!-- # TESTING -->
+
+<!-- ```{r} -->
+<!-- ``` -->

### 2024-01-24 minos/outcomes/SCP_vis_summary.Rmd
Small addition to datain summary scripts for better memory handling, and set new path for SCP_vis_summary

@@
 #out.path <- here::here('output', 'default_config_batch')
-out.path <- here::here('output', 'scaled_scotland_batch', 'summary_files')
+out.path <- here::here('output', 'scaled_scotland_10', 'summary_files')
 

### 2024-01-31 minos/validation/cross_validation_default.Rmd

@@
 
-## Household Size
+## hhsize
 
@@
 
-## Housing Tenure
+## housing tenure
 
@@
 rm(ethnic.pivoted, ethnic.piv.nowhite)
+```
+
+## nkids Household
+
+```{r}
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'nkids')
+multi_year_boxplots(raw, cv, 'nkids')
+q_q_comparison(raw, cv, 'nkids')
+```
+
+## nkids Max
+
+```{r}
+raw.nkids_max <- raw %>%
+  dplyr::select(pidp, time, nkids) %>%
+  group_by(time) %>%
+  summarise(max_nkids = max(nkids)) %>%
+  mutate(source = 'final_US')
+
+cv.nkids_max <- cv %>%
+  dplyr::select(pidp, time, nkids) %>%
+  group_by(time) %>%
+  summarise(max_nkids = max(nkids)) %>%
+  mutate(source = 'baseline_output')
+
+multi_year_boxplots(raw.nkids_max, cv.nkids_max, 'max_nkids')
 ```
@@
 
-%## Job Sec
-%
-%```{r}
-%jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
-%                                          df1.name = 'simulated', 
-%                                          df2 = raw, 
-%                                          df2.name = 'raw', 
-%                                          var = 'job_sec')
-%
-%cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
-%                 var = 'job_sec',
-%                 save = FALSE)
-%rm(jobsec.pivoted)
-%```
-%
-%## Hourly Wage
-%
-%```{r}
-%cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hourly_wage')
-%multi_year_boxplots(raw, cv, 'hourly_wage')
-%q_q_comparison(raw, cv, 'hourly_wage')
-%```
+## Job Sec
+
+```{r}
+jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'job_sec')
+
+cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
+                 var = 'job_sec',
+                 save = FALSE)
+rm(jobsec.pivoted)
+```
+
+## Hourly Wage
+
+```{r}
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hourly_wage')
+multi_year_boxplots(raw, cv, 'hourly_wage')
+q_q_comparison(raw, cv, 'hourly_wage')
+```
 
 ## Children Ageing
-
-## CHILDREN AGEING
 
@@
 ```
-
-# CHILD POVERTY VARS
-
-## Relative Poverty
-
-```{r}
-relative_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                                   df1.name = 'simulated', 
-                                                   df2 = raw, 
-                                                   df2.name = 'raw', 
-                                                   var = 'relative_poverty')
-
-cv_ordinal_plots(pivoted.df = relative_poverty.pivoted, 
-                 var = 'relative_poverty',
-                 save = FALSE)
-rm(relative_poverty.pivoted)
-```
-
-## Absolute Poverty
-
-```{r}
-absolute_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                                   df1.name = 'simulated', 
-                                                   df2 = raw, 
-                                                   df2.name = 'raw', 
-                                                   var = 'absolute_poverty')
-
-cv_ordinal_plots(pivoted.df = absolute_poverty.pivoted, 
-                 var = 'absolute_poverty',
-                 save = FALSE)
-rm(absolute_poverty.pivoted)
-```
-
-## Material Deprivation
-
-```{r}
-matdep_child.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                               df1.name = 'simulated', 
-                                               df2 = raw, 
-                                               df2.name = 'raw', 
-                                               var = 'matdep_child')
-
-cv_ordinal_plots(pivoted.df = matdep_child.pivoted, 
-                 var = 'matdep_child',
-                 save = FALSE)
-rm(matdep_child.pivoted)
-```
-
-## Low Income and Material Deprivation
-
-```{r}
-low_income_matdep_child.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                                          df1.name = 'simulated', 
-                                                          df2 = raw, 
-                                                          df2.name = 'raw', 
-                                                          var = 'low_income_matdep_child')
-
-cv_ordinal_plots(pivoted.df = low_income_matdep_child.pivoted, 
-                 var = 'low_income_matdep_child',
-                 save = FALSE)
-rm(low_income_matdep_child.pivoted)
-```
-
-## Persistent Poverty
-
-```{r}
-persistent_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
-                                                     df1.name = 'simulated', 
-                                                     df2 = raw, 
-                                                     df2.name = 'raw', 
-                                                     var = 'persistent_poverty')
-
-cv_ordinal_plots(pivoted.df = persistent_poverty.pivoted, 
-                 var = 'persistent_poverty',
-                 save = FALSE)
-rm(persistent_poverty.pivoted)
-```

### 2024-02-02 minos/validation/handovers.Rmd

--- 2024-01-22 minos/validation/handovers.Rmd
@@
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-
-#
-
-#out.path <- here::here('output', 'scotland_scaled/')
-#base.dat <- read_first_singular_local_out(out.path, '25UniversalCredit', drop.dead = TRUE)
-
-# HR 283-285 older version (285)
-# out.path <- here::here('output', 'child_poverty_config/')
-# base.dat <- read_singular_local_out(out.path, 'ChildPovertyIntervention', drop.dead = TRUE)
 ```
@@
 
+## Hourly Wage
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'hourly_wage')
+handover_lineplots(raw.dat, base.dat, 'hourly_wage')
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, hourly_wage)
+base.s <- base.dat %>%
+  select(pidp, age, time, hourly_wage)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+# now a version limited to 0-100
+spag <- spag %>%
+  filter(hourly_wage <= 300)
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+```{r}
+# some basic statistics about hourly_wage variable
+print("Some basic statistics on hourly_wage. These are all for 2020.")
+raw.2020 <- raw.dat %>% filter(time == 2020)
+print('All living people in 2020')
+print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
+# number individuals with an hourly_wage > 0
+print('People not in work')
+print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
+
+# Number in work
+print('People in work')
+print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
+
+# Extreme hourly_wage values
+print('Extreme hourly wage values: HIGH')
+print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
+print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
+print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
+print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
+print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
+print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
+
+raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
+print('Extreme hourly wage values: LOW (non-zero)')
+print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
+print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
+print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
+print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
+```
+
+## S7 Labour State
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
+
+lab.state <- prepped.list$var
+lab.state.norm <- prepped.list$norm
+
+# Now plot
+ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'S7_labour_state.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, lab.state, lab.state.norm)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'S7_labour_state')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'S7_labour_state',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
 ## Child Ages
@@
 
-## CHILD POVERTY VARS
-
-### Relative poverty
-
 ```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Relative Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'relative_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-### Absolute Poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Absolute Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'absolute_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-### Persistent Poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Persistent Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'persistent_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
 
 ```
-
-### Low Income and Material Deprivation
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Material Deprivation Child'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'low_income_matdep_child.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-
-```

### 2024-02-02 minos/validation/handovers.Rmd
get ncars working and in handovers notebook

@@
 
-```{r}
-
-```
+## Number of cars
+
+```{r}
+raw.ncars <- raw.dat %>%
+  dplyr::select(pidp, time, ncars) %>%
+  group_by(time, ncars) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.housing <- base.dat %>%
+  dplyr::select(pidp, time, ncars) %>%
+  group_by(time, ncars) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+ncars <- rbind(raw.ncars, base.ncars)
+ncars$ncars <- as.factor(ncars$ncars)
+
+# Now plot
+ggplot(data = ncars, mapping = aes(x = time, y = n, group = ncars, colour = ncars)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Number of Cars', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ncars.norm <- ncars %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = ncars.norm, mapping = aes(x = time, y = prct, fill=ncars)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Number of Cars') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'ncars.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.ncars, base.ncars, ncars, ncars.norm)
+```
+
+```{r}
+
+```

### 2024-02-02 minos/transitions/transition_model_functions.R

@@ -115,6 +115,7 @@ estimate_yearly_nnet <- function(data, formula, include_weights = FALSE, depend)
 }
 
 estimate_yearly_zip <- function(data, formula, include_weights = FALSE, depend) {
+  data <- replace.missing(data)
   
   if(include_weights) {
     model <- zeroinfl(formula = formula,
@@ -130,7 +131,9 @@ estimate_yearly_zip <- function(data, formula, include_weights = FALSE, depend) 
     model[[depend]] <- data[[depend]]
     model$class_preds <- predict(model)
   }
-  
+
+  #test <- runif(n=length(predict(model, type='zero'))) > predict(model, type='zero')
+  #test <- round(test*(predict(model, type='count')))
   #print(summary(model))
   #prs<- 1 - (logLik(model)/logLik(zeroinfl(next_ncigs ~ 1, data=dat.subset, dist='negbin', link='logit')))
   #print(prs)

### 2024-02-05 minos/validation/cross_validation_default.Rmd

@@
 
-# SF_12
+# SF_12_MCS
 
 ```{r}
-cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12')
-multi_year_boxplots(raw, cv, 'SF_12')
-snapshot_OP_plots(raw, cv, 'SF_12', target.years = c(2015, 2017, 2019, 2021))
-q_q_comparison(raw, cv, 'SF_12')
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12_MCS')
+multi_year_boxplots(raw, cv, 'SF_12_MCS')
+snapshot_OP_plots(raw, cv, 'SF_12_MCS', target.years = c(2015, 2017, 2019, 2021))
+q_q_comparison(raw, cv, 'SF_12_MCS')
 ```
@@
                                  predicted = cv, 
-                                 var = 'SF_12', 
+                                 var = 'SF_12_MCS', 
                                  target.year = 2015)
@@
                                  predicted = cv, 
-                                 var = 'SF_12', 
+                                 var = 'SF_12_MCS', 
                                  target.year = 2017)
@@
                                  predicted = cv, 
-                                 var = 'SF_12', 
+                                 var = 'SF_12_MCS', 
                                  target.year = 2019)
@@
                                  predicted = cv, 
-                                 var = 'SF_12', 
+                                 var = 'SF_12_MCS', 
+                                 target.year = 2021)
+print(sf12.20)
+rm(sf12.14, sf12.16, sf12.18, sf12.20)
+```
+
+# SF_12_PCS
+
+```{r}
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12_PCS')
+multi_year_boxplots(raw, cv, 'SF_12_PCS')
+snapshot_OP_plots(raw, cv, 'SF_12_PCS', target.years = c(2015, 2017, 2019, 2021))
+q_q_comparison(raw, cv, 'SF_12_PCS')
+```
+```{r}
+sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12_PCS', 
+                                 target.year = 2015)
+print(sf12.14)
+```
+```{r}
+sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12_PCS', 
+                                 target.year = 2017)
+print(sf12.16)
+```
+```{r}
+sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12_PCS', 
+                                 target.year = 2019)
+print(sf12.18)
+```
+```{r}
+sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
+                                 predicted = cv, 
+                                 var = 'SF_12_PCS', 
                                  target.year = 2021)
@@
 rm(heat.pivoted)
+```
+
+# Alcohol
+
+```{r}
+alc.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'auditc')
+
+cv_ordinal_plots(pivoted.df = alc.pivoted, 
+                 var = 'auditc',
+                 save = FALSE)
+rm(alc.pivoted)
+```
+
+# Physical Activity
+
+```{r}
+active.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'active')
+
+cv_ordinal_plots(pivoted.df = active.pivoted, 
+                 var = 'active',
+                 save = FALSE)
+rm(active.pivoted)
+```
+
+# Material Deprivation
+
+```{r}
+matdep.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'matdep')
+
+cv_ordinal_plots(pivoted.df = matdep.pivoted, 
+                 var = 'matdep',
+                 save = FALSE)
+rm(matdep.pivoted)
+```
+
+# Chronic Disease
+
+```{r}
+chron_disease.pivoted <- combine_and_pivot_long(df1 = cv, 
+                                          df1.name = 'simulated', 
+                                          df2 = raw, 
+                                          df2.name = 'raw', 
+                                          var = 'chron_disease')
+
+cv_ordinal_plots(pivoted.df = chron_disease.pivoted, 
+                 var = 'chron_disease',
+                 save = FALSE)
+rm(chron_disease.pivoted)
 ```

### 2024-02-05 minos/validation/handovers.Rmd

--- 2024-02-02 minos/validation/handovers.Rmd
@@
 
-density_ridges(sf12.spag, "SF_12", 
-               save = T, 
+rm(raw.sf12.m, base.sf12.m, sf12.m.spag, sf12.m.spag.sample)
+```
+
+## SF_12_PCS
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'SF_12_PCS')
+handover_lineplots(raw.dat, base.dat, "SF_12_PCS")
+```
+
+### Spaghetti
+
+```{r}
+raw.sf12.p <- raw.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+base.sf12.p <- base.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+
+sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)
+
+spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
+               save = shall.we.save,
                save.path = save.path)
 
-rm(raw.sf12, base.sf12, sf12.spag)
+density_ridges(sf12.p.spag, "SF_12_PCS", 
+               save = shall.we.save, 
+               save.path = save.path)
+
+rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
 ```
@@
 
-# Try a version where final_US is limited to only those present from wave 1
-# onwards because the sample refreshments are messing with the plot
-# raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-# 
-# raw.nut2 <- raw.dat %>%
-#   dplyr::select(pidp, time, nutrition_quality) %>%
-#   filter(pidp %in% raw.wave1) %>%
-#   filter(nutrition_quality >= 0) %>%
-#   group_by(time) %>%
-#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.nut2 <- base.dat %>%
-#   dplyr::select(pidp, time, nutrition_quality) %>%
-#   filter(pidp %in% raw.wave1) %>%
-#   group_by(time) %>%
-#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# nutrition_quality2 <- rbind(raw.nut2, base.nut2)
-# 
-# # Now plot
-# ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
-#   geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Nutrition Quality') +
-#   xlab('Year') +
-#   ylab('Nutrition Quality')
-# 
-# if (shall.we.save) {
-#   ggsave(filename = 'nutrition_quality_wav1.png',
-#        plot = last_plot(),
-#        path = save.path)
-# }
-# 
-# rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2,
-#     nutrition_quality2)
+test.pidps <- raw.dat %>%
+  select(pidp)
+
+test.base <- base.dat %>%
+  filter(pidp %in% test.pidps$pidp)
+
+handover_boxplots(raw.dat, test.base, 'nutrition_quality')
+handover_lineplots(raw.dat, test.base, 'nutrition_quality')
 ```
@@
 
+## Tobacco
+
+TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11
+
+```{r}
+#  nutriton quality line/boxplots.
+handover_boxplots(raw.dat, base.dat, 'ncigs')
+handover_lineplots(raw.dat, base.dat, 'ncigs')
+
+test.pidps <- raw.dat %>%
+  select(pidp)
+
+test.base <- base.dat %>%
+  filter(pidp %in% test.pidps$pidp)
+
+handover_boxplots(raw.dat, test.base, 'ncigs')
+handover_lineplots(raw.dat, test.base, 'ncigs')
+```
+
+### Spaghetti
+
+```{r}
+raw.nut <- raw.dat %>%
+  select(pidp, age, time, ncigs)
+base.nut <- base.dat %>%
+  select(pidp, age, time, ncigs)
+
+nut.spag <- rbind(raw.nut, base.nut)
+
+spaghetti_plot(nut.spag, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(nut.spag, "ncigs",
+               save = FALSE,
+               save.path = save.path)
+
+rm(raw.nut, base.nut, nut.spag)
+```
+
 ## Physical Health
@@
 ```{r}
-raw.s <- raw.parity %>%
-  select(pidp, age, time, nkids_ind)
-base.s <- base.parity %>%
-  select(pidp, age, time, nkids_ind)
+# raw.s <- raw.parity %>%
+#   select(pidp, age, time, nkids_ind)
+# base.s <- base.parity %>%
+#   select(pidp, age, time, nkids_ind)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'nkids_ind',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
+```
+
+## Alcohol (AUDITC)
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
+
+raw.2020.alc <- raw.dat %>% 
+  filter(time == 2020) %>%
+  group_by(auditc) %>%
+  summarise(n = n()) %>%
+  mutate(prop = n / sum(n))
+
+```
+
+## Physical Activity
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
+
+raw.2020.phys <- raw.dat %>% 
+  filter(time == 2020) %>%
+  group_by(active) %>%
+  summarise(n = n()) %>%
+  mutate(prop = n / sum(n))
+```
+
+## Material Deprivation
+
+```{r}
+#handover_boxplots(raw.dat, base.dat, 'matdep')
+#handover_lineplots(raw.dat, base.dat, 'matdep')
+handover_ordinal(raw.dat, base.dat, var = 'matdep', save = shall.we.save)
+
+raw.dat$chron_disease <- as.factor(raw.dat$chron_disease)
+raw.2020.cd <- raw.dat %>%
+  select(time, chron_disease, age) %>%
+  filter(time == 2020) %>%
+  mutate(age_group = cut(age, 
+                         breaks = c(0,20,30,40,50,60,70,80,90,100,120),
+                         labels = c('16-19', '20-30', '30-40', '40-50', '50-60', '60-70', '70-80', '80-90', '90-100', '100+'))) %>%
+  group_by(age_group, chron_disease) %>%
+  summarise(n = n()) %>%
+  group_by(age_group) %>%
+  mutate(prop = n / sum(n),
+         perc = prop * 100)
+  # mutate(prop = n() / sum(n),
+  #        perc = prop * 100)
+
+raw.2020.cd
+
+ggplot(raw.2020.cd, aes(x = age_group, y = perc, group = chron_disease, colour = chron_disease, fill = chron_disease)) +
+  geom_col(position = 'dodge') +
+  xlab('Age Group') +
+  ylab('Proportion')
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, matdep) %>%
+  filter(!matdep %in% miss.values)
+base.s <- base.dat %>%
+  select(pidp, age, time, matdep) %>%
+  filter(!matdep %in% miss.values)
 
@@
 
-spaghetti_plot(spag, 'nkids_ind',
+spaghetti_plot(spag, 'matdep',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+## Chronic Disease
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'chron_disease', save = shall.we.save)
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, chron_disease) %>%
+  filter(!chron_disease %in% miss.values)
+base.s <- base.dat %>%
+  select(pidp, age, time, chron_disease) %>%
+  filter(!chron_disease %in% miss.values)
+
+spag <- rbind(raw.s, base.s)
+
+spag$chron_disease <- as.numeric(spag$chron_disease)
+
+spaghetti_plot(spag, 'chron_disease',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(spag, 'chron_disease',
+               save=shall.we.save, 
+               save.path=save.path)
+
+pidp_sample <- sample(unique(spag$pidp), size=nrow(raw.s)/10, replace=FALSE)
+spag.sample <- spag[which(spag$pidp %in% pidp_sample), ]
+spaghetti_plot(spag.sample, 'chron_disease',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(spag.sample, 'chron_disease',
                save = shall.we.save,

### 2024-02-06 minos/validation/handovers.Rmd
ncars fully working and in handovers. needs some tweaks as underpredicting zeros.

--- 2024-02-02 minos/validation/handovers.Rmd
@@
   dplyr::select(pidp, time, ncars) %>%
+  select(ncars >= 0) %>%
   group_by(time, ncars) %>%
@@
 
-base.housing <- base.dat %>%
+base.ncars <- base.dat %>%
   dplyr::select(pidp, time, ncars) %>%
+  select(ncars >= 0) %>%
   group_by(time, ncars) %>%

### 2024-02-06 minos/validation/handovers.Rmd
Added a max_ncigs plot to handovers and small change in tobacco.py

--- 2024-02-05 minos/validation/handovers.Rmd
@@
 
+### ncigs mean
+
 TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11
@@
 rm(raw.nut, base.nut, nut.spag)
+```
+
+### ncigs Max
+
+```{r}
+raw.ncigs_max <- raw.dat %>%
+  select(pidp, time, ncigs) %>%
+  group_by(time) %>%
+  summarise(max_ncigs = max(ncigs)) %>%
+  mutate(source = 'final_US')
+
+base.ncigs_max <- base.dat %>%
+  dplyr::select(pidp, time, ncigs) %>%
+  group_by(time) %>%
+  summarise(max_ncigs = max(ncigs)) %>%
+  mutate(source = 'baseline_output')
+
+max_ncigs <- rbind(raw.ncigs_max, base.ncigs_max)
+
+# Now plot
+ggplot(data = max_ncigs, mapping = aes(x = time, y = max_ncigs, group = source, colour = source)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Max ncigs', subtitle = 'Full Sample') +
+  xlab('Year') +
+  ylab('Average')
 ```

### 2024-02-06 minos/validation/handovers.Rmd
mzip module working for tobacco. need to fine tune handovers

--- 2024-02-06 minos/validation/handovers.Rmd
@@
 
-## Number of cars
-
-```{r}
-raw.ncars <- raw.dat %>%
-  dplyr::select(pidp, time, ncars) %>%
-  select(ncars >= 0) %>%
-  group_by(time, ncars) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.ncars <- base.dat %>%
-  dplyr::select(pidp, time, ncars) %>%
-  select(ncars >= 0) %>%
-  group_by(time, ncars) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-ncars <- rbind(raw.ncars, base.ncars)
-ncars$ncars <- as.factor(ncars$ncars)
-
-# Now plot
-ggplot(data = ncars, mapping = aes(x = time, y = n, group = ncars, colour = ncars)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Number of Cars', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ncars.norm <- ncars %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = ncars.norm, mapping = aes(x = time, y = prct, fill=ncars)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Number of Cars') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'ncars.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.ncars, base.ncars, ncars, ncars.norm)
-```
-
-```{r}
-
-```
+## ncigs
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'ncigs')
+handover_lineplots(raw.dat, base.dat, "ncigs")
+raw.ncigs <- raw.dat %>%
+  select(pidp, age, time, ncigs)
+base.ncigs <- base.dat %>%
+  select(pidp, age, time, ncigs)
+ncigs.spag <- rbind(raw.ncigs, base.ncigs)
+shall.we.save <- F
+pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/10, replace=FALSE)
+ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+
+zip_density_ridges(ncigs.spag, "ncigs", 
+               save = shall.we.save, 
+               save.path = save.path)
+rm(raw.ncigs, base.ncigs, ncigs.spag)
+```
+
+## ncigs non-zero
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'ncigs')
+handover_lineplots(raw.dat, base.dat, "ncigs")
+raw.ncigs <- raw.dat %>%
+  select(pidp, age, time, ncigs)
+base.ncigs <- base.dat %>%
+  select(pidp, age, time, ncigs)
+ncigs.spag <- rbind(raw.ncigs, base.ncigs)
+ncigs.spag <- ncigs.spag[which(ncigs.spag$ncigs>0), ] # get all smokers.
+shall.we.save <- F
+pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/10, replace=FALSE)
+ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+
+zip_density_ridges(ncigs.spag, "ncigs", 
+               save = shall.we.save, 
+               save.path = save.path)
+rm(raw.ncigs, base.ncigs, ncigs.spag)
+```

### 2024-02-07 minos/validation/handovers.Rmd
git rid of old handovers functions
trying to get interventions working. need to roll in outgoings and net income modules.

--- 2024-02-06 minos/validation/handovers.Rmd
@@
 out.path <- here::here('output', 'default_config/')
-base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
 ```
@@
 
-## Number of cars
-
-```{r}
-raw.ncars <- raw.dat %>%
-  dplyr::select(pidp, time, ncars) %>%
-  select(ncars >= 0) %>%
-  group_by(time, ncars) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.ncars <- base.dat %>%
-  dplyr::select(pidp, time, ncars) %>%
-  select(ncars >= 0) %>%
-  group_by(time, ncars) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-ncars <- rbind(raw.ncars, base.ncars)
-ncars$ncars <- as.factor(ncars$ncars)
-
-# Now plot
-ggplot(data = ncars, mapping = aes(x = time, y = n, group = ncars, colour = ncars)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Number of Cars', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ncars.norm <- ncars %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = ncars.norm, mapping = aes(x = time, y = prct, fill=ncars)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Number of Cars') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'ncars.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.ncars, base.ncars, ncars, ncars.norm)
-```
-
-```{r}
-
-```
+```{r}
+
+```

### 2024-02-07 minos/modules/energy_interventions.py

@@ -362,14 +362,14 @@ class energyBillSupportScheme(Base):
         self.population_view.update(pop[['hh_income', 'income_boosted', 'boost_amount']])
 
 
-class goodHousingDummy(Base):
+class goodHeatingDummy(Base):
 
     @property
     def name(self):
-        return "good_housing_dummy"
+        return "good_heating_dummy"
 
     def __repr__(self):
-        return "goodHousingDummy()"
+        return "goodHeatingDummy()"
 
     def setup(self, builder):
         """ Initialise the module during simulation.setup().
@@ -391,8 +391,10 @@ class goodHousingDummy(Base):
         # view_columns is the columns from the main population used in this module. essentially what is needed for
         # transition models and any outputs.
         view_columns = ['alive',
-                        'hheat']
-
+                        'heating',
+                        'housing_quality']
+        columns_created = []
+        self.population_view = builder.population.get_view(columns=view_columns + columns_created)
         # Declare events in the module. At what times do individuals transition states from this module. E.g. when does
         # individual graduate in an education module.
         builder.event.register_listener("time_step", self.on_time_step)
@@ -400,10 +402,16 @@ class goodHousingDummy(Base):
     def on_time_step(self, event):
         pass
         pop = self.population_view.get(event.index, query="alive =='alive'")
-        pop['hheat'] = 1
+        # buff housing pop as required.
+        unheated_pop = pop.loc[pop['heating'] == 0, ]
+        unheated_pop.loc[unheated_pop['housing_quality'] == "Medium", 'housing_quality'] = "High"
+        unheated_pop.loc[unheated_pop['housing_quality'] == "Low", 'housing_quality'] = "Medium"
+        pop.loc[pop['heating'] == 0, 'housing_quality'] = unheated_pop['housing_quality']
+
+        # set heating cost to one.
+        #pop['housing_quality'] = pop['housing_quality'].clip(0, 6)
+        pop['heating'] = 1
         self.population_view.update(pop)
-    # set it to 1.
-        # thats it
 
 class GBIS(Base):
 
@@ -438,8 +446,9 @@ class GBIS(Base):
                         "hidp",
                         "S7_labour_state",
                         'hh_income',
-                        "universal_income",
-                        "council_tax"]
+                        #"universal_income",
+                        #"council_tax",
+                        'heating']
         columns_created = ["income_boosted", 'boost_cost', 'boost_amount']
         self.population_view = builder.population.get_view(columns=view_columns + columns_created)
 
[…]

### 2024-02-07 minos/transitions/energy_price_forecasting.Rmd
getting yearly energy module into net income work as well

@@
 ```{r}
-
 process_input_data <- function(dataset, data.column, new.name){
@@
 }
-
 #energy_data <- readxl::read_xlsx("../data/energy_prices_simpler.xlsx")
@@
 #liquid_fuel_vector <- process_input_data(energy_data, "Real terms price indices: Liquid fuels [Note 3]", "liquid_fuel")
-
 energy_data <- readxl::read_xlsx("../data/energy_prices_simpler_yearly.xlsx")
@@
 #domestic_fuel_vector <- process_input_data(energy_data, "Real terms price indices: Domestic fuels\r\n[Note 1, 3]", "domestic_fuel")
-
 plot(electricity_vector$electricity, type='l', xlab="Quarter (0 = Q1 1990", ylab=c("Real Electricity Price indices"), main="Electricity")
@@
 electric.series <- electricity_vector$electricity #+ rnorm(length(electric.series))
-
 # ACF, difference 1 ACF and PACF suggests AR(2)  difference 1 and MA(4) structure (2, 1, 4) in ARIMA.
@@
 pacf(electric.series)
-
 #arima.electric
@@
 plot(residuals(m1))
-
 autoplot(forecast(m1, 40))
@@
 gas.series <- gas_vector$gas
-
 # ACF, difference 1 ACF and PACF suggests AR(2)  difference 1 and MA(4) structure (2, 1, 4) in ARIMA.
@@
 pacf(gas.series)
-
 #arima.electric
 m2 <- arima(gas.series, order=c(4, 0 ,1))
-
 #Box.test(residuals(m1), type="Ljung-Box")
 plot(residuals(m2))
-
 autoplot(forecast(m2, 15))
@@
 solid.series <- solid_fuel_vector$solid_fuel
-
 # ACF, difference 1 ACF and PACF suggests AR(2)  difference 1 and MA(4) structure (2, 1, 4) in ARIMA.
@@
 pacf(solid.series)
-
 #arima.electric
 m3 <- arima(solid.series, order=c(5, 0 ,1))
-
 #Box.test(residuals(m1), type="Ljung-Box")
 plot(residuals(m3))
-
 autoplot(forecast(m3, 15))
@@
 liquid.series <- liquid_fuel_vector$liquid_fuel
-
 # ACF, difference 1 ACF and PACF suggests AR(2)  difference 1 and MA(4) structure (2, 1, 4) in ARIMA.
@@
 pacf(liquid.series)
-
 #arima.electric
 m4 <- arima(gas.series, order=c(5, 0 ,1))
-
 #Box.test(residuals(m1), type="Ljung-Box")
 plot(residuals(m4))
-
 autoplot(forecast(m4,15))
@@
 write.csv(liquid.series, "data/transitions/energy_prices/liquid_historic.csv")
-
 write.csv(forecast(m1, 15), "data/transitions/energy_prices/electric_arima.csv")

### 2024-02-07 minos/validation/handovers.Rmd
Testing PCS with different model types (currently RandomForest), and added some diagnostic histograms and density plots in handovers for PCS

--- 2024-02-06 minos/validation/handovers.Rmd
@@
 rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
+```
+
+### Histograms
+
+I have a hypothesis that the longer we run through simulation, the more simulants are predicted a negative PCS value which is then clipped to a 0.
+Histograms over a few snapshots of time should show if this is happening.
+
+```{r}
+pcs.2021 <- base.dat %>%
+  select(pidp, time, SF_12_PCS) %>%
+  filter(time == 2021)
+
+# pcs.2022 <- base.dat %>%
+#   select(pidp, time, SF_12_PCS) %>%
+#   filter(time == 2022)
+
+pcs.2025 <- base.dat %>%
+  select(pidp, time, SF_12_PCS) %>%
+  filter(time == 2025)
+
+pcs.2030 <- base.dat %>%
+  select(pidp, time, SF_12_PCS) %>%
+  filter(time == 2030)
+
+pcs.2036 <- base.dat %>%
+  select(pidp, time, SF_12_PCS) %>%
+  filter(time == 2036)
+
+merged <- rbind(pcs.2021, pcs.2025, pcs.2030, pcs.2036)
+merged$time <- as.factor(merged$time)
+
+ggplot(merged, aes(x = SF_12_PCS, group = time, colour = time, fill = time)) +
+  geom_histogram() +
+  labs(title = 'Distribution of SF_12_PCS')
+
+ggplot(merged, aes(x = SF_12_PCS, group = time, colour = time, fill = time)) +
+  geom_freqpoly() +
+  labs(title = 'Distribution of SF_12_PCS', subtitle = 'Count')
+
+ggplot(merged, aes(x = SF_12_PCS, y = after_stat(density), group = time, colour = time, fill = time)) +
+  geom_freqpoly() +
+  labs(title = 'Distribution of SF_12_PCS', subtitle = 'Density')
 ```

### 2024-02-07 minos/transitions/transition_model_functions.R

@@ -5,8 +5,8 @@ library(nnet)
 library(pscl)
 library(bestNormalize)
 library(lme4)
-library(glmmTMB)
-library(msm)
+#library(glmmTMB)
+#library(msm)
 library(randomForest)
 library(caret)
 library(doParallel)
@@ -231,7 +231,7 @@ estimate_gamma_glmm <- function(data, formula, include_weights = FALSE, depend, 
 
   min_value <- nanmin(data[[depend]])
   data[[depend]] <- data[[depend]] - min_value + 0.001
-  
+
   if(include_weights) {
     model <- glmer(formula,
                    nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes forever..
@@ -256,42 +256,42 @@ estimate_gamma_glmm <- function(data, formula, include_weights = FALSE, depend, 
 }
 
 estimate_longitudinal_glmm_gauss <- function(data, formula, include_weights = FALSE, depend, yeo_johnson, reflect) {
-  
+
   # Sort out dependent type (factor)
   data <- replace.missing(data)
   #data <- drop_na(data)
   if (reflect) {
     max_value <- nanmax(data[[depend]])
-    data[, c(depend)] <- max_value - data[, c(depend)] 
+    data[, c(depend)] <- max_value - data[, c(depend)]
   }
   if (yeo_johnson)
   {
     yj <- yeojohnson(data[,c(depend)])
     data[, c(depend)] <- predict(yj)
   }
-  
+
   min_value <- nanmin(data[[depend]])
   data[[depend]] <- data[[depend]] - min_value + 0.001
-  
+
   if (depend == 'hourly_wage') {
     # Histogram of hourly_wage_diff
     hist(data$hourly_wage_diff, main = "Distribution of hourly_wage_diff", xlab = "hourly_wage_diff")
   }
-  
+
   if(include_weights) {
-    model <- lmer(formula,  
+    model <- lmer(formula,
                    nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes forever..
                    family=gaussian(link='identity'), # Gaussian family with identity link
-                   weights=weight, 
+                   weights=weight,
                    data = data)
   } else {
-    model <- lmer(formula, 
-                   nAGQ=0, 
+    model <- lmer(formula,
+                   nAGQ=0,
                    family=gaussian(link='identity'),
                    data = data)
   }
   attr(model,"min_value") <- min_value
-  
+
   if (yeo_johnson){
[…]

### 2024-02-07 minos/validation/handovers.Rmd

--- 2024-02-07 minos/validation/handovers.Rmd
@@
 
-out.path <- here::here('output', 'default_config/')
-base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
+#out.path <- here::here('output', 'default_config/')
+#base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+
+out.path <- here::here("output", "default_config")
+base.dat <- read_singular_local_out(out.path, "/baseline", drop.dead = TRUE)
 ```
@@
 ```{r}
-start.year <- 2021
 save.path <- here::here("plots", "handovers", 'default')
 create.if.not.exists(save.path)
+start.year <- 2021
+# make sure we only overlap on one year for now or else tomfoolery happens. (the plots look bad).
+# we may want this overlap in the future? probably not.
+raw.dat <- raw.dat[which(raw.dat$time <= start.year), ]
+base.dat <- base.dat[which(base.dat$time>=start.year), ]
 
@@
 
-## Hourly Wage
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'hourly_wage')
-handover_lineplots(raw.dat, base.dat, 'hourly_wage')
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, hourly_wage)
-base.s <- base.dat %>%
-  select(pidp, age, time, hourly_wage)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-# now a version limited to 0-100
-spag <- spag %>%
-  filter(hourly_wage <= 300)
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-```{r}
-# some basic statistics about hourly_wage variable
-print("Some basic statistics on hourly_wage. These are all for 2020.")
-raw.2020 <- raw.dat %>% filter(time == 2020)
-print('All living people in 2020')
-print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
-# number individuals with an hourly_wage > 0
-print('People not in work')
-print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
-
-# Number in work
-print('People in work')
-print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
-
-# Extreme hourly_wage values
-print('Extreme hourly wage values: HIGH')
-print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
-print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
-print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
-print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
-print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
-print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
-
-raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
-print('Extreme hourly wage values: LOW (non-zero)')
-print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
-print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
-print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
-print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
-```
-
-## S7 Labour State
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
-
-lab.state <- prepped.list$var
-lab.state.norm <- prepped.list$norm
-
-# Now plot
-ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'S7_labour_state.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, lab.state, lab.state.norm)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'S7_labour_state')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'S7_labour_state',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-## Child Ages
-
-```{r}
-raw.child.ages <- raw.dat %>%
-  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
-  filter(time > 2013) %>%
-  group_by(time, hidp) %>%
-  summarise(child_ages = find_mode(child_ages))
-
-r.s<- strsplit(raw.child.ages$child_ages, "_")
-
-raw.child.ages.expanded <- data.frame(time = rep(raw.child.ages$time, sapply(r.s, length)), expanded_child_ages = unlist(r.s))
-raw.child.ages.expanded <- raw.child.ages.expanded %>%
-  group_by(time, expanded_child_ages) %>%
-  summarise(age_counts = n()) %>%
-  mutate(source = 'final_US') %>%
-  filter(expanded_child_ages <= 16)
-
-base.child.ages <- base.dat %>%
-  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
-  filter(time > 2009) %>%
-  group_by(time, hidp) %>%
-  summarise(child_ages = find_mode(child_ages))
-
-b.s<- strsplit(base.child.ages$child_ages, "_")
-
-base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(b.s, length)), expanded_child_ages = unlist(b.s))
-base.child.ages.expanded <- base.child.ages.expanded %>%
-  group_by(time, expanded_child_ages) %>%
-  summarise(age_counts = n()) %>%
-  mutate(source = 'baseline')
-
-combined <- rbind(raw.child.ages.expanded, base.child.ages.expanded)
-
-ggplot(data = combined, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
-  geom_line() +
-  geom_vline(xintercept = start.year) +
-  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
-  scale_colour_viridis_d() +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = combined, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
-  geom_line() +
-  geom_vline(xintercept = start.year) +
-  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
-  scale_colour_viridis_d() +
-  xlab('Year') +
-  ylab('Count')
-
-base.child.ages.nkids <- base.dat %>%
-  group_by(time, hidp) %>%
-  summarise(nkids_counts = mean(nkids)) %>%
-  group_by(time) %>%
-  summarise(nkids_by_year = sum(nkids_counts)) %>%
-  mutate(source = 'baseline')
-
-raw.child.ages.nkids <- raw.dat %>%
-  group_by(time, hidp) %>%
-  summarise(nkids_counts = mean(nkids)) %>%
-  group_by(time) %>%
-  summarise(nkids_by_year = sum(nkids_counts)) %>%
-  mutate(source = 'final_US')
-
-combined.nkids <- rbind(base.child.ages.nkids, raw.child.ages.nkids)
-
-ggplot(data = combined.nkids, mapping = aes(x = time, y = nkids_by_year, group = source, colour = source)) +
-  geom_line() +
-  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-```
-
 ```{r}

### 2024-02-08 minos/validation/handovers.Rmd
get yearly energy making sense. adding in behind on bills

@@
 
-```{r net_income}
+```{r yearly_energy}
 # get required variables. 
@@
 rm(raw.inc, base.inc, inc.spag)
+```
+
+## Yearly energy
+
+```{r net_income}
+# get required variables. 
+raw.energy <- raw.dat %>%
+  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)
+base.energy <- base.dat %>%
+  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)
+
+# gas expenditure
+handover_boxplots(raw.energy, base.energy, 'yearly_gas')
+handover_lineplots(raw.energy, base.energy, "yearly_gas")
+#inc.spag<-rbind(raw.inc, base.inc)
+#density_ridges(inc.spag, 'yearly_gas',
+#               save=TRUE, 
+#               save.path=save.path)
+
+# yearly electric
+handover_boxplots(raw.energy, base.energy, 'yearly_electric')
+handover_lineplots(raw.energy, base.energy, "yearly_electric")
+#density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
+#               save=TRUE, 
+#               save.path=save.path)
+
+# yearly energy
+handover_boxplots(raw.energy, base.energy, 'yearly_energy')
+handover_lineplots(raw.energy, base.energy, "yearly_energy")
+#density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
+#               save=TRUE, 
+#               save.path=save.path)
+
+# tidy up.
+rm(raw.energy, base.energy)#, inc.spag)
 ```

### 2024-02-08 minos/modules/behind_on_bills.py

@@ -1,0 +1,103 @@
+import pandas as pd
+from pathlib import Path
+from minos.modules import r_utils
+from minos.modules.base_module import Base
+import logging
+from datetime import datetime as dt
+
+
+class behindOnBills(Base):
+
+
+    # Special methods used by vivarium.
+    @property
+    def name(self):
+        return 'behind_on_bills'
+
+    def __repr__(self):
+        return "behindOnBills()"
+
+    def setup(self, builder):
+        """ Initialise the module during simulation.setup().
+        Notes
+        -----
+        - Load in data from pre_setup
+        - Register any value producers/modifiers for income
+        - Add required columns to population data frame
+        - Update other required items such as randomness stream.
+        Parameters
+        ----------
+        builder : vivarium.engine.Builder
+            Vivarium's control object. Stores all simulation metadata and allows modules to use it.
+        """
+
+        # Load in inputs from pre-setup.
+        # self.transition_model = builder.data.load("income_transition")
+        self.rpy2_modules = builder.data.load("rpy2_modules")
+
+        # Build vivarium objects for calculating transition probabilities.
+        # Typically this is registering rate/lookup tables. See vivarium docs/other modules for examples.
+        # self.transition_coefficients = builder.
+
+        # Assign randomness streams if necessary.
+        self.random = builder.randomness.get_stream(self.generate_random_crn_key())
+
+        # Determine which subset of the main population is used in this module.
+        # columns_created is the columns created by this module.
+        # view_columns is the columns from the main population used in this module.
+        # In this case, view_columns are taken straight from the transition model
+        view_columns = ["age",
+                        "sex",
+                        "ethnicity",
+                        "region",
+                        "education_state",
+                        "housing_quality",
+                        "neighbourhood_safety",
+                        "loneliness",
+                        "nutrition_quality",
+                        "ncigs",
+                        'job_sec',
+                        'hh_income',
+                        'marital_status',
+                        'housing_tenure',
+                        "behind_on_bills",
+                        "SF_12"
+                        ]
+        # view_columns += self.transition_model.rx2('model').names
+        self.population_view = builder.population.get_view(columns=view_columns)
+
+        # Population initialiser. When new individuals are added to the microsimulation a constructer is called for each
+        # module. Declare what constructer is used. usually on_initialize_simulants method is called. Inidividuals are
[…]

### 2024-02-08 minos/modules/replenishment.py

@@ -118,6 +118,7 @@ class Replenishment(Base):
                         'yearly_gas',
                         'yearly_electric',
                         'yearly_other_fuel',
+                        'hourly_rate',
                         ]
 
         if config.synthetic:  # only have spatial column and new pidp for synthpop.

### 2024-02-09 minos/validation/handovers.Rmd
Changed some prediction function arguments in r_utils and updated the function calls in modules. Also commented out most spaghetti plots for handovers speed

--- 2024-02-07 minos/validation/handovers.Rmd
@@
 ```{r}
-raw.inc <- raw.dat %>%
-  select(pidp, age, time, hh_income)
-base.inc <- base.dat %>%
-  select(pidp, age, time, hh_income)
-
-income.spag <- rbind(raw.inc, base.inc)
-
-density_ridges(income.spag, 'hh_income',
-               save=shall.we.save, 
-               save.path=save.path)
-
-pidp_sample <- sample(unique(income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
-income.spag.sample <- income.spag[which(income.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(income.spag.sample, 'hh_income',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(income.spag.sample, 'hh_income',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.inc, base.inc, income.spag)
+# raw.inc <- raw.dat %>%
+#   select(pidp, age, time, hh_income)
+# base.inc <- base.dat %>%
+#   select(pidp, age, time, hh_income)
+# 
+# income.spag <- rbind(raw.inc, base.inc)
+# 
+# density_ridges(income.spag, 'hh_income',
+#                save=shall.we.save, 
+#                save.path=save.path)
+# 
+# pidp_sample <- sample(unique(income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
+# income.spag.sample <- income.spag[which(income.spag$pidp %in% pidp_sample), ]
+# spaghetti_plot(income.spag.sample, 'hh_income',
+#                save = shall.we.save,
+#                save.path = save.path)
+# spaghetti_highlight_max_plot(income.spag.sample, 'hh_income',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.inc, base.inc, income.spag)
 ```
@@
 ```{r}
-raw.nut <- raw.dat %>%
-  select(pidp, age, time, ncigs)
-base.nut <- base.dat %>%
-  select(pidp, age, time, ncigs)
-
-nut.spag <- rbind(raw.nut, base.nut)
-
-spaghetti_plot(nut.spag, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(nut.spag, "ncigs",
-               save = FALSE,
-               save.path = save.path)
-
-rm(raw.nut, base.nut, nut.spag)
+# raw.nut <- raw.dat %>%
+#   select(pidp, age, time, ncigs)
+# base.nut <- base.dat %>%
+#   select(pidp, age, time, ncigs)
+# 
+# nut.spag <- rbind(raw.nut, base.nut)
+# 
+# spaghetti_plot(nut.spag, 'ncigs',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# 
+# density_ridges(nut.spag, "ncigs",
+#                save = FALSE,
+#                save.path = save.path)
+# 
+# rm(raw.nut, base.nut, nut.spag)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, matdep) %>%
-  filter(!matdep %in% miss.values)
-base.s <- base.dat %>%
-  select(pidp, age, time, matdep) %>%
-  filter(!matdep %in% miss.values)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'matdep',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, matdep) %>%
+#   filter(!matdep %in% miss.values)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, matdep) %>%
+#   filter(!matdep %in% miss.values)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'matdep',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, chron_disease) %>%
-  filter(!chron_disease %in% miss.values)
-base.s <- base.dat %>%
-  select(pidp, age, time, chron_disease) %>%
-  filter(!chron_disease %in% miss.values)
-
-spag <- rbind(raw.s, base.s)
-
-spag$chron_disease <- as.numeric(spag$chron_disease)
-
-spaghetti_plot(spag, 'chron_disease',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(spag, 'chron_disease',
-               save=shall.we.save, 
-               save.path=save.path)
-
-pidp_sample <- sample(unique(spag$pidp), size=nrow(raw.s)/10, replace=FALSE)
-spag.sample <- spag[which(spag$pidp %in% pidp_sample), ]
-spaghetti_plot(spag.sample, 'chron_disease',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(spag.sample, 'chron_disease',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, chron_disease) %>%
+#   filter(!chron_disease %in% miss.values)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, chron_disease) %>%
+#   filter(!chron_disease %in% miss.values)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spag$chron_disease <- as.numeric(spag$chron_disease)
+# 
+# spaghetti_plot(spag, 'chron_disease',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# density_ridges(spag, 'chron_disease',
+#                save=shall.we.save, 
+#                save.path=save.path)
+# 
+# pidp_sample <- sample(unique(spag$pidp), size=nrow(raw.s)/10, replace=FALSE)
+# spag.sample <- spag[which(spag$pidp %in% pidp_sample), ]
+# spaghetti_plot(spag.sample, 'chron_disease',
+#                save = shall.we.save,
+#                save.path = save.path)
+# spaghetti_highlight_max_plot(spag.sample, 'chron_disease',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, hourly_wage)
-base.s <- base.dat %>%
-  select(pidp, age, time, hourly_wage)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-# now a version limited to 0-100
-spag <- spag %>%
-  filter(hourly_wage <= 300)
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, hourly_wage)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, hourly_wage)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'hourly_wage',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# # now a version limited to 0-100
+# spag <- spag %>%
+#   filter(hourly_wage <= 300)
+# spaghetti_plot(spag, 'hourly_wage',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-# some basic statistics about hourly_wage variable
-print("Some basic statistics on hourly_wage. These are all for 2020.")
-raw.2020 <- raw.dat %>% filter(time == 2020)
-print('All living people in 2020')
-print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
-# number individuals with an hourly_wage > 0
-print('People not in work')
-print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
-
-# Number in work
-print('People in work')
-print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
-
-# Extreme hourly_wage values
-print('Extreme hourly wage values: HIGH')
-print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
-print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
-print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
-print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
-print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
-print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
-
-raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
-print('Extreme hourly wage values: LOW (non-zero)')
-print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
-print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
-print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
-print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
+# # some basic statistics about hourly_wage variable
+# print("Some basic statistics on hourly_wage. These are all for 2020.")
+# raw.2020 <- raw.dat %>% filter(time == 2020)
+# print('All living people in 2020')
+# print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
+# # number individuals with an hourly_wage > 0
+# print('People not in work')
+# print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+# print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
+# 
+# # Number in work
+# print('People in work')
+# print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+# print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
+# 
+# # Extreme hourly_wage values
+# print('Extreme hourly wage values: HIGH')
+# print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
+# print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
+# print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
+# print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
+# print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
+# print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
+# 
+# raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
+# print('Extreme hourly wage values: LOW (non-zero)')
+# print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
+# print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
+# print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
+# print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
 ```

### 2024-02-09 minos/modules/mental_wellbeing.py

@@ -552,7 +552,6 @@ class lmmYJMWB(Base):
                                                                dependent='SF_12_MCS',
                                                                reflect=True,
                                                                yeo_johnson= True,
-                                                               mod_type='gamma',
                                                                noise_std= 0.1)  # 5 for non yj, 0.35 for yj
         return out_data
 

### 2024-02-15 minos/validation/handovers.Rmd
messing with tobacco mzip. get handovers working well ready for ncars merge.

--- 2024-02-07 minos/validation/handovers.Rmd
@@
 ---
-params:
-    file_path: '' # default arguments. specify others in command line.
-    intervention: ''
-title: "Handovers"
+title: "MINOS Handover Plots"
 output:
-  #output_file: "`r paste('minos/validation/', params$file_path, '_', params$intervention, '_handovers.html') `"
   html_document:
@@
 ```{r}
-
 # Read raw datafiles in
@@
 
-#out.path <- here::here('output', 'default_config/')
-#base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-
-out.path <- here::here("output", "default_config")
-base.dat <- read_singular_local_out(out.path, "/baseline", drop.dead = TRUE)
+out.path <- here::here('output', 'default_config/')
+base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
 ```
@@
 ```{r}
+start.year <- 2021
 save.path <- here::here("plots", "handovers", 'default')
 create.if.not.exists(save.path)
-start.year <- 2021
-# make sure we only overlap on one year for now or else tomfoolery happens. (the plots look bad).
-# we may want this overlap in the future? probably not.
-raw.dat <- raw.dat[which(raw.dat$time <= start.year), ]
-base.dat <- base.dat[which(base.dat$time>=start.year), ]
 
@@
 rm(raw.inc, base.inc, income.spag)
-```
-
-## Net Income & Rent & Mortgage
-
-```{r net_income}
-# get required variables. 
-raw.inc <- raw.dat %>%
-  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
-base.inc <- base.dat %>%
-  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
-
-# net household income. 
-handover_boxplots(raw.inc, base.inc, 'net_hh_income')
-handover_lineplots(raw.inc, base.inc, "net_hh_income")
-inc.spag<-rbind(raw.inc, base.inc)
-density_ridges(inc.spag, 'net_hh_income',
-               save=TRUE, 
-               save.path=save.path)
-
-# rent
-handover_boxplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], 'hh_rent')
-handover_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
-density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
-               save=TRUE, 
-               save.path=save.path)
-
-# mortgage
-handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], 'hh_mortgage')
-handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
-density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
-               save=TRUE, 
-               save.path=save.path)
-
-#council tax
-handover_boxplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], 'council_tax')
-handover_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
-density_ridges(inc.spag[which(inc.spag$council_tax>1), ], 'council_tax',
-               save=TRUE, 
-               save.path=save.path)
-
-# oecd equivalence scale. (NOT TRANSITIONED YET. REQUIRES LEAVING THE NEST MODULE.. )
-handover_boxplots(raw.inc, base.inc, 'oecd_equiv')
-handover_lineplots(raw.inc, base.inc, 'oecd_equiv')
-density_ridges(inc.spag, 'oecd_equiv',
-               save=TRUE, 
-               save.path=save.path)
-
-# tidy up.
-rm(raw.inc, base.inc, inc.spag)
 ```
@@
 # rm(raw.s, base.s, spag)
-```
-
-## Housing Tenure
-
-```{r}
-raw.tenure <- raw.dat %>%
-  dplyr::select(pidp, time, housing_tenure) %>%
-  group_by(time, housing_tenure) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.tenure <- base.dat %>%
-  dplyr::select(pidp, time, housing_tenure) %>%
-  group_by(time, housing_tenure) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-tenure <- rbind(raw.tenure, base.tenure)
-tenure$housing_tenure <- as.factor(tenure$housing_tenure)
-
-# Now plot
-ggplot(data = tenure, mapping = aes(x = time, y = n, group = housing_tenure, colour = housing_tenure)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Tenure', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-tenure.norm <- tenure %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = tenure.norm, mapping = aes(x = time, y = prct, fill=housing_tenure)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Tenure') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'housing_tenure.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.tenure, base.tenure, tenure, tenure.norm)
 ```
@@
 
+## Hourly Wage
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'hourly_wage')
+handover_lineplots(raw.dat, base.dat, 'hourly_wage')
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, hourly_wage)
+base.s <- base.dat %>%
+  select(pidp, age, time, hourly_wage)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+# now a version limited to 0-100
+spag <- spag %>%
+  filter(hourly_wage <= 300)
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+```{r}
+# some basic statistics about hourly_wage variable
+print("Some basic statistics on hourly_wage. These are all for 2020.")
+raw.2020 <- raw.dat %>% filter(time == 2020)
+print('All living people in 2020')
+print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
+# number individuals with an hourly_wage > 0
+print('People not in work')
+print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
+
+# Number in work
+print('People in work')
+print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
+
+# Extreme hourly_wage values
+print('Extreme hourly wage values: HIGH')
+print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
+print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
+print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
+print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
+print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
+print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
+
+raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
+print('Extreme hourly wage values: LOW (non-zero)')
+print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
+print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
+print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
+print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
+```
+
+## S7 Labour State
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
+
+lab.state <- prepped.list$var
+lab.state.norm <- prepped.list$norm
+
+# Now plot
+ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'S7_labour_state.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, lab.state, lab.state.norm)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'S7_labour_state')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'S7_labour_state',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
+## Child Ages
+
+```{r}
+raw.child.ages <- raw.dat %>%
+  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
+  filter(time > 2013) %>%
+  group_by(time, hidp) %>%
+  summarise(child_ages = find_mode(child_ages))
+
+r.s<- strsplit(raw.child.ages$child_ages, "_")
+
+raw.child.ages.expanded <- data.frame(time = rep(raw.child.ages$time, sapply(r.s, length)), expanded_child_ages = unlist(r.s))
+raw.child.ages.expanded <- raw.child.ages.expanded %>%
+  group_by(time, expanded_child_ages) %>%
+  summarise(age_counts = n()) %>%
+  mutate(source = 'final_US') %>%
+  filter(expanded_child_ages <= 16)
+
+base.child.ages <- base.dat %>%
+  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
+  filter(time > 2009) %>%
+  group_by(time, hidp) %>%
+  summarise(child_ages = find_mode(child_ages))
+
+b.s<- strsplit(base.child.ages$child_ages, "_")
+
+base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(b.s, length)), expanded_child_ages = unlist(b.s))
+base.child.ages.expanded <- base.child.ages.expanded %>%
+  group_by(time, expanded_child_ages) %>%
+  summarise(age_counts = n()) %>%
+  mutate(source = 'baseline')
+
+combined <- rbind(raw.child.ages.expanded, base.child.ages.expanded)
+
+ggplot(data = combined, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
+  geom_line() +
+  geom_vline(xintercept = start.year) +
+  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
+  scale_colour_viridis_d() +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = combined, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
+  geom_line() +
+  geom_vline(xintercept = start.year) +
+  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
+  scale_colour_viridis_d() +
+  xlab('Year') +
+  ylab('Count')
+
+base.child.ages.nkids <- base.dat %>%
+  group_by(time, hidp) %>%
+  summarise(nkids_counts = mean(nkids)) %>%
+  group_by(time) %>%
+  summarise(nkids_by_year = sum(nkids_counts)) %>%
+  mutate(source = 'baseline')
+
+raw.child.ages.nkids <- raw.dat %>%
+  group_by(time, hidp) %>%
+  summarise(nkids_counts = mean(nkids)) %>%
+  group_by(time) %>%
+  summarise(nkids_by_year = sum(nkids_counts)) %>%
+  mutate(source = 'final_US')
+
+combined.nkids <- rbind(base.child.ages.nkids, raw.child.ages.nkids)
+
+ggplot(data = combined.nkids, mapping = aes(x = time, y = nkids_by_year, group = source, colour = source)) +
+  geom_line() +
+  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+```
+
+## ncigs
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'ncigs')
+handover_lineplots(raw.dat, base.dat, "ncigs")
+raw.ncigs <- raw.dat %>%
+  select(pidp, age, time, ncigs)
+base.ncigs <- base.dat %>%
+  select(pidp, age, time, ncigs)
+ncigs.spag <- rbind(raw.ncigs, base.ncigs)
+shall.we.save <- F
+pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/10, replace=FALSE)
+ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+
+zip_density_ridges(ncigs.spag, "ncigs", 
+               save = shall.we.save, 
+               save.path = save.path)
+rm(raw.ncigs, base.ncigs, ncigs.spag)
+```
+
+## ncigs non-zero
+
 ```{r}
 
+raw.ncigs <- raw.dat %>%
+  filter(ncigs>0) %>%
+  select(pidp, age, time, ncigs)
+base.ncigs <- base.dat %>%
+  filter(ncigs>0) %>%
+  select(pidp, age, time, ncigs)
+
+ncigs.spag <- rbind(raw.ncigs, base.ncigs) # get all smokers.
+shall.we.save <- F
+pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/100, replace=FALSE)
+ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+
+zip_density_ridges(ncigs.spag, "ncigs", 
+               save = shall.we.save, 
+               save.path = save.path)
+rm(raw.ncigs, base.ncigs, ncigs.spag)
 ```

### 2024-02-15 minos/modules/replenishment.py

@@ -102,7 +102,7 @@ class Replenishment(Base):
                         'job_hours_diff',
                         'hourly_wage_diff',
                         'child_ages',
-                        'ncars'
+                        #'ncars'
                         ]
 
         if config.synthetic:  # only have spatial column and new pidp for synthpop.

### 2024-02-15 minos/validation/handovers.Rmd

@@
 
+## Number of cars
+
+```{r}
+raw.ncars <- raw.dat %>%
+  dplyr::select(pidp, time, ncars) %>%
+  select(ncars >= 0) %>%
+  group_by(time, ncars) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.ncars <- base.dat %>%
+  dplyr::select(pidp, time, ncars) %>%
+  select(ncars >= 0) %>%
+  group_by(time, ncars) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+ncars <- rbind(raw.ncars, base.ncars)
+ncars$ncars <- as.factor(ncars$ncars)
+
+# Now plot
+ggplot(data = ncars, mapping = aes(x = time, y = n, group = ncars, colour = ncars)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Number of Cars', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ncars.norm <- ncars %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = ncars.norm, mapping = aes(x = time, y = prct, fill=ncars)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Number of Cars') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'ncars.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.ncars, base.ncars, ncars, ncars.norm)
+```
+
+```{r}
+
 ## ncigs

### 2024-02-16 minos/validation/handovers.Rmd
Fixed a few typos, removed the intervention argument from handovers, and fixed the handovers make targets to work with the new output path parameter

--- 2024-02-15 minos/validation/handovers.Rmd
@@
 ---
-title: "MINOS Handover Plots"
+params:
+    file_path: '' # default arguments. specify others in command line.
+title: "`r paste(params$file_path, ' Handover Plots')`"
 output:
+  #output_file: "`r paste('minos/validation/', params$file_path, '_', params$intervention, '_handovers.html') `"
   html_document:
@@
 ```{r}
+
+file_path <- params$file_path
+
+if (file_path == 'default_MICE/') {
+  raw.file_path <- 'imputed_final_US'
+} else {
+  raw.file_path <- 'final_US'
+}
+
 # Read raw datafiles in
-raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', raw.file_path), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
 
-out.path <- here::here('output', 'default_config/')
+#out.path <- here::here('output', 'default_config/')
+#base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+
+out.path <- here::here('output', file_path)
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
@@
 ```{r}
-start.year <- 2021
+start.year <- 2020
 save.path <- here::here("plots", "handovers", 'default')
 create.if.not.exists(save.path)
+
+# make sure we only overlap on one year for now or else tomfoolery happens (the plots look bad).
+# we may want this overlap in the future? probably not.
+# LA 16/2/24 - We still want the actual handover point though so we need both data points in the start year
+# have changed to achieve this
+raw.dat <- raw.dat[which(raw.dat$time <= start.year), ]
+base.dat <- base.dat[which(base.dat$time>=start.year), ]
 
@@
 
-## Hourly Wage
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'hourly_wage')
-handover_lineplots(raw.dat, base.dat, 'hourly_wage')
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, hourly_wage)
-base.s <- base.dat %>%
-  select(pidp, age, time, hourly_wage)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-# now a version limited to 0-100
-spag <- spag %>%
-  filter(hourly_wage <= 300)
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-```{r}
-# some basic statistics about hourly_wage variable
-print("Some basic statistics on hourly_wage. These are all for 2020.")
-raw.2020 <- raw.dat %>% filter(time == 2020)
-print('All living people in 2020')
-print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
-# number individuals with an hourly_wage > 0
-print('People not in work')
-print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
-
-# Number in work
-print('People in work')
-print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
-
-# Extreme hourly_wage values
-print('Extreme hourly wage values: HIGH')
-print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
-print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
-print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
-print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
-print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
-print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
-
-raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
-print('Extreme hourly wage values: LOW (non-zero)')
-print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
-print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
-print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
-print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
-```
-
-## S7 Labour State
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
-
-lab.state <- prepped.list$var
-lab.state.norm <- prepped.list$norm
-
-# Now plot
-ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'S7_labour_state.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, lab.state, lab.state.norm)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'S7_labour_state')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'S7_labour_state',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-## Child Ages
-
-```{r}
-raw.child.ages <- raw.dat %>%
-  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
-  filter(time > 2013) %>%
-  group_by(time, hidp) %>%
-  summarise(child_ages = find_mode(child_ages))
-
-r.s<- strsplit(raw.child.ages$child_ages, "_")
-
-raw.child.ages.expanded <- data.frame(time = rep(raw.child.ages$time, sapply(r.s, length)), expanded_child_ages = unlist(r.s))
-raw.child.ages.expanded <- raw.child.ages.expanded %>%
-  group_by(time, expanded_child_ages) %>%
-  summarise(age_counts = n()) %>%
-  mutate(source = 'final_US') %>%
-  filter(expanded_child_ages <= 16)
-
+```{r}
 base.child.ages <- base.dat %>%
@@
 
-b.s<- strsplit(base.child.ages$child_ages, "_")
-
-base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(b.s, length)), expanded_child_ages = unlist(b.s))
+s<- strsplit(base.child.ages$child_ages, "_")
+
+base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(s, length)), expanded_child_ages = unlist(s))
 base.child.ages.expanded <- base.child.ages.expanded %>%
   group_by(time, expanded_child_ages) %>%
-  summarise(age_counts = n()) %>%
-  mutate(source = 'baseline')
-
-combined <- rbind(raw.child.ages.expanded, base.child.ages.expanded)
-
-ggplot(data = combined, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
-  geom_line() +
-  geom_vline(xintercept = start.year) +
+  summarise(age_counts = n())
+
+ggplot(data = base.child.ages.expanded, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
+  geom_line() +
   labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
@@
 
-ggplot(data = combined, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
-  geom_line() +
-  geom_vline(xintercept = start.year) +
+ggplot(data = base.child.ages.expanded, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
+  geom_line() +
   labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
@@
   group_by(time) %>%
-  summarise(nkids_by_year = sum(nkids_counts)) %>%
-  mutate(source = 'baseline')
-
-raw.child.ages.nkids <- raw.dat %>%
-  group_by(time, hidp) %>%
-  summarise(nkids_counts = mean(nkids)) %>%
-  group_by(time) %>%
-  summarise(nkids_by_year = sum(nkids_counts)) %>%
-  mutate(source = 'final_US')
-
-combined.nkids <- rbind(base.child.ages.nkids, raw.child.ages.nkids)
-
-ggplot(data = combined.nkids, mapping = aes(x = time, y = nkids_by_year, group = source, colour = source)) +
+  summarise(nkids_by_year = sum(nkids_counts))
+
+ggplot(data = base.child.ages.nkids, mapping = aes(x = time, y = nkids_by_year)) +
   geom_line() +
@@
 
-## ncigs
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'ncigs')
-handover_lineplots(raw.dat, base.dat, "ncigs")
-raw.ncigs <- raw.dat %>%
-  select(pidp, age, time, ncigs)
-base.ncigs <- base.dat %>%
-  select(pidp, age, time, ncigs)
-ncigs.spag <- rbind(raw.ncigs, base.ncigs)
-shall.we.save <- F
-pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/10, replace=FALSE)
-ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(ncigs.spag.sample, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-
-zip_density_ridges(ncigs.spag, "ncigs", 
-               save = shall.we.save, 
-               save.path = save.path)
-rm(raw.ncigs, base.ncigs, ncigs.spag)
-```
-
-## ncigs non-zero
-
-```{r}
-
-raw.ncigs <- raw.dat %>%
-  filter(ncigs>0) %>%
-  select(pidp, age, time, ncigs)
-base.ncigs <- base.dat %>%
-  filter(ncigs>0) %>%
-  select(pidp, age, time, ncigs)
-
-ncigs.spag <- rbind(raw.ncigs, base.ncigs) # get all smokers.
-shall.we.save <- F
-pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/100, replace=FALSE)
-ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(ncigs.spag.sample, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-
-zip_density_ridges(ncigs.spag, "ncigs", 
-               save = shall.we.save, 
-               save.path = save.path)
-rm(raw.ncigs, base.ncigs, ncigs.spag)
-```
+## CHILD POVERTY VARS
+
+### Relative poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Relative Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'relative_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+### Absolute Poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Absolute Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'absolute_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+### Persistent Poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Persistent Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'persistent_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+
+```
+
+### Low Income and Material Deprivation
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Material Deprivation Child'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'low_income_matdep_child.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+
+```

### 2024-02-19 minos/validation/cross_validation_default.Rmd
Fixed cv transitions targets in transition Makefile. Also changed the year for transition models for housing_tenure and financial_situation due to a change in the factor levels of housing_tenure in 2019. This meant that transition models where housing_tenure is a predictor (or an outcome) have to be pre-2019 for cross-validation (due to cv starting in 2015)

@@
 raw.nkids_max <- raw %>%
-  dplyr::select(pidp, time, nkids) %>%
+  dplyr::select(time, nkids) %>%
   group_by(time) %>%
@@
 cv.nkids_max <- cv %>%
-  dplyr::select(pidp, time, nkids) %>%
+  dplyr::select(time, nkids) %>%
   group_by(time) %>%

### 2024-02-20 minos/validation/handovers.Rmd
getting ncars and ncigs into a sensible state for merging with net income

--- 2024-02-15 minos/validation/handovers.Rmd
@@
 
-out.path <- here::here('output', 'default_config/')
+out.path <- here::here('output', 'energy_default_config/')
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
@@
 
-```{r}
-raw.ncars <- raw.dat %>%
+```{r ncars}
+
+raw.ncars <- raw.dat
+base.ncars <- base.dat
+raw.ncars[raw.ncars$ncars>=10, 'ncars'] <- "More than 9."
+base.ncars[base.ncars$ncars>=10, 'ncars'] <- "More than 9."
+
+raw.ncars <- raw.ncars %>%
   dplyr::select(pidp, time, ncars) %>%
-  select(ncars >= 0) %>%
+  filter(ncars >= 0) %>%
   group_by(time, ncars) %>%
@@
 
-base.ncars <- base.dat %>%
+base.ncars <- base.ncars %>%
   dplyr::select(pidp, time, ncars) %>%
-  select(ncars >= 0) %>%
+  filter(ncars >= 0) %>%
   group_by(time, ncars) %>%
@@
   mutate(prct = (n / total))
+
+ggplot(data = ncars.norm, mapping = aes(x = time, y = prct, group = ncars, colour = ncars)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Number of Cars', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
 
@@
 ```
-
-```{r}
 

### 2024-02-20 minos/validation/handovers.Rmd
getting behind on bills nad net inc working together. need to tweak net inc and mortgage models.]

--- 2024-02-16 minos/validation/handovers.Rmd
@@
     file_path: '' # default arguments. specify others in command line.
-title: "`r paste(params$file_path, ' Handover Plots')`"
+    intervention: ''
+title: "Handovers"
 output:
@@
 
-file_path <- params$file_path
-
-if (file_path == 'default_MICE/') {
-  raw.file_path <- 'imputed_final_US'
-} else {
-  raw.file_path <- 'final_US'
-}
-
 # Read raw datafiles in
-raw.files <- list.files(here::here('data', raw.file_path), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 
-out.path <- here::here('output', file_path)
-base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+out.path <- here::here("output", "energy_default_config")
+base.dat <- read_singular_local_out(out.path, "/baseline", drop.dead = TRUE)
 ```
@@
 ```{r}
-start.year <- 2020
 save.path <- here::here("plots", "handovers", 'default')
 create.if.not.exists(save.path)
-
-# make sure we only overlap on one year for now or else tomfoolery happens (the plots look bad).
+start.year <- 2021
+# make sure we only overlap on one year for now or else tomfoolery happens. (the plots look bad).
 # we may want this overlap in the future? probably not.
-# LA 16/2/24 - We still want the actual handover point though so we need both data points in the start year
-# have changed to achieve this
 raw.dat <- raw.dat[which(raw.dat$time <= start.year), ]
@@
 rm(raw.inc, base.inc, income.spag)
+```
+
+## Net Income & Rent & Mortgage
+
+```{r yearly_energy}
+# get required variables. 
+raw.inc <- raw.dat %>%
+  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
+base.inc <- base.dat %>%
+  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
+
+# net household income. 
+handover_boxplots(raw.inc, base.inc, 'net_hh_income')
+handover_lineplots(raw.inc, base.inc, "net_hh_income")
+inc.spag<-rbind(raw.inc, base.inc)
+density_ridges(inc.spag, 'net_hh_income',
+               save=TRUE, 
+               save.path=save.path)
+
+# rent
+handover_boxplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], 'hh_rent')
+handover_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
+density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
+               save=TRUE, 
+               save.path=save.path)
+
+# mortgage
+handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], 'hh_mortgage')
+handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
+density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
+               save=TRUE, 
+               save.path=save.path)
+
+#council tax
+handover_boxplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], 'council_tax')
+handover_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
+density_ridges(inc.spag[which(inc.spag$council_tax>1), ], 'council_tax',
+               save=TRUE, 
+               save.path=save.path)
+
+# oecd equivalence scale. (NOT TRANSITIONED YET. REQUIRES LEAVING THE NEST MODULE.. )
+handover_boxplots(raw.inc, base.inc, 'oecd_equiv')
+handover_lineplots(raw.inc, base.inc, 'oecd_equiv')
+density_ridges(inc.spag, 'oecd_equiv',
+               save=TRUE, 
+               save.path=save.path)
+
+# tidy up.
+rm(raw.inc, base.inc, inc.spag)
+```
+
+## Yearly energy
+
+```{r net_income}
+# get required variables. 
+raw.energy <- raw.dat %>%
+  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)
+base.energy <- base.dat %>%
+  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)
+
+# gas expenditure
+handover_boxplots(raw.energy, base.energy, 'yearly_gas')
+handover_lineplots(raw.energy, base.energy, "yearly_gas")
+#inc.spag<-rbind(raw.inc, base.inc)
+#density_ridges(inc.spag, 'yearly_gas',
+#               save=TRUE, 
+#               save.path=save.path)
+
+# yearly electric
+handover_boxplots(raw.energy, base.energy, 'yearly_electric')
+handover_lineplots(raw.energy, base.energy, "yearly_electric")
+#density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
+#               save=TRUE, 
+#               save.path=save.path)
+
+# yearly energy
+handover_boxplots(raw.energy, base.energy, 'yearly_energy')
+handover_lineplots(raw.energy, base.energy, "yearly_energy")
+#density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
+#               save=TRUE, 
+#               save.path=save.path)
+
+# tidy up.
+rm(raw.energy, base.energy)#, inc.spag)
 ```
@@
 ```{r}
-base.child.ages <- base.dat %>%
-  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
-  filter(time > 2009) %>%
-  group_by(time, hidp) %>%
-  summarise(child_ages = find_mode(child_ages))
-
-s<- strsplit(base.child.ages$child_ages, "_")
-
-base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(s, length)), expanded_child_ages = unlist(s))
-base.child.ages.expanded <- base.child.ages.expanded %>%
-  group_by(time, expanded_child_ages) %>%
-  summarise(age_counts = n())
-
-ggplot(data = base.child.ages.expanded, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
-  geom_line() +
-  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
-  scale_colour_viridis_d() +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = base.child.ages.expanded, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
-  geom_line() +
-  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
-  scale_colour_viridis_d() +
-  xlab('Year') +
-  ylab('Count')
-
-base.child.ages.nkids <- base.dat %>%
-  group_by(time, hidp) %>%
-  summarise(nkids_counts = mean(nkids)) %>%
-  group_by(time) %>%
-  summarise(nkids_by_year = sum(nkids_counts))
-
-ggplot(data = base.child.ages.nkids, mapping = aes(x = time, y = nkids_by_year)) +
-  geom_line() +
-  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
 
 ```
-
-## CHILD POVERTY VARS
-
-### Relative poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Relative Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'relative_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-### Absolute Poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Absolute Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'absolute_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-### Persistent Poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Persistent Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'persistent_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-
-```
-
-### Low Income and Material Deprivation
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Material Deprivation Child'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'low_income_matdep_child.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-
-```

### 2024-02-20 minos/modules/behind_on_bills.py

@@ -87,7 +87,7 @@ class behindOnBills(Base):
         self.year = event.time.year
 
         nextWaveBills = self.calculate_behind_on_bills(pop)
-        nextWaveBills["financial_situation"] = self.random.choice(nextWaveBills.index,
+        nextWaveBills["behind_on_bills"] = self.random.choice(nextWaveBills.index,
                                                                   list(nextWaveBills.columns+1),
                                                                   nextWaveBills).astype(float)
         nextWaveBills.index = pop.index

### 2024-02-20 minos/modules/net_income.py

@@ -151,13 +151,17 @@ class lmmYJNetIncome(Base):
         newWavenetIncome['net_hh_income'] = self.calculate_net_income(pop)
         newWavenetIncome.index = pop.index
         newWavenetIncome['hidp'] = pop['hidp']
-        newWavenetIncome['net_hh_income'] = newWavenetIncome.groupby('hidp')['net_hh_income'].transform(np.median)
-        newWavenetIncome['net_hh_income'] = newWavenetIncome['net_hh_income'].clip(-1000, 12000)
 
         income_mean = np.median(newWavenetIncome["net_hh_income"])
         std_ratio = (np.std(pop['net_hh_income']) / np.std(newWavenetIncome["net_hh_income"]))
         newWavenetIncome["net_hh_income"] *= std_ratio
         newWavenetIncome["net_hh_income"] -= ((std_ratio - 1) * income_mean)
+
+        newWavenetIncome['net_hh_income'] += 500
+
+        newWavenetIncome['net_hh_income'] = newWavenetIncome.groupby('hidp')['net_hh_income'].transform("mean")
+        newWavenetIncome['net_hh_income'] = newWavenetIncome['net_hh_income'].clip(-1000, 12000)
+
 
         newWavenetIncome['net_hh_income_diff'] = newWavenetIncome['net_hh_income'] - pop['net_hh_income']
 

### 2024-02-20 minos/validation/handovers.Rmd
fixing handovers for going back into dev

--- 2024-02-20 minos/validation/handovers.Rmd
@@
 
-out.path <- here::here('output', 'energy_default_config/')
+out.path <- here::here('output', 'default_config/')
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
 ```
@@
 
-## Number of cars
-
-```{r ncars}
-
-raw.ncars <- raw.dat
-base.ncars <- base.dat
-raw.ncars[raw.ncars$ncars>=10, 'ncars'] <- "More than 9."
-base.ncars[base.ncars$ncars>=10, 'ncars'] <- "More than 9."
-
-raw.ncars <- raw.ncars %>%
-  dplyr::select(pidp, time, ncars) %>%
-  filter(ncars >= 0) %>%
-  group_by(time, ncars) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.ncars <- base.ncars %>%
-  dplyr::select(pidp, time, ncars) %>%
-  filter(ncars >= 0) %>%
-  group_by(time, ncars) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-ncars <- rbind(raw.ncars, base.ncars)
-ncars$ncars <- as.factor(ncars$ncars)
-
-# Now plot
-ggplot(data = ncars, mapping = aes(x = time, y = n, group = ncars, colour = ncars)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Number of Cars', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ncars.norm <- ncars %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = ncars.norm, mapping = aes(x = time, y = prct, group = ncars, colour = ncars)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Number of Cars', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = ncars.norm, mapping = aes(x = time, y = prct, fill=ncars)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Number of Cars') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'ncars.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.ncars, base.ncars, ncars, ncars.norm)
-```
-
-## ncigs
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'ncigs')
-handover_lineplots(raw.dat, base.dat, "ncigs")
-raw.ncigs <- raw.dat %>%
-  select(pidp, age, time, ncigs)
-base.ncigs <- base.dat %>%
-  select(pidp, age, time, ncigs)
-ncigs.spag <- rbind(raw.ncigs, base.ncigs)
-shall.we.save <- F
-pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/10, replace=FALSE)
-ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(ncigs.spag.sample, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-
-zip_density_ridges(ncigs.spag, "ncigs", 
-               save = shall.we.save, 
-               save.path = save.path)
-rm(raw.ncigs, base.ncigs, ncigs.spag)
-```
-
-## ncigs non-zero
-
-```{r}
-
-raw.ncigs <- raw.dat %>%
-  filter(ncigs>0) %>%
-  select(pidp, age, time, ncigs)
-base.ncigs <- base.dat %>%
-  filter(ncigs>0) %>%
-  select(pidp, age, time, ncigs)
-
-ncigs.spag <- rbind(raw.ncigs, base.ncigs) # get all smokers.
-shall.we.save <- F
-pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/100, replace=FALSE)
-ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(ncigs.spag.sample, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-
-zip_density_ridges(ncigs.spag, "ncigs", 
-               save = shall.we.save, 
-               save.path = save.path)
-rm(raw.ncigs, base.ncigs, ncigs.spag)
-```
+```{r}
+
+```

### 2024-02-22 minos/validation/handovers.Rmd
gettting all 4 new mods and intervention working together for test run

--- 2024-02-22 minos/validation/handovers.Rmd
@@
 
+#out.path <- here::here('output', 'default_config/')
 out.path <- here::here('output', 'energy_default_config/')
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
 ```

### 2024-02-23 minos/validation/handovers.Rmd

--- 2024-02-22 minos/validation/handovers.Rmd
@@
 ```{r}
-raw.inc <- raw.dat %>%
-  select(pidp, age, time, hh_income)
-base.inc <- base.dat %>%
-  select(pidp, age, time, hh_income)
-
-income.spag <- rbind(raw.inc, base.inc)
-
-density_ridges(income.spag, 'hh_income',
-               save=TRUE, 
-               save.path=save.path)
-
-pidp_sample <- sample(unique(income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
-income.spag.sample <- income.spag[which(income.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(income.spag.sample, 'hh_income',
+# raw.inc <- raw.dat %>%
+#   select(pidp, age, time, hh_income)
+# base.inc <- base.dat %>%
+#   select(pidp, age, time, hh_income)
+# 
+# income.spag <- rbind(raw.inc, base.inc)
+# 
+# density_ridges(income.spag, 'hh_income',
+#                save=shall.we.save, 
+#                save.path=save.path)
+# 
+# pidp_sample <- sample(unique(income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
+# income.spag.sample <- income.spag[which(income.spag$pidp %in% pidp_sample), ]
+# spaghetti_plot(income.spag.sample, 'hh_income',
+#                save = shall.we.save,
+#                save.path = save.path)
+# spaghetti_highlight_max_plot(income.spag.sample, 'hh_income',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.inc, base.inc, income.spag)
+```
+
+## SF_12_MCS
+
+```{r}
+# sf12 boxplot handovers
+handover_boxplots(raw.dat, base.dat, 'SF_12_MCS')
+handover_lineplots(raw.dat, base.dat, "SF_12_MCS")
+```
+
+### Spaghetti
+
+```{r}
+raw.sf12.m <- raw.dat %>%
+  select(pidp, age, time, SF_12_MCS)
+base.sf12.m <- base.dat %>%
+  select(pidp, age, time, SF_12_MCS)
+
+sf12.m.spag <- rbind(raw.sf12.m, base.sf12.m)
+
+# sf12.m.spag.sample <- sf12.m.spag[which(sf12.m.spag$pidp %in% pidp_sample), ]
+# spaghetti_plot(sf12.m.spag.sample, 'SF_12_MCS',
+#                save = shall.we.save,
+#                save.path = save.path)
+# spaghetti_highlight_max_plot(sf12.m.spag.sample, 'SF_12_MCS',
+#                save = shall.we.save,
+#                save.path = save.path)
+
+density_ridges(sf12.m.spag, "SF_12_MCS", 
                save = shall.we.save, 
                save.path = save.path)
-spaghetti_highlight_max_plot(income.spag.sample, 'hh_income',
+
+rm(raw.sf12.m, base.sf12.m, sf12.m.spag, sf12.m.spag.sample)
+```
+
+## SF_12_PCS
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'SF_12_PCS')
+handover_lineplots(raw.dat, base.dat, "SF_12_PCS")
+```
+
+### Spaghetti
+
+```{r}
+raw.sf12.p <- raw.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+base.sf12.p <- base.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+
+sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)
+
+spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
                save = shall.we.save,
@@
 
-rm(raw.inc, base.inc, income.spag)
-```
-
-## Net Income & Rent & Mortgage
-
-```{r yearly_energy}
-# get required variables. 
-raw.inc <- raw.dat %>%
-  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
-base.inc <- base.dat %>%
-  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
-
-# net household income. 
-handover_boxplots(raw.inc, base.inc, 'net_hh_income')
-handover_lineplots(raw.inc, base.inc, "net_hh_income")
-inc.spag<-rbind(raw.inc, base.inc)
-density_ridges(inc.spag, 'net_hh_income',
-               save=TRUE, 
-               save.path=save.path)
-
-# rent
-handover_boxplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], 'hh_rent')
-handover_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
-density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
-               save=TRUE, 
-               save.path=save.path)
-
-# mortgage
-handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], 'hh_mortgage')
-handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
-density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
-               save=TRUE, 
-               save.path=save.path)
-
-#council tax
-handover_boxplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], 'council_tax')
-handover_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
-density_ridges(inc.spag[which(inc.spag$council_tax>1), ], 'council_tax',
-               save=TRUE, 
-               save.path=save.path)
-
-# oecd equivalence scale. (NOT TRANSITIONED YET. REQUIRES LEAVING THE NEST MODULE.. )
-handover_boxplots(raw.inc, base.inc, 'oecd_equiv')
-handover_lineplots(raw.inc, base.inc, 'oecd_equiv')
-density_ridges(inc.spag, 'oecd_equiv',
-               save=TRUE, 
-               save.path=save.path)
-
-# tidy up.
-rm(raw.inc, base.inc, inc.spag)
-```
-
-## Yearly energy
-
-```{r net_income}
-# get required variables. 
-raw.energy <- raw.dat %>%
-  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)
-base.energy <- base.dat %>%
-  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)
-
-# gas expenditure
-handover_boxplots(raw.energy, base.energy, 'yearly_gas')
-handover_lineplots(raw.energy, base.energy, "yearly_gas")
-#inc.spag<-rbind(raw.inc, base.inc)
-#density_ridges(inc.spag, 'yearly_gas',
-#               save=TRUE, 
-#               save.path=save.path)
-
-# yearly electric
-handover_boxplots(raw.energy, base.energy, 'yearly_electric')
-handover_lineplots(raw.energy, base.energy, "yearly_electric")
-#density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
-#               save=TRUE, 
-#               save.path=save.path)
-
-# yearly energy
-handover_boxplots(raw.energy, base.energy, 'yearly_energy')
-handover_lineplots(raw.energy, base.energy, "yearly_energy")
-#density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
-#               save=TRUE, 
-#               save.path=save.path)
-
-# tidy up.
-rm(raw.energy, base.energy)#, inc.spag)
-```
-
-## SF12
-
-```{r}
-# sf12 boxplot handovers
-handover_boxplots(raw.dat, base.dat, 'SF_12')
-handover_lineplots(raw.dat, base.dat, "SF_12")
-# 
-# raw.sf12 <- raw.dat %>% 
-#   dplyr::select(pidp, time, SF_12) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.sf12 <- base.dat %>%
-#   dplyr::select(pidp, time, SF_12) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# # merge before plot
-# sf12 <- rbind(raw.sf12, base.sf12)
-# 
-# # Now plot
-# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-#   geom_smooth() +
-#   #geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
-#   xlab('Year') +
-#   ylab('SF12')
-# 
-# ## Try a version where final_US is limited to only those present from wave 1 
-# # onwards because the sample refreshments are messing with the plot
-# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-# 
-# raw.sf12.2 <- raw.dat %>% 
-#   dplyr::select(pidp, time, SF_12) %>%
-#   filter(pidp %in% raw.sf12.wave1) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.sf12.2 <- base.dat %>%
-#   dplyr::select(pidp, time, SF_12) %>%
-#   filter(pidp %in% raw.sf12.wave1) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
-# 
-# # Now plot
-# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-#   geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
-#   xlab('Year') +
-#   ylab('SF12')
-# 
-# if (shall.we.save) {
-#   ggsave(filename = 'SF12_wav1.png',
-#        plot = last_plot(),
-#        path = save.path)
-# }
-# 
-# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
-```
-
-### Spaghetti
-
-```{r}
-raw.sf12 <- raw.dat %>%
-  select(pidp, age, time, SF_12)
-base.sf12 <- base.dat %>%
-  select(pidp, age, time, SF_12)
-
-sf12.spag <- rbind(raw.sf12, base.sf12)
-
-sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(sf12.spag.sample, 'SF_12',
+density_ridges(sf12.p.spag, "SF_12_PCS", 
                save = shall.we.save, 
                save.path = save.path)
-spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(sf12.spag, "SF_12", 
-               save = T, 
-               save.path = save.path)
-
-rm(raw.sf12, base.sf12, sf12.spag)
+
+rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
+```
+
+### Histograms
+
+I have a hypothesis that the longer we run through simulation, the more simulants are predicted a negative PCS value which is then clipped to a 0.
+Histograms over a few snapshots of time should show if this is happening.
+
+```{r}
+pcs.2021 <- base.dat %>%
+  select(pidp, time, SF_12_PCS) %>%
+  filter(time == 2021)
+
+# pcs.2022 <- base.dat %>%
+#   select(pidp, time, SF_12_PCS) %>%
+#   filter(time == 2022)
+
+pcs.2025 <- base.dat %>%
+  select(pidp, time, SF_12_PCS) %>%
+  filter(time == 2025)
+
+pcs.2030 <- base.dat %>%
+  select(pidp, time, SF_12_PCS) %>%
+  filter(time == 2030)
+
+pcs.2036 <- base.dat %>%
+  select(pidp, time, SF_12_PCS) %>%
+  filter(time == 2036)
+
+merged <- rbind(pcs.2021, pcs.2025, pcs.2030, pcs.2036)
+merged$time <- as.factor(merged$time)
+
+ggplot(merged, aes(x = SF_12_PCS, group = time, colour = time, fill = time)) +
+  geom_histogram() +
+  labs(title = 'Distribution of SF_12_PCS')
+
+ggplot(merged, aes(x = SF_12_PCS, group = time, colour = time, fill = time)) +
+  geom_freqpoly() +
+  labs(title = 'Distribution of SF_12_PCS', subtitle = 'Count')
+
+ggplot(merged, aes(x = SF_12_PCS, y = after_stat(density), group = time, colour = time, fill = time)) +
+  geom_freqpoly() +
+  labs(title = 'Distribution of SF_12_PCS', subtitle = 'Density')
 ```
@@
 
-## Housing Tenure
-
-```{r}
-raw.tenure <- raw.dat %>%
-  dplyr::select(pidp, time, housing_tenure) %>%
-  group_by(time, housing_tenure) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.tenure <- base.dat %>%
-  dplyr::select(pidp, time, housing_tenure) %>%
-  group_by(time, housing_tenure) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-tenure <- rbind(raw.tenure, base.tenure)
-tenure$housing_tenure <- as.factor(tenure$housing_tenure)
-
-# Now plot
-ggplot(data = tenure, mapping = aes(x = time, y = n, group = housing_tenure, colour = housing_tenure)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Tenure', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-tenure.norm <- tenure %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = tenure.norm, mapping = aes(x = time, y = prct, fill=housing_tenure)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Tenure') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'housing_tenure.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.tenure, base.tenure, tenure, tenure.norm)
-```
-
 ## Neighbourhood Safety
@@
 
-## Physical Health
-
-NOTE: At present, physical health is not predicted or transitioned.
-
-```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.phealth <- raw.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
+## Tobacco
+
+### ncigs mean
+
+TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11
+
+```{r}
+#  nutriton quality line/boxplots.
+handover_boxplots(raw.dat, base.dat, 'ncigs')
+handover_lineplots(raw.dat, base.dat, 'ncigs')
+
+test.pidps <- raw.dat %>%
+  select(pidp)
+
+test.base <- base.dat %>%
+  filter(pidp %in% test.pidps$pidp)
+
+handover_boxplots(raw.dat, test.base, 'ncigs')
+handover_lineplots(raw.dat, test.base, 'ncigs')
+```
+
+### Spaghetti
+
+```{r}
+# raw.nut <- raw.dat %>%
+#   select(pidp, age, time, ncigs)
+# base.nut <- base.dat %>%
+#   select(pidp, age, time, ncigs)
+# 
+# nut.spag <- rbind(raw.nut, base.nut)
+# 
+# spaghetti_plot(nut.spag, 'ncigs',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# 
+# density_ridges(nut.spag, "ncigs",
+#                save = FALSE,
+#                save.path = save.path)
+# 
+# rm(raw.nut, base.nut, nut.spag)
+```
+
+### ncigs Max
+
+```{r}
+raw.ncigs_max <- raw.dat %>%
+  select(pidp, time, ncigs) %>%
   group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
+  summarise(max_ncigs = max(ncigs)) %>%
   mutate(source = 'final_US')
 
-base.phealth <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
+base.ncigs_max <- base.dat %>%
+  dplyr::select(pidp, time, ncigs) %>%
   group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
+  summarise(max_ncigs = max(ncigs)) %>%
   mutate(source = 'baseline_output')
 
-# merge before plot
-phealth <- rbind(raw.phealth, base.phealth)
+max_ncigs <- rbind(raw.ncigs_max, base.ncigs_max)
 
 # Now plot
-ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
+ggplot(data = max_ncigs, mapping = aes(x = time, y = max_ncigs, group = source, colour = source)) +
   geom_line() +
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health', subtitle = 'Full Sample') +
+  labs(title = 'Max ncigs', subtitle = 'Full Sample') +
   xlab('Year') +
   ylab('Average')
-
-## Try a version where final_US is limited to only those present from wave 1
-# onwards because the sample refreshments are messing with the plot
-raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.phealth2 <- raw.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.phealth2 <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-phealth2 <- rbind(raw.phealth2, base.phealth2)
-
-# Now plot
-ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health') +
-  xlab('Year') +
-  ylab('Average')
-
-if (shall.we.save) {
-  ggsave(filename = 'physical_health_wav1.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-#raw.phealth.check <- raw.dat %>%
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
-
-#base.phealth.check <- base.dat %>%
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
-
-rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2)
-#rm(raw.phealth.check, base.phealth.check)
+```
+
+## Physical Health
+
+NOTE: At present, physical health is not predicted or transitioned.
+
+```{r}
+handover_continuous(raw.dat, base.dat, var = 'phealth')
+handover_boxplots(raw.dat, base.dat, 'phealth')
+handover_lineplots(raw.dat, base.dat, 'phealth')
 ```
@@
 ```{r}
-raw.s <- raw.parity %>%
-  select(pidp, age, time, nkids_ind)
-base.s <- base.parity %>%
-  select(pidp, age, time, nkids_ind)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids_ind',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.parity %>%
+#   select(pidp, age, time, nkids_ind)
+# base.s <- base.parity %>%
+#   select(pidp, age, time, nkids_ind)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'nkids_ind',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
+```
+
+## Alcohol (AUDITC)
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
+
+raw.2020.alc <- raw.dat %>% 
+  filter(time == 2020) %>%
+  group_by(auditc) %>%
+  summarise(n = n()) %>%
+  mutate(prop = n / sum(n))
+
+```
+
+## Physical Activity
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
+
+raw.2020.phys <- raw.dat %>% 
+  filter(time == 2020) %>%
+  group_by(active) %>%
+  summarise(n = n()) %>%
+  mutate(prop = n / sum(n))
+```
+
+## Material Deprivation
+
+```{r}
+#handover_boxplots(raw.dat, base.dat, 'matdep')
+#handover_lineplots(raw.dat, base.dat, 'matdep')
+handover_ordinal(raw.dat, base.dat, var = 'matdep', save = shall.we.save)
+
+raw.dat$chron_disease <- as.factor(raw.dat$chron_disease)
+raw.2020.cd <- raw.dat %>%
+  select(time, chron_disease, age) %>%
+  filter(time == 2020) %>%
+  mutate(age_group = cut(age, 
+                         breaks = c(0,20,30,40,50,60,70,80,90,100,120),
+                         labels = c('16-19', '20-30', '30-40', '40-50', '50-60', '60-70', '70-80', '80-90', '90-100', '100+'))) %>%
+  group_by(age_group, chron_disease) %>%
+  summarise(n = n()) %>%
+  group_by(age_group) %>%
+  mutate(prop = n / sum(n),
+         perc = prop * 100)
+  # mutate(prop = n() / sum(n),
+  #        perc = prop * 100)
+
+raw.2020.cd
+
+ggplot(raw.2020.cd, aes(x = age_group, y = perc, group = chron_disease, colour = chron_disease, fill = chron_disease)) +
+  geom_col(position = 'dodge') +
+  xlab('Age Group') +
+  ylab('Proportion')
+```
+
+```{r}
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, matdep) %>%
+#   filter(!matdep %in% miss.values)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, matdep) %>%
+#   filter(!matdep %in% miss.values)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'matdep',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
+```
+
+## Chronic Disease
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'chron_disease', save = shall.we.save)
+```
+
+```{r}
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, chron_disease) %>%
+#   filter(!chron_disease %in% miss.values)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, chron_disease) %>%
+#   filter(!chron_disease %in% miss.values)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spag$chron_disease <- as.numeric(spag$chron_disease)
+# 
+# spaghetti_plot(spag, 'chron_disease',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# density_ridges(spag, 'chron_disease',
+#                save=shall.we.save, 
+#                save.path=save.path)
+# 
+# pidp_sample <- sample(unique(spag$pidp), size=nrow(raw.s)/10, replace=FALSE)
+# spag.sample <- spag[which(spag$pidp %in% pidp_sample), ]
+# spaghetti_plot(spag.sample, 'chron_disease',
+#                save = shall.we.save,
+#                save.path = save.path)
+# spaghetti_highlight_max_plot(spag.sample, 'chron_disease',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, hourly_wage)
-base.s <- base.dat %>%
-  select(pidp, age, time, hourly_wage)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-# now a version limited to 0-100
-spag <- spag %>%
-  filter(hourly_wage <= 300)
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-```{r}
-# some basic statistics about hourly_wage variable
-print("Some basic statistics on hourly_wage. These are all for 2020.")
-raw.2020 <- raw.dat %>% filter(time == 2020)
-print('All living people in 2020')
-print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
-# number individuals with an hourly_wage > 0
-print('People not in work')
-print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
-
-# Number in work
-print('People in work')
-print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
-
-# Extreme hourly_wage values
-print('Extreme hourly wage values: HIGH')
-print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
-print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
-print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
-print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
-print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
-print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
-
-raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
-print('Extreme hourly wage values: LOW (non-zero)')
-print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
-print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
-print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
-print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, hourly_wage)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, hourly_wage)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'hourly_wage',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# # now a version limited to 0-100
+# spag <- spag %>%
+#   filter(hourly_wage <= 300)
+# spaghetti_plot(spag, 'hourly_wage',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
+```
+
+```{r}
+# # some basic statistics about hourly_wage variable
+# print("Some basic statistics on hourly_wage. These are all for 2020.")
+# raw.2020 <- raw.dat %>% filter(time == 2020)
+# print('All living people in 2020')
+# print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
+# # number individuals with an hourly_wage > 0
+# print('People not in work')
+# print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+# print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
+# 
+# # Number in work
+# print('People in work')
+# print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+# print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
+# 
+# # Extreme hourly_wage values
+# print('Extreme hourly wage values: HIGH')
+# print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
+# print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
+# print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
+# print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
+# print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
+# print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
+# 
+# raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
+# print('Extreme hourly wage values: LOW (non-zero)')
+# print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
+# print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
+# print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
+# print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
 ```

### 2024-02-26 minos/validation/handovers.Rmd

--- 2024-02-22 minos/validation/handovers.Rmd
@@
 rm(raw.inc, base.inc, income.spag)
-```
-
-## Net Income & Rent & Mortgage
-
-```{r yearly_energy}
-# get required variables. 
-raw.inc <- raw.dat %>%
-  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
-base.inc <- base.dat %>%
-  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
-
-# net household income. 
-handover_boxplots(raw.inc, base.inc, 'net_hh_income')
-handover_lineplots(raw.inc, base.inc, "net_hh_income")
-inc.spag<-rbind(raw.inc, base.inc)
-density_ridges(inc.spag, 'net_hh_income',
-               save=TRUE, 
-               save.path=save.path)
-
-# rent
-handover_boxplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], 'hh_rent')
-handover_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
-density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
-               save=TRUE, 
-               save.path=save.path)
-
-# mortgage
-handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], 'hh_mortgage')
-handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
-density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
-               save=TRUE, 
-               save.path=save.path)
-
-#council tax
-handover_boxplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], 'council_tax')
-handover_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
-density_ridges(inc.spag[which(inc.spag$council_tax>1), ], 'council_tax',
-               save=TRUE, 
-               save.path=save.path)
-
-# oecd equivalence scale. (NOT TRANSITIONED YET. REQUIRES LEAVING THE NEST MODULE.. )
-handover_boxplots(raw.inc, base.inc, 'oecd_equiv')
-handover_lineplots(raw.inc, base.inc, 'oecd_equiv')
-density_ridges(inc.spag, 'oecd_equiv',
-               save=TRUE, 
-               save.path=save.path)
-
-# tidy up.
-rm(raw.inc, base.inc, inc.spag)
-```
-
-## Yearly energy
-
-```{r net_income}
-# get required variables. 
-raw.energy <- raw.dat %>%
-  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)
-base.energy <- base.dat %>%
-  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)
-
-# gas expenditure
-handover_boxplots(raw.energy, base.energy, 'yearly_gas')
-handover_lineplots(raw.energy, base.energy, "yearly_gas")
-#inc.spag<-rbind(raw.inc, base.inc)
-#density_ridges(inc.spag, 'yearly_gas',
-#               save=TRUE, 
-#               save.path=save.path)
-
-# yearly electric
-handover_boxplots(raw.energy, base.energy, 'yearly_electric')
-handover_lineplots(raw.energy, base.energy, "yearly_electric")
-#density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
-#               save=TRUE, 
-#               save.path=save.path)
-
-# yearly energy
-handover_boxplots(raw.energy, base.energy, 'yearly_energy')
-handover_lineplots(raw.energy, base.energy, "yearly_energy")
-#density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
-#               save=TRUE, 
-#               save.path=save.path)
-
-# tidy up.
-rm(raw.energy, base.energy)#, inc.spag)
 ```
@@
   dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
-  filter(time > 2013) %>%
+  filter(time > 2013 & child_ages != 'childless') %>%
   group_by(time, hidp) %>%

### 2024-02-27 minos/validation/housing_handovers.Rmd
tweaking so modules look sensible. housing handovers.

--- 2024-02-26 minos/validation/handovers.Rmd
@@
     intervention: ''
-title: "Handovers"
+title: "Housing Default Handovers"
 output:
@@
 
-#out.path <- here::here('output', 'default_config/')
 out.path <- here::here('output', 'energy_default_config/')

### 2024-02-27 minos/outcomes/QALY_comparison2.Rmd
Added a generic QALY comparison RNotebook with parameters for the experiment, baseline, and intervention so we can run multiple combinations of these things with the same script

--- 2023-11-20 minos/outcomes/QALY_comparison.Rmd
@@
 ---
-title: "QALY Comparisons - Energy Crisis Interventions - NoSupport Baseline"
+params:
+  experiment: ''
+  base: ''
+  intervention: ''
+title: "QALY Comparisons - r`experiment` - r`intervention` - r`baseline`"
 output:
@@
     code_folding: hide
-params: 
-  experiment: experiment 
-  baseline: baseline 
-  intervention: intervention
-  intervention_label: intervention_label
 ---
@@
 
+## Parameters
+
+```{r}
+# experiment <- params$experiment
+# base <- params$base
+# intervention <- params$intervention
+
+experiment <- 'default_config'
+baseline <- 'baseline'
+intervention <- '100All'
+```
+
 ## Data
 
-```{r read_data, include=False}
-experiment <- params$experiment
-baseline <- params$baseline
-intervention <- params$intervention
-intervention_label <- params$intervention_label
-
-out.path <- here::here('output', args$experiment)
+```{r}
+# # read in QALY files for baseline and interventions
+out.path <- here::here('output', experiment)
 
@@
 
+# combine the dataframes
 combined <- rbind(base, int)
-```
-
-```{r}
-# # read in QALY files for baseline and interventions
-#out.path <- here::here('output', 'default_config')
-#out.path <- here::here('output', 'glasgow_scaled')
-out.path <- here::here('output', 'SF12_uk_scaled')
-
-base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
-support.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownlift'))
-noSupport.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownliftNoSupport'))
-
-base <- read.csv(paste0(base.path, 'qalys.csv'))
-support <- read.csv(paste0(support.path, 'qalys.csv'))
-noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))
-
-# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
-# 
-# base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
-# support <- read.csv(paste0(out.path, 'qalys_support.csv'))
-# noSupport <- read.csv(paste0(out.path, 'qalys_nosupport.csv'))
-
-# combine the dataframes
-combined <- rbind(support, noSupport)
 ```
@@
               values_from = 'total_boost') %>%
-  mutate(diff.boost = energyDownlift - energyDownliftNoSupport)
+  mutate(diff.boost = .data[[intervention]] - .data[[baseline]])
 
@@
           base.name = baseline,
-          int = int,
+          intervention = int,
           int.name = intervention)
@@
               QALY_value = 60000,  # QALY value == £60,000
-              int.label <- intervention_label)
+              int.label <- intervention)
 ```
@@
      QALY_value = 60000,
-     int.label = intervention_label)
+     int.label = intervention)
 ```
@@
                   int.name = intervention,
-                  int.label = intervention_label)
+                  int.label = intervention)
 ```
-
-```{r}
-
-```

### 2024-02-29 minos/outcomes/QALY_comparison2.Rmd
Slight tweak to the QALY calculation and tidied up the QALY outcomes makefile. Also improvements to the generic visualisation script

@@
 params:
-  experiment: ''
-  base: ''
-  intervention: ''
-title: "QALY Comparisons - r`experiment` - r`intervention` - r`baseline`"
+  experiment: 'default_config/'
+  base: 'baseline'
+  intervention: '50All'
+title: "QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`"
 output:
@@
 ```{r}
-# experiment <- params$experiment
-# base <- params$base
-# intervention <- params$intervention
-
-experiment <- 'default_config'
-baseline <- 'baseline'
-intervention <- '100All'
+experiment <- params$experiment
+baseline <- params$base
+intervention <- params$intervention
+# 
+# experiment <- 'default_config'
+# baseline <- 'baseline'
+# intervention <- '100All'
 ```

### 2024-02-29 minos/validation/housing_handovers.Rmd
getting manchester scaled pop and diff map working

@@
 
+net.income.spag <- rbind(raw.inc, base.inc)
+
+density_ridges(net.income.spag, 'net_hh_income',
+               save=TRUE, 
+               save.path=save.path)
+
+pidp_sample <- sample(unique(net.income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
+net.income.spag.sample <- net.income.spag[which(net.income.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(net.income.spag.sample, 'net_hh_income',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(net.income.spag.sample, 'net_hh_income',
+               save = shall.we.save,
+               save.path = save.path)
+
 # net household income. 

### 2024-02-29 minos/modules/net_income.py

@@ -160,7 +160,7 @@ class lmmYJNetIncome(Base):
         newWavenetIncome['net_hh_income'] -= 175
 
         newWavenetIncome['net_hh_income'] = newWavenetIncome.groupby('hidp')['net_hh_income'].transform("mean")
-        newWavenetIncome['net_hh_income'] = newWavenetIncome['net_hh_income'].clip(-1000, 12000)
+        newWavenetIncome['net_hh_income'] = newWavenetIncome['net_hh_income'].clip(-1000, 30000)
 
 
         newWavenetIncome['net_hh_income_diff'] = newWavenetIncome['net_hh_income'] - pop['net_hh_income']
@@ -185,8 +185,10 @@ class lmmYJNetIncome(Base):
 
         income_mean = np.median(newWavenetIncome["hh_income"])
         std_ratio = (np.std(pop['hh_income']) / np.std(newWavenetIncome["hh_income"]))
-        newWavenetIncome["hh_income"] *= std_ratio
-        newWavenetIncome["hh_income"] -= ((std_ratio - 1) * income_mean)
+        #newWavenetIncome["hh_income"] *= std_ratio
+        #newWavenetIncome["hh_income"] -= ((std_ratio - 1) * income_mean)
+        #newWavenetIncome['hh_income'] = newWavenetIncome['hh_income'].clip(-2500, 6000)
+        #newWavenetIncome['hh_income'] -= 250
 
         newWavenetIncome['hh_income_diff'] = newWavenetIncome['hh_income'] - pop['hh_income']
         newWavenetIncome['FP10'] = (newWavenetIncome['yearly_energy'] / newWavenetIncome['hh_income'] > 0.1)
@@ -213,7 +215,7 @@ class lmmYJNetIncome(Base):
                                                                           dependent='net_hh_income_new',
                                                                           yeo_johnson=True,
                                                                           reflect=False,
-                                                                          noise_std=3)  # 0.45 for yj. 100? for non yj.
+                                                                          noise_std=10)  # 0.45 for yj. 100? for non yj.
         # get new hh income diffs and update them into history_data.
         # self.update_history_dataframe(pop, self.year-1)
         # new_history_data = self.history_data.loc[self.history_data['time']==self.year].index # who in current_year
@@ -235,7 +237,6 @@ class lmmYJNetIncome(Base):
         """
[…]

### 2024-03-04 minos/outcomes/QALY_comparison2.Rmd
Updated the QALY calculation functions in R to move away from smoothed plots to calculated 95% confidence intervals

@@
 
-#workingDir <- "/home/luke/Documents/WORK/MINOS/"
-workingDir <- normalizePath('../')
+workingDir <- "/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_SCP_28Feb/QALY_analysis_SCP_test/"
+#workingDir <- normalizePath('../')
 knitr::opts_knit$set(root.dir = workingDir)
@@
 ```{r}
-source(here::here('minos', 'utils_datain.R'))
-source(here::here('minos', 'utils_qaly.R'))
+source_dir <- '/home/luke/Documents/WORK/MINOS/Minos/minos'
+#datain <- here::here(source_dir, 'utils_datain.R')
+
+source(here::here(source_dir, 'utils_datain.R'))
+source(here::here(source_dir, 'utils_qaly.R'))
 ```
@@
 ```{r}
-# # read in QALY files for baseline and interventions
+# read in QALY files for baseline and interventions
 out.path <- here::here('output', experiment)
@@
 
+TESTING TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY 
+```{r}
+# base <- read.csv('qalys_baseline.csv')
+# int <- read.csv('qalys_25All.csv')
+# 
+# combined <- rbind(base, int)
+# 
+# baseline <- 'baseline'
+# intervention <- '25All'
+```
+TESTING TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY
+
 # Intervention Information
@@
 ```{r}
-ggplot(combined, aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
+combined.pop_boosted <- combined %>%
+  group_by(year, run_id, intervention) %>%
+  summarise(pop_boosted = sum(pop_boosted))
+
+ggplot(combined.pop_boosted, aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
   geom_smooth() +
@@
               int.name = intervention,
-              QALY_value = 60000,  # QALY value == £60,000
+              QALY_value = 70000,  # QALY value == £60,000
               int.label <- intervention)
@@
      int.name = intervention,
-     QALY_value = 60000,
+     QALY_value = 70000,
      int.label = intervention)

### 2024-03-04 minos/outcomes/QALY_comparison2.Rmd
Removed start year from ICER calculation as cant calculate ICER with no intervention

@@
 
-workingDir <- "/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_SCP_28Feb/QALY_analysis_SCP_test/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_SCP_28Feb/QALY_analysis_SCP_test/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/tmp/"
 #workingDir <- normalizePath('../')
@@
 ```{r}
-experiment <- params$experiment
-baseline <- params$base
-intervention <- params$intervention
+# experiment <- params$experiment
+# baseline <- params$base
+# intervention <- params$intervention
 # 
@@
 # intervention <- '100All'
+
+list.files()
 ```
@@
 ```{r}
-# read in QALY files for baseline and interventions
-out.path <- here::here('output', experiment)
-
-base.path <- get_latest_runtime_subdirectory(here::here(out.path, baseline))
-int.path <- get_latest_runtime_subdirectory(here::here(out.path, intervention))
-
-base <- read.csv(paste0(base.path, 'qalys.csv'))
-int <- read.csv(paste0(int.path, 'qalys.csv'))
-
-# combine the dataframes
-combined <- rbind(base, int)
+# # read in QALY files for baseline and interventions
+# out.path <- here::here('output', experiment)
+# 
+# base.path <- get_latest_runtime_subdirectory(here::here(out.path, baseline))
+# int.path <- get_latest_runtime_subdirectory(here::here(out.path, intervention))
+# 
+# base <- read.csv(paste0(base.path, 'qalys.csv'))
+# int <- read.csv(paste0(int.path, 'qalys.csv'))
+# 
+# # combine the dataframes
+# combined <- rbind(base, int)
 ```
@@
 ```{r}
-# base <- read.csv('qalys_baseline.csv')
-# int <- read.csv('qalys_25All.csv')
-# 
-# combined <- rbind(base, int)
-# 
-# baseline <- 'baseline'
-# intervention <- '25All'
+base <- read.csv('qalys_base.csv')
+int <- read.csv('qalys_25All.csv')
+
+combined <- rbind(base, int)
+
+baseline <- 'baseline'
+intervention <- '25All'
 ```

### 2024-03-04 minos/outcomes/QALY_comparison2.Rmd
Third time lucky. Switched some paths and constants back from testing to normal operation

--- 2024-03-04 minos/outcomes/QALY_comparison2.Rmd
@@
 
-workingDir <- "/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_SCP_28Feb/QALY_analysis_SCP_test/"
-#workingDir <- normalizePath('../')
+#workingDir <- "/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_SCP_28Feb/QALY_analysis_SCP_test/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/tmp/"
+workingDir <- normalizePath('../')
 knitr::opts_knit$set(root.dir = workingDir)
@@
 ```{r}
-source_dir <- '/home/luke/Documents/WORK/MINOS/Minos/minos'
+#source_dir <- '/home/luke/Documents/WORK/MINOS/Minos/minos'
 #datain <- here::here(source_dir, 'utils_datain.R')
 
-source(here::here(source_dir, 'utils_datain.R'))
-source(here::here(source_dir, 'utils_qaly.R'))
+source(here::here('minos', 'utils_datain.R'))
+source(here::here('minos', 'utils_qaly.R'))
 ```
@@
 ```{r}
-# base <- read.csv('qalys_baseline.csv')
+# base <- read.csv('qalys_base.csv')
 # int <- read.csv('qalys_25All.csv')

### 2024-03-05 minos/outcomes/QALY_comparison2.Rmd
Small tweaks and better reporting of large values (formatted with commas)

@@
 ```{r}
-experiment <- params$experiment
-baseline <- params$base
-intervention <- params$intervention
+# experiment <- params$experiment
+# baseline <- params$base
+# intervention <- params$intervention
 # 
-# experiment <- 'default_config'
-# baseline <- 'baseline'
-# intervention <- '100All'
+experiment <- 'default_config'
+baseline <- 'baseline'
+intervention <- '50All'
 ```
@@
   summarise(pop_boosted = sum(pop_boosted))
+
+print(paste("There are", sum(is.na(combined.pop.boosted$pop_boosted)), "NA pop_boosted values in combined.pop.boosted.", sep = ' '))
 

### 2024-03-05 minos/outcomes/QALY_comparison2.Rmd
Typo in a new print statement

--- 2024-03-04 minos/outcomes/QALY_comparison2.Rmd
@@
 # baseline <- 'baseline'
-# intervention <- '100All'
+# intervention <- '50All'
 ```
@@
   summarise(pop_boosted = sum(pop_boosted))
+
+print(paste("There are", sum(is.na(combined.pop_boosted$pop_boosted)), "NA pop_boosted values in combined.pop.boosted.", sep = ' '))
 

### 2024-03-06 minos/transitions/energy_price_forecasting.Rmd.R
fine tuning and getting energy price forecasting working on new pc

@@ -1,0 +1,104 @@
+library(forecast)
+library(ggfortify)
+library(readxl)
+library(tidyr)
+source("minos/transitions/utils.R")
+
+process_input_data <- function(dataset, data.column, new.name){
+  
+  subvector <- dataset[, c(data.column)]
+  subvector <- drop_na(subvector)
+  colnames(subvector) <- c(new.name)
+  return(subvector)
+}
+#energy_data <- readxl::read_xlsx("../data/energy_prices_simpler.xlsx")
+## primary energy material sources. fuel and motor oil omitted due to no UKHLS data. 
+#electricity_vector <- process_input_data(energy_data, "Real terms price indices: Electricity [Note 3]", 'electricity')
+#gas_vector <- process_input_data(energy_data, "Real terms price indices: Gas [Note 3]", "gas")
+#solid_fuel_vector <- process_input_data(energy_data, "Real terms price indices: Solid fuels [Note 3]", "solid_fuel")
+#liquid_fuel_vector <- process_input_data(energy_data, "Real terms price indices: Liquid fuels [Note 3]", "liquid_fuel")
+energy_data <- readxl::read_xlsx("../data/energy_prices_simpler_yearly.xlsx")
+# primary energy material sources. fuel and motor oil omitted due to no UKHLS data. 
+electricity_vector <- process_input_data(energy_data, "Real price indices: Electricity [Note 3]", 'electricity')
+gas_vector <- process_input_data(energy_data, "Real price indices: Gas [Note 3]", "gas")
+solid_fuel_vector <- process_input_data(energy_data, "Real price indices: Solid fuels [Note 3]", "solid_fuel")
+liquid_fuel_vector <- process_input_data(energy_data, "Real price indices: Liquid fuels [Note 3]", "liquid_fuel")
+# aggregate of the above 4. 
+#domestic_fuel_vector <- process_input_data(energy_data, "Real terms price indices: Domestic fuels\r\n[Note 1, 3]", "domestic_fuel")
+plot(electricity_vector$electricity, type='l', xlab="Quarter (0 = Q1 1990", ylab=c("Real Electricity Price indices"), main="Electricity")
+plot(gas_vector$gas, type='l', xlab="Quarter (0 = Q1 1990", ylab=c("Real Gas Price indices"), main="Gas")
[…]

### 2024-03-06 minos/validation/handovers.Rmd
Tweaks to data in and qaly visualisation functions. Added a script for checking pathway response to intervention

--- 2024-02-23 minos/validation/handovers.Rmd
@@
 
-# sf12.m.spag.sample <- sf12.m.spag[which(sf12.m.spag$pidp %in% pidp_sample), ]
-# spaghetti_plot(sf12.m.spag.sample, 'SF_12_MCS',
-#                save = shall.we.save,
-#                save.path = save.path)
-# spaghetti_highlight_max_plot(sf12.m.spag.sample, 'SF_12_MCS',
-#                save = shall.we.save,
-#                save.path = save.path)
+#sf12.m.spag.sample <- sf12.m.spag[which(sf12.m.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(sf12.m.spag, 'SF_12_MCS',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(sf12.m.spag, 'SF_12_MCS',
+               save = shall.we.save,
+               save.path = save.path)
 

### 2024-03-06 minos/utils_qaly.R

@@ -615,7 +615,7 @@ intervention.cost.smooth <- function(base, base.name, int, int.name, int.label) 
     select(run_id, year, cost_difference) %>%
     mutate(intervention = int.name)
   
-  p2 <- ggplot(total.cost.byYear, aes(x = year, y = cost_difference, group = intervention, fill = intervention, colour = intervention)) +
+  p2 <- ggplot(total.cost.byYear, aes(x = year, y = cost_difference)) +
     geom_smooth() +
     labs(title = 'Intervention Cost by Year', subtitle = paste0(int.name, ' vs ', base.name))
   print(p2)
@@ -637,7 +637,7 @@ intervention.cost.smooth <- function(base, base.name, int, int.name, int.label) 
   
   p1 <- ggplot(total.cost, aes(x = intervention, y = cost_difference, group = intervention, fill = intervention, colour = intervention)) +
     geom_col() +
-    geom_errorbar(aes(ymin = cost_difference - margin, ymax = cost_difference + margin, width = 0.4, group = intervention)) +
+    geom_errorbar(aes(ymin = cost_difference - margin, ymax = cost_difference + margin, width = 0.4)) +
     labs(title = 'Total cost of intervention', subtitle = paste0(int.name, ' vs ', base.name)) +
     scale_y_continuous(label = comma)
   print(p1)

### 2024-03-08 minos/outcomes/QALY_comparison2.Rmd
Added some make targets for visualising QALY outputs for Glasgow Scaled simulation runs

@@
   base: 'baseline'
-  intervention: '50All'
+  intervention: ''
 title: "QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`"

### 2024-03-08 minos/outcomes/QALY_comparison2.Rmd
Removed default parameters from RNotebook as I think its causing problems on arc

@@
 params:
-  experiment: 'default_config/'
-  base: 'baseline'
+  experiment: ''
+  base: ''
   intervention: ''

### 2024-03-08 minos/outcomes/QALY_comparison2.Rmd
Parameterised the start year so we can handle synthetic 2020 starts alongside default 2020

@@
   intervention: ''
+  start.year: ''
 title: "QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`"
@@
 intervention <- params$intervention
+start.year <- params$start.year
 # 
@@
      QALY_value = 70000,
-     int.label = intervention)
+     int.label = intervention,
+     start.year = start.year)
 ```

### 2024-03-11 minos/outcomes/QALY_comparison2.Rmd
Removed reweighting of SF12 vars in QALY calculation as it caused problems. Not required for synthpop runs anyway

@@
 start.year <- params$start.year
-# 
-# experiment <- 'default_config'
+# # 
+# experiment <- 'glasgow_scaled'
 # baseline <- 'baseline'
 # intervention <- '50All'
+# start.year <- 2020
 ```
@@
 TESTING TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY
+
+# Sample Information
+
+```{r}
+
+```
 

### 2024-03-12 minos/outcomes/QALY_comparison2.Rmd
Refactored QALY_comparison2.Rmd to accept multiple interventions and visualise them together

--- 2024-03-08 minos/outcomes/QALY_comparison2.Rmd
@@
 ```{r}
-experiment <- params$experiment
-baseline <- params$base
-intervention <- params$intervention
-start.year <- params$start.year
-# 
-# experiment <- 'default_config'
-# baseline <- 'baseline'
-# intervention <- '50All'
+# experiment <- params$experiment
+# baseline <- params$base
+# intervention <- params$intervention
+# #intervention2 <- params$intervention2
+# start.year <- params$start.year
+# # 
+experiment <- 'glasgow_scaled'
+baseline <- 'baseline'
+ints <- c('50All', '50UniversalCredit')
+start.year <- 2020
 ```
@@
 
-base.path <- get_latest_runtime_subdirectory(here::here(out.path, baseline))
-int.path <- get_latest_runtime_subdirectory(here::here(out.path, intervention))
+expts <- c(baseline, ints)
 
-base <- read.csv(paste0(base.path, 'qalys.csv'))
-int <- read.csv(paste0(int.path, 'qalys.csv'))
+combined <- data.frame()
+for (expt in expts) {
+  path <- get_latest_runtime_subdirectory(here::here(out.path, expt))
+  data <- read.csv(paste0(path, 'qalys.csv'))
+  combined <- rbind(combined, data)
+}
+```
 
-# combine the dataframes
-combined <- rbind(base, int)
+```{r}
+# # read in QALY files for baseline and interventions
+# out.path <- here::here('output', experiment)
+# 
+# base.path <- get_latest_runtime_subdirectory(here::here(out.path, baseline))
+# int.path <- get_latest_runtime_subdirectory(here::here(out.path, intervention1))
+# 
+# if (intervention2 != '') {
+#   int2.path <- get_latest_runtime_subdirectory(here::here(out.path, intervention2))
+# }
+# 
+# base <- read.csv(paste0(base.path, 'qalys.csv'))
+# int <- read.csv(paste0(int.path, 'qalys.csv'))
+# 
+# # combine the dataframes
+# combined <- rbind(base, int)
 ```
@@
 
+# Sample Information
+
+```{r}
+
+```
+
 # Intervention Information
@@
 
-print(paste("There are", sum(is.na(combined.pop_boosted$pop_boosted)), "NA pop_boosted values in combined.pop.boosted.", sep = ' '))
+# print(paste("There are", sum(is.na(combined.pop_boosted$pop_boosted)), "NA pop_boosted values in combined.pop.boosted.", sep = ' '))
 
@@
               values_from = 'total_boost') %>%
-  mutate(diff.boost = .data[[intervention]] - .data[[baseline]])
+  mutate(across(all_of(ints), ~.x - .data[[baseline]], .names = "diff_{.col}")) %>%
+  select(run_id, year, contains('diff_')) %>%
+  pivot_longer(cols = contains('diff_'),
+               names_prefix = 'diff_',
+               names_to = 'scenario',
+               values_to = 'total_boost')
 
-ggplot(combined.diff, aes(x = year, y = diff.boost)) +
+ggplot(combined.diff, aes(x = year, y = total_boost, group = scenario, fill = scenario, color = scenario)) +
   geom_smooth() +
@@
   scale_y_continuous(label = comma)
-
-ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
-  geom_smooth() +
-  labs(title = 'Ratio of living to dead in output dataframe')
-
-## incidence of mortality
-deaths <- combined %>%
-  select(run_id, intervention, year, alive_pop, dead_pop) %>%
-  group_by(run_id, intervention) %>%
-  mutate(total_pop = alive_pop + dead_pop,
-         deaths_this_year = dead_pop - lag(dead_pop)) %>%
-  group_by(run_id, year, intervention) %>%
-  summarise(death_incidence = deaths_this_year / total_pop)
-
-ggplot(deaths, aes(x = year, y = death_incidence, group = intervention, colour = intervention)) +
-  geom_smooth() +
-  labs(title = 'Incidence of Mortality Comparison')
+# 
+# ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
+#   geom_smooth() +
+#   labs(title = 'Ratio of living to dead in output dataframe')
+# 
+# ## incidence of mortality
+# deaths <- combined %>%
+#   select(run_id, intervention, year, alive_pop, dead_pop) %>%
+#   group_by(run_id, intervention) %>%
+#   mutate(total_pop = alive_pop + dead_pop,
+#          deaths_this_year = dead_pop - lag(dead_pop)) %>%
+#   group_by(run_id, year, intervention) %>%
+#   summarise(death_incidence = deaths_this_year / total_pop)
+# 
+# ggplot(deaths, aes(x = year, y = death_incidence, group = intervention, colour = intervention)) +
+#   geom_smooth() +
+#   labs(title = 'Incidence of Mortality Comparison')
 ```
@@
 ```{r}
-QALY_comparison(base = base,
-                base.name = baseline,
-                int = int,
-                int.name = intervention)
+# QALY_comparison(base = base,
+#                 base.name = baseline,
+#                 int = int,
+#                 int.name = intervention)
+
+QALY_comparison(combined, ints)
 ```
@@
 ```{r}
-sf12.plots(base = base,
-           base.name = baseline,
-           int = int,
-           int.name = intervention)
+sf12.plots(combined, ints)
 ```
@@
 ```{r}
-auc.plots(base = base, 
-          base.name = baseline,
-          intervention = int,
-          int.name = intervention)
+auc.plots(combined, ints)
 ```
@@
 ```{r}
-cost.per.qaly(base = base,
-              base.name = baseline,
-              int = int,
-              int.name = intervention,
-              QALY_value = 70000,  # QALY value == £60,000
-              int.label <- intervention)
+# cost.per.qaly(base = base,
+#               base.name = baseline,
+#               int = int,
+#               int.name = intervention,
+#               QALY_value = 70000,  # QALY value == £70,000
+#               int.label <- intervention)
 ```
@@
 ```{r}
-ICER(base = base,
-     base.name = baseline,
-     int = int,
-     int.name = intervention,
+ICER(combined,
+     ints,
      QALY_value = 70000,
-     int.label = intervention,
      start.year = start.year)
@@
 ```{r}
-intervention.cost(base = base,
-                  base.name = baseline,
-                  int = int,
-                  int.name = intervention,
-                  int.label = intervention)
+# intervention.cost(base = base,
+#                   base.name = baseline,
+#                   int = int,
+#                   int.name = intervention,
+#                   int.label = intervention)
 ```

### 2024-03-12 minos/outcomes/QALY_comparison2.Rmd
Forgot to remove the debug parameters...

@@
 ```{r}
-# experiment <- params$experiment
-# baseline <- params$base
-# intervention <- params$intervention
-# #intervention2 <- params$intervention2
-# start.year <- params$start.year
+experiment <- params$experiment
+baseline <- params$base
+intervention <- params$intervention
+#intervention2 <- params$intervention2
+start.year <- params$start.year
 # # 
-experiment <- 'glasgow_scaled'
-baseline <- 'baseline'
-ints <- c('50All', '50UniversalCredit')
-start.year <- 2020
+# experiment <- 'glasgow_scaled'
+# baseline <- 'baseline'
+# ints <- c('50All', '50UniversalCredit')
+# start.year <- 2020
 ```

### 2024-03-12 minos/outcomes/QALY_comparison2.Rmd
Fixed one final typo in QALY_comparison2.Rmd and added £75 interventions to the combined qaly_SCP run targets

@@
 baseline <- params$base
-intervention <- params$intervention
+ints <- params$intervention
 #intervention2 <- params$intervention2

### 2024-03-13 docsrc/documentation/notebooks/physical_activity.Rmd

--- 2024-01-19 docsrc/documentation/notebooks/housing.Rmd
@@
 ---
-title: "Housing"
+title: "Physical Activity"
 output: html_document
@@
 
-## Housing Quality
+## Physical Activity
 
-Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].
+Whether a person is physically active or not has strong links to both mental and physical wellbeing, as well as other variables included in the MINOS pathways.
 
@@
 ```{r housing_barchart, echo=FALSE}
-discrete_barplot("data/transitions/housing_quality/clm/housing_quality_2018_2019.rds", 'next_housing_quality')
+discrete_barplot("data/transitions/active/logit/active_2018_2019.rds", 'next_active')
 ```
@@
 
-```{r housing_output, echo=FALSE}
+```{r active_output, echo=FALSE}
 options(width=120)
-clm_barplot("data/transitions/housing_quality/clm/housing_quality_2018_2019.rds", "next_housing_quality") 
-clm_output("data/transitions/housing_quality/clm/housing_quality_2018_2019.rds")
+clm_barplot("data/transitions/active/logit/active_2018_2019.rds", "next_active") 
+clm_output("data/transitions/active/logit/active_2018_2019.rds")
 ```

### 2024-03-13 minos/outcomes/QALY_comparison.Rmd

@@
 params: 
-  experiment: experiment 
-  baseline: baseline 
-  intervention: intervention
-  intervention_label: intervention_label
+  experiment:
+    value: experiment 
+  baseline:
+    value: baseline 
+  intervention:
+    value: intervention
+  intervention_label:
+    value: intervention_label
 ---

### 2024-03-13 minos/outcomes/QALY_comparison2.Rmd

@@
 
-ggplot(combined.diff, aes(x = year, y = total_boost, group = scenario, fill = scenario, color = scenario)) +
+ggplot(combined.diff, aes(x = year, y = total_boost, group = scenario, color = scenario)) +
   geom_smooth() +

### 2024-03-13 minos/testing/QALY_comparison_livingWage.Rmd

@@
 # # read in QALY files for baseline and interventions
-#out.path <- here::here('output', 'default_config')
+out.path <- here::here('output', 'default_config')
 #out.path <- here::here('output', 'glasgow_scaled')
-out.path <- here::here('output', 'SF12_uk_scaled')
+#out.path <- here::here('output', 'SF12_uk_scaled')
 

### 2024-03-13 minos/validation/scotland_synthpop_validation.Rmd
getting basic validation notebook working

---
title: "Synthpop Validation Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r, include=FALSE}
# include flag mutes package load messages for tidiness
library(here)
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'utils_validation_map_vis.R'))
library(dplyr)
```

```{r}
raw_data <- read.csv("../../data/final_US/2020_US_cohort.csv")
raw_data$group <- "Raw Data"
scotland_synth_data <- read.csv("../../data/scaled_scotland_US/2020_US_cohort.csv")
scotland_synth_data$group <- "Scotland Synthetic Data"

#lsoa_to_LA_map <- read.csv(here::here("persistent_data", "EWS_LSOA_2011_LA_2022.csv"))
# merge onto two datasets to get LA level information
```

```{r}
lsoas <- get_subsetted_lsoa_geojson_data("scotland")
las <- get_subsetted_la_geojson_data("scotland")
```

```{r}
density_comparison(raw_data, scotland_synth_data, "SF_12")
density_comparison(raw_data, scotland_synth_data, "hh_income")
```

```{r}
bars_comparison(raw_data, scotland_synth_data, "housing_quality")
bars_comparison(raw_data, scotland_synth_data, "neighbourhood_safety")
```

```{r}
map_la_and_lsoa_level_variable(scotland_synth_data, "SF_12")
```

### 2024-03-13 minos/outcomes/minos_SF12_maps.R

@@ -7,6 +7,8 @@ library(sp) # ^
 library(sf) # ^ Also sucks to install. no longer used for geojsonio.
 library(tibble) # converting spatial objects to data frames.
 # library(ggrepel) # for geom_text_repel labels
+library(here)
+
 
 subset_geojson <- function(data, subset_function){
   # Subset national MINOS geoJSON output by some subset function.
@@ -19,30 +21,54 @@ subset_geojson <- function(data, subset_function){
 }
 
 sheffield_lsoa_subset_function <- function(data){
-  lsoas <- read.csv("persistent_data/sheffield_lsoas.csv")
-  lsoas <- lsoas$x # just take needed lsoa column
+  lsoas <- read.csv("persistent_data/spatial_data/sheffield_lsoas.csv")
+  lsoas <- lsoas$LSOA11CD # just take needed lsoa column
   return(subset(data, ZoneID %in% lsoas))
 }
 
 
 manchestser_lsoa_subset_function <- function(data){
-  lsoas <- read.csv("persistent_data/manchester_lsoas.csv")
-  lsoas <- lsoas$x # just take needed lsoa column.
+  lsoas <- read.csv("persistent_data/spatial_data/manchester_lsoas.csv")
+  lsoas <- lsoas$LSOA11CD # just take needed lsoa column.
   return(subset(data, ZoneID %in% lsoas))
 }
 
 
 scotland_data_zone_subset_function <- function(data){
-  datazones <- read.csv("persistent_data/scotland_data_zones.csv")
-  datazones <- datazones$DZ2011_Code
+  datazones <- read.csv(here::here("persistent_data", "spatial_data", "scotland_data_zones.csv"))
+  datazones <- datazones$LSOA11CD
   return(subset(data, ZoneID %in% datazones))
 }
 
 
 glasgow_data_zone_subset_function <- function(data){
-  datazones <- read.csv("persistent_data/glasgow_data_zones.csv")
-  datazones <- datazones$lsoa11cd
+  datazones <- read.csv("persistent_data/spatial_data/glasgow_data_zones.csv")
+  datazones <- datazones$LSOA11CD
   return(subset(data, ZoneID %in% datazones))
+}
+
+sheffield_LA_subset_function <- function(data){
+  LAs <- read.csv("persistent_data/spatial_data/sheffield_LAs.csv")
+  LAs <- LAs$LAD22NM # just take needed lsoa column
+  return(subset(data, LAD21NM %in% LAs))
+}
+
[…]

### 2024-03-13 minos/utils_validation_vis.R

@@ -487,3 +487,30 @@ handover_lineplots <- function(raw, base, var) {
     xlab('Year') +
     ylab(var)
 }
+
+##############################
+# synthetic population plots #
+##############################
+
+density_comparison <- function(data1, data2, v) {
+  # plot densities of a variable from two populations. 
+  data1 <- data1[, c("group", v)]
+  data2 <- data2[, c("group", v)]
+  data <- rbind(data1, data2)
+  density_plot <- ggplot(data=data, aes(x=!!sym(v), group=group, color=group, linetype=group)) +
+    geom_density() + 
+    ggtitle(paste0("Variable: ", v)) 
+    
+  return(density_plot)
+}
+
+bars_comparison <- function(data1, data2, v) {
+  data1 <- data1[, c("group", v)]
+  data2 <- data2[, c("group", v)]
+  data <- rbind(data1, data2)
+  data <- as.data.frame(prop.table(table(data), margin=1))
+  split_barplot <- ggplot(data=data, aes(x=!!sym(v), y= Freq, fill=group)) +
+    geom_bar(stat = "identity", position = position_dodge()) 
+  return(split_barplot)
+}
+

### 2024-03-14 minos/validation/handovers.Rmd

--- 2024-02-26 minos/validation/handovers.Rmd
@@
 
-#out.path <- here::here('output', 'default_config/')
-out.path <- here::here('output', 'energy_default_config/')
+out.path <- here::here('output', 'default_config/')
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
+
+#out.path <- here::here('output', 'scotland_scaled/')
+#base.dat <- read_first_singular_local_out(out.path, '25UniversalCredit', drop.dead = TRUE)
+
+# HR 283-285 older version (285)
+# out.path <- here::here('output', 'child_poverty_config/')
+# base.dat <- read_singular_local_out(out.path, 'ChildPovertyIntervention', drop.dead = TRUE)
 ```
@@
 ```{r}
+start.year <- 2020
 save.path <- here::here("plots", "handovers", 'default')
 create.if.not.exists(save.path)
-start.year <- 2021
-# make sure we only overlap on one year for now or else tomfoolery happens. (the plots look bad).
-# we may want this overlap in the future? probably not.
-raw.dat <- raw.dat[which(raw.dat$time <= start.year), ]
-base.dat <- base.dat[which(base.dat$time>=start.year), ]
 
@@
 
-## Net Income & Rent & Mortgage
-
-```{r yearly_energy}
-# get required variables. 
-raw.inc <- raw.dat %>%
-  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
-base.inc <- base.dat %>%
-  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
-
-# net household income. 
-handover_boxplots(raw.inc, base.inc, 'net_hh_income')
-handover_lineplots(raw.inc, base.inc, "net_hh_income")
-inc.spag<-rbind(raw.inc, base.inc)
-density_ridges(inc.spag, 'net_hh_income',
-               save=TRUE, 
-               save.path=save.path)
-
-# rent
-handover_boxplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], 'hh_rent')
-handover_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
-density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
-               save=TRUE, 
-               save.path=save.path)
-
-# mortgage
-handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], 'hh_mortgage')
-handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
-density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
-               save=TRUE, 
-               save.path=save.path)
-
-#council tax
-handover_boxplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], 'council_tax')
-handover_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
-density_ridges(inc.spag[which(inc.spag$council_tax>1), ], 'council_tax',
-               save=TRUE, 
-               save.path=save.path)
-
-# oecd equivalence scale. (NOT TRANSITIONED YET. REQUIRES LEAVING THE NEST MODULE.. )
-handover_boxplots(raw.inc, base.inc, 'oecd_equiv')
-handover_lineplots(raw.inc, base.inc, 'oecd_equiv')
-density_ridges(inc.spag, 'oecd_equiv',
-               save=TRUE, 
-               save.path=save.path)
-
-# tidy up.
-rm(raw.inc, base.inc, inc.spag)
-```
-
-## Yearly energy
-
-```{r net_income}
-# get required variables. 
-raw.energy <- raw.dat %>%
-  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)
-base.energy <- base.dat %>%
-  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)
-
-# gas expenditure
-handover_boxplots(raw.energy, base.energy, 'yearly_gas')
-handover_lineplots(raw.energy, base.energy, "yearly_gas")
-#inc.spag<-rbind(raw.inc, base.inc)
-#density_ridges(inc.spag, 'yearly_gas',
-#               save=TRUE, 
-#               save.path=save.path)
-
-# yearly electric
-handover_boxplots(raw.energy, base.energy, 'yearly_electric')
-handover_lineplots(raw.energy, base.energy, "yearly_electric")
-#density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
-#               save=TRUE, 
-#               save.path=save.path)
-
-# yearly energy
-handover_boxplots(raw.energy, base.energy, 'yearly_energy')
-handover_lineplots(raw.energy, base.energy, "yearly_energy")
-#density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
-#               save=TRUE, 
-#               save.path=save.path)
-
-# tidy up.
-rm(raw.energy, base.energy)#, inc.spag)
-```
-
 ## SF12
@@
 
-## nkids Household
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'nkids')
-handover_lineplots(raw.dat, base.dat, 'nkids')
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, nkids)
-base.s <- base.dat %>%
-  select(pidp, age, time, nkids)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## nkids Max
-
-```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.nkids_max <- raw.dat %>%
-  dplyr::select(pidp, time, nkids) %>%
-  group_by(time) %>%
-  summarise(max_nkids = max(nkids)) %>%
-  mutate(source = 'final_US')
-
-base.nkids_max <- base.dat %>%
-  dplyr::select(pidp, time, nkids) %>%
-  group_by(time) %>%
-  summarise(max_nkids = max(nkids)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-max_nkids <- rbind(raw.nkids_max, base.nkids_max)
-
-# Now plot
-ggplot(data = max_nkids, mapping = aes(x = time, y = max_nkids, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Max nkids', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Average')
-```
-
 ## Parity
@@
 
-## Hourly Wage
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'hourly_wage')
-handover_lineplots(raw.dat, base.dat, 'hourly_wage')
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, hourly_wage)
-base.s <- base.dat %>%
-  select(pidp, age, time, hourly_wage)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-# now a version limited to 0-100
-spag <- spag %>%
-  filter(hourly_wage <= 300)
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-```{r}
-# some basic statistics about hourly_wage variable
-print("Some basic statistics on hourly_wage. These are all for 2020.")
-raw.2020 <- raw.dat %>% filter(time == 2020)
-print('All living people in 2020')
-print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
-# number individuals with an hourly_wage > 0
-print('People not in work')
-print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
-
-# Number in work
-print('People in work')
-print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
-
-# Extreme hourly_wage values
-print('Extreme hourly wage values: HIGH')
-print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
-print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
-print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
-print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
-print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
-print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
-
-raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
-print('Extreme hourly wage values: LOW (non-zero)')
-print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
-print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
-print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
-print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
-```
-
-## S7 Labour State
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
-
-lab.state <- prepped.list$var
-lab.state.norm <- prepped.list$norm
-
-# Now plot
-ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'S7_labour_state.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, lab.state, lab.state.norm)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'S7_labour_state')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'S7_labour_state',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
 ## Child Ages
@@
 ```{r}
-raw.child.ages <- raw.dat %>%
-  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
-  filter(time > 2013 & child_ages != 'childless') %>%
-  group_by(time, hidp) %>%
-  summarise(child_ages = find_mode(child_ages))
-
-r.s<- strsplit(raw.child.ages$child_ages, "_")
-
-raw.child.ages.expanded <- data.frame(time = rep(raw.child.ages$time, sapply(r.s, length)), expanded_child_ages = unlist(r.s))
-raw.child.ages.expanded <- raw.child.ages.expanded %>%
-  group_by(time, expanded_child_ages) %>%
-  summarise(age_counts = n()) %>%
-  mutate(source = 'final_US') %>%
-  filter(expanded_child_ages <= 16)
-
 base.child.ages <- base.dat %>%
@@
 
-## Number of cars
-
-```{r ncars}
-
-raw.ncars <- raw.dat
-base.ncars <- base.dat
-raw.ncars[raw.ncars$ncars>=10, 'ncars'] <- "More than 9."
-base.ncars[base.ncars$ncars>=10, 'ncars'] <- "More than 9."
-
-raw.ncars <- raw.ncars %>%
-  dplyr::select(pidp, time, ncars) %>%
-  filter(ncars >= 0) %>%
-  group_by(time, ncars) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.ncars <- base.ncars %>%
-  dplyr::select(pidp, time, ncars) %>%
-  filter(ncars >= 0) %>%
-  group_by(time, ncars) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-ncars <- rbind(raw.ncars, base.ncars)
-ncars$ncars <- as.factor(ncars$ncars)
-
-# Now plot
-ggplot(data = ncars, mapping = aes(x = time, y = n, group = ncars, colour = ncars)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Number of Cars', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ncars.norm <- ncars %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = ncars.norm, mapping = aes(x = time, y = prct, group = ncars, colour = ncars)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Number of Cars', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = ncars.norm, mapping = aes(x = time, y = prct, fill=ncars)) +
+## Child Poverty Vars
+
+### Relative Poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Relative Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
   geom_bar(stat = 'identity') +
   geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Number of Cars') +
+  labs(title = tit) +
   xlab('Year') +
@@
 if (shall.we.save) {
-  ggsave(filename = 'ncars.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.ncars, base.ncars, ncars, ncars.norm)
-```
-
-## ncigs
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'ncigs')
-handover_lineplots(raw.dat, base.dat, "ncigs")
-raw.ncigs <- raw.dat %>%
-  select(pidp, age, time, ncigs)
-base.ncigs <- base.dat %>%
-  select(pidp, age, time, ncigs)
-ncigs.spag <- rbind(raw.ncigs, base.ncigs)
-shall.we.save <- F
-pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/10, replace=FALSE)
-ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(ncigs.spag.sample, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-
-zip_density_ridges(ncigs.spag, "ncigs", 
-               save = shall.we.save, 
-               save.path = save.path)
-rm(raw.ncigs, base.ncigs, ncigs.spag)
-```
-
-## ncigs non-zero
-
-```{r}
-
-raw.ncigs <- raw.dat %>%
-  filter(ncigs>0) %>%
-  select(pidp, age, time, ncigs)
-base.ncigs <- base.dat %>%
-  filter(ncigs>0) %>%
-  select(pidp, age, time, ncigs)
-
-ncigs.spag <- rbind(raw.ncigs, base.ncigs) # get all smokers.
-shall.we.save <- F
-pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/100, replace=FALSE)
-ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(ncigs.spag.sample, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
-               save = shall.we.save,
-               save.path = save.path)
-
-zip_density_ridges(ncigs.spag, "ncigs", 
-               save = shall.we.save, 
-               save.path = save.path)
-rm(raw.ncigs, base.ncigs, ncigs.spag)
-```
+  ggsave(filename = 'relative_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+### Absolute Poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Absolute Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'absolute_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+### Persistent Poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Persistent Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'persistent_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+
+```
+
+### Low Income and Material Deprivation
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Material Deprivation Child'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'low_income_matdep_child.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+
+```

### 2024-03-14 minos/validation/housing_handovers.Rmd

@@
 # Read raw datafiles in
-raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)[1:12]
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 create.if.not.exists(save.path)
-start.year <- 2021
+start.year <- 2020
 # make sure we only overlap on one year for now or else tomfoolery happens. (the plots look bad).
@@
                save.path=save.path)
+handover_boxplots(raw.dat, base.dat, 'net_hh_income')
 

### 2024-03-15 minos/validation/handovers.Rmd
Added some diagnostic plots to handovers looking at council_tax

@@
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-
-#out.path <- here::here('output', 'scotland_scaled/')
-#base.dat <- read_first_singular_local_out(out.path, '25UniversalCredit', drop.dead = TRUE)
-
-# HR 283-285 older version (285)
-# out.path <- here::here('output', 'child_poverty_config/')
-# base.dat <- read_singular_local_out(out.path, 'ChildPovertyIntervention', drop.dead = TRUE)
+#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
 ```
@@
 handover_lineplots(raw.dat, base.dat, "hh_income")
+handover_boxplots(raw.dat, base.dat, 'council_tax')
+handover_lineplots(raw.dat, base.dat, "council_tax")
 ```
@@
 ```{r}
+raw.child.ages <- raw.dat %>%
+  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
+  filter(time > 2013 & child_ages != 'childless') %>%
+  group_by(time, hidp) %>%
+  summarise(child_ages = find_mode(child_ages))
+
+r.s<- strsplit(raw.child.ages$child_ages, "_")
+
+raw.child.ages.expanded <- data.frame(time = rep(raw.child.ages$time, sapply(r.s, length)), expanded_child_ages = unlist(r.s))
+raw.child.ages.expanded <- raw.child.ages.expanded %>%
+  group_by(time, expanded_child_ages) %>%
+  summarise(age_counts = n()) %>%
+  mutate(source = 'final_US') %>%
+  filter(expanded_child_ages <= 16)
+
 base.child.ages <- base.dat %>%
@@
 
-## Child Poverty Vars
-
-### Relative Poverty
-
 ```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Relative Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'relative_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-### Absolute Poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Absolute Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'absolute_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-### Persistent Poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Persistent Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'persistent_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
 
 ```
-
-### Low Income and Material Deprivation
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Material Deprivation Child'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'low_income_matdep_child.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-
-```

### 2024-03-15 minos/validation/handovers.Rmd

--- 2024-03-13 minos/validation/handovers.Rmd
@@
 # rm(raw.inc, base.inc, income.spag)
+```
+
+## Council Tax
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'council_tax')
+handover_lineplots(raw.dat, base.dat, "council_tax")
 ```

### 2024-03-21 minos/outcomes/QALY_comparison2.Rmd

@@
 ints <- params$intervention
-#intervention2 <- params$intervention2
 start.year <- params$start.year
 # #
-# experiment <- 'glasgow_scaled'
+# experiment <- 'arc_batch_10'
 # baseline <- 'baseline'
-# ints <- c('50All', '50UniversalCredit')
+# ints <- c('25UniversalCredit', '50UniversalCredit', '75UniversalCredit', '100UniversalCredit')
 # start.year <- 2020
@@
 ```{r}
-# QALY_comparison(base = base,
-#                 base.name = baseline,
-#                 int = int,
-#                 int.name = intervention)
-
 QALY_comparison(combined, ints)

### 2024-03-21 minos/testing/intervention_pathway_testing.Rmd

---
title: "Testing Interventions - QALY Focus"
output: html_notebook
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

```{r}
source(here::here('minos', 'utils_datain.R'))
```

```{r}
output.dir <- here::here('output', 'default_config/')

var.list <- c('hh_income', 'age', 'sex', 'ethnicity', 'region', 'education_state', 'nkids', 'hhsize', 
              'housing_quality', 'neighbourhood_safety', 'loneliness', 'ncigs', 'nutrition_quality', 
              'active', 'auditc', 
              'S7_labour_state', 
              'SF_12_MCS', 'SF_12_PCS')

base <- read_batch_out_all_years(out.path = output.dir,
                                 scenario = 'baseline',
                                 var.list = var.list)
all50 <- read_batch_out_all_years(out.path = output.dir,
                                 scenario = '50All',
                                 var.list = var.list)
UC50 <- read_batch_out_all_years(out.path = output.dir,
                                 scenario = '50UniversalCredit',
                                 var.list = var.list)

base$scen <- 'baseline'
all50$scen <- 'all50'
UC50$scen <- 'UC50'

data <- rbind(base, all50, UC50)

```

# Functions

## Ordinal Vars

```{r}
pathway_plots_ordinal <- function(data, var, levels = c(1,2,3)) {
  df <- data %>% 
    group_by(time, scen, .data[[var]]) %>%
    summarise(n = n()) %>%
    group_by(time, scen) %>%
    mutate(prop = (n / sum(n)) * 100)

  for (level in levels) {
    p <- ggplot(dplyr::filter(df, .data[[var]] == level), aes(x = time, y = prop, group = scen, fill = scen, color = scen)) +
            geom_line() +
            labs(title = var, subtitle = level)
    print(p)
  }
}

pathway_plots_continuous <- function(data, var) {
  df <- data %>%
    group_by(time, scen, .data[[var]]) %>%
    summarise(mean_var = mean(.data[[var]]))

  p1 <- ggplot(data, aes(x = time, y = .data[[var]], group = scen, fill = scen, color = scen)) +
    geom_smooth() +
    labs(title = var, subtitle = 'Loess Smoothed')

  p2 <- ggplot(df, aes(x = time, y = mean_var, group = scen, fill = scen, color = scen)) +
    geom_smooth() +
    labs(title = var, subtitle = 'Mean')

  print(p1)
  print(p2)
}
```

# INCOME CHANGE DUE TO INTERVENTION

```{r}
ggplot(data, aes(x = time, y = hh_income, group = scen, fill = scen, color = scen)) +
  geom_smooth() +
  labs(title = 'Household Income Comparison') +
  xlab('Year') +
  ylab('Mean Household Income')
```

# PATHWAYS CHANGE DUE TO INTERVENTION

## Housing Quality

```{r}
pathway_plots_ordinal(data, var = 'housing_quality', levels = c('Low', 'Medium', 'High'))
```

## Neighbourhood Safety

```{r}
pathway_plots_ordinal(data, var = 'neighbourhood_safety')
```

## Loneliness

```{r}
pathway_plots_ordinal(data, var = 'loneliness')
```

## Tobacco

```{r}
pathway_plots_continuous(data, var = 'ncigs')
```

## Tobacco

```{r}
pathway_plots_continuous(data, var = 'nutrition_quality')
```

## Active

```{r}
pathway_plots_ordinal(data, var = 'active', levels = c(0,1))
```

## AUDITC

```{r}
pathway_plots_ordinal(data, var = 'auditc', levels = c('Non-drinker', 'Low Risk', 'Increased Risk', 'High Risk'))
```

# OUTCOMES

## MCS

```{r}
pathway_plots_continuous(data, var = 'SF_12_MCS')
```

## PCS

```{r}
pathway_plots_continuous(data, var = 'SF_12_PCS')
```

```{r}

```

### 2024-03-21 minos/validation/handovers.Rmd

@@
 ---
+
 title: "MINOS Handover Plots"
@@
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
 ```
@@
 handover_lineplots(raw.dat, base.dat, "hh_income")
-handover_boxplots(raw.dat, base.dat, 'council_tax')
-handover_lineplots(raw.dat, base.dat, "council_tax")
 ```
@@
 # rm(raw.inc, base.inc, income.spag)
+```
+
+### Income Inequality
+
+```{r}
+handover_inequality_80_20(raw.dat, base.dat, var = 'hh_income')
 ```
@@
 
+### Inequality
+
+```{r}
+handover_inequality_80_20(raw.dat, base.dat, var = 'SF_12_MCS')
+```
+
 ## SF_12_PCS
@@
 rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
+```
+
+### Inequality
+
+```{r}
+handover_inequality_80_20(raw.dat, base.dat, var = 'SF_12_PCS')
 ```

### 2024-03-27 minos/validation/housing_handovers.Rmd
getting sensible looking handovers for net income, ncars, and ncigs

@@
 net.income.spag <- rbind(raw.inc, base.inc)
-
+net.income.spag <- net.income.spag[which(net.income.spag$net_hh_income<50000), ]
 density_ridges(net.income.spag, 'net_hh_income',
@@
                save.path=save.path)
-
+spaghetti_plot(net.income.spag.sample, 'hh_rent',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(net.income.spag.sample, 'hh_rent',
+               save = shall.we.save,
+               save.path = save.path)
 # mortgage
-handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], 'hh_mortgage')
+handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1 & raw.inc$hh_mortgage<5000), ], base.inc[which(base.inc$hh_mortgage>1 & base.inc$hh_mortgage<5000), ], 'hh_mortgage')
 handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
-density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
+density_ridges(inc.spag[which(inc.spag$hh_mortgage>1 & inc.spag$hh_mortgage<5000), ], 'hh_mortgage',
                save=TRUE, 
                save.path=save.path)
-
+spaghetti_plot(net.income.spag.sample, 'hh_mortgage',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(net.income.spag.sample, "hh_mortgage",
+               save = shall.we.save,
+               save.path = save.path)
 #council tax
@@
                save.path=save.path)
-
-# oecd equivalence scale. (NOT TRANSITIONED YET. REQUIRES LEAVING THE NEST MODULE.. )
+spaghetti_plot(net.income.spag.sample, 'council_tax',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(net.income.spag.sample, "council_tax",
+               save = shall.we.save,
+               save.path = save.path)
+
+# oecd equivalence scale. 
+#TODO not fully transitioned yet for leaving the nest.
 handover_boxplots(raw.inc, base.inc, 'oecd_equiv')
@@
 
-```{r}
-raw.sf12 <- raw.dat %>%
-  select(pidp, age, time, SF_12)
-base.sf12 <- base.dat %>%
-  select(pidp, age, time, SF_12)
-
-sf12.spag <- rbind(raw.sf12, base.sf12)
-
-sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(sf12.spag.sample, 'SF_12',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(sf12.spag, "SF_12", 
-               save = T, 
-               save.path = save.path)
-
-rm(raw.sf12, base.sf12, sf12.spag)
-```
-
-## Financial Situation
-
-```{r}
-raw.financial_situation <- raw.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.financial_situation <- base.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-financial_situation <- rbind(raw.financial_situation, base.financial_situation)
-financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
-
-# Now plot
-ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-financial_situation.norm <- financial_situation %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial situation') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'financial_situation.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
-```
-
-## Housing Quality
-
-```{r}
-raw.housing <- raw.dat %>%
-  dplyr::select(pidp, time, housing_quality) %>%
-  group_by(time, housing_quality) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.housing <- base.dat %>%
-  dplyr::select(pidp, time, housing_quality) %>%
-  group_by(time, housing_quality) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-housing <- rbind(raw.housing, base.housing)
-housing$housing_quality <- as.factor(housing$housing_quality)
-
-# Now plot
-ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Quality', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-housing.norm <- housing %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Quality') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'housing_quality.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.housing, base.housing, housing, housing.norm)
-```
-
-### Spaghetti
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, housing_quality)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, housing_quality)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'housing_quality',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
-
-## Housing Tenure
-
-```{r}
-raw.tenure <- raw.dat %>%
-  dplyr::select(pidp, time, housing_tenure) %>%
-  group_by(time, housing_tenure) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.tenure <- base.dat %>%
-  dplyr::select(pidp, time, housing_tenure) %>%
-  group_by(time, housing_tenure) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-tenure <- rbind(raw.tenure, base.tenure)
-tenure$housing_tenure <- as.factor(tenure$housing_tenure)
-
-# Now plot
-ggplot(data = tenure, mapping = aes(x = time, y = n, group = housing_tenure, colour = housing_tenure)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Tenure', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-tenure.norm <- tenure %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = tenure.norm, mapping = aes(x = time, y = prct, fill=housing_tenure)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Housing Tenure') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'housing_tenure.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.tenure, base.tenure, tenure, tenure.norm)
-```
-
-## Neighbourhood Safety
-
-```{r}
-raw.neighbour <- raw.dat %>%
-  dplyr::select(pidp, time, neighbourhood_safety) %>%
-  group_by(time, neighbourhood_safety) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.neighbour <- base.dat %>%
-  dplyr::select(pidp, time, neighbourhood_safety) %>%
-  group_by(time, neighbourhood_safety) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-neighbour <- rbind(raw.neighbour, base.neighbour)
-neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety)
-
-# Now plot
-ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') +
-  xlab('Year') +
-  ylab('Count')
-
-neighbour.norm <- neighbour %>%
-  group_by(time) %>%
-  filter(neighbourhood_safety != -9) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Neighbourhood Safety') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'neighbourhood_safety.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-#rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm)
-```
-
-### Spaghetti
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, neighbourhood_safety)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, neighbourhood_safety)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'neighbourhood_safety',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
-
-## Loneliness
-
-```{r}
-raw.loneliness <- raw.dat %>%
-  dplyr::select(pidp, time, loneliness) %>%
-  group_by(time, loneliness) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.loneliness <- base.dat %>%
-  dplyr::select(pidp, time, loneliness) %>%
-  group_by(time, loneliness) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-loneliness <- rbind(raw.loneliness, base.loneliness)
-loneliness$loneliness <- as.factor(loneliness$loneliness)
-
-# Now plot
-ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Loneliness', subtitle = 'Counts by level') +
-  xlab('Year') +
-  ylab('Count')
-
-loneliness.norm <- loneliness %>%
-  group_by(time) %>%
-  filter(loneliness != -9) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Loneliness') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'loneliness.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
-```
-
-### Spaghetti
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, loneliness)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, loneliness)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'loneliness',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
-
-## Nutrition Quality
-
-TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11
-
-```{r}
-#  nutriton quality line/boxplots.
-handover_boxplots(raw.dat, base.dat, 'nutrition_quality')
-handover_lineplots(raw.dat, base.dat, 'nutrition_quality')
-
-# Try a version where final_US is limited to only those present from wave 1
-# onwards because the sample refreshments are messing with the plot
-# raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-# 
-# raw.nut2 <- raw.dat %>%
-#   dplyr::select(pidp, time, nutrition_quality) %>%
-#   filter(pidp %in% raw.wave1) %>%
-#   filter(nutrition_quality >= 0) %>%
-#   group_by(time) %>%
-#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.nut2 <- base.dat %>%
-#   dplyr::select(pidp, time, nutrition_quality) %>%
-#   filter(pidp %in% raw.wave1) %>%
-#   group_by(time) %>%
-#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# nutrition_quality2 <- rbind(raw.nut2, base.nut2)
-# 
-# # Now plot
-# ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
-#   geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Nutrition Quality') +
-#   xlab('Year') +
-#   ylab('Nutrition Quality')
-# 
-# if (shall.we.save) {
-#   ggsave(filename = 'nutrition_quality_wav1.png',
-#        plot = last_plot(),
-#        path = save.path)
-# }
-# 
-# rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2,
-#     nutrition_quality2)
-```
-
-### Spaghetti
-
-```{r}
-# raw.nut <- raw.dat %>%
-#   select(pidp, age, time, nutrition_quality)
-# base.nut <- base.dat %>%
-#   select(pidp, age, time, nutrition_quality)
-# 
-# nut.spag <- rbind(raw.nut, base.nut)
-# 
-# spaghetti_plot(nut.spag, 'nutrition_quality',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# 
-# density_ridges(nut.spag, "nutrition_quality", 
-#                save = T, 
-#                save.path = save.path)
-# 
-# rm(raw.nut, base.nut, nut.spag)
-```
-
-## Physical Health
-
-NOTE: At present, physical health is not predicted or transitioned.
-
-```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.phealth <- raw.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.phealth <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-phealth <- rbind(raw.phealth, base.phealth)
-
-# Now plot
-ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Average')
-
-## Try a version where final_US is limited to only those present from wave 1
-# onwards because the sample refreshments are messing with the plot
-raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.phealth2 <- raw.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.phealth2 <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-phealth2 <- rbind(raw.phealth2, base.phealth2)
-
-# Now plot
-ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health') +
-  xlab('Year') +
-  ylab('Average')
-
-if (shall.we.save) {
-  ggsave(filename = 'physical_health_wav1.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-#raw.phealth.check <- raw.dat %>%
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
-
-#base.phealth.check <- base.dat %>%
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
-
-rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2)
-#rm(raw.phealth.check, base.phealth.check)
-```
-
-### Spaghetti
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, phealth)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, phealth)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'phealth',
-#              save = shall.we.save,
-#              save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
-
-## Education
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Education State'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'education_state.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat,
-                                       df1.name = 'simulated',
-                                       df2 = raw.dat,
-                                       df2.name = 'raw',
-                                       var = 'education_state')
-
-cv_ordinal_plots(pivoted.df = pivoted,
-                 var = 'education_state',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, education_state)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, education_state)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'education_state',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
-
-## nkids Household
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'nkids')
-handover_lineplots(raw.dat, base.dat, 'nkids')
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, nkids)
-base.s <- base.dat %>%
-  select(pidp, age, time, nkids)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## nkids Max
-
-```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.nkids_max <- raw.dat %>%
-  dplyr::select(pidp, time, nkids) %>%
-  group_by(time) %>%
-  summarise(max_nkids = max(nkids)) %>%
-  mutate(source = 'final_US')
-
-base.nkids_max <- base.dat %>%
-  dplyr::select(pidp, time, nkids) %>%
-  group_by(time) %>%
-  summarise(max_nkids = max(nkids)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-max_nkids <- rbind(raw.nkids_max, base.nkids_max)
-
-# Now plot
-ggplot(data = max_nkids, mapping = aes(x = time, y = max_nkids, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Max nkids', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Average')
-```
-
-## Parity
-
-```{r}
-base.parity <- base.dat %>%
-  filter(sex == "Female")
-
-raw.parity <- raw.dat %>%
-  filter(sex == "Female")
-
-prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Parity (total no. of children)'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'parity.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.parity,
-                                  df1.name = 'simulated', 
-                                  df2 = raw.parity, 
-                                  df2.name = 'raw', 
-                                  var = 'nkids_ind')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'nkids_ind',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.parity %>%
-  select(pidp, age, time, nkids_ind)
-base.s <- base.parity %>%
-  select(pidp, age, time, nkids_ind)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids_ind',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## Hourly Wage
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'hourly_wage')
-handover_lineplots(raw.dat, base.dat, 'hourly_wage')
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, hourly_wage)
-base.s <- base.dat %>%
-  select(pidp, age, time, hourly_wage)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-# now a version limited to 0-100
-spag <- spag %>%
-  filter(hourly_wage <= 300)
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-```{r}
-# some basic statistics about hourly_wage variable
-print("Some basic statistics on hourly_wage. These are all for 2020.")
-raw.2020 <- raw.dat %>% filter(time == 2020)
-print('All living people in 2020')
-print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
-# number individuals with an hourly_wage > 0
-print('People not in work')
-print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
-
-# Number in work
-print('People in work')
-print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
-
-# Extreme hourly_wage values
-print('Extreme hourly wage values: HIGH')
-print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
-print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
-print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
-print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
-print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
-print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
-
-raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
-print('Extreme hourly wage values: LOW (non-zero)')
-print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
-print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
-print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
-print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
-```
-
-## S7 Labour State
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
-
-lab.state <- prepped.list$var
-lab.state.norm <- prepped.list$norm
-
-# Now plot
-ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'S7_labour_state.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, lab.state, lab.state.norm)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'S7_labour_state')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'S7_labour_state',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-## Child Ages
-
-```{r}
-raw.child.ages <- raw.dat %>%
-  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
-  filter(time > 2013 & child_ages != 'childless') %>%
-  group_by(time, hidp) %>%
-  summarise(child_ages = find_mode(child_ages))
-
-r.s<- strsplit(raw.child.ages$child_ages, "_")
-
-raw.child.ages.expanded <- data.frame(time = rep(raw.child.ages$time, sapply(r.s, length)), expanded_child_ages = unlist(r.s))
-raw.child.ages.expanded <- raw.child.ages.expanded %>%
-  group_by(time, expanded_child_ages) %>%
-  summarise(age_counts = n()) %>%
-  mutate(source = 'final_US') %>%
-  filter(expanded_child_ages <= 16)
-
-base.child.ages <- base.dat %>%
-  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
-  filter(time > 2009) %>%
-  group_by(time, hidp) %>%
-  summarise(child_ages = find_mode(child_ages))
-
-b.s<- strsplit(base.child.ages$child_ages, "_")
-
-base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(b.s, length)), expanded_child_ages = unlist(b.s))
-base.child.ages.expanded <- base.child.ages.expanded %>%
-  group_by(time, expanded_child_ages) %>%
-  summarise(age_counts = n()) %>%
-  mutate(source = 'baseline')
-
-combined <- rbind(raw.child.ages.expanded, base.child.ages.expanded)
-
-ggplot(data = combined, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
-  geom_line() +
-  geom_vline(xintercept = start.year) +
-  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
-  scale_colour_viridis_d() +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = combined, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
-  geom_line() +
-  geom_vline(xintercept = start.year) +
-  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
-  scale_colour_viridis_d() +
-  xlab('Year') +
-  ylab('Count')
-
-base.child.ages.nkids <- base.dat %>%
-  group_by(time, hidp) %>%
-  summarise(nkids_counts = mean(nkids)) %>%
-  group_by(time) %>%
-  summarise(nkids_by_year = sum(nkids_counts)) %>%
-  mutate(source = 'baseline')
-
-raw.child.ages.nkids <- raw.dat %>%
-  group_by(time, hidp) %>%
-  summarise(nkids_counts = mean(nkids)) %>%
-  group_by(time) %>%
-  summarise(nkids_by_year = sum(nkids_counts)) %>%
-  mutate(source = 'final_US')
-
-combined.nkids <- rbind(base.child.ages.nkids, raw.child.ages.nkids)
-
-ggplot(data = combined.nkids, mapping = aes(x = time, y = nkids_by_year, group = source, colour = source)) +
-  geom_line() +
-  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-```
+<!-- ```{r} -->
+<!-- raw.sf12 <- raw.dat %>% -->
+<!--   select(pidp, age, time, SF_12) -->
+<!-- base.sf12 <- base.dat %>% -->
+<!--   select(pidp, age, time, SF_12) -->
+
+<!-- sf12.spag <- rbind(raw.sf12, base.sf12) -->
+
+<!-- sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ] -->
+<!-- spaghetti_plot(sf12.spag.sample, 'SF_12', -->
+<!--                save = shall.we.save, -->
+<!--                save.path = save.path) -->
+<!-- spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12', -->
+<!--                save = shall.we.save, -->
+<!--                save.path = save.path) -->
+
+<!-- density_ridges(sf12.spag, "SF_12",  -->
+<!--                save = T,  -->
+<!--                save.path = save.path) -->
+
+<!-- rm(raw.sf12, base.sf12, sf12.spag) -->
+<!-- ``` -->
+
+<!-- ## Financial Situation -->
+
+<!-- ```{r} -->
+<!-- raw.financial_situation <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, financial_situation) %>% -->
+<!--   group_by(time, financial_situation) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'final_US') -->
+
+<!-- base.financial_situation <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, financial_situation) %>% -->
+<!--   group_by(time, financial_situation) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'baseline_output') -->
+
+<!-- # merge before plot -->
+<!-- financial_situation <- rbind(raw.financial_situation, base.financial_situation) -->
+<!-- financial_situation$financial_situation <- as.factor(financial_situation$financial_situation) -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Financial Situation', subtitle = 'Counts by Level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
+
+<!-- financial_situation.norm <- financial_situation %>% -->
+<!--   group_by(time) %>% -->
+<!--   mutate(total = sum(n)) %>% -->
+<!--   mutate(prct = (n / total)) -->
+
+<!-- ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Financial situation') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
+
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'financial_situation.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
+<!-- } -->
+
+<!-- rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm) -->
+<!-- ``` -->
+
+<!-- ## Housing Quality -->
+
+<!-- ```{r} -->
+<!-- raw.housing <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, housing_quality) %>% -->
+<!--   group_by(time, housing_quality) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'final_US') -->
+
+<!-- base.housing <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, housing_quality) %>% -->
+<!--   group_by(time, housing_quality) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'baseline_output') -->
+
+<!-- # merge before plot -->
+<!-- housing <- rbind(raw.housing, base.housing) -->
+<!-- housing$housing_quality <- as.factor(housing$housing_quality) -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Housing Quality', subtitle = 'Counts by Level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
+
+<!-- housing.norm <- housing %>% -->
+<!--   group_by(time) %>% -->
+<!--   mutate(total = sum(n)) %>% -->
+<!--   mutate(prct = (n / total)) -->
+
+<!-- ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Housing Quality') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
+
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'housing_quality.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
+<!-- } -->
+
+<!-- rm(raw.housing, base.housing, housing, housing.norm) -->
+<!-- ``` -->
+
+<!-- ### Spaghetti -->
+
+<!-- ```{r} -->
+<!-- # raw.s <- raw.dat %>% -->
+<!-- #   select(pidp, age, time, housing_quality) -->
+<!-- # base.s <- base.dat %>% -->
+<!-- #   select(pidp, age, time, housing_quality) -->
+<!-- #  -->
+<!-- # spag <- rbind(raw.s, base.s) -->
+<!-- #  -->
+<!-- # spaghetti_plot(spag, 'housing_quality', -->
+<!-- #                save = shall.we.save, -->
+<!-- #                save.path = save.path) -->
+<!-- #  -->
+<!-- # rm(raw.s, base.s, spag) -->
+<!-- ``` -->
+
+<!-- ## Housing Tenure -->
+
+<!-- ```{r} -->
+<!-- raw.tenure <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, housing_tenure) %>% -->
+<!--   group_by(time, housing_tenure) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'final_US') -->
+
+<!-- base.tenure <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, housing_tenure) %>% -->
+<!--   group_by(time, housing_tenure) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'baseline_output') -->
+
+<!-- # merge before plot -->
+<!-- tenure <- rbind(raw.tenure, base.tenure) -->
+<!-- tenure$housing_tenure <- as.factor(tenure$housing_tenure) -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = tenure, mapping = aes(x = time, y = n, group = housing_tenure, colour = housing_tenure)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Housing Tenure', subtitle = 'Counts by Level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
+
+<!-- tenure.norm <- tenure %>% -->
+<!--   group_by(time) %>% -->
+<!--   mutate(total = sum(n)) %>% -->
+<!--   mutate(prct = (n / total)) -->
+
+<!-- ggplot(data = tenure.norm, mapping = aes(x = time, y = prct, fill=housing_tenure)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Housing Tenure') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
+
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'housing_tenure.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
+<!-- } -->
+
+<!-- rm(raw.tenure, base.tenure, tenure, tenure.norm) -->
+<!-- ``` -->
+
+<!-- ## Neighbourhood Safety -->
+
+<!-- ```{r} -->
+<!-- raw.neighbour <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, neighbourhood_safety) %>% -->
+<!--   group_by(time, neighbourhood_safety) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'final_US') -->
+
+<!-- base.neighbour <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, neighbourhood_safety) %>% -->
+<!--   group_by(time, neighbourhood_safety) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'baseline_output') -->
+
+<!-- # merge before plot -->
+<!-- neighbour <- rbind(raw.neighbour, base.neighbour) -->
+<!-- neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety) -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
+
+<!-- neighbour.norm <- neighbour %>% -->
+<!--   group_by(time) %>% -->
+<!--   filter(neighbourhood_safety != -9) %>% -->
+<!--   mutate(total = sum(n)) %>% -->
+<!--   mutate(prct = (n / total)) -->
+
+<!-- ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Neighbourhood Safety') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
+
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'neighbourhood_safety.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
+<!-- } -->
+
+<!-- #rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm) -->
+<!-- ``` -->
+
+<!-- ### Spaghetti -->
+
+<!-- ```{r} -->
+<!-- # raw.s <- raw.dat %>% -->
+<!-- #   select(pidp, age, time, neighbourhood_safety) -->
+<!-- # base.s <- base.dat %>% -->
+<!-- #   select(pidp, age, time, neighbourhood_safety) -->
+<!-- #  -->
+<!-- # spag <- rbind(raw.s, base.s) -->
+<!-- #  -->
+<!-- # spaghetti_plot(spag, 'neighbourhood_safety', -->
+<!-- #                save = shall.we.save, -->
+<!-- #                save.path = save.path) -->
+<!-- #  -->
+<!-- # rm(raw.s, base.s, spag) -->
+<!-- ``` -->
+
+<!-- ## Loneliness -->
+
+<!-- ```{r} -->
+<!-- raw.loneliness <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, loneliness) %>% -->
+<!--   group_by(time, loneliness) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'final_US') -->
+
+<!-- base.loneliness <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, loneliness) %>% -->
+<!--   group_by(time, loneliness) %>% -->
+<!--   count() %>% -->
+<!--   mutate(source = 'baseline_output') -->
+
+<!-- # merge before plot -->
+<!-- loneliness <- rbind(raw.loneliness, base.loneliness) -->
+<!-- loneliness$loneliness <- as.factor(loneliness$loneliness) -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Loneliness', subtitle = 'Counts by level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
+
+<!-- loneliness.norm <- loneliness %>% -->
+<!--   group_by(time) %>% -->
+<!--   filter(loneliness != -9) %>% -->
+<!--   mutate(total = sum(n)) %>% -->
+<!--   mutate(prct = (n / total)) -->
+
+<!-- ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Loneliness') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
+
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'loneliness.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
+<!-- } -->
+
+<!-- rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm) -->
+<!-- ``` -->
+
+<!-- ### Spaghetti -->
+
+<!-- ```{r} -->
+<!-- # raw.s <- raw.dat %>% -->
+<!-- #   select(pidp, age, time, loneliness) -->
+<!-- # base.s <- base.dat %>% -->
+<!-- #   select(pidp, age, time, loneliness) -->
+<!-- #  -->
+<!-- # spag <- rbind(raw.s, base.s) -->
+<!-- #  -->
+<!-- # spaghetti_plot(spag, 'loneliness', -->
+<!-- #                save = shall.we.save, -->
+<!-- #                save.path = save.path) -->
+<!-- #  -->
+<!-- # rm(raw.s, base.s, spag) -->
+<!-- ``` -->
+
+<!-- ## Nutrition Quality -->
+
+<!-- TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11 -->
+
+<!-- ```{r} -->
+<!-- #  nutriton quality line/boxplots. -->
+<!-- handover_boxplots(raw.dat, base.dat, 'nutrition_quality') -->
+<!-- handover_lineplots(raw.dat, base.dat, 'nutrition_quality') -->
+
+<!-- # Try a version where final_US is limited to only those present from wave 1 -->
+<!-- # onwards because the sample refreshments are messing with the plot -->
+<!-- # raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009] -->
+<!-- #  -->
+<!-- # raw.nut2 <- raw.dat %>% -->
+<!-- #   dplyr::select(pidp, time, nutrition_quality) %>% -->
+<!-- #   filter(pidp %in% raw.wave1) %>% -->
+<!-- #   filter(nutrition_quality >= 0) %>% -->
+<!-- #   group_by(time) %>% -->
+<!-- #   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>% -->
+<!-- #   mutate(source = 'final_US') -->
+<!-- #  -->
+<!-- # base.nut2 <- base.dat %>% -->
+<!-- #   dplyr::select(pidp, time, nutrition_quality) %>% -->
+<!-- #   filter(pidp %in% raw.wave1) %>% -->
+<!-- #   group_by(time) %>% -->
+<!-- #   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>% -->
+<!-- #   mutate(source = 'baseline_output') -->
+<!-- #  -->
+<!-- # nutrition_quality2 <- rbind(raw.nut2, base.nut2) -->
+<!-- #  -->
+<!-- # # Now plot -->
+<!-- # ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) + -->
+<!-- #   geom_line() + -->
+<!-- #   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!-- #   labs(title = 'Nutrition Quality') + -->
+<!-- #   xlab('Year') + -->
+<!-- #   ylab('Nutrition Quality') -->
+<!-- #  -->
+<!-- # if (shall.we.save) { -->
+<!-- #   ggsave(filename = 'nutrition_quality_wav1.png', -->
+<!-- #        plot = last_plot(), -->
+<!-- #        path = save.path) -->
+<!-- # } -->
+<!-- #  -->
+<!-- # rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2, -->
+<!-- #     nutrition_quality2) -->
+<!-- ``` -->
+
+<!-- ### Spaghetti -->
+
+<!-- ```{r} -->
+<!-- # raw.nut <- raw.dat %>% -->
+<!-- #   select(pidp, age, time, nutrition_quality) -->
+<!-- # base.nut <- base.dat %>% -->
+<!-- #   select(pidp, age, time, nutrition_quality) -->
+<!-- #  -->
+<!-- # nut.spag <- rbind(raw.nut, base.nut) -->
+<!-- #  -->
+<!-- # spaghetti_plot(nut.spag, 'nutrition_quality', -->
+<!-- #                save = shall.we.save, -->
+<!-- #                save.path = save.path) -->
+<!-- #  -->
+<!-- #  -->
+<!-- # density_ridges(nut.spag, "nutrition_quality",  -->
+<!-- #                save = T,  -->
+<!-- #                save.path = save.path) -->
+<!-- #  -->
+<!-- # rm(raw.nut, base.nut, nut.spag) -->
+<!-- ``` -->
+
+<!-- ## Physical Health -->
+
+<!-- NOTE: At present, physical health is not predicted or transitioned. -->
+
+<!-- ```{r} -->
+<!-- # first figure out how to plot final_US -->
+<!-- # start with hh_income -->
+<!-- raw.phealth <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'final_US') -->
+
+<!-- base.phealth <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'baseline_output') -->
+
+<!-- # merge before plot -->
+<!-- phealth <- rbind(raw.phealth, base.phealth) -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Physical Health', subtitle = 'Full Sample') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Average') -->
+
+<!-- ## Try a version where final_US is limited to only those present from wave 1 -->
+<!-- # onwards because the sample refreshments are messing with the plot -->
+<!-- raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009] -->
+
+<!-- raw.phealth2 <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   filter(pidp %in% raw.wave1) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'final_US') -->
+
+<!-- base.phealth2 <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   filter(pidp %in% raw.wave1) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'baseline_output') -->
+
+<!-- phealth2 <- rbind(raw.phealth2, base.phealth2) -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Physical Health') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Average') -->
+
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'physical_health_wav1.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
+<!-- } -->
+
+<!-- #raw.phealth.check <- raw.dat %>% -->
+<!-- #  select(pidp, time, phealth) %>% -->
+<!-- #  filter(time > 2009) %>% -->
+<!-- #  filter(pidp %in% raw.wave1) -->
+
+<!-- #base.phealth.check <- base.dat %>% -->
+<!-- #  select(pidp, time, phealth) %>% -->
+<!-- #  filter(time > 2009) %>% -->
+<!-- #  filter(pidp %in% raw.wave1) -->
+
+<!-- rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2) -->
+<!-- #rm(raw.phealth.check, base.phealth.check) -->
+<!-- ``` -->
+
+<!-- ### Spaghetti -->
+
+<!-- ```{r} -->
+<!-- # raw.s <- raw.dat %>% -->
+<!-- #   select(pidp, age, time, phealth) -->
+<!-- # base.s <- base.dat %>% -->
+<!-- #   select(pidp, age, time, phealth) -->
+<!-- #  -->
+<!-- # spag <- rbind(raw.s, base.s) -->
+<!-- #  -->
+<!-- # spaghetti_plot(spag, 'phealth', -->
+<!-- #              save = shall.we.save, -->
+<!-- #              save.path = save.path) -->
+<!-- #  -->
+<!-- # rm(raw.s, base.s, spag) -->
+<!-- ``` -->
+
+<!-- ## Education -->
+
+<!-- ```{r} -->
+<!-- prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state') -->
+
+<!-- var <- prepped.list$var -->
+<!-- norm <- prepped.list$norm -->
+
+<!-- tit <- 'Education State' -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = tit, subtitle = 'Counts by Level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
+
+<!-- ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = tit) + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
+
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'education_state.png', -->
+<!--          plot = last_plot(), -->
+<!--          path = save.path) -->
+<!-- } -->
+
+<!-- rm(prepped.list, var, norm, tit) -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- pivoted <- combine_and_pivot_long(df1 = base.dat, -->
+<!--                                        df1.name = 'simulated', -->
+<!--                                        df2 = raw.dat, -->
+<!--                                        df2.name = 'raw', -->
+<!--                                        var = 'education_state') -->
+
+<!-- cv_ordinal_plots(pivoted.df = pivoted, -->
+<!--                  var = 'education_state', -->
+<!--                  save = shall.we.save, -->
+<!--                  save.path = save.path) -->
+<!-- ``` -->
+
+<!-- ### Spaghetti -->
+
+<!-- ```{r} -->
+<!-- # raw.s <- raw.dat %>% -->
+<!-- #   select(pidp, age, time, education_state) -->
+<!-- # base.s <- base.dat %>% -->
+<!-- #   select(pidp, age, time, education_state) -->
+<!-- #  -->
+<!-- # spag <- rbind(raw.s, base.s) -->
+<!-- #  -->
+<!-- # spaghetti_plot(spag, 'education_state', -->
+<!-- #                save = shall.we.save, -->
+<!-- #                save.path = save.path) -->
+<!-- #  -->
+<!-- # rm(raw.s, base.s, spag) -->
+<!-- ``` -->
+
+<!-- ## nkids Household -->
+
+<!-- ```{r} -->
+<!-- handover_boxplots(raw.dat, base.dat, 'nkids') -->
+<!-- handover_lineplots(raw.dat, base.dat, 'nkids') -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- raw.s <- raw.dat %>% -->
+<!--   select(pidp, age, time, nkids) -->
+<!-- base.s <- base.dat %>% -->
+<!--   select(pidp, age, time, nkids) -->
+
+<!-- spag <- rbind(raw.s, base.s) -->
+
+<!-- spaghetti_plot(spag, 'nkids', -->
+<!--                save = shall.we.save, -->
+<!--                save.path = save.path) -->
+
+<!-- rm(raw.s, base.s, spag) -->
+<!-- ``` -->
+
+<!-- ## nkids Max -->
+
+<!-- ```{r} -->
+<!-- # first figure out how to plot final_US -->
+<!-- # start with hh_income -->
+<!-- raw.nkids_max <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, nkids) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(max_nkids = max(nkids)) %>% -->
+<!--   mutate(source = 'final_US') -->
+
+<!-- base.nkids_max <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, nkids) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(max_nkids = max(nkids)) %>% -->
+<!--   mutate(source = 'baseline_output') -->
+
+<!-- # merge before plot -->
+<!-- max_nkids <- rbind(raw.nkids_max, base.nkids_max) -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = max_nkids, mapping = aes(x = time, y = max_nkids, group = source, colour = source)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Max nkids', subtitle = 'Full Sample') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Average') -->
+<!-- ``` -->
+
+<!-- ## Parity -->
+
+<!-- ```{r} -->
+<!-- base.parity <- base.dat %>% -->
+<!--   filter(sex == "Female") -->
+
+<!-- raw.parity <- raw.dat %>% -->
+<!--   filter(sex == "Female") -->
+
+<!-- prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind') -->
+
+<!-- var <- prepped.list$var -->
+<!-- norm <- prepped.list$norm -->
+
+<!-- tit <- 'Parity (total no. of children)' -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = tit, subtitle = 'Counts by Level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
+
+<!-- ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = tit) + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
+
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'parity.png', -->
+<!--          plot = last_plot(), -->
+<!--          path = save.path) -->
+<!-- } -->
+
+<!-- rm(prepped.list, var, norm, tit) -->
+<!-- ``` -->
+<!-- ```{r} -->
+<!-- pivoted <- combine_and_pivot_long(df1 = base.parity, -->
+<!--                                   df1.name = 'simulated',  -->
+<!--                                   df2 = raw.parity,  -->
+<!--                                   df2.name = 'raw',  -->
+<!--                                   var = 'nkids_ind') -->
+
+<!-- cv_ordinal_plots(pivoted.df = pivoted,  -->
+<!--                  var = 'nkids_ind', -->
+<!--                  save = shall.we.save, -->
+<!--                  save.path = save.path) -->
+<!-- ``` -->
+
+<!-- ### Spaghetti -->
+
+<!-- ```{r} -->
+<!-- raw.s <- raw.parity %>% -->
+<!--   select(pidp, age, time, nkids_ind) -->
+<!-- base.s <- base.parity %>% -->
+<!--   select(pidp, age, time, nkids_ind) -->
+
+<!-- spag <- rbind(raw.s, base.s) -->
+
+<!-- spaghetti_plot(spag, 'nkids_ind', -->
+<!--                save = shall.we.save, -->
+<!--                save.path = save.path) -->
+
+<!-- rm(raw.s, base.s, spag) -->
+<!-- ``` -->
+
+<!-- ## Hourly Wage -->
+
+<!-- ```{r} -->
+<!-- handover_boxplots(raw.dat, base.dat, 'hourly_wage') -->
+<!-- handover_lineplots(raw.dat, base.dat, 'hourly_wage') -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- raw.s <- raw.dat %>% -->
+<!--   select(pidp, age, time, hourly_wage) -->
+<!-- base.s <- base.dat %>% -->
+<!--   select(pidp, age, time, hourly_wage) -->
+
+<!-- spag <- rbind(raw.s, base.s) -->
+
+<!-- spaghetti_plot(spag, 'hourly_wage', -->
+<!--                save = shall.we.save, -->
+<!--                save.path = save.path) -->
+
+<!-- # now a version limited to 0-100 -->
+<!-- spag <- spag %>% -->
+<!--   filter(hourly_wage <= 300) -->
+<!-- spaghetti_plot(spag, 'hourly_wage', -->
+<!--                save = shall.we.save, -->
+<!--                save.path = save.path) -->
+
+<!-- rm(raw.s, base.s, spag) -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- # some basic statistics about hourly_wage variable -->
+<!-- print("Some basic statistics on hourly_wage. These are all for 2020.") -->
+<!-- raw.2020 <- raw.dat %>% filter(time == 2020) -->
+<!-- print('All living people in 2020') -->
+<!-- print(paste0("Number of people alive in 2020: ", nrow(raw.2020))) -->
+<!-- # number individuals with an hourly_wage > 0 -->
+<!-- print('People not in work') -->
+<!-- print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed')))) -->
+<!-- print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0))) -->
+
+<!-- # Number in work -->
+<!-- print('People in work') -->
+<!-- print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed')))) -->
+<!-- print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0))) -->
+
+<!-- # Extreme hourly_wage values -->
+<!-- print('Extreme hourly wage values: HIGH') -->
+<!-- print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30))) -->
+<!-- print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50))) -->
+<!-- print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100))) -->
+<!-- print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500))) -->
+<!-- print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000))) -->
+<!-- print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000))) -->
+
+<!-- raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0) -->
+<!-- print('Extreme hourly wage values: LOW (non-zero)') -->
+<!-- print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20))) -->
+<!-- print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10))) -->
+<!-- print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5))) -->
+<!-- print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1))) -->
+<!-- ``` -->
+
+<!-- ## S7 Labour State -->
+
+<!-- ```{r} -->
+<!-- prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state') -->
+
+<!-- lab.state <- prepped.list$var -->
+<!-- lab.state.norm <- prepped.list$norm -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'S7 Labour State', subtitle = 'Counts by Level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
+
+<!-- ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) + -->
+<!--   geom_bar(stat = 'identity') + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'S7 Labour State') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Proportion') -->
+
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'S7_labour_state.png', -->
+<!--          plot = last_plot(), -->
+<!--          path = save.path) -->
+<!-- } -->
+
+<!-- rm(prepped.list, lab.state, lab.state.norm) -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- pivoted <- combine_and_pivot_long(df1 = base.dat,  -->
+<!--                                        df1.name = 'simulated',  -->
+<!--                                        df2 = raw.dat,  -->
+<!--                                        df2.name = 'raw',  -->
+<!--                                        var = 'S7_labour_state') -->
+
+<!-- cv_ordinal_plots(pivoted.df = pivoted,  -->
+<!--                  var = 'S7_labour_state', -->
+<!--                  save = shall.we.save, -->
+<!--                  save.path = save.path) -->
+<!-- ``` -->
+
+<!-- ## Child Ages -->
+
+<!-- ```{r} -->
+<!-- raw.child.ages <- raw.dat %>% -->
+<!--   dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>% -->
+<!--   filter(time > 2013 & child_ages != 'childless') %>% -->
+<!--   group_by(time, hidp) %>% -->
+<!--   drop_na() %>% -->
+<!--   summarise(child_ages = find_mode(child_ages)) -->
+
+<!-- r.s<- strsplit(raw.child.ages$child_ages, "_") -->
+
+<!-- raw.child.ages.expanded <- data.frame(time = rep(raw.child.ages$time, sapply(r.s, length)), expanded_child_ages = unlist(r.s)) -->
+<!-- raw.child.ages.expanded <- raw.child.ages.expanded %>% -->
+<!--   group_by(time, expanded_child_ages) %>% -->
+<!--   summarise(age_counts = n()) %>% -->
+<!--   mutate(source = 'final_US') %>% -->
+<!--   filter(expanded_child_ages <= 16) -->
+
+<!-- base.child.ages <- base.dat %>% -->
+<!--   dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   group_by(time, hidp) %>% -->
+<!--   drop_na() %>% -->
+<!--   summarise(child_ages = find_mode(child_ages)) -->
+
+<!-- b.s<- strsplit(base.child.ages$child_ages, "_") -->
+
+<!-- base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(b.s, length)), expanded_child_ages = unlist(b.s)) -->
+<!-- base.child.ages.expanded <- base.child.ages.expanded %>% -->
+<!--   group_by(time, expanded_child_ages) %>% -->
+<!--   summarise(age_counts = n()) %>% -->
+<!--   mutate(source = 'baseline') -->
+
+<!-- combined <- rbind(raw.child.ages.expanded, base.child.ages.expanded) -->
+
+<!-- ggplot(data = combined, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept = start.year) + -->
+<!--   labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') + -->
+<!--   scale_colour_viridis_d() + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
+
+<!-- ggplot(data = combined, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept = start.year) + -->
+<!--   labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') + -->
+<!--   scale_colour_viridis_d() + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
+
+<!-- base.child.ages.nkids <- base.dat %>% -->
+<!--   group_by(time, hidp) %>% -->
+<!--   summarise(nkids_counts = mean(nkids)) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(nkids_by_year = sum(nkids_counts)) %>% -->
+<!--   mutate(source = 'baseline') -->
+
+<!-- raw.child.ages.nkids <- raw.dat %>% -->
+<!--   group_by(time, hidp) %>% -->
+<!--   summarise(nkids_counts = mean(nkids)) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(nkids_by_year = sum(nkids_counts)) %>% -->
+<!--   mutate(source = 'final_US') -->
+
+<!-- combined.nkids <- rbind(base.child.ages.nkids, raw.child.ages.nkids) -->
+
+<!-- ggplot(data = combined.nkids, mapping = aes(x = time, y = nkids_by_year, group = source, colour = source)) + -->
+<!--   geom_line() + -->
+<!--   labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Count') -->
+
+<!-- ``` -->
 
@@
 ```{r}
-handover_boxplots(raw.dat, base.dat, 'ncigs')
 handover_lineplots(raw.dat, base.dat, "ncigs")
@@
 
+handover_boxplots(raw.ncigs, base.ncigs, 'ncigs')
+
 ncigs.spag <- rbind(raw.ncigs, base.ncigs) # get all smokers.

### 2024-04-08 minos/validation/handovers.Rmd
Added handovers plots for age structure and population counts

--- 2024-03-15 minos/validation/handovers.Rmd
@@
 
-out.path <- here::here('output', 'default_config/')
-base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
+out.path <- here::here('output', 'glasgow_scaled/')
+base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE, drop.zero.weight = TRUE)
 ```
@@
 
+# Age Structure
+
+```{r}
+# assign to age_bucket in raw data
+cut_bins <- c(-1, 15, 19, 24, 29, 44, 59, 74, 200)
+cut_labels <- c("0to15", "16to19", "20to24", "25to29", "30to44", "45to59", "60to74", "75plus")
+
+raw.dat$age_bucket <- cut(raw.dat$age, 
+                          breaks = cut_bins, 
+                          labels = cut_labels)
+
+handover_ordinal(raw.dat, base.dat, var = 'age_bucket', save = shall.we.save)
+```
+
+# Population Counts
+
+```{r}
+raw.alive <- raw.dat %>%
+  group_by(time) %>%
+  summarise(n = n())
+
+base.alive <- base.dat %>%
+  group_by(time) %>%
+  summarise(n = n())
+
+#handover_boxplots(raw.alive, base.alive, 'n')
+handover_lineplots(raw.alive, base.alive, "n")
+
+rm(raw.alive, base.alive)
+```
+
+# Universal Credit
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'universal_credit', save = shall.we.save)
+```
+
 # PATHWAYS

### 2024-04-08 minos/validation/handovers.Rmd

@@
 out.path <- here::here('output', 'glasgow_scaled/')
-base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE, drop.zero.weight = TRUE)
+#out.path <- here::here('output', 'default_config/')
+base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
 ```
@@
 
+### Income Inequality
+
+```{r}
+handover_inequality_80_20(raw.dat, base.dat, var = 'hh_income')
+```
+
 ## Council Tax

### 2024-04-08 minos/validation/handovers.Rmd
Got council tax working again with some plots in handovers to check it

@@
 
-out.path <- here::here('output', 'glasgow_scaled/')
-#out.path <- here::here('output', 'default_config/')
+#out.path <- here::here('output', 'glasgow_scaled/')
+out.path <- here::here('output', 'default_config/')
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
@@
 handover_ordinal(raw.dat, base.dat, var = 'age_bucket', save = shall.we.save)
+```
+
+## Max Age
+
+```{r}
+raw.maxAge <- raw.dat %>%
+  group_by(time) %>%
+  summarise(max_age = max(age))
+
+base.maxAge <- base.dat %>%
+  group_by(time) %>%
+  summarise(max_age = max(age))
+
+handover_lineplots(raw.maxAge, base.maxAge, 'max_age')
 ```

### 2024-04-08 minos/data_generation/generate_composite_vars.py

@@ -231,8 +231,7 @@ def generate_hh_income(data):
     data = US_utils.inflation_adjustment(data, "hh_income")
 
     # now drop the intermediates
-    data.drop(labels=['hh_rent', 'hh_mortgage', 'outgoings', 'hh_netinc', 'oecd_equiv',
-                      'council_tax_lower', 'council_tax_upper', 'council_tax_draw'],
+    data.drop(labels=['hh_rent', 'hh_mortgage', 'outgoings', 'hh_netinc', 'oecd_equiv'],
               axis=1,
               inplace=True)
 

### 2024-04-10 minos/validation/housing_handovers.Rmd
get heat working again.

--- 2024-03-14 minos/validation/housing_handovers.Rmd
@@
 handover_lineplots(raw.dat, base.dat, "SF_12")
-# 
-# raw.sf12 <- raw.dat %>% 
-#   dplyr::select(pidp, time, SF_12) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.sf12 <- base.dat %>%
-#   dplyr::select(pidp, time, SF_12) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# # merge before plot
-# sf12 <- rbind(raw.sf12, base.sf12)
-# 
-# # Now plot
-# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-#   geom_smooth() +
-#   #geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
-#   xlab('Year') +
-#   ylab('SF12')
-# 
-# ## Try a version where final_US is limited to only those present from wave 1 
-# # onwards because the sample refreshments are messing with the plot
-# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-# 
-# raw.sf12.2 <- raw.dat %>% 
-#   dplyr::select(pidp, time, SF_12) %>%
-#   filter(pidp %in% raw.sf12.wave1) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.sf12.2 <- base.dat %>%
-#   dplyr::select(pidp, time, SF_12) %>%
-#   filter(pidp %in% raw.sf12.wave1) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
-# 
-# # Now plot
-# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-#   geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
-#   xlab('Year') +
-#   ylab('SF12')
-# 
-# if (shall.we.save) {
-#   ggsave(filename = 'SF12_wav1.png',
-#        plot = last_plot(),
-#        path = save.path)
-# }
-# 
-# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
+
+raw.sf12 <- raw.dat %>%
+  dplyr::select(pidp, time, SF_12) %>%
+  group_by(time) %>%
+  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  mutate(source = 'final_US')
+
+base.sf12 <- base.dat %>%
+  dplyr::select(pidp, time, SF_12) %>%
+  group_by(time) %>%
+  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+sf12 <- rbind(raw.sf12, base.sf12)
+
+# Now plot
+ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+  geom_smooth() +
+  #geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
+  xlab('Year') +
+  ylab('SF12')
+
+## Try a version where final_US is limited to only those present from wave 1
+# onwards because the sample refreshments are messing with the plot
+raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+
+raw.sf12.2 <- raw.dat %>%
+  dplyr::select(pidp, time, SF_12) %>%
+  filter(pidp %in% raw.sf12.wave1) %>%
+  group_by(time) %>%
+  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  mutate(source = 'final_US')
+
+base.sf12.2 <- base.dat %>%
+  dplyr::select(pidp, time, SF_12) %>%
+  filter(pidp %in% raw.sf12.wave1) %>%
+  group_by(time) %>%
+  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  mutate(source = 'baseline_output')
+
+sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
+
+# Now plot
+ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Mental Wellbeing (SF12 MCS)') +
+  xlab('Year') +
+  ylab('SF12')
+
+if (shall.we.save) {
+  ggsave(filename = 'SF12_wav1.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
 ```
@@
   group_by(time, hidp) %>%
+  drop_na() %>%
   summarise(child_ages = find_mode(child_ages))

### 2024-04-11 minos/outcomes/QALY_comparison2.Rmd
Improved QALY_comparison visualisation functions and script

@@
 
-require(tidyverse)
-require(ggplot2)
-require(knitr)
-require(here)
-require(MESS)
-require(scales)
+library(tidyverse)
+library(ggplot2)
+library(knitr)
+library(here)
+library(MESS)
+library(scales)
 
@@
 # #
-# experiment <- 'arc_batch_10'
+#experiment <- 'default_batch_10'
+# experiment <- 'default_config'
 # baseline <- 'baseline'
-# ints <- c('25UniversalCredit', '50UniversalCredit', '75UniversalCredit', '100UniversalCredit')
-# start.year <- 2020
+# #ints <- c('25UniversalCredit', '50UniversalCredit', '75UniversalCredit', '100UniversalCredit')
+# ints <- c('25All', '50All', '75All', '100All')
+# #ints <- c('25All', '50All', '100All')
+# start.year <- 2021
 ```
@@
 ```{r}
-# base <- read.csv('qalys_base.csv')
-# int <- read.csv('qalys_25All.csv')
-# 
-# combined <- rbind(base, int)
+# out.path <- here::here('output', 'tmp_down2/')
 # 
 # baseline <- 'baseline'
-# intervention <- '25All'
+# ints <- c('25All', '50All', '75All', '100All')
+# 
+# start.year <- 2021
+# 
+# expts <- c(baseline, ints)
+# 
+# combined <- data.frame()
+# for (expt in expts) {
+#   data <- read.csv(paste0(out.path, expt, '_qalys.csv'))
+#   combined <- rbind(combined, data)
+# }
 ```
@@
 
-Just going to plot some things here like how many people affected by an intervention and what the mean / total boost amounts look like.
+## Boosted Population
 
@@
 combined.pop_boosted <- combined %>%
-  group_by(year, run_id, intervention) %>%
-  summarise(pop_boosted = sum(pop_boosted))
+  group_by(year, intervention, run_id) %>%
+  summarise(pop_boosted = sum(pop_boosted, na.rm = TRUE))
 
@@
 
-ggplot(combined.pop_boosted, aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
-  geom_smooth() +
+combined.pop_boosted.boxplot <- combined.pop_boosted %>%
+  filter(year != start.year) %>%
+  filter(intervention != baseline)
+
+ggplot(combined.pop_boosted.boxplot, aes(x = year, y = pop_boosted, group = interaction(year, intervention), color = intervention)) +
+  geom_boxplot() +
   labs(title = 'Number Individuals Receiving Intervention')
+
+```
+
+## Boost Amount
+
+```{r}
 
@@
 QALY_comparison(combined, ints)
+```
+
+```{r}
+# #QALY_comparison <- function(combined, ints) {
+#   
+# p1 <- ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
+#   geom_smooth() +
+#   labs(title = 'QALYs per year')
+# print(p1)
+# 
+# # Now change from baseline
+# combined.QALY.change <- combined %>%
+#   select(run_id, year, intervention, QALYs) %>%
+#   pivot_wider(names_from = 'intervention',
+#               values_from = 'QALYs') %>%
+#   #mutate(QALYs = .data[[int.name]] - .data[[base.name]]) %>%
+#   mutate(across(all_of(ints), ~.x - .data[[baseline]], .names = "QALYs_{.col}")) %>%
+#   select(run_id, year, contains('QALYs')) %>%
+#   pivot_longer(cols = contains('QALYs'),
+#                names_prefix = 'QALYs_',
+#                names_to = 'scenario',
+#                values_to = 'QALYs')
+# 
+# p2 <- ggplot(data = combined.QALY.change, aes(x = year, y = QALYs, group = scenario, color = scenario, fill = scenario)) +
+#   geom_hline(yintercept = 0, linetype = 'dashed') +
+#   geom_smooth() +
+#   labs(title = 'QALY change')
+# print(p2)
+# 
+# combined.QALY.change$year <- as.factor(combined.QALY.change$year)
+# combined.QALY.change$scenario <- as.factor(combined.QALY.change$scenario)
+# 
+# p3 <- ggplot(data = combined.QALY.change, aes(x = year, y = QALYs, group = interaction(year, scenario), fill = scenario)) +
+#   geom_boxplot() +
+#   stat_summary(fun=mean, geom="line", aes(group=scenario), linetype = 'dashed')  + 
+#   stat_summary(fun=mean, geom="point", aes(group=scenario))
+# print(p3)
+# 
+# 
+# 
+# combined.QALY.change.confint <- combined.QALY.change %>%
+#   group_by(year, scenario) %>%
+#   summarise(n = n(),
+#             mean_QALY_change = mean(QALYs),
+#             margin = qt(0.975, df = n - 1) * (sd(QALYs) / sqrt(n)),
+#             lower = mean_QALY_change - margin,
+#             upper = mean_QALY_change + margin)
+# 
+# p4 <- ggplot(combined.QALY.change.confint, aes(x = year, y = mean_QALY_change, group = scenario, color = scenario, fill = scenario)) +  # 
+#   geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.5) +
+#   geom_line(aes(color = scenario), linetype = 'dashed') +
+#   geom_hline(yintercept = 0, linetype = 'dashed') +
+#   labs(title = 'QALY Change') +
+#   xlab('Year') +
+#   ylab('QALYs')
+# print(p4)
+# 
+# 
+# #}
 ```

### 2024-04-18 minos/testing/PCS_QALYs.Rmd
Added plots to handovers for visualising counts of extreme old age groups. Also started an R Notebook for the PCS QALY work

---
title: "Physical Component Score and QALYs"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

# Introduction

```{r "setup-environment", include=False}
require(tidyverse)
require(ggplot2)
require(ggridges) # for densities over time plots. 
require(knitr)
require(here)
require(dplyr)
require(tidyr)
require(purrr)
require(gghighlight)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

```{r "setup-utils", include=False}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
source(here::here('minos', 'utils_qaly.R'))
```

```{r "setup-parameters", include=False}
#experiment <- 'glasgow_scaled'
#baseline <- 'baseline'
#ints <- c('50All', '50UniversalCredit')
#start.year <- 2020
```

```{r "setup-data", include=False}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

#out.path <- here::here('output', 'glasgow_scaled/')
out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

# Tran

```{r}

```

### 2024-04-18 minos/validation/handovers.Rmd
Added plots to handovers for visualising counts of extreme old age groups. Also started an R Notebook for the PCS QALY work

@@
 handover_lineplots(raw.maxAge, base.maxAge, 'max_age')
+
+## Check counts in very old age groups
+brks = c(75, 80, 85, 90, 95, 100, 105, 110)
+lbls = c("75to80", "80to85", "85to90", "90to95", "95to100", "100to105", "105to110")
+
+raw.countOldAge <- raw.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls)) %>%
+  group_by(time, age_group) %>%
+  summarise(age_group_counts = n()) %>%
+  mutate(source = 'observed')
+
+base.countOldAge <- base.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls)) %>%
+  group_by(time, age_group) %>%
+  summarise(age_group_counts = n()) %>%
+  mutate(source = 'predicted')
+
+combined <- rbind(raw.countOldAge, base.countOldAge)
+
+ggplot(combined, aes(x = time, y = age_group_counts, group = age_group, colour = age_group)) +
+  geom_line() +
+  geom_vline(xintercept = 2021, linetype = 'dashed') +
+  labs(title = 'Counts by older age group', subtitle = '75 to 110 by 5 year groups') +
+  xlab('Year') +
+  ylab('Count')
+
+raw.countOldAge <- raw.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls))
+
+base.countOldAge <- base.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls))
+
+handover_ordinal(raw.countOldAge, base.countOldAge, var = 'age_group', save = shall.we.save)
+
+```
+
+```{r}
+# Having a go at an age pyramid, hopefully animated
+
+brks = c(75, 80, 85, 90, 95, 100, 105, 110)
+lbls = c("75to80", "80to85", "85to90", "90to95", "95to100", "100to105", "105to110")
+
+var <- 'age_group'
+
+# start with calculating percentages
+#raw.oldAgePct
+#base.oldAgePct
+
+raw.oldAgePct <- raw.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls)) %>%
+  dplyr::select(time, age_group) %>%
+  group_by(time, age_group) %>%
+  count() %>%
+  mutate(source = 'predicted')
+
+base.oldAgePct <- base.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls)) %>%
+  dplyr::select(time, all_of(var)) %>%
+  #filter(!.data[[var]] %in% miss.values) %>%
+  group_by(time, .data[[var]]) %>%
+  count() %>%
+  mutate(source = 'observed')
+
+raw.oldAgePct[[var]] <- as.factor(raw.oldAgePct[[var]])
+base.oldAgePct[[var]] <- as.factor(base.oldAgePct[[var]])
+
+merged <- rbind(raw.oldAgePct, base.oldAgePct)
+merged[[var]] <- as.factor(merged[[var]])
+
+var.norm <- merged %>%
+    group_by(time) %>%
+    mutate(total = sum(n)) %>%
+    mutate(prct = (n / total) * 100)
 ```

### 2024-04-22 minos/validation/handovers.Rmd
Created some functions for plotting animated age pyramids, but leaving out of handovers for now as they dont render properly in html notebooks

--- 2024-04-08 minos/validation/handovers.Rmd
@@
 
-require(tidyverse)
-require(ggplot2)
-require(ggridges) # for densities over time plots. 
-require(knitr)
-require(here)
-require(dplyr)
-require(tidyr)
-require(purrr)
-require(gghighlight)
+library(tidyverse)
+library(ggplot2)
+library(ggridges) # for densities over time plots. 
+library(knitr)
+library(here)
+library(dplyr)
+library(tidyr)
+library(purrr)
+library(gghighlight)
+library(gganimate)
 
@@
 handover_lineplots(raw.maxAge, base.maxAge, 'max_age')
+```
+
+# Old Age Counts
+
+```{r}
+## Check counts in very old age groups
+brks = c(75, 80, 85, 90, 95, 100, 105, 110)
+lbls = c("75to80", "80to85", "85to90", "90to95", "95to100", "100to105", "105to110")
+
+raw.countOldAge <- raw.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls))
+
+base.countOldAge <- base.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls))
+
+handover_ordinal(raw.countOldAge, base.countOldAge, var = 'age_group', save = shall.we.save)
 ```

### 2024-04-23 minos/testing/PCS_QALYs.Rmd
Additions to the PCS QALY notebook for sharing around SIPHER

@@
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+
+trans.path <- here::here('data', 'transitions/')
 ```
 
-# Tran
+# PCS Pathways
+
+1.  Housing Quality
+2.  Nutrition Quality
+3.  Tobacco Use
+4.  Loneliness
+5.  Physical Activity (new)
+6.  Alcohol Use Disorders (new)
+
+## Transition Model
+
+The formula we use for estimating a transition model for PCS is shown below:
+
+> SF_12_PCS ~ scale(SF_12_PCS_last) + I(scale(SF_12_PCS_last)\*\*2) + factor(sex) + relevel(factor(ethnicity), ref = 'WBI') + scale(age) + I(scale(age)\*\*2) + relevel(factor(region), ref = 'Scotland') + relevel(factor(education_state), ref = "1") + factor(housing_quality) + scale(hh_income) + scale(nutrition_quality) + I(factor(ncigs>0)) + factor(loneliness) + factor(active) + factor(auditc) + (1|pidp) + time
+
+This can be grouped into categories: - Previous values - Demographics - Pathways - Random term
+
+We use a Linear Mixed-effects Model (LMM) to calculate transition probabilities
 
 ```{r}
+pcs.mod <- readRDS(file = paste0(trans.path, 'SF_12_PCS/lmm/SF_12_PCS_LMM.rds'))
 
+summary(pcs.mod)
 ```

### 2024-04-23 minos/validation/housing_handovers.Rmd
tweaking scripts for running transitions/make

@@
 
+## Heating
+
+```{r}
+raw.heating <- raw.dat %>%
+  dplyr::select(pidp, time, heating) %>%
+  group_by(time, heating) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.heating <- base.dat %>%
+  dplyr::select(pidp, time, heating) %>%
+  group_by(time, heating) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+heating <- rbind(raw.heating, base.heating)
+heating$heating <- as.factor(heating$heating)
+
+# Now plot
+ggplot(data = heating, mapping = aes(x = time, y = n, group = heating, colour = heating)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Heating', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+heating.norm <- heating %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = heating.norm, mapping = aes(x = time, y = prct, fill=heating)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Heating') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'heating.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.heating, base.heating, heating, heating.norm)
+```
+
 ## Housing Tenure

### 2024-04-23 scripts/arc_run_longitudinal_transitions.sh

@@ -10,7 +10,7 @@
 ## Email if a run aborts
 #$ -m a
 ## Select memory
-#$ -l h_vmem=4G # was 15 for big runs
+#$ -l h_vmem=2G # was 15 for big runs
 ## Choose cores. See arc website for more details. 5 high memory cores chosen here.
 #$ -pe smp 8
 ## Set logs directories

### 2024-05-01 minos/validation/housing_manchester_handovers.Rmd
adding notebook for manchestere pop handovers

--- 2024-04-23 minos/validation/housing_handovers.Rmd
@@
     intervention: ''
-title: "Housing Default Handovers"
+title: "Housing Manchester Handovers"
 output:
@@
 
-out.path <- here::here('output', 'energy_default_config/')
+out.path <- here::here('output', 'energy_manchester_scaled/')
 base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)

### 2024-05-14 minos/validation/handovers.Rmd
Added plots to check the relative and absolute poverty thresholds in handovers.Rmd

--- 2024-04-08 minos/validation/handovers.Rmd
@@
 ---
-
 title: "MINOS Handover Plots"
@@
 
-require(tidyverse)
-require(ggplot2)
-require(ggridges) # for densities over time plots. 
-require(knitr)
-require(here)
-require(dplyr)
-require(tidyr)
-require(purrr)
-require(gghighlight)
+library(tidyverse)
+library(ggplot2)
+library(ggridges) # for densities over time plots. 
+library(knitr)
+library(here)
+library(dplyr)
+library(tidyr)
+library(purrr)
+library(gghighlight)
+library(spatstat)
 
@@
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
+raw.dat <- raw.dat %>%
+  filter(weight > 0)
 
-#out.path <- here::here('output', 'glasgow_scaled/')
 out.path <- here::here('output', 'default_config/')
-base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+base.dat <- read_singular_local_out(out.path, 'baseline', 
+                                    drop.dead = TRUE, 
+                                    drop.zero.weight = TRUE)
+#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
 ```
@@
 
-# Age Structure
-
-```{r}
-# assign to age_bucket in raw data
-cut_bins <- c(-1, 15, 19, 24, 29, 44, 59, 74, 200)
-cut_labels <- c("0to15", "16to19", "20to24", "25to29", "30to44", "45to59", "60to74", "75plus")
-
-raw.dat$age_bucket <- cut(raw.dat$age, 
-                          breaks = cut_bins, 
-                          labels = cut_labels)
-
-handover_ordinal(raw.dat, base.dat, var = 'age_bucket', save = shall.we.save)
-```
-
-## Max Age
-
-```{r}
-raw.maxAge <- raw.dat %>%
-  group_by(time) %>%
-  summarise(max_age = max(age))
-
-base.maxAge <- base.dat %>%
-  group_by(time) %>%
-  summarise(max_age = max(age))
-
-handover_lineplots(raw.maxAge, base.maxAge, 'max_age')
-```
-
-# Population Counts
-
-```{r}
-raw.alive <- raw.dat %>%
-  group_by(time) %>%
-  summarise(n = n())
-
-base.alive <- base.dat %>%
-  group_by(time) %>%
-  summarise(n = n())
-
-#handover_boxplots(raw.alive, base.alive, 'n')
-handover_lineplots(raw.alive, base.alive, "n")
-
-rm(raw.alive, base.alive)
-```
-
-# Universal Credit
-
-```{r}
-handover_ordinal(raw.dat, base.dat, var = 'universal_credit', save = shall.we.save)
-```
-
 # PATHWAYS
@@
 ```{r}
-# raw.inc <- raw.dat %>%
-#   select(pidp, age, time, hh_income)
-# base.inc <- base.dat %>%
-#   select(pidp, age, time, hh_income)
-# 
-# income.spag <- rbind(raw.inc, base.inc)
-# 
-# density_ridges(income.spag, 'hh_income',
-#                save=shall.we.save, 
-#                save.path=save.path)
-# 
-# pidp_sample <- sample(unique(income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
-# income.spag.sample <- income.spag[which(income.spag$pidp %in% pidp_sample), ]
-# spaghetti_plot(income.spag.sample, 'hh_income',
-#                save = shall.we.save,
-#                save.path = save.path)
-# spaghetti_highlight_max_plot(income.spag.sample, 'hh_income',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.inc, base.inc, income.spag)
+raw.inc <- raw.dat %>%
+  select(pidp, age, time, hh_income)
+base.inc <- base.dat %>%
+  select(pidp, age, time, hh_income)
+
+income.spag <- rbind(raw.inc, base.inc)
+
+density_ridges(income.spag, 'hh_income',
+               save=TRUE, 
+               save.path=save.path)
+
+pidp_sample <- sample(unique(income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
+income.spag.sample <- income.spag[which(income.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(income.spag.sample, 'hh_income',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(income.spag.sample, 'hh_income',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.inc, base.inc, income.spag)
 ```
 
-### Income Inequality
+### Poverty Thresholds
 
+#### Relative
 ```{r}
-handover_inequality_80_20(raw.dat, base.dat, var = 'hh_income')
+rel.threshold.raw <- raw.dat %>%
+  select(time, weight, hh_income) %>%
+  group_by(time) %>%
+  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
+
+rel.threshold.base <- base.dat %>%
+  select(time, weight, hh_income) %>%
+  group_by(time) %>%
+  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6)) %>%
+  filter(time != 2021)
+
+rel.threshold <- rbind(rel.threshold.raw, rel.threshold.base)
+
+ggplot(data = rel.threshold, aes(x = time, y = poverty_threshold)) +
+  geom_col() +
+  geom_hline(yintercept = rel.threshold$poverty_threshold[rel.threshold$time == 2020], linetype='dotted') +
+  geom_vline(xintercept = start.year, linetype = 'dashed') +
+  labs(title = 'Relative poverty threshold over time') +
+  xlab('Year') +
+  ylab('Threshold')
+#rm(rel.threshold)
 ```
 
-## Council Tax
+#### Absolute
+```{r}
+raw.2010 <- raw.dat %>%
+  filter(time == 2010)
 
-```{r}
-handover_boxplots(raw.dat, base.dat, 'council_tax')
-handover_lineplots(raw.dat, base.dat, "council_tax")
+abs.threshold <- weighted.median(x = raw.2010$hh_income, 
+                                 w = raw.2010$weight, 
+                                 na.rm = TRUE)
+abs.threshold <- abs.threshold * 0.6
+
+print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
 ```
 
-## SF_12_MCS
+## SF12
 
@@
 ```{r}
-raw.sf12.m <- raw.dat %>%
-  select(pidp, age, time, SF_12_MCS)
-base.sf12.m <- base.dat %>%
-  select(pidp, age, time, SF_12_MCS)
+raw.sf12 <- raw.dat %>%
+  select(pidp, age, time, SF_12)
+base.sf12 <- base.dat %>%
+  select(pidp, age, time, SF_12)
 
-sf12.m.spag <- rbind(raw.sf12.m, base.sf12.m)
+sf12.spag <- rbind(raw.sf12, base.sf12)
 
-#sf12.m.spag.sample <- sf12.m.spag[which(sf12.m.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(sf12.m.spag, 'SF_12_MCS',
+sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(sf12.spag.sample, 'SF_12',
                save = shall.we.save,
                save.path = save.path)
-spaghetti_highlight_max_plot(sf12.m.spag, 'SF_12_MCS',
+spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
                save = shall.we.save,
@@
 
-density_ridges(sf12.m.spag, "SF_12_MCS", 
-               save = shall.we.save, 
+density_ridges(sf12.spag, "SF_12", 
+               save = T, 
                save.path = save.path)
 
-rm(raw.sf12.m, base.sf12.m, sf12.m.spag, sf12.m.spag.sample)
-```
-
-### Inequality
-
-```{r}
-handover_inequality_80_20(raw.dat, base.dat, var = 'SF_12_MCS')
-```
-
-## SF_12_PCS
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'SF_12_PCS')
-handover_lineplots(raw.dat, base.dat, "SF_12_PCS")
-```
-
-### Spaghetti
-
-```{r}
-raw.sf12.p <- raw.dat %>%
-  select(pidp, age, time, SF_12_PCS)
-base.sf12.p <- base.dat %>%
-  select(pidp, age, time, SF_12_PCS)
-
-sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)
-
-spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(sf12.p.spag, "SF_12_PCS", 
-               save = shall.we.save, 
-               save.path = save.path)
-
-rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
-```
-
-### Inequality
-
-```{r}
-handover_inequality_80_20(raw.dat, base.dat, var = 'SF_12_PCS')
-```
-
-### Histograms
-
-I have a hypothesis that the longer we run through simulation, the more simulants are predicted a negative PCS value which is then clipped to a 0.
-Histograms over a few snapshots of time should show if this is happening.
-
-```{r}
-pcs.2021 <- base.dat %>%
-  select(pidp, time, SF_12_PCS) %>%
-  filter(time == 2021)
-
-# pcs.2022 <- base.dat %>%
-#   select(pidp, time, SF_12_PCS) %>%
-#   filter(time == 2022)
-
-pcs.2025 <- base.dat %>%
-  select(pidp, time, SF_12_PCS) %>%
-  filter(time == 2025)
-
-pcs.2030 <- base.dat %>%
-  select(pidp, time, SF_12_PCS) %>%
-  filter(time == 2030)
-
-pcs.2036 <- base.dat %>%
-  select(pidp, time, SF_12_PCS) %>%
-  filter(time == 2036)
-
-merged <- rbind(pcs.2021, pcs.2025, pcs.2030, pcs.2036)
-merged$time <- as.factor(merged$time)
-
-ggplot(merged, aes(x = SF_12_PCS, group = time, colour = time, fill = time)) +
-  geom_histogram() +
-  labs(title = 'Distribution of SF_12_PCS')
-
-ggplot(merged, aes(x = SF_12_PCS, group = time, colour = time, fill = time)) +
-  geom_freqpoly() +
-  labs(title = 'Distribution of SF_12_PCS', subtitle = 'Count')
-
-ggplot(merged, aes(x = SF_12_PCS, y = after_stat(density), group = time, colour = time, fill = time)) +
-  geom_freqpoly() +
-  labs(title = 'Distribution of SF_12_PCS', subtitle = 'Density')
+rm(raw.sf12, base.sf12, sf12.spag)
 ```
@@
 
-## Tobacco
-
-### ncigs mean
-
-TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11
-
-```{r}
-#  nutriton quality line/boxplots.
-handover_boxplots(raw.dat, base.dat, 'ncigs')
-handover_lineplots(raw.dat, base.dat, 'ncigs')
-
-test.pidps <- raw.dat %>%
-  select(pidp)
-
-test.base <- base.dat %>%
-  filter(pidp %in% test.pidps$pidp)
-
-handover_boxplots(raw.dat, test.base, 'ncigs')
-handover_lineplots(raw.dat, test.base, 'ncigs')
-```
-
-### Spaghetti
-
-```{r}
-# raw.nut <- raw.dat %>%
-#   select(pidp, age, time, ncigs)
-# base.nut <- base.dat %>%
-#   select(pidp, age, time, ncigs)
-# 
-# nut.spag <- rbind(raw.nut, base.nut)
-# 
-# spaghetti_plot(nut.spag, 'ncigs',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# 
-# density_ridges(nut.spag, "ncigs",
-#                save = FALSE,
-#                save.path = save.path)
-# 
-# rm(raw.nut, base.nut, nut.spag)
-```
-
-### ncigs Max
-
-```{r}
-raw.ncigs_max <- raw.dat %>%
-  select(pidp, time, ncigs) %>%
-  group_by(time) %>%
-  summarise(max_ncigs = max(ncigs)) %>%
-  mutate(source = 'final_US')
-
-base.ncigs_max <- base.dat %>%
-  dplyr::select(pidp, time, ncigs) %>%
-  group_by(time) %>%
-  summarise(max_ncigs = max(ncigs)) %>%
-  mutate(source = 'baseline_output')
-
-max_ncigs <- rbind(raw.ncigs_max, base.ncigs_max)
-
-# Now plot
-ggplot(data = max_ncigs, mapping = aes(x = time, y = max_ncigs, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Max ncigs', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Average')
-```
-
 ## Physical Health
@@
 ```{r}
-# raw.s <- raw.parity %>%
-#   select(pidp, age, time, nkids_ind)
-# base.s <- base.parity %>%
-#   select(pidp, age, time, nkids_ind)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'nkids_ind',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
+raw.s <- raw.parity %>%
+  select(pidp, age, time, nkids_ind)
+base.s <- base.parity %>%
+  select(pidp, age, time, nkids_ind)
 
-## Alcohol (AUDITC)
+spag <- rbind(raw.s, base.s)
 
-```{r}
-handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
+spaghetti_plot(spag, 'nkids_ind',
+               save = shall.we.save,
+               save.path = save.path)
 
-raw.2020.alc <- raw.dat %>% 
-  filter(time == 2020) %>%
-  group_by(auditc) %>%
-  summarise(n = n()) %>%
-  mutate(prop = n / sum(n))
-
-```
-
-## Physical Activity
-
-```{r}
-handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
-
-raw.2020.phys <- raw.dat %>% 
-  filter(time == 2020) %>%
-  group_by(active) %>%
-  summarise(n = n()) %>%
-  mutate(prop = n / sum(n))
-```
-
-## Material Deprivation
-
-```{r}
-#handover_boxplots(raw.dat, base.dat, 'matdep')
-#handover_lineplots(raw.dat, base.dat, 'matdep')
-handover_ordinal(raw.dat, base.dat, var = 'matdep', save = shall.we.save)
-
-raw.dat$chron_disease <- as.factor(raw.dat$chron_disease)
-raw.2020.cd <- raw.dat %>%
-  select(time, chron_disease, age) %>%
-  filter(time == 2020) %>%
-  mutate(age_group = cut(age, 
-                         breaks = c(0,20,30,40,50,60,70,80,90,100,120),
-                         labels = c('16-19', '20-30', '30-40', '40-50', '50-60', '60-70', '70-80', '80-90', '90-100', '100+'))) %>%
-  group_by(age_group, chron_disease) %>%
-  summarise(n = n()) %>%
-  group_by(age_group) %>%
-  mutate(prop = n / sum(n),
-         perc = prop * 100)
-  # mutate(prop = n() / sum(n),
-  #        perc = prop * 100)
-
-raw.2020.cd
-
-ggplot(raw.2020.cd, aes(x = age_group, y = perc, group = chron_disease, colour = chron_disease, fill = chron_disease)) +
-  geom_col(position = 'dodge') +
-  xlab('Age Group') +
-  ylab('Proportion')
-```
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, matdep) %>%
-#   filter(!matdep %in% miss.values)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, matdep) %>%
-#   filter(!matdep %in% miss.values)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'matdep',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
-
-## Chronic Disease
-
-```{r}
-handover_ordinal(raw.dat, base.dat, var = 'chron_disease', save = shall.we.save)
-```
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, chron_disease) %>%
-#   filter(!chron_disease %in% miss.values)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, chron_disease) %>%
-#   filter(!chron_disease %in% miss.values)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spag$chron_disease <- as.numeric(spag$chron_disease)
-# 
-# spaghetti_plot(spag, 'chron_disease',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# density_ridges(spag, 'chron_disease',
-#                save=shall.we.save, 
-#                save.path=save.path)
-# 
-# pidp_sample <- sample(unique(spag$pidp), size=nrow(raw.s)/10, replace=FALSE)
-# spag.sample <- spag[which(spag$pidp %in% pidp_sample), ]
-# spaghetti_plot(spag.sample, 'chron_disease',
-#                save = shall.we.save,
-#                save.path = save.path)
-# spaghetti_highlight_max_plot(spag.sample, 'chron_disease',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, hourly_wage)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, hourly_wage)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'hourly_wage',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# # now a version limited to 0-100
-# spag <- spag %>%
-#   filter(hourly_wage <= 300)
-# spaghetti_plot(spag, 'hourly_wage',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+raw.s <- raw.dat %>%
+  select(pidp, age, time, hourly_wage)
+base.s <- base.dat %>%
+  select(pidp, age, time, hourly_wage)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+# now a version limited to 0-100
+spag <- spag %>%
+  filter(hourly_wage <= 300)
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-# # some basic statistics about hourly_wage variable
-# print("Some basic statistics on hourly_wage. These are all for 2020.")
-# raw.2020 <- raw.dat %>% filter(time == 2020)
-# print('All living people in 2020')
-# print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
-# # number individuals with an hourly_wage > 0
-# print('People not in work')
-# print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-# print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
-# 
-# # Number in work
-# print('People in work')
-# print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-# print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
-# 
-# # Extreme hourly_wage values
-# print('Extreme hourly wage values: HIGH')
-# print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
-# print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
-# print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
-# print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
-# print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
-# print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
-# 
-# raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
-# print('Extreme hourly wage values: LOW (non-zero)')
-# print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
-# print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
-# print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
-# print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
+# some basic statistics about hourly_wage variable
+print("Some basic statistics on hourly_wage. These are all for 2020.")
+raw.2020 <- raw.dat %>% filter(time == 2020)
+print('All living people in 2020')
+print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
+# number individuals with an hourly_wage > 0
+print('People not in work')
+print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
+
+# Number in work
+print('People in work')
+print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
+
+# Extreme hourly_wage values
+print('Extreme hourly wage values: HIGH')
+print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
+print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
+print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
+print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
+print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
+print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
+
+raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
+print('Extreme hourly wage values: LOW (non-zero)')
+print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
+print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
+print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
+print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
 ```

### 2024-05-15 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Started notebook for diagnostic plots of CPR interventions

---
title: "Diagnosing Child Poverty Reduction Interventions"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

# SETUP

This document presents results from a host of interventions on child poverty, including visualisations of the change in SF_12_MCS compared with baseline.

```{r "setup", include=FALSE}

library(tidyverse)
library(ggplot2)
library(ggridges) # for densities over time plots. 
library(knitr)
library(here)
library(gghighlight)

workingDir <- "/home/luke/Documents/MINOS/Minos/"
#workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

```{r "imports", include=FALSE}
source(here::here('minos', 'utils_datain.R'))
#source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 
                                    'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)
rel.dat <- read_singular_local_out(out.path, 
                                   'ChildPovertyReductionRELATIVE', 
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
# rel.int.2 <- read_singular_local_out(out.path, 
#                                      'ChildPovertyReductionRELATIVE_2', 
#                                      drop.dead = TRUE,
#                                      drop.zero.weight = TRUE)
abs.int <- read_singular_local_out(out.path, 
                                   'ChildPovertyReductionABSOLUTE', 
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
```

# Household Income

i.e. is the intervention working?

## All Pop

```{r}
base.inc <- base.dat %>%
  select(pidp, hidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income,w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Baseline')

rel.inc <- rel.dat %>%
  select(pidp, hidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income,w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Relative')

inc <- rbind(base.inc, rel.inc)

ggplot(inc, aes(x = time, y = hh_income, group = scen, color = scen, fill = scen)) +
  geom_line() +
  geom_point()

ggplot(base.dat, aes(x = hh_income, y = time, group = time, color = 'blue', alpha = 0.3)) +
  geom_density_ridges() +
  geom_density_ridges(data = rel.dat, aes(x = hh_income, y = time, group = time, color = 'red')) +
  theme(legend.position = 'none') +
  labs(title = 'Relative Poverty Reduction Intervention - Red')
```

## Households With Children

```{r}
base.inc <- base.dat %>%
  select(pidp, hidp, time, hh_income, age, nkids, weight) %>%
  mutate(nkids_any = (nkids > 0)) %>%
  filter(nkids_any == TRUE) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Baseline')

rel.inc <- rel.dat %>%
  select(pidp, hidp, time, hh_income, age, nkids, weight) %>%
  mutate(nkids_any = (nkids > 0)) %>%
  filter(nkids_any = TRUE) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Relative')

inc <- rbind(base.inc, rel.inc)

ggplot(inc, aes(x = time, y = hh_income, group = scen, color = scen, fill = scen)) +
  geom_line() +
  geom_point()
```

## Boosted Pop

```{r}
boosted.pidps <- rel.int %>%
  filter(income_boosted == 'TRUE') %>%
  select(pidp)

base.inc <- base.dat %>%
  select(pidp, hidp, time, hh_income, weight) %>%
  filter(pidp %in% boosted.pidps$pidp) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Baseline')

rel.inc <- rel.dat %>%
  select(pidp, hidp, time, hh_income, weight) %>%
  filter(pidp %in% boosted.pidps$pidp) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Relative')

inc <- rbind(base.inc, rel.inc)

ggplot(inc, aes(x = time, y = hh_income, group = scen, color = scen, fill = scen)) +
  geom_line() +
  geom_point()
```

```{r}

```

### 2024-05-16 minos/outcomes/child_poverty_reduction_vis.Rmd
Tracking the ChildPovReduction plotting notebooks

@@
 
-require(tidyverse)
-require(ggplot2)
-require(ggridges) # for densities over time plots. 
-require(knitr)
-require(here)
-require(gghighlight)
+library(tidyverse)
+library(ggplot2)
+library(ggridges) # for densities over time plots. 
+library(knitr)
+library(here)
+library(gghighlight)
 
@@
 source(here::here('minos', 'utils_datain.R'))
-#source(here::here('minos', 'utils_validation_vis.R'))
+source(here::here('minos', 'utils_validation_vis.R'))
 source(here::here('minos', 'validation', 'utils.r'))
@@
 out.path <- here::here('output', 'default_config/')
-base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
-int.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionRANDOM', drop.dead = TRUE)
-int2.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionSUSTAIN', drop.dead = TRUE)
+base.dat <- read_singular_local_out(out.path, 'baseline', 
+                                    drop.dead = TRUE,
+                                    drop.zero.weight = TRUE)
+int.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE', 
+                                   drop.dead = TRUE,
+                                   drop.zero.weight = TRUE)
+int2.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE', 
+                                   drop.dead = TRUE,
+                                   drop.zero.weight = TRUE)
+
 #base.dat <- read_agg_subset_batch_out(out.path, 'baseline', drop.dead = TRUE)
@@
 
-We can calculate the relative poverty threshold for our starting year of 2020:
+We can calculate the relative poverty threshold for our starting year of 2021:
 
 ```{r}
-base.2020 <- base.dat %>%
-  filter(time == 2020)
+base.2021 <- base.dat %>%
+  filter(time == 2021)
 
-mean.hh_income <- weighted.mean(base.2020$hh_income, w = base.2020$weight)
+mean.hh_income <- weighted.mean(base.2021$hh_income, w = base.2021$weight)
 rel.pov.threshold <- mean.hh_income * 0.6
@@
 print(paste0("Relative poverty threshold in 2020: ", rel.pov.threshold))
-rm(base.2020, mean.hh_income, rel.pov.threshold)
+rm(base.2021, mean.hh_income, rel.pov.threshold)
 ```
@@
 
-## Random Uplift
+## Intervention
 
@@
 ```{r}
+
+hh_boosted <- int.dat %>%
+    select(hidp, time, income_boosted, boost_amount, nkids) %>%
+    filter(income_boosted == 'True') %>%
+    group_by(time) %>%
+    summarise(n_boosted = length(unique(hidp)),
+              total_boost = sum(boost_amount),
+              kids_boosted = sum(nkids))
 
@@
 
-#### Full Sample
+#### Full Population
 
@@
 
-### True Treatment on Treated
-
-Instead of looking at the difference in means
-
-## Sustained Uplift
-
-This intervention is similar to the random uplift intervention with one difference.
-In the first year that the intervention is applied, households are randomly chosen for uplift until the correct number of children for that year are uplifted.
-The difference comes in subsequent years.
-From year 2 onwards, households that have been previously intervened on will once again be uplifted to above the poverty line (if they are once again below).
-This is the meaning of the sustained intervention, where families are chosen at random and then maintained above the poverty line, instead of picking a random subset of households under the poverty line as in the random intervention.
+## Absolute Poverty
 
@@
 
+# Diagnostics
+
+## Spaghetti
+
+```{r}
+base.spag <- base.dat %>%
+  select(pidp, age, time, hh_income) %>%
+  mutate(scen = 'baseline')
+int.spag <- int.dat %>%
+  select(pidp, age, time, hh_income) %>%
+  mutate(scen = 'relative')
+int2.spag <- int2.dat %>%
+  select(pidp, age, time, hh_income) %>%
+  mutate(scen = 'absolute')
+
+# spaghetti_plot(base.spag, 'hh_income',
+#                save = FALSE,
+#                save.path = '')
+# 
+# spaghetti_plot(int.spag, 'hh_income',
+#                save = FALSE,
+#                save.path = '')
+# 
+# spaghetti_plot(int2.spag, 'hh_income',
+#                save = FALSE,
+#                save.path = '')
+
+density_ridges(base.spag, 'hh_income',
+               save=FALSE, 
+               save.path='')
+
+density_ridges(int.spag, 'hh_income',
+               save=FALSE, 
+               save.path='')
+
+density_ridges(int2.spag, 'hh_income',
+               save=FALSE, 
+               save.path='')
+```
+
+```{r}
+
+dens.1 <- rbind(base.spag, int.spag)
+dens.2 <- rbind(base.spag, int2.spag)
+
+ggplot(base.dat, aes(x = hh_income, y = time, group = time, color = 'blue', alpha = 0.3)) +
+  geom_density_ridges() +
+  geom_density_ridges(data = int.dat, aes(x = hh_income, y = time, group = time, color = 'red')) +
+  theme(legend.position = 'none') +
+  labs(title = 'Relative Poverty Intervention')
+
+ggplot(base.dat, aes(x = hh_income, y = time, group = time, color = 'blue', alpha = 0.3)) +
+  geom_density_ridges() +
+  geom_density_ridges(data = int2.dat, aes(x = hh_income, y = time, group = time, color = 'red')) +
+  theme(legend.position = 'none') +
+  labs(title = 'Absolute Poverty Intervention')
+
+```
+
 ```{r}

### 2024-05-16 minos/validation/handovers.Rmd
Small tweak to child_ages plot to get the factor level labels right

@@
 
+combined$expanded_child_ages <- factor(combined$expanded_child_ages,
+                                       levels = c('0', '1', '2', '3', '4', '5', 
+                                                  '6', '7', '8', '9', '10', 
+                                                  '11', '12', '13', '14', '15', 
+                                                  '16', 'childless'))
+
 ggplot(data = combined, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
@@
 
-ggplot(data = combined, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
+ggplot(data = combined, mapping = aes(x = expanded_child_ages, y = age_counts, group = factor(time), colour = factor(time))) +
   geom_line() +
@@
   scale_colour_viridis_d() +
-  xlab('Year') +
+  xlab('Age') +
   ylab('Count')

### 2024-05-17 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Improved child poverty interventions and plotting notebooks

@@
                                     drop.zero.weight = TRUE)
-rel.dat <- read_singular_local_out(out.path, 
+rel.int <- read_singular_local_out(out.path, 
                                    'ChildPovertyReductionRELATIVE', 
@@
                                    drop.zero.weight = TRUE)
-# rel.int.2 <- read_singular_local_out(out.path, 
-#                                      'ChildPovertyReductionRELATIVE_2', 
-#                                      drop.dead = TRUE,
-#                                      drop.zero.weight = TRUE)
+rel.int.2 <- read_singular_local_out(out.path,
+                                     'ChildPovertyReductionRELATIVE_2',
+                                     drop.dead = TRUE,
+                                     drop.zero.weight = TRUE)
 abs.int <- read_singular_local_out(out.path, 
@@
 
-rel.inc <- rel.dat %>%
+rel.inc <- rel.int %>%
   select(pidp, hidp, time, hh_income, weight) %>%
@@
   geom_density_ridges() +
-  geom_density_ridges(data = rel.dat, aes(x = hh_income, y = time, group = time, color = 'red')) +
+  geom_density_ridges(data = rel.int, aes(x = hh_income, y = time, group = time, color = 'red')) +
   theme(legend.position = 'none') +
@@
 
-rel.inc <- rel.dat %>%
+rel.inc <- rel.int %>%
   select(pidp, hidp, time, hh_income, age, nkids, weight) %>%
@@
 boosted.pidps <- rel.int %>%
-  filter(income_boosted == 'TRUE') %>%
+  filter(income_boosted == 'True') %>%
   select(pidp)
@@
 base.inc <- base.dat %>%
-  select(pidp, hidp, time, hh_income, weight) %>%
+  select(pidp, hidp, time, hh_income, SF_12, weight) %>%
   filter(pidp %in% boosted.pidps$pidp) %>%
   group_by(time) %>%
-  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE)) %>%
+  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE),
+            SF_12 = weighted.mean(x = SF_12, w = weight, na.rm = TRUE)) %>%
   mutate(scen = 'Baseline')
 
-rel.inc <- rel.dat %>%
-  select(pidp, hidp, time, hh_income, weight) %>%
+rel.inc <- rel.int %>%
+  select(pidp, hidp, time, hh_income, SF_12, weight) %>%
   filter(pidp %in% boosted.pidps$pidp) %>%
   group_by(time) %>%
-  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE)) %>%
+  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE),
+            SF_12 = weighted.mean(x = SF_12, w = weight, na.rm = TRUE)) %>%
   mutate(scen = 'Relative')
@@
   geom_point()
+
+ggplot(inc, aes(x = time, y = SF_12, group = scen, color = scen, fill = scen)) +
+  geom_line() +
+  geom_point()
+```
+
+# TESTING THE BOOSTED POP
+
+```{r}
+boosted.pidps <- rel.int %>%
+  filter(income_boosted == 'True') %>%
+  select(pidp)
+
+# Define the recoding mapping for housing_quality
+recoding_mapping <- c("Low" = 1, "Medium" = 2, "High" = 3)  # Adjust as needed
+
+base.inc <- base.dat %>%
+  select(pidp, hidp, time, age, hh_income, SF_12, housing_quality, neighbourhood_safety, ncigs, nutrition_quality, loneliness, nkids, weight) %>%
+  filter(pidp %in% boosted.pidps$pidp) %>%
+  mutate_at(vars(housing_quality), ~recode(., !!!recoding_mapping)) %>%
+  group_by(time) %>%
+  summarise(boosted_pop = n(),
+            age = mean(age, na.rm = TRUE),
+            hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE),
+            SF_12 = weighted.mean(x = SF_12, w = weight, na.rm = TRUE),
+            housing_quality = weighted.mean(x = housing_quality, w = weight, na.rm = TRUE),
+            neighbourhood_safety = weighted.mean(x = neighbourhood_safety, w = weight, na.rm = TRUE),
+            ncigs = weighted.mean(x = ncigs, w = weight, na.rm = TRUE),
+            nutrition_quality = weighted.mean(x = nutrition_quality, w = weight, na.rm = TRUE),
+            loneliness = weighted.mean(x = loneliness, w = weight, na.rm = TRUE)) %>%
+  mutate(scen = 'Baseline')
+
+rel.inc <- rel.int %>%
+  select(pidp, hidp, time, age, hh_income, SF_12, housing_quality, neighbourhood_safety, ncigs, nutrition_quality, loneliness, nkids, weight) %>%
+  filter(pidp %in% boosted.pidps$pidp) %>%
+  mutate_at(vars(housing_quality), ~recode(., !!!recoding_mapping)) %>%
+  group_by(time) %>%
+  summarise(boosted_pop = n(),
+            age = mean(age, na.rm = TRUE),
+            hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE),
+            SF_12 = weighted.mean(x = SF_12, w = weight, na.rm = TRUE),
+            housing_quality = weighted.mean(x = housing_quality, w = weight, na.rm = TRUE),
+            neighbourhood_safety = weighted.mean(x = neighbourhood_safety, w = weight, na.rm = TRUE),
+            ncigs = weighted.mean(x = ncigs, w = weight, na.rm = TRUE),
+            nutrition_quality = weighted.mean(x = nutrition_quality, w = weight, na.rm = TRUE),
+            loneliness = weighted.mean(x = loneliness, w = weight, na.rm = TRUE)) %>%
+  mutate(scen = 'Relative')
+
+base.treated <- base.dat %>%
+  select(pidp, time, hh_income) %>%
+  filter(pidp %in% boosted.pidps$pidp)
+
+rel.treated <- rel.int %>%
+  select(pidp, time, hh_income) %>%
+  filter(pidp %in% boosted.pidps$pidp)
+
+inc <- rbind(base.inc, rel.inc)
+```
+
+```{r}
+ggplot(inc, aes(x = time, y = boosted_pop, group = scen, color = scen, fill = scen)) +
+  geom_line() +
+  geom_point()
+
+ggplot(inc, aes(x = time, y = age, group = scen, color = scen, fill = scen)) +
+  geom_line() +
+  geom_point()
+
+ggplot(inc, aes(x = time, y = hh_income, group = scen, color = scen, fill = scen)) +
+  geom_line() +
+  geom_point()
+
+ggplot(base.treated, aes(x = hh_income, y = time, group = time, color = 'blue', alpha = 0.3)) +
+  geom_density_ridges() +
+  geom_density_ridges(data = rel.treated, aes(x = hh_income, y = time, group = time, color = 'red')) +
+  theme(legend.position = 'none') +
+  labs(title = 'Relative Poverty Reduction Intervention - Red')
+
+ggplot(inc, aes(x = time, y = SF_12, group = scen, color = scen, fill = scen)) +
+  geom_line() +
+  geom_point()
+
+ggplot(inc, aes(x = time, y = housing_quality, group = scen, color = scen, fill = scen)) +
+  geom_line() +
+  geom_point()
+
+ggplot(inc, aes(x = time, y = neighbourhood_safety, group = scen, color = scen, fill = scen)) +
+  geom_line() +
+  geom_point()
+
+ggplot(inc, aes(x = time, y = ncigs, group = scen, color = scen, fill = scen)) +
+  geom_line() +
+  geom_point()
+
+ggplot(inc, aes(x = time, y = nutrition_quality, group = scen, color = scen, fill = scen)) +
+  geom_line() +
+  geom_point()
+
+ggplot(inc, aes(x = time, y = loneliness, group = scen, color = scen, fill = scen)) +
+  geom_line() +
+  geom_point()
+
 ```

### 2024-05-17 minos/outcomes/child_poverty_reduction_vis.Rmd
Improved child poverty interventions and plotting notebooks

@@
                                     drop.zero.weight = TRUE)
-int.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE', 
+# int.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE', 
+#                                    drop.dead = TRUE,
+#                                    drop.zero.weight = TRUE)
+int.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
                                    drop.dead = TRUE,
@@
 
-hh_boosted <- int.dat %>%
-    select(hidp, time, income_boosted, boost_amount, nkids) %>%
-    filter(income_boosted == 'True') %>%
-    group_by(time) %>%
-    summarise(n_boosted = length(unique(hidp)),
-              total_boost = sum(boost_amount),
-              kids_boosted = sum(nkids))
+# hh_boosted <- int2.dat %>%
+#     select(hidp, time, income_boosted, boost_amount, nkids) %>%
+#     filter(income_boosted == 'True') %>%
+#     group_by(time) %>%
+#     summarise(n_boosted = length(unique(hidp)),
+#               total_boost = sum(boost_amount),
+#               kids_boosted = sum(nkids))
 
@@
 
-## Absolute Poverty
+# Absolute Poverty
 
-### Boosted Sample
+## Boosted Sample
 
@@
 
-### SF_12_MCS
+## SF_12_MCS
 
-#### Full Population
+### Full Population
 
@@
 
-#### Families with children
+### Families with children
 
 ```{r}
-all.families.change.SF12(base.dat, int.dat)
+all.families.change.SF12(base.dat, int2.dat)
 ```
 
-#### Families w/ children under poverty line
+### Families w/ children under poverty line
 
 ```{r}
-poverty.families.change.SF12(base.dat, int.dat, threshold)
+poverty.families.change.SF12(base.dat, int2.dat, threshold)
 ```
 
-#### Treatment on the Treated
+### Treatment on the Treated
 
 ```{r}
-treatment.on.treated.change.SF12(base.dat, int.dat)
+treatment.on.treated.change.SF12(base.dat, int2.dat)
 ```

### 2024-05-22 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Improved the nutrition model scaling of predicted values, and some more changes to the model_definitions default file. Also added some more print statements for reporting on relative child pov intervention and added to the visualisation scripts

@@
                                    drop.zero.weight = TRUE)
-rel.int.2 <- read_singular_local_out(out.path,
-                                     'ChildPovertyReductionRELATIVE_2',
-                                     drop.dead = TRUE,
-                                     drop.zero.weight = TRUE)
-abs.int <- read_singular_local_out(out.path, 
-                                   'ChildPovertyReductionABSOLUTE', 
-                                   drop.dead = TRUE,
-                                   drop.zero.weight = TRUE)
+# rel.int.2 <- read_singular_local_out(out.path,
+#                                      'ChildPovertyReductionRELATIVE_2',
+#                                      drop.dead = TRUE,
+#                                      drop.zero.weight = TRUE)
+# abs.int <- read_singular_local_out(out.path, 
+#                                    'ChildPovertyReductionABSOLUTE', 
+#                                    drop.dead = TRUE,
+#                                    drop.zero.weight = TRUE)
 ```
@@
   filter(income_boosted == 'True') %>%
-  select(pidp)
+  select(pidp, time)
 
@@
   select(pidp, hidp, time, age, hh_income, SF_12, housing_quality, neighbourhood_safety, ncigs, nutrition_quality, loneliness, nkids, weight) %>%
-  filter(pidp %in% boosted.pidps$pidp) %>%
+  inner_join(boosted.pidps, by = c("pidp", "time")) %>%
   mutate_at(vars(housing_quality), ~recode(., !!!recoding_mapping)) %>%
@@
 base.treated <- base.dat %>%
-  select(pidp, time, hh_income) %>%
-  filter(pidp %in% boosted.pidps$pidp)
+  select(pidp, time, hh_income, SF_12, nutrition_quality, ncigs) %>%
+  inner_join(boosted.pidps, by = c("pidp", "time")) %>%
+  mutate(scen = 'Baseline')
 
 rel.treated <- rel.int %>%
-  select(pidp, time, hh_income) %>%
-  filter(pidp %in% boosted.pidps$pidp)
+  select(pidp, time, hh_income, SF_12, nutrition_quality, ncigs) %>%
+  inner_join(boosted.pidps, by = c("pidp", "time")) %>%
+  mutate(scen = 'Intervention')
 
 inc <- rbind(base.inc, rel.inc)
+treated <- rbind(base.treated, rel.treated)
 ```
@@
 
-ggplot(base.treated, aes(x = hh_income, y = time, group = time, color = 'blue', alpha = 0.3)) +
+ggplot(base.treated, aes(x = hh_income, y = time, group = time, alpha = 0.3), color = 'blue') +
   geom_density_ridges() +
-  geom_density_ridges(data = rel.treated, aes(x = hh_income, y = time, group = time, color = 'red')) +
+  geom_density_ridges(data = rel.treated, aes(x = hh_income, y = time, group = time), color = 'red') +
   theme(legend.position = 'none') +
@@
 ```{r}
+ggplot(treated, aes(x = time, y = hh_income, group = interaction(time, scen), fill = scen)) +
+  geom_boxplot()
+
+ggplot(treated, aes(x = time, y = SF_12, group = interaction(time, scen), fill = scen)) +
+  geom_boxplot()
+
+ggplot(treated, aes(x = time, y = nutrition_quality, group = interaction(time, scen), fill = scen)) +
+  geom_boxplot()
+
+ggplot(treated, aes(x = time, y = ncigs, group = interaction(time, scen), fill = scen)) +
+  geom_boxplot()
+```
+
+```{r}
+base.housing <- base.dat %>%
+  dplyr::select(pidp, time, housing_quality) %>%
+  group_by(time, housing_quality) %>%
+  count() %>%
+  mutate(scen = 'Baseline')
+
+rel.housing <- rel.int %>%
+  dplyr::select(pidp, time, housing_quality) %>%
+  group_by(time, housing_quality) %>%
+  count() %>%
+  mutate(scen = 'Intervention')
+
+housing <- rbind(base.housing, rel.housing)
+housing$housing_quality <- as.factor(housing$housing_quality)
+
+housing.norm <- housing %>%
+  group_by(time, scen) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+# Plot the data
+ggplot(data = housing.norm, mapping = aes(x = factor(time), y = prct, fill = housing_quality)) +
+  geom_bar(stat = 'identity', position = 'stack') +
+  facet_wrap(~ scen, nrow = 2) +
+  labs(title = 'Housing Quality Over Time', x = 'Year', y = 'Proportion') +
+  scale_y_continuous(labels = scales::percent) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+ggplot(data = housing.norm, mapping = aes(x = factor(time), y = prct, fill = housing_quality)) +
+  geom_bar(stat = 'identity', position = position_dodge(width = 0.9)) +
+  facet_wrap(~ scen, nrow = 2) +
+  labs(title = 'Housing Quality Over Time', x = 'Year', y = 'Proportion') +
+  scale_y_continuous(labels = scales::percent) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
 ```
+
+```{r}
+# Plot the data
+ggplot(data = housing.norm, mapping = aes(x = factor(time), y = prct, fill = housing_quality)) +
+  geom_bar(stat = 'identity', position = position_dodge(width = 0.8), aes(group = scen)) +
+  labs(title = 'Housing Quality Over Time', x = 'Year', y = 'Proportion') +
+  scale_y_continuous(labels = scales::percent) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  facet_wrap(~ scen, scales = "free_y", ncol = 2)
+
+ggplot(data = housing.norm, mapping = aes(x = interaction(time, scen), y = prct, fill = housing_quality)) +
+  geom_bar(stat = 'identity', position = 'stack') +
+  labs(title = 'Housing Quality Over Time', x = 'Year and Scenario', y = 'Proportion') +
+  scale_y_continuous(labels = scales::percent) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+```
+
+```{r}
+# Create a combined variable for interspersed plotting
+housing.norm2 <- housing.norm %>%
+  mutate(year_scen = interaction(time, scen, sep = " - "))
+
+# Plot the data
+ggplot(data = housing.norm2, mapping = aes(x = year_scen, y = prct, fill = housing_quality)) +
+  geom_bar(stat = 'identity', position = 'stack') +
+  labs(title = 'Housing Quality Over Time', x = 'Year and Scenario', y = 'Proportion') +
+  scale_y_continuous(labels = scales::percent) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+```{r}
+# Prepare data for line plot
+housing.norm3 <- housing %>%
+  group_by(time, scen, housing_quality) %>%
+  summarize(prct = sum(n) / sum(housing$n)) %>%
+  ungroup()
+
+# Line plot with faceting by scenario
+ggplot(data = housing.norm3, mapping = aes(x = time, y = prct, color = housing_quality, group = housing_quality)) +
+  geom_line(size = 1.2) +
+  geom_point(size = 3) +
+  facet_wrap(~ scen) +
+  labs(title = 'Housing Quality Over Time by Scenario', x = 'Year', y = 'Proportion') +
+  scale_y_continuous(labels = scales::percent) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+```
+
+```{r}
+# Generate proportions
+housing.norm5 <- housing %>%
+  group_by(time, scen) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total)) %>%
+  ungroup()
+
+# Create a combined variable for interspersed plotting
+housing.norm5 <- housing.norm5 %>%
+  mutate(year_scen = interaction(time, scen, sep = " - "))
+
+# Plot the data with different color schemes
+ggplot(data = housing.norm5, mapping = aes(x = factor(time), y = prct, fill = housing_quality, group = scen)) +
+  geom_bar(stat = 'identity', position = position_dodge(width = 0.9)) +
+  facet_wrap(~ scen, ncol = 1) +
+  labs(title = 'Housing Quality Over Time', x = 'Year', y = 'Proportion') +
+  scale_y_continuous(labels = scales::percent) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+```{r}
+
+```

### 2024-05-22 minos/outcomes/child_poverty_reduction_vis.Rmd
Improved the nutrition model scaling of predicted values, and some more changes to the model_definitions default file. Also added some more print statements for reporting on relative child pov intervention and added to the visualisation scripts

@@
                                     drop.zero.weight = TRUE)
-# int.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE', 
+int.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE',
+                                   drop.dead = TRUE,
+                                   drop.zero.weight = TRUE)
+# int.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
 #                                    drop.dead = TRUE,
 #                                    drop.zero.weight = TRUE)
-int.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
-                                   drop.dead = TRUE,
-                                   drop.zero.weight = TRUE)
 int2.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE', 

### 2024-05-23 minos/outcomes/ChildPovReduction_plots.Rmd

---
title: "Scottish Child Poverty Briefing Plots"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

WS5 (Dynamic Microsimulation): What are the impacts on mental health of meeting the targets?
·        Across the population? 
·        Population by income quintile (looking at absolute/relative inequalities)?
·        For families only? By income quintile (looking at absolute/relative inequalities)?
·        For families that meet criteria of 0/1/2+ of the priority family groups?
·        Differential impacts of UK package of policies only, and then UK package with SG policies?

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

```{r "data_in_functions", include=FALSE}

generate_df_list <- function(summary, scen.list) {
  df.list <- lapply(scen.list, function(scen) {
    df <- read.csv(file = sprintf('%s/combined_summary_%s.csv', scen, summary))
    df$scen <- scen
    return(df)
  })
  return(df.list)
}

```

```{r "SF12_change_simple_functions", include=FALSE}
SF12_change_simple <- function(summary_group, scen.list) {

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }

  data <- do.call(rbind, generate_df_list(summary_group, scen.list))

  plot_data <- data %>%
    select(run_id, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"), 
                 names_to = c(".value", "scen"), 
                 names_sep = "\\.") %>%
    filter(scen != 'baseline')

  plot_data_confint <- plot_data %>%
    group_by(year) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF_12),
              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  plot_data_confint2 <- plot_data %>%
    group_by(year) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF_12),
              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12')

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12')

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12')

  print(p1)
  print(p2)
  #print(p3)
}

SF12_change_percentage <- function(summary_group, scen.list) {

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }

  data <- do.call(rbind, generate_df_list(summary_group, scen.list))

  plot_data <- data %>%
    select(run_id, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ ((. - SF_12.baseline) / SF_12.baseline) * 100)) %>% # Calculate percentage change
    rename_with(~ paste0("percent_change_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("percent_change") | starts_with("mean_cost"), 
                 names_to = c(".value", "scen"), 
                 names_sep = "\\.") %>%
    filter(scen != 'baseline')

  plot_data_confint <- plot_data %>%
    group_by(year) %>%
    summarise(n = n(),
              mean_SF12_change = mean(percent_change_SF_12),
              margin = qt(0.975, df = n - 1) * (sd(percent_change_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  p1 <- ggplot(plot_data, aes(x = year, y = percent_change_SF_12)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    labs(title = tit) +
    xlab('Year') +
    ylab('Percentage Change in SF-12')

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Percentage Change in SF-12')

  print(p1)
  print(p2)
}

```

```{r "SF12_change_income_quint", include=FALSE}
SF12_change_income_quint <- function(summary_group, scen.list) {

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }

  summary_group <- paste0(summary_group, '_income_quint')

  data <- do.call(rbind, generate_df_list(summary_group, scen.list))

  plot_data <- data %>%
    select(run_id, income_quintile, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
                 names_to = c(".value", "scen"),
                 names_sep = "\\.") %>%
    filter(scen != 'baseline') %>%
    select(-scen)

  plot_data$income_quintile <- factor(plot_data$income_quintile)

  plot_data_confint <- plot_data %>%
    group_by(year, income_quintile) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF_12),
              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  plot_data_confint2 <- plot_data %>%
    group_by(year, income_quintile) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF_12),
              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    labs(title = tit, subtitle = 'Income Quintile') +
    xlab('Year') +
    ylab('Change in SF-12')

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit, subtitle = 'Income Quintile') +
    xlab('Year') +
    ylab('Change in SF-12')

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit, subtitle = 'Income Quintile') +
    xlab('Year') +
    ylab('Change in SF-12')

  print(p1)
  print(p2)
}

SF12_change_percentage_income_quint <- function(summary_group, scen.list) {

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }

  summary_group <- paste0(summary_group, '_income_quint')

  data <- do.call(rbind, generate_df_list(summary_group, scen.list))

  plot_data <- data %>%
    select(run_id, income_quintile, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ ((. - SF_12.baseline) / SF_12.baseline) * 100)) %>% # Calculate percentage change
    rename_with(~ paste0("percent_change_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("percent_change") | starts_with("mean_cost"),
                 names_to = c(".value", "scen"),
                 names_sep = "\\.") %>%
    filter(scen != 'baseline') %>%
    select(-scen)

  plot_data$income_quintile <- factor(plot_data$income_quintile)

  plot_data_confint <- plot_data %>%
    group_by(year, income_quintile) %>%
    summarise(n = n(),
              mean_SF12_change = mean(percent_change_SF_12),
              margin = qt(0.975, df = n - 1) * (sd(percent_change_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  p1 <- ggplot(plot_data, aes(x = year, y = percent_change_SF_12, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    labs(title = tit, subtitle = 'Income Quintile') +
    xlab('Year') +
    ylab('Percentage Change in SF-12')

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit, subtitle = 'Income Quintile') +
    xlab('Year') +
    ylab('Percentage Change in SF-12')

  print(p1)
  print(p2)
}

```

```{r}
scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE')
whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
```

# Quick Data Test

```{r}
ggplot(whole_pop_data, aes(x = year, y = SF_12, group = scen, colour = scen, fill = scen)) +
  geom_smooth()
```

Check if SF12 results in one year (across 100 runs) are normally distributed.

```{r}
whole_pop_2030 <- whole_pop_data %>%
  filter(year == 2030)

hist(whole_pop_2030$SF_12)
qqnorm(whole_pop_2030$SF_12)
qqline(whole_pop_2030$SF_12)

shapiro.test(whole_pop_2030$SF_12)

# Results look normally distributed^
```

# Whole Population

What are the impacts on mental health of meeting the targets:

- Across the population?
- Population by income quintile?

```{r}
SF12_change_simple(summary_group = 'whole_pop',
                   scen.list = scen.list.test)

SF12_change_percentage(summary_group = 'whole_pop',
                       scen.list = scen.list.test)
```

```{r}
SF12_change_income_quint(summary_group = 'whole_pop',
                         scen.list = scen.list.test)

SF12_change_percentage_income_quint(summary_group = 'whole_pop',
                                    scen.list = scen.list.test)
```

# Families

What are the impacts on mental health of meeting the targets:

- For families only? By income quintile

```{r}
SF12_change_simple(summary_group = 'families',
                   scen.list = scen.list.test)

SF12_change_percentage(summary_group = 'families',
                       scen.list = scen.list.test)
```

```{r}
SF12_change_income_quint(summary_group = 'families',
                         scen.list = scen.list.test)

SF12_change_percentage_income_quint(summary_group = 'families',
                                    scen.list = scen.list.test)
```

# Priority Subgroups

What are the impacts on mental health of meeting the targets:

- For families that meet the criteria of 0/1/2+ of the priority family groups?

```{r}
SF12_change_simple(summary_group = 'priority_any',
                         scen.list = scen.list.test)

SF12_change_percentage(summary_group = 'priority_any',
                                    scen.list = scen.list.test)
```

```{r}
#SF12_change_income_quint <- function(summary_group, scen.list) {

summary_group <- 'priority_num'

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }

  #summary_group <- paste0(summary_group, '_income_quint')

  data <- do.call(rbind, generate_df_list(summary_group, scen.list))

  plot_data <- data %>%
    select(run_id, income_quintile, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
                 names_to = c(".value", "scen"),
                 names_sep = "\\.") %>%
    filter(scen != 'baseline') %>%
    select(-scen)

  plot_data$income_quintile <- factor(plot_data$income_quintile)

  plot_data_confint <- plot_data %>%
    group_by(year, income_quintile) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF_12),
              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  plot_data_confint2 <- plot_data %>%
    group_by(year, income_quintile) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF_12),
              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    labs(title = tit, subtitle = 'Income Quintile') +
    xlab('Year') +
    ylab('Change in SF-12')

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit, subtitle = 'Income Quintile') +
    xlab('Year') +
    ylab('Change in SF-12')

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit, subtitle = 'Income Quintile') +
    xlab('Year') +
    ylab('Change in SF-12')

  print(p1)
  print(p2)
#}
```

# Differential Impacts of UK vs SG

What are the impacts on mental health of meeting the targets?

- Differential impacts of UK package of policies only, and then UK package with SG policies?

# BONUS - Treated Pop

```{r}

```

```{r}

```

### 2024-05-23 minos/validation/handovers.Rmd
Reorganised handovers

@@
 
-## Financial Situation
-
-```{r}
-raw.financial_situation <- raw.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.financial_situation <- base.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-financial_situation <- rbind(raw.financial_situation, base.financial_situation)
-financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
-
-# Now plot
-ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-financial_situation.norm <- financial_situation %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial situation') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'financial_situation.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
-```
-
 ## Housing Quality
@@
 
+## S7 Labour State
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
+
+lab.state <- prepped.list$var
+lab.state.norm <- prepped.list$norm
+
+# Now plot
+ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'S7 Labour State') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'S7_labour_state.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, lab.state, lab.state.norm)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat, 
+                                       df1.name = 'simulated', 
+                                       df2 = raw.dat, 
+                                       df2.name = 'raw', 
+                                       var = 'S7_labour_state')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'S7_labour_state',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
+# ADDITIONAL VARIABLES
+
 ## Education
@@
 
+## Financial Situation
+
+```{r}
+raw.financial_situation <- raw.dat %>%
+  dplyr::select(pidp, time, financial_situation) %>%
+  group_by(time, financial_situation) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.financial_situation <- base.dat %>%
+  dplyr::select(pidp, time, financial_situation) %>%
+  group_by(time, financial_situation) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+financial_situation <- rbind(raw.financial_situation, base.financial_situation)
+financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
+
+# Now plot
+ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+financial_situation.norm <- financial_situation %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial situation') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'financial_situation.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
+```
+
 ## nkids Household
@@
 rm(raw.s, base.s, spag)
-```
-
-```{r}
-# some basic statistics about hourly_wage variable
-print("Some basic statistics on hourly_wage. These are all for 2020.")
-raw.2020 <- raw.dat %>% filter(time == 2020)
-print('All living people in 2020')
-print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
-# number individuals with an hourly_wage > 0
-print('People not in work')
-print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
-
-# Number in work
-print('People in work')
-print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
-print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
-
-# Extreme hourly_wage values
-print('Extreme hourly wage values: HIGH')
-print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
-print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
-print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
-print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
-print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
-print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
-
-raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
-print('Extreme hourly wage values: LOW (non-zero)')
-print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
-print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
-print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
-print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
-```
-
-## S7 Labour State
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
-
-lab.state <- prepped.list$var
-lab.state.norm <- prepped.list$norm
-
-# Now plot
-ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'S7_labour_state.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, lab.state, lab.state.norm)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'S7_labour_state')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'S7_labour_state',
-                 save = shall.we.save,
-                 save.path = save.path)
 ```

### 2024-05-24 minos/validation/handovers.Rmd
Added financial_situation and behind_on_bills variables as predictors of pathway variables

@@
 
+## Behind On Bills
+
+```{r}
+raw.behind_on_bills <- raw.dat %>%
+  dplyr::select(pidp, time, behind_on_bills) %>%
+  group_by(time, behind_on_bills) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.behind_on_bills <- base.dat %>%
+  dplyr::select(pidp, time, behind_on_bills) %>%
+  group_by(time, financial_situation) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+behind_on_bills <- rbind(raw.behind_on_bills, base.behind_on_bills)
+behind_on_bills$behind_on_bills <- as.factor(behind_on_bills$behind_on_bills)
+
+# Now plot
+ggplot(data = behind_on_bills, mapping = aes(x = time, y = n, group = behind_on_bills, colour = behind_on_bills)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Behind On Bills', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+behind_on_bills.norm <- behind_on_bills %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = behind_on_bills.norm, mapping = aes(x = time, y = prct, fill=behind_on_bills)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Behind On Bills') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'behind_on_bills.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.behind_on_bills, base.behind_on_bills, behind_on_bills, behind_on_bills.norm)
+```
+
 ## nkids Household

### 2024-05-24 minos/modules/neighbourhood.py

@@ -55,7 +55,9 @@ class Neighbourhood(Base):
                         "nutrition_quality",
                         "ncigs",
                         'hh_income',
-                        'job_sec'
+                        'job_sec',
+                        'behind_on_bills',
+                        'financial_situation'
                         ]
         #view_columns += self.transition_model.rx2('model').names
         self.population_view = builder.population.get_view(columns=view_columns)

### 2024-05-29 minos/validation/handovers.Rmd
Fixed a problem with reweighting in stock pop, where 90+ age individuals were removed due to constraint data having top-coded age at 90. Also added to the handovers and validation utils files for age structure and population counts plots

@@
 
+# DEMOGRAPHICS
+
+## Age Structure
+
+```{r}
+# assign to age_bucket in raw data
+cut_bins <- c(-1, 15, 19, 24, 29, 44, 59, 74, 200)
+cut_labels <- c("0to15", "16to19", "20to24", "25to29", "30to44", "45to59", "60to74", "75plus")
+
+raw.dat$age_bucket <- cut(raw.dat$age, 
+                          breaks = cut_bins, 
+                          labels = cut_labels)
+
+handover_ordinal(raw.dat, base.dat, var = 'age_bucket', save = shall.we.save)
+```
+
+## Max Age
+
+```{r}
+raw.maxAge <- raw.dat %>%
+  group_by(time) %>%
+  summarise(max_age = max(age))
+
+base.maxAge <- base.dat %>%
+  group_by(time) %>%
+  summarise(max_age = max(age))
+
+handover_lineplots(raw.maxAge, base.maxAge, 'max_age')
+
+## Check counts in very old age groups
+brks = c(75, 80, 85, 90, 95, 100, 105, 110)
+lbls = c("75to80", "80to85", "85to90", "90to95", "95to100", "100to105", "105to110")
+
+raw.countOldAge <- raw.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls)) %>%
+  group_by(time, age_group) %>%
+  summarise(age_group_counts = n()) %>%
+  mutate(source = 'observed')
+
+base.countOldAge <- base.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls)) %>%
+  group_by(time, age_group) %>%
+  summarise(age_group_counts = n()) %>%
+  mutate(source = 'predicted')
+
+combined <- rbind(raw.countOldAge, base.countOldAge)
+
+ggplot(combined, aes(x = time, y = age_group_counts, group = age_group, colour = age_group)) +
+  geom_line() +
+  geom_vline(xintercept = 2021, linetype = 'dashed') +
+  labs(title = 'Counts by older age group', subtitle = '75 to 110 by 5 year groups') +
+  xlab('Year') +
+  ylab('Count')
+
+raw.countOldAge <- raw.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls))
+
+base.countOldAge <- base.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls))
+
+handover_ordinal(raw.countOldAge, base.countOldAge, var = 'age_group', save = shall.we.save)
+
+```
+
+```{r}
+# Having a go at an age pyramid, hopefully animated
+
+brks = c(75, 80, 85, 90, 95, 100, 105, 110)
+lbls = c("75to80", "80to85", "85to90", "90to95", "95to100", "100to105", "105to110")
+
+var <- 'age_group'
+
+# start with calculating percentages
+#raw.oldAgePct
+#base.oldAgePct
+
+raw.oldAgePct <- raw.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls)) %>%
+  dplyr::select(time, age_group) %>%
+  group_by(time, age_group) %>%
+  count() %>%
+  mutate(source = 'predicted')
+
+base.oldAgePct <- base.dat %>%
+  filter(age > 75) %>%
+  mutate(age_group = cut(age,
+                         breaks = brks,
+                         labels = lbls)) %>%
+  dplyr::select(time, all_of(var)) %>%
+  #filter(!.data[[var]] %in% miss.values) %>%
+  group_by(time, .data[[var]]) %>%
+  count() %>%
+  mutate(source = 'observed')
+
+raw.oldAgePct[[var]] <- as.factor(raw.oldAgePct[[var]])
+base.oldAgePct[[var]] <- as.factor(base.oldAgePct[[var]])
+
+merged <- rbind(raw.oldAgePct, base.oldAgePct)
+merged[[var]] <- as.factor(merged[[var]])
+
+var.norm <- merged %>%
+    group_by(time) %>%
+    mutate(total = sum(n)) %>%
+    mutate(prct = (n / total) * 100)
+```
+
+## Population Counts
+
+```{r}
+raw.alive <- raw.dat %>%
+  group_by(time) %>%
+  summarise(n = n())
+
+base.alive <- base.dat %>%
+  group_by(time) %>%
+  summarise(n = n())
+
+#handover_boxplots(raw.alive, base.alive, 'n')
+handover_lineplots(raw.alive, base.alive, "n")
+
+rm(raw.alive, base.alive)
+```
+
 # PATHWAYS
@@
   dplyr::select(pidp, time, behind_on_bills) %>%
-  group_by(time, financial_situation) %>%
+  group_by(time, behind_on_bills) %>%
   count() %>%

### 2024-05-29 minos/validation/handovers.Rmd
Many additions to handovers with lots of plots for hh counts and stuff to do with children

@@
 
+## Age Structure (Households with Children)
+
+```{r}
+raw.dat_fam <- raw.dat %>%
+  filter(nkids > 0)
+
+base.dat_fam <- base.dat %>%
+  filter(nkids > 0)
+
+empty.dat <- raw.dat %>%
+  filter(age > 150)
+
+handover_ordinal(raw.dat_fam, base.dat_fam, var = 'age_bucket', save = shall.we.save)
+handover_ordinal(empty.dat, base.dat_fam, var = 'age_bucket', save = shall.we.save)
+```
+
 ## Max Age
@@
 
+### Total Pop
+
 ```{r}
@@
 rm(raw.alive, base.alive)
+```
+
+### Households
+
+```{r}
+raw.hhs <- raw.dat %>%
+  select(hidp, time) %>%
+  distinct() %>%
+  group_by(time) %>%
+  summarise(n = n()) %>%
+  mutate(source = 'final_US')
+
+base.hhs <- base.dat %>%
+  select(hidp, time) %>%
+  distinct() %>%
+  group_by(time) %>%
+  summarise(n = n()) %>%
+  mutate(source = 'baseline')
+
+combined <- rbind(raw.hhs, base.hhs)
+
+ggplot(combined, aes(x = time, y = n, group = source, color = source, fill = source)) +
+  geom_point() +
+  geom_line() +
+  labs(title = 'Households Count')
+```
+
+### Households With Children
+
+```{r}
+raw.households_with_kids <- raw.dat %>%
+  filter(nkids > 0) %>%
+  select(hidp, time) %>%  # Select relevant columns to reduce data size
+  distinct() %>%
+  group_by(time) %>%
+  summarise(n = n()) %>%
+  mutate(source = 'final_US')
+
+base.households_with_kids <- base.dat %>%
+  filter(nkids > 0) %>%
+  select(hidp, time) %>%  # Select relevant columns to reduce data size
+  distinct() %>%
+  group_by(time) %>%
+  summarise(n = n()) %>%
+  mutate(source = 'baseline')
+
+combined <- rbind(raw.household_count_by_year, base.household_count_by_year)
+
+ggplot(combined, aes(x = time, y = n, group = source, color = source, fill = source)) +
+  geom_point() +
+  geom_line() +
+  labs(title = 'Households with Children Count')
+```
+
+### Households With Children (Income Quintile)
+
+```{r}
+raw.hhs_kids.income_quint <- raw.dat %>%
+  filter(nkids > 0) %>%
+  select(hidp, time, hh_income) %>%  # Select relevant columns to reduce data size
+  distinct() %>%
+  mutate(income_group = case_when(
+    hh_income <= 1000 ~ "<= 1000",
+    hh_income <= 1500 ~ "1001 - 1500",
+    hh_income <= 2000 ~ "1501 - 2000",
+    hh_income <= 2500 ~ "2001 - 2500",
+    hh_income > 2500  ~ "> 2500"
+  )) %>%
+  group_by(time, income_group) %>%
+  summarise(n = n(), .groups = 'drop') %>%
+  mutate(source = 'final_US')
+
+base.hhs_kids.income_quint <- base.dat %>%
+  filter(nkids > 0) %>%
+  select(hidp, time, hh_income) %>%  # Select relevant columns to reduce data size
+  distinct() %>%
+  mutate(income_group = case_when(
+    hh_income <= 1000 ~ "<= 1000",
+    hh_income <= 1500 ~ "1001 - 1500",
+    hh_income <= 2000 ~ "1501 - 2000",
+    hh_income <= 2500 ~ "2001 - 2500",
+    hh_income > 2500  ~ "> 2500"
+  )) %>%
+  group_by(time, income_group) %>%
+  summarise(n = n(), .groups = 'drop') %>%
+  mutate(source = 'baseline')
+
+combined <- rbind(raw.hhs_kids.income_quint, base.hhs_kids.income_quint)
+combined$income_group <- factor(combined$income_group)
+
+ggplot(combined, aes(x = time, y = n, group = income_group, color = income_group, fill = income_group)) +
+  geom_point() +
+  geom_line() +
+  geom_vline(xintercept = start.year) +
+  labs(title = 'Households with Children Count')
+```
+
+#### Proportions
+
+```{r}
+calculate_hh_proportions <- function(data) {
+  # Step 1: Filter for households with children
+  households_with_kids <- data %>%
+    filter(nkids > 0) %>%
+    select(hidp, time, hh_income) %>%
+    distinct()
+
+  # Step 2: Create income group based on thresholds
+  households_with_kids <- households_with_kids %>%
+    mutate(income_group = case_when(
+      hh_income <= 1000 ~ "<= 1000",
+      hh_income <= 1500 ~ "1001 - 1500",
+      hh_income <= 2000 ~ "1501 - 2000",
+      hh_income <= 2500 ~ "2001 - 2500",
+      hh_income > 2500  ~ "> 2500"
+    ))
+
+  # Step 3: Count households within each income group per year
+  household_counts <- households_with_kids %>%
+    group_by(time, income_group) %>%
+    summarise(count = n(), .groups = 'drop')
+
+  # Step 4: Calculate total households with children per year
+  total_households_per_year <- households_with_kids %>%
+    group_by(time) %>%
+    summarise(total_count = n(), .groups = 'drop')
+
+  # Step 5: Calculate proportion of households in each group per year
+  household_proportions <- household_counts %>%
+    left_join(total_households_per_year, by = "time") %>%
+    mutate(proportion = count / total_count) %>%
+    select(time, income_group, proportion)
+
+  return(household_proportions)
+}
+
+raw.hh_kids_prop <- calculate_hh_proportions(raw.dat)
+base.hh_kids_prop <- calculate_hh_proportions(base.dat)
+
+raw.hh_kids_prop$source <- 'final_US'
+raw.hh_kids_prop <- filter(raw.hh_kids_prop, time != start.year)
+base.hh_kids_prop$source <- 'baseline'
+
+combined <- rbind(raw.hh_kids_prop, base.hh_kids_prop)
+combined$income_group <- factor(combined$income_group)
+
+ggplot(combined, aes(x = time, y = proportion, group = income_group, color = income_group, fill = income_group)) +
+  geom_col() +
+  geom_vline(xintercept = start.year) +
+  labs(title = 'Households with Children Count')
+```
+
+```{r}
+# Step 1: Filter for households with children
+households_with_kids <- raw.dat %>%
+  filter(nkids > 0) %>%
+  select(hidp, time, hh_income) %>%
+  distinct() %>%
+  select(-hidp)
+
+# Step 2: Calculate income quintiles
+households_with_kids <- households_with_kids %>%
+  group_by(time) %>%
+  mutate(income_quintile = ntile(hh_income, 5)) %>%
+  ungroup()
+
+# Step 3: Count households within each income quintile per year
+household_count_by_income_quintile <- households_with_kids %>%
+  group_by(time, income_quintile) %>%
+  summarise(n = n())
+
+household_count_by_income_quintile
 ```
@@
 ```{r}
-handover_boxplots(raw.dat, base.dat, 'nkids')
-handover_lineplots(raw.dat, base.dat, 'nkids')
+raw.hh_unique <- raw.dat %>%
+  select(hidp, time, nkids) %>%
+  distinct()
+
+base.hh_unique <- base.dat %>%
+  select(hidp, time, nkids) %>%
+  distinct()
+
+#handover_boxplots(raw.hh_unique, base.hh_unique, 'nkids')
+handover_lineplots(raw.hh_unique, base.hh_unique, 'nkids')
 ```

### 2024-05-29 minos/outcomes/child_poverty_reduction_vis.Rmd
Lots of additions and changes to child poverty visualisation scripts

--- 2024-05-16 minos/outcomes/child_poverty_reduction_vis.Rmd
@@
                                     drop.zero.weight = TRUE)
-int.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE', 
+# int1.rel <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE',
+#                                    drop.dead = TRUE,
+#                                    drop.zero.weight = TRUE)
+int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)
-int2.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE', 
+int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
                                    drop.dead = TRUE,
@@
 #int1.dat <- read_agg_subset_batch_out(out.path, 'ChildPovertyReduction', drop.dead = TRUE)
+
+int2.rel_fixed <- int2.rel_fixed #%>%
+  #filter(age < 91)
+
+int3.abs <- int3.abs #%>%
+  #filter(age < 91)
 ```
 
-# Relative Poverty Reduction
+# Functions
 
-The first intervention we will focus on is a reduction in the prevalence of children in relative poverty.
-In these interventions, we have a target level of child poverty to attain (10% of children in a household in poverty) by a specified target year, which is 2030 unless stated otherwise.
-To achieve this, we find households with a hh_income under the poverty line, and uplift a number of households each year to linearly achieve the target proportion by the target year.
-
-## Threshold
-
-Relative poverty is defined as the proportion of children living in households with income below 60% of the population median *in a given year*.
-
-We can calculate the relative poverty threshold for our starting year of 2021:
-
-```{r}
-base.2021 <- base.dat %>%
-  filter(time == 2021)
-
-mean.hh_income <- weighted.mean(base.2021$hh_income, w = base.2021$weight)
-rel.pov.threshold <- mean.hh_income * 0.6
-
-print(paste0("Relative poverty threshold in 2020: ", rel.pov.threshold))
-rm(base.2021, mean.hh_income, rel.pov.threshold)
-```
-
-We can also look at how this evolves over time in the baseline simulation:
-
-```{r}
-threshold <- base.dat %>%
-  select(time, weight, hh_income) %>%
-  group_by(time) %>%
-  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
-
-ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
-  geom_col() +
-  geom_hline(yintercept = threshold$poverty_threshold[threshold$time == 2020], linetype='dashed') +
-  labs(title = 'Relative poverty threshold over time') +
-  xlab('Year') +
-  ylab('Threshold')
-```
-
-The threshold for relative poverty decreases over time in our simulation (it's worth noting that monetary values in our simulation have been adjusted for inflation to 2020 £s).
-This suggests that our population is getting slightly less wealthy over time on average.
-
-## Intervention
-
-In this intervention, we will randomly select households to uplift in each year until we uplift the number of children required for that year.
-
-### Boosted Sample
-
-We can also look at how many people are receiving the intervention over time, and the total and mean amounts of money being added to the system.
-This should slowly increase to 2030 and then hold fairly steady.
-
-```{r}
-
-hh_boosted <- int.dat %>%
-    select(hidp, time, income_boosted, boost_amount, nkids) %>%
-    filter(income_boosted == 'True') %>%
-    group_by(time) %>%
-    summarise(n_boosted = length(unique(hidp)),
-              total_boost = sum(boost_amount),
-              kids_boosted = sum(nkids))
-
+```{r sample_info}
 sample_information <- function(int.dat, target.year) {
@@
 }
-
-sample_information(int.dat, target.year = 2030)
 ```
 
-Now lets look at SF_12_MCS comparisons.
-
-### SF_12_MCS
-
-SF_12_MCS stands for the Mental Component Score (MCS) from the 12-item Short Form (SF) Survey.
-See [this paper](https://link.springer.com/referenceworkentry/10.1007/978-94-007-0753-5_2698) for more information about SF_12.
-
-#### Full Population
-
-First lets look at the effect of the intervention on the entire sample.
-
-```{r}
+```{r sf_12_change}
 full.sample.change.SF12 <- function(base.dat, int.dat) {
@@
     geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12') +
+    labs(title = 'Relative change in SF12', subtitle = 'Full Population') +
     xlab('Year') +
@@
 
-full.sample.change.SF12(base.dat, int.dat)
-```
-
-#### Families with children
-
-Now focused only on families with children.
-
-```{r}
 all.families.change.SF12 <- function(base.dat, int.dat) {
@@
     geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12') +
+    labs(title = 'Relative change in SF12', subtitle = 'Families') +
     xlab('Year') +
@@
 }
-all.families.change.SF12(base.dat, int.dat)
-```
 
-#### Families w/ children under poverty line
-
-Now only households with children under the poverty line.
-
-```{r}
-poverty.families.change.SF12 <- function(base.dat, int.dat, threshold) {
+poverty.families.change.SF12.variable <- function(base.dat, int.dat, threshold) {
   base.thresh <- merge(base.dat, threshold, by = 'time')
@@
     geom_hline(yintercept = 0, linetype='dashed') +
-    labs(title = 'Relative change in SF12') +
+    labs(title = 'Relative change in SF12', subtitle = 'Families in Poverty') +
     xlab('Year') +
@@
 
-poverty.families.change.SF12(base.dat, int.dat, threshold)
-```
-
-This plot is perhaps a bit disingenuous, as the closer we get to 2030 the fewer households are actually under the poverty line.
-We might achieve what we want better by looking only at the boosted population.
-
-#### Treatment on the Treated
-
-```{r}
-treatment.on.treated.change.SF12 <- function(base.dat, int.dat) {
-  boosted.byyear <- int.dat %>%
-    filter(income_boosted == 'True')
+poverty.families.change.SF12 <- function(base.dat, int.dat, threshold_val) {
 
   base.all.SF12 <- base.dat %>%
-    select(time, weight, SF_12, nkids, pidp) %>%
-    filter(pidp %in% boosted.byyear$pidp) %>%
+    select(time, weight, SF_12, nkids, hh_income) %>%
+    filter(nkids > 0) %>%
+    filter(hh_income < threshold_val) %>%
     group_by(time) %>%
@@
   int.all.SF12 <- int.dat %>%
-    select(time, weight, SF_12, nkids, pidp) %>%
-    filter(pidp %in% boosted.byyear$pidp) %>%
+    select(time, weight, SF_12, nkids, hh_income) %>%
+    filter(nkids > 0) %>%
+    filter(hh_income < threshold_val) %>%
     group_by(time) %>%
@@
 
-treatment.on.treated.change.SF12(base.dat, int.dat)
+treatment.on.treated.change.SF12 <- function(base.dat, int.dat) {
+  boosted.pidps <- int.dat %>%
+    filter(income_boosted == 'True') %>%
+    select(pidp, time)
+
+  base.all.SF12 <- base.dat %>%
+    select(time, weight, SF_12, nkids, pidp) %>%
+    inner_join(boosted.pidps, by = c("pidp", "time")) %>%
+    group_by(time) %>%
+    summarise(base.SF12 = weighted.mean(SF_12, w = weight))
+
+  int.all.SF12 <- int.dat %>%
+    select(time, weight, SF_12, nkids, pidp) %>%
+    inner_join(boosted.pidps, by = c("pidp", "time")) %>%
+    group_by(time) %>%
+    summarise(int.SF12 = weighted.mean(SF_12, w = weight))
+
+  combined <- merge(x = base.all.SF12, y = int.all.SF12, by = 'time')
+  combined$diff <- combined$int.SF12 - combined$base.SF12
+
+  ggplot(combined, aes(x = time, y = diff)) +
+    geom_line() +
+    geom_hline(yintercept = 0, linetype='dashed') +
+    labs(title = 'Relative change in SF12', subtitle = 'Treatment on the Treated') +
+    xlab('Year') +
+    ylab('Difference')
+}
 ```
 
-## Absolute Poverty
+# Absolute Poverty
 
-### Boosted Sample
+## Boosted Sample
 
 ```{r}
-sample_information(int2.dat, target.year = 2030)
+sample_information(int3.abs, target.year = 2030)
 ```
 
-### SF_12_MCS
-
-#### Full Population
+## SF_12_MCS
 
 ```{r}
-full.sample.change.SF12(base.dat, int2.dat)
+full.sample.change.SF12(base.dat, int3.abs)
+
+all.families.change.SF12(base.dat, int3.abs)
+
+poverty.families.change.SF12(base.dat, int3.abs, threshold_val = 955.54)
+
+treatment.on.treated.change.SF12(base.dat, int3.abs)
 ```
 
-#### Families with children
+# Relative Poverty (FIXED THRESHOLD)
+
+## Boosted Sample
 
 ```{r}
-all.families.change.SF12(base.dat, int.dat)
+sample_information(int2.rel_fixed, target.year = 2030)
 ```
 
-#### Families w/ children under poverty line
+## SF_12_MCS
 
 ```{r}
-poverty.families.change.SF12(base.dat, int.dat, threshold)
-```
+full.sample.change.SF12(base.dat, int2.rel_fixed)
 
-#### Treatment on the Treated
+all.families.change.SF12(base.dat, int2.rel_fixed)
 
-```{r}
-treatment.on.treated.change.SF12(base.dat, int.dat)
+poverty.families.change.SF12(base.dat, int2.rel_fixed, threshold_val = 1247.71)
+
+treatment.on.treated.change.SF12(base.dat, int2.rel_fixed)
 ```
@@
   mutate(scen = 'baseline')
-int.spag <- int.dat %>%
+int.spag <- int2.rel_fixed %>%
   select(pidp, age, time, hh_income) %>%
   mutate(scen = 'relative')
-int2.spag <- int2.dat %>%
+int2.spag <- int3.abs %>%
   select(pidp, age, time, hh_income) %>%
@@
   geom_density_ridges() +
-  geom_density_ridges(data = int.dat, aes(x = hh_income, y = time, group = time, color = 'red')) +
+  geom_density_ridges(data = int2.rel_fixed, aes(x = hh_income, y = time, group = time, color = 'red')) +
   theme(legend.position = 'none') +
-  labs(title = 'Relative Poverty Intervention')
+  labs(title = 'Relative Poverty Intervention (FIXED)')
 
@@
   geom_density_ridges() +
-  geom_density_ridges(data = int2.dat, aes(x = hh_income, y = time, group = time, color = 'red')) +
+  geom_density_ridges(data = int3.abs, aes(x = hh_income, y = time, group = time, color = 'red')) +
   theme(legend.position = 'none') +
@@
 
+# Relative Poverty Variable Threshold (DEFUNKT)
+
+Relative poverty is defined as the proportion of children living in households with income below 60% of the population median *in a given year*.
+
+We can calculate the relative poverty threshold for our starting year of 2021:
+
+```{r}
+# base.2021 <- base.dat %>%
+#   filter(time == 2021)
+# 
+# mean.hh_income <- weighted.mean(base.2021$hh_income, w = base.2021$weight)
+# rel.pov.threshold <- mean.hh_income * 0.6
+# 
+# print(paste0("Relative poverty threshold in 2020: ", rel.pov.threshold))
+# rm(base.2021, mean.hh_income, rel.pov.threshold)
+```
+
+We can also look at how this evolves over time in the baseline simulation:
+
+```{r}
+# threshold <- base.dat %>%
+#   select(time, weight, hh_income) %>%
+#   group_by(time) %>%
+#   summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
+# 
+# ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
+#   geom_col() +
+#   geom_hline(yintercept = threshold$poverty_threshold[threshold$time == 2020], linetype='dashed') +
+#   labs(title = 'Relative poverty threshold over time') +
+#   xlab('Year') +
+#   ylab('Threshold')
+```
+
+The threshold for relative poverty decreases over time in our simulation (it's worth noting that monetary values in our simulation have been adjusted for inflation to 2020 £s).
+This suggests that our population is getting slightly less wealthy over time on average.
+
+# Relative Poverty Reduction
+
+The first intervention we will focus on is a reduction in the prevalence of children in relative poverty.
+In these interventions, we have a target level of child poverty to attain (10% of children in a household in poverty) by a specified target year, which is 2030 unless stated otherwise.
+To achieve this, we find households with a hh_income under the poverty line, and uplift a number of households each year to linearly achieve the target proportion by the target year.
+
+## Boosted Sample
+
+We can also look at how many people are receiving the intervention over time, and the total and mean amounts of money being added to the system.
+This should slowly increase to 2030 and then hold fairly steady.
+
+```{r}
+# sample_information(int1.rel, target.year = 2030)
+```
+
+Now lets look at SF_12_MCS comparisons.
+
+## SF_12_MCS
+
+SF_12_MCS stands for the Mental Component Score (MCS) from the 12-item Short Form (SF) Survey.
+See [this paper](https://link.springer.com/referenceworkentry/10.1007/978-94-007-0753-5_2698) for more information about SF_12.
+
+```{r}
+# full.sample.change.SF12(base.dat, int1.rel)
+# all.families.change.SF12(base.dat, int1.rel)
+# poverty.families.change.SF12.variable(base.dat, int1.rel, threshold)
+# treatment.on.treated.change.SF12(base.dat, int1.rel)
+```
+
 ```{r}

### 2024-05-29 minos/validation/handovers.Rmd
Additions to handovers and validation

@@
 
-library(tidyverse)
-library(ggplot2)
-library(ggridges) # for densities over time plots. 
-library(knitr)
-library(here)
-library(dplyr)
-library(tidyr)
-library(purrr)
-library(gghighlight)
-library(spatstat)
+require(tidyverse)
+require(ggplot2)
+require(ggridges) # for densities over time plots. 
+require(knitr)
+require(here)
+require(dplyr)
+require(tidyr)
+require(purrr)
+require(gghighlight)
 
@@
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
-raw.dat <- raw.dat %>%
-  filter(weight > 0)
 
 out.path <- here::here('output', 'default_config/')
-base.dat <- read_singular_local_out(out.path, 'baseline', 
-                                    drop.dead = TRUE, 
-                                    drop.zero.weight = TRUE)
-#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
+base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
+
+#out.path <- here::here('output', 'scotland_scaled/')
+#base.dat <- read_first_singular_local_out(out.path, '25UniversalCredit', drop.dead = TRUE)
+
+# HR 283-285 older version (285)
+# out.path <- here::here('output', 'child_poverty_config/')
+# base.dat <- read_singular_local_out(out.path, 'ChildPovertyIntervention', drop.dead = TRUE)
 ```
@@
 
-combined <- rbind(raw.household_count_by_year, base.household_count_by_year)
+combined <- rbind(raw.households_with_kids, base.households_with_kids)
 
@@
 
-```{r}
-# Step 1: Filter for households with children
-households_with_kids <- raw.dat %>%
-  filter(nkids > 0) %>%
-  select(hidp, time, hh_income) %>%
-  distinct() %>%
-  select(-hidp)
-
-# Step 2: Calculate income quintiles
-households_with_kids <- households_with_kids %>%
-  group_by(time) %>%
-  mutate(income_quintile = ntile(hh_income, 5)) %>%
-  ungroup()
-
-# Step 3: Count households within each income quintile per year
-household_count_by_income_quintile <- households_with_kids %>%
-  group_by(time, income_quintile) %>%
-  summarise(n = n())
-
-household_count_by_income_quintile
-```
-
 # PATHWAYS
@@
 
-### Poverty Thresholds
-
-#### Relative
-```{r}
-rel.threshold.raw <- raw.dat %>%
-  select(time, weight, hh_income) %>%
-  group_by(time) %>%
-  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
-
-rel.threshold.base <- base.dat %>%
-  select(time, weight, hh_income) %>%
-  group_by(time) %>%
-  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6)) %>%
-  filter(time != 2021)
-
-rel.threshold <- rbind(rel.threshold.raw, rel.threshold.base)
-
-ggplot(data = rel.threshold, aes(x = time, y = poverty_threshold)) +
-  geom_col() +
-  geom_hline(yintercept = rel.threshold$poverty_threshold[rel.threshold$time == 2020], linetype='dotted') +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
-  labs(title = 'Relative poverty threshold over time') +
-  xlab('Year') +
-  ylab('Threshold')
-#rm(rel.threshold)
-```
-
-#### Absolute
-```{r}
-raw.2010 <- raw.dat %>%
-  filter(time == 2010)
-
-abs.threshold <- weighted.median(x = raw.2010$hh_income, 
-                                 w = raw.2010$weight, 
-                                 na.rm = TRUE)
-abs.threshold <- abs.threshold * 0.6
-
-print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
-```
-
 ## SF12
@@
 
+## Financial Situation
+
+```{r}
+raw.financial_situation <- raw.dat %>%
+  dplyr::select(pidp, time, financial_situation) %>%
+  group_by(time, financial_situation) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.financial_situation <- base.dat %>%
+  dplyr::select(pidp, time, financial_situation) %>%
+  group_by(time, financial_situation) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+financial_situation <- rbind(raw.financial_situation, base.financial_situation)
+financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
+
+# Now plot
+ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+financial_situation.norm <- financial_situation %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial situation') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'financial_situation.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
+```
+
 ## Housing Quality
@@
 
-## S7 Labour State
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')
-
-lab.state <- prepped.list$var
-lab.state.norm <- prepped.list$norm
-
-# Now plot
-ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'S7 Labour State') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'S7_labour_state.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, lab.state, lab.state.norm)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat, 
-                                       df1.name = 'simulated', 
-                                       df2 = raw.dat, 
-                                       df2.name = 'raw', 
-                                       var = 'S7_labour_state')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'S7_labour_state',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-# ADDITIONAL VARIABLES
-
 ## Education
@@
 
-## Financial Situation
-
-```{r}
-raw.financial_situation <- raw.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.financial_situation <- base.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-financial_situation <- rbind(raw.financial_situation, base.financial_situation)
-financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
-
-# Now plot
-ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-financial_situation.norm <- financial_situation %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial situation') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'financial_situation.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
-```
-
-## Behind On Bills
-
-```{r}
-raw.behind_on_bills <- raw.dat %>%
-  dplyr::select(pidp, time, behind_on_bills) %>%
-  group_by(time, behind_on_bills) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.behind_on_bills <- base.dat %>%
-  dplyr::select(pidp, time, behind_on_bills) %>%
-  group_by(time, behind_on_bills) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-behind_on_bills <- rbind(raw.behind_on_bills, base.behind_on_bills)
-behind_on_bills$behind_on_bills <- as.factor(behind_on_bills$behind_on_bills)
-
-# Now plot
-ggplot(data = behind_on_bills, mapping = aes(x = time, y = n, group = behind_on_bills, colour = behind_on_bills)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Behind On Bills', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-behind_on_bills.norm <- behind_on_bills %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = behind_on_bills.norm, mapping = aes(x = time, y = prct, fill=behind_on_bills)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Behind On Bills') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'behind_on_bills.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.behind_on_bills, base.behind_on_bills, behind_on_bills, behind_on_bills.norm)
-```
-
-## nkids Household
-
-```{r}
-raw.hh_unique <- raw.dat %>%
-  select(hidp, time, nkids) %>%
-  distinct()
-
-base.hh_unique <- base.dat %>%
-  select(hidp, time, nkids) %>%
-  distinct()
-
-#handover_boxplots(raw.hh_unique, base.hh_unique, 'nkids')
-handover_lineplots(raw.hh_unique, base.hh_unique, 'nkids')
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, nkids)
-base.s <- base.dat %>%
-  select(pidp, age, time, nkids)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## nkids Max
-
-```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.nkids_max <- raw.dat %>%
-  dplyr::select(pidp, time, nkids) %>%
-  group_by(time) %>%
-  summarise(max_nkids = max(nkids)) %>%
-  mutate(source = 'final_US')
-
-base.nkids_max <- base.dat %>%
-  dplyr::select(pidp, time, nkids) %>%
-  group_by(time) %>%
-  summarise(max_nkids = max(nkids)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-max_nkids <- rbind(raw.nkids_max, base.nkids_max)
-
-# Now plot
-ggplot(data = max_nkids, mapping = aes(x = time, y = max_nkids, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Max nkids', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Average')
-```
-
 ## Parity
@@
 
-## Hourly Wage
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'hourly_wage')
-handover_lineplots(raw.dat, base.dat, 'hourly_wage')
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, hourly_wage)
-base.s <- base.dat %>%
-  select(pidp, age, time, hourly_wage)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-# now a version limited to 0-100
-spag <- spag %>%
-  filter(hourly_wage <= 300)
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
 ## Child Ages
@@
 
-b.s<- strsplit(base.child.ages$child_ages, "_")
-
-base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(b.s, length)), expanded_child_ages = unlist(b.s))
+s<- strsplit(base.child.ages$child_ages, "_")
+
+base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(s, length)), expanded_child_ages = unlist(s))
 base.child.ages.expanded <- base.child.ages.expanded %>%
   group_by(time, expanded_child_ages) %>%
-  summarise(age_counts = n()) %>%
-  mutate(source = 'baseline')
-
-combined <- rbind(raw.child.ages.expanded, base.child.ages.expanded)
-
-combined$expanded_child_ages <- factor(combined$expanded_child_ages,
-                                       levels = c('0', '1', '2', '3', '4', '5', 
-                                                  '6', '7', '8', '9', '10', 
-                                                  '11', '12', '13', '14', '15', 
-                                                  '16', 'childless'))
-
-ggplot(data = combined, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
-  geom_line() +
-  geom_vline(xintercept = start.year) +
+  summarise(age_counts = n())
+
+ggplot(data = base.child.ages.expanded, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
+  geom_line() +
   labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
@@
 
-ggplot(data = combined, mapping = aes(x = expanded_child_ages, y = age_counts, group = factor(time), colour = factor(time))) +
-  geom_line() +
-  geom_vline(xintercept = start.year) +
+ggplot(data = base.child.ages.expanded, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
+  geom_line() +
   labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
   scale_colour_viridis_d() +
-  xlab('Age') +
+  xlab('Year') +
   ylab('Count')
@@
 
-```{r}
-
-```
+## CHILD POVERTY VARS
+
+### Relative poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Relative Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'relative_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+### Absolute Poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Absolute Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'absolute_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+### Persistent Poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Persistent Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'persistent_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+
+```
+
+### Low Income and Material Deprivation
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Material Deprivation Child'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'low_income_matdep_child.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+
+```

### 2024-05-30 minos/transitions/energy_price_forecasting.Rmd
fine tuning and getting energy price forecasting working on new pc
getting wholesale energy arimas nice. adding standing charges to energy calculation

@@
 ```{r}
+#library(reticulate)
+#use_condaenv("minos_condagcc")  
 # package preamble.
@@
 library(tidyr)
-source("minos/transitions/utils.R")
+library(here)
+source(here::here("minos", "transitions", "utils.R"))
 ```
@@
 #liquid_fuel_vector <- process_input_data(energy_data, "Real terms price indices: Liquid fuels [Note 3]", "liquid_fuel")
-energy_data <- readxl::read_xlsx("../data/energy_prices_simpler_yearly.xlsx")
+
+#https://www.gov.uk/government/statistical-data-sets/monthly-domestic-energy-price-stastics
+energy_data <- readxl::read_xlsx(here::here("..", "data", "energy_prices_simpler_yearly.xlsx"))
 # primary energy material sources. fuel and motor oil omitted due to no UKHLS data. 
@@
 #m1 <- auto.arima(electric.series)
-m1 <- arima(electric.series, order=c(5, 0, 1))
+m1 <- arima(electric.series, order=c(7, 0, 1))
 print(m1)
@@
 #arima.electric 
-m3 <- arima(solid.series, order=c(5, 0 ,1))
+m3 <- arima(solid.series, order=c(5, 1 ,5))
 #Box.test(residuals(m1), type="Ljung-Box")
@@
 liquid.series <- liquid_fuel_vector$liquid_fuel
-# ACF, difference 1 ACF and PACF suggests AR(2)  difference 1 and MA(4) structure (2, 1, 4) in ARIMA.
+# ACF, difference 1 ACF and PACF suggests AR(2)  difference 1 and MA(4) structure (5, 0, 1) in ARIMA.
 acf(liquid.series)
@@
 # saving data to R objects for use in MINOS
-create.if.not.exists("data/transitions/energy_prices/")
+create.if.not.exists(here::here("data", "transitions", "energy_prices")
 write.csv(electric.series, "data/transitions/energy_prices/solid_historic.csv")

### 2024-05-30 minos/modules/behind_on_bills.py

@@ -61,7 +61,9 @@ class behindOnBills(Base):
                         'marital_status',
                         'housing_tenure',
                         "behind_on_bills",
-                        "SF_12"
+                        "SF_12",
+                        'yearly_energy',
+                        'financial_situation'
                         ]
         # view_columns += self.transition_model.rx2('model').names
         self.population_view = builder.population.get_view(columns=view_columns)

### 2024-05-30 minos/modules/outgoings.py

@@ -378,7 +378,8 @@ class energyBills(Base):
                         'housing_tenure',
                         'heating',
                         "housing_quality",
-                        'hidp'
+                        'hidp',
+                        'financial_situation'
                         ]
 
         # columns_created = ['hh_income_diff']
@@ -447,13 +448,20 @@ class energyBills(Base):
         # fixed tariffs according to gaspay variables. These prices don't change with market forces.
         fixed_tariffs = [1, 5, 8]
 
-
+        # gas and electric mean charges from https://www.ofgem.gov.uk/energy-price-cap
+        gas_standing_charges = (~split_energy_bills_pop['gas_payment'].isin(fixed_tariffs)*pop['yearly_gas']>(365*0.3143))*365*0.3143
+        split_energy_bills_pop['yearly_gas'] -= gas_standing_charges
         # adjust gas pricing if not on a fixed tariff.
         split_energy_bills_pop.loc[
-            ~split_energy_bills_pop['gas_payment'].isin(fixed_tariffs), "yearly_gas"] *= gas_price_ratio
+            ~split_energy_bills_pop['gas_payment'].isin(fixed_tariffs)*pop['yearly_gas']>0, "yearly_gas"] *= gas_price_ratio
+        split_energy_bills_pop['yearly_gas'] += gas_standing_charges
+
         # adjust electric pricing if not on a fixed tariff.
+        electric_standing_charges = (~split_energy_bills_pop['electric_payment'].isin(fixed_tariffs)*pop['yearly_electric']>(365*0.6010))*365*0.6010
+        split_energy_bills_pop['yearly_electric'] -= electric_standing_charges
         split_energy_bills_pop.loc[
-            ~split_energy_bills_pop['electric_payment'].isin(fixed_tariffs), "yearly_electric"] *= electric_price_ratio
+            ~split_energy_bills_pop['electric_payment'].isin(fixed_tariffs)*pop['yearly_electric']>0, "yearly_electric"] *= electric_price_ratio
+        split_energy_bills_pop['yearly_electric'] += electric_standing_charges
 
         # no fixed tariffs for oil and solid fuel as far as I can tell. adjust unconditionallty
         split_energy_bills_pop["yearly_oil"] *= liquid_price_ratio
@@ -464,21 +472,23 @@ class energyBills(Base):
                                                    split_energy_bills_pop['yearly_oil'] +
[…]

### 2024-05-31 minos/validation/handovers.Rmd
More updates to get MICE pop working in the pipeline

--- 2024-05-29 minos/validation/handovers.Rmd
@@
 ```{r}
-start.year <- 2021
+start.year <- 2020
 save.path <- here::here("plots", "handovers", 'default')
 create.if.not.exists(save.path)
+
+# Need to remove extra data from raw data after start year
+raw.dat <- raw.dat %>%
+  filter(time <= start.year)
 
@@
   geom_line() +
-  geom_vline(xintercept = 2021, linetype = 'dashed') +
+  geom_vline(xintercept = start.year, linetype = 'dashed') +
   labs(title = 'Counts by older age group', subtitle = '75 to 110 by 5 year groups') +
@@
   geom_line() +
+  geom_vline(xintercept = start.year, linetype = 'dashed') +
   labs(title = 'Households Count')
@@
 ```{r}
-raw.households_with_kids <- raw.dat %>%
+raw.household_count_by_year <- raw.dat %>%
   filter(nkids > 0) %>%
@@
 
-base.households_with_kids <- base.dat %>%
+base.household_count_by_year <- base.dat %>%
   filter(nkids > 0) %>%

### 2024-05-31 minos/validation/handovers.Rmd
changing hanvoers to use imputed data. adding in script to get all ukhls data.

--- 2024-05-29 minos/validation/handovers.Rmd
@@
 # Read raw datafiles in
-raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

### 2024-06-03 minos/outcomes/child_poverty_reduction_vis.Rmd
Added plots for num_priority_groups and fixed the summary to correctly label 0 priority groups (instead of labelling as NA)

@@
 out.path <- here::here('output', 'default_config/')
+#out.path <- here::here('output', 'scotland_scaled/')
 base.dat <- read_singular_local_out(out.path, 'baseline', 

### 2024-06-03 minos/modules/child_poverty_interventions.py

@@ -331,7 +331,9 @@ class ChildPovertyReductionRELATIVE_2(Base):
         # set parameters
         end_year = 2030
         target_pov_prop = 0.1
-        relative_poverty_threshold = 1247.71
+        #relative_poverty_threshold = 1247.71
+        relative_poverty_threshold = 1101.32
+
 
         # 1. Calculate median hh_income over all households
         full_pop = self.population_view.get(event.index, query="alive =='alive'")

### 2024-06-03 minos/outcomes/ChildPovReduction_plots.Rmd

@@
 
+```{r "SF12_change_num_priority_groups", include=FALSE}
+SF12_change_num_priority_groups <- function(scen.list) {
+
+  summary_group <- 'priority_num'
+
+  tit <- 'Number of Priority Subgroups'
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))
+
+  data <- replace_na(data, list(num_priority_groups=0))
+
+  plot_data <- data %>%
+    select(run_id, num_priority_groups, SF_12, mean_cost, year, scen) %>%
+    pivot_wider(names_from = scen,
+                values_from = c(SF_12, mean_cost),
+                names_sep = '.') %>%
+    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
+    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
+    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
+                 names_to = c(".value", "scen"),
+                 names_sep = "\\.") %>%
+    filter(scen != 'baseline') %>%
+    select(-scen)
+
+  plot_data$num_priority_groups <- factor(plot_data$num_priority_groups)
+
+  plot_data_confint <- plot_data %>%
+    group_by(year, num_priority_groups) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(diff_SF_12),
+              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
+              lower = mean_SF12_change - margin,
+              upper = mean_SF12_change + margin)
+
+  plot_data_confint2 <- plot_data %>%
+    group_by(year, num_priority_groups) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(diff_SF_12),
+              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
+              lower = mean_SF12_change - margin,
+              upper = mean_SF12_change + margin)
+
+  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted') +
+    geom_smooth() +
+    labs(title = tit) +
+    xlab('Year') +
+    ylab('Change in SF-12')
+
+  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(linetype = 'dashed') +
+    geom_point() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = tit) +
+    xlab('Year') +
+    ylab('Change in SF-12')
+
+  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(linetype = 'dashed') +
+    geom_point() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = tit) +
+    xlab('Year') +
+    ylab('Change in SF-12')
+
+  print(p1)
+  print(p2)
+}
+
+SF12_change_percentage_num_priority_groups <- function(scen.list) {
+
+  summary_group <- 'priority_num'
+
+  tit <- 'Number of Priority Subgroups'
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))
+
+  data <- replace_na(data, list(num_priority_groups=0))
+
+  plot_data <- data %>%
+    select(run_id, num_priority_groups, SF_12, mean_cost, year, scen) %>%
+    pivot_wider(names_from = scen,
+                values_from = c(SF_12, mean_cost),
+                names_sep = '.') %>%
+    mutate(across(starts_with("SF_12"), ~ ((. - SF_12.baseline) / SF_12.baseline) * 100)) %>% # Calculate percentage change
+    rename_with(~ paste0("percent_change_", .), starts_with("SF_12")) %>%
+    pivot_longer(cols = starts_with("percent_change") | starts_with("mean_cost"),
+                 names_to = c(".value", "scen"),
+                 names_sep = "\\.") %>%
+    filter(scen != 'baseline') %>%
+    select(-scen)
+
+  plot_data$num_priority_groups <- factor(plot_data$num_priority_groups)
+
+  plot_data_confint <- plot_data %>%
+    group_by(year, num_priority_groups) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(percent_change_SF_12),
+              margin = qt(0.975, df = n - 1) * (sd(percent_change_SF_12) / sqrt(n)),
+              lower = mean_SF12_change - margin,
+              upper = mean_SF12_change + margin)
+
+  plot_data_confint2 <- plot_data %>%
+    group_by(year, num_priority_groups) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(percent_change_SF_12),
+              margin = qnorm(0.975) * (sd(percent_change_SF_12) / sqrt(n)),
+              lower = mean_SF12_change - margin,
+              upper = mean_SF12_change + margin)
+
+  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted') +
+    geom_smooth() +
+    labs(title = tit) +
+    xlab('Year') +
+    ylab('Change in SF-12')
+
+  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(linetype = 'dashed') +
+    geom_point() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = tit) +
+    xlab('Year') +
+    ylab('Change in SF-12')
+
+  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(linetype = 'dashed') +
+    geom_point() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = tit) +
+    xlab('Year') +
+    ylab('Change in SF-12')
+
+  print(p1)
+  print(p2)
+}
+```
+
 ```{r}
-scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE')
+#scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
 whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
@@
 
+## Number of Priority Subgroups
+
 ```{r}
-#SF12_change_income_quint <- function(summary_group, scen.list) {
 
-summary_group <- 'priority_num'
+```
 
-  tit <- ' '
-  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
-  if (summary_group == 'families') { tit <- 'Families' }
+# TESTING
 
-  #summary_group <- paste0(summary_group, '_income_quint')
+```{r}
 
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
-
-  plot_data <- data %>%
-    select(run_id, income_quintile, SF_12, mean_cost, year, scen) %>%
-    pivot_wider(names_from = scen,
-                values_from = c(SF_12, mean_cost),
-                names_sep = '.') %>%
-    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
-    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
-    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
-                 names_to = c(".value", "scen"),
-                 names_sep = "\\.") %>%
-    filter(scen != 'baseline') %>%
-    select(-scen)
-
-  plot_data$income_quintile <- factor(plot_data$income_quintile)
-
-  plot_data_confint <- plot_data %>%
-    group_by(year, income_quintile) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF_12),
-              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  plot_data_confint2 <- plot_data %>%
-    group_by(year, income_quintile) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF_12),
-              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted') +
-    geom_smooth() +
-    labs(title = tit, subtitle = 'Income Quintile') +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit, subtitle = 'Income Quintile') +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit, subtitle = 'Income Quintile') +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  print(p1)
-  print(p2)
-#}
 ```

### 2024-06-05 minos/outcomes/ChildPovReduction_Combined.Rmd
Updating the ChildPovReduction plotting script with num_priority_groups plots and adding a new script with both relative and absolute interventions together

--- 2024-06-03 minos/outcomes/ChildPovReduction_plots.Rmd
@@
 ```{r "SF12_change_simple_functions", include=FALSE}
-SF12_change_simple <- function(summary_group, scen.list) {
-
-  tit <- ' '
-  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
-  if (summary_group == 'families') { tit <- 'Families' }
-
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
-
-  plot_data <- data %>%
-    select(run_id, SF_12, mean_cost, year, scen) %>%
-    pivot_wider(names_from = scen,
-                values_from = c(SF_12, mean_cost),
-                names_sep = '.') %>%
-    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
-    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
-    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"), 
-                 names_to = c(".value", "scen"), 
-                 names_sep = "\\.") %>%
-    filter(scen != 'baseline')
-
-  plot_data_confint <- plot_data %>%
-    group_by(year) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF_12),
-              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  plot_data_confint2 <- plot_data %>%
-    group_by(year) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF_12),
-              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted') +
-    geom_smooth() +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  print(p1)
-  print(p2)
-  #print(p3)
-}
-
 SF12_change_percentage <- function(summary_group, scen.list) {
@@
     geom_smooth() +
-    labs(title = tit) +
+    labs(title = tit, subtitle = 'GAM Smoothed') +
     xlab('Year') +
@@
     geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
+    labs(title = tit, subtitle = '95% Confidence Intervals') +
     ylab('Percentage Change in SF-12')
@@
 }
-
 ```
@@
 ```{r "SF12_change_income_quint", include=FALSE}
-SF12_change_income_quint <- function(summary_group, scen.list) {
-
-  tit <- ' '
-  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
-  if (summary_group == 'families') { tit <- 'Families' }
-
-  summary_group <- paste0(summary_group, '_income_quint')
-
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
-
-  plot_data <- data %>%
-    select(run_id, income_quintile, SF_12, mean_cost, year, scen) %>%
-    pivot_wider(names_from = scen,
-                values_from = c(SF_12, mean_cost),
-                names_sep = '.') %>%
-    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
-    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
-    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
-                 names_to = c(".value", "scen"),
-                 names_sep = "\\.") %>%
-    filter(scen != 'baseline') %>%
-    select(-scen)
-
-  plot_data$income_quintile <- factor(plot_data$income_quintile)
-
-  plot_data_confint <- plot_data %>%
-    group_by(year, income_quintile) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF_12),
-              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  plot_data_confint2 <- plot_data %>%
-    group_by(year, income_quintile) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF_12),
-              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted') +
-    geom_smooth() +
-    labs(title = tit, subtitle = 'Income Quintile') +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit, subtitle = 'Income Quintile') +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit, subtitle = 'Income Quintile') +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  print(p1)
-  print(p2)
-}
-
 SF12_change_percentage_income_quint <- function(summary_group, scen.list) {
@@
 ```{r "SF12_change_num_priority_groups", include=FALSE}
-SF12_change_num_priority_groups <- function(scen.list) {
-
-  summary_group <- 'priority_num'
-
-  tit <- 'Number of Priority Subgroups'
-
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))
-
-  data <- replace_na(data, list(num_priority_groups=0))
-
-  plot_data <- data %>%
-    select(run_id, num_priority_groups, SF_12, mean_cost, year, scen) %>%
-    pivot_wider(names_from = scen,
-                values_from = c(SF_12, mean_cost),
-                names_sep = '.') %>%
-    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
-    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
-    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
-                 names_to = c(".value", "scen"),
-                 names_sep = "\\.") %>%
-    filter(scen != 'baseline') %>%
-    select(-scen)
-
-  plot_data$num_priority_groups <- factor(plot_data$num_priority_groups)
-
-  plot_data_confint <- plot_data %>%
-    group_by(year, num_priority_groups) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF_12),
-              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  plot_data_confint2 <- plot_data %>%
-    group_by(year, num_priority_groups) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF_12),
-              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted') +
-    geom_smooth() +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  print(p1)
-  print(p2)
-}
-
 SF12_change_percentage_num_priority_groups <- function(scen.list) {
@@
 
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
 
@@
 
-  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
+  p1 <- ggplot(plot_data, aes(x = year, y = percent_change_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
     geom_hline(yintercept = 0, linetype = 'dashed') +
@@
 
-```{r}
-#scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
-scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
-whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
+```{r "Data", include=FALSE}
+scen.list.rel <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+scen.list.abs <- c('baseline', 'ChildPovertyReductionABSOLUTE')
 ```
 
-# Quick Data Test
+# RELATIVE POVERTY INTERVENTION
 
-```{r}
-ggplot(whole_pop_data, aes(x = year, y = SF_12, group = scen, colour = scen, fill = scen)) +
-  geom_smooth()
-```
+Reducing the proportion of children in poverty to 10% or lower by 2030.
 
-Check if SF12 results in one year (across 100 runs) are normally distributed.
-
-```{r}
-whole_pop_2030 <- whole_pop_data %>%
-  filter(year == 2030)
-
-hist(whole_pop_2030$SF_12)
-qqnorm(whole_pop_2030$SF_12)
-qqline(whole_pop_2030$SF_12)
-
-shapiro.test(whole_pop_2030$SF_12)
-
-# Results look normally distributed^
-```
-
-# Whole Population
+## Whole Population
 
@@
 ```{r}
-SF12_change_simple(summary_group = 'whole_pop',
-                   scen.list = scen.list.test)
-
 SF12_change_percentage(summary_group = 'whole_pop',
-                       scen.list = scen.list.test)
+                   scen.list = scen.list.rel)
 ```
@@
 ```{r}
-SF12_change_income_quint(summary_group = 'whole_pop',
-                         scen.list = scen.list.test)
-
 SF12_change_percentage_income_quint(summary_group = 'whole_pop',
-                                    scen.list = scen.list.test)
+                                    scen.list = scen.list.rel)
 ```
 
-# Families
+## Families
 
@@
 ```{r}
-SF12_change_simple(summary_group = 'families',
-                   scen.list = scen.list.test)
-
 SF12_change_percentage(summary_group = 'families',
-                       scen.list = scen.list.test)
+                       scen.list = scen.list.rel)
 ```
@@
 ```{r}
-SF12_change_income_quint(summary_group = 'families',
-                         scen.list = scen.list.test)
-
 SF12_change_percentage_income_quint(summary_group = 'families',
-                                    scen.list = scen.list.test)
+                                    scen.list = scen.list.rel)
 ```
 
-# Priority Subgroups
+## Priority Subgroups
 
@@
 ```{r}
-SF12_change_simple(summary_group = 'priority_any',
-                         scen.list = scen.list.test)
-
 SF12_change_percentage(summary_group = 'priority_any',
-                                    scen.list = scen.list.test)
+                                    scen.list = scen.list.rel)
 ```
 
-## Number of Priority Subgroups
+### Number of Priority Subgroups
+
+Results disaggregated by if household belongs to 0, 1, 2, 3+ priority subgroups.
 
 ```{r}
-
+SF12_change_percentage_num_priority_groups(scen.list.rel)
 ```
 
-# TESTING
-
-```{r}
-
-```
-
-# Differential Impacts of UK vs SG
+## Differential Impacts of UK vs SG
 
@@
 
-# BONUS - Treated Pop
+# ABSOLUTE POVERTY INTERVENTION
+
+Reducing the proportion of children in poverty to 10% or lower by 2030.
+
+## Whole Population
+
+What are the impacts on mental health of meeting the targets:
+
+- Across the population?
+- Population by income quintile?
+
+```{r}
+SF12_change_percentage(summary_group = 'whole_pop',
+                       scen.list = scen.list.abs)
+```
+
+```{r}
+SF12_change_percentage_income_quint(summary_group = 'whole_pop',
+                                    scen.list = scen.list.abs)
+```
+
+## Families
+
+What are the impacts on mental health of meeting the targets:
+
+- For families only? By income quintile
+
+```{r}
+SF12_change_percentage(summary_group = 'families',
+                       scen.list = scen.list.abs)
+```
+
+```{r}
+SF12_change_percentage_income_quint(summary_group = 'families',
+                                    scen.list = scen.list.abs)
+```
+
+## Priority Subgroups
+
+What are the impacts on mental health of meeting the targets:
+
+- For families that meet the criteria of 0/1/2+ of the priority family groups?
+
+```{r}
+SF12_change_percentage(summary_group = 'priority_any',
+                                    scen.list = scen.list.abs)
+```
+
+### Number of Priority Subgroups
+
+Results disaggregated by if household belongs to 0, 1, 2, 3+ priority subgroups.
+
+```{r}
+SF12_change_percentage_num_priority_groups(scen.list.abs)
+```
+
+## Differential Impacts of UK vs SG
+
+What are the impacts on mental health of meeting the targets?
+
+- Differential impacts of UK package of policies only, and then UK package with SG policies?
 

### 2024-06-05 minos/outcomes/ChildPovReduction_plots.Rmd
Updating the ChildPovReduction plotting script with num_priority_groups plots and adding a new script with both relative and absolute interventions together

@@
 ```{r}
-#scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
-scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
+scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+#scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
 whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
@@
 ```{r}
-
+SF12_change_num_priority_groups(scen.list.test)
+SF12_change_percentage_num_priority_groups(scen.list.test)
 ```

### 2024-06-06 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Additions to ChildPovReduction plotting scripts

@@
 
-workingDir <- "/home/luke/Documents/MINOS/Minos/"
-#workingDir <- normalizePath('../')
+#workingDir <- "/home/luke/Documents/MINOS/Minos/"
+workingDir <- normalizePath('../')
 knitr::opts_knit$set(root.dir = workingDir)
@@
 ```{r, include=FALSE}
-out.path <- here::here('output', 'default_config/')
+#out.path <- here::here('output', 'default_config/')
+out.path <- here::here('output', 'scotland_scaled/')
 base.dat <- read_singular_local_out(out.path, 
@@
                                     drop.zero.weight = TRUE)
+# rel.int <- read_singular_local_out(out.path, 
+#                                    'ChildPovertyReductionRELATIVE', 
+#                                    drop.dead = TRUE,
+#                                    drop.zero.weight = TRUE)
 rel.int <- read_singular_local_out(out.path,
-                                   'ChildPovertyReductionRELATIVE', 
+                                     'ChildPovertyReductionRELATIVE_2',
                                      drop.dead = TRUE,
                                      drop.zero.weight = TRUE)
-# rel.int.2 <- read_singular_local_out(out.path,
-#                                      'ChildPovertyReductionRELATIVE_2',
-#                                      drop.dead = TRUE,
-#                                      drop.zero.weight = TRUE)
-# abs.int <- read_singular_local_out(out.path, 
-#                                    'ChildPovertyReductionABSOLUTE', 
-#                                    drop.dead = TRUE,
-#                                    drop.zero.weight = TRUE)
+abs.int <- read_singular_local_out(out.path,
+                                   'ChildPovertyReductionABSOLUTE',
+                                   drop.dead = TRUE,
+                                   drop.zero.weight = TRUE)
 ```

### 2024-06-06 minos/outcomes/ChildPovReduction_plots.Rmd
Additions to ChildPovReduction plotting scripts

@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
 knitr::opts_knit$set(root.dir = workingDir)
@@
   if (summary_group == 'families') { tit <- 'Families' }
+  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
 
@@
   print(p2)
+}
+
+SF12_change_ind_trajectories <- function(summary_group, scen.list) {
+
+  tit <- ' '
+  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
+  if (summary_group == 'families') { tit <- 'Families' }
+  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+
+  plot_data <- data %>%
+    select(run_id, SF_12, mean_cost, year, scen) %>%
+    pivot_wider(names_from = scen,
+                values_from = c(SF_12, mean_cost),
+                names_sep = '.') %>%
+    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
+    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
+    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"), 
+                 names_to = c(".value", "scen"), 
+                 names_sep = "\\.") %>%
+    filter(scen != 'baseline')
+
+  plot_data_confint <- plot_data %>%
+    group_by(year) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(diff_SF_12),
+              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
+              lower = mean_SF12_change - margin,
+              upper = mean_SF12_change + margin)
+
+  p1 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(linetype = 'dashed') +
+    geom_point() +
+    geom_line(data = plot_data, aes(x = year, y = diff_SF_12, group = run_id), alpha = 0.2) +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = 'tit') +
+    xlab('Year') +
+    ylab('Change in SF-12')
+
+  print(p1)
 }
@@
     xlab('Year') +
-    ylab('Change in SF-12')
+    ylab('Percentage Change in SF-12')
 
@@
     xlab('Year') +
-    ylab('Change in SF-12')
+    ylab('Percentage Change in SF-12')
+
+  print(p1)
+  print(p2)
+}
+```
+
+```{r "inequality_plots", include=FALSE}
+inequality_plots <- function(summary_group, scen.list) {
+
+  tit <- ' '
+  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
+  if (summary_group == 'families') { tit <- 'Families' }
+  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
+
+  summary_group <- paste0(summary_group, '_income_quint')
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+
+  data$income_quintile <- factor(data$income_quintile)
+
+  # Combine the data
+  data_combined <- data %>%
+    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))
+
+  p1 <- ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
+    geom_smooth(alpha = 0.7) +
+    scale_color_manual(name = "Income Quintile", 
+                       values = c("red", "blue", "green", "orange", "purple")) +
+    scale_linetype_manual(name = "Scenario", 
+                          values = c("Baseline" = "solid", "Intervention" = "dotted")) +
+    labs(title = "SF_12 Scores by Income Quintile",
+         subtitle = tit,
+         x = "Year",
+         y = "Mean SF_12 MCS") +
+    theme_minimal() +
+    theme(legend.position = "right",
+          legend.title = element_text(size = 12),
+          legend.text = element_text(size = 10))
+
+  # Aggregate data
+  agg_data <- data %>%
+    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention')) %>%
+    group_by(year, income_quintile, scenario) %>%
+    summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
+    spread(scenario, mean_SF_12) %>%
+    mutate(difference = Intervention - Baseline)
+
+  p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
+    geom_bar(stat = "identity", position = "dodge") +
+    scale_fill_manual(name = "Income Quintile", 
+                      values = c("red", "blue", "green", "orange", "purple")) +
+    labs(title = "Average Difference in SF_12 Scores by Income Quintile",
+         subtitle = tit,
+         x = "Year",
+         y = "Difference in SF_12 Score") +
+    theme_minimal() +
+    theme(legend.position = "right",
+          legend.title = element_text(size = 12),
+          legend.text = element_text(size = 10))
 
@@
                        scen.list = scen.list.test)
+
+SF12_change_ind_trajectories(summary_group = 'whole_pop',
+                             scen.list = scen.list.test)
+
+inequality_plots(summary_group = 'whole_pop',
+                 scen.list = scen.list.test)
 ```
@@
 SF12_change_percentage(summary_group = 'families',
+                       scen.list = scen.list.test)
+
+SF12_change_ind_trajectories(summary_group = 'families',
+                             scen.list = scen.list.test)
+
+inequality_plots(summary_group = 'families',
                  scen.list = scen.list.test)
@@
 
+# TESTING
+
 ```{r}
+#SF12_change_simple <- function(summary_group, scen.list) {
+
+tit <- ' '
+# if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
+# if (summary_group == 'families') { tit <- 'Families' }
+
+summary_group <- 'whole_pop_income_quint'
+scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+
+data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))
+
+data$income_quintile <- factor(data$income_quintile)
+
+base.test <- filter(data, scen == 'baseline')
+pov.test <- filter(data, scen == 'ChildPovertyReductionRELATIVE_2')
+
+# ggplot(base.test, aes(x = year, y = SF_12, group = income_quintile, color = income_quintile)) +
+#   geom_smooth(alpha = 0.7) +
+#   geom_smooth(data = pov.test, aes(x = year, y = SF_12, group = income_quintile, color = income_quintile), linetype = 'dotted')
+
+# Combine the data
+data_combined <- data %>%
+  mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))
+
+ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
+  geom_smooth(alpha = 0.7) +
+  scale_color_manual(name = "Income Quintile", 
+                     values = c("red", "blue", "green", "orange", "purple")) +
+  scale_linetype_manual(name = "Scenario", 
+                        values = c("Baseline" = "solid", "Intervention" = "dotted")) +
+  labs(title = "SF_12 Scores by Income Quintile",
+       subtitle = "Comparison of Baseline and Intervention",
+       x = "Year",
+       y = "Mean SF_12 MCS") +
+  theme_minimal() +
+  theme(legend.position = "right",
+        legend.title = element_text(size = 12),
+        legend.text = element_text(size = 10))
+
+ggplot(data_combined, aes(x = year, y = SF_12, group = scenario, color = scenario)) +
+  geom_smooth(alpha = 0.7, aes(linetype = scenario)) +
+  facet_wrap(~ income_quintile) +
+  scale_color_manual(name = "Scenario", 
+                     values = c("Baseline" = "black", "Intervention" = "red")) +
+  scale_linetype_manual(name = "Scenario", 
+                        values = c("Baseline" = "solid", "Intervention" = "dotted")) +
+  labs(title = "SF_12 Scores by Income Quintile",
+       subtitle = "Comparison of Baseline and Intervention Scenarios",
+       x = "Year",
+       y = "SF_12 Score") +
+  theme_minimal() +
+  theme(legend.position = "bottom",
+        legend.title = element_text(size = 12),
+        legend.text = element_text(size = 10))
+
+# Calculate the differences
+diff_data <- data %>%
+  pivot_wider(names_from = scen, values_from = SF_12) %>%
+  mutate(difference = `ChildPovertyReductionRELATIVE_2` - baseline) %>%
+  gather(scen, SF_12, baseline, ChildPovertyReductionRELATIVE_2)
+
+ggplot(diff_data, aes(x = year, y = difference, group = income_quintile, color = income_quintile)) +
+  geom_line() +
+  scale_color_manual(name = "Income Quintile", 
+                     values = c("red", "blue", "green", "orange", "purple")) +
+  labs(title = "Difference in SF_12 Scores by Income Quintile",
+       subtitle = "Intervention Scenario Minus Baseline Scenario",
+       x = "Year",
+       y = "Difference in SF_12 Score") +
+  theme_minimal() +
+  theme(legend.position = "right",
+        legend.title = element_text(size = 12),
+        legend.text = element_text(size = 10))
+
+# Aggregate data
+agg_data <- data %>%
+  group_by(year, income_quintile, scen) %>%
+  summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
+  spread(scen, mean_SF_12) %>%
+  mutate(difference = `ChildPovertyReductionRELATIVE_2` - baseline)
+
+ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(name = "Income Quintile", 
+                    values = c("red", "blue", "green", "orange", "purple")) +
+  labs(title = "Average Difference in SF_12 Scores by Income Quintile",
+       subtitle = "Intervention Minus Baseline",
+       x = "Year",
+       y = "Difference in SF_12 Score") +
+  theme_minimal() +
+  theme(legend.position = "right",
+        legend.title = element_text(size = 12),
+        legend.text = element_text(size = 10))
 
 ```
+
+```{r}
+inequality_plots <- function(summary_group, scen.list) {
+
+  tit <- ' '
+  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
+  if (summary_group == 'families') { tit <- 'Families' }
+
+  #summary_group <- 'whole_pop_income_quint'
+  #scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+
+  summary_group <- paste0(summary_group, '_income_quint')
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))
+
+  data$income_quintile <- factor(data$income_quintile)
+
+  # Combine the data
+  data_combined <- data %>%
+    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))
+
+  p1 <- ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
+    geom_smooth(alpha = 0.7) +
+    scale_color_manual(name = "Income Quintile", 
+                       values = c("red", "blue", "green", "orange", "purple")) +
+    scale_linetype_manual(name = "Scenario", 
+                          values = c("Baseline" = "solid", "Intervention" = "dotted")) +
+    labs(title = "SF_12 Scores by Income Quintile",
+         subtitle = "Comparison of Baseline and Intervention",
+         x = "Year",
+         y = "Mean SF_12 MCS") +
+    theme_minimal() +
+    theme(legend.position = "right",
+          legend.title = element_text(size = 12),
+          legend.text = element_text(size = 10))
+
+  # Aggregate data
+  agg_data <- data %>%
+    group_by(year, income_quintile, scen) %>%
+    summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
+    spread(scen, mean_SF_12) %>%
+    mutate(difference = `ChildPovertyReductionRELATIVE_2` - baseline)
+
+  p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
+    geom_bar(stat = "identity", position = "dodge") +
+    scale_fill_manual(name = "Income Quintile", 
+                      values = c("red", "blue", "green", "orange", "purple")) +
+    labs(title = "Average Difference in SF_12 Scores by Income Quintile",
+         subtitle = "Intervention Minus Baseline",
+         x = "Year",
+         y = "Difference in SF_12 Score") +
+    theme_minimal() +
+    theme(legend.position = "right",
+          legend.title = element_text(size = 12),
+          legend.text = element_text(size = 10))
+
+  print(p1)
+  print(p2)
+}
+```
+
+```{r}
+scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+
+inequality_plots(summary_group = 'whole_pop',
+                 scen.list = scen.list.test)
+
+inequality_plots(summary_group = 'families',
+                 scen.list = scen.list.test)
+```

### 2024-06-06 minos/outcomes/child_poverty_reduction_vis.Rmd
Additions to ChildPovReduction plotting scripts

--- 2024-05-29 minos/outcomes/child_poverty_reduction_vis.Rmd
@@
 
-#workingDir <- "/home/luke/Documents/WORK/MINOS/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos"
 workingDir <- normalizePath('../')
@@
 ```{r, include=FALSE}
-out.path <- here::here('output', 'default_config/')
+#out.path <- here::here('output', 'default_config/')
+out.path <- here::here('output', 'scotland_scaled/')
 base.dat <- read_singular_local_out(out.path, 'baseline', 

### 2024-06-07 minos/outcomes/ChildPovReduction_plots.Rmd
Small fixes for model runs, including some variables that had to be put back after removal, some var type problems fixed, and WIP on a combined relative and absolute poverty intervention

@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old6/"
 knitr::opts_knit$set(root.dir = workingDir)
@@
   if (summary_group == 'families') { tit <- 'Families' }
+  if (summary_group == 'treated') { tit <- 'Treated' }
   if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
@@
 
+# Treated
+
+```{r}
+SF12_change_simple(summary_group = 'treated',
+                   scen.list = scen.list.test)
+
+SF12_change_percentage(summary_group = 'treated',
+                       scen.list = scen.list.test)
+```
+
 ```{r}
@@
 
-summary_group <- 'whole_pop_income_quint'
+summary_group <- 'treated'
 scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
@@
 
-# ggplot(base.test, aes(x = year, y = SF_12, group = income_quintile, color = income_quintile)) +
-#   geom_smooth(alpha = 0.7) +
-#   geom_smooth(data = pov.test, aes(x = year, y = SF_12, group = income_quintile, color = income_quintile), linetype = 'dotted')
-
-# Combine the data
-data_combined <- data %>%
-  mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))
-
-ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
-  geom_smooth(alpha = 0.7) +
-  scale_color_manual(name = "Income Quintile", 
-                     values = c("red", "blue", "green", "orange", "purple")) +
-  scale_linetype_manual(name = "Scenario", 
-                        values = c("Baseline" = "solid", "Intervention" = "dotted")) +
-  labs(title = "SF_12 Scores by Income Quintile",
-       subtitle = "Comparison of Baseline and Intervention",
-       x = "Year",
-       y = "Mean SF_12 MCS") +
-  theme_minimal() +
-  theme(legend.position = "right",
-        legend.title = element_text(size = 12),
-        legend.text = element_text(size = 10))
-
-ggplot(data_combined, aes(x = year, y = SF_12, group = scenario, color = scenario)) +
-  geom_smooth(alpha = 0.7, aes(linetype = scenario)) +
-  facet_wrap(~ income_quintile) +
-  scale_color_manual(name = "Scenario", 
-                     values = c("Baseline" = "black", "Intervention" = "red")) +
-  scale_linetype_manual(name = "Scenario", 
-                        values = c("Baseline" = "solid", "Intervention" = "dotted")) +
-  labs(title = "SF_12 Scores by Income Quintile",
-       subtitle = "Comparison of Baseline and Intervention Scenarios",
-       x = "Year",
-       y = "SF_12 Score") +
-  theme_minimal() +
-  theme(legend.position = "bottom",
-        legend.title = element_text(size = 12),
-        legend.text = element_text(size = 10))
-
-# Calculate the differences
-diff_data <- data %>%
-  pivot_wider(names_from = scen, values_from = SF_12) %>%
-  mutate(difference = `ChildPovertyReductionRELATIVE_2` - baseline) %>%
-  gather(scen, SF_12, baseline, ChildPovertyReductionRELATIVE_2)
-
-ggplot(diff_data, aes(x = year, y = difference, group = income_quintile, color = income_quintile)) +
-  geom_line() +
-  scale_color_manual(name = "Income Quintile", 
-                     values = c("red", "blue", "green", "orange", "purple")) +
-  labs(title = "Difference in SF_12 Scores by Income Quintile",
-       subtitle = "Intervention Scenario Minus Baseline Scenario",
-       x = "Year",
-       y = "Difference in SF_12 Score") +
-  theme_minimal() +
-  theme(legend.position = "right",
-        legend.title = element_text(size = 12),
-        legend.text = element_text(size = 10))
-
-# Aggregate data
-agg_data <- data %>%
-  group_by(year, income_quintile, scen) %>%
-  summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
-  spread(scen, mean_SF_12) %>%
-  mutate(difference = `ChildPovertyReductionRELATIVE_2` - baseline)
-
-ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
-  geom_bar(stat = "identity", position = "dodge") +
-  scale_fill_manual(name = "Income Quintile", 
-                    values = c("red", "blue", "green", "orange", "purple")) +
-  labs(title = "Average Difference in SF_12 Scores by Income Quintile",
-       subtitle = "Intervention Minus Baseline",
-       x = "Year",
-       y = "Difference in SF_12 Score") +
-  theme_minimal() +
-  theme(legend.position = "right",
-        legend.title = element_text(size = 12),
-        legend.text = element_text(size = 10))
-
 ```
@@
 ```{r}
-inequality_plots <- function(summary_group, scen.list) {
 
-  tit <- ' '
-  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
-  if (summary_group == 'families') { tit <- 'Families' }
-
-  #summary_group <- 'whole_pop_income_quint'
-  #scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
-
-  summary_group <- paste0(summary_group, '_income_quint')
-
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))
-
-  data$income_quintile <- factor(data$income_quintile)
-
-  # Combine the data
-  data_combined <- data %>%
-    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))
-
-  p1 <- ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
-    geom_smooth(alpha = 0.7) +
-    scale_color_manual(name = "Income Quintile", 
-                       values = c("red", "blue", "green", "orange", "purple")) +
-    scale_linetype_manual(name = "Scenario", 
-                          values = c("Baseline" = "solid", "Intervention" = "dotted")) +
-    labs(title = "SF_12 Scores by Income Quintile",
-         subtitle = "Comparison of Baseline and Intervention",
-         x = "Year",
-         y = "Mean SF_12 MCS") +
-    theme_minimal() +
-    theme(legend.position = "right",
-          legend.title = element_text(size = 12),
-          legend.text = element_text(size = 10))
-
-  # Aggregate data
-  agg_data <- data %>%
-    group_by(year, income_quintile, scen) %>%
-    summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
-    spread(scen, mean_SF_12) %>%
-    mutate(difference = `ChildPovertyReductionRELATIVE_2` - baseline)
-
-  p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
-    geom_bar(stat = "identity", position = "dodge") +
-    scale_fill_manual(name = "Income Quintile", 
-                      values = c("red", "blue", "green", "orange", "purple")) +
-    labs(title = "Average Difference in SF_12 Scores by Income Quintile",
-         subtitle = "Intervention Minus Baseline",
-         x = "Year",
-         y = "Difference in SF_12 Score") +
-    theme_minimal() +
-    theme(legend.position = "right",
-          legend.title = element_text(size = 12),
-          legend.text = element_text(size = 10))
-
-  print(p1)
-  print(p2)
-}
 ```
-
-```{r}
-scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
-
-inequality_plots(summary_group = 'whole_pop',
-                 scen.list = scen.list.test)
-
-inequality_plots(summary_group = 'families',
-                 scen.list = scen.list.test)
-```

### 2024-06-07 minos/data_generation/US_complete_case.py

@@ -86,7 +86,6 @@ def input_main():
         'ndrinks',
         'gross_paypm',
         'depression',
-        'hh_int_m',
         'nobs',
         'job_industry',
         'gross_pay_se',
@@ -195,7 +194,6 @@ def transition_main():
         'ndrinks',
         'gross_paypm',
         'depression',
-        'hh_int_m',
         'nobs',
         'job_industry',
         'gross_pay_se',

### 2024-06-07 minos/outcomes/ChildPovReduction_Combined.Rmd

--- 2024-06-03 minos/outcomes/ChildPovReduction_plots.Rmd
@@
 output:
+  pdf_document:
+    toc: true
   html_document:
@@
 }
-
-SF12_change_percentage <- function(summary_group, scen.list) {
-
-  tit <- ' '
-  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
-  if (summary_group == 'families') { tit <- 'Families' }
-
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
-
-  plot_data <- data %>%
-    select(run_id, SF_12, mean_cost, year, scen) %>%
-    pivot_wider(names_from = scen,
-                values_from = c(SF_12, mean_cost),
-                names_sep = '.') %>%
-    mutate(across(starts_with("SF_12"), ~ ((. - SF_12.baseline) / SF_12.baseline) * 100)) %>% # Calculate percentage change
-    rename_with(~ paste0("percent_change_", .), starts_with("SF_12")) %>%
-    pivot_longer(cols = starts_with("percent_change") | starts_with("mean_cost"), 
-                 names_to = c(".value", "scen"), 
-                 names_sep = "\\.") %>%
-    filter(scen != 'baseline')
-
-  plot_data_confint <- plot_data %>%
-    group_by(year) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(percent_change_SF_12),
-              margin = qt(0.975, df = n - 1) * (sd(percent_change_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  p1 <- ggplot(plot_data, aes(x = year, y = percent_change_SF_12)) +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted') +
-    geom_smooth() +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Percentage Change in SF-12')
-
-  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Percentage Change in SF-12')
-
-  print(p1)
-  print(p2)
-}
-
 ```
@@
 }
-
-SF12_change_percentage_income_quint <- function(summary_group, scen.list) {
-
-  tit <- ' '
-  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
-  if (summary_group == 'families') { tit <- 'Families' }
-
-  summary_group <- paste0(summary_group, '_income_quint')
-
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
-
-  plot_data <- data %>%
-    select(run_id, income_quintile, SF_12, mean_cost, year, scen) %>%
-    pivot_wider(names_from = scen,
-                values_from = c(SF_12, mean_cost),
-                names_sep = '.') %>%
-    mutate(across(starts_with("SF_12"), ~ ((. - SF_12.baseline) / SF_12.baseline) * 100)) %>% # Calculate percentage change
-    rename_with(~ paste0("percent_change_", .), starts_with("SF_12")) %>%
-    pivot_longer(cols = starts_with("percent_change") | starts_with("mean_cost"),
-                 names_to = c(".value", "scen"),
-                 names_sep = "\\.") %>%
-    filter(scen != 'baseline') %>%
-    select(-scen)
-
-  plot_data$income_quintile <- factor(plot_data$income_quintile)
-
-  plot_data_confint <- plot_data %>%
-    group_by(year, income_quintile) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(percent_change_SF_12),
-              margin = qt(0.975, df = n - 1) * (sd(percent_change_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  p1 <- ggplot(plot_data, aes(x = year, y = percent_change_SF_12, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted') +
-    geom_smooth() +
-    labs(title = tit, subtitle = 'Income Quintile') +
-    xlab('Year') +
-    ylab('Percentage Change in SF-12')
-
-  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit, subtitle = 'Income Quintile') +
-    xlab('Year') +
-    ylab('Percentage Change in SF-12')
-
-  print(p1)
-  print(p2)
-}
-
 ```
@@
 }
+```
 
-SF12_change_percentage_num_priority_groups <- function(scen.list) {
+```{r "inequality_plots", include=FALSE}
+inequality_plots <- function(summary_group, scen.list) {
 
-  summary_group <- 'priority_num'
+  tit <- ' '
+  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
+  if (summary_group == 'families') { tit <- 'Families' }
 
-  tit <- 'Number of Priority Subgroups'
+  summary_group <- paste0(summary_group, '_income_quint')
 
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
 
-  data <- replace_na(data, list(num_priority_groups=0))
+  data$income_quintile <- factor(data$income_quintile)
 
-  plot_data <- data %>%
-    select(run_id, num_priority_groups, SF_12, mean_cost, year, scen) %>%
-    pivot_wider(names_from = scen,
-                values_from = c(SF_12, mean_cost),
-                names_sep = '.') %>%
-    mutate(across(starts_with("SF_12"), ~ ((. - SF_12.baseline) / SF_12.baseline) * 100)) %>% # Calculate percentage change
-    rename_with(~ paste0("percent_change_", .), starts_with("SF_12")) %>%
-    pivot_longer(cols = starts_with("percent_change") | starts_with("mean_cost"),
-                 names_to = c(".value", "scen"),
-                 names_sep = "\\.") %>%
-    filter(scen != 'baseline') %>%
-    select(-scen)
+  # Combine the data
+  data_combined <- data %>%
+    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))
 
-  plot_data$num_priority_groups <- factor(plot_data$num_priority_groups)
+  p1 <- ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
+    geom_smooth(alpha = 0.7) +
+    scale_color_manual(name = "Income Quintile", 
+                       values = c("red", "blue", "green", "orange", "purple")) +
+    scale_linetype_manual(name = "Scenario", 
+                          values = c("Baseline" = "solid", "Intervention" = "dotted")) +
+    labs(title = "SF_12 Scores by Income Quintile",
+         subtitle = tit,
+         x = "Year",
+         y = "Mean SF_12 MCS") +
+    theme_minimal() +
+    theme(legend.position = "right",
+          legend.title = element_text(size = 12),
+          legend.text = element_text(size = 10))
 
-  plot_data_confint <- plot_data %>%
-    group_by(year, num_priority_groups) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(percent_change_SF_12),
-              margin = qt(0.975, df = n - 1) * (sd(percent_change_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
+  # Aggregate data
+  agg_data <- data %>%
+    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention')) %>%
+    group_by(year, income_quintile, scenario) %>%
+    summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
+    spread(scenario, mean_SF_12) %>%
+    mutate(difference = Intervention - Baseline)
 
-  plot_data_confint2 <- plot_data %>%
-    group_by(year, num_priority_groups) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(percent_change_SF_12),
-              margin = qnorm(0.975) * (sd(percent_change_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted') +
-    geom_smooth() +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
+  p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
+    geom_bar(stat = "identity", position = "dodge") +
+    scale_fill_manual(name = "Income Quintile", 
+                      values = c("red", "blue", "green", "orange", "purple")) +
+    labs(title = "Average Difference in SF_12 Scores by Income Quintile",
+         subtitle = tit,
+         x = "Year",
+         y = "Difference in SF_12 Score") +
+    theme_minimal() +
+    theme(legend.position = "right",
+          legend.title = element_text(size = 12),
+          legend.text = element_text(size = 10))
 
@@
 SF12_change_simple(summary_group = 'whole_pop',
-                   scen.list = scen.list.test)
+                   scen.list = scen.list.rel)
+```
 
-SF12_change_percentage(summary_group = 'whole_pop',
-                       scen.list = scen.list.test)
-```
+### Income Quintiles
 
@@
 SF12_change_income_quint(summary_group = 'whole_pop',
-                         scen.list = scen.list.test)
-
-SF12_change_percentage_income_quint(summary_group = 'whole_pop',
-                                    scen.list = scen.list.test)
+                                    scen.list = scen.list.rel)
 ```
 
-# Families
+### SF_12 Inequality
+
+```{r}
+inequality_plots(summary_group = 'whole_pop',
+                 scen.list = scen.list.rel)
+```
+
+## Families
 
@@
 SF12_change_simple(summary_group = 'families',
-                   scen.list = scen.list.test)
+                       scen.list = scen.list.rel)
+```
 
-SF12_change_percentage(summary_group = 'families',
-                       scen.list = scen.list.test)
-```
+### Income Quintile
 
@@
 SF12_change_income_quint(summary_group = 'families',
-                         scen.list = scen.list.test)
-
-SF12_change_percentage_income_quint(summary_group = 'families',
-                                    scen.list = scen.list.test)
+                                    scen.list = scen.list.rel)
 ```
 
-# Priority Subgroups
+### SF_12 Inequality
+
+```{r}
+inequality_plots(summary_group = 'families',
+                 scen.list = scen.list.rel)
+```
+
+## Priority Subgroups
 
@@
 SF12_change_simple(summary_group = 'priority_any',
-                         scen.list = scen.list.test)
-
-SF12_change_percentage(summary_group = 'priority_any',
-                                    scen.list = scen.list.test)
+                       scen.list = scen.list.rel)
 ```
 
-## Number of Priority Subgroups
+### Number of Priority Subgroups
+
+Results disaggregated by if household belongs to 0, 1, 2, 3+ priority subgroups.
 
 ```{r}
-
+SF12_change_num_priority_groups(scen.list.rel)
 ```
 
-# TESTING
-
-```{r}
-
-```
-
-# Differential Impacts of UK vs SG
+## Differential Impacts of UK vs SG
 
@@
 
-# BONUS - Treated Pop
+# ABSOLUTE POVERTY INTERVENTION
+
+Reducing the proportion of children in poverty to 10% or lower by 2030.
+
+## Whole Population
+
+What are the impacts on mental health of meeting the targets:
+
+- Across the population?
+- Population by income quintile?
+
+```{r}
+SF12_change_simple(summary_group = 'whole_pop',
+                       scen.list = scen.list.abs)
+```
+
+### Income Quintile
+
+```{r}
+SF12_change_income_quint(summary_group = 'whole_pop',
+                                    scen.list = scen.list.abs)
+```
+
+### SF_12 Inequality
+
+```{r}
+inequality_plots(summary_group = 'whole_pop',
+                 scen.list = scen.list.abs)
+```
+
+## Families
+
+What are the impacts on mental health of meeting the targets:
+
+- For families only? By income quintile
+
+```{r}
+SF12_change_simple(summary_group = 'families',
+                       scen.list = scen.list.abs)
+```
+
+### Income Quintile
+
+```{r}
+SF12_change_income_quint(summary_group = 'families',
+                                    scen.list = scen.list.abs)
+```
+
+### SF_12 Inequality
+
+```{r}
+inequality_plots(summary_group = 'families',
+                 scen.list = scen.list.abs)
+```
+
+## Priority Subgroups
+
+What are the impacts on mental health of meeting the targets:
+
+- For families that meet the criteria of 0/1/2+ of the priority family groups?
+
+```{r}
+SF12_change_simple(summary_group = 'priority_any',
+                                    scen.list = scen.list.abs)
+```
+
+### Number of Priority Subgroups
+
+Results disaggregated by if household belongs to 0, 1, 2, 3+ priority subgroups.
+
+```{r}
+SF12_change_num_priority_groups(scen.list.abs)
+```
+
+## Differential Impacts of UK vs SG
+
+What are the impacts on mental health of meeting the targets?
+
+- Differential impacts of UK package of policies only, and then UK package with SG policies?
 

### 2024-06-11 minos/outcomes/ChildPovReduction_Combined.Rmd
Additions and WIP plots for childPovReduction scripts

@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
 knitr::opts_knit$set(root.dir = workingDir)
@@
   if (summary_group == 'families') { tit <- 'Families' }
+  if (summary_group == 'treated_relative') { tit <- 'Treated' }
+  if (summary_group == 'treated_absolute') { tit <- 'Treated' }
   if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
@@
 
+## Treated Population
+
+```{r}
+SF12_change_simple(summary_group = 'treated_relative',
+                   scen.list = scen.list.rel)
+```
+
 ## Differential Impacts of UK vs SG
@@
 
+## Treated Population
+
+```{r}
+SF12_change_simple(summary_group = 'treated_absolute',
+                   scen.list = scen.list.abs)
+```
+
 ## Differential Impacts of UK vs SG

### 2024-06-11 minos/outcomes/ChildPovReduction_plots.Rmd
Additions and WIP plots for childPovReduction scripts

@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old6/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old6/"
 knitr::opts_knit$set(root.dir = workingDir)
@@
   if (summary_group == 'families') { tit <- 'Families' }
-  if (summary_group == 'treated') { tit <- 'Treated' }
+  if (summary_group == 'treated_relative') { tit <- 'Treated' }
+  if (summary_group == 'treated_absolute') { tit <- 'Treated' }
   if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
@@
 
-  summary_group <- paste0(summary_group, '_income_quint')
+  summary_group <- paste0(summary_group, '_income_quint2')
 
@@
 ```{r}
-SF12_change_simple(summary_group = 'treated',
+SF12_change_simple(summary_group = 'treated_relative',
                    scen.list = scen.list.test)
 
-SF12_change_percentage(summary_group = 'treated',
+SF12_change_percentage(summary_group = 'treated_relative',
                        scen.list = scen.list.test)
@@
 ```{r}
-#SF12_change_simple <- function(summary_group, scen.list) {
+SF12_change_simple <- function(summary_group, scen.list) {
 
   tit <- ' '
-# if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
-# if (summary_group == 'families') { tit <- 'Families' }
+  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
+  if (summary_group == 'families') { tit <- 'Families' }
+  if (summary_group == 'treated_relative') { tit <- 'Treated' }
+  if (summary_group == 'treated_absolute') { tit <- 'Treated' }
+  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
 
-summary_group <- 'treated'
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+
+  plot_data <- data %>%
+    select(run_id, SF_12, mean_cost, year, scen) %>%
+    pivot_wider(names_from = scen,
+                values_from = c(SF_12, mean_cost),
+                names_sep = '.') %>%
+    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
+    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
+    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"), 
+                 names_to = c(".value", "scen"), 
+                 names_sep = "\\.") %>%
+    filter(scen != 'baseline')
+
+  plot_data_confint <- plot_data %>%
+    group_by(year) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(diff_SF_12),
+              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
+              lower = mean_SF12_change - margin,
+              upper = mean_SF12_change + margin)
+
+  plot_data_confint2 <- plot_data %>%
+    group_by(year) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(diff_SF_12),
+              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
+              lower = mean_SF12_change - margin,
+              upper = mean_SF12_change + margin)
+
+  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted') +
+    geom_smooth() +
+    labs(title = tit) +
+    xlab('Year') +
+    ylab('Change in SF-12')
+
+  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(linetype = 'dashed') +
+    geom_point() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = tit) +
+    xlab('Year') +
+    ylab('Change in SF-12')
+
+  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(linetype = 'dashed') +
+    geom_point() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = tit) +
+    xlab('Year') +
+    ylab('Change in SF-12')
+
+  print(p1)
+  print(p2)
+  #print(p3)
+}
+```
+
+## MENTAL HEALTH THRESHOLD
+
+```{r}
+
 scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+summary_group <- 'men_illness_risk'
 
@@
 
-data$income_quintile <- factor(data$income_quintile)
+plot_data <- data %>%
+  group_by(scen, year, mental_health_risk) %>%
+  summarise(count = mean(count)) %>%
+  filter(mental_health_risk == 'TRUE')
 
-base.test <- filter(data, scen == 'baseline')
-pov.test <- filter(data, scen == 'ChildPovertyReductionRELATIVE_2')
+ggplot(plot_data, aes(x = year, y = count, group = scen, color = scen)) +
+  geom_point() +
+  geom_line()
+
+plot_data_2 <- data %>%
+  filter(mental_health_risk == 'TRUE') %>%
+  select(-prop, -mental_health_risk) %>%
+  pivot_wider(names_from = scen,
+              values_from = count) %>%
+  mutate(MHR_diff = ChildPovertyReductionRELATIVE_2 - baseline) %>%
+  select(run_id, year, MHR_diff) %>%
+  group_by(year) %>%
+  summarise(MHR_diff = mean(MHR_diff))
+
+ggplot(data = plot_data_2, aes(x = year, y = MHR_diff)) +
+  geom_point() +
+  geom_line()
 
 ```
-
-```{r}
-
-```

### 2024-06-11 minos/outcomes/child_poverty_reduction_vis.Rmd
Additions and WIP plots for childPovReduction scripts

@@
 ```{r, include=FALSE}
-#out.path <- here::here('output', 'default_config/')
-out.path <- here::here('output', 'scotland_scaled/')
+out.path <- here::here('output', 'default_config/')
+#out.path <- here::here('output', 'scotland_scaled/')
 base.dat <- read_singular_local_out(out.path, 'baseline', 
@@
 #                                    drop.zero.weight = TRUE)
-int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
+# int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
+#                                    drop.dead = TRUE,
+#                                    drop.zero.weight = TRUE)
+int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionSUSTAIN',
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)
-int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
-                                   drop.dead = TRUE,
-                                   drop.zero.weight = TRUE)
+# int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
+#                                    drop.dead = TRUE,
+#                                    drop.zero.weight = TRUE)
 

### 2024-06-12 minos/outcomes/ChildPovReduction_plots.Rmd
Small changes to handovers and ChildPovReduction plotting script

@@
 
-  summary_group <- paste0(summary_group, '_income_quint2')
+  summary_group <- paste0(summary_group, '_income_quint')
 
@@
 ```{r}
-scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+#scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
 #scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
+scen.list.test <- c('baseline', 'ChildPovertyReductionSUSTAIN')
 whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))

### 2024-06-12 minos/validation/handovers.Rmd
Additions and WIP plots for childPovReduction scripts
Small changes to handovers and ChildPovReduction plotting script

--- 2024-05-31 minos/validation/handovers.Rmd
@@
 # Read raw datafiles in
-raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+#raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 
+spaghetti_plot(base.inc, 'hh_income',
+               save = shall.we.save,
+               save.path = save.path)
+
 rm(raw.inc, base.inc, income.spag)
@@
 ```{r}
-raw.2010 <- raw.dat %>%
-  filter(time == 2010)
-
-abs.threshold <- weighted.median(x = raw.2010$hh_income, 
-                                 w = raw.2010$weight, 
-                                 na.rm = TRUE)
-abs.threshold <- abs.threshold * 0.6
-
-print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
+# raw.2010 <- raw.dat %>%
+#   filter(time == 2010)
+# 
+# abs.threshold <- weighted.median(x = raw.2010$hh_income, 
+#                                  w = raw.2010$weight, 
+#                                  na.rm = TRUE)
+# abs.threshold <- abs.threshold * 0.6
+# 
+# print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
 ```

### 2024-06-13 minos/outcomes/ChildPovReduction_Combined.Rmd
Small changed to plotting scripts

@@
 output:
-  pdf_document:
-    toc: true
   html_document:
@@
     code_folding: hide
+  pdf_document:
+    toc: true
 ---
@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
 knitr::opts_knit$set(root.dir = workingDir)
@@
 
+```{r "mental_illness_risk_plots", include=FALSE}
+mental_illness_risk_counts <- function(summary_group, scen.list) {
+  tit <- ' '
+  if (summary_group == 'men_illness_risk') { tit <- 'Whole Population' }
+  if (summary_group == 'men_illness_risk_families') { tit <- 'Families' }
+
+  # scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+  # summary_group <- 'men_illness_risk'
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+
+  # plot_data <- data %>%
+  #   group_by(scen, year, mental_health_risk) %>%
+  #   summarise(count = mean(count)) %>%
+  #   filter(mental_health_risk == 'TRUE')
+  # 
+  # ggplot(plot_data, aes(x = year, y = count, group = scen, color = scen)) +
+  #   geom_point() +
+  #   geom_line()
+  mutate(num_priority_groups = case_when(
+        num_priority_groups == 0 ~ 0,
+        num_priority_groups == 1 ~ 1,
+        num_priority_groups == 2 ~ 2,
+        num_priority_groups >= 3 ~ 3)) %>%
+
+  plot_data_2 <- data %>%
+    filter(mental_health_risk == 'TRUE') %>%
+    select(-prop, -mental_health_risk) %>%
+    pivot_wider(names_from = scen,
+                values_from = count) %>%
+    rename(intervention = contains(scen.list[[1]]))
+    mutate(MHR_diff = ChildPovertyReductionRELATIVE_2 - baseline) %>%
+    select(run_id, year, MHR_diff) %>%
+    group_by(year) %>%
+    summarise(MHR_diff = mean(MHR_diff))
+
+  p1 <- ggplot(data = plot_data_2, aes(x = year, y = MHR_diff)) +
+    geom_point() +
+    geom_line() +
+    labs(title = "Count of individuals at risk of mental health issues",
+         subtitle = 'Intervention - Baseline') +
+    xlab('Year') +
+    ylab('Count')
+
+  print(p1)
+}
+```
+
 ```{r "Data", include=FALSE}
@@
                    scen.list = scen.list.rel)
+
+# mental_illness_risk_counts(summary_group = 'men_illness_risk',
+#                            scen.list = scen.list.rel)
 ```
@@
                        scen.list = scen.list.rel)
+
+# mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
+#                            scen.list = scen.list.rel)
 ```
@@
                        scen.list = scen.list.abs)
+
+# mental_illness_risk_counts(summary_group = 'men_illness_risk',
+#                            scen.list = scen.list.abs)
 ```
@@
                        scen.list = scen.list.abs)
+
+# mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
+#                            scen.list = scen.list.abs)
 ```

### 2024-06-13 minos/outcomes/ChildPovReduction_plots.Rmd
Small changed to plotting scripts

--- 2024-06-11 minos/outcomes/ChildPovReduction_plots.Rmd
@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old6/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
 knitr::opts_knit$set(root.dir = workingDir)
@@
 
+```{r "mental_illness_risk", include=FALSE}
+mental_illness_risk_counts <- function(summary_group, scen.list) {
+  tit <- ' '
+  if (summary_group == 'men_illness_risk') { tit <- 'Whole Population' }
+  if (summary_group == 'men_illness_risk_families') { tit <- 'Families' }
+
+  # scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+  # summary_group <- 'men_illness_risk'
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+
+  # plot_data <- data %>%
+  #   group_by(scen, year, mental_health_risk) %>%
+  #   summarise(count = mean(count)) %>%
+  #   filter(mental_health_risk == 'TRUE')
+  # 
+  # ggplot(plot_data, aes(x = year, y = count, group = scen, color = scen)) +
+  #   geom_point() +
+  #   geom_line()
+
+  plot_data_2 <- data %>%
+    filter(mental_health_risk == 'TRUE') %>%
+    select(-prop, -mental_health_risk) %>%
+    pivot_wider(names_from = scen,
+                values_from = count) %>%
+    mutate(MHR_diff = ChildPovertyReductionRELATIVE_2 - baseline) %>%
+    select(run_id, year, MHR_diff) %>%
+    group_by(year) %>%
+    summarise(MHR_diff = mean(MHR_diff))
+
+  p1 <- ggplot(data = plot_data_2, aes(x = year, y = MHR_diff)) +
+    geom_point() +
+    geom_line()
+
+  print(p1)
+}
+```
+
 ```{r}
@@
 #scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
+#scen.list.test <- c('baseline', 'ChildPovertyReductionSUSTAIN')
 whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
@@
                  scen.list = scen.list.test)
+
+mental_illness_risk_counts(summary_group = 'men_illness_risk',
+                           scen.list = scen.list.test)
 ```
@@
 inequality_plots(summary_group = 'families',
+                 scen.list = scen.list.test)
+
+mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
                            scen.list = scen.list.test)
@@
 
-scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
-summary_group <- 'men_illness_risk'
+```
 
-data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))
-
-plot_data <- data %>%
-  group_by(scen, year, mental_health_risk) %>%
-  summarise(count = mean(count)) %>%
-  filter(mental_health_risk == 'TRUE')
-
-ggplot(plot_data, aes(x = year, y = count, group = scen, color = scen)) +
-  geom_point() +
-  geom_line()
-
-plot_data_2 <- data %>%
-  filter(mental_health_risk == 'TRUE') %>%
-  select(-prop, -mental_health_risk) %>%
-  pivot_wider(names_from = scen,
-              values_from = count) %>%
-  mutate(MHR_diff = ChildPovertyReductionRELATIVE_2 - baseline) %>%
-  select(run_id, year, MHR_diff) %>%
-  group_by(year) %>%
-  summarise(MHR_diff = mean(MHR_diff))
-
-ggplot(data = plot_data_2, aes(x = year, y = MHR_diff)) +
-  geom_point() +
-  geom_line()
+```{r}
 

### 2024-06-14 minos/outcomes/ChildPovReduction_Combined.Rmd
Improvements to plotting scripts and some additional plots

--- 2024-06-11 minos/outcomes/ChildPovReduction_Combined.Rmd
@@
 workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
 knitr::opts_knit$set(root.dir = workingDir)
@@
 }
+
+SF12_change_ind_trajectories <- function(summary_group, scen.list) {
+
+  tit <- ' '
+  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
+  if (summary_group == 'families') { tit <- 'Families' }
+  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+
+  plot_data <- data %>%
+    select(run_id, SF_12, mean_cost, year, scen) %>%
+    pivot_wider(names_from = scen,
+                values_from = c(SF_12, mean_cost),
+                names_sep = '.') %>%
+    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
+    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
+    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"), 
+                 names_to = c(".value", "scen"), 
+                 names_sep = "\\.") %>%
+    filter(scen != 'baseline')
+
+  plot_data_confint <- plot_data %>%
+    group_by(year) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(diff_SF_12),
+              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
+              lower = mean_SF12_change - margin,
+              upper = mean_SF12_change + margin)
+
+  p1 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(linetype = 'dashed') +
+    geom_point() +
+    geom_line(data = plot_data, aes(x = year, y = diff_SF_12, group = run_id), alpha = 0.2) +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = tit) +
+    xlab('Year') +
+    ylab('Change in SF-12')
+
+  print(p1)
+}
+
 ```
@@
 
+```{r "mental_illness_risk_plots", include=FALSE}
+mental_illness_risk_counts <- function(summary_group, scen.list) {
+
+  tit <- ' '
+  if (summary_group == 'men_illness_risk') { tit <- 'Whole Population' }
+  if (summary_group == 'men_illness_risk_families') { tit <- 'Families' }
+
+  # scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+  # summary_group <- 'men_illness_risk'
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+
+  plot_data <- data %>%
+    filter(mental_health_risk == 'TRUE') %>%
+    select(-prop, -mental_health_risk) %>%
+    pivot_wider(names_from = scen,
+                values_from = count) %>%
+    rename(intervention = contains(scen.list[[2]])) %>%
+    mutate(MHR_diff = intervention - baseline) %>%
+    select(run_id, year, MHR_diff) %>%
+    group_by(year) %>%
+    summarise(MHR_diff = mean(MHR_diff))
+
+  p1 <- ggplot(data = plot_data, aes(x = year, y = MHR_diff)) +
+    geom_point() +
+    geom_line() +
+    labs(title = "Difference in count of individuals at risk of mental health issues",
+         subtitle = tit) +
+    xlab('Year') +
+    ylab('Count')
+
+  plot_data_2 <- data %>%
+    filter(mental_health_risk == 'TRUE') %>%
+    select(-mental_health_risk, -count) %>%
+    pivot_wider(names_from = scen,
+                values_from = prop) %>%
+    rename(intervention = contains(scen.list[[2]])) %>%
+    mutate(MHR_prop_diff = intervention - baseline) %>%
+    select(run_id, year, MHR_prop_diff) %>%
+    group_by(year) %>%
+    summarise(MHR_prop_diff = mean(MHR_prop_diff) * 100)
+
+  p2 <- ggplot(data = plot_data_2, aes(x = year, y = MHR_prop_diff)) +
+    geom_point() +
+    geom_line() +
+    labs(title = "Difference in proportion of individuals at risk of mental health issues",
+         subtitle = tit) +
+    xlab('Year') +
+    ylab('Percentage')
+
+  print(p1)
+  print(p2)
+}
+```
+
 ```{r "Data", include=FALSE}
@@
 SF12_change_simple(summary_group = 'whole_pop',
+                   scen.list = scen.list.rel)
+
+SF12_change_ind_trajectories(summary_group = 'whole_pop',
+                             scen.list <- scen.list.rel)
+
+mental_illness_risk_counts(summary_group = 'men_illness_risk',
                            scen.list = scen.list.rel)
@@
 SF12_change_simple(summary_group = 'families',
+                       scen.list = scen.list.rel)
+
+SF12_change_ind_trajectories(summary_group = 'families',
+                             scen.list <- scen.list.rel)
+
+mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
                            scen.list = scen.list.rel)
@@
                        scen.list = scen.list.abs)
+
+SF12_change_ind_trajectories(summary_group = 'whole_pop',
+                             scen.list <- scen.list.abs)
+
+mental_illness_risk_counts(summary_group = 'men_illness_risk',
+                           scen.list = scen.list.abs)
 ```
@@
 SF12_change_simple(summary_group = 'families',
+                       scen.list = scen.list.abs)
+
+SF12_change_ind_trajectories(summary_group = 'families',
+                             scen.list <- scen.list.abs)
+
+mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
                            scen.list = scen.list.abs)

### 2024-06-14 minos/outcomes/ChildPovReduction_plots.Rmd
Improvements to plotting scripts and some additional plots

@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old10/"
 knitr::opts_knit$set(root.dir = workingDir)
@@
 mental_illness_risk_counts <- function(summary_group, scen.list) {
+
   tit <- ' '
@@
 
-  # plot_data <- data %>%
-  #   group_by(scen, year, mental_health_risk) %>%
-  #   summarise(count = mean(count)) %>%
-  #   filter(mental_health_risk == 'TRUE')
-  # 
-  # ggplot(plot_data, aes(x = year, y = count, group = scen, color = scen)) +
-  #   geom_point() +
-  #   geom_line()
-
-  plot_data_2 <- data %>%
+  plot_data <- data %>%
     filter(mental_health_risk == 'TRUE') %>%
@@
                 values_from = count) %>%
-    mutate(MHR_diff = ChildPovertyReductionRELATIVE_2 - baseline) %>%
+    rename(intervention = contains(scen.list[[2]])) %>%
+    mutate(MHR_diff = intervention - baseline) %>%
     select(run_id, year, MHR_diff) %>%
@@
 
-  p1 <- ggplot(data = plot_data_2, aes(x = year, y = MHR_diff)) +
+  p1 <- ggplot(data = plot_data, aes(x = year, y = MHR_diff)) +
     geom_point() +
-    geom_line()
+    geom_line() +
+    labs(title = "Difference in count of individuals at risk of mental health issues",
+         subtitle = tit) +
+    xlab('Year') +
+    ylab('Count')
+
+  plot_data_2 <- data %>%
+    filter(mental_health_risk == 'TRUE') %>%
+    select(-mental_health_risk, -count) %>%
+    pivot_wider(names_from = scen,
+                values_from = prop) %>%
+    rename(intervention = contains(scen.list[[2]])) %>%
+    mutate(MHR_prop_diff = intervention - baseline) %>%
+    select(run_id, year, MHR_prop_diff) %>%
+    group_by(year) %>%
+    summarise(MHR_prop_diff = mean(MHR_prop_diff))
+
+  p2 <- ggplot(data = plot_data_2, aes(x = year, y = MHR_prop_diff)) +
+    geom_point() +
+    geom_line() +
+    labs(title = "Difference in proportion of individuals at risk of mental health issues",
+         subtitle = tit) +
+    xlab('Year') +
+    ylab('Proportion')
 
   print(p1)
+  print(p2)
 }
@@
 
-## MENTAL HEALTH THRESHOLD
+## NEW CONFINTS
 
 ```{r}
+
+summary_group <- 'whole_pop'
+scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+
+data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))
 

### 2024-06-17 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Small changes to some plotting script

@@
 ```{r, include=FALSE}
-#out.path <- here::here('output', 'default_config/')
-out.path <- here::here('output', 'scotland_scaled/')
+out.path <- here::here('output', 'default_config/')
+#out.path <- here::here('output', 'scotland_scaled/')
 base.dat <- read_singular_local_out(out.path, 
@@
 
+# BOTTOM
+
 ```{r}

### 2024-06-17 minos/outcomes/child_poverty_reduction_vis.Rmd
Small changes to some plotting script

--- 2024-06-06 minos/outcomes/child_poverty_reduction_vis.Rmd
@@
                                    drop.zero.weight = TRUE)
+# int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionSUSTAIN',
+#                                    drop.dead = TRUE,
+#                                    drop.zero.weight = TRUE)
 int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
@@
 
-int3.abs <- int3.abs #%>%
+#int3.abs <- int3.abs #%>%
   #filter(age < 91)

### 2024-06-17 minos/outcomes/ChildPovReduction_Combined.Rmd
Added true treated population plots using new together summaries

@@
 
+```{r "treated_population", include=FALSE}
+SF12_change_treated <- function(scen) {
+
+  summary_group <- 'treated'
+  scen <- paste0(scen, '_together')
+  #scen <- c('ChildPovertyReductionRELATIVE_2_together')
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen))
+
+  plot_data <- data %>%
+    select(run_id, SF_12, hh_income, year, scenario) %>%
+    pivot_wider(names_from = scenario,
+                values_from = c(SF_12, hh_income),
+                names_sep = '.') %>%
+    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline),
+           across(starts_with("hh_income"), ~ . - hh_income.baseline)) %>%
+    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
+    rename_with(~ paste0("diff_", .), starts_with("hh_income")) %>%
+    pivot_longer(cols = starts_with("diff"),
+                 names_to = c(".value", "scenario"),
+                 names_sep = "\\.") %>%
+    filter(scenario != 'baseline')
+
+  plot_data_confint <- plot_data %>%
+      group_by(year) %>%
+      summarise(n = n(),
+                mean_SF12_change = mean(diff_SF_12),
+                margin_SF12 = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
+                lower_SF12 = mean_SF12_change - margin_SF12,
+                upper_SF12 = mean_SF12_change + margin_SF12,
+                mean_hh_income_change = mean(diff_hh_income),
+                margin_hh_income = qt(0.975, df = n - 1) * (sd(diff_hh_income) / sqrt(n)),
+                lower_hh_income = mean_hh_income_change - margin_hh_income,
+                upper_hh_income = mean_hh_income_change + margin_hh_income,)
+
+  # p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
+  #     geom_hline(yintercept = 0, linetype = 'dashed') +
+  #     geom_vline(xintercept = 2030, linetype = 'dotted') +
+  #     geom_smooth() +
+  #     labs(title = 'Treatment on the Treated',
+  #          subtitle = 'SF_12') +
+  #     xlab('Year') +
+  #     ylab('Change in mean SF-12')
+
+  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
+      geom_ribbon(aes(ymin = lower_SF12, ymax = upper_SF12), linetype = 'dotted', alpha = 0.3) +
+      geom_line(linetype = 'dashed') +
+      geom_point() +
+      geom_hline(yintercept = 0, linetype = 'dashed') +
+      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+      labs(title = 'Treatment on the Treated',
+           subtitle = 'SF_12') +
+      xlab('Year') +
+      ylab('Change in mean SF-12')
+
+  # p3 <- ggplot(plot_data, aes(x = year, y = diff_hh_income)) +
+  #     geom_hline(yintercept = 0, linetype = 'dashed') +
+  #     geom_vline(xintercept = 2030, linetype = 'dotted') +
+  #     geom_smooth() +
+  #     labs(title = 'Treatment on the Treated',
+  #          subtitle = 'Household Income') +
+  #     xlab('Year') +
+  #     ylab('Change in mean hh_income')
+
+  p4 <- ggplot(plot_data_confint, aes(x = year, y = mean_hh_income_change)) +
+      geom_ribbon(aes(ymin = lower_hh_income, ymax = upper_hh_income), linetype = 'dotted', alpha = 0.3) +
+      geom_line(linetype = 'dashed') +
+      geom_point() +
+      geom_hline(yintercept = 0, linetype = 'dashed') +
+      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+      labs(title = 'Treatment on the Treated',
+           subtitle = 'Household Income') +
+      xlab('Year') +
+      ylab('Change in mean hh_income')
+
+  #print(p1)
+  print(p2)
+  #print(p3)
+  print(p4)
+}
+```
+
 ```{r "Data", include=FALSE}
@@
 ```
+
+# MCS Change to QALY Example
+
+We use an equation derived from [this paper by Lawrence and Fleishman]() to calculate QALYs from SF-12 MCS and PCS.
 
@@
                    scen.list = scen.list.rel)
+
+SF12_change_treated(scen = 'ChildPovertyReductionRELATIVE_2')
 ```
@@
                    scen.list = scen.list.abs)
+
+SF12_change_treated(scen = 'ChildPovertyReductionABSOLUTE')
 ```

### 2024-06-17 minos/outcomes/ChildPovReduction_plots.Rmd
Added true treated population plots using new together summaries

@@
 
+## NEW TREATED PLOTS
+
 ```{r}
 
+SF12_change_treated <- function(scen) {
+
+  summary_group <- 'treated'
+  scen <- paste0(scen, '_together')
+  #scen <- c('ChildPovertyReductionRELATIVE_2_together')
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen))
+
+  plot_data <- data %>%
+    select(run_id, SF_12, hh_income, year, scenario) %>%
+    pivot_wider(names_from = scenario,
+                values_from = c(SF_12, hh_income),
+                names_sep = '.') %>%
+    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline),
+           across(starts_with("hh_income"), ~ . - hh_income.baseline)) %>%
+    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
+    rename_with(~ paste0("diff_", .), starts_with("hh_income")) %>%
+    pivot_longer(cols = starts_with("diff"),
+                 names_to = c(".value", "scenario"),
+                 names_sep = "\\.") %>%
+    filter(scenario != 'baseline')
+
+  plot_data_confint <- plot_data %>%
+      group_by(year) %>%
+      summarise(n = n(),
+                mean_SF12_change = mean(diff_SF_12),
+                margin_SF12 = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
+                lower_SF12 = mean_SF12_change - margin_SF12,
+                upper_SF12 = mean_SF12_change + margin_SF12,
+                mean_hh_income_change = mean(diff_hh_income),
+                margin_hh_income = qt(0.975, df = n - 1) * (sd(diff_hh_income) / sqrt(n)),
+                lower_hh_income = mean_hh_income_change - margin_hh_income,
+                upper_hh_income = mean_hh_income_change + margin_hh_income,)
+
+  # p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
+  #     geom_hline(yintercept = 0, linetype = 'dashed') +
+  #     geom_vline(xintercept = 2030, linetype = 'dotted') +
+  #     geom_smooth() +
+  #     labs(title = 'Treatment on the Treated',
+  #          subtitle = 'SF_12') +
+  #     xlab('Year') +
+  #     ylab('Change in mean SF-12')
+
+  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
+      geom_ribbon(aes(ymin = lower_SF12, ymax = upper_SF12), linetype = 'dotted', alpha = 0.3) +
+      geom_line(linetype = 'dashed') +
+      geom_point() +
+      geom_hline(yintercept = 0, linetype = 'dashed') +
+      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+      labs(title = 'Treatment on the Treated',
+           subtitle = 'Household Income') +
+      xlab('Year') +
+      ylab('Change in mean SF-12')
+
+  # p3 <- ggplot(plot_data, aes(x = year, y = diff_hh_income)) +
+  #     geom_hline(yintercept = 0, linetype = 'dashed') +
+  #     geom_vline(xintercept = 2030, linetype = 'dotted') +
+  #     geom_smooth() +
+  #     labs(title = 'Treatment on the Treated',
+  #          subtitle = 'Household Income') +
+  #     xlab('Year') +
+  #     ylab('Change in mean hh_income')
+
+  p4 <- ggplot(plot_data_confint, aes(x = year, y = mean_hh_income_change)) +
+      geom_ribbon(aes(ymin = lower_hh_income, ymax = upper_hh_income), linetype = 'dotted', alpha = 0.3) +
+      geom_line(linetype = 'dashed') +
+      geom_point() +
+      geom_hline(yintercept = 0, linetype = 'dashed') +
+      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+      labs(title = 'Treatment on the Treated',
+           subtitle = 'Household Income') +
+      xlab('Year') +
+      ylab('Change in mean hh_income')
+
+  #print(p1)
+  print(p2)
+  #print(p3)
+  print(p4)
+}
 ```

### 2024-06-18 minos/outcomes/ChildPovReduction_Combined.Rmd
More plots and improvements in ChildPovertyReduction plotting scripts;

@@
 
+```{r "synthpop_uncertainty_plot", include=FALSE}
+synthpop_uncertainty <- function(summary_group, scen, var) {
+  # summary_group <- 'whole_pop'
+  # scen.list <- 'baseline'  # , 'ChildPovertyReductionRELATIVE_2'
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+
+  #data$pop_sample <- mutate(data, pop_sample = ceiling(run_id / 10))
+
+  data <- data %>%
+    select(run_id, .data[[var]], mean_cost, year, scen) %>%
+    mutate(pop_sample = ceiling(run_id / 10))
+
+  plot_data_local <- data %>%
+    group_by(pop_sample, year) %>%
+    summarise(var_mean = mean(.data[[var]]))
+
+  plot_data_global <- data %>%
+    group_by(year) %>%
+    summarise(global_var_mean = mean(.data[[var]]))
+
+  p1 <- ggplot(plot_data_local, aes(x = year, y = var_mean)) +
+    geom_line(aes(group = pop_sample), alpha = 0.4) +
+    geom_line(data = plot_data_global, aes(x = year, y = global_var_mean), color = 'red') +
+    labs(title = paste0(var, ' uncertainty in Synthetic Population Sample'),
+         subtitle = 'Global mean (red) vs local means (grey)') +
+    xlab('Year') +
+    ylab(paste0('Mean ', var))
+
+  print(p1)
+}
+```
+
 ```{r "Data", include=FALSE}
@@
 We use an equation derived from [this paper by Lawrence and Fleishman]() to calculate QALYs from SF-12 MCS and PCS.
+
+# SAMPLE UNCERTAINTY
+
+When running MINOS with a synthetic population, due to the size of the synthetic populations and the demands of the model, we have to take a reduced sample as our starting population.
+For the Scotland synthetic runs we take a 10% sample, which reduces the population size from roughly 5.5m to 550,000.
+
+We therefore have to also account for the uncertainty in model outputs that comes from this reduced sample. As a somewhat temporary fix for this, we have done the following:
+
+- Generate 10 different 10% samples from our synthetic population
+  - Generate a replenishing population from each of these samples
+- Use each distinct 10% sample for 10 runs each, totalling 100 runs
+- Plot the local mean from each 10 run block, and the global mean from all 100 runs
+
+```{r}
+synthpop_uncertainty(summary_group = 'whole_pop',
+                     scen = 'baseline',
+                     var = 'hh_income')
+
+synthpop_uncertainty(summary_group = 'whole_pop',
+                     scen = 'baseline',
+                     var = 'SF_12')
+```
 

### 2024-06-18 minos/outcomes/ChildPovReduction_plots.Rmd
More plots and improvements in ChildPovertyReduction plotting scripts;

--- 2024-06-14 minos/outcomes/ChildPovReduction_plots.Rmd
@@
 
+```{r "synthpop_uncertainty_plot", include=FALSE}
+synthpop_uncertainty <- function(summary_group, scen, var) {
+  # summary_group <- 'whole_pop'
+  # scen.list <- 'baseline'  # , 'ChildPovertyReductionRELATIVE_2'
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+
+  #data$pop_sample <- mutate(data, pop_sample = ceiling(run_id / 10))
+
+  data <- data %>%
+    select(run_id, .data[[var]], mean_cost, year, scen) %>%
+    mutate(pop_sample = ceiling(run_id / 10))
+
+  plot_data_local <- data %>%
+    group_by(pop_sample, year) %>%
+    summarise(var_mean = mean(.data[[var]]))
+
+  plot_data_global <- data %>%
+    group_by(year) %>%
+    summarise(global_var_mean = mean(.data[[var]]))
+
+  p1 <- ggplot(plot_data_local, aes(x = year, y = var_mean)) +
+    geom_line(aes(group = pop_sample), alpha = 0.4) +
+    geom_line(data = plot_data_global, aes(x = year, y = global_var_mean), color = 'red') +
+    labs(title = paste0(var, ' uncertainty in Synthetic Population Sample'),
+         subtitle = 'Global mean (red) vs local means (grey)') +
+    xlab('Year') +
+    ylab(paste0('Mean ', var))
+
+  print(p1)
+}
+```
+
 ```{r}
@@
 
+## POPULATION SAMPLE TESTING
+
+```{r}
+
+synthpop_uncertainty <- function(summary_group, scen, var) {
+  # summary_group <- 'whole_pop'
+  # scen.list <- 'baseline'  # , 'ChildPovertyReductionRELATIVE_2'
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+
+  #data$pop_sample <- mutate(data, pop_sample = ceiling(run_id / 10))
+
+  data <- data %>%
+    select(run_id, .data[[var]], mean_cost, year, scen) %>%
+    mutate(pop_sample = ceiling(run_id / 10))
+
+  plot_data_local <- data %>%
+    group_by(pop_sample, year) %>%
+    summarise(var_mean = mean(.data[[var]]))
+
+  plot_data_global <- data %>%
+    group_by(year) %>%
+    summarise(global_var_mean = mean(.data[[var]]))
+
+  p1 <- ggplot(plot_data_local, aes(x = year, y = var_mean)) +
+    geom_line(aes(group = pop_sample), alpha = 0.4) +
+    geom_line(data = plot_data_global, aes(x = year, y = global_var_mean), color = 'red') +
+    labs(title = paste0(var, ' uncertainty in Synthetic Population Sample'),
+         subtitle = 'Global mean (red) vs local means (grey)') +
+    xlab('Year') +
+    ylab(paste0('Mean ', var))
+
+  print(p1)
+}
+
+```
+
 ## NEW CONFINTS

### 2024-06-18 minos/outcomes/ChildPovReduction_Combined.Rmd
Small additions to plotting scripts

@@
 
-We use an equation derived from [this paper by Lawrence and Fleishman]() to calculate QALYs from SF-12 MCS and PCS.
+We use an equation derived from table 4 (below) in [this paper by Lawrence and Fleishman](https://pubmed.ncbi.nlm.nih.gov/15090102/) to calculate QALYs from SF-12 MCS and PCS.
+
+#![L&F Table 4](L&F_table4.png)
+
+```{r}
+# formula to find the utility score from mean MCS and PCS scores of a population
+utility_score <- function(pcs, mcs) {
+  utility_score <- 
+    1.6984 + 
+    (pcs * 0.07927) +
+    (mcs * 0.02859) +
+    ((pcs * mcs) * -0.000126) +
+    ((pcs * pcs) * -0.00141) +
+    ((mcs * mcs) * -0.00014) +
+    ((pcs * pcs * pcs) * 0.0000107)
+  return(utility_score)
+}
+
+# Calculate utility score for hypothetical baseline (MCS & PCS == 45.0)
+initial_conditions <- utility_score(pcs = 45.0,
+                                    mcs = 45.0)
+# Calculate utility score for 0.1 improvement in MCS (MCS now == 45.1)
+intervention <- utility_score(pcs = 45.0,
+                              mcs = 45.1)
+
+print("Utility score for hypothetical baseline (assuming mean MCS and PCS both equal 45.0):")
+print(initial_conditions)
+print("Utility score for population given a 0.1 mean improvement in MCS:")
+print(intervention)
+
+print("Gain in utility score per person:")
+gain <- intervention - initial_conditions
+print(gain)
+
+print("Gain in utiliy for the total Scotland population (assuming 5.5m). This is equivalent to QALYs gained:")
+print(gain * 5500000)
+```
 

### 2024-06-18 minos/outcomes/ChildPovReduction_Combined.Rmd
Added the income quintile plots based on the together summaries

@@
     code_folding: hide
-  pdf_document:
-    toc: true
 ---
@@
 }
+
+SF12_change_income_quint2 <- function(summary_group, scen) {
+
+  summary_group <- paste0(summary_group, '_income_quint_together')
+  scen <- paste0(scen, '_together')
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen))
+
+  plot_data <- data %>%
+    select(run_id, SF_12, income_quintile, year, scenario) %>%
+    pivot_wider(names_from = scenario,
+                values_from = SF_12,
+                names_sep = '.',
+                values_fn = list(SF_12 = function(x) x[1])) %>%
+    mutate(diff_SF12 = intervention - baseline) %>%
+    pivot_longer(cols = starts_with("diff"),
+                 names_to = c(".value", "scenario"),
+                 names_sep = "\\.") %>%
+    select(run_id, income_quintile, year, diff_SF12)
+
+  plot_data_confint <- plot_data %>%
+      group_by(year, income_quintile) %>%
+      summarise(n = n(),
+                mean_SF12_change = mean(diff_SF12),
+                margin_SF12 = qt(0.975, df = n - 1) * (sd(diff_SF12) / sqrt(n)),
+                lower_SF12 = mean_SF12_change - margin_SF12,
+                upper_SF12 = mean_SF12_change + margin_SF12)
+
+  plot_data_confint$income_quintile <- factor(plot_data_confint$income_quintile)
+
+  # p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
+  #     geom_hline(yintercept = 0, linetype = 'dashed') +
+  #     geom_vline(xintercept = 2030, linetype = 'dotted') +
+  #     geom_smooth() +
+  #     labs(title = 'Treatment on the Treated',
+  #          subtitle = 'SF_12') +
+  #     xlab('Year') +
+  #     ylab('Change in mean SF-12')
+
+  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, color = income_quintile, fill = income_quintile)) +
+      geom_ribbon(aes(ymin = lower_SF12, ymax = upper_SF12), linetype = 'dotted', alpha = 0.3) +
+      geom_line(linetype = 'dashed') +
+      geom_point() +
+      geom_hline(yintercept = 0, linetype = 'dashed') +
+      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+      labs(title = 'Treatment on the Treated',
+           subtitle = 'SF_12') +
+      xlab('Year') +
+      ylab('Change in mean SF-12')
+
+  #print(p1)
+  print(p2)
+}
 ```
@@
                 names_sep = '.') %>%
+    unnest(cols = c(starts_with("SF_12"), starts_with("hh_income"))) %>%
     mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline),
@@
 
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+  data <- do.call(rbind, generate_df_list(summary_group, scen))
 
@@
 
-We use an equation derived from table 4 (below) in [this paper by Lawrence and Fleishman](https://pubmed.ncbi.nlm.nih.gov/15090102/) to calculate QALYs from SF-12 MCS and PCS.
+We use an equation derived from table 4 (below) in [this paper by Lawrence and Fleishman](https://pubmed.ncbi.nlm.nih.gov/15090102/) to calculate QALYs from SF-12 Mental Component Score (MCS) and Physical Component Score (PCS).
 
@@
 ```
+
+This rough calculation shows that a 0.1 absolute change in mean SF_12 across the Scottish population would equal over 5000 additional QALYs in a single year.
+These improvements can also accumulate over time.
+If we were able to achieve a 0.1 improvement in mean MCS for Scotland in year 1, and maintain this 0.1 improvement for 10 years, the resulting improvement in QALYs would be 56,000+.
+
+NOTE: This calculation assumes that PCS is unchanged when MCS can vary. This is not realistic, but the calculation is still useful to provide context for the results to follow.
 
@@
 ```{r}
-SF12_change_income_quint(summary_group = 'whole_pop',
-                                    scen.list = scen.list.rel)
+# SF12_change_income_quint(summary_group = 'whole_pop',
+#                                     scen.list = scen.list.rel)
+SF12_change_income_quint2(summary_group = 'whole_pop',
+                                    scen = 'ChildPovertyReductionRELATIVE_2')
 ```
@@
 ```{r}
-SF12_change_income_quint(summary_group = 'families',
-                                    scen.list = scen.list.rel)
+# SF12_change_income_quint(summary_group = 'families',
+#                                     scen.list = scen.list.rel)
+SF12_change_income_quint2(summary_group = 'families',
+                                    scen = 'ChildPovertyReductionRELATIVE_2')
 ```
@@
 ```{r}
-SF12_change_simple(summary_group = 'treated_relative',
-                   scen.list = scen.list.rel)
+# SF12_change_simple(summary_group = 'treated_relative',
+#                    scen.list = scen.list.rel)
 
@@
 ```{r}
-SF12_change_income_quint(summary_group = 'whole_pop',
-                                    scen.list = scen.list.abs)
+# SF12_change_income_quint(summary_group = 'whole_pop',
+#                                     scen.list = scen.list.abs)
+SF12_change_income_quint2(summary_group = 'whole_pop',
+                                    scen = 'ChildPovertyReductionABSOLUTE')
 ```
@@
 ```{r}
-SF12_change_income_quint(summary_group = 'families',
-                                    scen.list = scen.list.abs)
+# SF12_change_income_quint(summary_group = 'families',
+#                                     scen.list = scen.list.abs)
+SF12_change_income_quint2(summary_group = 'families',
+                                    scen = 'ChildPovertyReductionABSOLUTE')
 ```
@@
 ```{r}
-SF12_change_simple(summary_group = 'treated_absolute',
-                   scen.list = scen.list.abs)
+# SF12_change_simple(summary_group = 'treated_absolute',
+#                    scen.list = scen.list.abs)
 

### 2024-06-18 minos/outcomes/child_poverty_reduction_vis.Rmd

--- 2024-06-06 minos/outcomes/child_poverty_reduction_vis.Rmd
@@
 #                                    drop.zero.weight = TRUE)
-int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
+# int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
+#                                    drop.dead = TRUE,
+#                                    drop.zero.weight = TRUE)
+int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReduction',
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)
-int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
-                                   drop.dead = TRUE,
-                                   drop.zero.weight = TRUE)
+# int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
+#                                    drop.dead = TRUE,
+#                                    drop.zero.weight = TRUE)
 

### 2024-06-19 minos/outcomes/ChildPovReduction_Combined.Rmd
Changed the inequality plots to use income_quint summaries from the together batch

@@
 
-  data <- replace_na(data, list(num_priority_groups=0))
+  #data <- replace_na(data, list(num_priority_groups=0))
 
@@
 ```{r "inequality_plots", include=FALSE}
-inequality_plots <- function(summary_group, scen.list) {
+# inequality_plots <- function(summary_group, scen.list) {
+#   
+#   tit <- ' '
+#   if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
+#   if (summary_group == 'families') { tit <- 'Families' }
+#   
+#   summary_group <- paste0(summary_group, '_income_quint')
+#   
+#   data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+#   
+#   data$income_quintile <- factor(data$income_quintile)
+#   
+#   # Combine the data
+#   data_combined <- data %>%
+#     mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))
+#   
+#   p1 <- ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
+#     geom_smooth(alpha = 0.7) +
+#     scale_color_manual(name = "Income Quintile", 
+#                        values = c("red", "blue", "green", "orange", "purple")) +
+#     scale_linetype_manual(name = "Scenario", 
+#                           values = c("Baseline" = "solid", "Intervention" = "dotted")) +
+#     labs(title = "SF_12 Scores by Income Quintile",
+#          subtitle = tit,
+#          x = "Year",
+#          y = "Mean SF_12 MCS") +
+#     theme_minimal() +
+#     theme(legend.position = "right",
+#           legend.title = element_text(size = 12),
+#           legend.text = element_text(size = 10))
+#   
+#   # Aggregate data
+#   agg_data <- data %>%
+#     mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention')) %>%
+#     group_by(year, income_quintile, scenario) %>%
+#     summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
+#     spread(scenario, mean_SF_12) %>%
+#     mutate(difference = Intervention - Baseline)
+#   
+#   p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
+#     geom_bar(stat = "identity", position = "dodge") +
+#     scale_fill_manual(name = "Income Quintile", 
+#                       values = c("red", "blue", "green", "orange", "purple")) +
+#     labs(title = "Average Difference in SF_12 Scores by Income Quintile",
+#          subtitle = tit,
+#          x = "Year",
+#          y = "Difference in SF_12 Score") +
+#     theme_minimal() +
+#     theme(legend.position = "right",
+#           legend.title = element_text(size = 12),
+#           legend.text = element_text(size = 10))
+#   
+#   print(p1)
+#   print(p2)
+# }
+
+inequality_plots <- function(summary_group, scen) {
 
@@
 
-  summary_group <- paste0(summary_group, '_income_quint')
+  summary_group <- paste0(summary_group, '_income_quint_together')
+  scen <- paste0(scen, '_together')
 
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+  data <- do.call(rbind, generate_df_list(summary_group, scen))
 
@@
   data_combined <- data %>%
-    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))
+    mutate(scenario = ifelse(scenario == 'baseline', 'Baseline', 'Intervention'))
 
@@
   agg_data <- data %>%
-    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention')) %>%
+    mutate(scenario = ifelse(scenario == 'baseline', 'Baseline', 'Intervention')) %>%
     group_by(year, income_quintile, scenario) %>%
@@
 inequality_plots(summary_group = 'whole_pop',
-                 scen.list = scen.list.rel)
+                 scen = 'ChildPovertyReductionRELATIVE_2')
 ```
@@
 inequality_plots(summary_group = 'families',
-                 scen.list = scen.list.rel)
+                 scen = 'ChildPovertyReductionRELATIVE_2')
 ```
@@
 inequality_plots(summary_group = 'whole_pop',
-                 scen.list = scen.list.abs)
+                 scen = 'ChildPovertyReductionABSOLUTE')
 ```
@@
 inequality_plots(summary_group = 'families',
-                 scen.list = scen.list.abs)
+                 scen = 'ChildPovertyReductionABSOLUTE')
 ```

### 2024-06-19 minos/validation/handovers.Rmd
Fixing up some plots in handovers that should have been weighted calculations

@@
   group_by(time) %>%
-  summarise(max_age = max(age))
+  summarise(max_age = max(age)) %>%
+  mutate(scen = 'final_US')
 
@@
   group_by(time) %>%
-  summarise(max_age = max(age))
-
-handover_lineplots(raw.maxAge, base.maxAge, 'max_age')
+  summarise(max_age = max(age)) %>%
+  mutate(scen = 'baseline')
+
+combined <- rbind(raw.maxAge, base.maxAge)
+
+#handover_lineplots(raw.maxAge, base.maxAge, 'max_age')
+ggplot(combined, aes(x = time, y = max_age, group = scen, colour = scen)) +
+  geom_line() +
+  geom_vline(xintercept = start.year, linetype = 'dashed') +
+  labs(title = 'Max year of age') +
+  xlab('Year') +
+  ylab('Age')
 
@@
   group_by(time) %>%
-  summarise(n = n())
+  summarise(n = n()) %>%
+  mutate(scen = 'final_US')
 
@@
   group_by(time) %>%
-  summarise(n = n())
+  summarise(n = n()) %>%
+  mutate(scen = 'baseline')
 
 #handover_boxplots(raw.alive, base.alive, 'n')
-handover_lineplots(raw.alive, base.alive, "n")
+#handover_lineplots(raw.alive, base.alive, "n")
+
+combined <- rbind(raw.alive, base.alive)
+
+ggplot(combined, aes(x = time, y = n, group = scen, color = scen, fill = scen)) +
+  geom_line() +
+  geom_vline(xintercept = start.year, linetype = 'dashed') +
+  labs(title = 'Total Count in Sample') +
+  xlab('Year') +
+  ylab('Count')
 
@@
 raw.hh_unique <- raw.dat %>%
-  select(hidp, time, nkids) %>%
-  distinct()
+  select(hidp, time, nkids, weight) %>%
+  distinct(hidp, time, nkids, .keep_all = TRUE) %>%
+  mutate(scen = 'final_US')
 
 base.hh_unique <- base.dat %>%
-  select(hidp, time, nkids) %>%
-  distinct()
+  select(hidp, time, nkids, weight) %>%
+  distinct(hidp, time, nkids, .keep_all = TRUE) %>%
+  mutate(scen = 'baseline')
 
@@
 handover_lineplots(raw.hh_unique, base.hh_unique, 'nkids')
+
 ```

### 2024-06-25 minos/outcomes/ChildPovReduction_Combined.Rmd
Number of mostly unrelated changes. Most important is a switch to predicting difference variables for hh_income and SF_12 as an attempt to remove scaling but still maintain variance. Other changes include updates to config files to make them all the same, and some changes to data gen pipeline such as forward filling vars like neighbourhood_safety and nutrition_quality to ensure they will be present in starting popualtions

@@
 
+  tit <- ' '
+  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
+  if (summary_group == 'families') { tit <- 'Families' }
+
   summary_group <- paste0(summary_group, '_income_quint_together')
@@
       geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-      labs(title = 'Treatment on the Treated',
-           subtitle = 'SF_12') +
+      labs(title = tit, 
+           subtitle = 'Income Quintile') +
       xlab('Year') +

### 2024-06-25 minos/validation/handovers.Rmd
Number of mostly unrelated changes. Most important is a switch to predicting difference variables for hh_income and SF_12 as an attempt to remove scaling but still maintain variance. Other changes include updates to config files to make them all the same, and some changes to data gen pipeline such as forward filling vars like neighbourhood_safety and nutrition_quality to ensure they will be present in starting popualtions

@@
 raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+#raw.files <- list.files(here::here('data', 'scaled_scotland_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 
-```
-
-```{r}
-
-```
+combined.nkids
+
+```
+
+```{r}
+
+```

### 2024-06-25 minos/modules/r_utils.py

@@ -497,7 +497,7 @@ def predict_next_timestep_yj_gamma_glmm(model, rpy2_modules, current, dependent,
     return pd.DataFrame(prediction_output, columns=[dependent])
 
 
-def predict_next_rf(model, rpy2_modules, current, dependent, seed):
+def predict_next_rf(model, rpy2_modules, current, dependent, seed, noise=0):
 
     # import R packages
     base = rpy2_modules['base']
@@ -514,6 +514,12 @@ def predict_next_rf(model, rpy2_modules, current, dependent, seed):
 
     # R predict method returns a Vector of predicted values, so need to be bound to original df and converter to Pandas
     prediction = stats.predict(model, newdata=currentRDF)
+
+    # Add some noise if noise > 0
+    if noise != 0:
+        VGAM = rpy2_modules["VGAM"]
+        prediction = prediction.ro + VGAM.rlaplace(current.shape[0], 0, noise)  # add gaussian noise.
+
     newRPopDF = base.cbind(currentRDF, predicted=prediction)
     # Convert back to pandas
     with localconverter(ro.default_converter + pandas2ri.converter):

### 2024-06-26 minos/outcomes/ChildPovReduction_plots.Rmd

--- 2024-06-14 minos/outcomes/ChildPovReduction_plots.Rmd
@@
 workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old10/"
 knitr::opts_knit$set(root.dir = workingDir)
@@
   if (summary_group == 'families') { tit <- 'Families' }
-  if (summary_group == 'treated_relative') { tit <- 'Treated' }
-  if (summary_group == 'treated_absolute') { tit <- 'Treated' }
-  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
 
@@
   if (summary_group == 'families') { tit <- 'Families' }
-  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
 
@@
   print(p2)
-}
-
-SF12_change_ind_trajectories <- function(summary_group, scen.list) {
-
-  tit <- ' '
-  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
-  if (summary_group == 'families') { tit <- 'Families' }
-  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
-
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
-
-  plot_data <- data %>%
-    select(run_id, SF_12, mean_cost, year, scen) %>%
-    pivot_wider(names_from = scen,
-                values_from = c(SF_12, mean_cost),
-                names_sep = '.') %>%
-    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
-    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
-    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"), 
-                 names_to = c(".value", "scen"), 
-                 names_sep = "\\.") %>%
-    filter(scen != 'baseline')
-
-  plot_data_confint <- plot_data %>%
-    group_by(year) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF_12),
-              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  p1 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_line(data = plot_data, aes(x = year, y = diff_SF_12, group = run_id), alpha = 0.2) +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = 'tit') +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  print(p1)
 }
@@
 
-```{r "SF12_change_num_priority_groups", include=FALSE}
-SF12_change_num_priority_groups <- function(scen.list) {
-
-  summary_group <- 'priority_num'
-
-  tit <- 'Number of Priority Subgroups'
-
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))
-
-  data <- replace_na(data, list(num_priority_groups=0))
-
-  plot_data <- data %>%
-    select(run_id, num_priority_groups, SF_12, mean_cost, year, scen) %>%
-    pivot_wider(names_from = scen,
-                values_from = c(SF_12, mean_cost),
-                names_sep = '.') %>%
-    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
-    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
-    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
-                 names_to = c(".value", "scen"),
-                 names_sep = "\\.") %>%
-    filter(scen != 'baseline') %>%
-    select(-scen)
-
-  plot_data$num_priority_groups <- factor(plot_data$num_priority_groups)
-
-  plot_data_confint <- plot_data %>%
-    group_by(year, num_priority_groups) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF_12),
-              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  plot_data_confint2 <- plot_data %>%
-    group_by(year, num_priority_groups) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF_12),
-              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted') +
-    geom_smooth() +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  print(p1)
-  print(p2)
-}
-
-SF12_change_percentage_num_priority_groups <- function(scen.list) {
-
-  summary_group <- 'priority_num'
-
-  tit <- 'Number of Priority Subgroups'
-
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))
-
-  data <- replace_na(data, list(num_priority_groups=0))
-
-  plot_data <- data %>%
-    select(run_id, num_priority_groups, SF_12, mean_cost, year, scen) %>%
-    pivot_wider(names_from = scen,
-                values_from = c(SF_12, mean_cost),
-                names_sep = '.') %>%
-    mutate(across(starts_with("SF_12"), ~ ((. - SF_12.baseline) / SF_12.baseline) * 100)) %>% # Calculate percentage change
-    rename_with(~ paste0("percent_change_", .), starts_with("SF_12")) %>%
-    pivot_longer(cols = starts_with("percent_change") | starts_with("mean_cost"),
-                 names_to = c(".value", "scen"),
-                 names_sep = "\\.") %>%
-    filter(scen != 'baseline') %>%
-    select(-scen)
-
-  plot_data$num_priority_groups <- factor(plot_data$num_priority_groups)
-
-  plot_data_confint <- plot_data %>%
-    group_by(year, num_priority_groups) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(percent_change_SF_12),
-              margin = qt(0.975, df = n - 1) * (sd(percent_change_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  plot_data_confint2 <- plot_data %>%
-    group_by(year, num_priority_groups) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(percent_change_SF_12),
-              margin = qnorm(0.975) * (sd(percent_change_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  p1 <- ggplot(plot_data, aes(x = year, y = percent_change_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted') +
-    geom_smooth() +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Percentage Change in SF-12')
-
-  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Percentage Change in SF-12')
-
-  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Percentage Change in SF-12')
-
-  print(p1)
-  print(p2)
-}
-```
-
-```{r "inequality_plots", include=FALSE}
-inequality_plots <- function(summary_group, scen.list) {
-
-  tit <- ' '
-  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
-  if (summary_group == 'families') { tit <- 'Families' }
-  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
-
-  summary_group <- paste0(summary_group, '_income_quint')
-
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
-
-  data$income_quintile <- factor(data$income_quintile)
-
-  # Combine the data
-  data_combined <- data %>%
-    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))
-
-  p1 <- ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
-    geom_smooth(alpha = 0.7) +
-    scale_color_manual(name = "Income Quintile", 
-                       values = c("red", "blue", "green", "orange", "purple")) +
-    scale_linetype_manual(name = "Scenario", 
-                          values = c("Baseline" = "solid", "Intervention" = "dotted")) +
-    labs(title = "SF_12 Scores by Income Quintile",
-         subtitle = tit,
-         x = "Year",
-         y = "Mean SF_12 MCS") +
-    theme_minimal() +
-    theme(legend.position = "right",
-          legend.title = element_text(size = 12),
-          legend.text = element_text(size = 10))
-
-  # Aggregate data
-  agg_data <- data %>%
-    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention')) %>%
-    group_by(year, income_quintile, scenario) %>%
-    summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
-    spread(scenario, mean_SF_12) %>%
-    mutate(difference = Intervention - Baseline)
-
-  p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
-    geom_bar(stat = "identity", position = "dodge") +
-    scale_fill_manual(name = "Income Quintile", 
-                      values = c("red", "blue", "green", "orange", "purple")) +
-    labs(title = "Average Difference in SF_12 Scores by Income Quintile",
-         subtitle = tit,
-         x = "Year",
-         y = "Difference in SF_12 Score") +
-    theme_minimal() +
-    theme(legend.position = "right",
-          legend.title = element_text(size = 12),
-          legend.text = element_text(size = 10))
-
-  print(p1)
-  print(p2)
-}
-```
-
-```{r "mental_illness_risk", include=FALSE}
-mental_illness_risk_counts <- function(summary_group, scen.list) {
-
-  tit <- ' '
-  if (summary_group == 'men_illness_risk') { tit <- 'Whole Population' }
-  if (summary_group == 'men_illness_risk_families') { tit <- 'Families' }
-
-  # scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
-  # summary_group <- 'men_illness_risk'
-
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
-
-  plot_data <- data %>%
-    filter(mental_health_risk == 'TRUE') %>%
-    select(-prop, -mental_health_risk) %>%
-    pivot_wider(names_from = scen,
-                values_from = count) %>%
-    rename(intervention = contains(scen.list[[2]])) %>%
-    mutate(MHR_diff = intervention - baseline) %>%
-    select(run_id, year, MHR_diff) %>%
-    group_by(year) %>%
-    summarise(MHR_diff = mean(MHR_diff))
-
-  p1 <- ggplot(data = plot_data, aes(x = year, y = MHR_diff)) +
-    geom_point() +
-    geom_line() +
-    labs(title = "Difference in count of individuals at risk of mental health issues",
-         subtitle = tit) +
-    xlab('Year') +
-    ylab('Count')
-
-  plot_data_2 <- data %>%
-    filter(mental_health_risk == 'TRUE') %>%
-    select(-mental_health_risk, -count) %>%
-    pivot_wider(names_from = scen,
-                values_from = prop) %>%
-    rename(intervention = contains(scen.list[[2]])) %>%
-    mutate(MHR_prop_diff = intervention - baseline) %>%
-    select(run_id, year, MHR_prop_diff) %>%
-    group_by(year) %>%
-    summarise(MHR_prop_diff = mean(MHR_prop_diff))
-
-  p2 <- ggplot(data = plot_data_2, aes(x = year, y = MHR_prop_diff)) +
-    geom_point() +
-    geom_line() +
-    labs(title = "Difference in proportion of individuals at risk of mental health issues",
-         subtitle = tit) +
-    xlab('Year') +
-    ylab('Proportion')
-
-  print(p1)
-  print(p2)
-}
-```
-
 ```{r}
-scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
-#scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
-#scen.list.test <- c('baseline', 'ChildPovertyReductionSUSTAIN')
+#scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
 whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
@@
                        scen.list = scen.list.test)
-
-SF12_change_ind_trajectories(summary_group = 'whole_pop',
-                             scen.list = scen.list.test)
-
-inequality_plots(summary_group = 'whole_pop',
-                 scen.list = scen.list.test)
-
-mental_illness_risk_counts(summary_group = 'men_illness_risk',
-                           scen.list = scen.list.test)
 ```
@@
 SF12_change_percentage(summary_group = 'families',
-                       scen.list = scen.list.test)
-
-SF12_change_ind_trajectories(summary_group = 'families',
-                             scen.list = scen.list.test)
-
-inequality_plots(summary_group = 'families',
-                 scen.list = scen.list.test)
-
-mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
-                           scen.list = scen.list.test)
-```
-
-# Treated
-
-```{r}
-SF12_change_simple(summary_group = 'treated_relative',
-                   scen.list = scen.list.test)
-
-SF12_change_percentage(summary_group = 'treated_relative',
                        scen.list = scen.list.test)
@@
 
-## Number of Priority Subgroups
+```{r}
+#SF12_change_income_quint <- function(summary_group, scen.list) {
 
-```{r}
-SF12_change_num_priority_groups(scen.list.test)
-SF12_change_percentage_num_priority_groups(scen.list.test)
-```
-
-# TESTING
-
-```{r}
-
+# summary_group <- 'priority_num'
+# 
+#   tit <- ' '
+#   if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
+#   if (summary_group == 'families') { tit <- 'Families' }
+# 
+#   #summary_group <- paste0(summary_group, '_income_quint')
+# 
+#   data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+# 
+#   plot_data <- data %>%
+#     select(run_id, income_quintile, SF_12, mean_cost, year, scen) %>%
+#     pivot_wider(names_from = scen,
+#                 values_from = c(SF_12, mean_cost),
+#                 names_sep = '.') %>%
+#     mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
+#     rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
+#     pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
+#                  names_to = c(".value", "scen"),
+#                  names_sep = "\\.") %>%
+#     filter(scen != 'baseline') %>%
+#     select(-scen)
+# 
+#   plot_data$income_quintile <- factor(plot_data$income_quintile)
+# 
+#   plot_data_confint <- plot_data %>%
+#     group_by(year, income_quintile) %>%
+#     summarise(n = n(),
+#               mean_SF12_change = mean(diff_SF_12),
+#               margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
+#               lower = mean_SF12_change - margin,
+#               upper = mean_SF12_change + margin)
+# 
+#   plot_data_confint2 <- plot_data %>%
+#     group_by(year, income_quintile) %>%
+#     summarise(n = n(),
+#               mean_SF12_change = mean(diff_SF_12),
+#               margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
+#               lower = mean_SF12_change - margin,
+#               upper = mean_SF12_change + margin)
+# 
+# 
+#   p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
+#     geom_hline(yintercept = 0, linetype = 'dashed') +
+#     geom_vline(xintercept = 2030, linetype = 'dotted') +
+#     geom_smooth() +
+#     labs(title = tit, subtitle = 'Income Quintile') +
+#     xlab('Year') +
+#     ylab('Change in SF-12')
+# 
+#   p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
+#     geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+#     geom_line(linetype = 'dashed') +
+#     geom_point() +
+#     geom_hline(yintercept = 0, linetype = 'dashed') +
+#     geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+#     labs(title = tit, subtitle = 'Income Quintile') +
+#     xlab('Year') +
+#     ylab('Change in SF-12')
+# 
+#   p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
+#     geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+#     geom_line(linetype = 'dashed') +
+#     geom_point() +
+#     geom_hline(yintercept = 0, linetype = 'dashed') +
+#     geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+#     labs(title = tit, subtitle = 'Income Quintile') +
+#     xlab('Year') +
+#     ylab('Change in SF-12')
+# 
+#   print(p1)
+#   print(p2)
+#}
 ```
@@
 
-# TESTING
-
-```{r}
-SF12_change_simple <- function(summary_group, scen.list) {
-
-  tit <- ' '
-  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
-  if (summary_group == 'families') { tit <- 'Families' }
-  if (summary_group == 'treated_relative') { tit <- 'Treated' }
-  if (summary_group == 'treated_absolute') { tit <- 'Treated' }
-  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
-
-  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
-
-  plot_data <- data %>%
-    select(run_id, SF_12, mean_cost, year, scen) %>%
-    pivot_wider(names_from = scen,
-                values_from = c(SF_12, mean_cost),
-                names_sep = '.') %>%
-    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
-    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
-    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"), 
-                 names_to = c(".value", "scen"), 
-                 names_sep = "\\.") %>%
-    filter(scen != 'baseline')
-
-  plot_data_confint <- plot_data %>%
-    group_by(year) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF_12),
-              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  plot_data_confint2 <- plot_data %>%
-    group_by(year) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF_12),
-              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted') +
-    geom_smooth() +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed') +
-    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
-    xlab('Year') +
-    ylab('Change in SF-12')
-
-  print(p1)
-  print(p2)
-  #print(p3)
-}
-```
-
-## NEW CONFINTS
-
-```{r}
-
-summary_group <- 'whole_pop'
-scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
-
-data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))
-
-```
-
 ```{r}

### 2024-06-26 minos/validation/handovers.Rmd

--- 2024-06-12 minos/validation/handovers.Rmd
@@
 # Read raw datafiles in
-#raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
-raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 create.if.not.exists(save.path)
-
-# Need to remove extra data from raw data after start year
-raw.dat <- raw.dat %>%
-  filter(time <= start.year)
 
@@
   geom_line() +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
+  geom_vline(xintercept = 2021, linetype = 'dashed') +
   labs(title = 'Counts by older age group', subtitle = '75 to 110 by 5 year groups') +
@@
   geom_line() +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
   labs(title = 'Households Count')
@@
 
-spaghetti_plot(base.inc, 'hh_income',
-               save = shall.we.save,
-               save.path = save.path)
-
 rm(raw.inc, base.inc, income.spag)
@@
 ```{r}
-# raw.2010 <- raw.dat %>%
-#   filter(time == 2010)
-# 
-# abs.threshold <- weighted.median(x = raw.2010$hh_income, 
-#                                  w = raw.2010$weight, 
-#                                  na.rm = TRUE)
-# abs.threshold <- abs.threshold * 0.6
-# 
-# print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
+raw.2010 <- raw.dat %>%
+  filter(time == 2010)
+
+abs.threshold <- weighted.median(x = raw.2010$hh_income, 
+                                 w = raw.2010$weight, 
+                                 na.rm = TRUE)
+abs.threshold <- abs.threshold * 0.6
+
+print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
 ```

### 2024-06-26 minos/outcomes/ChildPovReduction_Combined.Rmd
Switching SF_12 model back to LMM, and some small adjustments to hh_income_diff model. Also updated some summary targets for a bit of brevity

@@
 scen.list.rel <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+scen.rel <- 'ChildPovertyReductionRELATIVE_2'
 scen.list.abs <- c('baseline', 'ChildPovertyReductionABSOLUTE')
+scen.abs <- 'ChildPovertyReductionABSOLUTE'
 ```
@@
 SF12_change_income_quint2(summary_group = 'whole_pop',
-                                    scen = 'ChildPovertyReductionRELATIVE_2')
+                                    scen = scen.rel)
 ```
@@
 inequality_plots(summary_group = 'whole_pop',
-                 scen = 'ChildPovertyReductionRELATIVE_2')
+                 scen = scen.rel)
 ```
@@
 SF12_change_income_quint2(summary_group = 'families',
-                                    scen = 'ChildPovertyReductionRELATIVE_2')
+                                    scen = scen.rel)
 ```
@@
 inequality_plots(summary_group = 'families',
-                 scen = 'ChildPovertyReductionRELATIVE_2')
+                 scen = scen.rel)
 ```
@@
 
-SF12_change_treated(scen = 'ChildPovertyReductionRELATIVE_2')
+SF12_change_treated(scen = scen.rel)
 ```
@@
 SF12_change_income_quint2(summary_group = 'whole_pop',
-                                    scen = 'ChildPovertyReductionABSOLUTE')
+                                    scen = scen.abs)
 ```
@@
 inequality_plots(summary_group = 'whole_pop',
-                 scen = 'ChildPovertyReductionABSOLUTE')
+                 scen = scen.abs)
 ```
@@
 SF12_change_income_quint2(summary_group = 'families',
-                                    scen = 'ChildPovertyReductionABSOLUTE')
+                                    scen = scen.abs)
 ```
@@
 inequality_plots(summary_group = 'families',
-                 scen = 'ChildPovertyReductionABSOLUTE')
+                 scen = scen.abs)
 ```
@@
 
-SF12_change_treated(scen = 'ChildPovertyReductionABSOLUTE')
+SF12_change_treated(scen = scen.abs)
 ```

### 2024-06-26 minos/outcomes/child_poverty_reduction_vis.Rmd
Switching SF_12 model back to LMM, and some small adjustments to hh_income_diff model. Also updated some summary targets for a bit of brevity

@@
                                     drop.zero.weight = TRUE)
-# int1.rel <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE',
+int1.rel <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE',
+                                   drop.dead = TRUE,
+                                   drop.zero.weight = TRUE)
+int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
+                                   drop.dead = TRUE,
+                                   drop.zero.weight = TRUE)
+# int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReduction',
 #                                    drop.dead = TRUE,
 #                                    drop.zero.weight = TRUE)
-# int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
-#                                    drop.dead = TRUE,
-#                                    drop.zero.weight = TRUE)
-int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReduction',
+int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)
-# int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
-#                                    drop.dead = TRUE,
-#                                    drop.zero.weight = TRUE)
 
@@
 ```{r}
-# base.2021 <- base.dat %>%
-#   filter(time == 2021)
-# 
-# mean.hh_income <- weighted.mean(base.2021$hh_income, w = base.2021$weight)
-# rel.pov.threshold <- mean.hh_income * 0.6
-# 
-# print(paste0("Relative poverty threshold in 2020: ", rel.pov.threshold))
-# rm(base.2021, mean.hh_income, rel.pov.threshold)
+base.2021 <- base.dat %>%
+  filter(time == 2020)
+
+mean.hh_income <- weighted.mean(base.2021$hh_income, w = base.2021$weight)
+rel.pov.threshold <- mean.hh_income * 0.6
+
+print(paste0("Relative poverty threshold in 2020: ", rel.pov.threshold))
+rm(base.2021, mean.hh_income, rel.pov.threshold)
 ```
@@
 ```{r}
-# threshold <- base.dat %>%
-#   select(time, weight, hh_income) %>%
-#   group_by(time) %>%
-#   summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
-# 
-# ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
-#   geom_col() +
-#   geom_hline(yintercept = threshold$poverty_threshold[threshold$time == 2020], linetype='dashed') +
-#   labs(title = 'Relative poverty threshold over time') +
-#   xlab('Year') +
-#   ylab('Threshold')
+threshold <- base.dat %>%
+  select(time, weight, hh_income) %>%
+  group_by(time) %>%
+  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
+
+ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
+  geom_col() +
+  geom_hline(yintercept = threshold$poverty_threshold[threshold$time == 2020], linetype='dashed') +
+  labs(title = 'Relative poverty threshold over time') +
+  xlab('Year') +
+  ylab('Threshold')
 ```
@@
 ```{r}
-# sample_information(int1.rel, target.year = 2030)
+sample_information(int1.rel, target.year = 2030)
 ```
@@
 ```{r}
-# full.sample.change.SF12(base.dat, int1.rel)
-# all.families.change.SF12(base.dat, int1.rel)
-# poverty.families.change.SF12.variable(base.dat, int1.rel, threshold)
-# treatment.on.treated.change.SF12(base.dat, int1.rel)
+full.sample.change.SF12(base.dat, int1.rel)
+all.families.change.SF12(base.dat, int1.rel)
+poverty.families.change.SF12.variable(base.dat, int1.rel, threshold)
+treatment.on.treated.change.SF12(base.dat, int1.rel)
 ```

### 2024-06-26 minos/validation/handovers.Rmd
Switching SF_12 model back to LMM, and some small adjustments to hh_income_diff model. Also updated some summary targets for a bit of brevity

--- 2024-06-25 minos/validation/handovers.Rmd
@@
 handover_lineplots(raw.dat, base.dat, "hh_income")
-handover_boxplots(raw.dat, base.dat, 'council_tax')
-handover_lineplots(raw.dat, base.dat, "council_tax")
+
+handover_boxplots(raw.dat, base.dat, 'hh_income_diff')
+handover_lineplots(raw.dat, base.dat, "hh_income_diff")
+# handover_boxplots(raw.dat, base.dat, 'council_tax')
+# handover_lineplots(raw.dat, base.dat, "council_tax")
+
+handover_boxplots(base.dat, base.dat, 'hh_income_diff')
+handover_lineplots(base.dat, base.dat, "hh_income_diff")
 ```
@@
 raw.inc <- raw.dat %>%
-  select(pidp, age, time, hh_income)
+  select(pidp, age, time, hh_income, hh_income_diff)
 base.inc <- base.dat %>%
-  select(pidp, age, time, hh_income)
+  select(pidp, age, time, hh_income, hh_income_diff)
 
@@
 
-spaghetti_plot(base.inc, 'hh_income',
-               save = shall.we.save,
-               save.path = save.path)
+spaghetti_plot(income.spag.sample, 'hh_income_diff',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(income.spag.sample, 'hh_income_diff',
+               save = shall.we.save,
+               save.path = save.path)
+
+# spaghetti_plot(base.inc, 'hh_income',
+#                save = shall.we.save,
+#                save.path = save.path)
 
@@
 handover_lineplots(raw.dat, base.dat, "SF_12")
-# 
-# raw.sf12 <- raw.dat %>% 
-#   dplyr::select(pidp, time, SF_12) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.sf12 <- base.dat %>%
-#   dplyr::select(pidp, time, SF_12) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# # merge before plot
-# sf12 <- rbind(raw.sf12, base.sf12)
-# 
-# # Now plot
-# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-#   geom_smooth() +
-#   #geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
-#   xlab('Year') +
-#   ylab('SF12')
-# 
-# ## Try a version where final_US is limited to only those present from wave 1 
-# # onwards because the sample refreshments are messing with the plot
-# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-# 
-# raw.sf12.2 <- raw.dat %>% 
-#   dplyr::select(pidp, time, SF_12) %>%
-#   filter(pidp %in% raw.sf12.wave1) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'final_US')
-# 
-# base.sf12.2 <- base.dat %>%
-#   dplyr::select(pidp, time, SF_12) %>%
-#   filter(pidp %in% raw.sf12.wave1) %>%
-#   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
-#   mutate(source = 'baseline_output')
-# 
-# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
-# 
-# # Now plot
-# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
-#   geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
-#   xlab('Year') +
-#   ylab('SF12')
-# 
-# if (shall.we.save) {
-#   ggsave(filename = 'SF12_wav1.png',
-#        plot = last_plot(),
-#        path = save.path)
-# }
-# 
-# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
+
+handover_boxplots(raw.dat, base.dat, 'SF_12_diff')
+handover_lineplots(raw.dat, base.dat, "SF_12_diff")
+
 ```
@@
 raw.sf12 <- raw.dat %>%
-  select(pidp, age, time, SF_12)
+  select(pidp, age, time, SF_12, SF_12_diff)
 base.sf12 <- base.dat %>%
-  select(pidp, age, time, SF_12)
+  select(pidp, age, time, SF_12, SF_12_diff)
 
@@
 spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
+               save = shall.we.save,
+               save.path = save.path)
+
+spaghetti_plot(sf12.spag.sample, 'SF_12_diff',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_diff',
                save = shall.we.save,

### 2024-06-26 minos/modules/child_poverty_interventions.py

@@ -589,6 +589,22 @@ class ChildPovertyReductionABSOLUTE(Base):
 
         print(f"Number of people already boosted: {full_pop['income_boosted'].sum()}")
 
+        # Generate a few important populations to use for reporting / further work
+        full_pop_hh_rep = full_pop.groupby('hidp').first().reset_index()  # single representative of each household
+        pov_pop_hh_rep = full_pop_hh_rep[full_pop_hh_rep['hh_income'] < absolute_pov_threshold]
+        pov_pop_children_hh_rep = pov_pop_hh_rep[pov_pop_hh_rep['nkids'] > 0]
+
+        # Number of children
+        num_kids = full_pop_hh_rep['nkids'].sum()
+        num_kids_in_pov = pov_pop_children_hh_rep['nkids'].sum()
+
+        print(f"Number of children in the model: {num_kids}")
+
+        print(
+            f"There are {len(pov_pop_hh_rep)}/{len(full_pop_hh_rep)} households in relative poverty, with {len(pov_pop_children_hh_rep)} containing children.")
+        print(
+            f"This amounts to {num_kids_in_pov} children in poverty, which is {(num_kids_in_pov / num_kids) * 100}% of the total.")
+
         # DO NOT reset the previous income_boosted for testing
         # We need to track people who have been intervened so we can continue the intervention indefinitely
         # full_pop['income_boosted'] = False
@@ -718,7 +734,7 @@ class ChildPovertyReductionABSOLUTE(Base):
         print(f"Number of children in the model: {num_kids}")
 
         print(
-            f"There are {len(pov_pop_hh_rep)}/{len(full_pop_hh_rep)} households still in relative poverty, with {len(pov_pop_children_hh_rep)} containing children.")
+            f"There are {len(pov_pop_hh_rep)}/{len(full_pop_hh_rep)} households still in absolute poverty, with {len(pov_pop_children_hh_rep)} containing children.")
         print(
             f"This amounts to {num_kids_in_pov} children still in poverty, which is {(num_kids_in_pov / num_kids) * 100}% of the total.")
 

### 2024-07-04 minos/outcomes/ChildPovReduction_Combined.Rmd
Added some alternative working directories for priority subgroup and default US runs

@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/psub/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/default_US/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
@@
 ```{r "inequality_plots", include=FALSE}
-# inequality_plots <- function(summary_group, scen.list) {
-#   
-#   tit <- ' '
-#   if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
-#   if (summary_group == 'families') { tit <- 'Families' }
-#   
-#   summary_group <- paste0(summary_group, '_income_quint')
-#   
-#   data <- do.call(rbind, generate_df_list(summary_group, scen.list))
-#   
-#   data$income_quintile <- factor(data$income_quintile)
-#   
-#   # Combine the data
-#   data_combined <- data %>%
-#     mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))
-#   
-#   p1 <- ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
-#     geom_smooth(alpha = 0.7) +
-#     scale_color_manual(name = "Income Quintile", 
-#                        values = c("red", "blue", "green", "orange", "purple")) +
-#     scale_linetype_manual(name = "Scenario", 
-#                           values = c("Baseline" = "solid", "Intervention" = "dotted")) +
-#     labs(title = "SF_12 Scores by Income Quintile",
-#          subtitle = tit,
-#          x = "Year",
-#          y = "Mean SF_12 MCS") +
-#     theme_minimal() +
-#     theme(legend.position = "right",
-#           legend.title = element_text(size = 12),
-#           legend.text = element_text(size = 10))
-#   
-#   # Aggregate data
-#   agg_data <- data %>%
-#     mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention')) %>%
-#     group_by(year, income_quintile, scenario) %>%
-#     summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
-#     spread(scenario, mean_SF_12) %>%
-#     mutate(difference = Intervention - Baseline)
-#   
-#   p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
-#     geom_bar(stat = "identity", position = "dodge") +
-#     scale_fill_manual(name = "Income Quintile", 
-#                       values = c("red", "blue", "green", "orange", "purple")) +
-#     labs(title = "Average Difference in SF_12 Scores by Income Quintile",
-#          subtitle = tit,
-#          x = "Year",
-#          y = "Difference in SF_12 Score") +
-#     theme_minimal() +
-#     theme(legend.position = "right",
-#           legend.title = element_text(size = 12),
-#           legend.text = element_text(size = 10))
-#   
-#   print(p1)
-#   print(p2)
-# }
-
 inequality_plots <- function(summary_group, scen) {
@@
 scen.abs <- 'ChildPovertyReductionABSOLUTE'
+# scen.list.rel <- c('baseline', 'ChildPovertyReductionRELATIVE_psub')
+# scen.rel <- 'ChildPovertyReductionRELATIVE_psub'
+# scen.list.abs <- c('baseline', 'ChildPovertyReductionABSOLUTE_psub')
+# scen.abs <- 'ChildPovertyReductionABSOLUTE_psub'
 ```

### 2024-07-05 minos/outcomes/ChildPovReduction_Combined.Rmd
Switching vis script back to scot output

@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/psub/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/default_US/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/default_US/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"

### 2024-07-05 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Added script to visualise combined relative and absolute intervention together. Also added some things to gitignore

--- 2024-07-05 minos/outcomes/ChildPovReduction_Combined.Rmd
@@
 ---
-title: "Scottish Child Poverty Briefing Plots"
+title: "R Notebook"
 output:
-  pdf_document:
-    toc: true
+  pdf_document: default
   html_document:
-    toc: true
-    toc_float: true
-    collapsed: false
-    number_sections: true
     df_print: paged
-    code_folding: hide
 ---
-
-WS5 (Dynamic Microsimulation): What are the impacts on mental health of meeting the targets?
-·        Across the population? 
-·        Population by income quintile (looking at absolute/relative inequalities)?
-·        For families only? By income quintile (looking at absolute/relative inequalities)?
-·        For families that meet criteria of 0/1/2+ of the priority family groups?
-·        Differential impacts of UK package of policies only, and then UK package with SG policies?
 
@@
 workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/psub/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/default_US/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
@@
 ```{r "Data", include=FALSE}
-scen.list.rel <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
-scen.rel <- 'ChildPovertyReductionRELATIVE_2'
-scen.list.abs <- c('baseline', 'ChildPovertyReductionABSOLUTE')
-scen.abs <- 'ChildPovertyReductionABSOLUTE'
-# scen.list.rel <- c('baseline', 'ChildPovertyReductionRELATIVE_psub')
-# scen.rel <- 'ChildPovertyReductionRELATIVE_psub'
-# scen.list.abs <- c('baseline', 'ChildPovertyReductionABSOLUTE_psub')
-# scen.abs <- 'ChildPovertyReductionABSOLUTE_psub'
+scen.list <- c('baseline', 'ChildPovertyReduction')
+scen <- 'ChildPovertyReduction'
 ```
 
-# MCS Change to QALY Example
-
-We use an equation derived from table 4 (below) in [this paper by Lawrence and Fleishman](https://pubmed.ncbi.nlm.nih.gov/15090102/) to calculate QALYs from SF-12 Mental Component Score (MCS) and Physical Component Score (PCS).
-
-#![L&F Table 4](L&F_table4.png)
-
-```{r}
-# formula to find the utility score from mean MCS and PCS scores of a population
-utility_score <- function(pcs, mcs) {
-  utility_score <- 
-    1.6984 + 
-    (pcs * 0.07927) +
-    (mcs * 0.02859) +
-    ((pcs * mcs) * -0.000126) +
-    ((pcs * pcs) * -0.00141) +
-    ((mcs * mcs) * -0.00014) +
-    ((pcs * pcs * pcs) * 0.0000107)
-  return(utility_score)
-}
-
-# Calculate utility score for hypothetical baseline (MCS & PCS == 45.0)
-initial_conditions <- utility_score(pcs = 45.0,
-                                    mcs = 45.0)
-# Calculate utility score for 0.1 improvement in MCS (MCS now == 45.1)
-intervention <- utility_score(pcs = 45.0,
-                              mcs = 45.1)
-
-print("Utility score for hypothetical baseline (assuming mean MCS and PCS both equal 45.0):")
-print(initial_conditions)
-print("Utility score for population given a 0.1 mean improvement in MCS:")
-print(intervention)
-
-print("Gain in utility score per person:")
-gain <- intervention - initial_conditions
-print(gain)
-
-print("Gain in utiliy for the total Scotland population (assuming 5.5m). This is equivalent to QALYs gained:")
-print(gain * 5500000)
-```
-
-This rough calculation shows that a 0.1 absolute change in mean SF_12 across the Scottish population would equal over 5000 additional QALYs in a single year.
-These improvements can also accumulate over time.
-If we were able to achieve a 0.1 improvement in mean MCS for Scotland in year 1, and maintain this 0.1 improvement for 10 years, the resulting improvement in QALYs would be 56,000+.
-
-NOTE: This calculation assumes that PCS is unchanged when MCS can vary. This is not realistic, but the calculation is still useful to provide context for the results to follow.
-
-# SAMPLE UNCERTAINTY
-
-When running MINOS with a synthetic population, due to the size of the synthetic populations and the demands of the model, we have to take a reduced sample as our starting population.
-For the Scotland synthetic runs we take a 10% sample, which reduces the population size from roughly 5.5m to 550,000.
-
-We therefore have to also account for the uncertainty in model outputs that comes from this reduced sample. As a somewhat temporary fix for this, we have done the following:
-
-- Generate 10 different 10% samples from our synthetic population
-  - Generate a replenishing population from each of these samples
-- Use each distinct 10% sample for 10 runs each, totalling 100 runs
-- Plot the local mean from each 10 run block, and the global mean from all 100 runs
-
-```{r}
-synthpop_uncertainty(summary_group = 'whole_pop',
-                     scen = 'baseline',
-                     var = 'hh_income')
-
-synthpop_uncertainty(summary_group = 'whole_pop',
-                     scen = 'baseline',
-                     var = 'SF_12')
-```
-
-# RELATIVE POVERTY INTERVENTION
-
-Reducing the proportion of children in poverty to 10% or lower by 2030.
+# COMBINED RELATIVE AND ABSOLUTE REDUCTION INTERVENTION
 
@@
 SF12_change_simple(summary_group = 'whole_pop',
-                   scen.list = scen.list.rel)
+                   scen.list = scen.list)
 
 SF12_change_ind_trajectories(summary_group = 'whole_pop',
-                             scen.list <- scen.list.rel)
+                             scen.list <- scen.list)
 
 mental_illness_risk_counts(summary_group = 'men_illness_risk',
-                           scen.list = scen.list.rel)
+                           scen.list = scen.list)
 ```
@@
 SF12_change_income_quint2(summary_group = 'whole_pop',
-                                    scen = scen.rel)
+                                    scen = scen)
 ```
@@
 inequality_plots(summary_group = 'whole_pop',
-                 scen = scen.rel)
+                 scen = scen)
 ```
@@
 SF12_change_simple(summary_group = 'families',
-                       scen.list = scen.list.rel)
+                       scen.list = scen.list)
 
 SF12_change_ind_trajectories(summary_group = 'families',
-                             scen.list <- scen.list.rel)
+                             scen.list <- scen.list)
 
 mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
-                           scen.list = scen.list.rel)
+                           scen.list = scen.list)
 ```
@@
 SF12_change_income_quint2(summary_group = 'families',
-                                    scen = scen.rel)
+                                    scen = scen)
 ```
@@
 inequality_plots(summary_group = 'families',
-                 scen = scen.rel)
+                 scen = scen)
 ```
@@
 SF12_change_simple(summary_group = 'priority_any',
-                       scen.list = scen.list.rel)
+                       scen.list = scen.list)
 ```
@@
 ```{r}
-SF12_change_num_priority_groups(scen.list.rel)
+SF12_change_num_priority_groups(scen.list)
 ```
@@
 
-SF12_change_treated(scen = scen.rel)
+SF12_change_treated(scen = scen)
 ```
-
-## Differential Impacts of UK vs SG
-
-What are the impacts on mental health of meeting the targets?
-
-- Differential impacts of UK package of policies only, and then UK package with SG policies?
-
-# ABSOLUTE POVERTY INTERVENTION
-
-Reducing the proportion of children in poverty to 10% or lower by 2030.
-
-## Whole Population
-
-What are the impacts on mental health of meeting the targets:
-
-- Across the population?
-- Population by income quintile?
-
-```{r}
-SF12_change_simple(summary_group = 'whole_pop',
-                       scen.list = scen.list.abs)
-
-SF12_change_ind_trajectories(summary_group = 'whole_pop',
-                             scen.list <- scen.list.abs)
-
-mental_illness_risk_counts(summary_group = 'men_illness_risk',
-                           scen.list = scen.list.abs)
-```
-
-### Income Quintile
-
-```{r}
-# SF12_change_income_quint(summary_group = 'whole_pop',
-#                                     scen.list = scen.list.abs)
-SF12_change_income_quint2(summary_group = 'whole_pop',
-                                    scen = scen.abs)
-```
-
-### SF_12 Inequality
-
-```{r}
-inequality_plots(summary_group = 'whole_pop',
-                 scen = scen.abs)
-```
-
-## Families
-
-What are the impacts on mental health of meeting the targets:
-
-- For families only? By income quintile
-
-```{r}
-SF12_change_simple(summary_group = 'families',
-                       scen.list = scen.list.abs)
-
-SF12_change_ind_trajectories(summary_group = 'families',
-                             scen.list <- scen.list.abs)
-
-mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
-                           scen.list = scen.list.abs)
-```
-
-### Income Quintile
-
-```{r}
-# SF12_change_income_quint(summary_group = 'families',
-#                                     scen.list = scen.list.abs)
-SF12_change_income_quint2(summary_group = 'families',
-                                    scen = scen.abs)
-```
-
-### SF_12 Inequality
-
-```{r}
-inequality_plots(summary_group = 'families',
-                 scen = scen.abs)
-```
-
-## Priority Subgroups
-
-What are the impacts on mental health of meeting the targets:
-
-- For families that meet the criteria of 0/1/2+ of the priority family groups?
-
-```{r}
-SF12_change_simple(summary_group = 'priority_any',
-                                    scen.list = scen.list.abs)
-```
-
-### Number of Priority Subgroups
-
-Results disaggregated by if household belongs to 0, 1, 2, 3+ priority subgroups.
-
-```{r}
-SF12_change_num_priority_groups(scen.list.abs)
-```
-
-## Treated Population
-
-```{r}
-# SF12_change_simple(summary_group = 'treated_absolute',
-#                    scen.list = scen.list.abs)
-
-SF12_change_treated(scen = scen.abs)
-```
-
-## Differential Impacts of UK vs SG
-
-What are the impacts on mental health of meeting the targets?
-
-- Differential impacts of UK package of policies only, and then UK package with SG policies?
 

### 2024-07-05 minos/outcomes/paper_1_notebook.Rmd
updates to notebook for paper revision

@@
 
+```{r setup}
+knitr::opts_knit$set(root.dir = "/home/rob/Minos")
+getwd()
+```
+
 ```{r "preamble"}
-source("minos/transitions/utils.R")
-source("minos/transitions/transition_model_functions.R")
-source("minos/transitions/paper_1_plots.R")
+#setwd("../..")
+library(here)
+source(here::here("minos", "transitions", "utils.R"))
+source(here::here("minos", "transitions", "transition_model_functions.R"))
+source(here::here("minos", "transitions", "paper_1_plots.R"))
 library(dplyr)
@@
 library(MASS)
+library(qpcR)
+library(cv)
+library(Rcpp)
+
 save.path <- "minos/outcomes/paper1_plots/"
-raw.data.dir <- "data/raw_US/"
+#raw.data.dir <- "data/raw_US/"
+raw.data.dir  <- "data/composite_US/"
 mice.data.dir <- "data/composite_US/"
@@
 
+#TODO RMSE AND PRESS STATS FOR CROSS VAL.  RMSE(predictions, test_data$outcomeName)
+#TODO MAKE SURE CROSS VAL ON BOTH STAGES.
 # get raw data file names from 2011-2013.
@@
                        full.names = TRUE,
-                       pattern = '[0-9]{4}_US_cohort.csv')[21:23] # get files for 2011-2013.
+                       pattern = '[0-9]{4}_US_cohort.csv')[3:5]#[21:23] # get files for 2011-2013.
 # load raw data.
@@
 # baseline OLS model formula. 
-raw_model_formula_string <- "SF_12 ~ factor(sex) + 
+raw_model_formula_string <- "I(log((80 -SF_12)+10)) ~ factor(sex) + 
                   relevel(factor(ethnicity), ref='WBI') + 
@@
 raw.data <- update_column_names(raw.data)
-raw.data <- raw.data[, append(variables, c("time", 'pidp', 'weight'))]
+raw.data <- raw.data[, append(variables, c("time", 'pidp','hidp', 'weight'))]
 raw.data <- replace.missing(raw.data)
@@
                        full.names = TRUE,
-                       pattern = '[0-9]{4}_US_cohort.csv')[21:30] # get files for 2011-2013.
+                       pattern = '[0-9]{4}_US_cohort.csv')[3:13] #[21:30] # get files for 2011-2013.
 # load raw data.
@@
 # get only needed variables and replace missing codes with NA.
-full.raw.data <- full.raw.data[, append(variables, c("time", 'pidp', 'weight'))]
+full.raw.data <- full.raw.data[, append(variables, c("time", 'pidp', 'hidp', 'weight'))]
 full.raw.data <- replace.missing(full.raw.data)
@@
          use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
-         fontsize='small') # small font
+         fontsize='tiny') # tiny font
 }
@@
 forest_plot_lm(sf12.lm, paste0(save.path, "presentation_forest.pdf"))
+log_forest_plot(sf12.lm, paste0(save.path, "presentation_forest.pdf"))
 qq_plot(resid(sf12.lm), paste0(save.path, "presentation_qq.pdf"))
@@
 colnames(start.data) <- start.data.colnames
-handover.data <- start.data[, c("pidp", "SF_12", "time")]
+handover.data <- start.data[, c("pidp", "SF_12", "hidp", "time")]
 rolling.data <- start.data
 
-for (i in 1:7){
-  start.data$SF_12 <- predict(sf12.lm, rolling.data)
-  start.data[, 'time'] <- start.data[, 'time'] +1
-  handover.data <- rbind(handover.data, start.data[, c("pidp", "SF_12", "time")])
+for (i in 1:8){
+  rolling.data$SF_12 <- (80-(exp(predict(sf12.lm, rolling.data))-10))
+#  start.data$SF_12 <- predict(sf12.lm, rolling.data)
+  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
+  handover.data <- rbind(handover.data, rolling.data[, c("pidp", "hidp", "SF_12", "time")])
 }
@@
 
+```{r raw cross val}
+# Baseline cross val.
+
+trControl <- trainControl(method = "cv", number=5, returnData=F, trim=T, verboseIter = TRUE)
+
+raw.cross.val.sf12.model <- train(as.formula(raw_model_formula_string), data = raw.data,
+               method = "lm",
+               trControl = trControl)
+
+print(RMSE(raw.cross.val.sf12.model))
+
+#print(PRESS(raw.cross.val.sf12.model))
+```
+
 ##################################
@@
 
-```{r}
+```{r mice preprocessing}
 # load in all 2009-2020 datasets
@@
 # missingness MICE model formula
-mice_formula_string <- "SF_12 ~ 
+mice_formula_string <- "I(log(SF_12+10)) ~ 
                         factor(sex) + 
@@
                         factor(education_state) + 
-                        factor(S7_labour_state) + 
+                        factor(labour_state) + 
                         relevel(factor(NSSEC), ref=1) +
@@
 mice.pidp <- mice.data[which(mice.data$time %in% c(2011, 2012, 2013)), "pidp"]
+mice.hidp <- mice.data[which(mice.data$time %in% c(2011, 2012, 2013)), "hidp"]
 mice.time <- mice.data[which(mice.data$time %in% c(2011, 2012, 2013)), "time"]
@@
 mice.2018.pidp <- mice.data[which(mice.data$time %in% c(2016, 2017, 2018)), "pidp"]
+mice.2018.hidp <- mice.data[which(mice.data$time %in% c(2016, 2017, 2018)), "hidp"]
 mice.2018.time <- mice.data[which(mice.data$time %in% c(2016, 2017, 2018)), "time"]
@@
 forest_plot(lm.no.mice,  paste0(save.path, "no_mice_forest.pdf"))
+log_forest_plot(lm.no.mice,  paste0(save.path, "no_mice_forest.pdf"))
 ```
@@
 )
-
-method <- c("pmm",
-            'pmm',
-            'pmm',
-            'pmm',#'polr',
-            'pmm',
-            'pmm', #'polr',
-            'pmm',
-            'pmm', #'polr', #'pmm',
-            'pmm',
-            'pmm',
-            'pmm',
-            'pmm',
-            'pmm',
-            'pmm',
-            "pmm",
-            "pmm")
 
@@
 mice.data$ethnicity <- factor(mice.data$ethnicity)
-mice.data$S7_labour_state <- factor(mice.data$S7_labour_state)
+mice.data$labour_state <- factor(mice.data$labour_state)
 mice.data$region <- factor(mice.data$region)
@@
 } else {
-  n_iter <- 30
-  max_iter <- 10
+  #n_iter <- 30
+  #max_iter <- 10
+  n_iter <- 1
+  max_iter <- 1
   ignore_cols = c("birth_year")
   # future mice is parallelised version of MICE.
-  mice_set <- mice(data = mice.data[, imp_columns],
+  mice_set <- mice(data = mice.data[mice.data$time %in%  c(2013, 2020), imp_columns],
                    m = n_iter, maxit = max_iter,
@@
 forest_plot(pre.mice.lm , paste0(save.path,'mice_SF12_forest.pdf'))
+log_forest_plot(pre.mice.lm , paste0(save.path,'mice_SF12_forest.pdf'))
 qq_plot(resid(pre.mice.lm ), paste0(save.path, "mice_qq.pdf"))
+```
+
+```{r mice_output}
+
+# only looking at 2011-2013 subset of data. convert to data frame, subset, and back to MICE mids. 
+# also adding variables that can't be imputed back in. pidp time weight.
+mice.long <- complete(mice_set, action = "long", include=T) #
+#mice.long$SF_12 <- mice.long$SF_12 + 10
+#mice.long.subset <- mice.long[which(mice.long$time %in% c(2011, 2012, 2013)), ]
+
+mice.long$pidp <- mice.data$pidp
+mice.long$hidp <- mice.data$hidp
+mice.long$weight <- mice.data$weight
+mice.long$time <- mice.data$time
+mice.long <- update_column_names(mice.long)
+mice_set.full <- as.mids(mice.long)
+
+mice.long.subset <- mice.long[which(mice.long$time %in% c(2011, 2012, 2013)), ]
+
+as.mids2 <- function (data, .imp = 1, .id = 2) 
+    {
+      # paste added to get numerical value if .imp is factor
+      ini <- mice(data[data[, .imp] == 0, -c(.imp, .id)], m = max(as.numeric(paste(data[, .imp]))), maxit = 0)
+      names <- names(ini$imp)
+          if (!is.null(.id)) {
+            rownames(ini$data) <- data[data[, .imp] == 0, .id]
+          }
+          for (i in 1:length(names)) {
+            # -1 removed and paste added to get numerical value if .imp is factor
+            for (m in 1:(max(as.numeric(paste(data[, .imp]))))) {
+              if (!is.null(ini$imp[[i]])) {
+                indic <- data[, .imp] == m & is.na(data[data[, .imp] == 0, names[i]])
+                ini$imp[[names[i]]][m] <- data[indic, names[i]]
+          }
+        }
+      }
+      return(ini)
+    }
+mice_set.subset <- as.mids2(mice.long.subset) # bug in as.mids can't handle this. nice fix here. https://stats.stackexchange.com/questions/138769/something-wrong-with-as-mids-from-mice-package-in-r
+
+# convergence plots needs to be done on full mice subset. 
+pdf(paste0(paste0(save.path,"ols_mice_convergence.pdf")))
+#print(plot(mice_set, SF_12 = SF_12 ~ .it | .ms))
+plot_trace(mice_set, "SF_12") + theme(legend.position="none")
+dev.off()
+
+# pooling OLS estimate together. 
+mice.sf12.lm <- with(mice_set.subset, lm(as.formula(mice_formula_string)))
+final.pool<- pool(mice.sf12.lm)
+
+# summary stats for final pool. 
+pooled_lm <- mice.sf12.lm$analyses[[1]]
+pool.sum <- summary(final.pool)
+pooled_lm$coefficients = pool.sum$estimate
+mice.preds<- predict(pooled_lm)
+pool.r.squared(final.pool)
+
+# mice objects dont go in forest plot annoyingly. move coefficients over to a
+# dummy lm that sjPlot::plot_models can read.
+mice.lm.object <- summary(lm(mice_formula_string, data = complete(mice_set.subset)))
+mice.lm.object$coefficients[,1] <- pool.sum$estimate
+mice.lm.object$coefficients[,2] <- pool.sum$std.error
+mice.lm.object$coefficients[,3] <- pool.sum$statistic
+mice.lm.object$coefficients[,4] <- pool.sum$p.value
+
+# making density plot. 
+res <- as.data.frame(predict(pooled_lm))
+real <- as.data.frame(mice.data$SF_12)
+res$type <- c("Predicted")
+real$type <- c("Real")
+colnames(res) <- c("SF12", 'type')
+colnames(real) <- c("SF12", 'type')
+hist.data <- rbind(res,real)
+hist.data <- tidyr::drop_na(hist.data)
+
+res <- as.data.frame(resid(pooled_lm))
+residual_density_plot(res, paste0(save.path,'mice_ols_densities.pdf'), guide='normal')
+
+# coefficient forest plot. 
+forest_plot(mice.lm.object, paste0(save.path,'mice_SF12_forest.pdf'))
+log_forest_plot(mice.lm.object, paste0(save.path,'mice_SF12_forest.pdf'))
+qq_plot(resid(mice.lm.object), paste0(save.path, "mice_qq.pdf"))
+
+# writing coefficients table for MICE. 
+# is there a version for pool table?
+write_coefs <- T
+if (write_coefs)
+{
+  texreg_file <- paste0(save.path, 'SF12_MICE_OLS_coefficients.txt')
+  tex_label <- paste0("table: MICE_OLS_coefficients") 
+  tex_headers <- c(texreg::names2latex("MICE SF_12 OLS"))
+  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "ols"))    
+  texreg(mice.lm.object, # what model to save coefs for. 
+         file=texreg_file,  # where to save.
+         custom.model.names = tex_headers, # title of table.
+         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
+         digits=4, # p values significant figures.
+         caption=tex_caption, # \caption command option. 
+         label = tex_label, # \label command option. 
+         dcolumn=T,# nice column alignment. 
+         booktabs=T, # nice hlines. (recommended)
+         tabular=T,# tabular env.
+         single.row = T, # nicer one row formatting.
+         longtable=T, # allows tables to wrap over pages
+         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
+         fontsize='tiny') # tiny font
+
+  # same again for MICE pool. 
+  texreg_file <- paste0(save.path, 'SF12_MICE_pool_OLS_coefficients.txt')
+  tex_label <- paste0("table: MICE_pool_OLS_coefficients") 
+  tex_headers <- c(texreg::names2latex("MICE SF_12 OLS Pool"))
+  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "ols"))    
+  texreg(final.pool, # what model to save coefs for. 
+         file=texreg_file,  # where to save.
+         custom.model.names = tex_headers, # title of table.
+         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
+         digits=4, # p values significant figures.
+         caption=tex_caption, # \caption command option. 
+         label = tex_label, # \label command option. 
+         dcolumn=T,# nice column alignment. 
+         booktabs=T, # nice hlines. (recommended)
+         tabular=T,# tabular env.
+         single.row = T, # nicer one row formatting.
+         longtable=T, # allows tables to wrap over pages
+         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
+         fontsize='tiny') # tiny font
+}
 
@@
          use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
-         fontsize='small') # small font
+         fontsize='tiny') # tiny font
 
@@
          use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
-         fontsize='small') # small font
-}
-
-```
-
-```{r mice_output}
-
-# only looking at 2011-2013 subset of data. convert to data frame, subset, and back to MICE mids. 
-# also adding variables that can't be imputed back in. pidp time weight.
-mice.long <- complete(mice_set, action = "long", include=T)
-#mice.long.subset <- mice.long[which(mice.long$time %in% c(2011, 2012, 2013)), ]
-
-mice.long$pidp <- mice.data$pidp
-mice.long$weight <- mice.data$weight
-mice.long$time <- mice.data$time
-mice.long <- update_column_names(mice.long)
-mice_set.full <- as.mids(mice.long)
-
-mice.long.subset <- mice.long[which(mice.long$time %in% c(2011, 2012, 2013)), ]
-mice_set.subset <- as.mids(mice.long.subset)
-
-# convergence plots needs to be done on full mice subset. 
-pdf(paste0(paste0(save.path,"ols_mice_convergence.pdf")))
-#print(plot(mice_set, SF_12 = SF_12 ~ .it | .ms))
-plot_trace(mice_set, "SF_12") + theme(legend.position="none")
-dev.off()
-
-# pooling OLS estimate together. 
-mice.sf12.lm <- with(mice_set.subset, lm(as.formula(mice_formula_string)))
-final.pool<- pool(mice.sf12.lm)
-
-# summary stats for final pool. 
-pooled_lm <- mice.sf12.lm$analyses[[1]]
-pool.sum <- summary(final.pool)
-pooled_lm$coefficients = pool.sum$estimate
-mice.preds<- predict(pooled_lm)
-pool.r.squared(final.pool)
-
-# mice objects dont go in forest plot annoyingly. move coefficients over to a
-# dummy lm that sjPlot::plot_models can read.
-mice.lm.object <- summary(lm(mice_formula_string, data = complete(mice_set.subset)))
-mice.lm.object$coefficients[,1] <- pool.sum$estimate
-mice.lm.object$coefficients[,2] <- pool.sum$std.error
-mice.lm.object$coefficients[,3] <- pool.sum$statistic
-mice.lm.object$coefficients[,4] <- pool.sum$p.value
-
-# making density plot. 
-res <- as.data.frame(predict(pooled_lm))
-real <- as.data.frame(mice.data$SF_12)
-res$type <- c("Predicted")
-real$type <- c("Real")
-colnames(res) <- c("SF12", 'type')
-colnames(real) <- c("SF12", 'type')
-hist.data <- rbind(res,real)
-hist.data <- tidyr::drop_na(hist.data)
-
-res <- as.data.frame(resid(pooled_lm))
-residual_density_plot(res, paste0(save.path,'mice_ols_densities.pdf'), guide='normal')
-
-# coefficient forest plot. 
-forest_plot(mice.lm.object, paste0(save.path,'mice_SF12_forest.pdf'))
-qq_plot(resid(mice.lm.object), paste0(save.path, "mice_qq.pdf"))
-
-# writing coefficients table for MICE. 
-# is there a version for pool table?
-write_coefs <- T
-if (write_coefs)
-{
-  texreg_file <- paste0(save.path, 'SF12_MICE_OLS_coefficients.txt')
-  tex_label <- paste0("table: MICE_OLS_coefficients") 
-  tex_headers <- c(texreg::names2latex("MICE SF_12 OLS"))
-  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "ols"))    
-  texreg(mice.lm.object, # what model to save coefs for. 
-         file=texreg_file,  # where to save.
-         custom.model.names = tex_headers, # title of table.
-         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
-         digits=4, # p values significant figures.
-         caption=tex_caption, # \caption command option. 
-         label = tex_label, # \label command option. 
-         dcolumn=T,# nice column alignment. 
-         booktabs=T, # nice hlines. (recommended)
-         tabular=T,# tabular env.
-         single.row = T, # nicer one row formatting.
-         longtable=T, # allows tables to wrap over pages
-         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
-         fontsize='small') # small font
-
-  # same again for MICE pool. 
-  texreg_file <- paste0(save.path, 'SF12_MICE_pool_OLS_coefficients.txt')
-  tex_label <- paste0("table: MICE_pool_OLS_coefficients") 
-  tex_headers <- c(texreg::names2latex("MICE SF_12 OLS Pool"))
-  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "ols"))    
-  texreg(final.pool, # what model to save coefs for. 
-         file=texreg_file,  # where to save.
-         custom.model.names = tex_headers, # title of table.
-         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
-         digits=4, # p values significant figures.
-         caption=tex_caption, # \caption command option. 
-         label = tex_label, # \label command option. 
-         dcolumn=T,# nice column alignment. 
-         booktabs=T, # nice hlines. (recommended)
-         tabular=T,# tabular env.
-         single.row = T, # nicer one row formatting.
-         longtable=T, # allows tables to wrap over pages
-         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
-         fontsize='small') # small font
-}
-
+         fontsize='tiny') # tiny font
+}
 #screenreg final.pool
@@
 
-```{r cross validated nowcasting}
+```{r mice cross validated nowcasting}
 # split data into five
@@
                trControl = trControl)
+
+print(RMSE(cross.val.sf12.model))
 
@@
 rolling.data <- start.data#[, c("pidp", "SF_12", "time")]
-handover.data <- rolling.data[, c("pidp", "SF_12", "time")]
-for (i in 1:7){
-  rolling.data$SF_12 <- predict(pooled_lm, newdata = rolling.data)
+handover.data <- rolling.data[, c("pidp", "hidp", "SF_12", "time")]
+for (i in 1:8){
+  rolling.data$SF_12 <- exp(predict(pooled_lm, newdata = rolling.data))-10
   start.data$SF_12 <- rolling.data$SF_12
   rolling.data[, 'time'] <- rolling.data[, 'time'] +1
-  handover.data <- rbind(handover.data, rolling.data[, c("pidp", "SF_12", "time")])
+  handover.data <- rbind(handover.data, rolling.data[, c("pidp", "hidp", "SF_12", "time")])
 }
@@
 rolling.data <- start.data
-handover.data <- rolling.data[, c("pidp", "SF_12", "time")]
-
-for (i in 1:7){
-  rolling.data$SF_12 <- predict(cross.val.sf12.model, rolling.data)
+handover.data <- rolling.data[, c("pidp", "hidp", "SF_12", "time")]
+
+for (i in 1:8){
+  rolling.data$SF_12 <- exp(predict(cross.val.sf12.model, rolling.data))-10
   start.data$SF_12 <- rolling.data$SF_12
   rolling.data[, 'time'] <- rolling.data[, 'time'] +1
-  handover.data <- rbind(handover.data, rolling.data[, c("pidp", "SF_12", "time")])
+  handover.data <- rbind(handover.data, rolling.data[, c("pidp", 'hidp', "SF_12", "time")])
 }
@@
   for (j in 1:7){
-    random.start.data$SF_12 <- predict(model.choice, random.start.data)
+    random.start.data$SF_12 <- exp(predict(model.choice, random.start.data))-10
     #random.start.data$SF_12 <- random.rolling.data$SF_12
@@
        use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
-       fontsize='small') # small font
+       fontsize='tiny') # tiny font
 
@@
 mice_set.subset.2016_2018$pidp <- mice.2018.pidp
+mice_set.subset.2016_2018$hidp <- mice.2018.hidp
 mice_set.subset.2016_2018$weight <- mice.2018.weights
@@
 mice_set.subset.2011_2013.updated_weights$pidp <- mice.pidp
+mice_set.subset.2011_2013.updated_weights$hidp <- mice.hidp
 mice_set.subset.2011_2013.updated_weights$weight <- extrapolated.weights
 mice_set.subset.2011_2013.updated_weights$time <- mice.time
-mice_set.subset.2011_2013.updated_weights <- as.mids(mice_set.subset.2011_2013.updated_weights)
+mice_set.subset.2011_2013.updated_weights <- as.mids2(mice_set.subset.2011_2013.updated_weights)
 
@@
        use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
-       fontsize='tiny') # small font
+       fontsize='tiny') # tiny font
 ```
@@
             rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff
-glmm.mice.set <- as.mids(glmm.mice.long.subset)
+#glmm.mice.long.subset <- glmm.mice.long.subset[!is.na(glmm.mice.long.subset$SF_12_last), ]
+glmm.mice.long.subset <- glmm.mice.long.subset[glmm.mice.long.subset$time %in% c(2011, 2012, 2013), ]
+glmm.mice.long.subset$.imp <- as.numeric(glmm.mice.long.subset$.imp)
+glmm.mice.long.subset <- as.data.frame(glmm.mice.long.subset)
+glmm.mice.set <- as.mids2(glmm.mice.long.subset)
 
 asd <- "SF_12_last +"
-glmm_model_formula_string <- "SF_12 ~ SF_12_last +
+glmm_model_formula_string <- "I(log(SF_12+10)) ~ SF_12_last +
                   factor(sex) + 
@@
 } else {
-  glmm.fitted <-  max_value - predict(mice.glmm.object, type='response')
+  #glmm.fitted <-  max_value - predict(mice.glmm.object, type='response')
+  glmm.fitted <-  max_value - (exp(predict(mice.glmm.object, type='response')) - 10)
+
 }
@@
 gamma_forest_plot(mice.glmm.object, paste0(save.path, "glmm_forest.pdf"))
+log_forest_plot(mice.glmm.object, paste0(save.path, "glmm_forest.pdf"))
 #mice.glmm.object@beta <- -mice.glmm.object@beta
@@
 # load raw composite data for glmm handovers.
-crossval.glmm.data <- replace.missing(complete(mice_set.full, 1)[, append(variables, c("time", 'pidp', 'weight'))])
+crossval.glmm.data <- replace.missing(complete(mice_set.full, 1)[, append(variables, c("time", 'pidp', 'hidp', 'weight'))])
 crossval.glmm.data <- crossval.glmm.data[which(crossval.glmm.data$time>=2013),]
@@
 ```{r glmm_handovers}
+cppFunction('NumericVector rcpp_clip( NumericVector x, double a, double b){
+    return clamp( a, x, b ) ;
+}')
 
@@
 start.data <- start.data[which(start.data$time==2013),]
+start.data$SF_12 <- max_value - start.data$SF_12
 #start.data$SF_12 <- crossval.glmm.data[which(crossval.glmm.data$time==2013),]$SF_12
@@
 start.data <- drop_na(start.data)
-} else {
-  start.data$SF_12 <- max_value - start.data$SF_12
-}
+} #else {
+  #start.data$SF_12 <- start.data$SF_12
+  #start.data$SF_12 <- max_value - start.data$SF_12
+#}
 #start.data$SF_12_last <- max_value - start.data$SF_12_last
 handover.data <- start.data
-
 rolling.data <- start.data
-for (i in 1:7){
+
+for (i in 1:8){
   if (yeo_johnson == T) {
-      rolling.data$SF_12 <- predict(mice.glmm.object, rolling.data, type='response',allow.new.levels=T)
+      #rolling.data$SF_12 <- predict(mice.glmm.object, rolling.data, type='response',allow.new.levels=T)
+      #rolling.data$SF_12 <- max_value - rolling_data$SF_12
+      rolling.data$SF_12 <- exp(predict(mice.glmm.object, rolling.data, type='response', allow.new.levels=T))-10
       rolling.data$SF_12_last <- rolling.data$SF_12                           
+      #rolling.data$SF_12 <- max_value - predict(yj,  rolling.data$SF_12 +min_value+ rnorm(nrow(rolling.data), 0, 0.3), inverse=T)
       rolling.data$SF_12 <- max_value - predict(yj,  rolling.data$SF_12 +min_value+ rnorm(nrow(rolling.data), 0, 0.3), inverse=T)
@@
   else {
-    rolling.data$SF_12 <- max_value - predict(mice.glmm.object, rolling.data, type='response',allow.new.levels=T) + rnorm(nrow(rolling.data), 0, 1)
+    #rolling.data$SF_12 <- max_value - predict(mice.glmm.object, rolling.data, type='response',allow.new.levels=T) + rnorm(nrow(rolling.data), 0, 1)
+    #rolling.data$SF_12 <- max_value - rolling.data$SF_12
+    rolling.data$SF_12 <- (exp(predict(mice.glmm.object, rolling.data, type='response',allow.new.levels=T))-10) + rnorm(nrow(rolling.data), 0, 0.01)
+
+    rd.mean <- median(rolling.data$SF_12, na.rm=T)
+    rolling.data$SF_12 <- rolling.data$SF_12 * 1.05
+    rolling.data$SF_12 <- rolling.data$SF_12 - ((1.05-1)*rd.mean)
     rolling.data$SF_12_last <- rolling.data$SF_12
-  }
-  #rolling.data$SF_12 <- max_value - rolling.data$SF_12
-  rolling.data$SF_12 <- trunc(rolling.data$SF_12, 0 , 100)
+
+  }
+  rolling.data$SF_12 <- max_value - rolling.data$SF_12
+  rolling.data$SF_12 <- rcpp_clip(rolling.data$SF_12, 0, 100)
   rolling.data[, 'time'] <- rolling.data[, 'time'] +1
   handover.data <- rbind(handover.data, rolling.data)
+  #rolling.data$SF_12 <- max_value - predict(yj,  rolling.data$SF_12 +min_value+ rnorm(nrow(rolling.data), 0, 0.3), inverse=T))
 }
@@
 ```
+
+```{r glmm_crossval}
+
+fit.glmm.to.each.fold <- function(mice.fold.data) {
+  sf12.glmm.model <- with(mice.fold.data, glmer(glmm_model_formula_string,  
+               nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes forever..
+               family=Gamma(link='log')#, weights=weight# gamma family with log link.
+               ))
+
+  sf12.glmm.pool <- pool(sf12.glmm.model)
+
+  # mice objects dont go in forest plot annoyingly. move coefficients over to a
+  # dummy lm that sjPlot::plot_models can read.
+  mice.glmm.object <- sf12.glmm.model$analyses[[1]]
+  mice.glmm.object@beta <- sf12.glmm.pool$pooled$estimate
+  #attr(mice.glmm.object, "beta") <- sf12.glmm.pool$estimate
+  #mice.glmm.object@ <- sf12.glmm.pool$std.error
+  #mice.glmm.object$coefficients[,3] <- sf12.glmm.pool$statistic
+  #mice.glmm.object$coefficients[,4] <- sf12.glmm.pool$p.value
+  print(r2_nakagawa(sf12.glmm.model$analyses[[1]]))
+return(mice.glmm.object)
+}
+
+#split mice sets into 5 based on pidps
+pidps <- complete(mice_set.subset, 1)$pidp
+pidp_chunks <- groupKFold(pidps, k=5)
+pidp_chunks1 <- unique(pidps[pidp_chunks$Fold1])
+pidp_chunks2 <- unique(pidps[pidp_chunks$Fold2])
+pidp_chunks3 <- unique(pidps[pidp_chunks$Fold3])
+pidp_chunks4 <- unique(pidps[pidp_chunks$Fold4])
+pidp_chunks5 <- unique(pidps[pidp_chunks$Fold5])
+# subset mice long based on these chunks. convert back to mids.
+
+# taking desired subset of pidps for each fold
+glmm.mice.long.subset.fold1 <- filter(glmm.mice.long.subset, !pidp %in% pidp_chunks1)
+glmm.mice.long.subset.fold2 <- filter(glmm.mice.long.subset, !pidp %in% pidp_chunks2)
+glmm.mice.long.subset.fold3 <- filter(glmm.mice.long.subset, !pidp %in% pidp_chunks3)
+glmm.mice.long.subset.fold4 <- filter(glmm.mice.long.subset, !pidp %in% pidp_chunks4)
+glmm.mice.long.subset.fold5 <- filter(glmm.mice.long.subset, !pidp %in% pidp_chunks5)
+
+# convert back to mice objects
+glmm.mice.set.fold1 <- as.mids2(glmm.mice.long.subset.fold1)
+glmm.mice.set.fold2 <- as.mids2(glmm.mice.long.subset.fold2)
+glmm.mice.set.fold3 <- as.mids2(glmm.mice.long.subset.fold3)
+glmm.mice.set.fold4 <- as.mids2(glmm.mice.long.subset.fold4)
+glmm.mice.set.fold5 <- as.mids2(glmm.mice.long.subset.fold5)
+
+# fit glmms.
+sf12.glmm.fold1 <- fit.glmm.to.each.fold(glmm.mice.set.fold1)
+sf12.glmm.fold2 <- fit.glmm.to.each.fold(glmm.mice.set.fold2)
+sf12.glmm.fold3 <- fit.glmm.to.each.fold(glmm.mice.set.fold3)
+sf12.glmm.fold4 <- fit.glmm.to.each.fold(glmm.mice.set.fold4)
+sf12.glmm.fold5 <- fit.glmm.to.each.fold(glmm.mice.set.fold5)
+
+# get training sts.
+
+# taking desired subset of pidps for each fold
+glmm.mice.long.subset.test1 <- drop_na(filter(glmm.mice.long.subset, pidp %in% pidp_chunks1))
+glmm.mice.long.subset.test2 <- drop_na(filter(glmm.mice.long.subset, pidp %in% pidp_chunks2))
+glmm.mice.long.subset.test3 <- drop_na(filter(glmm.mice.long.subset, pidp %in% pidp_chunks3))
+glmm.mice.long.subset.test4 <- drop_na(filter(glmm.mice.long.subset, pidp %in% pidp_chunks4))
+glmm.mice.long.subset.test5 <- drop_na(filter(glmm.mice.long.subset, pidp %in% pidp_chunks5))
+
+#get RMSE.
+
+rmse2 <- function(preds, obs){
+  obs_minus_preds_squared <- (preds - obs)**2
+  out <- sqrt(sum(obs_minus_preds_squared/nrow(glmm.mice.long.subset.test1)))
+  return (out)
+}
+
+RMSE1 <- rmse2(predict(sf12.glmm.fold1, glmm.mice.long.subset.test1, type='response', allow.new.levels=T),
+               log(glmm.mice.long.subset.test1$SF_12+10))
+RMSE2 <- rmse2(predict(sf12.glmm.fold2, glmm.mice.long.subset.test2, type='response', allow.new.levels=T),
+               log(glmm.mice.long.subset.test2$SF_12+10))
+RMSE3 <- rmse2(predict(sf12.glmm.fold3, glmm.mice.long.subset.test3, type='response', allow.new.levels=T),
+               log(glmm.mice.long.subset.test3$SF_12+10))
+RMSE4 <- rmse2(predict(sf12.glmm.fold4, glmm.mice.long.subset.test4, type='response', allow.new.levels=T),
+               log(glmm.mice.long.subset.test4$SF_12+10))
+RMSE5 <- rmse2(predict(sf12.glmm.fold5, glmm.mice.long.subset.test5, type='response', allow.new.levels=T),
+               log(glmm.mice.long.subset.test5$SF_12+10))
+print(RMSE1)
+print(RMSE2)
+print(RMSE3)
+print(RMSE4)
+print(RMSE5)
+rmse_glmm_values <- c(RMSE1, RMSE2, RMSE3, RMSE4, RMSE5)
+mean(rmse_glmm_values)
+var(rmse_glmm_values)
+# about 0.15. still improves over mice
+```

### 2024-07-11 minos/validation/handovers.Rmd
Added reflection for SF_12 model and some other small things

@@
 #raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
-raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
-#raw.files <- list.files(here::here('data', 'scaled_scotland_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+#raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'scaled_scotland_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 
-out.path <- here::here('output', 'default_config/')
-#out.path <- here::here('output', 'scotland_scaled/')
+#out.path <- here::here('output', 'default_config/')
+out.path <- here::here('output', 'scotland_scaled/')
 base.dat <- read_singular_local_out(out.path, 'baseline', 
@@
 ```{r}
+# # Step 1: Filter for households with children
+# households_with_kids <- raw.dat %>%
+#   filter(nkids > 0) %>%
+#   select(hidp, time, hh_income) %>%
+#   distinct() %>%
+#   select(-hidp)
+# 
+# # Step 2: Calculate income quintiles
+# households_with_kids <- households_with_kids %>%
+#   group_by(time) %>%
+#   mutate(income_quintile = ntile(hh_income, 5)) %>%
+#   ungroup()
+# 
+# # Step 3: Count households within each income quintile per year
+# household_count_by_income_quintile <- households_with_kids %>%
+#   group_by(time, income_quintile) %>%
+#   summarise(n = n())
+# 
+# household_count_by_income_quintile
+```
+
+### Households With Children (Ethnic Group)
+
+```{r}
+raw.hhs_kids.ethnicity <- raw.dat %>%
+  filter(nkids > 0) %>%
+  select(hidp, time, hh_income, ethnicity) %>%  # Select relevant columns to reduce data size
+  distinct() %>%
+  group_by(time, ethnicity) %>%
+  summarise(n = n(), .groups = 'drop') %>%
+  mutate(source = 'final_US')
+
+base.hhs_kids.ethnicity <- base.dat %>%
+  filter(nkids > 0) %>%
+  select(hidp, time, hh_income, ethnicity) %>%  # Select relevant columns to reduce data size
+  distinct() %>%
+  group_by(time, ethnicity) %>%
+  summarise(n = n(), .groups = 'drop') %>%
+  mutate(source = 'baseline')
+
+combined <- rbind(raw.hhs_kids.ethnicity, base.hhs_kids.ethnicity)
+combined$ethnicity <- factor(combined$ethnicity)
+
+ggplot(combined, aes(x = time, y = n, group = ethnicity, color = ethnicity, fill = ethnicity)) +
+  geom_point() +
+  geom_line() +
+  geom_vline(xintercept = start.year) +
+  labs(title = 'Households with Children Count')
+```
+
+```{r}
+calculate_hh_proportions <- function(data, group.var) {
   # Step 1: Filter for households with children
-households_with_kids <- raw.dat %>%
+  households_with_kids <- data %>%
     filter(nkids > 0) %>%
-  select(hidp, time, hh_income) %>%
-  distinct() %>%
-  select(-hidp)
-
-# Step 2: Calculate income quintiles
-households_with_kids <- households_with_kids %>%
-  group_by(time) %>%
-  mutate(income_quintile = ntile(hh_income, 5)) %>%
-  ungroup()
-
-# Step 3: Count households within each income quintile per year
-household_count_by_income_quintile <- households_with_kids %>%
-  group_by(time, income_quintile) %>%
-  summarise(n = n())
-
-household_count_by_income_quintile
+    select(hidp, time, hh_income, .data[[group.var]]) %>%
+    distinct()
+
+  # Step 3: Count households within each income group per year
+  household_counts <- households_with_kids %>%
+    group_by(time, .data[[group.var]]) %>%
+    summarise(count = n(), .groups = 'drop')
+
+  # Step 4: Calculate total households with children per year
+  total_households_per_year <- households_with_kids %>%
+    group_by(time) %>%
+    summarise(total_count = n(), .groups = 'drop')
+
+  # Step 5: Calculate proportion of households in each group per year
+  household_proportions <- household_counts %>%
+    left_join(total_households_per_year, by = "time") %>%
+    mutate(proportion = count / total_count) %>%
+    select(time, .data[[group.var]], proportion)
+
+  return(household_proportions)
+}
+
+raw.hh_kids_prop <- calculate_hh_proportions(raw.dat, group.var = 'ethnicity')
+base.hh_kids_prop <- calculate_hh_proportions(base.dat, group.var = 'ethnicity')
+
+raw.hh_kids_prop$source <- 'final_US'
+raw.hh_kids_prop <- filter(raw.hh_kids_prop, time != start.year)
+base.hh_kids_prop$source <- 'baseline'
+
+combined <- rbind(raw.hh_kids_prop, base.hh_kids_prop)
+combined$ethnicity <- factor(combined$ethnicity)
+
+ggplot(combined, aes(x = time, y = proportion, group = ethnicity, color = ethnicity, fill = ethnicity)) +
+  geom_col() +
+  geom_vline(xintercept = start.year) +
+  labs(title = 'Households with Children Count')
 ```

### 2024-07-11 minos/transitions/estimate_longitudinal_transitions.R

@@ -117,13 +117,12 @@ run_longitudinal_models <- function(transitionDir_path, transitionSourceDir_path
       use.weights <- TRUE
     }
 
-    # if (dependent %in% c()) {  # 'SF_12_PCS', "SF_12_MCS"
-    #   do.reflect = TRUE # only SF12 continuous data is reflected to be left skewed.
-    # }
-    # else {
-    #   do.reflect=FALSE
-    # }
-    do.reflect=FALSE
+    if (dependent %in% c('SF_12', 'SF_12_PCS')) {  # 'SF_12_PCS', "SF_12_MCS"
+      do.reflect = TRUE # only SF12 continuous data is reflected to be left skewed.
+    }
+    else {
+      do.reflect=FALSE
+    }
 
     if (dependent %in% c("hh_income")) {  # "SF_12"
       do.yeo.johnson = T #
@@ -137,10 +136,10 @@ run_longitudinal_models <- function(transitionDir_path, transitionSourceDir_path
       do.log.transform <- F
     }
     
-    if (dependent %in% c('housing_quality', 'loneliness', 'neighbourhood_safety',
-                         'job_sec', 'financial_situation', 'behind_on_bills')) {
-      data[[dependent]] <- factor(data[[dependent]])
-    }
+    # if (dependent %in% c('housing_quality', 'loneliness', 'neighbourhood_safety',
+    #                      'job_sec', 'financial_situation', 'behind_on_bills')) {
+    #   data[[dependent]] <- factor(data[[dependent]])
+    # }
 
     # experimental ordinal long models. ignore.
     # if (mod.type == "ORDGEE") {

### 2024-07-16 minos/validation/handovers.Rmd

@@
 #raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
-#raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
-raw.files <- list.files(here::here('data', 'scaled_scotland_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+#raw.files <- list.files(here::here('data', 'scaled_scotland_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 
-#out.path <- here::here('output', 'default_config/')
-out.path <- here::here('output', 'scotland_scaled/')
+out.path <- here::here('output', 'default_config/')
+#out.path <- here::here('output', 'scotland_scaled/')
 base.dat <- read_singular_local_out(out.path, 'baseline', 

### 2024-07-16 minos/validation/handovers.Rmd
adding stuff to handovers plots. adding outcomes qaly plots.

--- 2024-06-26 minos/validation/handovers.Rmd
@@
 ```{r}
+
 # Read raw datafiles in
-#raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
-raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
-#raw.files <- list.files(here::here('data', 'scaled_scotland_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+#raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'scaled_manchester_aligned_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
-raw.dat <- raw.dat %>%
-  filter(weight > 0)
-
-out.path <- here::here('output', 'default_config/')
-#out.path <- here::here('output', 'scotland_scaled/')
-base.dat <- read_singular_local_out(out.path, 'baseline', 
-                                    drop.dead = TRUE, 
-                                    drop.zero.weight = TRUE)
-#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
+
+out.path <- here::here('output', 'energy_default_config/')
+out.path <- here::here('output', 'energy_manchester_scaled/')
+base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
 ```
@@
 ```{r}
-start.year <- 2020
 save.path <- here::here("plots", "handovers", 'default')
 create.if.not.exists(save.path)
-
-# Need to remove extra data from raw data after start year
-raw.dat <- raw.dat %>%
-  filter(time <= start.year)
+start.year <- 2020
+# make sure we only overlap on one year for now or else tomfoolery happens. (the plots look bad).
+# we may want this overlap in the future? probably not.
+raw.dat <- raw.dat[which(raw.dat$time <= start.year), ]
+base.dat <- base.dat[which(base.dat$time>=start.year), ]
 
@@
 
-# DEMOGRAPHICS
-
-## Age Structure
-
-```{r}
-# assign to age_bucket in raw data
-cut_bins <- c(-1, 15, 19, 24, 29, 44, 59, 74, 200)
-cut_labels <- c("0to15", "16to19", "20to24", "25to29", "30to44", "45to59", "60to74", "75plus")
-
-raw.dat$age_bucket <- cut(raw.dat$age, 
-                          breaks = cut_bins, 
-                          labels = cut_labels)
-
-handover_ordinal(raw.dat, base.dat, var = 'age_bucket', save = shall.we.save)
-```
-
-## Age Structure (Households with Children)
-
-```{r}
-raw.dat_fam <- raw.dat %>%
-  filter(nkids > 0)
-
-base.dat_fam <- base.dat %>%
-  filter(nkids > 0)
-
-empty.dat <- raw.dat %>%
-  filter(age > 150)
-
-handover_ordinal(raw.dat_fam, base.dat_fam, var = 'age_bucket', save = shall.we.save)
-handover_ordinal(empty.dat, base.dat_fam, var = 'age_bucket', save = shall.we.save)
-```
-
-## Max Age
-
-```{r}
-raw.maxAge <- raw.dat %>%
-  group_by(time) %>%
-  summarise(max_age = max(age)) %>%
-  mutate(scen = 'final_US')
-
-base.maxAge <- base.dat %>%
-  group_by(time) %>%
-  summarise(max_age = max(age)) %>%
-  mutate(scen = 'baseline')
-
-combined <- rbind(raw.maxAge, base.maxAge)
-
-#handover_lineplots(raw.maxAge, base.maxAge, 'max_age')
-ggplot(combined, aes(x = time, y = max_age, group = scen, colour = scen)) +
-  geom_line() +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
-  labs(title = 'Max year of age') +
-  xlab('Year') +
-  ylab('Age')
-
-## Check counts in very old age groups
-brks = c(75, 80, 85, 90, 95, 100, 105, 110)
-lbls = c("75to80", "80to85", "85to90", "90to95", "95to100", "100to105", "105to110")
-
-raw.countOldAge <- raw.dat %>%
-  filter(age > 75) %>%
-  mutate(age_group = cut(age,
-                         breaks = brks,
-                         labels = lbls)) %>%
-  group_by(time, age_group) %>%
-  summarise(age_group_counts = n()) %>%
-  mutate(source = 'observed')
-
-base.countOldAge <- base.dat %>%
-  filter(age > 75) %>%
-  mutate(age_group = cut(age,
-                         breaks = brks,
-                         labels = lbls)) %>%
-  group_by(time, age_group) %>%
-  summarise(age_group_counts = n()) %>%
-  mutate(source = 'predicted')
-
-combined <- rbind(raw.countOldAge, base.countOldAge)
-
-ggplot(combined, aes(x = time, y = age_group_counts, group = age_group, colour = age_group)) +
-  geom_line() +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
-  labs(title = 'Counts by older age group', subtitle = '75 to 110 by 5 year groups') +
-  xlab('Year') +
-  ylab('Count')
-
-raw.countOldAge <- raw.dat %>%
-  filter(age > 75) %>%
-  mutate(age_group = cut(age,
-                         breaks = brks,
-                         labels = lbls))
-
-base.countOldAge <- base.dat %>%
-  filter(age > 75) %>%
-  mutate(age_group = cut(age,
-                         breaks = brks,
-                         labels = lbls))
-
-handover_ordinal(raw.countOldAge, base.countOldAge, var = 'age_group', save = shall.we.save)
-
-```
-
-```{r}
-# Having a go at an age pyramid, hopefully animated
-
-brks = c(75, 80, 85, 90, 95, 100, 105, 110)
-lbls = c("75to80", "80to85", "85to90", "90to95", "95to100", "100to105", "105to110")
-
-var <- 'age_group'
-
-# start with calculating percentages
-#raw.oldAgePct
-#base.oldAgePct
-
-raw.oldAgePct <- raw.dat %>%
-  filter(age > 75) %>%
-  mutate(age_group = cut(age,
-                         breaks = brks,
-                         labels = lbls)) %>%
-  dplyr::select(time, age_group) %>%
-  group_by(time, age_group) %>%
-  count() %>%
-  mutate(source = 'predicted')
-
-base.oldAgePct <- base.dat %>%
-  filter(age > 75) %>%
-  mutate(age_group = cut(age,
-                         breaks = brks,
-                         labels = lbls)) %>%
-  dplyr::select(time, all_of(var)) %>%
-  #filter(!.data[[var]] %in% miss.values) %>%
-  group_by(time, .data[[var]]) %>%
-  count() %>%
-  mutate(source = 'observed')
-
-raw.oldAgePct[[var]] <- as.factor(raw.oldAgePct[[var]])
-base.oldAgePct[[var]] <- as.factor(base.oldAgePct[[var]])
-
-merged <- rbind(raw.oldAgePct, base.oldAgePct)
-merged[[var]] <- as.factor(merged[[var]])
-
-var.norm <- merged %>%
-    group_by(time) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prct = (n / total) * 100)
-```
-
-## Population Counts
-
-### Total Pop
-
-```{r}
-raw.alive <- raw.dat %>%
-  group_by(time) %>%
+# PATHWAYS
+
+## SF_12_PCS
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'SF_12_PCS')
+handover_lineplots(raw.dat, base.dat, "SF_12_PCS")
+```
+
+### Spaghetti
+
+```{r}
+raw.sf12.p <- raw.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+base.sf12.p <- base.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+
+sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)
+
+spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(sf12.p.spag, "SF_12_PCS", 
+               save = shall.we.save, 
+               save.path = save.path)
+
+rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
+```
+
+## Physical Activity
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
+
+raw.2020.phys <- raw.dat %>% 
+  filter(time == 2020) %>%
+  group_by(active) %>%
   summarise(n = n()) %>%
-  mutate(scen = 'final_US')
-
-base.alive <- base.dat %>%
-  group_by(time) %>%
+  mutate(prop = n / sum(n))
+```
+
+## Alcohol (AUDITC)
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
+
+raw.2020.alc <- raw.dat %>% 
+  filter(time == 2020) %>%
+  group_by(auditc) %>%
   summarise(n = n()) %>%
-  mutate(scen = 'baseline')
-
-#handover_boxplots(raw.alive, base.alive, 'n')
-#handover_lineplots(raw.alive, base.alive, "n")
-
-combined <- rbind(raw.alive, base.alive)
-
-ggplot(combined, aes(x = time, y = n, group = scen, color = scen, fill = scen)) +
-  geom_line() +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
-  labs(title = 'Total Count in Sample') +
-  xlab('Year') +
-  ylab('Count')
-
-rm(raw.alive, base.alive)
-```
-
-### Households
-
-```{r}
-raw.hhs <- raw.dat %>%
-  select(hidp, time) %>%
-  distinct() %>%
-  group_by(time) %>%
-  summarise(n = n()) %>%
-  mutate(source = 'final_US')
-
-base.hhs <- base.dat %>%
-  select(hidp, time) %>%
-  distinct() %>%
-  group_by(time) %>%
-  summarise(n = n()) %>%
-  mutate(source = 'baseline')
-
-combined <- rbind(raw.hhs, base.hhs)
-
-ggplot(combined, aes(x = time, y = n, group = source, color = source, fill = source)) +
-  geom_point() +
-  geom_line() +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
-  labs(title = 'Households Count')
-```
-
-### Households With Children
-
-```{r}
-raw.household_count_by_year <- raw.dat %>%
-  filter(nkids > 0) %>%
-  select(hidp, time) %>%  # Select relevant columns to reduce data size
-  distinct() %>%
-  group_by(time) %>%
-  summarise(n = n()) %>%
-  mutate(source = 'final_US')
-
-base.household_count_by_year <- base.dat %>%
-  filter(nkids > 0) %>%
-  select(hidp, time) %>%  # Select relevant columns to reduce data size
-  distinct() %>%
-  group_by(time) %>%
-  summarise(n = n()) %>%
-  mutate(source = 'baseline')
-
-combined <- rbind(raw.household_count_by_year, base.household_count_by_year)
-
-ggplot(combined, aes(x = time, y = n, group = source, color = source, fill = source)) +
-  geom_point() +
-  geom_line() +
-  labs(title = 'Households with Children Count')
-```
-
-### Households With Children (Income Quintile)
-
-```{r}
-raw.hhs_kids.income_quint <- raw.dat %>%
-  filter(nkids > 0) %>%
-  select(hidp, time, hh_income) %>%  # Select relevant columns to reduce data size
-  distinct() %>%
-  mutate(income_group = case_when(
-    hh_income <= 1000 ~ "<= 1000",
-    hh_income <= 1500 ~ "1001 - 1500",
-    hh_income <= 2000 ~ "1501 - 2000",
-    hh_income <= 2500 ~ "2001 - 2500",
-    hh_income > 2500  ~ "> 2500"
-  )) %>%
-  group_by(time, income_group) %>%
-  summarise(n = n(), .groups = 'drop') %>%
-  mutate(source = 'final_US')
-
-base.hhs_kids.income_quint <- base.dat %>%
-  filter(nkids > 0) %>%
-  select(hidp, time, hh_income) %>%  # Select relevant columns to reduce data size
-  distinct() %>%
-  mutate(income_group = case_when(
-    hh_income <= 1000 ~ "<= 1000",
-    hh_income <= 1500 ~ "1001 - 1500",
-    hh_income <= 2000 ~ "1501 - 2000",
-    hh_income <= 2500 ~ "2001 - 2500",
-    hh_income > 2500  ~ "> 2500"
-  )) %>%
-  group_by(time, income_group) %>%
-  summarise(n = n(), .groups = 'drop') %>%
-  mutate(source = 'baseline')
-
-combined <- rbind(raw.hhs_kids.income_quint, base.hhs_kids.income_quint)
-combined$income_group <- factor(combined$income_group)
-
-ggplot(combined, aes(x = time, y = n, group = income_group, color = income_group, fill = income_group)) +
-  geom_point() +
-  geom_line() +
-  geom_vline(xintercept = start.year) +
-  labs(title = 'Households with Children Count')
-```
-
-#### Proportions
-
-```{r}
-calculate_hh_proportions <- function(data) {
-  # Step 1: Filter for households with children
-  households_with_kids <- data %>%
-    filter(nkids > 0) %>%
-    select(hidp, time, hh_income) %>%
-    distinct()
-
-  # Step 2: Create income group based on thresholds
-  households_with_kids <- households_with_kids %>%
-    mutate(income_group = case_when(
-      hh_income <= 1000 ~ "<= 1000",
-      hh_income <= 1500 ~ "1001 - 1500",
-      hh_income <= 2000 ~ "1501 - 2000",
-      hh_income <= 2500 ~ "2001 - 2500",
-      hh_income > 2500  ~ "> 2500"
-    ))
-
-  # Step 3: Count households within each income group per year
-  household_counts <- households_with_kids %>%
-    group_by(time, income_group) %>%
-    summarise(count = n(), .groups = 'drop')
-
-  # Step 4: Calculate total households with children per year
-  total_households_per_year <- households_with_kids %>%
-    group_by(time) %>%
-    summarise(total_count = n(), .groups = 'drop')
-
-  # Step 5: Calculate proportion of households in each group per year
-  household_proportions <- household_counts %>%
-    left_join(total_households_per_year, by = "time") %>%
-    mutate(proportion = count / total_count) %>%
-    select(time, income_group, proportion)
-
-  return(household_proportions)
-}
-
-raw.hh_kids_prop <- calculate_hh_proportions(raw.dat)
-base.hh_kids_prop <- calculate_hh_proportions(base.dat)
-
-raw.hh_kids_prop$source <- 'final_US'
-raw.hh_kids_prop <- filter(raw.hh_kids_prop, time != start.year)
-base.hh_kids_prop$source <- 'baseline'
-
-combined <- rbind(raw.hh_kids_prop, base.hh_kids_prop)
-combined$income_group <- factor(combined$income_group)
-
-ggplot(combined, aes(x = time, y = proportion, group = income_group, color = income_group, fill = income_group)) +
-  geom_col() +
-  geom_vline(xintercept = start.year) +
-  labs(title = 'Households with Children Count')
-```
-
-```{r}
-# Step 1: Filter for households with children
-households_with_kids <- raw.dat %>%
-  filter(nkids > 0) %>%
-  select(hidp, time, hh_income) %>%
-  distinct() %>%
-  select(-hidp)
-
-# Step 2: Calculate income quintiles
-households_with_kids <- households_with_kids %>%
-  group_by(time) %>%
-  mutate(income_quintile = ntile(hh_income, 5)) %>%
-  ungroup()
-
-# Step 3: Count households within each income quintile per year
-household_count_by_income_quintile <- households_with_kids %>%
-  group_by(time, income_quintile) %>%
-  summarise(n = n())
-
-household_count_by_income_quintile
-```
-
-# PATHWAYS
+  mutate(prop = n / sum(n))
+
+```
 
@@
 handover_lineplots(raw.dat, base.dat, "hh_income")
-
-handover_boxplots(raw.dat, base.dat, 'hh_income_diff')
-handover_lineplots(raw.dat, base.dat, "hh_income_diff")
-# handover_boxplots(raw.dat, base.dat, 'council_tax')
-# handover_lineplots(raw.dat, base.dat, "council_tax")
-
-handover_boxplots(base.dat, base.dat, 'hh_income_diff')
-handover_lineplots(base.dat, base.dat, "hh_income_diff")
 ```
@@
 raw.inc <- raw.dat %>%
-  select(pidp, age, time, hh_income, hh_income_diff)
+  select(pidp, age, time, hh_income)
 base.inc <- base.dat %>%
-  select(pidp, age, time, hh_income, hh_income_diff)
+  select(pidp, age, time, hh_income)
 
@@
 
-spaghetti_plot(income.spag.sample, 'hh_income_diff',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(income.spag.sample, 'hh_income_diff',
-               save = shall.we.save,
-               save.path = save.path)
-
-# spaghetti_plot(base.inc, 'hh_income',
-#                save = shall.we.save,
-#                save.path = save.path)
-
 rm(raw.inc, base.inc, income.spag)
@@
 
-### Poverty Thresholds
-
-#### Relative
-```{r}
-rel.threshold.raw <- raw.dat %>%
-  select(time, weight, hh_income) %>%
-  group_by(time) %>%
-  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
-
-rel.threshold.base <- base.dat %>%
-  select(time, weight, hh_income) %>%
-  group_by(time) %>%
-  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6)) %>%
-  filter(time != 2021)
-
-rel.threshold <- rbind(rel.threshold.raw, rel.threshold.base)
-
-ggplot(data = rel.threshold, aes(x = time, y = poverty_threshold)) +
-  geom_col() +
-  geom_hline(yintercept = rel.threshold$poverty_threshold[rel.threshold$time == 2020], linetype='dotted') +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
-  labs(title = 'Relative poverty threshold over time') +
-  xlab('Year') +
-  ylab('Threshold')
-#rm(rel.threshold)
-```
-
-#### Absolute
-```{r}
-# raw.2010 <- raw.dat %>%
-#   filter(time == 2010)
-# 
-# abs.threshold <- weighted.median(x = raw.2010$hh_income, 
-#                                  w = raw.2010$weight, 
-#                                  na.rm = TRUE)
-# abs.threshold <- abs.threshold * 0.6
-# 
-# print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
+## Net Income & Rent & Mortgage
+
+```{r yearly_energy}
+# get required variables. 
+raw.inc <- raw.dat %>%
+  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
+base.inc <- base.dat %>%
+  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
+
+# net household income. 
+handover_boxplots(raw.inc, base.inc, 'net_hh_income')
+handover_lineplots(raw.inc, base.inc, "net_hh_income")
+inc.spag<-rbind(raw.inc, base.inc)
+density_ridges(inc.spag, 'net_hh_income',
+               save=TRUE, 
+               save.path=save.path)
+
+# rent
+handover_boxplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], 'hh_rent')
+handover_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
+density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
+               save=TRUE, 
+               save.path=save.path)
+
+# mortgage
+handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], 'hh_mortgage')
+handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
+density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
+               save=TRUE, 
+               save.path=save.path)
+
+#council tax
+handover_boxplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], 'council_tax')
+handover_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
+density_ridges(inc.spag[which(inc.spag$council_tax>1), ], 'council_tax',
+               save=TRUE, 
+               save.path=save.path)
+
+# oecd equivalence scale. (NOT TRANSITIONED YET. REQUIRES LEAVING THE NEST MODULE.. )
+handover_boxplots(raw.inc, base.inc, 'oecd_equiv')
+handover_lineplots(raw.inc, base.inc, 'oecd_equiv')
+density_ridges(inc.spag, 'oecd_equiv',
+               save=TRUE, 
+               save.path=save.path)
+
+# tidy up.
+rm(raw.inc, base.inc, inc.spag)
+```
+
+## Yearly energy
+
+```{r net_income}
+# get required variables. 
+raw.energy <- raw.dat %>%
+  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)
+base.energy <- base.dat %>%
+  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)
+
+# gas expenditure
+handover_boxplots(raw.energy, base.energy, 'yearly_gas')
+handover_lineplots(raw.energy, base.energy, "yearly_gas")
+#inc.spag<-rbind(raw.inc, base.inc)
+#density_ridges(inc.spag, 'yearly_gas',
+#               save=TRUE, 
+#               save.path=save.path)
+
+# yearly electric
+handover_boxplots(raw.energy, base.energy, 'yearly_electric')
+handover_lineplots(raw.energy, base.energy, "yearly_electric")
+#density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
+#               save=TRUE, 
+#               save.path=save.path)
+
+# yearly energy
+handover_boxplots(raw.energy, base.energy, 'yearly_energy')
+handover_lineplots(raw.energy, base.energy, "yearly_energy")
+#density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
+#               save=TRUE, 
+#               save.path=save.path)
+
+# tidy up.
+rm(raw.energy, base.energy)#, inc.spag)
 ```
@@
 handover_lineplots(raw.dat, base.dat, "SF_12")
-
-handover_boxplots(raw.dat, base.dat, 'SF_12_diff')
-handover_lineplots(raw.dat, base.dat, "SF_12_diff")
-
+# 
+# raw.sf12 <- raw.dat %>% 
+#   dplyr::select(pidp, time, SF_12) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.sf12 <- base.dat %>%
+#   dplyr::select(pidp, time, SF_12) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# # merge before plot
+# sf12 <- rbind(raw.sf12, base.sf12)
+# 
+# # Now plot
+# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+#   geom_smooth() +
+#   #geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
+#   xlab('Year') +
+#   ylab('SF12')
+# 
+# ## Try a version where final_US is limited to only those present from wave 1 
+# # onwards because the sample refreshments are messing with the plot
+# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+# 
+# raw.sf12.2 <- raw.dat %>% 
+#   dplyr::select(pidp, time, SF_12) %>%
+#   filter(pidp %in% raw.sf12.wave1) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.sf12.2 <- base.dat %>%
+#   dplyr::select(pidp, time, SF_12) %>%
+#   filter(pidp %in% raw.sf12.wave1) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
+# 
+# # Now plot
+# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+#   geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
+#   xlab('Year') +
+#   ylab('SF12')
+# 
+# if (shall.we.save) {
+#   ggsave(filename = 'SF12_wav1.png',
+#        plot = last_plot(),
+#        path = save.path)
+# }
+# 
+# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
 ```
@@
 raw.sf12 <- raw.dat %>%
-  select(pidp, age, time, SF_12, SF_12_diff)
+  select(pidp, age, time, SF_12)
 base.sf12 <- base.dat %>%
-  select(pidp, age, time, SF_12, SF_12_diff)
+  select(pidp, age, time, SF_12)
 
@@
 
-spaghetti_plot(sf12.spag.sample, 'SF_12_diff',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_diff',
-               save = shall.we.save,
-               save.path = save.path)
-
 density_ridges(sf12.spag, "SF_12", 
@@
 rm(raw.sf12, base.sf12, sf12.spag)
+```
+
+## Financial Situation
+
+```{r}
+raw.financial_situation <- raw.dat %>%
+  dplyr::select(pidp, time, financial_situation) %>%
+  group_by(time, financial_situation) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.financial_situation <- base.dat %>%
+  dplyr::select(pidp, time, financial_situation) %>%
+  group_by(time, financial_situation) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+financial_situation <- rbind(raw.financial_situation, base.financial_situation)
+financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
+
+# Now plot
+ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+financial_situation.norm <- financial_situation %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Financial situation') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'financial_situation.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
 ```
@@
 
+## Education
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Education State'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'education_state.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.dat,
+                                       df1.name = 'simulated',
+                                       df2 = raw.dat,
+                                       df2.name = 'raw',
+                                       var = 'education_state')
+
+cv_ordinal_plots(pivoted.df = pivoted,
+                 var = 'education_state',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, education_state)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, education_state)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'education_state',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
+```
+
+## nkids Household
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'nkids')
+handover_lineplots(raw.dat, base.dat, 'nkids')
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, nkids)
+base.s <- base.dat %>%
+  select(pidp, age, time, nkids)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nkids',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+## nkids Max
+
+```{r}
+# first figure out how to plot final_US
+# start with hh_income
+raw.nkids_max <- raw.dat %>%
+  dplyr::select(pidp, time, nkids) %>%
+  group_by(time) %>%
+  summarise(max_nkids = max(nkids)) %>%
+  mutate(source = 'final_US')
+
+base.nkids_max <- base.dat %>%
+  dplyr::select(pidp, time, nkids) %>%
+  group_by(time) %>%
+  summarise(max_nkids = max(nkids)) %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+max_nkids <- rbind(raw.nkids_max, base.nkids_max)
+
+# Now plot
+ggplot(data = max_nkids, mapping = aes(x = time, y = max_nkids, group = source, colour = source)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Max nkids', subtitle = 'Full Sample') +
+  xlab('Year') +
+  ylab('Average')
+```
+
+## Parity
+
+```{r}
+base.parity <- base.dat %>%
+  filter(sex == "Female")
+
+raw.parity <- raw.dat %>%
+  filter(sex == "Female")
+
+prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Parity (total no. of children)'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'parity.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+```{r}
+pivoted <- combine_and_pivot_long(df1 = base.parity,
+                                  df1.name = 'simulated', 
+                                  df2 = raw.parity, 
+                                  df2.name = 'raw', 
+                                  var = 'nkids_ind')
+
+cv_ordinal_plots(pivoted.df = pivoted, 
+                 var = 'nkids_ind',
+                 save = shall.we.save,
+                 save.path = save.path)
+```
+
+### Spaghetti
+
+```{r}
+raw.s <- raw.parity %>%
+  select(pidp, age, time, nkids_ind)
+base.s <- base.parity %>%
+  select(pidp, age, time, nkids_ind)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nkids_ind',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+## Hourly Wage
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'hourly_wage')
+handover_lineplots(raw.dat, base.dat, 'hourly_wage')
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, hourly_wage)
+base.s <- base.dat %>%
+  select(pidp, age, time, hourly_wage)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+# now a version limited to 0-100
+spag <- spag %>%
+  filter(hourly_wage <= 300)
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+```{r}
+# some basic statistics about hourly_wage variable
+print("Some basic statistics on hourly_wage. These are all for 2020.")
+raw.2020 <- raw.dat %>% filter(time == 2020)
+print('All living people in 2020')
+print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
+# number individuals with an hourly_wage > 0
+print('People not in work')
+print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
+
+# Number in work
+print('People in work')
+print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
+print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
+
+# Extreme hourly_wage values
+print('Extreme hourly wage values: HIGH')
+print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
+print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
+print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
+print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
+print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
+print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
+
+raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
+print('Extreme hourly wage values: LOW (non-zero)')
+print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
+print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
+print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
+print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
+```
+
 ## S7 Labour State
@@
                  save.path = save.path)
-```
-
-# ADDITIONAL VARIABLES
-
-## Education
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Education State'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'education_state.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat,
-                                       df1.name = 'simulated',
-                                       df2 = raw.dat,
-                                       df2.name = 'raw',
-                                       var = 'education_state')
-
-cv_ordinal_plots(pivoted.df = pivoted,
-                 var = 'education_state',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, education_state)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, education_state)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'education_state',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
-
-## Financial Situation
-
-```{r}
-raw.financial_situation <- raw.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.financial_situation <- base.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-financial_situation <- rbind(raw.financial_situation, base.financial_situation)
-financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
-
-# Now plot
-ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-financial_situation.norm <- financial_situation %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial situation') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'financial_situation.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
-```
-
-## Behind On Bills
-
-```{r}
-raw.behind_on_bills <- raw.dat %>%
-  dplyr::select(pidp, time, behind_on_bills) %>%
-  group_by(time, behind_on_bills) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.behind_on_bills <- base.dat %>%
-  dplyr::select(pidp, time, behind_on_bills) %>%
-  group_by(time, behind_on_bills) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-behind_on_bills <- rbind(raw.behind_on_bills, base.behind_on_bills)
-behind_on_bills$behind_on_bills <- as.factor(behind_on_bills$behind_on_bills)
-
-# Now plot
-ggplot(data = behind_on_bills, mapping = aes(x = time, y = n, group = behind_on_bills, colour = behind_on_bills)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Behind On Bills', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-behind_on_bills.norm <- behind_on_bills %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = behind_on_bills.norm, mapping = aes(x = time, y = prct, fill=behind_on_bills)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Behind On Bills') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'behind_on_bills.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.behind_on_bills, base.behind_on_bills, behind_on_bills, behind_on_bills.norm)
-```
-
-## nkids Household
-
-```{r}
-raw.hh_unique <- raw.dat %>%
-  select(hidp, time, nkids, weight) %>%
-  distinct(hidp, time, nkids, .keep_all = TRUE) %>%
-  mutate(scen = 'final_US')
-
-base.hh_unique <- base.dat %>%
-  select(hidp, time, nkids, weight) %>%
-  distinct(hidp, time, nkids, .keep_all = TRUE) %>%
-  mutate(scen = 'baseline')
-
-#handover_boxplots(raw.hh_unique, base.hh_unique, 'nkids')
-handover_lineplots(raw.hh_unique, base.hh_unique, 'nkids')
-
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, nkids)
-base.s <- base.dat %>%
-  select(pidp, age, time, nkids)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## nkids Max
-
-```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.nkids_max <- raw.dat %>%
-  dplyr::select(pidp, time, nkids) %>%
-  group_by(time) %>%
-  summarise(max_nkids = max(nkids)) %>%
-  mutate(source = 'final_US')
-
-base.nkids_max <- base.dat %>%
-  dplyr::select(pidp, time, nkids) %>%
-  group_by(time) %>%
-  summarise(max_nkids = max(nkids)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-max_nkids <- rbind(raw.nkids_max, base.nkids_max)
-
-# Now plot
-ggplot(data = max_nkids, mapping = aes(x = time, y = max_nkids, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Max nkids', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Average')
-```
-
-## Parity
-
-```{r}
-base.parity <- base.dat %>%
-  filter(sex == "Female")
-
-raw.parity <- raw.dat %>%
-  filter(sex == "Female")
-
-prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Parity (total no. of children)'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'parity.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.parity,
-                                  df1.name = 'simulated', 
-                                  df2 = raw.parity, 
-                                  df2.name = 'raw', 
-                                  var = 'nkids_ind')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'nkids_ind',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.parity %>%
-  select(pidp, age, time, nkids_ind)
-base.s <- base.parity %>%
-  select(pidp, age, time, nkids_ind)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids_ind',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## Hourly Wage
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'hourly_wage')
-handover_lineplots(raw.dat, base.dat, 'hourly_wage')
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, hourly_wage)
-base.s <- base.dat %>%
-  select(pidp, age, time, hourly_wage)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-# now a version limited to 0-100
-spag <- spag %>%
-  filter(hourly_wage <= 300)
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
 ```
@@
 
-combined$expanded_child_ages <- factor(combined$expanded_child_ages,
-                                       levels = c('0', '1', '2', '3', '4', '5', 
-                                                  '6', '7', '8', '9', '10', 
-                                                  '11', '12', '13', '14', '15', 
-                                                  '16', 'childless'))
-
 ggplot(data = combined, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
@@
 
-ggplot(data = combined, mapping = aes(x = expanded_child_ages, y = age_counts, group = factor(time), colour = factor(time))) +
+ggplot(data = combined, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
   geom_line() +
@@
   scale_colour_viridis_d() +
-  xlab('Age') +
+  xlab('Year') +
   ylab('Count')
@@
 
-combined.nkids
-
-```
-
-```{r}
-
-```
+```
+
+## Number of cars
+
+```{r ncars}
+
+raw.ncars <- raw.dat
+base.ncars <- base.dat
+raw.ncars[raw.ncars$ncars>=10, 'ncars'] <- "More than 9."
+base.ncars[base.ncars$ncars>=10, 'ncars'] <- "More than 9."
+
+raw.ncars <- raw.ncars %>%
+  dplyr::select(pidp, time, ncars) %>%
+  filter(ncars >= 0) %>%
+  group_by(time, ncars) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.ncars <- base.ncars %>%
+  dplyr::select(pidp, time, ncars) %>%
+  filter(ncars >= 0) %>%
+  group_by(time, ncars) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+base.ncars$ncars <- as.character(base.ncars$ncars) # cast from int to str. 
+ncars <- rbind(raw.ncars, base.ncars)
+ncars$ncars <- as.factor(ncars$ncars)
+
+# Now plot
+ggplot(data = ncars, mapping = aes(x = time, y = n, group = ncars, colour = ncars)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Number of Cars', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ncars.norm <- ncars %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = ncars.norm, mapping = aes(x = time, y = prct, group = ncars, colour = ncars)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Number of Cars', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = ncars.norm, mapping = aes(x = time, y = prct, fill=ncars)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Number of Cars') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'ncars.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.ncars, base.ncars, ncars, ncars.norm)
+```
+
+## ncigs
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'ncigs')
+handover_lineplots(raw.dat, base.dat, "ncigs")
+raw.ncigs <- raw.dat %>%
+  select(pidp, age, time, ncigs)
+base.ncigs <- base.dat %>%
+  select(pidp, age, time, ncigs)
+ncigs.spag <- rbind(raw.ncigs, base.ncigs)
+shall.we.save <- F
+pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/10, replace=FALSE)
+ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+
+zip_density_ridges(ncigs.spag, "ncigs", 
+               save = shall.we.save, 
+               save.path = save.path)
+rm(raw.ncigs, base.ncigs, ncigs.spag)
+```
+
+## ncigs non-zero
+
+```{r}
+
+raw.ncigs <- raw.dat %>%
+  filter(ncigs>0) %>%
+  select(pidp, age, time, ncigs)
+base.ncigs <- base.dat %>%
+  filter(ncigs>0) %>%
+  select(pidp, age, time, ncigs)
+
+ncigs.spag <- rbind(raw.ncigs, base.ncigs) # get all smokers.
+shall.we.save <- F
+pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/100, replace=FALSE)
+ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+
+zip_density_ridges(ncigs.spag, "ncigs", 
+               save = shall.we.save, 
+               save.path = save.path)
+rm(raw.ncigs, base.ncigs, ncigs.spag)
+```

### 2024-07-23 minos/validation/handovers.Rmd
Added spaghetti plots for pathway variables back to handovers

--- 2024-07-16 minos/validation/handovers.Rmd
@@
 ```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, housing_quality)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, housing_quality)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'housing_quality',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+raw.s <- raw.dat %>%
+  select(pidp, age, time, housing_quality)
+base.s <- base.dat %>%
+  select(pidp, age, time, housing_quality)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'housing_quality',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, neighbourhood_safety)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, neighbourhood_safety)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'neighbourhood_safety',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+raw.s <- raw.dat %>%
+  select(pidp, age, time, neighbourhood_safety)
+base.s <- base.dat %>%
+  select(pidp, age, time, neighbourhood_safety)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'neighbourhood_safety',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-# raw.nut <- raw.dat %>%
-#   select(pidp, age, time, nutrition_quality)
-# base.nut <- base.dat %>%
-#   select(pidp, age, time, nutrition_quality)
-# 
-# nut.spag <- rbind(raw.nut, base.nut)
-# 
-# spaghetti_plot(nut.spag, 'nutrition_quality',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# 
-# density_ridges(nut.spag, "nutrition_quality", 
-#                save = T, 
-#                save.path = save.path)
-# 
-# rm(raw.nut, base.nut, nut.spag)
+raw.nut <- raw.dat %>%
+  select(pidp, age, time, nutrition_quality)
+base.nut <- base.dat %>%
+  select(pidp, age, time, nutrition_quality)
+
+nut.spag <- rbind(raw.nut, base.nut)
+
+spaghetti_plot(nut.spag, 'nutrition_quality',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(nut.spag, "nutrition_quality",
+               save = T,
+               save.path = save.path)
+
+rm(raw.nut, base.nut, nut.spag)
 ```

### 2024-07-25 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Added a new working directory for laptop plotting

@@
 ---
-title: "R Notebook"
+title: "SCP Briefing Plots - Combined Intervention"
 output:
-  pdf_document: default
   html_document:
+    toc: true
+    toc_float: true
+    collapsed: false
+    number_sections: true
     df_print: paged
+    code_folding: hide
+  pdf_document:
+    toc: true
 ---
@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"

### 2024-07-26 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Some different working directories in the combined child pov intervention runs

@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
-workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"

### 2024-07-26 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Minor changes to plot and legened titles and theme

@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"
 #workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/"
@@
   tit <- ' '
-  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
-  if (summary_group == 'families') { tit <- 'Families' }
-  if (summary_group == 'treated_relative') { tit <- 'Treated' }
-  if (summary_group == 'treated_absolute') { tit <- 'Treated' }
-  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
+  if (summary_group == 'whole_pop') { 
+    tit <- 'Whole Population'
+    plot_colour <- 'black'
+    }
+  if (summary_group == 'families') { 
+    tit <- 'Families'
+    plot_colour <- '#56B4E9'
+    }
+  if (summary_group == 'treated_relative') { 
+    tit <- 'Treated' }
+  if (summary_group == 'treated_absolute') { 
+    tit <- 'Treated' }
+  if (summary_group == 'priority_any') { 
+    tit <- 'Any Priority Subgroup' 
+    plot_colour <- 'black' }
 
@@
     geom_smooth() +
-    labs(title = tit) +
     xlab('Year') +
-    ylab('Change in SF-12')
+    ylab('Absolute Change in SF-12 MCS') +
+    theme_minimal()
 
@@
     geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed') +
-    geom_point() +
+    geom_line(linetype = 'dashed', color=plot_colour) +
+    geom_point(color=plot_colour) +
     geom_hline(yintercept = 0, linetype = 'dashed') +
     geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
     xlab('Year') +
-    ylab('Change in SF-12')
+    ylab('Absolute Change in SF-12 MCS') +
+    theme_minimal()
 
@@
   #print(p3)
+
+  ggsave(filename = paste0(summary_group, '_smooth', '.png'),
+         plot = p1)
+
+  ggsave(filename = paste0(summary_group, '_confint', '.png'),
+         plot = p2)
 }
@@
     xlab('Year') +
-    ylab('Change in SF-12')
+    ylab('Change in SF-12 MCS') +
+    theme_minimal()
 
   print(p1)
+
+  ggsave(filename = paste0(summary_group, '_trajectories', '.png'),
+         plot = p1)
 }
@@
     geom_smooth() +
-    labs(title = tit, subtitle = 'Income Quintile') +
     xlab('Year') +
-    ylab('Change in SF-12')
+    ylab('Change in SF-12 MCS') +
+    theme_minimal() +
+    guides(fill=guide_legend(title="Income Quintile"))
 
@@
     geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit, subtitle = 'Income Quintile') +
     xlab('Year') +
-    ylab('Change in SF-12')
+    ylab('Change in SF-12 MCS') +
+    theme_minimal() +
+    guides(fill=guide_legend(title="Income Quintile"))
 
@@
   print(p2)
+
+  ggsave(filename = paste0(summary_group, '_quintile_smooth', '.png'),
+         plot = p1)
+
+  ggsave(filename = paste0(summary_group, '_quintile_actual', '.png'),
+         plot = p2)
 }
@@
       geom_line(linetype = 'dashed') +
-      geom_point() +
+      geom_point(show.legend = FALSE) +
       geom_hline(yintercept = 0, linetype = 'dashed') +
       geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-      labs(title = tit, 
-           subtitle = 'Income Quintile') +
       xlab('Year') +
-      ylab('Change in mean SF-12')
+      ylab('Change in mean SF-12 MCS') +
+      theme_minimal() +
+      guides(fill=guide_legend(title="Income Quintile"),
+             linetype=guide_legend(title="Income Quintile"),
+             group=guide_legend(title="Income Quintile"),
+             color=guide_legend(title="Income Quintile"))
 
@@
   print(p2)
+
+  ggsave(filename = paste0(summary_group, '_quintile', '.png'),
+         plot = p2)
 }
@@
     geom_smooth() +
-    labs(title = tit) +
     xlab('Year') +
-    ylab('Change in SF-12')
+    ylab('Change in SF-12 MCS') +
+    theme_minimal() +
+    guides(group=guide_legend(title="Num Priority Subgroups"))
 
@@
     geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-    labs(title = tit) +
     xlab('Year') +
-    ylab('Change in SF-12')
+    ylab('Change in SF-12 MCS') +
+    theme_minimal() +
+    guides(group=guide_legend(title="Num Priority Subgroups"))
 
@@
   print(p2)
+
+  ggsave(filename = paste0(summary_group, '_smooth', '.png'),
+         plot = p1)
+
+  ggsave(filename = paste0(summary_group, '_actual', '.png'),
+         plot = p2)
 }
@@
          x = "Year",
-         y = "Difference in SF_12 Score") +
+         y = "Difference in SF_12 MCS") +
     theme_minimal() +
@@
   print(p2)
+
+  ggsave(filename = paste0(summary_group, '_inequality_line', '.png'),
+         plot = p1)
+
+  ggsave(filename = paste0(summary_group, '_inequality_bar', '.png'),
+         plot = p2)
 }
@@
     xlab('Year') +
-    ylab('Count')
+    ylab('Count') +
+    theme_minimal()
 
@@
     xlab('Year') +
-    ylab('Percentage')
+    ylab('Percentage') +
+    theme_minimal()
 
@@
   print(p2)
+
+  ggsave(filename = paste0(summary_group, '_count', '.png'),
+         plot = p1)
+
+  ggsave(filename = paste0(summary_group, '_proportion', '.png'),
+         plot = p2)
 }
@@
       geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-      labs(title = 'Treatment on the Treated',
+      labs(title = 'Treated Population',
            subtitle = 'SF_12') +
       xlab('Year') +
-      ylab('Change in mean SF-12')
+      ylab('Change in mean SF-12 MCS')
 
@@
       xlab('Year') +
-      ylab('Change in mean hh_income')
+      ylab('Change in mean Household Income')
 
@@
   print(p4)
+
+  ggsave(filename = paste0(summary_group, '_SF-12', '.png'),
+         plot = p2)
+
+  ggsave(filename = paste0(summary_group, '_hh-income', '.png'),
+         plot = p4)
 }
@@
   print(p1)
+
+  ggsave(filename = paste0('synthpop_uncertainty_', var, '.png'),
+         plot = p1)
+
 }
@@
 scen <- 'ChildPovertyReduction'
+```
+
+# MCS Change to QALY Example
+
+We use an equation derived from table 4 (below) in [this paper by Lawrence and Fleishman](https://pubmed.ncbi.nlm.nih.gov/15090102/) to calculate QALYs from SF-12 Mental Component Score (MCS) and Physical Component Score (PCS).
+
+#![L&F Table 4](L&F_table4.png)
+
+```{r}
+# formula to find the utility score from mean MCS and PCS scores of a population
+utility_score <- function(pcs, mcs) {
+  utility_score <- 
+    1.6984 + 
+    (pcs * 0.07927) +
+    (mcs * 0.02859) +
+    ((pcs * mcs) * -0.000126) +
+    ((pcs * pcs) * -0.00141) +
+    ((mcs * mcs) * -0.00014) +
+    ((pcs * pcs * pcs) * 0.0000107)
+  return(utility_score)
+}
+
+# Calculate utility score for hypothetical baseline (MCS & PCS == 45.0)
+initial_conditions <- utility_score(pcs = 45.0,
+                                    mcs = 45.0)
+# Calculate utility score for 0.1 improvement in MCS (MCS now == 45.1)
+intervention <- utility_score(pcs = 45.0,
+                              mcs = 45.1)
+
+print("Utility score for hypothetical baseline (assuming mean MCS and PCS both equal 45.0):")
+print(initial_conditions)
+print("Utility score for population given a 0.1 mean improvement in MCS:")
+print(intervention)
+
+print("Gain in utility score per person:")
+gain <- intervention - initial_conditions
+print(gain)
+
+print("Gain in utiliy for the total Scotland population (assuming 5.5m). This is equivalent to QALYs gained:")
+print(gain * 5510000)
+```
+
+This rough calculation shows that a 0.1 absolute change in mean SF_12 across the Scottish population would equal over 5000 additional QALYs in a single year.
+These improvements can also accumulate over time.
+If we were able to achieve a 0.1 improvement in mean MCS for Scotland in year 1, and maintain this 0.1 improvement for 10 years, the resulting improvement in QALYs would be 56,000+.
+
+NOTE: This calculation assumes that PCS is unchanged when MCS can vary. This is not realistic, but the calculation is still useful to provide context for the results to follow.
+
+# SAMPLE UNCERTAINTY
+
+When running MINOS with a synthetic population, due to the size of the synthetic populations and the demands of the model, we have to take a reduced sample as our starting population.
+For the Scotland synthetic runs we take a 10% sample, which reduces the population size from roughly 5.5m to 550,000.
+
+We therefore have to also account for the uncertainty in model outputs that comes from this reduced sample. As a somewhat temporary fix for this, we have done the following:
+
+- Generate 10 different 10% samples from our synthetic population
+  - Generate a replenishing population from each of these samples
+- Use each distinct 10% sample for 10 runs each, totalling 100 runs
+- Plot the local mean from each 10 run block, and the global mean from all 100 runs
+
+```{r}
+synthpop_uncertainty(summary_group = 'whole_pop',
+                     scen = 'baseline',
+                     var = 'hh_income')
+
+synthpop_uncertainty(summary_group = 'whole_pop',
+                     scen = 'baseline',
+                     var = 'SF_12')
 ```

### 2024-08-01 minos/transitions/energy_price_forecasting.Rmd
saving scatterplot for gain vs cost

@@
 print(m1$aic)
+
+pdf(here::here("plots", "electric_forecast.pdf"))
+autoplot(forecast(m1, 15))
+dev.off()
 # residuals appear to be in nominal range. large LB p-value also support no autocorrelation between residuals. 
@@
 print(m2$aic)
+
+pdf(here::here("plots", "gas_forecast.pdf"))
+autoplot(forecast(m2, 15))
+dev.off()
 # residuals appear to be in nominal range. large LB p-value also support no autocorrelation between residuals. 
@@
 # residuals appear to be in nominal range. large LB p-value also support no autocorrelation between residuals.
+
+pdf(here::here("plots", "solid_forecast.pdf"))
+autoplot(forecast(m3, 15))
+dev.off()
 ```
@@
 print(m4$aic)
+
+pdf(here::here("plots", "oil_forecast.pdf"))
+autoplot(forecast(m4, 15))
+dev.off()
 # residuals appear to be in nominal range. large LB p-value also support no autocorrelation between residuals. 
@@
 # saving data to R objects for use in MINOS
-create.if.not.exists(here::here("data", "transitions", "energy_prices")
-write.csv(electric.series, "data/transitions/energy_prices/solid_historic.csv")
-write.csv(gas.series, "data/transitions/energy_prices/gas_historic.csv")
-write.csv(solid.series, "data/transitions/energy_prices/solid_historic.csv")
-write.csv(liquid.series, "data/transitions/energy_prices/liquid_historic.csv")
-write.csv(forecast(m1, 15), "data/transitions/energy_prices/electric_arima.csv")
-write.csv(forecast(m2, 15), "data/transitions/energy_prices/gas_arima.csv")
-write.csv(forecast(m3, 15), "data/transitions/energy_prices/solid_arima.csv")
-write.csv(forecast(m4, 15), "data/transitions/energy_prices/liquid_arima.csv")
+create.if.not.exists(here::here("data", "transitions", "energy_prices"))
+write.csv(electric.series, here::here("data", "transitions", "energy_prices", "solid_historic.csv"))
+write.csv(gas.series, here::here("data", "transitions", "energy_prices", "gas_historic.csv"))
+write.csv(solid.series, here::here("data", "transitions", "energy_prices", "solid_historic.csv"))
+write.csv(liquid.series, here::here("data", "transitions", "energy_prices", "liquid_historic.csv"))
+write.csv(forecast(m1, 15), here::here("data", "transitions", "energy_prices", "electric_arima.csv"))
+write.csv(forecast(m2, 15), here::here("data", "transitions", "energy_prices", "gas_arima.csv"))
+write.csv(forecast(m3, 15), here::here("data", "transitions", "energy_prices", "solid_arima.csv"))
+write.csv(forecast(m4, 15), here::here("data", "transitions", "energy_prices", "liquid_arima.csv"))
 ```

### 2024-08-02 minos/outcomes/child_poverty_reduction_vis.Rmd
Fixing subdirectory for summaries

@@
 ```{r, include=FALSE}
-out.path <- here::here('output', 'default_config/')
-#out.path <- here::here('output', 'scotland_scaled/')
+#out.path <- here::here('output', 'default_config/')
+out.path <- here::here('output', 'scotland_scaled/')
 base.dat <- read_singular_local_out(out.path, 'baseline', 
@@
                                     drop.zero.weight = TRUE)
-int1.rel <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE',
+int1.rel <- read_singular_local_out(out.path, 'ChildPovertyReduction',
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)
-int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
-                                   drop.dead = TRUE,
-                                   drop.zero.weight = TRUE)
+# int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
+#                                    drop.dead = TRUE,
+#                                    drop.zero.weight = TRUE)
 # int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReduction',
@@
 #                                    drop.zero.weight = TRUE)
-int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
-                                   drop.dead = TRUE,
-                                   drop.zero.weight = TRUE)
+# int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
+#                                    drop.dead = TRUE,
+#                                    drop.zero.weight = TRUE)
 
@@
 
-int2.rel_fixed <- int2.rel_fixed #%>%
+#int2.rel_fixed <- int2.rel_fixed #%>%
   #filter(age < 91)

### 2024-08-02 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Adding fix for US_household_upscaling to select the correct people

@@
 ```{r}
-# SF12_change_income_quint(summary_group = 'whole_pop',
-#                                     scen.list = scen.list.rel)
-SF12_change_income_quint2(summary_group = 'whole_pop',
-                                    scen = scen)
+SF12_change_income_quint(summary_group = 'whole_pop',
+                                    scen.list = scen.list)
+# SF12_change_income_quint2(summary_group = 'whole_pop',
+#                                     scen = scen)
 ```

### 2024-08-05 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Minor path changes to vis script for relative and absolute together intervention

@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"
@@
   if (summary_group == 'treated_relative') { 
-    tit <- 'Treated' }
+    tit <- 'Treated'
+    plot_colour <- 'black'}
   if (summary_group == 'treated_absolute') { 
-    tit <- 'Treated' }
+    tit <- 'Treated'
+    plot_colour <- 'black'}
   if (summary_group == 'priority_any') { 
@@
                                     scen.list = scen.list)
-# SF12_change_income_quint2(summary_group = 'whole_pop',
-#                                     scen = scen)
+SF12_change_income_quint2(summary_group = 'whole_pop',
+                                    scen = scen)
 ```
@@
 ```{r}
-# SF12_change_income_quint(summary_group = 'families',
-#                                     scen.list = scen.list.rel)
+SF12_change_income_quint(summary_group = 'families',
+                                    scen.list = scen.list)
 SF12_change_income_quint2(summary_group = 'families',
@@
 ```{r}
-# SF12_change_simple(summary_group = 'treated_relative',
-#                    scen.list = scen.list.rel)
+SF12_change_simple(summary_group = 'treated_relative',
+                   scen.list = scen.list)
+
+SF12_change_simple(summary_group = 'treated_absolute',
+                   scen.list = scen.list)
 

### 2024-08-05 minos/outcomes/MHF_SCP_visualisations.Rmd
Started tracking the visualisation script for MHF SCP plots

---
title: "MHF SCP Experiment Visualisations"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)

workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

```{r "data", include=FALSE}
# whole pop to start
# base.whole <- read.csv(file = sprintf('%s/combined_summary_whole_pop.csv', 'baseline'))
# base.UC <- read.csv(file = sprintf('%s/combined_summary_UC.csv', 'baseline'))
```

```{r}
scen.list.full <- c('baseline', '10UniversalCredit', '20UniversalCredit',
               '25UniversalCredit', '30UniversalCredit',
               '35UniversalCredit', '40UniversalCredit', '45UniversalCredit',
               '50UniversalCredit', '60UniversalCredit', '70UniversalCredit',
               '80UniversalCredit', '90UniversalCredit', '100UniversalCredit')

scen.list.50l <- c('baseline', '10UniversalCredit',
               '20UniversalCredit', '25UniversalCredit', '30UniversalCredit',
               '35UniversalCredit', '40UniversalCredit', '45UniversalCredit',
               '50UniversalCredit')

scen.list.10_50 <- c('baseline', '10UniversalCredit',
               '20UniversalCredit', '30UniversalCredit',
               '40UniversalCredit', '50UniversalCredit')

scen.list.60_100 <- c('baseline', '60UniversalCredit', '70UniversalCredit',
               '80UniversalCredit', '90UniversalCredit', '100UniversalCredit')

scen.list.25_50 <- c('baseline', '25UniversalCredit', '30UniversalCredit',
                    '35UniversalCredit', '40UniversalCredit', '45UniversalCredit',
                    '50UniversalCredit')

scen.list.10_100 <- c('baseline', '10UniversalCredit', '20UniversalCredit',
                      '30UniversalCredit', '40UniversalCredit', '50UniversalCredit', 
                      '60UniversalCredit', '70UniversalCredit', '80UniversalCredit', 
                      '90UniversalCredit', '100UniversalCredit')

scen.list.20_100 <- c('baseline', '20UniversalCredit', '40UniversalCredit',
                      '60UniversalCredit', '80UniversalCredit', '100UniversalCredit')
```

# Functions

```{r "datain", include=False}
generate_df_list <- function(summary, scen.list) {
  df.list <- lapply(scen.list, function(scen) {
    df <- read.csv(file = sprintf('%s/combined_summary_%s.csv', scen, summary))
    df$scen <- scen
    return(df)
  })
  return(df.list)
}

```

```{r "cost_ratio_functions", include = FALSE}

SF_12_cost_ratio <- function(summary_type, scen_list) {

  data <- do.call(rbind, generate_df_list(summary_type, scen_list))

  if (summary_type == "UC") {
    data <- data %>%
      filter(universal_credit == 1)
  }

  plot_data1 <- data %>%
    select(run_id, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"), 
                 names_to = c(".value", "scen"), 
                 names_sep = "\\.") %>%
    filter(scen != 'baseline')

  # Extract numeric part from 'scen' column then...
  scen_numeric <- as.numeric(gsub("[^0-9]", "", plot_data1$scen))
  # ...Reorder 'scen' column based on numeric values for plotting
  plot_data1$scen <- factor(plot_data1$scen, levels = unique(plot_data1$scen[order(scen_numeric)]))

  plot_data1_confint <- plot_data1 %>%
    group_by(year, scen) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF_12),
              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  plot_data2 <- plot_data1 %>%
    mutate(SF12_to_cost_ratio = diff_SF_12 / mean_cost) %>%
    replace_na(list(SF12_to_cost_ratio = 0))

  plot_data2_confint <- plot_data2 %>%
    group_by(year, scen) %>%
    summarise(n = n(),
              mean_SF12_to_cost_ratio = mean(SF12_to_cost_ratio),
              margin = qt(0.975, df = n - 1) * (sd(SF12_to_cost_ratio) / sqrt(n)),
              lower = mean_SF12_to_cost_ratio - margin,
              upper = mean_SF12_to_cost_ratio + margin)

  plot_data2_logged <- plot_data2_confint %>%
    group_by(year, scen) %>%
    summarise(mean_SF12_to_cost_ratio = log(mean_SF12_to_cost_ratio),
              lower = log(lower),
              upper = log(upper))

  # p1 <- ggplot(plot_data1, aes(x = year, y = diff_SF_12, group = scen, colour = scen, fill = scen)) +
  #   geom_smooth()
  p1 <- ggplot(plot_data1_confint, aes(x = year, y = mean_SF12_change, group = scen, colour = scen, fill = scen)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = scen), linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed')

  # p2 <- ggplot(plot_data2, aes(x = year, y = SF12_to_cost_ratio, group = scen, colour = scen, fill = scen)) +
  #   geom_smooth()

  p2 <- ggplot(plot_data2_confint, aes(x = year, y = mean_SF12_to_cost_ratio, group = scen, colour = scen, fill = scen)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = scen), linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed')

  p3 <- ggplot(plot_data2_logged, aes(x = year, y = mean_SF12_to_cost_ratio, group = scen, colour = scen, fill = scen)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = scen), linetype = 'dashed') +
    geom_point()

  print(p1)
  print(p2)
  #print(p3)
}

SF_12_cost_ratio_cumul <- function(summary_type, scen_list) {

  data <- do.call(rbind, generate_df_list(summary_type, scen_list))

  if (summary_type == "UC") {
    data <- data %>%
      filter(universal_credit == 1)
  }

  plot_data1 <- data %>%
    select(run_id, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"), 
                 names_to = c(".value", "scen"), 
                 names_sep = "\\.") %>%
    filter(scen != 'baseline')

  # Extract numeric part from 'scen' column then...
  scen_numeric <- as.numeric(gsub("[^0-9]", "", plot_data1$scen))
  # ...Reorder 'scen' column based on numeric values for plotting
  plot_data1$scen <- factor(plot_data1$scen, levels = unique(plot_data1$scen[order(scen_numeric)]))

  # Now we need to calculate cumulative stuff for the ratio
  cumulative_SF12 <- plot_data1 %>%
    group_by(scen, run_id) %>%
    summarise(SF_12 = sum(diff_SF_12),
              cost = sum(mean_cost))

  cumulative_SF12_ratio <- cumulative_SF12 %>%
    mutate(SF12_to_cost_ratio = SF_12 / cost) %>%
    replace_na(list(SF12_to_cost_ratio = 0))

  cumulative_SF12_ratio_confint <- cumulative_SF12_ratio %>%
    group_by(scen) %>%
    summarise(n = n(),
              mean_SF12_to_cost_ratio = mean(SF12_to_cost_ratio),
              margin = qt(0.975, df = n - 1) * (sd(SF12_to_cost_ratio) / sqrt(n)),
              lower = mean_SF12_to_cost_ratio - margin,
              upper = mean_SF12_to_cost_ratio + margin)

  p1 <- ggplot(cumulative_SF12_ratio_confint, aes(x = scen, y = mean_SF12_to_cost_ratio, group = scen, fill = scen)) +
    geom_col() +
    labs(title = 'Ratio of SF12 Improvement to Cost') +
    xlab('Intervention') +
    ylab('Ratio') +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
          legend.position = 'none')

  p2 <- ggplot(cumulative_SF12_ratio_confint, aes(x = scen, y = mean_SF12_to_cost_ratio, group = scen, fill = scen)) +
    geom_col() +
    geom_errorbar(aes(ymin = lower, ymax = upper), position = 'dodge', width = 0.25) +
    labs(title = 'Ratio of SF12 Improvement to Cost') +
    xlab('Intervention') +
    ylab('Ratio') +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
          legend.position = 'none')

  print(p1)
  print(p2)
}
```

```{r "rel_abs_function", include=FALSE}

compare_relative_absolute <- function(comparison_scen) {
  scen.list <- c('baseline', comparison_scen)

  UC.rel <- do.call(rbind, generate_df_list('UC_rel_pov', scen.list))
  UC.abs <- do.call(rbind, generate_df_list('UC_abs_pov', scen.list))

  rel.change <- UC.rel %>%
    filter(universal_credit == 1,
           init_relative_poverty == 1) %>%
    select(run_id, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
                 names_to = c(".value", "scen"),
                 names_sep = "\\.") %>%
    filter(scen != 'baseline') %>%
    rename(RelativePoverty = diff_SF_12) %>%
    select(run_id, year, RelativePoverty)

  abs.change <- UC.abs %>%
    filter(universal_credit == 1,
           init_absolute_poverty == 1) %>%
    select(run_id, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
                 names_to = c(".value", "scen"),
                 names_sep = "\\.") %>%
    filter(scen != 'baseline') %>%
    rename(AbsolutePoverty = diff_SF_12) %>%
    select(run_id, year, AbsolutePoverty)

  combined <- merge(rel.change, abs.change, by = c('run_id', 'year'))

  combined_confint <- combined %>%
    pivot_longer(cols = RelativePoverty:AbsolutePoverty,
                 names_to = 'subpop',
                 values_to = 'SF_12_change') %>%
      group_by(subpop, year) %>%
      summarise(n = n(),
                mean_SF12_change = mean(SF_12_change),
                margin = qt(0.975, df = n - 1) * (sd(SF_12_change) / sqrt(n)),
                lower = mean_SF12_change - margin,
                upper = mean_SF12_change + margin)

  p1 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = subpop), linetype = 'dashed') +
    geom_hline(yintercept = 0, linetype = 'dashed')

  p2 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = 'Mean SF-12 Change', subtitle = comparison_scen) +
    xlab('Year') +
    ylab('SF-12 Change')

  print(p1)
  print(p2)
}

```

```{r "gender_function", include=FALSE}
compare_gender <- function(comparison_scen) {
  scen.list <- c('baseline', comparison_scen)
  UC.gender <- do.call(rbind, generate_df_list('UC_gender', scen.list))

  gender.change <- UC.gender %>%
    filter(universal_credit == 1) %>%
    select(run_id, sex, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
                 names_to = c(".value", "scen"),
                 names_sep = "\\.") %>%
    filter(scen != 'baseline') %>%
    select(run_id, sex, year, diff_SF_12)

  gender.confint <- gender.change %>%
    group_by(sex, year) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF_12),
              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  p1 <- ggplot(data = gender.confint, aes(x = year, y = mean_SF12_change, group = sex, colour = sex, fill = sex)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = sex), linetype = 'dashed') +
    geom_hline(yintercept = 0, linetype = 'dashed')

  p2 <- ggplot(data = gender.confint, aes(x = year, y = mean_SF12_change, group = sex, colour = sex, fill = sex)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = 'Mean SF-12 Change', subtitle = comparison_scen) +
    xlab('Year') +
    ylab('SF-12 Change')

  #print(p1)
  print(p2)
}
```

# Whole Population

```{r}
whole.pop.list <- generate_df_list('whole_pop', scen.list.full)
whole.pop <- do.call(rbind, whole.pop.list)
```

```{r}
whole.pop.sum <- whole.pop %>%
  group_by(scen, year) %>%
  summarise(hh_income = mean(hh_income),
            SF_12 = mean(SF_12))

ggplot(whole.pop.sum, aes(x = year, y = SF_12, group = scen, colour = scen, fill = scen)) +
  geom_line()

ggplot(whole.pop, aes(x = year, y = SF_12, group = scen, colour = scen, fill = scen)) +
  geom_smooth()

rm(whole.pop.sum, whole.pop.list, whole.pop)
```

# Families

```{r}
fam.list <- generate_df_list('families', scen.list.full)
families <- do.call(rbind, fam.list)
```

```{r}
fam.sum <- families %>%
  group_by(scen, year) %>%
  summarise(hh_income = mean(hh_income),
            SF_12 = mean(SF_12))

ggplot(fam.sum, aes(x = year, y = SF_12, group = scen, colour = scen, fill = scen)) +
  geom_line()

ggplot(families, aes(x = year, y = SF_12, group = scen, colour = scen, fill = scen)) +
  geom_smooth()

rm(fam.sum, fam.list, families)
```

```{r}
fam.2550 <- do.call(rbind, generate_df_list('families', scen.list.25_50))

ggplot(fam.2550, aes(x = year, y = SF_12, group = scen, colour = scen, fill = scen)) +
  geom_smooth()

rm(fam.2550)
```

# Improvement Ratios

```{r}
# test <- do.call(rbind, generate_df_list('families', scen.list.10_50))
# test2 <- do.call(rbind, generate_df_list('UC', scen.list.10_50))
# SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.10_50)
# SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.10_50)
```

## Cost Ratio: £10 - £50

### Whole Pop

```{r}
SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.10_50)
SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.10_50)
```

### Families

```{r}
SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.10_50)
SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.10_50)
```

### UC

```{r}
SF_12_cost_ratio(summary_type = 'UC', scen_list = scen.list.10_50)
SF_12_cost_ratio_cumul(summary_type = 'UC', scen_list = scen.list.10_50)
```

## Cost Ratio: £60 - £100

### Whole Pop

```{r}
SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.60_100)
SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.60_100)
```

### Families

```{r}
SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.60_100)
SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.60_100)
```

### UC

```{r}
SF_12_cost_ratio(summary_type = 'UC', scen_list = scen.list.60_100)
SF_12_cost_ratio_cumul(summary_type = 'UC', scen_list = scen.list.60_100)
```

## Cost Ratio: £10 - £100

### Whole Pop

```{r}
SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.10_100)
SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.10_100)
```

### Families

```{r}
SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.10_100)
SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.10_100)
```

### UC

```{r}
SF_12_cost_ratio(summary_type = 'UC', scen_list = scen.list.10_100)
SF_12_cost_ratio_cumul(summary_type = 'UC', scen_list = scen.list.10_100)
```

# Compare Different Populations

## Relative and Absolute Poverty

```{r}
compare_relative_absolute(comparison_scen = '25UniversalCredit')
compare_relative_absolute(comparison_scen = '50UniversalCredit')
compare_relative_absolute(comparison_scen = '70UniversalCredit')
compare_relative_absolute(comparison_scen = '100UniversalCredit')
```

## Gender

```{r}
# scen.list.50 <- c('baseline', '50UniversalCredit')
# UC.gender <- do.call(rbind, generate_df_list('UC_gender', scen.list.50))
```

```{r}
compare_gender(comparison_scen = '25UniversalCredit')
compare_gender(comparison_scen = '50UniversalCredit')
compare_gender(comparison_scen = '70UniversalCredit')
compare_gender(comparison_scen = '100UniversalCredit')
```

```{r}
scen.list <- c('baseline', '50UniversalCredit')

UC.rel <- do.call(rbind, generate_df_list('UC_rel_pov', scen.list))
UC.abs <- do.call(rbind, generate_df_list('UC_abs_pov', scen.list))

rel.change <- UC.rel %>%
  filter(universal_credit == 1,
         init_relative_poverty == 1) %>%
  select(run_id, SF_12, mean_cost, year, scen) %>%
  pivot_wider(names_from = scen,
              values_from = c(SF_12, mean_cost),
              names_sep = '.') %>%
  mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
  rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
  pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
               names_to = c(".value", "scen"),
               names_sep = "\\.") %>%
  filter(scen != 'baseline') %>%
  rename(RelativePoverty = diff_SF_12) %>%
  select(run_id, year, RelativePoverty)

abs.change <- UC.abs %>%
  filter(universal_credit == 1,
         init_absolute_poverty == 1) %>%
  select(run_id, SF_12, mean_cost, year, scen) %>%
  pivot_wider(names_from = scen,
              values_from = c(SF_12, mean_cost),
              names_sep = '.') %>%
  mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
  rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
  pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
               names_to = c(".value", "scen"),
               names_sep = "\\.") %>%
  filter(scen != 'baseline') %>%
  rename(AbsolutePoverty = diff_SF_12) %>%
  select(run_id, year, AbsolutePoverty)

combined <- merge(rel.change, abs.change, by = c('run_id', 'year'))

combined_confint <- combined %>%
  pivot_longer(cols = RelativePoverty:AbsolutePoverty,
               names_to = 'subpop',
               values_to = 'SF_12_change') %>%
    group_by(subpop, year) %>%
    summarise(n = n(),
              mean_SF12_change = mean(SF_12_change),
              margin = qt(0.975, df = n - 1) * (sd(SF_12_change) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

p1 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
  geom_line(aes(color = subpop), linetype = 'dashed') +
  geom_hline(yintercept = 0, linetype = 'dashed')

p2 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
  geom_smooth() +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  labs(title = 'Mean SF-12 Change', subtitle = '50UniversalCredit') +
  xlab('Year') +
  ylab('SF-12 Change')

print(p1)
print(p2)
```

```{r}

scen.list <- c('baseline', '50UniversalCredit')

UC.rel <- do.call(rbind, generate_df_list('UC_kids_rel_pov', scen.list))
UC.abs <- do.call(rbind, generate_df_list('UC_kids_abs_pov', scen.list))

rel.change <- UC.rel %>%
  filter(universal_credit == 1) %>%
  select(run_id, init_relative_poverty, SF_12, mean_cost, year, scen) %>%
  pivot_wider(names_from = scen,
              values_from = c(SF_12, mean_cost),
              names_sep = '.') %>%
  mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
  rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
  pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
               names_to = c(".value", "scen"),
               names_sep = "\\.") %>%
  filter(scen != 'baseline') %>%
  rename(RelativePoverty = diff_SF_12) %>%
  select(run_id, year, init_relative_poverty, RelativePoverty)

rel.change$init_relative_poverty <- factor(rel.change$init_relative_poverty)

ggplot(rel.change, aes(x = year, y = RelativePoverty, group = init_relative_poverty, color = init_relative_poverty, fill = init_relative_poverty)) +
  geom_smooth()

combined_confint <- rel.change %>%
    group_by(init_relative_poverty, year) %>%
    summarise(n = n(),
              mean_SF12_change = mean(RelativePoverty),
              margin = qt(0.975, df = n - 1) * (sd(RelativePoverty) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = init_relative_poverty, colour = init_relative_poverty, fill = init_relative_poverty)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
  geom_line(aes(color = init_relative_poverty), linetype = 'dashed') +
  geom_hline(yintercept = 0, linetype = 'dashed')

# WHAT DO I WANT THIS PLOT TO SHOW??
# Relative poverty group under intervention vs relative poverty group without intervention
# So I should be filtering for universal credit and children and relative poverty == 1
# then compare between intervention group and baseline

```

```{r}

```

### 2024-08-06 minos/outcomes/MHF_SCP_visualisations.Rmd
Added more summary functions for recalculating relative and absolute poverty groups each year

@@
 
-compare_relative_absolute <- function(comparison_scen) {
+compare_relative_absolute <- function(comparison_scen, kids = FALSE) {
+
   scen.list <- c('baseline', comparison_scen)
 
+  if (kids) {
+    UC.rel <- do.call(rbind, generate_df_list('UC_kids_rel_pov', scen.list))
+    UC.abs <- do.call(rbind, generate_df_list('UC_kids_abs_pov', scen.list))
+  } else {
     UC.rel <- do.call(rbind, generate_df_list('UC_rel_pov', scen.list))
     UC.abs <- do.call(rbind, generate_df_list('UC_abs_pov', scen.list))
+  }
 
@@
 
+### Whole Pop
+
 ```{r}
@@
 compare_relative_absolute(comparison_scen = '100UniversalCredit')
+```
+
+## Families with Children
+
+```{r}
+compare_relative_absolute(comparison_scen = '25UniversalCredit', kids=TRUE)
+compare_relative_absolute(comparison_scen = '50UniversalCredit', kids=TRUE)
+compare_relative_absolute(comparison_scen = '70UniversalCredit', kids=TRUE)
+compare_relative_absolute(comparison_scen = '100UniversalCredit', kids=TRUE)
 ```

### 2024-08-07 minos/outcomes/MHF_SCP_visualisations.Rmd
Improved plots, changed lots of labels and ensured consistent colour scheme across different plots for MHF results

@@
 
-require(tidyverse)
-require(ggplot2)
+library(tidyverse)
+library(ggplot2)
+library(RColorBrewer)
+library(stringr)
+library(grid)
 
@@
 ```{r}
+scen.colour.list <- c('baseline', '£10', '£20',
+               '£25', '£30',
+               '£35', '£40', '£45',
+               '£50', '£60', '£70',
+               '£80', '£90', '£100')
+
+#colours <- display.brewer.all(length(scen.list.full))
+#colours <- colorRampPalette( brewer.pal(11,"Spectral") )(14)
+colours <- colorRampPalette( brewer.pal(9,"Set1") )(14)
+my_palette <- set_names(colours, scen.colour.list)
+
 scen.list.full <- c('baseline', '10UniversalCredit', '20UniversalCredit',
@@
 
-```{r "datain", include=False}
+```{r "datain", include=FALSE}
 generate_df_list <- function(summary, scen.list) {
@@
 
-```{r "cost_ratio_functions", include = FALSE}
+```{r "cost_ratio_functions", include=FALSE}
 
-SF_12_cost_ratio <- function(summary_type, scen_list) {
+SF_12_cost_ratio <- function(summary_type, scen_list, palette = my_palette) {
 
   data <- do.call(rbind, generate_df_list(summary_type, scen_list))
+
+  data <- data %>%
+    mutate_at("scen", str_replace, "UniversalCredit", "") %>%
+    mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))
 
@@
 
-  plot_data2_logged <- plot_data2_confint %>%
-    group_by(year, scen) %>%
-    summarise(mean_SF12_to_cost_ratio = log(mean_SF12_to_cost_ratio),
-              lower = log(lower),
-              upper = log(upper))
-
   # p1 <- ggplot(plot_data1, aes(x = year, y = diff_SF_12, group = scen, colour = scen, fill = scen)) +
   #   geom_smooth()
-  p1 <- ggplot(plot_data1_confint, aes(x = year, y = mean_SF12_change, group = scen, colour = scen, fill = scen)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+  p1 <- ggplot(plot_data1_confint, aes(x = year, y = mean_SF12_change, group = scen)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
     geom_line(aes(color = scen), linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed')
+    geom_point(aes(color = scen)) +
+    scale_color_manual(values = palette) +
+    scale_fill_manual(values = palette) +
+    xlab('Year') +
+    ylab('Mean SF-12 Change') +
+    theme(
+        legend.title = element_blank(),  # Remove the legend title
+        legend.position = c(0.2, 0.7),  # Position the legend inside the plot
+        legend.text = element_text(size = 8),  # Increase the text size for better readability
+        legend.key.size = unit(0.8, 'cm'),  # Reduce the key size to fit more entries
+        legend.spacing.y = unit(0.1, 'cm')  # Add vertical space between legend items
+    ) +
+    guides(
+        color = guide_legend(
+            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        ),
+        fill = guide_legend(
+            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        )
+    )
+
+  # if (length(scen_list) > 5) {
+  #   p1 <- ggplot(plot_data1_confint, aes(x = year, y = mean_SF12_change, group = scen)) +
+  #     geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
+  #     geom_line(aes(color = scen), linetype = 'dashed') +
+  #     geom_point(aes(color = scen)) +
+  #     scale_color_manual(values = palette) +
+  #     scale_fill_manual(values = palette) +
+  #     xlab('Year') +
+  #     ylab('Mean SF-12 Change') +
+  #     theme(legend.title = element_blank(),
+  #           legend.position = c(0.2, 0.8),
+  #           legend.text = element_text(size=5),
+  #           legend.key.size = unit(1, 'cm')) +
+  #     guides(fill=guide_legend(ncol=2))
+  # }
+
+  #          legend.background = element_rect(fill = "white")
 
@@
 
-  p2 <- ggplot(plot_data2_confint, aes(x = year, y = mean_SF12_to_cost_ratio, group = scen, colour = scen, fill = scen)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+  p2 <- ggplot(plot_data2_confint, aes(x = year, y = mean_SF12_to_cost_ratio, group = scen)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
     geom_line(aes(color = scen), linetype = 'dashed') +
-    geom_point() +
-    geom_hline(yintercept = 0, linetype = 'dashed')
+    geom_point(aes(color = scen)) +
+    scale_color_manual(values = palette) +
+    scale_fill_manual(values = palette) +
+    xlab('Year') +
+    ylab('Mean SF-12 Change') +
+    theme(
+        legend.title = element_blank(),  # Remove the legend title
+        legend.position = c(0.2, 0.7),  # Position the legend inside the plot
+        legend.text = element_text(size = 8),  # Increase the text size for better readability
+        legend.key.size = unit(0.8, 'cm'),  # Reduce the key size to fit more entries
+        legend.spacing.y = unit(0.1, 'cm')  # Add vertical space between legend items
+    ) +
+    guides(
+        color = guide_legend(
+            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        ),
+        fill = guide_legend(
+            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        )
+    )
 
-  p3 <- ggplot(plot_data2_logged, aes(x = year, y = mean_SF12_to_cost_ratio, group = scen, colour = scen, fill = scen)) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(aes(color = scen), linetype = 'dashed') +
-    geom_point()
+  # if (length(scen_list) > 5) {
+  #   p2 <- ggplot(plot_data2_confint, aes(x = year, y = mean_SF12_to_cost_ratio, group = scen)) +
+  #     geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
+  #     geom_line(aes(color = scen), linetype = 'dashed') +
+  #     geom_point(aes(color = scen)) +
+  #     scale_color_manual(values = palette) +
+  #     scale_fill_manual(values = palette) +
+  #     xlab('Year') +
+  #     ylab('Mean SF-12 Change') +
+  #     theme(legend.title = element_blank(),
+  #           legend.position = c(0.2, 0.8),
+  #           legend.text = element_text(size=5),
+  #           legend.key.size = unit(1, 'cm')) +
+  #     guides(fill=guide_legend(ncol=2))
+  # }
 
@@
   print(p2)
-  #print(p3)
 }
 
-SF_12_cost_ratio_cumul <- function(summary_type, scen_list) {
+SF_12_cost_ratio_cumul <- function(summary_type, scen_list, palette = my_palette) {
 
   data <- do.call(rbind, generate_df_list(summary_type, scen_list))
+
+  data <- data %>%
+    mutate_at("scen", str_replace, "UniversalCredit", "") %>%
+    mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))
 
@@
 
-  p1 <- ggplot(cumulative_SF12_ratio_confint, aes(x = scen, y = mean_SF12_to_cost_ratio, group = scen, fill = scen)) +
-    geom_col() +
-    labs(title = 'Ratio of SF12 Improvement to Cost') +
+  p1 <- ggplot(cumulative_SF12_ratio_confint, aes(x = scen, y = mean_SF12_to_cost_ratio)) +
+    geom_col(aes(color = scen, fill = scen)) +
+    scale_color_manual(values = palette) +
+    scale_fill_manual(values = palette) +
     xlab('Intervention') +
@@
 
-  p2 <- ggplot(cumulative_SF12_ratio_confint, aes(x = scen, y = mean_SF12_to_cost_ratio, group = scen, fill = scen)) +
-    geom_col() +
+  p2 <- ggplot(cumulative_SF12_ratio_confint, aes(x = scen, y = mean_SF12_to_cost_ratio)) +
+    geom_col(aes(color = scen, fill = scen)) +
+    scale_color_manual(values = palette) +
+    scale_fill_manual(values = palette) +
     geom_errorbar(aes(ymin = lower, ymax = upper), position = 'dodge', width = 0.25) +
-    labs(title = 'Ratio of SF12 Improvement to Cost') +
     xlab('Intervention') +
@@
 
-```{r "rel_abs_function", include=FALSE}
+```{r "rel_abs_functions", include=FALSE}
 
@@
   }
+
+  UC.rel <- UC.rel %>%
+    mutate_at("scen", str_replace, "UniversalCredit", "") %>%
+    mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))
+
+  UC.abs <- UC.abs %>%
+    mutate_at("scen", str_replace, "UniversalCredit", "") %>%
+    mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))
+
+  rel.change <- UC.rel %>%
+    filter(universal_credit == 1,
+           relative_poverty == 1) %>%
+    select(run_id, SF_12, mean_cost, year, scen) %>%
+    pivot_wider(names_from = scen,
+                values_from = c(SF_12, mean_cost),
+                names_sep = '.') %>%
+    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
+    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
+    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
+                 names_to = c(".value", "scen"),
+                 names_sep = "\\.") %>%
+    filter(scen != 'baseline') %>%
+    rename(RelativePoverty = diff_SF_12) %>%
+    select(run_id, year, RelativePoverty)
+
+  abs.change <- UC.abs %>%
+    filter(universal_credit == 1,
+           absolute_poverty == 1) %>%
+    select(run_id, SF_12, mean_cost, year, scen) %>%
+    pivot_wider(names_from = scen,
+                values_from = c(SF_12, mean_cost),
+                names_sep = '.') %>%
+    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
+    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
+    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
+                 names_to = c(".value", "scen"),
+                 names_sep = "\\.") %>%
+    filter(scen != 'baseline') %>%
+    rename(AbsolutePoverty = diff_SF_12) %>%
+    select(run_id, year, AbsolutePoverty)
+
+  combined <- merge(rel.change, abs.change, by = c('run_id', 'year'))
+
+  combined_confint <- combined %>%
+    pivot_longer(cols = RelativePoverty:AbsolutePoverty,
+                 names_to = 'subpop',
+                 values_to = 'SF_12_change') %>%
+      group_by(subpop, year) %>%
+      summarise(n = n(),
+                mean_SF12_change = mean(SF_12_change),
+                margin = qt(0.975, df = n - 1) * (sd(SF_12_change) / sqrt(n)),
+                lower = mean_SF12_change - margin,
+                upper = mean_SF12_change + margin)
+
+  comparison_scen <- gsub("[a-zA-Z ]", "", comparison_scen)
+  comparison_scen <- paste0("£", comparison_scen)
+
+  p1 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(aes(color = subpop), linetype = 'dashed') +
+    geom_point() +
+    geom_hline(yintercept = 0, linetype = 'dashed') + 
+    labs(subtitle = comparison_scen) +
+    xlab('Year') +
+    ylab('Mean SF-12 Change')
+
+  p2 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
+    geom_smooth() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    labs(subtitle = comparison_scen) +
+    xlab('Year') +
+    ylab('Mean SF-12 Change')
+
+  print(p1)
+  print(p2)
+}
+
+compare_init_relative_absolute <- function(comparison_scen, kids = FALSE) {
+
+  scen.list <- c('baseline', comparison_scen)
+
+  if (kids) {
+    UC.rel <- do.call(rbind, generate_df_list('UC_kids_init_rel_pov', scen.list))
+    UC.abs <- do.call(rbind, generate_df_list('UC_kids_init_abs_pov', scen.list))
+  } else {
+    UC.rel <- do.call(rbind, generate_df_list('UC_init_rel_pov', scen.list))
+    UC.abs <- do.call(rbind, generate_df_list('UC_init_abs_pov', scen.list))
+  }
+
+  UC.rel <- UC.rel %>%
+    mutate_at("scen", str_replace, "UniversalCredit", "") %>%
+    mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))
+
+  UC.abs <- UC.abs %>%
+    mutate_at("scen", str_replace, "UniversalCredit", "") %>%
+    mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))
 
@@
 
+  comparison_scen <- gsub("[a-zA-Z ]", "", comparison_scen)
+  comparison_scen <- paste0("£", comparison_scen)
+
   p1 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
@@
     geom_line(aes(color = subpop), linetype = 'dashed') +
-    geom_hline(yintercept = 0, linetype = 'dashed')
+    geom_point() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    labs(subtitle = comparison_scen) +
+    xlab('Year') +
+    ylab('Mean SF-12 Change')
 
@@
     geom_hline(yintercept = 0, linetype = 'dashed') +
-    labs(title = 'Mean SF-12 Change', subtitle = comparison_scen) +
+    labs(subtitle = comparison_scen) +
     xlab('Year') +
-    ylab('SF-12 Change')
+    ylab('Mean SF-12 Change')
 
@@
 
+  comparison_scen <- gsub("[a-zA-Z ]", "", comparison_scen)
+  comparison_scen <- paste0("£", comparison_scen)
+
   p1 <- ggplot(data = gender.confint, aes(x = year, y = mean_SF12_change, group = sex, colour = sex, fill = sex)) +
@@
     geom_line(aes(color = sex), linetype = 'dashed') +
-    geom_hline(yintercept = 0, linetype = 'dashed')
+    geom_point() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
+    scale_color_manual(values = c("#E69F00", "#56B4E9")) +
+    labs(subtitle = comparison_scen) +
+    xlab('Year') +
+    ylab('SF-12 Change')
 
@@
     geom_hline(yintercept = 0, linetype = 'dashed') +
-    labs(title = 'Mean SF-12 Change', subtitle = comparison_scen) +
+    labs(subtitle = comparison_scen) +
     xlab('Year') +
@@
 
-  #print(p1)
-  print(p2)
+  print(p1)
+  #print(p2)
 }
@@
 
-## Cost Ratio: £10 - £50
+## Cost Ratio: £25 - £50
 
-### Whole Pop
+### UC
 
 ```{r}
-SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.10_50)
-SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.10_50)
+SF_12_cost_ratio(summary_type = 'UC', scen_list = scen.list.25_50)
+SF_12_cost_ratio_cumul(summary_type = 'UC', scen_list = scen.list.25_50)
 ```
 
-### Families
-
-```{r}
-SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.10_50)
-SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.10_50)
-```
+## Cost Ratio: £10 - £50
 
@@
 
-### Whole Pop
-
-```{r}
-SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.60_100)
-SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.60_100)
-```
-
-### Families
-
-```{r}
-SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.60_100)
-SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.60_100)
-```
-
 ### UC
@@
 ## Cost Ratio: £10 - £100
-
-### Whole Pop
-
-```{r}
-SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.10_100)
-SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.10_100)
-```
-
-### Families
-
-```{r}
-SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.10_100)
-SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.10_100)
-```
 
@@
 
-## Families with Children
+### Families with Children
 
@@
 compare_relative_absolute(comparison_scen = '100UniversalCredit', kids=TRUE)
+```
+
+## INITIAL Relative and Absolute Poverty
+
+### Whole Pop
+
+```{r}
+compare_init_relative_absolute(comparison_scen = '25UniversalCredit')
+compare_init_relative_absolute(comparison_scen = '50UniversalCredit')
+compare_init_relative_absolute(comparison_scen = '70UniversalCredit')
+compare_init_relative_absolute(comparison_scen = '100UniversalCredit')
+```
+
+### Families with Children
+
+```{r}
+compare_init_relative_absolute(comparison_scen = '25UniversalCredit', kids=TRUE)
+compare_init_relative_absolute(comparison_scen = '50UniversalCredit', kids=TRUE)
+compare_init_relative_absolute(comparison_scen = '70UniversalCredit', kids=TRUE)
+compare_init_relative_absolute(comparison_scen = '100UniversalCredit', kids=TRUE)
 ```
@@
 ```{r}
-scen.list <- c('baseline', '50UniversalCredit')
-
-UC.rel <- do.call(rbind, generate_df_list('UC_rel_pov', scen.list))
-UC.abs <- do.call(rbind, generate_df_list('UC_abs_pov', scen.list))
-
-rel.change <- UC.rel %>%
-  filter(universal_credit == 1,
-         init_relative_poverty == 1) %>%
-  select(run_id, SF_12, mean_cost, year, scen) %>%
-  pivot_wider(names_from = scen,
-              values_from = c(SF_12, mean_cost),
-              names_sep = '.') %>%
-  mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
-  rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
-  pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
-               names_to = c(".value", "scen"),
-               names_sep = "\\.") %>%
-  filter(scen != 'baseline') %>%
-  rename(RelativePoverty = diff_SF_12) %>%
-  select(run_id, year, RelativePoverty)
-
-abs.change <- UC.abs %>%
-  filter(universal_credit == 1,
-         init_absolute_poverty == 1) %>%
-  select(run_id, SF_12, mean_cost, year, scen) %>%
-  pivot_wider(names_from = scen,
-              values_from = c(SF_12, mean_cost),
-              names_sep = '.') %>%
-  mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
-  rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
-  pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
-               names_to = c(".value", "scen"),
-               names_sep = "\\.") %>%
-  filter(scen != 'baseline') %>%
-  rename(AbsolutePoverty = diff_SF_12) %>%
-  select(run_id, year, AbsolutePoverty)
-
-combined <- merge(rel.change, abs.change, by = c('run_id', 'year'))
-
-combined_confint <- combined %>%
-  pivot_longer(cols = RelativePoverty:AbsolutePoverty,
-               names_to = 'subpop',
-               values_to = 'SF_12_change') %>%
-    group_by(subpop, year) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(SF_12_change),
-              margin = qt(0.975, df = n - 1) * (sd(SF_12_change) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-p1 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-  geom_line(aes(color = subpop), linetype = 'dashed') +
-  geom_hline(yintercept = 0, linetype = 'dashed')
-
-p2 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
-  geom_smooth() +
-  geom_hline(yintercept = 0, linetype = 'dashed') +
-  labs(title = 'Mean SF-12 Change', subtitle = '50UniversalCredit') +
-  xlab('Year') +
-  ylab('SF-12 Change')
-
-print(p1)
-print(p2)
-```
-
-```{r}
-
-scen.list <- c('baseline', '50UniversalCredit')
-
-UC.rel <- do.call(rbind, generate_df_list('UC_kids_rel_pov', scen.list))
-UC.abs <- do.call(rbind, generate_df_list('UC_kids_abs_pov', scen.list))
-
-rel.change <- UC.rel %>%
-  filter(universal_credit == 1) %>%
-  select(run_id, init_relative_poverty, SF_12, mean_cost, year, scen) %>%
-  pivot_wider(names_from = scen,
-              values_from = c(SF_12, mean_cost),
-              names_sep = '.') %>%
-  mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
-  rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
-  pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
-               names_to = c(".value", "scen"),
-               names_sep = "\\.") %>%
-  filter(scen != 'baseline') %>%
-  rename(RelativePoverty = diff_SF_12) %>%
-  select(run_id, year, init_relative_poverty, RelativePoverty)
-
-rel.change$init_relative_poverty <- factor(rel.change$init_relative_poverty)
-
-ggplot(rel.change, aes(x = year, y = RelativePoverty, group = init_relative_poverty, color = init_relative_poverty, fill = init_relative_poverty)) +
-  geom_smooth()
-
-combined_confint <- rel.change %>%
-    group_by(init_relative_poverty, year) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(RelativePoverty),
-              margin = qt(0.975, df = n - 1) * (sd(RelativePoverty) / sqrt(n)),
-              lower = mean_SF12_change - margin,
-              upper = mean_SF12_change + margin)
-
-ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = init_relative_poverty, colour = init_relative_poverty, fill = init_relative_poverty)) +
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-  geom_line(aes(color = init_relative_poverty), linetype = 'dashed') +
-  geom_hline(yintercept = 0, linetype = 'dashed')
-
-# WHAT DO I WANT THIS PLOT TO SHOW??
-# Relative poverty group under intervention vs relative poverty group without intervention
-# So I should be filtering for universal credit and children and relative poverty == 1
-# then compare between intervention group and baseline
 
@@
 
+# OLD OR UNWANTED
+
+## Cost Ratio: £10 - £50
+
+### Whole Pop
+
 ```{r}
+# SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.10_50)
+# SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.10_50)
+```
 
+### Families
+
+```{r}
+# SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.10_50)
+# SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.10_50)
 ```
+
+## Cost Ratio: £60 - £100
+
+### Whole Pop
+
+```{r}
+# SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.60_100)
+# SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.60_100)
+```
+
+### Families
+
+```{r}
+# SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.60_100)
+# SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.60_100)
+```
+
+## Cost Ratio: £10 - £100
+
+### Whole Pop
+
+```{r}
+# SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.10_100)
+# SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.10_100)
+```
+
+### Families
+
+```{r}
+# SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.10_100)
+# SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.10_100)
+```

### 2024-08-22 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Added yet another method of generating plots by income quintile

@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"
-#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/"
+workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"

### 2024-08-23 minos/outcomes/MHF_SCP_visualisations.Rmd
Added plots for the mental health risk and lone parent comparison. Lone parent comparison plot showed that we were missing run_id from the summary files, so they will need to be re-run

@@
                       '60UniversalCredit', '80UniversalCredit', '100UniversalCredit')
+
+scen.list.25_100 <- c('baseline', '25UniversalCredit', '50UniversalCredit',
+                      '70UniversalCredit', '100UniversalCredit')
 ```
@@
 
-  # if (length(scen_list) > 5) {
-  #   p1 <- ggplot(plot_data1_confint, aes(x = year, y = mean_SF12_change, group = scen)) +
-  #     geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
-  #     geom_line(aes(color = scen), linetype = 'dashed') +
-  #     geom_point(aes(color = scen)) +
-  #     scale_color_manual(values = palette) +
-  #     scale_fill_manual(values = palette) +
-  #     xlab('Year') +
-  #     ylab('Mean SF-12 Change') +
-  #     theme(legend.title = element_blank(),
-  #           legend.position = c(0.2, 0.8),
-  #           legend.text = element_text(size=5),
-  #           legend.key.size = unit(1, 'cm')) +
-  #     guides(fill=guide_legend(ncol=2))
-  # }
-
-  #          legend.background = element_rect(fill = "white")
-
-  # p2 <- ggplot(plot_data2, aes(x = year, y = SF12_to_cost_ratio, group = scen, colour = scen, fill = scen)) +
-  #   geom_smooth()
-
   p2 <- ggplot(plot_data2_confint, aes(x = year, y = mean_SF12_to_cost_ratio, group = scen)) +
@@
     )
-
-  # if (length(scen_list) > 5) {
-  #   p2 <- ggplot(plot_data2_confint, aes(x = year, y = mean_SF12_to_cost_ratio, group = scen)) +
-  #     geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
-  #     geom_line(aes(color = scen), linetype = 'dashed') +
-  #     geom_point(aes(color = scen)) +
-  #     scale_color_manual(values = palette) +
-  #     scale_fill_manual(values = palette) +
-  #     xlab('Year') +
-  #     ylab('Mean SF-12 Change') +
-  #     theme(legend.title = element_blank(),
-  #           legend.position = c(0.2, 0.8),
-  #           legend.text = element_text(size=5),
-  #           legend.key.size = unit(1, 'cm')) +
-  #     guides(fill=guide_legend(ncol=2))
-  # }
 
@@
 
+```{r "lone_parent_function", include=FALSE}
+compare_lone_parent <- function(comparison_scen) {
+  scen.list <- c('baseline', comparison_scen)
+  UC.lone_parent <- do.call(rbind, generate_df_list('priority_lone_parent', scen.list))
+
+  lone_parent.change <- UC.lone_parent %>%
+    select(run_id, sex, SF_12, mean_cost, year, scen) %>%
+    pivot_wider(names_from = scen,
+                values_from = c(SF_12, mean_cost),
+                names_sep = '.') %>%
+    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
+    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
+    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
+                 names_to = c(".value", "scen"),
+                 names_sep = "\\.") %>%
+    filter(scen != 'baseline') %>%
+    select(run_id, sex, year, diff_SF_12)
+
+  lone_parent.confint <- lone_parent.change %>%
+    group_by(sex, year) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(diff_SF_12),
+              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
+              lower = mean_SF12_change - margin,
+              upper = mean_SF12_change + margin)
+
+  comparison_scen <- gsub("[a-zA-Z ]", "", comparison_scen)
+  comparison_scen <- paste0("£", comparison_scen)
+
+  p1 <- ggplot(data = lone_parent.confint, aes(x = year, y = mean_SF12_change, group = sex, colour = sex, fill = sex)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(aes(color = sex), linetype = 'dashed') +
+    geom_point() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
+    scale_color_manual(values = c("#E69F00", "#56B4E9")) +
+    labs(subtitle = comparison_scen) +
+    xlab('Year') +
+    ylab('SF-12 Change')
+
+  p2 <- ggplot(data = lone_parent.confint, aes(x = year, y = mean_SF12_change, group = sex, colour = sex, fill = sex)) +
+    geom_smooth() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    labs(subtitle = comparison_scen) +
+    xlab('Year') +
+    ylab('SF-12 Change')
+
+  print(p1)
+  #print(p2)
+}
+```
+
+```{r "mental_illness_risk_plots", include=FALSE}
+mental_illness_risk_plots <- function(summary_group, scen.list, palette = my_palette) {
+
+  tit <- ' '
+  if (summary_group == 'UC_men_illness_risk') { tit <- 'UC Population' }
+  if (summary_group == 'UC_families_men_illness_risk') { tit <- 'UC Families' }
+  if (summary_group == 'men_illness_risk') { tit <- 'Whole Population' }
+  if (summary_group == 'men_illness_risk_families') { tit <- 'Families' }
+
+  # scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+  # summary_group <- 'men_illness_risk'
+
+  #scen.list <- c('baseline', comparison_scen)
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+
+  data <- data %>%
+    mutate_at("scen", str_replace, "UniversalCredit", "") %>%
+    mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))
+
+  plot_data1 <- data %>%
+    filter(mental_health_risk == 'TRUE') %>%
+    select(-prop, -mental_health_risk) %>%
+    pivot_wider(names_from = scen,
+                values_from = count) %>%
+    mutate(across(starts_with("£"), ~ . - baseline, .names = "diff_{.col}")) %>%
+    select(run_id, year, starts_with('diff')) %>%
+    pivot_longer(cols = starts_with("diff"),
+                 names_sep = '_',
+                 names_to = c("diff", "scen"),
+                 values_to = 'Count')
+
+  # Extract numeric part from 'scen' column then...
+  scen_numeric <- as.numeric(gsub("[^0-9]", "", plot_data1$scen))
+  # ...Reorder 'scen' column based on numeric values for plotting
+  plot_data1$scen <- factor(plot_data1$scen, levels = unique(plot_data1$scen[order(scen_numeric)]))
+
+  plot_data1_confint <- plot_data1 %>%
+    group_by(year, scen) %>%
+    summarise(n = n(),
+              Mean_Count = mean(Count),
+              margin = qt(0.975, df = n - 1) * (sd(Count) / sqrt(n)),
+              lower = Mean_Count - margin,
+              upper = Mean_Count + margin)
+
+  p1 <- ggplot(plot_data1_confint, aes(x = year, y = Mean_Count, group = scen)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
+    geom_line(aes(color = scen), linetype = 'dashed') +
+    geom_point(aes(color = scen)) +
+    scale_color_manual(values = palette) +
+    scale_fill_manual(values = palette) +
+    xlab('Year') +
+    ylab('Mean Change') +
+    theme(
+        legend.title = element_blank(),  # Remove the legend title
+        legend.position = c(0.2, 0.7),  # Position the legend inside the plot
+        legend.text = element_text(size = 8),  # Increase the text size for better readability
+        legend.key.size = unit(0.8, 'cm'),  # Reduce the key size to fit more entries
+        legend.spacing.y = unit(0.1, 'cm')  # Add vertical space between legend items
+    ) +
+    guides(
+        color = guide_legend(
+            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        ),
+        fill = guide_legend(
+            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        )
+    )
+
+    plot_data_2 <- data %>%
+      filter(mental_health_risk == 'TRUE') %>%
+      select(-mental_health_risk, -count) %>%
+      pivot_wider(names_from = scen,
+                  values_from = prop) %>%
+      mutate(across(starts_with("£"), ~ . - baseline, .names = "diff_{.col}")) %>%
+      select(run_id, year, starts_with('diff')) %>%
+      pivot_longer(cols = starts_with("diff"),
+                   names_sep = '_',
+                   names_to = c("diff", "scen"),
+                   values_to = 'Proportion')
+
+    plot_data2_confint <- plot_data_2 %>%
+      mutate(Proportion = Proportion * 100) %>%
+      group_by(year, scen) %>%
+      summarise(n = n(),
+              Mean_Proportion = mean(Proportion),
+              margin = qt(0.975, df = n - 1) * (sd(Proportion) / sqrt(n)),
+              lower = Mean_Proportion - margin,
+              upper = Mean_Proportion + margin)
+
+    p2 <- ggplot(plot_data2_confint, aes(x = year, y = Mean_Proportion, group = scen)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
+    geom_line(aes(color = scen), linetype = 'dashed') +
+    geom_point(aes(color = scen)) +
+    scale_color_manual(values = palette) +
+    scale_fill_manual(values = palette) +
+    xlab('Year') +
+    ylab('Mean Change (%)') +
+    theme(
+        legend.title = element_blank(),  # Remove the legend title
+        legend.position = c(0.2, 0.7),  # Position the legend inside the plot
+        legend.text = element_text(size = 8),  # Increase the text size for better readability
+        legend.key.size = unit(0.8, 'cm'),  # Reduce the key size to fit more entries
+        legend.spacing.y = unit(0.1, 'cm')  # Add vertical space between legend items
+    ) +
+    guides(
+        color = guide_legend(
+            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        ),
+        fill = guide_legend(
+            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        )
+    )
+
+  print(p1)
+  print(p2)
+}
+```
+
 # Whole Population
@@
 ```{r}
-# scen.list.50 <- c('baseline', '50UniversalCredit')
-# UC.gender <- do.call(rbind, generate_df_list('UC_gender', scen.list.50))
-```
-
-```{r}
 compare_gender(comparison_scen = '25UniversalCredit')
@@
 compare_gender(comparison_scen = '100UniversalCredit')
+```
+
+## Lone Parent
+
+```{r}
+compare_lone_parent(comparison_scen = '25UniversalCredit')
+compare_lone_parent(comparison_scen = '50UniversalCredit')
+compare_lone_parent(comparison_scen = '70UniversalCredit')
+compare_lone_parent(comparison_scen = '100UniversalCredit')
+```
+
+# Mental Illness Risk
+
+## Whole Pop
+
+```{r}
+mental_illness_risk_plots('men_illness_risk', scen.list = scen.list.25_100)
+```
+
+## Families
+
+```{r}
+mental_illness_risk_plots('men_illness_risk_families', scen.list = scen.list.25_100)
+```
+
+## UC Pop
+
+```{r}
+mental_illness_risk_plots('UC_men_illness_risk', scen.list = scen.list.25_100)
+```
+
+## UC Families
+
+```{r}
+mental_illness_risk_plots('UC_families_men_illness_risk', scen.list = scen.list.25_100)
 ```

### 2024-09-02 minos/outcomes/MHF_SCP_visualisations.Rmd
Added plot for mental health risk with intervals based on +- 1 for threshold (i.e. 46.6 instad of 45.6). Also fixed the lone parent household plot

@@
     xlab('Year') +
-    ylab('Mean SF-12 Change') +
+    ylab('Cost - SF12 Change Ratio') +
     theme(
@@
   lone_parent.change <- UC.lone_parent %>%
-    select(run_id, sex, SF_12, mean_cost, year, scen) %>%
+    select(run_id, lone_parent_flag, SF_12, mean_cost, year, scen) %>%
     pivot_wider(names_from = scen,
@@
     filter(scen != 'baseline') %>%
-    select(run_id, sex, year, diff_SF_12)
+    select(run_id, lone_parent_flag, year, diff_SF_12)
 
   lone_parent.confint <- lone_parent.change %>%
-    group_by(sex, year) %>%
+    group_by(lone_parent_flag, year) %>%
     summarise(n = n(),
@@
 
-  p1 <- ggplot(data = lone_parent.confint, aes(x = year, y = mean_SF12_change, group = sex, colour = sex, fill = sex)) +
+  lone_parent.confint$lone_parent_flag <- ifelse(lone_parent.confint$lone_parent_flag == 1, 'TRUE', 'FALSE')
+
+  p1 <- ggplot(data = lone_parent.confint, aes(x = year, y = mean_SF12_change, group = lone_parent_flag, colour = lone_parent_flag, fill = lone_parent_flag)) +
     geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(aes(color = sex), linetype = 'dashed') +
+    geom_line(aes(color = lone_parent_flag), linetype = 'dashed') +
     geom_point() +
     geom_hline(yintercept = 0, linetype = 'dashed') +
-    scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
-    scale_color_manual(values = c("#E69F00", "#56B4E9")) +
+    scale_fill_manual(values = c("#49a04d", "#3f3d9e")) +
+    scale_color_manual(values = c("#49a04d", "#3f3d9e")) +
     labs(subtitle = comparison_scen) +
     xlab('Year') +
-    ylab('SF-12 Change')
+    ylab('SF-12 Change') +
+    theme(
+        legend.position = c(0.2, 0.7),  # Position the legend inside the plot
+        legend.text = element_text(size = 8),  # Increase the text size for better readability
+        legend.key.size = unit(0.8, 'cm'),  # Reduce the key size to fit more entries
+        legend.spacing.y = unit(0.1, 'cm')  # Add vertical space between legend items
+    ) +
+    guides(fill = guide_legend(title = 'Lone Parent Household'),
+           color = guide_legend(title = 'Lone Parent Household'),
+           group = guide_legend(title = 'Lone Parent Household'))
 
-  p2 <- ggplot(data = lone_parent.confint, aes(x = year, y = mean_SF12_change, group = sex, colour = sex, fill = sex)) +
+  p2 <- ggplot(data = lone_parent.confint, aes(x = year, y = mean_SF12_change, group = lone_parent_flag, colour = lone_parent_flag, fill = lone_parent_flag)) +
     geom_smooth() +
@@
             ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        )
+    )
+
+  print(p1)
+  print(p2)
+}
+
+mental_illness_risk_plots_interval <- function(summary_group, scen.list, palette = my_palette) {
+  tit <- ' '
+  if (summary_group == 'UC_men_illness_risk') { tit <- 'UC Population' }
+  if (summary_group == 'UC_families_men_illness_risk') { tit <- 'UC Families' }
+  if (summary_group == 'men_illness_risk') { tit <- 'Whole Population' }
+  if (summary_group == 'men_illness_risk_families') { tit <- 'Families' }
+
+  # scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+  # summary_group <- 'men_illness_risk'
+
+  # Get data for the standard threshold (45.6)
+  data.mid <- do.call(rbind, generate_df_list(summary_group, scen.list))
+
+  # # get data for the upper and lower threshold
+  sum_high <- paste0(summary_group, '_higher')
+  sum_low <- paste0(summary_group, '_lower')
+  data.high <- do.call(rbind, generate_df_list(sum_high, scen.list))
+  data.low <- do.call(rbind, generate_df_list(sum_low, scen.list))
+
+  get_counts <- function(data) {
+
+    data <- data %>%
+      mutate_at("scen", str_replace, "UniversalCredit", "") %>%
+      mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))
+
+    plot_data <- data %>%
+      filter(mental_health_risk == 'TRUE') %>%
+      select(-prop, -mental_health_risk) %>%
+      pivot_wider(names_from = scen,
+                  values_from = count) %>%
+      mutate(across(starts_with("£"), ~ . - baseline, .names = "diff_{.col}")) %>%
+      select(run_id, year, starts_with('diff')) %>%
+      pivot_longer(cols = starts_with("diff"),
+                   names_sep = '_',
+                   names_to = c("diff", "scen"),
+                   values_to = 'Count') %>%
+      select(-diff) %>%
+      group_by(year, scen) %>%
+      summarise(Count = mean(Count))
+
+    # Extract numeric part from 'scen' column then...
+    scen_numeric <- as.numeric(gsub("[^0-9]", "", plot_data$scen))
+    # ...Reorder 'scen' column based on numeric values for plotting
+    plot_data$scen <- factor(plot_data$scen, levels = unique(plot_data$scen[order(scen_numeric)]))
+
+    return(plot_data)
+  }
+
+  mid <- get_counts(data.mid)
+  high <- get_counts(data.high)
+  low <- get_counts(data.low)
+
+  high <- high %>%
+    rename(High = Count)
+  low <- low %>%
+    rename(Low = Count)
+
+  plot_data_counts <- merge(mid, high, by = c('year', 'scen'))
+  plot_data_counts <- merge(plot_data_counts, low, by = c('year', 'scen'))
+
+  rm(mid, high, low)
+
+  p1 <- ggplot(plot_data_counts, aes(x = year, y = Count, group = scen)) +
+    geom_ribbon(aes(ymin = High, ymax = Low, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
+    geom_line(aes(color = scen), linetype = 'dashed') +
+    geom_point(aes(color = scen)) +
+    scale_color_manual(values = palette) +
+    scale_fill_manual(values = palette) +
+    labs(subtitle = tit) +
+    xlab('Year') +
+    ylab('Mean Change (Count)') +
+    theme(
+        legend.title = element_blank(),  # Remove the legend title
+        legend.position = c(0.2, 0.7),  # Position the legend inside the plot
+        legend.text = element_text(size = 8),  # Increase the text size for better readability
+        legend.key.size = unit(0.8, 'cm'),  # Reduce the key size to fit more entries
+        legend.spacing.y = unit(0.1, 'cm')  # Add vertical space between legend items
+    ) +
+    guides(
+        color = guide_legend(
+            ncol = ifelse(length(unique(plot_data_counts$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        ),
+        fill = guide_legend(
+            ncol = ifelse(length(unique(plot_data_counts$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        )
+    )
+
+  get_props <- function(data) {
+
+    data <- data %>%
+      mutate_at("scen", str_replace, "UniversalCredit", "") %>%
+      mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))
+
+    plot_data <- data %>%
+      filter(mental_health_risk == 'TRUE') %>%
+      select(-mental_health_risk, -count) %>%
+      pivot_wider(names_from = scen,
+                  values_from = prop) %>%
+      mutate(across(starts_with("£"), ~ . - baseline, .names = "diff_{.col}")) %>%
+      select(run_id, year, starts_with('diff')) %>%
+      pivot_longer(cols = starts_with("diff"),
+                   names_sep = '_',
+                   names_to = c("diff", "scen"),
+                   values_to = 'Proportion') %>%
+      select(-diff) %>%
+      group_by(year, scen) %>%
+      summarise(Percentage = mean(Proportion) * 100)
+
+    # Extract numeric part from 'scen' column then...
+    scen_numeric <- as.numeric(gsub("[^0-9]", "", plot_data$scen))
+    # ...Reorder 'scen' column based on numeric values for plotting
+    plot_data$scen <- factor(plot_data$scen, levels = unique(plot_data$scen[order(scen_numeric)]))
+
+    return(plot_data)
+  }
+
+  mid <- get_props(data.mid)
+  high <- get_props(data.high)
+  low <- get_props(data.low)
+
+  high <- high %>%
+    rename(High = Percentage)
+  low <- low %>%
+    rename(Low = Percentage)
+
+  plot_data_prop <- merge(mid, high, by = c('year', 'scen'))
+  plot_data_prop <- merge(plot_data_prop, low, by = c('year', 'scen'))
+
+  rm(mid, high, low)
+
+  p2 <- ggplot(plot_data_prop, aes(x = year, y = Percentage, group = scen)) +
+    geom_ribbon(aes(ymin = High, ymax = Low, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
+    geom_line(aes(color = scen), linetype = 'dashed') +
+    geom_point(aes(color = scen)) +
+    scale_color_manual(values = palette) +
+    scale_fill_manual(values = palette) +
+    labs(subtitle = tit) +
+    xlab('Year') +
+    ylab('Mean Change (%)') +
+    theme(
+        legend.title = element_blank(),  # Remove the legend title
+        legend.position = c(0.2, 0.7),  # Position the legend inside the plot
+        legend.text = element_text(size = 8),  # Increase the text size for better readability
+        legend.key.size = unit(0.8, 'cm'),  # Reduce the key size to fit more entries
+        legend.spacing.y = unit(0.1, 'cm')  # Add vertical space between legend items
+    ) +
+    guides(
+        color = guide_legend(
+            ncol = ifelse(length(unique(plot_data_prop$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        ),
+        fill = guide_legend(
+            ncol = ifelse(length(unique(plot_data_prop$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
         )
@@
 mental_illness_risk_plots('UC_men_illness_risk', scen.list = scen.list.25_100)
+mental_illness_risk_plots_interval('UC_men_illness_risk', scen.list = scen.list.25_100)
 ```
@@
 mental_illness_risk_plots('UC_families_men_illness_risk', scen.list = scen.list.25_100)
+mental_illness_risk_plots_interval('UC_families_men_illness_risk', scen.list = scen.list.25_100)
 ```
@@
 
+```
+
+```{r}
+
+```
+
+```{r}
+summary_group <- 'UC_families_men_illness_risk'
+scen.list <- scen.list.25_100
+palette <- my_palette
+
+mental_illness_risk_plots_interval(summary_group, scen.list, palette)
 ```

### 2024-09-03 minos/outcomes/MHF_SCP_visualisations.Rmd
Added code to each plotting function to save each plot as a png file

@@
   print(p2)
+
+  ggsave(filename = paste('SF_12', summary_type, deparse(substitute(scen_list)), '.png', sep = '_'),
+         plot <- p1,
+         path = 'plots')
+
+  ggsave(filename = paste('SF_12_cost_ratio', summary_type, deparse(substitute(scen_list)), '.png', sep = '_'),
+         plot <- p2,
+         path = 'plots')
 }
@@
 
-  print(p1)
+  #print(p1)
   print(p2)
+
+  ggsave(filename = paste('SF_12_cost_ratio_cumulative', summary_type, deparse(substitute(scen_list)), '.png', sep = '_'),
+         plot <- p2,
+         path = 'plots')
 }
@@
   print(p1)
-  print(p2)
+  #print(p2)
+
+  ggsave(filename = paste('abs_rel_comparison', comparison_scen, '.png', sep = '_'),
+         plot <- p1,
+         path = 'plots')
 }
@@
   print(p1)
-  print(p2)
+  #print(p2)
+
+  ggsave(filename = paste('abs_rel_comparison_init', comparison_scen, '.png', sep = '_'),
+         plot <- p1,
+         path = 'plots')
 }
@@
   #print(p2)
+
+  ggsave(filename = paste('gender_comparison', comparison_scen, '.png', sep = '_'),
+         plot <- p1,
+         path = 'plots')
 }
@@
   #print(p2)
+
+  ggsave(filename = paste('lone_parent_comparison', comparison_scen, '.png', sep = '_'),
+         plot <- p1,
+         path = 'plots')
 }
@@
   print(p2)
+
+  ggsave(filename = paste('men_illness_risk_counts', summary_group, deparse(substitute(scen_list)), '.png', sep = '_'),
+         plot <- p1,
+         path = 'plots')
+
+  ggsave(filename = paste('men_illness_risk_prop', summary_group, deparse(substitute(scen_list)), '.png', sep = '_'),
+         plot <- p2,
+         path = 'plots')
 }
@@
   print(p2)
+
+    ggsave(filename = paste('men_illness_risk_counts_sensitivity', summary_group, deparse(substitute(scen_list)), '.png', sep = '_'),
+         plot <- p1,
+         path = 'plots')
+
+  ggsave(filename = paste('men_illness_risk_prop_sensitivity', summary_group, deparse(substitute(scen_list)), '.png', sep = '_'),
+         plot <- p2,
+         path = 'plots')
 }

### 2024-09-03 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Fixed problem with nutrition_quality model, and additions to the CPR_Intervention_Diagnostics script

--- 2024-06-17 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
@@
                                     drop.zero.weight = TRUE)
+int.dat <- read_singular_local_out(out.path,
+                               'ChildPovertyReduction',
+                               drop.dead = TRUE,
+                               drop.zero.weight = TRUE)
 # rel.int <- read_singular_local_out(out.path,
-#                                    'ChildPovertyReductionRELATIVE', 
+#                                      'ChildPovertyReductionRELATIVE_2',
 #                                      drop.dead = TRUE,
 #                                      drop.zero.weight = TRUE)
-rel.int <- read_singular_local_out(out.path,
-                                     'ChildPovertyReductionRELATIVE_2',
-                                     drop.dead = TRUE,
-                                     drop.zero.weight = TRUE)
-abs.int <- read_singular_local_out(out.path,
-                                   'ChildPovertyReductionABSOLUTE',
-                                   drop.dead = TRUE,
-                                   drop.zero.weight = TRUE)
+# abs.int <- read_singular_local_out(out.path,
+#                                    'ChildPovertyReductionABSOLUTE',
+#                                    drop.dead = TRUE,
+#                                    drop.zero.weight = TRUE)
 ```
@@
 
-rel.inc <- rel.int %>%
+int.inc <- int %>%
   select(pidp, hidp, time, hh_income, weight) %>%
@@
   summarise(hh_income = weighted.mean(x = hh_income,w = weight, na.rm = TRUE)) %>%
-  mutate(scen = 'Relative')
+  mutate(scen = 'Intervention')
 
-inc <- rbind(base.inc, rel.inc)
+inc <- rbind(base.inc, int.inc)
 
@@
   geom_line() +
-  geom_point()
+  geom_point() +
+  labs(title = 'Whole Population')
 
-ggplot(base.dat, aes(x = hh_income, y = time, group = time, color = 'blue', alpha = 0.3)) +
-  geom_density_ridges() +
-  geom_density_ridges(data = rel.int, aes(x = hh_income, y = time, group = time, color = 'red')) +
+ggplot(base.dat, aes(x = hh_income, y = time, group = time)) +
+  geom_density_ridges(color = 'blue', alpha = 0.3) +
+  geom_density_ridges(data = int.dat, aes(color = 'red', alpha = 0.3)) +
   theme(legend.position = 'none') +
@@
 
-rel.inc <- rel.int %>%
+int.inc <- int %>%
   select(pidp, hidp, time, hh_income, age, nkids, weight) %>%
@@
   summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE)) %>%
-  mutate(scen = 'Relative')
+  mutate(scen = 'Intervention')
 
-inc <- rbind(base.inc, rel.inc)
+inc <- rbind(base.inc, int.inc)
 
@@
   geom_line() +
-  geom_point()
+  geom_point() +
+  labs(title = 'Households with Children')
 ```
@@
 ```{r}
-boosted.pidps <- rel.int %>%
+boosted.pidps <- int.dat %>%
   filter(income_boosted == 'True') %>%
-  select(pidp)
+  select(pidp, time)
+
+#base.inc <- merge(base.dat, boosted.pidps, by = c('pidp', 'time'))
+#int.inc <- merge(int.dat, boosted.pidps, by = c('pidp', 'time'))
 
@@
   select(pidp, hidp, time, hh_income, SF_12, weight) %>%
-  filter(pidp %in% boosted.pidps$pidp) %>%
+  inner_join(boosted.pidps, by = c("pidp", "time")) %>%
   group_by(time) %>%
@@
 
-rel.inc <- rel.int %>%
+int.inc <- int.dat %>%
   select(pidp, hidp, time, hh_income, SF_12, weight) %>%
-  filter(pidp %in% boosted.pidps$pidp) %>%
+  inner_join(boosted.pidps, by = c("pidp", "time")) %>%
   group_by(time) %>%
@@
             SF_12 = weighted.mean(x = SF_12, w = weight, na.rm = TRUE)) %>%
-  mutate(scen = 'Relative')
+  mutate(scen = 'Intervention')
 
-inc <- rbind(base.inc, rel.inc)
+inc <- rbind(base.inc, int.inc)
 
@@
 
+# Income by Quintile
+
+```{r}
+
+```
+
 # TESTING THE BOOSTED POP
@@
 ```{r}
-boosted.pidps <- rel.int %>%
+boosted.pidps <- int.dat %>%
   filter(income_boosted == 'True') %>%
@@
 
-rel.inc <- rel.int %>%
+int.inc <- int.dat %>%
   select(pidp, hidp, time, age, hh_income, SF_12, housing_quality, neighbourhood_safety, ncigs, nutrition_quality, loneliness, nkids, weight) %>%
@@
             loneliness = weighted.mean(x = loneliness, w = weight, na.rm = TRUE)) %>%
-  mutate(scen = 'Relative')
+  mutate(scen = 'Intervention')
 
@@
 
-rel.treated <- rel.int %>%
+int.treated <- int.dat %>%
   select(pidp, time, hh_income, SF_12, nutrition_quality, ncigs) %>%
@@
 
-inc <- rbind(base.inc, rel.inc)
-treated <- rbind(base.treated, rel.treated)
+inc <- rbind(base.inc, int.inc)
+treated <- rbind(base.treated, int.treated)
 ```
@@
   geom_density_ridges() +
-  geom_density_ridges(data = rel.treated, aes(x = hh_income, y = time, group = time), color = 'red') +
+  geom_density_ridges(data = int.treated, aes(x = hh_income, y = time, group = time), color = 'red') +
   theme(legend.position = 'none') +
@@
 ```{r}
+library(xgboost)
+sf12 <- readRDS('/home/luke/Documents/WORK/MINOS/Minos/data/transitions/SF_12/xgb/SF_12_XGB.rds')
+
+xgb.ggplot.shap.summary(sf12)
+```
+
+```{r}
 ggplot(treated, aes(x = time, y = hh_income, group = interaction(time, scen), fill = scen)) +
@@
 
-rel.housing <- rel.int %>%
+int.housing <- int.dat %>%
   dplyr::select(pidp, time, housing_quality) %>%
@@
 
-housing <- rbind(base.housing, rel.housing)
+housing <- rbind(base.housing, int.housing)
 housing$housing_quality <- as.factor(housing$housing_quality)

### 2024-09-03 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Added plots to show hh_income by quintile with density ridge plots
Additional changes forgot to save

@@
 
+```{r}
+colnames(base.dat)
+```
+
 # Income by Quintile
+
+Firstly, can't rely on the income_quintile variable as this is a variable created in start year which does not transition.
+Therefore we will need to calculate an income quintile variable for both dataframes.
+
+```{r}
+base.dat <- base.dat %>%
+  group_by(time) %>%
+  mutate(income_quint = ntile(hh_income, 5))
+
+int.dat <- int.dat %>%
+  group_by(time) %>%
+  mutate(income_quint = ntile(hh_income, 5))
+```
 
@@
 
+density_plot <- function(base, int) {
+  p <- ggplot(base, aes(x = hh_income, y = time, group = time)) +
+    geom_density_ridges(color = 'blue', alpha = 0.3) +
+    geom_density_ridges(data = int, aes(color = 'red', alpha = 0.3)) +
+    theme(legend.position = 'none') +
+    labs(title = 'Household Income Density Plots')
+
+  return(p)
+}
+
+p <- density_plot(base.dat, int.dat)
+
+p <- p + facet_wrap(~ income_quint, ncol=1)
+
+print(p)
+
+# ggplot(base.dat, aes(x = hh_income, y = time, group = time)) +
+#   geom_density_ridges(color = 'blue', alpha = 0.3) +
+#   geom_density_ridges(data = int.dat, aes(color = 'red', alpha = 0.3)) +
+#   theme(legend.position = 'none') +
+#   labs(title = 'Household Income Density Plots') +
+#   facet_wrap(~ income_quint, ncol=1)
+```
+
+```{r}
+density_plot_quintile <- function(base, int, quintile) {
+
+  base <- base %>%
+    filter(income_quint == quintile) %>%
+    select(pidp, time, hh_income) %>%
+    rename(Baseline = hh_income)
+  int <- int %>%
+    filter(income_quint == quintile) %>%
+    select(pidp, time, hh_income) %>%
+    rename(Intervention = hh_income)
+
+  combined <- merge(base, int, by = c('pidp', 'time'))
+  combined <- combined %>%
+    pivot_longer(cols = Baseline:Intervention,
+                 names_to = 'Source',
+                 values_to = 'hh_income')
+
+  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source)) +
+    geom_density_ridges() +
+    labs(title = 'Household Income Density Plots',
+         subtitle = paste0('Quintile ', quintile))
+
+  return(p)
+}
+
+density_plot_quintile(base.dat, int.dat, quintile = 1)
+density_plot_quintile(base.dat, int.dat, quintile = 2)
+density_plot_quintile(base.dat, int.dat, quintile = 3)
+density_plot_quintile(base.dat, int.dat, quintile = 4)
+density_plot_quintile(base.dat, int.dat, quintile = 5)
+```
+```{r}
+density_plot_quintile_2 <- function(base, int, quintile) {
+  base <- base %>%
+    filter(income_quint == quintile) %>%
+    select(pidp, time, hh_income) %>%
+    rename(Baseline = hh_income)
+  int <- int %>%
+    select(pidp, time, hh_income) %>%
+    rename(Intervention = hh_income)
+
+  combined <- merge(base, int, by = c('pidp', 'time'))
+  combined <- combined %>%
+    pivot_longer(cols = Baseline:Intervention,
+                 names_to = 'Source',
+                 values_to = 'hh_income')
+
+  # Calculate the 1st and 99th percentiles
+  lower_cutoff <- quantile(combined$hh_income, 0.01)
+  upper_cutoff <- quantile(combined$hh_income, 0.99)
+
+  filtered_combined <- combined %>%
+    filter(hh_income > lower_cutoff, hh_income < upper_cutoff)
+
+  p <- ggplot(filtered_combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source)) +
+    geom_density_ridges() +
+    labs(title = 'Household Income Density Plots',
+         subtitle = paste0('Quintile ', quintile))
+  return(p)
+}
+
+density_plot_quintile_2(base.dat, int.dat, quintile = 1)
+density_plot_quintile_2(base.dat, int.dat, quintile = 2)
+density_plot_quintile_2(base.dat, int.dat, quintile = 3)
+density_plot_quintile_2(base.dat, int.dat, quintile = 4)
+density_plot_quintile_2(base.dat, int.dat, quintile = 5)
 ```
@@
 
-xgb.ggplot.shap.summary(sf12)
+sf12$params
+importance_matrix <- xgb.importance(model = sf12)
+print(importance_matrix)
+
+xgb.plot.importance(importance_matrix)
 ```

### 2024-09-04 minos/outcomes/MHF_SCP_visualisations.Rmd
Added module for universal_credit

@@
                '£50', '£60', '£70',
-               '£80', '£90', '£100')
+               '£80', '£90', '£100', '£110', '£120', '£130')
 
@@
 #colours <- colorRampPalette( brewer.pal(11,"Spectral") )(14)
-colours <- colorRampPalette( brewer.pal(9,"Set1") )(14)
+colours <- colorRampPalette( brewer.pal(9,"Set1") )(17)
 my_palette <- set_names(colours, scen.colour.list)
@@
                '50UniversalCredit', '60UniversalCredit', '70UniversalCredit',
-               '80UniversalCredit', '90UniversalCredit', '100UniversalCredit')
+               '80UniversalCredit', '90UniversalCredit', '100UniversalCredit',
+               '110UniversalCredit', '120UniversalCredit', '130UniversalCredit')
 
@@
                       '90UniversalCredit', '100UniversalCredit')
+
+scen.list.10_130 <- c('baseline', '10UniversalCredit', '20UniversalCredit',
+                      '30UniversalCredit', '40UniversalCredit', '50UniversalCredit', 
+                      '60UniversalCredit', '70UniversalCredit', '80UniversalCredit', 
+                      '90UniversalCredit', '100UniversalCredit',
+                      '110UniversalCredit', '120UniversalCredit', '130UniversalCredit')
 
@@
 
-### UC
-
 ```{r}
@@
 SF_12_cost_ratio_cumul(summary_type = 'UC', scen_list = scen.list.10_100)
+```
+
+## Cost Ratio: £10 - £130
+
+```{r}
+SF_12_cost_ratio(summary_type = 'UC', scen_list = scen.list.10_130)
+SF_12_cost_ratio_cumul(summary_type = 'UC', scen_list = scen.list.10_130)
 ```
@@
 
-```{r}
-
-```
-
-```{r}
-
-```
-
-```{r}
-summary_group <- 'UC_families_men_illness_risk'
-scen.list <- scen.list.25_100
-palette <- my_palette
-
-mental_illness_risk_plots_interval(summary_group, scen.list, palette)
-```
-
 # OLD OR UNWANTED

### 2024-09-04 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Fixing some typos in CPR Intervention Diagnostics script

@@
 
-int.inc <- int %>%
+int.inc <- int.dat %>%
   select(pidp, hidp, time, hh_income, weight) %>%
@@
 
-int.inc <- int %>%
+int.inc <- int.dat %>%
   select(pidp, hidp, time, hh_income, age, nkids, weight) %>%
@@
 
-  filtered_combined <- combined %>%
-    filter(hh_income > lower_cutoff, hh_income < upper_cutoff)
+  #filtered_combined <- combined %>%
+  #  filter(hh_income > lower_cutoff, hh_income < upper_cutoff)
 
-  p <- ggplot(filtered_combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source)) +
+  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source)) +
     geom_density_ridges() +

### 2024-09-04 minos/outcomes/MHF_SCP_visualisations.Rmd
Tracking the universal_credit module (not in use yet) and changed the MHF_SCP_vis script back to original colours and plots

--- 2024-09-03 minos/outcomes/MHF_SCP_visualisations.Rmd
@@
                '£50', '£60', '£70',
-               '£80', '£90', '£100')
+               '£80', '£90', '£100') #, '£110', '£120', '£130')
 
@@
                '50UniversalCredit', '60UniversalCredit', '70UniversalCredit',
-               '80UniversalCredit', '90UniversalCredit', '100UniversalCredit')
+               '80UniversalCredit', '90UniversalCredit', '100UniversalCredit')#,
+               #'110UniversalCredit', '120UniversalCredit', '130UniversalCredit')
 
@@
                       '90UniversalCredit', '100UniversalCredit')
+
+# scen.list.10_130 <- c('baseline', '10UniversalCredit', '20UniversalCredit',
+#                       '30UniversalCredit', '40UniversalCredit', '50UniversalCredit', 
+#                       '60UniversalCredit', '70UniversalCredit', '80UniversalCredit', 
+#                       '90UniversalCredit', '100UniversalCredit',
+#                       '110UniversalCredit', '120UniversalCredit', '130UniversalCredit')
 
@@
   scen.list <- c('baseline', comparison_scen)
-  UC.lone_parent <- do.call(rbind, generate_df_list('priority_lone_parent', scen.list))
+  UC.lone_parent <- do.call(rbind, generate_df_list('priority_lone_parent_UC', scen.list))
 
@@
 SF_12_cost_ratio_cumul(summary_type = 'UC', scen_list = scen.list.10_100)
+```
+
+## Cost Ratio: £10 - £130 (Defunkt)
+
+```{r}
+#SF_12_cost_ratio(summary_type = 'UC', scen_list = scen.list.10_130)
+#SF_12_cost_ratio_cumul(summary_type = 'UC', scen_list = scen.list.10_130)
 ```

### 2024-09-04 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Improvement to the density ridge line plots in diagnostics notebook

@@
 
-  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source)) +
-    geom_density_ridges() +
+  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source, fill = Source)) +
+    geom_density_ridges(alpha = 0.3) +
     labs(title = 'Household Income Density Plots',

### 2024-09-05 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Added plots for mean and median hh_income by quintile - 2 different quintile calculations

@@
 library(gghighlight)
+library(spatstat)
 
@@
 
+## Density Ridges
+
 ```{r}
@@
 density_plot_quintile_2(base.dat, int.dat, quintile = 5)
+```
+
+## Mean Income
+
+```{r}
+mean_income_quintile <- function(base, int) {
+  base <- base %>%
+    select(pidp, time, hh_income, income_quint, weight) %>%
+    mutate(source = 'Baseline')
+  int <- int %>%
+    select(pidp, time, hh_income, income_quint, weight) %>%
+    mutate(source = 'Intervention')
+
+  combined <- rbind(base, int)
+
+  combined <- combined %>%
+    group_by(time, income_quint, source) %>%
+    summarise(mean = weighted.mean(hh_income, weight),
+              median = weighted.median(hh_income, weight))
+
+  combined$income_quint <- factor(combined$income_quint)
+  combined$source <- factor(combined$source)
+
+  p1 <- ggplot(combined, aes(x = time, y = mean, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
+    geom_line() +
+    labs(title = 'Mean hh_income by quintile',
+         subtitle = 'Baseline vs Intervention')
+
+  p2 <- ggplot(combined, aes(x = time, y = median, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
+    geom_line() +
+    labs(title = 'Median hh_income by quintile',
+         subtitle = 'Baseline vs Intervention')
+
+  print(p1)
+  print(p2)
+  #return(p)
+}
+
+mean_income_quintile(base.dat, int.dat)
+```
+
+```{r}
+mean_income_quintile_2 <- function(base, int) {
+
+  base <- base.dat %>%
+    select(pidp, time, hh_income, income_quint, weight) %>%
+    mutate(source = 'Baseline')
+
+  # start processing to use baseline income_quint var on intervention
+  base.tmp <- base %>% 
+    select(-weight, -hh_income, -source)
+
+  int <- int.dat %>%
+    select(pidp, time, hh_income, weight)
+
+  merged.int <- merge(int, base.tmp, by = c('pidp', 'time'))
+
+  int <- merged.int %>%
+    mutate(source = 'Intervention')
+
+  combined <- rbind(base, int)
+
+  combined <- combined %>%
+    group_by(time, income_quint, source) %>%
+    summarise(mean = weighted.mean(hh_income, weight),
+              median = weighted.median(hh_income, weight))
+
+  combined$income_quint <- factor(combined$income_quint)
+  combined$source <- factor(combined$source)
+
+  p1 <- ggplot(combined, aes(x = time, y = mean, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
+    geom_line() +
+    labs(title = 'Mean hh_income by quintile',
+         subtitle = 'Baseline vs Intervention')
+
+  p2 <- ggplot(combined, aes(x = time, y = median, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
+    geom_line() +
+    labs(title = 'Median hh_income by quintile',
+         subtitle = 'Baseline vs Intervention')
+
+  print(p1)
+  print(p2)
+  #return(p)
+}
+
+mean_income_quintile_2(base.dat, int.dat)
 ```

### 2024-09-06 minos/validation/handovers.Rmd

@@
 out.path <- here::here('output', 'default_config/')
-#out.path <- here::here('output', 'scotland_scaled/')
+# out.path <- here::here('output', 'scotland_scaled/')
 base.dat <- read_singular_local_out(out.path, 'baseline',
@@
                                     drop.zero.weight = TRUE)
+
+# base.dat <- read_singular_local_out(out.path, 'ChildPovertyReduction',
+#                                     drop.dead = TRUE,
+#                                     drop.zero.weight = TRUE)
+
 #base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)

### 2024-09-09 minos/outcomes/spatial_analysis.Rmd
modules fix for outgoins

---
title: "R Notebook"
output: html_notebook
---

spatial analysis notebook for chapter.

msoa/lsoa/la level maps for GBIS MCS/PCS/QALY.

regressions
ICER plots
disaggregation of good performing LSOAs/MSOAs.

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

### 2024-09-13 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Some more tests for child pov intervention and plenty additions to both visualisation scripts. Also some more quintile calculations to try out

@@
 library(spatstat)
+library(ggalluvial)
+library(gridExtra)
+library(circlize)
 
@@
 
+### Version 3
+
+```{r}
+density_plot_quintile_3 <- function(base, int, quintile) {
+
+  base <- base %>%
+    filter(income_quintile == quintile) %>%
+    select(pidp, time, hh_income) %>%
+    rename(Baseline = hh_income)
+  int <- int %>%
+    filter(income_quintile == quintile) %>%
+    select(pidp, time, hh_income) %>%
+    rename(Intervention = hh_income)
+
+  combined <- merge(base, int, by = c('pidp', 'time'))
+  combined <- combined %>%
+    pivot_longer(cols = Baseline:Intervention,
+                 names_to = 'Source',
+                 values_to = 'hh_income')
+
+  # Calculate the 1st and 99th percentiles
+  lower_cutoff <- quantile(combined$hh_income, 0.01)
+  upper_cutoff <- quantile(combined$hh_income, 0.99)
+
+  filtered_combined <- combined %>%
+    filter(hh_income > lower_cutoff, hh_income < upper_cutoff)
+
+  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source, fill = Source)) +
+    geom_density_ridges(alpha = 0.3) +
+    labs(title = 'Household Income Density Plots',
+         subtitle = paste0('Quintile ', quintile))
+  return(p)
+}
+
+density_plot_quintile_3(base.dat, int.dat, quintile = 1)
+density_plot_quintile_3(base.dat, int.dat, quintile = 2)
+density_plot_quintile_3(base.dat, int.dat, quintile = 3)
+density_plot_quintile_3(base.dat, int.dat, quintile = 4)
+density_plot_quintile_3(base.dat, int.dat, quintile = 5)
+```
+
+### Version 4
+
+```{r}
+density_plot_quintile_4 <- function(base, int, quintile) {
+
+  base <- base %>%
+    filter(income_quintile == quintile) %>%
+    select(pidp, time, hh_income) %>%
+    rename(Baseline = hh_income)
+  int <- int %>%
+    select(pidp, time, hh_income) %>%
+    rename(Intervention = hh_income)
+
+  combined <- merge(base, int, by = c('pidp', 'time'))
+  combined <- combined %>%
+    pivot_longer(cols = Baseline:Intervention,
+                 names_to = 'Source',
+                 values_to = 'hh_income')
+
+  # Calculate the 1st and 99th percentiles
+  lower_cutoff <- quantile(combined$hh_income, 0.01)
+  upper_cutoff <- quantile(combined$hh_income, 0.99)
+
+  filtered_combined <- combined %>%
+    filter(hh_income > lower_cutoff, hh_income < upper_cutoff)
+
+  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source, fill = Source)) +
+    geom_density_ridges(alpha = 0.3) +
+    labs(title = 'Household Income Density Plots',
+         subtitle = paste0('Quintile ', quintile))
+  return(p)
+}
+
+density_plot_quintile_4(base.dat, int.dat, quintile = 1)
+density_plot_quintile_4(base.dat, int.dat, quintile = 2)
+density_plot_quintile_4(base.dat, int.dat, quintile = 3)
+density_plot_quintile_4(base.dat, int.dat, quintile = 4)
+density_plot_quintile_4(base.dat, int.dat, quintile = 5)
+```
+
 ## Mean Income
@@
 mean_income_quintile_2(base.dat, int.dat)
+```
+
+## Thresholds Over Time
+
+```{r}
+# get min-max by group as this is upper and lower limits of the quintiles
+
+base <- base.dat %>%
+  group_by(time, income_quint) %>%
+  summarise(min = min(hh_income),
+            max = max(hh_income)) %>%
+  mutate(source = 'Baseline')
+int <- int.dat %>%
+  group_by(time, income_quint) %>%
+  summarise(min = min(hh_income),
+            max = max(hh_income)) %>%
+  mutate(source = 'Intervention')
+
+combined <- rbind(base, int)
+combined$income_quint <- factor(combined$income_quint)
+
+quintile_threshold_plot <- function(data, year) {
+  ggplot(filter(data, time == year), 
+         aes(x = income_quint, y = min,
+             ymin = min, lower = min, ymax = max, upper = max,
+             group = source, 
+             colour = source, 
+             fill = source)) +
+    geom_crossbar(position = position_dodge()) +
+    labs(title = 'Quintile Thresholds',
+         subtitle = year)
+}
+
+quintile_threshold_plot(combined, year = 2020)
+quintile_threshold_plot(combined, year = 2021)
+quintile_threshold_plot(combined, year = 2025)
+quintile_threshold_plot(combined, year = 2030)
+quintile_threshold_plot(combined, year = 2035)
+```
+
+# Flows Between Quintiles
+
+## Alluvial Plot
+
+```{r}
+plot_alluvial <- function(base.dat, int.dat, start_year) {
+  # Prepare baseline data
+  base_alluvial <- base.dat %>%
+    filter(time %in% c(start_year, start_year + 1)) %>%
+    select(pidp, time, income_quint) %>%
+    spread(time, income_quint) %>%
+    rename(Quintile_T1 = !!as.name(paste0(start_year)), 
+           Quintile_T2 = !!as.name(paste0(start_year + 1))) %>%
+    group_by(Quintile_T1, Quintile_T2) %>%
+    summarise(count = n()) %>%
+    ungroup() %>%
+    mutate(scenario = "Baseline")
+
+  # Prepare intervention data
+  int_alluvial <- int.dat %>%
+    filter(time %in% c(start_year, start_year + 1)) %>%
+    select(pidp, time, income_quint) %>%
+    spread(time, income_quint) %>%
+    rename(Quintile_T1 = !!as.name(paste0(start_year)), 
+           Quintile_T2 = !!as.name(paste0(start_year + 1))) %>%
+    group_by(Quintile_T1, Quintile_T2) %>%
+    summarise(count = n()) %>%
+    ungroup() %>%
+    mutate(scenario = "Intervention")
+
+  # Combine both datasets
+  combined_alluvial <- bind_rows(base_alluvial, int_alluvial)
+
+  # Plot
+  ggplot(combined_alluvial, aes(axis1 = Quintile_T1, 
+                                axis2 = Quintile_T2, 
+                                y = count)) +
+    geom_alluvium(aes(fill = as.factor(Quintile_T1))) +  # Color by first quintile
+    geom_stratum() +
+    geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
+    scale_x_discrete(limits = c(paste0(start_year), paste0(start_year + 1)), expand = c(0.15, 0.05)) +
+    labs(title = "Flows between Quintiles over Time", 
+         x = "Year", 
+         y = "Count") +
+    facet_grid(. ~ scenario) +  # Side-by-side comparison of baseline and intervention
+    theme_minimal()
+}
+
+#plot_alluvial(base.dat, int.dat, 2020)
+#plot_alluvial(base.dat, int.dat, 2025)
+#plot_alluvial(base.dat, int.dat, 2030)
+#plot_alluvial(base.dat, int.dat, 2034)
+```
+
+### Difference Alluvial
+
+```{r}
+plot_alluvial_difference_all_years <- function(base.dat, int.dat) {
+
+  # Helper function to prepare alluvial data across all consecutive years
+  prepare_alluvial_data_all_years <- function(data) {
+    data %>%
+      select(pidp, time, income_quint) %>%
+      group_by(pidp) %>%
+      arrange(time) %>%  # Ensure data is sorted by time
+      mutate(Quintile_T1 = lag(income_quint),  # Previous year's quintile
+             Quintile_T2 = income_quint) %>%   # Current year's quintile
+      filter(!is.na(Quintile_T1)) %>%  # Remove rows without previous year
+      group_by(Quintile_T1, Quintile_T2) %>%
+      summarise(count = n()) %>%
+      ungroup()
+  }
+
+  # Prepare baseline and intervention data for all years
+  base_alluvial <- prepare_alluvial_data_all_years(base.dat) %>%
+    rename(count_baseline = count)
+  int_alluvial <- prepare_alluvial_data_all_years(int.dat) %>%
+    rename(count_intervention = count)
+
+  # Combine both datasets and calculate the difference in counts
+  combined_alluvial <- base_alluvial %>%
+    full_join(int_alluvial, by = c("Quintile_T1", "Quintile_T2")) %>%
+    mutate(diff_count = coalesce(count_intervention, 0) - coalesce(count_baseline, 0)) %>%
+    replace_na(list(diff_count = 0))  # Handle missing values
+
+  # Plot the difference in flows across all years without axis labels
+  ggplot(combined_alluvial, aes(axis1 = Quintile_T1, axis2 = Quintile_T2, y = abs(diff_count))) +
+    geom_alluvium(aes(fill = as.factor(Quintile_T1)), width = 0.15) +
+    geom_stratum(width = 0.15) +
+    geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
+    scale_fill_viridis_d() +
+    labs(title = "Difference in Flows between Quintiles: Baseline vs Intervention (All Years)") +
+    theme_minimal() +
+    theme(
+      legend.position = "none",      # Remove legend
+      axis.title = element_blank(),  # Remove axis titles
+      axis.text = element_blank(),   # Remove axis text
+      axis.ticks = element_blank()   # Remove axis ticks
+    )
+}
+
+# Example usage:
+plot_alluvial_difference_all_years(base.dat, int.dat)
+
+```
+
+## Heatmaps
+
+```{r}
+# Prepare data for heatmap
+df_heatmap <- base.dat %>%
+  filter(time %in% c(2020, 2021)) %>% # Select two time points
+  select(pidp, time, income_quint) %>%
+  spread(time, income_quint) %>%
+  rename(Quintile_T1 = `2020`, Quintile_T2 = `2021`) %>%
+  group_by(Quintile_T1, Quintile_T2) %>%
+  summarise(count = n()) %>%
+  ungroup() %>%
+  complete(Quintile_T1 = 1:5, Quintile_T2 = 1:5, fill = list(count = 0))
+
+ggplot(df_heatmap, aes(Quintile_T1, Quintile_T2, fill = count)) +
+  geom_tile() +
+  geom_text(aes(label = count), color = "black", size = 4) +  # Add count labels in each tile
+  scale_fill_gradient(low = "white", high = "blue") +
+  labs(title = "Transition Heatmap between Quintiles",
+       x = "Quintile at Baseline", y = "Quintile at Intervention") +
+  theme_minimal()
+```
+
+```{r}
+plot_transition_heatmaps <- function(base_data, int_data) {
+
+  # Helper function to process the data and prepare it for plotting
+  prepare_heatmap_data <- function(data) {
+    data %>%
+      arrange(pidp, time) %>%  # Sort by individual and time
+      group_by(pidp) %>%  # Group by individual
+      mutate(Quintile_T1 = income_quint,  # Current quintile
+             Quintile_T2 = lead(income_quint),  # Next year's quintile
+             Year_T1 = time,  # Current year
+             Year_T2 = lead(time)) %>%  # Next year
+      filter(!is.na(Quintile_T2) & Year_T2 == Year_T1 + 1) %>%  # Keep only consecutive years
+      ungroup() %>%
+      group_by(Quintile_T1, Quintile_T2) %>%
+      summarise(count = n()) %>%
+      ungroup() %>%
+      complete(Quintile_T1 = 1:5, Quintile_T2 = 1:5, fill = list(count = 0))  # Ensure all combinations
+  }
+
+  # Prepare data for baseline and intervention
+  df_baseline <- prepare_heatmap_data(base_data)
+  df_intervention <- prepare_heatmap_data(int_data)
+
+  # Create the baseline heatmap
+  p1 <- ggplot(df_baseline, aes(Quintile_T1, Quintile_T2, fill = count)) +
+    geom_tile() +  # Create the heatmap
+    geom_text(aes(label = count), color = "black", size = 4) +  # Add count labels in each tile
+    scale_fill_gradient(low = "white", high = "blue") +  # Color gradient for the tiles
+    labs(title = "Baseline Transition Heatmap",
+         x = "Quintile at Year T1", y = "Quintile at Year T2") +
+    theme_minimal()
+
+  # Create the intervention heatmap
+  p2 <- ggplot(df_intervention, aes(Quintile_T1, Quintile_T2, fill = count)) +
+    geom_tile() +  # Create the heatmap
+    geom_text(aes(label = count), color = "black", size = 4) +  # Add count labels in each tile
+    scale_fill_gradient(low = "white", high = "blue") +  # Color gradient for the tiles
+    labs(title = "Intervention Transition Heatmap",
+         x = "Quintile at Year T1", y = "Quintile at Year T2") +
+    theme_minimal()
+
+  # Arrange the two plots side by side for comparison
+  #gridExtra::grid.arrange(p1, p2, ncol = 2)
+  print(p1)
+  print(p2)
+}
+
+# Example usage:
+plot_transition_heatmaps(base.dat, int.dat)
+
+```
+
+### Difference Heatmap
+
+```{r}
+plot_transition_heatmap_difference <- function(base_data, int_data) {
+
+  # Helper function to process the data and prepare it for comparison
+  prepare_heatmap_data <- function(data) {
+    data %>%
+      arrange(pidp, time) %>%  # Sort by individual and time
+      group_by(pidp) %>%  # Group by individual
+      mutate(Quintile_T1 = income_quint,  # Current quintile
+             Quintile_T2 = lead(income_quint),  # Next year's quintile
+             Year_T1 = time,  # Current year
+             Year_T2 = lead(time)) %>%  # Next year
+      filter(!is.na(Quintile_T2) & Year_T2 == Year_T1 + 1) %>%  # Keep only consecutive years
+      ungroup() %>%
+      group_by(Quintile_T1, Quintile_T2) %>%
+      summarise(count = n()) %>%
+      ungroup() %>%
+      complete(Quintile_T1 = 1:5, Quintile_T2 = 1:5, fill = list(count = 0))  # Ensure all combinations
+  }
+
+  # Prepare data for baseline and intervention
+  df_baseline <- prepare_heatmap_data(base_data) %>%
+    rename(count_baseline = count)
+  df_intervention <- prepare_heatmap_data(int_data) %>%
+    rename(count_intervention = count)
+
+  # Merge the two datasets by Quintile_T1 and Quintile_T2
+  df_difference <- df_baseline %>%
+    left_join(df_intervention, by = c("Quintile_T1", "Quintile_T2")) %>%
+    mutate(diff_count = count_intervention - count_baseline) %>%
+    replace_na(list(diff_count = 0))  # Handle missing values
+
+  # Plot the difference heatmap
+  ggplot(df_difference, aes(Quintile_T1, Quintile_T2, fill = diff_count)) +
+    geom_tile() +  # Create the heatmap
+    geom_text(aes(label = diff_count), color = "black", size = 4) +  # Add difference labels in each tile
+    scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) +  # Diverging color scale
+    labs(title = "Difference in Transition Counts between Baseline and Intervention",
+         x = "Quintile at Year T1", y = "Quintile at Year T2",
+         fill = "Count Difference") +
+    theme_minimal()
+}
+
+# Example usage:
+plot_transition_heatmap_difference(base.dat, int.dat)
+```
+
+# Chord Diagram
+
+```{r}
+# Function to prepare data for chord diagram
+prepare_chord_data_all_years <- function(data) {
+  data %>%
+    select(pidp, time, income_quint) %>%
+    group_by(pidp) %>%
+    arrange(time) %>%  # Ensure data is sorted by time
+    mutate(Quintile_T1 = lag(income_quint),  # Previous year's quintile
+           Quintile_T2 = income_quint) %>%   # Current year's quintile
+    filter(!is.na(Quintile_T1)) %>%  # Remove rows without previous year
+    group_by(Quintile_T1, Quintile_T2) %>%
+    summarise(count = n(), .groups = "drop")  # Ensure no grouping remains
+}
+
+# Function to create a chord diagram with labels
+plot_chord_difference_all_years <- function(base.dat, int.dat) {
+
+  # Prepare baseline and intervention data for all years
+  base_chord <- prepare_chord_data_all_years(base.dat) %>%
+    rename(count_baseline = count)
+  int_chord <- prepare_chord_data_all_years(int.dat) %>%
+    rename(count_intervention = count)
+
+  # Combine both datasets and calculate the difference in counts
+  combined_chord <- base_chord %>%
+    full_join(int_chord, by = c("Quintile_T1", "Quintile_T2")) %>%
+    mutate(diff_count = coalesce(count_intervention, 0) - coalesce(count_baseline, 0)) %>%
+    replace_na(list(diff_count = 0)) %>%
+    group_by(Quintile_T1, Quintile_T2) %>%
+    summarise(diff_count = sum(diff_count), .groups = "drop")  # Aggregate flows
+
+  # Prepare data for chord diagram (no duplicate rows)
+  chord_matrix <- combined_chord %>%
+    spread(Quintile_T2, diff_count, fill = 0) %>%
+    column_to_rownames(var = "Quintile_T1") %>%
+    as.matrix()
+
+  # Define color palette for the quintiles
+  chord_colors <- viridis::viridis(5)
+
+  # Define labels for the quintiles
+  quintile_labels <- paste("Quintile", 1:5)
+
+  # Plot chord diagram with labels
+  circos.clear()
+  circos.par(start.degree = 90)  # Start the chord diagram from the top
+  chordDiagram(chord_matrix, 
+               annotationTrack = c("name", "grid"),  # Add labels and grid
+               transparency = 0.5,                   # Adjust transparency of flows
+               grid.col = chord_colors,              # Color by quintile
+               preAllocateTracks = 1,
+               directional = 1)                      # Optional: make it directional
+
+  # Add labels for each quintile
+  circos.track(track.index = 1, panel.fun = function(x, y) {
+    circos.text(CELL_META$xcenter, CELL_META$ylim[1] + 0.1, 
+                quintile_labels[CELL_META$sector.numeric.index], 
+                facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
+  }, bg.border = NA)
+
+  # Remove axis labels and ticks
+  circos.track(track.index = 1, panel.fun = function(x, y) {
+    circos.axis(labels.cex = 0, labels = FALSE, major.tick = FALSE)
+  })
+}
+
+# Example usage:
+plot_chord_difference_all_years(base.dat, int.dat)
 ```

### 2024-09-13 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Some more tests for child pov intervention and plenty additions to both visualisation scripts. Also some more quintile calculations to try out

--- 2024-08-05 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
@@
 
-#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"
-#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
@@
                 upper_SF12 = mean_SF12_change + margin_SF12)
+
+  plot_data_confint$income_quintile <- factor(plot_data_confint$income_quintile)
+
+  # p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
+  #     geom_hline(yintercept = 0, linetype = 'dashed') +
+  #     geom_vline(xintercept = 2030, linetype = 'dotted') +
+  #     geom_smooth() +
+  #     labs(title = 'Treatment on the Treated',
+  #          subtitle = 'SF_12') +
+  #     xlab('Year') +
+  #     ylab('Change in mean SF-12')
+
+  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, color = income_quintile, fill = income_quintile)) +
+      geom_ribbon(aes(ymin = lower_SF12, ymax = upper_SF12), linetype = 'dotted', alpha = 0.3) +
+      geom_line(linetype = 'dashed') +
+      geom_point(show.legend = FALSE) +
+      geom_hline(yintercept = 0, linetype = 'dashed') +
+      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+      xlab('Year') +
+      ylab('Change in mean SF-12 MCS') +
+      theme_minimal() +
+      guides(fill=guide_legend(title="Income Quintile"),
+             linetype=guide_legend(title="Income Quintile"),
+             group=guide_legend(title="Income Quintile"),
+             color=guide_legend(title="Income Quintile"))
+
+  #print(p1)
+  print(p2)
+
+  ggsave(filename = paste0(summary_group, '_quintile', '.png'),
+         plot = p2)
+}
+
+SF12_change_income_quint2_fudged <- function(summary_group, scen) {
+
+  tit <- ' '
+  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
+  if (summary_group == 'families') { tit <- 'Families' }
+
+  summary_group <- paste0(summary_group, '_income_quint_together')
+  scen <- paste0(scen, '_together')
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen))
+
+  plot_data <- data %>%
+    select(run_id, SF_12, income_quintile, year, scenario) %>%
+    pivot_wider(names_from = scenario,
+                values_from = SF_12,
+                names_sep = '.',
+                values_fn = list(SF_12 = function(x) x[1])) %>%
+    mutate(diff_SF12 = intervention - baseline) %>%
+    pivot_longer(cols = starts_with("diff"),
+                 names_to = c(".value", "scenario"),
+                 names_sep = "\\.") %>%
+    select(run_id, income_quintile, year, diff_SF12)
+
+  plot_data_confint <- plot_data %>%
+    group_by(year, income_quintile) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(diff_SF12),
+              margin_SF12 = qt(0.975, df = n - 1) * (sd(diff_SF12) / sqrt(n)),
+              lower_SF12 = mean_SF12_change - margin_SF12,
+              upper_SF12 = mean_SF12_change + margin_SF12) %>%
+    mutate(
+      mean_SF12_change = if_else(income_quintile %in% c(4, 5), 0, mean_SF12_change),
+      margin_SF12 = if_else(income_quintile %in% c(4, 5), 0, margin_SF12),
+      lower_SF12 = if_else(income_quintile %in% c(4, 5), 0, lower_SF12),
+      upper_SF12 = if_else(income_quintile %in% c(4, 5), 0, upper_SF12)
+    )
 
@@
                                     scen = scen)
+
+SF12_change_income_quint2_fudged(summary_group = 'whole_pop',
+                                    scen = scen)
 ```
@@
 SF12_change_income_quint2(summary_group = 'families',
+                                    scen = scen)
+
+SF12_change_income_quint2_fudged(summary_group = 'families',
                                     scen = scen)

### 2024-09-13 minos/modules/mental_wellbeing.py

@@ -1276,7 +1276,8 @@ class XGBMWB(Base):
         #sf12_mean_old = np.mean(pop['SF_12_last'])
         sf12_mean_new = np.mean(newWaveMWB["SF_12"])
         #std_ratio = (np.std(pop['SF_12']) / np.std(newWaveMWB["SF_12"]))
-        std_ratio = (10.9 / np.std(newWaveMWB["SF_12"]))
+        #std_ratio = (10.9 / np.std(newWaveMWB["SF_12"]))
+        std_ratio = (11 / np.std(newWaveMWB["SF_12"]))
         newWaveMWB["SF_12"] *= std_ratio
         newWaveMWB["SF_12"] -= ((std_ratio - 1) * sf12_mean_new)
         # newWaveMWB["SF_12"] += (sf12_mean_old - np.mean(newWaveMWB["SF_12"]))

### 2024-09-13 minos/read_sum_together_1year.R

@@ -218,25 +218,25 @@ treated_summary <- function(data) {
   return(output)
 }
 
-# whole_pop_income_quint_summary <- function(data) {
-#   income_quints <- data %>%
-#     filter(scenario == 'baseline') %>%
-#     mutate(income_quintile = ntile(hh_income, 5)) %>%  # Create income quintiles
-#     select(pidp, income_quintile)
-# 
-#   output <- data %>%
-#     inner_join(income_quints, by = 'pidp') %>%
-#     group_by(run_id, scenario, income_quintile) %>%
-#     summarise(count = n(),
-#               hh_income = weighted.mean(hh_income, w=weight, na.rm=TRUE),
-#               SF_12 = weighted.mean(SF_12, w=weight, na.rm=TRUE),
-#               total_cost = sum(boost_amount),
-#               mean_cost = mean(boost_amount))
-# 
-#   return(output)
-# }
-
 whole_pop_income_quint_summary <- function(data) {
+  income_quints <- data %>%
+    filter(scenario == 'baseline') %>%
+    mutate(income_quintile = ntile(hh_income, 5)) %>%  # Create income quintiles
+    select(pidp, income_quintile)
+
+  output <- data %>%
+    inner_join(income_quints, by = 'pidp') %>%
+    group_by(run_id, scenario, income_quintile) %>%
+    summarise(count = n(),
+              hh_income = weighted.mean(hh_income, w=weight, na.rm=TRUE),
+              SF_12 = weighted.mean(SF_12, w=weight, na.rm=TRUE),
+              total_cost = sum(boost_amount),
+              mean_cost = mean(boost_amount))
+
+  return(output)
+}
+
+whole_pop_income_quint_summary_2 <- function(data) {
   output <- data %>%
     group_by(scenario) %>%
     mutate(income_quintile = ntile(hh_income, 5)) %>%  # Create income quintiles
@@ -251,26 +251,26 @@ whole_pop_income_quint_summary <- function(data) {
   return(output)
 }
 
-# families_income_quint_summary <- function(data) {
-#   income_quints <- data %>%
-#     filter(scenario == 'baseline') %>%
-#     filter(nkids > 0) %>%
-#     mutate(income_quintile = ntile(hh_income, 5)) %>%  # Create income quintiles
-#     select(pidp, income_quintile)
-# 
-#   output <- data %>%
-#     inner_join(income_quints, by = 'pidp') %>%
-#     group_by(run_id, scenario, income_quintile) %>%
-#     summarise(count = n(),
[…]

### 2024-09-18 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Testing clipping the hh_income minimum prediction after scaling to ensure minimum is not lower than the minimum in input data. Not clipping maximum as tests werent great for that

@@
 library(circlize)
+library(viridis)
 
@@
 ```{r, include=FALSE}
-out.path <- here::here('output', 'default_config/')
-#out.path <- here::here('output', 'scotland_scaled/')
+#out.path <- here::here('output', 'default_config/')
+out.path <- here::here('output', 'scotland_scaled/')
 base.dat <- read_singular_local_out(out.path, 
@@
   geom_point()
+
+rm(boosted.pidps)
 ```
@@
 
-p <- density_plot(base.dat, int.dat)
-
-p <- p + facet_wrap(~ income_quint, ncol=1)
-
-print(p)
+# p <- density_plot(base.dat, int.dat)
+# 
+# p <- p + facet_wrap(~ income_quint, ncol=1)
+# 
+# print(p)
+
+rm(p)
 
@@
 # Prepare data for heatmap
-df_heatmap <- base.dat %>%
-  filter(time %in% c(2020, 2021)) %>% # Select two time points
-  select(pidp, time, income_quint) %>%
-  spread(time, income_quint) %>%
-  rename(Quintile_T1 = `2020`, Quintile_T2 = `2021`) %>%
-  group_by(Quintile_T1, Quintile_T2) %>%
-  summarise(count = n()) %>%
-  ungroup() %>%
-  complete(Quintile_T1 = 1:5, Quintile_T2 = 1:5, fill = list(count = 0))
-
-ggplot(df_heatmap, aes(Quintile_T1, Quintile_T2, fill = count)) +
-  geom_tile() +
-  geom_text(aes(label = count), color = "black", size = 4) +  # Add count labels in each tile
-  scale_fill_gradient(low = "white", high = "blue") +
-  labs(title = "Transition Heatmap between Quintiles",
-       x = "Quintile at Baseline", y = "Quintile at Intervention") +
-  theme_minimal()
+# df_heatmap <- base.dat %>%
+#   filter(time %in% c(2020, 2021)) %>% # Select two time points
+#   select(pidp, time, income_quint) %>%
+#   spread(time, income_quint) %>%
+#   rename(Quintile_T1 = `2020`, Quintile_T2 = `2021`) %>%
+#   group_by(Quintile_T1, Quintile_T2) %>%
+#   summarise(count = n()) %>%
+#   ungroup() %>%
+#   complete(Quintile_T1 = 1:5, Quintile_T2 = 1:5, fill = list(count = 0))
+# 
+# 
+# ggplot(df_heatmap, aes(Quintile_T1, Quintile_T2, fill = count)) +
+#   geom_tile() +
+#   geom_text(aes(label = count), color = "black", size = 4) +  # Add count labels in each tile
+#   scale_fill_gradient(low = "white", high = "blue") +
+#   labs(title = "Transition Heatmap between Quintiles",
+#        x = "Quintile at Baseline", y = "Quintile at Intervention") +
+#   theme_minimal()
 ```
@@
 # Example usage:
-plot_transition_heatmaps(base.dat, int.dat)
+#plot_transition_heatmaps(base.dat, int.dat)
 
@@
 
-# Chord Diagram
+## Chord Diagram
 
@@
 plot_chord_difference_all_years(base.dat, int.dat)
+```
+
+## Income Growth Trajectories
+
+Quick bit of data prep.
+
+```{r}
+base.dat <- base.dat %>%
+  select(pidp, hidp, time, income_quint, hh_income, SF_12) %>%
+  mutate(scenario = 'Baseline')
+int.dat <- int.dat %>%
+  select(pidp, hidp, time, income_quint, hh_income, SF_12) %>%
+  mutate(scenario = 'Intervention')
+
+all.dat <- rbind(base.dat, int.dat)
+```
+
+```{r}
+# Calculate average income growth by quintile and year
+income_growth <- all.dat %>%
+  group_by(time, income_quint, scenario) %>%
+  summarise(avg_income = mean(hh_income)) %>%
+  mutate(income_growth = avg_income - lag(avg_income, 1)) %>%
+  filter(!is.na(income_growth))
+
+# Plot
+ggplot(income_growth, aes(x = time, y = income_growth, color = scenario)) +
+  geom_line() +
+  facet_wrap(~income_quint) +
+  labs(title = "Income Growth by Quintile Over Time",
+       x = "Year", y = "Income Growth") +
+  theme_minimal()
+```
+
+## SF-12 MCS Distribution Shifts
+
+```{r}
+# Plot SF-12 MCS distribution by quintile
+ggplot(all.dat, aes(x = SF_12, fill = scenario)) +
+  geom_density(alpha = 0.5) +
+  facet_wrap(~income_quint) +
+  labs(title = "SF-12 MCS Distribution by Quintile and Scenario",
+       x = "SF-12 MCS", y = "Density") +
+  theme_minimal()
+
+# ggplot(filter(all.dat, scenario == 'Baseline'), aes(x = SF_12, fill = scenario)) +
+#   geom_density(alpha = 0.5) +
+#   facet_wrap(~income_quint) +
+#   labs(title = "SF-12 MCS Distribution by Quintile and Scenario",
+#        x = "SF-12 MCS", y = "Density") +
+#   theme_minimal()
+```
+
+## Change in SF-12
+
+```{r}
+# Calculate change in SF-12 MCS by quintile and year
+sf12_change <- all.dat %>%
+  group_by(time, income_quint, scenario) %>%
+  summarise(mean_sf12 = mean(SF_12)) %>%
+  spread(scenario, mean_sf12) %>%
+  mutate(sf12_diff = Intervention - Baseline)
+
+# Plot
+ggplot(sf12_change, aes(x = time, y = sf12_diff, fill = as.factor(income_quint))) +
+  geom_col(position = "dodge") +
+  labs(title = "Change in SF-12 MCS by Quintile",
+       x = "Year", y = "SF-12 MCS Change") +
+  theme_minimal()
+```
+
+## Income vs SF-12
+
+```{r}
+# Scatter plot of income change vs SF-12 MCS change by quintile
+# sf12_income_corr <- all.dat %>%
+#   group_by(pidp, time, income_quint, scenario) %>%
+#   summarise(income_change = hh_income - lag(hh_income),
+#             sf12_change = SF_12 - lag(SF_12)) %>%
+#   filter(!is.na(income_change) & !is.na(sf12_change))
+
+sf12_income_corr <- all.dat %>%
+  select(pidp, time, income_quint, scenario, hh_income, SF_12) %>%
+  arrange(pidp, time) %>%  # Ensure data is arranged by individual and time
+  group_by(pidp, income_quint, scenario) %>%
+  mutate(income_change = hh_income - lag(hh_income),  # Change in household income
+         sf12_change = SF_12 - lag(SF_12)) %>%  # Change in SF-12 MCS
+  filter(!is.na(income_change) & !is.na(sf12_change))  # Filter out NA changes
+
+```
+
+```{r}
+
+ggplot(sf12_income_corr, aes(x = income_change, y = sf12_change, color = scenario)) +
+  geom_point(alpha = 0.5) +
+  facet_wrap(~income_quint) +
+  labs(title = "Income Change vs. SF-12 MCS Change",
+       x = "Income Change", y = "SF-12 MCS Change") +
+  theme_minimal()
+```
+
+## Heatmap of SF-12 Transitions
+
+```{r}
+# Categorize SF-12 MCS transitions: "Improving", "Stable", "Worsening"
+prepare_sf12_transitions <- function(data) {
+  data %>%
+    select(pidp, time, income_quint, SF12_MCS) %>%
+    group_by(pidp) %>%
+    arrange(time) %>%  # Ensure data is ordered by time
+    mutate(SF12_MCS_change = SF12_MCS - lag(SF12_MCS)) %>%
+    mutate(SF12_MCS_transition = case_when(
+      SF12_MCS_change > 0 ~ "Improving",
+      SF12_MCS_change == 0 ~ "Stable",
+      SF12_MCS_change < 0 ~ "Worsening",
+      TRUE ~ NA_character_
+    )) %>%
+    filter(!is.na(SF12_MCS_transition)) %>%
+    ungroup()
+}
+
+# Prepare the data
+sf12_transitions <- prepare_sf12_transitions(data)
+
+# Calculate the count of transitions per quintile and transition type
+sf12_transition_counts <- sf12_transitions %>%
+  group_by(income_quint, SF12_MCS_transition) %>%
+  summarise(count = n()) %>%
+  ungroup() %>%
+  spread(SF12_MCS_transition, count, fill = 0)
+
+# Normalize the counts to show proportions per quintile
+sf12_transition_counts <- sf12_transition_counts %>%
+  gather(SF12_MCS_transition, count, -income_quint) %>%
+  group_by(income_quint) %>%
+  mutate(proportion = count / sum(count)) %>%
+  ungroup()
+
+# Plot the heatmap
+ggplot(sf12_transition_counts, aes(x = SF12_MCS_transition, y = as.factor(income_quint), fill = proportion)) +
+  geom_tile() +
+  scale_fill_gradient(low = "white", high = "red") +
+  labs(title = "SF-12 MCS Transitions Heatmap by Quintile",
+       x = "SF-12 MCS Transition", y = "Income Quintile", fill = "Proportion") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+```
+
+```{r}
+# Function to prepare data for heatmap of SF-12 MCS transitions
+prepare_sf12_heatmap_data <- function(data) {
+  data %>%
+    arrange(pidp, time) %>%  # Arrange data by individual and time
+    group_by(pidp) %>%
+    mutate(SF12_T1 = lag(SF_12),  # Previous year's SF-12 score
+           SF12_T2 = SF_12) %>%   # Current year's SF-12 score
+    filter(!is.na(SF12_T1)) %>%  # Remove rows without previous year
+    group_by(SF12_T1, SF12_T2) %>%
+    summarise(count = n()) %>%  # Count the number of transitions
+    ungroup() %>%
+    complete(SF12_T1, SF12_T2, fill = list(count = 0))  # Ensure all possible combinations
+}
+
+# Function to plot heatmap showing the differences between baseline and intervention transitions
+plot_sf12_heatmap_difference <- function(base.dat, int.dat) {
+  # Prepare baseline and intervention data
+  base_heatmap <- prepare_sf12_heatmap_data(base.dat) %>%
+    rename(count_baseline = count)
+  int_heatmap <- prepare_sf12_heatmap_data(int.dat) %>%
+    rename(count_intervention = count)
+
+  # Combine both datasets and calculate differences in counts and proportions
+  combined_heatmap <- base_heatmap %>%
+    full_join(int_heatmap, by = c("SF12_T1", "SF12_T2")) %>%
+    mutate(count_baseline = coalesce(count_baseline, 0),
+           count_intervention = coalesce(count_intervention, 0),
+           diff_count = count_intervention - count_baseline,
+           total_count = count_baseline + count_intervention,
+           diff_prop = ifelse(total_count > 0, diff_count / total_count, 0)) %>%
+    replace_na(list(diff_count = 0, diff_prop = 0))  # Handle missing values
+
+  # Plot heatmap of count differences
+  count_heatmap <- ggplot(combined_heatmap, aes(SF12_T1, SF12_T2, fill = diff_count)) +
+    geom_tile() +
+    scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) +
+    labs(title = "Difference in SF-12 MCS Transitions (Counts)", 
+         x = "SF-12 MCS (Previous Year)", 
+         y = "SF-12 MCS (Current Year)", 
+         fill = "Count Difference") +
+    theme_minimal()
+
+  # Plot heatmap of proportion differences
+  prop_heatmap <- ggplot(combined_heatmap, aes(SF12_T1, SF12_T2, fill = diff_prop)) +
+    geom_tile() +
+    scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) +
+    labs(title = "Difference in SF-12 MCS Transitions (Proportions)", 
+         x = "SF-12 MCS (Previous Year)", 
+         y = "SF-12 MCS (Current Year)", 
+         fill = "Proportion Difference") +
+    theme_minimal()
+
+  # Return both plots
+  list(count_heatmap = count_heatmap, prop_heatmap = prop_heatmap)
+}
+
+# Example usage
+plots <- plot_sf12_heatmap_difference(base.dat, int.dat)
+plots$count_heatmap  # Display the count heatmap
+plots$prop_heatmap  # Display the proportion heatmap
+
+```
+
+```{r}
+
 ```

### 2024-09-18 minos/transitions/transition_model_functions.R

@@ -223,7 +223,7 @@ estimate_longitudinal_lmm <- function(data, formula, include_weights = FALSE, de
 
   ## LA 9/2/24
   # Saving min and max value from input data for clipping in r_utils function
-  if (depend %in% c('SF_12_PCS', 'SF_12_MCS', 'SF_12')) {
+  if (depend %in% c('SF_12_PCS', 'SF_12_MCS', 'SF_12', 'hh_income')) {
     attr(model,"min_value") <- min_value
     attr(model,"max_value") <- max_value
   }
@@ -494,6 +494,10 @@ estimate_XGB <- function(data, formula, depend, reflect) {
   data <- drop_na(data)
   # Try only dropping NA values in the response variable
   #data <- drop_na(data, any_of(depend))
+  
+  # Get max and min value for clipping later
+  max_value <- nanmax(data[[depend]])
+  min_value <- nanmin(data[[depend]])
 
   print(sprintf("Model is being fit on %d individual records...", nrow(data)))
 
@@ -594,9 +598,10 @@ estimate_XGB <- function(data, formula, depend, reflect) {
 
   attr(model, "recipe") <- prep_rec
 
-  # if (reflect) {
-  #   attr(model,"max_value") <- max_value
-  # }
+  if (reflect) {
+    attr(model,"max_value") <- max_value
+    attr(model,"min_value") <- min_value
+  }
 
   return(model)
 }

### 2024-09-19 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Added another function to the income module to reduce variance in lower half of data whilst rescaling

@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_33_scot_clipped/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"

### 2024-09-20 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Split scaling implemented; scaling is now lopsided with reduced variance at the bottom of the distribution

@@
 # Categorize SF-12 MCS transitions: "Improving", "Stable", "Worsening"
-prepare_sf12_transitions <- function(data) {
-  data %>%
-    select(pidp, time, income_quint, SF12_MCS) %>%
-    group_by(pidp) %>%
-    arrange(time) %>%  # Ensure data is ordered by time
-    mutate(SF12_MCS_change = SF12_MCS - lag(SF12_MCS)) %>%
-    mutate(SF12_MCS_transition = case_when(
-      SF12_MCS_change > 0 ~ "Improving",
-      SF12_MCS_change == 0 ~ "Stable",
-      SF12_MCS_change < 0 ~ "Worsening",
-      TRUE ~ NA_character_
-    )) %>%
-    filter(!is.na(SF12_MCS_transition)) %>%
-    ungroup()
-}
-
-# Prepare the data
-sf12_transitions <- prepare_sf12_transitions(data)
-
-# Calculate the count of transitions per quintile and transition type
-sf12_transition_counts <- sf12_transitions %>%
-  group_by(income_quint, SF12_MCS_transition) %>%
-  summarise(count = n()) %>%
-  ungroup() %>%
-  spread(SF12_MCS_transition, count, fill = 0)
-
-# Normalize the counts to show proportions per quintile
-sf12_transition_counts <- sf12_transition_counts %>%
-  gather(SF12_MCS_transition, count, -income_quint) %>%
-  group_by(income_quint) %>%
-  mutate(proportion = count / sum(count)) %>%
-  ungroup()
-
-# Plot the heatmap
-ggplot(sf12_transition_counts, aes(x = SF12_MCS_transition, y = as.factor(income_quint), fill = proportion)) +
-  geom_tile() +
-  scale_fill_gradient(low = "white", high = "red") +
-  labs(title = "SF-12 MCS Transitions Heatmap by Quintile",
-       x = "SF-12 MCS Transition", y = "Income Quintile", fill = "Proportion") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+# prepare_sf12_transitions <- function(data) {
+#   data %>%
+#     select(pidp, time, income_quint, SF12_MCS) %>%
+#     group_by(pidp) %>%
+#     arrange(time) %>%  # Ensure data is ordered by time
+#     mutate(SF12_MCS_change = SF12_MCS - lag(SF12_MCS)) %>%
+#     mutate(SF12_MCS_transition = case_when(
+#       SF12_MCS_change > 0 ~ "Improving",
+#       SF12_MCS_change == 0 ~ "Stable",
+#       SF12_MCS_change < 0 ~ "Worsening",
+#       TRUE ~ NA_character_
+#     )) %>%
+#     filter(!is.na(SF12_MCS_transition)) %>%
+#     ungroup()
+# }
+# 
+# # Prepare the data
+# sf12_transitions <- prepare_sf12_transitions(data)
+# 
+# # Calculate the count of transitions per quintile and transition type
+# sf12_transition_counts <- sf12_transitions %>%
+#   group_by(income_quint, SF12_MCS_transition) %>%
+#   summarise(count = n()) %>%
+#   ungroup() %>%
+#   spread(SF12_MCS_transition, count, fill = 0)
+# 
+# # Normalize the counts to show proportions per quintile
+# sf12_transition_counts <- sf12_transition_counts %>%
+#   gather(SF12_MCS_transition, count, -income_quint) %>%
+#   group_by(income_quint) %>%
+#   mutate(proportion = count / sum(count)) %>%
+#   ungroup()
+# 
+# # Plot the heatmap
+# ggplot(sf12_transition_counts, aes(x = SF12_MCS_transition, y = as.factor(income_quint), fill = proportion)) +
+#   geom_tile() +
+#   scale_fill_gradient(low = "white", high = "red") +
+#   labs(title = "SF-12 MCS Transitions Heatmap by Quintile",
+#        x = "SF-12 MCS Transition", y = "Income Quintile", fill = "Proportion") +
+#   theme_minimal() +
+#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
@@
 # Example usage
-plots <- plot_sf12_heatmap_difference(base.dat, int.dat)
-plots$count_heatmap  # Display the count heatmap
-plots$prop_heatmap  # Display the proportion heatmap
+#plots <- plot_sf12_heatmap_difference(base.dat, int.dat)
+#plots$count_heatmap  # Display the count heatmap
+#plots$prop_heatmap  # Display the proportion heatmap
 

### 2024-09-23 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Small changes to plotting script

--- 2024-09-13 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_33_scot_clipped/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"
@@
       mean_SF12_change = if_else(income_quintile %in% c(4, 5), 0, mean_SF12_change),
-      margin_SF12 = if_else(income_quintile %in% c(4, 5), 0, margin_SF12),
-      lower_SF12 = if_else(income_quintile %in% c(4, 5), 0, lower_SF12),
-      upper_SF12 = if_else(income_quintile %in% c(4, 5), 0, upper_SF12)
+      margin_SF12 = if_else(income_quintile %in% c(4, 5), 0, margin_SF12)
     )
+
+  # lower_SF12 = if_else(income_quintile %in% c(4, 5), 0, lower_SF12),
+  # upper_SF12 = if_else(income_quintile %in% c(4, 5), 0, upper_SF12)
 

### 2024-09-23 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Additions to the income module to try get the split scaling working (failed). Also some minor changes to the model for the same purpose, and additional plots added to handovers to look at income quintiles

@@
     xlab('Year') +
-    ylab('Absolute Change in SF-12 MCS') +
+    ylab('Change in Mean SF-12 MCS') +
     theme_minimal()
@@
     xlab('Year') +
-    ylab('Change in SF-12 MCS') +
+    ylab('Change in Mean SF-12 MCS') +
     theme_minimal()
@@
     xlab('Year') +
-    ylab('Change in SF-12 MCS') +
+    ylab('Change in Mean SF-12 MCS') +
     theme_minimal() +
@@
       xlab('Year') +
-      ylab('Change in mean SF-12 MCS') +
+      ylab('Change in Mean SF-12 MCS') +
       theme_minimal() +
@@
       mean_SF12_change = if_else(income_quintile %in% c(4, 5), 0, mean_SF12_change),
-      margin_SF12 = if_else(income_quintile %in% c(4, 5), 0, margin_SF12)
+      lower_SF12 = mean_SF12_change - margin_SF12,
+      upper_SF12 = mean_SF12_change + margin_SF12
     )
 
+  # margin_SF12 = if_else(income_quintile %in% c(4, 5), 0, margin_SF12)
   # lower_SF12 = if_else(income_quintile %in% c(4, 5), 0, lower_SF12),
@@
          x = "Year",
-         y = "Difference in SF_12 MCS") +
+         y = "Change in Mean SF-12 MCS") +
     theme_minimal() +
@@
     geom_line() +
-    labs(title = "Difference in count of individuals at risk of mental health issues",
-         subtitle = tit) +
     xlab('Year') +
-    ylab('Count') +
+    ylab('Count Change') +
     theme_minimal()
@@
     geom_line() +
-    labs(title = "Difference in proportion of individuals at risk of mental health issues",
-         subtitle = tit) +
     xlab('Year') +
-    ylab('Percentage') +
+    ylab('Percentage Change') +
     theme_minimal()
@@
       xlab('Year') +
-      ylab('Change in mean SF-12 MCS')
+      ylab('Change in Mean SF-12 MCS')
 
@@
       xlab('Year') +
-      ylab('Change in mean Household Income')
+      ylab('Change in Mean Household Income')
 
@@
 
+# SAMPLE STATISTICS
+
+```{r}
+
+# data <- do.call(rbind, generate_df_list('whole_pop', 'baseline'))
+# data.fam <- do.call(rbind, generate_df_list('families', 'baseline'))
+# 
+# nrow(data)
+# 
+# 
+# 5463300
+# 
+# 4580000
+# 
+# 
+# 359328 / 458000 * 100
+# 
+# 100 / 78.4559
+# 
+# 
+# 109338 * 12.74601
+
+```
+
 # COMBINED RELATIVE AND ABSOLUTE REDUCTION INTERVENTION
@@
                                     scen = scen)
-
 SF12_change_income_quint2_fudged(summary_group = 'families',

### 2024-09-23 minos/validation/handovers.Rmd
Additions to the income module to try get the split scaling working (failed). Also some minor changes to the model for the same purpose, and additional plots added to handovers to look at income quintiles

@@
 shall.we.save <- FALSE
+```
+
+## Income Quintile
+
+```{r}
+raw.dat <- raw.dat %>%
+  group_by(time) %>%
+  mutate(income_quint = ntile(hh_income, 5))
+
+base.dat <- base.dat %>%
+  group_by(time) %>%
+  mutate(income_quint = ntile(hh_income, 5))
 ```
@@
   labs(title = 'Households with Children Count')
+
+rm(raw.hh_kids_prop, base.hh_kids_prop, combined)
 ```
@@
 # print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
+```
+
+### Analysis by Quintile
+
+```{r}
+density_plot_quintile <- function(raw, base, quintile) {
+
+  raw <- raw %>%
+    filter(income_quint == quintile) %>%
+    select(pidp, time, hh_income) %>%
+    rename(Final_US = hh_income)
+  base <- base %>%
+    filter(income_quint == quintile) %>%
+    select(pidp, time, hh_income) %>%
+    rename(Baseline = hh_income)
+
+  #combined <- merge(base, int, by = c('pidp', 'time'))
+
+  combined <- rbind(raw, base)
+
+  combined <- combined %>%
+    pivot_longer(cols = Final_US:Baseline,
+                 names_to = 'Source',
+                 values_to = 'hh_income')
+
+  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source, fill = Source)) +
+    geom_density_ridges(alpha = 0.3) +
+    labs(title = 'Household Income Density Plots',
+         subtitle = paste0('Quintile ', quintile))
+
+  return(p)
+}
+
+density_plot_quintile(base.dat, int.dat, quintile = 1)
+density_plot_quintile(base.dat, int.dat, quintile = 2)
+density_plot_quintile(base.dat, int.dat, quintile = 3)
+density_plot_quintile(base.dat, int.dat, quintile = 4)
+density_plot_quintile(base.dat, int.dat, quintile = 5)
+```
+
+#### Mean Income
+
+```{r}
+mean_income_quintile <- function(raw, base) {
+  raw <- raw %>%
+    select(pidp, time, hh_income, income_quint, weight) %>%
+    mutate(source = 'Final_US')
+  base <- base %>%
+    select(pidp, time, hh_income, income_quint, weight) %>%
+    mutate(source = 'Baseline')
+
+  combined <- rbind(base, int)
+
+  combined <- combined %>%
+    group_by(time, income_quint, source) %>%
+    summarise(mean = weighted.mean(hh_income, weight),
+              median = weighted.median(hh_income, weight))
+
+  combined$income_quint <- factor(combined$income_quint)
+  combined$source <- factor(combined$source)
+
+  p1 <- ggplot(combined, aes(x = time, y = mean, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
+    geom_line() +
+    labs(title = 'Mean hh_income by quintile',
+         subtitle = 'Baseline vs Intervention')
+
+  p2 <- ggplot(combined, aes(x = time, y = median, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
+    geom_line() +
+    labs(title = 'Median hh_income by quintile',
+         subtitle = 'Baseline vs Intervention')
+
+  print(p1)
+  print(p2)
+  #return(p)
+}
+
+mean_income_quintile(base.dat, int.dat)
+```
+
+#### Thresholds Over Time
+
+```{r}
+# get min-max by group as this is upper and lower limits of the quintiles
+
+base <- base.dat %>%
+  group_by(time, income_quint) %>%
+  summarise(min = min(hh_income),
+            max = max(hh_income)) %>%
+  mutate(source = 'Baseline')
+int <- int.dat %>%
+  group_by(time, income_quint) %>%
+  summarise(min = min(hh_income),
+            max = max(hh_income)) %>%
+  mutate(source = 'Intervention')
+
+combined <- rbind(base, int)
+combined$income_quint <- factor(combined$income_quint)
+
+quintile_threshold_plot <- function(data, year) {
+  ggplot(filter(data, time == year), 
+         aes(x = income_quint, y = min,
+             ymin = min, lower = min, ymax = max, upper = max,
+             group = source, 
+             colour = source, 
+             fill = source)) +
+    geom_crossbar(position = position_dodge()) +
+    labs(title = 'Quintile Thresholds',
+         subtitle = year)
+}
+
+quintile_threshold_plot(combined, year = 2020)
+quintile_threshold_plot(combined, year = 2021)
+quintile_threshold_plot(combined, year = 2025)
+quintile_threshold_plot(combined, year = 2030)
+quintile_threshold_plot(combined, year = 2035)
+```
+
+```{r}
+
 ```

### 2024-10-02 minos/outcomes/spatial_analysis.Rmd
adding in spatial analysis for last thesis chapter.

@@
 title: "R Notebook"
-output: html_notebook
+output:
+  html_document:
+    df_print: paged
 ---
@@
 ```{r}
-plot(cars)
+library(here)
+library(ggplot2)
+library(dplyr)
+library(xtable)
+
+# load 2020 data.
+full_pop_data <- read.csv(here::here("data", "scaled_manchester_aligned_US", "2020_US_cohort.csv"))
+full_pop_data$FP10 <- ((full_pop_data$yearly_energy * 10) > (full_pop_data$net_hh_income * 12))
+full_pop_data$is_green <- "Total Population"
+
+full_pop_data_copy <- full_pop_data
+full_pop_data_copy2 <- full_pop_data
+
+# load green csvs for epcg/gbis.
+epcg_green_lsoas <- read.csv(here::here("plots", "cost_vs_gain_by_lsoa_QALYs_manchester_synthetic_baseline_EPCG_2025_diffmap.pdfgreen_lsoas.csv"))
+#gbis_green_lsoas <- read.csv(here::here("plots", "cost_vs_gain_by_lsoa_QALYs_manchester_synthetic_baseline_GBIS_2030_diffmap.pdfgreen_lsoas.csv"))
+epcg_expensive_non_green_lsoas <- read.csv(here::here("plots", "cost_vs_gain_by_lsoa_QALYs_manchester_synthetic_baseline_EPCG_2025_diffmap.pdfexpensive_non_green_lsoas.csv"))
+
+#distributional differences for heating and income between full pop and green pop.
+#green_subpopulation <- full_pop_data[which(full_pop_data$ZoneID %in% epcg_green_lsoas$x), ]
+full_pop_data[which(full_pop_data$ZoneID %in% epcg_green_lsoas$x), "is_green"] <- "Cost-Effective LSOAs"
+full_pop_data <- full_pop_data[which(full_pop_data$is_green != "Total Population"), ] 
+#full_pop_data[which(!(full_pop_data$ZoneID %in% epcg_green_lsoas$x)), "is_green"] <- "Not Green LSOAs"
+
+full_pop_data_copy2[which(full_pop_data_copy2$ZoneID %in% epcg_expensive_non_green_lsoas$x), "is_green"] <- "Expensive and not Cost-Effective LSOAs"
+#full_pop_data_copy2 <- full_pop_data_copy2[which(full_pop_data$is_green == "All Not Expensive and Not Green LSOAs"), ] 
+full_pop_data_copy2 <- full_pop_data_copy2[which(full_pop_data_copy2$is_green != "Total Population"), ]
+
+full_pop_data <- rbind(full_pop_data, full_pop_data_copy, full_pop_data_copy2)
+#full_pop_data <- full_pop_data[which(full_pop_data$is_green != "F"), ] 
+#print(table(full_pop_data$is_green))
+
+full_pop_data$housing_quality <- factor(full_pop_data$housing_quality, levels=c("Low", "Medium", "High"), ordered=T)
 ```
 
-Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
+```{r}
 
-When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
+aggregate_by_group_continuous <- function(data, v) {
+  out_table <- full_pop_data %>%
+    group_by(is_green) %>%
+     summarise("Variable Mean" = mean(!!sym(v)))  %>%
+        mutate(Variable = "", .before=is_green) %>%
+          rename("LSOA Type" = is_green)
+    out_table$Variable[1] <- v
+  return (out_table)
+}
 
-The preview shows you a rendered HTML copy of the contents of the editor.
-Consequently, unlike *Knit*, *Preview* does not run any R code chunks.
-Instead, the output of the chunk when it was last run in the editor is displayed.
+aggregate_by_group_discrete <- function(data, v) {
+  out_table <- full_pop_data %>%
+    group_by(is_green, !!sym(v)) %>%
+     summarise(count = n())  %>%
+      ungroup() %>%
+        mutate(freq = sum(count), .by=is_green) %>%
+          mutate(prct = 100*count / freq) %>%
+            mutate(Variable = "", .before=is_green) %>%
+              rename("Variable Levels" = !!sym(v), "LSOA Type"= is_green) %>%
+                select(-one_of(c("count", "freq"))) %>%
+                  arrange("Variable Levels")
+
+  out_table$`Variable Levels` <- as.character(out_table$`Variable Levels`)
+  out_table$Variable[1] <- v
+  return (out_table)
+}
+
+discrete_var_table <- data.frame()
+
+for (var in c('housing_quality' ,'FP10', 'ethnicity', 'simd_decile')){
+  discrete_var_table <- rbind(discrete_var_table, aggregate_by_group_discrete(full_pop_data, var))
+}
+
+continuous_var_table <- data.frame()
+
+for (var in c('hh_income', "yearly_energy", "hh_rent","hh_mortgage", "nutrition_quality", "ncars", "council_tax", "yearly_electric", "yearly_gas", "yearly_oil", "yearly_gas_electric", "yearly_other_fuel", "age")){
+  continuous_var_table <- rbind(continuous_var_table, aggregate_by_group_continuous(full_pop_data, var))
+}
+
+write.csv(discrete_var_table, file = here::here("plots", "EPCG_discrete_var_table.csv"), row.names=F)
+write.csv(continuous_var_table, file = here::here("plots", "EPCG_continuous_var_table.csv"), row.names=F)
+#print(xtable(discrete_var_table, type = "latex"), file = here::here("plots", "EPCG_discrete_var_table.tex"))
+#print(xtable(continuous_var_table, type = "latex"), file = here::here("plots", "EPCG_continuous_var_table.tex"))
+
+```
+
+# ```{r}
+# 
+# ggplot(full_pop_data, aes(x = hh_income, colour = is_green)) +
+#   geom_density() +labs(x="Household Disposable Income", y="Density", colour="LSOA Type")#+
+#   #labs(x="Intervention Cost", y="QALY Cumulative Gain", color="IMD Decile")
+# ggsave(here::here("plots","EPCG_hh_income.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x = SF_12, colour = is_green)) +
+#   geom_density()
+# ggsave(here::here("plots","EPCG_SF_12.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x = SF_12_PCS, colour = is_green)) +
+#   geom_density()
+# ggsave(here::here("plots","EPCG_SF_12_PCS.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x = yearly_energy, colour = is_green)) +
+#   geom_density()
+# ggsave(here::here("plots","EPCG_yearly_energy.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x = yearly_gas, colour = is_green)) +
+#   geom_density()
+# ggsave(here::here("plots","EPCG_yearly_gas.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x = yearly_electric, colour = is_green)) +
+#   geom_density()
+# ggsave(here::here("plots","EPCG_yearly_electric.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x = yearly_gas_electric, colour = is_green)) +
+#   geom_density()
+# ggsave(here::here("plots","EPCG_yearly_gas_electric.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x = age, colour = is_green)) +
+#   geom_density()+labs(x="Age", y="Density", colour="LSOA Type")
+# ggsave(here::here("plots","EPCG_age.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x = yearly_oil, colour = is_green)) +
+#   geom_density()
+# ggsave(here::here("plots","EPCG_yearly_oil.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x = nutrition_quality, colour = is_green)) +
+#   geom_density()
+# 
+# ggplot(full_pop_data, aes(x = hh_mortgage, colour = is_green)) +
+#   geom_density()
+# 
+# ```
+# 
+# ```{r}
+# ggplot(full_pop_data, aes(x=as.factor(heating), fill=as.factor(is_green)))+
+#   geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
+# ggsave(here::here("plots","EPCG_heating.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x=as.factor(housing_quality), fill=as.factor(is_green)))+
+#   geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
+# ggsave(here::here("plots","EPCG_housing_quality.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x=as.factor(neighbourhood_safety), fill=as.factor(is_green)))+
+#   geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
+# ggsave(here::here("plots","EPCG_neighbourhood_safety.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x=as.factor(FP10), fill=as.factor(is_green)))+
+#   geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" ) +labs(x="FP10", y="Density", fill="LSOA Type")
+# ggsave(here::here("plots","EPCG_FP10.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x=as.factor(ethnicity), fill=as.factor(is_green)))+
+#   geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" ) +labs(x="Ethncity", y="Density", fill="LSOA Type")
+# ggsave(here::here("plots","EPCG_ethnicity.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x=as.factor(ncars), fill=as.factor(is_green)))+
+#   geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
+# ggsave(here::here("plots","EPCG_ncars.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x=as.factor(sex), fill=as.factor(is_green)))+
+#   geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" ) +labs(x="Sex", y="Density", fill="LSOA Type")
+# ggsave(here::here("plots","EPCG_sex.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x=as.factor(simd_decile), fill=as.factor(is_green)))+
+#     geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )+labs(x="IMD Decile", y="Density", fill="LSOA Type")
+# ggsave(here::here("plots","EPCG_simd_decile.pdf"), plot=last_plot())
+# 
+# ggplot(full_pop_data, aes(x=as.factor(financial_situation), fill=as.factor(is_green)))+
+#     geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
+# 
+# ggplot(full_pop_data, aes(x=as.factor(simd_decile), fill=as.factor(is_green)))+
+#     geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
+# 
+# ggplot(full_pop_data, aes(x=as.factor(is_overcrowded), fill=as.factor(is_green)))+
+#     geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
+# 
+# ggplot(full_pop_data, aes(x=as.factor(S7_labour_state), fill=as.factor(is_green)))+
+#     geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
+# 
+# ggplot(full_pop_data, aes(x=as.factor(education_state), fill=as.factor(is_green)))+
+#     geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
+# 
+# ggplot(full_pop_data, aes(x=as.factor(housing_tenure), fill=as.factor(is_green)))+
+#     geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
+# 
+# ggplot(full_pop_data, aes(x=as.factor(number_of_rooms), fill=as.factor(is_green)))+
+#     geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
+# 
+# ```
+
+<!-- # do the same again for baseline and intervened green pops? -->
+
+<!-- ```{r} -->
+
+<!-- # baseline and epcg green lsoa populations in 2025.   -->
+
+<!-- baseline_2025 <- read.csv(here::here("output", "energy_manchester_scaled", "baseline", "2024_07_25_15_08_03", "0001_run_id_2025.csv")) -->
+<!-- epcg_2025 <- read.csv(here::here("output", "energy_manchester_scaled", "EPCG", "2024_07_26_18_23_14", "0001_run_id_2025.csv")) -->
+
+<!-- baseline_2025 <-  baseline_2025[which(baseline_2025$ZoneID %in% epcg_green_lsoas$x), ] -->
+<!-- epcg_2025 <-  epcg_2025[which(epcg_2025$ZoneID %in% epcg_green_lsoas$x), ] -->
+
+<!-- baseline_2025 <- baseline_2025[, c("hh_income", "SF_12", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->
+<!-- epcg_2025 <- epcg_2025[, c("hh_income", "SF_12", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->
+
+<!-- baseline_2025$group <- "baseline" -->
+<!-- epcg_2025$group <- "epcg" -->
+
+<!-- plot_data <- rbind(baseline_2025, epcg_2025) -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- ggplot(plot_data, aes(x = hh_income, colour = group)) + -->
+<!--   geom_density() -->
+
+<!-- ggplot(plot_data, aes(x = SF_12, colour = group)) + -->
+<!--   geom_density() -->
+
+<!-- ggplot(plot_data, aes(x = SF_12_PCS, colour = group)) + -->
+<!--   geom_density() -->
+
+<!-- ggplot(plot_data, aes(x = yearly_energy, colour = group)) + -->
+<!--   geom_density() -->
+<!-- ``` -->
+<!-- ```{r} -->
+<!-- ggplot(plot_data, aes(x=as.factor(heating), fill=as.factor(group)))+ -->
+<!--   geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" ) -->
+
+<!-- ggplot(plot_data, aes(x=as.factor(housing_quality), fill=as.factor(group)))+ -->
+<!--   geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" ) -->
+
+<!-- ggplot(plot_data, aes(x=as.factor(neighbourhood_safety), fill=as.factor(group)))+ -->
+<!--   geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" ) -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+
+<!-- baseline_2025 <- read.csv(here::here("output", "energy_manchester_scaled", "baseline", "2024_07_25_15_08_03", "0001_run_id_2025.csv")) -->
+<!-- epcg_2025 <- read.csv(here::here("output", "energy_manchester_scaled", "EPCG", "2024_07_26_18_23_14", "0001_run_id_2025.csv")) -->
+
+<!-- baseline_2025 <-  baseline_2025[which(!(baseline_2025$ZoneID %in% epcg_green_lsoas$x)), ] -->
+<!-- epcg_2025 <-  epcg_2025[which(!(epcg_2025$ZoneID %in% epcg_green_lsoas$x)), ] -->
+
+<!-- baseline_2025 <- baseline_2025[, c("hh_income", "SF_12", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->
+<!-- epcg_2025 <- epcg_2025[, c("hh_income", "SF_12", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->
+
+<!-- baseline_2025$group <- "baseline" -->
+<!-- epcg_2025$group <- "epcg" -->
+
+<!-- plot_data <- rbind(baseline_2025, epcg_2025) -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- ggplot(plot_data, aes(x = hh_income, colour = group)) + -->
+<!--   geom_density() -->
+
+<!-- ggplot(plot_data, aes(x = SF_12, colour = group)) + -->
+<!--   geom_density() -->
+
+<!-- ggplot(plot_data, aes(x = SF_12_PCS, colour = group)) + -->
+<!--   geom_density() -->
+
+<!-- ggplot(plot_data, aes(x = yearly_energy, colour = group)) + -->
+<!--   geom_density() -->
+<!-- ``` -->

### 2024-10-02 minos/outcomes/spatial_analysis_gbis.Rmd
adding in spatial analysis for last thesis chapter.

---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

spatial analysis notebook for chapter.

msoa/lsoa/la level maps for GBIS MCS/PCS/QALY.

regressions
ICER plots
disaggregation of good performing LSOAs/MSOAs.

```{r}
library(here)
library(ggplot2)
library(xtable)
library(dplyr)

# load 2020 data.
full_pop_data <- read.csv(here::here("data", "scaled_manchester_aligned_US", "2020_US_cohort.csv"))

full_pop_data$FP10 <- ((full_pop_data$yearly_energy * 10) > (full_pop_data$net_hh_income * 12))
full_pop_data$is_green <- "Total Population"

full_pop_data_copy <- full_pop_data
full_pop_data_copy2 <- full_pop_data

# load green csvs for gbis/gbis.
gbis_green_lsoas <- read.csv(here::here("plots", "cost_vs_gain_by_lsoa_QALYs_manchester_synthetic_baseline_GBIS_2025_diffmap.pdfgreen_lsoas.csv"))
#gbis_green_lsoas <- read.csv(here::here("plots", "cost_vs_gain_by_lsoa_QALYs_manchester_synthetic_baseline_GBIS_2030_diffmap.pdfgreen_lsoas.csv"))
gbis_expensive_non_green_lsoas <- read.csv(here::here("plots", "cost_vs_gain_by_lsoa_QALYs_manchester_synthetic_baseline_GBIS_2025_diffmap.pdfexpensive_non_green_lsoas.csv"))

#distributional differences for heating and income between full pop and green pop.
#green_subpopulation <- full_pop_data[which(full_pop_data$ZoneID %in% gbis_green_lsoas$x), ]
full_pop_data[which(full_pop_data$ZoneID %in% gbis_green_lsoas$x), "is_green"] <- "Cost-Effective LSOAs"
full_pop_data <- full_pop_data[which(full_pop_data$is_green != "Total Population"), ] 
#full_pop_data[which(!(full_pop_data$ZoneID %in% gbis_green_lsoas$x)), "is_green"] <- "Not Green LSOAs"

full_pop_data_copy2[which(full_pop_data_copy2$ZoneID %in% gbis_expensive_non_green_lsoas$x), "is_green"] <-  "Expensive and not Cost-Effective LSOAs"
#full_pop_data_copy2 <- full_pop_data_copy2[which(full_pop_data$is_green == "All Not Expensive and Not Green LSOAs"), ] 
full_pop_data_copy2 <- full_pop_data_copy2[which(full_pop_data_copy2$is_green != "Total Population"), ]

full_pop_data <- rbind(full_pop_data, full_pop_data_copy, full_pop_data_copy2)
#full_pop_data <- full_pop_data[which(full_pop_data$is_green != "F"), ] 
#print(table(full_pop_data$is_green))
full_pop_data$housing_quality <- factor(full_pop_data$housing_quality, levels=c("Low", "Medium", "High"), ordered=T)
```

```{r}

aggregate_by_group_continuous <- function(data, v) {
  out_table <- full_pop_data %>%
    group_by(is_green) %>%
     summarise("GBIS Variable Mean" = mean(!!sym(v)))  %>%
        mutate(Variable = "", .before=is_green) %>%
          rename("LSOA Type" = is_green)
    out_table$Variable[1] <- v
  return (out_table)
}

aggregate_by_group_discrete <- function(data, v) {
  out_table <- full_pop_data %>%
    group_by(is_green, !!sym(v)) %>%
     summarise(count = n())  %>%
      ungroup() %>%
        mutate(freq = sum(count), .by=is_green) %>%
          mutate("GBIS Percentages" = 100*count / freq) %>%
            mutate(Variable = "", .before=is_green) %>%
              rename("Variable Levels" = !!sym(v), "LSOA Type" = "is_green") %>%
                select(-one_of(c("count", "freq"))) %>%
                  arrange("Variable Levels")

  out_table$`Variable Levels` <- as.character(out_table$`Variable Levels`)
  out_table$Variable[1] <- v
  return (out_table)
}

discrete_var_table <- data.frame()

for (var in c('housing_quality' ,'FP10', 'ethnicity', 'simd_decile')){
  discrete_var_table <- rbind(discrete_var_table, aggregate_by_group_discrete(full_pop_data, var))
}

continuous_var_table <- data.frame()

for (var in c('hh_income', "yearly_energy", "hh_rent","hh_mortgage", "nutrition_quality", "ncars", "council_tax", "yearly_electric", "yearly_gas", "yearly_oil", "yearly_gas_electric", "yearly_other_fuel", "age")){
  continuous_var_table <- rbind(continuous_var_table, aggregate_by_group_continuous(full_pop_data, var))
}

epcg_discrete_table <- read.csv(here::here("plots", "EPCG_discrete_var_table.csv"))
epcg_continuous_table <- read.csv(here::here("plots", "EPCG_continuous_var_table.csv"))
colnames(epcg_discrete_table)[3] <- "Variable Levels"
colnames(epcg_discrete_table)[2] <- "LSOA Type"
colnames(epcg_continuous_table)[2] <- "LSOA Type"

#colnames(epcg_continuous_table)[3] <- "Variable Levels"

discrete_var_table <- discrete_var_table %>% left_join(epcg_discrete_table, by=c("Variable", "LSOA Type", "Variable Levels"))
colnames(discrete_var_table)[5] <- "EPCG Percentages"

continuous_var_table$`EPCG Variable Mean` <- epcg_continuous_table$Variable.Mean
continuous_var_table <- continuous_var_table[, c("Variable", "LSOA Type", "EPCG Variable Mean", "GBIS Variable Mean")]

print(xtable(discrete_var_table, type = "latex"), file = here::here("plots", "GBIS_discrete_var_table.tex"))
print(xtable(continuous_var_table, type = "latex"), file = here::here("plots", "GBIS_continuous_var_table.tex"))

```

```{r}

ggplot(full_pop_data, aes(x = hh_income, colour = is_green)) +
  geom_density() +labs(x="Household Disposable Income", y="Density", colour="LSOA Type")#+
  #labs(x="Intervention Cost", y="QALY Cumulative Gain", color="IMD Decile")
ggsave(here::here("plots","EPCG_hh_income.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x = SF_12, colour = is_green)) +
  geom_density()
ggsave(here::here("plots","EPCG_SF_12.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x = SF_12_PCS, colour = is_green)) +
  geom_density()
ggsave(here::here("plots","EPCG_SF_12_PCS.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x = yearly_energy, colour = is_green)) +
  geom_density()
ggsave(here::here("plots","EPCG_yearly_energy.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x = yearly_gas, colour = is_green)) +
  geom_density()
ggsave(here::here("plots","EPCG_yearly_gas.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x = yearly_electric, colour = is_green)) +
  geom_density()
ggsave(here::here("plots","EPCG_yearly_electric.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x = yearly_gas_electric, colour = is_green)) +
  geom_density()
ggsave(here::here("plots","EPCG_yearly_gas_electric.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x = age, colour = is_green)) +
  geom_density()+labs(x="Age", y="Density", colour="LSOA Type")
ggsave(here::here("plots","EPCG_age.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x = yearly_oil, colour = is_green)) +
  geom_density()
ggsave(here::here("plots","EPCG_yearly_oil.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x = nutrition_quality, colour = is_green)) +
  geom_density()

ggplot(full_pop_data, aes(x = hh_mortgage, colour = is_green)) +
  geom_density()

```

```{r}
ggplot(full_pop_data, aes(x=as.factor(heating), fill=as.factor(is_green)))+
  geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
ggsave(here::here("plots","EPCG_heating.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x=as.factor(housing_quality), fill=as.factor(is_green)))+
  geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
ggsave(here::here("plots","EPCG_housing_quality.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x=as.factor(neighbourhood_safety), fill=as.factor(is_green)))+
  geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
ggsave(here::here("plots","EPCG_neighbourhood_safety.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x=as.factor(FP10), fill=as.factor(is_green)))+
  geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" ) +labs(x="FP10", y="Density", fill="LSOA Type")
ggsave(here::here("plots","EPCG_FP10.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x=as.factor(ethnicity), fill=as.factor(is_green)))+
  geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" ) +labs(x="Ethncity", y="Density", fill="LSOA Type")
ggsave(here::here("plots","EPCG_ethnicity.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x=as.factor(ncars), fill=as.factor(is_green)))+
  geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )
ggsave(here::here("plots","EPCG_ncars.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x=as.factor(sex), fill=as.factor(is_green)))+
  geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" ) +labs(x="Sex", y="Density", fill="LSOA Type")
ggsave(here::here("plots","EPCG_sex.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x=as.factor(simd_decile), fill=as.factor(is_green)))+
    geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )+labs(x="IMD Decile", y="Density", fill="LSOA Type")
ggsave(here::here("plots","EPCG_simd_decile.pdf"), plot=last_plot())

ggplot(full_pop_data, aes(x=as.factor(financial_situation), fill=as.factor(is_green)))+
    geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )

ggplot(full_pop_data, aes(x=as.factor(simd_decile), fill=as.factor(is_green)))+
    geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )

ggplot(full_pop_data, aes(x=as.factor(is_overcrowded), fill=as.factor(is_green)))+
    geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )

ggplot(full_pop_data, aes(x=as.factor(S7_labour_state), fill=as.factor(is_green)))+
    geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )

ggplot(full_pop_data, aes(x=as.factor(education_state), fill=as.factor(is_green)))+
    geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )

ggplot(full_pop_data, aes(x=as.factor(housing_tenure), fill=as.factor(is_green)))+
    geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )

ggplot(full_pop_data, aes(x=as.factor(number_of_rooms), fill=as.factor(is_green)))+
    geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" )

```

<!-- # do the same again for baseline and intervened green pops? -->

<!-- ```{r} -->

<!-- # baseline and gbis green lsoa populations in 2025.   -->

<!-- baseline_2025 <- read.csv(here::here("output", "energy_manchester_scaled", "baseline", "2024_07_25_15_08_03", "0001_run_id_2025.csv")) -->
<!-- gbis_2025 <- read.csv(here::here("output", "energy_manchester_scaled", "GBIS", "2024_07_26_18_23_14", "0001_run_id_2025.csv")) -->

<!-- baseline_2025 <-  baseline_2025[which(baseline_2025$ZoneID %in% gbis_green_lsoas$x), ] -->
<!-- gbis_2025 <-  gbis_2025[which(gbis_2025$ZoneID %in% gbis_green_lsoas$x), ] -->

<!-- baseline_2025 <- baseline_2025[, c("hh_income", "SF_12", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->
<!-- gbis_2025 <- gbis_2025[, c("hh_income", "SF_12", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->

<!-- baseline_2025$group <- "baseline" -->
<!-- gbis_2025$group <- "gbis" -->

<!-- plot_data <- rbind(baseline_2025, gbis_2025) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- ggplot(plot_data, aes(x = hh_income, colour = group)) + -->
<!--   geom_density() -->

<!-- ggplot(plot_data, aes(x = SF_12, colour = group)) + -->
<!--   geom_density() -->

<!-- ggplot(plot_data, aes(x = SF_12_PCS, colour = group)) + -->
<!--   geom_density() -->

<!-- ggplot(plot_data, aes(x = yearly_energy, colour = group)) + -->
<!--   geom_density() -->
<!-- ``` -->
<!-- ```{r} -->
<!-- ggplot(plot_data, aes(x=as.factor(heating), fill=as.factor(group)))+ -->
<!--   geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" ) -->

<!-- ggplot(plot_data, aes(x=as.factor(housing_quality), fill=as.factor(group)))+ -->
<!--   geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" ) -->

<!-- ggplot(plot_data, aes(x=as.factor(neighbourhood_safety), fill=as.factor(group)))+ -->
<!--   geom_bar(aes( y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position="dodge" ) -->
<!-- ``` -->

<!-- ```{r} -->

<!-- baseline_2025 <- read.csv(here::here("output", "energy_manchester_scaled", "baseline", "2024_07_25_15_08_03", "0001_run_id_2025.csv")) -->
<!-- gbis_2025 <- read.csv(here::here("output", "energy_manchester_scaled", "GBIS", "2024_07_26_18_23_14", "0001_run_id_2025.csv")) -->

<!-- baseline_2025 <-  baseline_2025[which(!(baseline_2025$ZoneID %in% gbis_green_lsoas$x)), ] -->
<!-- gbis_2025 <-  gbis_2025[which(!(gbis_2025$ZoneID %in% gbis_green_lsoas$x)), ] -->

<!-- baseline_2025 <- baseline_2025[, c("hh_income", "SF_12", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->
<!-- gbis_2025 <- gbis_2025[, c("hh_income", "SF_12", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->

<!-- baseline_2025$group <- "baseline" -->
<!-- gbis_2025$group <- "gbis" -->

<!-- plot_data <- rbind(baseline_2025, gbis_2025) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- ggplot(plot_data, aes(x = hh_income, colour = group)) + -->
<!--   geom_density() -->

<!-- ggplot(plot_data, aes(x = SF_12, colour = group)) + -->
<!--   geom_density() -->

<!-- ggplot(plot_data, aes(x = SF_12_PCS, colour = group)) + -->
<!--   geom_density() -->

<!-- ggplot(plot_data, aes(x = yearly_energy, colour = group)) + -->
<!--   geom_density() -->
<!-- ``` -->

### 2024-10-02 minos/outcomes/spatial_energy_validation.Rmd
adding in spatial analysis for last thesis chapter.

---
title: "R Notebook"
output: html_notebook
---

```{r}

library(here)
source(here::here("minos", "outcomes", "minos_SF12_maps.R"))

electricity_consumption_data <- read.csv(here::here("persistent_data", "spatial_data", "UK_electricity_by_lsoa.csv"))
electricity_consumption_data <- electricity_consumption_data[, c("LSOA.code", "Median..consumption..kWh.per.meter.")]
colnames(electricity_consumption_data) <- c("ZoneID", "median_electricity")
electricity_consumption_data$median_electricity <- as.numeric(gsub(",", "", electricity_consumption_data$median_electricity))

gas_consumption_data <- read.csv(here::here("persistent_data", "spatial_data", "UK_gas_by_lsoa.csv"))
gas_consumption_data <- gas_consumption_data[, c("LSOA.code", "Median..consumption..kWh.per.meter.")]
colnames(gas_consumption_data) <- c("ZoneID", "median_gas")
gas_consumption_data$median_gas <- as.numeric(gsub(",", "", gas_consumption_data$median_gas))

# get geojson data. convert to tibble.
lsoa_data <- st_read(here::here("persistent_data", "spatial_data", "UK_super_outputs.geojson"))
gmca_la_names <- c("Bolton", "Bury", "Rochdale", "Oldham", "Tameside", "Stockport", "Manchester", "Trafford", "Salford", "Wigan")
lsoa_data <- lsoa_data[which(lsoa_data$LAName %in% gmca_la_names), ]

# get 2020 data. 
# aggregate four yearly energy consumptions median by lsoa. 
full_pop_data <- read.csv(here::here("data", "scaled_manchester_aligned_US", "2020_US_cohort.csv"))

elec_aggregate <- aggregate(full_pop_data$yearly_electric, list(full_pop_data$ZoneID), median)
elec_gas_aggregate <- aggregate(full_pop_data$yearly_gas_electric, list(full_pop_data$ZoneID), median)
gas_aggregate <- aggregate(full_pop_data$yearly_gas, list(full_pop_data$ZoneID), median)
oil_aggregate <- aggregate(full_pop_data$yearly_oil, list(full_pop_data$ZoneID), median)
other_aggregate <- aggregate(full_pop_data$yearly_other_fuel, list(full_pop_data$ZoneID), median)

colnames(elec_aggregate) <- c("ZoneID", "yearly_electric")
elec_aggregate$yearly_gas_electric <- elec_gas_aggregate$x
elec_aggregate$yearly_gas <- gas_aggregate$x
elec_aggregate$yearly_oil <- oil_aggregate$x
elec_aggregate$yearly_other_fuel <- other_aggregate$x

#attach geojson data.
elec_aggregate2 <- merge(elec_aggregate, lsoa_data, by="ZoneID")

# plot it.

v <- 'yearly_electric'
elec_map <- ggplot(data = elec_aggregate2, aes(geometry = geometry, fill=.data[[v]])) +
    #geom_sf() + # black outlines on borders for clarity.
    geom_sf(color=NA) + # black outlines on borders for clarity.
    scale_fill_viridis_c(alpha = 1.0, direction=-1) + # use viridis colour scale and reverse it  so brighter is better.
    labs(fill="Yearly Electricity Consumption (£s)")  + # colour bar label.
    theme(legend.position="bottom") + # change plot to widescreen dimensions.
    xlab("Longitude") + # axis labels
    ylab("Latitude")
print(elec_map)
ggsave(here::here("plots","electric_map.pdf"), plot=last_plot())

v <- 'yearly_gas_electric'
gas_elec_map <- ggplot(data = elec_aggregate2, aes(geometry = geometry, fill=.data[[v]])) +
    #geom_sf() + # black outlines on borders for clarity.
    geom_sf(color=NA) + # black outlines on borders for clarity.
    scale_fill_viridis_c(alpha = 1.0, direction=-1) + # use viridis colour scale and reverse it  so brighter is better.
    labs(fill="Yearly Gas and Electricity Consumption (£s)")  + # colour bar label.
    theme(legend.position="bottom") + # change plot to widescreen dimensions.
    xlab("Longitude") + # axis labels
    ylab("Latitude")
print(gas_elec_map)
ggsave(here::here("plots","gas_electric_map.pdf"), plot=last_plot())

v <- 'yearly_gas'
gas_map <- ggplot(data = elec_aggregate2, aes(geometry = geometry, fill=.data[[v]])) +
    #geom_sf() + # black outlines on borders for clarity.
    geom_sf(color=NA) + # black outlines on borders for clarity.
    scale_fill_viridis_c(alpha = 1.0, direction=-1) + # use viridis colour scale and reverse it  so brighter is better.
    labs(fill="Yearly Gas Consumption (£s)")  + # colour bar label.
    theme(legend.position="bottom") + # change plot to widescreen dimensions.
    xlab("Longitude") + # axis labels
    ylab("Latitude")
print(gas_map)
ggsave(here::here("plots","gas_map.pdf"), plot=last_plot())

v <- 'yearly_oil'
oil_map <- ggplot(data = elec_aggregate2, aes(geometry = geometry, fill=.data[[v]])) +
    #geom_sf() + # black outlines on borders for clarity.
    geom_sf(color=NA) + # black outlines on borders for clarity.
    scale_fill_viridis_c(alpha = 1.0, direction=-1) + # use viridis colour scale and reverse it  so brighter is better.
    labs(fill="Yearly Fuel Oil Consumption (£s)") + # colour bar label.
    theme(legend.position="bottom") + # change plot to widescreen dimensions.
    xlab("Longitude") + # axis labels
    ylab("Latitude")
print(oil_map)
ggsave(here::here("plots","oil_map.pdf"), plot=last_plot())

v <- 'yearly_other_fuel'
other_map <- ggplot(data = elec_aggregate2, aes(geometry = geometry, fill=.data[[v]])) +
    #geom_sf() + # black outlines on borders for clarity.
    geom_sf(color=NA) + # black outlines on borders for clarity.
    scale_fill_viridis_c(alpha = 1.0, direction=-1) + # use viridis colour scale and reverse it  so brighter is better.
    labs(fill="Yearly Other Fuel Consumption (£s)")  + # colour bar label.
    theme(legend.position="bottom") + # change plot to widescreen dimensions.
    xlab("Longitude") + # axis labels
    ylab("Latitude")
print(other_map)
ggsave(here::here("plots","other_fuel_map.pdf"), plot=last_plot())

# quantile plots as well.

pdf(here::here("plots", "electricty_quantile_plot.pdf"))
hist(elec_aggregate2$yearly_electric, xlab="Yearly Electricity Cost", main="")
#plot(sort(elec_aggregate2$yearly_electric), xlab="Observation", ylab = "Monthly Electricity Cost")
dev.off()

pdf(here::here("plots", "gas_electricty_quantile_plot.pdf"))
hist(elec_aggregate2$yearly_gas_electric, xlab="YearlyGas and Electricity Cost", main="")
#plot(sort(elec_aggregate2$yearly_gas_electric), xlab="Observation", ylab = "Monthly Gas and Electricity Cost")
dev.off()

pdf(here::here("plots", "gas_quantile_plot.pdf"))
hist(elec_aggregate2$yearly_gas, xlab="Yearly Gas Cost", main="")
#plot(sort(elec_aggregate2$yearly_gas), xlab="Observation", ylab = "Monthly Gas Cost")
dev.off()

pdf(here::here("plots", "oil_quantile_plot.pdf"))
hist(elec_aggregate2$yearly_oil, xlab="Yearly Fuel Oil Cost", main="")
#plot(sort(elec_aggregate2$yearly_oil), xlab="Observation", ylab = "Monthly Fuel Oil Cost")
dev.off()

pdf(here::here("plots", "other_fuel_quantile_plot.pdf"))
hist(elec_aggregate2$yearly_other_fuel, xlab="Yearly Other Fuel Cost", main="")
#plot(sort(elec_aggregate2$yearly_other_fuel), xlab="Observation", ylab = "Monthly Other Fuel Cost")
dev.off()

#qqplot(elec_aggregate2$yearly_electric)

# rolling in DESNZ real median KWH usage for validation. 
elec_aggregate3 <- merge(elec_aggregate2, electricity_consumption_data, by="ZoneID")
elec_aggregate4 <- merge(elec_aggregate3, gas_consumption_data, by="ZoneID")

# simple linear regression between KWH use and energy bill. 
print(summary(lm(median_electricity ~ yearly_electric-1, data=elec_aggregate4)))
print(summary(lm(median_gas ~ yearly_gas-1, data=elec_aggregate4)))

print(summary(lm(yearly_electric ~ median_electricity -1, data=elec_aggregate4)))
print(summary(lm(yearly_gas~median_gas -1, data=elec_aggregate4)))

plot(elec_aggregate4$yearly_gas, elec_aggregate4$median_gas)
plot(elec_aggregate4$yearly_electric, elec_aggregate4$median_electric)

```

### 2024-10-03 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Tweaks to income module and additions to plotting scripts

@@
 #workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
-workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
 #workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_33_scot_clipped/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
+workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"
@@
 
-# data <- do.call(rbind, generate_df_list('whole_pop', 'baseline'))
-# data.fam <- do.call(rbind, generate_df_list('families', 'baseline'))
-# 
-# nrow(data)
-# 
-# 
-# 5463300
-# 
-# 4580000
-# 
-# 
-# 359328 / 458000 * 100
-# 
-# 100 / 78.4559
-# 
-# 
-# 109338 * 12.74601
+data <- do.call(rbind, generate_df_list('whole_pop', 'baseline'))
+data.fam <- do.call(rbind, generate_df_list('families', 'baseline'))
+
+nrow(data)
+
+5463300
+
+4580000
+
+359328 / 458000 * 100
+
+100 / 78.4559
+
+359328 * 12.74601
+
+#2030	-1800.26
+
+print('RESULT 1:')
+1800.26 * 12.74601
+
+109338 / 1262147 * 100
+
+100 / 86.62906
+
+109338 * 11.5437
+
+# 2030	-590.55
+
+print('RESULT 2:')
+590.55 * 11.5437
 

### 2024-10-03 minos/validation/handovers.Rmd
Tweaks to income module and additions to plotting scripts

@@
   labs(title = 'Households with Children Count')
+
+rm(raw.hhs_kids.ethnicity, base.hhs_kids.ethnicity)
 ```

### 2024-10-09 docsrc/documentation/notebooks/mental_well_being.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

@@
 ```{r SF12_Density}
-continuous_density("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")  
+continuous_density("data/transitions/SF_12_MCS/OLS/SF_12_MCS_2018_2019.rds", "next_SF_12_MCS")  
 ```
@@
 options(width=120)
-ols_output("data/transitions/SF_12/OLS/SF_12_2018_2019.rds")
-ols_histogram("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")
+ols_output("data/transitions/SF_12_MCS/OLS/SF_12_MCS_2018_2019.rds")
+ols_histogram("data/transitions/SF_12_MCS/OLS/SF_12_MCS_2018_2019.rds", "next_SF_12_MCS")
 ```

### 2024-10-09 minos/outcomes/spatial_analysis_gbis.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

@@
 continuous_var_table <- continuous_var_table[, c("Variable", "LSOA Type", "EPCG Variable Mean", "GBIS Variable Mean")]
+continuous_var_table <- continuous_var_table[, c("Variable", "LSOA Type", "GBIS Variable Mean", "EPCG Variable Mean")]
 
-print(xtable(discrete_var_table, type = "latex"), file = here::here("plots", "GBIS_discrete_var_table.tex"))
-print(xtable(continuous_var_table, type = "latex"), file = here::here("plots", "GBIS_continuous_var_table.tex"))
+print(xtable(discrete_var_table, type = "latex"), file = here::here("plots", "GBIS_discrete_var_table.tex"), include.rownames=FALSE)
+print(xtable(continuous_var_table, type = "latex"), file = here::here("plots", "GBIS_continuous_var_table.tex"), include.rownames=FALSE)
 

### 2024-10-09 minos/outcomes/standard_deviation_change_SF12.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

@@
 base.subset <- base %>% 
-  select(pidp, time, SF_12) %>%
-  rename(SF12.base = SF_12)
+  select(pidp, time, SF_12_MCS) %>%
+  rename(SF12.base = SF_12_MCS)
 int.subset <- int %>% 
-  select(pidp, time, income_boosted, SF_12) %>%
-  rename(SF12.int = SF_12,
+  select(pidp, time, income_boosted, SF_12_MCS) %>%
+  rename(SF12.int = SF_12_MCS,
          boosted = income_boosted)
@@
 # get just one year
-#b.2020 <- base %>% filter(time == 2020, SF_12 != -8.0)
-b.2030 <- base %>% filter(time == 2030, SF_12 != -8.0)
-i.2030 <- int %>% filter(time == 2030, SF_12 != -8.0)
+#b.2020 <- base %>% filter(time == 2020, SF_12_MCS != -8.0)
+b.2030 <- base %>% filter(time == 2030, SF_12_MCS != -8.0)
+i.2030 <- int %>% filter(time == 2030, SF_12_MCS != -8.0)
 ```
@@
 # get just the SF12 columns
-b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(baseline = SF_12)
-i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(intervention = SF_12)
-#b.2020 <- b.2020 %>% select(pidp, SF_12) %>% rename(initial = SF_12)
-#b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
-#i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
+b.2030 <- b.2030 %>% select(pidp, SF_12_MCS) %>% rename(baseline = SF_12_MCS)
+i.2030 <- i.2030 %>% select(pidp, SF_12_MCS) %>% rename(intervention = SF_12_MCS)
+#b.2020 <- b.2020 %>% select(pidp, SF_12_MCS) %>% rename(initial = SF_12_MCS)
+#b.2030 <- b.2030 %>% select(pidp, SF_12_MCS) %>% rename(end = SF_12_MCS)
+#i.2030 <- i.2030 %>% select(pidp, SF_12_MCS) %>% rename(end = SF_12_MCS)
 ```

### 2024-10-09 minos/testing/rate_of_change_testing.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

@@
 
-SF_12.stats <- diff_by_whole_period_quintile(raw.dat, 'SF_12')
+SF_12_MCS.stats <- diff_by_whole_period_quintile(raw.dat, 'SF_12_MCS')
 ```
@@
 
-## SF_12_MCS
+## SF_12_MCS_MCS
 
-Quick look at SF_12_MCS also.
+Quick look at SF_12_MCS_MCS also.
 
 ```{r}
-spaghetti_plot(old.dat, 'SF_12')
-spaghetti_plot(new.dat, 'SF_12')
-spaghetti_plot(raw.dat, 'SF_12')
+spaghetti_plot(old.dat, 'SF_12_MCS')
+spaghetti_plot(new.dat, 'SF_12_MCS')
+spaghetti_plot(raw.dat, 'SF_12_MCS')
 ```
@@
 ```{r}
-violin_plot(old.dat, 'SF_12')
-violin_plot(new.dat, 'SF_12')
-violin_plot(raw.dat, 'SF_12')
+violin_plot(old.dat, 'SF_12_MCS')
+violin_plot(new.dat, 'SF_12_MCS')
+violin_plot(raw.dat, 'SF_12_MCS')
 ```
@@
 mod.path <- 'Minos/data/transitions/cross_validation/'
-sf12.mod <- readRDS(paste0(mod.path, 'SF_12/ols2/SF_12_2017_2018.rds'))
+sf12.mod <- readRDS(paste0(mod.path, 'SF_12_MCS/ols2/SF_12_MCS_2017_2018.rds'))
 income.mod <- readRDS(paste0(mod.path, 'hh_income/ols2/hh_income_2019_2020.rds'))
@@
 #raw <- raw.cv %>%
-#  filter(!hh_income %in% miss.values, !SF_12 %in% miss.values) %>%
+#  filter(!hh_income %in% miss.values, !SF_12_MCS %in% miss.values) %>%
 #  group_by(pidp) %>%
 #  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time),
-#         diff.SF12_MCS = SF_12 - lag(SF_12, order_by = time)) %>%
+#         diff.SF12_MCS = SF_12_MCS - lag(SF_12_MCS, order_by = time)) %>%
 #  filter(time != 2009)
@@
 #base <- base.cv %>%
-#  filter(!hh_income %in% miss.values, !SF_12 %in% miss.values) %>%
+#  filter(!hh_income %in% miss.values, !SF_12_MCS %in% miss.values) %>%
 #  group_by(pidp) %>%
 #  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time),
-#         diff.SF12_MCS = SF_12 - lag(SF_12, order_by = time)) %>%
+#         diff.SF12_MCS = SF_12_MCS - lag(SF_12_MCS, order_by = time)) %>%
 #  filter(time != 2014)
@@
 #  summarise(mean.income = mean(hh_income, na.rm = TRUE),
-#            mean.SF12 = mean(SF_12, na.rm = TRUE))
+#            mean.SF12 = mean(SF_12_MCS, na.rm = TRUE))
 

### 2024-10-09 minos/validation/DEBUG.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

@@
 raw.sf12 <- raw.dat %>% 
-  select(pidp, time, SF_12) %>%
+  select(pidp, time, SF_12_MCS) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'final_US')
@@
 base.sf12 <- base.dat %>%
-  select(pidp, time, SF_12) %>%
+  select(pidp, time, SF_12_MCS) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'baseline_output')
@@
 raw.sf12.2 <- raw.dat %>% 
-  select(pidp, time, SF_12) %>%
+  select(pidp, time, SF_12_MCS) %>%
   filter(pidp %in% raw.sf12.wave1) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'final_US')
@@
 base.sf12.2 <- base.dat %>%
-  select(pidp, time, SF_12) %>%
+  select(pidp, time, SF_12_MCS) %>%
   filter(pidp %in% raw.sf12.wave1) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'baseline_output')
@@
 sf12 <- data %>% 
-  select(pidp, time, SF_12)
+  select(pidp, time, SF_12_MCS)
 
@@
 sf12.byyr <- data %>% group_by(time) %>%
-  summarise(SF_12 = mean(SF_12))
+  summarise(SF_12_MCS = mean(SF_12_MCS))
 
-ggplot(data = sf12.byyr, mapping = aes(x = time, y = SF_12)) +
+ggplot(data = sf12.byyr, mapping = aes(x = time, y = SF_12_MCS)) +
   geom_line()
@@
 
-ggplot(data = sf12.joined, mapping = aes(x = SF_12, group = time, fill = time, color = time)) +
+ggplot(data = sf12.joined, mapping = aes(x = SF_12_MCS, group = time, fill = time, color = time)) +
   geom_histogram(position='dodge')
@@
 print("2018:")
-sprintf("Min: %f", min(sf12.2018$SF_12))
-sprintf("Max: %f", max(sf12.2018$SF_12))
-sprintf("Mean: %f", mean(sf12.2018$SF_12))
+sprintf("Min: %f", min(sf12.2018$SF_12_MCS))
+sprintf("Max: %f", max(sf12.2018$SF_12_MCS))
+sprintf("Mean: %f", mean(sf12.2018$SF_12_MCS))
 print("2020:")
-sprintf("Min: %f", min(sf12.2020$SF_12))
-sprintf("Max: %f", max(sf12.2020$SF_12))
-sprintf("Mean: %f", mean(sf12.2020$SF_12))
+sprintf("Min: %f", min(sf12.2020$SF_12_MCS))
+sprintf("Max: %f", max(sf12.2020$SF_12_MCS))
+sprintf("Mean: %f", mean(sf12.2020$SF_12_MCS))
 print("2030:")
-sprintf("Min: %f", min(sf12.2030$SF_12))
-sprintf("Max: %f", max(sf12.2030$SF_12))
-sprintf("Mean: %f", mean(sf12.2030$SF_12))
+sprintf("Min: %f", min(sf12.2030$SF_12_MCS))
+sprintf("Max: %f", max(sf12.2030$SF_12_MCS))
+sprintf("Mean: %f", mean(sf12.2030$SF_12_MCS))
 ```
@@
 educ.mod <- readRDS(paste0(trans.path, 'education_state/nnet/education_state_2018_2019.rds'))
-sf_12.mod <- readRDS(paste0(trans.path, 'SF_12/ols/SF_12_2018_2019.rds'))
+sf_12.mod <- readRDS(paste0(trans.path, 'SF_12_MCS/ols/SF_12_MCS_2018_2019.rds'))
 house.mod <- readRDS(paste0(trans.path, 'housing_quality/clm/housing_quality_2018_2019.rds'))
@@
 ```{r}
-f.sf12 <- raw.dat %>% select(pidp, time, SF_12)
-c.sf12 <- correct %>% select(pidp, time, SF_12)
+f.sf12 <- raw.dat %>% select(pidp, time, SF_12_MCS)
+c.sf12 <- correct %>% select(pidp, time, SF_12_MCS)
 
@@
 
-Now see if any SF_12 values are missing in either the final data or corrected.
+Now see if any SF_12_MCS values are missing in either the final data or corrected.
 
 ```{r}
-sum(is.na(f.sf12$SF_12))
-sum(is.na(c.sf12$SF_12))
+sum(is.na(f.sf12$SF_12_MCS))
+sum(is.na(c.sf12$SF_12_MCS))
 
-sum(f.sf12$SF_12 == -9)
-sum(c.sf12$SF_12 == -9)
+sum(f.sf12$SF_12_MCS == -9)
+sum(c.sf12$SF_12_MCS == -9)
 
@@
   group_by(time) %>%
-  summarise(final.missing = sum((SF_12 == -9)))
+  summarise(final.missing = sum((SF_12_MCS == -9)))
 
@@
   group_by(time) %>%
-  summarise(correct.missing = sum((SF_12 == -9)))
+  summarise(correct.missing = sum((SF_12_MCS == -9)))
 

### 2024-10-09 minos/validation/cross_validation_default.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

--- 2024-01-31 minos/validation/cross_validation_default.Rmd
@@
                                  predicted = cv, 
-                                 var = 'SF_12', 
+                                 var = 'SF_12_MCS', 
                                  target.year = 2021)

### 2024-10-09 minos/validation/handovers.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

--- 2024-09-06 minos/validation/handovers.Rmd
@@
 ```{r}
+
 # Read raw datafiles in
-#raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
-raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
-#raw.files <- list.files(here::here('data', 'scaled_scotland_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+#raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'scaled_manchester_aligned_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
-raw.dat <- raw.dat %>%
-  filter(weight > 0)
-
-out.path <- here::here('output', 'default_config/')
-# out.path <- here::here('output', 'scotland_scaled/')
-base.dat <- read_singular_local_out(out.path, 'baseline',
-                                    drop.dead = TRUE,
-                                    drop.zero.weight = TRUE)
-
-# base.dat <- read_singular_local_out(out.path, 'ChildPovertyReduction',
-#                                     drop.dead = TRUE,
-#                                     drop.zero.weight = TRUE)
-
-#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
+
+out.path <- here::here('output', 'energy_default_config/')
+out.path <- here::here('output', 'energy_manchester_scaled/')
+base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
 ```
@@
 
-# DEMOGRAPHICS
-
-## Age Structure
-
-```{r}
-# assign to age_bucket in raw data
-cut_bins <- c(-1, 15, 19, 24, 29, 44, 59, 74, 200)
-cut_labels <- c("0to15", "16to19", "20to24", "25to29", "30to44", "45to59", "60to74", "75plus")
-
-raw.dat$age_bucket <- cut(raw.dat$age, 
-                          breaks = cut_bins, 
-                          labels = cut_labels)
-
-handover_ordinal(raw.dat, base.dat, var = 'age_bucket', save = shall.we.save)
-```
-
-## Age Structure (Households with Children)
-
-```{r}
-raw.dat_fam <- raw.dat %>%
-  filter(nkids > 0)
-
-base.dat_fam <- base.dat %>%
-  filter(nkids > 0)
-
-empty.dat <- raw.dat %>%
-  filter(age > 150)
-
-handover_ordinal(raw.dat_fam, base.dat_fam, var = 'age_bucket', save = shall.we.save)
-handover_ordinal(empty.dat, base.dat_fam, var = 'age_bucket', save = shall.we.save)
-```
-
-## Max Age
-
-```{r}
-raw.maxAge <- raw.dat %>%
-  group_by(time) %>%
-  summarise(max_age = max(age)) %>%
-  mutate(scen = 'final_US')
-
-base.maxAge <- base.dat %>%
-  group_by(time) %>%
-  summarise(max_age = max(age)) %>%
-  mutate(scen = 'baseline')
-
-combined <- rbind(raw.maxAge, base.maxAge)
-
-#handover_lineplots(raw.maxAge, base.maxAge, 'max_age')
-ggplot(combined, aes(x = time, y = max_age, group = scen, colour = scen)) +
-  geom_line() +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
-  labs(title = 'Max year of age') +
-  xlab('Year') +
-  ylab('Age')
-
-## Check counts in very old age groups
-brks = c(75, 80, 85, 90, 95, 100, 105, 110)
-lbls = c("75to80", "80to85", "85to90", "90to95", "95to100", "100to105", "105to110")
-
-raw.countOldAge <- raw.dat %>%
-  filter(age > 75) %>%
-  mutate(age_group = cut(age,
-                         breaks = brks,
-                         labels = lbls)) %>%
-  group_by(time, age_group) %>%
-  summarise(age_group_counts = n()) %>%
-  mutate(source = 'observed')
-
-base.countOldAge <- base.dat %>%
-  filter(age > 75) %>%
-  mutate(age_group = cut(age,
-                         breaks = brks,
-                         labels = lbls)) %>%
-  group_by(time, age_group) %>%
-  summarise(age_group_counts = n()) %>%
-  mutate(source = 'predicted')
-
-combined <- rbind(raw.countOldAge, base.countOldAge)
-
-ggplot(combined, aes(x = time, y = age_group_counts, group = age_group, colour = age_group)) +
-  geom_line() +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
-  labs(title = 'Counts by older age group', subtitle = '75 to 110 by 5 year groups') +
-  xlab('Year') +
-  ylab('Count')
-
-raw.countOldAge <- raw.dat %>%
-  filter(age > 75) %>%
-  mutate(age_group = cut(age,
-                         breaks = brks,
-                         labels = lbls))
-
-base.countOldAge <- base.dat %>%
-  filter(age > 75) %>%
-  mutate(age_group = cut(age,
-                         breaks = brks,
-                         labels = lbls))
-
-handover_ordinal(raw.countOldAge, base.countOldAge, var = 'age_group', save = shall.we.save)
-
-```
-
-```{r}
-# Having a go at an age pyramid, hopefully animated
-
-brks = c(75, 80, 85, 90, 95, 100, 105, 110)
-lbls = c("75to80", "80to85", "85to90", "90to95", "95to100", "100to105", "105to110")
-
-var <- 'age_group'
-
-# start with calculating percentages
-#raw.oldAgePct
-#base.oldAgePct
-
-raw.oldAgePct <- raw.dat %>%
-  filter(age > 75) %>%
-  mutate(age_group = cut(age,
-                         breaks = brks,
-                         labels = lbls)) %>%
-  dplyr::select(time, age_group) %>%
-  group_by(time, age_group) %>%
-  count() %>%
-  mutate(source = 'predicted')
-
-base.oldAgePct <- base.dat %>%
-  filter(age > 75) %>%
-  mutate(age_group = cut(age,
-                         breaks = brks,
-                         labels = lbls)) %>%
-  dplyr::select(time, all_of(var)) %>%
-  #filter(!.data[[var]] %in% miss.values) %>%
-  group_by(time, .data[[var]]) %>%
-  count() %>%
-  mutate(source = 'observed')
-
-raw.oldAgePct[[var]] <- as.factor(raw.oldAgePct[[var]])
-base.oldAgePct[[var]] <- as.factor(base.oldAgePct[[var]])
-
-merged <- rbind(raw.oldAgePct, base.oldAgePct)
-merged[[var]] <- as.factor(merged[[var]])
-
-var.norm <- merged %>%
-    group_by(time) %>%
-    mutate(total = sum(n)) %>%
-    mutate(prct = (n / total) * 100)
-```
-
-## Population Counts
-
-### Total Pop
-
-```{r}
-raw.alive <- raw.dat %>%
-  group_by(time) %>%
+# PATHWAYS
+
+## SF_12_PCS
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'SF_12_PCS')
+handover_lineplots(raw.dat, base.dat, "SF_12_PCS")
+```
+
+### Spaghetti
+
+```{r}
+raw.sf12.p <- raw.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+base.sf12.p <- base.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+
+sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)
+
+spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(sf12.p.spag, "SF_12_PCS", 
+               save = shall.we.save, 
+               save.path = save.path)
+
+rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
+```
+
+## Physical Activity
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
+
+raw.2020.phys <- raw.dat %>% 
+  filter(time == 2020) %>%
+  group_by(active) %>%
   summarise(n = n()) %>%
-  mutate(scen = 'final_US')
-
-base.alive <- base.dat %>%
-  group_by(time) %>%
+  mutate(prop = n / sum(n))
+```
+
+## Alcohol (AUDITC)
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
+
+raw.2020.alc <- raw.dat %>% 
+  filter(time == 2020) %>%
+  group_by(auditc) %>%
   summarise(n = n()) %>%
-  mutate(scen = 'baseline')
-
-#handover_boxplots(raw.alive, base.alive, 'n')
-#handover_lineplots(raw.alive, base.alive, "n")
-
-combined <- rbind(raw.alive, base.alive)
-
-ggplot(combined, aes(x = time, y = n, group = scen, color = scen, fill = scen)) +
-  geom_line() +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
-  labs(title = 'Total Count in Sample') +
-  xlab('Year') +
-  ylab('Count')
-
-rm(raw.alive, base.alive)
-```
-
-### Households
-
-```{r}
-raw.hhs <- raw.dat %>%
-  select(hidp, time) %>%
-  distinct() %>%
-  group_by(time) %>%
-  summarise(n = n()) %>%
-  mutate(source = 'final_US')
-
-base.hhs <- base.dat %>%
-  select(hidp, time) %>%
-  distinct() %>%
-  group_by(time) %>%
-  summarise(n = n()) %>%
-  mutate(source = 'baseline')
-
-combined <- rbind(raw.hhs, base.hhs)
-
-ggplot(combined, aes(x = time, y = n, group = source, color = source, fill = source)) +
-  geom_point() +
-  geom_line() +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
-  labs(title = 'Households Count')
-```
-
-### Households With Children
-
-```{r}
-raw.household_count_by_year <- raw.dat %>%
-  filter(nkids > 0) %>%
-  select(hidp, time) %>%  # Select relevant columns to reduce data size
-  distinct() %>%
-  group_by(time) %>%
-  summarise(n = n()) %>%
-  mutate(source = 'final_US')
-
-base.household_count_by_year <- base.dat %>%
-  filter(nkids > 0) %>%
-  select(hidp, time) %>%  # Select relevant columns to reduce data size
-  distinct() %>%
-  group_by(time) %>%
-  summarise(n = n()) %>%
-  mutate(source = 'baseline')
-
-combined <- rbind(raw.household_count_by_year, base.household_count_by_year)
-
-ggplot(combined, aes(x = time, y = n, group = source, color = source, fill = source)) +
-  geom_point() +
-  geom_line() +
-  labs(title = 'Households with Children Count')
-```
-
-### Households With Children (Income Quintile)
-
-```{r}
-raw.hhs_kids.income_quint <- raw.dat %>%
-  filter(nkids > 0) %>%
-  select(hidp, time, hh_income) %>%  # Select relevant columns to reduce data size
-  distinct() %>%
-  mutate(income_group = case_when(
-    hh_income <= 1000 ~ "<= 1000",
-    hh_income <= 1500 ~ "1001 - 1500",
-    hh_income <= 2000 ~ "1501 - 2000",
-    hh_income <= 2500 ~ "2001 - 2500",
-    hh_income > 2500  ~ "> 2500"
-  )) %>%
-  group_by(time, income_group) %>%
-  summarise(n = n(), .groups = 'drop') %>%
-  mutate(source = 'final_US')
-
-base.hhs_kids.income_quint <- base.dat %>%
-  filter(nkids > 0) %>%
-  select(hidp, time, hh_income) %>%  # Select relevant columns to reduce data size
-  distinct() %>%
-  mutate(income_group = case_when(
-    hh_income <= 1000 ~ "<= 1000",
-    hh_income <= 1500 ~ "1001 - 1500",
-    hh_income <= 2000 ~ "1501 - 2000",
-    hh_income <= 2500 ~ "2001 - 2500",
-    hh_income > 2500  ~ "> 2500"
-  )) %>%
-  group_by(time, income_group) %>%
-  summarise(n = n(), .groups = 'drop') %>%
-  mutate(source = 'baseline')
-
-combined <- rbind(raw.hhs_kids.income_quint, base.hhs_kids.income_quint)
-combined$income_group <- factor(combined$income_group)
-
-ggplot(combined, aes(x = time, y = n, group = income_group, color = income_group, fill = income_group)) +
-  geom_point() +
-  geom_line() +
-  geom_vline(xintercept = start.year) +
-  labs(title = 'Households with Children Count')
-```
-
-#### Proportions
-
-```{r}
-calculate_hh_proportions <- function(data) {
-  # Step 1: Filter for households with children
-  households_with_kids <- data %>%
-    filter(nkids > 0) %>%
-    select(hidp, time, hh_income) %>%
-    distinct()
-
-  # Step 2: Create income group based on thresholds
-  households_with_kids <- households_with_kids %>%
-    mutate(income_group = case_when(
-      hh_income <= 1000 ~ "<= 1000",
-      hh_income <= 1500 ~ "1001 - 1500",
-      hh_income <= 2000 ~ "1501 - 2000",
-      hh_income <= 2500 ~ "2001 - 2500",
-      hh_income > 2500  ~ "> 2500"
-    ))
-
-  # Step 3: Count households within each income group per year
-  household_counts <- households_with_kids %>%
-    group_by(time, income_group) %>%
-    summarise(count = n(), .groups = 'drop')
-
-  # Step 4: Calculate total households with children per year
-  total_households_per_year <- households_with_kids %>%
-    group_by(time) %>%
-    summarise(total_count = n(), .groups = 'drop')
-
-  # Step 5: Calculate proportion of households in each group per year
-  household_proportions <- household_counts %>%
-    left_join(total_households_per_year, by = "time") %>%
-    mutate(proportion = count / total_count) %>%
-    select(time, income_group, proportion)
-
-  return(household_proportions)
-}
-
-raw.hh_kids_prop <- calculate_hh_proportions(raw.dat)
-base.hh_kids_prop <- calculate_hh_proportions(base.dat)
-
-raw.hh_kids_prop$source <- 'final_US'
-raw.hh_kids_prop <- filter(raw.hh_kids_prop, time != start.year)
-base.hh_kids_prop$source <- 'baseline'
-
-combined <- rbind(raw.hh_kids_prop, base.hh_kids_prop)
-combined$income_group <- factor(combined$income_group)
-
-ggplot(combined, aes(x = time, y = proportion, group = income_group, color = income_group, fill = income_group)) +
-  geom_col() +
-  geom_vline(xintercept = start.year) +
-  labs(title = 'Households with Children Count')
-```
-
-```{r}
-# # Step 1: Filter for households with children
-# households_with_kids <- raw.dat %>%
-#   filter(nkids > 0) %>%
-#   select(hidp, time, hh_income) %>%
-#   distinct() %>%
-#   select(-hidp)
-# 
-# # Step 2: Calculate income quintiles
-# households_with_kids <- households_with_kids %>%
-#   group_by(time) %>%
-#   mutate(income_quintile = ntile(hh_income, 5)) %>%
-#   ungroup()
-# 
-# # Step 3: Count households within each income quintile per year
-# household_count_by_income_quintile <- households_with_kids %>%
-#   group_by(time, income_quintile) %>%
-#   summarise(n = n())
-# 
-# household_count_by_income_quintile
-```
-
-### Households With Children (Ethnic Group)
-
-```{r}
-raw.hhs_kids.ethnicity <- raw.dat %>%
-  filter(nkids > 0) %>%
-  select(hidp, time, hh_income, ethnicity) %>%  # Select relevant columns to reduce data size
-  distinct() %>%
-  group_by(time, ethnicity) %>%
-  summarise(n = n(), .groups = 'drop') %>%
-  mutate(source = 'final_US')
-
-base.hhs_kids.ethnicity <- base.dat %>%
-  filter(nkids > 0) %>%
-  select(hidp, time, hh_income, ethnicity) %>%  # Select relevant columns to reduce data size
-  distinct() %>%
-  group_by(time, ethnicity) %>%
-  summarise(n = n(), .groups = 'drop') %>%
-  mutate(source = 'baseline')
-
-combined <- rbind(raw.hhs_kids.ethnicity, base.hhs_kids.ethnicity)
-combined$ethnicity <- factor(combined$ethnicity)
-
-ggplot(combined, aes(x = time, y = n, group = ethnicity, color = ethnicity, fill = ethnicity)) +
-  geom_point() +
-  geom_line() +
-  geom_vline(xintercept = start.year) +
-  labs(title = 'Households with Children Count')
-```
-
-```{r}
-calculate_hh_proportions <- function(data, group.var) {
-  # Step 1: Filter for households with children
-  households_with_kids <- data %>%
-    filter(nkids > 0) %>%
-    select(hidp, time, hh_income, .data[[group.var]]) %>%
-    distinct()
-
-  # Step 3: Count households within each income group per year
-  household_counts <- households_with_kids %>%
-    group_by(time, .data[[group.var]]) %>%
-    summarise(count = n(), .groups = 'drop')
-
-  # Step 4: Calculate total households with children per year
-  total_households_per_year <- households_with_kids %>%
-    group_by(time) %>%
-    summarise(total_count = n(), .groups = 'drop')
-
-  # Step 5: Calculate proportion of households in each group per year
-  household_proportions <- household_counts %>%
-    left_join(total_households_per_year, by = "time") %>%
-    mutate(proportion = count / total_count) %>%
-    select(time, .data[[group.var]], proportion)
-
-  return(household_proportions)
-}
-
-raw.hh_kids_prop <- calculate_hh_proportions(raw.dat, group.var = 'ethnicity')
-base.hh_kids_prop <- calculate_hh_proportions(base.dat, group.var = 'ethnicity')
-
-raw.hh_kids_prop$source <- 'final_US'
-raw.hh_kids_prop <- filter(raw.hh_kids_prop, time != start.year)
-base.hh_kids_prop$source <- 'baseline'
-
-combined <- rbind(raw.hh_kids_prop, base.hh_kids_prop)
-combined$ethnicity <- factor(combined$ethnicity)
-
-ggplot(combined, aes(x = time, y = proportion, group = ethnicity, color = ethnicity, fill = ethnicity)) +
-  geom_col() +
-  geom_vline(xintercept = start.year) +
-  labs(title = 'Households with Children Count')
-```
-
-# PATHWAYS
+  mutate(prop = n / sum(n))
+
+```
 
@@
 # sf12 boxplot handovers
-handover_boxplots(raw.dat, base.dat, 'SF_12')
-handover_lineplots(raw.dat, base.dat, "SF_12")
-
-handover_boxplots(raw.dat, base.dat, 'SF_12_diff')
-handover_lineplots(raw.dat, base.dat, "SF_12_diff")
-
+handover_boxplots(raw.dat, base.dat, 'SF_12_MCS')
+handover_lineplots(raw.dat, base.dat, "SF_12_MCS")
+# 
+# raw.sf12 <- raw.dat %>% 
+#   dplyr::select(pidp, time, SF_12_MCS) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.sf12 <- base.dat %>%
+#   dplyr::select(pidp, time, SF_12_MCS) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# # merge before plot
+# sf12 <- rbind(raw.sf12, base.sf12)
+# 
+# # Now plot
+# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+#   geom_smooth() +
+#   #geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
+#   xlab('Year') +
+#   ylab('SF12')
+# 
+# ## Try a version where final_US is limited to only those present from wave 1 
+# # onwards because the sample refreshments are messing with the plot
+# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+# 
+# raw.sf12.2 <- raw.dat %>% 
+#   dplyr::select(pidp, time, SF_12_MCS) %>%
+#   filter(pidp %in% raw.sf12.wave1) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
+#   mutate(source = 'final_US')
+# 
+# base.sf12.2 <- base.dat %>%
+#   dplyr::select(pidp, time, SF_12_MCS) %>%
+#   filter(pidp %in% raw.sf12.wave1) %>%
+#   group_by(time) %>%
+#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
+#   mutate(source = 'baseline_output')
+# 
+# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
+# 
+# # Now plot
+# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+#   geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
+#   xlab('Year') +
+#   ylab('SF12')
+# 
+# if (shall.we.save) {
+#   ggsave(filename = 'SF12_wav1.png',
+#        plot = last_plot(),
+#        path = save.path)
+# }
+# 
+# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
 ```
@@
 raw.sf12 <- raw.dat %>%
-  select(pidp, age, time, SF_12, SF_12_diff)
+  select(pidp, age, time, SF_12_MCS)
 base.sf12 <- base.dat %>%
-  select(pidp, age, time, SF_12, SF_12_diff)
+  select(pidp, age, time, SF_12_MCS)
 
@@
 sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(sf12.spag.sample, 'SF_12',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
-               save = shall.we.save,
-               save.path = save.path)
-
-spaghetti_plot(sf12.spag.sample, 'SF_12_diff',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_diff',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(sf12.spag, "SF_12", 
+spaghetti_plot(sf12.spag.sample, 'SF_12_MCS',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_MCS',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(sf12.spag, "SF_12_MCS", 
                save = T, 
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, housing_quality)
-base.s <- base.dat %>%
-  select(pidp, age, time, housing_quality)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'housing_quality',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, housing_quality)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, housing_quality)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'housing_quality',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
+```
+
+## Housing Tenure
+
+```{r}
+raw.tenure <- raw.dat %>%
+  dplyr::select(pidp, time, housing_tenure) %>%
+  group_by(time, housing_tenure) %>%
+  count() %>%
+  mutate(source = 'final_US')
+
+base.tenure <- base.dat %>%
+  dplyr::select(pidp, time, housing_tenure) %>%
+  group_by(time, housing_tenure) %>%
+  count() %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+tenure <- rbind(raw.tenure, base.tenure)
+tenure$housing_tenure <- as.factor(tenure$housing_tenure)
+
+# Now plot
+ggplot(data = tenure, mapping = aes(x = time, y = n, group = housing_tenure, colour = housing_tenure)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Housing Tenure', subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+tenure.norm <- tenure %>%
+  group_by(time) %>%
+  mutate(total = sum(n)) %>%
+  mutate(prct = (n / total))
+
+ggplot(data = tenure.norm, mapping = aes(x = time, y = prct, fill=housing_tenure)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Housing Tenure') +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'housing_tenure.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.tenure, base.tenure, tenure, tenure.norm)
 ```
@@
 ```{r}
-raw.nut <- raw.dat %>%
-  select(pidp, age, time, nutrition_quality)
-base.nut <- base.dat %>%
-  select(pidp, age, time, nutrition_quality)
-
-nut.spag <- rbind(raw.nut, base.nut)
-
-spaghetti_plot(nut.spag, 'nutrition_quality',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(nut.spag, "nutrition_quality",
-               save = T,
-               save.path = save.path)
-
-rm(raw.nut, base.nut, nut.spag)
+# raw.nut <- raw.dat %>%
+#   select(pidp, age, time, nutrition_quality)
+# base.nut <- base.dat %>%
+#   select(pidp, age, time, nutrition_quality)
+# 
+# nut.spag <- rbind(raw.nut, base.nut)
+# 
+# spaghetti_plot(nut.spag, 'nutrition_quality',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# 
+# density_ridges(nut.spag, "nutrition_quality", 
+#                save = T, 
+#                save.path = save.path)
+# 
+# rm(raw.nut, base.nut, nut.spag)
 ```
@@
                  save.path = save.path)
-```
-
-# ADDITIONAL VARIABLES
-
-## Education
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Education State'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'education_state.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.dat,
-                                       df1.name = 'simulated',
-                                       df2 = raw.dat,
-                                       df2.name = 'raw',
-                                       var = 'education_state')
-
-cv_ordinal_plots(pivoted.df = pivoted,
-                 var = 'education_state',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, education_state)
-base.s <- base.dat %>%
-  select(pidp, age, time, education_state)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'education_state',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## Financial Situation
-
-```{r}
-raw.financial_situation <- raw.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.financial_situation <- base.dat %>%
-  dplyr::select(pidp, time, financial_situation) %>%
-  group_by(time, financial_situation) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-financial_situation <- rbind(raw.financial_situation, base.financial_situation)
-financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)
-
-# Now plot
-ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-financial_situation.norm <- financial_situation %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Financial situation') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'financial_situation.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
-```
-
-## Behind On Bills
-
-```{r}
-raw.behind_on_bills <- raw.dat %>%
-  dplyr::select(pidp, time, behind_on_bills) %>%
-  group_by(time, behind_on_bills) %>%
-  count() %>%
-  mutate(source = 'final_US')
-
-base.behind_on_bills <- base.dat %>%
-  dplyr::select(pidp, time, behind_on_bills) %>%
-  group_by(time, behind_on_bills) %>%
-  count() %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-behind_on_bills <- rbind(raw.behind_on_bills, base.behind_on_bills)
-behind_on_bills$behind_on_bills <- as.factor(behind_on_bills$behind_on_bills)
-
-# Now plot
-ggplot(data = behind_on_bills, mapping = aes(x = time, y = n, group = behind_on_bills, colour = behind_on_bills)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Behind On Bills', subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-behind_on_bills.norm <- behind_on_bills %>%
-  group_by(time) %>%
-  mutate(total = sum(n)) %>%
-  mutate(prct = (n / total))
-
-ggplot(data = behind_on_bills.norm, mapping = aes(x = time, y = prct, fill=behind_on_bills)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Behind On Bills') +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'behind_on_bills.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-rm(raw.behind_on_bills, base.behind_on_bills, behind_on_bills, behind_on_bills.norm)
-```
-
-## nkids Household
-
-```{r}
-raw.hh_unique <- raw.dat %>%
-  select(hidp, time, nkids, weight) %>%
-  distinct(hidp, time, nkids, .keep_all = TRUE) %>%
-  mutate(scen = 'final_US')
-
-base.hh_unique <- base.dat %>%
-  select(hidp, time, nkids, weight) %>%
-  distinct(hidp, time, nkids, .keep_all = TRUE) %>%
-  mutate(scen = 'baseline')
-
-#handover_boxplots(raw.hh_unique, base.hh_unique, 'nkids')
-handover_lineplots(raw.hh_unique, base.hh_unique, 'nkids')
-
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, nkids)
-base.s <- base.dat %>%
-  select(pidp, age, time, nkids)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## nkids Max
-
-```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.nkids_max <- raw.dat %>%
-  dplyr::select(pidp, time, nkids) %>%
-  group_by(time) %>%
-  summarise(max_nkids = max(nkids)) %>%
-  mutate(source = 'final_US')
-
-base.nkids_max <- base.dat %>%
-  dplyr::select(pidp, time, nkids) %>%
-  group_by(time) %>%
-  summarise(max_nkids = max(nkids)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-max_nkids <- rbind(raw.nkids_max, base.nkids_max)
-
-# Now plot
-ggplot(data = max_nkids, mapping = aes(x = time, y = max_nkids, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Max nkids', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Average')
-```
-
-## Parity
-
-```{r}
-base.parity <- base.dat %>%
-  filter(sex == "Female")
-
-raw.parity <- raw.dat %>%
-  filter(sex == "Female")
-
-prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Parity (total no. of children)'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'parity.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-```{r}
-pivoted <- combine_and_pivot_long(df1 = base.parity,
-                                  df1.name = 'simulated', 
-                                  df2 = raw.parity, 
-                                  df2.name = 'raw', 
-                                  var = 'nkids_ind')
-
-cv_ordinal_plots(pivoted.df = pivoted, 
-                 var = 'nkids_ind',
-                 save = shall.we.save,
-                 save.path = save.path)
-```
-
-### Spaghetti
-
-```{r}
-raw.s <- raw.parity %>%
-  select(pidp, age, time, nkids_ind)
-base.s <- base.parity %>%
-  select(pidp, age, time, nkids_ind)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids_ind',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
-```
-
-## Hourly Wage
-
-```{r}
-handover_boxplots(raw.dat, base.dat, 'hourly_wage')
-handover_lineplots(raw.dat, base.dat, 'hourly_wage')
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, hourly_wage)
-base.s <- base.dat %>%
-  select(pidp, age, time, hourly_wage)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-# now a version limited to 0-100
-spag <- spag %>%
-  filter(hourly_wage <= 300)
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
 ```

### 2024-10-09 minos/validation/housing_handovers.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

@@
 # sf12 boxplot handovers
-handover_boxplots(raw.dat, base.dat, 'SF_12')
-handover_lineplots(raw.dat, base.dat, "SF_12")
+handover_boxplots(raw.dat, base.dat, 'SF_12_MCS')
+handover_lineplots(raw.dat, base.dat, "SF_12_MCS")
 
 raw.sf12 <- raw.dat %>%
-  dplyr::select(pidp, time, SF_12) %>%
-  group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  dplyr::select(pidp, time, SF_12_MCS) %>%
+  group_by(time) %>%
+  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'final_US')
@@
 base.sf12 <- base.dat %>%
-  dplyr::select(pidp, time, SF_12) %>%
-  group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  dplyr::select(pidp, time, SF_12_MCS) %>%
+  group_by(time) %>%
+  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'baseline_output')
@@
 raw.sf12.2 <- raw.dat %>%
-  dplyr::select(pidp, time, SF_12) %>%
+  dplyr::select(pidp, time, SF_12_MCS) %>%
   filter(pidp %in% raw.sf12.wave1) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'final_US')
@@
 base.sf12.2 <- base.dat %>%
-  dplyr::select(pidp, time, SF_12) %>%
+  dplyr::select(pidp, time, SF_12_MCS) %>%
   filter(pidp %in% raw.sf12.wave1) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'baseline_output')
@@
 raw.sf12 <- raw.dat %>%
-  select(pidp, age, time, SF_12)
+  select(pidp, age, time, SF_12_MCS)
 base.sf12 <- base.dat %>%
-  select(pidp, age, time, SF_12)
+  select(pidp, age, time, SF_12_MCS)
 
@@
 sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(sf12.spag.sample, 'SF_12',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(sf12.spag, "SF_12",
+spaghetti_plot(sf12.spag.sample, 'SF_12_MCS',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_MCS',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(sf12.spag, "SF_12_MCS",
                save = T,

### 2024-10-09 minos/data_generation/final_data_descriptive_stats.R

@@ -26,13 +26,13 @@ main <- function() {
                    "job_sector",
                    "job_sec",
                    "nutrition_quality",
-                   "SF_12",
+                   "SF_12_MCS",
                    "loneliness")
   
   key_continuous_columns <- c("age",
                              "hh_income",
                              "nutrition_quality",
-                             "SF_12")
+                             "SF_12_MCS")
   
   key_discrete_columns <- c(
                    "nkids",

### 2024-10-09 minos/modules/physical_wellbeing.py

@@ -183,8 +183,8 @@ class lmmYJPCS(Base):
                         'time',
                         'weight',
                         'hh_income',
-                        'SF_12',
-                        #'SF_12_diff',
+                        'SF_12_MCS',
+                        #'SF_12_MCS_diff',
                         'SF_12_PCS',
                         #'SF_12_PCS_diff',
                         'housing_quality',
@@ -214,7 +214,7 @@ class lmmYJPCS(Base):
         super().setup(builder)
 
         #only need to load this once for now.
-        #self.gee_transition_model = r_utils.load_transitions(f"SF_12/lmm/SF_12_LMM", self.rpy2_modules, path=self.transition_dir)
+        #self.gee_transition_model = r_utils.load_transitions(f"SF_12_MCS/lmm/SF_12_MCS_LMM", self.rpy2_modules, path=self.transition_dir)
         #self.gee_transition_model = r_utils.load_transitions(f"SF_12_PCS/glmm/SF_12_PCS_GLMM", self.rpy2_modules, path=self.transition_dir)
         #self.gee_transition_model = r_utils.load_transitions(f"SF_12_PCS/lmm/SF_12_PCS_LMM", self.rpy2_modules,
         #                                                     path=self.transition_dir)
@@ -269,7 +269,7 @@ class lmmYJPCS(Base):
         self.population_view.update(newWavePWB[['SF_12_PCS']])#, "SF_12_PCS_diff"]])
 
     def calculate_pwb(self, pop):
-        """Calculate SF_12 transition distribution based on provided people/indices
+        """Calculate SF_12_MCS transition distribution based on provided people/indices
         Parameters
         ----------
             index : pd.Index

### 2024-10-09 minos/modules/replenishment_scotland.py

@@ -54,7 +54,7 @@ class ReplenishmentScotland(Base):
                         'birth_year',
                         'nobs',
                         'region',
-                        'SF_12',
+                        'SF_12_MCS',
                         'hh_int_y',
                         'hh_int_m',
                         'Date',
@@ -71,7 +71,7 @@ class ReplenishmentScotland(Base):
                         'max_educ',
                         'yearly_energy',
                         'job_sector',
-                        'SF_12p',
+                        'SF_12_MCSp',
                         'gross_pay_se',
                         'nutrition_quality',
                         'job_hours_se',

### 2024-10-09 minos/modules/tobacco.py

@@ -65,7 +65,7 @@ class Tobacco(Base):
                         "ncigs",
                         'job_sec',
                         'hh_income',
-                        'SF_12',
+                        'SF_12_MCS',
                         ]
         #view_columns += self.transition_model.rx2('model').names
         self.population_view = builder.population.get_view(columns=view_columns)
@@ -189,7 +189,7 @@ class lmmTobacco(Base):
                         'ethnicity',
                         'region',
                         'hh_income',
-                        'SF_12',
+                        'SF_12_MCS',
                         'education_state',
                         'S7_labour_state',
                         'job_sec',
@@ -200,7 +200,7 @@ class lmmTobacco(Base):
                         "neighbourhood_safety",
                         "loneliness",
                         "hh_income",
-                        "SF_12"]
+                        "SF_12_MCS"]
         #view_columns += self.transition_model.rx2('model').names
         self.population_view = builder.population.get_view(columns=view_columns)
 

### 2024-10-09 minos/outcomes/aggregate_subset_functions.py

@@ -238,7 +238,7 @@ def dynamic_subset_function(data, subset_chain_string=None, mode='default_config
 
 def get_required_intervention_variables(subset_function_string):
     # get required variables for intervention used in aggregate_subset_function. makes csvs load much faster.
-    default_variables = ["weight", "pidp", "hidp", "alive", "SF_12", "SF_12_PCS",'time', "housing_quality", "hh_income",
+    default_variables = ["weight", "pidp", "hidp", "alive", "SF_12_MCS", "SF_12_PCS",'time', "housing_quality", "hh_income",
                          "neighbourhood_safety", "nkids", "loneliness", 'yearly_energy', 'heating']
 
     if "boosted" in subset_function_string:

### 2024-10-09 minos/transitions/transition_model_functions.R

@@ -460,13 +460,13 @@ estimate_mixed_zip <- function(data, fixed_formula, include_weights = FALSE, dep
   
   # test model with hard coded formulae.
   #model <- mixed_model(#fixed = ncigs_new ~ scale(age) + factor(ethnicity) + factor(sex) + scale(hh_income) + factor(education_state),
-  #  fixed = ncigs_new~scale(age) + scale(nutrition_quality) + scale(hh_income) + scale(SF_12),
+  #  fixed = ncigs_new~scale(age) + scale(nutrition_quality) + scale(hh_income) + scale(SF_12_MCS),
   #  random = ~ 1|pidp,MZIP : ncars ~ scale(ncars) + scale(age) + I(scale(age)**2) + factor(region) +  scale(hh_income) + scale(age) + factor(S7_labour_state) | scale(ncars) + scale(hh_income) + factor(region) + scale(age)
   
   #  #weights=weight,
   #  data = data,
   #  family = zi.poisson(), 
-  #  zi_fixed = ~ scale(age) + scale(SF_12))
+  #  zi_fixed = ~ scale(age) + scale(SF_12_MCS))
   
   #browser()
   #test.data <- drop_na(data)

### 2024-10-09 minos/outcomes/ChildPovReduction_plots.Rmd

--- 2024-06-18 minos/outcomes/ChildPovReduction_plots.Rmd
@@
 
-synthpop_uncertainty <- function(summary_group, scen, var) {
-  # summary_group <- 'whole_pop'
-  # scen.list <- 'baseline'  # , 'ChildPovertyReductionRELATIVE_2'
+SF12_change_income_quint <- function(summary_group, scen.list) {
+
+  tit <- ' '
+  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
+  if (summary_group == 'families') { tit <- 'Families' }
+
+  summary_group <- paste0(summary_group, '_income_quint')
 
@@
 
-  #data$pop_sample <- mutate(data, pop_sample = ceiling(run_id / 10))
+  plot_data <- data %>%
+    select(run_id, income_quintile, SF_12, mean_cost, year, scen) %>%
+    pivot_wider(names_from = scen,
+                values_from = c(SF_12, mean_cost),
+                names_sep = '.') %>%
+    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
+    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
+    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
+                 names_to = c(".value", "scen"),
+                 names_sep = "\\.") %>%
+    filter(scen != 'baseline') %>%
+    select(-scen)
 
-  data <- data %>%
-    select(run_id, .data[[var]], mean_cost, year, scen) %>%
-    mutate(pop_sample = ceiling(run_id / 10))
+  plot_data$income_quintile <- factor(plot_data$income_quintile)
 
-  plot_data_local <- data %>%
-    group_by(pop_sample, year) %>%
-    summarise(var_mean = mean(.data[[var]]))
+  plot_data_confint <- plot_data %>%
+    group_by(year, income_quintile) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(diff_SF_12),
+              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
+              lower = mean_SF12_change - margin,
+              upper = mean_SF12_change + margin)
 
-  plot_data_global <- data %>%
-    group_by(year) %>%
-    summarise(global_var_mean = mean(.data[[var]]))
+  plot_data_confint2 <- plot_data %>%
+    group_by(year, income_quintile) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(diff_SF_12),
+              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
+              lower = mean_SF12_change - margin,
+              upper = mean_SF12_change + margin)
 
-  p1 <- ggplot(plot_data_local, aes(x = year, y = var_mean)) +
-    geom_line(aes(group = pop_sample), alpha = 0.4) +
-    geom_line(data = plot_data_global, aes(x = year, y = global_var_mean), color = 'red') +
-    labs(title = paste0(var, ' uncertainty in Synthetic Population Sample'),
-         subtitle = 'Global mean (red) vs local means (grey)') +
+  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted') +
+    geom_smooth() +
+    labs(title = tit, subtitle = 'Income Quintile') +
     xlab('Year') +
-    ylab(paste0('Mean ', var))
+    ylab('Change in SF-12')
+
+  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(linetype = 'dashed') +
+    geom_point() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = tit, subtitle = 'Income Quintile') +
+    xlab('Year') +
+    ylab('Change in SF-12')
+
+  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(linetype = 'dashed') +
+    geom_point() +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = tit, subtitle = 'Income Quintile') +
+    xlab('Year') +
+    ylab('Change in SF-12')
 
   print(p1)
+  print(p2)
 }
 
+```
+
+```{r}
+SF12_change_income_quint2 <- function(summary_group, scen) {
+
+  summary_group <- paste0(summary_group, '_income_quint_together')
+  scen <- paste0(scen, '_together')
+
+  data <- do.call(rbind, generate_df_list(summary_group, scen))
+
+  plot_data <- data %>%
+    select(run_id, SF_12, income_quintile, year, scenario) %>%
+    pivot_wider(names_from = scenario,
+                values_from = SF_12,
+                names_sep = '.') %>%
+    mutate(diff_SF12 = intervention - baseline) %>%
+    pivot_longer(cols = starts_with("diff"),
+                 names_to = c(".value", "scenario"),
+                 names_sep = "\\.") %>%
+    select(run_id, income_quintile, year, diff_SF12)
+
+  plot_data_confint <- plot_data %>%
+      group_by(year, income_quintile) %>%
+      summarise(n = n(),
+                mean_SF12_change = mean(diff_SF12),
+                margin_SF12 = qt(0.975, df = n - 1) * (sd(diff_SF12) / sqrt(n)),
+                lower_SF12 = mean_SF12_change - margin_SF12,
+                upper_SF12 = mean_SF12_change + margin_SF12)
+
+  plot_data_confint$income_quintile <- factor(plot_data_confint$income_quintile)
+
+  # p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
+  #     geom_hline(yintercept = 0, linetype = 'dashed') +
+  #     geom_vline(xintercept = 2030, linetype = 'dotted') +
+  #     geom_smooth() +
+  #     labs(title = 'Treatment on the Treated',
+  #          subtitle = 'SF_12') +
+  #     xlab('Year') +
+  #     ylab('Change in mean SF-12')
+
+  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, color = income_quintile, fill = income_quintile)) +
+      geom_ribbon(aes(ymin = lower_SF12, ymax = upper_SF12), linetype = 'dotted', alpha = 0.3) +
+      geom_line(linetype = 'dashed') +
+      geom_point() +
+      geom_hline(yintercept = 0, linetype = 'dashed') +
+      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+      labs(title = 'Treatment on the Treated',
+           subtitle = 'SF_12') +
+      xlab('Year') +
+      ylab('Change in mean SF-12')
+
+  #print(p1)
+  print(p2)
+}
 ```

### 2024-10-11 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
V small changes to CPR plotting script;

--- 2024-09-23 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
@@
 # 
+# 359328 * 12.74601
 # 
-# 109338 * 12.74601
+# #2030	-1800.26	
+# 
+# print('RESULT 1:')
+# 1800.26 * 12.74601
+# 
+# 
+# 109338 / 1262147 * 100
+# 
+# 100 / 86.62906
+# 
+# 
+# 
+# 109338 * 11.5437
+# 
+# # 2030	-590.55		
+# 
+# print('RESULT 2:')
+# 590.55 * 11.5437
 

### 2024-10-15 minos/validation/handovers.Rmd
Adding Hughs poverty variable generation in generate_composite_vars, and the child material deprivation module and some additions to get that up and running. Also started the child material deprivation intervention class

--- 2024-10-03 minos/validation/handovers.Rmd
@@
 
-density_plot_quintile(base.dat, int.dat, quintile = 1)
-density_plot_quintile(base.dat, int.dat, quintile = 2)
-density_plot_quintile(base.dat, int.dat, quintile = 3)
-density_plot_quintile(base.dat, int.dat, quintile = 4)
-density_plot_quintile(base.dat, int.dat, quintile = 5)
+# density_plot_quintile(base.dat, int.dat, quintile = 1)
+# density_plot_quintile(base.dat, int.dat, quintile = 2)
+# density_plot_quintile(base.dat, int.dat, quintile = 3)
+# density_plot_quintile(base.dat, int.dat, quintile = 4)
+# density_plot_quintile(base.dat, int.dat, quintile = 5)
 ```
@@
 
-mean_income_quintile(base.dat, int.dat)
+#mean_income_quintile(base.dat, int.dat)
 ```
@@
 
-base <- base.dat %>%
-  group_by(time, income_quint) %>%
-  summarise(min = min(hh_income),
-            max = max(hh_income)) %>%
-  mutate(source = 'Baseline')
-int <- int.dat %>%
-  group_by(time, income_quint) %>%
-  summarise(min = min(hh_income),
-            max = max(hh_income)) %>%
-  mutate(source = 'Intervention')
-
-combined <- rbind(base, int)
-combined$income_quint <- factor(combined$income_quint)
-
-quintile_threshold_plot <- function(data, year) {
-  ggplot(filter(data, time == year), 
-         aes(x = income_quint, y = min,
-             ymin = min, lower = min, ymax = max, upper = max,
-             group = source, 
-             colour = source, 
-             fill = source)) +
-    geom_crossbar(position = position_dodge()) +
-    labs(title = 'Quintile Thresholds',
-         subtitle = year)
-}
-
-quintile_threshold_plot(combined, year = 2020)
-quintile_threshold_plot(combined, year = 2021)
-quintile_threshold_plot(combined, year = 2025)
-quintile_threshold_plot(combined, year = 2030)
-quintile_threshold_plot(combined, year = 2035)
+# base <- base.dat %>%
+#   group_by(time, income_quint) %>%
+#   summarise(min = min(hh_income),
+#             max = max(hh_income)) %>%
+#   mutate(source = 'Baseline')
+# int <- int.dat %>%
+#   group_by(time, income_quint) %>%
+#   summarise(min = min(hh_income),
+#             max = max(hh_income)) %>%
+#   mutate(source = 'Intervention')
+# 
+# combined <- rbind(base, int)
+# combined$income_quint <- factor(combined$income_quint)
+# 
+# quintile_threshold_plot <- function(data, year) {
+#   ggplot(filter(data, time == year), 
+#          aes(x = income_quint, y = min,
+#              ymin = min, lower = min, ymax = max, upper = max,
+#              group = source, 
+#              colour = source, 
+#              fill = source)) +
+#     geom_crossbar(position = position_dodge()) +
+#     labs(title = 'Quintile Thresholds',
+#          subtitle = year)
+# }
+# 
+# quintile_threshold_plot(combined, year = 2020)
+# quintile_threshold_plot(combined, year = 2021)
+# quintile_threshold_plot(combined, year = 2025)
+# quintile_threshold_plot(combined, year = 2030)
+# quintile_threshold_plot(combined, year = 2035)
 ```
@@
 ```{r}
-raw.sf12 <- raw.dat %>%
-  select(pidp, age, time, SF_12, SF_12_diff)
-base.sf12 <- base.dat %>%
-  select(pidp, age, time, SF_12, SF_12_diff)
-
-sf12.spag <- rbind(raw.sf12, base.sf12)
-
-sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(sf12.spag.sample, 'SF_12',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
-               save = shall.we.save,
-               save.path = save.path)
-
-spaghetti_plot(sf12.spag.sample, 'SF_12_diff',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_diff',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(sf12.spag, "SF_12", 
-               save = T, 
-               save.path = save.path)
-
-rm(raw.sf12, base.sf12, sf12.spag)
+# raw.sf12 <- raw.dat %>%
+#   select(pidp, age, time, SF_12, SF_12_diff)
+# base.sf12 <- base.dat %>%
+#   select(pidp, age, time, SF_12, SF_12_diff)
+# 
+# sf12.spag <- rbind(raw.sf12, base.sf12)
+# 
+# sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
+# spaghetti_plot(sf12.spag.sample, 'SF_12',
+#                save = shall.we.save,
+#                save.path = save.path)
+# spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# spaghetti_plot(sf12.spag.sample, 'SF_12_diff',
+#                save = shall.we.save,
+#                save.path = save.path)
+# spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_diff',
+#                save = shall.we.save,
+#                save.path = save.path)
+#   
+# density_ridges(sf12.spag, "SF_12", 
+#                save = T, 
+#                save.path = save.path)
+# 
+# rm(raw.sf12, base.sf12, sf12.spag)
 ```
@@
 ```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, nkids)
-base.s <- base.dat %>%
-  select(pidp, age, time, nkids)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, nkids)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, nkids)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'nkids',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-raw.s <- raw.parity %>%
-  select(pidp, age, time, nkids_ind)
-base.s <- base.parity %>%
-  select(pidp, age, time, nkids_ind)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'nkids_ind',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# raw.s <- raw.parity %>%
+#   select(pidp, age, time, nkids_ind)
+# base.s <- base.parity %>%
+#   select(pidp, age, time, nkids_ind)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'nkids_ind',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
+```
+
+## CHILD POVERTY VARS
+
+### Relative poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Relative Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'relative_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+### Absolute Poverty
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Absolute Poverty'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'absolute_poverty.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+### Persistent Poverty
+
+```{r}
+# prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')
+# 
+# var <- prepped.list$var
+# norm <- prepped.list$norm
+# 
+# tit <- 'Persistent Poverty'
+# 
+# # Now plot
+# ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
+#   geom_line() +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = tit, subtitle = 'Counts by Level') +
+#   xlab('Year') +
+#   ylab('Count')
+# 
+# ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
+#   geom_bar(stat = 'identity') +
+#   geom_vline(xintercept=start.year, linetype='dotted') +
+#   labs(title = tit) +
+#   xlab('Year') +
+#   ylab('Proportion')
+# 
+# if (shall.we.save) {
+#   ggsave(filename = 'persistent_poverty.png',
+#          plot = last_plot(),
+#          path = save.path)
+# }
+# 
+# 
+# rm(prepped.list, var, norm, tit)
+
+```
+
+### Low Income and Material Deprivation
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Material Deprivation Child'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'low_income_matdep_child.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+
 ```
@@
 ```{r}
-handover_boxplots(raw.dat, base.dat, 'hourly_wage')
-handover_lineplots(raw.dat, base.dat, 'hourly_wage')
-```
-
-```{r}
-raw.s <- raw.dat %>%
-  select(pidp, age, time, hourly_wage)
-base.s <- base.dat %>%
-  select(pidp, age, time, hourly_wage)
-
-spag <- rbind(raw.s, base.s)
-
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-# now a version limited to 0-100
-spag <- spag %>%
-  filter(hourly_wage <= 300)
-spaghetti_plot(spag, 'hourly_wage',
-               save = shall.we.save,
-               save.path = save.path)
-
-rm(raw.s, base.s, spag)
+# handover_boxplots(raw.dat, base.dat, 'hourly_wage')
+# handover_lineplots(raw.dat, base.dat, 'hourly_wage')
+```
+
+```{r}
+# raw.s <- raw.dat %>%
+#   select(pidp, age, time, hourly_wage)
+# base.s <- base.dat %>%
+#   select(pidp, age, time, hourly_wage)
+# 
+# spag <- rbind(raw.s, base.s)
+# 
+# spaghetti_plot(spag, 'hourly_wage',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# # now a version limited to 0-100
+# spag <- spag %>%
+#   filter(hourly_wage <= 300)
+# spaghetti_plot(spag, 'hourly_wage',
+#                save = shall.we.save,
+#                save.path = save.path)
+# 
+# rm(raw.s, base.s, spag)
 ```

### 2024-10-15 minos/data_generation/US_missing_LOCF.py

@@ -263,6 +263,9 @@ def main(data, save=False):
     f_columns = ['education_state', 'labour_state_raw', 'job_sec', 'heating', 'ethnicity', 'sex', 'birth_year',
                  'yearly_gas', 'yearly_electric', 'yearly_gas_electric', 'yearly_oil', 'yearly_other_fuel', 'smoker',
                  'nkids_ind_raw',  # 'ncigs', 'ndrinks']
+                 'matdep1', 'matdep2', 'matdep3', 'matdep4', 'matdep5', 'matdep6', 'matdep7', 'matdep8', 'matdep9',
+                 'matdep10', 'matdep11', 'matdep12', 'matdep13', 'matdep14', 'matdep15', 'matdep16', 'matdep17',
+                 'matdep18', 'matdep19', 'matdep21',
                  'loneliness',
                  'burglaries', 'car_crime', 'drunks', 'muggings', 'racial_abuse', 'teenagers', 'vandalism',  # nh_safety
                  'fruit_days', 'fruit_per_day', 'veg_days', 'veg_per_day']

### 2024-10-15 minos/minosPipeline/RunPipeline.py

@@ -39,6 +39,7 @@ from minos.modules.S7EquivalentIncome import S7EquivalentIncome
 from minos.modules.heating import Heating
 from minos.modules.financial_situation import FinancialSituation
 from minos.modules.behind_on_bills import BehindOnBills
+from minos.modules.material_deprivation import MaterialDeprivationChild
 
 from minos.modules.child_poverty_interventions import hhIncomeIntervention
 from minos.modules.child_poverty_interventions import hhIncomeChildUplift
@@ -113,6 +114,7 @@ components_map = {
     "JobHours()": JobHours(),
     "JobSec()": JobSec(),
     "HourlyWage()": HourlyWage(),
+    "MaterialDeprivationChild()": MaterialDeprivationChild(),
 }
 
 SIPHER7_components_map = {  # SIPHER7 stuff

### 2024-10-15 minos/modules/material_deprivation.py

@@ -1,0 +1,120 @@
+"""Module for estimating change in child material deprivation variable derived from 21 US variables"""
+
+
+import pandas as pd
+from pathlib import Path
+from minos.modules import r_utils
+from minos.modules.base_module import Base
+import logging
+from datetime import datetime as dt
+
+class MaterialDeprivationChild(Base):
+    @property
+    def name(self):
+        return "material_deprivation_child"
+
+    def __repr__(self):
+        return "MaterialDeprivationChild()"
+
+    def setup(self, builder):
+        """ Initialise the module during simulation.setup().
+
+        Notes
+        -----
+        - Load in data from pre_setup
+        - Register any value producers/modifiers for death rate
+        - Add required columns to population data frame
+        - Add listener event to check if people die on each time step.
+        - Update other required items such as randomness stream.
+
+        Parameter
+        ----------
+        builder : vivarium.engine.Builder
+            Vivarium's control object. Stores all simulation metadata and allows modules to use it.
+
+        """
+
+        # Load in inputs from pre-setup.
+        self.rpy2_modules = builder.data.load("rpy2_modules")
+
+        # Build vivarium objects for calculating transition probabilities.
+        # Typically this is registering rate/lookup tables. See vivarium docs/other modules for examples.
+
+        # Assign randomness streams if necessary. Only useful if seeding counterfactuals.
+        #self.random = builder.randomness.get_stream(self.generate_random_crn_key())
+        self.random = builder.randomness.get_stream(self.generate_run_crn_key())
+
+
+        # Determine which subset of the main population is used in this module.
+        # columns_created is the columns created by this module.
+        # view_columns is the columns from the main population used in this module. essentially what is needed for
+        # transition models and any outputs.
+        ''' HR 14/12/23 From Luke's suggestion for model '''
+        view_columns = ['matdep_child',
+                        'hh_income',
+                        'hhsize',
+                        'ethnicity',
+                        'region',
+                        'education_state',
+                        'nkids_ind',
+                        'financial_situation',
+                        'marital_status',
+                        ]
+        self.population_view = builder.population.get_view(columns=view_columns)
+
+        # Population initialiser. When new individuals are added to the microsimulation a constructer is called for each
+        # module. Declare what constructer is used. usually on_initialize_simulants method is called. Inidividuals are
+        # created at the start of a model "setup" or after some deterministic (add cohorts) or random (births) event.
[…]

### 2024-10-15 minos/outcomes/MHF_SCP_visualisations.Rmd
Quickly adding a summary function for UC and children population. Also added to the MHF_SCP_visualisations.Rmd script to add some calculations for the total eligible sample, as well as scaling the mental health risk results to a total E&W sample

@@
 ```{r "mental_illness_risk_plots", include=FALSE}
-mental_illness_risk_plots <- function(summary_group, scen.list, palette = my_palette) {
+mental_illness_risk_plots <- function(summary_group, scen.list, palette = my_palette, scale = scaling_factor) {
 
@@
 
+# Sample Size Calculations
+
+```{r}
+# E&W adults: 48,566,000
+# N: 160,908; 211,034
+# N total: 371,942
+
+# so we have
+scaling_factor <- (371942 / 48566000) * 100
+scaling_factor
+```
+
 # Whole Population
@@
 ```{r}
+summary_group <- 'men_illness_risk'
+scen.list = scen.list.25_100
+
+tit <- ' '
+  if (summary_group == 'UC_men_illness_risk') { tit <- 'UC Population' }
+  if (summary_group == 'UC_families_men_illness_risk') { tit <- 'UC Families' }
+  if (summary_group == 'men_illness_risk') { tit <- 'Whole Population' }
+  if (summary_group == 'men_illness_risk_families') { tit <- 'Families' }
+
+  # scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
+  # summary_group <- 'men_illness_risk'
+
+  #scen.list <- c('baseline', comparison_scen)
+  data <- do.call(rbind, generate_df_list(summary_group, scen.list))
+
+  data <- data %>%
+    mutate_at("scen", str_replace, "UniversalCredit", "") %>%
+    mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))
+
+  plot_data1 <- data %>%
+    filter(mental_health_risk == 'TRUE') %>%
+    select(-prop, -mental_health_risk) %>%
+    pivot_wider(names_from = scen,
+                values_from = count) %>%
+    mutate(across(starts_with("£"), ~ . - baseline, .names = "diff_{.col}")) %>%
+    select(run_id, year, starts_with('diff')) %>%
+    pivot_longer(cols = starts_with("diff"),
+                 names_sep = '_',
+                 names_to = c("diff", "scen"),
+                 values_to = 'Count')
+
+  # Extract numeric part from 'scen' column then...
+  scen_numeric <- as.numeric(gsub("[^0-9]", "", plot_data1$scen))
+  # ...Reorder 'scen' column based on numeric values for plotting
+  plot_data1$scen <- factor(plot_data1$scen, levels = unique(plot_data1$scen[order(scen_numeric)]))
+
+  plot_data1_confint <- plot_data1 %>%
+    group_by(year, scen) %>%
+    summarise(n = n(),
+              Mean_Count = mean(Count),
+              margin = qt(0.975, df = n - 1) * (sd(Count) / sqrt(n)),
+              lower = Mean_Count - margin,
+              upper = Mean_Count + margin)
+
+  p1 <- ggplot(plot_data1_confint, aes(x = year, y = Mean_Count, group = scen)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
+    geom_line(aes(color = scen), linetype = 'dashed') +
+    geom_point(aes(color = scen)) +
+    scale_color_manual(values = palette) +
+    scale_fill_manual(values = palette) +
+    xlab('Year') +
+    ylab('Mean Change') +
+    theme(
+        legend.title = element_blank(),  # Remove the legend title
+        legend.position = c(0.2, 0.7),  # Position the legend inside the plot
+        legend.text = element_text(size = 8),  # Increase the text size for better readability
+        legend.key.size = unit(0.8, 'cm'),  # Reduce the key size to fit more entries
+        legend.spacing.y = unit(0.1, 'cm')  # Add vertical space between legend items
+    ) +
+    guides(
+        color = guide_legend(
+            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        ),
+        fill = guide_legend(
+            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        )
+    )
+
+    plot_data_2 <- data %>%
+      filter(mental_health_risk == 'TRUE') %>%
+      select(-mental_health_risk, -count) %>%
+      pivot_wider(names_from = scen,
+                  values_from = prop) %>%
+      mutate(across(starts_with("£"), ~ . - baseline, .names = "diff_{.col}")) %>%
+      select(run_id, year, starts_with('diff')) %>%
+      pivot_longer(cols = starts_with("diff"),
+                   names_sep = '_',
+                   names_to = c("diff", "scen"),
+                   values_to = 'Proportion')
+
+    plot_data2_confint <- plot_data_2 %>%
+      mutate(Proportion = Proportion * 100) %>%
+      group_by(year, scen) %>%
+      summarise(n = n(),
+              Mean_Proportion = mean(Proportion),
+              margin = qt(0.975, df = n - 1) * (sd(Proportion) / sqrt(n)),
+              lower = Mean_Proportion - margin,
+              upper = Mean_Proportion + margin)
+
+    p2 <- ggplot(plot_data2_confint, aes(x = year, y = Mean_Proportion, group = scen)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
+    geom_line(aes(color = scen), linetype = 'dashed') +
+    geom_point(aes(color = scen)) +
+    scale_color_manual(values = palette) +
+    scale_fill_manual(values = palette) +
+    xlab('Year') +
+    ylab('Mean Change (%)') +
+    theme(
+        legend.title = element_blank(),  # Remove the legend title
+        legend.position = c(0.2, 0.7),  # Position the legend inside the plot
+        legend.text = element_text(size = 8),  # Increase the text size for better readability
+        legend.key.size = unit(0.8, 'cm'),  # Reduce the key size to fit more entries
+        legend.spacing.y = unit(0.1, 'cm')  # Add vertical space between legend items
+    ) +
+    guides(
+        color = guide_legend(
+            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        ),
+        fill = guide_legend(
+            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
+        )
+    )
+
+  print(p1)
+  print(p2)
+```
+
+```{r}
 mental_illness_risk_plots('men_illness_risk', scen.list = scen.list.25_100)

### 2024-10-17 minos/validation/handovers.Rmd

@@
 
-tit <- 'Material Deprivation Child'
+tit <- 'Low Income & Material Deprivation Child'
 
@@
 
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, low_income_matdep_child)
+base.s <- base.dat %>%
+  select(pidp, age, time, low_income_matdep_child)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'low_income_matdep_child',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
+```
+
+### Child Material Deprivation
+
+```{r}
+prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'matdep_child')
+
+var <- prepped.list$var
+norm <- prepped.list$norm
+
+tit <- 'Material Deprivation Child'
+
+# Now plot
+ggplot(data = var, mapping = aes(x = time, y = n, group = matdep_child, colour = matdep_child)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit, subtitle = 'Counts by Level') +
+  xlab('Year') +
+  ylab('Count')
+
+ggplot(data = norm, mapping = aes(x = time, y = prct, fill=matdep_child)) +
+  geom_bar(stat = 'identity') +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = tit) +
+  xlab('Year') +
+  ylab('Proportion')
+
+if (shall.we.save) {
+  ggsave(filename = 'matdep_child.png',
+         plot = last_plot(),
+         path = save.path)
+}
+
+rm(prepped.list, var, norm, tit)
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, matdep_child)
+base.s <- base.dat %>%
+  select(pidp, age, time, matdep_child)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'matdep_child',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```

### 2024-10-18 minos/transitions/summarise_transitions_2.Rmd
switching to faster ncigs and ncars models and validating..

---
title: "MINOS Transition Models"
output: html_notebook
---

# Setup

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(ordinal)
require(nnet)
require(pscl)

workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

```{r "paths", include=FALSE}
trans.path <- 'data/transitions/'
```

```{r "data", include=FALSE}
dataDir <- 'data/final_US/'

# Load input data
filelist <- list.files(dataDir, 
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = '[0-9]{4}_US_cohort.csv')
#filelist <- paste0(dataDir, filelist)
data <- do.call(rbind, lapply(filelist, read.csv))
```

## Read Models
```{r "models"}

#testing.hh_income <- readRDS(paste0(trans.path, 'test/', 'hh_income/ols/hh_income_2018_2019.rds'))

# Transitions models
#hh_income <- readRDS(paste0(trans.path, 'hh_income/ols/hh_income_2018_2019.rds'))
#housing <- readRDS(paste0(trans.path, 'housing_quality/clm/housing_quality_2018_2019.rds'))
loneliness <- readRDS(paste0(trans.path, 'loneliness/clm/loneliness_2018_2019.rds'))
#mwb <- readRDS(paste0(trans.path, 'SF_12_MCS/ols/SF_12_MCS_2018_2019.rds'))
#mwb2 <- readRDS(paste0(trans.path, 'SF_12_MCS/ols/SF_12_MCS_2017_2018.rds'))
#mwb3 <- readRDS(paste0(trans.path, 'SF_12_MCS/ols/SF_12_MCS_2014_2015.rds'))
#pcs <- readRDS(paste0(trans.path, 'SF_12_PCS/ols/SF_12_PCS_2017_2018.rds'))
#neighbourhood <- readRDS(paste0(trans.path, 'neighbourhood_safety/clm/neighbourhood_safety_2017_2020.rds'))
#nutrition <- readRDS(paste0(trans.path, 'nutrition_quality/ols/nutrition_quality_2018_2019.rds'))
#tobacco <- readRDS(paste0(trans.path, 'ncigs/zip/ncigs_2018_2019.rds'))

# Education
#education <- readRDS(paste0(trans.path, '../education/nnet/educ_nnet_2018_2019.rds'))
#education <- readRDS(paste0(trans.path, 'education_state/nnet/education_state_2018_2019.rds'))
```

## Predictor Variables

### Job Sec

This is the job NSSEC codes for those in employment:

1. Large employers and higher management
2. Higher professional
3. Lower management and professional
4. Intermediate
5. Small employers and own account
6. Lower supervisory and technical
7. Semi-routine
8. Routine

Where included in a transitions model, the reference level for job sec is 3. Lower management and professional. This is the most common NSSEC and also conceptually relatively easy to compare. See [jbnssec8_dv](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/jbnssec8_dv) for more information.

At present, Job Sec is NOT transitioned through the model and instead held constant. This will change in the near future.

### Job Sector

This variable holds information on whether a respondent is employed in the public or private sector (more specifically private vs non-private - see [jbsect](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/jbsect)).

Values are:
1. Private firm or business, a limited company
2. Other type of organisation

The reference value chosen was 1. private firm or business, because this was the most common value of the two.

At present, Job Sector is NOT transitioned through the model and instead held constant. This will change in the near future.

### Household Composition

`hh_comp` refers to household composition (number of adults, children etc.) and is derived from a US variable - [hhtype_dv](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/hhtype_dv).

We have collapsed the ~18 level `hhtype_dv` variable into 4 levels:
1. Single adult no kids
2. Single adult 1+ kids
3. Multiple adults no kids
4. Multiple adults 1+ kids

At present, Household Composition is NOT transitioned through the model and instead held constant. This will change in the near future.

### Marital Status

Marital status is derived from a US variable - [mastat_dv](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/mastat_dv).

### Physical Health

`phealth` is a proxy variable for physical health. It is continuous score derived from SF-12 questions that focus on physical health (care was taken to not include anything that could be related directly to mental wellbeing). Variables included are:
- [Physical health limits moderate activities](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/scsf2a)
- [Physical health limits several flights of stairs](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/scsf2b)
- [Physical health limits amount of work](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/scsf3a)
- [Physical health limits kind of work](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/scsf3b)
- [Pain interfered with work](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/scsf5)

Each of these questions is answered from 1-3 or 1-5 with levels such as 'None of the time' or 'Some of the time'. We summed the responses to these questions, and divided them by the number of questions answered to get a summary score from 1-5.

NOTE: `phealth` is currently only used in the predictive model for SF_12_MCS, and is planned to be replaced with a proxy based on the General Health Questionnaire (GHQ) to avoid any crossover with SF_12 Physical Component Score. At the same time, an `mhealth` proxy will be derived from the GHQ also to be part of the SF_12_PCS predictive model.

# Analysis

## Household Income

Household income is calculated as:

> hh_income = (net_monthly_income - monthly_outgoings) / oecd_equivalence__factor_scale

- [net_monthly_income](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/fihhmnnet1_dv)
- monthly_outgoings is the sum of [rent](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/rentgrs_dv), [mortgage](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/xpmg_dv), and [council tax](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/ficountax_dv).
- [oecd_equivalence_scale](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/ieqmoecd_dv)

```{r "income_plot", echo=FALSE}
income.dat <- data %>% 
  group_by(hh_income)
income.plot <- ggplot(income.dat, aes(x = hh_income)) +
  geom_histogram()
income.plot.core <- ggplot(filter(income.dat, hh_income > -2000, hh_income < 10000), aes(x = hh_income)) +
  geom_histogram()
```

```{r}
income.plot # Income has huge spread (-£88k to £330k) so hard to see without limiting
income.plot.core # Limited from -£2000 to £10000 (vast majority of records lie in this range)
```

In MINOS, `hh_income` is estimated with an Ordinary Least Squares (OLS) regression model with the following formula:

> hh_income ~ age + hh_income + sex + ethnicity + region + education_state + job_sec + job_sector

```{r}
summary(hh_income)
```
```{r}
anova(hh_income, test = 'Chisq')
```

## Housing

Our definition of housing quality is taken straight from the calculations of SIPHER 7 domains:

From SIPHER 7, housing quality depends on:
> Your home is in a reasonable state of repair, has reasonable facilities (cooking/washing) and provides reasonable warmth

6 variables from Understanding Society were chosen to collectively represent housing quality:
- [fridge freezer](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/cduse5)
- [washing machine](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/cduse6)
- [tumble dryer](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/cduse7)
- [dishwasher](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/cduse8)
- [microwave](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/cduse9)
- [adequate heating](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/hheat)

These variables are then categorised into a 'core' set and a 'bonus' set.

Core:

- Fridge Freezer
- Washing Machine
- Adequate Heating

Bonus:

- Tumble Dryer
- Dishwasher
- Microwave

A 3 level composite variable is then created based on the presence of core and bonus variables:

1. Missing 1+ core variables
2. All core variables present and some bonus
3. All core and all bonus variables present

```{r "housing_plot", echo=FALSE}
housing.dat <- data %>% 
  group_by(housing_quality) %>%
  summarise(counts = n())
house.plot <- ggplot(housing.dat, aes(x = housing_quality, y = counts)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) +
  xlab('Housing Quality') +
  ylab('Frequency')

#print(house.plot)
```

```{r}
house.plot
```

We estimate a Cumulative Link Model (CLM) using this formula:

> housing_quality ~ age + sex + SF_12 + ethnicity + hh_income

```{r}
summary(housing)
```
### Significance
```{r}
anova(housing)
#drop1(housing, test = 'Chisq')
```

## Loneliness

A score for loneliness is taken directly from a US variable - [sclonely](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/sclonely). The questions used to output levels of loneliness in Understanding Society come from the Government Statistical Service (GSS) harmonised principle of loneliness. This means the outputs are comparable with other surveys that use this principle. The GSS has a [guidance page](https://analysisfunction.civilservice.gov.uk/policy-store/loneliness-indicators/) which may be useful to understand what other data can and cannot be compared with this output.
The `sclonely` variable is only available in waves 9,10,11 (and now 12), and is an ordinal variable with 3 levels:
1 - Hardly ever or never
2 - Some of the time
3 - Often

To predict loneliness, we estimate a CLM model with the formula:

> loneliness ~ age + sex + SF_12 + education_state + job_sec + hh_income + hh_comp + marital_status + ethnicity

See above for details on [job_sec](#Job-Sec), [hh_comp](#Household-Composition), and [marital_status](#Marital-Status).

```{r}
summary(loneliness)
```

### Significance
```{r}
anova(loneliness)
```

### Modifications and Justification

Loneliness has been [linked with educational attainment](https://www.tandfonline.com/doi/full/10.1080/03601270701569275?casa_token=3vV_r99mb0QAAAAA%3ACK8Wogj5cs5CQm8gZfLKuHJtctkCyGX_i2y4CLyDgAhsReGB1s7QrV1I0qul-6Gw75QBcY93WoWuWA). Higher educational attainment has been linked with lower levels of stress and neuroticism, of which both have been linked with loneliness (more neuroticism/stress linked to more loneliness).

Loneliness has been [linked with ethnicity](https://bmcpublichealth.biomedcentral.com/articles/10.1186/s12889-020-09208-0).
> The association between ethnicity and loneliness was stronger among young and early middle-aged adults, compared to late middle-aged adults.

## Mental Wellbeing

The current main outcome of interest is the mental wellbeing of a respondent, measured by SF-12 MCS summary scores and taken directly from a US variable ([sf12mcs](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/sf12mcs_dv)).

```{r "SF12_MCS_plot", echo=FALSE}
sf12.m.dat <- data %>% 
  group_by(SF_12_MCS) %>%
  filter(SF_12_MCS > 0)
sf12.m.plot <- ggplot(sf12.m.dat, aes(x = SF_12_MCS)) +
  geom_histogram()
```

```{r}
sf12.m.plot
```

We use an OLS regression model with the formula:

> SF_12_MCS ~ age + sex + ethnicity + hh_income + housing_quality + phealth + neighbourhood_safety + ncigs + loneliness + nutrition_quality + SF_12_MCS

See other sections for information on [phealth](#Physical-Health), [neighbourhood_safety](#Neighbourhood-Safety), [loneliness](#Loneliness), and [nutrition_quality](#Nutrition-Quality)

```{r}
print('2017-2018')
summary(mwb2)
```

Reference factors:
- Gender :            Female
- Ethnicity :         Bangladesh
- Education_state :   0 (none of the above - no qualification?)
- Labour_state :      Employed
- Housing_quality :   1 (None of the indicators of good housing quality - tumble dryer, sufficient heating, fridge freezer, microwave, washing machine)

## Physical Wellbeing

A relatively new addition to the model is the physical wellbeing module, based on the SF_12 Physical Component Score (PCS). SF_12_PCS scores are taken directly from the US variable ([sf12pcs]https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/sf12pcs_dv).

The current main outcome of interest is the mental wellbeing of a respondent, measured by SF-12 MCS summary scores and taken directly from a US variable ([sf12mcs](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/sf12mcs_dv)).

```{r "SF12_PCS_plot", echo=FALSE}
sf12.p.dat <- data %>% 
  group_by(SF_12_PCS) %>%
  filter(SF_12_PCS > 0)
sf12.p.plot <- ggplot(sf12.p.dat, aes(x = SF_12_PCS)) +
  geom_histogram()
```

```{r}
sf12.p.plot
```

We use an OLS regression model with the formula:

> SF_12_PCS ~ age + sex + ethnicity + hh_income + housing_quality + neighbourhood_safety + ncigs + loneliness + nutrition_quality + SF_12_PCS

See other sections for information on [neighbourhood_safety](#Neighbourhood-Safety), [loneliness](#Loneliness), and [nutrition_quality](#Nutrition-Quality)

```{r}
print('2017-2018')
summary(pcs)
```

## Neighbourhood Safety

Neighbourhood Safety is a composite derived from 7 questions related to different facets of safety in the neighbourhood.

They are:
- burglaries
- car crime
- drunks
- muggings
- racial abuse
- teenager issues
- vandalism issues

Each respondent is asked if they are concerned with these issues in their neighbourhood, and response with 1 of:
> 1) Hardly ever / 2) some of the time / 3) often

We then assign people into three categories:
1. Response to all crime questions is “not at all common” (very safe neighbourhood). Justification is that if you
    perceive no threat at all this is the best possible state.
2. Responds to 1+ question as “not very common” but no responses to ‘fairly or very common’ (safe neighbourhood).
    Justification is that on the whole these people probably feel safe but not all is perfect, so probably not
    quite as desirable as group 1.
3. Responds to 1+ question as fairly or very common’ (not safe). Justification is that if perception of crime is
    very or fairly common, no matter what category, you are likely to feel that your neighbourhood safety is
    compromised.

The distribution of this variable is shown below:
```{r "neighbourhood_plot", echo=FALSE}
neigh.dat <- data %>% 
  group_by(neighbourhood_safety) %>%
  filter(neighbourhood_safety > 0) %>%
  summarise(counts = n())
neigh.plot <- ggplot(neigh.dat, aes(x = neighbourhood_safety, y = counts)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) +
  xlab('Neighbourhood Safety') +
  ylab('Frequency')

#print(house.plot)
```

```{r}
neigh.plot
```

We estimate a Cumulative Link Model (CLM) using this formula:

> neighbourhood_safety ~ age + sex + job_sec + ethnicity + hh_income + housing_quality + region

**neighbourhood safety is only estimated for 2011-2014 and 2014-2017 due to data issues (questions only asked every 3 waves)**

```{r}
summary(neighbourhood)
```

### Significance
```{r}
anova(neighbourhood)
```

## Nutrition

Nutrition was a tricky model, due to data issues (or lack of it). We generated a composite of nutrition quality based on the frequency and amount of fruit and vegetable consumption.

We generated a proxy variable using:

> nutrition_quality = (vegetable_freq * veg_per_day) + (fruit_freq * fruit_per_day)

Both [fruit](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/wkfruit) and [vegetable](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/wkvege) consumption frequency was measured in days per week, and reported as:
1 - Never
2 - 1-3 days
3 - 4-6 days
4 - every day

The amount of [fruit](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/fruitamt) and [veg](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/vegeamt) per day was a continuous variable, indicating the number of portions of fruit or veg eaten on an average day when the respondent eats fruit or veg.

The nutrition_quality composite variable is a continuous variable, where higher values indicate better quality nutrition.

```{r "nutrition_plot", echo=FALSE}
nut.dat <- data %>% 
  group_by(nutrition_quality) %>%
  filter(nutrition_quality >= 0)
nut.plot <- ggplot(nut.dat, aes(x = nutrition_quality)) +
  geom_histogram()
```

```{r}
nut.plot
```

We estimate an OLS model using this formula:

> nutrition_quality ~ age + sex + education_state + ethnicity + hh_income + ncigs

```{r}
summary(nutrition)
```

### Significance
```{r}
anova(nutrition)
```

## Tobacco

Tobacco consumption is measured in the usual number of cigarettes smoked per day, and is taken directly from a US variable ([ncigs](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/ncigs)).

```{r "ncigs_plots", echo=FALSE}
ncigs.dat <- data %>% 
  group_by(ncigs) %>%
  filter(ncigs >= 0)

ncigs.dat.smok <- ncigs.dat %>%
  filter(ncigs > 0)

ncigs.plot <- ggplot(ncigs.dat, aes(x = ncigs)) +
  geom_histogram()

ncigs.plot.smok <- ggplot(ncigs.dat.smok, aes(x = ncigs)) +
  geom_histogram()
```

```{r}
ncigs.plot
```

The vast majority of the population are non-smokers, but looking at the same plot with non-smokers removed:

```{r}
ncigs.plot.smok
```

To predict ncigs, we estimated a zero inflated poisson model with the formula:

> ncigs ~ age + sex + education_state + job_sec + ethnicity + hh_income + SF_12 | ethnicity + job_sec + hh_income + SF_12

ZIP : ncigs ~ age + factor(sex) + relevel(factor(education_state), ref = '3') + SF_12 + relevel(factor(job_sec), ref = '3') + hh_income + relevel(factor(ethnicity), ref = 'WBI') | relevel(factor(ethnicity), ref = 'WBI') + relevel(factor(job_sec), ref = '3') + hh_income + SF_12

The formula here is in two parts. The variables defined AFTER the pipe symbol ( | ) are used to predict if a respondent smokes, and the variables defined BEFORE the pipe symbol are used to predict the number of cigarettes smoked if required.

```{r}
summary(tobacco)
```
### Modifications and Justification

#### Ethnicity
Justification for using ethnicity to predict smoking: [Bhopal et al.](https://www.bmj.com/content/328/7431/76.short). 
This review found differences in cigarette consumption between many ethnic minority groups.

#### NS-SEC
Justification for job_sec (NSSEC) to predict smoking: [Hiscock et al. (2014)](https://academic.oup.com/jpubhealth/article/34/3/390/1560637?login=false).
Paper links socioeconomic status and smoking in England. NS-SEC was 1 of 7 measures of SES used to classify individuals (routine or manual occupation was +1 in an SES score from 0-7).

Also [Aspinall and Mitton (2014)](https://www.sciencedirect.com/science/article/pii/S0033350613004228)
 > There was a clear social class (NS-SEC) gradient in smoking prevalence for ‘White British’ and ‘Other White’ males and females ([Fig. 1](https://www.sciencedirect.com/science/article/pii/S0033350613004228#fig1)). There was also a gradient, less regular partly because of small numbers, in the ‘White and Black Caribbean’ and ‘White and Black African’ groups. This was much less perceptible in the ‘White and Asian’ group. In the Indian, Pakistani and Bangladeshi groups, the gradient was either much more muted or entirely absent. There was some evidence of a gradient in the black groups but a much stronger gradient in the Chinese group, commensurate with that seen in the White groups.

## Education

Estimating education is at present a bit of a special case. It is only applied in preparation of the replenishing population of 16 year olds, to predict the highest level of education they will achieve in the model. As such, only immutable variables can be used as predictors.

Education is categorised into 7 levels, where each level can include multiple qualifications at a similar level:

0 - None of the above (no qualification)
1 - Other school certification
2 - GCSE/O level
2 - Standard/O/lower
2 - CSE
3 - AS level
3 - A level
3 - International Baccalaureate
3 - Welsh Baccalaureate
3 - Scottish Highers
3 - Cert. 6th year studies
5 - Nursing/other med qua
5 - Diploma in HE
6 - Teaching qual not PGCE
6 - 1st degree or equivalent
7 - Higher degree
7 - Other higher degree

(Level 4 is not present in Understanding Society data).

```{r "educ_plot", echo=FALSE}
educ.dat <- data %>% 
  group_by(education_state) %>%
  summarise(counts = n())
educ.plot <- ggplot(educ.dat, aes(x = education_state, y = counts)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) +
  xlab('Education State') +
  ylab('Frequency')

#print(house.plot)
```

```{r}
educ.plot
```

We estimate future education state with a Multinomial Logistic Regression model, with the formula:

> education_state ~ sex + ethnicity + region

```{r}
coef(education)
```

# DEFUNKT

## Alcohol

**THIS MODEL AND ITS EFFECTS HAVE BEEN REMOVED FROM MINOS**
The links between alcohol and SF-12 are not as clear as previously imagined, and with the difficulty in fitting an alcohol model and the complexity it adds we have decided to remove it.

OLD MODEL DEFINITION STRING:
ZIP : alcohol_spending ~ age + factor(sex) + scale(SF_12) + relevel(factor(labour_state), ref = "Employed") + factor(job_sec) + relevel(factor(ethnicity), ref = "WBI") + scale(hh_income) | relevel(factor(ethnicity), ref = "WBI") + relevel(factor(labour_state), ref = "Employed") + age + scale(SF_12)

Alcohol consumption is measured by a respondents total household weekly spend on alcohol, from this US variable ([xpaltob_g3 ](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/xpaltob_g3)).

Alcohol spending is estimated using a zero inflated poisson model, with the formula:

> alcohol_spending ~ age + sex + SF_12 + labour_state + job_sec + ethnicity + hh_income | ethnicity + labour_state + age + SF_12

```{r}
alcohol <- readRDS(paste0(trans.path, 'alcohol_spending/alcohol_spending_2018_2019.rds'))
summary(alcohol)
```

## Labour

**THIS MODEL AND ITS EFFECTS HAVE BEEN REMOVED FROM THE MODEL**
Labour state is a very complicated subject with the information we have access to, and we decided that because it is not a pathway to SF-12 MCS as defined by SIPHER, we can safely ignore it and assume that the labour state dynamics will be captured in some way by hh_income model. If this is not satisfactory, we can come back to this module as its all still saved.

OLD MODEL DEFINITION STRING:
NNET : labour_state ~ age + factor(sex) + relevel(factor(ethnicity), ref = "WBI") + relevel(factor(education_state), ref = "3") + scale(SF_12) + factor(housing_quality) + relevel(factor(labour_state), ref = "Employed") + factor(job_sec) + scale(hh_income) + scale(alcohol_spending)

Labour state is an ordinal variable with 10 levels, relating to the type of employment:

1 - Self-employed
2 - Employed
3 - Unemployed
4 - Retired
5 - Maternity Leave
6 - Family care
7 - Full time student, school
8 - Long term sick, disabled
9 - Government training scheme
10 - Other

We estimate next labour state with a multinomial logistic regression model, with the formula:

> labour_state ~ age + sex + ethnicity + education_state + SF_12 + housing_quality + labour_state + job_sec + hh_income + alcohol_spending

```{r}
#labour <- readRDS(paste0(trans.path, '../labour/nnet/labour_nnet_2018_2019.rds'))
labour <- readRDS(paste0(trans.path, 'labour_state/labour_state_2018_2019.rds'))
summary(labour)
```

```{r}
#summary(labour)$coefficients
```

```{r}

```

EXPLAIN RESPONSE VARIABLE
EXPLAIN MODEL PREDICTORS AND JUSTIFY
EXPLAIN MODEL STRUCTURE
INCLUDING GOODNESS OF FIT PLOTS AND STATISTICS.

## Energy Poverty Additional Pathways

### net income

### mortgage, rent, council tax, oecd

### yearly energy. four constituent components.

### heating

### behind on bills

### financial situation

### housing tenure (is this transitinoed?)

### 2024-10-18 minos/modules/r_utils.py

@@ -170,7 +170,7 @@ def predict_next_timestep_clm(model, rpy2modules, current, dependent):
         currentRDF = ro.conversion.py2rpy(current)
 
     # need to cast the dependent var to an R FactorVector
-    if dependent in ['loneliness', 'neighbourhood_safety', 'housing_quality']:
+    if dependent in ['loneliness', 'neighbourhood_safety', 'housing_quality', 'ncars']:
         dependent_index = list(currentRDF.colnames).index(dependent)
         dependent_col = FactorVector(currentRDF.rx2(dependent))
         currentRDF[dependent_index] = dependent_col

### 2024-10-18 minos/modules/tobacco.py

@@ -96,14 +96,18 @@ class Tobacco(Base):
         self.year = event.time.year
 
         # Predict next tobacco value
-        newWaveTobacco = pd.DataFrame(self.calculate_tobacco(pop))
-        newWaveTobacco.columns = ['ncigs']
+        newWaveTobacco  = pd.DataFrame(self.calculate_tobacco_clm(pop))
+        newWaveTobacco["ncigs"] = self.random.choice(newWaveTobacco.index,
+                                                                list(5*newWaveTobacco.columns),
+                                                                newWaveTobacco ).astype(int)
+        #newWaveTobacco.columns = ['ncigs']
         newWaveTobacco.index = pop.index
+
 
         newWaveTobacco["ncigs"] = newWaveTobacco["ncigs"].astype(int)
         # Draw individuals next states randomly from this distribution.
         # Update population with new tobacco
-        newWaveTobacco["ncigs"] = np.clip(newWaveTobacco['ncigs'], 0, 300)
+        #newWaveTobacco["ncigs"] = np.clip(newWaveTobacco['ncigs'], 0, 300)
         self.population_view.update(newWaveTobacco["ncigs"])
 
     def calculate_tobacco(self, pop):
@@ -135,6 +139,37 @@ class Tobacco(Base):
                                                             current=pop,
                                                             dependent='ncigs')
         return nextWaveTobacco
+
+    def calculate_tobacco_clm(self, pop):
+        """Calculate tobacco transition distribution based on provided people/indices
+
+        Parameters
+        ----------
+            index : pd.Index
+                Which individuals to calculate transitions for.
+        Returns
+        -------
+        """
+        # load transition model based on year.
+        if self.cross_validation:
+            # if cross-val, fix year to final year model
+            year = 2020
+        else:
+            year = max(self.year, 2014)
+            year = min(year, 2020)
+
+        # if simulation goes beyond real data in 2020 dont load the transition model again.
+        if not self.transition_model or year <= 2020:
+            self.transition_model = r_utils.load_transitions(f"ncigs/clm/ncigs_{year}_{year + 1}", self.rpy2Modules, path=self.transition_dir)
[…]

### 2024-10-18 minos/validation/housing_handovers.Rmd
updating validation handovers and ncars and ncigs composites

@@
 handover_lineplots(raw.dat, base.dat, "hh_income")
+handover_median_lineplots(raw.dat, base.dat, "hh_income")
+
 ```
@@
 handover_lineplots(raw.inc, base.inc, "net_hh_income")
+handover_median_lineplots(raw.inc, base.inc, "net_hh_income")
+
 inc.spag<-rbind(raw.inc, base.inc)
@@
 handover_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
+handover_median_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
+
 density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
@@
 handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
+handover_median_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
+
 density_ridges(inc.spag[which(inc.spag$hh_mortgage>1 & inc.spag$hh_mortgage<5000), ], 'hh_mortgage',
@@
 handover_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
+handover_median_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
+
 density_ridges(inc.spag[which(inc.spag$council_tax>1), ], 'council_tax',
@@
 
-## SF12
+## SF12 MCS
 
@@
 
-raw.sf12 <- raw.dat %>%
+raw.sf12_mcs <- raw.dat %>%
   dplyr::select(pidp, time, SF_12_MCS) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
+  summarise(sf12_mcs = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'final_US')
 
-base.sf12 <- base.dat %>%
+base.sf12_mcs <- base.dat %>%
   dplyr::select(pidp, time, SF_12_MCS) %>%
   group_by(time) %>%
-  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
+  summarise(sf12_mcs = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'baseline_output')
@@
 # merge before plot
-sf12 <- rbind(raw.sf12, base.sf12)
+sf12_mcs <- rbind(raw.sf12_mcs, base.sf12_mcs)
 
 # Now plot
-ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+ggplot(data = sf12_mcs, mapping = aes(x = time, y = sf12_mcs, group = source, colour = source)) +
   geom_smooth() +
@@
   xlab('Year') +
-  ylab('SF12')
+  ylab('SF12 MCS')
 
@@
 # onwards because the sample refreshments are messing with the plot
-raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.sf12.2 <- raw.dat %>%
+raw.sf12_mcs.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+
+raw.sf12_mcs.2 <- raw.dat %>%
   dplyr::select(pidp, time, SF_12_MCS) %>%
-  filter(pidp %in% raw.sf12.wave1) %>%
-  group_by(time) %>%
-  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
+  filter(pidp %in% raw.sf12_mcs.wave1) %>%
+  group_by(time) %>%
+  summarise(sf12_mcs = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'final_US')
 
-base.sf12.2 <- base.dat %>%
+base.sf12_mcs.2 <- base.dat %>%
   dplyr::select(pidp, time, SF_12_MCS) %>%
-  filter(pidp %in% raw.sf12.wave1) %>%
-  group_by(time) %>%
-  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
+  filter(pidp %in% raw.sf12_mcs.wave1) %>%
+  group_by(time) %>%
+  summarise(sf12_mcs = mean(SF_12_MCS, na.rm = TRUE)) %>%
   mutate(source = 'baseline_output')
 
-sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
+sf12_mcs.2 <- rbind(raw.sf12_mcs.2, base.sf12_mcs.2)
 
 # Now plot
-ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
+ggplot(data = sf12_mcs.2, mapping = aes(x = time, y = sf12_mcs, group = source, colour = source)) +
   geom_line() +
@@
   xlab('Year') +
-  ylab('SF12')
+  ylab('SF12 MCS')
 
 if (shall.we.save) {
-  ggsave(filename = 'SF12_wav1.png',
+  ggsave(filename = 'SF12_MCS_wav1.png',
        plot = last_plot(),
@@
 
-rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
+rm(raw.sf12_mcs, base.sf12_mcs, sf12_mcs, raw.sf12_mcs.wave1, raw.sf12_mcs.2, base.sf12_mcs.2, sf12_mcs.2)
 ```
@@
 ```{r}
-raw.sf12 <- raw.dat %>%
+raw.sf12_mcs <- raw.dat %>%
   select(pidp, age, time, SF_12_MCS)
-base.sf12 <- base.dat %>%
+base.sf12_mcs <- base.dat %>%
   select(pidp, age, time, SF_12_MCS)
 
-sf12.spag <- rbind(raw.sf12, base.sf12)
-
-sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(sf12.spag.sample, 'SF_12_MCS',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_MCS',
-               save = shall.we.save,
-               save.path = save.path)
-
-density_ridges(sf12.spag, "SF_12_MCS",
+sf12_mcs.spag <- rbind(raw.sf12_mcs, base.sf12_mcs)
+
+pidp_sample <- sample(unique(sf12_mcs.spag$pidp), size=100, replace=FALSE)
+
+sf12_mcs.spag.sample <- sf12_mcs.spag[which(sf12_mcs.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(sf12_mcs.spag.sample, 'SF_12_MCS',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(sf12_mcs.spag.sample, 'SF_12_MCS',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(sf12_mcs.spag, "SF_12_MCS",
                save = T,
@@
 
-rm(raw.sf12, base.sf12, sf12.spag)
+rm(raw.sf12_mcs, base.sf12_mcs, sf12_mcs.spag)
+```
+
+## SF12 PCS
+
+```{r}
+# sf12 boxplot handovers
+handover_boxplots(raw.dat, base.dat, 'SF_12_PCS')
+handover_lineplots(raw.dat, base.dat, "SF_12_PCS")
+
+raw.sf12_pcs <- raw.dat %>%
+  dplyr::select(pidp, time, SF_12_PCS) %>%
+  group_by(time) %>%
+  summarise(sf12_pcs = mean(SF_12_PCS, na.rm = TRUE)) %>%
+  mutate(source = 'final_US')
+
+base.sf12_pcs <- base.dat %>%
+  dplyr::select(pidp, time, SF_12_PCS) %>%
+  group_by(time) %>%
+  summarise(sf12_pcs = mean(SF_12_PCS, na.rm = TRUE)) %>%
+  mutate(source = 'baseline_output')
+
+# merge before plot
+sf12_pcs <- rbind(raw.sf12_pcs, base.sf12_pcs)
+
+# Now plot
+ggplot(data = sf12_pcs, mapping = aes(x = time, y = sf12_pcs, group = source, colour = source)) +
+  geom_smooth() +
+  #geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Physical Wellbeing (SF12)', subtitle = 'Full Sample') +
+  xlab('Year') +
+  ylab('SF12 PCS')
+
+## Try a version where final_US is limited to only those present from wave 1
+# onwards because the sample refreshments are messing with the plot
+raw.sf12_pcs.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
+
+raw.sf12_pcs.2 <- raw.dat %>%
+  dplyr::select(pidp, time, SF_12_PCS) %>%
+  filter(pidp %in% raw.sf12_pcs.wave1) %>%
+  group_by(time) %>%
+  summarise(sf12_pcs = mean(SF_12_PCS, na.rm = TRUE)) %>%
+  mutate(source = 'final_US')
+
+base.sf12_pcs.2 <- base.dat %>%
+  dplyr::select(pidp, time, SF_12_PCS) %>%
+  filter(pidp %in% raw.sf12_pcs.wave1) %>%
+  group_by(time) %>%
+  summarise(sf12_pcs = mean(SF_12_PCS, na.rm = TRUE)) %>%
+  mutate(source = 'baseline_output')
+
+sf12_pcs.2 <- rbind(raw.sf12_pcs.2, base.sf12_pcs.2)
+
+# Now plot
+ggplot(data = sf12_pcs.2, mapping = aes(x = time, y = sf12_pcs, group = source, colour = source)) +
+  geom_line() +
+  geom_vline(xintercept=start.year, linetype='dotted') +
+  labs(title = 'Mental Wellbeing (SF12 MCS)') +
+  xlab('Year') +
+  ylab('SF12 PCS')
+
+if (shall.we.save) {
+  ggsave(filename = 'SF12_PCS_wav1.png',
+       plot = last_plot(),
+       path = save.path)
+}
+
+rm(raw.sf12_pcs, base.sf12_pcs, sf12_pcs, raw.sf12_pcs.wave1, raw.sf12_pcs.2, base.sf12_pcs.2, sf12_pcs.2)
+```
+
+### Spaghetti
+
+```{r}
+raw.sf12_pcs <- raw.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+base.sf12_pcs <- base.dat %>%
+  select(pidp, age, time, SF_12_PCS)
+
+sf12_pcs.spag <- rbind(raw.sf12_pcs, base.sf12_pcs)
+
+pidp_sample <- sample(unique(sf12_pcs.spag$pidp), size=100, replace=FALSE)
+
+sf12_pcs.spag.sample <- sf12_pcs.spag[which(sf12_pcs.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(sf12_pcs.spag.sample, 'SF_12_PCS',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(sf12_pcs.spag.sample, 'SF_12_PCS',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(sf12_pcs.spag, "SF_12_PCS",
+               save = T,
+               save.path = save.path)
+
+rm(raw.sf12_pcs, base.sf12_pcs, sf12_pcs.spag)
 ```
@@
 
-## Physical Health
-
-NOTE: At present, physical health is not predicted or transitioned.
-
-```{r}
-# first figure out how to plot final_US
-# start with hh_income
-raw.phealth <- raw.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.phealth <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-# merge before plot
-phealth <- rbind(raw.phealth, base.phealth)
-
-# Now plot
-ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health', subtitle = 'Full Sample') +
-  xlab('Year') +
-  ylab('Average')
-
-## Try a version where final_US is limited to only those present from wave 1
-# onwards because the sample refreshments are messing with the plot
-raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
-
-raw.phealth2 <- raw.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'final_US')
-
-base.phealth2 <- base.dat %>%
-  dplyr::select(pidp, time, phealth) %>%
-  filter(time > 2009) %>%
-  filter(pidp %in% raw.wave1) %>%
-  group_by(time) %>%
-  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
-  mutate(source = 'baseline_output')
-
-phealth2 <- rbind(raw.phealth2, base.phealth2)
-
-# Now plot
-ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = 'Physical Health') +
-  xlab('Year') +
-  ylab('Average')
-
-if (shall.we.save) {
-  ggsave(filename = 'physical_health_wav1.png',
-       plot = last_plot(),
-       path = save.path)
-}
-
-#raw.phealth.check <- raw.dat %>%
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
-
-#base.phealth.check <- base.dat %>%
-#  select(pidp, time, phealth) %>%
-#  filter(time > 2009) %>%
-#  filter(pidp %in% raw.wave1)
-
-rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2)
-#rm(raw.phealth.check, base.phealth.check)
-```
-
-### Spaghetti
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, phealth)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, phealth)
-#
-# spag <- rbind(raw.s, base.s)
-#
-# spaghetti_plot(spag, 'phealth',
-#              save = shall.we.save,
-#              save.path = save.path)
-#
-# rm(raw.s, base.s, spag)
+<!-- ## Physical Health -->
+
+<!-- NOTE: At present, physical health is not predicted or transitioned. -->
+
+<!-- ```{r} -->
+<!-- # first figure out how to plot final_US -->
+<!-- # start with hh_income -->
+<!-- raw.phealth <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'final_US') -->
+
+<!-- base.phealth <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'baseline_output') -->
+
+<!-- # merge before plot -->
+<!-- phealth <- rbind(raw.phealth, base.phealth) -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Physical Health', subtitle = 'Full Sample') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Average') -->
+
+<!-- ## Try a version where final_US is limited to only those present from wave 1 -->
+<!-- # onwards because the sample refreshments are messing with the plot -->
+<!-- raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009] -->
+
+<!-- raw.phealth2 <- raw.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   filter(pidp %in% raw.wave1) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'final_US') -->
+
+<!-- base.phealth2 <- base.dat %>% -->
+<!--   dplyr::select(pidp, time, phealth) %>% -->
+<!--   filter(time > 2009) %>% -->
+<!--   filter(pidp %in% raw.wave1) %>% -->
+<!--   group_by(time) %>% -->
+<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
+<!--   mutate(source = 'baseline_output') -->
+
+<!-- phealth2 <- rbind(raw.phealth2, base.phealth2) -->
+
+<!-- # Now plot -->
+<!-- ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
+<!--   geom_line() + -->
+<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
+<!--   labs(title = 'Physical Health') + -->
+<!--   xlab('Year') + -->
+<!--   ylab('Average') -->
+
+<!-- if (shall.we.save) { -->
+<!--   ggsave(filename = 'physical_health_wav1.png', -->
+<!--        plot = last_plot(), -->
+<!--        path = save.path) -->
+<!-- } -->
+
+<!-- #raw.phealth.check <- raw.dat %>% -->
+<!-- #  select(pidp, time, phealth) %>% -->
+<!-- #  filter(time > 2009) %>% -->
+<!-- #  filter(pidp %in% raw.wave1) -->
+
+<!-- #base.phealth.check <- base.dat %>% -->
+<!-- #  select(pidp, time, phealth) %>% -->
+<!-- #  filter(time > 2009) %>% -->
+<!-- #  filter(pidp %in% raw.wave1) -->
+
+<!-- rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2) -->
+<!-- #rm(raw.phealth.check, base.phealth.check) -->
+<!-- ``` -->
+
+<!-- ### Spaghetti -->
+
+<!-- ```{r} -->
+<!-- # raw.s <- raw.dat %>% -->
+<!-- #   select(pidp, age, time, phealth) -->
+<!-- # base.s <- base.dat %>% -->
+<!-- #   select(pidp, age, time, phealth) -->
+<!-- # -->
+<!-- # spag <- rbind(raw.s, base.s) -->
+<!-- # -->
+<!-- # spaghetti_plot(spag, 'phealth', -->
+<!-- #              save = shall.we.save, -->
+<!-- #              save.path = save.path) -->
+<!-- # -->
+<!-- # rm(raw.s, base.s, spag) -->
+<!-- ``` -->
+
+## Alcohol (AUDITC)
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
+
+raw.2020.alc <- raw.dat %>% 
+  filter(time == 2020) %>%
+  group_by(auditc) %>%
+  summarise(n = n()) %>%
+  mutate(prop = n / sum(n))
+
+```
+
+## Physical Activity
+
+```{r}
+handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
+
+raw.2020.phys <- raw.dat %>% 
+  filter(time == 2020) %>%
+  group_by(active) %>%
+  summarise(n = n()) %>%
+  mutate(prop = n / sum(n))
 ```
@@
 
-### Spaghetti
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, education_state)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, education_state)
-#
-# spag <- rbind(raw.s, base.s)
-#
-# spaghetti_plot(spag, 'education_state',
-#                save = shall.we.save,
-#                save.path = save.path)
-#
-# rm(raw.s, base.s, spag)
-```
+<!-- ### Spaghetti -->
+
+<!-- ```{r} -->
+<!-- # raw.s <- raw.dat %>% -->
+<!-- #   select(pidp, age, time, education_state) -->
+<!-- # base.s <- base.dat %>% -->
+<!-- #   select(pidp, age, time, education_state) -->
+<!-- # -->
+<!-- # spag <- rbind(raw.s, base.s) -->
+<!-- # -->
+<!-- # spaghetti_plot(spag, 'education_state', -->
+<!-- #                save = shall.we.save, -->
+<!-- #                save.path = save.path) -->
+<!-- # -->
+<!-- # rm(raw.s, base.s, spag) -->
+<!-- ``` -->
 

### 2024-10-21 minos/validation/handovers.Rmd
adding ncigs back into handovers

--- 2024-10-15 minos/validation/handovers.Rmd
@@
 # Read raw datafiles in
-#raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
-raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
-#raw.files <- list.files(here::here('data', 'scaled_scotland_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
+raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
 raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
@@
 out.path <- here::here('output', 'default_config/')
-# out.path <- here::here('output', 'scotland_scaled/')
 base.dat <- read_singular_local_out(out.path, 'baseline', 
@@
                                     drop.zero.weight = TRUE)
-
-# base.dat <- read_singular_local_out(out.path, 'ChildPovertyReduction',
-#                                     drop.dead = TRUE,
-#                                     drop.zero.weight = TRUE)
-
 #base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
@@
 
-# Need to remove extra data from raw data after start year
-raw.dat <- raw.dat %>%
-  filter(time <= start.year)
-
 shall.we.save <- FALSE
-```
-
-## Income Quintile
-
-```{r}
-raw.dat <- raw.dat %>%
-  group_by(time) %>%
-  mutate(income_quint = ntile(hh_income, 5))
-
-base.dat <- base.dat %>%
-  group_by(time) %>%
-  mutate(income_quint = ntile(hh_income, 5))
 ```
@@
   group_by(time) %>%
-  summarise(max_age = max(age)) %>%
-  mutate(scen = 'final_US')
+  summarise(max_age = max(age))
 
@@
   group_by(time) %>%
-  summarise(max_age = max(age)) %>%
-  mutate(scen = 'baseline')
-
-combined <- rbind(raw.maxAge, base.maxAge)
-
-#handover_lineplots(raw.maxAge, base.maxAge, 'max_age')
-ggplot(combined, aes(x = time, y = max_age, group = scen, colour = scen)) +
-  geom_line() +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
-  labs(title = 'Max year of age') +
-  xlab('Year') +
-  ylab('Age')
+  summarise(max_age = max(age))
+
+handover_lineplots(raw.maxAge, base.maxAge, 'max_age')
 
@@
   group_by(time) %>%
-  summarise(n = n()) %>%
-  mutate(scen = 'final_US')
+  summarise(n = n())
 
@@
   group_by(time) %>%
-  summarise(n = n()) %>%
-  mutate(scen = 'baseline')
+  summarise(n = n())
 
 #handover_boxplots(raw.alive, base.alive, 'n')
-#handover_lineplots(raw.alive, base.alive, "n")
-
-combined <- rbind(raw.alive, base.alive)
-
-ggplot(combined, aes(x = time, y = n, group = scen, color = scen, fill = scen)) +
-  geom_line() +
-  geom_vline(xintercept = start.year, linetype = 'dashed') +
-  labs(title = 'Total Count in Sample') +
-  xlab('Year') +
-  ylab('Count')
+handover_lineplots(raw.alive, base.alive, "n")
 
@@
 ```{r}
-# # Step 1: Filter for households with children
-# households_with_kids <- raw.dat %>%
-#   filter(nkids > 0) %>%
-#   select(hidp, time, hh_income) %>%
-#   distinct() %>%
-#   select(-hidp)
-# 
-# # Step 2: Calculate income quintiles
-# households_with_kids <- households_with_kids %>%
-#   group_by(time) %>%
-#   mutate(income_quintile = ntile(hh_income, 5)) %>%
-#   ungroup()
-# 
-# # Step 3: Count households within each income quintile per year
-# household_count_by_income_quintile <- households_with_kids %>%
-#   group_by(time, income_quintile) %>%
-#   summarise(n = n())
-# 
-# household_count_by_income_quintile
-```
-
-### Households With Children (Ethnic Group)
-
-```{r}
-raw.hhs_kids.ethnicity <- raw.dat %>%
+# Step 1: Filter for households with children
+households_with_kids <- raw.dat %>%
   filter(nkids > 0) %>%
-  select(hidp, time, hh_income, ethnicity) %>%  # Select relevant columns to reduce data size
+  select(hidp, time, hh_income) %>%
   distinct() %>%
-  group_by(time, ethnicity) %>%
-  summarise(n = n(), .groups = 'drop') %>%
-  mutate(source = 'final_US')
-
-base.hhs_kids.ethnicity <- base.dat %>%
-  filter(nkids > 0) %>%
-  select(hidp, time, hh_income, ethnicity) %>%  # Select relevant columns to reduce data size
-  distinct() %>%
-  group_by(time, ethnicity) %>%
-  summarise(n = n(), .groups = 'drop') %>%
-  mutate(source = 'baseline')
-
-combined <- rbind(raw.hhs_kids.ethnicity, base.hhs_kids.ethnicity)
-combined$ethnicity <- factor(combined$ethnicity)
-
-ggplot(combined, aes(x = time, y = n, group = ethnicity, color = ethnicity, fill = ethnicity)) +
-  geom_point() +
-  geom_line() +
-  geom_vline(xintercept = start.year) +
-  labs(title = 'Households with Children Count')
-
-rm(raw.hhs_kids.ethnicity, base.hhs_kids.ethnicity)
-```
-
-```{r}
-calculate_hh_proportions <- function(data, group.var) {
-  # Step 1: Filter for households with children
-  households_with_kids <- data %>%
-    filter(nkids > 0) %>%
-    select(hidp, time, hh_income, .data[[group.var]]) %>%
-    distinct()
-
-  # Step 3: Count households within each income group per year
-  household_counts <- households_with_kids %>%
-    group_by(time, .data[[group.var]]) %>%
-    summarise(count = n(), .groups = 'drop')
-
-  # Step 4: Calculate total households with children per year
-  total_households_per_year <- households_with_kids %>%
-    group_by(time) %>%
-    summarise(total_count = n(), .groups = 'drop')
-
-  # Step 5: Calculate proportion of households in each group per year
-  household_proportions <- household_counts %>%
-    left_join(total_households_per_year, by = "time") %>%
-    mutate(proportion = count / total_count) %>%
-    select(time, .data[[group.var]], proportion)
-
-  return(household_proportions)
-}
-
-raw.hh_kids_prop <- calculate_hh_proportions(raw.dat, group.var = 'ethnicity')
-base.hh_kids_prop <- calculate_hh_proportions(base.dat, group.var = 'ethnicity')
-
-raw.hh_kids_prop$source <- 'final_US'
-raw.hh_kids_prop <- filter(raw.hh_kids_prop, time != start.year)
-base.hh_kids_prop$source <- 'baseline'
-
-combined <- rbind(raw.hh_kids_prop, base.hh_kids_prop)
-combined$ethnicity <- factor(combined$ethnicity)
-
-ggplot(combined, aes(x = time, y = proportion, group = ethnicity, color = ethnicity, fill = ethnicity)) +
-  geom_col() +
-  geom_vline(xintercept = start.year) +
-  labs(title = 'Households with Children Count')
-
-rm(raw.hh_kids_prop, base.hh_kids_prop, combined)
+  select(-hidp)
+
+# Step 2: Calculate income quintiles
+households_with_kids <- households_with_kids %>%
+  group_by(time) %>%
+  mutate(income_quintile = ntile(hh_income, 5)) %>%
+  ungroup()
+
+# Step 3: Count households within each income quintile per year
+household_count_by_income_quintile <- households_with_kids %>%
+  group_by(time, income_quintile) %>%
+  summarise(n = n())
+
+household_count_by_income_quintile
 ```
@@
 handover_lineplots(raw.dat, base.dat, "hh_income")
-
-handover_boxplots(raw.dat, base.dat, 'hh_income_diff')
-handover_lineplots(raw.dat, base.dat, "hh_income_diff")
-# handover_boxplots(raw.dat, base.dat, 'council_tax')
-# handover_lineplots(raw.dat, base.dat, "council_tax")
-
-handover_boxplots(base.dat, base.dat, 'hh_income_diff')
-handover_lineplots(base.dat, base.dat, "hh_income_diff")
+handover_boxplots(raw.dat, base.dat, 'council_tax')
+handover_lineplots(raw.dat, base.dat, "council_tax")
 ```
@@
                save.path = save.path)
-
-spaghetti_plot(income.spag.sample, 'hh_income_diff',
-               save = shall.we.save,
-               save.path = save.path)
-spaghetti_highlight_max_plot(income.spag.sample, 'hh_income_diff',
-               save = shall.we.save,
-               save.path = save.path)
-
-# spaghetti_plot(base.inc, 'hh_income',
-#                save = shall.we.save,
-#                save.path = save.path)
 
@@
 ```{r}
-# raw.2010 <- raw.dat %>%
-#   filter(time == 2010)
-# 
-# abs.threshold <- weighted.median(x = raw.2010$hh_income, 
-#                                  w = raw.2010$weight, 
-#                                  na.rm = TRUE)
-# abs.threshold <- abs.threshold * 0.6
-# 
-# print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
-```
-
-### Analysis by Quintile
-
-```{r}
-density_plot_quintile <- function(raw, base, quintile) {
-
-  raw <- raw %>%
-    filter(income_quint == quintile) %>%
-    select(pidp, time, hh_income) %>%
-    rename(Final_US = hh_income)
-  base <- base %>%
-    filter(income_quint == quintile) %>%
-    select(pidp, time, hh_income) %>%
-    rename(Baseline = hh_income)
-
-  #combined <- merge(base, int, by = c('pidp', 'time'))
-
-  combined <- rbind(raw, base)
-
-  combined <- combined %>%
-    pivot_longer(cols = Final_US:Baseline,
-                 names_to = 'Source',
-                 values_to = 'hh_income')
-
-  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source, fill = Source)) +
-    geom_density_ridges(alpha = 0.3) +
-    labs(title = 'Household Income Density Plots',
-         subtitle = paste0('Quintile ', quintile))
-
-  return(p)
-}
-
-# density_plot_quintile(base.dat, int.dat, quintile = 1)
-# density_plot_quintile(base.dat, int.dat, quintile = 2)
-# density_plot_quintile(base.dat, int.dat, quintile = 3)
-# density_plot_quintile(base.dat, int.dat, quintile = 4)
-# density_plot_quintile(base.dat, int.dat, quintile = 5)
-```
-
-#### Mean Income
-
-```{r}
-mean_income_quintile <- function(raw, base) {
-  raw <- raw %>%
-    select(pidp, time, hh_income, income_quint, weight) %>%
-    mutate(source = 'Final_US')
-  base <- base %>%
-    select(pidp, time, hh_income, income_quint, weight) %>%
-    mutate(source = 'Baseline')
-
-  combined <- rbind(base, int)
-
-  combined <- combined %>%
-    group_by(time, income_quint, source) %>%
-    summarise(mean = weighted.mean(hh_income, weight),
-              median = weighted.median(hh_income, weight))
-
-  combined$income_quint <- factor(combined$income_quint)
-  combined$source <- factor(combined$source)
-
-  p1 <- ggplot(combined, aes(x = time, y = mean, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
-    geom_line() +
-    labs(title = 'Mean hh_income by quintile',
-         subtitle = 'Baseline vs Intervention')
-
-  p2 <- ggplot(combined, aes(x = time, y = median, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
-    geom_line() +
-    labs(title = 'Median hh_income by quintile',
-         subtitle = 'Baseline vs Intervention')
-
-  print(p1)
-  print(p2)
-  #return(p)
-}
-
-#mean_income_quintile(base.dat, int.dat)
-```
-
-#### Thresholds Over Time
-
-```{r}
-# get min-max by group as this is upper and lower limits of the quintiles
-
-# base <- base.dat %>%
-#   group_by(time, income_quint) %>%
-#   summarise(min = min(hh_income),
-#             max = max(hh_income)) %>%
-#   mutate(source = 'Baseline')
-# int <- int.dat %>%
-#   group_by(time, income_quint) %>%
-#   summarise(min = min(hh_income),
-#             max = max(hh_income)) %>%
-#   mutate(source = 'Intervention')
-# 
-# combined <- rbind(base, int)
-# combined$income_quint <- factor(combined$income_quint)
-# 
-# quintile_threshold_plot <- function(data, year) {
-#   ggplot(filter(data, time == year), 
-#          aes(x = income_quint, y = min,
-#              ymin = min, lower = min, ymax = max, upper = max,
-#              group = source, 
-#              colour = source, 
-#              fill = source)) +
-#     geom_crossbar(position = position_dodge()) +
-#     labs(title = 'Quintile Thresholds',
-#          subtitle = year)
-# }
-# 
-# quintile_threshold_plot(combined, year = 2020)
-# quintile_threshold_plot(combined, year = 2021)
-# quintile_threshold_plot(combined, year = 2025)
-# quintile_threshold_plot(combined, year = 2030)
-# quintile_threshold_plot(combined, year = 2035)
-```
-
-```{r}
-
+raw.2010 <- raw.dat %>%
+  filter(time == 2010)
+
+abs.threshold <- weighted.median(x = raw.2010$hh_income, 
+                                 w = raw.2010$weight, 
+                                 na.rm = TRUE)
+abs.threshold <- abs.threshold * 0.6
+
+print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
 ```
@@
 ```{r}
-# raw.sf12 <- raw.dat %>%
-#   select(pidp, age, time, SF_12, SF_12_diff)
-# base.sf12 <- base.dat %>%
-#   select(pidp, age, time, SF_12, SF_12_diff)
-# 
-# sf12.spag <- rbind(raw.sf12, base.sf12)
-# 
-# sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
-# spaghetti_plot(sf12.spag.sample, 'SF_12',
-#                save = shall.we.save,
-#                save.path = save.path)
-# spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# spaghetti_plot(sf12.spag.sample, 'SF_12_diff',
-#                save = shall.we.save,
-#                save.path = save.path)
-# spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_diff',
-#                save = shall.we.save,
-#                save.path = save.path)
-#   
-# density_ridges(sf12.spag, "SF_12", 
-#                save = T, 
-#                save.path = save.path)
-# 
-# rm(raw.sf12, base.sf12, sf12.spag)
+raw.sf12 <- raw.dat %>%
+  select(pidp, age, time, SF_12)
+base.sf12 <- base.dat %>%
+  select(pidp, age, time, SF_12)
+
+sf12.spag <- rbind(raw.sf12, base.sf12)
+
+sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(sf12.spag.sample, 'SF_12',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
+               save = shall.we.save,
+               save.path = save.path)
+
+density_ridges(sf12.spag, "SF_12", 
+               save = T, 
+               save.path = save.path)
+
+rm(raw.sf12, base.sf12, sf12.spag)
 ```
@@
 
+## ncigs
+
+```{r}
+handover_boxplots(raw.dat, base.dat, 'ncigs')
+handover_lineplots(raw.dat, base.dat, "ncigs")
+raw.ncigs <- raw.dat %>%
+  select(pidp, age, time, ncigs)
+base.ncigs <- base.dat %>%
+  select(pidp, age, time, ncigs)
+ncigs.spag <- rbind(raw.ncigs, base.ncigs)
+shall.we.save <- F
+pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/10, replace=FALSE)
+ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+
+zip_density_ridges(ncigs.spag, "ncigs", 
+               save = shall.we.save, 
+               save.path = save.path)
+rm(raw.ncigs, base.ncigs, ncigs.spag)
+```
+
+## ncigs non-zero
+
+```{r}
+
+raw.ncigs <- raw.dat %>%
+  filter(ncigs>0) %>%
+  select(pidp, age, time, ncigs)
+base.ncigs <- base.dat %>%
+  filter(ncigs>0) %>%
+  select(pidp, age, time, ncigs)
+
+ncigs.spag <- rbind(raw.ncigs, base.ncigs) # get all smokers.
+shall.we.save <- F
+pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/100, replace=FALSE)
+ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
+spaghetti_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
+               save = shall.we.save,
+               save.path = save.path)
+
+zip_density_ridges(ncigs.spag, "ncigs", 
+               save = shall.we.save, 
+               save.path = save.path)
+rm(raw.ncigs, base.ncigs, ncigs.spag)
+```
+
 ## nkids Household
@@
 raw.hh_unique <- raw.dat %>%
-  select(hidp, time, nkids, weight) %>%
-  distinct(hidp, time, nkids, .keep_all = TRUE) %>%
-  mutate(scen = 'final_US')
+  select(hidp, time, nkids) %>%
+  distinct()
 
 base.hh_unique <- base.dat %>%
-  select(hidp, time, nkids, weight) %>%
-  distinct(hidp, time, nkids, .keep_all = TRUE) %>%
-  mutate(scen = 'baseline')
+  select(hidp, time, nkids) %>%
+  distinct()
 
@@
 handover_lineplots(raw.hh_unique, base.hh_unique, 'nkids')
-
-```
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, nkids)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, nkids)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'nkids',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, nkids)
+base.s <- base.dat %>%
+  select(pidp, age, time, nkids)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nkids',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-# raw.s <- raw.parity %>%
-#   select(pidp, age, time, nkids_ind)
-# base.s <- base.parity %>%
-#   select(pidp, age, time, nkids_ind)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'nkids_ind',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
-```
-
-## CHILD POVERTY VARS
-
-### Relative poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Relative Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'relative_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-### Absolute Poverty
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Absolute Poverty'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'absolute_poverty.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-```
-
-### Persistent Poverty
-
-```{r}
-# prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')
-# 
-# var <- prepped.list$var
-# norm <- prepped.list$norm
-# 
-# tit <- 'Persistent Poverty'
-# 
-# # Now plot
-# ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
-#   geom_line() +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = tit, subtitle = 'Counts by Level') +
-#   xlab('Year') +
-#   ylab('Count')
-# 
-# ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
-#   geom_bar(stat = 'identity') +
-#   geom_vline(xintercept=start.year, linetype='dotted') +
-#   labs(title = tit) +
-#   xlab('Year') +
-#   ylab('Proportion')
-# 
-# if (shall.we.save) {
-#   ggsave(filename = 'persistent_poverty.png',
-#          plot = last_plot(),
-#          path = save.path)
-# }
-# 
-# 
-# rm(prepped.list, var, norm, tit)
-
-```
-
-### Low Income and Material Deprivation
-
-```{r}
-prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')
-
-var <- prepped.list$var
-norm <- prepped.list$norm
-
-tit <- 'Material Deprivation Child'
-
-# Now plot
-ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
-  geom_line() +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit, subtitle = 'Counts by Level') +
-  xlab('Year') +
-  ylab('Count')
-
-ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
-  geom_bar(stat = 'identity') +
-  geom_vline(xintercept=start.year, linetype='dotted') +
-  labs(title = tit) +
-  xlab('Year') +
-  ylab('Proportion')
-
-if (shall.we.save) {
-  ggsave(filename = 'low_income_matdep_child.png',
-         plot = last_plot(),
-         path = save.path)
-}
-
-rm(prepped.list, var, norm, tit)
-
+raw.s <- raw.parity %>%
+  select(pidp, age, time, nkids_ind)
+base.s <- base.parity %>%
+  select(pidp, age, time, nkids_ind)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'nkids_ind',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 ```{r}
-# handover_boxplots(raw.dat, base.dat, 'hourly_wage')
-# handover_lineplots(raw.dat, base.dat, 'hourly_wage')
-```
-
-```{r}
-# raw.s <- raw.dat %>%
-#   select(pidp, age, time, hourly_wage)
-# base.s <- base.dat %>%
-#   select(pidp, age, time, hourly_wage)
-# 
-# spag <- rbind(raw.s, base.s)
-# 
-# spaghetti_plot(spag, 'hourly_wage',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# # now a version limited to 0-100
-# spag <- spag %>%
-#   filter(hourly_wage <= 300)
-# spaghetti_plot(spag, 'hourly_wage',
-#                save = shall.we.save,
-#                save.path = save.path)
-# 
-# rm(raw.s, base.s, spag)
+handover_boxplots(raw.dat, base.dat, 'hourly_wage')
+handover_lineplots(raw.dat, base.dat, 'hourly_wage')
+```
+
+```{r}
+raw.s <- raw.dat %>%
+  select(pidp, age, time, hourly_wage)
+base.s <- base.dat %>%
+  select(pidp, age, time, hourly_wage)
+
+spag <- rbind(raw.s, base.s)
+
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+# now a version limited to 0-100
+spag <- spag %>%
+  filter(hourly_wage <= 300)
+spaghetti_plot(spag, 'hourly_wage',
+               save = shall.we.save,
+               save.path = save.path)
+
+rm(raw.s, base.s, spag)
 ```
@@
 
-combined.nkids
-
-```
-
-```{r}
-
-```
+```
+
+```{r}
+
+```

### 2024-10-21 docsrc/documentation/notebooks/housing.Rmd
fixing up website to work on dev. can be expanded easily now after fixing some annoying bits like pathing.

--- 2022-12-19 docsrc/documentation/notebooks/housing.Rmd
@@
 bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
-  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
+  - "`r here::here('docsrc', 'refs.bib')`"
+
 ---
 
-# Housing Quality
+```{r setup, include=FALSE}
+library(here)
+library(glmnet)
+library(plyr)
+
+source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
+model_path <- here::here("data", "transitions", "housing_quality", "rfo", "housing_quality_RFO.rds")
+model <- readRDS(model_path)
+
+data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
+obs <- data$housing_quality
+data$housing_quality_last <- data$housing_quality
+
+preds <- ranger::predictions(stats::predict(model, data))
+column_names <- colnames(preds)
+preds <-glmnet::rmult(preds)
+preds <- plyr::mapvalues(preds, from=c(1,2,3), to= column_names)
+v <- "housing_quality"
+
+```
+
+## Housing Quality
 
@@
 
-```{r setup, include=FALSE}
-source('sphinx_notebook_utils.R')
-```
-
-## Methods
+### Methods
 
@@
 
-## Data
+```{r housing_barchart, echo=FALSE}
+discrete_barplot(obs, 'housing_quality')
+```
+
+### Data
 
@@
 options(width=120)
-clm_output("../../../data/transitions/test/housing_clm_2018_2019.rds")
+discrete_barplot2(obs, preds, "housing_quality") 
+rfo_output(model)
 ```
 
-## References
+### References

### 2024-10-21 docsrc/documentation/notebooks/labour.Rmd
fixing up website to work on dev. can be expanded easily now after fixing some annoying bits like pathing.

--- 2023-02-15 docsrc/documentation/notebooks/labour.Rmd
@@
 bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
-  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
+  - "`r here::here('docsrc', 'refs.bib')`" # finally figure out how to combine these for debugging and actual 
 ---
 
-```{r setup, include=FALSE}
-source('sphinx_notebook_utils.R')
+```{r load_data, include=FALSE}
+library(here)
+source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
+model_path <- here::here("data", "transitions", "S7_labour_state", "nnet", "S7_labour_state_2019_2020.rds")
+model <- readRDS(model_path)
+
+data <-  read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
+obs <- data$S7_labour_state
+preds <- stats::predict(model, data, type='class')
+v <- "S7_labour_state"
 ```
@@
 ```{r labour_barchart, echo=FALSE}
-discrete_barplot("labour_state")
+discrete_barplot(obs)
+discrete_barplot2(obs, preds, "S7_labour_state")
 ```
@@
 options(width=120)
-nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds")
-nnet_confusion_matrix("../../../data/transitions/test/labour_nnet_2018_2019.rds", mode='multinom', 'factor(labour_state_next)')
+#nnet_output("data/transitions/labour/nnet/labour_nnet_2018_2019.rds")
+nnet_confusion_matrix(obs, preds, mode='multinom', 'S7_labour_state') # Note this is transition out of this state. 
 ```

### 2024-10-23 docsrc/documentation/notebooks/loneliness.Rmd

--- 2022-12-19 docsrc/documentation/notebooks/loneliness.Rmd
@@
 bibliography: 
-  - "refs.bib"  # bib reference depending on where the file is being run. Use this one when compiling the website using the makefile.
-  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging. Make sure to switch back when done..
+  - "`r here::here('docsrc', 'refs.bib')`" # finally figure out how to combine these for debugging and actual 
 ---
 
-# Loneliness
-
-Introductory fluff. Why do we need this module? test reference [@1987:nelson].
+## Loneliness
 
 ```{r setup, include=FALSE}
-source('sphinx_notebook_utils.R')
+library(here)
+library(glmnet)
+library(plyr)
+
+source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
+model_path <- here::here("data", "transitions", "loneliness", "rfo", "loneliness_RFO.rds")
+model <- readRDS(model_path)
+
+data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
+obs <- data$loneliness
+data$loneliness_last <- data$loneliness
+
+preds <- ranger::predictions(stats::predict(model, data))
+column_names <- colnames(preds)
+preds <-glmnet::rmult(preds)
+preds <- plyr::mapvalues(preds, from=c(1,2,3), to= column_names)
+v <- "loneliness"
+
 ```
 
-## Methods
+### Methods
 
@@
 
-## Data
+```{r loneliness_data}
+discrete_barplot(obs, 'loneliness')
+```
+
+### Data
 
@@
 options(width=120)
-clm_output("../../../data/transitions/test/loneliness_clm_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
+discrete_barplot2(obs, preds, "loneliness") 
+rfo_output(model)
 ```
 
-## References
+### References

### 2024-10-23 docsrc/documentation/notebooks/mental_well_being.Rmd

--- 2023-02-17 docsrc/documentation/notebooks/mental_well_being.Rmd
@@
 bibliography: 
-  - "docsrc/refs.bib"
+  - "`r here::here('docsrc', 'refs.bib')`"
 ---
-
-```{r setup, include=FALSE}
-knitr::opts_knit$set(root.dir= "../minos")
-```
 
@@
 ```{r load_data, include=FALSE}
-source("docsrc/documentation/notebooks/sphinx_notebook_utils.R")
+library(here)
+source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
+model_path <- here::here("data", "transitions", "SF_12", "lmm", "SF_12_LMM.rds")
+model <- readRDS(model_path)
+
+obs <- model@frame$SF_12
+preds <- predict(model, type='response')
+v <- "SF_12"
 ```
@@
 What methods are used? Justification due to output data type. explanation of model output.
-
-```{r SF12_Density}
-continuous_density("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")  
-```
 
@@
 options(width=120)
-ols_output("data/transitions/SF_12/OLS/SF_12_2018_2019.rds")
-ols_histogram("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")
+#ols_output("data/transitions/SF_12/OLS/SF_12_2018_2019.rds")
+#ols_histogram("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")
+
+#glmm_output(model_path)
+continuous_densities(obs, preds, v)
+print(summary(model))
+plot(model)
 ```

### 2024-10-23 docsrc/documentation/notebooks/tobacco.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

--- 2023-02-15 docsrc/documentation/notebooks/tobacco.Rmd
@@
 title: "Tobacco"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
-  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
+  - "`r here::here('docsrc', 'refs.bib')`"
 ---
+
+```{r setup, include=FALSE}
+library(here)
+library(glmnet)
+library(plyr)
+
+source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
+model_path <- here::here("data", "transitions", "ncigs", "rfo", "ncigs_RFO.rds")
+model <- readRDS(model_path)
+
+data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
+obs <- data$ncigs
+data$ncigs_last <- data$ncigs
+
+preds <- ranger::predictions(stats::predict(model, data))
+column_names <- colnames(preds)
+preds <-glmnet::rmult(preds) - 1
+preds <- 5 * preds
+
+v <- "ncigs"
+
+```
 
@@
 Number of cigarettes consumed is an indicator of several mental illnesses including anxiety [@lawrence2010anxiety].
-
-```{r setup, include=FALSE}
-source('sphinx_notebook_utils.R')
-```
 
@@
 ```{r tobacco_data}
-counts_density('ncigs')
+discrete_barplot(obs, "ncigs")
 ```
@@
 options(width=120)
-zip_output("../../../data/transitions/test/tobacco_zip_2018_2019.rds")
-zip_density("../../../data/transitions/test/tobacco_zip_2018_2019.rds", 'ncigs_next')
+discrete_barplot2(obs, preds, "housing_quality") 
+rfo_output(model)
 ```

### 2024-10-29 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Trying the old versions of summary and vis scripts

--- 2024-09-23 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
@@
 
+#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
+#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
 workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
-#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_33_scot_clipped/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
-#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"
-#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
 #workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
@@
   tit <- ' '
-  if (summary_group == 'whole_pop') { 
-    tit <- 'Whole Population'
-    plot_colour <- 'black'
-    }
-  if (summary_group == 'families') { 
-    tit <- 'Families'
-    plot_colour <- '#56B4E9'
-    }
-  if (summary_group == 'treated_relative') { 
-    tit <- 'Treated'
-    plot_colour <- 'black'}
-  if (summary_group == 'treated_absolute') { 
-    tit <- 'Treated'
-    plot_colour <- 'black'}
-  if (summary_group == 'priority_any') { 
-    tit <- 'Any Priority Subgroup' 
-    plot_colour <- 'black' }
+  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
+  if (summary_group == 'families') { tit <- 'Families' }
+  if (summary_group == 'treated_relative') { tit <- 'Treated' }
+  if (summary_group == 'treated_absolute') { tit <- 'Treated' }
+  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }
 
@@
     geom_smooth() +
+    labs(title = tit) +
     xlab('Year') +
-    ylab('Change in Mean SF-12 MCS') +
-    theme_minimal()
+    ylab('Change in SF-12')
 
@@
     geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
-    geom_line(linetype = 'dashed', color=plot_colour) +
-    geom_point(color=plot_colour) +
+    geom_line(linetype = 'dashed') +
+    geom_point() +
     geom_hline(yintercept = 0, linetype = 'dashed') +
     geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = tit) +
     xlab('Year') +
-    ylab('Change in Mean SF-12 MCS') +
-    theme_minimal()
+    ylab('Change in SF-12')
 
@@
   #print(p3)
-
-  ggsave(filename = paste0(summary_group, '_smooth', '.png'),
-         plot = p1)
-
-  ggsave(filename = paste0(summary_group, '_confint', '.png'),
-         plot = p2)
 }
@@
     xlab('Year') +
-    ylab('Change in Mean SF-12 MCS') +
-    theme_minimal()
+    ylab('Change in SF-12')
 
   print(p1)
-
-  ggsave(filename = paste0(summary_group, '_trajectories', '.png'),
-         plot = p1)
 }
@@
     geom_smooth() +
+    labs(title = tit, subtitle = 'Income Quintile') +
     xlab('Year') +
-    ylab('Change in Mean SF-12 MCS') +
-    theme_minimal() +
-    guides(fill=guide_legend(title="Income Quintile"))
+    ylab('Change in SF-12')
 
@@
     geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = tit, subtitle = 'Income Quintile') +
     xlab('Year') +
-    ylab('Change in Mean SF-12 MCS') +
-    theme_minimal() +
-    guides(fill=guide_legend(title="Income Quintile"))
+    ylab('Change in SF-12')
 
@@
   print(p2)
-
-  ggsave(filename = paste0(summary_group, '_quintile_smooth', '.png'),
-         plot = p1)
-
-  ggsave(filename = paste0(summary_group, '_quintile_actual', '.png'),
-         plot = p2)
 }
@@
       geom_line(linetype = 'dashed') +
-      geom_point(show.legend = FALSE) +
+      geom_point() +
       geom_hline(yintercept = 0, linetype = 'dashed') +
       geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+      labs(title = tit, 
+           subtitle = 'Income Quintile') +
       xlab('Year') +
-      ylab('Change in Mean SF-12 MCS') +
-      theme_minimal() +
-      guides(fill=guide_legend(title="Income Quintile"),
-             linetype=guide_legend(title="Income Quintile"),
-             group=guide_legend(title="Income Quintile"),
-             color=guide_legend(title="Income Quintile"))
+      ylab('Change in mean SF-12')
 
@@
   print(p2)
-
-  ggsave(filename = paste0(summary_group, '_quintile', '.png'),
-         plot = p2)
-}
-
-SF12_change_income_quint2_fudged <- function(summary_group, scen) {
-
-  tit <- ' '
-  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
-  if (summary_group == 'families') { tit <- 'Families' }
-
-  summary_group <- paste0(summary_group, '_income_quint_together')
-  scen <- paste0(scen, '_together')
-
-  data <- do.call(rbind, generate_df_list(summary_group, scen))
-
-  plot_data <- data %>%
-    select(run_id, SF_12, income_quintile, year, scenario) %>%
-    pivot_wider(names_from = scenario,
-                values_from = SF_12,
-                names_sep = '.',
-                values_fn = list(SF_12 = function(x) x[1])) %>%
-    mutate(diff_SF12 = intervention - baseline) %>%
-    pivot_longer(cols = starts_with("diff"),
-                 names_to = c(".value", "scenario"),
-                 names_sep = "\\.") %>%
-    select(run_id, income_quintile, year, diff_SF12)
-
-  plot_data_confint <- plot_data %>%
-    group_by(year, income_quintile) %>%
-    summarise(n = n(),
-              mean_SF12_change = mean(diff_SF12),
-              margin_SF12 = qt(0.975, df = n - 1) * (sd(diff_SF12) / sqrt(n)),
-              lower_SF12 = mean_SF12_change - margin_SF12,
-              upper_SF12 = mean_SF12_change + margin_SF12) %>%
-    mutate(
-      mean_SF12_change = if_else(income_quintile %in% c(4, 5), 0, mean_SF12_change),
-      lower_SF12 = mean_SF12_change - margin_SF12,
-      upper_SF12 = mean_SF12_change + margin_SF12
-    )
-
-  # margin_SF12 = if_else(income_quintile %in% c(4, 5), 0, margin_SF12)
-  # lower_SF12 = if_else(income_quintile %in% c(4, 5), 0, lower_SF12),
-  # upper_SF12 = if_else(income_quintile %in% c(4, 5), 0, upper_SF12)
-
-  plot_data_confint$income_quintile <- factor(plot_data_confint$income_quintile)
-
-  # p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
-  #     geom_hline(yintercept = 0, linetype = 'dashed') +
-  #     geom_vline(xintercept = 2030, linetype = 'dotted') +
-  #     geom_smooth() +
-  #     labs(title = 'Treatment on the Treated',
-  #          subtitle = 'SF_12') +
-  #     xlab('Year') +
-  #     ylab('Change in mean SF-12')
-
-  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, color = income_quintile, fill = income_quintile)) +
-      geom_ribbon(aes(ymin = lower_SF12, ymax = upper_SF12), linetype = 'dotted', alpha = 0.3) +
-      geom_line(linetype = 'dashed') +
-      geom_point(show.legend = FALSE) +
-      geom_hline(yintercept = 0, linetype = 'dashed') +
-      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-      xlab('Year') +
-      ylab('Change in Mean SF-12 MCS') +
-      theme_minimal() +
-      guides(fill=guide_legend(title="Income Quintile"),
-             linetype=guide_legend(title="Income Quintile"),
-             group=guide_legend(title="Income Quintile"),
-             color=guide_legend(title="Income Quintile"))
-
-  #print(p1)
-  print(p2)
-
-  ggsave(filename = paste0(summary_group, '_quintile', '.png'),
-         plot = p2)
 }
@@
     geom_smooth() +
+    labs(title = tit) +
     xlab('Year') +
-    ylab('Change in Mean SF-12 MCS') +
-    theme_minimal() +
-    guides(group=guide_legend(title="Num Priority Subgroups"))
+    ylab('Change in SF-12')
 
@@
     geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = tit) +
     xlab('Year') +
-    ylab('Change in Mean SF-12 MCS') +
-    theme_minimal() +
-    guides(group=guide_legend(title="Num Priority Subgroups"))
+    ylab('Change in SF-12')
 
@@
   print(p2)
-
-  ggsave(filename = paste0(summary_group, '_smooth', '.png'),
-         plot = p1)
-
-  ggsave(filename = paste0(summary_group, '_actual', '.png'),
-         plot = p2)
 }
@@
          x = "Year",
-         y = "Change in Mean SF-12 MCS") +
+         y = "Difference in SF_12 Score") +
     theme_minimal() +
@@
   print(p2)
-
-  ggsave(filename = paste0(summary_group, '_inequality_line', '.png'),
-         plot = p1)
-
-  ggsave(filename = paste0(summary_group, '_inequality_bar', '.png'),
-         plot = p2)
 }
@@
     geom_line() +
+    labs(title = "Difference in count of individuals at risk of mental health issues",
+         subtitle = tit) +
     xlab('Year') +
-    ylab('Count Change') +
-    theme_minimal()
+    ylab('Count')
 
@@
     geom_line() +
+    labs(title = "Difference in proportion of individuals at risk of mental health issues",
+         subtitle = tit) +
     xlab('Year') +
-    ylab('Percentage Change') +
-    theme_minimal()
+    ylab('Percentage')
 
@@
   print(p2)
-
-  ggsave(filename = paste0(summary_group, '_count', '.png'),
-         plot = p1)
-
-  ggsave(filename = paste0(summary_group, '_proportion', '.png'),
-         plot = p2)
 }
@@
       geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
-      labs(title = 'Treated Population',
+      labs(title = 'Treatment on the Treated',
            subtitle = 'SF_12') +
       xlab('Year') +
-      ylab('Change in Mean SF-12 MCS')
+      ylab('Change in mean SF-12')
 
@@
       xlab('Year') +
-      ylab('Change in Mean Household Income')
+      ylab('Change in mean hh_income')
 
@@
   print(p4)
-
-  ggsave(filename = paste0(summary_group, '_SF-12', '.png'),
-         plot = p2)
-
-  ggsave(filename = paste0(summary_group, '_hh-income', '.png'),
-         plot = p4)
 }
@@
   print(p1)
-
-  ggsave(filename = paste0('synthpop_uncertainty_', var, '.png'),
-         plot = p1)
-
 }
@@
 scen <- 'ChildPovertyReduction'
-```
-
-# MCS Change to QALY Example
-
-We use an equation derived from table 4 (below) in [this paper by Lawrence and Fleishman](https://pubmed.ncbi.nlm.nih.gov/15090102/) to calculate QALYs from SF-12 Mental Component Score (MCS) and Physical Component Score (PCS).
-
-#![L&F Table 4](L&F_table4.png)
-
-```{r}
-# formula to find the utility score from mean MCS and PCS scores of a population
-utility_score <- function(pcs, mcs) {
-  utility_score <- 
-    1.6984 + 
-    (pcs * 0.07927) +
-    (mcs * 0.02859) +
-    ((pcs * mcs) * -0.000126) +
-    ((pcs * pcs) * -0.00141) +
-    ((mcs * mcs) * -0.00014) +
-    ((pcs * pcs * pcs) * 0.0000107)
-  return(utility_score)
-}
-
-# Calculate utility score for hypothetical baseline (MCS & PCS == 45.0)
-initial_conditions <- utility_score(pcs = 45.0,
-                                    mcs = 45.0)
-# Calculate utility score for 0.1 improvement in MCS (MCS now == 45.1)
-intervention <- utility_score(pcs = 45.0,
-                              mcs = 45.1)
-
-print("Utility score for hypothetical baseline (assuming mean MCS and PCS both equal 45.0):")
-print(initial_conditions)
-print("Utility score for population given a 0.1 mean improvement in MCS:")
-print(intervention)
-
-print("Gain in utility score per person:")
-gain <- intervention - initial_conditions
-print(gain)
-
-print("Gain in utiliy for the total Scotland population (assuming 5.5m). This is equivalent to QALYs gained:")
-print(gain * 5510000)
-```
-
-This rough calculation shows that a 0.1 absolute change in mean SF_12 across the Scottish population would equal over 5000 additional QALYs in a single year.
-These improvements can also accumulate over time.
-If we were able to achieve a 0.1 improvement in mean MCS for Scotland in year 1, and maintain this 0.1 improvement for 10 years, the resulting improvement in QALYs would be 56,000+.
-
-NOTE: This calculation assumes that PCS is unchanged when MCS can vary. This is not realistic, but the calculation is still useful to provide context for the results to follow.
-
-# SAMPLE UNCERTAINTY
-
-When running MINOS with a synthetic population, due to the size of the synthetic populations and the demands of the model, we have to take a reduced sample as our starting population.
-For the Scotland synthetic runs we take a 10% sample, which reduces the population size from roughly 5.5m to 550,000.
-
-We therefore have to also account for the uncertainty in model outputs that comes from this reduced sample. As a somewhat temporary fix for this, we have done the following:
-
-- Generate 10 different 10% samples from our synthetic population
-  - Generate a replenishing population from each of these samples
-- Use each distinct 10% sample for 10 runs each, totalling 100 runs
-- Plot the local mean from each 10 run block, and the global mean from all 100 runs
-
-```{r}
-synthpop_uncertainty(summary_group = 'whole_pop',
-                     scen = 'baseline',
-                     var = 'hh_income')
-
-synthpop_uncertainty(summary_group = 'whole_pop',
-                     scen = 'baseline',
-                     var = 'SF_12')
-```
-
-# SAMPLE STATISTICS
-
-```{r}
-
-# data <- do.call(rbind, generate_df_list('whole_pop', 'baseline'))
-# data.fam <- do.call(rbind, generate_df_list('families', 'baseline'))
-# 
-# nrow(data)
-# 
-# 
-# 5463300
-# 
-# 4580000
-# 
-# 
-# 359328 / 458000 * 100
-# 
-# 100 / 78.4559
-# 
-# 
-# 109338 * 12.74601
-
 ```
@@
 ```{r}
-SF12_change_income_quint(summary_group = 'whole_pop',
-                                    scen.list = scen.list)
+# SF12_change_income_quint(summary_group = 'whole_pop',
+#                                     scen.list = scen.list.rel)
 SF12_change_income_quint2(summary_group = 'whole_pop',
-                                    scen = scen)
-
-SF12_change_income_quint2_fudged(summary_group = 'whole_pop',
                                     scen = scen)
@@
 ```{r}
-SF12_change_income_quint(summary_group = 'families',
-                                    scen.list = scen.list)
+# SF12_change_income_quint(summary_group = 'families',
+#                                     scen.list = scen.list.rel)
 SF12_change_income_quint2(summary_group = 'families',
-                                    scen = scen)
-SF12_change_income_quint2_fudged(summary_group = 'families',
                                     scen = scen)
@@
 ```{r}
-SF12_change_simple(summary_group = 'treated_relative',
-                   scen.list = scen.list)
-
-SF12_change_simple(summary_group = 'treated_absolute',
-                   scen.list = scen.list)
+# SF12_change_simple(summary_group = 'treated_relative',
+#                    scen.list = scen.list.rel)
 

### 2024-11-21 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Updated summary and vis scripts to the latest version (with fixed num priority subgroup plot and plots for individual priority subgroups and lone adult households)

--- 2024-10-11 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
@@
 
+```{r "priority_subgroups", include=FALSE}
+priority_subgroup_plot <- function(priority_group, scen) {
+
+  priority_group <- paste0('priority_', priority_group)
+  scen <- paste0(scen, '_together')
+
+  #print(priority_group)
+  #print(scen)
+
+  data <- do.call(rbind, generate_df_list(priority_group, scen))
+
+  #return(data)
+
+  plot_data <- data %>%
+    select(run_id, SF_12, mean_cost, year, scenario) %>%
+    pivot_wider(names_from = scenario,
+                values_from = c(SF_12, mean_cost),
+                names_sep = '.') %>%
+    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
+    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
+    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"), 
+                 names_to = c(".value", "scen"), 
+                 names_sep = "\\.") %>%
+    filter(scen != 'baseline')
+
+  #return(plot_data)
+
+  plot_data_confint <- plot_data %>%
+    group_by(year) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(diff_SF_12),
+              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
+              lower = mean_SF12_change - margin,
+              upper = mean_SF12_change + margin)
+
+  plot_data_confint2 <- plot_data %>%
+    group_by(year) %>%
+    summarise(n = n(),
+              mean_SF12_change = mean(diff_SF_12),
+              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
+              lower = mean_SF12_change - margin,
+              upper = mean_SF12_change + margin)
+
+  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted') +
+    geom_smooth() +
+    xlab('Year') +
+    ylab('Change in Mean SF-12 MCS') +
+    theme_minimal()
+
+  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(linetype = 'dashed') +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = priority_group) +
+    xlab('Year') +
+    ylab('Change in Mean SF-12 MCS') +
+    theme_minimal()
+
+  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change)) +
+    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
+    geom_line(linetype = 'dashed') +
+    geom_hline(yintercept = 0, linetype = 'dashed') +
+    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
+    labs(title = priority_group) +
+    xlab('Year') +
+    ylab('Change in Mean SF-12 MCS') +
+    theme_minimal()
+
+  #print(p1)
+  print(p2)
+  #print(p3)
+
+  # ggsave(filename = paste0(priority_group, '_smooth', '.png'),
+  #        plot = p1)
+  # 
+  # ggsave(filename = paste0(priority_group, '_confint', '.png'),
+  #        plot = p2)
+}
+
+# test <- priority_subgroup_plot(priority_group = 'child_under_one',
+#                                scen = 'ChildPovertyReduction')
+```
+
+```{r}
+priority_subgroup_plot(priority_group = 'child_under_one',
+                               scen = 'ChildPovertyReduction')
+priority_subgroup_plot(priority_group = 'ethnicity',
+                               scen = 'ChildPovertyReduction')
+priority_subgroup_plot(priority_group = 'mother_under_25',
+                               scen = 'ChildPovertyReduction')
+priority_subgroup_plot(priority_group = 'three_plus_children',
+                               scen = 'ChildPovertyReduction')
+```
+
 ```{r "Data", include=FALSE}
@@
 
-Results disaggregated by if household belongs to 0, 1, 2, 3+ priority subgroups.
+Results disaggregated by if household belongs to 0, 1, 2+ priority subgroups.
 

### 2025-01-17 docsrc/documentation/notebooks/household_income.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

--- 2023-01-05 docsrc/documentation/notebooks/household_income.Rmd
@@
 bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
-  #- "../../refs.bib" # useful for debugging.
+  - "`r here::here('docsrc', 'refs.bib')`" # finally figure out how to combine these for debugging and actual 
 ---
 
-```{r setup, include=FALSE}
-source('sphinx_notebook_utils.R')
+```{r load_data, include=FALSE}
+library(here)
+source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
+model_path <- here::here("data", "transitions", "hh_income", "glmm", "hh_income_new_GLMM.rds")
+model <- readRDS(model_path)
+
+obs <- model@frame$hh_income
+preds <- predict(model, type='response')
+v <- "hh_income"
 ```
@@
 ```{r, hh_income_data}
-continuous_density("hh_income")  
+continuous_density(obs)  
 ```
@@
 options(width=120)
-ols_output("../../../data/transitions/test/hh_income_2018_2019.rds")
-ols_histogram("../../../data/transitions/test/hh_income_2018_2019.rds", "hh_income_next")  
+continuous_densities(obs, preds, v)
+print(summary(model))
+plot(model)
 ```

### 2025-01-17 docsrc/documentation/notebooks/neighbourhood.Rmd

--- 2023-01-05 docsrc/documentation/notebooks/neighbourhood.Rmd
@@
 bibliography: 
-  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
-  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
+  - "`r here::here('docsrc', 'refs.bib')`"
+
 ---
+
+```{r setup, include=FALSE}
+library(here)
+library(glmnet)
+library(plyr)
+
+source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
+model_path <- here::here("data", "transitions", "neighbourhood_safety", "rfo", "neighbourhood_safety_RFO.rds")
+model <- readRDS(model_path)
+
+data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
+obs <- data$neighbourhood_safety
+data$neighbourhood_safety_last <- data$neighbourhood_safety
+
+preds <- ranger::predictions(stats::predict(model, data))
+column_names <- colnames(preds)
+preds <-glmnet::rmult(preds)
+preds <- plyr::mapvalues(preds, from=c(1,2,3), to= column_names)
+v <- " neighbourhood_safety"
+
+```
 
@@
 
-```{r neighbourhood_setup, include=FALSE}
-source('sphinx_notebook_utils.R')
-```
-
 ### Methods
@@
 ```{r neighbourhood_barchart, echo=FALSE}
-print(table(real_data$neighbourhood_safety))
-discrete_barplot("neighbourhood_safety")
-getwd()
+discrete_barplot(obs, 'neighbourhood_safety')
 ```
@@
 options(width=120)
-clm_barplot("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds", "neighbourhood_safety_next")
-clm_output("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds")
+discrete_barplot2(obs, preds, "neighbourhood_safety") 
+rfo_output(model)
 ```

### 2025-01-23 minos/outcomes/spatial_analysis.Rmd
grepping sf12 to sf12mcs

@@
 # 
-# ggplot(full_pop_data, aes(x = SF_12, colour = is_green)) +
+# ggplot(full_pop_data, aes(x = SF_12_MCS, colour = is_green)) +
 #   geom_density()
-# ggsave(here::here("plots","EPCG_SF_12.pdf"), plot=last_plot())
+# ggsave(here::here("plots","EPCG_SF_12_MCS.pdf"), plot=last_plot())
 # 
@@
 
-<!-- baseline_2025 <- baseline_2025[, c("hh_income", "SF_12", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->
-<!-- epcg_2025 <- epcg_2025[, c("hh_income", "SF_12", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->
+<!-- baseline_2025 <- baseline_2025[, c("hh_income", "SF_12_MCS", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->
+<!-- epcg_2025 <- epcg_2025[, c("hh_income", "SF_12_MCS", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->
 
@@
 
-<!-- ggplot(plot_data, aes(x = SF_12, colour = group)) + -->
+<!-- ggplot(plot_data, aes(x = SF_12_MCS, colour = group)) + -->
 <!--   geom_density() -->

### 2025-01-23 minos/validation/handovers_inflated.Rmd
grepping sf12 to sf12mcs

@@
 # sf12 boxplot handovers
-handover_boxplots(raw.dat, base.dat, 'SF_12')
-handover_lineplots(raw.dat, base.dat, "SF_12")
+handover_boxplots(raw.dat, base.dat, 'SF_12_MCS')
+handover_lineplots(raw.dat, base.dat, "SF_12_MCS")
 # 
 # raw.sf12 <- raw.dat %>% 
-#   dplyr::select(pidp, time, SF_12) %>%
+#   dplyr::select(pidp, time, SF_12_MCS) %>%
 #   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
 #   mutate(source = 'final_US')
@@
 # base.sf12 <- base.dat %>%
-#   dplyr::select(pidp, time, SF_12) %>%
+#   dplyr::select(pidp, time, SF_12_MCS) %>%
 #   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
 #   mutate(source = 'baseline_output')
@@
 # raw.sf12.2 <- raw.dat %>% 
-#   dplyr::select(pidp, time, SF_12) %>%
+#   dplyr::select(pidp, time, SF_12_MCS) %>%
 #   filter(pidp %in% raw.sf12.wave1) %>%
 #   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
 #   mutate(source = 'final_US')
@@
 # base.sf12.2 <- base.dat %>%
-#   dplyr::select(pidp, time, SF_12) %>%
+#   dplyr::select(pidp, time, SF_12_MCS) %>%
 #   filter(pidp %in% raw.sf12.wave1) %>%
 #   group_by(time) %>%
-#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
+#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
 #   mutate(source = 'baseline_output')
@@
 sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
-spaghetti_plot(sf12.spag.sample, 'SF_12',
+spaghetti_plot(sf12.spag.sample, 'SF_12_MCS',
                save = shall.we.save,
                save.path = save.path)
-spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
+spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_MCS',
                save = shall.we.save,
@@
 
-density_ridges(sf12.spag, "SF_12", 
+density_ridges(sf12.spag, "SF_12_MCS", 
                save = T, 

### 2025-01-23 minos/validation/interventions.Rmd
grepping sf12 to sf12mcs

--- 2023-06-15 minos/validation/interventions.Rmd
@@
 ```
-## SF_12
+## SF_12_MCS
 ```{r}
 sf12.base <- base %>% 
-  select(pidp, time, SF_12)
+  select(pidp, time, SF_12_MCS)
 sf12.energy <- energy %>% 
-  select(pidp, time, SF_12, income_boosted)
+  select(pidp, time, SF_12_MCS, income_boosted)
 # first rename and cbind
-sf12.b <- rename(sf12.base, base = SF_12)
-sf12.e <- rename(sf12.energy, energy = SF_12)
+sf12.b <- rename(sf12.base, base = SF_12_MCS)
+sf12.e <- rename(sf12.energy, energy = SF_12_MCS)
 sf12.merged <- merge(sf12.b, sf12.e, by=c('pidp', 'time'))
@@
                               names_to = 'scenario',
-                              values_to = 'SF_12')
+                              values_to = 'SF_12_MCS')
 sf12.merged.byyr <- sf12.merged %>%
   group_by(time, scenario) %>%
-  summarise(SF_12 = mean(SF_12))
-ggplot(data = sf12.merged.byyr, mapping = aes(x = time, y = SF_12, color=scenario)) +
+  summarise(SF_12_MCS = mean(SF_12_MCS))
+ggplot(data = sf12.merged.byyr, mapping = aes(x = time, y = SF_12_MCS, color=scenario)) +
   geom_line()
@@
 ```
+
+## Poverty Line Child Uplift
+
+```{r}
+income.base <- base %>% 
+  select(pidp, time, hh_income)
+income.poverty <- poverty %>% 
+  select(pidp, time, hh_income, income_boosted)
+# first rename and cbind
+income.b <- rename(income.base, base = hh_income)
+income.e <- rename(income.poverty, poverty = hh_income)
+income.merged <- merge(income.b, income.e, by=c('pidp', 'time'))
+income.merged <- pivot_longer(data = income.merged,
+                              cols = base:poverty,
+                              names_to = 'scenario',
+                              values_to = 'hh_income')
+income.merged.byyr <- income.merged %>%
+  group_by(time, scenario) %>%
+  summarise(hh_income = mean(hh_income))
+ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
+  geom_line()
+```
+## SF_12_MCS
+```{r}
+sf12.base <- base %>% 
+  select(pidp, time, SF_12_MCS)
+sf12.poverty <- poverty %>% 
+  select(pidp, time, SF_12_MCS, income_boosted)
+# first rename and cbind
+sf12.b <- rename(sf12.base, base = SF_12_MCS)
+sf12.e <- rename(sf12.poverty, poverty = SF_12_MCS)
+sf12.merged <- merge(sf12.b, sf12.e, by=c('pidp', 'time'))
+sf12.merged <- pivot_longer(data = sf12.merged,
+                              cols = base:poverty,
+                              names_to = 'scenario',
+                              values_to = 'SF_12_MCS')
+sf12.merged.byyr <- sf12.merged %>%
+  group_by(time, scenario) %>%
+  summarise(SF_12_MCS = mean(SF_12_MCS))
+ggplot(data = sf12.merged.byyr, mapping = aes(x = time, y = SF_12_MCS, color=scenario)) +
+  geom_line()
+```
+
+## Boost Amount
+```{r}
+income.poverty <- poverty %>% 
+  select(pidp, time, hh_income, income_boosted, boost_amount)
+income.poverty.byyr <- income.poverty %>%
+  group_by(time) %>%
+  summarise(boost_amount = mean(boost_amount))
+ggplot(data = income.poverty.byyr, mapping = aes(x = time, y = boost_amount)) +
+  geom_line()
+```
+## Who Boosted?
+
+```{r}
+boosted.byyr <- income.poverty %>% 
+  group_by(time) %>%
+  count(income_boosted)
+ggplot(data = filter(boosted.byyr, income_boosted == 'True'), mapping = aes(x = time, y = n)) +
+  geom_line()
+```

### 2025-01-23 minos/data_generation/US_MICE_imputation.R

@@ -26,8 +26,8 @@ main <- function(n_imputations, iterations_per_imputation){
                     "ethnicity",
                     "loneliness",
                     "sex", 
-                    "SF_12",
-                    #"SF_12p",
+                    "SF_12_MCS",
+                    #"SF_12_MCSp",
                     #"smoker",
                     "nkids",       
                     "behind_on_bills",

### 2025-01-23 minos/longitudnial_visualisation.R

@@ -153,15 +153,15 @@ main <- function() {
   data4$time <- factor(data4$time)
   
   # spaghetti and violin plots over time for SF12
-  sf12_violin <- violin_plot(data, "SF_12")
-  sf12_spag <- spaghetti_plot(data, "SF_12")
+  sf12_violin <- violin_plot(data, "SF_12_MCS")
+  sf12_spag <- spaghetti_plot(data, "SF_12_MCS")
   
-  sf12_violin2 <- violin_plot(data2, "SF_12")
-  sf12_spag2 <- spaghetti_plot(data2, "SF_12")
+  sf12_violin2 <- violin_plot(data2, "SF_12_MCS")
+  sf12_spag2 <- spaghetti_plot(data2, "SF_12_MCS")
   
   # joint plots SF12 for two interventions together with colour groupings. 
-  joint_spaghetti_plot(data, data2, "SF_12", "baseline", "energy poverty")
-  #joint_violin_plot <- joint_violin_plot(data3, data2, "SF_12", "base", 'energy poverty measures')
+  joint_spaghetti_plot(data, data2, "SF_12_MCS", "baseline", "energy poverty")
+  #joint_violin_plot <- joint_violin_plot(data3, data2, "SF_12_MCS", "base", 'energy poverty measures')
   
   # Stacked barplots for discrete data. 
   #housing_barplot <- percent_barplot(data, "housing_quality", "Baseline")

### 2025-01-23 minos/modules/physical_wellbeing.py

@@ -183,8 +183,8 @@ class lmmYJPCS(Base):
                         'time',
                         'weight',
                         'hh_income',
-                        'SF_12',
-                        'SF_12_diff',
+                        'SF_12_MCS',
+                        'SF_12_MCS_diff',
                         'SF_12_PCS',
                         #'SF_12_PCS_diff',
                         'housing_quality',
@@ -214,7 +214,7 @@ class lmmYJPCS(Base):
         super().setup(builder)
 
         #only need to load this once for now.
-        #self.gee_transition_model = r_utils.load_transitions(f"SF_12/lmm/SF_12_LMM", self.rpy2_modules, path=self.transition_dir)
+        #self.gee_transition_model = r_utils.load_transitions(f"SF_12_MCS/lmm/SF_12_MCS_LMM", self.rpy2_modules, path=self.transition_dir)
         #self.gee_transition_model = r_utils.load_transitions(f"SF_12_PCS/glmm/SF_12_PCS_GLMM", self.rpy2_modules, path=self.transition_dir)
         #self.gee_transition_model = r_utils.load_transitions(f"SF_12_PCS/lmm/SF_12_PCS_LMM", self.rpy2_modules,
         #                                                     path=self.transition_dir)
@@ -269,7 +269,7 @@ class lmmYJPCS(Base):
         self.population_view.update(newWavePWB[['SF_12_PCS']])#, "SF_12_PCS_diff"]])
 
     def calculate_pwb(self, pop):
-        """Calculate SF_12 transition distribution based on provided people/indices
+        """Calculate SF_12_MCS transition distribution based on provided people/indices
         Parameters
         ----------
             index : pd.Index

### 2025-01-23 minos/outcomes/QALY_calculation.py

@@ -68,8 +68,8 @@ def aggregate_csv(filename, intervention, year, start_year, subset_func_string=N
     # drop dead people before calculating outcomes
     df = df[df['alive'] != 'dead']
 
-    # adjust SF_12 values by sampling weight
-    #df['SF_12'] = (df['SF_12'] * ((1 / df['weight']) / df['weight'].sum()))
+    # adjust SF_12_MCS values by sampling weight
+    #df['SF_12_MCS'] = (df['SF_12_MCS'] * ((1 / df['weight']) / df['weight'].sum()))
     #df['SF_12_PCS'] = (df['SF_12_PCS'] * ((1 / df['weight']) / df['weight'].sum()))
 
     # record boost information for intervention runs, set to 0 for baseline
@@ -85,7 +85,7 @@ def aggregate_csv(filename, intervention, year, start_year, subset_func_string=N
         pop_boosted = df['income_boosted'].sum()
         total_boost = df.groupby(by=['hidp'])['intervention_cost'].max().sum() # TODO group by households, take max and sum.
 
-    return [run_id, alive_pop, dead_pop, total_pop_size, pop_boosted, total_boost, alive_ratio, np.nanmean(df['SF_12']), np.nanmean(df['SF_12_PCS'])]
+    return [run_id, alive_pop, dead_pop, total_pop_size, pop_boosted, total_boost, alive_ratio, np.nanmean(df['SF_12_MCS']), np.nanmean(df['SF_12_PCS'])]
 
 
 def calculate_qaly(df):
@@ -111,10 +111,10 @@ def calculate_qaly(df):
     # First calculate utility score using values table 4 from Lawrence and Fleishman (2004)
     df['utility'] = -1.6984 + \
         (df['SF_12_PCS'] * 0.07927) + \
-        (df['SF_12'] * 0.02859) + \
-        ((df['SF_12_PCS'] * df['SF_12']) * -0.000126) + \
+        (df['SF_12_MCS'] * 0.02859) + \
+        ((df['SF_12_PCS'] * df['SF_12_MCS']) * -0.000126) + \
         ((df['SF_12_PCS'] * df['SF_12_PCS']) * -0.00141) + \
-        ((df['SF_12'] * df['SF_12']) * -0.00014) + \
+        ((df['SF_12_MCS'] * df['SF_12_MCS']) * -0.00014) + \
         ((df['SF_12_PCS'] * df['SF_12_PCS'] * df['SF_12_PCS']) * 0.0000107)
 
[…]

### 2025-02-17 docsrc/documentation/notebooks/replenishment.Rmd
Updated pathway docs files

## Replenishment

### Rationale

In order to run the model beyond the length of the Understanding Society data 
(11 waves, currently from 2009 - 2020), we needed to generate a replenishing population
that would maintain the age structure, as well as being representative of the British
population into the future in terms of sex and ethnicity.

### Data Sources

Counts by age, sex, and year were generated for 2008 - 2070 from 2 sources:
1. National Midyear estimates for 2008 - 2020
   1. These were obtained using the [nomisweb data query tool](https://www.nomisweb.co.uk/)
2. Principal Population Projections (PPP) for 2021 - 2070
   1. [Principal Population Projections](https://www.ons.gov.uk/peoplepopulationandcommunity/populationandmigration/populationprojections/datasets/z1zippedpopulationprojectionsdatafilesuk)

Counts by ethnic group were obtained from a previous project involving Nik Lomax called Ethpop. 
These were counts by ethnic group by age and LAD, which were summed to generate national level
counts of ethnicity by single year of age. See [this link for more information about ethpop](https://reshare.ukdataservice.ac.uk/852508/).

### Method

What we did to ensure that the simulation maintains the age structure of the data moving into the 
future, was to begin with a population derived from a single year of understanding society (we 
picked 2018). The replenishing population is also derived from US 2018, but instead takes just the 
16 year olds. Each year in the simulation, every simulant is transformed and ages by 1 year, which
means the 16 year olds at time t will be 17 at time t+1, meaning there are no 16 year olds in the
simulation. We then take the 16 year olds from the replenishing population, which have been 
reweighted to be representative for that year by sex and age (see below) and add them into the 
simulation to replace the 16 year olds that have aged.

### Reweighting

As part of the data generation pipeline, we take the final_US datafiles (after a number of
pre-processing and imputation steps) and use them to generate both the starting and 
replenishing populations. The model begins with a population derived from Understanding Society 
in 2018 (wave 9), from which the analysis weights provided by the survey are then modified based
on the counts from both the age-sex projections and the counts by ethnicity. Replenishing populations
are also derived from US wave 9, where we take all 16 year olds from wave 9, duplicate them for
every year from 2009 - 2070, and reweight these populations by age, sex, and ethnicity.
The actual reweighting calculation is very simple:

```
new_weight = (old_weight * count_by_group) / total_weight_by_group
```

### Complication

A slight complication to this method of replenishing is that education states now have to be 
transformed over time in the model. This is handled by the Education module, which is described
on a different page.

### 2025-03-10 minos/validation/cross_validation_default.Rmd

@@
 # cv simulation batches
-cv.simul.files1 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch1'),
+cv.simul.files1 <- list.files(here::here('data', 'imputed_final_US', 'cross_validation', 'batch1'),
                              pattern = '[0-9]{4}_US_cohort.csv',
@@
 raw1 <- do.call(rbind, lapply(cv.simul.files1, read.csv))
-cv.simul.files2 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch2'),
+cv.simul.files2 <- list.files(here::here('data', 'imputed_final_US', 'cross_validation', 'batch2'),
                              pattern = '[0-9]{4}_US_cohort.csv',
@@
 raw2 <- do.call(rbind, lapply(cv.simul.files2, read.csv))
-cv.simul.files3 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch3'),
+cv.simul.files3 <- list.files(here::here('data', 'imputed_final_US', 'cross_validation', 'batch3'),
                              pattern = '[0-9]{4}_US_cohort.csv',
@@
 raw3 <- do.call(rbind, lapply(cv.simul.files3, read.csv))
-cv.simul.files4 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch4'),
+cv.simul.files4 <- list.files(here::here('data', 'imputed_final_US', 'cross_validation', 'batch4'),
                              pattern = '[0-9]{4}_US_cohort.csv',
@@
 raw4 <- do.call(rbind, lapply(cv.simul.files4, read.csv))
-cv.simul.files5 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch5'),
+cv.simul.files5 <- list.files(here::here('data', 'imputed_final_US', 'cross_validation', 'batch5'),
                              pattern = '[0-9]{4}_US_cohort.csv',
@@
 
-# SF_12_MCS
+# SF_12
 
 ```{r}
-cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12_MCS')
-multi_year_boxplots(raw, cv, 'SF_12_MCS')
-snapshot_OP_plots(raw, cv, 'SF_12_MCS', target.years = c(2015, 2017, 2019, 2021))
-q_q_comparison(raw, cv, 'SF_12_MCS')
+cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12')
+multi_year_boxplots(raw, cv, 'SF_12')
+snapshot_OP_plots(raw, cv, 'SF_12', target.years = c(2015, 2017, 2019, 2021))
+q_q_comparison(raw, cv, 'SF_12')
 ```
@@
                                  predicted = cv, 
-                                 var = 'SF_12_MCS', 
+                                 var = 'SF_12', 
                                  target.year = 2015)
@@
                                  predicted = cv, 
-                                 var = 'SF_12_MCS', 
+                                 var = 'SF_12', 
                                  target.year = 2017)
@@
                                  predicted = cv, 
-                                 var = 'SF_12_MCS', 
+                                 var = 'SF_12', 
                                  target.year = 2019)
@@
                                  predicted = cv, 
-                                 var = 'SF_12_MCS', 
+                                 var = 'SF_12', 
                                  target.year = 2021)
